### 2009-04-16 notes/simulation_outline.tex
initial commit

%% LyX 1.5.3 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{amsmath}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

\usepackage{babel}
\makeatother

\begin{document}

\section*{Brief simulation - Gray Calhoun}

\subsection*{DGP and Forecasts}

The DGP is a trivariate AR(1):\begin{align*}
x_{t} & =0.3\cdot x_{t-1}+\varepsilon_{1t}\\
y_{t} & =0.1\cdot y_{t-1}+\varepsilon_{2t}\\
z_{t} & =0.3\cdot z_{t-1}+\varepsilon_{3t}\\
\left(\begin{array}{c}
\varepsilon_{1t}\\
\varepsilon_{2t}\\
\varepsilon_{3t}\end{array}\right) & \sim N\left(\mathbf{0},\mathbf{I}_{3}\right).\end{align*}
I construct two models to predict $y_{t}$. The first uses $x_{t-1}$
as the only predictor, the second uses four lags of $y_{t}$ and $z_{t}$
as predictors:

\begin{align}
\hat{y}_{1t}\left(\alpha\right) & =\alpha_{0}+\alpha_{1}x_{t-1}\label{eq:model1}\\
\hat{y}_{2t}(\beta) & =\beta_{0}+\beta_{1}z_{t-1}+\beta_{2}z_{t-2}+\beta_{3}z_{t-3}+\beta_{4}z_{t-4}\nonumber \\
 & \quad+\beta_{5}y_{t-1}+\beta_{6}y_{t-2}+\beta_{7}y_{t-3}+\beta_{8}y_{t-4}.\label{eq:model2}\end{align}

\subsection*{Test Statistic and Details}

We're interested in the behavior of \begin{equation}
\Delta\left(\hat{\alpha}_{R},\hat{\beta}_{R}\right)/\hat{\sigma}\left(\hat{\alpha}_{R},\hat{\beta}_{R}\right)\label{eq:teststat}\end{equation}
where $\hat{\alpha}_{R}$ and $\hat{\beta}_{R}$ are the OLS estimates
of the unknown coefficients in \eqref{eq:model1} and \eqref{eq:model2}
that use only the first $R$ observations in the data set. The random
functions $\bar{\Delta}$ and $\hat{\sigma}$ are defined as usual
-- $\bar{\Delta}$ is the pseudo-out-of-sample average,\[
\bar{\Delta}\left(\alpha,\beta\right)\equiv\frac{1}{P}\sum_{s=R+1}^{R+P}\left[\left(y_{s}-\hat{y}_{1s}\left(\alpha\right)\right)^{2}-\left(y_{s+1}-\hat{y}_{2s}\left(\beta\right)\right)^{2}\right],\]
and $\hat{\sigma}^{2}$ is a prewhitened Newey-West HAC estimator
of the variance of $\bar{\Delta}$. I generate 300 random samples
for each combination of $R$ and $P$ with $R$ taking the values
80, 240, and 480 and $P$ the values 40, 80, 240, and 480.

\subsection*{Size of West's Test Statistic}

West's theory implies that we could use the statistic \eqref{eq:teststat}
to test the null hypothesis\begin{equation}
H_{0}:\quad E\left(\left(y_{t}-\hat{y}_{1t}\left(\alpha^{*}\right)\right)^{2}\right)\geq E\left(\left(y_{t}-\hat{y}_{2t}\left(\beta^{*}\right)\right)^{2}\right)\label{eq:null}\end{equation}
against the one-sided alternative\[
H_{a}:\quad E\left(\left(y_{t}-\hat{y}_{1t}\left(\alpha^{*}\right)\right)^{2}\right)<E\left(\left(y_{t}-\hat{y}_{2t}\left(\beta^{*}\right)\right)^{2}\right),\]
where $\alpha^{*}$ and $\beta^{*}$ are the pseudo-true values for
models \eqref{eq:model1} and \eqref{eq:model2}. Since \eqref{eq:null}
is true for our DGP, we should expect that the statistic \eqref{eq:teststat}
would be less than $-1.288$ in fewer than $10\%$ of the simulations.
Table 1 lists the percent that were less than that value. Even for
rather large values of $P$ and $R$ the size is pretty bad.

\subsection*{Two Tables Supporting my Theory}

Since the theory I'm working on suggests that we should not focus
on the null hypothesis \eqref{eq:null}, we can't compare the size
directly. My theory implies that a better approximation is\begin{equation}
\left[\bar{\Delta}\left(\hat{\alpha}_{R},\hat{\beta}_{R}\right)-\mu\left(\hat{\alpha}_{R},\hat{\beta}_{R}\right)\right]/\hat{\sigma}\left(\hat{\alpha}_{R},\hat{\beta}_{R}\right)\xrightarrow{d}N\left(0,1\right)\label{eq:calrv}\end{equation}
with\[
\mu\left(\alpha,\beta\right)\equiv E\left[\left(y_{t}-\hat{y}_{1t}\left(\alpha\right)\right)^{2}-\left(y_{t}-\hat{y}_{2t}\left(\beta\right)\right)^{2}\right].\]
 For comparison, we can look at the number of simulations in which
the random variable in \eqref{eq:calrv} is less than the nominal
$10\%$ quantile, $-1.288$. Those percentages are listed in Table
2 and are close to the nominal level.

Finally, my approach also indicates that the random variable \begin{equation}
\frac{\bar{\Delta}\left(\hat{\alpha}_{R},\hat{\beta}_{R}\right)-\mu\left(\hat{\alpha}_{T},\hat{\beta}_{T}\right)}{\hat{\sigma}\left(\hat{\alpha}_{R},\hat{\beta}_{R}\right)}\label{eq:rv2}\end{equation}
should be standard normal if $P^{2}/R$ converges to zero as $P,R\to\infty$.
Table 3 gives the relevant quantiles for that random variable and
seems consistent with the theory.

%
\begin{table}[p]
\caption{West Statistic, Percentage of simulations less than nominal 0.10 quantile}

\begin{tabular}{cccccc}
 &  & \multicolumn{4}{l}{P}\tabularnewline
 &  & 40 & 80 & 240 & 480\tabularnewline
R & 80 & 0.33 & 0.43 & 0.63 & 0.78\tabularnewline
 & 240 & 0.24 & 0.19 & 0.26 & 0.41\tabularnewline
 & 480 & 0.17 & 0.14 & 0.17 & 0.18\tabularnewline
\end{tabular}
\end{table}

%
\begin{table}[p]
\caption{My RV 1 (eq. 5)- Percentage of Simulations less than nominal 0.10
quantile}

\begin{tabular}{cccccc}
 &  & \multicolumn{4}{l}{P}\tabularnewline
 &  & 40 & 80 & 240 & 480\tabularnewline
R & 80 & 0.15 & 0.11 & 0.10 & 0.12\tabularnewline
 & 240 & 0.16 & 0.11 & 0.10 & 0.13\tabularnewline
 & 480 & 0.15 & 0.12 & 0.12 & 0.10\tabularnewline
\end{tabular}
\end{table}

%
\begin{table}[p]
\caption{My RV 2 (eq. 6) - Percentage of Simulations less than nominal 0.10
quantile}

\begin{tabular}{ccllcc}
 &  & \multicolumn{4}{l}{P}\tabularnewline
 &  & 40 & 80 & 240 & 480\tabularnewline
R & 80 & 0.24 & 0.31 & 0.54 & 0.75\tabularnewline
 & 240 & 0.20 & 0.17 & 0.25 & 0.46\tabularnewline
 & 480 & 0.16 & 0.15 & 0.20 & 0.26\tabularnewline
\end{tabular}
\end{table}

\end{document}

### 2009-04-16 paper/calhoun_fixed_window.tex
initial commit

\documentclass[11pt]{article} \def\baselinestretch{1.08}
\usepackage{amssymb,amsmath,amsthm,harvard,graphicx, color, enumerate}
\usepackage[T1]{fontenc} \setcounter{MaxMatrixCols}{10}

% -- Margins for Editing --
\setlength{\voffset}{0.22in} \setlength{\hoffset}{-0.06in}
\setlength{\topmargin}{0in} \setlength{\headheight}{0in}
\setlength{\headsep}{0in} \setlength{\textheight}{7.33in}
\setlength{\oddsidemargin}{0in} \setlength{\textwidth}{5.67in}

\newcommand{\pp}[1]{#1} \newcommand{\intro}[1]{#1}
\newcommand{\context}{} \newcommand{\problem}{} \newcommand{\sowhat}{}
\newcommand{\solution}{} \newcommand{\point}[1]{#1}

\renewcommand{\qedsymbol}{\ensuremath \blacksquare}

%\newcommand{\pp}[1]{\textbf{#1}}
%\newcommand{\intro}[1]{\textsc{#1}}
%\newcommand{\context}{\subsubsection*{Shared Context}}
%\newcommand{\problem}{\subsubsection*{Statement of Problem}}
%\newcommand{\sowhat}{\subsubsection*{So What?}} 
%\newcommand{\solution}{\subsubsection*{Statement of Solution}}
%\newcommand{\point}[1]{\subsubsection*{Key Point} {#1}}

\input{../bib/definitions} \input{def}
\begin{document}

\title{Limit Theory for Overfit Forecasts} \author{Gray Calhoun}
\maketitle

\begin{abstract}
This paper proposes a new limit theory for statistics that evaluate
estimated models out-of-sample.  This theory implies out-of-sample
averages are asymptotically normal even when the models are nested and
are valid even when the models are overfit.  We introduce overfit by
assuming that the forecasts are produced by 
linear models and allowing the number of predictors, $K$, to increase
with the number of observations, $T$.  For at least one forecast, the
ratio $K/T$ converges to a positive constant, so in-sample statistics,
like the F-test, fail but, as we show, out-of-sample averages do not.
\end{abstract}
%%
\section{Introduction} 
%%
\context 
\intro{Consider two sequences of prediction errors, each of
  length $P$, the result of forecasting the same variable with two
  different estimated models.  The $R$ observations used to estimate
  the models are called, collectively, the estimation window, and the
  $P$ observations used to produce the errors are called the test
  sample.  There are $T$ observations in all, and $R + P = T$.
  \pp{This paper introduces a new asymptotic theory for the sample
  moments of these prediction errors that assumes at least one model
  is overfit, that statistics calculated from that model's sample
  residuals are unreliable because its estimated coefficients match
  the data too well.}}

If one of these models nests the other, a researcher can determine
whether the additional regressors help predict the dependent variable
(in population) by using one of two representative methods.  He or she
can run a regression over the full dataset and use a robust F-test to
directly test whether the coefficients on the extra predictors equal
zero.  Or he or she could instead produce a series of forecasts with each
model, and then test whether the models' predictive mean squared errors
(PMSE) are equal.  The first test is simple and easy, and the second
test is not; \citeasnoun{clark_tests_2001} and
\citeasnoun{mccracken_asymptotics_2007} show that the test statistic 
is not asymptotically normal and that the critical values must be
calculated by monte-carlo or bootstrap.  But the out-of-sample test
is much more popular among forecasters because it is believed to be
more reliable: see \citeasnoun{meese_empirical_1983},
\citeasnoun{stock_forecasting_2003} and
\citeasnoun{lettau_consumption_2001} for prominent examples.

The asymptotic theory used to derive these out-of-sample
statistics, however, does not imply that they are any more reliable
than their in-sample counterparts.  There are two main approaches to
approximate these statistics' distributions.  The first, begun by
\citeasnoun{diebold_comparing_1995} and
\citeasnoun{west_asymptotic_1996} and extended to nested models by
\citeasnoun{clark_tests_2001}, \citeasnoun{chao_out_2001},
\citeasnoun{corradi_consistent_2002}, and
\citeasnoun{mccracken_asymptotics_2007}, finds the limit distribution
as though all of values of the models' coefficients were known, and
then adjusts that distribution to account for estimation
error.\footnote{Diebold and Mariano (1995) assume that the
  coefficients are known.  West (1996) 
  introduces the adjustment.} This adjustment requires the estimated
coefficients to be consistent and asymptotically normal.  But if they
were, a forecaster could instead just use an F-test directly on the
coefficients.

The second method, proposed by \citeasnoun{giacomini_tests_2006}, is
becoming a popular alternative to
\possessivecite{west_asymptotic_1996} 
approach because it always
gives an asymptotically normal statistic.  Their method
requires that the forecaster use a fixed-length rolling estimation
window --- the model for each forecast is estimated over the
previous $R$ observations --- and they derive a statistic to test
whether the difference between the models' forecasts is 
predictable.\footnote{Although \citeasnoun{giacomini_tests_2006} claim that
  their results also apply to fixed-length fixed window schemes, their
  proofs do not apply to that situation.  For a rolling window of
  length $R$, the period-$s$ prediction error only depends on the
  observations of period $s-R-1$ through period $s$, and so, for any 
  finite $R$, this sequence inherits mixing from the underlying
  observations.  But for a fixed window of length $R$, the
  period-$s$ prediction error depends on all of the past
  observations, periods $1$ through $s$, and so does not inherit
  mixing  from the underlying observations. Giacomini and White's
  proofs  require the prediction errors to be mixing.}
This rolling window can be appropriate if the series exhibit
substantial instability, so \possessivecite{giacomini_tests_2006}
out-of-sample 
statistic should be reliable in settings where an in-sample statistic
is not.  But, by its nature, their statistic measures the forecasting
performance of the estimated models, and does not reflect the
predictive content of their variables in population.  So Giacomini and
White's method suggests a new criterion to use to choose between
forecasting methods, but does not indicate why a researcher who wants
to study the true relationship between several series should use an
out-of-sample statistic.

Although the foundation of West's approach --- asymptotic
normality of the coefficient estimates --- implies that in-sample
and out-of-sample statistics should behave similarly, in practice they
do not.  \citeasnoun{stock_forecasting_2003}, for example, show that
in-sample tests of Granger Causality are much more likely to find
predictive relationships when predicting output and inflation than
out-of-sample tests. As \citeasnoun{inoue_in-sample_2005} argue, this
fact can support either approach: either the in-sample tests do not
preserve size, or the out-of-sample tests have low power.  The monte
carlo evidence is mixed.\footnote{This issue has been studied both
  analytically and in simulations by
  \citename{inoue_in-sample_2005} (\citeyear*{inoue_in-sample_2005},
  \citeyear*{inoue_selection_2006}),
  \citeasnoun{mccracken_data_1998}, \citeasnoun{clark_can_2004}, 
  \citeasnoun{clark_power_2005}, and \citeasnoun{chen_note_2005}.}

\solution
\intro{This paper introduces a new approximation for out-of-sample
  sample averages
  that does not require the coefficient estimates to be consistent or
  asymptotically normal.  This approximation allows us to study the
  behavior of out-of-sample statistics when one of the models is
  overfit, and we find that these statistics can be reliable even when
  in-sample statistics are not.  We impose overfit by studying
  the limit distribution of a sequence of linear regression models in
  which the ratio $K/T$ remains positive; $K$ is the number of
  predictors.  \citeasnoun{huber_robust_1973} shows that the OLS
  estimators are not asymptotically normal under this limit theory and
  that they have positive variance in the limit, so robust F-tests
  should be invalid. \pp{This new approximation
    gives evidence that the out-of-sample average loss is a reliable
    statistic for comparing complex, overfit models to a simple
    benchmark and that ad hoc critical values, such as
    \possessivecite{clark_tests_2001}, are not necessary; using the
    standard normal critical values gives valid but conservative
    tests.  The approximation also leads to a new criterion to use to
    evaluate a model's expected forecasting performance.}}

\pp{This increasing-dimension asymptotic theory is discussed in detail
  in Sections \ref{sec_asmp} and \ref{sec_lit}.}  Section
  \ref{sec_asmp} presents the notation, assumptions, and models that
  the rest of the paper will use, and Section \ref{sec_lit} studies
  the behavior of \possessivecite{west_asymptotic_1996} approximation
  under this new limit theory.  West's asymptotic distribution no
  longer holds because the
  test statistics are not centered on the expected loss of the
  pseudo-true models. Section \ref{sec_lit} also presents the results
  of a brief  
simulation demonstrating that conventional fixed-$K$ asymptotic theory
can be inaccurate in finite samples when $K/T$ is as small $0.03$.

\pp{Section \ref{sec_mr} presents our new approximation.}  
The fixed-window average loss converges to a measure of the expected
performance of the estimated models and is asymptotically normal
in most applications. Section \ref{sec_nested} shows that this average
can be used to compare nested models when the larger model is overfit, and that
using standard normal critical values leads to an asymptotically valid
(if conservative) test statistic.

Section \ref{sec_perf} discusses the relationship between the
models' average loss and their future forecasting performance and
 shows that the conventional wisdom articulated by
 \citeasnoun{hastie_elements_2003} among others, that one should split
 the dataset in  half or in thirds is wrong: to estimate a model's
 future performance (under this paper's limit theory) $P/T$ must
 converge to zero and to construct a confidence interval, $P^2/T$ must
 converge to zero.

\pp{Section \ref{sec_mc} presents additional simulations.  The first
  simulation examines the size and power of naive one-sided tests for
  nested models and confirms that the true size is less than the
  nominal size.  The second simulation studies the use of the
  fixed-window average loss as a decision criterion for choosing a
  forecast.}

\point{
In short, this paper studies out-of-sample averages to see if they are
more robust to overfit than in-sample statistics and finds that they
are.  It shows that using a one-sided t-test to compare nested models
is conservative but preserves size as long as the benchmark is simple,
consistent with simulations presented in
\citeasnoun{clark_approximately_2007} but in 
contrast to existing theory.  It also shows that the test sample must
be much smaller than is commonly used if one hopes to accurately
compare the performance of the full-sample models that will be used to
produce real forecasts.} 
%%
\section{Notation and Assumptions} \label{sec_asmp}  
%%
This paper does not define a specific data generating process but
instead assumes that there are two competing forecasting models and both 
are misspecified.
\pp{The underlying data are represented as a stationary and absolutely
  regular stochastic array:
  \begin{equation} \label{eq_define_array}
  \{(\yT{t}, \xT{1}{t}, \xT{2}{t});\;t = 1,\dotsc,T+1;\;T\;\text{an integer}\},
  \end{equation}
and $\FT{t}$ denotes the information available in period $t$:
\[
\FT{t} \equiv \sigma(\yT{1},\xT{1}{1},\xT{2}{1},\dotsc,
\yT{t},\xT{1}{t},\xT{2}{t}).
\]}
The first model uses $\xT{1}{t}$ as predictors for $\yT{t}$ and the second
uses $\xT{2}{t}$. Each vector $\xT{j}{s}$ has $K_{jT}$ elements;
$K_{jT}$ can change with $T$, but is always assumed to be less than
$R_T$ (the sequence of estimation window sizes, $\{R_T\}$,
will be discussed in detail later in the paper).  Moreover,
$T$ and $R_T$ are implicitly assumed to be large enough that all of
the operations in this paper are well defined.  To keep the
presentation relatively clean, the $T$ subscript will be removed
whenever possible.  Although we only present results for one-period
forecasts, these results can be generalized easily to multi-period
forecasts.

Assumption \ref{asmp_array} states the moment and dependence conditions
that the array \eqref{eq_define_array} must satisfy.
\begin{asmp} \label{asmp_array}
  The random array \eqref{eq_define_array} 
  is stationary and absolutely regular with coefficients $\beta_\tau$ of
  size $- \rho/(\rho-2)$; $\rho$ is greater than two and discussed further
  in Assumption \ref{asmp_loss_bound}.  The variance of $\yT{t}$ is
  uniformly positive and finite, and all of the eigenvalues of the
  covariance matrices of $\xT{j}{T}$ are uniformly positive and finite
  as well. 
  \qed
\end{asmp}

Each forecast is produced by a linear model; \pp{model $j$'s forecast for 
  period $T+1$ is $\x{j}{T+1}'\b{j}{T}$, with $\b{j}{S}$ the OLS
  estimate using observations one through $S$.}
The models' pseudo-true coefficients are denoted
$\B{j}$ and defined by
\[
\BT{j} \equiv \argmin_\theta \E (\yT{T+1} - \xT{j}{T+1}'\theta)^2.
\]
Assumption \ref{asmp_pseudo_true} rules out the uninteresting cases
where the forecast error vanishes.
\begin{asmp} \label{asmp_pseudo_true}
  The Euclidean norm of the pseudo-true coefficients satisfies
  $|\BT{j}|_2 = O(1)$, and the population residuals,
  $\epT{j}{t} \equiv \yT{t} - \xT{j}{t}'\BT{j}$, have uniformly positive and finite
  variance.
\qed
\end{asmp}

\pp{Since this paper will apply limit theory to the average loss over the test
sample, the observed test sample loss satisfies moment restrictions.}
The observed loss for model $j$ in period $s$ is $\f{j}{s}$ which is 
defined by
\[
\f{j}{s} = L(\e{j}{t}) \equiv L(\y{s} - \x{j}{s}'\b{j}{R});
\]
$L$ is the loss function of interest.  The period-$s$ loss for the
forecast produced by model $j$'s pseudo-true coefficients is
$\ft{j}{s} \equiv L(\ep{j}{s})$,
and the period-$s$ loss for the forecast produced by the full-sample
estimates is
$\ff{j}{s} \equiv L(\y{s} - \x{j}{s}'\b{j}{T})$.

The vector $\el{}$ denotes the average loss of the estimated models
over the test sample: 
\[
\el{j} \equiv P^{-1} \sum_{s=R+1}^T \f{j}{s}.
\]
Assumption \ref{asmp_loss_bound} restricts the moments of $\f{}{s}$.
\begin{asmp}\label{asmp_loss_bound}
The loss function $L$ is convex and there is a constant $B_L$
such that $\|\fT{j}{s}\|_\rho \leq B_L$ for all $j$, $s$, and $T$.
Moreover, the function $\E L(\yT{T+1} -
\xT{j}{T+1}'\theta)$ is continuously differentiable in $\theta$.
\qed
\end{asmp}

Finally, $|\cdot|_v$ is the $l_v$-norm for vectors in $\R^p$ 
($p$ arbitrary) and $\|\cdot\|_v$ the $L_v$-norm for $L_v$-integrable 
random variables.  The functions $\lambda_i(\cdot)$ take a 
square matrix argument
and return its $i$th eigenvalue.  All limits are stated for 
$T\to\infty$ unless explicitly labeled otherwise.
%%
\section{Background} \label{sec_lit}
%%
\intro{A large sample does not guarantee the accuracy of an asymptotic 
result; other factors come into play, among them the complexity of the model
estimated.  \citetwo{clark_using_2006}{clark_approximately_2007} show
that parameter estimation error 
affects the analysis of nested models in practice, making
\possessivecite{west_asymptotic_1996} 
limit theory unreliable.  
\pp{This section shows that the same problems occur without nesting and
motivates the use of increasing-$K$ asymptotics as a method of studying
that estimation error formally.}}\footnote{For this section,
assume that there is only one model under consideration.}

\intro{\pp{It is natural to use sequences of models with $K/T$
    positive to study the failure of in-sample asymptotics}} because
\pp{applied researchers choosing between models routinely make adjustments
  that are proportional to $K/T$.}  Statisticians have proposed model 
selection criteria, such as Mallow's $C_p$
\cite{mallows_comments_1973}, the AIC, \cite{akaike_information_1973}
and cross validation, because a model's {\it apparent error}, its 
average loss over the dataset used to estimate its unknown
    coefficients, is a biased estimator of the expected loss one encounters after using that 
model to predict new observations. The bias is proportional to $K/T$,
and these criteria are estimated by correcting the apparent error by 
a term proportional to $K/T$ (see, for example,
    \citename{efron_biased_1986} \citeyear*{efron_biased_1986},
    \citeyear*{efron_estimation_2004}).

Moreover, \pp{since the variance of each element of $\b{}{T}$ is of
  order $T^{-1}$, the variance of this vector does not vanish if $K/T$
  remains positive.}  The behavior of M-estimators in this setting has
  been studied by Huber (1973), Yohai and Marona (1979), and Portnoy
  (1985, 1986).  If the coefficients are estimated by OLS, they are
  consistent and asymptotically normal only if $K/T$ converges to
  zero; if they are general M-estimates they require a faster rate of
  convergence.  By keeping $K/T$ positive, one can keep the variance
  of the coefficient estimates positive.  Since the coefficients are
  not asymptotically normal, the F-test is not necessarily
  asymptotically chi-square, so in-sample tests are unavailable.

  \intro{\pp{Expansions of $\el{}$ around the pseudo-true coefficients,
      like \possessivecite{west_asymptotic_1996} and
      \possessivecite{clark_tests_2001}, also do not hold when $K/T$ remains positive.}}
\pp{These approximations require that the coefficient
  estimates be root-$R$ consistent.} For a short illustration,
suppose that the underlying series are stationary; that the same
loss function is used to estimate the coefficients and evaluate
the forecasts; that $P$ and $R$ both equal $T/2$; and that a
fixed-window is used for evaluation.\footnote{These assumptions
  are not necessary, but simplify equation \eqref{eq_west}.} In this
special case, West's theory gives the approximation
\[
  P^{1/2} (\el{} - \E \ft{}{T+1})
  = P^{-1/2} \sum_{s=R+1}^T (\ft{}{s} - \E \ft{}{s})
  + o_p(R^{1/2} |\b{}{R} - \B{}|_2).
\]

Under conventional (fixed-$K$) asymptotic theory, $R^{1/2} |\b{}{R} -
\B{}|_2$ is tight, and the last term of the approximation converges to
zero in probability.  Then $P^{1/2}(\el{} - \E \ft{}{T+1})$ is
asymptotically normal as long as $P^{-1/2}\sum_s (\ft{}{s} - \E
\ft{}{s})$ is. But when $K$ grows proportionally to $T$, $R^{1/2}
|\b{}{R} - \B{}|_2$ is not tight. And since $\b{}{R}$ is not
asymptotically normal, the distribution of the remainder term is not
known.  In general, the variance of the fixed-window average remains
positive asymptotically, so $\el{}$ does not converge to any
non-random value.  Sections \ref{sec_mr} and \ref{sec_nested} will
explore this convergence in more detail.

\intro{In practice, $K/T$ will always be positive, so this discussion
indicates that West's approximation is unreliable unless this ratio is
close to zero, but it is not necessarily clear how small the ratio
must be to make West's results accurate.  \pp{Some brief simulations
  demonstrate that 
the size of his tests can be too high even when $K/T$ is as small as
$0.03$, and empirically relevant values of $K/T$ seem to be from
$0.01$ to about $0.2$.}} Economists are sometimes interested in
studying tightly parameterized models, but they are often interested
in larger structural models.  \possessivecite{meese_empirical_1983}
seminal study 
of exchange rate models, for example, includes some models for which
the $K/T$ is almost 0.3. More recently,
\citeasnoun{stock_forecasting_2003} 
consider a range of output and inflation forecasts with this ratio
between 0.01 and 0.08, and \citeasnoun{del_negro_fit_2007} study
Bayesian DSGE models for which it is roughly 0.15.

\begin{table}[!tb]
    \label{tab_mc1stat}
    \begin{center}
    \caption{Simulated Size.  Nominal size is 10\%}
    \begin{tabular}{rrr@{.}lr@{.}lr@{.}lr@{.}l}
      & P = & \multicolumn{2}{r}{40} & \multicolumn{2}{c}{80}
      & \multicolumn{2}{c}{120} & \multicolumn{2}{c}{160} \\ \hline
      R = 80 && 15&4 & 18&5 & 19&0 & 21&0 \\
      160 && 12&0 & 14&5 & 15&9 & 17&2 \\ {}
    \end{tabular}
    \end{center}
    {\small
      According to \possessivecite{west_asymptotic_1996} theory, the random variable
      \eqref{eq_mc1stat} is asymptotically standard normal.  Each cell
      lists the percentage of simulations for which that r.v. exceeds
      $1.282$, the $90\%$-quantile of the standard normal
      distribution.}
\end{table}

To see whether West's theory is accurate for these values of $K/T$, we
ran a brief monte-carlo experiment to study forecasting with a
bivariate VAR(4); $T$
ranges from $120$ to $320$, so $K/T$ is between $0.025$ and $0.075$.
\pp{The DGP is taken from \citeasnoun{clark_approximately_2007} and is designed to
  represent macroeconomic forecasting.} Each entry in Table 1
  is the simulated size of a test at the 10\%-level of
  the null hypothesis that the expected PMSE of the bivariate VAR(4) is
  less than or equal to its true value.  We ran 3000 simulations: for
  each simulation we drew 320 observations from the stationary process
  with independent innovations:
\begin{align*}
  y_t &= 2.237 + 0.261 y_{t-1} + \varepsilon_{1t} \\
  z_t &= (0.804, - 0.221, 0.226, - 0.205) \cdot (z_{t-1},\dotsc, z_{t-4})
  + \varepsilon_{2t} \\
  \varepsilon &\sim N\left(\boldsymbol{0}, \begin{pmatrix}
      10.505 & 1.036 \\ \cdot & 0.366
      \end{pmatrix}\right).
\end{align*}
For each $R$ and $P$, we constructed sequences of forecasts, $\hat
y_t$, $t = R+1,\dotsc, R+P$ from the bivariate VAR(4):
\begin{equation*}
  \hat y_t = \hat \alpha_0 + \sum_{j=1}^4 \hat \alpha_j y_{t-j} 
  + \sum_{j=1}^4 \hat \beta_j z_{t-j}
\end{equation*}
with the coefficients estimated recursively by OLS.

Each cell in Table 1 is the percentage of simulations for
which the random variable
\begin{equation} \label{eq_mc1stat}
P^{1/2} (\bar L - 10.505) / \hat \sigma
\end{equation}
is greater than $1.282$, with 
\[
\bar L \equiv P^{-1} \sum_{s=R+1}^{R+P} (y_s -\hat y_s)^2
\] 
and 
\[
\hat \sigma^2 \equiv (P-1)^{-1} \sum_{s=R+1}^{R+P} [(y_s -
\hat y_s)^2 - \bar L]^2.
\]
\pp{Under \possessivecite{west_asymptotic_1996} limit theory, this random variable is
  approximately standard normal, so each entry should be close to
  $10\%$; but the true size is higher, ranging from $12\%$ to $21\%$.} 
Since the parameter values of this simulation were chosen by Clark and West
(2007) to represent quarterly macroeconomic data, the values $R = 80$
and $P = 160$ roughly correspond to the common practice of estimating
forecasting models with pre-$1970$ data and assessing its performance
recursively from $1970$ on:\footnote{As in, for example, Stock and
  Watson (2003)} the true size is roughly twice the nominal size when
  testing this one-sided hypothesis with
such a procedure.  In general, increasing $P$ while keeping $R$
constant distorts the size more, suggesting that the variance of the
out-of-sample average decreases, but that the average is not centered at
$\E \ft{T+1}{}$.
%%
\section{The New Approximation} \label{sec_mr}
%%
Instead of using an expansion, we re-center each random sequence
$\{\f{}{s}\}$ by subtracting a random vector $\mmr{}$ from each term.
The new sequence is a mixingale, and $\mmr{}$ can be interpreted as a
conditional expectation after a change-of-measure.

\begin{lem} \label{lem_mixingale}
  Suppose that Assumptions \ref{asmp_array} to \ref{asmp_loss_bound}
  hold and define 
  \[
  \mmT{i}{\theta} \equiv \E L(\yT{T+1} - \xT{i}{T+1}'\theta).
  \]
  Then, for any $T$, any positive $j$, and any $\tau$ between zero and $j$,
  \begin{equation}
    \label{eq_mixingale_def}
    \| \E(\fT{i}{R_T+j} \mid \FT{R_T+j-\tau}) - \mmrT{i} \|_2 \leq 
     2^{1 + 1/\rho} B_L \; \zeta_{\tau}
  \end{equation}
  with $\zeta_\tau = O(\tau^{-1/2-\delta})$ for some positive
  $\delta$.  So the array 
  \[
  \{\fT{}{R_T+j} - \mmrT{}, \FT{R_T+j}\}
  \]
  is an $L_2$-mixingale array of size $-1/2$. 
  \qed
\end{lem}

The proof relies on a coupling argument due to
\citeasnoun{merlevede_coupling_2002} that builds on Berbee's Lemma
\cite{berbee_random_1979}.  \possessivecite{merlevede_coupling_2002}
statement of the Lemma is repeated here verbatim for reference.
\begin{BL}
  Let $X$ and $Y$ be random variables defined on $(\Omega, \mathcal T,
  \mathbb P)$ with values in a Polish space S.  Let $\sigma(X)$ be a
  $\sigma$-field generated by $X$ and $U$ be a random variable
  uniformly distributed on $[0,1]$ independent of $(X,Y)$.  Then there
  exists a random variable $Y^*$ measurable with respect to $\sigma(X)
  \vee \sigma(Y) \vee \sigma(U)$, independent of $X$ and distributed
  as $Y$, and such that
  \[
  \mathbb P(Y \neq Y^*) = \beta(X,Y).
  \] \qed
\end{BL}
The coefficient $\beta$ is the coefficient of absolute regularity.

\citeasnoun{merlevede_coupling_2002} use this result to bound the
$L_p$-norm of the distance between $Y$ and $Y^*$. We prove Lemma
\ref{lem_mixingale} by defining $(y^*, x^*)$ to satisfy:
\begin{enumerate}
\item $(y^*, x^*) \eqdist (\yT{R_T+j}, \xT{i}{R_T+j})$
\item $(y^*, x^*)$ is independent of $\FT{R_T+j-\tau}$.
\item $\p[(y^*, x^*) \neq (\yT{R_T+j}, \xT{i}{R_T+j})] = \beta_\tau$.
\end{enumerate}
Since $\mmrT{i} = \E(L(y^* - x^* \cdot \b{i}{R_T}) \mid
\FT{R_T+j-\tau})$ almost surely, the left side of
\eqref{eq_mixingale_def} is bounded by
\[
  \| \f{i}{R_T+j} - L(y^* - x^* \cdot \b{i}{R_T}) \|_2.
\]
We can directly use Merlevede and Peligrad's method of
proof to bound this last distance.

An immediate consequence of Lemma \ref{lem_mixingale} is that $\elT{i} -
\mmrT{i}$ converges to zero almost surely as $P_T$ increases.  We can
also show that $\sqrt{P_T} [\elT{} - \mmrT{}]$ is asymptotically
normal under a slightly stronger condition that its asymptotic
variance is positive definite.
\begin{lem} \label{lem_mixingale_normality}
  Suppose that the conditions of Lemma \ref{lem_mixingale} hold and that
  \[
  \lambda_{min}(\SrT)^{-1} = O_p(1),
  \] 
  with each element of $\ST{\cdot}$ defined by
  \[\left[\ST{(\theta_1,\theta_2)}\right]_{ij} \equiv P^{-1} \sum_{s,t=R+1}^T 
  \left[ \E L(\yT{s}-\xT{i}{s}'\theta_i) L(\yT{t}-\xT{j}{t}'\theta_j)
  - \mmT{i}{\theta_i} \mmT{j}{\theta_j}\right].
  \]
  If $P_T \to \infty$ as $T \to \infty$, then
  \begin{equation}
    P_T^{1/2} \SrT^{-1/2} \big[\elT{}  - \mmrT{}\big] \xrightarrow{d}
    N(0,I) \quad \text{as $T \to \infty$}. 
\end{equation}
\qed
\end{lem}
The proof is based on \possessivecite{de_jong_central_1997} Theorem 1,
a mixingale Central Limit Theorem.

This mixingale approximation allows us to work with sequences of
estimators that do not converge.  As in
\citeasnoun{giacomini_tests_2006}, such sequences can ensure that the
asymptotic variance matrix remains positive definite, even for nested
models.

It is useful to compare this approximation to
\possessivecite{mccracken_robust_2000}. McCracken assumes that the
estimators $\bT{}{R_T}$ are asymptotically normal and that the
function $\mmT{}{\cdot}$ is smooth enough that
\[
\sqrt{R_T} [\mmrT{i} - \mmmT{i}]
\]
is asymptotically normal as a consequence of the delta-method.  As a
result, he, like \citeasnoun{west_asymptotic_1996}, can apply a
central limit theorem to $P_T^{1/2} [\elT{} - \mmmT{}]$
and then adjust its covariance matrix to account for the difference
between $\mmrT{i}$ and $\mmmT{i}$.

Lemmas \ref{lem_mixingale} and \ref{lem_mixingale_normality} show that
we can apply a Central Limit Theorem directly to $P_T^{1/2} [\elT{} -
\mmrT{}]$.  This extra generality allows us to study how out-of-sample
averages perform when their models are estimated imprecisely.
However, we need to impose more restrictions before we can relate
$\mmrT{}$ to objects that a researcher should be interested in, such
as $\mmmT{}$.
%%
\section{Comparing Nested Models} \label{sec_nested}  
In most applications, the benchmark model is very simple (a random walk,
for example) so we can treat the smaller model as having fixed $K$.
Only the alternative model is complex.
In this case, we can construct a conservative one-sided test for the
null hypothesis that smaller model is more accurate (in terms of MSE)
in population.

\begin{thm}\label{thm_nesting1}
  Suppose that the conditions of Lemmas \ref{lem_mixingale} and
  \ref{lem_mixingale_normality} hold and that
  \begin{enumerate}
  \item[(i)] $K_{1T} = K_1$ and does not change with $T$; $K_{2T}/T \to
    k_2 > 0$; and $P_T/R_T \to \pi < \infty$. 
  \item[(ii)] $\hat \sigma_T$ is a consistent estimator of $(1,-1) \Sigma_T
    (1,-1)'$.
  \item[(iii)] Each of the smaller model's predictors is also used by
  the larger model (model two).
  \item[(iv)] $L(e) = e^2$.
  \end{enumerate}
  Then, under the null hypothesis
  \[
  H_0: \qquad \mT{1} = \mT{2} \qquad \text{for all $T$,}
  \]
  the one-sided t-test satisfies
  \begin{equation*}
    \lim_{T\to\infty} \p\Big[P_T^{1/2} (\elT{1} - \elT{2}) / \hat \sigma_T  \geq
    z_\alpha \Big] \leq \alpha,
  \end{equation*}
  with $z_\alpha$ the $(1-\alpha)$-quantile of the standard normal
  distribution.
  \qed
\end{thm}
In short, one-sided tests for nested models that (erroneously) act as
though the out-of-sample average were normal with mean $\m{}$ are
asymptotically valid.

This theorem relies on the inequality
\begin{multline} \label{eq_nesting_inequality}
  (\el{1} - \el{2}) - (\m{1} - \m{2}) \leq \\
\big[\el{1} - \mmr{1}\big] - \big[\el{2} - \mmr{2}\big] + o_p(R^{-1/2}),
\end{multline}
which holds because $\m{1} = \mmr{1} + o_p(R^{-1/2})$ and $\m{2} \leq
\mmr{2}$.

We should discuss the variance estimator, $\hat \sigma_T$, further.
Since the asymptotic variance, $\SrT$, is a random element that
depends on $\bT{}{R_T}$, the usual proofs that HAC estimators are
consistent do not apply.  Moreover, those proofs require NED
sequences, not mixingales, so they would not apply anyway.  Because of
the special structure of our mixingale process, though, it is
straightforward to prove the consistency of HAC estimators using a
coupling argument similar to the one used to prove Lemmas
\ref{lem_mixingale} and \ref{lem_mixingale_normality}.  In fact, one
can simply mimic the available NED proofs.  In this paper, we will
simply assume
the existence of a consistent estimator.  Lemma
\ref{lem_cov_matrix_appendix} (in the Appendix) contains the basic
argument for how to modify existing proofs,
\citename{davidson_consistency_1998}
(\citeyear*{davidson_consistency_1998},
\citeyear*{davidson_consistency_2000}) in particular.

In this case, there are more basic assumptions that guarantee that the
covariance matrix $\SrT$ is uniformly positive definite.  Remember
that the null hypothesis imposes that the coefficients on the
additional predictors used by the larger model are zero.  Under
Theorem \ref{thm_nesting1}'s assumptions, the models' prediction errors
satisfy the relationship
\begin{align*}
  \e{1}{s} & = \ep{1}{s} + o_p(1) \\
  \e{2}{s} & = \ep{1}{s} + z_{s}'\hat \alpha_{R_T} + o_p(1)
\end{align*}
with $z_s$ the additional predictors and $\hat \alpha_{R_T}$ their
coefficient estimates.  As long as $z_s$ and $\hat \alpha_{R_T}$ are
almost surely not zero, the two forecasts are almost surely
different.

This example is generalized slightly by the next lemma.  
\begin{lem} \label{lem_pd_conditions}
  Suppose that the conditions of Lemma \ref{lem_mixingale} and the
  additional conditions of Theorem \ref{thm_nesting1} hold.
  In addition, suppose that
  \begin{itemize}
  \item[(i)]  The maximum eigenvalues of
    $R_T^{-1} \XT{i}{R_T}'\XT{i}{R_T}$ and
    $R_T^{-1} \XT{i}{R_T}'\Ep{i}{R_T}\Ep{i}{R_T}'\XT{i}{R_T}$ are $O_p(1)$ and
    their minimum eigenvalues are bounded away from zero in probability.
  \item[(ii)] The first model's innovations, $\epT{1}{t}$, are
    sequentially exogenous and independent of $\xT{1}{s}$ and
    $\xT{2}{s}$ for $s = 1,\dotsc, t$.
  \item[(iii)] The elements of $\xT{2}{t}$ and $\bT{2}{R_T}$ are
    continuous random variables.
  \end{itemize}
  Then $[(1,-1) \SrT (1,-1)']^{-1} = O_p(1)$.
  \qed
\end{lem}
These eigenvalue conditions are analogous to the usual restrictions
made on asymptotic variance matrices.  The strong assumption of
sequential exogeneity simplifies the proof but is not crucial.  The
fact that the random variables are continuous rules out the
possibility that, for example, the estimation error,
$\xT{2}{T+1}'(\bT{2}{R_T} - \BT{2})$, is zero.

To summarize this section: researchers can use fixed-window
out-of-sample averages to compare the pseudo-true performance of an
overfit model to a simple benchmark.  If the benchmark is also overfit
(i.e., $K_{1T}/T$ remains positive), this approach does not work
because inequality \eqref{eq_nesting_inequality} does not hold.  Also,
if different loss functions are used to estimate and evaluate the
model, this approach again does not work because inequality
\eqref{eq_nesting_inequality} does not hold.  But Theorem
\ref{thm_nesting1} and Lemma \ref{lem_pd_conditions} 
justify using the naive out-of-sample one-sided t-test for most
empirical research.
%%
\section{Comparing Finite-Sample Performance} \label{sec_perf} 
%%
This section gives conditions under which $\mmrT{}$ converges to
$\mmtT{}$ and suggests that $\mmtT{}$ be used as a criterion for
choosing between forecasting models.

\pp{Ideally, a forecaster choosing between two models to use for period
  $T+1$ would chose the one that minimizes the expected loss given the
  information available in period $T$, $\ct{j}$.}  Even if the
underlying random variables are independent, $\F{T}$ has valuable
information about the models' performance --- the values of the
coefficient estimates $\b{1}{T}$ and $\b{2}{T}$. But usually a model
will use lagged variables as predictors, and their values are also
included in $\F{T}$. Consequently, a
forecaster choosing the model that minimizes the conditional
expectation will make better forecasts than one who minimizes the
unconditional expected loss, $\E \ff{j}{T+1}$.

For i.i.d. series, $\mmtT{} = \ct{}$ almost surely.  With dependence,
$\mmtT{}$ ignores the past information beyond the value of the
coefficient estimate, and so is a biased proxy for the true
conditional expectation.  However, the true conditional expectation
can be difficult to estimate, and the fixed-window out-of-sample
average can be used to estimate $\mmtT{}$.

\begin{lem} \label{lem_muR}
  Suppose that Assumptions \ref{asmp_array} to \ref{asmp_loss_bound}
  hold and that 
  \begin{itemize}
  \item[(i)] For each sequence $\{s_T\}$ with $s_T$ between $R_T$ and $T$, the
  maximum eigenvalues of $s_T^{-1} \XT{i}{s_T}'\XT{i}{s_T}$ and
  $s_T^{-1} \XT{i}{s_T}'\Ep{i}{s_T}\Ep{i}{s_T}'\XT{i}{s_T}$ are
  $O_p(1)$ and their minimum eigenvalues are bounded away from zero in
  probability.
  \item[(ii)] $P_T/R_T \to 0$, $K_{1T}/T \to k_1$, and $K_{2T}/T \to
  k_2$.  Both $k_1$ and $k_2$ are less than one.
  \item[(iii)] $L$ has finite left- and right-derivatives at every
  point, denoted $D_L(\cdot)$ and $D_R(\cdot)$ respectively.
  \end{itemize}
  Then
  \[
  \mmrT{i} - \mmtT{i} = O_{L_1}(\sqrt{P_T/R_T}),
  \]
  and so $\elT{} - \mmtT{} \to 0$ in probability.
  \qed
\end{lem}

Theorem \ref{thm_muR} is an immediate corollary.
\begin{thm} \label{thm_muR}
  Suppose the conditions of Lemmas \ref{lem_mixingale_normality}
  and \ref{lem_muR} hold.  If $P_T^2/R_T \to 0$, then
  \[
  P_T^{1/2} \SrT^{-1/2} \left[\elT{} - \mmtT{}\right] \xrightarrow{d}
  N(0, I) \quad \text{as $T \to \infty$.}
  \]
  \qed
\end{thm}

These results suggest two new ideas.  When the
models are overfit, out-of-sample averages implicitly condition on the
coefficient estimates.\footnote{\citeasnoun{efron_biased_1986} makes a
similar point about cross-validation in finite samples.  Our result,
though, is the first that we are aware of to study such conditioning
asymptotically.}  In economic forecasting applications, such
conditioning is desirable --- we will make predictions for the same
series using those coefficients, so averaging the forecasts'
performance over other hypothetical values for those coefficients is
inappropriate.  However, unless $P/R$ is very small, the forecasts
comparative performance can change when the models are re-estimated
over the entire dataset.  Since, in practice, $P$ must also be large
enough to justify a Law of Large Numbers or Central Limit Theorem,
these out-of-sample statistics may have limited use in macroeconomics.
%%
\section{Simulations} \label{sec_mc}
In progress.
\section{Conclusion} 
By studying the behavior of the fixed-window out-of-sample average
under a new limit theory that increases the number of predictors with
the number of observations, this paper shows that these out-of-sample
tests can prevent overfit and are properly sized when in-sample tests
are not.  Many of the previously known  results on these statistics do not
carry over to this setting, though: the performance of the model's
pseudo-true coefficients can not be estimated, but researchers can
still construct some one-sided confidence intervals; nested
comparisons are asymptotically normal; and the test sample must be
extremely small if this out-of-sample exercise will estimate how
well the models perform when they are re-estimated over the
full dataset.

Future research should study whether it is possible to improve the
power of out-of-sample tests while preserving size under this
asymptotic theory in the manner of
\citetwo{clark_using_2006}{clark_approximately_2007}; whether
resembling techniques can improve the restrictions on $P/R$; and how
these results can be extended to M-estimators and nonlinear models.
%%
\appendix
\section{Additional Technical Results and Proofs}
%%
\newcommand{\insum}{P_T^{-1/2}\sum_{s = R_T + (i-1)b_T + 1}^{R_T + i b_T}}
\newcommand{\insump}{P_T^{-1/2}
  \sum_{s = R_T + \lfloor P_T / b_T \rfloor b_T + 1}^T}
\newcommand{\outsum}{\sum_{i=1}^{\lfloor P_T/b_T \rfloor}}
\newcommand{\outsump}{\sum_{i=2}^{\lfloor P_T/b_T \rfloor + 1}}

\renewcommand{\L}{\mathcal L}

\begin{lem} \label{lem_coupling}
 Suppose Assumptions \ref{asmp_array} to \ref{asmp_loss_bound} hold.
 Then, for any $T$, $s$, $t$, and $u$, with $t \geq s > u \geq R_T$
 there exists an array $\{\tilde L_{jv}; v = s, \dotsc, t;\, j =
 1,2\}$  such that
 \begin{equation} \label{eq_coupling1}
   \E\left(\phi(\tilde L_s, \dotsc, \tilde L_t) \mid \FT{u} \right) = 
   \int \phi(\fT{}{s}, \dotsc, \fT{}{t}) \p(d\xT{}{s}, d\yT{s}, \dotsc,
   d\xT{}{t}, d\yT{t})
 \end{equation}
 almost surely for all measurable functions $\phi$ such that the expectations
 are finite.  Moreover, 
\begin{equation} \label{eq_coupling2}
  \p[\tilde L_{jv} \neq \fT{j}{v} \text{ for at least one $v$ and $j$}] =
 \beta_{s-u}
\end{equation}
 and
\begin{equation} \label{eq_coupling3}
  \| \tilde L_v - \fT{}{v} \|_2 \leq 2^{1+1/\rho} B_L
  \beta_{s-u}^{(\rho-2)/2\rho} \quad \text{for each $v$ and $j$.}
\end{equation}
\end{lem}

\begin{proof}
  \newcommand{\A}{\mathcal A}
  Fix $T$, $t$, $s$, and $u$.  The array $\A \equiv
  \{(\yT{\tau},\xT{}{\tau}, \dotsc, \yT{\tau + t-s}, \xT{}{\tau +
  t-s}); \; \tau\}$ is also absolutely regular of size
  $\rho/(\rho-2)$, so Berbee's Lemma allows
  us to construct a new array $\A^* \equiv \{( y_\tau^*,x_\tau^*,
  \dotsc, y_{\tau + t-s}^*, 
  x_{\tau + t-s}^*)\}$ that is independent of $\FT{u}$, equal to
  $\A$ in distribution, and satisfies $\p[\A^* \neq \A] =
  \beta_{s-u}$.

  Now it is easy to construct $\{\tilde L_{jv}\}$:
  \begin{equation}
    \tilde L_{jv} \equiv L(y_v^* - x_{jv}^* \cdot \bT{j}{R_T}), \quad j
    = 1,2, \quad v = s, \dotsc, t.
  \end{equation}
  Equations \eqref{eq_coupling1} and \eqref{eq_coupling2} are
  satisfied by construction, so it remains to prove
  \eqref{eq_coupling3}.  But \eqref{eq_coupling3} follows immediately
  from \possessivecite{merlevede_coupling_2002} Proposition 2.3 ---
  this proposition only uses (\ref{eq_coupling2}) and moment
  restrictions, not the equality of distributions.  As noted by
  \citeasnoun{dedecker_new_2005}, \citename{merlevede_coupling_2002}'s
  constant, $2^{p+2}$ can be reduced when $p=2$.
\end{proof}

\begin{lem} \label{lem_cov_matrix_appendix}
  Suppose $\{b_T\}$ is a sequence of positive integers such that $b_T
  \to \infty$ and $b_T/P_T \to 0$, and define 
  \[
  Z_{Ti} \equiv \insum [\fT{}{s} - \mmrT{}].
  \]
  If Assumptions \ref{asmp_array} to \ref{asmp_loss_bound} hold
  then
  \[
  \outsum \big[Z_{Ti}^2 - \meR(Z_{Ti}^2 \mid \FT{R_T})\big]
  \to 0 \quad \text{in $L_1$,}
  \]
  where $\meR$ is the integral with respect to a new probability
  measure $\peR$ that imposes independence between $\FT{R_T}$ and the
  sigma-field generated by the random variables 
  \[
  \{\yT{R_T+j}, \xT{1}{R_T+j}, \xT{2}{R_T+j};\; j>0\}
  \]
  but otherwise preserves the original probability measure.
\end{lem}

\begin{proof}
Much of the proof mimics that of \possessivecite{de_jong_central_1997}
Lemma 5.  For clarity, suppose that $Z_{Ti}$ is a scalar.  Define the
function
\[
h_c(x) = \begin{cases}
    \sgn(x) c \sqrt{b_T/P_T} & \text{if } |x| > c \sqrt{b_T/P_T} \\
    x & \text{otherwise}
\end{cases}
\]
for an arbitrary constant $c$.  \citeasnoun{mcleish_invariance_1975}
shows that (in this paper's notation) $\{P_T Z_{Ti}^2/b_T\}$ is
uniformly integrable,\footnote{Also see the remarks after
  \possessivecite{davidson_central_1992} Lemma 3.2.} so it is
sufficient to prove that  
\[
\outsum \big[h_c(Z_{Ti})^2 - \meR(h_c(Z_{Ti})^2 \mid \FT{R_T})\big]
\to 0
\]
in $L_1$ for any choice of $c$.

We prove this by showing that the array
\begin{equation} \label{eq_ap_array}
  \{h_c(Z_{Ti})^2 - \meR(h_c(Z_{Ti})^2 \mid \FT{R_T}), \FT{R_T +
    i\,b_T}\}
\end{equation}
 is another $L_2$-mixingale of size $-1/2$ with constants $d_{Ti}$
 that satisfy $\outsum d_{Ti}^2 \to 0$.  Fix $T$, $i$, and $\kappa$,
 and define the array $\{\tilde L_{jv}; v = R_T + (i-1)b_T + 1, \dotsc,
 R_T + i b_T; \, j = 1,2\}$ 
 independent of $\FT{R_T + (i-\kappa)b_T}$ using Lemma
 \ref{lem_coupling}.
 Now let
 \[
 W_{Ti} = \insum [\tilde L - \mmrT{}],
\]
so 
\begin{multline*}
\big\| \E\big[h_c(Z_{Ti})^2 - \meR(h_c(Z_{Ti})^2 \mid \FT{R_T}) \mid \FT{R_T +
  (i-\kappa)b_T}\big] \big\|_2 \\
= \big\| \E\big[ h_c(Z_{Ti})^2 - h_c(W_{Ti})^2 \mid \FT{R_T +
  (i-\kappa)b_T}\big] \big\|_2 \leq 
\big\| h_c(Z_{Ti})^2 - h_c(W_{Ti})^2 \big\|_2
\end{multline*}
and it suffices to bound the last quantity.

As in de Jong, we have the inequalities:
\begin{align*}
  \|h_c(Z_{Ti})^2 - h_c(W_{Ti})^2\|_2 
  & \leq 2 c \sqrt{b_T/P_T} \| h_c(Z_{Ti}) - h_c(W_{Ti}) \|_2 \\
  & \leq 2 c \sqrt{b_T/P_T} \; \Big\| 
    \sum_{s=R_T + (i-1)b_T + 1}^{R_T + i b_T} (\fT{}{s} - \tilde
  L_s)\Big\|_2 \\
  & \leq \left[2 c b_T^{3/2} P_T^{-1} \beta_{b_T}^{(\rho -
  2)/2\rho}\right] \beta_\kappa^{(\rho - 2)/2\rho}\\
  &\equiv d_{Ti} \; \beta_\kappa^{(\rho - 2)/2\rho}.
\end{align*}
Since $\beta_\kappa^{(\rho - 2)/2\rho}$, the array (\ref{eq_ap_array})
is an $L_2$-mixingale and has size $-1/2$, $\outsum 
d_{Ti}^2 \to 0$.  Then \possessivecite{mcleish_maximal_1975} Theorem 1.6
gives
\[
  \Big\| \outsum \big[h_c(Z_{Ti})^2 - \meR(h_c(Z_{Ti})^2
  \mid\FT{R_T})\big] \Big\|_1 =
  O\Big(\outsum d_{Ti}^2\Big),
\]
to complete the proof.
\end{proof}

\begin{proof}[Proof of Lemma \ref{lem_mixingale}]
We'll prove that 
\[
  \| \E(\fT{i}{R_T+j} - \mmrT{j} \mid \FT{R_T+j-\tau}) \|_2 
  \leq 2^{1+1/\rho} \; B_L \; \beta_\tau^{(\rho-2)/2\rho}
\]
Notice that $\beta_\tau^{(\rho-2)/2\rho} =
O(\tau^{-1/2-\delta}$. Define 
$\tilde L_s$ as in Lemma \ref{lem_coupling} to be independent of
$\FT{s-\tau}$.  Then
\begin{align*} \label{eq_mixingale_bound_1}
  \| \E(\fT{i}{s} - \mmrT{i} \mid \FT{s-\tau}) \|_2 
  & = \| \E(\fT{i}{s} - \tilde L_{is} \mid \FT{s-\tau}) \|_2 \\
  & \leq \| \fT{}{s} - \tilde L_{is} \|_2 \\
  & \leq 2^{1+1/\rho} B_L \beta_\tau^{(\rho-2)/2\rho}
\end{align*}
by Lemma \ref{lem_coupling}.
\end{proof}

\begin{proof}[Proof of Lemma \ref{lem_mixingale_normality}.]
\renewcommand{\insum}{\sum_{s=R_T + (i-1)b_T + l_T + 1}^{R_T + i b_T}}
Without loss of generality, assume that $\fT{}{s}$ is a scalar. 
We will modify \possessivecite{de_jong_central_1997} Theorem 1 to
establish normality. The only part of de Jong's proof that needs to be
changed is the handling of the covariance matrix; here it is a random
element and in de Jong's theorem it is a constant.

Let $\{b_T\}$, $\{l_T\}$, and $\{m_T\}$ be sequences of positive
integers that satisfy $P_T \geq b_T \geq l_T+1$, $b_T \to \infty$,
$l_T \to \infty$, $\lfloor P_T/b_T \rfloor \to \infty$, and
$l_T/b_T \to 0$. Then, De Jong proves that (in our notation)
\[
P_T^{-1/2} \big[\elT{} - \mmrT{}\big] = \outsum Z_{Ti} + o_p(1)
\]
with 
\[
Z_{Ti} \equiv \insum \big[\fT{}{s} - \E(\fT{}{s} \mid \FT{R_T + (i-1)b_T})\big].
\]
The array $\{Z_{Ti}, \FT{R_T + ib_T}, i = 1,\dotsc,m_T\}$ is a martingale 
difference array by construction and it suffices to apply a Central
Limit Theorem to $\sum_i Z_{Ti}$.

We apply \possessivecite{hall_martingale_1980} Theorem 3.3 to complete
the proof.\footnote{The covariance matrix, $\Sigma_T$, is measurable
  in all of the sub-sigma-fields $\FT{s}$, so Hall and Heyde's nesting
condition is unnecessary.  See the remarks surrounding their Theorem
for more details.  This measurability also allows us to use a sequence
of covariance matrices that does not necessarily converge.}  De Jong's
condition (9) ensures that Hall and Heyde's (3.18) and (3.20) are
satisfied, so it remains to prove that 
\[
  \outsum Z_{Ti}^2 = \Sigma_T + o_p(1).
\]
This last step is an immediate consequence of Lemma
 \ref{lem_cov_matrix_appendix} and De Jong's Lemmas 3 and 4.
\end{proof}

\begin{proof}[Proof of Theorem \ref{thm_nesting1}]
Under the null hypothesis,
\begin{align*}
  \elT{1} - \elT{2} &= [\elT{1} - \mmrT{1}] - [\elT{2} - \mmrT{2}]
  \\ &\quad + [\mmrT{1} - \mmmT{1}] + [\mmmT{2} - \mmrT{2}] \\
  & \leq [\elT{1} - \mmrT{1}] - [\elT{2} - \mmrT{2}] + o_p(R_T^{-1/2})
\end{align*}
since the derivative of $\mmT{1}{\cdot}$ at $\BT{1}$ is zero and
$[\mmmT{2} - \mmrT{2}]$ is positive.  Lemma
\ref{lem_mixingale_normality} ensures that this last quantity is
asymptotically normal with asymptotic variance $\hat \sigma_T$.
\end{proof}

\begin{proof}[Proof of Lemma \ref{lem_pd_conditions}]
  Let $\{(v_T, z_{1T}, z_{2T})\}$ be a sequence of random vectors,
  independent of $\bT{}{R_T}$ and equal in distribution to
  $\{(\epT{1}{t},\xT{1}{t},\xT{2}{t})\}$.  The prediction errors satisfy
  \begin{align*}
    \eT{1}{t} &= \epT{1}{t} + \xT{1}{t}'(\bT{1}{R_T} - \BT{1}) 
    \\ & = \epT{1}{t} + O_p(R_T^{-1/2}) \\
    \eT{2}{t} &= \epT{1}{t} + \xT{2}{t}'(\bT{2}{R_T} - \BT{2}).
  \end{align*}
  Since $z_T'(\bT{2}{R_T}- \BT{2})$ is a continuous random variable,
  the probability of it taking a value that guarantees constant loss
  is zero.
  To show that $[(1,-1) \SrT (1,-1)']^{-1} = O_p(1)$, then, it
  suffices to prove that the conditional variance (given $\bT{}{R_T}$)
  of the vector $(v_T^2,\, [v_T + z_T'(\bT{2}{R_T} -\BT{2})]^2)'$
  satisfies the same relationship. Since $z_T$ has uniformly positive
  variance, we only need to prove that $|\bT{2}{R_T} - \BT{2}|_2$ is
  uniformly a.s. positive.  This follows from the inequality
  \[
  |\bT{2}{R_T} - \BT{2}|_2^2 \geq
   \lambda_{max}(\XT{2}{R_T}'\XT{2}{R_T})^{-1}
   \lambda_{min}(\XT{2}{R_T}'\Ep{2}{R_T} \Ep{2}{R_T}'\XT{2}{R_T}).
  \]
\end{proof}

\begin{proof}[Proof of Lemma \ref{lem_muR}]
  Observe that 
  \begin{multline*}
    \mmrT{j} - \mmtT{j} = \\ \E\left[L(\psi_T - z_T'\bT{j}{R_T}) -
    L(\psi_T - z_T'\bT{j}{T}) \mid \bT{j}{R_T},\bT{j}{T}\right]
  \end{multline*}
  almost surely, with $(\psi_T, z_T) \eqdist (\yT{T+1},\xT{j}{T+1})$
  and independent of $(\bT{j}{R_T}, \bT{j}{T})$.  As a result, it
  suffices to show that
  \[
  \|L(\psi_T - z_T'\bT{j}{R_T}) - L(\psi_T - z_T'\bT{j}{T}) \|_1
  = O(\sqrt{P/R}).
  \]
  Since $L$ has finite left- and right-derivatives and is convex, 
  \[
  L(\psi_T - z_T'\bT{j}{R_T}) - L(\psi_T - z_T'\bT{j}{T})
  = O_p(1) z_T'(\bT{j}{R_T} - \bT{j}{T}),
  \]
  and, because this difference is uniformly integrable, we only need
  to prove that 
  \[
  |\bT{j}{R_T} - \bT{j}{T}|_2 = O_p(\sqrt{P_T/R_T}).
  \]

  Now, we can express this last difference as
  \begin{multline*}
  \bT{j}{R_T} - \bT{j}{T} = \left[
    (\XT{j}{T}'\XT{j}{T})^{-1} - (\XT{j}{R_T}'\XT{j}{R_T})^{-1}
  \right] \XT{j}{T}'\Ep{j}{T} \\
  + (\XT{j}{R_T}'\XT{j}{R_T})^{-1} \sum_{s=R_T+1}^T \xT{j}{s} \epT{j}{s}.
  \end{multline*}
  The square of each of these terms is $O_p(\sqrt{P_T/R_T})$.  First,
  observe that
  \begin{multline*}
    \left\lvert \left[
    (\XT{j}{T}'\XT{j}{T})^{-1} - (\XT{j}{R_T}'\XT{j}{R_T})^{-1}
  \right] \XT{j}{T}'\Ep{j}{T} \right\rvert_2^2\\
  = O_p(T) \sum_{i=1}^{K_{jT}} \lambda_i\left[(\XT{j}{T}'\XT{j}{T})^{-1}
    - (\XT{j}{R_T}'\XT{j}{R_T})^{-1}\right]^2,
  \end{multline*}
  which is $O_p(P_T/R_T)$ since 
  $(\XT{j}{T}'\XT{j}{T})^{-1} - (\XT{j}{R_T}'\XT{j}{R_T})^{-1}$ has
  rank $P_T$ and its largest eigenvalue is $O_p(1/T)$.
  A similar argument proves that the second term is
  $O_p(\sqrt{P_T/R_T})$ as well, completing the proof.
\end{proof}
%%

\bibliography{zoterolibrary}
\bibliographystyle{econometrica}
\end{document}

### 2009-04-16 empirics/mainScript.R

@@ -1,0 +1,67 @@
+source("makeDataMatrices.R")
+
+mainData <- read.csv("phillipsCurve.csv")
+baseSeries <- ts(mainData[,c("unemployment", "inflation")], end = c(2008, 4), frequency = 12)
+
+pdf("unemploymentPlot.pdf", width = 8.2, height = 3.7)
+plot(baseSeries[,"unemployment"], main = "Unemployment Rate", ylab = "", xlab = "", las = 1)
+dev.off()
+pdf("inflationPlot.pdf", width = 8.2, height = 3.7)
+plot(baseSeries[,"inflation"], main = "CPI Inflation (%)", ylab = "", xlab = "", las = 1)
+dev.off()
+
+dataMatrices <- makeDataMatrices(y = mainData$inflationChange, x = mainData$unemployment)
+
+target <- dataMatrices$target
+predictors <- dataMatrices$predictorMatrix
+rm(list = c("mainData", "dataMatrices"))
+
+n <- length(target)
+rvec <- 108:(n-120)
+
+rmse1 <- matrix(NA, length(rvec), 6)
+rmse2 <- matrix(NA, length(rvec), 6)
+
+testWindow <- seq(to = n, length = 120)
+
+for (r in rvec) {
+  estimationWindow2.r <- seq(to = testWindow[1] - 1, length = r)
+  rmse1[r - rvec[1] + 1, 1] <- sqrt(mean((target[testWindow] - mean(target[1:r]))^2))
+  rmse2[r - rvec[1] + 1, 1] <- sqrt(mean((target[testWindow] - mean(target[estimationWindow2.r]))^2))
+  for (k in 1:5) {
+    rmse1[r - rvec[1] + 1, k+1] <- sqrt(mean((target[testWindow] - predictors[testWindow, c(1, 1 + 1:k, 13 + 1:k)] %*%
+                                              lm.fit(y = target[1:r],
+                                                     x = predictors[1:r,
+                                                       c(1, 1 + 1:k, 13 + 1:k)])$coef)^2))
+    rmse2[r - rvec[1] + 1, k+1] <- sqrt(mean((target[testWindow] - predictors[testWindow, c(1, 1 + 1:k, 13 + 1:k)] %*%
+                                              lm.fit(y = target[estimationWindow2.r],
[…]

### 2009-04-16 empirics/makeDataMatrices.R

@@ -1,0 +1,14 @@
+makeDataMatrices <- function(y, x) {
+  if (length(y) != length(x))
+    stop("input vectors are not equal length.")
+  
+  n <- length(y) - 24
+
+  target <- y[-(1:24)]
+  predictorMatrix <- matrix(1, n, 25)
+  for (i in 1:12) {
+    predictorMatrix[,1+i] <- y[(1:n) + (13-i)]
+    predictorMatrix[,13+i] <- x[(1:n) + (13-i)]
+  }
+  list(target = target, predictorMatrix = predictorMatrix)
+}

### 2009-04-16 mc/confidenceIntervals-pop.R

@@ -1,0 +1,73 @@
+### Simulation to calculate probability of choosing worse-forecasting larger model.
+
+### initialize
+rm(list = ls())
+set.seed(5700)
+library(lattice)
+library(fixedWindow)
+
+### set coefficient values to use for simulation
+rootVCV <- matrix(c(sqrt(10.505), 0, 1.036 / sqrt(10.505),
+                    sqrt(0.366 - 1.036^2 / 10.505)), 2, 2)
+B <- matrix(c(2.237, 0.261, 3.363, 0.000,-0.633, 0.000,-0.377, 0.000,-0.529,
+              0.000, 0.000, 0.804, 0.000,-0.221, 0.000, 0.226, 0.000,-0.205), 
+            byrow = T, nrow = 2)
+
+levelvec <- c(0.90, 0.95, 0.99)
+## column 1 - R values
+## column 2 - P values
+windowmat <- matrix(c(50,  50, 100, 100, 100, 200, 200, 200,
+                      25,  50,  25,  50, 100,  25,  50, 100), ncol=2)
+evalwindow <- 30
+ndraw <- evalwindow + max(rowSums(windowmat))
+
+realPerformance <- rep(NA, (nsims <- 1500) * dim(windowmat)[1])
+ciCal <- ciCW <- ciMc <-
+  matrix(NA, length(realPerformance), length(levelvec))
+
+for (i in 1:nsims) {
+  cat("Simulation", i, "of", nsims, "\n")
+  ## draw a random dataset
+  d.i <- rData1(ndraw, B, rootVCV)
+  ## loop over values of R and P
+  for (j in 1:dim(windowmat)[1]) {
+    ij <- j + (i-1) * dim(windowmat)[1]
+
+    R.ij <- windowmat[j,1]
+    P.ij <- windowmat[j,2]
+
+    preds0.ij <- forecast0(R.ij, P.ij, d.i)
+    predsA.ij <- forecastA(R.ij, P.ij, d.i)
+    target.ij <- d.i[1:P.ij + R.ij,1]
+
+    realPerformance[ij] <- mean((d.i[R.ij+P.ij + 1:evalwindow,1] -
+                                 forecast0(R.ij+P.ij, evalwindow, d.i))^2 -
+                                (d.i[R.ij+P.ij + 1:evalwindow,1] -
+                                 forecastA(R.ij+P.ij, evalwindow, d.i))^2)
+
+    ## loop over confidence levels
[…]

### 2009-04-16 mc/cw_eloss.R

@@ -1,0 +1,18 @@
+cw.eloss <- function(coef) {
+  F <- matrix(0, 10, 10)
+  F[1,1] <- 0.261
+  F[2:5,1:4] <- diag(4)
+  F[6,6] <- 0.804
+  F[6,7] <- -0.221
+  F[6,8] <- 0.226
+  F[6,9] <- -0.205
+  F[7:10,6:9] <- diag(4)
+
+  mu <- 2.237 / (1 - 0.261)
+  
+  Q <- matrix(0, 10, 10)
+  Q[c(1,6),c(1,6)] <- c(10.505, 1.036, 1.036, 0.366)
+  S <- matrix(solve(diag(100) - kronecker(F, F), c(Q)), 10, 10)
+  c(1, - coef[2:5], 0, -coef[6:9]) %*% S %*% c(1, - coef[2:5], 0, -coef[6:9]) +
+    (coef[1] - (1 - sum(coef[2:5])) * mu)^2
+}

### 2009-04-16 mc/cw_tests.R

@@ -1,0 +1,32 @@
+cw.tests <- function(Rvec, Pvec) {
+  r <- rep(NA, length(Rvec) * length(Pvec))
+  k <- 0
+  
+  d <- rcw(max(Rvec) + max(Pvec))
+  for (R in Rvec) {
+    s1 <- 2:R
+    s2 <- 5:R
+    c1 <- lm.fit(y = d$y[s1], x = cbind(1, d$y[s1 - 1]))$coef
+    c2 <- lm.fit(y = d$y[s2], x = cbind(1, d$y[s2-1], d$y[s2-2], d$y[s2-3],
+                                d$y[s2-4], d$z[s2-1], d$z[s2-2], d$z[s2-3],
+                                d$z[s2-4]))$coef
+    L1 <- rep(NA, max(Pvec))
+    L2 <- rep(NA, max(Pvec))
+    for (s in 1:max(Pvec)) {
+      L1[s] <- (d$y[R+s] - crossprod(c(1, d$y[R+s-1]), c1))^2
+      L2[s] <- (d$y[R+s] - crossprod(c(1, d$y[R+s - 1:4], d$z[R+s - 1:4]), c2))^2
+    }
+    for (P in Pvec) {
+      t1 <- 2:(R+P)
+      t2 <- 5:(R+P)
+      avg.P <- lm((L1[1:P] - L2[1:P]) ~ 1)
+      std.P <- sqrt(NeweyWest(avg.P)[1,1])
+      ediff <- c(1, -1) %*% cw.eloss(lm.fit(y = d$y[t1], x = cbind(1, d$y[t1 - 1]))$coef,
+                                     lm.fit(y = d$y[t2], x = cbind(1, d$y[t2-1], d$y[t2-2], d$y[t2-3],
+                                                           d$y[t2-4], d$z[t2-1], d$z[t2-2], d$z[t2-3],
+                                                           d$z[t2-4]))$coef)
+      r[k <- k+1] <- !(ediff > avg.P$coef + 1.65 * std.P) & !(ediff < avg.P$coef - 1.65 * std.P)
+    }
+  }
+  matrix(c(rep(Rvec,each = length(Pvec)), rep(Pvec, length(Rvec)), r), length(Rvec) * length(Pvec), 3)
+}

### 2009-04-16 mc/experiment1.R

@@ -1,0 +1,44 @@
+library(lattice)
+rm(list = ls())
+
+rootVCV <- matrix(c(sqrt(10.505), 0, 1.036 / sqrt(10.505),
+sqrt(0.366 - 1.036^2 / 10.505)), 2, 2)
+B <- matrix(c(2.237, 0.261, 3.363, 0.000,-0.633, 0.000,-0.377, 0.000,-0.529,
+              0.000, 0.000, 0.804, 0.000,-0.221, 0.000, 0.226, 0.000,-0.205), 
+            byrow = T, nrow = 2)
+
+set.seed(5343)
+source("mcFunctions.R")
+n <- c(80, 120, 240, 480)
+Rratio <- c(1/4, 1/2, 3/4, 9/10)
+
+minwindow <- 20
+lossFrame <- cbind(expand.grid(R = paste(Rratio,"n"), sim = 1:(nsims <- 400), n = n),
+                   mFull1 = NA, mFull2 = NA, mTrain1 = NA, mTrain2 = NA)
+
+for (j in seq(along.with = n)) {
+  for (i in 1:nsims) {
+    cat(n[j], "--", i, "of", nsims, "\n")
+    d.ni <- rData1(n[j], B, rootVCV)
+    lossFrame[(j-1) * nsims * length(Rratio) + (i-1) * length(Rratio) + 1:length(Rratio),
+              c("mFull1", "mFull2")] <- rep(marginalLoss(makeb1(d.ni), makeb2(d.ni), B, rootVCV),
+                                            each = length(Rratio))
+    for (r in seq(along.with = Rratio)) {
+      lossFrame[(j-1) * nsims * length(Rratio) + (i-1) * length(Rratio) + r,
+                c("mTrain1", "mTrain2")] <- marginalLoss(makeb1(d.ni[1:round(Rratio[r] * n[j]),]),
+                                                         makeb2(d.ni[1:round(Rratio[r] * n[j]),]),
+                                                         B, rootVCV)
+    }
+  }
+}
+
+lims1 <- c(2.3, 3)
+xyplot(log(mFull1) ~ log(mTrain1) | n * Rratio, data = lossFrame,
+       xlim = lims1, ylim = lims1, aspect = "fill", pch = 19, cex = 0.1)
+
+histogram(~ log(mFull1) - log(mTrain1) | n * Rratio, data = lossFrame, nint = 180,
[…]

### 2009-04-16 mc/main_table.R

@@ -1,0 +1,26 @@
+source("../R/cw_prederrors.R")
+source("../R/rcw.R")
+library(sandwich)
+
+rvec <- c(80, 120)
+pvec <- c(40, 80, 120, 160)
+
+n <- 1
+n <- 3000
+maxn <- max(rvec) + max(pvec)
+minr <- min(rvec)
+
+teststat <- matrix(NA, n, length(rvec) * length(pvec))
+muR <- matrix(NA, n, length(rvec))
+
+k <- 0
+for (i in 1:n) {
+  d.i <- cw.prederrors(rcw(maxn), R = minr)^2 %*% c(1, -1)
+  for (r in rvec) {
+    for (p in pvec) {
+      stat.irp <- lm(d.i ~ 1, subset = r - minr + 1:p)
+      nw.irp <- NeweyWest(stat.irp)
+    teststat[i,k] <- stat.ik$coef / nw.ik
+  }
+  print(paste("done simulation", i, "of", n))
+}clear

### 2009-04-16 mc/mc-engelwest.R

@@ -1,0 +1,60 @@
+library(fixedWindow)
+set.seed(92)
+
+fstat <- function(y, xo, xa) {
+### xo contains the regressors of the null model (including a constant)
+### xa contains the regressors for the alternative (including a constant).
+  d <- getDimensions(xo, xa)
+
+  eo <- lm.fit(y = y, x = xo)$resid
+  ea <- lm.fit(y = y, x = xa)$resid
+  sum((eo^2 - ea^2)/d$m) / sum(ea^2/(d$n-d$ka))
+}
+
+getDimensions <- function(xo, xa) {
+  if (!is.matrix(xo)) stop("the predictors of the null model must be a matrix")
+  if (!is.matrix(xa)) stop("the predictors of the alternative model must be a matrix")
+  if (! (dim(xa)[1] == dim(xo)[1])) stop("both matrices must have the same number of observations")
+  if (dim(xa)[2] < dim(xo)[2]) stop("the null model must have fewer variables than the alternative.")
+  r <- list(n = dim(xa)[1], ko = dim(xo)[2], ka = dim(xa)[2], m = dim(xa)[2] - dim(xo)[2],
+            cn = (dim(xa)[2] - dim(xo)[2])/(dim(xa)[1] - dim(xa)[2]))
+}
+
+b <- 0.9
+phi <- 0.5
+gam <- 0.5
+
+n <- 100
+nburn <- 1000
+### generate dm_t and dp_t
+
+dm <- rep(0, n + nburn)
+dp <- rep(0, n + nburn)
+ds <- rep(0, n + nburn)
+
+ep <- rnorm(n + nburn)
+em <- rnorm(n + nburn)
+
+for (t in 1:(n+nburn)) {
+  dm[t+1] <- phi * dm[t] + em[t]
+  dp[t+1] <- gam * dp[t] + ep[t]
+
+  ds[t+1] <- phi*(1-b)/(1-b*phi) * dm[t] + 1/(1-b*phi) * em[t] +
+    b*gam/(1-b*gam) * dp[t] + b/((1-b)*(1-b*gam)) * ep[t]
+}
+
+ds    <- ds[nburn + 1:n]
+dmLag <- dm[nburn + 1:n - 1]
+dpLag <- dp[nburn + 1:n - 1]
+
+R <- 50
+P <- n-R
+
+calhounCI(pred0 = mean(ds[1:R]),
[…]

### 2009-04-16 mc/paper_intro.R

@@ -1,0 +1,36 @@
+r2 <- function(n){
+  y <- arima.sim(model = list(ar = 0.1), n + 4, n.start = 500)
+  x <- arima.sim(model = list(ar = 0.3), n + 4, n.start = 500)
+  data.frame(y = y[4 + 1:n], y1 = y[3 + 1:n], y2 = y[2 + 1:n], y3 = y[1 + 1:n], y4 = y[1:n],
+             x = x[4 + 1:n], x1 = x[3 + 1:n], x2 = x[2 + 1:n], x3 = x[1 + 1:n], x4 = x[1:n])
+}
+
+makeerrors <- function(dataset, k, R) {
+  P <- length(dataset$y) - R
+  varmodel <- switch(k,
+                     lm(data = dataset, subset = 1:R, y ~ 1),
+                     lm(data = dataset, subset = 1:R, y ~ y1),
+                     lm(data = dataset, subset = 1:R, y ~ y1 + x1),
+                     lm(data = dataset, subset = 1:R, y ~ y1 + x1 + y2),
+                     lm(data = dataset, subset = 1:R, y ~ y1 + x1 + y2 + x2),
+                     lm(data = dataset, subset = 1:R, y ~ y1 + x1 + y2 + x2 + y3),
+                     lm(data = dataset, subset = 1:R, y ~ y1 + x1 + y2 + x2 + y3 + x3),
+                     lm(data = dataset, subset = 1:R, y ~ y1 + x1 + y2 + x2 + y3 + x3 + y4),
+                     lm(data = dataset, subset = 1:R, y ~ y1 + x1 + y2 + x2 + y3 + x3 + y4 + x4))
+  dataset[R + 1:P, "y"] - predict(varmodel, newdata = dataset[R + 1:P,])
+}
+
+R <- 4 * 20
+P <- 4 * 30
+nsims <- 1000
+ncoefs <- 9
+pmse <- rep(NA, nsims * (ncoefs - 1))
+stat.i <- 0
+for (s in 1:nsims) {
+  vardata.s <- r2(R + P)
+  for (k in 2:9) {
+    stat.i <- stat.i + 1
+    pmse[stat.i] <- mean(makeerrors(vardata.s, k, R)^2)
+  }
+}
+mcresults <- data.frame(pmse = pmse, zstat = (pmse - 1) / (2 / sqrt(P)), k = rep(2:9))

### 2009-04-16 mc/rcw.R

@@ -1,0 +1,24 @@
+rcw <- function(n, v = 1, edist = rnorm) {
+### Generates dataframe of matrix of n observations y_t, z_t
+### from Clark and West's (2007) DGP 1
+### v is a scalar that multiplies the covariance matrix for debugging 
+
+  burn <- 3500
+  n <- n + burn
+
+  vcv <- v * matrix(c(sqrt(10.505), 0, 1.036 / sqrt(10.505),
+                      sqrt(0.366 - 1.036^2 / 10.505)), 2, 2)
+  
+  z <- rep(NA,n)
+  y <- rep(NA,n)
+  y[1:4] <- 0
+  z[1:4] <- 0
+
+  innovations <- crossprod(vcv, matrix(edist(n * 2), 2, n))
+  for (s in 5:n) {
+    y[s] <- 2.237 + 0.261 * y[s-1] + innovations[1,s]
+    z[s] <- 0.804 * z[s-1] - 0.221 * z[s-2] + 0.226 * z[s-3] - 0.205 * z[s-4] +
+      innovations[2, s]
+  }
+  data.frame(y = y[-(1:burn)], z = z[-(1:burn)])
+}

### 2009-04-16 mc/sec2_table.R

@@ -1,0 +1,24 @@
+source("../R/cw_prederrors.R")
+source("../R/rcw.R")
+
+cw.table <- matrix(byrow = TRUE, c(80, 40, NA,  80, 80, NA,  80, 120, NA,
+                     80, 160, NA, 120, 40, NA, 120, 80, NA, 120, 120, NA,
+                     120,160, NA), 8, 3)
+nstats <- dim(cw.table)[1]
+
+n <- 3000
+maxn <- max(rowSums(cw.table[,1:2]))
+minR <- min(cw.table[,1])
+teststat <- matrix(NA, n, dim(cw.table)[1])
+for (i in 1:n) {
+  d.i <- cw.prederrors(rcw(maxn), R = minR)[,2]^2
+  for (k in 1:nstats) {
+    R <- cw.table[k,1]
+    P <- cw.table[k,2]
+    teststat[i,k] <- (sqrt(P) * (mean(d.i[(R - minR) + 1:P]) - 10.505)
+                      / sd(d.i[(R - minR) + 1:P])) > 1.282
+  }
+  print(paste("done simulation", i, "of", n))
+}
+
+cw.table[,3] <- colMeans(teststat)

### 2009-04-16 mc/secMC_table2.R

@@ -1,0 +1,45 @@
+source("../R/cw_prederrors.R")
+source("../R/cw_eloss.R")
+
+
+i1 <- 2:maxn
+i2 <- 5:maxn
+
+for (i in 1:n) {
+
+  dataMatrix1.i$dep <- data.i$y[i1]
+  dataMatrix2.i$dep <- data.i$y[i2]
+  dataMatrix1.i$ylag <- data.i$y[i1-1]
+  for (j in 1:4) {
+    dataMatrix2.i[,paste("y",j, sep="")] <- data.i$y[i2 - j]
+    dataMatrix2.i[,paste("z",j, sep="")] <- data.i$z[i2 - j]
+  }
+  for (k in 1:nstats) {
+    R <- cw.table[k,1]
+    P <- cw.table[k,2]
+
+    lastPredictors.i <- c(1, as.matrix(dataMatrix2.i[R+P-3,-1]))
+    model1.ik <- lm(dep ~ ylag, data = dataMatrix1.i, subset = 1:(R-1))
+    model2.ik <- lm(dep ~ y1 + y2 + y3 + y4 + z1 + z2 + z3 + z4,
+                    data = dataMatrix2.i, subset = 1:(R-4))
+ 
+    fullCoef1.ik <- c(lm(dep ~ ylag, data = dataMatrix1.i, subset = 1:(R+P-1))$coef, rep(0, 7))
+    fullCoef2.ik <- lm(dep ~ y1 + y2 + y3 + y4 + z1 + z2 + z3 + z4,
+                       data = dataMatrix2.i, subset = 1:(R+P-4))$coef
+    
+    diffCE.ik <- (lastPredictors.i %*% (fullCoef1.ik - pseudoTrue))^2 - 
+      (lastPredictors.i %*% (fullCoef2.ik - pseudoTrue))^2
+    diffFull.ik <- cw.eloss(fullCoef1.ik) - cw.eloss(fullCoef2.ik)
+    diffSubsample.ik <- 
+
+    loss.ik <- (dataMatrix1.i$dep[R-1 + 1:P] - predict(model1.ik, dataMatrix1.i[R-1 + 1:P,]))^2 -
+      (dataMatrix2.i$dep[R-4 + 1:P] - predict(model2.ik, dataMatrix2.i[R-1 + 1:P,]))^2
+    
+    avg.ik <- lm(loss.ik ~ 1)
+
[…]

### 2009-04-16 mc/table3.R

@@ -1,0 +1,51 @@
+library(sandwich)
+library(lattice)
+source("rcw.R")
+source("cw_eloss.R")
+source("rTestStat.R")
+
+trPairs <- matrix(c(120,  40, 
+                    120,  80,
+                    240,  80,
+                    240, 160,
+                    240, 200,
+                    480, 160,
+                    480, 320,
+                    480, 400, 
+                    480, 440), 
+                  ncol = 2, byrow = TRUE, dimnames = list(NULL, c("T","R")))
+n <- 1000
+maxT <- max(trPairs[,1])
+
+rStatistic <- tStatistic <- rep(NA, n * dim(trPairs)[1])
+
+k <- 0
+for (i in 1:n) {
+  data.i <- rcw(maxT)
+  for (j in 1:dim(trPairs)[1]) {
+    R <- trPairs[j,2]
+    P <- trPairs[j,1] - R
+    k <- k+1
+    
+    testStats.ij  <- rTestStat(d = data.i[seq(to = maxT, length = R + P),], R, P)
+    rStatistic[k]  <- testStats.ij$mR
+    tStatistic[k]  <- testStats.ij$mT
+  }
+  print(i)
+}
+
+mcResults <- data.frame(rbind(trPairs, trPairs))
+mcResults$P <- as.factor(mcResults$T - mcResults$R)
+mcResults$T <- as.factor(paste("T =", mcResults$T))
+mcResults$R <- as.factor(mcResults$R)
+mcResults$stat <- as.factor(rep(c("R", "T"), each = dim(trPairs)[1]))
+mcResults$size <- 100 * c(rowMeans(matrix(abs(rStatistic)  > 1.645, ncol = n)),
+                          rowMeans(matrix(abs(tStatistic)  > 1.645, ncol = n)))
+
+png("mcTable.png", width = 720, height = 360)
+dotplot(data = mcResults, P ~ (100 - size) | T, ylab = "P", xlab = "Empirical Coverage",
+        groups = stat, pch = 19, col = c("black", "red"), layout = c(3,1),
+        scales = list(alternating = 1, axs = "i"), xlim = c(70, 100))
+dev.off()
+
+save.image(file = "mcData_redone.RData")

### 2009-04-16 notes/slides-cv/overfitQQ.R

@@ -1,0 +1,18 @@
+library(lattice)
+load("mcGlobal.Rdata")
+load("simulations.Rdata")
+
+muOverfit <- 1/3
+varOverfit <- (1/5 - muOverfit^2) / n
+
+## generate qq-plot for simulations vs. theoretical quantiles
+png("overfitQQ.png")
+qqmath(mcOverfit, col = "black", ylab = "Simulated Values", xlab = "Theoretical Values (West 1996)",
+       distribution = function(p) qnorm(p = p, mean = muOverfit, sd = sqrt(varOverfit)), aspect = "1")
+dev.off()
+
+png("overfitHist.png")
+hist(mcOverfit[mcOverfit < 1], 70, freq = F, ylim = c(0, 20), xlab = "Simulated Value", main = "")
+curve(dnorm(x, mean = muOverfit, sd = sqrt(varOverfit)), from = 0.25, to = 0.45, n = 1000, col = "red", add = T,
+      lwd = 2)
+dev.off()

### 2009-04-16 notes/slides-cv/quadQQ.R

@@ -1,0 +1,18 @@
+library(lattice)
+load("mcGlobal.Rdata")
+load("simulations.Rdata")
+
+muQuad <- 1/3
+varQuad <- (1/5 - muQuad^2) / n
+
+## generate qq-plot for simulations vs. theoretical quantiles
+png("quadQQ.png")
+qqmath(mcQuad, col = "black", ylab = "Simulated Values", xlab = "Theoretical Values (West 1996)",
+       distribution = function(p) qnorm(p = p, mean = muQuad, sd = sqrt(varQuad)), aspect = "1")
+dev.off()
+
+png("quadHist.png")
+hist(mcQuad, 70, freq = F, ylim = c(0, 20), xlab = "Simulated Value", main = "")
+curve(dnorm(x, mean = muQuad, sd = sqrt(varQuad)), from = 0.25, to = 0.45, n = 1000, col = "red", add = T,
+      lwd = 2)
+dev.off()

### 2009-04-16 paper/_joinem.pl

@@ -1,0 +1,20 @@
+open MASTER, "<calhoun_fixed_window.tex" or die "Can't even start!";
+open BIGBOY, ">calhoun_draft.tex" or die "can't open to write!";
+
+while (<MASTER>) {
+    chomp;
+    if (/^\\input\{(\w+)\}/) {
+	open ADJUNCT, "<$1.tex" or die "can't open $1.tex";
+	while (<ADJUNCT>) {
+	    unless (/^\%\%\%/) {
+		print BIGBOY;
+	    }
+	}
+	close ADJUNCT;
+    } else {
+	print BIGBOY $_ . "\n";
+    }
+}
+
+close MASTER;
+close BIGBOY;

### 2009-04-16 paper/_point.pl

@@ -1,0 +1,94 @@
+open MASTER, "<calhoun_fixed_window.tex" or die "Can't even start!";
+open BIGBOY, ">calhoun_outline.tex" or die "can't open to write!";
+open TEMP, ">temp.txt";
+
+chomp($line = <MASTER>);
+until ($line =~ /\\section/) {
+    chomp($line = <MASTER>);
+}
+
+print BIGBOY "\\documentclass[11pt]{article} \n" .
+    "\\usepackage{amssymb,amsmath,amsthm,harvard,graphicx} \n" .
+    "\\setcounter{MaxMatrixCols}{10} \n" .
+    "\\setlength{\\voffset}{0.22in} \n" .
+    "\\setlength{\\hoffset}{-0.06in} \n ".
+    "\\setlength{\\topmargin}{0in} \n" .
+    "\\setlength{\\headheight}{0in}\n" .
+    "\\setlength{\\headsep}{0in}\n" .
+    "\\setlength{\\textheight}{7.33in}\n" .
+    "\\setlength{\\oddsidemargin}{0in}\n" .
+    "\\setlength{\\textwidth}{5.67in}\n" .
+    "\\input{../bib/definitions}\n" .
+    "\\input{def}\n" . 
+    "\\newcommand{\\pp}[1]{\\textbf{#1}}\n";
+
+print BIGBOY "\\begin{document}";
+print BIGBOY $line . "\\begin{itemize}\n";
+while (<MASTER>) {
+    chomp;
+    if (/\\(\w)*section/) {
+	print BIGBOY "\\end{itemize}\n" . $_ . "\n\\begin{itemize}\n";
+    } elsif (/\\context/) {
+	print BIGBOY "\\end{itemize}\n " .
+	    "\\subsection{Shared Context} \n\\begin{itemize}\n";
+    } elsif (/\\problem/) {
+	print BIGBOY "\\end{itemize}\n " .
+	    "\\subsection{Statement of Problem} \n\\begin{itemize}\n";
+    } elsif (/\\sowhat/) {
+	print BIGBOY "\\end{itemize}\n " .
+	    "\\subsection{So What?} \n\\begin{itemize}\n";
+    } elsif (/\\solution/) {
+	print BIGBOY "\\end{itemize}\n " .
+	    "\\subsection{Statement of Solution} \n\\begin{itemize}\n";
+    } elsif (/\\begin{(thm|lem|asmp)}/) {
[…]

### 2009-04-16 seminar/approximationMC.R

@@ -1,0 +1,19 @@
+load("mcGlobal.Rdata")
+
+set.seed(30)
+
+mc <- rep(NA, nsims)
+integralMC <- rmc(n = 100000)
+
+for (i in 1:nsims) {
+  d.i <- rmc()
+  
+  model <- lm(y ~ poly(x, K), data = d.i, subset = estimationWindow)
+  err <- d.i$y[-estimationWindow] - predict(model, data.frame(x = d.i$x[-estimationWindow]))
+
+  mc[i] <- sqrt(100) * (mean(err^2) - mean((integralMC$y - predict(model, integralMC))^2)) / sd(err^2)
+  print(i)
+}
+## change
+
+save.image("approximation.Rdata")

### 2009-04-16 seminar/approximationQQ.R

@@ -1,0 +1,13 @@
+library(lattice)
+load("mcGlobal.Rdata")
+load("approximation.Rdata")
+
+## generate qq-plot for simulations vs. theoretical quantiles
+png("approximationQQ.png")
+qqmath(mc, col = "black", ylab = "Simulated Values", xlab = "Theoretical Values", aspect = "1")
+dev.off()
+
+png("approximationHist.png")
+hist(mc, 70, freq = F, xlab = "Standardized Simulated Value", main = "")
+curve(dnorm(x), n = 1000, from = -4, to = 4, col = "red", add = T, lwd = 2)
+dev.off()

### 2009-04-16 seminar/outOfSampleMC.R

@@ -1,0 +1,23 @@
+load("mcGlobal.Rdata")
+
+set.seed(30)
+
+mcQuad    <- rep(NA, nsims)
+mcOverfit <- rep(NA, nsims)
+
+for (i in 1:nsims) {
+  d.i <- rmc()
+  
+  modelQuad    <- lm(y ~ poly(x, 2), data = d.i, subset = estimationWindow)
+  modelOverfit <- lm(y ~ poly(x, K), data = d.i, subset = estimationWindow)
+
+  errQuad    <- d.i$y[-estimationWindow] - predict(modelQuad,    data.frame(x = d.i$x[-estimationWindow]))
+  errOverfit <- d.i$y[-estimationWindow] - predict(modelOverfit, data.frame(x = d.i$x[-estimationWindow]))
+
+  mcQuad[i]    <- mean(errQuad^2)
+  mcOverfit[i] <- mean(errOverfit^2)
+
+  print(i)
+}
+
+save.image("simulations.Rdata")

### 2009-04-16 seminar/outOfSamplePlots.R

@@ -1,0 +1,32 @@
+load("mcGlobal.Rdata")
+
+set.seed(30)
+d <- rmc()
+
+png("blankPlot.png")
+plot(y ~ x, las = 1, data = d)
+dev.off()
+
+png("quadWindow.png")
+quadModel <- lm(y ~ poly(x, 2), subset = estimationWindow, data = d)
+plot(y~x, las = 1, type = "n", data = d)
+points(y ~ x, subset = estimationWindow, data = d)
+curve(predict(quadModel, data.frame(x = x)), add = T, from = 0, to = 3, n = 1000, col = "red", lwd = 2)
+dev.off()
+
+png("quadTest.png")
+plot(y~x, las = 1, type = "n", data = d)
+points(y ~ x, subset = -estimationWindow, data = d)
+curve(predict(quadModel, data.frame(x = x)), add = T, from = 0, to = 3, n = 1000, col = "red", lwd = 2)
+dev.off()
+
+png("overfitPlot.png")
+overfitModel <- lm(y ~ poly(x, K), subset = estimationWindow, data = d)
+plot(y ~ x, las = 1, data = d)
+curve(predict(overfitModel, data.frame(x = x)), add = T, from = 0, to = 3, n = 1000, col = "red", lwd = 2)
+dev.off()
+
+png("overfitAsymptotic.png")
+plot(y ~ x, las = 1, data = rmc(4000))
+curve(predict(overfitModel, data.frame(x = x)), add = T, from = 0, to = 3, n = 1000, col = "red", lwd = 2)
+dev.off()

### 2009-04-16 test/cw_eloss.R

@@ -1,0 +1,11 @@
+source("../R/cw_eloss.R")
+
+if (! isTRUE(all.equal(cw.eloss(c(2.237, 0.261, rep(0, 7))), 10.505)))
+  stop("Does not return correct value at true parameters")
+
+if (! isTRUE(all.equal(optim(c(2.237, 0.261, rep(0, 7)),
+                             cw.eloss,
+                             control = list(maxit = 10000),
+                             method = "SANN")$value, 10.505)))
+  stop("Optimization does not return correct value at true parameters")
+

### 2009-04-16 test/cw_table.R

@@ -1,0 +1,33 @@
+source("../R/cw_prederrors.R")
+source("../R/rcw.R")
+
+
+### test that cw.prederrors can reproduce Clark and West's (2007) Table 1
+### - for DGP 2 recursive regressions.
+
+cw.table <- matrix(byrow = TRUE, c( 80, 40, 0.024,  80, 80, 0.010,  80, 120, 0.006,  80, 160, 0.002,
+                                   120, 40, 0.030, 120, 80, 0.013, 120, 120, 0.008, 120, 160, 0.006), 8, 3)
+nstats <- dim(cw.table)[1]
+
+n <- 3000
+maxn <- max(rowSums(cw.table[,1:2]))
+minR <- min(cw.table[,1])
+teststat <- matrix(NA, n, dim(cw.table)[1])
+for (i in 1:n) {
+  d.i <- as.matrix(cw.prederrors(rcw(maxn), R = minR)^2) %*% c(1, -1)
+  for (k in 1:nstats) {
+    R <- cw.table[k,1]
+    P <- cw.table[k,2]
+    teststat[i,k] <- (sqrt(P) * mean(d.i[(R - minR) + 1:P]) / sd(d.i[(R - minR) + 1:P])) > 1.282
+  }
+  print(paste("done simulation", i, "of", n))
+}
+
+for (k in 1:nstats) {
+  bt <- binom.test(x = sum(teststat[,k]), n, p = cw.table[k,3],
+                   alternative = "t")
+  if (bt$p.value < 0.001) 
+    stop("Monte Carlo inconsistent with Clark and West --- R ", cw.table[k,1],
+         " P ", cw.table[k,2], " CI = ", signif(bt$conf[1], 2), " to ",
+         signif(bt$conf[2], 2), " but should be ", cw.table[k,3])
+}

### 2009-04-16 test/makeDataMatrices.R

@@ -1,0 +1,10 @@
+source("../empirics/makeDataMatrices.R")
+
+y <- 1:30
+x <- 301:330
+
+r <- makeDataMatrices(y,x)
+if (!(isTRUE(all.equal(r$target, 25:30))))
+  stop("incorrect target")
+if (!(isTRUE(all.equal(r$predictorMatrix, cbind(1, outer(1:6,12:1,"+"), outer(301:306,12:1,"+"))))))
+  stop("incorrect predictor matrix")

### 2009-04-16 test/rTestStat.R

@@ -1,0 +1,34 @@
+source("../mc/rTestStat.R")
+source("../mc/rcw.R")
+source("../mc/cw_eloss.R")
+library(sandwich)
+
+testvec <- rTestStat(R = 50, P = 100)
+if (!is.list(testvec))
+  stop("rTestStat does not return a vector.")
+
+if (!is.numeric(testvec$avg))
+  stop("rTestStat does not return an average loss.")
+if (!is.numeric(testvec$mR))
+  stop("rTestStat does not return mR.")
+if (!is.numeric(testvec$mT))
+  stop("rTestStat does not return mT.")
+if (!is.numeric(testvec$CE))
+  stop("rTestStat does not return CE.")
+
+testvec2 <- testvec1 <- rep(NA, 400)
+for (i in 1:400) {
+  testvec1[i] <- rTestStat(100, 1000)$mR
+  testvec2[i] <- rTestStat(10000, 80)$mT
+}
+
+if (shapiro.test(testvec1)$p.value < 0.01)
+  stop("(R) failed normality test at 1%")
+if (t.test(testvec1)$p.value < 0.01)
+  stop("(R)failed t-test that mean is zero at 1%")
+
+if (shapiro.test(testvec2)$p.value < 0.01)
+  stop("(T) failed normality test at 1%")
+if (t.test(testvec2)$p.value < 0.01)
+  stop("(T)failed t-test that mean is zero at 1%")
+

### 2009-04-16 test/rcw.R

@@ -1,0 +1,12 @@
+source("../mc/rcw.R")
+n <- 30
+
+### first check that it returns the right number of series and observations
+
+td <- rcw(n)
+if (! is.data.frame(td))
+  stop("rcw does not return a data frame.")
+if (! isTRUE(all.equal(dim(td), c(n, 2)))) {
+  stop("rcw does not return the correct dimension")
+}
+

### 2010-10-18 mc/plot-insample-size.Rnw
Revised text of paper

\documentclass{article}
\SweaveOpts{prefix.string=plots/ftest}
\usepackage[margin=1in]{geometry}

\begin{document}
Basic file that generates plots for size of the F-test

<<fig=TRUE,width=5.5, height=4>>=
library(fwPackage)
library(lattice)
ltheme <- canonical.theme(color = FALSE)     ## in-built B&W theme  
ltheme$strip.background$col <- "transparent" ## change strip bg  
lattice.options(default.theme = ltheme)      ## set as default

dbc <- dbConnect(dbDriver("SQLite"), dbname = "simulations.db")
d <- dbGetQuery(dbc, "select reject, 'T=' || n as nlabel, altlabel, norm from viewftest 
                                     where label='size' and norm in (0,1)")
d$norm <- as.factor(d$norm)

print(dotplot(norm ~ reject | interaction(altlabel,nlabel, sep = ", "),
              dat = d, las = 1,
              xlab = "Rejection Probability", ylab = "c",
              xlim = c(-.1, 1.1),
              panel = function(x, y, ...) {
                panel.dotplot(x, y, ..., type = "n")
                panel.text(x, as.numeric(y), labels = sprintf("%.2f", x))
              },
              par.strip.text = list(cex = .65),
              layout = c(2,4),
              index.cond = list(c(3,4,7,8,5,6,1,2))))
@

<<>>=
dbDisconnect(dbc)
@
\end{document}

### 2010-10-18 mc/plot-interval.Rnw
Revised text of paper

\documentclass{article}
\SweaveOpts{prefix.string=plots/interval}
\usepackage[margin=1in]{geometry}

\begin{document}
Basic file that generates plots for the out-of-sample $t$-test
centered at $E_{R}\bar D_{1}$

<<>>=
library(fwPackage)
library(lattice)
ltheme <- canonical.theme(color = FALSE)     ## in-built B&W theme  
ltheme$strip.background$col <- "transparent" ## change strip bg  
lattice.options(default.theme = ltheme)      ## set as default

dbc <- dbConnect(dbDriver("SQLite"), dbname = "simulations.db")
mcpars <- dbGetQuery(dbc, "select count(jobnumber) as njobs from interval")
dstring <- "
select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
from interval 
where label='%s' and simIndex <= %d and transform = 'difference'
group by ntest, isim, idgp, transform, label) s 
join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp"

doxyplot <- function(dplot, ...) {
  print(xyplot(I(1 - reject) ~ I(ntest/n) | interaction(nlabel, altlabel, normlabel, sep = ", "),
               data = dplot,
               ylab = "Coverage", xlab = "P/T",
               panel = function(x,y,...) {
                 panel.xyplot(x,y,...,type = "l")
                 panel.lines(c(0,2/3),c(.9,.9), col = "gray")
               },
               layout = c(4,4),
               par.strip.text = list(cex = .65),
               index.cond = list(c(13,15,16,14,9,11,12,10,5,7,8,6,1,3,4,2))))
}
@

<<testerror1, fig=TRUE, height = 3.5, width=6>>=
d <- dbGetQuery(dbc, sprintf(dstring, 'test.error.1', 500))
d$nlabel <- sprintf("T=%d", d$n)
d$normlabel <- sprintf("c=%d", d$norm)

doxyplot(d) #Empirical coverage of one-sided interval
@

<<testerror2, fig=TRUE, height = 3.5, width=6>>=
d <- dbGetQuery(dbc, sprintf(dstring, 'test.error.2', 500))
d$nlabel <- sprintf("T=%d", d$n)
d$normlabel <- sprintf("c=%d", d$norm)
doxyplot(d) #Empirical coverage of two-sided interval
@

<<generror1, fig=TRUE, height = 3.5, width=6>>=
d <- dbGetQuery(dbc, sprintf(dstring, 'gen.error.1', 500))
d$nlabel <- sprintf("T=%d", d$n)
d$normlabel <- sprintf("c=%d", d$norm)
doxyplot(d) #Empirical coverage of one-sided interval
@

<<generror2, fig=TRUE, height = 3.5, width=6>>=
d <- dbGetQuery(dbc, sprintf(dstring, 'gen.error.2', 500))
d$nlabel <- sprintf("T=%d", d$n)
d$normlabel <- sprintf("c=%d", d$norm)
doxyplot(d) #Empirical coverage of two-sided interval
@

<<>>=
dbDisconnect(dbc)
@
\end{document}

### 2010-10-18 mc/plot-oos-size.Rnw
Revised text of paper

\documentclass{article}
\SweaveOpts{prefix.string=plots/size}
\usepackage[margin=1in]{geometry}

\begin{document}
Basic file that generates plots for the out-of-sample $t$-test
centered at $E_{R}\bar D_{1}$

<<>>=
library(fwPackage)
library(lattice)
ltheme <- canonical.theme(color = FALSE)     ## in-built B&W theme  
ltheme$strip.background$col <- "transparent" ## change strip bg  
lattice.options(default.theme = ltheme)      ## set as default

dbc <- dbConnect(dbDriver("SQLite"), dbname = "simulations.db")

d <- dbGetQuery(dbc, "
select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
from interval 
where label='size' and idgp in (1,2) and transform in ('mccracken', 'clarkwest', 'difference')
group by ntest, isim, idgp, transform, label) s 
join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp")
d$nlabel <- sprintf("T=%d", d$n)
d$normlabel <- sprintf("c=%d", d$norm)

dpower <- dbGetQuery(dbc, "
select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
from interval 
where label='power' and idgp in (2,3) and transform='difference'
group by ntest, isim, idgp, transform, label) s 
join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp")
dpower$nlabel <- sprintf("T=%d", dpower$n)
dpower$normlabel <- sprintf("c=%d", dpower$norm)

# dboth <- rbind(d, dpower)

doxyplot <- function(dframe, ...) {
  print(xyplot(reject ~ I(ntest/n) | interaction(nlabel,altlabel,normlabel, sep = ", "),
               data = dframe,
               ylab = "Rejection Probability", xlab = "P/T",
               panel = function(x,y,...) {
                 panel.lines(c(0,2/3),c(.1,.1), col = "lightgray")
                 panel.xyplot(x,y,...,type = "l")
               },
               layout = c(4,4),
               par.strip.text = list(cex = .65),
               index.cond = list(c(13,15,16,14,9,11,12,10,5,7,8,6,1,3,4,2))))
}
@

Empirical size of Clark and West test at 90\% confidence
<<clarkwest, fig=TRUE, width=6>>=
doxyplot(d[d$transform == "clarkwest",])
@

Empirical size of McCracken test at 90\% confidence
<<mccracken, fig=TRUE, width=6, height=3.5>>=
  print(xyplot(reject ~ I(ntest/n) | interaction(nlabel,altlabel,normlabel, sep = ", "),
               data = d[d$altlabel=="K=3" & d$transform == "mccracken",],
               ylab = "Rejection Probability", xlab = "P/T",
               panel = function(x,y,...) {
                 panel.lines(c(0,2/3),c(.1,.1), col = "lightgray")
                 panel.xyplot(x,y,...,type = "l")
               },
               layout = c(4,2),
               par.strip.text = list(cex = .65),
               index.cond = list(c(5,7,8,6,1,3,4,2))))
## doxyplot(d[d$altlabel=="K=3" & d$transform == "mccracken",])         
@

Empirical size of Naive OOS test at 90\% confidence
<<dmwsize, fig=TRUE, width=6>>=
doxyplot(d[d$transform == "difference",])
@

Empirical power of Naive oos test at 90\% confidence
<<dmwpower, fig=TRUE, width=6>>=
doxyplot(dpower[dpower$transform == "difference",]) 
@

<<>>=
dbDisconnect(dbc)
@
\end{document}

### 2010-10-18 paper.tex
Revised text of paper

\documentclass[11pt]{article}
%\linespread{1.2}\selectfont
\usepackage{tikz}
\usetikzlibrary{calc}
\usetikzlibrary{fit}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[round,comma]{natbib}
\usepackage{setspace,amsmath,amssymb,amsthm,ifthen,subfig,url,multicol}
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{\thepage}\chead{}\rhead{}
\lfoot{}\cfoot{}\rfoot{}
\renewcommand\headrulewidth{0pt}
\onehalfspacing
\usepackage[top=1.222222in,left=0.9444444in,right=1.888889in,bottom=2.4444444in]{geometry}
\usepackage{nath}

\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{claim}[thm]{Claim}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{asmp}{Assumption}
\newtheorem{example}{Example}
\newtheorem{defn}{Definition}

\DeclareMathOperator{\E}{E}
\DeclareMathOperator{\var}{var}
\DeclareMathOperator*{\plim}{plim}
\DeclareMathOperator{\tr}{tr}
\DeclareMathOperator{\atan}{atan*}

\newcommand{\citepos}[1]{\citeauthor{#1}'s \citeyearpar{#1}}
\newcommand{\Citepos}[1]{\Citeauthor{#1}'s \citeyearpar{#1}}

%% from http://blog.blubinc.net/
% Define a command for a given term. This will create a command which gives
% the long name, with a parenthesised acronym, on the first call.
% Additionally it will redefine itself to call the acronym function instead
% on subsequent executions.
%
% Takes:
%	1, command name
%	2, long name
%	3, acronym
% ie \newacronym{ols}{Ordinary Least Squares}{OLS} will define the
% command \ols 
\newcommand{\newacronym}[3]{%
\expandafter\newcommand\expandafter{\csname #1\endcsname}{#2 \textsc{(\MakeLowercase{#3})}%
\expandafter\renewcommand\expandafter{\csname #1\endcsname}{\textsc{\MakeLowercase{#3}}}}}

\newcommand{\oost}{\ensuremath{\operatorname{oos-t}}}
\newcommand{\oosSum}[2]{\ensuremath{\sum_{#1=R-\h+#2}^{T-\h}}}

\newcommand{\h}{h}
\newcommand{\InnerBlockL}[1]{\ensuremath{R+(#1-1)b_T + 1}}
\newcommand{\InnerBlockU}[1]{\ensuremath{R+#1 b_T}}
\newcommand{\OuterBlockU}{\lfloor \frac P{b_T} \rfloor}
\newcommand{\SumOuterBlock}[1]{\ensuremath{\sum_{#1=1}^{\OuterBlockU}}}
\newcommand{\SumInnerBlock}[2]{\ensuremath{\sum_{#1=\InnerBlockL{#2}}^{\InnerBlockU{#2}}}}

\newcommand{\CEOuterBlock}[2]{\ensuremath{\E_{\InnerBlockU{(#2-1)}} #1}}

\newcommand{\CenteredAverage}{\frac{\bar{D}_1 - \E_T\bar{D}_2}{\hat\sigma / \sqrt{P}}}
\newcommand{\CenteredAverageI}{\ensuremath{\frac{1}{\hat\sigma
    \sqrt{P}}\oosSum{t}{1} (D_{tR} - \E_R D_{tR})}}
\newcommand{\CenteredAverageII}{\ensuremath{\frac{\sqrt{P}}{\hat\sigma}
    (\E_R\bar D_1 - \E_T\bar{D}_2)}}

\newcommand{\MixingaleArray}[1]{\ensuremath{}}

\newcommand{\ZSummand}{D_{sR} - \E_R D_{sR}}
\newcommand{\ZDef}{ \frac1{\sqrt{P}} \SumInnerBlock{s}{i} [\ZSummand]}
\newcommand{\ZSqCE}{\ensuremath{\CEOuterBlock{Z_i^2}{i}}}
\newcommand{\ZTrunc}{\ensuremath{C\sqrt{b_{T}/P}}}
\newcommand{\PScaleTerm}{\ensuremath{\frac{C \sqrt{b_T}}{P}}}

\newcommand{\vWeight}{W((t-s)/\gamma)}
\newcommand{\vSummand}{\ensuremath{(D_{tR} - \E_R D_{tR})(D_{sR} - \E_R D_{sR}) \vWeight}}
\newcommand{\kernelBDefn}[1]{\ensuremath{\frac1{\delta\sqrt{2\pi}}e^{-\frac{#1^2}{2\delta^2}}}}
\newcommand{\kernelB}[1]{\ensuremath{\eta_{\delta}(#1)}}

\newcommand{\vtSum}{\ensuremath{\sum_{t=-P+1}^{2P}}}
\newcommand{\vtSumr}{\ensuremath{\sum_{i=1}^r}}
\newcommand{\vtSuma}{\ensuremath{\sum_{t=(2i-2)b_T-P+1}^{(2i-1)b_T-P}}}
\newcommand{\vtSumb}{\ensuremath{\sum_{t=(2i-1)b_T-P+1}^{2ib_T-P}}}
\newcommand{\vttLower}{\ensuremath{\max(1-t,-b_T)}}
\newcommand{\vttUpper}{\ensuremath{\min(P-t,b_T)}}

\newcommand{\varianceTermIDefn}{\ensuremath{\frac1{P}\oosSum{s,t}{1}
    \vSummand}}
\newcommand{\varianceTermI}{\ensuremath{\sigma_{0\delta}^2}}
\newcommand{\varianceTermII}{\ensuremath{\sigma_{1\delta}^2}}
\newcommand{\varianceTermIIa}{\ensuremath{\frac1{\sqrt{P\gamma}}
    \sum_{l=\max(1-t,-P)}^{\min(P-t,P)} (D_{t+l+R,R} - \E_R D_{t+l+R,R})
    W(l/\gamma)}}
\newcommand{\varianceTermIIb}{\ensuremath{\frac1{\sqrt{P\gamma}}
    \sum_{j=1-t}^{P-t} (D_{t+j+R,R} - \E_R D_{t+j+R,R})
    \kernelB{j/\gamma}}}
\newcommand{\varianceTermIII}{\ensuremath{\sigma_{2\delta}^{2}}}
\newcommand{\varianceTermIIIa}{\ensuremath{\frac1{\sqrt{P\gamma}}
    \sum_{l=\vttLower}^{\vttUpper} (D_{t+l+R,R} - \E_R D_{t+l+R,R})
    W(l/\gamma)}}
\newcommand{\varianceTermIV}{\ensuremath{\sigma_{3\delta}^{2}}}
\newcommand{\varianceTermIVb}{\ensuremath{\frac1{\sqrt{P\gamma}}
    \sum_{j=\vttLower}^{\vttUpper} (D_{t+j+R,R} - \E_R D_{t+j+R,R})
    \kernelB{j/\gamma}}}
\newcommand{\vtIIIsummand}{\ensuremath{(Z_{1t}Z_{2t} - \E_RZ_{1t}Z_{2t})}}

\newcommand{\varianceDiffA}{\ensuremath{\frac1{P} \oosSum{s,t}{1}
    \lvert (D_{tR} - \E_R D_{tR})(\E_R D_{sR} - \bar D_1) \rvert
    \vWeight}}
\newcommand{\varianceDiffAi}{\ensuremath{\frac1P \oosSum{s}{1}(\E_R
    D_{sR} - \bar D_1 )^2}}
\newcommand{\varianceDiffAii}{\ensuremath{\frac1P \oosSum{s}{1}
    (D_{sR} - \E_R D_{sR})^2}}

\newcommand{\rhoExp}{\ensuremath{\frac{\rho-2}{2\rho}}}
\newcommand{\absReg}{\ensuremath{\frac\rho{\rho-2}}}

\newcommand{\couplingConstant}{\ensuremath{2^{\frac{1+\rho}{\rho}} B_L}}
\newcommand{\couplingBeta}[1]{\ensuremath{\beta^{\frac{\rho-2}{2\rho}}_{#1}}}
\newcommand{\couplingBetaSq}[1]{\ensuremath{\beta^{\frac{\rho-2}{\rho}}_{#1}}}
\newcommand{\couplingBound}[1]{\couplingConstant \couplingBeta{#1}}

\newcommand{\OCoef}{\ensuremath{O_p(\frac{\sqrt{P}}{T})}}

\newcommand{\bh}[1]{\ensuremath{\hat\theta_{#1}}}
\newcommand{\ep}[1]{\ensuremath{\boldsymbol{\varepsilon}_{#1}}}

\newcommand{\olsMatrix}[2]{\ensuremath{(#1'#1)^{-1}#1'#2}}

\newcommand{\dmw}{\textsc{dmw}}
\newcommand{\ols}{\textsc{ols}}
\newcommand{\mds}{\textsc{mds}}
\newcommand{\clt}{\textsc{clt}}
\newcommand{\lln}{\textsc{lln}}
\newacronym{VAR}{Vector Autoregression}{VAR}
\newacronym{oos}{out-of-sample}{OOS}
\newcommand{\dgp}{\textsc{dgp}}
\newcommand{\hac}{\textsc{hac}}
\newacronym{ned}{Near Epoch Dependent}{NED}
\newacronym{mse}{Mean Squared Error}{MSE}
\newcommand{\sfield}{$\sigma$-field}
\newcommand{\sfields}{\sfield s}
\renewcommand{\Re}{\ensuremath{\mathbb{R}}}

\frenchspacing \title{Out-of-Sample Comparisons of Overfit Models}
\author{Gray Calhoun\thanks{email: \texttt{gcalhoun@iastate.edu}. I
    would like to thank Julian Betts, Marjorie Flavin, Nir Jaimovich,
    Lutz Kilian, Michael McCracken, Seth Pruitt, Ross Starr, Yixiao
    Sun, Allan Timmermann, participants at the 2010 Midwest Economics
    Association Annual Meetings, the 2010 Joint Statistical Meetings,
    and in many seminars at \textsc{ucsd}, and espeically Graham
    Elliott for their valuable suggestions, feedback and advice in
    writing this paper.  I would also like to thank Amit Goyal for
    providing computer code and data for his 2008 RFS paper with Ivo
    Welch \citep{goyal-welch-2008-rfs}.} \\ Iowa State University,
  Economics Department}

\begin{document}
\maketitle

\begin{abstract}\thispagestyle{empty}\noindent
  This paper uses dimension asymptotics to study why overfit linear
  regression models should be compared out-of-sample; we let the number of
  predictors used by the larger model increase with the number of
  observations so that their ratio remains uniformly positive.  Under
  this limit theory, the naive Diebold-Mariano-West out-of-sample test
  can test hypotheses about a key quantity for evaluating forecasting
  models---a time series analogue to the generalization error---as
  long as the out-of-sample period is small relative to the total
  sample size.  Moreover, tests that are designed to reject if the
  larger model is true, such as the usual in-sample Wald and
  \textsc{lm} tests and also Clark and McCracken's (2001, 2005a),
  \citepos{mccracken_asymptotics_2007} and Clark and West's (2006,
  2007) out-of-sample statistics, will choose the larger model too
  often when the smaller model is more accurate.

\noindent \textsc{jel} Classification: C12, C22, C52, C53

\noindent Keywords: Generalization Error, Forecasting, Model
Selection, t-test, Dimension Asymptotics
\end{abstract}

\section{Introduction}\label{sec:introduction}
Consider two sequences of length $P$ of prediction errors, the result
of forecasting the same variable with two different estimated models.
Both models are estimated with $R$ observations, collectively called
the {\em estimation window}, and are used to forecast an additional
$P$ observations, called the {\em test sample}.  There are $T$
observations in all, and $R+P=T$.  This paper introduces a new limit
theory for statistics constructed from these prediction errors
designed to approximate the behavior of the statistics when one of the
models is overfit.  In doing so, we provide a theoretical
justification for forecasters to use \oos\ instead of
in-sample comparisons.

Although \oos\ comparisons have been popular in macroeconomics and
finance since \citepos{meese_empirical_1983} seminal study of exchange
rate models, it is unclear from a theoretical perspective whether or
not the statistics are useful.  Empirical researchers often cite
``overfit'' or ``instability'' as reasons for using \oos\ comparisons,
as in \citet{stock_forecasting_2003}, but neither term is precisely
defined or formalized.  Compounding this problem, the asymptotic
distributions of these statistics are derived under conditions that
rule out either instability or overfit and allow a researcher to use a
conventional in-sample comparison---a variation of the F-test, for
example.  As \citet{inoue_kilian_2004} argue, the statistics
themselves are designed to test hypotheses that can be tested by these
in-sample statistics.  For example, \citet{diebold_comparing_1995} and
\citet{west_asymptotic_1996} derive the limiting distributions of many
popular \oos\ test statistics under conditions that would justify
these full-sample tests.\footnote{In this paper, we will refer to
  their basic \oos\ $t$-test as the \dmw\ test.}  Much of the
subsequent research by \citet{chao_out_2001},
\citet{clark_tests_2001,clark_evaluating_2005},
\citet{corradi_consistent_2002,corradi_recent_2004},
\citet{clark_using_2006,clark_approximately_2007},
\citet{mccracken_asymptotics_2007}, \citet{anatolyev_inference_2008},
and others relaxes several of Diebold and Mariano's and West's
assumptions, but maintains the stationarity and dependence conditions
that permit in-sample comparisons.\footnote{Like us,
  \citet{anatolyev_inference_2008} allows the number of regressors to
  increase with $T$.  But in that paper, they increase slowly enough
  that the \ols\ coefficients are consistent and asymptotically
  normal.}  \citet{giacomini_tests_2006}, and
\citet{giacomini-rossi-2009-REStud,giacomini-rossi-2010-JAppliedEconometrics}
are exceptions.  Instead of focusing on hypotheses that can be tested
by in-sample comparisons, \citet{giacomini_tests_2006} derive an \oos\
test for the null hypothesis that the difference between two models'
\oos\ forecasting performance is unpredictable, a martingale
difference sequence, \citet{giacomini-rossi-2009-REStud} test whether
the \oos\ forecasting performance of a model suffers from a breakdown
relative to its in-sample performance, and
\citet{giacomini-rossi-2010-JAppliedEconometrics} test whether the
forecasting performance is stable. However, those papers focus on a
particular \oos\ estimation strategy and do not address why naive
\oos\ comparisons might be generally useful.

Since in-sample and \oos\ statistics require similar assumptions and
test similar hypotheses, one might expect that they would give similar
results.  They do not.  Generally in-sample analysis supports more
complicated theoretical models and \oos\ analysis supports simple
benchmarks, as seen in \citet{meese_empirical_1983},
\citet{stock_forecasting_2003}, and \citet{goyal-welch-2008-rfs}.
Since these different approaches strongly influence the outcome of
research, it is important to know when each is appropriate.  The
explanations in favor of \oos\ comparisons claim that they should be
more robust to unmodeled instability
\citep{clark_power_2005,giacomini_tests_2006,giacomini-rossi-2009-REStud,giacomini-rossi-2010-JAppliedEconometrics}
or to overfit \citep{mccracken_data_1998,clark_can_2004}.  Both
explanations presume that the in-sample comparison is invalid and the
\oos\ comparisons are more reliable.  Of course, as
\citet{inoue_kilian_2004,inoue_selection_2006} point out, both
in-sample and \oos\ methods could be valid, but the \oos\ methods
could have lower power.

In this paper, we study the ``overfit'' possibility and leave
``instability'' to future research. This paper uses dimension
asymptotics to study the behavior of \oos\ comparisons when at least
one of the models is overfit---when the number of its regressors
increases with the number of observations so that their ratio remains
positive.  We focus on linear regression models estimated with a fixed
training window, but our basic conclusions should be true for other
estimation strategies and models as well.  We show that the usual
\oos\ average is asymptotically normal and can consistently estimate
the difference between the models' expected loss in periods
$T+1,T+2,\dots$ conditional on the on the data available in period
$T$, a time-series analogue to the generalization error.\footnote{See,
  for example, \citet{elemstatlearning}.}  Under these asymptotics,
the generalization error does not converge to the expected performance
of the pseudo-true models, so the in-sample and \oos\
comparisons measure different quantities and should be expected to
give different results for reasons beyond simple size and power
comparisons.  Under our theory, the model that is closer to the true
\dgp\ in population can forecast worse.  In such a situation, an
in-sample comparison would correctly reject the null hypothesis that
the benchmark is true, and an \oos\ comparison would correctly fail to
reject the null that the benchmark is more accurate.\footnote{In a
  pair of papers similar to ours,
  \citet{RePEc:fip:fedkrw:rwp09-10,RePEc:fip:fedkrw:rwp09-11} study
  in-sample and \oos\ tests that the larger model has nonzero
  coefficients that are too close to zero to expect the model to
  forecast more accurately.  Like this paper, they argue that the
  larger model can be true but less accurate.  However, they focus on
  an aspect of the \dgp\ that makes this phenomenon likely, while we
  focus on the coefficient estimates that produce less accurate
  forecasts.}

This result justifies \oos\ comparisons when researchers want to
choose a model for forecasting.  Although there has been little
emphasis on hypothesis testing in these settings, testing is usually
appropriate: there is usually a familiar benchmark model in place, and
the cost of incorrectly abandoning the benchmark for a less accurate
alternative model is higher than the cost of incorrectly failing to
switch to a more accurate alternative.\footnote{These costs can be
  monetary, in the form of computer upgrades, software installation,
  and training, or they can be reputational costs.}
We show that the \dmw\ test lets the forecaster control the
probability of the first error, just as with conventional hypothesis
testing.

However, since the models' coefficients are imprecisely
estimated, the test sample must be small to ensure that the model
estimated over the training sample is similar to the one that will be
estimated over the full sample.  In particular, $P/T \to 0$ is
required for consistent estimation, and $P^2/T \to 0$ is required for
valid confidence intervals and inference.  For larger $P$, the \oos\
comparisons remain asymptotically normal, but are centered on the
forecasting performance associated with the period-$R$ estimates.  In
practice, researchers typically use large values of $P$, so these
studies may be too pessimistic about their models' future accuracy if
they use the \dmw\ test.  Section~\ref{sec:oostheory} lays out the
asymptotic behavior of the \dmw\ test under this limit theory.

Under this asymptotic theory, the \ols\ coefficient estimator is no
longer consistent or asymptotically normal \citep{huber_robust_1973},
so this is a useful way to model overfit and imprecisely estimated
models.  Moreover, \citet{efron_biased_1986,efron_estimation_2004}
shows that in-sample comparisons overestimate models' accuracy by a
factor proportional to this ratio.  Despite the non-normality of the
coefficient estimators, modifications of the F-test are valid under
this asymptotic theory, as shown by \citet{boos_anova_1995},
\citet{akritas_asymptotics_2000},
\citet{akritas_heteroscedastic_2004}, and
\citet{calhoun_hypothesis_2009}, among others.  The F-test and Wald
tests are no longer asymptotically valid themselves.  Such results
establish that hypotheses about the parameters of the \dgp\ can be
tested in-sample even if one or both models are overfit.  For that
very reason, these tests can not reliably choose a model for
forecasting and will reject the benchmark too often.  We show this
analytically in Section~\ref{sec:insample}.  Moreover, under this
asymptotic theory, many recent \oos\ test statistics, such as those
derived by \cite{clark_tests_2001,clark_evaluating_2005},
\citet{mccracken_asymptotics_2007}, and
\citet{clark_using_2006,clark_approximately_2007} should behave like
the F-test.  These tests are also designed to reject the benchmark
when the alternative model is true, and so they may reject too often
when the benchmark is false but more accurate.  Obviously, since the
distribution of these statistics converges to the normal when $P/T \to
\infty$ (with the number of regressors fixed), these statistics behave
like the \dmw\ test when $P$ is small, but should over-reject the
benchmark when $P$ is large.  Section~\ref{sec:mc} presents
simulations that support these claims.

Finally, this paper also introduces a new method of proof for \oos\
statistics.  We use a coupling argument (Berbee's Lemma, 1979) to show
that sequences of \oos\ loss behave like mixingales when the
underlying series are absolutely regular, even if the forecasts depend
on non-convergent estimators.  Moreover, transformations of these
processes also behave like mixingales, so asymptotic results for \ned\
functions of mixing processes can be used for these \oos\ processes
with only slight modification.  Although we only present a proof that
this mixingale result holds for the fixed-window scheme, it is simple
to extend it to other estimation windows.

The rest of the paper proceeds as follows.
Section~\ref{sec:assumptions} introduces our notation and assumptions.
Section~\ref{sec:theory} gives the main theoretical results for the
\dmw\ \oos\ test and shows that the F-test rejects the benchmark model
too often when it is false but more accurate than the
alternative. Section~\ref{sec:mc} presents a Monte Carlo study
supporting our theoretical results.  Section~\ref{sec:empirics}
applies the \oos\ statistic to \citepos{goyal-welch-2008-rfs} dataset
for equity premium prediction, and Section~\ref{sec:conclusion}
concludes.  Proofs and supporting results are listed in the Appendix.

\section{Setup and Assumptions}\label{sec:assumptions}
We will set up our models and notation first, then list the assumptions
required for our results.  There are two competing linear models that
give forecasts for the target, $y_{t+\h}$:
\[
y_{t+\h} = x_{1t}'\theta_1 + \varepsilon_{1,t+h}
\]
and
\[
y_{t+\h} = x_{2t}'\theta_2 + \varepsilon_{2,t+h};
\]
$\h$ is the forecast horizon, and the variables $y_t$, $x_{1t}$, and
$x_{2t}$ are all known in period $t$.  Let
\begin{equation*}
  \mathcal{F}_t = \sigma(y_1, x_1, \dots, y_t, x_t)
\end{equation*}
with $x_t$ the vector of all elements of $x_{1t}$ and $x_{2t}$ after
removing duplicates, and let $\E_t$ and $\var_t$ denote the
conditional mean and variance given $\mathcal{F}_t$.  The first model
uses $K_1$ regressors, and the second uses $K_2$.  Without loss of
generality, assume that $K_1 \leq K_2$.  We will allow $K_1$ and $K_2$
to vary with $T$, so a stochastic array underlies all of our
asymptotic theory, but we suppress that notation to make the
presentation more clear.

Although our theory can apply to many different \oos\ statistics,
we'll only present results for the \dmw\ \oos\ $t$-test.  Both models
are estimated using \ols\ over the training sample:
\[
\hat y_{i,t+\h} = x_{it}'\bh{iR}, \quad i=1,2, \quad t = R+1,\dots,T-h
\]
with
\[
\bh{it} = (\sum_{s=1}^{t-\h} x_{is}x_{is}')^{-1} \sum_{s=1}^{t-\h} x_{is} y_{s+\h},
\quad i=1,2.
\]
The \oos\ average is denoted $\bar D_1$:
\[
\bar D_1 \equiv P^{-1} \oosSum{t}{1} D_{tR}
\quad \text{with} \quad D_{tS} \equiv L(y_{t+\h} - x_{1t}'\bh{1S}) -
L(y_{t+\h} - x_{2t}'\bh{2S}),
\]
$P = T - R$ and $L$ a known loss function.  The \oos\ statistic
of interest is 
\[
\oost \equiv \frac{\sqrt{P} \bar D_1}{\hat\sigma},
\]
for $\hat\sigma^2$ some (possibly Heteroskedasticity- and
Autocorrelation-Consistent, or \hac) estimator of the asymptotic
variance of $\bar D_1$.

We'll show that \oost\ can be used to test whether the models will
forecast equally accurately in the future.  Specifically, assume that
whichever model is chosen will be used for an additional $Q$ periods
in the future and let $\bar D_2$ denote the difference in average
performance over those periods:
\[
\bar D_2 \equiv Q^{-1} \sum_{t=T+1}^{T+Q} D_{tT}.
\]
Note that $\bar D_1$ depends on the training sample estimators,
$\hat\theta_{iR}$, and $\bar D_2$ depends on the full sample
estimators, $\hat\theta_{iT}$.  A forecaster has access to the
information set $\mathcal{F}_T$ when deciding between the two
forecasting models, but $\mathcal{F}_T$ does not contain $\bar D_2$.
So a forecaster should decide between the models based on the
conditional expectation, $\E_T \bar{D}_2$. If this quantity is
positive, the first model is expected to perform worse in the future,
and if it is negative the second is.

When the underlying series is i.i.d., this random variable, $\E_T
\bar{D}_2$, is equal to the difference in the models' generalization
error.  The generalization error of model $i$ is defined as
\begin{equation*}
  \E_{T} L(y_{T+\h}^{*} - x_{iT}^{*\prime}\hat{\theta}_{iT})
\end{equation*}
where $(y_{T+\h}^{*},x_{iT}^{*})$ has the same joint distribution as
$(y_{T+\h}, x_{iT})$ but is independent of $\mathcal{F}_T$.  Note that
$\hat{\theta}_{iT}$ is known in period $T$, so the generalization
error conditions on the observed coefficient estimates.  With
dependence, the coefficient estimates may be informative about future
values of $y_{t+\h}$ and $x_{it}$, but this influence dies out as $Q$
grows.  Conditional performance measures like these are especially
appropriate in areas like time-series economics where the forecaster
knows the coefficient values when choosing a model, but would be less
appropriate if the models will be re-estimated over an entirely new
dataset before forecasting.

Before stating the main theoretical assumptions, we define some more
notation.  The $l_v$-norm for vectors in $\Re^p$ (with $p$ arbitrary)
is denoted $\lvert \cdot \rvert_v$, and the $L_v$-norm for
$L_v$-integrable random variables is $\lVert \cdot \rVert_v$.  The
functions $\lambda_i(\cdot)$ take a square-matrix argument and return
its $i$th eigenvalue (with $\lambda_{i}(A) \leq \lambda_{i+1}(A)$ for
any matrix $A$).
All limits are taken as $T \to \infty$ unless stated otherwise.

We assume the next conditions hold throughout the paper.  The first
assumption controls the dependence of the underlying random array.
The second prevents the sequence of experiments from becoming
degenerate as $T$ increases.  The third assumption controls the
smoothness of the loss function and bounds the moments of the
difference in the models' performance; the fourth assumption describes
the behavior of the estimation and test windows.  The last assumption
describes the kernel used to estimate the \oos\ average's asymptotic
variance.

\begin{asmp}\label{asmp-1} 
  The random array $\{y_t,x_t\}$ is stationary and
  absolutely regular with coefficients $\beta_j$ of size
  $-\rho/(\rho-2)$; $\rho$ is greater than two and discussed further
  in Assumption \ref{asmp-3}.  Also, $K_1$ and $K_2$ are less than $R$,
  and $\frac{K_2}{T}$ and $\frac{K_2-K_0}{T}$ are uniformly positive;
  $K_0$ is the number of regressors shared by the two models ($K_1/T$
  can be uniformly positive as well, but is not required to be).
\end{asmp}

The first assumption is a standard condition on the dependence of the
underlying stochastic array.  We assume that the array is absolutely
regular instead of strong mixing, which is more common in
econometrics, because absolute regularity admits a particular coupling
argument \citep{berbee_random_1979} that is unavailable for strong
mixing sequences.

Assumption \ref{asmp-2} rules out uninteresting cases where the
forecast error vanishes.
\begin{asmp}\label{asmp-2}
  The variance of $y_{t+\h}$ given $\mathcal{F}_t$ is uniformly
  positive and finite, and all of the eigenvalues of the covariance
  matrix of $x_t$ are uniformly positive and finite as well.  The
  Euclidean norms of the pseudo-true coefficients, $\theta_1$ and
  $\theta_2$, satisfy $|\theta_1|_2 = O(1)$ and $|\theta_2|_2 = O(1)$.
  Moreover, there exist a $\delta > 0$ and finite $\Delta$ such that
  \begin{equation*}
    \lVert \lambda_{\max}(X_{iS_{T}}'X_{iS_{T}}) \rVert_{4+\delta}
    \leq S_{T}\, \Delta \\
    \lVert
    \lambda_{\max}(X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})
    \rVert_{4+\delta} \leq S_{T}\, \Delta \\
    \lVert \lambda_{\max}((X_{iS_{T}}'X_{iS_{T}})^{-1}) \rVert_{4+\delta} \leq \Delta/S_{T} \\
    \lVert
    \lambda_{\max}((X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})^{-1})\rVert_{4+\delta}
    \leq \Delta/S_{T}
  \end{equation*}
  for all $S_{T} \geq K_{2T}$ and large enough $T$, with $i =
  1,2$,
  \[ X_{iT} \equiv [x_{i1} \quad \dots \quad x_{i,T-\h}]' \]
  and
  \[ \ep{iT} = (\varepsilon_{i,1+\h}, \dots, \varepsilon_{i,T})'.\]
\end{asmp}

The assumption that $y_{t+\h}$ and $x_t$ have positive and finite
variance is straightforward.  The conditions on the eigenvalues are
technical and control the behavior of the \ols\ estimator as the
number of regressors gets large.  The restrictions on the pseudo-true
coefficients ensure that the regression model doesn't dominate the
variance of $y_{t+\h}$ in the limit.

\begin{asmp}\label{asmp-3}
  The loss function $L$ is continuous and has finite left and right
  derivatives almost everywhere.  Also, $L(0) = 0$, and there is a
  constant $B_L$ such that
  \begin{equation*}
    \|D_{R+j,R}\|_\rho \leq B_L \quad\text{and}\quad
    \|D_{T+j,T}\|_\rho \leq B_L.
  \end{equation*}
  for all $j \geq 1$.
\end{asmp}

This third assumption establishes basic moment and smoothness
conditions for the \oos\ loss.  The differentiability
condition is weak and allows the loss function itself to be
nondifferentiable; for example, absolute error and many asymmetric loss functions
satisfy this assumption.

\begin{asmp} \label{asmp-4} $P\to\infty$,
  $R\to\infty$, $Q\to\infty$, $P^2/T \to 0$, and $P = O(Q)$ as $T \to \infty$.
\end{asmp}

The requirements that $P$ and $R$ grow with $T$ are common.  Parts of
the assumption are new, in particular the requirement that $P^2/T \to
0$.  See Lemma \ref{res-convergence} for a discussion of its
implications.  In practical terms, this assumption requires that the
test sample be large, that the forecaster plans to use the model for
many periods in the future, and that there is enough data that
including or excluding the test sample does not affect the estimates
of $\theta_1$ or $\theta_2$ very much.

The next assumption restricts the class of variance estimators we will
consider.  We use the same class of estimators studied by
\citet{de_jong_consistency_2000} (their class $\mathcal{K}$); see
their paper for further discussion.

\begin{asmp}
  \label{asmp-5} $W$ is a kernel from 
$\Re$ to $[-1,1]$ such that $W(0) = 1$, $W(x) = W(-x)$ for all $x$,
\begin{equation*}
    \int_{-\infty}^{\infty} \lvert W(x) \rvert dx < \infty, \quad
    \int_{-\infty}^{\infty} \lvert \psi(x) \rvert dx < \infty
\end{equation*}
with
\begin{equation*} \psi(x) = \frac1{\sqrt{2\pi}} \int_{-\infty}^{\infty} W(z) e^{ixz}dz,
\end{equation*}
and $W(\cdot)$ is continuous at 0 and all but a finite number of
points.
\end{asmp}

\section{Theoretical Results}\label{sec:theory}
The main result of the paper is Theorem
\ref{res-confidence-intervals}, which shows that the \oos\ average is
asymptotically normal and centered on $E_T \bar D_2$.  This result
holds even for nested models and can be used to construct confidence
intervals or test hypotheses.  After presenting Theorem
\ref{res-confidence-intervals}, we explain and present two key Lemmas
used in its proof that add some insight into the nature of \oos\
comparisons, and then show that standard \hac\ \oos\ estimators can be
used to consistently estimate the asymptotic variance of the \oos\
average.  We then show that the F-test does not let researchers test
hypotheses about $E_{T} \bar D_2$ when the models are overfit.  In
fact, in the limit it rejects a more-accurate but false benchmark
model almost surely.

\subsection{Behavior of DMW Test with Overfit}\label{sec:oostheory}
Our first theorem justifies using the \dmw\ $t$-test with a a short
test sample.

\begin{thm}\label{res-confidence-intervals}
  Suppose that Assumptions \ref{asmp-1}--\ref{asmp-4} hold, that
  $\hat\sigma$ is an estimator satisfying
  \[
    \hat\sigma^2 = \sigma^2 + o_p(1), \quad \text{with}\quad 
    \sigma^2 \equiv \var_R(\sqrt{P} \bar D_1),
  \]
  and that $\sigma^2$ is uniformly a.s. positive.  Then
  \[
  \frac{\bar{D}_1 - \E_T\bar{D}_2}{\hat\sigma / \sqrt{P}}
  \to^d N(0,1).
  \]
  Consequently, each of the usual Gaussian confidence intervals,
  \begin{eqnarray}
  &&[\bar{D}_1 - z_{\alpha/2} \, \hat\sigma /
      \sqrt{P}, \bar{D}_1 + z_{\alpha/2} \hat\sigma / \sqrt{P}],\label{interval-twosided} \\
  &&[\bar{D}_1 - z_{\alpha} \, \hat\sigma / \sqrt{P}, +\infty), \label{interval-greater}
  \end{eqnarray}
  and
  \begin{equation} (-\infty, \bar{D}_1 + z_{\alpha}
      \, \hat\sigma / \sqrt{P}],
  \end{equation}
  contains $\E_T\bar{D}_2$ with probability $\alpha$ in the limit,
  with $z_{\alpha}$ the $1-\alpha$ quantile of the standard normal
  distribution.
\end{thm}
The requirement that $\sigma^2$ be uniformly a.s. positive is
not restrictive under our asymptotic theory.  Since the models'
coefficients are estimated with uncertainty in the limit, the two
models give different forecasts even if they both nest the \dgp.  This
is similar to \citepos{giacomini_tests_2006} rolling-window result,
but comes from different asymptotics.

This result allows forecasters to use the \dmw\ test to conduct
inference about the models' accuracy.  Since the \oos\ average,
$\bar D_1$, is asymptotically normal and centered on the expected
future performance, $t$-tests constructed from the \oos\ errors
necessarily test hypotheses about $\E_T \bar{D}_2$ and not the
performance of the pseudo-true models or the unconditional
performance of the models.

The application to testing can be expressed as a corollary:
\begin{cor}\label{res:oostest}
Suppose that the conditions of Theorem \ref{res-confidence-intervals}
hold.  Then
\begin{equation}
  \Pr[\sqrt{P}\bar D_{1}/\hat\sigma \geq z_{\alpha} \mid \E_{T}
  \bar{D}_{2} \leq 0] \to^p \alpha.
\end{equation}
\end{cor}

Two intermediate Lemmas will help us understand Theorem
\ref{res-confidence-intervals} better.  Its proof consists of two
steps: we can write
\begin{equation}
  \sqrt{P} (\bar{D}_1 - \E_T \bar{D}_2) = \sqrt{P} (\bar{D}_1 - \E_R
  \bar{D}_1) + \sqrt{P} (\E_R \bar{D}_1 - \E_T \bar{D}_2),
\end{equation}
so Theorem~\ref{res-confidence-intervals} holds if
\begin{equation}\label{normalpart}
  \sqrt{P}\frac{\bar{D}_1 - \E_R \bar{D}_1}{\sigma} \to^d N(0,1)
\end{equation}
and
\begin{equation}\label{coefpart}
  \E_R \bar{D}_1 = \E_T \bar{D}_2 + o_p(P^{-\frac12}).
\end{equation}
The first Lemma first shows that the process $\{D_{tR} - \E_R \bar
D_1\}$ is an $L_2$-mixingale of size $-1/2$ that satisfies a \clt,
ensuring~\eqref{normalpart}.  The second shows that~\eqref{coefpart}
holds under Assumption~\ref{asmp-4}.

\begin{lem}\label{res-mixingale}
  Part 1: If Assumptions~\ref{asmp-1}--\ref{asmp-3} hold then the inequality
  \begin{equation}\label{mixingaleR}
    \lVert \E_{R+j-l}(D_{R+j,R} - \E_R D_{R+j,R}) \rVert_2 \leq
    \couplingConstant \;
    \zeta_l
  \end{equation}
  with $\zeta_l = O(l^{-\frac12 - \delta})$ holds for some positive
  $\delta$, any positive $j$, and any $l$ between 0 and $j$.  As a
  consequence, $\{D_{t,R} - \E_R D_{t,R}, \mathcal F_t\}$ is an
  $L_2$-mixingales of size $-1/2$.

  \noindent Part
  2: Moreover,~\eqref{normalpart} holds under
  Assumptions~\ref{asmp-1}--\ref{asmp-3} if $P \to \infty$ as $T \to
  \infty$ and $\sigma^2$ is a.s. uniformly positive.
\end{lem}

Mixingales satisfies a weak-dependence condition similar to \mds es
and were introduced and studied extensively by
\citet{mcleish_dependent_1974,mcleish_invariance_1975,mcleish_maximal_1975,mcleish_invariance_1977}.
This lemma shows that the estimation uncertainty introduces dependence
into the \oos\ forecast errors, but that additional dependence is
contained in the term $\E_R \bar D_1$ and can be effectively removed
by subtraction.  The second part of the Lemma shows that the basic
mixingale \clt\ established by \citet{de_jong_central_1997} applies in
this setting.\footnote{De Jong proves two \clt s: one for mixingales
  and one for \ned\ functions of mixing processes.  His mixingale
  result makes assumptions about the behavior of the sample second
  moment that arise as consequences of \ned.  The proof of
  Lemma~\ref{res-mixingale} shows that the arguments used for de
  Jong's \ned\ \clt\ continue to hold for our \oos\ process---in
  effect, that the \oos\ process has slightly more structure than
  required for it to be a mixingale.}

\begin{lem} \label{res-convergence} Suppose that Assumptions
  \ref{asmp-1}--\ref{asmp-4} hold.  Then
\begin{equation*}
  \E_T \bar{D}_2 - \E_R \bar D_1 =  O_p(\sqrt{P/T}) +
  o_p(P^{-\frac12}) + o_p(Q^{-\frac12}).
\end{equation*}
\end{lem}

The justification for Lemma~\ref{res-convergence} is intuitive.  In
the limit, the difference between $\E_T \bar{D}_2$ and $\E_R \bar D_1$
comes from the coefficient estimators used: $\E_T\bar{D}_2$ is the
expected performance using the full-sample estimate, $\hat{\theta}_T$,
and $\E_R \bar D_1$ is the performance using the period-$R$ estimate,
$\hat{\theta}_R$.  When $P$ and $Q$ are large, the dependence between
the test and training samples vanishes, so the estimators of $\theta$
are the only variables affected by the conditioning $\sigma$-fields,
$\mathcal{F}_R$ and $\mathcal{F}_T$.  Since $L$ is smooth, the
difference between $\E_R \bar D_1$ and $\E_T \bar D_2$ is of order
$\lvert \hat\theta_R - \hat\theta_T \rvert_2$, which itself is of
order $\sqrt{\frac{P}{T}}$.

Finally, for Theorem \ref{res-confidence-intervals} to be useful, we
need a consistent estimator of $\sigma^2$. Lemma
\ref{res-variance-estimator} establishes that the usual \oos\ \hac\
variance estimators are consistent.\footnote{As with
      Lemma~\ref{res-mixingale}, the proof of this lemma takes
      \citepos{de_jong_consistency_2000} existing consistency results
      for \ned\ processes and shows that the same arguments can be
      applied to our \oos\ mixingale.}

\begin{lem}
  \label{res-variance-estimator}  Suppose Assumptions \ref{asmp-1},
  \ref{asmp-2}, \ref{asmp-3}, and \ref{asmp-5} hold, that $\gamma, P$
  and $R \to \infty$ as $T \to \infty$, and that $\gamma = o(P)$.  Then
  \begin{equation*}
    \frac1P \oosSum{s,t}{1} (D_{tR} - \bar D_1)(D_{sR} - \bar D_1)
    \vWeight = \sigma^2 + o_p(1).
  \end{equation*}
\end{lem}

\subsection{Failure of In-Sample Tests}\label{sec:insample}
This subsection establishes that the F-test can over-reject when the
benchmark is more accurate than the alternative.  We use stronger
assumptions than before, i.i.d. data, normal errors, \mse\ loss, and
nested models to ensure that the F-test performs as well as possible.
Indeed, we know its exact distribution.  But the basic idea of this
argument is much more general and should apply to other related tests,
including \oos\ tests.

\begin{thm}\label{res:ftest}
  Let $\h = 1$ and suppose that $x_{1t}$ and $x_{2t}$ are
  deterministic vectors such that $x_{2t} = (x_{1t}, z_t)$ and
\[
T^{-1} \sum_{t=1}^T x_{2t} x_{2t}'  = Q^{-1} \sum_{t=T+1}^{T+Q} x_{2t} x_{2t}' =
I.
\]
Also, suppose that $\theta_2 = (\theta_1, \psi)$, 
$\varepsilon_{2,t+1} \sim i.i.d.\ N(0,\tau^2)$,
$|\theta_1|_2 = \phi_1$, $|\psi|_2 = \phi_2$, $K_1/T = c_1 > 0$,
$K_2/T = c_2 > 0$, and $K_2 \geq 2$, and let $F$ be the F-statistic
for the test of the null hypothesis that $\psi = 0.$
Then 
\begin{equation}\label{eq:ftestreject1}
  \Pr[F \geq q_{K_2 - K_1, T - K_2}(1-\alpha) \mid E_T \bar{D}_2 \leq 0
  ] \to 1\mbox{ as $\phi_2 \to \infty$ ($T$ fixed)}
\end{equation}
and if $\phi_2 \geq \tau \sqrt{c_2 - c_1}$, then
\begin{equation}\label{eq:ftestreject2}
  \Pr[F \geq q_{K_2 - K_1, T - K_2}(1-\alpha) \mid E_T \bar{D}_2 \leq 0
  ] \to 1 \text{ as $T \to \infty$},
\end{equation}
where $q_{K_2-K_1, T-K_2}(1-\alpha)$ is the
$(1-\alpha)$-quantile of the $F_{K_2-K_1, T-K_2}$ distribution.
\end{thm}
The conditions on the regressors simplify the proof but can be
relaxed.  As in Corollary~\ref{res:oostest}, the event that we are
conditioning on in~\eqref{eq:ftestreject1} and~\eqref{eq:ftestreject2}
is the event that the benchmark model is expected to be more accurate
in the future.  Since the probability of this event converges to zero
as $\phi_2 \to \infty$, \eqref{eq:ftestreject1} is not an immediate
consequence of the power of the F-test increasing with $\phi_2$.

The first result,~\eqref{eq:ftestreject1}, can be understood through the case $K_2 = 2$ and
$K_1 = 0$, so
\begin{equation*}
  E_T \bar D_2 = \psi_1^2 + \psi_2^2 - (\hat{\psi}_1 - \psi_1)^2 - (\hat\psi_2 - \psi_2)^2,
\end{equation*}
where $\hat{\psi}$ is the \ols\ estimator.  Under these conditions,
the F-test rejects if $\hat{\psi}'\hat{\psi}$ lies outside the circle
centered at the origin with radius $\hat{\tau} (c_2 - c_1)^{0.5}
q_{K_2-K_1, T-K_2}^{0.5}(1-\alpha)$, and $E_T \bar{D}_2 \leq 0$ holds
for $\hat\psi$ on or outside a circle centered at $\psi$ passing
through the origin; $\hat{\tau}^2$ is the usual estimator of $\tau^2$.
Figure~\ref{fig:rreject} depicts these regions.  Since the \ols\
estimator $\hat\psi$ is normal with mean $\psi$, the probability that
$\hat{\psi}$ falls in the acceptance region given $E_T \bar{D}_2 \leq
0$ vanishes as $\phi_2 \to \infty$, even though the full model will
give worse forecasts than the restricted model.

\newcommand{\circlefigA}[4]{
  \begin{tikzpicture}
    \fill[lightgray] (-#3,-#3) rectangle (#4,#4);
    % rejection region for F-test
    \filldraw[fill=white,draw=black] (0,0) circle (#1);
    % circle of equal generalization error
    \filldraw[fill=white,draw=black] (1,1) let \p1=(1,1) in circle({veclen(\x1,\y1)});
    \draw (1,1) let \p1=(1,1) in circle({veclen(\x1,\y1)});
    \fill [black] (1,1) circle (2pt) node[right] {$(\psi_1,\psi_2)$};
    \draw (0,0) circle (#1);
    \draw (1,1)--(0,0);
    % axes
    \draw[->] (0,0)--(#2,0) node[right] {$\hat\psi_1$};
    \draw[->] (0,0)--(0,#2) node[above] {$\hat\psi_2$};
  \end{tikzpicture}
}
\newcommand{\circlefigB}[4]{
  \begin{tikzpicture}
    \fill[white] (-#3,-#3) rectangle (#4,#4);
    % rejection region for F-test
    \fill[lightgray] (0,0) circle (#1);
    % circle of equal generalization error
    \fill[white] (1,1) let \p1=(1,1) in circle({veclen(\x1,\y1)});
    \draw (0,0) circle (#1);
    \draw (1,1) let \p1=(1,1) in circle({veclen(\x1,\y1)});
    \fill [black] (1,1) circle (2pt) node[right] {$(\psi_1,\psi_2)$};
    \draw (1,1)--(0,0);
    % axes
    \draw[->] (0,0)--(#2,0) node[right] {$\hat\psi_1$};
    \draw[->] (0,0)--(0,#2) node[above] {$\hat\psi_2$};
  \end{tikzpicture}
}

\begin{figure}
  \centering
  \begin{tabular}{cc}
  \subfloat[]{\circlefigA{1}{2.5}{1.4}{3.2}\label{fig:circleA}} &
  \subfloat[]{\circlefigB{1}{2.5}{1.4}{3.2}\label{fig:circleB}}  \\
  \subfloat[]{\circlefigA{.3}{2.5}{1.4}{3.2}\label{fig:circleC}}  &
  \subfloat[]{\circlefigB{.3}{2.5}{1.4}{3.2}\label{fig:circleD}} 
  \end{tabular}
  \caption{Graphs indicating the rejection region and region of equal
    generalization error for the models discussed in Section
    \ref{sec:insample}.  The smaller model has no estimated parameters
    and the larger has two coefficients.  The shaded regions in
    Figures (a) and (b) show the rejection region and the acceptance
    region respectively of the F-test given $E_T \bar D_2 \leq 0$ when
    the true elements of $\psi$ are moderately small.  Figures (c) and (d)
    show the same regions when the true $\psi$ is large.}
\label{fig:rreject}
\end{figure}

The second part of Theorem \ref{res:ftest},~\eqref{eq:ftestreject2},
is more interesting and implies that the F-test rejects the benchmark
too often for forecasting whenever we have an overfit model (unless,
of course, $\psi = 0$).  The intuition is similar to the previous
case.  As $K_2$ increases, the volume that $\hat{\psi}$ can occupy
increases as well.  So the probability that $\hat{\psi}$ is close to
the origin and therefore inside the acceptance region of the F-test
decreases.  In the limit, the probability that $\hat{\psi}$ is outside
the acceptance region is one.\footnote{If $\phi_2 \geq \tau \sqrt{c_2
    - c_1}$ does not hold, then $\psi$ lies inside the acceptance
  region of the F-test for large enough $T$.  In that case, the
  rejection probability does not converge to one, but will converge to
  a probability greater than $\alpha$.}

It is important to remember that the F-test is valid for the null
$\psi = 0$ in this analysis.  However, the F-test is poorly suited for
choosing an accurate forecasting model, and performs worse when the
larger model is overfit or explains more of the variation of the
dependent variable.  Other valid unbiased tests of the null hypothesis
that $\psi = 0$ will suffer the same problem.

\section{Monte Carlo}\label{sec:mc}
\newcommand{\thetanorm}{\ensuremath{\lvert \theta \rvert_2}} This
section presents two simulations that investigate the accuracy of our
theory in small samples.\footnote{Simulations were conducted in R
  \citep{rproject} using the Lattice \citep{lattice} and RSQLite
  \citep{rsqlite} packages for graphics and data management
  respectively.}  The first looks at the asymptotic normality of the
\dmw\ statistic centered on either $E_R \bar D_1$ or $E_T \bar D_2$.
The previous section's results imply that centering on the first
should give an approximately normal statistic and centering on the
second should give a normal statistic when $P$ is small relative to
$T$.  The second simulation looks at the size and power of several
statistics when conducting inference about the difference in the
models' generalization error.

\subsection{Setup}\label{sec:simulation-design}
The Monte Carlo experiment is intentionally very simple so that we can
isolate the influence of the models' complexity.  In particular, we do
not include some features that are common in forecasting
environments---serial dependence, heteroskedasticity, and complicated
\dgp s.  We simulate data for both studies from the equation
\begin{equation}\label{eq:6}
  y_t = x_t'\theta + \varepsilon_t,\quad \varepsilon_t \sim N(0,1),
  \quad t=1,\dots,T.
\end{equation}
The first element of $x_t$ is 1 and the remaining $K_2-1$ elements are
independent Standard Normal.  The benchmark model is
\begin{equation}
  \label{eq:1}
  y_{1t} = \sum_{j=1}^{K_1} x_{jt}\theta_j + \varepsilon_t
\end{equation}
and the alternative model is the \dgp\ \eqref{eq:6}.  We let
$(K_1,K_2)$ equal either $(2,3)$ or $(T/20,T/10)$ to study our theory
in its intended application as well as for more parsimonious models.
We let $T$ equal 100, 250, 500, or 1000.  We also vary $\theta$, and do 
so giving the benchmark and the alternative model comparable weight in
predicting $y_t$.  Specifically, we set
\begin{equation*}
  \theta_j = 
\begin{cases} \frac{c}{\sqrt{K_1}} & j = 1,\dots,K_1 \\
\frac{c}{\sqrt{K_2 - K_1}} & j = K_1 + 1,\dots,K_2 \end{cases}  
\end{equation*}
with $c=0$ or 1.  When $c$ is large, we're more likely to draw
values of $X$ and $Y$ that make the estimated larger model more
accurate than the benchmark, and when $c$ is zero we're unlikely to
draw such values of $X$ and $Y$.  For all of the studies, $L(x) =
x^2$.

The first set of simulations study how well the theory in
Section~\ref{sec:oostheory} works in practice.  For each draw of $X$
and $Y$, we construct a one-sided and two-sided \oos\ interval of the
form
\begin{equation*}
  [ \bar D_1 - 1.28 \hat{\sigma}, \infty) \quad\text{and}\quad
  [ \bar D_1 - 1.64 \hat{\sigma}, \bar D_1 + 1.64\ \hat{\sigma}], \\
  \hat\sigma^2 = \frac1P \sum_{t=R+1}^T (D_t - \bar D_{1})^{2}
\end{equation*}
for $P$ set to every 10th value between $T$ and $\frac{2T}{3}$.  We
calculate the percentage of these intervals that contain $E_R \bar
D_1$ and that contain $E_T \bar D_2$.  Since the data are i.i.d.,
both of these quantities are easy to calculate:
\begin{equation*}
  E_R \bar D_1 = [\sum_{i=1}^{K_1} (\tilde{\theta}_{iR} - \theta_i)^2 +
  \sum_{i=K_1+1}^{K_2}\theta_i^2] - \sum_{i=1}^{K_2} (\hat{\theta}_{iR} -
  \theta_i)^2
\end{equation*}
and
\begin{equation*}
  E_T \bar D_2 = [\sum_{i=1}^{K_1} (\tilde{\theta}_{iT} - \theta_i)^2 +
  \sum_{i=K_1+1}^{K_2}\theta_i^2] - \sum_{i=1}^{K_2} (\hat{\theta}_{iT} -
  \theta_i)^2
\end{equation*}
where $\tilde{\theta}$ indicates that the coefficient is estimated
using only the regressors in the benchmark model and $\hat{\theta}$
the full model.  We draw 2000 samples for each choice of the design
parameters.

The second simulation looks at the size and power of the test
statistics when conducting inference about the models' generalization
error.  The null hypothesis we test is 
\begin{equation}\label{eq:9}
  H_0:\quad E_T \bar D_2 \leq 0,
\end{equation}
We look at four different statistics---the full-sample F-test, the
\dmw\ $t$-test, the
\oos\ $t$-test using McCracken's (2007)
critical values,\footnote{These critical values are not published for
  $K_2-K_1>10$, so we do not report them for $K_2 = T/10$.}
and Clark and West's (2006, 2007) Gaussian out-of-sample
statistic.\footnote{Clark and West (2006, 2007) derive their statistic
using the rolling window estimation scheme.  Here we use the same
statistic, but with a fixed window scheme.}
For the F-test, we simply test whether the coefficients on the larger
model are nonzero.  For the out-of-sample tests, we conduct a
one-sided test of out-of-sample performance for every 10th value of
$P$ as before.

To estimate each test's size for the hypothesis \eqref{eq:9}, we draw
samples from the \dgp\ and discard those for which \eqref{eq:9} does
not hold, until we have 2000 for each choice of the design parameters.
The estimated size is the fraction of those samples in which the test
statistic rejects.
\subsection{Results}
We'll discuss results for the confidence intervals first.
Figures~\ref{fig:interval-R} and~\ref{fig:interval-T} show the
coverage probability of these intervals as a function of $P$ for each
combination of $T$, $K_1$ and $K_2$, and $c$.  The gray horizontal
line shows the intervals' nominal coverage probability.  Each panel
displays the coverage for a different choice of interval, centering
term ($E_R \bar D_1$ or $E_T \bar D_2$) and combination of design
parameters.

Figure~\ref{fig:interval-R} gives the results for $E_R \bar D_1$.  For
both the one and two-sided intervals, the actual coverage is very
close to the nominal coverage except when $P$ is small.  The poor
behavior for small $P$ is unsurprising, as it simply means that the
\clt\ is a poor approximation when the test sample is small.  The
intervals' good coverage holds even for the parsimonious models
($K_1=1$ and $K_2= 3$) which our theory does not necessarily apply to.

Figure~\ref{fig:interval-T} gives the results for $E_T \bar D_2$.  In
rows 2, 4, 6, and 8, the overfit models, the coverage is near nominal
coverage for moderately small values of $P$.  As $P$ increases to $2T/3$, the
coverage either increases to 1 (for the one-sided interval) or fall to
zero (the two-sided).  With the parsimonious model, the coverage is near
nominal coverage for all $P$ for the one-sided interval with $c=1$,
but only for moderately small $P$ for the two-sided interval or when
$c=0$.

The behavior for $K_2 = T/10$ is exactly what our theory predicts.
When $P^2/T$ is small, the coverage is near nominal levels.  The
behavior as $P$ increases, combined with the results for $E_R
\bar{D}_1$, indicate that $E_T \bar D_2 \geq E_R \bar D_1$ in general.
Since
\[E_{T} \bar D_2 = E_{R} \bar D_1 + (E_{T} \bar D_2 - E_{R} \bar
D_1), \] and the interval is approximately centered at $E_R \bar D_1$,
the difference $E_{T} \bar D_2 - E_{R} \bar D_1$ adds a substantial
positive quantity when $P^2/T$ is not near zero, increasing the
coverage of the one-sided interval but taking $E_T \bar D_2$ outside
the two-sided interval.

We next present the size simulations,
Figures~\ref{fig:ftest}--\ref{fig:ttest-power}.  For the \oos\ tests,
the conditional rejection probability is plotted for each combination
of $T$, $K_1$, $K_2$, and $c$ as a function of $P$.  The F-test does
not depend on $P$, so a single value is presented for each
combination.

We'll look at the F-test first.  To make comparisons easier, the size
is displayed as a dot plot in Figure~\ref{fig:ftest}.  Different
panels display a different combination of $K_1$, $K_2$, and $T$, and
each individual plot shows the empirical size for each choice of $c$.
We see immediately that the actual and nominal size are essentially
equal for $c = 0$, which is unsurprising.  For $c = 0$, the F-test is
exact; moreover, the larger model will almost always be less accurate
than the smaller one, so conditioning on $\E_T \bar{D}_2 \leq 0$ is
almost unrestrictive.  When $c$ increases, though, the F-test
over-rejects badly---rejecting at roughly 50\% when $c = 1$ for the
parsimonious model and from 70\% to 100\% for the overfit model.  As
our discussion in Section~\ref{sec:insample} predicts, the rejection
probability increases with $T$ for the overfit model but does not
depend on $T$ for the small model.

Figure~\ref{fig:ttest-size} presents the size estimates for the \dmw\
$t$-test.  Again, different panels display results for different
combinations of the design parameters.  Each graph plots the rejection
probability against $P/T$.  For $K/T=10$, the rejection probability
falls as $P/T$ increases, from near nominal size when $P/T$ is small
to zero when $P/T$ is near $2/3$.  Moreover, the rejection probability
falls faster when $T$ is large, as our theory predicts.  When $K=3$,
the rejection probability stays closer to nominal size, but falls with
$P/T$ for $c=0$, under-rejecting by about 5pp when $P/T = 2/3$, and
rises with $P/T$ for $c=1$, over-rejecting by about 10pp when
$P/T=2/3$.  For small $P$, the rejection probability is near 10\% for
all simulations (the farthest is $K=T/10$, $c=0$, where the rejection
probability is about 5\%; the other simulations are much closer).

We observe the following patterns.  The
\dmw\ test has close to nominal size when $P$ is small for every
combination of design parameters.  In most cases, the rejection
probability decreases as $P/T$ increases---the exception is for $K_2 =
3$ and $c=1$.  For the large-$K$ simulations, the rejection
probability drops to zero for most of the simulations as $P/T$
increases.  The rejection probability increases with $c$, but the
rejection probability still is near nominal probability for small $P$
with $c=1$.

Clark and West's (2006, 2007) statistic, presented in
Figure~\ref{fig:clarkwest}, behaves quite differently.  For $c=0$ the
test is correctly sized for both the overfit and parsimonious studies,
as we saw for the F-test.  When $c=1$, the rejection probability
increases rapidly with $P/T$.  For $K_2=3$, the rejection probability
is near 10\% when $P$ is small but about 40\% when $P/T = 2/3$.  For
$K=T/10$, the rejection probability is even higher and increases with
$T$ as well, from a maximum over 50\% when $T=100$ to a maximum of
nearly 100\% when $T=1000$.

Results using \citepos{mccracken_asymptotics_2007} critical values are
presented in Figure~\ref{fig:mccracken} and are similar to those using
Clark and West's test.  For $c=0$ the rejection probability is nearly
the test's nominal size.  For $c=1$, the rejection probability
increases with $P/T$, from close to the nominal size when $P/T$ is
small to over 25\% when $P/T = 2/3$.  Note that all of the simulations
use the parsimonious model.  McCracken's statistic over-rejects here
by slightly less than Clark and West's, but still by a substantial
amount.

Since the \dmw\ test tends to have low rejection probability, the
test's power is a concern.  We'll present some power results,
simulating from \eqref{eq:1} with $c = 1$ or 2 subject to the
constraint that $E_T \bar D_2 > 0$.\footnote{Draws of $X$ and $Y$ with
  $E_T \bar D_2 > 0$ are very rare when $c=0$, so we do not present
  results for that value of $c$.}  Figure~\ref{fig:ttest-power} plots
the power for the \dmw\ test; since the other test statistics greatly
over-reject, we do not present their power.  For $c=1$, the power is
never greater than nominal size and decreases to zero as $P/T$
increases for the overfit model.  For $c=2$ the power is better,
increasing with $P/T$ for a stretch and then decreasing as $P/T$ grows
beyond approximately 1/4 for the overfit model.  Larger values of $T$
give a higher peak and greater power overall, but the power still
falls to nearly zero if $P/T$ is too large (approximately 2/3 in our
simulations).  The power with the parsimonious model is typically
quite low but greater than nominal size for $c = 2$.

Both sets of simulations support our theoretical results.  The first
simulation confirms that the \dmw\ \oos\ $t$-test is centered at $E_R
\bar D_1$ for all choices of $P$ and $R$ and is centered on $E_T \bar
D_2$ only when $P$ is small.  The second simulation confirms that the
\dmw\ test has correct size for the null hypothesis that $E_T \bar D_2
\leq 0$ when $P$ is small and that tests designed to test whether the
benchmark is true, like the F-test and Clark and West's (2006, 2007)
and McCracken's (2007) \oos\ tests can reject by much more than their
nominal size when testing the null $E_T \bar D_2 \leq 0$.
Moreover, these simulations demonstrate that the restriction $P^2/T
\to 0$ is binding in practice, as the \dmw\ test under-rejects and has
very low power when it is not satisfied.
\section{Empirical Exercise}\label{sec:empirics}
This section presents an analysis of equity premium predictability
similar to \citet{goyal-welch-2008-rfs}.\footnote{All of the
  calculations in this section are done in R \citep{rproject}.  We
  also use code provided by \citet{zeileis-hothorn-2002-RNews},
  \citet{zeileis-2004-JStatSoftware}, and \citet{harrell-2010-R}.}  We
estimate the expected forecasting performance of the largest model
they consider, a model with 13 regressors, using 81 observations
(annual data from 1928 to 2009).  We construct confidence intervals
for the difference in performance between this model and a prevailing
mean benchmark, and do so for different values of $R$ and $P$ to
examine the effect of the training and test sample choice on this
\oos\ statistic.  We find that the estimate of the larger model's
\mse\ decreases relative to the benchmark as $R$ increases, but it is
never smaller than the benchmark's.  This result, combined with the
larger model's in-sample significance, suggests that there may be a
real relationship between the equity premium and some of these
predictors, but that the relationship can not be estimated accurately
enough to be useful for forecasting and supports
\citepos{goyal-welch-2008-rfs} conclusions.  These results hold even
when imposing \citepos{campbell-thompson-2008-rfs} restriction that
the equity premium forecast be non-negative.

We'll start with a very brief review.  \citet{goyal-welch-2008-rfs}
study the \oos\ forecasting performance of different variables thought
to predict the equity premium (calculated as the difference between
the return on the S\&P 500 index and the T-bill rate).  Some of these
variables are listed in
Table~\ref{tab:equity}.\footnote{Table~\ref{tab:equity} only lists the
  variables used in \citepos{goyal-welch-2008-rfs} ``kitchen sink''
  model.  Some of the variables that they use in bivariate models are
  excluded from this model either because the series are too short or
  because the variables are linear combinations of other variables.}
\citet{goyal-welch-2008-rfs} estimate the \oos\ forecasting
performance of bivariate models of the form
\[
r_{t+1} = \beta_0 + \beta_1 x_t + \varepsilon_{t+1}
\]
using \ols\ with a recursive window, where $r_{t+1}$ is the equity
premium and $x_t$ is a generic predictor, as well as some larger
models.  They find that these models forecast no better than the
prevailing mean of the equity premium.
\citet{campbell-thompson-2008-rfs} find that nonlinear extensions of
Goyal and Welch's models are more accurate, either imposing sign
restrictions on the estimated coefficients or imposing that the
forecast be non-negative, but do not test for significance.

Obviously, \citepos{goyal-welch-2008-rfs} bivariate models do not
match the asymptotic theory of this paper, so we restrict our
attention here to their ``kitchen sink'' model, which includes all of
the variables, except for a few dropped because of data availability or
(perfect) multicollinearity.  Formally, the benchmark and alternative models are
\begin{eqnarray}
  \label{eq:3}
  r_{t+1} &=& \mu + \varepsilon_{1,t+1} \\
  \label{eq:2}
r_{t+1} &=& \beta_0 + \sum_{i=1}^K \beta_{i} x_{it} + \varepsilon_{2,t+1}  
\end{eqnarray}
respectively and are estimated by \ols\ using the fixed-window scheme.
The predictors are listed in Table~\ref{tab:equity}; for a detailed
description of each predictor, please see Goyal and Welch's original
paper.  In this model, there are 13 regressors (including the constant
term) and we estimate the coefficients using annual data from 1928 to
2009.  This makes the ratio $K/T$ equal to about 0.16.  We also
present results for one of \citepos{campbell-thompson-2008-rfs}
restricted forecasting models.  For this model, we estimate
\eqref{eq:3} and \eqref{eq:2}, but impose that $\hat r_{t+1}$ be
non-negative for each forecast.  We then calculate the \oos\ test just
as for the unconstrained model.

Table~\ref{tab:gwinsample} gives the results of the full sample
regression for Equation~\eqref{eq:2}, using Newey-West standard errors
with two lags \citep{newey_simple_1987}.\footnote{We compare the test
  statistic to critical values from the $F$-distribution.}  The
$p$-value is very small (less than 0.01), indicating that the
coefficients are nonzero in population and at least one of these
predictors is correlated with the equity premium.  As we argue
earlier, this result does not imply that the model will forecast well,
which we look at next.

To study the effect of the training sample size on the \dmw\ statistic, we
calculate the one-sided confidence interval for $E_T \bar D_2$ given
by \eqref{interval-greater} corresponding to the null and alternative
hypotheses
\[ H_0: \quad E_T \bar D_2 \leq 0 \qquad
H_A: \quad E_T \bar D_2 > 0
\]
for each value of $R$ between 20 and $T-10$.  The standard deviation
is estimated using a Newey-West estimator with $\lfloor
P^{\frac14}\rfloor$ lags.  For small values of $R$, the \oos\ average
is expected to underestimate the performance of the larger model
relative to the smaller, but this may not hold in this particular
dataset.

Figures~\ref{fig:empirics1} plots the \ols\ results and
Figure~\ref{fig:empirics2} imposes
\citepos{campbell-thompson-2008-rfs} restriction.  The solid line
in each figure shows the \oos\ average, $\bar D_1$, and the shaded
region indicates the 95\% one-sided confidence interval implied by the
\dmw\ test.  Negative numbers indicate that the kitchen sink model has
higher out-of-sample loss.  We can see that the same patterns hold for
both models: the performance difference decreases with $R$, but the
kitchen sink model is never more accurate.  We also see that the
performance difference decreases suddenly over the period $R=29$ to
$R=34$ (corresponding to the years 1956--1961).
Figure~\ref{fig:empirics3} plots the accuracy of the individual
forecasts (only for the linear models) and shows that this change is
the result of a sudden improvement in the kitchen sink model.  This
change may indicate instability in the underlying relationship, as
\citet{goyal-welch-2008-rfs} propose.

In summary, we fail to reject the null that the benchmark prevailing
mean model is more accurate than \citepos{goyal-welch-2008-rfs}
kitchen sink.  This result is consistent with Goyal and Welch's
original analysis.  Unlike Goyal and Welch, we attribute this result,
at least in part, to parameter uncertainty---the full sample results
indicate that the larger model could predict better than the
benchmark with enough data.  Obviously, this is an illustrative
exercise only and is not meant to be comprehensive.  In this dataset,
there is likely parameter instability that we have not addressed, and
we have not dealt with variable persistence at all.
\section{Conclusion}\label{sec:conclusion}
This paper gives a theoretical motivation for using \oos\ comparisons:
the \dmw\ \oos\ test allows a forecaster to conduct inference about
the expected future accuracy of his or her models when one or both is
overfit.  We show analytically and through Monte Carlo that existing
in-sample test statistics can not test hypotheses about this
performance.

Our paper also shows that popular test and training sample sizes may
give misleading results if researchers are concerned about
overfit.\footnote{As we mention in the introduction, forecasters also
  use these statistics if they are concerned about unmodeled
  instability, which this paper does not address.}  We show that
$P^2/T$ must converge to zero for the \dmw\ test to give valid
inference about the expected forecast accuracy, otherwise the test
measures the accuracy of the estimates constructed using only the
training sample.  In empirical research, $P$ is typically much larger
than this.  Our simulations indicate that using large values of $P$
with the \dmw\ test gives undersized tests with low power, so this
practice may favor simple benchmark models too much.  Existing
corrections, proposed by
\citet{clark_tests_2001,clark_evaluating_2005},
\citet{mccracken_asymptotics_2007} and
\citet{clark_using_2006,clark_approximately_2007}, seem to correct too
much, though, and reject too often when the benchmark model is more
accurate.

More work remains.  Our requirement that $\frac{P^2}{T}$ converge to
zero is limiting, as it implies that in typical macroeconomic
datasets, only a handful of observations should be used for testing.
This restriction could be addressed by directly estimating $\E_R \bar
D_1 - \E_T \bar{D}_2$ or by deriving its asymptotic distribution,
which would allow larger values of $P$.  It could also be mitigated by
extending our results to cross-validation or other resampling
strategies.  It would also be useful to extend our results to other
estimation windows and forecasting models, and to explore how
stationarity could be relaxed.

\appendix
\section{Supporting results}
The results in this paper rely heavily on a coupling argument for
absolutely regular sequences, Berbee's Lemma
\citep{berbee_random_1979}.  In fact, many of the results of this
paper (\ref{res-confidence-intervals}, \ref{res-mixingale}, and
\ref{res-variance-estimator}) are modifications of existing
results for \ned\ functions of mixing processes by
\citet{de_jong_central_1997} and \citet{de_jong_consistency_2000};
this coupling argument is used to explicitly derive inequalities that
arise naturally for \ned\ processes.  Lemma \ref{lem-basic-coupling}
establishes these inequalities, which are based on a proposition of
\citet{merlevede_coupling_2002}.

We present \citeauthor{merlevede_coupling_2002}'s
(\citeyear{merlevede_coupling_2002}) statement of Berbee's Lemma for
the reader's reference.  In the following Lemma, $\beta(X,Y)$ is the
coefficient of absolute regularity:
\[
\beta(X,Y) = \sup_{A \in \sigma(Y)} \E \lvert \Pr(A \mid \sigma(X))
  - \Pr(A) \rvert.
\]
\begin{quotation}
\begin{lem}\label{lem-berbee}
  Let $X$ and $Y$ be random variables defined on a probability space
  $(\Omega, \mathcal{T}, \mathbf{P})$ with values in a Polish space
  $S$.  Let $\sigma(X)$ be a $\sigma$-algebra generated by $X$ and let
  $U$ be a random variable uniformly distributed on $[0,1]$
  independent of $(X,Y)$.  Then there exists a random variable $Y^{*}$
  measurable with respect to $\sigma(X) \vee \sigma(Y) \vee
  \sigma(U)$, independent of $X$ and distributed as $Y$, and such that
  $\mathbf{P}(Y \neq Y^{*}) = \beta(X,Y)$.
\end{lem}
\noindent\citep{merlevede_coupling_2002}
\end{quotation}

The advantage of this result over coupling arguments that use other
forms of weak dependence is that the difference between the original
variable, $Y$, and the new variable, $Y^{*}$, does not depend on their
dimension.  Similar results for strong mixing sequences depend on the
dimension of $Y$, which makes them unsuitable for our applications.
The remaining results in this section use Berbee's Lemma to establish
some basic inequalities.

\begin{lem}\label{lem-extend-mp}
  Suppose that $X$ and $X^*$ are $L_p$-bounded random variables, with
  $p > 2$, that satisfy ${\Pr[X \neq X^*] = c}$.  Then
  \[
    \lVert X - X^* \rVert_2 \leq 2^{1/p} (\lVert X \rVert_p + \lVert
    X^* \rVert_p) c^{(p-2)/2p}
  \]
\end{lem}

The proof is virtually identical to the proof of Proposition 2.3 in
\citet{merlevede_coupling_2002} and is omitted.

\begin{lem}\label{lem-basic-coupling}
  Suppose Assumptions \ref{asmp-1}--\ref{asmp-3} hold.  Then, for any
  T, $s$, $t$, $u$, and $w$, with $t \geq s > u \geq w$, there exist random
  variables $\tilde D_s,\dots,\tilde D_t$ such that
  \begin{equation}\label{eq:coupling1}
    P[(\tilde D_s,\dots,\tilde D_t) \neq (D_{sw},\dots,D_{tw})] \leq \beta_{s-u}
  \end{equation}
  and
  \begin{equation}\label{eq:coupling2}
    \E(\phi(\tilde D_s,\dots, \tilde D_t) \mid \mathcal{F}_u ) = 
    \int
    \phi(D_{sw},\dots,D_{tw}) f(\mathbf{x}, \mathbf{y})\ d\mathbf{x}\ d\mathbf{y}
  \end{equation}
  almost surely for all measurable functions $\phi$ such that the
  expectations are finite, where 
  \[ \mathbf{x} = (x_{s}', \dots, x_{t}')', \\
  \mathbf{y} = (y_{s+\h},\dots,y_{t+\h})'\] and $f$ is the
  joint density of $(\mathbf{x}, \mathbf{y})$.  Moreover,
 \begin{equation}\label{eq:coupling3}
   \| \tilde D_v - D_{vw} \|_2 \leq 2^{1+1/\rho} B_L
   \beta_{s-u}^\rhoExp, \qquad v = s,\dots,t.
 \end{equation}
\end{lem}

\begin{proof}
  The proof follows as a consequence of Lemmas \ref{lem-berbee} and
  \ref{lem-extend-mp}.  Let $l = t-s$.  For any fixed values of $l$
  and $T$, the sequence of vectors
  \[ V_s = (y_{s+\h}, x_{s}', \dots, y_{s+l+\h}, x_{s+l}') \] is
  absolutely regular of size $\rho/(\rho-2)$.  Berbee's Lemma implies
  that there is a random vector $V^*$ that is independent of
  $\mathcal{F}_u$, equal to $V_s$ in distribution, and satisfies
  \[\Pr[V^* \neq V_s] = \beta_{s-u}.\]

  Now define
  \[ \tilde D_v \equiv L(y_{v+\h}^* - x_{1v}^* \cdot
  \hat{\theta}_w) - L(y_{v+\h}^* - x_{2v}^* \cdot
  \hat{\theta}_w), \quad v = s,\dotsc, t,
  \]
  with $y_{v+\h}^*$ and $x_{iv}^*$ denoting the elements of $V^*$
  corresponding to $y_{v+\h}$ and $x_{iv}$ in $V_s$.  Equations
  (\ref{eq:coupling1}) and (\ref{eq:coupling2}) are satisfied by
  construction, and (\ref{eq:coupling3}) follows from Lemma
  \ref{lem-extend-mp}.
\end{proof}

\section{Proofs of results in main text}
\begin{proof}[Proof of Theorem \ref{res-confidence-intervals}]
It suffices to prove asymptotic normality.  We can rewrite the
centered \oos\ average as
  \[
    \CenteredAverage = \CenteredAverageI + \CenteredAverageII.
  \]
Lemmas \ref{res-mixingale} and 
\ref{res-convergence} ensure that the first term is asymptotically
normal and the second term vanishes.
\end{proof}

\begin{proof}[Proof of Lemma \ref{res-mixingale}, Part 1.]
Fix $R$, $j$ and $l$ and use Lemma
\ref{lem-basic-coupling} to define $\tilde{D}_{R+j}$ so that
\[\E_R\tilde D_{R+j} = \E_{R+j-l} \tilde D_{R+j} \quad a.s. \]
and
\[\lVert D_{R+j,R} - \tilde D_{R+j} \rVert_2 \leq \couplingBound{l}.\]
Then
\[
\lVert \E_{R+j-l} D_{R+j,R} - \E_R D_{R+j,R} \rVert_2 \wall \leq 
\lVert \E_{R+j-l} D_{R+j,R} - \E_{R+j-l} \tilde{D}_{R+j} \rVert_2 \\
\quad + \lVert
\E_{R+j-l} \tilde{D}_{R+j} - \E_R D_{R+j,R} \rVert_2 \\
\leq 2 \lVert D_{R+j,R} - \tilde D_{R+j} \rVert_2 \\
\leq 2^{2 + \frac1\rho}\ B_L\ \couplingBeta{l}.\return
\]
Now $\couplingBeta{l} = O(l^{-\frac12 - \delta})$ for some
positive $\delta$, completing the proof.
\end{proof}

\begin{proof}[Proof of Lemma \ref{res-mixingale}, Part 2.]
  A modification of \citepos{de_jong_central_1997} \clt s for
  mixingale and \ned\ arrays will complete the proof.

Define
\[\label{eq:z1}
  Z_i = \ZDef
\]
where $b_T$ is a sequence that satisfies $b_T\leq P$,
$b_T\to\infty$, and $b_T/P\to 0$.  The same arguments used in
\citepos{de_jong_central_1997} Theorem 1 show that
\begin{equation*}
   \SumOuterBlock{i} Z_i = \frac1{\sqrt{P}} \oosSum{s}{1} (D_{tR} - \E_R D_{tR}) + o_p(1).
\end{equation*}
and
\begin{equation*}
  \SumOuterBlock{i} Z_i = \SumOuterBlock{i} (Z_i - E_{R + (i-1)b_T}
  Z_i) + o_p(1).
\end{equation*}
Note that $\{Z_i - E_{R + (i-1)b_T},\mathcal{F}_{R + i b_T}\}_i$ is an
\mds\ by construction, so \citepos{hall_martingale_1980} Theorem 3.2
and Corollary 3.1 ensure that\footnote{Note that $\sigma^2 \in
  \mathcal{F}_t$ for all $t \geq R$, so Hall and Heyde's condition
  (3.21) is unnecessary---see the remarks after their result.}
\[
\frac1{\sigma} \SumOuterBlock{i} Z_i \to^p
N(0,1)
\]
as long as
\begin{equation}\label{eq:cltvar2}
  \sigma^2 - \SumOuterBlock{i} \E_R Z_i^2 \to^p 0,
\end{equation}
and
\begin{equation}\label{eq:cltvar1}
  \SumOuterBlock{i} \E_R Z_i^2 - \SumOuterBlock{i} \ZSqCE \to^p 0.
\end{equation}
Equation (\ref{eq:cltvar2}) holds as in \citet{de_jong_central_1997}
(see the proof of his Theorem 2); to see that (\ref{eq:cltvar1})
holds, we'll use an argument based on his Lemma 5.  Define
\[
\tilde Z_i = \frac1{\sqrt{P}} \SumInnerBlock{s}{i} \tilde D_s -
\E_R \tilde D_s,
\]
with $\tilde D_{R+(i-1)b_T + 1},\dots,\tilde D_{R+ib_T}$ new random
variables that satisfy
\[
\lVert \tilde D_s - D_{sR} \rVert_2 \leq 2^{1 + \frac1\rho} B_L \beta_{s -
  (i-1)b_T + R}^{\rhoExp}, \quad s = R+(i-1)b_T + 1,\dots,R+i b_T
\]
and
\[
\E_R \phi(\tilde D_s) = \E_{R+(i-1)b_T} \phi(\tilde D_s) \quad \text{a.s.}, \quad s = R+(i-1)b_T + 1,\dots,R+i b_T
\]
for all measurable $\phi$ such that the expectations are finite; the
existence of these variables is ensured by Lemma
\ref{lem-basic-coupling}.  Then $\tilde Z_i$ satisfies
\[
\E_R \tilde Z_i^2 = \CEOuterBlock{\tilde Z_i^2}{i} \quad \text{a.s.},
\]
giving the inequality
\[
\lVert \ZSqCE - \E_R Z_i^2 \rVert_1 \wall= \lVert \wall\CEOuterBlock{(Z_i^2 -
  \tilde Z_i^2)}{i} \\ - (\E_R Z_i^2 - \CEOuterBlock{\tilde Z_i^2}{i})
\rVert_1 \return\\
\leq 2 \lVert Z_i^2 - \tilde Z_i^2 \rVert_1.
\return
\]

Also define 
\[
V_{i,C} = \begin{cases} Z_i & \text{if } |Z_i| < \ZTrunc \\ 
  \ZTrunc & \text{if } Z_i \geq \ZTrunc \\
- \ZTrunc & \text{if } Z_i \leq -\ZTrunc
  \end{cases}
\]
and
\[
\tilde V_{i,C} = \begin{cases} 
 \tilde Z_i & \text{if } |\tilde Z_i| < \ZTrunc \\ 
  \ZTrunc & \text{if } \tilde Z_i \geq \ZTrunc \\
- \ZTrunc & \text{if } \tilde Z_i \leq -\ZTrunc.
\end{cases} 
\]
Both $Z_i\sqrt{\frac{P}{b_T}}$ and $\tilde Z_i\sqrt{\frac{P}{b_T}}$
are uniformly integrable, so $C$ can be chosen to make
\[
\lVert \SumOuterBlock{i} [(Z_i^2 - \tilde Z_i^2) - (V_{i,C}^2 - \tilde V_{i,C}^2)] \rVert_1
\]
arbitrarily small.  As a result, \eqref{eq:cltvar1} holds if we can
prove that
\[
\lVert \SumOuterBlock{i} (V_{i,C}^2 - \tilde V_{i,C}^2) \rVert_1 \to 0
\]
for arbitrary $C$, which we will show next.

Note that 
\[\lvert V_{i,C} - \tilde V_{i,C} \rvert \leq \lvert Z_{i,C} - \tilde
Z_{i,C} \rvert \quad \text{and} \quad \lvert V_{i,C} + \tilde V_{i,C}
\rvert \leq 2 C \sqrt{b_T/P} \quad \text{a.s.}\] 
It follows that
\[
\SumOuterBlock{i} \lVert V_{i,C}^2 - \tilde V_{i,C}^2 \rVert_1 
\wall
 \leq 2 \ZTrunc \SumOuterBlock{i} \lVert Z_i - \tilde Z_i \rVert_2 \\
 \leq \frac{2 C \sqrt{b_T}}{P}\SumOuterBlock{i} \SumInnerBlock{s}{i} \lVert \wall \ZSummand \\
  - (\tilde D_s - \E_R \tilde D_s) \rVert_2 \return \\ 
 = O(\frac{\sqrt{b_T}}{P}) \SumOuterBlock{i} \SumInnerBlock{s}{i} \lVert D_{sR} - \tilde D_s \rVert_2 \\
 = O(b_T^{-\frac12}) \sum_{s=1}^{b_T} \couplingBeta{s}
 \return
 \]
Finally, $\couplingBeta{s} = O(s^{-1/2-\delta})$ for some positive
$\delta$, making the last term $o(1)$ and completing the proof.
\end{proof}

\begin{proof}[Proof of Lemma \ref{res-convergence}]
\newcommand{\resConvgRHS}[1]{\ensuremath{\E(L(y^* - x_1^{*\prime}\bh{1#1}) - L(y^{*} -
x_2^{*\prime}\bh{2#1}) \mid \bh{#1})}}
\newcommand{\resConvgEstDiff}[1]{\ensuremath{\E(L(y^{*} -
    x_{#1}^{*\prime}\bh{#1R}) \mid \bh{R}) - 
\E(L(y^{*} - x_{#1}^{*\prime}\bh{#1T}) \mid \bh{T})}}
\newcommand{\resConvgEstDiffRV}[1]{\ensuremath{L(y^{*} -
    x_{#1}^{*\prime}\bh{#1R}) - L(y^{*} - x_{#1}^{*\prime}\bh{#1T})}}
We'll first show that 
\begin{equation}\label{EQ-oosaverage1}
\E_R \bar D_1 = \resConvgRHS{R} + o_p(P^{-\frac12})
\end{equation}
and
\begin{equation}\label{EQ-oosaverage2}
\E_T \bar D_2 = \resConvgRHS{T} + o_p(Q^{-\frac12})
\end{equation}
where $\hat\theta_R = (\hat\theta_{1R}, \hat\theta_{2R})$,
$\hat\theta_T = (\hat\theta_{1T}, \hat\theta_{2T})$, and $y^{*}$,
$x_1^{*}$ and $x_2^{*}$ are random variables drawn from the joint
distribution of $(y_{t+\h},x_{1t},x_{2t})$ independently of
$\mathcal{F}_T$.  We'll then show that
\begin{equation}\label{EQ-thetaconvg1}
\resConvgEstDiff{1} = O_p(\sqrt{P/T})
\end{equation}
and
\begin{equation}\label{EQ-thetaconvg2}
\resConvgEstDiff{1} = O_p(\sqrt{P/T})
\end{equation}
to complete the proof.

To prove (\ref{EQ-oosaverage1}), define $\tilde D_t$ for each $t = R+1,\dots,T-\h$ as
in Lemma \ref{lem-basic-coupling} so that
\[
\lVert \tilde D_t - D_{tR} \rVert_2 \leq \couplingBound{t-R}
\]
and 
\[
\E_R \tilde D_t = \resConvgRHS{R} \quad\text{a.s.}
\]
for all $t$.  Then 
\[
\lVert \E_R \bar D_1 - \wall \resConvgRHS{R} \rVert_2  \\
\leq \frac1P \oosSum{t}{1} \lVert \E_R (D_{tR} - \tilde D_t) \rVert_2 \\
\leq \frac{\couplingConstant}{P} \oosSum{s}{1} \couplingBeta{s} \\
= o(P^{-\frac12}).
\return
\]
The proof of (\ref{EQ-oosaverage2}) is identical.

Equations (\ref{EQ-thetaconvg1}) and (\ref{EQ-thetaconvg2}) both
follow the same argument, so we'll just prove (\ref{EQ-thetaconvg1}).
Since 
\[ \lVert \resConvgEstDiff{1} \rVert_1 \\ \quad= \| \E(L(y^{*} -
x_1^{*\prime} \hat{\theta}_{1R}) - L(y^{*} - x_2^{*\prime}
\hat{\theta}_{dR}) \mid \hat{\theta}_{1R}, \hat{\theta}_{1T}) \|_1 \\
\quad\leq \lVert \resConvgEstDiffRV{1} \rVert_1, \] it suffices to
prove
\[ \resConvgEstDiffRV{1} = O_p(\sqrt{P/T}). \]
Moreover, smoothness of the loss function ensures that
\[ \resConvgEstDiffRV{1} = O_p(1) x_1^{*\prime} (\bh{1R} -
\bh{1T}), \]
and it suffices to show that
\begin{equation*}
  \lVert x_1^{*\prime}(\bh{1R} - \bh{1T}) \rVert_2 = O(\sqrt{P/T}).
\end{equation*}

Manipulating the formula for the \ols\ estimator gives us
\begin{equation} \label{eq-theta-convergence-1}
\lVert x_1^{*\prime} (\bh{1R} - \bh{1T}) \rVert_2 \wall \leq
\lVert x_1^{*\prime} [(X_{1R}'X_{1R})^{-1} - (X_{1T}'X_{1T})]
X_{1T}'\ep{1T} \rVert_2  \\ \quad +
\lVert x_1^{*\prime} (X_{1R}'X_{1R})^{-1}\oosSum{t}{1} x_{1t}\varepsilon_{i,t+\h}
\rVert_2.
\end{equation}
The first term on the right side of \eqref{eq-theta-convergence-1}
satisfies the relationship
\[
\lVert x_{1}^{*\prime}[(X_{1R}'X_{1R})^{-1} -
(X_{1T}'X_{1T})^{-1} ]
X_{1T}'\ep{1T} \rVert_2^2 \\ = O(1)
\E\{\lambda_{\max}(X_{1T}' \ep{1T} \ep{1T}'
    X_{1T}) \sum_{i=1}^{K_1}
    \lambda_i^2([X_{1R}'X_{1R}]^{-1} -
        [X_{1T}'X_{1T}]^{-1} )\}.
\]
By assumption, $\lambda_{\max}(X_{1T}'\ep{1T} \ep{1T}' X_{1T}) =
O_p(T)$.  The matrix $(X_{1R}'X_{1R})^{-1} - (X_{1T}'X_{1T})^{-1}$ has
rank $P$ and its eigenvalues are bounded by those of
$(X_{1R}'X_{1R})^{-1}$, so
  \[\sum_{i=1}^{K_1}\lambda_i^2((X_{1R}'X_{1R})^{-1} -
  (X_{1T}'X_{1T})^{-1} )  \wall \leq
  \sum_{i=K_1 - P + 1}^{K_1}\lambda_i^2((X_{1R}'X_{1R})^{-1})  \\ = O_p(P/T^2).
  \]
The moment bounds in Assumption~\ref{asmp-2} guarantee that
convergence in probability implies convergence in $L_2$, so
  \[
    \lVert x_1^{*\prime} [(X_{1R}'X_{1R})^{-1} -
        (X_{1T}'X_{1T})^{-1} ]
      X_{1T}'\ep{1T} \rVert_2 = O(\sqrt{P/T}).
  \]
  A similar argument shows that
  \[
    \lVert x_1^{*\prime} (X_{1R}'X_{1R})^{-1}\oosSum{t}{1} x_{1t}\varepsilon_{1T}
    \rVert_2 =   O(\sqrt{P/T}),
  \]
  completing the proof.
\end{proof}

\begin{proof}[Proof of Lemma \ref{res-variance-estimator}]
  The proof follows \citepos{de_jong_consistency_2000} Theorem 2.1
  closely.  We start by defining similar quantities to theirs,
  borrowing their notation when possible to make the similarities
  apparent.  For positive $\delta$, define $b_T \equiv \lfloor
  \frac\gamma\delta \rfloor$,
\begin{equation*}
  \kernelB{x} \equiv \kernelBDefn{x},
\end{equation*}
\begin{equation*}
  \varianceTermI \equiv \varianceTermIDefn,
\end{equation*}
\begin{equation*}
  \varianceTermII \equiv \vtSum \wall \varianceTermIIa\\ \times
  \varianceTermIIb,\return
\end{equation*}
\begin{equation*}
  \varianceTermIII \equiv \vtSum \wall \varianceTermIIIa\\ 
  \times \varianceTermIIb, \return 
\end{equation*}
\begin{equation*}
  \varianceTermIV \equiv \vtSum \wall \varianceTermIIIa \\
  \times \varianceTermIVb, \return
\end{equation*}
giving us the inequalities
\begin{equation*}
  \lVert \hat\sigma^2 - \sigma^2 \rVert_1 \wall 
  \leq \lVert \hat\sigma^2 - \varianceTermI \rVert_1 
  + \lVert \varianceTermI - \varianceTermII \rVert_1 
  + \lVert \varianceTermII - \varianceTermIII \rVert_1 
  + \lVert \varianceTermIII - \varianceTermIV \rVert_1\\\quad
  + \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1 
  + \lVert \E_R\varianceTermIII - \E_R\varianceTermIV \rVert_1
  + \lVert \E_R\varianceTermII - \E_R\varianceTermIII \rVert_1\\\quad 
  + \lVert \E_R\varianceTermI - \E_R\varianceTermII \rVert_1 
  + \lVert \E_R \varianceTermI - \sigma^2 \rVert_1
  \\ 
  \leq  \lVert \hat\sigma^2 - \varianceTermI \rVert_1 
  + 2(\lVert \varianceTermI - \varianceTermII \rVert_1 
      + \lVert \varianceTermII - \varianceTermIII \rVert_1 
      + \lVert \varianceTermIII - \varianceTermIV \rVert_1) \\ 
  \quad + \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1 
  + \lVert \E_R \varianceTermI - \sigma^2 \rVert_1.
\end{equation*}
De Jong and Davidson (2000) prove that
\begin{equation} \label{dd1}
\lim_{\delta\to0} \limsup_{T\to\infty} \lVert \varianceTermI -
\varianceTermII\rVert_1 = 0,
\end{equation}
\begin{equation} \label{dd2}
\lim_{\delta\to0} \limsup_{T\to\infty} \lVert \varianceTermII - \varianceTermIII
\rVert_1 = 0,
\end{equation}
\begin{equation} \label{dd3}
\lim_{\delta\to0} \limsup_{T\to\infty} \lVert \varianceTermIII - \varianceTermIV
\rVert_1 = 0,  
\end{equation}
and
\begin{equation} \label{dd4}
\lim \lVert \E_R \varianceTermI - \sigma^2 \rVert_1 = 0.
\end{equation}
Their proofs of \eqref{dd1}--\eqref{dd4} use the fact that \ned\
functions of mixing processes are also mixingale processes, and do not
use any properties specific to \ned\ processes, so they hold here as
well.  We do need to modify their proofs that
\begin{equation}
  \label{eq:4} \lVert \hat{\sigma}^2 - \varianceTermI \rVert_1 \to 0
\end{equation}
and
\begin{equation}
  \label{eq:5} \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1
  \to 0 \quad \text{for all positive $\delta$},
\end{equation}
though, since their proofs exploit \ned\ properties.

We'll start with (\ref{eq:4}). It follows from simple algebra that
\[
\lvert \hat\sigma^2 - \varianceTermI \rvert \leq \wall
\varianceDiffA \\ +
\frac1{P} \oosSum{s,t}{1} \lvert (D_{tR} - \bar D_1)(\E_R D_{sR} - \bar D_1) \rvert
\vWeight,
\]
so we'll show that each summation is $o_p(1)$.  The two
arguments are almost identical, so we'll only present the first.

Applying the Cauchy-Scwarz inequality twice and simplifying gives the
upper bound
\[
\varianceDiffA \\ \quad \leq O(1) [\varianceDiffAii]^{\frac12} [\varianceDiffAi]^{\frac12}.
\]
Now,
$\frac1P \oosSum{s}{1}(D_{sR} - \E_R D_{sR})^2 = O_p(1)$, and it suffices to prove
that \[\varianceDiffAi = o_p(1).\]  Observe that
\[
\varianceDiffAi \wall =  O_p(\frac1P \oosSum{s}{1}(\E_{R}D_{sR} -
\E_R\bar D_1)^2) \\
\quad + O_p(\bar D_1 - \E_R\bar D_1)^{2} \\
= O_p(\frac1P \oosSum{s}{1} (\E_RD_{sR})^2 - (\E_R\bar D_1)^2) + o_p(1),    \return
\]
with the second term vanishing by Lemma \ref{res-mixingale} and
\citepos{davidson_l1-convergence_1993} mixingale \lln.

Now define $\tilde D_s$, $s = R+1,\dots,T-\h$, as in Lemma
\ref{lem-basic-coupling} so that $\E_{s-1} \tilde D_s = \E_R \tilde
D_s$ almost surely.  Note that we also have the almost sure equality
$\E_R \tilde D_s = \E_R \tilde D_{R+1}$ almost surely for all $s\geq R+1$,
and so
\[
\frac1P \oosSum{s}{1} (\E_R \tilde D_s)^2 = (\frac1P \oosSum{s}{1} \E_R
\tilde D_s)^2 \quad \text{a.s..}
\]

Consequently,
\[
\frac1P \oosSum{s}{1} (\E_R D_{sR})^2 - (\E_R\bar D_1)^2 \wall = 
\frac1P \oosSum{s}{1} [(\E_R D_{sR})^2 - (\E_R\tilde D_s)^2]\\
\quad+ (\frac1P \oosSum{s}{1} \E_R \tilde D_s)^2 - (\E_R\bar D_1)^2 \quad \text{a.s}.\\
= O_p(\frac1P \oosSum{s}{1} [(\E_R D_{sR})^2 - (\E_R \tilde D_s)^2]).
\]
Finally, 
\[
\lVert \frac1P \wall\oosSum{s}{1} [(\E_RD_{sR})^2 - (\E_R \tilde D_s)^2] \rVert_1
\\ \leq \frac1P \oosSum{s}{1} \lVert \E_RD_{sR} - \E_R \tilde D_s \rVert_2 \lVert
\E_RD_{sR} + \E_R \tilde D_s \rVert_2
\\ \leq \frac{4 B_L}P \oosSum{s}{1} \lVert \E_RD_{sR} - \E_R \tilde D_s \rVert_2,
\return
\]
and this last term vanishes as in the proof of Lemma
\ref{res-mixingale}.

\newcommand{\UFiltration}[1]{\ensuremath{\mathcal{F}_{(#1)b_{T}+R-P}}}%
Next, we'll prove (\ref{eq:5}). As in
\citet{de_jong_consistency_2000}, let
\begin{equation*}
  Z_{1t} = \varianceTermIIIa,
\end{equation*}
and
\begin{equation*}
  Z_{2t} = \varianceTermIVb,
\end{equation*}
so
\begin{equation*}
  \varianceTermIV - \E_R \varianceTermIV = \vtSum (Z_{1t}Z_{2t} - \E_R Z_{1t}Z_{2t}),
\end{equation*}
and note that $\{Z_{1t}^2 \frac{P\gamma}{b_T}\}$ and $\{Z_{2t}^2
\frac{P\gamma}{b_T}\}$ are uniformly integrable.  As in the proof of Theorem
\ref{res-confidence-intervals}, we can assume that there is a constant
$C$ such that $Z_{1t}$ and $Z_{2t}$ are bounded in absolute value by
$C\sqrt{\frac{b_T}{P\gamma}}$; uniform integrability ensures that the
difference between the unbounded random variables and these truncated
versions is negligible for large enough values of $C$.  Let $r =
\lfloor \frac{3P}{2b} \rfloor$ and rewrite the summation as
\begin{equation*}
  \vtSum \vtIIIsummand \wall= \vtSumr \vtSuma \vtIIIsummand \\
  \quad+ \vtSumr \vtSumb \vtIIIsummand \\
  \quad+ \sum_{t=r b - P + 1}^{2P} \vtIIIsummand \\
  \equiv \vtSumr (U_i - \E_R U_i) + \vtSumr (U_i' - \E_R U_i') + o_{L_1}(1).\return
\end{equation*}
The proof then holds if we can show that both $U_i$ and $U_i'$ obey
\lln s.  We'll do so by proving that $\{U_i -\E_R U_i,
\UFiltration{2i-1}\}$ and $\{U_i' - \E_R U_i', \UFiltration{2i}\}$ are
$L_2$-mixingales of size $-1/2$ and using the bound $E(\vtSumr (U_i -
\E_R U_i))^2 = O(\vtSumr c_i^2)$ where the $c_i$ are the mixingale
magnitude indices \citep{mcleish_maximal_1975}.

For non-negative $m$, we have 
\begin{equation*}
U_i - \E_R U_i \in \UFiltration{2i+2m-1},
\end{equation*}
establishing part of the mixingale result trivially.  Now fix $i$ and $m >
0$ and use Lemma \ref{lem-basic-coupling} to define $\tilde{D}_{ts}$
for each $t =(2i-2)b_T-P+1,\dots,(2i-1)b_T-P$ and $s =
\max(t+R-b_T,R-\h+1),\dots,\min(t+R+b_T,T)$ such that
\begin{equation*}
 \E_R \tilde D_{ts} = \E_{(2i-2m-1)b_T+R-P} \tilde D_{ts} \quad a.s.
\end{equation*}
and
\begin{equation*}
  \lVert \tilde D_{ts} - D_{sR} \rVert_2 \leq \couplingBound{s - (2i-2m-1)b_T-R+P}.
\end{equation*}
Also define
\begin{equation*}
  \tilde Z_{1t} = \frac1{\sqrt{P\gamma}} \sum_{l=\vttLower}^{\vttUpper}
  (\tilde D_{t,t+l+R} - \E_R\tilde D_{t,t+l+R})\ W(l/\gamma), \\
\end{equation*}
and
\begin{equation*}
\tilde Z_{2t} = \frac1{\sqrt{P\gamma}} \sum_{j=\vttLower}^{\vttUpper}
    (\tilde D_{t,t+l+R} - \E_R\tilde D_{t,t+l+R})\ \kernelB{j/\gamma}.
\end{equation*}

Now, we have the inequalities
\begin{equation*}
  \lVert \E( U_i - \wall \E_R U_i \mid \UFiltration{2i-2m-1}) \rVert_2
  \\ \leq
  \vtSuma \lVert \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) - \E_R
  Z_{1t}Z_{2t} \rVert_2 \\
  = \vtSuma \lVert \wall \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
  - \E(\tilde{Z}_{1t}\tilde{Z}_{2t} \mid \UFiltration{2i-2m-1}) \\
  + \E(\tilde{Z}_{1t}\tilde{Z}_{2t} \mid \UFiltration{2i-2m-1})
  - \E_R Z_{1t}Z_{2t} \rVert_2 \return \\
%  \leq \vtSuma (\wall \lVert \wall \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
%  - \E(\tilde{Z}_{1t}\tilde{Z}_{2t} \mid \UFiltration{2i-2m-1}) \rVert_2\return
%  \\ + \lVert \E_R Z_{1t}Z_{2t} - \E_R \tilde{Z}_{1t}\tilde{Z}_{2t}
%  \rVert_2)\return \\
  \leq 2 \vtSuma \lVert Z_{1t} Z_{2t} - \tilde Z_{1t} \tilde{Z}_{2t}
  \rVert_2 \\
  \leq 2 \vtSuma (\lVert Z_{1t} - \tilde{Z}_{1t} \rVert_2 \lVert
  Z_{2t} \rVert_{\infty}
  + \lVert Z_{2t} - \tilde{Z}_{2t} \rVert_2 \lVert \tilde{Z}_{1t} \rVert_{\infty}) \\
  \leq 2 C \sqrt{\frac{b_T}{P\gamma}} \vtSuma (\lVert Z_{1t} - \tilde{Z}_{1t} \rVert_2 
  + \lVert Z_{2t} - \tilde{Z}_{2t} \rVert_2).
  \return
\end{equation*}

And we can finish the proof with the following inequalities:
\begin{equation*}
  2 C \wall \sqrt{\frac{b_T}{P \gamma}} \vtSuma \lVert Z_{1t} - \tilde{Z}_{1t} \rVert_2 \\ \leq
  \frac{4C \sqrt{b_T}}{P\gamma} \vtSuma \sum_{l=\vttLower}^{\vttUpper} \lVert
  D_{t+l+R,R} - \tilde{D}_{t,t+l+R} \rVert_2 W(l/\gamma) \\
  \leq O(\frac{\sqrt{b_T}}{P\gamma}) \vtSuma
  \sum_{l=\vttLower}^{\vttUpper} \couplingBeta{t+l-(2i-2m-1)b_T+P}\\
  = O(\frac{\sqrt{b_T}}{P\gamma}) O(b_T^{\frac32-u}\, m^{-\frac12-u})
\end{equation*}
for some positive $u$.  The same argument holds for $Z_{2t}$.
As a result,
\[
E(\vtSumr (U_i - \E_R U_i))^2 = o(\vtSumr \frac{b_T^2}{P\gamma}) =
o(\frac{3P}{2b_T} \frac{b^2}{P\gamma}) = o(\frac{b_T}{\gamma}) \to 0,
\]
as required.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{res:ftest}]
  To clean up the notation, we'll write $\theta_1$ as $\theta$ and
  $q_{K_2-K_1,T-K_2}(1-\alpha)$ as $q_\alpha$.  Let
  $(\hat{\theta}, \hat{\psi})$ denote the \ols\ coefficient estimator
  using the full model and let 
  \[\hat\tau^2 = \frac{1}{T-K_2}\sum_{t=0}^{T-1} (y_{t+1} - x_{1t}'\hat{\theta} -
  x_{2t}'\hat{\psi})^2. \] Since the regressors are orthogonal,
  $\hat\theta$ also is the \ols\ estimator of $\theta$ using the
  restricted model.  The difference between the two models'
  generalization error is
\[
E_T \bar D_2 = \sum_{j=K_1+1}^{K_2} [\psi_j^2 - (\hat{\psi}_j - \psi_j)^2]
\]
For any $\hat{\theta}$, $E_T \bar D_2$ equals zero when
$\hat{\psi}$ lies on the surface of the hypersphere centered at
$\psi$ with radius $|\psi|_2$, and $E_T \bar D_2$ and is greater
than zero when $\hat{\psi}$ lies outside that sphere.
Also, the rejection region in $\Re^{K_2}$ for is the set of values of $\hat{\psi}$
on or beyond the sphere
\[
\hat{\psi}'\hat{\psi} = \hat{\tau}^2 q_\alpha \frac{K_2-K_1}{T}.
\]

We can get a lower bound for the probability
\[\Pr[F \geq q_\alpha \mid E_T \bar{D}_2 \leq 0]\]
by rewriting $\hat{\psi}$ in spherical coordinates re-centered at
$\psi$: $(\hat{r}, \hat{\omega}_1, \dots,
\hat{\omega}_{K_2-K_1-1})$, with 
\[\hat{r} = |\hat{\psi} - \psi|_2 \\
\hat{\omega}_{i} = \tan^{-1}(\frac{(\sum\nolimits_{j=K_1+i+1}^{K_2}(\hat{\psi}_j -
    \psi_j)^2)^{\frac12}}{\hat{\psi}_{K_1+i} - \psi_{K_1+i}}), \quad
  i=1,\dots,K_2-K_1-2, \\
\hat{\omega}_{K_2-K_1-1} =\atan(\hat{\psi}_{K_2-K_1} - \psi_{K_2-K_1},
  \hat{\psi}_{K_2-K_1-1}- \psi_{K_2-K_1-1} )
\]
and
\[
\atan(a, b) \equiv 
\begin{cases}
\tan^{-1}(a/b) & a > 0 \\
\pi + \tan^{-1}(a/b) & a < 0, b \geq 0 \\
-\pi + \tan^{-1}(a/b) & a < 0, b < 0 \\
\pi/2 & a = 0, b > 0 \\
- \pi/2 & a = 0, b < 0 \\
\text{undefined} & a = 0, b = 0.
\end{cases}
\]
Note that $\hat{\omega}_1,\dots,\hat{\omega}_{K_2-K_1 - 2} \sim
\operatorname{uniform}(-\pi/2, \pi/2)$ and
$\hat{\omega}_{K_2-K_1-1}\sim \operatorname{uniform}(-\pi, \pi)$.
Under this coordinate system, the acceptance region is centered at
$(|\psi|_2, \tilde{\omega}_1, \dots, \tilde{\omega}_{K_2-K_1-1})$ with
\[
\tilde{\omega}_i = \tan^{-1}([\sum_{j=i+1}^{K_2-K_1}
  (\psi_j/\psi_i)^2]^{\frac12}) \quad \text{for } i = 1,\dots,K_2-2,\\
\tilde{\omega}_{K_2-K_1-1} = \atan(\psi_{K_2-K_1}, \psi_{K_2-K_1-1}).
\]

If $\psi$ lies outside the acceptance region of the F-test, that
acceptance region is contained in the cone
\[\{(r, \omega_1,\dots,\omega_{K_2-1}) : r \geq 0,\, \tilde{\omega}_{i}
- \xi \leq \omega_i \leq \tilde{\omega}_i + \xi\}\]
with
\[
 \xi = \sin^{-1}(\frac{\hat{\tau}}{|\psi|_2}\sqrt{\frac{q_\alpha (K_2-K_1)}{T}})
\] 
for $\hat{\tau}^2$ given.\footnote{This setup assumes that
  $[\tilde\omega_i - \xi, \tilde\omega_i + \xi] \subset
  [-\pi/2,\pi/2]$ for each $i$.  If not, the region can be rotated
  without changing the results.}

As a result,
\[
\Pr[F \geq q_{\alpha}\wall \mid E_T \bar{D}_2 \leq 0] = 
\Pr[\hat{\psi}'\hat{\psi} \geq \hat \tau^2 q_\alpha \frac{K_2 - K_1}{T}
\mid |\hat{\psi}-\psi|_2 \geq |\psi|_2] \\
\geq 1 - \E(\Pr\{ \hat{\omega}_i \in [\tilde{\omega}_i - \xi, \tilde{\omega}_i +
\xi] \ \forall i  \mid \hat{\tau}^2,
|\hat{\psi}-\psi|_2 \geq |\psi|_2\} 
\mid |\hat{\psi}-\psi|_2 \geq |\psi|_2)\quad a.s. \\ 
= 1 - \frac12 E ((2\xi / \pi)^{K_2-K_1-1}\mid
|\hat{\psi}-\psi|_2 \geq |\psi|_2)\quad a.s. \\
= 1 - \frac12 E (2\xi/\pi)^{K_2-K_1-1} \quad a.s..
\]
The second equality holds because the $\hat{\omega}_i$s are uniform
and the third holds because $\hat{\tau}$ is independent of
$\hat{\psi}$ under normality.

Now~\eqref{eq:ftestreject1} holds since $\xi \to 0$ almost surely as
$\phi_2 \to \infty.$  Moreover, as
$T\to\infty$, $\hat{\tau}^2\to^p\tau^2$ and $q_{\alpha}\to 1$, so
$\plim \xi < \frac{\pi}{2}$.  Consequently,
$(\frac{2\xi}{\pi})^{K_2-K_1-1}\to^p0$, proving~\eqref{eq:ftestreject2}.
\end{proof}
\bibliographystyle{abbrvnat}
\bibliography{../../texlibrary.bzr/main}

\begin{table}[b]
 \begin{multicols}{2}
  \begin{itemize}
  \item log Dividend Price Ratio
  \item log Earnings Price Ratio
  \item Stock Market Variance
  \item Book to Market Ratio
  \item Net Equity Expansion
  \item Percent Equity Issuing
  \item Treasury Bill
  \item Long Term Yield
  \item Long Term Rate
  \item Default Return Spread
  \item Default Yield Spread
  \item Inflation
  \end{itemize}
 \end{multicols}
 \caption{Variables used in Section \ref{sec:empirics} and by Goyal
   and Welch (2008) to predict the equity premium.  Please see Goyal
   and Welch's original paper
   for a detailed description of each variable.}
 \label{tab:equity}
\end{table}

\begin{table}[!tbp]
 \begin{center}
 \begin{tabular}{lrrrr}\hline\hline
\multicolumn{1}{l}{waldtest}&\multicolumn{1}{c}{Res.Df}&\multicolumn{1}{c}{Df}&\multicolumn{1}{c}{F}&\multicolumn{1}{c}{Pr(\textgreaterF)}\tabularnewline
\hline
1&69&&&\\
2&81&$-$12&3.4&0.00066 \\
\hline
\end{tabular}
\caption{Wald test for the null hypothesis that all of the
  coefficients in Goyal and Welch's (2008) ``kitchen sink'' model are
  zero, except for the intercept, using the Newey-West
  variance-covariance matrix.  The p-value is calculated from the $F$
  distribution.\label{tab:gwinsample}}
\end{center}
\end{table}

\clearpage
\begin{figure}
\centering
\textbf{\large{Simulated Coverage of One-Sided DMW Interval for $E_R\bar D_1$}}
\includegraphics{mc/plots/interval-testerror1}
\textbf{\large{Simulated Coverage of Two-Sided DMW Interval for $E_R\bar D_1$}}
\includegraphics{mc/plots/interval-testerror2}
\caption{Simulated coverage of $E_R \bar D_1$ at 90\% confidence using
a one- and two-sided intervals based on the \protect\textsc{dmw} \protect\textsc{oos}
test, plotted as a function of the fraction of observations used in
the test sample, $P/T$.  The solid horizontal line denotes the
intervals' nominal coverage.}
 \label{fig:interval-R}
\end{figure}
\clearpage
\begin{figure}
\centering
\textbf{\large{Simulated Coverage of One-Sided DMW Interval for $E_T\bar D_2$}}
\includegraphics{mc/plots/interval-generror1}
\textbf{\large{Simulated Coverage of Two-Sided DMW Interval for $E_T\bar D_2$}}
\includegraphics{mc/plots/interval-generror2}
\caption{Simulated coverage of $E_T \bar D_2$ at 90\% confidence using
a one- and two-sided intervals based on the \protect\textsc{dmw} \protect\textsc{oos}
test, plotted as a function of the fraction of observations used in
the test sample, $P/T$.  The solid horizontal line denotes the
intervals' nominal coverage.}
\label{fig:interval-T}
\end{figure}
\clearpage

\begin{figure}
  \centering
  \textbf{\large{Simulated Rejection Probability of F-test Under $E_T
      \bar{D}_2 \leq 0$}}
  \includegraphics{mc/plots/ftest-001}
  \caption{Simulated rejection probabilities for the F-test given
    $\E_T \bar{D}_2 \leq 0$ with nominal size 10\%.  Values greater
    than 10\% indicate that the test rejects the benchmark model too
    often.  See Section~\ref{sec:simulation-design} for a discussion
    of the simulation design.}
  \label{fig:ftest}
\end{figure}
\clearpage
\begin{figure}
  \centering
  \textbf{\large{Simulated Rejection Probability of DMW Test Under $E_T
      \bar{D}_2 \leq 0$}}
  \includegraphics{mc/plots/size-dmwsize}  
  \caption{Simulated rejection probabilities for the \protect\textsc{dmw}
    \protect\textsc{oos} $t$-test given $\E_T \bar{D}_2 \leq 0$ with nominal
    size 10\%.  Values greater than 10\% indicate that the test
    rejects the benchmark model too often.  The solid horizontal line
    indicates the nominal rejection probability.  See
    Section~\ref{sec:simulation-design} for a discussion of the
    simulation design.}
  \label{fig:ttest-size}
\end{figure}

\begin{figure}
  \centering
  \textbf{\large{Simulated Rejection Probability of Clark and West
      (2006, 2007) Test Under $E_T \bar{D}_2 \leq 0$}}
  \includegraphics{mc/plots/size-clarkwest}
  \caption{Simulated rejection probabilities for Clark and West's
    (2006, 2007) \protect\textsc{oos} test statistic given $\E_T \bar{D}_2
    \leq 0$ with nominal size 10\%.  Values greater than 10\% indicate
    that the test rejects the benchmark model too often.  The solid
    horizontal line indicates the nominal rejection probability.  See
    Section~\ref{sec:simulation-design} for a discussion of the
    simulation design.}
   \label{fig:clarkwest}
\end{figure}

\begin{figure}
  \centering
  \textbf{\large{Simulated Rejection Probability of McCracken (2007)
      Test \\ Under $E_T \bar{D}_2 \leq 0$}}
  \includegraphics{mc/plots/size-mccracken}
  \caption{Simulated rejection probabilities for McCracken's (2007)
    \protect \textsc{oos} test statistic given $\E_T \bar{D}_2 \leq 0$ with
    nominal size 10\%.  Values greater than 10\% indicate that the
    test rejects the benchmark model too often.  The solid horizontal
    line indicates the nominal rejection probability.  See
    Section~\ref{sec:simulation-design} for a discussion of the
    simulation design.}
  \label{fig:mccracken}
\end{figure}

\begin{figure}
  \centering
  \textbf{\large{Simulated Rejection Probability of DMW Test Under $E_T
      \bar{D}_2 > 0$}}
  \includegraphics{mc/plots/size-dmwpower}
  \caption{Simulated rejection probabilities for the \protect \textsc{dmw}
    \protect\textsc{oos} $t$-test given $\E_T \bar{D}_2 > 0$ with nominal
    size 10\%.  Values greater than 10\% indicate that the test
    rejects the benchmark model too often.  The solid horizontal line
    indicates the nominal rejection probability.  See
    Section~\ref{sec:simulation-design} for a discussion of the
    simulation design.}
  \label{fig:ttest-power}
\end{figure}

\begin{figure}
\centering
\textbf{\large{Difference in OOS MSE of Prevailing Mean and\\ Kitchen
    Sink Models of Equity Premium (OLS)}}
\includegraphics{empirics/plots/oos-mse-1}
\includegraphics{empirics/plots/oos-mse-1b}
\caption{\protect \textsc{oos} difference in the \protect\textsc{mse}
  of the prevailing mean benchmark and the kitchen sink model as a
  function of the test sample size, $R$.  Both models forecast the
  equity premium using annual data from 1928--2008.  The solid line
  gives the \protect \textsc{oos} average, and the shaded region indicates the
  one-sided 95\% confidence interval implied by the \protect
  \textsc{dmw} test.  The bottom panel is a detailed view of the top
  panel for $R \geq 50$.}
\label{fig:empirics1}
\end{figure}

\begin{figure}
\centering
\textbf{\large{Difference in OOS MSE of Prevailing Mean and\\ Kitchen
    Sink Models of Equity Premium (CT)}}
\includegraphics{empirics/plots/oos-mse-2}
\includegraphics{empirics/plots/oos-mse-2b}
\caption{\protect \textsc{oos} difference in the \protect\textsc{mse}
  of the prevailing mean benchmark and the kitchen sink model as a
  function of the test sample size, $R$.  Both models forecast the
  equity premium using annual data from 1928--2008.  The solid line
  gives the \protect \textsc{oos} average, and the shaded region indicates the
  one-sided 95\% confidence interval implied by the \protect
  \textsc{dmw} test.  The bottom panel is a detailed view of the top
  panel for $R \geq 50$.}
\label{fig:empirics2}
\end{figure}

\begin{figure}
\centering
\textbf{\large{OOS MSE of Individual Forecasts of Equity Premium}}
\includegraphics{empirics/plots/oos-ind-ks}
\includegraphics{empirics/plots/oos-ind-pm}
\caption{\protect{\textsc{oos} \textsc{mse} of the Prevailing Mean (\textsc{pm}) and
    Kitchen Sink (\textsc{ks}) models for equity premium prediction as
    a function of the size of the training sample, $R$.  Please note
    that the vertical scales are different in the two plots.}}
\label{fig:empirics3}
\end{figure}

\end{document}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "paper"
%%% End:

% LocalWords: LM clark meese diebold chao corradi mccracken giacomini lm jel iR
% analyses inoue datasets huber efron anova akritas
% calhoun iR berbee th de nondifferentiable jong
% mixingales mcleish AIC Berbee's merlevede Heyde's ib
% mixingaleR TP eq dx dy tex tR tS tT iT sR sw tw vw
% reestimate davidson over-reject anatolyev Anatolyev's iS izx
% coefpart normalpart Jong's jt oos underrejects cltvar Scwarz JEL
% hansen lm McCracken's jel RSQLite elemstatlearning rproject rsqlite
% LocalWords:  McCracken's kilian anatolyev rossi REStud JAppliedEconometrics
% LocalWords:  goyal welch rfs reputational calhoun Berbee's mixingales tR tS
% LocalWords:  Heteroskedasticity Autocorrelation tT iT th berbee iS de dx ixz
% LocalWords:  DMW mcleish sR eq ftestreject lightgray veclen RSQLite zeileis
% LocalWords:  heteroskedasticity hothorn RNews JStatSoftware harrell campbell
% LocalWords:  thompson bivariate Welch's multicollinearity Newey newey tw vw
% LocalWords:  merlevede cltvar dR Scwarz davidson indices lrrrr waldtest Df
% LocalWords:  dmw McCracken MSE OLS mse

### 2010-10-18 R/ResultsFrame.R

@@ -1,22 +1,0 @@
-## The function 'ResultsFrame' takes a string that contains the text
-## for an SQL query and returns a dataframe giving its results and
-## adding ordered factors that label the coefficient values, number of
-## observations, and number of regressors.
-setGeneric("ResultsFrame", function(object,...) standardGeneric("ResultsFrame"))
-setMethod("ResultsFrame", "character",
-          function(object,...) {
-            nlabel <- dbGetQuery(dbc, "select distinct nlabel from nobs order by n;")$nlabel
-            altlabel <- dbGetQuery(dbc, "select distinct altlabel from nobs order by kAlt;")$altlabel
-            nulllabel <- dbGetQuery(dbc, "select distinct nulllabel from nobs order by kNull;")$nulllabel
-            normlabel <- dbGetQuery(dbc, "select distinct normlabel from coefficients order by norm;")$normlabel
-            d <- dbGetQuery(dbc, paste("select * from (", object, ") s, pars p ",
-                                       "on s.isim = p.isim and s.idgp = p.idgp;"))
-            d$ntotal <- d$n
-            k0 <- ordered(d$nulllabel, nulllabel)
-            ka <- ordered(d$altlabel, altlabel)
-            d$k <- k0:ka
-            d$b <- ordered(d$normlabel, normlabel)
-            d$n <- ordered(d$nlabel, nlabel)
-            subset(d, select = c(-isim, -idgp, -nlabel, -kNull, -nulllabel, -kAlt, 
-                        -altlabel, -norm, -normlabel))
-          })

### 2010-10-18 empirics/oos-analysis.R

@@ -60,7 +60,9 @@ oosT <- function(R, mod.formula, dframe, nonneg) {
   
   varest <- drop(NeweyWest(lm(loss1 - loss2 ~ 1), lag = floor(ntest^.25),
                            adjust = TRUE, prewhite = FALSE))
-  list(estimate = avgdiff,
+  list(avg1 = mean(loss1),
+       avg2 = mean(loss2),
+       estimate = avgdiff,
        conf.int = c(avgdiff - sqrt(varest / ntest), Inf),
        p.value = pt(sqrt(ntest / varest) * avgdiff,
          ntest - 1, lower.tail = FALSE))
@@ -78,10 +80,12 @@ fullmod <- lm(fullmodel, data = dframe)
 temp <- latex(coeftest(fullmod, vcov=NeweyWest(fullmod, prewhite=FALSE, lag=2)),
               file = "tables/coeftest.tex", digits = 2)
 temp <- latex(waldtest(fullmod, vcov=NeweyWest(fullmod, prewhite=FALSE, lag=2), test="F"),
-              file = "tables/waldtest.tex", digits = 2)
+              file = "tables/waldtest.tex", digits = 2, caption = "Wald test for the null hypothesis that all of the coefficients in Goyal and Welch's (2008) ``kitchen sink'' model are zero, except for the intercept.", label = "tab:gwinsample")
 
 oosStats <- function(tstats) 
-  ts(cbind(average  = sapply(tstats, function(x) x$estimate),
+  ts(cbind(PM = sapply(tstats, function(x) x$avg1),
+           KS = sapply(tstats, function(x) x$avg2),           
+           average  = sapply(tstats, function(x) x$estimate),
            interval = sapply(tstats, function(x) min(x$conf.int)),
            pvalue   = sapply(tstats, function(x) x$p.value)),
      start = RStart, frequency = 1)
@@ -89,89 +93,61 @@ oosStats <- function(tstats)
 oos    <- oosStats(tstats)
 oos.ct <- oosStats(tstats.ct)
 
+indplot <- function(name, series, file, height = 2, width = 5.5, xlabel = "",
+                    ticks = NULL, labels = TRUE,...) {
+  pdf(file = file, height = height, width = width)
+  par(mar = c(5.1, 4.2, 1.1, 0))
+  plot(cbind(series, 0), yaxt = "n", ylab = name,
+       plot.type = "single", bty = "n",
+       xlab = xlabel, lwd = 0.8,
+       col = c("white", "white"))
[…]

### 2010-12-23 paper.tex
Edited paper to reflect Seth's comments

@@
 \author{Gray Calhoun\thanks{email: \texttt{gcalhoun@iastate.edu}. I
-    would like to thank Julian Betts, Marjorie Flavin, Nir Jaimovich,
-    Lutz Kilian, Michael McCracken, Seth Pruitt, Ross Starr, Yixiao
-    Sun, Allan Timmermann, participants at the 2010 Midwest Economics
-    Association Annual Meetings, the 2010 Joint Statistical Meetings,
-    and in many seminars at \textsc{ucsd}, and espeically Graham
-    Elliott for their valuable suggestions, feedback and advice in
-    writing this paper.  I would also like to thank Amit Goyal for
-    providing computer code and data for his 2008 RFS paper with Ivo
-    Welch \citep{goyal-welch-2008-rfs}.} \\ Iowa State University,
+    would like to thank Julian Betts, Helle Bunzel, Marjorie Flavin,
+    Nir Jaimovich, Lutz Kilian, Michael McCracken, Seth Pruitt, Ross
+    Starr, Yixiao Sun, Allan Timmermann, participants at the 2010
+    Midwest Economics Association Annual Meetings, the 2010 Joint
+    Statistical Meetings, and in many seminars at \textsc{ucsd}, and
+    espeically Graham Elliott for their valuable suggestions, feedback
+    and advice in writing this paper.  I would also like to thank Amit
+    Goyal for providing computer code and data for his 2008 RFS paper
+    with Ivo Welch \citep{GoW:08}.} \\ Iowa State University,
   Economics Department}
+\date{October 24, 2011}
 
@@
   This paper uses dimension asymptotics to study why overfit linear
-  regression models should be compared out-of-sample; we let the number of
-  predictors used by the larger model increase with the number of
-  observations so that their ratio remains uniformly positive.  Under
-  this limit theory, the naive Diebold-Mariano-West out-of-sample test
-  can test hypotheses about a key quantity for evaluating forecasting
-  models---a time series analogue to the generalization error---as
-  long as the out-of-sample period is small relative to the total
-  sample size.  Moreover, tests that are designed to reject if the
-  larger model is true, such as the usual in-sample Wald and
-  \textsc{lm} tests and also Clark and McCracken's (2001, 2005a),
-  \citepos{mccracken_asymptotics_2007} and Clark and West's (2006,
-  2007) out-of-sample statistics, will choose the larger model too
-  often when the smaller model is more accurate.
+  regression models should be compared out-of-sample; we let the
+  number of predictors used by the larger model increase with the
+  number of observations so that their ratio remains uniformly
+  positive.  Under this limit theory, the naive Diebold-Mariano-West
+  out-of-sample test can test hypotheses about a key quantity for
+  evaluating forecasting models---a time series analogue to the
+  generalization error---as long as the out-of-sample period is small
+  relative to the total sample size.  Moreover, tests that are
+  designed to reject if the larger model is true, such as the usual
+  in-sample Wald and \textsc{lm} tests and also Clark and McCracken's
+  (2001, 2005a), \citepos{Mcc:07} and Clark and West's (2006, 2007)
+  out-of-sample statistics, will choose the larger model too often
+  when the smaller model is more accurate.
 
@@
 Although \oos\ comparisons have been popular in macroeconomics and
-finance since \citepos{meese_empirical_1983} seminal study of exchange
-rate models, it is unclear from a theoretical perspective whether or
-not the statistics are useful.  Empirical researchers often cite
-``overfit'' or ``instability'' as reasons for using \oos\ comparisons,
-as in \citet{stock_forecasting_2003}, but neither term is precisely
-defined or formalized.  Compounding this problem, the asymptotic
-distributions of these statistics are derived under conditions that
-rule out either instability or overfit and allow a researcher to use a
-conventional in-sample comparison---a variation of the F-test, for
-example.  As \citet{inoue_kilian_2004} argue, the statistics
-themselves are designed to test hypotheses that can be tested by these
-in-sample statistics.  For example, \citet{diebold_comparing_1995} and
-\citet{west_asymptotic_1996} derive the limiting distributions of many
-popular \oos\ test statistics under conditions that would justify
-these full-sample tests.\footnote{In this paper, we will refer to
-  their basic \oos\ $t$-test as the \dmw\ test.}  Much of the
-subsequent research by \citet{chao_out_2001},
-\citet{clark_tests_2001,clark_evaluating_2005},
-\citet{corradi_consistent_2002,corradi_recent_2004},
-\citet{clark_using_2006,clark_approximately_2007},
-\citet{mccracken_asymptotics_2007}, \citet{anatolyev_inference_2008},
-and others relaxes several of Diebold and Mariano's and West's
-assumptions, but maintains the stationarity and dependence conditions
-that permit in-sample comparisons.\footnote{Like us,
-  \citet{anatolyev_inference_2008} allows the number of regressors to
-  increase with $T$.  But in that paper, they increase slowly enough
-  that the \ols\ coefficients are consistent and asymptotically
-  normal.}  \citet{giacomini_tests_2006}, and
-\citet{giacomini-rossi-2009-REStud,giacomini-rossi-2010-JAppliedEconometrics}
-are exceptions.  Instead of focusing on hypotheses that can be tested
-by in-sample comparisons, \citet{giacomini_tests_2006} derive an \oos\
-test for the null hypothesis that the difference between two models'
-\oos\ forecasting performance is unpredictable, a martingale
-difference sequence, \citet{giacomini-rossi-2009-REStud} test whether
-the \oos\ forecasting performance of a model suffers from a breakdown
-relative to its in-sample performance, and
-\citet{giacomini-rossi-2010-JAppliedEconometrics} test whether the
-forecasting performance is stable. However, those papers focus on a
-particular \oos\ estimation strategy and do not address why naive
-\oos\ comparisons might be generally useful.
+finance since \citepos{MeR:83} seminal study of exchange rate models,
+it is unclear from a theoretical perspective whether or not the
+statistics are useful.  Empirical researchers often cite ``overfit''
+or ``instability'' as reasons for using \oos\ comparisons, as in
+\citet{StW:03}, but neither term is precisely defined or formalized.
+Compounding this problem, the asymptotic distributions of these
+statistics are derived under conditions that rule out either
+instability or overfit and allow a researcher to use a conventional
+in-sample comparison---a variation of the F-test, for example.  As
+\citet{InK:04} argue, the statistics themselves are designed to test
+hypotheses that can be tested by these in-sample statistics.  For
+example, \citet{DiM:95} and \citet{Wes:96} derive the limiting
+distributions of many popular \oos\ test statistics under conditions
+that would justify these full-sample tests.\footnote{In this paper, we
+  will refer to their basic \oos\ $t$-test as the \dmw\ test.}  Much
+of the subsequent research by \citet{CCS:01}, \citet{ClM:01,ClM:05},
+\citet{CoS:02,CoS:04}, \citet{ClW:06,ClW:07}, \citet{Mcc:07},
+\citet{Ana:07}, and others relaxes several of Diebold and Mariano's
+and West's assumptions, but maintains the stationarity and dependence
+conditions that permit in-sample comparisons.\footnote{Like us,
+  \citet{Ana:07} allows the number of regressors to increase with $T$.
+  But in that paper, they increase slowly enough that the \ols\
+  coefficients are consistent and asymptotically normal.}
+\citet{GiW:06}, and \citet{GiR:09, GiR:10} are exceptions.  Instead of
+focusing on hypotheses that can be tested by in-sample comparisons,
+\citet{GiW:06} derive an \oos\ test for the null hypothesis that the
+difference between two models' \oos\ forecasting performance is
+unpredictable, a martingale difference sequence, \citet{GiR:09} test
+whether the \oos\ forecasting performance of a model suffers from a
+breakdown relative to its in-sample performance, and \citet{GiR:10}
+test whether the forecasting performance is stable. However, those
+papers focus on a particular \oos\ estimation strategy and do not
+address why naive \oos\ comparisons might be generally useful.
 
@@
 complicated theoretical models and \oos\ analysis supports simple
-benchmarks, as seen in \citet{meese_empirical_1983},
-\citet{stock_forecasting_2003}, and \citet{goyal-welch-2008-rfs}.
-Since these different approaches strongly influence the outcome of
-research, it is important to know when each is appropriate.  The
-explanations in favor of \oos\ comparisons claim that they should be
-more robust to unmodeled instability
-\citep{clark_power_2005,giacomini_tests_2006,giacomini-rossi-2009-REStud,giacomini-rossi-2010-JAppliedEconometrics}
-or to overfit \citep{mccracken_data_1998,clark_can_2004}.  Both
-explanations presume that the in-sample comparison is invalid and the
-\oos\ comparisons are more reliable.  Of course, as
-\citet{inoue_kilian_2004,inoue_selection_2006} point out, both
-in-sample and \oos\ methods could be valid, but the \oos\ methods
-could have lower power.
+benchmarks, as seen in \citet{MeR:83}, \citet{StW:03}, and
+\citet{GoW:08}.  Since these different approaches strongly influence
+the outcome of research, it is important to know when each is
+appropriate.  The explanations in favor of \oos\ comparisons claim
+that they should be more robust to unmodeled instability
+\citep{ClM:05,GiW:06,GiR:09,GiR:10} or to overfit
+\citep{Mcc:98,Cla:04}.  Both explanations presume that the in-sample
+comparison is invalid and the \oos\ comparisons are more reliable.  Of
+course, as \citet{InK:04,InK:06} point out, both in-sample and \oos\
+methods could be valid, but the \oos\ methods could have lower power.
 
@@
 training window, but our basic conclusions should be true for other
-estimation strategies and models as well.  We show that the usual
-\oos\ average is asymptotically normal and can consistently estimate
-the difference between the models' expected loss in periods
-$T+1,T+2,\dots$ conditional on the on the data available in period
-$T$, a time-series analogue to the generalization error.\footnote{See,
-  for example, \citet{elemstatlearning}.}  Under these asymptotics,
-the generalization error does not converge to the expected performance
-of the pseudo-true models, so the in-sample and \oos\
-comparisons measure different quantities and should be expected to
-give different results for reasons beyond simple size and power
-comparisons.  Under our theory, the model that is closer to the true
-\dgp\ in population can forecast worse.  In such a situation, an
-in-sample comparison would correctly reject the null hypothesis that
-the benchmark is true, and an \oos\ comparison would correctly fail to
-reject the null that the benchmark is more accurate.\footnote{In a
-  pair of papers similar to ours,
-  \citet{RePEc:fip:fedkrw:rwp09-10,RePEc:fip:fedkrw:rwp09-11} study
-  in-sample and \oos\ tests that the larger model has nonzero
-  coefficients that are too close to zero to expect the model to
-  forecast more accurately.  Like this paper, they argue that the
-  larger model can be true but less accurate.  However, they focus on
-  an aspect of the \dgp\ that makes this phenomenon likely, while we
-  focus on the coefficient estimates that produce less accurate
-  forecasts.}
+estimation strategies and models as well.  Under this asymptotic
+theory, the \ols\ coefficient estimator is no longer consistent or
+asymptotically normal \citep{Hub:73} and has positive variance in the
+limit.  Even so, we show that the usual \oos\ average is
+asymptotically normal and can consistently estimate the difference
+between the models' expected loss in periods $T+1,T+2,\dots$
+conditional on the on the data available in period $T$, a time-series
+analogue to the generalization error.\footnote{See, for example,
+  \citet{HTF:08}.}  Under these asymptotics, the generalization error
+does not converge to the expected performance of the pseudo-true
+models, so the in-sample and \oos\ comparisons measure different
+quantities and should be expected to give different results for
+reasons beyond simple size and power comparisons.  Under our theory,
+the model that is closer to the true \dgp\ in population can forecast
+worse.  In such a situation, an in-sample comparison would correctly
+reject the null hypothesis that the benchmark is true, and an \oos\
+comparison would correctly fail to reject the null that the benchmark
+is more accurate.\footnote{In a pair of papers similar to ours,
+  \citet{ClM:09,ClM:09b} study in-sample and \oos\ tests that the
+  larger model has nonzero coefficients that are too close to zero to
+  expect the model to forecast more accurately.  Like this paper, they
+  argue that the larger model can be true but less accurate.  However,
+  they focus on an aspect of the \dgp\ that makes this phenomenon
+  likely, while we focus on the coefficient estimates that produce
+  less accurate forecasts.}
 
@@
 choose a model for forecasting.  Although there has been little
-emphasis on hypothesis testing in these settings, testing is usually
+emphasis on hypothesis testing in this setting, testing is usually
 appropriate: there is usually a familiar benchmark model in place, and
@@
 
-However, since the models' coefficients are imprecisely
-estimated, the test sample must be small to ensure that the model
-estimated over the training sample is similar to the one that will be
-estimated over the full sample.  In particular, $P/T \to 0$ is
-required for consistent estimation, and $P^2/T \to 0$ is required for
-valid confidence intervals and inference.  For larger $P$, the \oos\
+Since the models' coefficients are imprecisely estimated in the limit,
+the test sample must be small to ensure that the model estimated over
+the training sample is similar to the one that will be estimated over
+the full sample.  In particular, $P/T \to 0$ is required for
+consistent estimation, and $P^2/T \to 0$ is required for valid
+confidence intervals and inference.  For larger $P$, the \oos\
 comparisons remain asymptotically normal, but are centered on the
@@
 
-Under this asymptotic theory, the \ols\ coefficient estimator is no
-longer consistent or asymptotically normal \citep{huber_robust_1973},
-so this is a useful way to model overfit and imprecisely estimated
-models.  Moreover, \citet{efron_biased_1986,efron_estimation_2004}
-shows that in-sample comparisons overestimate models' accuracy by a
-factor proportional to this ratio.  Despite the non-normality of the
-coefficient estimators, modifications of the F-test are valid under
-this asymptotic theory, as shown by \citet{boos_anova_1995},
-\citet{akritas_asymptotics_2000},
-\citet{akritas_heteroscedastic_2004}, and
-\citet{calhoun_hypothesis_2009}, among others.  The F-test and Wald
-tests are no longer asymptotically valid themselves.  Such results
-establish that hypotheses about the parameters of the \dgp\ can be
-tested in-sample even if one or both models are overfit.  For that
-very reason, these tests can not reliably choose a model for
-forecasting and will reject the benchmark too often.  We show this
-analytically in Section~\ref{sec:insample}.  Moreover, under this
-asymptotic theory, many recent \oos\ test statistics, such as those
-derived by \cite{clark_tests_2001,clark_evaluating_2005},
-\citet{mccracken_asymptotics_2007}, and
-\citet{clark_using_2006,clark_approximately_2007} should behave like
-the F-test.  These tests are also designed to reject the benchmark
-when the alternative model is true, and so they may reject too often
-when the benchmark is false but more accurate.  Obviously, since the
+Since the \ols\ coefficient estimator is no longer consistent or
+asymptotically normal, the F-test and Wald tests are no longer
+asymptotically valid.  Moreover, \citet{Efr:86,Efr:04} shows that
+naive comparisons of in-sample loss overestimate models' accuracy by a
+factor proportional to $K/T$, $K$ being the number of regressors.  But
+modifications of the F-test are valid under this asymptotic theory, as
+shown by \citet{BoB:95}, \citet{AkA:00}, \citet{AkP:04}, and
+\citet{Cal:10b}, among others.  Such results establish that hypotheses
+about the parameters of the \dgp\ can be tested in-sample even if one
+or both models are overfit.  For that very reason, these tests can not
+reliably choose a model for forecasting and will reject the benchmark
+too often.  We show this analytically in Section~\ref{sec:insample}.
+Moreover, under this asymptotic theory, many recent \oos\ test
+statistics, such as those derived by \cite{ClM:01,ClM:05},
+\citet{Mcc:07}, and \citet{ClW:06,ClW:07} should behave like the
+F-test.  These tests are also designed to reject the benchmark when
+the alternative model is true, and so they may reject too often when
+the benchmark is false but more accurate.  Obviously, since the
 distribution of these statistics converges to the normal when $P/T \to
-\infty$ (with the number of regressors fixed), these statistics behave
+0$ (with the number of regressors fixed), these statistics behave
 like the \dmw\ test when $P$ is small, but should over-reject the
@@
 supporting our theoretical results.  Section~\ref{sec:empirics}
-applies the \oos\ statistic to \citepos{goyal-welch-2008-rfs} dataset
+applies the \oos\ statistic to \citepos{GoW:08} dataset
 for equity premium prediction, and Section~\ref{sec:conclusion}
@@
 econometrics, because absolute regularity admits a particular coupling
-argument \citep{berbee_random_1979} that is unavailable for strong
-mixing sequences.
+argument \citep{Ber:79} that is unavailable for strong mixing
+sequences.  Please see, for example, \citet{Dav:94} for a discussion
+of these mixing conditions.
 
@@
   \begin{equation*}
-    \lVert \lambda_{\max}(X_{iS_{T}}'X_{iS_{T}}) \rVert_{4+\delta}
+    \lVert \lambda_{\max}(X_{iS_{T}}'X_{iS_{T}}) \rVert_{3+\delta}
     \leq S_{T}\, \Delta \\
@@
     \lambda_{\max}(X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})
-    \rVert_{4+\delta} \leq S_{T}\, \Delta \\
-    \lVert \lambda_{\max}((X_{iS_{T}}'X_{iS_{T}})^{-1}) \rVert_{4+\delta} \leq \Delta/S_{T} \\
+    \rVert_{3+\delta} \leq S_{T}\, \Delta \\
+    \lVert \lambda_{\max}((X_{iS_{T}}'X_{iS_{T}})^{-1}) \rVert_{3+\delta} \leq \Delta/S_{T} \\
     \lVert
-    \lambda_{\max}((X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})^{-1})\rVert_{4+\delta}
+    \lambda_{\max}((X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})^{-1})\rVert_{3+\delta}
     \leq \Delta/S_{T}
@@
 condition is weak and allows the loss function itself to be
-nondifferentiable; for example, absolute error and many asymmetric loss functions
+non-differentiable; for example, absolute error and many asymmetric loss functions
 satisfy this assumption.
@@
 implications.  In practical terms, this assumption requires that the
-test sample be large, that the forecaster plans to use the model for
-many periods in the future, and that there is enough data that
-including or excluding the test sample does not affect the estimates
-of $\theta_1$ or $\theta_2$ very much.
+forecaster plans to use the model for many periods in the future, that
+the test sample be large, and that the training sample be much larger,
+so that including or excluding the test sample does not affect the
+estimates of $\theta_1$ or $\theta_2$ very much.
 
@@
 consider.  We use the same class of estimators studied by
-\citet{de_jong_consistency_2000} (their class $\mathcal{K}$); see
+\citet{DeD:00} (their class $\mathcal{K}$); see
 their paper for further discussion.
@@
 \end{thm}
-The requirement that $\sigma^2$ be uniformly a.s. positive is
-not restrictive under our asymptotic theory.  Since the models'
+The requirement that $\sigma^2$ be uniformly a.s. positive is not
+restrictive under our asymptotic theory.  Since the models'
 coefficients are estimated with uncertainty in the limit, the two
 models give different forecasts even if they both nest the \dgp.  This
-is similar to \citepos{giacomini_tests_2006} rolling-window result,
-but comes from different asymptotics.
+is similar to \citepos{GiW:06} rolling-window result, but comes from
+different asymptotics.
 
@@
 and were introduced and studied extensively by
-\citet{mcleish_dependent_1974,mcleish_invariance_1975,mcleish_maximal_1975,mcleish_invariance_1977}.
-This lemma shows that the estimation uncertainty introduces dependence
-into the \oos\ forecast errors, but that additional dependence is
-contained in the term $\E_R \bar D_1$ and can be effectively removed
-by subtraction.  The second part of the Lemma shows that the basic
-mixingale \clt\ established by \citet{de_jong_central_1997} applies in
-this setting.\footnote{De Jong proves two \clt s: one for mixingales
-  and one for \ned\ functions of mixing processes.  His mixingale
-  result makes assumptions about the behavior of the sample second
-  moment that arise as consequences of \ned.  The proof of
-  Lemma~\ref{res-mixingale} shows that the arguments used for de
-  Jong's \ned\ \clt\ continue to hold for our \oos\ process---in
-  effect, that the \oos\ process has slightly more structure than
-  required for it to be a mixingale.}
+\citet{Mcl:74,Mcl:75,Mcl:75b,Mcl:77}.  This lemma shows that the
+estimation uncertainty introduces dependence into the \oos\ forecast
+errors, but that additional dependence is contained in the term $\E_R
+\bar D_1$ and can be effectively removed by subtraction.  The second
+part of the Lemma shows that the basic mixingale \clt\ established by
+\citet{Dej:97} applies in this setting.\footnote{De Jong proves two
+  \clt s: one for mixingales and one for \ned\ functions of mixing
+  processes.  His mixingale result makes assumptions about the
+  behavior of the sample second moment that arise as consequences of
+  \ned.  The proof of Lemma~\ref{res-mixingale} shows that the
+  arguments used for de Jong's \ned\ \clt\ continue to hold for our
+  \oos\ process---in effect, that the \oos\ process has slightly more
+  structure than required for it to be a mixingale.}
 
@@
       Lemma~\ref{res-mixingale}, the proof of this lemma takes
-      \citepos{de_jong_consistency_2000} existing consistency results
+      \citepos{DeD:00} existing consistency results
       for \ned\ processes and shows that the same arguments can be
@@
 theory in small samples.\footnote{Simulations were conducted in R
-  \citep{rproject} using the Lattice \citep{lattice} and RSQLite
-  \citep{rsqlite} packages for graphics and data management
+  \citep{Rde:10} using the Lattice \citep{Sar:10} and RSQLite
+  \citep{Jam:10} packages for graphics and data management
   respectively.}  The first looks at the asymptotic normality of the
@@
 
-Results using \citepos{mccracken_asymptotics_2007} critical values are
+Results using \citepos{Mcc:07} critical values are
 presented in Figure~\ref{fig:mccracken} and are similar to those using
@@
 This section presents an analysis of equity premium predictability
-similar to \citet{goyal-welch-2008-rfs}.\footnote{All of the
-  calculations in this section are done in R \citep{rproject}.  We
-  also use code provided by \citet{zeileis-hothorn-2002-RNews},
-  \citet{zeileis-2004-JStatSoftware}, and \citet{harrell-2010-R}.}  We
-estimate the expected forecasting performance of the largest model
-they consider, a model with 13 regressors, using 81 observations
-(annual data from 1928 to 2009).  We construct confidence intervals
-for the difference in performance between this model and a prevailing
-mean benchmark, and do so for different values of $R$ and $P$ to
-examine the effect of the training and test sample choice on this
-\oos\ statistic.  We find that the estimate of the larger model's
-\mse\ decreases relative to the benchmark as $R$ increases, but it is
-never smaller than the benchmark's.  This result, combined with the
-larger model's in-sample significance, suggests that there may be a
-real relationship between the equity premium and some of these
-predictors, but that the relationship can not be estimated accurately
-enough to be useful for forecasting and supports
-\citepos{goyal-welch-2008-rfs} conclusions.  These results hold even
-when imposing \citepos{campbell-thompson-2008-rfs} restriction that
-the equity premium forecast be non-negative.
-
-We'll start with a very brief review.  \citet{goyal-welch-2008-rfs}
+similar to \citet{GoW:08}.\footnote{All of the calculations in this
+  section are done in R \citep{Rde:10}.  We also use code provided by
+  \citet{Zeh:02}, \citet{Zei:04}, and \citet{Har:10}.}  We estimate
+the expected forecasting performance of the largest model they
+consider, a model with 13 regressors, using 81 observations (annual
+data from 1928 to 2009).  We construct confidence intervals for the
+difference in performance between this model and a prevailing mean
+benchmark, and do so for different values of $R$ and $P$ to examine
+the effect of the training and test sample choice on this \oos\
+statistic.  We find that the estimate of the larger model's \mse\
+decreases relative to the benchmark as $R$ increases, but it is never
+smaller than the benchmark's.  This result, combined with the larger
+model's in-sample significance, suggests that there may be a real
+relationship between the equity premium and some of these predictors,
+but that the relationship can not be estimated accurately enough to be
+useful for forecasting and supports \citepos{GoW:08}
+conclusions.  These results hold even when imposing
+\citepos{CaT:08} restriction that the equity
+premium forecast be non-negative.
+
+We'll start with a very brief review.  \citet{GoW:08}
 study the \oos\ forecasting performance of different variables thought
@@
 Table~\ref{tab:equity}.\footnote{Table~\ref{tab:equity} only lists the
-  variables used in \citepos{goyal-welch-2008-rfs} ``kitchen sink''
+  variables used in \citepos{GoW:08} ``kitchen sink''
   model.  Some of the variables that they use in bivariate models are
@@
   because the variables are linear combinations of other variables.}
-\citet{goyal-welch-2008-rfs} estimate the \oos\ forecasting
+\citet{GoW:08} estimate the \oos\ forecasting
 performance of bivariate models of the form
@@
 prevailing mean of the equity premium.
-\citet{campbell-thompson-2008-rfs} find that nonlinear extensions of
+\citet{CaT:08} find that nonlinear extensions of
 Goyal and Welch's models are more accurate, either imposing sign
@@
 
-Obviously, \citepos{goyal-welch-2008-rfs} bivariate models do not
+Obviously, \citepos{GoW:08} bivariate models do not
 match the asymptotic theory of this paper, so we restrict our
@@
 2009.  This makes the ratio $K/T$ equal to about 0.16.  We also
-present results for one of \citepos{campbell-thompson-2008-rfs}
+present results for one of \citepos{CaT:08}
 restricted forecasting models.  For this model, we estimate
@@
 regression for Equation~\eqref{eq:2}, using Newey-West standard errors
-with two lags \citep{newey_simple_1987}.\footnote{We compare the test
-  statistic to critical values from the $F$-distribution.}  The
-$p$-value is very small (less than 0.01), indicating that the
-coefficients are nonzero in population and at least one of these
-predictors is correlated with the equity premium.  As we argue
-earlier, this result does not imply that the model will forecast well,
-which we look at next.
+with two lags \citep{NeW:87}.\footnote{We compare the test statistic
+  to critical values from the $F$-distribution.}  The $p$-value is
+very small (less than 0.01), indicating that the coefficients are
+nonzero in population and at least one of these predictors is
+correlated with the equity premium.  As we argue earlier, this result
+does not imply that the model will forecast well, which we look at
+next.
 
@@
 Figures~\ref{fig:empirics1} plots the \ols\ results and
-Figure~\ref{fig:empirics2} imposes
-\citepos{campbell-thompson-2008-rfs} restriction.  The solid line
-in each figure shows the \oos\ average, $\bar D_1$, and the shaded
-region indicates the 95\% one-sided confidence interval implied by the
-\dmw\ test.  Negative numbers indicate that the kitchen sink model has
-higher out-of-sample loss.  We can see that the same patterns hold for
-both models: the performance difference decreases with $R$, but the
-kitchen sink model is never more accurate.  We also see that the
-performance difference decreases suddenly over the period $R=29$ to
-$R=34$ (corresponding to the years 1956--1961).
+Figure~\ref{fig:empirics2} imposes \citepos{CaT:08} restriction.  The
+solid line in each figure shows the \oos\ average, $\bar D_1$, and the
+shaded region indicates the 95\% one-sided confidence interval implied
+by the \dmw\ test.  Negative numbers indicate that the kitchen sink
+model has higher out-of-sample loss.  We can see that the same
+patterns hold for both models: the performance difference decreases
+with $R$, but the kitchen sink model is never more accurate.  We also
+see that the performance difference decreases suddenly over the period
+$R=29$ to $R=34$ (corresponding to the years 1956--1961).
 Figure~\ref{fig:empirics3} plots the accuracy of the individual
@@
 change may indicate instability in the underlying relationship, as
-\citet{goyal-welch-2008-rfs} propose.
+\citet{GoW:08} propose.
 
 In summary, we fail to reject the null that the benchmark prevailing
-mean model is more accurate than \citepos{goyal-welch-2008-rfs}
-kitchen sink.  This result is consistent with Goyal and Welch's
-original analysis.  Unlike Goyal and Welch, we attribute this result,
-at least in part, to parameter uncertainty---the full sample results
-indicate that the larger model could predict better than the
-benchmark with enough data.  Obviously, this is an illustrative
-exercise only and is not meant to be comprehensive.  In this dataset,
-there is likely parameter instability that we have not addressed, and
-we have not dealt with variable persistence at all.
+mean model is more accurate than \citepos{GoW:08} kitchen sink.  This
+result is consistent with Goyal and Welch's original analysis.  Unlike
+Goyal and Welch, we attribute this result, at least in part, to
+parameter uncertainty---the full sample results indicate that the
+larger model could predict better than the benchmark with enough data.
+Obviously, this is an illustrative exercise only and is not meant to
+be comprehensive.  In this dataset, there is likely parameter
+instability that we have not addressed, and we have not dealt with
+variable persistence at all.
 \section{Conclusion}\label{sec:conclusion}
@@
 practice may favor simple benchmark models too much.  Existing
-corrections, proposed by
-\citet{clark_tests_2001,clark_evaluating_2005},
-\citet{mccracken_asymptotics_2007} and
-\citet{clark_using_2006,clark_approximately_2007}, seem to correct too
-much, though, and reject too often when the benchmark model is more
-accurate.
+corrections, proposed by \citet{ClM:01,ClM:05}, \citet{Mcc:07} and
+\citet{ClW:06,ClW:07}, seem to correct too much, though, and reject
+too often when the benchmark model is more accurate.
 
@@
 The results in this paper rely heavily on a coupling argument for
-absolutely regular sequences, Berbee's Lemma
-\citep{berbee_random_1979}.  In fact, many of the results of this
-paper (\ref{res-confidence-intervals}, \ref{res-mixingale}, and
-\ref{res-variance-estimator}) are modifications of existing
-results for \ned\ functions of mixing processes by
-\citet{de_jong_central_1997} and \citet{de_jong_consistency_2000};
-this coupling argument is used to explicitly derive inequalities that
-arise naturally for \ned\ processes.  Lemma \ref{lem-basic-coupling}
-establishes these inequalities, which are based on a proposition of
-\citet{merlevede_coupling_2002}.
-
-We present \citeauthor{merlevede_coupling_2002}'s
-(\citeyear{merlevede_coupling_2002}) statement of Berbee's Lemma for
+absolutely regular sequences, Berbee's Lemma \citep{Ber:79}.  In fact,
+many of the results of this paper (\ref{res-confidence-intervals},
+\ref{res-mixingale}, and \ref{res-variance-estimator}) are
+modifications of existing results for \ned\ functions of mixing
+processes by \citet{Dej:97} and
+\citet{DeD:00}; this coupling argument is used to
+explicitly derive inequalities that arise naturally for \ned\
+processes.  Lemma \ref{lem-basic-coupling} establishes these
+inequalities, which are based on a proposition of
+\citet{MeP:02}.
+
+We present \citeauthor{MeP:02}'s
+(\citeyear{MeP:02}) statement of Berbee's Lemma for
 the reader's reference.  In the following Lemma, $\beta(X,Y)$ is the
@@
 \end{lem}
-\noindent\citep{merlevede_coupling_2002}
+\noindent\citep{MeP:02}
 \end{quotation}
@@
 The proof is virtually identical to the proof of Proposition 2.3 in
-\citet{merlevede_coupling_2002} and is omitted.
+\citet{MeP:02} and is omitted.
 
@@
 \begin{proof}[Proof of Lemma \ref{res-mixingale}, Part 2.]
-  A modification of \citepos{de_jong_central_1997} \clt s for
+  A modification of \citepos{Dej:97} \clt s for
   mixingale and \ned\ arrays will complete the proof.
@@
 $b_T\to\infty$, and $b_T/P\to 0$.  The same arguments used in
-\citepos{de_jong_central_1997} Theorem 1 show that
+\citepos{Dej:97} Theorem 1 show that
 \begin{equation*}
@@
 Note that $\{Z_i - E_{R + (i-1)b_T},\mathcal{F}_{R + i b_T}\}_i$ is an
-\mds\ by construction, so \citepos{hall_martingale_1980} Theorem 3.2
-and Corollary 3.1 ensure that\footnote{Note that $\sigma^2 \in
-  \mathcal{F}_t$ for all $t \geq R$, so Hall and Heyde's condition
-  (3.21) is unnecessary---see the remarks after their result.}
+\mds\ by construction, so \citepos{HaH:80} Theorem 3.2 and Corollary
+3.1 ensure that\footnote{Note that $\sigma^2 \in \mathcal{F}_t$ for
+  all $t \geq R$, so Hall and Heyde's condition (3.21) is
+  unnecessary---see the remarks after their result.}
 \[
@@
 \end{equation}
-Equation (\ref{eq:cltvar2}) holds as in \citet{de_jong_central_1997}
-(see the proof of his Theorem 2); to see that (\ref{eq:cltvar1})
-holds, we'll use an argument based on his Lemma 5.  Define
+Equation (\ref{eq:cltvar2}) holds as in \citet{Dej:97} (see the proof
+of his Theorem 2); to see that (\ref{eq:cltvar1}) holds, we'll use an
+argument based on his Lemma 5.  Define
 \[
@@
 \begin{proof}[Proof of Lemma \ref{res-variance-estimator}]
-  The proof follows \citepos{de_jong_consistency_2000} Theorem 2.1
+  The proof follows \citepos{DeD:00} Theorem 2.1
   closely.  We start by defining similar quantities to theirs,
@@
 with the second term vanishing by Lemma \ref{res-mixingale} and
-\citepos{davidson_l1-convergence_1993} mixingale \lln.
+\citepos{Dav:93} mixingale \lln.
 
@@
 \newcommand{\UFiltration}[1]{\ensuremath{\mathcal{F}_{(#1)b_{T}+R-P}}}%
-Next, we'll prove (\ref{eq:5}). As in
-\citet{de_jong_consistency_2000}, let
+Next, we'll prove (\ref{eq:5}). As in \citet{DeD:00}, let
 \begin{equation*}
@@
 \E_R U_i))^2 = O(\vtSumr c_i^2)$ where the $c_i$ are the mixingale
-magnitude indices \citep{mcleish_maximal_1975}.
+magnitude indices \citep{Mcl:75}.
 
@@
 % LocalWords:  thompson bivariate Welch's multicollinearity Newey newey tw vw
-% LocalWords:  merlevede cltvar dR Scwarz davidson indices lrrrr waldtest Df
-% LocalWords:  dmw McCracken MSE OLS mse
+% LocalWords:  merlevede cltvar dR Scwarz davidson indices lrrrr waldtest Df jt
+% LocalWords:  dmw McCracken MSE OLS mse inoue huber elemstatlearning efron sw
+% LocalWords:  anova akritas jong normalpart coefpart Jong's rproject rsqlite
+% LocalWords:  unrestrictive datasets Heyde's ib oos

### 2011-02-22 paper.tex
Edited paper to reflect Graham's comments

@@
 
+\newcommand{\oosA}{\bar{D}_a}
+\newcommand{\oosB}{\bar{D}_b}
+
 \newcommand{\oost}{\ensuremath{\operatorname{oos-t}}}
@@
 
-\newcommand{\CenteredAverage}{\frac{\bar{D}_1 - \E_T\bar{D}_2}{\hat\sigma / \sqrt{P}}}
+\newcommand{\CenteredAverage}{\frac{\oosA - \E_T\oosT}{\hat\sigma / \sqrt{P}}}
 \newcommand{\CenteredAverageI}{\ensuremath{\frac{1}{\hat\sigma
@@
 \newcommand{\CenteredAverageII}{\ensuremath{\frac{\sqrt{P}}{\hat\sigma}
-    (\E_R\bar D_1 - \E_T\bar{D}_2)}}
+    (\E_R\oosA - \E_T\oosB)}}
 
@@
 \newcommand{\varianceDiffA}{\ensuremath{\frac1{P} \oosSum{s,t}{1}
-    \lvert (D_{tR} - \E_R D_{tR})(\E_R D_{sR} - \bar D_1) \rvert
+    \lvert (D_{tR} - \E_R D_{tR})(\E_R D_{sR} - \oosA) \rvert
     \vWeight}}
 \newcommand{\varianceDiffAi}{\ensuremath{\frac1P \oosSum{s}{1}(\E_R
-    D_{sR} - \bar D_1 )^2}}
+    D_{sR} - \oosA )^2}}
 \newcommand{\varianceDiffAii}{\ensuremath{\frac1P \oosSum{s}{1}
@@
   will refer to their basic \oos\ $t$-test as the \dmw\ test.}  Much
-of the subsequent research by \citet{CCS:01}, \citet{ClM:01,ClM:05},
-\citet{CoS:02,CoS:04}, \citet{ClW:06,ClW:07}, \citet{Mcc:07},
+of the subsequent research by \citet{Mcc:00, Mcc:07}, \citet{CCS:01},
+\citet{ClM:01,ClM:05}, \citet{CoS:02,CoS:04}, \citet{ClW:06,ClW:07},
 \citet{Ana:07}, and others relaxes several of Diebold and Mariano's
@@
 difference between two models' \oos\ forecasting performance is
-unpredictable, a martingale difference sequence, \citet{GiR:09} test
+unpredictable, a martingale difference sequence; \citet{GiR:09} test
 whether the \oos\ forecasting performance of a model suffers from a
-breakdown relative to its in-sample performance, and \citet{GiR:10}
+breakdown relative to its in-sample performance; and \citet{GiR:10}
 test whether the forecasting performance is stable. However, those
@@
 shown by \citet{BoB:95}, \citet{AkA:00}, \citet{AkP:04}, and
-\citet{Cal:10b}, among others.  Such results establish that hypotheses
+\citet{Cal:10}, among others.  Such results establish that hypotheses
 about the parameters of the \dgp\ can be tested in-sample even if one
@@
 distribution of these statistics converges to the normal when $P/T \to
-0$ (with the number of regressors fixed), these statistics behave
-like the \dmw\ test when $P$ is small, but should over-reject the
-benchmark when $P$ is large.  Section~\ref{sec:mc} presents
-simulations that support these claims.
+0$ (with the number of regressors fixed), these statistics behave like
+the \dmw\ test when $P$ is small, but should over-reject the benchmark
+when $P$ is large.  Section~\ref{sec:mc} presents simulations that
+support these claims.
 
@@
 \]
-The \oos\ average is denoted $\bar D_1$:
-\[
-\bar D_1 \equiv P^{-1} \oosSum{t}{1} D_{tR}
+The \oos\ average is denoted $\oosA$:
+\[
+\oosA \equiv P^{-1} \oosSum{t}{1} D_{tR}
 \quad \text{with} \quad D_{tS} \equiv L(y_{t+\h} - x_{1t}'\bh{1S}) -
@@
 \[
-\oost \equiv \frac{\sqrt{P} \bar D_1}{\hat\sigma},
+\oost \equiv \frac{\sqrt{P} \oosA}{\hat\sigma},
 \]
@@
 Autocorrelation-Consistent, or \hac) estimator of the asymptotic
-variance of $\bar D_1$.
+variance of $\oosA$.
 
@@
 whichever model is chosen will be used for an additional $Q$ periods
-in the future and let $\bar D_2$ denote the difference in average
+in the future and let $\oosB$ denote the difference in average
 performance over those periods:
 \[
-\bar D_2 \equiv Q^{-1} \sum_{t=T+1}^{T+Q} D_{tT}.
-\]
-Note that $\bar D_1$ depends on the training sample estimators,
-$\hat\theta_{iR}$, and $\bar D_2$ depends on the full sample
+\oosB \equiv Q^{-1} \sum_{t=T+1}^{T+Q} D_{tT}.
+\]
+Note that $\oosA$ depends on the training sample estimators,
+$\hat\theta_{iR}$, and $\oosB$ depends on the full sample
 estimators, $\hat\theta_{iT}$.  A forecaster has access to the
 information set $\mathcal{F}_T$ when deciding between the two
-forecasting models, but $\mathcal{F}_T$ does not contain $\bar D_2$.
+forecasting models, but $\mathcal{F}_T$ does not contain $\oosB$.
 So a forecaster should decide between the models based on the
-conditional expectation, $\E_T \bar{D}_2$. If this quantity is
+conditional expectation, $\E_T \oosB$. If this quantity is
 positive, the first model is expected to perform worse in the future,
@@
 When the underlying series is i.i.d., this random variable, $\E_T
-\bar{D}_2$, is equal to the difference in the models' generalization
+\oosB$, is equal to the difference in the models' generalization
 error.  The generalization error of model $i$ is defined as
@@
 implications.  In practical terms, this assumption requires that the
-forecaster plans to use the model for many periods in the future, that
+forecaster plan to use the model for many periods in the future, that
 the test sample be large, and that the training sample be much larger,
-so that including or excluding the test sample does not affect the
-estimates of $\theta_1$ or $\theta_2$ very much.
+by enough that including or excluding the test sample does not affect
+the estimates of $\theta_1$ or $\theta_2$ very much.
 
@@
 
+Assumptions~\ref{asmp-1}--\ref{asmp-5} are broadly similar to
+\citepos{Wes:96} assumptions, except with regard to model complexity
+and the size of the test sample.  West assumes that $K_1$ and $K_2$
+are both finite, while we let them grow rapidly with $T$
+(Assumption~\ref{asmp-1}), and West lets $P/R$ converge to any value
+in $[0,\infty]$, while we require $P^2/R \to 0$
+(Assumption~\ref{asmp-4}).\footnote{\citet{Wes:96} does not have a
+  second \oos\ period, so there is no analogue in his paper to our
+  restriction on $Q$.}  Obviously, these differences are
+related---allowing for complex models requires tighter constraints on
+the size of the test sample.
+
+Our other assumptions are similar.  The loss function must be smooth
+almost everywhere, which is slightly less restrictive than
+\citet{Wes:96} requires but is not new; \citet{Mcc:00} extends West's
+results to cover a similar case.  West relaxes our assumption that the
+forecasts come from a linear regression model; we could relax our
+assumption to include other linear estimators, but there would be
+little new insight.  We assume full stationarity and absolute
+regularity of the underlying random array, while West assumes
+covariance stationarity and strong mixing of the transformed forecast
+errors; and the details our moment conditions are different, but seem
+that they would hold in similar environment to West's.  Finally, since
+West's is a more standard environment, he assumes the existence of a
+consistent estimator of the variance, while we construct it
+explicitly.  Only West's assumptions governing model complexity and
+the size of the test sample are substantially different than ours.
+
 \section{Theoretical Results}\label{sec:theory}
@@
 \ref{res-confidence-intervals}, which shows that the \oos\ average is
-asymptotically normal and centered on $E_T \bar D_2$.  This result
+asymptotically normal and centered on $E_T \oosB$.  This result
 holds even for nested models and can be used to construct confidence
@@
 average.  We then show that the F-test does not let researchers test
-hypotheses about $E_{T} \bar D_2$ when the models are overfit.  In
+hypotheses about $E_{T} \oosB$ when the models are overfit.  In
 fact, in the limit it rejects a more-accurate but false benchmark
@@
     \hat\sigma^2 = \sigma^2 + o_p(1), \quad \text{with}\quad 
-    \sigma^2 \equiv \var_R(\sqrt{P} \bar D_1),
+    \sigma^2 \equiv \var_R(\sqrt{P} \oosA),
   \]
@@
   \[
-  \frac{\bar{D}_1 - \E_T\bar{D}_2}{\hat\sigma / \sqrt{P}}
+  \frac{\oosA - \E_T\oosB}{\hat\sigma / \sqrt{P}}
   \to^d N(0,1).
@@
   \begin{eqnarray}
-  &&[\bar{D}_1 - z_{\alpha/2} \, \hat\sigma /
-      \sqrt{P}, \bar{D}_1 + z_{\alpha/2} \hat\sigma / \sqrt{P}],\label{interval-twosided} \\
-  &&[\bar{D}_1 - z_{\alpha} \, \hat\sigma / \sqrt{P}, +\infty), \label{interval-greater}
+  &&[\oosA - z_{\alpha/2} \, \hat\sigma /
+      \sqrt{P}, \oosA + z_{\alpha/2} \hat\sigma / \sqrt{P}],\label{interval-twosided} \\
+  &&[\oosA - z_{\alpha} \, \hat\sigma / \sqrt{P}, +\infty), \label{interval-greater}
   \end{eqnarray}
   and
-  \begin{equation} (-\infty, \bar{D}_1 + z_{\alpha}
+  \begin{equation} (-\infty, \oosA + z_{\alpha}
       \, \hat\sigma / \sqrt{P}],
   \end{equation}
-  contains $\E_T\bar{D}_2$ with probability $\alpha$ in the limit,
+  contains $\E_T\oosB$ with probability $\alpha$ in the limit,
   with $z_{\alpha}$ the $1-\alpha$ quantile of the standard normal
@@
 inference about the models' accuracy.  Since the \oos\ average,
-$\bar D_1$, is asymptotically normal and centered on the expected
+$\oosA$, is asymptotically normal and centered on the expected
 future performance, $t$-tests constructed from the \oos\ errors
-necessarily test hypotheses about $\E_T \bar{D}_2$ and not the
+necessarily test hypotheses about $\E_T \oosB$ and not the
 performance of the pseudo-true models or the unconditional
@@
 \begin{equation}
-  \Pr[\sqrt{P}\bar D_{1}/\hat\sigma \geq z_{\alpha} \mid \E_{T}
-  \bar{D}_{2} \leq 0] \to^p \alpha.
+  \Pr[\sqrt{P}\oosA/\hat\sigma \geq z_{\alpha} \mid \E_{T}
+  \oosB \leq 0] \to^p \alpha.
 \end{equation}
@@
 \begin{equation}
-  \sqrt{P} (\bar{D}_1 - \E_T \bar{D}_2) = \sqrt{P} (\bar{D}_1 - \E_R
-  \bar{D}_1) + \sqrt{P} (\E_R \bar{D}_1 - \E_T \bar{D}_2),
+  \sqrt{P} (\oosA - \E_T \oosB) = \sqrt{P} (\oosA - \E_R
+  \oosA) + \sqrt{P} (\E_R \oosA - \E_T \oosB),
 \end{equation}
@@
 \begin{equation}\label{normalpart}
-  \sqrt{P}\frac{\bar{D}_1 - \E_R \bar{D}_1}{\sigma} \to^d N(0,1)
+  \sqrt{P}\frac{\oosA - \E_R \oosA}{\sigma} \to^d N(0,1)
 \end{equation}
@@
 \begin{equation}\label{coefpart}
-  \E_R \bar{D}_1 = \E_T \bar{D}_2 + o_p(P^{-\frac12}).
-\end{equation}
-The first Lemma first shows that the process $\{D_{tR} - \E_R \bar
-D_1\}$ is an $L_2$-mixingale of size $-1/2$ that satisfies a \clt,
+  \E_R \oosA = \E_T \oosB + o_p(P^{-\frac12}).
+\end{equation}
+The first Lemma first shows that the process $\{D_{tR} - \E_R \oosA\}$
+is an $L_2$-mixingale of size $-1/2$ that satisfies a \clt,
 ensuring~\eqref{normalpart}.  The second shows that~\eqref{coefpart}
@@
 errors, but that additional dependence is contained in the term $\E_R
-\bar D_1$ and can be effectively removed by subtraction.  The second
+\oosA$ and can be effectively removed by subtraction.  The second
 part of the Lemma shows that the basic mixingale \clt\ established by
@@
 \begin{equation*}
-  \E_T \bar{D}_2 - \E_R \bar D_1 =  O_p(\sqrt{P/T}) +
+  \E_T \oosB - \E_R \oosA =  O_p(\sqrt{P/T}) +
   o_p(P^{-\frac12}) + o_p(Q^{-\frac12}).
@@
 The justification for Lemma~\ref{res-convergence} is intuitive.  In
-the limit, the difference between $\E_T \bar{D}_2$ and $\E_R \bar D_1$
-comes from the coefficient estimators used: $\E_T\bar{D}_2$ is the
+the limit, the difference between $\E_T \oosB$ and $\E_R \oosA$
+comes from the coefficient estimators used: $\E_T\oosB$ is the
 expected performance using the full-sample estimate, $\hat{\theta}_T$,
-and $\E_R \bar D_1$ is the performance using the period-$R$ estimate,
+and $\E_R \oosA$ is the performance using the period-$R$ estimate,
 $\hat{\theta}_R$.  When $P$ and $Q$ are large, the dependence between
@@
 $\mathcal{F}_R$ and $\mathcal{F}_T$.  Since $L$ is smooth, the
-difference between $\E_R \bar D_1$ and $\E_T \bar D_2$ is of order
+difference between $\E_R \oosA$ and $\E_T \oosB$ is of order
 $\lvert \hat\theta_R - \hat\theta_T \rvert_2$, which itself is of
@@
   \begin{equation*}
-    \frac1P \oosSum{s,t}{1} (D_{tR} - \bar D_1)(D_{sR} - \bar D_1)
+    \frac1P \oosSum{s,t}{1} (D_{tR} - \oosA)(D_{sR} - \oosA)
     \vWeight = \sigma^2 + o_p(1).
@@
 \begin{equation}\label{eq:ftestreject1}
-  \Pr[F \geq q_{K_2 - K_1, T - K_2}(1-\alpha) \mid E_T \bar{D}_2 \leq 0
+  \Pr[F \geq q_{K_2 - K_1, T - K_2}(1-\alpha) \mid E_T \oosB \leq 0
   ] \to 1\mbox{ as $\phi_2 \to \infty$ ($T$ fixed)}
@@
 \begin{equation}\label{eq:ftestreject2}
-  \Pr[F \geq q_{K_2 - K_1, T - K_2}(1-\alpha) \mid E_T \bar{D}_2 \leq 0
+  \Pr[F \geq q_{K_2 - K_1, T - K_2}(1-\alpha) \mid E_T \oosB \leq 0
   ] \to 1 \text{ as $T \to \infty$},
@@
 \begin{equation*}
-  E_T \bar D_2 = \psi_1^2 + \psi_2^2 - (\hat{\psi}_1 - \psi_1)^2 - (\hat\psi_2 - \psi_2)^2,
+  E_T \oosB = \psi_1^2 + \psi_2^2 - (\hat{\psi}_1 - \psi_1)^2 - (\hat\psi_2 - \psi_2)^2,
 \end{equation*}
 where $\hat{\psi}$ is the \ols\ estimator.  Under these conditions,
-the F-test rejects if $\hat{\psi}'\hat{\psi}$ lies outside the circle
-centered at the origin with radius $\hat{\tau} (c_2 - c_1)^{0.5}
-q_{K_2-K_1, T-K_2}^{0.5}(1-\alpha)$, and $E_T \bar{D}_2 \leq 0$ holds
-for $\hat\psi$ on or outside a circle centered at $\psi$ passing
-through the origin; $\hat{\tau}^2$ is the usual estimator of $\tau^2$.
+the F-test rejects if $\hat{\psi}$ lies outside the circle centered at
+the origin with radius $\hat{\tau} (c_2 - c_1)^{0.5} q_{K_2-K_1,
+  T-K_2}^{0.5}(1-\alpha)$, and $E_T \oosB \leq 0$ holds for $\hat\psi$
+on or outside a circle centered at $\psi$ passing through the origin;
+$\hat{\tau}^2$ is the usual estimator of $\tau^2$.
 Figure~\ref{fig:rreject} depicts these regions.  Since the \ols\
 estimator $\hat\psi$ is normal with mean $\psi$, the probability that
-$\hat{\psi}$ falls in the acceptance region given $E_T \bar{D}_2 \leq
-0$ vanishes as $\phi_2 \to \infty$, even though the full model will
-give worse forecasts than the restricted model.
+$\hat{\psi}$ falls in the acceptance region given $E_T \oosB \leq 0$
+vanishes as $\phi_2 \to \infty$, even though the full model will give
+worse forecasts than the restricted model.
 
@@
     Figures (a) and (b) show the rejection region and the acceptance
-    region respectively of the F-test given $E_T \bar D_2 \leq 0$ when
+    region respectively of the F-test given $E_T \oosB \leq 0$ when
     the true elements of $\psi$ are moderately small.  Figures (c) and (d)
@@
   respectively.}  The first looks at the asymptotic normality of the
-\dmw\ statistic centered on either $E_R \bar D_1$ or $E_T \bar D_2$.
+\dmw\ statistic centered on either $E_R \oosA$ or $E_T \oosB$.
 The previous section's results imply that centering on the first
@@
 \begin{equation*}
-  [ \bar D_1 - 1.28 \hat{\sigma}, \infty) \quad\text{and}\quad
-  [ \bar D_1 - 1.64 \hat{\sigma}, \bar D_1 + 1.64\ \hat{\sigma}], \\
-  \hat\sigma^2 = \frac1P \sum_{t=R+1}^T (D_t - \bar D_{1})^{2}
+  [ \oosA - 1.28 \hat{\sigma}, \infty) \quad\text{and}\quad
+  [ \oosA - 1.64 \hat{\sigma}, \oosA + 1.64\ \hat{\sigma}], \\
+  \hat\sigma^2 = \frac1P \sum_{t=R+1}^T (D_t - \oosA)^{2}
 \end{equation*}
 for $P$ set to every 10th value between $T$ and $\frac{2T}{3}$.  We
-calculate the percentage of these intervals that contain $E_R \bar
-D_1$ and that contain $E_T \bar D_2$.  Since the data are i.i.d.,
-both of these quantities are easy to calculate:
-\begin{equation*}
-  E_R \bar D_1 = [\sum_{i=1}^{K_1} (\tilde{\theta}_{iR} - \theta_i)^2 +
+calculate the percentage of these intervals that contain $E_R \oosA$
+and that contain $E_T \oosB$.  Since the data are i.i.d., both of
+these quantities are easy to calculate:
+\begin{equation*}
+  E_R \oosA = [\sum_{i=1}^{K_1} (\tilde{\theta}_{iR} - \theta_i)^2 +
   \sum_{i=K_1+1}^{K_2}\theta_i^2] - \sum_{i=1}^{K_2} (\hat{\theta}_{iR} -
@@
 \begin{equation*}
-  E_T \bar D_2 = [\sum_{i=1}^{K_1} (\tilde{\theta}_{iT} - \theta_i)^2 +
+  E_T \oosB = [\sum_{i=1}^{K_1} (\tilde{\theta}_{iT} - \theta_i)^2 +
   \sum_{i=K_1+1}^{K_2}\theta_i^2] - \sum_{i=1}^{K_2} (\hat{\theta}_{iT} -
@@
 using only the regressors in the benchmark model and $\hat{\theta}$
-the full model.  We draw 2000 samples for each choice of the design
-parameters.
+the full model.  We draw 2000 samples for each combination of the
+design parameters.
 
@@
 \begin{equation}\label{eq:9}
-  H_0:\quad E_T \bar D_2 \leq 0,
+  H_0:\quad E_T \oosB \leq 0,
 \end{equation}
@@
 \subsection{Results}
-We'll discuss results for the confidence intervals first.
+We next discuss results for the confidence intervals first.
 Figures~\ref{fig:interval-R} and~\ref{fig:interval-T} show the
@@
 displays the coverage for a different choice of interval, centering
-term ($E_R \bar D_1$ or $E_T \bar D_2$) and combination of design
+term ($E_R \oosA$ or $E_T \oosB$) and combination of design
 parameters.
 
-Figure~\ref{fig:interval-R} gives the results for $E_R \bar D_1$.  For
+Figure~\ref{fig:interval-R} gives the results for $E_R \oosA$.  For
 both the one and two-sided intervals, the actual coverage is very
@@
 
-Figure~\ref{fig:interval-T} gives the results for $E_T \bar D_2$.  In
+Figure~\ref{fig:interval-T} gives the results for $E_T \oosB$.  In
 rows 2, 4, 6, and 8, the overfit models, the coverage is near nominal
@@
 behavior as $P$ increases, combined with the results for $E_R
-\bar{D}_1$, indicate that $E_T \bar D_2 \geq E_R \bar D_1$ in general.
+\oosA$, indicate that $E_T \oosB \geq E_R \oosA$ in general.
 Since
-\[E_{T} \bar D_2 = E_{R} \bar D_1 + (E_{T} \bar D_2 - E_{R} \bar
-D_1), \] and the interval is approximately centered at $E_R \bar D_1$,
-the difference $E_{T} \bar D_2 - E_{R} \bar D_1$ adds a substantial
-positive quantity when $P^2/T$ is not near zero, increasing the
-coverage of the one-sided interval but taking $E_T \bar D_2$ outside
-the two-sided interval.
+\[E_{T} \oosB = E_{R} \oosA + (E_{T} \oosB - E_{R} \oosA), \] and the
+interval is approximately centered at $E_R \oosA$, the difference
+$E_{T} \oosB - E_{R} \oosA$ adds a substantial positive quantity when
+$P^2/T$ is not near zero, increasing the coverage of the one-sided
+interval but taking $E_T \oosB$ outside the two-sided interval.
 
@@
 exact; moreover, the larger model will almost always be less accurate
-than the smaller one, so conditioning on $\E_T \bar{D}_2 \leq 0$ is
+than the smaller one, so conditioning on $\E_T \oosB \leq 0$ is
 almost unrestrictive.  When $c$ increases, though, the F-test
@@
 simulating from \eqref{eq:1} with $c = 1$ or 2 subject to the
-constraint that $E_T \bar D_2 > 0$.\footnote{Draws of $X$ and $Y$ with
-  $E_T \bar D_2 > 0$ are very rare when $c=0$, so we do not present
+constraint that $E_T \oosB > 0$.\footnote{Draws of $X$ and $Y$ with
+  $E_T \oosB > 0$ are very rare when $c=0$, so we do not present
   results for that value of $c$.}  Figure~\ref{fig:ttest-power} plots
@@
 simulation confirms that the \dmw\ \oos\ $t$-test is centered at $E_R
-\bar D_1$ for all choices of $P$ and $R$ and is centered on $E_T \bar
-D_2$ only when $P$ is small.  The second simulation confirms that the
-\dmw\ test has correct size for the null hypothesis that $E_T \bar D_2
-\leq 0$ when $P$ is small and that tests designed to test whether the
+\oosA$ for all choices of $P$ and $R$ and is centered on $E_T \oosB$
+only when $P$ is small.  The second simulation confirms that the \dmw\
+test has correct size for the null hypothesis that $E_T \oosB \leq 0$
+when $P$ is small and that tests designed to test whether the
 benchmark is true, like the F-test and Clark and West's (2006, 2007)
 and McCracken's (2007) \oos\ tests can reject by much more than their
-nominal size when testing the null $E_T \bar D_2 \leq 0$.
-Moreover, these simulations demonstrate that the restriction $P^2/T
-\to 0$ is binding in practice, as the \dmw\ test under-rejects and has
-very low power when it is not satisfied.
+nominal size when testing the null $E_T \oosB \leq 0$.  Moreover,
+these simulations demonstrate that the restriction $P^2/T \to 0$ is
+binding in practice, as the \dmw\ test under-rejects and has very low
+power when it is not satisfied.
 \section{Empirical Exercise}\label{sec:empirics}
@@
 To study the effect of the training sample size on the \dmw\ statistic, we
-calculate the one-sided confidence interval for $E_T \bar D_2$ given
+calculate the one-sided confidence interval for $E_T \oosB$ given
 by \eqref{interval-greater} corresponding to the null and alternative
 hypotheses
-\[ H_0: \quad E_T \bar D_2 \leq 0 \qquad
-H_A: \quad E_T \bar D_2 > 0
+\[ H_0: \quad E_T \oosB \leq 0 \qquad
+H_A: \quad E_T \oosB > 0
 \]
@@
 Figure~\ref{fig:empirics2} imposes \citepos{CaT:08} restriction.  The
-solid line in each figure shows the \oos\ average, $\bar D_1$, and the
+solid line in each figure shows the \oos\ average, $\oosA$, and the
 shaded region indicates the 95\% one-sided confidence interval implied
@@
 model has higher out-of-sample loss.  We can see that the same
-patterns hold for both models: the performance difference decreases
-with $R$, but the kitchen sink model is never more accurate.  We also
+patterns hold for both models: the performance difference decreases as
+$R$ grows, but the kitchen sink model is never more accurate.  We also
 see that the performance difference decreases suddenly over the period
@@
 datasets, only a handful of observations should be used for testing.
-This restriction could be addressed by directly estimating $\E_R \bar
-D_1 - \E_T \bar{D}_2$ or by deriving its asymptotic distribution,
-which would allow larger values of $P$.  It could also be mitigated by
-extending our results to cross-validation or other resampling
-strategies.  It would also be useful to extend our results to other
-estimation windows and forecasting models, and to explore how
-stationarity could be relaxed.
+This restriction could be addressed by directly estimating $\E_R \oosA
+- \E_T \oosB$ or by deriving its asymptotic distribution, which would
+allow larger values of $P$.  It could also be mitigated by extending
+our results to cross-validation or other resampling strategies.  It
+would also be useful to extend our results to other estimation windows
+and forecasting models, and to explore how stationarity could be
+relaxed.
 
@@
 \begin{equation}\label{EQ-oosaverage1}
-\E_R \bar D_1 = \resConvgRHS{R} + o_p(P^{-\frac12})
+\E_R \oosA = \resConvgRHS{R} + o_p(P^{-\frac12})
 \end{equation}
@@
 \begin{equation}\label{EQ-oosaverage2}
-\E_T \bar D_2 = \resConvgRHS{T} + o_p(Q^{-\frac12})
+\E_T \oosB = \resConvgRHS{T} + o_p(Q^{-\frac12})
 \end{equation}
@@
 \[
-\lVert \E_R \bar D_1 - \wall \resConvgRHS{R} \rVert_2  \\
+\lVert \E_R \oosA - \wall \resConvgRHS{R} \rVert_2  \\
 \leq \frac1P \oosSum{t}{1} \lVert \E_R (D_{tR} - \tilde D_t) \rVert_2 \\
@@
 \varianceDiffA \\ +
-\frac1{P} \oosSum{s,t}{1} \lvert (D_{tR} - \bar D_1)(\E_R D_{sR} - \bar D_1) \rvert
+\frac1{P} \oosSum{s,t}{1} \lvert (D_{tR} - \oosA)(\E_R D_{sR} - \oosA) \rvert
 \vWeight,
@@
 \varianceDiffAi \wall =  O_p(\frac1P \oosSum{s}{1}(\E_{R}D_{sR} -
-\E_R\bar D_1)^2) \\
-\quad + O_p(\bar D_1 - \E_R\bar D_1)^{2} \\
-= O_p(\frac1P \oosSum{s}{1} (\E_RD_{sR})^2 - (\E_R\bar D_1)^2) + o_p(1),    \return
+\E_R\oosA)^2) \\
+\quad + O_p(\oosA - \E_R\oosA)^{2} \\
+= O_p(\frac1P \oosSum{s}{1} (\E_RD_{sR})^2 - (\E_R\oosA)^2) + o_p(1),    \return
 \]
@@
 \[
-\frac1P \oosSum{s}{1} (\E_R D_{sR})^2 - (\E_R\bar D_1)^2 \wall = 
+\frac1P \oosSum{s}{1} (\E_R D_{sR})^2 - (\E_R\oosA)^2 \wall = 
 \frac1P \oosSum{s}{1} [(\E_R D_{sR})^2 - (\E_R\tilde D_s)^2]\\
-\quad+ (\frac1P \oosSum{s}{1} \E_R \tilde D_s)^2 - (\E_R\bar D_1)^2 \quad \text{a.s}.\\
+\quad+ (\frac1P \oosSum{s}{1} \E_R \tilde D_s)^2 - (\E_R\oosA)^2 \quad \text{a.s}.\\
 = O_p(\frac1P \oosSum{s}{1} [(\E_R D_{sR})^2 - (\E_R \tilde D_s)^2]).
@@
 \[
-E_T \bar D_2 = \sum_{j=K_1+1}^{K_2} [\psi_j^2 - (\hat{\psi}_j - \psi_j)^2]
-\]
-For any $\hat{\theta}$, $E_T \bar D_2$ equals zero when
+E_T \oosB = \sum_{j=K_1+1}^{K_2} [\psi_j^2 - (\hat{\psi}_j - \psi_j)^2]
+\]
+For any $\hat{\theta}$, $E_T \oosB$ equals zero when
 $\hat{\psi}$ lies on the surface of the hypersphere centered at
-$\psi$ with radius $|\psi|_2$, and $E_T \bar D_2$ and is greater
+$\psi$ with radius $|\psi|_2$, and $E_T \oosB$ and is greater
 than zero when $\hat{\psi}$ lies outside that sphere.
@@
 We can get a lower bound for the probability
-\[\Pr[F \geq q_\alpha \mid E_T \bar{D}_2 \leq 0]\]
+\[\Pr[F \geq q_\alpha \mid E_T \oosB \leq 0]\]
 by rewriting $\hat{\psi}$ in spherical coordinates re-centered at
@@
 \[
-\Pr[F \geq q_{\alpha}\wall \mid E_T \bar{D}_2 \leq 0] = 
+\Pr[F \geq q_{\alpha}\wall \mid E_T \oosB \leq 0] = 
 \Pr[\hat{\psi}'\hat{\psi} \geq \hat \tau^2 q_\alpha \frac{K_2 - K_1}{T}
@@
 \centering
-\textbf{\large{Simulated Coverage of One-Sided DMW Interval for $E_R\bar D_1$}}
+\large{Simulated Coverage of One-Sided DMW Interval for $E_R\oosA$}
 \includegraphics{mc/plots/interval-testerror1}
-\textbf{\large{Simulated Coverage of Two-Sided DMW Interval for $E_R\bar D_1$}}
+\large{Simulated Coverage of Two-Sided DMW Interval for $E_R\oosA$}
 \includegraphics{mc/plots/interval-testerror2}
-\caption{Simulated coverage of $E_R \bar D_1$ at 90\% confidence using
-a one- and two-sided intervals based on the \protect\textsc{dmw} \protect\textsc{oos}
-test, plotted as a function of the fraction of observations used in
-the test sample, $P/T$.  The solid horizontal line denotes the
-intervals' nominal coverage.}
+\caption{Simulated coverage of $E_R \oosA$ at 90\% confidence using a
+  one- and two-sided intervals based on the \protect\textsc{dmw}
+  \protect\textsc{oos} test, plotted as a function of the fraction of
+  observations used in the test sample, $P/T$.  The solid horizontal
+  line denotes the intervals' nominal coverage.}
  \label{fig:interval-R}
@@
 \centering
-\textbf{\large{Simulated Coverage of One-Sided DMW Interval for $E_T\bar D_2$}}
+\large{Simulated Coverage of One-Sided DMW Interval for $E_T\oosB$}
 \includegraphics{mc/plots/interval-generror1}
-\textbf{\large{Simulated Coverage of Two-Sided DMW Interval for $E_T\bar D_2$}}
+\large{Simulated Coverage of Two-Sided DMW Interval for $E_T\oosB$}
 \includegraphics{mc/plots/interval-generror2}
-\caption{Simulated coverage of $E_T \bar D_2$ at 90\% confidence using
-a one- and two-sided intervals based on the \protect\textsc{dmw} \protect\textsc{oos}
-test, plotted as a function of the fraction of observations used in
-the test sample, $P/T$.  The solid horizontal line denotes the
-intervals' nominal coverage.}
+\caption{Simulated coverage of $E_T \oosB$ at 90\% confidence using a
+  one- and two-sided intervals based on the \protect\textsc{dmw}
+  \protect\textsc{oos} test, plotted as a function of the fraction of
+  observations used in the test sample, $P/T$.  The solid horizontal
+  line denotes the intervals' nominal coverage.}
 \label{fig:interval-T}
@@
   \centering
-  \textbf{\large{Simulated Rejection Probability of F-test Under $E_T
-      \bar{D}_2 \leq 0$}}
+\large{Simulated Rejection Probability of F-test Under $E_T
+      \oosB \leq 0$}
   \includegraphics{mc/plots/ftest-001}
   \caption{Simulated rejection probabilities for the F-test given
-    $\E_T \bar{D}_2 \leq 0$ with nominal size 10\%.  Values greater
-    than 10\% indicate that the test rejects the benchmark model too
-    often.  See Section~\ref{sec:simulation-design} for a discussion
-    of the simulation design.}
+    $\E_T \oosB \leq 0$ with nominal size 10\%.  Values greater than
+    10\% indicate that the test rejects the benchmark model too often.
+    See Section~\ref{sec:simulation-design} for a discussion of the
+    simulation design.}
   \label{fig:ftest}
@@
   \centering
-  \textbf{\large{Simulated Rejection Probability of DMW Test Under $E_T
-      \bar{D}_2 \leq 0$}}
+  \large{Simulated Rejection Probability of DMW Test Under $E_T
+      \oosB \leq 0$}
   \includegraphics{mc/plots/size-dmwsize}  
   \caption{Simulated rejection probabilities for the \protect\textsc{dmw}
-    \protect\textsc{oos} $t$-test given $\E_T \bar{D}_2 \leq 0$ with nominal
+    \protect\textsc{oos} $t$-test given $\E_T \oosB \leq 0$ with nominal
     size 10\%.  Values greater than 10\% indicate that the test
@@
   \centering
-  \textbf{\large{Simulated Rejection Probability of Clark and West
-      (2006, 2007) Test Under $E_T \bar{D}_2 \leq 0$}}
+  \large{Simulated Rejection Probability of Clark and West
+      (2006, 2007) Test Under $E_T \oosB \leq 0$}
   \includegraphics{mc/plots/size-clarkwest}
   \caption{Simulated rejection probabilities for Clark and West's
-    (2006, 2007) \protect\textsc{oos} test statistic given $\E_T \bar{D}_2
+    (2006, 2007) \protect\textsc{oos} test statistic given $\E_T \oosB
     \leq 0$ with nominal size 10\%.  Values greater than 10\% indicate
@@
   \centering
-  \textbf{\large{Simulated Rejection Probability of McCracken (2007)
-      Test \\ Under $E_T \bar{D}_2 \leq 0$}}
+  \large{Simulated Rejection Probability of McCracken (2007)
+      Test \\ Under $E_T \oosB \leq 0$}
   \includegraphics{mc/plots/size-mccracken}
   \caption{Simulated rejection probabilities for McCracken's (2007)
-    \protect \textsc{oos} test statistic given $\E_T \bar{D}_2 \leq 0$ with
+    \protect \textsc{oos} test statistic given $\E_T \oosB \leq 0$ with
     nominal size 10\%.  Values greater than 10\% indicate that the
@@
   \centering
-  \textbf{\large{Simulated Rejection Probability of DMW Test Under $E_T
-      \bar{D}_2 > 0$}}
+  \large{Simulated Rejection Probability of DMW Test Under $E_T
+      \oosB > 0$}
   \includegraphics{mc/plots/size-dmwpower}
   \caption{Simulated rejection probabilities for the \protect \textsc{dmw}
-    \protect\textsc{oos} $t$-test given $\E_T \bar{D}_2 > 0$ with nominal
+    \protect\textsc{oos} $t$-test given $\E_T \oosB > 0$ with nominal
     size 10\%.  Values greater than 10\% indicate that the test
@@
 \centering
-\textbf{\large{Difference in OOS MSE of Prevailing Mean and\\ Kitchen
-    Sink Models of Equity Premium (OLS)}}
+\large{Difference in OOS MSE of Prevailing Mean and\\ Kitchen
+    Sink Models of Equity Premium (OLS)}
 \includegraphics{empirics/plots/oos-mse-1}
@@
 \centering
-\textbf{\large{Difference in OOS MSE of Prevailing Mean and\\ Kitchen
-    Sink Models of Equity Premium (CT)}}
+\large{Difference in OOS MSE of Prevailing Mean and\\ Kitchen
+    Sink Models of Equity Premium (CT)}
 \includegraphics{empirics/plots/oos-mse-2}
@@
 \centering
-\textbf{\large{OOS MSE of Individual Forecasts of Equity Premium}}
+\large{OOS MSE of Individual Forecasts of Equity Premium}
 \includegraphics{empirics/plots/oos-ind-ks}

### 2011-02-24 mc/plot-interval.Rnw
Final edits before submission to Econometrica

@@
                panel = function(x,y,...) {
+                 panel.lines(c(0,2/3),c(.9,.9), col = "gray")
                  panel.xyplot(x,y,...,type = "l")
-                 panel.lines(c(0,2/3),c(.9,.9), col = "gray")
                },
@@
 
+Check empirical coverage of $E_{R} \bar{D}_{1}$ for the one-sided
+naive out-of-sample t-test-based interval.
 <<testerror1, fig=TRUE, height = 3.5, width=6>>=
@@
 
-doxyplot(d) #Empirical coverage of one-sided interval
+doxyplot(d)
 @
 
+Check empirical coverage of $E_{R} \bar{D}_{1}$ for the two-sided
+naive out-of-sample t-test-based interval.
 <<testerror2, fig=TRUE, height = 3.5, width=6>>=
@@
 d$normlabel <- sprintf("c=%d", d$norm)
-doxyplot(d) #Empirical coverage of two-sided interval
+doxyplot(d)
 @
 
+Check empirical coverage of $E_{T} \bar{D}_{2}$ for the one-sided
+naive out-of-sample t-test-based interval.
 <<generror1, fig=TRUE, height = 3.5, width=6>>=
@@
 
+Check empirical coverage of $E_{T} \bar{D}_{2}$ for the two-sided
+naive out-of-sample t-test-based interval.
 <<generror2, fig=TRUE, height = 3.5, width=6>>=

### 2011-02-24 paper.tex
Final edits before submission to Econometrica

@@
 \onehalfspacing
-\usepackage[top=1.222222in,left=0.9444444in,right=1.888889in,bottom=2.4444444in]{geometry}
+\usepackage[margin=1in]{geometry}
 \usepackage{nath}
@@
 
-\newcommand{\oosA}{\bar{D}_a}
-\newcommand{\oosB}{\bar{D}_b}
+\newcommand{\oosA}{\bar{D}_{R}}
+\newcommand{\oosB}{\bar{D}_{T}}
 
@@
     Starr, Yixiao Sun, Allan Timmermann, participants at the 2010
-    Midwest Economics Association Annual Meetings, the 2010 Joint
+    Midwest Economics Association Annual Meetings, the 2010
+    International Symposium on Forecasting, the 2010 Joint
     Statistical Meetings, and in many seminars at \textsc{ucsd}, and
@@
   in-sample Wald and \textsc{lm} tests and also Clark and McCracken's
-  (2001, 2005a), \citepos{Mcc:07} and Clark and West's (2006, 2007)
+  (2001, 2005a), \citepos{Mcc:07}, and Clark and West's (2006, 2007)
   out-of-sample statistics, will choose the larger model too often
@@
 
-\noindent \textsc{jel} Classification: C12, C22, C52, C53
+\noindent \textsc{jel} Classification: C01, C12, C22, C52, C53
 
@@
 \end{abstract}
+\newpage
 
@@
 \[
-E_T \oosB = \sum_{j=K_1+1}^{K_2} [\psi_j^2 - (\hat{\psi}_j - \psi_j)^2]
-\]
-For any $\hat{\theta}$, $E_T \oosB$ equals zero when
-$\hat{\psi}$ lies on the surface of the hypersphere centered at
-$\psi$ with radius $|\psi|_2$, and $E_T \oosB$ and is greater
-than zero when $\hat{\psi}$ lies outside that sphere.
-Also, the rejection region in $\Re^{K_2}$ for is the set of values of $\hat{\psi}$
-on or beyond the sphere
+E_T \oosB = \sum_{j=K_1+1}^{K_2} [\psi_j^2 - (\hat{\psi}_j - \psi_j)^2].
+\]
+For any $\hat{\theta}$, $E_T \oosB$ equals zero when $\hat{\psi}$ lies
+on the surface of the hypersphere centered at $\psi$ with radius
+$|\psi|_2$, and $E_T \oosB$ and is greater than zero when $\hat{\psi}$
+lies outside that sphere.  Also, the rejection region in $\Re^{K_2}$
+for the F-test is the set of values of $\hat{\psi}$ on or beyond the
+sphere
 \[
@@
 \mid |\hat{\psi}-\psi|_2 \geq |\psi|_2] \\
-\geq 1 - \E(\Pr\{ \hat{\omega}_i \in [\tilde{\omega}_i - \xi, \tilde{\omega}_i +
-\xi] \ \forall i  \mid \hat{\tau}^2,
-|\hat{\psi}-\psi|_2 \geq |\psi|_2\} 
-\mid |\hat{\psi}-\psi|_2 \geq |\psi|_2)\quad a.s. \\ 
+\geq 1 - \E(\;\Pr[ \hat{\omega}_i \in [\tilde{\omega}_i - \xi, \tilde{\omega}_i +
+\xi] \ \forall i  \mid \wall \hat{\tau}^2,
+|\hat{\psi}-\psi|_2 \geq |\psi|_2] \\ 
+\mid |\hat{\psi}-\psi|_2 \geq |\psi|_2)\quad a.s. \return \\ 
 = 1 - \frac12 E ((2\xi / \pi)^{K_2-K_1-1}\mid
@@
 \bibliographystyle{abbrvnat}
-\bibliography{../../texlibrary.bzr/main}
-
-\begin{table}[b]
+\bibliography{AllRefs}
+
+\begin{table}[h]
  \begin{multicols}{2}
@@
 
-\begin{table}[!tbp]
+\begin{table}[b]
  \begin{center}
@@
   \large{Simulated Rejection Probability of Clark and West
-      (2006, 2007) Test Under $E_T \oosB \leq 0$}
+      (2006, 2007) Test \\ Under $E_T \oosB \leq 0$}
   \includegraphics{mc/plots/size-clarkwest}
@@
 % LocalWords:  anova akritas jong normalpart coefpart Jong's rproject rsqlite
-% LocalWords:  unrestrictive datasets Heyde's ib oos
+% LocalWords:  unrestrictive datasets Heyde's ib oos Mcc MeR StW InK DiM CCS
+% LocalWords:  ClM CoS ClW GiW GiR GoW Cla HTF Efr BoB AkA AkP DeD Mcl Dej Rde
+% LocalWords:  Sar Zeh Zei Har CaT NeW MeP HaH AllRefs

### 2012-03-30 paper.tex
Edited paper to reflect Helle's comments.

--- 2010-12-23 paper.tex
@@
     Goyal for providing computer code and data for his 2008 RFS paper
-    with Ivo Welch \citep{GoW:08}.} \\ Iowa State University,
-  Economics Department}
+    with Ivo Welch \citep{goyal-welch-2008-rfs}.} \\ Iowa State
+  University, Economics Department}
 \date{October 24, 2011}
@@
   This paper uses dimension asymptotics to study why overfit linear
-  regression models should be compared out-of-sample; we let the
-  number of predictors used by the larger model increase with the
-  number of observations so that their ratio remains uniformly
-  positive.  Under this limit theory, the naive Diebold-Mariano-West
-  out-of-sample test can test hypotheses about a key quantity for
-  evaluating forecasting models---a time series analogue to the
-  generalization error---as long as the out-of-sample period is small
-  relative to the total sample size.  Moreover, tests that are
-  designed to reject if the larger model is true, such as the usual
-  in-sample Wald and \textsc{lm} tests and also Clark and McCracken's
-  (2001, 2005a), \citepos{Mcc:07} and Clark and West's (2006, 2007)
-  out-of-sample statistics, will choose the larger model too often
-  when the smaller model is more accurate.
+  regression models should be compared out-of-sample; we let the number of
+  predictors used by the larger model increase with the number of
+  observations so that their ratio remains uniformly positive.  Under
+  this limit theory, the naive Diebold-Mariano-West out-of-sample test
+  can test hypotheses about a key quantity for evaluating forecasting
+  models---a time series analogue to the generalization error---as
+  long as the out-of-sample period is small relative to the total
+  sample size.  Moreover, tests that are designed to reject if the
+  larger model is true, such as the usual in-sample Wald and
+  \textsc{lm} tests and also Clark and McCracken's (2001, 2005a),
+  \citepos{mccracken_asymptotics_2007} and Clark and West's (2006,
+  2007) out-of-sample statistics, will choose the larger model too
+  often when the smaller model is more accurate.
 
@@
 Although \oos\ comparisons have been popular in macroeconomics and
-finance since \citepos{MeR:83} seminal study of exchange rate models,
-it is unclear from a theoretical perspective whether or not the
-statistics are useful.  Empirical researchers often cite ``overfit''
-or ``instability'' as reasons for using \oos\ comparisons, as in
-\citet{StW:03}, but neither term is precisely defined or formalized.
-Compounding this problem, the asymptotic distributions of these
-statistics are derived under conditions that rule out either
-instability or overfit and allow a researcher to use a conventional
-in-sample comparison---a variation of the F-test, for example.  As
-\citet{InK:04} argue, the statistics themselves are designed to test
-hypotheses that can be tested by these in-sample statistics.  For
-example, \citet{DiM:95} and \citet{Wes:96} derive the limiting
-distributions of many popular \oos\ test statistics under conditions
-that would justify these full-sample tests.\footnote{In this paper, we
-  will refer to their basic \oos\ $t$-test as the \dmw\ test.}  Much
-of the subsequent research by \citet{CCS:01}, \citet{ClM:01,ClM:05},
-\citet{CoS:02,CoS:04}, \citet{ClW:06,ClW:07}, \citet{Mcc:07},
-\citet{Ana:07}, and others relaxes several of Diebold and Mariano's
-and West's assumptions, but maintains the stationarity and dependence
-conditions that permit in-sample comparisons.\footnote{Like us,
-  \citet{Ana:07} allows the number of regressors to increase with $T$.
-  But in that paper, they increase slowly enough that the \ols\
-  coefficients are consistent and asymptotically normal.}
-\citet{GiW:06}, and \citet{GiR:09, GiR:10} are exceptions.  Instead of
-focusing on hypotheses that can be tested by in-sample comparisons,
-\citet{GiW:06} derive an \oos\ test for the null hypothesis that the
-difference between two models' \oos\ forecasting performance is
-unpredictable, a martingale difference sequence, \citet{GiR:09} test
-whether the \oos\ forecasting performance of a model suffers from a
-breakdown relative to its in-sample performance, and \citet{GiR:10}
-test whether the forecasting performance is stable. However, those
-papers focus on a particular \oos\ estimation strategy and do not
-address why naive \oos\ comparisons might be generally useful.
+finance since \citepos{meese_empirical_1983} seminal study of exchange
+rate models, it is unclear from a theoretical perspective whether or
+not the statistics are useful.  Empirical researchers often cite
+``overfit'' or ``instability'' as reasons for using \oos\ comparisons,
+as in \citet{stock_forecasting_2003}, but neither term is precisely
+defined or formalized.  Compounding this problem, the asymptotic
+distributions of these statistics are derived under conditions that
+rule out either instability or overfit and allow a researcher to use a
+conventional in-sample comparison---a variation of the F-test, for
+example.  As \citet{inoue_kilian_2004} argue, the statistics
+themselves are designed to test hypotheses that can be tested by these
+in-sample statistics.  For example, \citet{diebold_comparing_1995} and
+\citet{west_asymptotic_1996} derive the limiting distributions of many
+popular \oos\ test statistics under conditions that would justify
+these full-sample tests.\footnote{In this paper, we will refer to
+  their basic \oos\ $t$-test as the \dmw\ test.}  Much of the
+subsequent research by \citet{chao_out_2001},
+\citet{clark_tests_2001,clark_evaluating_2005},
+\citet{corradi_consistent_2002,corradi_recent_2004},
+\citet{clark_using_2006,clark_approximately_2007},
+\citet{mccracken_asymptotics_2007}, \citet{anatolyev_inference_2008},
+and others relaxes several of Diebold and Mariano's and West's
+assumptions, but maintains the stationarity and dependence conditions
+that permit in-sample comparisons.\footnote{Like us,
+  \citet{anatolyev_inference_2008} allows the number of regressors to
+  increase with $T$.  But in that paper, they increase slowly enough
+  that the \ols\ coefficients are consistent and asymptotically
+  normal.}  \citet{giacomini_tests_2006}, and
+\citet{giacomini-rossi-2009-REStud,giacomini-rossi-2010-JAppliedEconometrics}
+are exceptions.  Instead of focusing on hypotheses that can be tested
+by in-sample comparisons, \citet{giacomini_tests_2006} derive an \oos\
+test for the null hypothesis that the difference between two models'
+\oos\ forecasting performance is unpredictable, a martingale
+difference sequence, \citet{giacomini-rossi-2009-REStud} test whether
+the \oos\ forecasting performance of a model suffers from a breakdown
+relative to its in-sample performance, and
+\citet{giacomini-rossi-2010-JAppliedEconometrics} test whether the
+forecasting performance is stable. However, those papers focus on a
+particular \oos\ estimation strategy and do not address why naive
+\oos\ comparisons might be generally useful.
 
@@
 complicated theoretical models and \oos\ analysis supports simple
-benchmarks, as seen in \citet{MeR:83}, \citet{StW:03}, and
-\citet{GoW:08}.  Since these different approaches strongly influence
-the outcome of research, it is important to know when each is
-appropriate.  The explanations in favor of \oos\ comparisons claim
-that they should be more robust to unmodeled instability
-\citep{ClM:05,GiW:06,GiR:09,GiR:10} or to overfit
-\citep{Mcc:98,Cla:04}.  Both explanations presume that the in-sample
-comparison is invalid and the \oos\ comparisons are more reliable.  Of
-course, as \citet{InK:04,InK:06} point out, both in-sample and \oos\
-methods could be valid, but the \oos\ methods could have lower power.
+benchmarks, as seen in \citet{meese_empirical_1983},
+\citet{stock_forecasting_2003}, and \citet{goyal-welch-2008-rfs}.
+Since these different approaches strongly influence the outcome of
+research, it is important to know when each is appropriate.  The
+explanations in favor of \oos\ comparisons claim that they should be
+more robust to unmodeled instability
+\citep{clark_power_2005,giacomini_tests_2006,giacomini-rossi-2009-REStud,giacomini-rossi-2010-JAppliedEconometrics}
+or to overfit \citep{mccracken_data_1998,clark_can_2004}.  Both
+explanations presume that the in-sample comparison is invalid and the
+\oos\ comparisons are more reliable.  Of course, as
+\citet{inoue_kilian_2004,inoue_selection_2006} point out, both
+in-sample and \oos\ methods could be valid, but the \oos\ methods
+could have lower power.
 
@@
 theory, the \ols\ coefficient estimator is no longer consistent or
-asymptotically normal \citep{Hub:73} and has positive variance in the
-limit.  Even so, we show that the usual \oos\ average is
+asymptotically normal \citep{huber_robust_1973} with positive variance
+in the limit.  Even so, we show that the usual \oos\ average is
 asymptotically normal and can consistently estimate the difference
@@
 analogue to the generalization error.\footnote{See, for example,
-  \citet{HTF:08}.}  Under these asymptotics, the generalization error
-does not converge to the expected performance of the pseudo-true
-models, so the in-sample and \oos\ comparisons measure different
-quantities and should be expected to give different results for
-reasons beyond simple size and power comparisons.  Under our theory,
-the model that is closer to the true \dgp\ in population can forecast
-worse.  In such a situation, an in-sample comparison would correctly
-reject the null hypothesis that the benchmark is true, and an \oos\
-comparison would correctly fail to reject the null that the benchmark
-is more accurate.\footnote{In a pair of papers similar to ours,
-  \citet{ClM:09,ClM:09b} study in-sample and \oos\ tests that the
-  larger model has nonzero coefficients that are too close to zero to
-  expect the model to forecast more accurately.  Like this paper, they
-  argue that the larger model can be true but less accurate.  However,
-  they focus on an aspect of the \dgp\ that makes this phenomenon
-  likely, while we focus on the coefficient estimates that produce
-  less accurate forecasts.}
+  \citet{elemstatlearning}.}  Under these asymptotics, the
+generalization error does not converge to the expected performance of
+the pseudo-true models, so the in-sample and \oos\ comparisons measure
+different quantities and should be expected to give different results
+for reasons beyond simple size and power comparisons.  Under our
+theory, the model that is closer to the true \dgp\ in population can
+forecast worse.  In such a situation, an in-sample comparison would
+correctly reject the null hypothesis that the benchmark is true, and
+an \oos\ comparison would correctly fail to reject the null that the
+benchmark is more accurate.\footnote{In a pair of papers similar to
+  ours, \citet{RePEc:fip:fedkrw:rwp09-10,RePEc:fip:fedkrw:rwp09-11}
+  study in-sample and \oos\ tests that the larger model has nonzero
+  coefficients that are too close to zero to expect the model to
+  forecast more accurately.  Like this paper, they argue that the
+  larger model can be true but less accurate.  However, they focus on
+  an aspect of the \dgp\ that makes this phenomenon likely, while we
+  focus on the coefficient estimates that produce less accurate
+  forecasts.}
 
@@
 choose a model for forecasting.  Although there has been little
-emphasis on hypothesis testing in this setting, testing is usually
+emphasis on hypothesis testing in these settings, testing is usually
 appropriate: there is usually a familiar benchmark model in place, and
@@
 asymptotically normal, the F-test and Wald tests are no longer
-asymptotically valid.  Moreover, \citet{Efr:86,Efr:04} shows that
-naive comparisons of in-sample loss overestimate models' accuracy by a
+asymptotically valid.  Moreover,
+\citet{efron_biased_1986,efron_estimation_2004} shows that naive
+comparisons of in-sample loss overestimate models' accuracy by a
 factor proportional to $K/T$, $K$ being the number of regressors.  But
 modifications of the F-test are valid under this asymptotic theory, as
-shown by \citet{BoB:95}, \citet{AkA:00}, \citet{AkP:04}, and
-\citet{Cal:10b}, among others.  Such results establish that hypotheses
-about the parameters of the \dgp\ can be tested in-sample even if one
-or both models are overfit.  For that very reason, these tests can not
-reliably choose a model for forecasting and will reject the benchmark
-too often.  We show this analytically in Section~\ref{sec:insample}.
-Moreover, under this asymptotic theory, many recent \oos\ test
-statistics, such as those derived by \cite{ClM:01,ClM:05},
-\citet{Mcc:07}, and \citet{ClW:06,ClW:07} should behave like the
-F-test.  These tests are also designed to reject the benchmark when
-the alternative model is true, and so they may reject too often when
-the benchmark is false but more accurate.  Obviously, since the
+shown by \citet{boos_anova_1995}, \citet{akritas_asymptotics_2000},
+\citet{akritas_heteroscedastic_2004}, and
+\citet{calhoun_hypothesis_2009}, among others.  Such results establish
+that hypotheses about the parameters of the \dgp\ can be tested
+in-sample even if one or both models are overfit.  For that very
+reason, these tests can not reliably choose a model for forecasting
+and will reject the benchmark too often.  We show this analytically in
+Section~\ref{sec:insample}.  Moreover, under this asymptotic theory,
+many recent \oos\ test statistics, such as those derived by
+\cite{clark_tests_2001,clark_evaluating_2005},
+\citet{mccracken_asymptotics_2007}, and
+\citet{clark_using_2006,clark_approximately_2007} should behave like
+the F-test.  These tests are also designed to reject the benchmark
+when the alternative model is true, and so they may reject too often
+when the benchmark is false but more accurate.  Obviously, since the
 distribution of these statistics converges to the normal when $P/T \to
-0$ (with the number of regressors fixed), these statistics behave
+\infty$ (with the number of regressors fixed), these statistics behave
 like the \dmw\ test when $P$ is small, but should over-reject the
@@
 supporting our theoretical results.  Section~\ref{sec:empirics}
-applies the \oos\ statistic to \citepos{GoW:08} dataset
+applies the \oos\ statistic to \citepos{goyal-welch-2008-rfs} dataset
 for equity premium prediction, and Section~\ref{sec:conclusion}
@@
 econometrics, because absolute regularity admits a particular coupling
-argument \citep{Ber:79} that is unavailable for strong mixing
-sequences.  Please see, for example, \citet{Dav:94} for a discussion
-of these mixing conditions.
+argument \citep{berbee_random_1979} that is unavailable for strong
+mixing sequences.  Please see, for example,
+\citet{davidson_stochastic_1994} for a discussion of these mixing
+conditions.
 
@@
 condition is weak and allows the loss function itself to be
-non-differentiable; for example, absolute error and many asymmetric loss functions
+nondifferentiable; for example, absolute error and many asymmetric loss functions
 satisfy this assumption.
@@
 implications.  In practical terms, this assumption requires that the
-forecaster plans to use the model for many periods in the future, that
-the test sample be large, and that the training sample be much larger,
-so that including or excluding the test sample does not affect the
-estimates of $\theta_1$ or $\theta_2$ very much.
+test sample be large, that the forecaster plans to use the model for
+many periods in the future, and that there is enough data that
+including or excluding the test sample does not affect the estimates
+of $\theta_1$ or $\theta_2$ very much.
 
@@
 consider.  We use the same class of estimators studied by
-\citet{DeD:00} (their class $\mathcal{K}$); see
+\citet{de_jong_consistency_2000} (their class $\mathcal{K}$); see
 their paper for further discussion.
@@
 \end{thm}
-The requirement that $\sigma^2$ be uniformly a.s. positive is not
-restrictive under our asymptotic theory.  Since the models'
+The requirement that $\sigma^2$ be uniformly a.s. positive is
+not restrictive under our asymptotic theory.  Since the models'
 coefficients are estimated with uncertainty in the limit, the two
 models give different forecasts even if they both nest the \dgp.  This
-is similar to \citepos{GiW:06} rolling-window result, but comes from
-different asymptotics.
+is similar to \citepos{giacomini_tests_2006} rolling-window result,
+but comes from different asymptotics.
 
@@
 and were introduced and studied extensively by
-\citet{Mcl:74,Mcl:75,Mcl:75b,Mcl:77}.  This lemma shows that the
-estimation uncertainty introduces dependence into the \oos\ forecast
-errors, but that additional dependence is contained in the term $\E_R
-\bar D_1$ and can be effectively removed by subtraction.  The second
-part of the Lemma shows that the basic mixingale \clt\ established by
-\citet{Dej:97} applies in this setting.\footnote{De Jong proves two
-  \clt s: one for mixingales and one for \ned\ functions of mixing
-  processes.  His mixingale result makes assumptions about the
-  behavior of the sample second moment that arise as consequences of
-  \ned.  The proof of Lemma~\ref{res-mixingale} shows that the
-  arguments used for de Jong's \ned\ \clt\ continue to hold for our
-  \oos\ process---in effect, that the \oos\ process has slightly more
-  structure than required for it to be a mixingale.}
+\citet{mcleish_dependent_1974,mcleish_invariance_1975,mcleish_maximal_1975,mcleish_invariance_1977}.
+This lemma shows that the estimation uncertainty introduces dependence
+into the \oos\ forecast errors, but that additional dependence is
+contained in the term $\E_R \bar D_1$ and can be effectively removed
+by subtraction.  The second part of the Lemma shows that the basic
+mixingale \clt\ established by \citet{de_jong_central_1997} applies in
+this setting.\footnote{De Jong proves two \clt s: one for mixingales
+  and one for \ned\ functions of mixing processes.  His mixingale
+  result makes assumptions about the behavior of the sample second
+  moment that arise as consequences of \ned.  The proof of
+  Lemma~\ref{res-mixingale} shows that the arguments used for de
+  Jong's \ned\ \clt\ continue to hold for our \oos\ process---in
+  effect, that the \oos\ process has slightly more structure than
+  required for it to be a mixingale.}
 
@@
       Lemma~\ref{res-mixingale}, the proof of this lemma takes
-      \citepos{DeD:00} existing consistency results
+      \citepos{de_jong_consistency_2000} existing consistency results
       for \ned\ processes and shows that the same arguments can be
@@
 theory in small samples.\footnote{Simulations were conducted in R
-  \citep{Rde:10} using the Lattice \citep{Sar:10} and RSQLite
-  \citep{Jam:10} packages for graphics and data management
+  \citep{rproject} using the Lattice \citep{lattice} and RSQLite
+  \citep{rsqlite} packages for graphics and data management
   respectively.}  The first looks at the asymptotic normality of the
@@
 
-Results using \citepos{Mcc:07} critical values are
+Results using \citepos{mccracken_asymptotics_2007} critical values are
 presented in Figure~\ref{fig:mccracken} and are similar to those using
@@
 This section presents an analysis of equity premium predictability
-similar to \citet{GoW:08}.\footnote{All of the calculations in this
-  section are done in R \citep{Rde:10}.  We also use code provided by
-  \citet{Zeh:02}, \citet{Zei:04}, and \citet{Har:10}.}  We estimate
-the expected forecasting performance of the largest model they
-consider, a model with 13 regressors, using 81 observations (annual
-data from 1928 to 2009).  We construct confidence intervals for the
-difference in performance between this model and a prevailing mean
-benchmark, and do so for different values of $R$ and $P$ to examine
-the effect of the training and test sample choice on this \oos\
-statistic.  We find that the estimate of the larger model's \mse\
-decreases relative to the benchmark as $R$ increases, but it is never
-smaller than the benchmark's.  This result, combined with the larger
-model's in-sample significance, suggests that there may be a real
-relationship between the equity premium and some of these predictors,
-but that the relationship can not be estimated accurately enough to be
-useful for forecasting and supports \citepos{GoW:08}
-conclusions.  These results hold even when imposing
-\citepos{CaT:08} restriction that the equity
-premium forecast be non-negative.
-
-We'll start with a very brief review.  \citet{GoW:08}
+similar to \citet{goyal-welch-2008-rfs}.\footnote{All of the
+  calculations in this section are done in R \citep{rproject}.  We
+  also use code provided by \citet{zeileis-hothorn-2002-RNews},
+  \citet{zeileis-2004-JStatSoftware}, and \citet{harrell-2010-R}.}  We
+estimate the expected forecasting performance of the largest model
+they consider, a model with 13 regressors, using 81 observations
+(annual data from 1928 to 2009).  We construct confidence intervals
+for the difference in performance between this model and a prevailing
+mean benchmark, and do so for different values of $R$ and $P$ to
+examine the effect of the training and test sample choice on this
+\oos\ statistic.  We find that the estimate of the larger model's
+\mse\ decreases relative to the benchmark as $R$ increases, but it is
+never smaller than the benchmark's.  This result, combined with the
+larger model's in-sample significance, suggests that there may be a
+real relationship between the equity premium and some of these
+predictors, but that the relationship can not be estimated accurately
+enough to be useful for forecasting and supports
+\citepos{goyal-welch-2008-rfs} conclusions.  These results hold even
+when imposing \citepos{campbell-thompson-2008-rfs} restriction that
+the equity premium forecast be non-negative.
+
+We'll start with a very brief review.  \citet{goyal-welch-2008-rfs}
 study the \oos\ forecasting performance of different variables thought
@@
 Table~\ref{tab:equity}.\footnote{Table~\ref{tab:equity} only lists the
-  variables used in \citepos{GoW:08} ``kitchen sink''
+  variables used in \citepos{goyal-welch-2008-rfs} ``kitchen sink''
   model.  Some of the variables that they use in bivariate models are
@@
   because the variables are linear combinations of other variables.}
-\citet{GoW:08} estimate the \oos\ forecasting
+\citet{goyal-welch-2008-rfs} estimate the \oos\ forecasting
 performance of bivariate models of the form
@@
 prevailing mean of the equity premium.
-\citet{CaT:08} find that nonlinear extensions of
+\citet{campbell-thompson-2008-rfs} find that nonlinear extensions of
 Goyal and Welch's models are more accurate, either imposing sign
@@
 
-Obviously, \citepos{GoW:08} bivariate models do not
+Obviously, \citepos{goyal-welch-2008-rfs} bivariate models do not
 match the asymptotic theory of this paper, so we restrict our
@@
 2009.  This makes the ratio $K/T$ equal to about 0.16.  We also
-present results for one of \citepos{CaT:08}
+present results for one of \citepos{campbell-thompson-2008-rfs}
 restricted forecasting models.  For this model, we estimate
@@
 regression for Equation~\eqref{eq:2}, using Newey-West standard errors
-with two lags \citep{NeW:87}.\footnote{We compare the test statistic
-  to critical values from the $F$-distribution.}  The $p$-value is
-very small (less than 0.01), indicating that the coefficients are
-nonzero in population and at least one of these predictors is
-correlated with the equity premium.  As we argue earlier, this result
-does not imply that the model will forecast well, which we look at
-next.
+with two lags \citep{newey_simple_1987}.\footnote{We compare the test
+  statistic to critical values from the $F$-distribution.}  The
+$p$-value is very small (less than 0.01), indicating that the
+coefficients are nonzero in population and at least one of these
+predictors is correlated with the equity premium.  As we argue
+earlier, this result does not imply that the model will forecast well,
+which we look at next.
 
@@
 Figures~\ref{fig:empirics1} plots the \ols\ results and
-Figure~\ref{fig:empirics2} imposes \citepos{CaT:08} restriction.  The
-solid line in each figure shows the \oos\ average, $\bar D_1$, and the
-shaded region indicates the 95\% one-sided confidence interval implied
-by the \dmw\ test.  Negative numbers indicate that the kitchen sink
-model has higher out-of-sample loss.  We can see that the same
-patterns hold for both models: the performance difference decreases
-with $R$, but the kitchen sink model is never more accurate.  We also
-see that the performance difference decreases suddenly over the period
-$R=29$ to $R=34$ (corresponding to the years 1956--1961).
+Figure~\ref{fig:empirics2} imposes
+\citepos{campbell-thompson-2008-rfs} restriction.  The solid line
+in each figure shows the \oos\ average, $\bar D_1$, and the shaded
+region indicates the 95\% one-sided confidence interval implied by the
+\dmw\ test.  Negative numbers indicate that the kitchen sink model has
+higher out-of-sample loss.  We can see that the same patterns hold for
+both models: the performance difference decreases with $R$, but the
+kitchen sink model is never more accurate.  We also see that the
+performance difference decreases suddenly over the period $R=29$ to
+$R=34$ (corresponding to the years 1956--1961).
 Figure~\ref{fig:empirics3} plots the accuracy of the individual
@@
 change may indicate instability in the underlying relationship, as
-\citet{GoW:08} propose.
+\citet{goyal-welch-2008-rfs} propose.
 
 In summary, we fail to reject the null that the benchmark prevailing
-mean model is more accurate than \citepos{GoW:08} kitchen sink.  This
-result is consistent with Goyal and Welch's original analysis.  Unlike
-Goyal and Welch, we attribute this result, at least in part, to
-parameter uncertainty---the full sample results indicate that the
-larger model could predict better than the benchmark with enough data.
-Obviously, this is an illustrative exercise only and is not meant to
-be comprehensive.  In this dataset, there is likely parameter
-instability that we have not addressed, and we have not dealt with
-variable persistence at all.
+mean model is more accurate than \citepos{goyal-welch-2008-rfs}
+kitchen sink.  This result is consistent with Goyal and Welch's
+original analysis.  Unlike Goyal and Welch, we attribute this result,
+at least in part, to parameter uncertainty---the full sample results
+indicate that the larger model could predict better than the
+benchmark with enough data.  Obviously, this is an illustrative
+exercise only and is not meant to be comprehensive.  In this dataset,
+there is likely parameter instability that we have not addressed, and
+we have not dealt with variable persistence at all.
 \section{Conclusion}\label{sec:conclusion}
@@
 practice may favor simple benchmark models too much.  Existing
-corrections, proposed by \citet{ClM:01,ClM:05}, \citet{Mcc:07} and
-\citet{ClW:06,ClW:07}, seem to correct too much, though, and reject
-too often when the benchmark model is more accurate.
+corrections, proposed by
+\citet{clark_tests_2001,clark_evaluating_2005},
+\citet{mccracken_asymptotics_2007} and
+\citet{clark_using_2006,clark_approximately_2007}, seem to correct too
+much, though, and reject too often when the benchmark model is more
+accurate.
 
@@
 The results in this paper rely heavily on a coupling argument for
-absolutely regular sequences, Berbee's Lemma \citep{Ber:79}.  In fact,
-many of the results of this paper (\ref{res-confidence-intervals},
-\ref{res-mixingale}, and \ref{res-variance-estimator}) are
-modifications of existing results for \ned\ functions of mixing
-processes by \citet{Dej:97} and
-\citet{DeD:00}; this coupling argument is used to
-explicitly derive inequalities that arise naturally for \ned\
-processes.  Lemma \ref{lem-basic-coupling} establishes these
-inequalities, which are based on a proposition of
-\citet{MeP:02}.
-
-We present \citeauthor{MeP:02}'s
-(\citeyear{MeP:02}) statement of Berbee's Lemma for
+absolutely regular sequences, Berbee's Lemma
+\citep{berbee_random_1979}.  In fact, many of the results of this
+paper (\ref{res-confidence-intervals}, \ref{res-mixingale}, and
+\ref{res-variance-estimator}) are modifications of existing
+results for \ned\ functions of mixing processes by
+\citet{de_jong_central_1997} and \citet{de_jong_consistency_2000};
+this coupling argument is used to explicitly derive inequalities that
+arise naturally for \ned\ processes.  Lemma \ref{lem-basic-coupling}
+establishes these inequalities, which are based on a proposition of
+\citet{merlevede_coupling_2002}.
+
+We present \citeauthor{merlevede_coupling_2002}'s
+(\citeyear{merlevede_coupling_2002}) statement of Berbee's Lemma for
 the reader's reference.  In the following Lemma, $\beta(X,Y)$ is the
@@
 \end{lem}
-\noindent\citep{MeP:02}
+\noindent\citep{merlevede_coupling_2002}
 \end{quotation}
@@
 The proof is virtually identical to the proof of Proposition 2.3 in
-\citet{MeP:02} and is omitted.
+\citet{merlevede_coupling_2002} and is omitted.
 
@@
 \begin{proof}[Proof of Lemma \ref{res-mixingale}, Part 2.]
-  A modification of \citepos{Dej:97} \clt s for
+  A modification of \citepos{de_jong_central_1997} \clt s for
   mixingale and \ned\ arrays will complete the proof.
@@
 $b_T\to\infty$, and $b_T/P\to 0$.  The same arguments used in
-\citepos{Dej:97} Theorem 1 show that
+\citepos{de_jong_central_1997} Theorem 1 show that
 \begin{equation*}
@@
 Note that $\{Z_i - E_{R + (i-1)b_T},\mathcal{F}_{R + i b_T}\}_i$ is an
-\mds\ by construction, so \citepos{HaH:80} Theorem 3.2 and Corollary
-3.1 ensure that\footnote{Note that $\sigma^2 \in \mathcal{F}_t$ for
-  all $t \geq R$, so Hall and Heyde's condition (3.21) is
-  unnecessary---see the remarks after their result.}
+\mds\ by construction, so \citepos{hall_martingale_1980} Theorem 3.2
+and Corollary 3.1 ensure that\footnote{Note that $\sigma^2 \in
+  \mathcal{F}_t$ for all $t \geq R$, so Hall and Heyde's condition
+  (3.21) is unnecessary---see the remarks after their result.}
 \[
@@
 \end{equation}
-Equation (\ref{eq:cltvar2}) holds as in \citet{Dej:97} (see the proof
-of his Theorem 2); to see that (\ref{eq:cltvar1}) holds, we'll use an
-argument based on his Lemma 5.  Define
+Equation (\ref{eq:cltvar2}) holds as in \citet{de_jong_central_1997}
+(see the proof of his Theorem 2); to see that (\ref{eq:cltvar1})
+holds, we'll use an argument based on his Lemma 5.  Define
 \[
@@
 \begin{proof}[Proof of Lemma \ref{res-variance-estimator}]
-  The proof follows \citepos{DeD:00} Theorem 2.1
+  The proof follows \citepos{de_jong_consistency_2000} Theorem 2.1
   closely.  We start by defining similar quantities to theirs,
@@
 with the second term vanishing by Lemma \ref{res-mixingale} and
-\citepos{Dav:93} mixingale \lln.
+\citepos{davidson_l1-convergence_1993} mixingale \lln.
 
@@
 \newcommand{\UFiltration}[1]{\ensuremath{\mathcal{F}_{(#1)b_{T}+R-P}}}%
-Next, we'll prove (\ref{eq:5}). As in \citet{DeD:00}, let
+Next, we'll prove (\ref{eq:5}). As in
+\citet{de_jong_consistency_2000}, let
 \begin{equation*}
@@
 \E_R U_i))^2 = O(\vtSumr c_i^2)$ where the $c_i$ are the mixingale
-magnitude indices \citep{Mcl:75}.
+magnitude indices \citep{mcleish_maximal_1975}.
 
@@
 % LocalWords:  thompson bivariate Welch's multicollinearity Newey newey tw vw
-% LocalWords:  merlevede cltvar dR Scwarz davidson indices lrrrr waldtest Df jt
-% LocalWords:  dmw McCracken MSE OLS mse inoue huber elemstatlearning efron sw
-% LocalWords:  anova akritas jong normalpart coefpart Jong's rproject rsqlite
-% LocalWords:  unrestrictive datasets Heyde's ib oos
+% LocalWords:  merlevede cltvar dR Scwarz davidson indices lrrrr waldtest Df
+% LocalWords:  dmw McCracken MSE OLS mse

### 2012-03-30 paper.tex
Updated BibTeX keys

@@
     Goyal for providing computer code and data for his 2008 RFS paper
-    with Ivo Welch \citep{goyal-welch-2008-rfs}.} \\ Iowa State
-  University, Economics Department}
+    with Ivo Welch \citep{GoW:08}.} \\ Iowa State University,
+  Economics Department}
 \date{October 24, 2011}
@@
 theory, the \ols\ coefficient estimator is no longer consistent or
-asymptotically normal \citep{huber_robust_1973} with positive variance
-in the limit.  Even so, we show that the usual \oos\ average is
+asymptotically normal \citep{Hub:73} and has positive variance in the
+limit.  Even so, we show that the usual \oos\ average is
 asymptotically normal and can consistently estimate the difference
@@
 analogue to the generalization error.\footnote{See, for example,
-  \citet{elemstatlearning}.}  Under these asymptotics, the
-generalization error does not converge to the expected performance of
-the pseudo-true models, so the in-sample and \oos\ comparisons measure
-different quantities and should be expected to give different results
-for reasons beyond simple size and power comparisons.  Under our
-theory, the model that is closer to the true \dgp\ in population can
-forecast worse.  In such a situation, an in-sample comparison would
-correctly reject the null hypothesis that the benchmark is true, and
-an \oos\ comparison would correctly fail to reject the null that the
-benchmark is more accurate.\footnote{In a pair of papers similar to
-  ours, \citet{RePEc:fip:fedkrw:rwp09-10,RePEc:fip:fedkrw:rwp09-11}
-  study in-sample and \oos\ tests that the larger model has nonzero
-  coefficients that are too close to zero to expect the model to
-  forecast more accurately.  Like this paper, they argue that the
-  larger model can be true but less accurate.  However, they focus on
-  an aspect of the \dgp\ that makes this phenomenon likely, while we
-  focus on the coefficient estimates that produce less accurate
-  forecasts.}
+  \citet{HTF:08}.}  Under these asymptotics, the generalization error
+does not converge to the expected performance of the pseudo-true
+models, so the in-sample and \oos\ comparisons measure different
+quantities and should be expected to give different results for
+reasons beyond simple size and power comparisons.  Under our theory,
+the model that is closer to the true \dgp\ in population can forecast
+worse.  In such a situation, an in-sample comparison would correctly
+reject the null hypothesis that the benchmark is true, and an \oos\
+comparison would correctly fail to reject the null that the benchmark
+is more accurate.\footnote{In a pair of papers similar to ours,
+  \citet{ClM:09,ClM:09b} study in-sample and \oos\ tests that the
+  larger model has nonzero coefficients that are too close to zero to
+  expect the model to forecast more accurately.  Like this paper, they
+  argue that the larger model can be true but less accurate.  However,
+  they focus on an aspect of the \dgp\ that makes this phenomenon
+  likely, while we focus on the coefficient estimates that produce
+  less accurate forecasts.}
 
@@
 asymptotically normal, the F-test and Wald tests are no longer
-asymptotically valid.  Moreover,
-\citet{efron_biased_1986,efron_estimation_2004} shows that naive
-comparisons of in-sample loss overestimate models' accuracy by a
+asymptotically valid.  Moreover, \citet{Efr:86,Efr:04} shows that
+naive comparisons of in-sample loss overestimate models' accuracy by a
 factor proportional to $K/T$, $K$ being the number of regressors.  But
 modifications of the F-test are valid under this asymptotic theory, as
-shown by \citet{boos_anova_1995}, \citet{akritas_asymptotics_2000},
-\citet{akritas_heteroscedastic_2004}, and
-\citet{calhoun_hypothesis_2009}, among others.  Such results establish
-that hypotheses about the parameters of the \dgp\ can be tested
-in-sample even if one or both models are overfit.  For that very
-reason, these tests can not reliably choose a model for forecasting
-and will reject the benchmark too often.  We show this analytically in
-Section~\ref{sec:insample}.  Moreover, under this asymptotic theory,
-many recent \oos\ test statistics, such as those derived by
-\cite{clark_tests_2001,clark_evaluating_2005},
-\citet{mccracken_asymptotics_2007}, and
-\citet{clark_using_2006,clark_approximately_2007} should behave like
-the F-test.  These tests are also designed to reject the benchmark
-when the alternative model is true, and so they may reject too often
-when the benchmark is false but more accurate.  Obviously, since the
+shown by \citet{BoB:95}, \citet{AkA:00}, \citet{AkP:04}, and
+\citet{Cal:10}, among others.  Such results establish that hypotheses
+about the parameters of the \dgp\ can be tested in-sample even if one
+or both models are overfit.  For that very reason, these tests can not
+reliably choose a model for forecasting and will reject the benchmark
+too often.  We show this analytically in Section~\ref{sec:insample}.
+Moreover, under this asymptotic theory, many recent \oos\ test
+statistics, such as those derived by \cite{ClM:01,ClM:05},
+\citet{Mcc:07}, and \citet{ClW:06,ClW:07} should behave like the
+F-test.  These tests are also designed to reject the benchmark when
+the alternative model is true, and so they may reject too often when
+the benchmark is false but more accurate.  Obviously, since the
 distribution of these statistics converges to the normal when $P/T \to
@@
 econometrics, because absolute regularity admits a particular coupling
-argument \citep{berbee_random_1979} that is unavailable for strong
-mixing sequences.  Please see, for example,
-\citet{davidson_stochastic_1994} for a discussion of these mixing
-conditions.
+argument \citep{Ber:79} that is unavailable for strong mixing
+sequences.  Please see, for example, \citet{Dav:94} for a discussion
+of these mixing conditions.
 

### 2012-03-30 paper.tex
Added decision letter and referee reports from Econometrica

--- 2011-02-24 paper.tex
@@
 \documentclass[11pt]{article}
-%\linespread{1.2}\selectfont
 \usepackage{tikz}
@@
 \usepackage{setspace,amsmath,amssymb,amsthm,ifthen,subfig,url,multicol}
-\usepackage{fancyhdr}
-\pagestyle{fancy}
-\lhead{\thepage}\chead{}\rhead{}
-\lfoot{}\cfoot{}\rfoot{}
-\renewcommand\headrulewidth{0pt}
-\onehalfspacing
+\onehalfspacing\frenchspacing
 \usepackage[margin=1in]{geometry}
-\usepackage{nath}
 
@@
 \newcommand{\Citepos}[1]{\Citeauthor{#1}'s \citeyearpar{#1}}
+\newcommand{\clws}{\citeauthor{ClW:06}'s \citeyearpar{ClW:06,ClW:07}}
 
@@
 \newcommand{\oost}{\ensuremath{\operatorname{oos-t}}}
-\newcommand{\oosSum}[2]{\ensuremath{\sum_{#1=R-\h+#2}^{T-\h}}}
+\newcommand{\oosSum}[2]{\ensuremath{\sum_{#1=R+#2}^{T-\h}}}
 
@@
 \newcommand{\CEOuterBlock}[2]{\ensuremath{\E_{\InnerBlockU{(#2-1)}} #1}}
-
-\newcommand{\CenteredAverage}{\frac{\oosA - \E_T\oosT}{\hat\sigma / \sqrt{P}}}
-\newcommand{\CenteredAverageI}{\ensuremath{\frac{1}{\hat\sigma
-    \sqrt{P}}\oosSum{t}{1} (D_{tR} - \E_R D_{tR})}}
-\newcommand{\CenteredAverageII}{\ensuremath{\frac{\sqrt{P}}{\hat\sigma}
-    (\E_R\oosA - \E_T\oosB)}}
-
-\newcommand{\MixingaleArray}[1]{\ensuremath{}}
 
@@
 
-\newcommand{\couplingConstant}{\ensuremath{2^{\frac{1+\rho}{\rho}} B_L}}
-\newcommand{\couplingBeta}[1]{\ensuremath{\beta^{\frac{\rho-2}{2\rho}}_{#1}}}
-\newcommand{\couplingBetaSq}[1]{\ensuremath{\beta^{\frac{\rho-2}{\rho}}_{#1}}}
+\newcommand{\couplingConstant}{\ensuremath{2^{(1+\rho)/\rho} B_L}}
+\newcommand{\couplingBeta}[1]{\ensuremath{\beta^{(\rho-2)/2\rho}_{#1}}}
+\newcommand{\couplingBetaSq}[1]{\ensuremath{\beta^{(\rho-2)/\rho}_{#1}}}
 \newcommand{\couplingBound}[1]{\couplingConstant \couplingBeta{#1}}
@@
     would like to thank Julian Betts, Helle Bunzel, Marjorie Flavin,
-    Nir Jaimovich, Lutz Kilian, Michael McCracken, Seth Pruitt, Ross
-    Starr, Yixiao Sun, Allan Timmermann, participants at the 2010
+    Nir Jaimovich, Lutz Kilian, Ivana Komunjer, Michael McCracken,
+    Seth Pruitt, Ross Starr, Jim Stock, Yixiao Sun, Allan Timmermann,
+    Hal White, several anonymous referees, participants at the 2010
     Midwest Economics Association Annual Meetings, the 2010
-    International Symposium on Forecasting, the 2010 Joint
-    Statistical Meetings, and in many seminars at \textsc{ucsd}, and
-    espeically Graham Elliott for their valuable suggestions, feedback
-    and advice in writing this paper.  I would also like to thank Amit
-    Goyal for providing computer code and data for his 2008 RFS paper
-    with Ivo Welch \citep{GoW:08}.} \\ Iowa State University,
-  Economics Department}
+    International Symposium on Forecasting, the 2010 Joint Statistical
+    Meetings, and in many seminars at \textsc{ucsd}, and espeically
+    Graham Elliott for their valuable suggestions, feedback and advice
+    in writing this paper.  I would also like to thank Amit Goyal for
+    providing computer code and data for his 2008 RFS paper with Ivo
+    Welch \citep{GoW:08}.} \\ Iowa State University}
 \date{October 24, 2011}
@@
   positive.  Under this limit theory, the naive Diebold-Mariano-West
-  out-of-sample test can test hypotheses about a key quantity for
-  evaluating forecasting models---a time series analogue to the
-  generalization error---as long as the out-of-sample period is small
-  relative to the total sample size.  Moreover, tests that are
-  designed to reject if the larger model is true, such as the usual
-  in-sample Wald and \textsc{lm} tests and also Clark and McCracken's
-  (2001, 2005a), \citepos{Mcc:07}, and Clark and West's (2006, 2007)
-  out-of-sample statistics, will choose the larger model too often
-  when the smaller model is more accurate.
-
-\noindent \textsc{jel} Classification: C01, C12, C22, C52, C53
+  out-of-sample test can test hypotheses about the models'
+  generalization error, a key quantity for evaluating forecasting
+  models.  Moreover, tests that are designed to reject if the larger
+  model is true, such as the usual in-sample Wald and \textsc{lm}
+  tests and also Clark and McCracken's (2001, 2005a),
+  \citepos{Mcc:07}, and Clark and West's (2006, 2007) out-of-sample
+  statistics, will choose the larger model too often when the smaller
+  model is more accurate.
+
+\noindent \textsc{jel} Classification: C12, C22, C52, C53
 
@@
 models is overfit.  In doing so, we provide a theoretical
-justification for forecasters to use \oos\ instead of
-in-sample comparisons.
+justification for forecasters to use \oos\ instead of in-sample
+comparisons and discover a practical limitation in existing statistics.
 
@@
   coefficients are consistent and asymptotically normal.}
-\citet{GiW:06}, and \citet{GiR:09, GiR:10} are exceptions.  Instead of
+\citet{GiW:06} and \citet{GiR:09, GiR:10} are exceptions.  Instead of
 focusing on hypotheses that can be tested by in-sample comparisons,
@@
 papers focus on a particular \oos\ estimation strategy and do not
-address why naive \oos\ comparisons might be generally useful.
+address why \oos\ comparisons might be useful as a general strategy.
 
@@
 increases with the number of observations so that their ratio remains
-positive.  We focus on linear regression models estimated with a fixed
-training window, but our basic conclusions should be true for other
-estimation strategies and models as well.  Under this asymptotic
-theory, the \ols\ coefficient estimator is no longer consistent or
-asymptotically normal \citep{Hub:73} and has positive variance in the
-limit.  Even so, we show that the usual \oos\ average is
-asymptotically normal and can consistently estimate the difference
-between the models' expected loss in periods $T+1,T+2,\dots$
-conditional on the on the data available in period $T$, a time-series
-analogue to the generalization error.\footnote{See, for example,
+positive.  Although overfit is sometimes used to describe the
+situation where a forecaster chooses from many different models, we
+view that as a separate issue.  Procedures that account for the
+presence of many models are being developed \citep[see, for
+example,][]{Whi:00,RoW:05}, but there is still disagreement about
+whether those procedures should themselves use in-sample or \oos\
+comparisons.  Understanding this issue in the context of a simple
+comparison between two models is necessary before resolving any new
+issues that arise with multiple comparisons.
+
+We focus on linear regression models for simplicity, but our basic
+conclusions should be true for other estimation strategies and models
+as well.  Under this asymptotic theory, the \ols\ coefficient
+estimator is no longer consistent or asymptotically normal
+\citep{Hub:73} and has positive variance in the limit.  Even so, we
+show that the usual \oos\ average is asymptotically normal and can
+consistently estimate the difference between the models'
+generalization error, the expected loss in the future conditional on
+the on the data available in period $T$.\footnote{See, for example,
   \citet{HTF:08}.}  Under these asymptotics, the generalization error
@@
 the model that is closer to the true \dgp\ in population can forecast
-worse.  In such a situation, an in-sample comparison would correctly
-reject the null hypothesis that the benchmark is true, and an \oos\
-comparison would correctly fail to reject the null that the benchmark
-is more accurate.\footnote{In a pair of papers similar to ours,
-  \citet{ClM:09,ClM:09b} study in-sample and \oos\ tests that the
-  larger model has nonzero coefficients that are too close to zero to
-  expect the model to forecast more accurately.  Like this paper, they
-  argue that the larger model can be true but less accurate.  However,
-  they focus on an aspect of the \dgp\ that makes this phenomenon
-  likely, while we focus on the coefficient estimates that produce
-  less accurate forecasts.}
+worse.  In such a situation, a standard in-sample comparison would
+correctly reject the null hypothesis that the benchmark is true, and
+an \oos\ comparison would correctly fail to reject the null that the
+benchmark is more accurate.\footnote{In a pair of papers similar to
+  ours, \citet{ClM:09,ClM:09b} study in-sample and \oos\ tests that
+  the larger model has nonzero coefficients that are too close to zero
+  to expect the model to forecast more accurately.  Like this paper,
+  they argue that the larger model can be true but less accurate.
+  However, they focus on an aspect of the \dgp\ that makes this
+  phenomenon likely, while we focus on the coefficient estimates that
+  produce less accurate forecasts.}
 
@@
 alternative model is higher than the cost of incorrectly failing to
-switch to a more accurate alternative.\footnote{These costs can be
-  monetary, in the form of computer upgrades, software installation,
-  and training, or they can be reputational costs.}
+switch to a more accurate alternative.\footnote{Because we focus on
+  testing relative to a benchmark, rather than model selection with
+  now benchmark, we will not discuss in-sample statistics with
+  penalties for overparametrization, e.g. the \textsc{aic} or adjusted
+  R-square.  \citet{Lee:08} discusses similar issues to ours related
+  to model selection.}
 We show that the \dmw\ test lets the forecaster control the
@@
 Since the models' coefficients are imprecisely estimated in the limit,
-the test sample must be small to ensure that the model estimated over
+the test sample must be small enough that the model estimated over
 the training sample is similar to the one that will be estimated over
@@
 shown by \citet{BoB:95}, \citet{AkA:00}, \citet{AkP:04}, and
-\citet{Cal:10}, among others.  Such results establish that hypotheses
-about the parameters of the \dgp\ can be tested in-sample even if one
-or both models are overfit.  For that very reason, these tests can not
-reliably choose a model for forecasting and will reject the benchmark
-too often.  We show this analytically in Section~\ref{sec:insample}.
-Moreover, under this asymptotic theory, many recent \oos\ test
-statistics, such as those derived by \cite{ClM:01,ClM:05},
-\citet{Mcc:07}, and \citet{ClW:06,ClW:07} should behave like the
-F-test.  These tests are also designed to reject the benchmark when
-the alternative model is true, and so they may reject too often when
-the benchmark is false but more accurate.  Obviously, since the
+\citet{Ana:12}, \citet{Cal:11c}, among others.  Such results establish
+that hypotheses about the parameters of the \dgp\ can be tested
+in-sample even if one or both models are overfit.  For that very
+reason, these tests can not reliably choose a model for forecasting
+and will reject the benchmark too often.  We show this analytically in
+Section~\ref{sec:insample}.  Moreover, under this asymptotic theory,
+many recent \oos\ test statistics, such as those derived by
+\cite{ClM:01,ClM:05}, \citet{Mcc:07}, and \citet{ClW:06,ClW:07} should
+behave like the F-test.\footnote{Our theoretical results apply
+  directly to \citepos{Mcc:07} \oost test, since it simply proposes
+  more liberal critical values for the same test statistic.  Since
+  \citet{ClW:06,ClW:07} use a finite length estimation window, our
+  asymptotics are incompatible with theirs and prevent us from
+  studying their test directly, as well as \citepos{GiW:06} and other
+  similar tests.  But \clws\ test can be viewed as a stochastic
+  adjustment to the critical values of the usual \oost test, so our
+  theoretical results should apply informally as well.  Specifically,
+  we show that the \dmw\ test rejects probability equal to nominal
+  size, so more liberal critical values result in over-rejection.}
+These tests are also designed to reject the benchmark when the
+alternative model is true, and so they may reject too often when the
+benchmark is false but more accurate.  Obviously, since the
 distribution of these statistics converges to the normal when $P/T \to
@@
 functions of mixing processes can be used for these \oos\ processes
-with only slight modification.  Although we only present a proof that
-this mixingale result holds for the fixed-window scheme, it is simple
-to extend it to other estimation windows.
+with only slight modification.
 
@@
 \[
-y_{t+\h} = x_{1t}'\theta_1 + \varepsilon_{1,t+h}
-\]
-and
-\[
+y_{t+\h} = x_{1t}'\theta_1 + \varepsilon_{1,t+h}, \quad\text{and}\quad
 y_{t+\h} = x_{2t}'\theta_2 + \varepsilon_{2,t+h};
 \]
-$\h$ is the forecast horizon, and the variables $y_t$, $x_{1t}$, and
-$x_{2t}$ are all known in period $t$.  Let
+$t = 1,\dots,T-h$, $\h$ is the forecast horizon, and the
+variables $y_t$, $x_{1t}$, and $x_{2t}$ are all known in period $t$.
+Let
 \begin{equation*}
@@
 
-Although our theory can apply to many different \oos\ statistics,
-we'll only present results for the \dmw\ \oos\ $t$-test.  Both models
-are estimated using \ols\ over the training sample:
-\[
-\hat y_{i,t+\h} = x_{it}'\bh{iR}, \quad i=1,2, \quad t = R+1,\dots,T-h
+We assume the following forecasting environment: the forecaster
+observs the data $(y_t,x_t)$ for periods 1 through $T$ and divides
+them into an estimation sample of the first $R+h$ observations and a
+test sample of the remaining $P$ observations.  After choosing one of
+the models, the forecaster will use that model to make predictions for
+periods $T + h$ through $T + h + Q$, where $Q$ is a known positive
+integer.  The forecaster's goal is to choose the model that will have
+lower average loss over periods $T+h$ through $T+h+Q$, evaluated by
+the known loss function $L$.
+
+Both models are estimated using \ols\ with a recursive, fixed, or
+rolling window:
+\[
+\hat y_{i,t+\h} = x_{it}'\bh{iR}, \qquad i=1,2, \qquad t = R+1,\dots,T-h
 \]
 with
-\[
-\bh{it} = (\sum_{s=1}^{t-\h} x_{is}x_{is}')^{-1} \sum_{s=1}^{t-\h} x_{is} y_{s+\h},
-\quad i=1,2.
-\]
-The \oos\ average is denoted $\oosA$:
-\[
-\oosA \equiv P^{-1} \oosSum{t}{1} D_{tR}
-\quad \text{with} \quad D_{tS} \equiv L(y_{t+\h} - x_{1t}'\bh{1S}) -
-L(y_{t+\h} - x_{2t}'\bh{2S}),
-\]
-$P = T - R$ and $L$ a known loss function.  The \oos\ statistic
-of interest is 
-\[
-\oost \equiv \frac{\sqrt{P} \oosA}{\hat\sigma},
-\]
-for $\hat\sigma^2$ some (possibly Heteroskedasticity- and
+\begin{equation*}
+\bh{it}^{R} = \begin{cases} \big(\sum_{s=1}^{t-\h} x_{is}x_{is}'\big)^{-1}
+\sum_{s=1}^{t-\h} x_{is} y_{s+\h} & \text{recursive window}\\
+ \big(\sum_{s=t - \h - R}^{t-\h} x_{is}x_{is}'\big)^{-1}
+\sum_{s=t - \h - R}^{t-\h} x_{is} y_{s+\h} & \text{rolling window} \\
+ \big(\sum_{s=1}^{R-\h} x_{is}x_{is}'\big)^{-1} 
+\sum_{s=1}^{R-\h} x_{is} y_{s+\h} & \text{fixed window}
+\end{cases}
+\end{equation*}
+The observed \oos\ average is denoted $\oosA$: \[\oosA \equiv P^{-1}
+\oosSum{t}{1} D_{Rt}\]  with
+\[
+D_{Rt} \equiv L(y_{t+\h} - x_{1t}'\bh{1t}^R) - L(y_{t+\h}
+  - x_{2t}'\bh{2t}^R).
+\]
+The \oos\ statistic of interest is $\oost \equiv \sqrt{P} \oosA /
+\hat\sigma$, for $\hat\sigma^2$ some (possibly Heteroskedasticity- and
 Autocorrelation-Consistent, or \hac) estimator of the asymptotic
@@
 
-We'll show that \oost\ can be used to test whether the models will
-forecast equally accurately in the future.  Specifically, assume that
-whichever model is chosen will be used for an additional $Q$ periods
-in the future and let $\oosB$ denote the difference in average
-performance over those periods:
-\[
-\oosB \equiv Q^{-1} \sum_{t=T+1}^{T+Q} D_{tT}.
-\]
-Note that $\oosA$ depends on the training sample estimators,
-$\hat\theta_{iR}$, and $\oosB$ depends on the full sample
-estimators, $\hat\theta_{iT}$.  A forecaster has access to the
-information set $\mathcal{F}_T$ when deciding between the two
-forecasting models, but $\mathcal{F}_T$ does not contain $\oosB$.
-So a forecaster should decide between the models based on the
-conditional expectation, $\E_T \oosB$. If this quantity is
-positive, the first model is expected to perform worse in the future,
-and if it is negative the second is.
-
-When the underlying series is i.i.d., this random variable, $\E_T
-\oosB$, is equal to the difference in the models' generalization
-error.  The generalization error of model $i$ is defined as
+As discussed above, the forecaster's goal is to choose the model with
+lower average future loss; i.e. to determine whether $\oosB$ is
+positive or negative,with
+\[
+\oosB \equiv Q^{-1} \sum_{t=T+1}^{T+Q} D_{Tt},
+\]
+with
+\[
+D_{Tt} \equiv L(y_{t+h} - x_{1t}' \bh{1t}^T) - L(y_{t+h} - x_{2t}' \bh{2t}^T)
+\]
+and 
 \begin{equation*}
-  \E_{T} L(y_{T+\h}^{*} - x_{iT}^{*\prime}\hat{\theta}_{iT})
+\bh{it}^{T} = \begin{cases} \big(\sum_{s=1}^{t-\h} x_{is}x_{is}'\big)^{-1}
+\sum_{s=1}^{t-\h} x_{is} y_{s+\h} & \text{recursive window}\\
+ \big(\sum_{s=t - \h - T}^{t-\h} x_{is}x_{is}'\big)^{-1}
+\sum_{s=t - \h - T}^{t-\h} x_{is} y_{s+\h} & \text{rolling window} \\
+ \big(\sum_{s=1}^{T-\h} x_{is}x_{is}'\big)^{-1} 
+\sum_{s=1}^{T-\h} x_{is} y_{s+\h} & \text{fixed window}.
+\end{cases}
 \end{equation*}
-where $(y_{T+\h}^{*},x_{iT}^{*})$ has the same joint distribution as
-$(y_{T+\h}, x_{iT})$ but is independent of $\mathcal{F}_T$.  Note that
-$\hat{\theta}_{iT}$ is known in period $T$, so the generalization
-error conditions on the observed coefficient estimates.  With
-dependence, the coefficient estimates may be informative about future
-values of $y_{t+\h}$ and $x_{it}$, but this influence dies out as $Q$
-grows.  Conditional performance measures like these are especially
-appropriate in areas like time-series economics where the forecaster
-knows the coefficient values when choosing a model, but would be less
-appropriate if the models will be re-estimated over an entirely new
-dataset before forecasting.
+Note that the coefficients are reestimated with a larger dataset for
+the fixed and rolling windows.  Since the forecaster's information
+set, $\mathcal{F}_T$, does not contain $\oosB$, he or she should
+decide between the models based on the conditional expectation, $\E_T
+\oosB$. If this quantity is positive, the first model is expected to
+perform worse in the future, and if it is negative the second is.
+
+This random variable is related to several well known measures of
+model performance.  As $Q \to \infty$, it converges to the difference
+in the models' generalization error and equals it for i.i.d. data.
+Moreover, if the data are i.i.d., the expectation of $\E_T \oosB$
+equals \citepos{Aka:69} Final Prediction Error (\textsc{fpe}).  Both
+generalization error and \textsc{fpe} are defined as teh performance
+on a new, independent, data set; here the new data is not
+independent.  Since $Q \to \infty$ in our asymptotic theory, though,
+we will call $\E_T \oosB$ the difference in generalization error
+throughout the paper with hopefully no risk of confusion.
 
@@
 \begin{asmp}\label{asmp-1} 
-  The random array $\{y_t,x_t\}$ is stationary and
-  absolutely regular with coefficients $\beta_j$ of size
-  $-\rho/(\rho-2)$; $\rho$ is greater than two and discussed further
-  in Assumption \ref{asmp-3}.  Also, $K_1$ and $K_2$ are less than $R$,
-  and $\frac{K_2}{T}$ and $\frac{K_2-K_0}{T}$ are uniformly positive;
-  $K_0$ is the number of regressors shared by the two models ($K_1/T$
-  can be uniformly positive as well, but is not required to be).
+  The random array $\{y_t,x_t\}$ is stationary and absolutely regular
+  with coefficients $\beta_j$ of size $-\rho/(\rho-2)$; $\rho$ is
+  greater than two and discussed further in Assumption \ref{asmp-3}.
+  Also, $K_1$ and $K_2$ are less than $R$, and $K_2/T$ and
+  $(K_2-K_0)/T$ are uniformly positive; $K_0$ is the number of
+  regressors shared by the two models ($K_1/T$ can be uniformly
+  positive as well, but is not required to be).
 \end{asmp}
@@
   Moreover, there exist a $\delta > 0$ and finite $\Delta$ such that
-  \begin{equation*}
+  \begin{align*}
     \lVert \lambda_{\max}(X_{iS_{T}}'X_{iS_{T}}) \rVert_{3+\delta}
-    \leq S_{T}\, \Delta \\
+    &\leq S_{T}\, \Delta, &
     \lVert
     \lambda_{\max}(X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})
-    \rVert_{3+\delta} \leq S_{T}\, \Delta \\
-    \lVert \lambda_{\max}((X_{iS_{T}}'X_{iS_{T}})^{-1}) \rVert_{3+\delta} \leq \Delta/S_{T} \\
+    \rVert_{3+\delta} &\leq S_{T}\, \Delta, \\
+    \lVert \lambda_{\max}((X_{iS_{T}}'X_{iS_{T}})^{-1}) \rVert_{3+\delta} &\leq \Delta/S_{T}, &
     \lVert
     \lambda_{\max}((X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})^{-1})\rVert_{3+\delta}
-    \leq \Delta/S_{T}
-  \end{equation*}
+    &\leq \Delta/S_{T},
+  \end{align*}
   for all $S_{T} \geq K_{2T}$ and large enough $T$, with $i =
@@
   \begin{equation*}
-    \|D_{R+j,R}\|_\rho \leq B_L \quad\text{and}\quad
-    \|D_{T+j,T}\|_\rho \leq B_L.
+    \|D_{R,R+j}\|_\rho \leq B_L \quad\text{and}\quad
+    \|D_{T,T+j}\|_\rho \leq B_L.
   \end{equation*}
-  for all $j \geq 1$.
+  for all $j \geq 1$; $\rho$ is defined in Assumption~\ref{asmp-1}.
 \end{asmp}
@@
 
-\begin{asmp} \label{asmp-4} $P\to\infty$,
-  $R\to\infty$, $Q\to\infty$, $P^2/T \to 0$, and $P = O(Q)$ as $T \to \infty$.
+\begin{asmp} \label{asmp-4} $P\to\infty$, $R\to\infty$, $Q\to\infty$,
+  $P = o(T^{1/2}) + O(Q)$ as $T \to \infty$.  For the rolling and
+  recursive windows, $Q = o(T^{1/2})$ as well.
 \end{asmp}
@@
 consider.  We use the same class of estimators studied by
-\citet{DeD:00} (their class $\mathcal{K}$); see
+\citet{JoD:00} (their class $\mathcal{K}$); see
 their paper for further discussion.
@@
 related---allowing for complex models requires tighter constraints on
-the size of the test sample.
+the size of the test sample.  West allows more general estimation
+methods, while we restrict attention to \ols; the advantage of using
+\ols\ is that it gives a necessary bound, $\| x_{it}' \theta_{it}^{R} - x_{it}'
+\theta_{iR}^R \|_2 \leq O(P/T^{1/2})$.  Our main results will hold for
+other models as long as a similar inequality exists, but proving such
+inequalities for other models is left for future research.
 
 Our other assumptions are similar.  The loss function must be smooth
-almost everywhere, which is slightly less restrictive than
-\citet{Wes:96} requires but is not new; \citet{Mcc:00} extends West's
-results to cover a similar case.  West relaxes our assumption that the
-forecasts come from a linear regression model; we could relax our
-assumption to include other linear estimators, but there would be
-little new insight.  We assume full stationarity and absolute
-regularity of the underlying random array, while West assumes
-covariance stationarity and strong mixing of the transformed forecast
-errors; and the details our moment conditions are different, but seem
-that they would hold in similar environment to West's.  Finally, since
-West's is a more standard environment, he assumes the existence of a
-consistent estimator of the variance, while we construct it
-explicitly.  Only West's assumptions governing model complexity and
-the size of the test sample are substantially different than ours.
+almost everywhere, which is less restrictive than \citet{Wes:96}
+requires but is not new; \citet{Mcc:00} extends West's results to
+cover a similar case.\footnote{Our assumptions allow for discontinuous
+  loss functions, such as that proposed by \citet{PeT:92}.
+  \citet{Mcc:07} does not allow for such loss functions, but it
+  appears that his conclusions hold for them under the restriction
+  $P/T \to 0$.}  We assume full stationarity and absolute regularity
+of the underlying random array, while West assumes covariance
+stationarity and strong mixing of the transformed forecast errors; and
+the details our moment conditions are different, but seem that they
+would hold in similar environment to West's.  Finally, since West's is
+a more standard environment, he assumes the existence of a consistent
+estimator of the variance, while we construct it explicitly.  Only
+West's assumptions governing model complexity and the size of the test
+sample are substantially different than ours.
 
@@
 hypotheses about $E_{T} \oosB$ when the models are overfit.  In
-fact, in the limit it rejects a more-accurate but false benchmark
+fact, in the limit it rejects a more accurate but false benchmark
 model almost surely.
@@
   Consequently, each of the usual Gaussian confidence intervals,
-  \begin{eqnarray}
-  &&[\oosA - z_{\alpha/2} \, \hat\sigma /
+  \begin{gather}
+  [\oosA - z_{\alpha/2} \, \hat\sigma /
       \sqrt{P}, \oosA + z_{\alpha/2} \hat\sigma / \sqrt{P}],\label{interval-twosided} \\
-  &&[\oosA - z_{\alpha} \, \hat\sigma / \sqrt{P}, +\infty), \label{interval-greater}
-  \end{eqnarray}
-  and
-  \begin{equation} (-\infty, \oosA + z_{\alpha}
+  [\oosA - z_{\alpha} \, \hat\sigma / \sqrt{P}, +\infty), \label{interval-greater}
+  \intertext{and}
+(-\infty, \oosA + z_{\alpha}
       \, \hat\sigma / \sqrt{P}],
-  \end{equation}
+    \end{gather}
     contains $\E_T\oosB$ with probability $\alpha$ in the limit,
@@
 models give different forecasts even if they both nest the \dgp.  This
-is similar to \citepos{GiW:06} rolling-window result, but comes from
-different asymptotics.
+is intuitively similar to \citepos{GiW:06} rolling-window result, but
+comes from different asymptotics; Giacomini and White keep the
+variance of the \oos\ average positive by letting $P \to \infty$ with
+$R$ fixed; in this paper, $R \to \infty$ but the variance remains
+positive since $K \to \infty$ (quickly) as well.
 
@@
 \begin{equation}
-  \Pr[\sqrt{P}\oosA/\hat\sigma \geq z_{\alpha} \mid \E_{T}
+  \Pr[P^{1/2}\oosA/\hat\sigma \geq z_{\alpha} \mid \E_{T}
   \oosB \leq 0] \to^p \alpha.
@@
 so Theorem~\ref{res-confidence-intervals} holds if
+\begin{equation}\label{coefpart}
+  \E_R \oosA = \E_T \oosB + o_p(P^{-\frac12}).
+\end{equation}
+and
 \begin{equation}\label{normalpart}
@@
 \end{equation}
+The first Lemma shows that the rolling and recirsive window statistics
+can be approximated by the fixed widnow statistic and that
+that~\eqref{coefpart} holds for the fixed window.  The second Lemma
+shows that the process $\{D_{Rt} - \E_R \oosA\}$ is an $L_2$-mixingale
+of size $-1/2$ that satisfies a \clt\ for the fixed window statistic,
+ensuring~\eqref{normalpart}.
+
+\begin{lem} \label{res-convergence} Suppose that Assumptions
+  \ref{asmp-1}--\ref{asmp-4} hold, let $D_{Rt}'$ and $D_{Tt}'$ denote
+  the loss differences associated with the rolling or recursive
+  window, and let $D_{Rt}$ and $D_{Tt}$ those of the fixed window.  Then
+  \begin{equation}
+    \label{eq:8}
+    P^{1/2} \oosA' = P^{1/2} \oosA + o_p, \qquad Q^{1/2} \oosB' =
+    Q^{1/2} \oosB + o_p,
+  \end{equation}
   and
-\begin{equation}\label{coefpart}
-  \E_R \oosA = \E_T \oosB + o_p(P^{-\frac12}).
-\end{equation}
-The first Lemma first shows that the process $\{D_{tR} - \E_R \oosA\}$
-is an $L_2$-mixingale of size $-1/2$ that satisfies a \clt,
-ensuring~\eqref{normalpart}.  The second shows that~\eqref{coefpart}
-holds under Assumption~\ref{asmp-4}.
+  \begin{equation}\label{eq:7}
+    \E_T \oosB - \E_R \oosA =  O_p(\sqrt{P/T}) +
+    o_p(P^{-\frac12}) + o_p(Q^{-\frac12}).
+  \end{equation}
+\end{lem}
+
+There is an intuitive reason that Lemma~\ref{res-convergence} holds.
+In the limit, the difference between $\E_T \oosB$ and $\E_R \oosA$
+comes from the coefficient estimators used: $\E_T\oosB$ is the
+expected performance using the full-sample estimate, $\hat{\theta}_T$,
+and $\E_R \oosA$ is the performance using the period-$R$ estimate,
+$\hat{\theta}_R$.  When $P$ and $Q$ are large, the dependence between
+the test and training samples vanishes, so the estimators of $\theta$
+are the only variables affected by the conditioning $\sigma$-fields,
+$\mathcal{F}_R$ and $\mathcal{F}_T$.  Since $L$ is smooth, the
+difference between $\E_R \oosA$ and $\E_T \oosB$ is of order $\lvert
+\hat\theta_R - \hat\theta_T \rvert_2$, which itself is of order
+$\sqrt{P/T}$.  The logic behind approximating the rolling and
+recursive window statistics with the fixed window statistic is the
+same.
 
 \begin{lem}\label{res-mixingale}
-  Part 1: If Assumptions~\ref{asmp-1}--\ref{asmp-3} hold then the inequality
+  Part 1: If Assumptions~\ref{asmp-1}--\ref{asmp-3} hold and the fixed
+  window estimation window is used, then the inequality
   \begin{equation}\label{mixingaleR}
-    \lVert \E_{R+j-l}(D_{R+j,R} - \E_R D_{R+j,R}) \rVert_2 \leq
+    \lVert \E_{R+j-l}(D_{R,R+j} - \E_R D_{R,R+j}) \rVert_2 \leq
     \couplingConstant \;
@@
   \end{equation}
-  with $\zeta_l = O(l^{-\frac12 - \delta})$ holds for some positive
+  with $\zeta_l = O(l^{-1/2 - \delta})$ holds for some positive
   $\delta$, any positive $j$, and any $l$ between 0 and $j$.  As a
-  consequence, $\{D_{t,R} - \E_R D_{t,R}, \mathcal F_t\}$ is an
-  $L_2$-mixingales of size $-1/2$.
-
-  \noindent Part
-  2: Moreover,~\eqref{normalpart} holds under
-  Assumptions~\ref{asmp-1}--\ref{asmp-3} if $P \to \infty$ as $T \to
-  \infty$ and $\sigma^2$ is a.s. uniformly positive.
+  consequence, $\{D_{Rt} - \E_R D_{Rt}, \mathcal F_t\}$ is an
+  $L_2$-mixingale of size $-1/2$.
+
+  \noindent Part 2: Moreover,~\eqref{normalpart} holds under the
+  conditions of Part 1 if $P \to \infty$ as $T \to \infty$ and
+  $\sigma^2$ is a.s. uniformly positive.
 \end{lem}
@@
 part of the Lemma shows that the basic mixingale \clt\ established by
-\citet{Dej:97} applies in this setting.\footnote{De Jong proves two
+\citet{Jon:97} applies in this setting.\footnote{De Jong proves two
   \clt s: one for mixingales and one for \ned\ functions of mixing
@@
 
-\begin{lem} \label{res-convergence} Suppose that Assumptions
-  \ref{asmp-1}--\ref{asmp-4} hold.  Then
-\begin{equation*}
-  \E_T \oosB - \E_R \oosA =  O_p(\sqrt{P/T}) +
-  o_p(P^{-\frac12}) + o_p(Q^{-\frac12}).
-\end{equation*}
-\end{lem}
-
-The justification for Lemma~\ref{res-convergence} is intuitive.  In
-the limit, the difference between $\E_T \oosB$ and $\E_R \oosA$
-comes from the coefficient estimators used: $\E_T\oosB$ is the
-expected performance using the full-sample estimate, $\hat{\theta}_T$,
-and $\E_R \oosA$ is the performance using the period-$R$ estimate,
-$\hat{\theta}_R$.  When $P$ and $Q$ are large, the dependence between
-the test and training samples vanishes, so the estimators of $\theta$
-are the only variables affected by the conditioning $\sigma$-fields,
-$\mathcal{F}_R$ and $\mathcal{F}_T$.  Since $L$ is smooth, the
-difference between $\E_R \oosA$ and $\E_T \oosB$ is of order
-$\lvert \hat\theta_R - \hat\theta_T \rvert_2$, which itself is of
-order $\sqrt{\frac{P}{T}}$.
-
 Finally, for Theorem \ref{res-confidence-intervals} to be useful, we
@@
       Lemma~\ref{res-mixingale}, the proof of this lemma takes
-      \citepos{DeD:00} existing consistency results
+      \citepos{JoD:00} existing consistency results
       for \ned\ processes and shows that the same arguments can be
@@
   \ref{asmp-2}, \ref{asmp-3}, and \ref{asmp-5} hold, that $\gamma, P$
-  and $R \to \infty$ as $T \to \infty$, and that $\gamma = o(P)$.  Then
+  and $R \to \infty$ as $T \to \infty$, and that $\gamma = o(P)$.
+  Then
   \begin{equation*}
-    \frac1P \oosSum{s,t}{1} (D_{tR} - \oosA)(D_{sR} - \oosA)
+    P^{-1} \oosSum{s,t}{1} (D_{Rt} - \oosA)(D_{Rs} - \oosA)
     \vWeight = \sigma^2 + o_p(1).
@@
 
+\subsection{An Example}\label{sec:example}
+
 \subsection{Failure of In-Sample Tests}\label{sec:insample}
 This subsection establishes that the F-test can over-reject when the
-benchmark is more accurate than the alternative.  We use stronger
-assumptions than before, i.i.d. data, normal errors, \mse\ loss, and
-nested models to ensure that the F-test performs as well as possible.
-Indeed, we know its exact distribution.  But the basic idea of this
-argument is much more general and should apply to other related tests,
-including \oos\ tests.
-
+benchmark is more accurate than the alternative.  The issue explored
+here is different than that of \citet{Ana:12} and \citet{Cal:11c}; in
+those papers, the authors demonstrate that full sample Wald and $F$
+tests can be invalid under these asymptotics.  But in this subsection,
+we make stronger assumptions than elsewhere in the paper to guarantee
+that the $F$-test is valid; we assume the models are nested, the loss
+function is squared-error, the regressors are fixed, and the errors
+are i.i.d. normal, so the exact finite sample distribution of the
+$F$-test is known.\footnote{These assumptions are made to ensure the
+  most favorable conditions for the full-sample test.  The proof of
+  this section's main result relies only on their implication that the
+  acceptence region of the test is an ellipse centered at the origin
+  and the conclusions of Theorem~\ref{res:ftest} should hold
+  qualitatively for any test statistic that has such an acceptance
+  region, including \oos\ tests.} Even so, the $F$-test can not test
+the hypotheses discussed in the previous subsection; under these
+conditions, the probability that it rejects converges to one under the
+null that the benchmark is more accurate.
+
+Theorem~\ref{res:ftest} presents the details.
 \begin{thm}\label{res:ftest}
@@
 as $\phi_2 \to \infty$, \eqref{eq:ftestreject1} is not an immediate
-consequence of the power of the F-test increasing with $\phi_2$.
-
-The first result,~\eqref{eq:ftestreject1}, can be understood through the case $K_2 = 2$ and
-$K_1 = 0$, so
+consequence of the power of the $F$-test increasing with $\phi_2$.
+
+The first result,~\eqref{eq:ftestreject1}, can be understood through
+the case $K_2 = 2$ and $K_1 = 0$, so
 \begin{equation*}
@@
 It is important to remember that the F-test is valid for the null
-$\psi = 0$ in this analysis.  However, the F-test is poorly suited for
-choosing an accurate forecasting model, and performs worse when the
-larger model is overfit or explains more of the variation of the
-dependent variable.  Other valid unbiased tests of the null hypothesis
-that $\psi = 0$ will suffer the same problem.
+$\psi = 0$ in this analysis, so previous research, such as
+\citet{Ana:12} and \citet{Cal:11c}, does not predict these results.
+However, the $F$-test is poorly suited for choosing an accurate
+forecasting model, and performs worse when the larger model is overfit
+or explains more of the variation of the dependent variable.  Other
+asymptotically valid, unbiased tests of the null hypothesis that $\psi
+= 0$ will suffer the same problem.
 
@@
 \begin{equation*}
-  E_R \oosA = [\sum_{i=1}^{K_1} (\tilde{\theta}_{iR} - \theta_i)^2 +
-  \sum_{i=K_1+1}^{K_2}\theta_i^2] - \sum_{i=1}^{K_2} (\hat{\theta}_{iR} -
+  E_R \oosA = \Bigg[\sum_{i=1}^{K_1} (\tilde{\theta}_{iR} - \theta_i)^2 +
+  \sum_{i=K_1+1}^{K_2}\theta_i^2\Bigg] - \sum_{i=1}^{K_2} (\hat{\theta}_{iR} -
   \theta_i)^2
@@
 \begin{equation*}
-  E_T \oosB = [\sum_{i=1}^{K_1} (\tilde{\theta}_{iT} - \theta_i)^2 +
-  \sum_{i=K_1+1}^{K_2}\theta_i^2] - \sum_{i=1}^{K_2} (\hat{\theta}_{iT} -
+  E_T \oosB = \Bigg[\sum_{i=1}^{K_1} (\tilde{\theta}_{iT} - \theta_i)^2 +
+  \sum_{i=K_1+1}^{K_2}\theta_i^2\Bigg] - \sum_{i=1}^{K_2} (\hat{\theta}_{iT} -
   \theta_i)^2
@@
 modifications of existing results for \ned\ functions of mixing
-processes by \citet{Dej:97} and
-\citet{DeD:00}; this coupling argument is used to
+processes by \citet{Jon:97} and
+\citet{JoD:00}; this coupling argument is used to
 explicitly derive inequalities that arise naturally for \ned\
@@
 
+\begin{lem}
+  Suppose the conditions of Lemma~\ref{res-variance-estimator} hold
+  and let $D_{Rt}$ denote the fixed window statistic and $D_{Rt}'$ the
+  recursive or rolling window statsitics.  Then
+  \begin{multline*}P^{-1} \oosSum{s,t}{1} (D_{Rt}' - \oosA')(D_{Rs}' -
+    \oosA') \vWeight = \\ P^{-1} \oosSum{s,t}{1} (D_{Rt} - \oosA)(D_{Rs}
+    - \oosA) \vWeight + o_p.
+  \end{multline*}
+\end{lem}
+
+\begin{proof}
+  yeah!
+\end{proof}
+
 \section{Proofs of results in main text}
@@
 centered \oos\ average as
-  \[
-    \CenteredAverage = \CenteredAverageI + \CenteredAverageII.
+
+\[
+\frac{\bar{D}_{R} - \E_T \bar{D}_T}{\hat\sigma / \sqrt{P}} =
+\frac{1}{\hat\sigma \sqrt{P}}\oosSum{t}{1} (D_{Rt} - \E_R D_{Rt}) +
+\frac{\sqrt{P}}{\hat\sigma} (\E_R\oosA - \E_T\oosB).
 \]
@@
 Then
-\[
-\lVert \E_{R+j-l} D_{R+j,R} - \E_R D_{R+j,R} \rVert_2 \wall \leq 
+\begin{align*}
+\lVert \E_{R+j-l} D_{R+j,R} - \E_R D_{R+j,R} \rVert_2 & \leq 
 \lVert \E_{R+j-l} D_{R+j,R} - \E_{R+j-l} \tilde{D}_{R+j} \rVert_2 \\
-\quad + \lVert
+&\quad + \lVert
 \E_{R+j-l} \tilde{D}_{R+j} - \E_R D_{R+j,R} \rVert_2 \\
-\leq 2 \lVert D_{R+j,R} - \tilde D_{R+j} \rVert_2 \\
-\leq 2^{2 + \frac1\rho}\ B_L\ \couplingBeta{l}.\return
-\]
+&\leq 2 \lVert D_{R+j,R} - \tilde D_{R+j} \rVert_2 \\
+&\leq 2^{2 + 1/\rho}\ B_L\ \couplingBeta{l}.
+\end{align*}
 Now $\couplingBeta{l} = O(l^{-\frac12 - \delta})$ for some
@@
 \begin{proof}[Proof of Lemma \ref{res-mixingale}, Part 2.]
-  A modification of \citepos{Dej:97} \clt s for
+  A modification of \citepos{Jon:97} \clt s for
   mixingale and \ned\ arrays will complete the proof.
@@
 $b_T\to\infty$, and $b_T/P\to 0$.  The same arguments used in
-\citepos{Dej:97} Theorem 1 show that
+\citepos{Jon:97} Theorem 1 show that
 \begin{equation*}
-   \SumOuterBlock{i} Z_i = \frac1{\sqrt{P}} \oosSum{s}{1} (D_{tR} - \E_R D_{tR}) + o_p(1).
+   \SumOuterBlock{i} Z_i = \frac1{\sqrt{P}} \oosSum{s}{1} (D_{Rt} - \E_R D_{Rt}) + o_p(1).
 \end{equation*}
@@
 \end{equation}
-Equation (\ref{eq:cltvar2}) holds as in \citet{Dej:97} (see the proof
+Equation (\ref{eq:cltvar2}) holds as in \citet{Jon:97} (see the proof
 of his Theorem 2); to see that (\ref{eq:cltvar1}) holds, we'll use an
@@
 \[
-\lVert \tilde D_s - D_{sR} \rVert_2 \leq 2^{1 + \frac1\rho} B_L \beta_{s -
+\lVert \tilde D_s - D_{Rs} \rVert_2 \leq 2^{1 + \frac1\rho} B_L \beta_{s -
   (i-1)b_T + R}^{\rhoExp}, \quad s = R+(i-1)b_T + 1,\dots,R+i b_T
@@
 giving the inequality
-\[
-\lVert \ZSqCE - \E_R Z_i^2 \rVert_1 \wall= \lVert \wall\CEOuterBlock{(Z_i^2 -
-  \tilde Z_i^2)}{i} \\ - (\E_R Z_i^2 - \CEOuterBlock{\tilde Z_i^2}{i})
-\rVert_1 \return\\
-\leq 2 \lVert Z_i^2 - \tilde Z_i^2 \rVert_1.
-\return
-\]
+\begin{align*}
+  \lVert \ZSqCE - \E_R Z_i^2 \rVert_1 &= \lVert
+  \CEOuterBlock{(Z_i^2 - \tilde Z_i^2)}{i} - (\E_R Z_i^2 -
+  \CEOuterBlock{\tilde Z_i^2}{i}) \rVert_1 \\ & \leq 2 \lVert Z_i^2 -
+  \tilde Z_i^2 \rVert_1.
+\end{align*}
 
@@
 It follows that
-\[
-\SumOuterBlock{i} \lVert V_{i,C}^2 - \tilde V_{i,C}^2 \rVert_1 
-\wall
+\begin{align*}
+  \SumOuterBlock{i} \lVert V_{i,C}^2 - \tilde V_{i,C}^2 \rVert_1 &
   \leq 2 \ZTrunc \SumOuterBlock{i} \lVert Z_i - \tilde Z_i \rVert_2 \\
- \leq \frac{2 C \sqrt{b_T}}{P}\SumOuterBlock{i} \SumInnerBlock{s}{i} \lVert \wall \ZSummand \\
-  - (\tilde D_s - \E_R \tilde D_s) \rVert_2 \return \\ 
- = O(\frac{\sqrt{b_T}}{P}) \SumOuterBlock{i} \SumInnerBlock{s}{i} \lVert D_{sR} - \tilde D_s \rVert_2 \\
- = O(b_T^{-\frac12}) \sum_{s=1}^{b_T} \couplingBeta{s}
- \return
- \]
+  & \leq \frac{2 C \sqrt{b_T}}{P}\SumOuterBlock{i} \SumInnerBlock{s}{i} \lVert \ZSummand
+  - (\tilde D_s - \E_R \tilde D_s) \rVert_2 \\
+  & = O(\frac{\sqrt{b_T}}{P}) \SumOuterBlock{i} \SumInnerBlock{s}{i} \lVert D_{Rs} - \tilde D_s \rVert_2 \\
+  & = O(b_T^{-\frac12}) \sum_{s=1}^{b_T} \couplingBeta{s} 
+\end{align*}
 Finally, $\couplingBeta{s} = O(s^{-1/2-\delta})$ for some positive
@@
 \[
-\lVert \tilde D_t - D_{tR} \rVert_2 \leq \couplingBound{t-R}
+\lVert \tilde D_t - D_{Rt} \rVert_2 \leq \couplingBound{t-R}
 \]
@@
 for all $t$.  Then 
-\[
-\lVert \E_R \oosA - \wall \resConvgRHS{R} \rVert_2  \\
-\leq \frac1P \oosSum{t}{1} \lVert \E_R (D_{tR} - \tilde D_t) \rVert_2 \\
-\leq \frac{\couplingConstant}{P} \oosSum{s}{1} \couplingBeta{s} \\
-= o(P^{-\frac12}).
-\return
-\]
+\begin{align*}
+\lVert \E_R \oosA - & \resConvgRHS{R} \rVert_2  \\
+& \leq \frac1P \oosSum{t}{1} \lVert \E_R (D_{Rt} - \tilde D_t) \rVert_2 \\
+& \leq \frac{\couplingConstant}{P} \oosSum{s}{1} \couplingBeta{s} \\
+& = o(P^{-\frac12}).
+\end{align*}
 The proof of (\ref{EQ-oosaverage2}) is identical.
@@
 Manipulating the formula for the \ols\ estimator gives us
-\begin{equation} \label{eq-theta-convergence-1}
-\lVert x_1^{*\prime} (\bh{1R} - \bh{1T}) \rVert_2 \wall \leq
+\begin{multline} \label{eq-theta-convergence-1}
+\lVert x_1^{*\prime} (\bh{1R} - \bh{1T}) \rVert_2  \leq\\
 \lVert x_1^{*\prime} [(X_{1R}'X_{1R})^{-1} - (X_{1T}'X_{1T})]
-X_{1T}'\ep{1T} \rVert_2  \\ \quad +
+X_{1T}'\ep{1T} \rVert_2  +
 \lVert x_1^{*\prime} (X_{1R}'X_{1R})^{-1}\oosSum{t}{1} x_{1t}\varepsilon_{i,t+\h}
 \rVert_2.
-\end{equation}
+\end{multline}
 The first term on the right side of \eqref{eq-theta-convergence-1}
 satisfies the relationship
-\[
-\lVert x_{1}^{*\prime}[(X_{1R}'X_{1R})^{-1} -
-(X_{1T}'X_{1T})^{-1} ]
-X_{1T}'\ep{1T} \rVert_2^2 \\ = O(1)
-\E\{\lambda_{\max}(X_{1T}' \ep{1T} \ep{1T}'
-    X_{1T}) \sum_{i=1}^{K_1}
-    \lambda_i^2([X_{1R}'X_{1R}]^{-1} -
-        [X_{1T}'X_{1T}]^{-1} )\}.
-\]
+\begin{multline*}
+  \lVert x_{1}^{*\prime}[(X_{1R}'X_{1R})^{-1} - (X_{1T}'X_{1T})^{-1} ]
+  X_{1T}'\ep{1T} \rVert_2^2 = \\ O(1) \E\{\lambda_{\max}(X_{1T}'
+  \ep{1T} \ep{1T}' X_{1T}) \sum_{i=1}^{K_1}
+  \lambda_i^2([X_{1R}'X_{1R}]^{-1} - [X_{1T}'X_{1T}]^{-1} )\}.
+\end{multline*}
 By assumption, $\lambda_{\max}(X_{1T}'\ep{1T} \ep{1T}' X_{1T}) =
@@
   \[\sum_{i=1}^{K_1}\lambda_i^2((X_{1R}'X_{1R})^{-1} -
-  (X_{1T}'X_{1T})^{-1} )  \wall \leq
+  (X_{1T}'X_{1T})^{-1} ) \leq
   \sum_{i=K_1 - P + 1}^{K_1}\lambda_i^2((X_{1R}'X_{1R})^{-1})  \\ = O_p(P/T^2).
@@
 \begin{proof}[Proof of Lemma \ref{res-variance-estimator}]
-  The proof follows \citepos{DeD:00} Theorem 2.1
-  closely.  We start by defining similar quantities to theirs,
-  borrowing their notation when possible to make the similarities
-  apparent.  For positive $\delta$, define $b_T \equiv \lfloor
-  \frac\gamma\delta \rfloor$,
-\begin{equation*}
-  \kernelB{x} \equiv \kernelBDefn{x},
-\end{equation*}
-\begin{equation*}
-  \varianceTermI \equiv \varianceTermIDefn,
-\end{equation*}
-\begin{equation*}
-  \varianceTermII \equiv \vtSum \wall \varianceTermIIa\\ \times
-  \varianceTermIIb,\return
-\end{equation*}
-\begin{equation*}
-  \varianceTermIII \equiv \vtSum \wall \varianceTermIIIa\\ 
-  \times \varianceTermIIb, \return 
-\end{equation*}
-\begin{equation*}
-  \varianceTermIV \equiv \vtSum \wall \varianceTermIIIa \\
-  \times \varianceTermIVb, \return
-\end{equation*}
+  The proof follows \citepos{JoD:00} Theorem 2.1 closely.  We start by
+  defining similar quantities to theirs, borrowing their notation when
+  possible to make the similarities apparent.  For positive $\delta$,
+  define $b_T \equiv \lfloor \frac\gamma\delta \rfloor$, $\kernelB{x}
+  \equiv \kernelBDefn{x}$, and
+\begin{align*}
+  \varianceTermI &\equiv
+  \varianceTermIDefn,\\ \varianceTermII &\equiv \vtSum
+  \varianceTermIIa\\& \quad \times \varianceTermIIb,\\
+  \varianceTermIII &\equiv \vtSum \varianceTermIIIa\\
+  &\quad \times \varianceTermIIb,\\
+  \varianceTermIV &\equiv \vtSum \varianceTermIIIa \\
+  &\quad\times \varianceTermIVb,
+\end{align*}
 giving us the inequalities
-\begin{equation*}
-  \lVert \hat\sigma^2 - \sigma^2 \rVert_1 \wall 
+\begin{align*}
+  \lVert \hat\sigma^2 - \sigma^2 \rVert_1 &
   \leq \lVert \hat\sigma^2 - \varianceTermI \rVert_1 
@@
   + \lVert \varianceTermII - \varianceTermIII \rVert_1 
-  + \lVert \varianceTermIII - \varianceTermIV \rVert_1\\\quad
+  + \lVert \varianceTermIII - \varianceTermIV \rVert_1\\ & \quad
   + \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1 
   + \lVert \E_R\varianceTermIII - \E_R\varianceTermIV \rVert_1
-  + \lVert \E_R\varianceTermII - \E_R\varianceTermIII \rVert_1\\\quad 
+  + \lVert \E_R\varianceTermII - \E_R\varianceTermIII \rVert_1\\ & \quad 
   + \lVert \E_R\varianceTermI - \E_R\varianceTermII \rVert_1 
   + \lVert \E_R \varianceTermI - \sigma^2 \rVert_1
-  \\ 
+  \\ &
   \leq  \lVert \hat\sigma^2 - \varianceTermI \rVert_1 
@@
       + \lVert \varianceTermIII - \varianceTermIV \rVert_1) \\ 
-  \quad + \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1 
+  & \quad + \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1 
   + \lVert \E_R \varianceTermI - \sigma^2 \rVert_1.
-\end{equation*}
+\end{align*}
 De Jong and Davidson (2000) prove that
@@
 We'll start with (\ref{eq:4}). It follows from simple algebra that
-\[
-\lvert \hat\sigma^2 - \varianceTermI \rvert \leq \wall
-\varianceDiffA \\ +
-\frac1{P} \oosSum{s,t}{1} \lvert (D_{tR} - \oosA)(\E_R D_{sR} - \oosA) \rvert
-\vWeight,
-\]
+\begin{align*}
+  \lvert \hat\sigma^2 - \varianceTermI \rvert & \leq  
+  \varianceDiffA \\ & \quad + \frac1{P} \oosSum{s,t}{1} \lvert (D_{Rt} -
+  \oosA)(\E_R D_{Rs} - \oosA) \rvert \vWeight,
+\end{align*}
 so we'll show that each summation is $o_p(1)$.  The two
@@
 upper bound
-\[
-\varianceDiffA \\ \quad \leq O(1) [\varianceDiffAii]^{\frac12} [\varianceDiffAi]^{\frac12}.
-\]
+\begin{multline*}
+\varianceDiffA \\ \leq O(1) [\varianceDiffAii]^{\frac12} [\varianceDiffAi]^{\frac12}.
+\end{multline*}
 Now,
-$\frac1P \oosSum{s}{1}(D_{sR} - \E_R D_{sR})^2 = O_p(1)$, and it suffices to prove
+$\frac1P \oosSum{s}{1}(D_{Rs} - \E_R D_{Rs})^2 = O_p(1)$, and it suffices to prove
 that \[\varianceDiffAi = o_p(1).\]  Observe that
-\[
-\varianceDiffAi \wall =  O_p(\frac1P \oosSum{s}{1}(\E_{R}D_{sR} -
-\E_R\oosA)^2) \\
-\quad + O_p(\oosA - \E_R\oosA)^{2} \\
-= O_p(\frac1P \oosSum{s}{1} (\E_RD_{sR})^2 - (\E_R\oosA)^2) + o_p(1),    \return
-\]
+\begin{align*}
+  \varianceDiffAi & = O_p\Big(P^{-1} \oosSum{s}{1}(\E_{R}D_{Rs} -
+  \E_R\oosA)^2\Big) + O_p(\oosA - \E_R\oosA)^{2} \\
+  &= O_p\Big(P^{-1} \oosSum{s}{1} (\E_RD_{Rs})^2 - (\E_R\oosA)\Big) +
+  o_p(1),
+\end{align*}
 with the second term vanishing by Lemma \ref{res-mixingale} and
@@
 Consequently,
-\[
-\frac1P \oosSum{s}{1} (\E_R D_{sR})^2 - (\E_R\oosA)^2 \wall = 
-\frac1P \oosSum{s}{1} [(\E_R D_{sR})^2 - (\E_R\tilde D_s)^2]\\
-\quad+ (\frac1P \oosSum{s}{1} \E_R \tilde D_s)^2 - (\E_R\oosA)^2 \quad \text{a.s}.\\
-= O_p(\frac1P \oosSum{s}{1} [(\E_R D_{sR})^2 - (\E_R \tilde D_s)^2]).
-\]
+\begin{align*}
+\frac1P \oosSum{s}{1} (\E_R D_{Rs})^2 - (\E_R\oosA)^2 & = 
+\frac1P \oosSum{s}{1} [(\E_R D_{Rs})^2 - (\E_R\tilde D_s)^2]\\
+&\quad+ \Big(P^{-1} \oosSum{s}{1} \E_R \tilde D_s\Big)^2 - (\E_R\oosA)^2 \quad \text{a.s}.\\
+&= O_p\Big(P^{-1} \oosSum{s}{1} [(\E_R D_{Rs})^2 - (\E_R \tilde D_s)^2]\Big).
+\end{align*}
 Finally, 
-\[
-\lVert \frac1P \wall\oosSum{s}{1} [(\E_RD_{sR})^2 - (\E_R \tilde D_s)^2] \rVert_1
-\\ \leq \frac1P \oosSum{s}{1} \lVert \E_RD_{sR} - \E_R \tilde D_s \rVert_2 \lVert
-\E_RD_{sR} + \E_R \tilde D_s \rVert_2
-\\ \leq \frac{4 B_L}P \oosSum{s}{1} \lVert \E_RD_{sR} - \E_R \tilde D_s \rVert_2,
-\return
-\]
+\begin{align*}
+\lVert \frac1P \oosSum{s}{1} [(\E_RD_{Rs})^2 - (\E_R \tilde D_s)^2] \rVert_1
+&\leq \frac1P \oosSum{s}{1} \lVert \E_RD_{Rs} - \E_R \tilde D_s \rVert_2 \lVert
+\E_RD_{Rs} + \E_R \tilde D_s \rVert_2
+\\ &\leq \frac{4 B_L}P \oosSum{s}{1} \lVert \E_RD_{Rs} - \E_R \tilde D_s \rVert_2,
+\end{align*}
 and this last term vanishes as in the proof of Lemma
@@
 \newcommand{\UFiltration}[1]{\ensuremath{\mathcal{F}_{(#1)b_{T}+R-P}}}%
-Next, we'll prove (\ref{eq:5}). As in \citet{DeD:00}, let
+Next, we'll prove (\ref{eq:5}). As in \citet{JoD:00}, let
 \begin{equation*}
@@
 \lfloor \frac{3P}{2b} \rfloor$ and rewrite the summation as
-\begin{equation*}
-  \vtSum \vtIIIsummand \wall= \vtSumr \vtSuma \vtIIIsummand \\
-  \quad+ \vtSumr \vtSumb \vtIIIsummand \\
-  \quad+ \sum_{t=r b - P + 1}^{2P} \vtIIIsummand \\
-  \equiv \vtSumr (U_i - \E_R U_i) + \vtSumr (U_i' - \E_R U_i') + o_{L_1}(1).\return
-\end{equation*}
+\begin{align*}
+  \vtSum \vtIIIsummand &= \vtSumr \vtSuma \vtIIIsummand \\
+  &\quad+ \vtSumr \vtSumb \vtIIIsummand \\
+  &\quad+ \sum_{t=r b - P + 1}^{2P} \vtIIIsummand \\
+  &\equiv \vtSumr (U_i - \E_R U_i) + \vtSumr (U_i' - \E_R U_i') + o_{L_1}(1).
+\end{align*}
 The proof then holds if we can show that both $U_i$ and $U_i'$ obey
@@
 \begin{equation*}
-  \lVert \tilde D_{ts} - D_{sR} \rVert_2 \leq \couplingBound{s - (2i-2m-1)b_T-R+P}.
+  \lVert \tilde D_{ts} - D_{Rs} \rVert_2 \leq \couplingBound{s - (2i-2m-1)b_T-R+P}.
 \end{equation*}
@@
 Now, we have the inequalities
-\begin{equation*}
-  \lVert \E( U_i - \wall \E_R U_i \mid \UFiltration{2i-2m-1}) \rVert_2
-  \\ \leq
+\begin{align*}
+  \lVert \E( U_i - \E_R U_i \mid \UFiltration{2i-2m-1}) \rVert_2
+  &\leq
   \vtSuma \lVert \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) - \E_R
   Z_{1t}Z_{2t} \rVert_2 \\
-  = \vtSuma \lVert \wall \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
-  - \E(\tilde{Z}_{1t}\tilde{Z}_{2t} \mid \UFiltration{2i-2m-1}) \\
-  + \E(\tilde{Z}_{1t}\tilde{Z}_{2t} \mid \UFiltration{2i-2m-1})
-  - \E_R Z_{1t}Z_{2t} \rVert_2 \return \\
+  &= \vtSuma \lVert \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
+  &\quad - \E(\tilde{Z}_{1t}\tilde{Z}_{2t} \mid \UFiltration{2i-2m-1}) \\
+  &\quad + \E(\tilde{Z}_{1t}\tilde{Z}_{2t} \mid \UFiltration{2i-2m-1})
+  - \E_R Z_{1t}Z_{2t} \rVert_2 \\
 %  \leq \vtSuma (\wall \lVert \wall \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
@@
 %  \rVert_2)\return \\
-  \leq 2 \vtSuma \lVert Z_{1t} Z_{2t} - \tilde Z_{1t} \tilde{Z}_{2t}
+  &\leq 2 \vtSuma \lVert Z_{1t} Z_{2t} - \tilde Z_{1t} \tilde{Z}_{2t}
   \rVert_2 \\
-  \leq 2 \vtSuma (\lVert Z_{1t} - \tilde{Z}_{1t} \rVert_2 \lVert
+  &\leq 2 \vtSuma (\lVert Z_{1t} - \tilde{Z}_{1t} \rVert_2 \lVert
   Z_{2t} \rVert_{\infty}
   + \lVert Z_{2t} - \tilde{Z}_{2t} \rVert_2 \lVert \tilde{Z}_{1t} \rVert_{\infty}) \\
-  \leq 2 C \sqrt{\frac{b_T}{P\gamma}} \vtSuma (\lVert Z_{1t} - \tilde{Z}_{1t} \rVert_2 
+  &\leq 2 C \sqrt{\frac{b_T}{P\gamma}} \vtSuma (\lVert Z_{1t} - \tilde{Z}_{1t} \rVert_2 
   + \lVert Z_{2t} - \tilde{Z}_{2t} \rVert_2).
-  \return
-\end{equation*}
+\end{align*}
 
 And we can finish the proof with the following inequalities:
-\begin{equation*}
-  2 C \wall \sqrt{\frac{b_T}{P \gamma}} \vtSuma \lVert Z_{1t} - \tilde{Z}_{1t} \rVert_2 \\ \leq
+\begin{align*}
+  2 C \sqrt{\frac{b_T}{P \gamma}} \vtSuma & \lVert Z_{1t} - \tilde{Z}_{1t} \rVert_2 \\& \leq
   \frac{4C \sqrt{b_T}}{P\gamma} \vtSuma \sum_{l=\vttLower}^{\vttUpper} \lVert
-  D_{t+l+R,R} - \tilde{D}_{t,t+l+R} \rVert_2 W(l/\gamma) \\
+  D_{t+l+R,R} - \tilde{D}_{t,t+l+R} \rVert_2 W(l/\gamma) \\&
   \leq O(\frac{\sqrt{b_T}}{P\gamma}) \vtSuma
-  \sum_{l=\vttLower}^{\vttUpper} \couplingBeta{t+l-(2i-2m-1)b_T+P}\\
+  \sum_{l=\vttLower}^{\vttUpper} \couplingBeta{t+l-(2i-2m-1)b_T+P}\\&
   = O(\frac{\sqrt{b_T}}{P\gamma}) O(b_T^{\frac32-u}\, m^{-\frac12-u})
-\end{equation*}
+\end{align*}
 for some positive $u$.  The same argument holds for $Z_{2t}$.
@@
 As a result,
-\[
-\Pr[F \geq q_{\alpha}\wall \mid E_T \oosB \leq 0] = 
-\Pr[\hat{\psi}'\hat{\psi} \geq \hat \tau^2 q_\alpha \frac{K_2 - K_1}{T}
+\begin{align*}
+  \Pr[F \geq q_{\alpha} \mid E_T \oosB \leq 0] &=
+  \Pr[\hat{\psi}'\hat{\psi} \geq \hat \tau^2 q_\alpha \frac{K_2 -
+    K_1}{T}
   \mid |\hat{\psi}-\psi|_2 \geq |\psi|_2] \\
-\geq 1 - \E(\;\Pr[ \hat{\omega}_i \in [\tilde{\omega}_i - \xi, \tilde{\omega}_i +
-\xi] \ \forall i  \mid \wall \hat{\tau}^2,
+  &\geq 1 - \E(\;\Pr[ \hat{\omega}_i \in [\tilde{\omega}_i - \xi,
+  \tilde{\omega}_i + \xi] \ \forall i \mid \hat{\tau}^2,
   |\hat{\psi}-\psi|_2 \geq |\psi|_2] \\
-\mid |\hat{\psi}-\psi|_2 \geq |\psi|_2)\quad a.s. \return \\ 
-= 1 - \frac12 E ((2\xi / \pi)^{K_2-K_1-1}\mid
+  &\qquad\qquad \mid |\hat{\psi}-\psi|_2 \geq |\psi|_2)\quad a.s. \\
+  &= 1 - \frac12 E ((2\xi / \pi)^{K_2-K_1-1}\mid
   |\hat{\psi}-\psi|_2 \geq |\psi|_2)\quad a.s. \\
-= 1 - \frac12 E (2\xi/\pi)^{K_2-K_1-1} \quad a.s..
-\]
+  &= 1 - \frac12 E (2\xi/\pi)^{K_2-K_1-1} \quad a.s..
+\end{align*}
 The second equality holds because the $\hat{\omega}_i$s are uniform
@@
  \begin{tabular}{lrrrr}\hline\hline
-\multicolumn{1}{l}{waldtest}&\multicolumn{1}{c}{Res.Df}&\multicolumn{1}{c}{Df}&\multicolumn{1}{c}{F}&\multicolumn{1}{c}{Pr(\textgreaterF)}\tabularnewline
+   \multicolumn{1}{l}{waldtest}&\multicolumn{1}{c}{Res.Df}&\multicolumn{1}{c}{Df}&\multicolumn{1}{c}{F}&\multicolumn{1}{c}{Pr(\textgreater
+     F)}\tabularnewline
    \hline
@@
 
-% LocalWords: LM clark meese diebold chao corradi mccracken giacomini lm jel iR
-% analyses inoue datasets huber efron anova akritas
-% calhoun iR berbee th de nondifferentiable jong
-% mixingales mcleish AIC Berbee's merlevede Heyde's ib
-% mixingaleR TP eq dx dy tex tR tS tT iT sR sw tw vw
-% reestimate davidson over-reject anatolyev Anatolyev's iS izx
-% coefpart normalpart Jong's jt oos underrejects cltvar Scwarz JEL
-% hansen lm McCracken's jel RSQLite elemstatlearning rproject rsqlite
 % LocalWords:  McCracken's kilian anatolyev rossi REStud JAppliedEconometrics
-% LocalWords:  goyal welch rfs reputational calhoun Berbee's mixingales tR tS
-% LocalWords:  Heteroskedasticity Autocorrelation tT iT th berbee iS de dx ixz
-% LocalWords:  DMW mcleish sR eq ftestreject lightgray veclen RSQLite zeileis
+% LocalWords:  goyal welch rfs reputational calhoun Berbee's mixingales Rt tS
+% LocalWords:  Heteroskedasticity Autocorrelation Tt iT th berbee iS de dx ixz
+% LocalWords:  DMW mcleish Rs eq ftestreject lightgray veclen RSQLite zeileis
 % LocalWords:  heteroskedasticity hothorn RNews JStatSoftware harrell campbell

### 2012-03-30 paper.tex
Added link to AllRefs.bib to ignore file

--- 2012-03-30 paper.tex
@@
 \author{Gray Calhoun\thanks{email: \texttt{gcalhoun@iastate.edu}. I
-    would like to thank Julian Betts, Helle Bunzel, Marjorie Flavin,
-    Nir Jaimovich, Lutz Kilian, Michael McCracken, Seth Pruitt, Ross
-    Starr, Yixiao Sun, Allan Timmermann, participants at the 2010
-    Midwest Economics Association Annual Meetings, the 2010 Joint
-    Statistical Meetings, and in many seminars at \textsc{ucsd}, and
-    espeically Graham Elliott for their valuable suggestions, feedback
-    and advice in writing this paper.  I would also like to thank Amit
-    Goyal for providing computer code and data for his 2008 RFS paper
-    with Ivo Welch \citep{goyal-welch-2008-rfs}.} \\ Iowa State
-  University, Economics Department}
+    would like to thank Julian Betts, Marjorie Flavin, Nir Jaimovich,
+    Lutz Kilian, Michael McCracken, Seth Pruitt, Ross Starr, Yixiao
+    Sun, Allan Timmermann, participants at the 2010 Midwest Economics
+    Association Annual Meetings, the 2010 Joint Statistical Meetings,
+    and in many seminars at \textsc{ucsd}, and espeically Graham
+    Elliott for their valuable suggestions, feedback and advice in
+    writing this paper.  I would also like to thank Amit Goyal for
+    providing computer code and data for his 2008 RFS paper with Ivo
+    Welch \citep{goyal-welch-2008-rfs}.} \\ Iowa State University,
+  Economics Department}
 \date{October 24, 2011}
@@
 training window, but our basic conclusions should be true for other
-estimation strategies and models as well.  Under this asymptotic
-theory, the \ols\ coefficient estimator is no longer consistent or
-asymptotically normal \citep{huber_robust_1973} with positive variance
-in the limit.  Even so, we show that the usual \oos\ average is
-asymptotically normal and can consistently estimate the difference
-between the models' expected loss in periods $T+1,T+2,\dots$
-conditional on the on the data available in period $T$, a time-series
-analogue to the generalization error.\footnote{See, for example,
-  \citet{elemstatlearning}.}  Under these asymptotics, the
-generalization error does not converge to the expected performance of
-the pseudo-true models, so the in-sample and \oos\ comparisons measure
-different quantities and should be expected to give different results
-for reasons beyond simple size and power comparisons.  Under our
-theory, the model that is closer to the true \dgp\ in population can
-forecast worse.  In such a situation, an in-sample comparison would
-correctly reject the null hypothesis that the benchmark is true, and
-an \oos\ comparison would correctly fail to reject the null that the
-benchmark is more accurate.\footnote{In a pair of papers similar to
-  ours, \citet{RePEc:fip:fedkrw:rwp09-10,RePEc:fip:fedkrw:rwp09-11}
-  study in-sample and \oos\ tests that the larger model has nonzero
+estimation strategies and models as well.  We show that the usual
+\oos\ average is asymptotically normal and can consistently estimate
+the difference between the models' expected loss in periods
+$T+1,T+2,\dots$ conditional on the on the data available in period
+$T$, a time-series analogue to the generalization error.\footnote{See,
+  for example, \citet{elemstatlearning}.}  Under these asymptotics,
+the generalization error does not converge to the expected performance
+of the pseudo-true models, so the in-sample and \oos\
+comparisons measure different quantities and should be expected to
+give different results for reasons beyond simple size and power
+comparisons.  Under our theory, the model that is closer to the true
+\dgp\ in population can forecast worse.  In such a situation, an
+in-sample comparison would correctly reject the null hypothesis that
+the benchmark is true, and an \oos\ comparison would correctly fail to
+reject the null that the benchmark is more accurate.\footnote{In a
+  pair of papers similar to ours,
+  \citet{RePEc:fip:fedkrw:rwp09-10,RePEc:fip:fedkrw:rwp09-11} study
+  in-sample and \oos\ tests that the larger model has nonzero
   coefficients that are too close to zero to expect the model to
@@
 
-Since the models' coefficients are imprecisely estimated in the limit,
-the test sample must be small to ensure that the model estimated over
-the training sample is similar to the one that will be estimated over
-the full sample.  In particular, $P/T \to 0$ is required for
-consistent estimation, and $P^2/T \to 0$ is required for valid
-confidence intervals and inference.  For larger $P$, the \oos\
+However, since the models' coefficients are imprecisely
+estimated, the test sample must be small to ensure that the model
+estimated over the training sample is similar to the one that will be
+estimated over the full sample.  In particular, $P/T \to 0$ is
+required for consistent estimation, and $P^2/T \to 0$ is required for
+valid confidence intervals and inference.  For larger $P$, the \oos\
 comparisons remain asymptotically normal, but are centered on the
@@
 
-Since the \ols\ coefficient estimator is no longer consistent or
-asymptotically normal, the F-test and Wald tests are no longer
-asymptotically valid.  Moreover,
-\citet{efron_biased_1986,efron_estimation_2004} shows that naive
-comparisons of in-sample loss overestimate models' accuracy by a
-factor proportional to $K/T$, $K$ being the number of regressors.  But
-modifications of the F-test are valid under this asymptotic theory, as
-shown by \citet{boos_anova_1995}, \citet{akritas_asymptotics_2000},
+Under this asymptotic theory, the \ols\ coefficient estimator is no
+longer consistent or asymptotically normal \citep{huber_robust_1973},
+so this is a useful way to model overfit and imprecisely estimated
+models.  Moreover, \citet{efron_biased_1986,efron_estimation_2004}
+shows that in-sample comparisons overestimate models' accuracy by a
+factor proportional to this ratio.  Despite the non-normality of the
+coefficient estimators, modifications of the F-test are valid under
+this asymptotic theory, as shown by \citet{boos_anova_1995},
+\citet{akritas_asymptotics_2000},
 \citet{akritas_heteroscedastic_2004}, and
-\citet{calhoun_hypothesis_2009}, among others.  Such results establish
-that hypotheses about the parameters of the \dgp\ can be tested
-in-sample even if one or both models are overfit.  For that very
-reason, these tests can not reliably choose a model for forecasting
-and will reject the benchmark too often.  We show this analytically in
-Section~\ref{sec:insample}.  Moreover, under this asymptotic theory,
-many recent \oos\ test statistics, such as those derived by
-\cite{clark_tests_2001,clark_evaluating_2005},
+\citet{calhoun_hypothesis_2009}, among others.  The F-test and Wald
+tests are no longer asymptotically valid themselves.  Such results
+establish that hypotheses about the parameters of the \dgp\ can be
+tested in-sample even if one or both models are overfit.  For that
+very reason, these tests can not reliably choose a model for
+forecasting and will reject the benchmark too often.  We show this
+analytically in Section~\ref{sec:insample}.  Moreover, under this
+asymptotic theory, many recent \oos\ test statistics, such as those
+derived by \cite{clark_tests_2001,clark_evaluating_2005},
 \citet{mccracken_asymptotics_2007}, and
@@
 argument \citep{berbee_random_1979} that is unavailable for strong
-mixing sequences.  Please see, for example,
-\citet{davidson_stochastic_1994} for a discussion of these mixing
-conditions.
+mixing sequences.
 
@@
   \begin{equation*}
-    \lVert \lambda_{\max}(X_{iS_{T}}'X_{iS_{T}}) \rVert_{3+\delta}
+    \lVert \lambda_{\max}(X_{iS_{T}}'X_{iS_{T}}) \rVert_{4+\delta}
     \leq S_{T}\, \Delta \\
@@
     \lambda_{\max}(X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})
-    \rVert_{3+\delta} \leq S_{T}\, \Delta \\
-    \lVert \lambda_{\max}((X_{iS_{T}}'X_{iS_{T}})^{-1}) \rVert_{3+\delta} \leq \Delta/S_{T} \\
+    \rVert_{4+\delta} \leq S_{T}\, \Delta \\
+    \lVert \lambda_{\max}((X_{iS_{T}}'X_{iS_{T}})^{-1}) \rVert_{4+\delta} \leq \Delta/S_{T} \\
     \lVert
-    \lambda_{\max}((X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})^{-1})\rVert_{3+\delta}
+    \lambda_{\max}((X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})^{-1})\rVert_{4+\delta}
     \leq \Delta/S_{T}

### 2012-03-30 mc/plot-insample-size.Rnw
Collapsed hold history into a single commit

@@
 
-<<fig=TRUE,width=5.5, height=4>>=
+<<fig=TRUE>>=
 library(fwPackage)
 library(lattice)
-ltheme <- canonical.theme(color = FALSE)     ## in-built B&W theme  
-ltheme$strip.background$col <- "transparent" ## change strip bg  
-lattice.options(default.theme = ltheme)      ## set as default
 
 dbc <- dbConnect(dbDriver("SQLite"), dbname = "simulations.db")
-d <- dbGetQuery(dbc, "select reject, 'T=' || n as nlabel, altlabel, norm from viewftest 
-                                     where label='size' and norm in (0,1)")
-d$norm <- as.factor(d$norm)
 
 print(dotplot(norm ~ reject | interaction(altlabel,nlabel, sep = ", "),
-              dat = d, las = 1,
-              xlab = "Rejection Probability", ylab = "c",
+              dat = dbGetQuery(dbc, "select reject, 'n=' || n as nlabel, altlabel, norm from viewftest 
+                                     where label='size' and norm in (0,1)"),
+              xlab = "Rejection Probability",
               xlim = c(-.1, 1.1),
@@
               },
+              par.settings = standard.theme(color=FALSE),
               par.strip.text = list(cex = .65),
               layout = c(2,4),
-              index.cond = list(c(3,4,7,8,5,6,1,2))))
+              index.cond = list(c(3,4,7,8,5,6,1,2)),
+              main = "Rejection probability for F-test at 10% (size)\nbenchmark has smaller generalization error"))
 @

### 2012-03-30 mc/plot-interval.Rnw
Collapsed hold history into a single commit

--- 2010-10-18 mc/plot-interval.Rnw
@@
 library(lattice)
-ltheme <- canonical.theme(color = FALSE)     ## in-built B&W theme  
-ltheme$strip.background$col <- "transparent" ## change strip bg  
-lattice.options(default.theme = ltheme)      ## set as default
 
 dbc <- dbConnect(dbDriver("SQLite"), dbname = "simulations.db")
-mcpars <- dbGetQuery(dbc, "select count(jobnumber) as njobs from interval")
-dstring <- "
+d <- dbGetQuery(dbc, "
 select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
 from interval 
-where label='%s' and simIndex <= %d and transform = 'difference'
+where label in ('test.error.1', 'test.error.2', 'gen.error.1', 'gen.error.2')
+and simIndex <= 500
 group by ntest, isim, idgp, transform, label) s 
-join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp"
+join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp")
+d$nlabel <- sprintf("n=%d", d$n)
+d$normlabel <- sprintf("c=%d", d$norm)
 
-doxyplot <- function(dplot, ...) {
-  print(xyplot(I(1 - reject) ~ I(ntest/n) | interaction(nlabel, altlabel, normlabel, sep = ", "),
+doxyplot <- function(dframe, label, maintext, ...) {
+  dplot <- dframe[dframe$label==label,]
+  print(xyplot(I(1 - reject) ~ ntest | interaction(nlabel, altlabel, normlabel, sep = ", "),
                data = dplot,
-               ylab = "Coverage", xlab = "P/T",
+               ylab = "coverage", main = maintext,
+##               ylim = c(-0.05,1.05),
                panel = function(x,y,...) {
                  panel.xyplot(x,y,...,type = "l")
-                 panel.lines(c(0,2/3),c(.9,.9), col = "gray")
+                 panel.lines(c(1,600),c(.9,.9), col = rgb(0,0,0,0.5))
                },
-               layout = c(4,4),
                par.strip.text = list(cex = .65),
-               index.cond = list(c(13,15,16,14,9,11,12,10,5,7,8,6,1,3,4,2))))
+               index.cond = list(c(13,15,16,14,9,11,12,10,5,7,8,6,1,3,4,2)),
+               par.settings = standard.theme(color=FALSE),...))
 }
@@
 
-<<testerror1, fig=TRUE, height = 3.5, width=6>>=
-d <- dbGetQuery(dbc, sprintf(dstring, 'test.error.1', 500))
-d$nlabel <- sprintf("T=%d", d$n)
-d$normlabel <- sprintf("c=%d", d$norm)
-
-doxyplot(d) #Empirical coverage of one-sided interval
+<<fig=TRUE>>=
+doxyplot(d, "test.error.1", "Empirical coverage of one-sided interval")
 @
 
-<<testerror2, fig=TRUE, height = 3.5, width=6>>=
-d <- dbGetQuery(dbc, sprintf(dstring, 'test.error.2', 500))
-d$nlabel <- sprintf("T=%d", d$n)
-d$normlabel <- sprintf("c=%d", d$norm)
-doxyplot(d) #Empirical coverage of two-sided interval
+<<fig=TRUE>>=
+doxyplot(d, "test.error.2", "Empirical coverage of two-sided interval")
 @
 
-<<generror1, fig=TRUE, height = 3.5, width=6>>=
-d <- dbGetQuery(dbc, sprintf(dstring, 'gen.error.1', 500))
-d$nlabel <- sprintf("T=%d", d$n)
-d$normlabel <- sprintf("c=%d", d$norm)
-doxyplot(d) #Empirical coverage of one-sided interval
+<<fig=TRUE>>=
+doxyplot(d, "gen.error.1", "Empirical coverage of one-sided interval")
 @
 
-<<generror2, fig=TRUE, height = 3.5, width=6>>=
-d <- dbGetQuery(dbc, sprintf(dstring, 'gen.error.2', 500))
-d$nlabel <- sprintf("T=%d", d$n)
-d$normlabel <- sprintf("c=%d", d$norm)
-doxyplot(d) #Empirical coverage of two-sided interval
+<<fig=TRUE>>=
+doxyplot(d, "gen.error.2", "Empirical coverage of two-sided interval")
 @
 
+<<fig=TRUE>>=
+doxyplot(d, "gen.error.2", "Details of empirical coverage of two-sided interval", 
+         xlim = c(0,350), ylim = c(.75, .95))
+@ 
 <<>>=

### 2012-03-30 mc/plot-oos-diff.Rnw
Collapsed hold history into a single commit

\documentclass{article}
\SweaveOpts{prefix.string=plots/diff}
\usepackage[margin=1in]{geometry}

\begin{document}
Basic file that generates plots for the out-of-sample $t$-test
centered at $E_{R}\bar D_{1}$

<<>>=
library(fwPackage)
library(lattice)

dbc <- dbConnect(dbDriver("SQLite"), dbname = "simulations.db")

doxyplot <- function(trans, kalt, maintext) {
  print(xyplot(value ~ ntest | n + norm, groups = paste(jobnumber, " ", simIndex),
               data = dbGetQuery(dbc, paste("select * from viewdiff where transform = '", trans, "' ",
                 "and altlabel = '", kalt, "'", sep="")),
               main = paste("Normalized difference between ", maintext, ", ", kalt, sep = ""),
               type = "l", ylim = c(-2, 15), col = rgb(0,0,0,0.003),
               par.settings = standard.theme(color=FALSE),
               strip = strip.custom(strip.levels=c(TRUE,TRUE), strip.names=c(TRUE,TRUE), shingle.intervals=NULL)))
}
@

<<fig=TRUE>>=
doxyplot("difference", "K=3", "L1 - L2")
@
<<fig=TRUE>>=
doxyplot("ratio", "K=3", "L1/L2")
@
<<fig=TRUE>>=
doxyplot("rmse.difference", "K=3", "sqrt(L1) - sqrt(L2)")
@
<<fig=TRUE>>=
doxyplot("log.difference", "K=3", "log(L1) - log(L2)")
@
<<fig=TRUE>>=
doxyplot("rmse.ratio", "K=3", "sqrt(L1)/sqrt(L2)")
@
<<fig=TRUE>>=
doxyplot("difference", "K=n/10", "L1 - L2")
@

<<fig=TRUE>>=
doxyplot("ratio", "K=n/10", "L1/L2")
@

<<fig=TRUE>>=
doxyplot("rmse.difference", "K=n/10", "sqrt(L1) - sqrt(L2)")
@

<<fig=TRUE>>=
doxyplot("log.difference", "K=n/10", "log(L1) - log(L2)")
@

<<fig=TRUE>>=
doxyplot("rmse.ratio", "K=n/10", "sqrt(L1)/sqrt(L2)")
@

\end{document}

### 2012-03-30 mc/plot-oos-size.Rnw
Collapsed hold history into a single commit

@@
 library(lattice)
-ltheme <- canonical.theme(color = FALSE)     ## in-built B&W theme  
-ltheme$strip.background$col <- "transparent" ## change strip bg  
-lattice.options(default.theme = ltheme)      ## set as default
 
@@
 join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp")
-d$nlabel <- sprintf("T=%d", d$n)
+d$nlabel <- sprintf("n=%d", d$n)
 d$normlabel <- sprintf("c=%d", d$norm)
@@
 join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp")
-dpower$nlabel <- sprintf("T=%d", dpower$n)
+dpower$nlabel <- sprintf("n=%d", dpower$n)
 dpower$normlabel <- sprintf("c=%d", dpower$norm)
@@
 
-doxyplot <- function(dframe, ...) {
-  print(xyplot(reject ~ I(ntest/n) | interaction(nlabel,altlabel,normlabel, sep = ", "),
+doxyplot <- function(dframe, maintext, ...) {
+  print(xyplot(reject ~ ntest | interaction(nlabel,altlabel,normlabel, sep = ", "),
                data = dframe,
-               ylab = "Rejection Probability", xlab = "P/T",
+               ylab = "size", main = maintext,
                panel = function(x,y,...) {
-                 panel.lines(c(0,2/3),c(.1,.1), col = "lightgray")
                  panel.xyplot(x,y,...,type = "l")
+                 panel.lines(c(1,600),c(.1,.1), col = rgb(0,0,0,0.5))
                },
@@
                par.strip.text = list(cex = .65),
-               index.cond = list(c(13,15,16,14,9,11,12,10,5,7,8,6,1,3,4,2))))
+               index.cond = list(c(13,15,16,14,9,11,12,10,5,7,8,6,1,3,4,2)),
+               par.settings = standard.theme(color=FALSE)))
 }
@@
 
-Empirical size of Clark and West test at 90\% confidence
-<<clarkwest, fig=TRUE, width=6>>=
-doxyplot(d[d$transform == "clarkwest",])
+<<fig=TRUE>>=
+doxyplot(d[d$transform == "clarkwest",], 
+         "Empirical size of Clark and West test at 90% confidence")
 @
 
-Empirical size of McCracken test at 90\% confidence
-<<mccracken, fig=TRUE, width=6, height=3.5>>=
-  print(xyplot(reject ~ I(ntest/n) | interaction(nlabel,altlabel,normlabel, sep = ", "),
-               data = d[d$altlabel=="K=3" & d$transform == "mccracken",],
-               ylab = "Rejection Probability", xlab = "P/T",
-               panel = function(x,y,...) {
-                 panel.lines(c(0,2/3),c(.1,.1), col = "lightgray")
-                 panel.xyplot(x,y,...,type = "l")
-               },
-               layout = c(4,2),
-               par.strip.text = list(cex = .65),
-               index.cond = list(c(5,7,8,6,1,3,4,2))))
-## doxyplot(d[d$altlabel=="K=3" & d$transform == "mccracken",])         
+<<fig=TRUE>>=
+doxyplot(d[d$altlabel=="K=3" & d$transform == "mccracken",], 
+         "K=3", "Empirical size of McCracken test at 90% confidence")
 @
 
-Empirical size of Naive OOS test at 90\% confidence
-<<dmwsize, fig=TRUE, width=6>>=
-doxyplot(d[d$transform == "difference",])
+<<fig=TRUE>>=
+doxyplot(d[d$transform == "difference",], 
+         "K=3", "Empirical size of Naive OOS test at 90% confidence", auto.key = list(lines=TRUE, points=FALSE))
 @
 
-Empirical power of Naive oos test at 90\% confidence
-<<dmwpower, fig=TRUE, width=6>>=
-doxyplot(dpower[dpower$transform == "difference",]) 
+<<fig=TRUE>>=
+doxyplot(dpower[dpower$transform == "difference",], 
+         "Empirical power of Naive oos test at 90% confidence", auto.key = list(lines=TRUE, points=FALSE))
 @

### 2012-03-30 paper.tex
Collapsed hold history into a single commit

@@
 \documentclass[11pt]{article}
-%\linespread{1.2}\selectfont
-\usepackage{tikz}
-\usetikzlibrary{calc}
-\usetikzlibrary{fit}
+% \makeatletter
+% \renewcommand\@seccntformat[1]{\protect\makebox[0pt][r]{\csname
+%     the#1\endcsname\quad}}
+% \renewcommand\section{\@startsection
+% {section}{1}{0mm}{\baselineskip}{\baselineskip}{\normalfont\normalsize\scshape}}
+% \renewcommand\subsection{\@startsection
+% {subsection}{2}{0mm}{\baselineskip}{\baselineskip}{\normalfont\normalsize\scshape}}
+% \renewcommand\subsubsection{\@startsection
+% {subsubsection}{3}{0mm}{\baselineskip}{\baselineskip}{\normalfont\normalsize\scshape}}
+% \renewcommand\paragraph{\@startsection
+% {paragraph}{4}{0mm}{\baselineskip}{\baselineskip}{\normalfont\normalsize\scshape}}
+% \renewcommand\subparagraph{\@startsection
+% {subparagraph}{5}{0mm}{\baselineskip}{\baselineskip}{\normalfont\normalsize\scshape}}
+% \makeatother
+\linespread{1.2}\selectfont
+\usepackage{tikz}\usetikzlibrary{calc}
 \usepackage{graphicx}
@@
 \usepackage[round,comma]{natbib}
-\usepackage{setspace,amsmath,amssymb,amsthm,ifthen,subfig,url,multicol}
-\usepackage{fancyhdr}
-\pagestyle{fancy}
-\lhead{\thepage}\chead{}\rhead{}
-\lfoot{}\cfoot{}\rfoot{}
-\renewcommand\headrulewidth{0pt}
-\onehalfspacing
-\usepackage[top=1.222222in,left=0.9444444in,right=1.888889in,bottom=2.4444444in]{geometry}
+\usepackage{setspace,amsmath,amssymb,amsthm,ifthen,subfig}
+\usepackage[top=1in,left=1in,right=1in,bottom=1in]{geometry}
+%\onehalfspacing
+%\usepackage[top=1.222222in,left=0.9444444in,right=1.888889in,bottom=2.4444444in]{geometry}
 \usepackage{nath}
-
+% \newcommand{\wall}{\,}
+% \newcommand{\return}{\,}
+
+%\newtheoremstyle{gc}{\topsep}{\topsep}{\itshape}{0pt}{\scshape}{}{\newline}{}
+%\theoremstyle{gc}
 \newtheorem{thm}{Theorem}[section]
@@
 
-\DeclareMathOperator{\E}{E}
-\DeclareMathOperator{\var}{var}
-\DeclareMathOperator*{\plim}{plim}
-\DeclareMathOperator{\tr}{tr}
-\DeclareMathOperator{\atan}{atan*}
+% \newcommand{\E}{E}
+% \newcommand{\var}{var}
+% \newcommand{\plim}{plim}
+% \DeclareMathOperator*{\argmin}{arg\,min}
+% \newcommand{\tr}{tr}
+\newcommand{\E}{`E}
+\newcommand{\var}{`var}
+\newcommand{\plim}{`plim}
+\newcommand{\tr}{`tr}
 
@@
 
-\newcommand{\oost}{\ensuremath{\operatorname{oos-t}}}
-\newcommand{\oosSum}[2]{\ensuremath{\sum_{#1=R-\h+#2}^{T-\h}}}
+% \newcommand{\oost}{\ensuremath{\operatorname{oos-t}}}
+\newcommand{\oost}{\ensuremath{'oos-'t}}
+\newcommand{\oosSum}[2]{\ensuremath{\sum_{#1=R+#2}^{T-\h}}}
 
@@
 \newcommand{\ZSqCE}{\ensuremath{\CEOuterBlock{Z_i^2}{i}}}
-\newcommand{\ZTrunc}{\ensuremath{C\sqrt{b_{T}/P}}}
+\newcommand{\ZTrunc}{\ensuremath{C\sqrt{\frac{b_{T}}{P}}}}
 \newcommand{\PScaleTerm}{\ensuremath{\frac{C \sqrt{b_T}}{P}}}
 
-\newcommand{\vWeight}{W((t-s)/\gamma)}
+\newcommand{\vWeight}{W(\frac{t-s}{\gamma})}
 \newcommand{\vSummand}{\ensuremath{(D_{tR} - \E_R D_{tR})(D_{sR} - \E_R D_{sR}) \vWeight}}
 \newcommand{\kernelBDefn}[1]{\ensuremath{\frac1{\delta\sqrt{2\pi}}e^{-\frac{#1^2}{2\delta^2}}}}
-\newcommand{\kernelB}[1]{\ensuremath{\eta_{\delta}(#1)}}
+\newcommand{\kernelB}[1]{\ensuremath{\tau_{\delta}(#1)}}
 
@@
     \sum_{l=\max(1-t,-P)}^{\min(P-t,P)} (D_{t+l+R,R} - \E_R D_{t+l+R,R})
-    W(l/\gamma)}}
+    W(\frac{l}{\gamma})}}
 \newcommand{\varianceTermIIb}{\ensuremath{\frac1{\sqrt{P\gamma}}
     \sum_{j=1-t}^{P-t} (D_{t+j+R,R} - \E_R D_{t+j+R,R})
-    \kernelB{j/\gamma}}}
+    \kernelB{\frac{j}{\gamma}}}}
 \newcommand{\varianceTermIII}{\ensuremath{\sigma_{2\delta}^{2}}}
@@
     \sum_{l=\vttLower}^{\vttUpper} (D_{t+l+R,R} - \E_R D_{t+l+R,R})
-    W(l/\gamma)}}
+    W(\frac{l}{\gamma})}}
 \newcommand{\varianceTermIV}{\ensuremath{\sigma_{3\delta}^{2}}}
@@
     \sum_{j=\vttLower}^{\vttUpper} (D_{t+j+R,R} - \E_R D_{t+j+R,R})
-    \kernelB{j/\gamma}}}
+    \kernelB{\frac{j}{\gamma}}}}
 \newcommand{\vtIIIsummand}{\ensuremath{(Z_{1t}Z_{2t} - \E_RZ_{1t}Z_{2t})}}
@@
 \vWeight}}
-\newcommand{\varianceDiffAi}{\ensuremath{\frac1P \oosSum{s}{1}(\E_R
-    D_{sR} - \bar D_1 )^2}}
+\newcommand{\varianceDiffAi}{\ensuremath{\frac1P \oosSum{s}{1}(\bar
+    D_1 - \E_R D_{sR})^2}}
 \newcommand{\varianceDiffAii}{\ensuremath{\frac1P \oosSum{s}{1}
@@
 
-\newcommand{\dmw}{\textsc{dmw}}
-\newcommand{\ols}{\textsc{ols}}
-\newcommand{\mds}{\textsc{mds}}
-\newcommand{\clt}{\textsc{clt}}
-\newcommand{\lln}{\textsc{lln}}
+\newacronym{ols}{Ordinary Least Squares}{OLS}
+\newacronym{mds}{Martingale Difference Sequence}{MDS}
+\newacronym{clt}{Central Limit Theorem}{CLT}
+\newacronym{lln}{Law of Large Numbers}{LLN}
 \newacronym{VAR}{Vector Autoregression}{VAR}
 \newacronym{oos}{out-of-sample}{OOS}
-\newcommand{\dgp}{\textsc{dgp}}
-\newcommand{\hac}{\textsc{hac}}
+\newacronym{dgp}{Data Generating Process}{DGP}
+\newacronym{hac}{Heteroskedasticty- and Autocorrelation-Consistent}{HAC}
 \newacronym{ned}{Near Epoch Dependent}{NED}
@@
 
-\frenchspacing \title{Out-of-Sample Comparisons of Overfit Models}
-\author{Gray Calhoun\thanks{email: \texttt{gcalhoun@iastate.edu}. I
-    would like to thank Julian Betts, Marjorie Flavin, Nir Jaimovich,
-    Lutz Kilian, Michael McCracken, Seth Pruitt, Ross Starr, Yixiao
-    Sun, Allan Timmermann, participants at the 2010 Midwest Economics
-    Association Annual Meetings, the 2010 Joint Statistical Meetings,
-    and in many seminars at \textsc{ucsd}, and espeically Graham
-    Elliott for their valuable suggestions, feedback and advice in
-    writing this paper.  I would also like to thank Amit Goyal for
-    providing computer code and data for his 2008 RFS paper with Ivo
-    Welch \citep{goyal-welch-2008-rfs}.} \\ Iowa State University,
-  Economics Department}
-\date{October 24, 2011}
+\frenchspacing 
+\title{Limit Theory for Out-of-Sample Comparisons of Overfit Models} 
+\author{Gray Calhoun\thanks{email: \texttt{gcalhoun@iastate.edu}. I would like to thank
+    Julian Betts, Robert de Jong, Marjorie Flavin, Nir Jaimovich,
+    Michael McCracken, Seth Pruitt, Ross Starr, Yixiao Sun, Allan
+    Timmermann, participants at the Midwest Economics Association
+    Annual Meetings and in many seminars at \textsc{ucsd}, and espeically
+    Graham Elliott for their valuable suggestions, feedback and advice in writing
+    this paper.  I would also like to thank Amit Goyal for providing
+    computer code and revised data for his 2008 RFS paper with Ivo
+    Welch \citep{goyal-welch-2008-rfs}.} \\ Iowa State University, Economics Department}
 
 \begin{document}
+\bibliographystyle{abbrvnat}
 \maketitle
 
-\begin{abstract}\thispagestyle{empty}\noindent
-  This paper uses dimension asymptotics to study why overfit linear
-  regression models should be compared out-of-sample; we let the number of
-  predictors used by the larger model increase with the number of
-  observations so that their ratio remains uniformly positive.  Under
-  this limit theory, the naive Diebold-Mariano-West out-of-sample test
-  can test hypotheses about a key quantity for evaluating forecasting
-  models---a time series analogue to the generalization error---as
-  long as the out-of-sample period is small relative to the total
-  sample size.  Moreover, tests that are designed to reject if the
-  larger model is true, such as the usual in-sample Wald and
-  \textsc{lm} tests and also Clark and McCracken's (2001, 2005a),
+\begin{abstract}\noindent
+  This paper uses dimension asymptotics to find a reason to compare
+  overfit forecasts out-of-sample instead of in-sample. The two models
+  to be compared are linear regressions, and the number of predictions
+  used by the larger model increases with the number of observations
+  so that their ratio remains uniformly positive. Under this limit
+  theory, tests that are designed to reject if the larger model is
+  true, such as the usual in-sample Wald and \textsc{lm} tests and
+  also Clark and McCracken's (2001, 2005a),
   \citepos{mccracken_asymptotics_2007} and Clark and West's (2006,
   2007) out-of-sample statistics, will choose the larger model too
-  often when the smaller model is more accurate.
+  often when the smaller model is more accurate. I show that the
+  Gaussian out-of-sample $t$-test is a valid test that the models have
+  equal generalization error as long as the out-of-sample period is
+  very small relative to the total sample size.
 
@@
 \noindent Keywords: Generalization Error, Forecasting, Model
-Selection, t-test, Dimension Asymptotics
+Selection, t-test
 \end{abstract}
@@
 rate models, it is unclear from a theoretical perspective whether or
-not the statistics are useful.  Empirical researchers often cite
-``overfit'' or ``instability'' as reasons for using \oos\ comparisons,
-as in \citet{stock_forecasting_2003}, but neither term is precisely
-defined or formalized.  Compounding this problem, the asymptotic
-distributions of these statistics are derived under conditions that
-rule out either instability or overfit and allow a researcher to use a
-conventional in-sample comparison---a variation of the F-test, for
-example.  As \citet{inoue_kilian_2004} argue, the statistics
-themselves are designed to test hypotheses that can be tested by these
-in-sample statistics.  For example, \citet{diebold_comparing_1995} and
+not the statistics are useful.  Empirical researchers often cite {\em
+  overfit} or {\em instability} as reasons for using \oos\
+comparisons, as in \citet{stock_forecasting_2003}, but neither term is
+precisely defined or formalized.  Compounding this problem, the
+asymptotic distributions of these statistics are derived under
+conditions that rule out either instability or overfit and allow a
+researcher to use a conventional in-sample comparison---a variation of
+the F-test, for example.  The statistics themselves are designed to
+test hypotheses that can be tested by these in-sample statistics.  For
+example, \citet{diebold_comparing_1995} and
 \citet{west_asymptotic_1996} derive the limiting distributions of many
 popular \oos\ test statistics under conditions that would justify
-these full-sample tests.\footnote{In this paper, we will refer to
-  their basic \oos\ $t$-test as the \dmw\ test.}  Much of the
-subsequent research by \citet{chao_out_2001},
+these full-sample tests.
+Much of the subsequent research by \citet{chao_out_2001},
 \citet{clark_tests_2001,clark_evaluating_2005},
 \citet{corradi_consistent_2002,corradi_recent_2004},
-\citet{clark_using_2006,clark_approximately_2007},
-\citet{mccracken_asymptotics_2007}, \citet{anatolyev_inference_2008},
-and others relaxes several of Diebold and Mariano's and West's
+\citet{clark_using_2006,clark_approximately_2007}, and
+\citet{mccracken_asymptotics_2007}, among others, relaxes several of
+\citepos{diebold_comparing_1995} and \citepos{west_asymptotic_1996}
 assumptions, but maintains the stationarity and dependence conditions
-that permit in-sample comparisons.\footnote{Like us,
-  \citet{anatolyev_inference_2008} allows the number of regressors to
-  increase with $T$.  But in that paper, they increase slowly enough
-  that the \ols\ coefficients are consistent and asymptotically
-  normal.}  \citet{giacomini_tests_2006}, and
-\citet{giacomini-rossi-2009-REStud,giacomini-rossi-2010-JAppliedEconometrics}
-are exceptions.  Instead of focusing on hypotheses that can be tested
-by in-sample comparisons, \citet{giacomini_tests_2006} derive an \oos\
-test for the null hypothesis that the difference between two models'
-\oos\ forecasting performance is unpredictable, a martingale
-difference sequence, \citet{giacomini-rossi-2009-REStud} test whether
-the \oos\ forecasting performance of a model suffers from a breakdown
-relative to its in-sample performance, and
-\citet{giacomini-rossi-2010-JAppliedEconometrics} test whether the
-forecasting performance is stable. However, those papers focus on a
-particular \oos\ estimation strategy and do not address why naive
-\oos\ comparisons might be generally useful.
+that permit in-sample comparisons.  \citepos{giacomini_tests_2006}
+paper is an exception.  Instead of
+focusing on hypotheses that can be tested by in-sample comparisons,
+\citet{giacomini_tests_2006} derive an \oos\ test for the null
+hypothesis that the difference between two models' \oos\ forecasting
+performance is unpredictable. However, \citet{giacomini_tests_2006}
+focus on a particular \oos\ estimation strategy and do not address why
+\oos\ comparisons might be useful in general.
 
 Since in-sample and \oos\ statistics require similar assumptions and
-test similar hypotheses, one might expect that they would give similar
-results.  They do not.  Generally in-sample analysis supports more
-complicated theoretical models and \oos\ analysis supports simple
-benchmarks, as seen in \citet{meese_empirical_1983},
-\citet{stock_forecasting_2003}, and \citet{goyal-welch-2008-rfs}.
-Since these different approaches strongly influence the outcome of
-research, it is important to know when each is appropriate.  The
-explanations in favor of \oos\ comparisons claim that they should be
-more robust to unmodeled instability
-\citep{clark_power_2005,giacomini_tests_2006,giacomini-rossi-2009-REStud,giacomini-rossi-2010-JAppliedEconometrics}
-or to overfit \citep{mccracken_data_1998,clark_can_2004}.  Both
-explanations presume that the in-sample comparison is invalid and the
-\oos\ comparisons are more reliable.  Of course, as
-\citet{inoue_kilian_2004,inoue_selection_2006} point out, both
+test similar hypotheses, one might expect that they would agree in
+practice.  They do not.  Generally in-sample analyses support more
+complicated theoretical models and \oos\ analyses support simple
+benchmarks, as seen in \citet{meese_empirical_1983} and
+\citet{stock_forecasting_2003}.  Since these different approaches
+strongly influence the outcome of research, it is important to know
+when each is appropriate.  The explanations in favor of \oos\
+comparisons claim that they should be more robust to unmodeled
+instability \citep{clark_power_2005,giacomini_tests_2006} or to
+overfit
+\citep{mccracken_data_1998,clark_can_2004,hansen_in-sample_2009}.
+Both explanations presume that the in-sample comparison is invalid and
+the \oos\ comparisons are more reliable.  Of course, as
+\citet{inoue_in-sample_2005,inoue_selection_2006} propose, both
 in-sample and \oos\ methods could be valid, but the \oos\ methods
@@
 
-In this paper, we study the ``overfit'' possibility and leave
-``instability'' to future research. This paper uses dimension
-asymptotics to study the behavior of \oos\ comparisons when at least
-one of the models is overfit---when the number of its regressors
-increases with the number of observations so that their ratio remains
-positive.  We focus on linear regression models estimated with a fixed
-training window, but our basic conclusions should be true for other
-estimation strategies and models as well.  We show that the usual
-\oos\ average is asymptotically normal and can consistently estimate
-the difference between the models' expected loss in periods
-$T+1,T+2,\dots$ conditional on the on the data available in period
-$T$, a time-series analogue to the generalization error.\footnote{See,
-  for example, \citet{elemstatlearning}.}  Under these asymptotics,
-the generalization error does not converge to the expected performance
-of the pseudo-true models, so the in-sample and \oos\
-comparisons measure different quantities and should be expected to
-give different results for reasons beyond simple size and power
-comparisons.  Under our theory, the model that is closer to the true
-\dgp\ in population can forecast worse.  In such a situation, an
-in-sample comparison would correctly reject the null hypothesis that
-the benchmark is true, and an \oos\ comparison would correctly fail to
-reject the null that the benchmark is more accurate.\footnote{In a
-  pair of papers similar to ours,
+This paper uses dimension asymptotics to study the behavior of \oos\
+comparisons when at least one of the models is overfit---the number of
+regressors increases with the number of observations so that their
+ratio remains positive.  We focus on linear regression models
+estimated with a fixed training window, but our basic conclusions
+should be true for other schemes as well.  We show that the usual
+\oos\ average is asymptotically normal and consistently estimates the
+difference between the models' generalization error, the expected loss
+of the estimated models' forecasts for new observations.  Under our
+asymptotics, the generalization error does not converge to the
+expected performance of the pseudo-true models.  Therefore, the
+in-sample and \oos\ comparisons measure different quantities and
+should be expected to give different results for reasons beyond simple
+size and power comparisons.  Under our theory, the model that is
+closer to the true \dgp\ in population can forecast worse.  In such a
+situation, an in-sample comparison would correctly reject the null
+hypothesis that the benchmark is true, and an \oos\ comparison would
+correctly fail to reject the null that the benchmark is more
+accurate.\footnote{In a pair of papers similar to ours,
   \citet{RePEc:fip:fedkrw:rwp09-10,RePEc:fip:fedkrw:rwp09-11} study
@@
 
-This result justifies \oos\ comparisons when researchers want to
-choose a model for forecasting.  Although there has been little
-emphasis on hypothesis testing in these settings, testing is usually
-appropriate: there is usually a familiar benchmark model in place, and
-the cost of incorrectly abandoning the benchmark for a less accurate
-alternative model is higher than the cost of incorrectly failing to
-switch to a more accurate alternative.\footnote{These costs can be
-  monetary, in the form of computer upgrades, software installation,
-  and training, or they can be reputational costs.}
-We show that the \dmw\ test lets the forecaster control the
-probability of the first error, just as with conventional hypothesis
-testing.
-
-However, since the models' coefficients are imprecisely
-estimated, the test sample must be small to ensure that the model
-estimated over the training sample is similar to the one that will be
-estimated over the full sample.  In particular, $P/T \to 0$ is
-required for consistent estimation, and $P^2/T \to 0$ is required for
-valid confidence intervals and inference.  For larger $P$, the \oos\
-comparisons remain asymptotically normal, but are centered on the
-forecasting performance associated with the period-$R$ estimates.  In
-practice, researchers typically use large values of $P$, so these
-studies may be too pessimistic about their models' future accuracy if
-they use the \dmw\ test.  Section~\ref{sec:oostheory} lays out the
-asymptotic behavior of the \dmw\ test under this limit theory.
-
-Under this asymptotic theory, the \ols\ coefficient estimator is no
-longer consistent or asymptotically normal \citep{huber_robust_1973},
-so this is a useful way to model overfit and imprecisely estimated
+Under this asymptotic theory, the \ols\ coefficient estimator is no longer
+consistent or asymptotically normal \citep{huber_robust_1973}, so this
+is a constructive way to model overfit and imprecisely estimated
 models.  Moreover, \citet{efron_biased_1986,efron_estimation_2004}
@@
 factor proportional to this ratio.  Despite the non-normality of the
-coefficient estimators, modifications of the F-test are valid under
-this asymptotic theory, as shown by \citet{boos_anova_1995},
+coefficient estimators, modifications of the F-test are valid
+under this asymptotic theory, as shown by \citet{boos_anova_1995},
 \citet{akritas_asymptotics_2000},
@@
 \citet{calhoun_hypothesis_2009}, among others.  The F-test and Wald
-tests are no longer asymptotically valid themselves.  Such results
-establish that hypotheses about the parameters of the \dgp\ can be
-tested in-sample even if one or both models are overfit.  For that
-very reason, these tests can not reliably choose a model for
-forecasting and will reject the benchmark too often.  We show this
-analytically in Section~\ref{sec:insample}.  Moreover, under this
-asymptotic theory, many recent \oos\ test statistics, such as those
-derived by \cite{clark_tests_2001,clark_evaluating_2005},
-\citet{mccracken_asymptotics_2007}, and
-\citet{clark_using_2006,clark_approximately_2007} should behave like
-the F-test.  These tests are also designed to reject the benchmark
-when the alternative model is true, and so they may reject too often
-when the benchmark is false but more accurate.  Obviously, since the
-distribution of these statistics converges to the normal when $P/T \to
-\infty$ (with the number of regressors fixed), these statistics behave
-like the \dmw\ test when $P$ is small, but should over-reject the
-benchmark when $P$ is large.  Section~\ref{sec:mc} presents
-simulations that support these claims.
-
-Finally, this paper also introduces a new method of proof for \oos\
-statistics.  We use a coupling argument (Berbee's Lemma, 1979) to show
-that sequences of \oos\ loss behave like mixingales when the
-underlying series are absolutely regular, even if the forecasts depend
-on non-convergent estimators.  Moreover, transformations of these
-processes also behave like mixingales, so asymptotic results for \ned\
-functions of mixing processes can be used for these \oos\ processes
-with only slight modification.  Although we only present a proof that
-this mixingale result holds for the fixed-window scheme, it is simple
-to extend it to other estimation windows.
+tests are no longer asymptotically valid themselves.
+
+Moreover, under this asymptotic theory, non-standard test statistics,
+such as those derived by \citet{mccracken_asymptotics_2007} and
+\cite{clark_tests_2001,clark_evaluating_2005}, are unnecessary, as in
+\citet{giacomini_tests_2006}.  Gaussian confidence intervals
+constructed over the test sample contain the difference between the
+models' future performance with the correct probability (i.e. 95\%
+confidence intervals contain it 95\% of the time).  In fact, using
+these non-Gaussian test statistics, or correcting the \oos\ average as
+in \citet{clark_using_2006,clark_approximately_2007}, will cause the
+forecaster to choose the larger model too often.  Since these tests
+are designed to reject if the benchmark model is false, they are
+invalid tests for equal generalization error in exactly the same way
+that the in-sample tests are: they can overreject when the larger model
+is true but less accurate.  Since these corrections vanish as $P/T$
+converges to zero, this criticism does not hold for small
+test-samples.
+
+However, there is a trade off.  Since we allow the coefficients to be
+imprecisely estimated, the test sample must be small to ensure that
+the model estimated over the training sample is similar to the one
+that will be estimated over the full sample.  In particular, $P/T \to
+0$ is required for the \oos\ average to consistently estimate the
+generalization error, and $P^2/T \to 0$ is required for valid
+confidence intervals.  For larger $P$, the \oos\ comparisons remain
+asymptotically normal, but are centered on the generalization error
+associated with the wrong estimates.
+In practice, researchers typically use large values of $P$, so these
+studies may be too pessimistic about their models' future accuracy.
+
+Our asymptotic theory is similar to that developed by
+\citet{anatolyev_inference_2008}, but there are several key
+distinctions.  \citet{anatolyev_inference_2008} derives the asymptotic
+distribution of \oos\ comparisons as the number of regressors
+increases with the number of observations, but slowly: their ratio
+does not remain positive in the limit.  Anatolyev's asymptotics
+motivate several corrections to the \oos\ statistic for it to continue
+to give valid inference about the models' population parameters; those
+corrections are unnecessary under our asymptotics because we focus on
+inference about the models' generalization error, not their
+pseudo-true parameters, and they would (likely) be insufficient to
+give valid inference about the population parameters under our faster
+growth rates for the number of regressors.
+
+This paper also introduces a new method of proof for \oos\ processes.
+We use a coupling argument (Berbee's 1979 Lemma) to show that these
+processes behave like Mixingales when the underlying series are
+absolutely regular, even if the forecasts depend on full-sample
+non-convergent estimators.  Moreover, transformations of these
+processes also behave like Mixingales, so asymptotic results for \ned\
+functions of mixing processes can be used on these \oos\ processes
+with slight modification.  Although we only present a proof that this
+mixingale result holds for the fixed-window scheme, it is simple to
+extend it to other estimation windows.
 
 The rest of the paper proceeds as follows.
-Section~\ref{sec:assumptions} introduces our notation and assumptions.
-Section~\ref{sec:theory} gives the main theoretical results for the
-\dmw\ \oos\ test and shows that the F-test rejects the benchmark model
-too often when it is false but more accurate than the
-alternative. Section~\ref{sec:mc} presents a Monte Carlo study
-supporting our theoretical results.  Section~\ref{sec:empirics}
-applies the \oos\ statistic to \citepos{goyal-welch-2008-rfs} dataset
-for equity premium prediction, and Section~\ref{sec:conclusion}
-concludes.  Proofs and supporting results are listed in the Appendix.
+Section~\ref{sec:assumptions} introduces this paper's notation and
+assumptions.  Section~\ref{sec:theory} gives the main theoretical
+results.  Section~\ref{sec:empirics} applies the \oos\ statistic to
+the \citet{goyal-welch-2008-rfs} dataset.  Section~\ref{sec:mc}
+presents a Monte Carlo study, and section~\ref{sec:conclusion}
+concludes.  Proofs and additional results are listed in the Appendix.
 
 \section{Setup and Assumptions}\label{sec:assumptions}
-We will set up our models and notation first, then list the assumptions
-required for our results.  There are two competing linear models that
+We will setup our models and notation first, then list the assumptions
+required for our theory.  There are two competing linear models that
 give forecasts for the target, $y_{t+\h}$:
@@
 asymptotic theory, but we suppress that notation to make the
-presentation more clear.
+presentation simpler.
 
 Although our theory can apply to many different \oos\ statistics,
-we'll only present results for the \dmw\ \oos\ $t$-test.  Both models
+we'll only present results for the \oos\ t-test (\oost).  Both models
 are estimated using \ols\ over the training sample:
@@
 \[
-\oost \equiv \frac{\sqrt{P} \bar D_1}{\hat\sigma},
-\]
-for $\hat\sigma^2$ some (possibly Heteroskedasticity- and
-Autocorrelation-Consistent, or \hac) estimator of the asymptotic
+\oost \equiv \sqrt{P} \frac{\bar D_1}{\hat\sigma_1},
+\]
+for $\hat\sigma^2$ some (possibly \hac) estimator of the asymptotic
 variance of $\bar D_1$.
 
-We'll show that \oost\ can be used to test whether the models will
-forecast equally accurately in the future.  Specifically, assume that
-whichever model is chosen will be used for an additional $Q$ periods
-in the future and let $\bar D_2$ denote the difference in average
-performance over those periods:
+We'll show that \oost\ can be used to test that the models have equal
+generalization error.  To motivate interest in this
+quantity, assume that whichever model is chosen will be used for an
+additional $Q$ periods in the future.  Let $\bar D_2$ denote the
+difference in average performance over those periods:
 \[
@@
 \]
-Note that $\bar D_1$ depends on the training sample estimators,
-$\hat\theta_{iR}$, and $\bar D_2$ depends on the full sample
-estimators, $\hat\theta_{iT}$.  A forecaster has access to the
-information set $\mathcal{F}_T$ when deciding between the two
-forecasting models, but $\mathcal{F}_T$ does not contain $\bar D_2$.
-So a forecaster should decide between the models based on the
-conditional expectation, $\E_T \bar{D}_2$. If this quantity is
-positive, the first model is expected to perform worse in the future,
-and if it is negative the second is.
-
-When the underlying series is i.i.d., this random variable, $\E_T
-\bar{D}_2$, is equal to the difference in the models' generalization
-error.  The generalization error of model $i$ is defined as
-\begin{equation*}
-  \E_{T} L(y_{T+\h}^{*} - x_{iT}^{*\prime}\hat{\theta}_{iT})
-\end{equation*}
-where $(y_{T+\h}^{*},x_{iT}^{*})$ has the same joint distribution as
-$(y_{T+\h}, x_{iT})$ but is independent of $\mathcal{F}_T$.  Note that
-$\hat{\theta}_{iT}$ is known in period $T$, so the generalization
-error conditions on the observed coefficient estimates.  With
-dependence, the coefficient estimates may be informative about future
-values of $y_{t+\h}$ and $x_{it}$, but this influence dies out as $Q$
-grows.  Conditional performance measures like these are especially
+Note that $\bar D_1$ uses the training sample estimators,
+$\hat\theta_{iR}$, and $\bar D_2$ uses the full sample estimators,
+$\hat\theta_{iT}$.  The forecaster has access to the information set
+$\mathcal{F}_T$ when deciding between the two forecasting models, but
+$\mathcal{F}_T$ does not contain $\bar D_2$.  So the forecaster should
+decide between them based on the conditional expectation, $\E_T
+\bar{D}_2$. If this quantity is positive, the first model is expected
+to perform worse in the future, and if it is negative the second is.
+
+This random variable, $\E_T \bar{D}_2$, is equal to the difference in
+the models' generalization error.  The generalization error of model
+$i$ equals
+\begin{equation*}
+  Q^{-1} \sum_{t=T+1}^{T+Q} \E_T L(y_{t+\h} - x_{it}'\hat{\theta}_{iT}),
+\end{equation*}
+which is the expected average loss associated the model's forecasts
+over the next $Q$ observations.\footnote{Note that the usual
+  definition of generalization error assumes that the observations are
+  independent and sets $Q$ equal to one.  See
+  \citet{elemstatlearning}, Chapter 7.}  Note that $\hat{\theta}_{iT}$ is known
+in period $T$, so the generalization error conditions on the observed
+coefficient estimates This performance measure is especially
 appropriate in areas like time-series economics where the forecaster
 knows the coefficient values when choosing a model, but would be less
-appropriate if the models will be re-estimated over an entirely new
+appropriate if the models will be reestimated over an entirely new
 dataset before forecasting.
@@
 functions $\lambda_i(\cdot)$ take a square-matrix argument and return
-its $i$th eigenvalue (with $\lambda_{i}(A) \leq \lambda_{i+1}(A)$ for
-any matrix $A$).
+its $i$th eigenvalue (with $\lambda_{i}(A) \leq \lambda_{i+1}(A)$).
 All limits are taken as $T \to \infty$ unless stated otherwise.
@@
 smoothness of the loss function and bounds the moments of the
-difference in the models' performance; the fourth assumption describes
-the behavior of the estimation and test windows.  The last assumption
-describes the kernel used to estimate the \oos\ average's asymptotic
-variance.
+difference in the models' performance; and the fourth assumption
+describes the behavior of the estimation and test windows.
 
@@
 underlying stochastic array.  We assume that the array is absolutely
-regular instead of strong mixing, which is more common in
-econometrics, because absolute regularity admits a particular coupling
-argument \citep{berbee_random_1979} that is unavailable for strong
-mixing sequences.
-
-Assumption \ref{asmp-2} rules out uninteresting cases where the
+regular instead of strong mixing, which is more common, because
+absolute regularity admits a particular coupling argument
+\citep{berbee_random_1979} that is unavailable for strong mixing
+sequences.
+
+Assumption \ref{asmp-2} rules out the uninteresting cases where the
 forecast error vanishes.
@@
   $\theta_2$, satisfy $|\theta_1|_2 = O(1)$ and $|\theta_2|_2 = O(1)$.
-  Moreover, there exist a $\delta > 0$ and finite $\Delta$ such that
-  \begin{equation*}
-    \lVert \lambda_{\max}(X_{iS_{T}}'X_{iS_{T}}) \rVert_{4+\delta}
-    \leq S_{T}\, \Delta \\
-    \lVert
-    \lambda_{\max}(X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})
-    \rVert_{4+\delta} \leq S_{T}\, \Delta \\
-    \lVert \lambda_{\max}((X_{iS_{T}}'X_{iS_{T}})^{-1}) \rVert_{4+\delta} \leq \Delta/S_{T} \\
-    \lVert
-    \lambda_{\max}((X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})^{-1})\rVert_{4+\delta}
-    \leq \Delta/S_{T}
-  \end{equation*}
-  for all $S_{T} \geq K_{2T}$ and large enough $T$, with $i =
-  1,2$,
+  Moreover, the largest eigenvalues of $X_{iS}'X_{iS}$ and
+  $X_{iS}'\ep{iS}\ep{iS}'X_{iS}$ and their inverses are of order $S$,
+  $S \geq K_2$, and have uniformly finite $2+\delta$ moments for
+  $\delta > 0$, with $i = 1,2$,
   \[ X_{iT} \equiv [x_{i1} \quad \dots \quad x_{i,T-\h}]' \]
@@
 coefficients ensure that the regression model doesn't dominate the
-variance of $y_{t+\h}$ in the limit.
+variance of $y_{t+\h}$ in the limit.  This assumption is compatible
+with a a model that has a few important regressors as well as a model
+that uses many weakly informative predictors.
 
 \begin{asmp}\label{asmp-3}
-  The loss function $L$ is continuous and has finite left and right
-  derivatives almost everywhere.  Also, $L(0) = 0$, and there is a
-  constant $B_L$ such that
-  \begin{equation*}
-    \|D_{R+j,R}\|_\rho \leq B_L \quad\text{and}\quad
-    \|D_{T+j,T}\|_\rho \leq B_L.
-  \end{equation*}
-  for all $j \geq 1$.
+  The loss function $L$ is convex, $L(0) = 0$, and there is a constant $B_L$ such that
+  \begin{equation*}
+    \|L(y_{t+\h} - x_{1t}'\bh{1R})\|_\rho \leq B_L \quad\text{and}\quad
+    \|L(y_{t+\h} - x_{2t}'\bh{2R})\|_\rho \leq B_L
+  \end{equation*}
+  for all $t$.  Moreover, $L$ is continuous and has finite left and
+  right derivatives everywhere.
 \end{asmp}
@@
 condition is weak and allows the loss function itself to be
-nondifferentiable; for example, absolute error and many asymmetric loss functions
-satisfy this assumption.
+nondifferentiable; absolute error and many asymmetric loss functions
+satisfy this assumption, for example.
 
@@
   \label{asmp-5} $W$ is a kernel from 
-$\Re$ to $[-1,1]$ such that $W(0) = 1$, $W(x) = W(-x)$ for all $x$,
-\begin{equation*}
-    \int_{-\infty}^{\infty} \lvert W(x) \rvert dx < \infty, \quad
-    \int_{-\infty}^{\infty} \lvert \psi(x) \rvert dx < \infty
-\end{equation*}
-with
-\begin{equation*} \psi(x) = \frac1{\sqrt{2\pi}} \int_{-\infty}^{\infty} W(z) e^{ixz}dz,
+$\Re$ to $[-1,1]$ such that $W(0) = 1$; $W(x) = W(-x)$ for all $x$;
+\begin{equation*}
+    \int_{-\infty}^{\infty} \lvert W(x) \rvert dx < \infty; \quad
+    \int_{-\infty}^{\infty} \lvert \psi(x) \rvert dx < \infty \quad\text{with}\quad
+    \psi(z) = \frac1{\sqrt{2\pi}} \int_{-\infty}^{\infty} W(x) e^{izx}dx;
 \end{equation*}
@@
 
-\section{Theoretical Results}\label{sec:theory}
+\section{Interval Construction}\label{sec:theory}
 The main result of the paper is Theorem
@@
 \ref{res-confidence-intervals}, we explain and present two key Lemmas
-used in its proof that add some insight into the nature of \oos\
-comparisons, and then show that standard \hac\ \oos\ estimators can be
-used to consistently estimate the asymptotic variance of the \oos\
-average.  We then show that the F-test does not let researchers test
-hypotheses about $E_{T} \bar D_2$ when the models are overfit.  In
-fact, in the limit it rejects a more-accurate but false benchmark
-model almost surely.
-
-\subsection{Behavior of DMW Test with Overfit}\label{sec:oostheory}
-Our first theorem justifies using the \dmw\ $t$-test with a a short
-test sample.
+in its proof.  These Lemmas add some insight into the nature of \oos\
+comparisons.
 
@@
   Consequently, each of the usual Gaussian confidence intervals,
-  \begin{eqnarray}
-  &&[\bar{D}_1 - z_{\alpha/2} \, \hat\sigma /
-      \sqrt{P}, \bar{D}_1 + z_{\alpha/2} \hat\sigma / \sqrt{P}],\label{interval-twosided} \\
-  &&[\bar{D}_1 - z_{\alpha} \, \hat\sigma / \sqrt{P}, +\infty), \label{interval-greater}
-  \end{eqnarray}
+  \begin{equation}
+  [\bar{D}_1 - z_{\alpha/2} \, \hat\sigma /
+      \sqrt{P}, \bar{D}_1 + z_{\alpha/2} \hat\sigma / \sqrt{P}], \\
+  [\bar{D}_1 - z_{\alpha} \, \hat\sigma / \sqrt{P}, +\infty), \label{interval-greater}
+  \end{equation}
   and
-  \begin{equation} (-\infty, \bar{D}_1 + z_{\alpha}
+  \begin{equation} (-\infty, \bar{D}_1 - z_{\alpha}
       \, \hat\sigma / \sqrt{P}],
@@
 \end{thm}
+
+This result allows forecasters to use \oos\ comparisons
+to conduct inference about the generalization error.  Since the \oos\
+average, $\bar D_1$, is asymptotically normal and centered on the
+expected future performance, $t$-tests constructed from the 
+\oos\ errors necessarily test hypotheses about $\E_T
+\bar{D}_2$.  If these tests are also valid tests for hypotheses about
+the performance of the pseudo-true models or the unconditional
+performance, it is
+only because those expected values are close to $\E_T \bar{D}_2$.  If
+the quantities are distinct, the tests are not informative or valid
+tests for the unconditional quantities.
+
 The requirement that $\sigma^2$ be uniformly a.s. positive is
-not restrictive under our asymptotic theory.  Since the models'
+nonrestrictive under our asymptotic theory.  Since the models'
 coefficients are estimated with uncertainty in the limit, the two
@@
 but comes from different asymptotics.
-
-This result allows forecasters to use the \dmw\ test to conduct
-inference about the models' accuracy.  Since the \oos\ average,
-$\bar D_1$, is asymptotically normal and centered on the expected
-future performance, $t$-tests constructed from the \oos\ errors
-necessarily test hypotheses about $\E_T \bar{D}_2$ and not the
-performance of the pseudo-true models or the unconditional
-performance of the models.
-
-The application to testing can be expressed as a corollary:
-\begin{cor}\label{res:oostest}
-Suppose that the conditions of Theorem \ref{res-confidence-intervals}
-hold.  Then
-\begin{equation}
-  \Pr[\sqrt{P}\bar D_{1}/\hat\sigma \geq z_{\alpha} \mid \E_{T}
-  \bar{D}_{2} \leq 0] \to^p \alpha.
-\end{equation}
-\end{cor}
 
@@
 The first Lemma first shows that the process $\{D_{tR} - \E_R \bar
-D_1\}$ is an $L_2$-mixingale of size $-1/2$ that satisfies a \clt,
-ensuring~\eqref{normalpart}.  The second shows that~\eqref{coefpart}
-holds under Assumption~\ref{asmp-4}.
+D_1\}$ is an $L_2$-mixingale of size $-1/2$ that satisfies a \clt.
+The second shows that~\eqref{coefpart} holds.
 
 \begin{lem}\label{res-mixingale}
-  Part 1: If Assumptions~\ref{asmp-1}--\ref{asmp-3} hold then the inequality
+  \begin{description}
+  \item[Part a.]   If Assumptions~\ref{asmp-1}--\ref{asmp-3} hold then the inequalities 
   \begin{equation}\label{mixingaleR}
@@
   \end{equation}
-  with $\zeta_l = O(l^{-\frac12 - \delta})$ holds for some positive
-  $\delta$, any positive $j$, and any $l$ between 0 and $j$.  As a
-  consequence, $\{D_{t,R} - \E_R D_{t,R}, \mathcal F_t\}$ is an
-  $L_2$-mixingales of size $-1/2$.
-
-  \noindent Part
-  2: Moreover,~\eqref{normalpart} holds under
-  Assumptions~\ref{asmp-1}--\ref{asmp-3} if $P \to \infty$ as $T \to
-  \infty$ and $\sigma^2$ is a.s. uniformly positive.
+  and
+  \begin{equation}\label{mixingaleT}
+    \lVert \E_{T+j-l}(D_{T+j,T} - \E_T D_{T+j,T}) \rVert_2 \leq  \couplingConstant \;
+    \zeta_l
+  \end{equation}
+  hold for some positive $\delta$, any positive $j$, and any $l$
+  between 0 and $j$ with $\zeta_l = O(l^{-\frac12 - \delta})$.  As a
+  consequence, $\{D_{t,R} - \E_R D_{t,R}, \mathcal F_t\}$ and
+  $\{D_{t,T} - \E_R D_{t,T}, \mathcal F_t\}$ are $L_2$-mixingales of
+  size $-1/2$.
+  \item[Part b.] Moreover,~\eqref{normalpart} holds under
+    Assumptions~\ref{asmp-1}--\ref{asmp-3} if $P \to \infty$ as $T
+    \to \infty$ and $\sigma^2$ is a.s. uniformly positive.
+  \end{description}
 \end{lem}
 
-Mixingales satisfies a weak-dependence condition similar to \mds es
-and were introduced and studied extensively by
+A Mixingale satisfies a weak-dependence condition similar to a \mds\ and
+these processes have been studied extensively by
 \citet{mcleish_dependent_1974,mcleish_invariance_1975,mcleish_maximal_1975,mcleish_invariance_1977}.
 This lemma shows that the estimation uncertainty introduces dependence
-into the \oos\ forecast errors, but that additional dependence is
-contained in the term $\E_R \bar D_1$ and can be effectively removed
-by subtraction.  The second part of the Lemma shows that the basic
-mixingale \clt\ established by \citet{de_jong_central_1997} applies in
-this setting.\footnote{De Jong proves two \clt s: one for mixingales
-  and one for \ned\ functions of mixing processes.  His mixingale
-  result makes assumptions about the behavior of the sample second
-  moment that arise as consequences of \ned.  The proof of
-  Lemma~\ref{res-mixingale} shows that the arguments used for de
-  Jong's \ned\ \clt\ continue to hold for our \oos\ process---in
-  effect, that the \oos\ process has slightly more structure than
-  required for it to be a mixingale.}
+into the \oos\ forecast errors, but that dependence is contained in
+the term $\E_R \bar D_1$ and can be effectively removed by
+subtraction.  The second part of the Lemma shows that the basic
+Mixingale \clt\ established by \citet{de_jong_central_1997} applies in
+this setting.\footnote{De Jong proves two \clt s: one for Mixingales
+  and one for \ned\ functions of mixing processes.  His Mixingale
+  result makes stronger assumptions about the behavior of the sample
+  second moment.  The proof of Lemma~\ref{res-mixingale} shows that
+  the arguments used for de Jong's \ned\ \clt\ continue to hold for
+  our \oos\ process.}
 
@@
 \begin{equation*}
-  \E_T \bar{D}_2 - \E_R \bar D_1 =  O_p(\sqrt{P/T}) +
+  \E_T \bar{D}_2 - \E_R \bar D_1 =  O_p(\sqrt{\frac PT}) +
   o_p(P^{-\frac12}) + o_p(Q^{-\frac12}).
@@
 
-The justification for Lemma~\ref{res-convergence} is intuitive.  In
-the limit, the difference between $\E_T \bar{D}_2$ and $\E_R \bar D_1$
-comes from the coefficient estimators used: $\E_T\bar{D}_2$ is the
-expected performance using the full-sample estimate, $\hat{\theta}_T$,
-and $\E_R \bar D_1$ is the performance using the period-$R$ estimate,
+The main steps of the argument are intuitive.  In the limit, the
+difference between $\E_T \bar{D}_2$ and $\E_R \bar D_1$ comes from the
+coefficient estimators used; $\E_T\bar{D}_2$ is the expected
+performance using the full-sample estimate, $\hat{\theta}_T$, and
+$\E_R \bar D_1$ is the performance using the period-$R$ estimate,
 $\hat{\theta}_R$.  When $P$ and $Q$ are large, the dependence between
 the test and training samples vanishes, so the estimators of $\theta$
-are the only variables affected by the conditioning $\sigma$-fields,
+are the only variables affected by the conditioning $\sigma$-fields
 $\mathcal{F}_R$ and $\mathcal{F}_T$.  Since $L$ is smooth, the
@@
 variance estimators are consistent.\footnote{As with
-      Lemma~\ref{res-mixingale}, the proof of this lemma takes
+      Lemma~\ref{res-mixingale}, the proof of this Lemma takes
       \citepos{de_jong_consistency_2000} existing consistency results
       for \ned\ processes and shows that the same arguments can be
-      applied to our \oos\ mixingale.}
+      applied to our \oos\ Mixingale.}
 
@@
   \label{res-variance-estimator}  Suppose Assumptions \ref{asmp-1},
-  \ref{asmp-2}, \ref{asmp-3}, and \ref{asmp-5} hold, that $\gamma, P$
-  and $R \to \infty$ as $T \to \infty$, and that $\gamma = o(P)$.  Then
+  \ref{asmp-2}, \ref{asmp-3}, and \ref{asmp-5} hold, that $\gamma$ and $P
+  \to \infty$ as $T \to \infty$, and that $\gamma = o(P)$.  Then
   \begin{equation*}
@@
 
-\subsection{Failure of In-Sample Tests}\label{sec:insample}
-This subsection establishes that the F-test can over-reject when the
-benchmark is more accurate than the alternative.  We use stronger
-assumptions than before, i.i.d. data, normal errors, \mse\ loss, and
-nested models to ensure that the F-test performs as well as possible.
-Indeed, we know its exact distribution.  But the basic idea of this
-argument is much more general and should apply to other related tests,
-including \oos\ tests.
-
-\begin{thm}\label{res:ftest}
-  Let $\h = 1$ and suppose that $x_{1t}$ and $x_{2t}$ are
-  deterministic vectors such that $x_{2t} = (x_{1t}, z_t)$ and
-\[
-T^{-1} \sum_{t=1}^T x_{2t} x_{2t}'  = Q^{-1} \sum_{t=T+1}^{T+Q} x_{2t} x_{2t}' =
-I.
-\]
-Also, suppose that $\theta_2 = (\theta_1, \psi)$, 
-$\varepsilon_{2,t+1} \sim i.i.d.\ N(0,\tau^2)$,
-$|\theta_1|_2 = \phi_1$, $|\psi|_2 = \phi_2$, $K_1/T = c_1 > 0$,
-$K_2/T = c_2 > 0$, and $K_2 \geq 2$, and let $F$ be the F-statistic
-for the test of the null hypothesis that $\psi = 0.$
-Then 
-\begin{equation}\label{eq:ftestreject1}
-  \Pr[F \geq q_{K_2 - K_1, T - K_2}(1-\alpha) \mid E_T \bar{D}_2 \leq 0
-  ] \to 1\mbox{ as $\phi_2 \to \infty$ ($T$ fixed)}
-\end{equation}
-and if $\phi_2 \geq \tau \sqrt{c_2 - c_1}$, then
-\begin{equation}\label{eq:ftestreject2}
-  \Pr[F \geq q_{K_2 - K_1, T - K_2}(1-\alpha) \mid E_T \bar{D}_2 \leq 0
-  ] \to 1 \text{ as $T \to \infty$},
-\end{equation}
-where $q_{K_2-K_1, T-K_2}(1-\alpha)$ is the
-$(1-\alpha)$-quantile of the $F_{K_2-K_1, T-K_2}$ distribution.
-\end{thm}
-The conditions on the regressors simplify the proof but can be
-relaxed.  As in Corollary~\ref{res:oostest}, the event that we are
-conditioning on in~\eqref{eq:ftestreject1} and~\eqref{eq:ftestreject2}
-is the event that the benchmark model is expected to be more accurate
-in the future.  Since the probability of this event converges to zero
-as $\phi_2 \to \infty$, \eqref{eq:ftestreject1} is not an immediate
-consequence of the power of the F-test increasing with $\phi_2$.
-
-The first result,~\eqref{eq:ftestreject1}, can be understood through the case $K_2 = 2$ and
-$K_1 = 0$, so
-\begin{equation*}
-  E_T \bar D_2 = \psi_1^2 + \psi_2^2 - (\hat{\psi}_1 - \psi_1)^2 - (\hat\psi_2 - \psi_2)^2,
-\end{equation*}
-where $\hat{\psi}$ is the \ols\ estimator.  Under these conditions,
-the F-test rejects if $\hat{\psi}'\hat{\psi}$ lies outside the circle
-centered at the origin with radius $\hat{\tau} (c_2 - c_1)^{0.5}
-q_{K_2-K_1, T-K_2}^{0.5}(1-\alpha)$, and $E_T \bar{D}_2 \leq 0$ holds
-for $\hat\psi$ on or outside a circle centered at $\psi$ passing
-through the origin; $\hat{\tau}^2$ is the usual estimator of $\tau^2$.
-Figure~\ref{fig:rreject} depicts these regions.  Since the \ols\
-estimator $\hat\psi$ is normal with mean $\psi$, the probability that
-$\hat{\psi}$ falls in the acceptance region given $E_T \bar{D}_2 \leq
-0$ vanishes as $\phi_2 \to \infty$, even though the full model will
-give worse forecasts than the restricted model.
-
-\newcommand{\circlefigA}[4]{
-  \begin{tikzpicture}
-    \fill[lightgray] (-#3,-#3) rectangle (#4,#4);
-    % rejection region for F-test
-    \filldraw[fill=white,draw=black] (0,0) circle (#1);
-    % circle of equal generalization error
-    \filldraw[fill=white,draw=black] (1,1) let \p1=(1,1) in circle({veclen(\x1,\y1)});
-    \draw (1,1) let \p1=(1,1) in circle({veclen(\x1,\y1)});
-    \fill [black] (1,1) circle (2pt) node[right] {$(\psi_1,\psi_2)$};
-    \draw (0,0) circle (#1);
-    \draw (1,1)--(0,0);
-    % axes
-    \draw[->] (0,0)--(#2,0) node[right] {$\hat\psi_1$};
-    \draw[->] (0,0)--(0,#2) node[above] {$\hat\psi_2$};
-  \end{tikzpicture}
-}
-\newcommand{\circlefigB}[4]{
-  \begin{tikzpicture}
-    \fill[white] (-#3,-#3) rectangle (#4,#4);
-    % rejection region for F-test
-    \fill[lightgray] (0,0) circle (#1);
-    % circle of equal generalization error
-    \fill[white] (1,1) let \p1=(1,1) in circle({veclen(\x1,\y1)});
-    \draw (0,0) circle (#1);
-    \draw (1,1) let \p1=(1,1) in circle({veclen(\x1,\y1)});
-    \fill [black] (1,1) circle (2pt) node[right] {$(\psi_1,\psi_2)$};
-    \draw (1,1)--(0,0);
-    % axes
-    \draw[->] (0,0)--(#2,0) node[right] {$\hat\psi_1$};
-    \draw[->] (0,0)--(0,#2) node[above] {$\hat\psi_2$};
-  \end{tikzpicture}
-}
-
-\begin{figure}
-  \centering
-  \begin{tabular}{cc}
-  \subfloat[]{\circlefigA{1}{2.5}{1.4}{3.2}\label{fig:circleA}} &
-  \subfloat[]{\circlefigB{1}{2.5}{1.4}{3.2}\label{fig:circleB}}  \\
-  \subfloat[]{\circlefigA{.3}{2.5}{1.4}{3.2}\label{fig:circleC}}  &
-  \subfloat[]{\circlefigB{.3}{2.5}{1.4}{3.2}\label{fig:circleD}} 
-  \end{tabular}
-  \caption{Graphs indicating the rejection region and region of equal
-    generalization error for the models discussed in Section
-    \ref{sec:insample}.  The smaller model has no estimated parameters
-    and the larger has two coefficients.  The shaded regions in
-    Figures (a) and (b) show the rejection region and the acceptance
-    region respectively of the F-test given $E_T \bar D_2 \leq 0$ when
-    the true elements of $\psi$ are moderately small.  Figures (c) and (d)
-    show the same regions when the true $\psi$ is large.}
-\label{fig:rreject}
-\end{figure}
-
-The second part of Theorem \ref{res:ftest},~\eqref{eq:ftestreject2},
-is more interesting and implies that the F-test rejects the benchmark
-too often for forecasting whenever we have an overfit model (unless,
-of course, $\psi = 0$).  The intuition is similar to the previous
-case.  As $K_2$ increases, the volume that $\hat{\psi}$ can occupy
-increases as well.  So the probability that $\hat{\psi}$ is close to
-the origin and therefore inside the acceptance region of the F-test
-decreases.  In the limit, the probability that $\hat{\psi}$ is outside
-the acceptance region is one.\footnote{If $\phi_2 \geq \tau \sqrt{c_2
-    - c_1}$ does not hold, then $\psi$ lies inside the acceptance
-  region of the F-test for large enough $T$.  In that case, the
-  rejection probability does not converge to one, but will converge to
-  a probability greater than $\alpha$.}
-
-It is important to remember that the F-test is valid for the null
-$\psi = 0$ in this analysis.  However, the F-test is poorly suited for
-choosing an accurate forecasting model, and performs worse when the
-larger model is overfit or explains more of the variation of the
-dependent variable.  Other valid unbiased tests of the null hypothesis
-that $\psi = 0$ will suffer the same problem.
-
-\section{Monte Carlo}\label{sec:mc}
-\newcommand{\thetanorm}{\ensuremath{\lvert \theta \rvert_2}} This
-section presents two simulations that investigate the accuracy of our
-theory in small samples.\footnote{Simulations were conducted in R
-  \citep{rproject} using the Lattice \citep{lattice} and RSQLite
-  \citep{rsqlite} packages for graphics and data management
-  respectively.}  The first looks at the asymptotic normality of the
-\dmw\ statistic centered on either $E_R \bar D_1$ or $E_T \bar D_2$.
-The previous section's results imply that centering on the first
-should give an approximately normal statistic and centering on the
-second should give a normal statistic when $P$ is small relative to
-$T$.  The second simulation looks at the size and power of several
-statistics when conducting inference about the difference in the
-models' generalization error.
-
-\subsection{Setup}\label{sec:simulation-design}
-The Monte Carlo experiment is intentionally very simple so that we can
-isolate the influence of the models' complexity.  In particular, we do
-not include some features that are common in forecasting
-environments---serial dependence, heteroskedasticity, and complicated
-\dgp s.  We simulate data for both studies from the equation
-\begin{equation}\label{eq:6}
-  y_t = x_t'\theta + \varepsilon_t,\quad \varepsilon_t \sim N(0,1),
-  \quad t=1,\dots,T.
-\end{equation}
-The first element of $x_t$ is 1 and the remaining $K_2-1$ elements are
-independent Standard Normal.  The benchmark model is
-\begin{equation}
-  \label{eq:1}
-  y_{1t} = \sum_{j=1}^{K_1} x_{jt}\theta_j + \varepsilon_t
-\end{equation}
-and the alternative model is the \dgp\ \eqref{eq:6}.  We let
-$(K_1,K_2)$ equal either $(2,3)$ or $(T/20,T/10)$ to study our theory
-in its intended application as well as for more parsimonious models.
-We let $T$ equal 100, 250, 500, or 1000.  We also vary $\theta$, and do 
-so giving the benchmark and the alternative model comparable weight in
-predicting $y_t$.  Specifically, we set
-\begin{equation*}
-  \theta_j = 
-\begin{cases} \frac{c}{\sqrt{K_1}} & j = 1,\dots,K_1 \\
-\frac{c}{\sqrt{K_2 - K_1}} & j = K_1 + 1,\dots,K_2 \end{cases}  
-\end{equation*}
-with $c=0$ or 1.  When $c$ is large, we're more likely to draw
-values of $X$ and $Y$ that make the estimated larger model more
-accurate than the benchmark, and when $c$ is zero we're unlikely to
-draw such values of $X$ and $Y$.  For all of the studies, $L(x) =
-x^2$.
-
-The first set of simulations study how well the theory in
-Section~\ref{sec:oostheory} works in practice.  For each draw of $X$
-and $Y$, we construct a one-sided and two-sided \oos\ interval of the
-form
-\begin{equation*}
-  [ \bar D_1 - 1.28 \hat{\sigma}, \infty) \quad\text{and}\quad
-  [ \bar D_1 - 1.64 \hat{\sigma}, \bar D_1 + 1.64\ \hat{\sigma}], \\
-  \hat\sigma^2 = \frac1P \sum_{t=R+1}^T (D_t - \bar D_{1})^{2}
-\end{equation*}
-for $P$ set to every 10th value between $T$ and $\frac{2T}{3}$.  We
-calculate the percentage of these intervals that contain $E_R \bar
-D_1$ and that contain $E_T \bar D_2$.  Since the data are i.i.d.,
-both of these quantities are easy to calculate:
-\begin{equation*}
-  E_R \bar D_1 = [\sum_{i=1}^{K_1} (\tilde{\theta}_{iR} - \theta_i)^2 +
-  \sum_{i=K_1+1}^{K_2}\theta_i^2] - \sum_{i=1}^{K_2} (\hat{\theta}_{iR} -
-  \theta_i)^2
-\end{equation*}
+\section{Failure of In-Sample Tests}\label{sec:insample}
+This section elaborates on the failure of standard full-sample tests
+to test hypotheses about the models' generalization error.  We look at
+the F-test with i.i.d. data, normal errors, and \mse\ loss, but the
+basic idea of this argument is much more general and applies to other
+tests of the null hypothesis that $\theta_2 = 0$, including \oos\
+tests.  We show that the F-test often overrejects for the hypothesis
+$E_T \bar D_2 \leq 0$.  In contrast to \citet{hansen_in-sample_2009},
+we show that the F-test is valid when the smaller model is the true
+\dgp, but overrejects as either the norm of the additional
+coefficients grows or the number of dimensions grow.
+
+Suppose we have two competing nested models,
+\[ y_{t+1} = x_{1t}'\theta_1 + \varepsilon_{1t} \\
+y_{t+1} = x_{1t}'\theta_1 + x_{2t}'\theta_2 + \varepsilon_{2t}\] with
+$\varepsilon_{2t} \sim N(0,\tau^2)$, $|\theta_1|_2 = \phi_1$,
+$|\theta_2|_2 = \phi_2$, $K_1/T = c_1$, $K_2/T = c_2$, and $K_2 \geq
+2$.  Moreover, suppose that $x_t$ is deterministic and 
+\[
+T^{-1} \sum_{t=1}^T x_t x_t'  = Q^{-1} \sum_{t=T+1}^{T+Q} x_t x_t' =
+I.\footnote{Allowing stocahstic $x_t$ complicates the presentation
+  without adding any new insight.}
+\]
+Let $\tilde{\theta}_1$ be the \ols\ estimate of $\theta_1$ in the
+first model, $\hat{\theta} = (\hat{\theta}_1', \hat{\theta}_2')'$ be
+the \ols\ estimate of $(\theta_1',\theta_2')'$ in the second, and
+define $\tilde{\theta} = (\tilde{\theta}',0,\dots,0)'$ as the implied
+estimate of the second model's coefficients using the first.  Since
+the regressors are orthogonal, $\tilde{\theta}_1 = \hat{\theta}_1$
+a.s.
+
+We can calculate the difference in generalization error between the
+two models easily:
+\[
+E_T \bar D_2 = Q^{-1} \sum_{T+1}^{T+Q}
+(\tilde{\theta}-\theta)' x_tx_t' (\tilde{\theta}-\theta)
+= |\hat{\theta} - \theta |_2^2 - |\tilde{\theta} - \theta |_2^2.
+\]
+For any $\hat{\theta}_1$, this quantity equals zero when
+$\hat{\theta}_2$ lies on the surface of the hypersphere centered at
+$\theta_2$ with radius $|\theta_2|_2$ and is greater
+than zero when $\hat{\theta}_2$ lies outside that hypersphere.
+
+Now consider using the F-test to pick one of these models for
+forecasting.  Under the null hypothesis that $\theta_2 = 0$, the
+F-test statistic has the $F(K_2, T-K)$ distribution exactly, since the
+errors are normal.  Consequently, given $\hat{\sigma}^2$, the
+rejection region in $\Re^{K_2}$ for the F-test at confidence $\alpha$
+is the set of values of $\hat{\theta}_2$ on or beyond the sphere
+\[
+\hat{\theta}_2'\hat{\theta}_2 = \frac{\hat{\sigma}^2 c_{\alpha} K_2}{T},
+\]
+where $c_{\alpha}$ is the $\alpha$-quantile of the $F(K_2,T-K)$
+distribution.
+
+Figures \ref{fig:circleO}--~\ref{fig:circleC} plot both of regions
+spheres for $K_2 = 2$ and different values of $\theta_2$.  As
+$|\theta_2|_2$ grows, the region where the second model has lower
+generalization error occupies more of the test's rejection region.  Of
+course, we're interested in the conditional probablity
+\[P[\text{reject benchmark} \mid E_T \bar D_2 \leq 0] =
+P[\hat{\theta}_2'\hat{\theta}_2 \geq \hat{\sigma}^2 c_{\alpha} K/T
+\mid |\hat{\theta}_2 - \theta_2| \geq |\theta_2|].\] It is clear that,
+as $|\theta_2|_2 \to 0$, this probability converges almost surely to
+$\alpha$, the unconditional probability of rejection for $\theta_2 =
+0$.
+
+We can get a lower bound on this probability by rewriting the
+estimates in polar coordinates.  Let
+\[\hat{r} = |\hat{\theta}_2 - \theta_2|_2 \\
+\hat{\psi}_{K_2-1} = 'tan^{-1}(\frac{ \hat{\theta}_K - \theta_K }{
+  \hat{\theta}_{K-1}- \theta_{K-1} }) \\
+\hat{\psi}_{i} = 'tan^{-1}(\frac{(\sum_{j=K_1+i+1}^{K}(\hat{\theta}_j -
+    \theta_j)^2)^{\frac12}}{\hat{\theta}_{K_1+i} - \theta_{K_1+i}}), \quad i=1,\dots,K_2-2.
+\]
+Under this coordinate system, if $\theta_2$ lies outside the
+acceptance region of the F-test, that acceptance region is
+contained in the cone 
+\[\{(r, \psi_1,\dots,\psi_{K_2-1}) : r \geq 0, \\ 
+\psi_{K_2-1} \in [\tilde{\psi}_{K_2-1} - \gamma, 
+\tilde{\psi}_{K_2-1} + \gamma], \\ 
+\psi_i \in [\tilde{\psi}_i - \gamma, \tilde{\psi}_i + \gamma] \ \text{for } i = 1,\dots,K_2-2
+\}\]
+ with
+ \[
+\tilde{\psi}_i = 'tan^{-1}([\sum_{j=i+1}^{K_2}
+  (\theta_j/\theta_i)^2]^{\frac12}) \ \text{for } i = 1,\dots,K_2-2,\\
+\tilde{\psi}_{K_2-1} = 'tan^{-1}(\theta_K/\theta_{K-1})
+\]
 and
-\begin{equation*}
-  E_T \bar D_2 = [\sum_{i=1}^{K_1} (\tilde{\theta}_{iT} - \theta_i)^2 +
-  \sum_{i=K_1+1}^{K_2}\theta_i^2] - \sum_{i=1}^{K_2} (\hat{\theta}_{iT} -
-  \theta_i)^2
-\end{equation*}
-where $\tilde{\theta}$ indicates that the coefficient is estimated
-using only the regressors in the benchmark model and $\hat{\theta}$
-the full model.  We draw 2000 samples for each choice of the design
-parameters.
-
-The second simulation looks at the size and power of the test
-statistics when conducting inference about the models' generalization
-error.  The null hypothesis we test is 
-\begin{equation}\label{eq:9}
-  H_0:\quad E_T \bar D_2 \leq 0,
-\end{equation}
-We look at four different statistics---the full-sample F-test, the
-\dmw\ $t$-test, the
-\oos\ $t$-test using McCracken's (2007)
-critical values,\footnote{These critical values are not published for
-  $K_2-K_1>10$, so we do not report them for $K_2 = T/10$.}
-and Clark and West's (2006, 2007) Gaussian out-of-sample
-statistic.\footnote{Clark and West (2006, 2007) derive their statistic
-using the rolling window estimation scheme.  Here we use the same
-statistic, but with a fixed window scheme.}
-For the F-test, we simply test whether the coefficients on the larger
-model are nonzero.  For the out-of-sample tests, we conduct a
-one-sided test of out-of-sample performance for every 10th value of
-$P$ as before.
-
-To estimate each test's size for the hypothesis \eqref{eq:9}, we draw
-samples from the \dgp\ and discard those for which \eqref{eq:9} does
-not hold, until we have 2000 for each choice of the design parameters.
-The estimated size is the fraction of those samples in which the test
-statistic rejects.
-\subsection{Results}
-We'll discuss results for the confidence intervals first.
-Figures~\ref{fig:interval-R} and~\ref{fig:interval-T} show the
-coverage probability of these intervals as a function of $P$ for each
-combination of $T$, $K_1$ and $K_2$, and $c$.  The gray horizontal
-line shows the intervals' nominal coverage probability.  Each panel
-displays the coverage for a different choice of interval, centering
-term ($E_R \bar D_1$ or $E_T \bar D_2$) and combination of design
-parameters.
-
-Figure~\ref{fig:interval-R} gives the results for $E_R \bar D_1$.  For
-both the one and two-sided intervals, the actual coverage is very
-close to the nominal coverage except when $P$ is small.  The poor
-behavior for small $P$ is unsurprising, as it simply means that the
-\clt\ is a poor approximation when the test sample is small.  The
-intervals' good coverage holds even for the parsimonious models
-($K_1=1$ and $K_2= 3$) which our theory does not necessarily apply to.
-
-Figure~\ref{fig:interval-T} gives the results for $E_T \bar D_2$.  In
-rows 2, 4, 6, and 8, the overfit models, the coverage is near nominal
-coverage for moderately small values of $P$.  As $P$ increases to $2T/3$, the
-coverage either increases to 1 (for the one-sided interval) or fall to
-zero (the two-sided).  With the parsimonious model, the coverage is near
-nominal coverage for all $P$ for the one-sided interval with $c=1$,
-but only for moderately small $P$ for the two-sided interval or when
-$c=0$.
-
-The behavior for $K_2 = T/10$ is exactly what our theory predicts.
-When $P^2/T$ is small, the coverage is near nominal levels.  The
-behavior as $P$ increases, combined with the results for $E_R
-\bar{D}_1$, indicate that $E_T \bar D_2 \geq E_R \bar D_1$ in general.
-Since
-\[E_{T} \bar D_2 = E_{R} \bar D_1 + (E_{T} \bar D_2 - E_{R} \bar
-D_1), \] and the interval is approximately centered at $E_R \bar D_1$,
-the difference $E_{T} \bar D_2 - E_{R} \bar D_1$ adds a substantial
-positive quantity when $P^2/T$ is not near zero, increasing the
-coverage of the one-sided interval but taking $E_T \bar D_2$ outside
-the two-sided interval.
-
-We next present the size simulations,
-Figures~\ref{fig:ftest}--\ref{fig:ttest-power}.  For the \oos\ tests,
-the conditional rejection probability is plotted for each combination
-of $T$, $K_1$, $K_2$, and $c$ as a function of $P$.  The F-test does
-not depend on $P$, so a single value is presented for each
-combination.
-
-We'll look at the F-test first.  To make comparisons easier, the size
-is displayed as a dot plot in Figure~\ref{fig:ftest}.  Different
-panels display a different combination of $K_1$, $K_2$, and $T$, and
-each individual plot shows the empirical size for each choice of $c$.
-We see immediately that the actual and nominal size are essentially
-equal for $c = 0$, which is unsurprising.  For $c = 0$, the F-test is
-exact; moreover, the larger model will almost always be less accurate
-than the smaller one, so conditioning on $\E_T \bar{D}_2 \leq 0$ is
-almost unrestrictive.  When $c$ increases, though, the F-test
-over-rejects badly---rejecting at roughly 50\% when $c = 1$ for the
-parsimonious model and from 70\% to 100\% for the overfit model.  As
-our discussion in Section~\ref{sec:insample} predicts, the rejection
-probability increases with $T$ for the overfit model but does not
-depend on $T$ for the small model.
-
-Figure~\ref{fig:ttest-size} presents the size estimates for the \dmw\
-$t$-test.  Again, different panels display results for different
-combinations of the design parameters.  Each graph plots the rejection
-probability against $P/T$.  For $K/T=10$, the rejection probability
-falls as $P/T$ increases, from near nominal size when $P/T$ is small
-to zero when $P/T$ is near $2/3$.  Moreover, the rejection probability
-falls faster when $T$ is large, as our theory predicts.  When $K=3$,
-the rejection probability stays closer to nominal size, but falls with
-$P/T$ for $c=0$, under-rejecting by about 5pp when $P/T = 2/3$, and
-rises with $P/T$ for $c=1$, over-rejecting by about 10pp when
-$P/T=2/3$.  For small $P$, the rejection probability is near 10\% for
-all simulations (the farthest is $K=T/10$, $c=0$, where the rejection
-probability is about 5\%; the other simulations are much closer).
-
-We observe the following patterns.  The
-\dmw\ test has close to nominal size when $P$ is small for every
-combination of design parameters.  In most cases, the rejection
-probability decreases as $P/T$ increases---the exception is for $K_2 =
-3$ and $c=1$.  For the large-$K$ simulations, the rejection
-probability drops to zero for most of the simulations as $P/T$
-increases.  The rejection probability increases with $c$, but the
-rejection probability still is near nominal probability for small $P$
-with $c=1$.
-
-Clark and West's (2006, 2007) statistic, presented in
-Figure~\ref{fig:clarkwest}, behaves quite differently.  For $c=0$ the
-test is correctly sized for both the overfit and parsimonious studies,
-as we saw for the F-test.  When $c=1$, the rejection probability
-increases rapidly with $P/T$.  For $K_2=3$, the rejection probability
-is near 10\% when $P$ is small but about 40\% when $P/T = 2/3$.  For
-$K=T/10$, the rejection probability is even higher and increases with
-$T$ as well, from a maximum over 50\% when $T=100$ to a maximum of
-nearly 100\% when $T=1000$.
-
-Results using \citepos{mccracken_asymptotics_2007} critical values are
-presented in Figure~\ref{fig:mccracken} and are similar to those using
-Clark and West's test.  For $c=0$ the rejection probability is nearly
-the test's nominal size.  For $c=1$, the rejection probability
-increases with $P/T$, from close to the nominal size when $P/T$ is
-small to over 25\% when $P/T = 2/3$.  Note that all of the simulations
-use the parsimonious model.  McCracken's statistic over-rejects here
-by slightly less than Clark and West's, but still by a substantial
-amount.
-
-Since the \dmw\ test tends to have low rejection probability, the
-test's power is a concern.  We'll present some power results,
-simulating from \eqref{eq:1} with $c = 1$ or 2 subject to the
-constraint that $E_T \bar D_2 > 0$.\footnote{Draws of $X$ and $Y$ with
-  $E_T \bar D_2 > 0$ are very rare when $c=0$, so we do not present
-  results for that value of $c$.}  Figure~\ref{fig:ttest-power} plots
-the power for the \dmw\ test; since the other test statistics greatly
-over-reject, we do not present their power.  For $c=1$, the power is
-never greater than nominal size and decreases to zero as $P/T$
-increases for the overfit model.  For $c=2$ the power is better,
-increasing with $P/T$ for a stretch and then decreasing as $P/T$ grows
-beyond approximately 1/4 for the overfit model.  Larger values of $T$
-give a higher peak and greater power overall, but the power still
-falls to nearly zero if $P/T$ is too large (approximately 2/3 in our
-simulations).  The power with the parsimonious model is typically
-quite low but greater than nominal size for $c = 2$.
-
-Both sets of simulations support our theoretical results.  The first
-simulation confirms that the \dmw\ \oos\ $t$-test is centered at $E_R
-\bar D_1$ for all choices of $P$ and $R$ and is centered on $E_T \bar
-D_2$ only when $P$ is small.  The second simulation confirms that the
-\dmw\ test has correct size for the null hypothesis that $E_T \bar D_2
-\leq 0$ when $P$ is small and that tests designed to test whether the
-benchmark is true, like the F-test and Clark and West's (2006, 2007)
-and McCracken's (2007) \oos\ tests can reject by much more than their
-nominal size when testing the null $E_T \bar D_2 \leq 0$.
-Moreover, these simulations demonstrate that the restriction $P^2/T
-\to 0$ is binding in practice, as the \dmw\ test under-rejects and has
-very low power when it is not satisfied.
+\[
+ \gamma = 'sin^{-1}(\frac{\hat{\sigma}}{|\theta_2|_2}\sqrt{\frac{c_{\alpha} K_2}{T}})
+\] 
+for given $\hat{\sigma}^2$.\footnote{This setup assumes that $\psi_i
+   \in [-\pi/2,\pi/2], i = 1,\dots,K_2-2$ and $\psi_{K_2-1} \in
+   [0,2\pi]$.  If that doesn't hold, the region can be reallocated to
+   different coordinates without changing it's shape.}
+
+As a result,
+\[
+P[\hat{\theta}_2'\hat{\theta}_2 \geq \hat \sigma^2 c_{\alpha} K_2/T
+\mid |\hat{\theta}_2-\theta_2|_2 \geq |\theta_2|_2] \\
+\geq 1 - \E(P[\hat{\psi}_i\in[\tilde{\psi}_i - \gamma, \tilde{\psi}_i +
+\gamma]\text{ for all } i \mid \hat{\sigma}^2,
+|\hat{\theta}_2-\theta_2|_2 \geq |\theta_2|_2]
+|\hat{\theta}_2-\theta_2|_2 \geq |\theta_2|_2)\quad a.s. \\ 
+= 1 - \frac12 E ((\frac{2\gamma}{\pi})^{K_2-1}\mid
+|\hat{\theta}_2-\theta_2|_2 \geq |\theta_2|_2)\quad a.s. \\
+= 1 - \frac12 E (\frac{2\gamma}{\pi})^{K_2-1} \quad a.s..
+\]
+The last equality holds because
+$\hat{\sigma}_2$ is independent of $\hat{\theta}_2$ under normality.
+
+This lower bound lets us consider what happens as $|\theta_2|_2 \to
+\infty$ and as $T \to \infty$ separately.  As $|\theta_2|_2 \to
+\infty$, $\gamma\to0$ almost surely, and the lower bound on the
+conditional probability of rejection converges to 1.  When
+$|\theta_2|_2$ is large enough, the F-test always rejects, even when
+the larger model is less accurate than the benchmark.\footnote{Of
+  course, as $|\theta_2|_2 \to \infty$, the probability that the
+  benchmark is more accurate vanishes as well.  But that is irrelevant
+  for the analysis we are doing here, and it is irrelevant for
+  controlling type I error when testing hypotheses about the models'
+  generalization error.}  Intuitively, the values of $\hat{\theta}_2$
+that give bad forecasts (ie at least as bad as setting
+$\hat{\theta}_2=0$) will be far from $\theta_2$ in any direction.  If
+$|\theta_2|_2$ is large, those values will typically be far from zero
+as well, and so will still constitute strong evidence against that
+null.  The F-test performs worse as a method for choosing forecasting
+models when $\theta_2$ is large.
+
+We can also see what happens as $K_2$ increases with fixed $K_2/T$.  As
+$T\to\infty$, $\hat{\sigma}^2\to^p\sigma^2$ and $c_{\alpha}\to 1$, so
+$\plim \gamma < \frac{\pi}{2}$.  Consequenly,
+$(\frac{2\gamma}{\pi})^{K_2-1}\to^p0$.  Again, The conditional
+probability that the F-test rejects given the benchmark is more
+accurate converges to 1.  The intuition is similar to the case where
+$|\theta_2|\to\infty$.  As $K_2$ increases, the volume that
+$\hat{\theta}_2$ can occupy increases as well, so the probability that
+it is close to the origin decreases.  So the F-test performs worse as
+a method for choosing forecasting models when the larger model is
+overfit.
+
+It is important to note that the F-test is valid in this analysis.
+The probablity it rejects given that $\theta_2 = 0$ is equal tot its
+nominal level.  However, it is poorly suited for choosing an accurate
+forecasting model, and performs worse when the larger model is either
+overfit or explains more of the variation in the dependent variable.
+Other valid tests of the null hypothesis that $\theta_2 = 0$ will
+suffer the same problem, and will reject the benchmark too often when
+it is more accurate.
+
 \section{Empirical Exercise}\label{sec:empirics}
 This section presents an analysis of equity premium predictability
-similar to \citet{goyal-welch-2008-rfs}.\footnote{All of the
-  calculations in this section are done in R \citep{rproject}.  We
-  also use code provided by \citet{zeileis-hothorn-2002-RNews},
-  \citet{zeileis-2004-JStatSoftware}, and \citet{harrell-2010-R}.}  We
-estimate the expected forecasting performance of the largest model
-they consider, a model with 13 regressors, using 81 observations
-(annual data from 1928 to 2009).  We construct confidence intervals
-for the difference in performance between this model and a prevailing
-mean benchmark, and do so for different values of $R$ and $P$ to
-examine the effect of the training and test sample choice on this
-\oos\ statistic.  We find that the estimate of the larger model's
-\mse\ decreases relative to the benchmark as $R$ increases, but it is
-never smaller than the benchmark's.  This result, combined with the
-larger model's in-sample significance, suggests that there may be a
-real relationship between the equity premium and some of these
-predictors, but that the relationship can not be estimated accurately
-enough to be useful for forecasting and supports
-\citepos{goyal-welch-2008-rfs} conclusions.  These results hold even
-when imposing \citepos{campbell-thompson-2008-rfs} restriction that
-the equity premium forecast be non-negative.
+similar to \citet{goyal-welch-2008-rfs}.  We estimate the
+generalization error of the largest model they consider, a model with
+13 regressors, using 81 observations (annual data from 1928 to 2009).
+We constructe confidence intervals for thedifference in generalization
+error between this model and a prevaling mean benchmark for many
+different values of $R$ to examine the effect of the training and test
+sample choice on these \oos\ statistics.  We find that the estimate of
+the larger model's generalization error decreases relative to the
+benchmark as $R$ increases, but it is never smaller than the
+benchmark's.  This result, combined with the larger model's in-sample
+significance, suggests that there may be a real relationship between
+the equity premium and some of these predictors, but that the
+relationship can not be estimated accurately enough for forecasting
+and supports \citepos{goyal-welch-2008-rfs} conclusions.  These
+results hold up even when imposing
+\citepos{campbell-thompson-2008-rfs} restriction that the equity
+premium forecast be nonnegative.
 
 We'll start with a very brief review.  \citet{goyal-welch-2008-rfs}
-study the \oos\ forecasting performance of different variables thought
-to predict the equity premium (calculated as the difference between
-the return on the S\&P 500 index and the T-bill rate).  Some of these
-variables are listed in
+study the \oos\ forecasting performance of models built on variables
+thought to predict the equity premium (calculated as the difference
+between the return on the S\&P 500 index and the T-bill rate).  Some
+of these variables are listed in
 Table~\ref{tab:equity}.\footnote{Table~\ref{tab:equity} only lists the
@@
   excluded from this model either because the series are too short or
-  because the variables are linear combinations of other variables.}
-\citet{goyal-welch-2008-rfs} estimate the \oos\ forecasting
-performance of bivariate models of the form
+  because the variables are linear combinations of other included
+  variables.}  \citet{goyal-welch-2008-rfs} estimate bivariate models
+of the form
 \[
@@
 \]
-using \ols\ with a recursive window, where $r_{t+1}$ is the equity
-premium and $x_t$ is a generic predictor, as well as some larger
-models.  They find that these models forecast no better than the
-prevailing mean of the equity premium.
-\citet{campbell-thompson-2008-rfs} find that nonlinear extensions of
-Goyal and Welch's models are more accurate, either imposing sign
-restrictions on the estimated coefficients or imposing that the
-forecast be non-negative, but do not test for significance.
-
-Obviously, \citepos{goyal-welch-2008-rfs} bivariate models do not
-match the asymptotic theory of this paper, so we restrict our
-attention here to their ``kitchen sink'' model, which includes all of
-the variables, except for a few dropped because of data availability or
-(perfect) multicollinearity.  Formally, the benchmark and alternative models are
-\begin{eqnarray}
+by \ols, where $r_{t+1}$ is the equity premium and $x_t$ is a generic
+predictor, as well as some larger models.  They find that, by and
+large, these models forecast no better than the prevailing mean of the
+equity premium.
+
+Goyal and Welch's results have been questioned by
+\citet{campbell-thompson-2008-rfs}, \citet{cochrane-2008-rfs}, and
+others.  Campbell and Thomson propose simple nonlinear extensions of
+Goyal and Welch's models, either imposing sign restrictions on the
+estimated coefficients or imposing that the forecast is nonnegative.
+Cochrane argues that an \oos\ comparison is unnecessary, because the
+unpredictability of the dividend yield requires the equity premium to
+be predictable.
+
+\citet{goyal-welch-2008-rfs} focus primarily on simple bivariate
+models.  Obviously, such parsimonious models do not match the
+asymptotic theory of this paper, so we restrict our attention here to
+Goyal and Welch's ``kitchen sink'' model, which includes all of their
+variables, except for a few dropped because of data availablity or
+multicollinearity concerns.  Formally, the benchmark and alternative
+models are
+\begin{equation}
   \label{eq:3}
-  r_{t+1} &=& \mu + \varepsilon_{1,t+1} \\
+  r_{1,t+1} = \mu + \varepsilon_{1,t+1}
+\end{equation}
+\begin{equation}
   \label{eq:2}
-r_{t+1} &=& \beta_0 + \sum_{i=1}^K \beta_{i} x_{it} + \varepsilon_{2,t+1}  
-\end{eqnarray}
-respectively and are estimated by \ols\ using the fixed-window scheme.
-The predictors are listed in Table~\ref{tab:equity}; for a detailed
-description of each predictor, please see Goyal and Welch's original
-paper.  In this model, there are 13 regressors (including the constant
-term) and we estimate the coefficients using annual data from 1928 to
-2009.  This makes the ratio $K/T$ equal to about 0.16.  We also
+r_{2,t+1} = \beta_0 + \sum_{i=1}^K \beta_{i} x_{it} + \varepsilon_{2,t+1}  
+\end{equation}
+and are estimated by \ols.  The predictors are listed in
+Table~\ref{tab:equity}; for a detailed description of each predictor,
+please see Goyal and Welch's original paper.  In this model, there are
+13 regressors (including the constant term) and we estimate the
+coefficients using annual data from 1928 to 2009.  This makes the
+ratio $K/T$ equal to about 0.16, which reasonably large and should
+ensure that comparing the standard \oos\ $t$-test to Gaussian critical
+values is appropriate.
+
+In addition to \citepos{goyal-welch-2008-rfs} \ols\ models, we also
 present results for one of \citepos{campbell-thompson-2008-rfs}
-restricted forecasting models.  For this model, we estimate
-\eqref{eq:3} and \eqref{eq:2}, but impose that $\hat r_{t+1}$ be
-non-negative for each forecast.  We then calculate the \oos\ test just
-as for the unconstrained model.
-
-Table~\ref{tab:gwinsample} gives the results of the full sample
-regression for Equation~\eqref{eq:2}, using Newey-West standard errors
-with two lags \citep{newey_simple_1987}.\footnote{We compare the test
-  statistic to critical values from the $F$-distribution.}  The
-$p$-value is very small (less than 0.01), indicating that the
-coefficients are nonzero in population and at least one of these
-predictors is correlated with the equity premium.  As we argue
-earlier, this result does not imply that the model will forecast well,
-which we look at next.
-
-To study the effect of the training sample size on the \dmw\ statistic, we
-calculate the one-sided confidence interval for $E_T \bar D_2$ given
-by \eqref{interval-greater} corresponding to the null and alternative
+restricted forecasting models.  For this model, we impose that $\hat
+r_{t+1}$ be non-negative for each forecast.  We then calculate the
+\oos\ test just as for the unconstrained model.
+\citet{campbell-thompson-2008-rfs} also suggest restricting the \ols\
+coefficients to fit theoretically-motivated sign restrictions.  Since
+those restrictions are more suitable for bivariate models, we do not
+impose them here.
+
+To study the effect of $R$ on the \oos\ $t$-test, we calculate the
+one-sided confidence interval for $E_T \bar D_2$ given by
+\eqref{interval-greater} corresponding to the null and alternative
 hypotheses
-\[ H_0: \quad E_T \bar D_2 \leq 0 \qquad
+\[ H_0: \quad E_T \bar D_2 = 0 \qquad
 H_A: \quad E_T \bar D_2 > 0
 \]
-for each value of $R$ between 20 and $T-10$.  The standard deviation
-is estimated using a Newey-West estimator with $\lfloor
-P^{\frac14}\rfloor$ lags.  For small values of $R$, the \oos\ average
-is expected to underestimate the performance of the larger model
-relative to the smaller, but this may not hold in this particular
-dataset.
-
-Figures~\ref{fig:empirics1} plots the \ols\ results and
-Figure~\ref{fig:empirics2} imposes
-\citepos{campbell-thompson-2008-rfs} restriction.  The solid line
-in each figure shows the \oos\ average, $\bar D_1$, and the shaded
-region indicates the 95\% one-sided confidence interval implied by the
-\dmw\ test.  Negative numbers indicate that the kitchen sink model has
-higher out-of-sample loss.  We can see that the same patterns hold for
-both models: the performance difference decreases with $R$, but the
-kitchen sink model is never more accurate.  We also see that the
-performance difference decreases suddenly over the period $R=29$ to
-$R=34$ (corresponding to the years 1956--1961).
-Figure~\ref{fig:empirics3} plots the accuracy of the individual
-forecasts (only for the linear models) and shows that this change is
-the result of a sudden improvement in the kitchen sink model.  This
-change may indicate instability in the underlying relationship, as
-\citet{goyal-welch-2008-rfs} propose.
+and calculate these quantities for each value of $R$ between 20 and
+$T-10$.  The standard deviation is estimated using a Newey-West
+estimator with $\lfloor P^{0.25}\rfloor$ lags.  For small values of
+$R$, the \oos\ average is expected to underestimate the generalization
+error of the larger model relative to the smaller, but this may not
+hold in any particular dataset.
+
+Before discussing the intervals for the generalization error, we'll
+plot the forecasts for the equity premium for reference;
+Figure~\ref{fig:forecastplotI} gives the basic \ols\ models, and
+Figure~\ref{fig:forecastplotII} imposes
+\citepos{campbell-thompson-2008-rfs} restriction.  The forecasts are
+plotted over top of each other, but are grouped by $R$ for clarity.
+The left column presents forecasts from the kitchen sink model and
+the right column from the prevailing mean model.
+
+We can see that the forecasts made from the kitchen sink models
+estimated towards the beginning and middle of the sample are terrible,
+drifting far from the equity premium series in the 1980s and slowly
+returning in the 1990s and 2000s.  This performance could be due to
+parameter instability, but it could also come from other sources,
+e.g. poor estimates combined with persistance in the
+predictors.\footnote{Separate analysis shows that dropping the
+  Treasury Bill and long term yield variables removes most of this
+  pattern, and dropping the book to market ratio removes the rest.}
+We can see this pattern in both figures.
+
+Forecasts made from the kitchen sink model in the late 1970s and later
+are better, in that they do not diverge from the equity premium.
+However, they do not seem to track the equity premium closely.  Note
+that the \ols\ forecast gives many negative forecasts, so
+\citepos{campbell-thompson-2008-rfs} restriction that the forecasts be
+nonnegative matters more later in the sample.
+
+Figures~\ref{fig:oosmseI}--\ref{fig:oosmseIV} present the difference
+in \oos\ \mse\ between the kitchen sink and prevailing mean models as
+a function of $R$ for the unrestricted and restricted models.
+Negative numbers indicate that the kitchen sink model has higher
+out-of-sample loss.  The black line shows the \oos\ average, and the
+gray line shows the endpoint of a 95\% confidence interval for the
+difference in generalization error.  We can see that the same patterns
+hold for both models: the absolute difference decreases with $R$, but
+the kitchen sink model is never more accurate.\footnote{The same
+  pattern holds after removing the variables responsible for the
+  forecast's divergence mentioned earlier: Treasury Bill, long term
+  yield, and book to market ratio.}
 
 In summary, we fail to reject the null that the benchmark prevailing
-mean model is more accurate than \citepos{goyal-welch-2008-rfs}
-kitchen sink.  This result is consistent with Goyal and Welch's
-original analysis.  Unlike Goyal and Welch, we attribute this result,
-at least in part, to parameter uncertainty---the full sample results
-indicate that the larger model could predict better than the
-benchmark with enough data.  Obviously, this is an illustrative
-exercise only and is not meant to be comprehensive.  In this dataset,
-there is likely parameter instability that we have not addressed, and
-we have not dealt with variable persistence at all.
+mean model has lower generalization error than
+\citepos{goyal-welch-2008-rfs} largest model.  This result is
+consistent with Goyal and Welch's original analysis.  Unlike Goyal and
+Welch, we attribute this result, at least in part, to parameter
+uncertainty---with enough data, it is possible that the larger model
+would predict better than the benchmark.  Obviously, this is an
+illustrative exercise only and is not meant to be comprehensive.  In
+this dataset, there is likely parameter instability that we have not
+addressed, and we have not dealt with variable persistance at all,
+beyond differencing.
+
+\section{Monte Carlo}\label{sec:mc}
+\newcommand{\thetanorm}{\ensuremath{\lvert \theta \rvert_2}}
+
+This section presents simulations that investigate the small-sample
+properties of in-sample and \oos\ tests.  We look at the behavior of
+the in-sample F-test, the naive \oos\ $t$-test, and Clark and West's
+(2006, 2007) and \citepos{mccracken_asymptotics_2007} adjusted
+statistics when comparing two nested linear regression models
+estimated over i.i.d.  data.\footnote{Simulations were conducted in R
+  \citep{rproject} using the Lattice \citep{lattice} and RSQLite
+  \citep{rsqlite} packages for graphics and data management respectively.}
+
+Unlike other authors, we focus on the probability that each test
+statistic rejects given the benchmark model has smaller generalization
+error.  This rejection probability is similar conceptually to the
+test's size.  As we argue elsewhere in the paper, the generalization error is
+the more important quantity when choosing a model for actual
+forecasting.  At the risk of some confusion, we'll refer to the
+conditional probabilities
+\[P['reject\ 'benchmark \mid 'E_T \bar D_2 \leq 0] \quad \text{and}
+\quad P['reject\ 'benchmark \mid \E_T \bar D_2 > 0]\] as the test's
+``size'' and ``power'' respectively for the rest of this section,
+despite the fact that they do not correspond to hypotheses about the
+parameters of the \dgp.
+
+Unfortunately, we show that none of the existing methods are
+satisfactory at common sample sizes in macroeconomics when testing for
+equal generalization error: the F-test and Clark and West's (2006,
+2007) and \citepos{mccracken_asymptotics_2007} tests reject the
+benchmark much too often, while the naive $t$-test we propose rejects
+too little, leading to (the equivalent of) very low power---often much
+lower than the test's nominal size.
+\subsection{Simulation Design}\label{sec:simulation-design}
+We simulate data for the equation
+\begin{equation*}
+  y_t = x_t'\theta + \varepsilon_t,\quad \varepsilon_t \sim N(0,1),
+  \quad t=1,\dots,T.
+\end{equation*}
+The first element of $x_t$ is 1 and the remaining elements are
+independent Standard Normals.  The number of observations and the
+number of regressors take the values in Table~\ref{tab:mc-parameters}.
+Values of $k$ were selected to reflect strict alignment with our
+theory ($k=n/10$) as well as empirically relevant values.  The vector
+of coefficients, $\theta$, is chosen so that all of its elements are
+equal and its Euclidean norm equals the values listed in
+Table~\ref{tab:mc-parameters}.\footnote{This implies that $\theta_i =
+  \frac{\lvert \theta \rvert}{\sqrt{k}}$.}
+
+Each simulation compares the generalization error of a benchmark model
+\begin{equation}
+  \label{eq:1}
+  y_{1t} = \sum_{j=1}^{k_0} x_{jt}\theta_j + \varepsilon_t
+\end{equation}
+to the full regression model under \mse\ loss.  The values of $k_0$
+are listed in Table~\ref{tab:mc-parameters} as well.  Since the
+observations are i.i.d., the difference in generalization error is
+easy to calculate, and
+\[\E_T \bar D_2 = \lvert (\hat\theta_{1T}', 0,\dots, 0) - \theta
+\rvert_2^2 - \lvert \hat{\theta}_{2T} - \theta\rvert_2^2 \].
+
+For each combination of $T$, $k$, $k_0$, and $\thetanorm$,
+we draw 1000 samples satisfying 
+\[ \E_T \hat{D}_2 \leq 0 \]
+to measure the tests' size and 1000 samples satisfying
+\[ \E_T \hat{D}_2 > 0 \] to measure power.\footnote{For some
+  combinations, $\E_T \bar{D}_2$ takes positive or negative values too
+  infrequently to observe 1000 draws in a reasonable period of time,
+  so we don't report results for those combinations.}  For each
+sample, we calculate the following one-sided test statistics, using a
+nominal size of 10\%:
+
+\begin{description}
+\item[F-test] The basic F-test of the null hypothesis
+  \begin{equation*}
+    H_0: \quad \theta_{k_0+1}=\dots=\theta_k=0.
+  \end{equation*}
+  Note that our \dgp\ has normal errors, so the F-test statistic has
+  the exact F distribution for $\thetanorm = 0$.
+\item[oos-t] We calculate the naive \oos\ $t$-test for different choices
+  of $R$ and $P$.  We let $R$ take every other value from $T/3$ to
+  $T-2$.\footnote{The choice of every other value is somewhat
+    arbitrary, but reduces computation time while still preserving
+    detail.}  The asymptotic variance is estimated as 
+  \[ \frac1{P-1} \sum_{R+1}^{T} (D_{tR} - \bar D_1)^2. \]
+
+  The naive test rejects if \oost\ is greater than the 90th percentile
+  of the $t$ distribution with $P-1$ degrees of freedom.  We also
+  compare \oost\ to \citepos{mccracken_asymptotics_2007} alternative
+  critical values.  the values depend on $P/R$ and $k - k_0$---see his
+  paper for the exact values.  When $P/R$ does not correspond exactly
+  to a value listed in published tables, we use a linear interpolation
+  between the two closest values.  Critical values are published only
+  for $k - k_0 \leq 10$, and we do not calculate results here when
+  that difference is larger.
+
+\item[\citet{clark_using_2006,clark_approximately_2007}]
+  \citet{clark_using_2006,clark_approximately_2007} propose correcting
+  the \oost\ statistic to account for parameter estimation
+  error.\footnote{Their papers discuss the rolling window; we present
+    the analogous statistic for the fixed window scheme.}
+  They recommend conducting a one-sided t-test that the mean of the sequence
+  \[ (y_t - x_{1t}'\hat\theta_{1R})^2 - (y_t -
+  x_{2t}'\hat{\theta}_{2t})^2 + (x_{1t}'\hat{\theta}_{1R} -
+  x_{2t}'\hat\theta_{2R})^{2} \]
+  is zero.
+\end{description}
+\subsection{Results}
+For each statistic, the fraction of the ``size'' simulations for which
+the statistic rejects is an estimate of the statistic's actual
+size; remember that the nominal size is 10\%.  Results are presented
+in Figures~\ref{fig:ftest}--\ref{fig:ttest-power}.  For the \oos\
+tests, the size is plotted for each combination of $T$, $k_0$, $k$,
+and $\thetanorm$ as a function of $P$.  The F-test does
+not depend on $P$, so a single value is presented for each
+combination.
+
+We'll look at the F-test first.  To make comparisons easier, the size
+is displayed as a dot plot.  Different panels display a different
+combination of $k_0$, $k$, and $T$, and each individual plot shows the
+empirical size for that combination for each choice of $\thetanorm$.
+We see immediately that the actual and nominal size are essentially
+equal for $\thetanorm = 0$, which is unsurprising.  For $\thetanorm =
+0$, the F-test is exact; moreover, the larger model will almost always
+be less accurate than the smaller one, so conditioning on $\E_T
+\bar{D}_2 \leq 0$ is almost nonrestrictive.  As $\thetanorm$
+increases, though, the F-test overrejects badly---rejecting from
+roughly 15\% to 50\% when $\thetanorm = 0.1$ and 30\% to almost 100\%
+when $\thetanorm = 0.2$.  This pattern agrees with our earlier
+discussion---$\E_T \bar D_2$ is negative when $\hat\theta_{2T}$ is far
+from $\theta$, but as $\thetanorm$ increases, those values of
+$\hat\theta_{2T}$ are more likely to be significantly different from
+zero.
+
+The behavior of the F-test as $k$ and $T$ change is less pronounced.
+As $k$ or $k_0$ increase while $T$ remains fixed, the estimated size
+falls closer to its nominal value.  As $T$ increases while the ratio of
+$k/T$ remains fixed, the overrejection also increases.
+
+Figure~\ref{fig:ttest-size} presents the size estimates for the basic
+$t$-test.  Again, different panels display results for different
+combinations of $k_0$, $k$, and $T$.  Each graph plots the rejection
+probability against $P$.  Our theory predicts that its size should be near 10\% when $P$
+is small relative to $T$, but may deteriorate as $P$ gets larger.
+Previous research by \citet{clark_tests_2001},
+\citet{clark_using_2006,clark_approximately_2007} and
+\citet{mccracken_asymptotics_2007} also indicates that the size should
+be near 10\% for small $k$ and $P/T$, and should decrease as $P/T$
+increases---but those results apply to a different null hypothesis and
+may not carry over here.
+
+In fact, we observe that, when $k$ is large ($T/10$), the size drops
+from near 10\% when $P/T$ is small to near zero as $P$ increases, but
+increases with $P$ when $k$ is small---we see this in each plot for
+$k=3$, and for $k=10$ when $T$ is 600 or 1200.  This pattern suggests
+that the naive $t$-test should not overreject for overfit models even
+for large values of $P$, but the decrease in the size indicates that
+the test is likely to have very low power even for moderately large
+values of $P$.  As we would expect, the rejection probability
+increases with $\thetanorm$.  It also falls as $k$ increases.  The
+overall picture does not change as $T$ increases, as long as $k/T$
+remains constant, but the $t$-test overrejects as $P$ increases for
+small values of $k$---we can observe this pattern for every $T$ when
+$k$ equals 3, and for $k$ equal to 3 and $T$ equal to 600 or 1200.
+
+Results using \citepos{mccracken_asymptotics_2007} critical values are
+presented in Figure~\ref{fig:mccracken}.  The behavior of the \oost\
+statistic is much different than with the naive critical values.  The
+test is correctly sized when $\thetanorm = 0$, as with the F-test, and
+when $P/T$ is near zero.  As $P/T$ and \thetanorm grow, however, the
+test overrejects by increasing amounts, with a maximum near 70\%
+observed for $\thetanorm$ equal to 0.2 and $T$ equal to 600 with
+$\frac{P}{T}$ less than $\frac{1}{2}$.  The degree that the test
+overrejects also increases with $T$.  The behavior as $K$ changes is
+ambiguous, since we do not estimate results for very large values of
+$k$.
+
+Clark and West's (2006, 2007) statistic, presented
+in Figure~\ref{fig:clarkwest} shows the same patterns as the \oost\
+statistic using \citepos{mccracken_asymptotics_2007} critical values.
+When \thetanorm\ equals zero the test is correctly sized, and is
+correctly sized when $\frac{P}{T}$ is small as well.  As \thetanorm\
+and $\frac{P}{T}$ increase the degree of overrejection increases as
+well.  The maximum again comes for $\thetanorm = 0.2$ and $T = 600$
+and is near 90\%.    The test overrejects more as $T$ increases, but
+less as $K$ and $K_0$ increase.  For any choice of $T$ and $K$,
+though, the actual size of the test is at least 20\% for $\thetanorm =
+0.2$, and is often substantially higher.
+
+We present some power simulations in Figure~\ref{fig:ttest-power}.
+Since the F-test and \citepos{mccracken_asymptotics_2007} and Clark
+and West's (2006, 2007) tests all greatly overreject, we only present
+power for the naive $t$ critical values for \oost.  These graphs are
+similar to the size graphs in Figure~\ref{fig:ttest-size}: the test
+has nontrivial power when $K$ is 3 or 10 and $T$ is 600 or 1200, but
+the test does not control size for those values.\footnote{Note that
+  results are not reported for larger values of $k$ when $T$ is 600 or
+  1200 because it is too time-consuming to generate samples in which
+  the large model has smaller generalization error.}  As we discussed
+earlier, the test statistic underrejects for most choices of
+\thetanorm, $T$, and $K$; for those values, the power is also very
+low, less than the nominal size and often near zero.
 \section{Conclusion}\label{sec:conclusion}
-This paper gives a theoretical motivation for using \oos\ comparisons:
-the \dmw\ \oos\ test allows a forecaster to conduct inference about
-the expected future accuracy of his or her models when one or both is
-overfit.  We show analytically and through Monte Carlo that existing
-in-sample test statistics can not test hypotheses about this
-performance.
+This paper gives a theoretical justification for using \oos\
+comparisons: the \oost\ statistic will still allow a forecaster to
+conduct inference about generalization error when on of his or her
+forecasting models is overfit.  By choosing the model with lower
+generalization error, the forecaster can be confident that the model
+is expected to forecast better in the future.  Previous research has
+looked at the distribution of \oos\ test around quantities other than
+the generalization error, which has made these statistics' value unclear.  But
+existing full-sample statistics can not test hypotheses about the
+generalization error, as seen in our simulations.  So \oos\
+comparison fills this need.
 
@@
   instability, which this paper does not address.}  We show that
-$P^2/T$ must converge to zero for the \dmw\ test to give valid
-inference about the expected forecast accuracy, otherwise the test
-measures the accuracy of the estimates constructed using only the
-training sample.  In empirical research, $P$ is typically much larger
-than this.  Our simulations indicate that using large values of $P$
-with the \dmw\ test gives undersized tests with low power, so this
-practice may favor simple benchmark models too much.  Existing
-corrections, proposed by
+$P^2/T$ must converge to zero for \oos\ statistics to give valid
+inference about the generalization error, otherwise they measure the
+accuracy of the estimates constructed using only the training sample.
+In empirical research, $P$ is typically much larger.  Our simulations
+indicate that using large values of $P$ with the naive \oos\ $t$-test
+gives undersized tests with low power, so this practice may favor
+simple benchmark models too much.  Existing corrections, proposed by
 \citet{clark_tests_2001,clark_evaluating_2005},
@@
 \citet{clark_using_2006,clark_approximately_2007}, seem to correct too
-much, though, and reject too often when the benchmark model is more
-accurate.
-
-More work remains.  Our requirement that $\frac{P^2}{T}$ converge to
-zero is limiting, as it implies that in typical macroeconomic
-datasets, only a handful of observations should be used for testing.
-This restriction could be addressed by directly estimating $\E_R \bar
-D_1 - \E_T \bar{D}_2$ or by deriving its asymptotic distribution,
-which would allow larger values of $P$.  It could also be mitigated by
-extending our results to cross-validation or other resampling
-strategies.  It would also be useful to extend our results to other
-estimation windows and forecasting models, and to explore how
-stationarity could be relaxed.
+much, though, and reject too often when the benchmark model has
+smaller generalization error.
+
+More work on \oos\ comparisons remains.  Our requirement that
+$\frac{P^2}{T}$ converge to zero is particularly limiting, as it
+implies that in typical macroeconomic datasets, only a handful of
+observations should be used for testing.  This restriction could be
+addressed by directly estimating $\E_R \bar D_1 - \E_R \bar{D}_2$ or
+by deriving its asymptotic distribution, which would allow larger
+values of $P$.  It could also be mitigated by extending our results to
+cross-validation or another resampling scheme.  It would also be
+useful to extend these results to other estimation windows and
+forecasting models, and to explore how stationarity could be relaxed.
 
 \appendix
-\section{Supporting results}
+\section{Berbee's Lemma}
 The results in this paper rely heavily on a coupling argument for
@@
 paper (\ref{res-confidence-intervals}, \ref{res-mixingale}, and
-\ref{res-variance-estimator}) are modifications of existing
+\ref{res-variance-estimator}) are minor modifications of existing
 results for \ned\ functions of mixing processes by 
-\citet{de_jong_central_1997} and \citet{de_jong_consistency_2000};
-this coupling argument is used to explicitly derive inequalities that
-arise naturally for \ned\ processes.  Lemma \ref{lem-basic-coupling}
-establishes these inequalities, which are based on a proposition of
-\citet{merlevede_coupling_2002}.
+\citet{de_jong_central_1997} and \citet{de_jong_consistency_2000},
+where this coupling argument is used to explicitly derive inequalities
+that arise naturally for \ned\ processes---the remaining arguments are
+the same.  Lemma
+\ref{lem-basic-coupling} establishes these inequalities, which are
+based on a proposition of \citet{merlevede_coupling_2002}.
 
@@
 \[
-\beta(X,Y) = \sup_{A \in \sigma(Y)} \E \lvert \Pr(A \mid \sigma(X))
-  - \Pr(A) \rvert.
+\beta(X,Y) = 'sup_{A \in \sigma(Y)} \E \lvert P(A \mid \sigma(X))
+  - P(A) \rvert.
 \]
@@
 \begin{lem}\label{lem-berbee}
-  Let $X$ and $Y$ be random variables defined on a probability space
+  Let $X$ and $Y$ be random variables define on a probability space
   $(\Omega, \mathcal{T}, \mathbf{P})$ with values in a Polish space
-  $S$.  Let $\sigma(X)$ be a $\sigma$-algebra generated by $X$ and let
+  $S$.  Let $\sigma(X)$ be a $\sigma$-field generated by $X$ and let
   $U$ be a random variable uniformly distributed on $[0,1]$
@@
 \end{lem}
-\noindent\citep{merlevede_coupling_2002}
+\citep{merlevede_coupling_2002}
 \end{quotation}
@@
 dimension of $Y$, which makes them unsuitable for our applications.
-The remaining results in this section use Berbee's Lemma to establish
-some basic inequalities.
-
+
+\section{Supporting results}
 \begin{lem}\label{lem-extend-mp}
   Suppose that $X$ and $X^*$ are $L_p$-bounded random variables, with
-  $p > 2$, that satisfy ${\Pr[X \neq X^*] = c}$.  Then
+  $p > 2$, that satisfy ${P[X \neq X^*] = c}$.  Then
   \[
@@
   \begin{equation}\label{eq:coupling2}
-    \E(\phi(\tilde D_s,\dots, \tilde D_t) \mid \mathcal{F}_u ) = 
+    \E(\phi(\tilde D_s,\dots, \tilde D_t) \mid \mathcal{F}_u ) = \\ 
     \int
-    \phi(D_{sw},\dots,D_{tw}) f(\mathbf{x}, \mathbf{y})\ d\mathbf{x}\ d\mathbf{y}
+    \phi(D_{sw},\dots,D_{tw}) f(x_{1s}, x_{2s}, y_{s+\h}, \dots, x_{1t},
+    x_{2t}, y_{t+\h}) dx_{1s} dx_{2s} dy_{s+\h} \cdots dx_{1t} dx_{2t}
+    dy_{t+\h}
   \end{equation}
   almost surely for all measurable functions $\phi$ such that the
-  expectations are finite, where 
-  \[ \mathbf{x} = (x_{s}', \dots, x_{t}')', \\
-  \mathbf{y} = (y_{s+\h},\dots,y_{t+\h})'\] and $f$ is the
-  joint density of $(\mathbf{x}, \mathbf{y})$.  Moreover,
+  expectations are finite, where $f$ is the joint density of $x_{1s},x_{2s},
+  y_{s+\h}, \dots, x_{1t}, x_{2t}, y_{t+\h}$.  Moreover,
  \begin{equation}\label{eq:coupling3}
-   \| \tilde D_v - D_{vw} \|_2 \leq 2^{1+1/\rho} B_L
-   \beta_{s-u}^\rhoExp, \qquad v = s,\dots,t.
- \end{equation}
+   \| \tilde D_v - D_{vw} \|_2 \leq 2^{1+1/\rho} B_L \beta_{s-u}^\rhoExp
+ \end{equation}
+for each $v$.
 \end{lem}
@@
   and $T$, the sequence of vectors
-  \[ V_s = (y_{s+\h}, x_{s}', \dots, y_{s+l+\h}, x_{s+l}') \] is
-  absolutely regular of size $\rho/(\rho-2)$.  Berbee's Lemma implies
-  that there is a random vector $V^*$ that is independent of
+  \[ V_s = (y_{s+\h}, x_{1s}', x_{2s}, \dots, y_{s+l+\h}, x_{1,s+l}'
+  x_{2,s+l}) \] is absolutely regular of size \absReg.  Berbee's Lemma
+  implies that there is a random vector $V^*$ that is independent of
   $\mathcal{F}_u$, equal to $V_s$ in distribution, and satisfies
-  \[\Pr[V^* \neq V_s] = \beta_{s-u}.\]
+  $P[V^* \neq V_s] = \beta_{s-u}$.
 
@@
 
-\begin{proof}[Proof of Lemma \ref{res-mixingale}, Part 1.]
-Fix $R$, $j$ and $l$ and use Lemma
+\begin{proof}[Proof of Lemma \ref{res-mixingale}, part a.]
+The proofs of Equations \eqref{mixingaleR} and \eqref{mixingaleT} are
+identical, so we'll prove (\ref{res-mixingale}).  Fix $R$, $j$ and $l$ and use Lemma
 \ref{lem-basic-coupling} to define $\tilde{D}_{R+j}$ so that
@@
 \leq 2 \lVert D_{R+j,R} - \tilde D_{R+j} \rVert_2 \\
-\leq 2^{2 + \frac1\rho}\ B_L\ \couplingBeta{l}.\return
-\]
-Now $\couplingBeta{l} = O(l^{-\frac12 - \delta})$ for some
+\leq 2^{2 + \frac1\rho}\couplingBeta{l}.\return
+\]
+Now $\couplingBeta{l} = O(l^{-1/2 - \delta})$ for some
 positive $\delta$, completing the proof.
@@
 
-\begin{proof}[Proof of Lemma \ref{res-mixingale}, Part 2.]
-  A modification of \citepos{de_jong_central_1997} \clt s for
-  mixingale and \ned\ arrays will complete the proof.
+\begin{proof}[Proof of Lemma \ref{res-mixingale}, part b.]
+  A minor modification of \citepos{de_jong_central_1997} \clt\ for
+  mixingale arrays will complete the proof.
 
@@
 \]
-where $b_T$ is a sequence that satisfies $b_T\leq P$,
+where $b_T$ and is a sequence that satisfies $P \geq b_T$,
 $b_T\to\infty$, and $b_T/P\to 0$.  The same arguments used in
@@
 Note that $\{Z_i - E_{R + (i-1)b_T},\mathcal{F}_{R + i b_T}\}_i$ is an
-\mds\ by construction, so \citepos{hall_martingale_1980} Theorem 3.2
-and Corollary 3.1 ensure that\footnote{Note that $\sigma^2 \in
-  \mathcal{F}_t$ for all $t \geq R$, so Hall and Heyde's condition
-  (3.21) is unnecessary---see the remarks after their result.}
+\mds\ by construction, so \citepos{hall_martingale_1980} Theorem 3.1
+ensures that
 \[
@@
 \lVert \tilde D_s - D_{sR} \rVert_2 \leq 2^{1 + \frac1\rho} B_L \beta_{s -
-  (i-1)b_T + R}^{\rhoExp}, \quad s = R+(i-1)b_T + 1,\dots,R+i b_T
+  (i-1)b_T + R}^{\rhoExp}
 \]
@@
 \[
-\E_R \phi(\tilde D_s) = \E_{R+(i-1)b_T} \phi(\tilde D_s) \quad \text{a.s.}, \quad s = R+(i-1)b_T + 1,\dots,R+i b_T
+\E_R \phi(\tilde D_s) = \E_{R+(i-1)b_T} \phi(\tilde D_s) \quad \text{a.s.}
 \]
@@
 \[
-\lVert \ZSqCE - \E_R Z_i^2 \rVert_1 \wall= \lVert \wall\CEOuterBlock{(Z_i^2 -
-  \tilde Z_i^2)}{i} \\ - (\E_R Z_i^2 - \CEOuterBlock{\tilde Z_i^2}{i})
-\rVert_1 \return\\
+\lVert \ZSqCE - \E_R Z_i^2 \rVert_1 \wall= \lVert \CEOuterBlock{(Z_i^2 -
+  \tilde Z_i^2)}{i} - (\E_R Z_i^2 - \CEOuterBlock{\tilde Z_i^2}{i})
+\rVert_1 \\
 \leq 2 \lVert Z_i^2 - \tilde Z_i^2 \rVert_1.
@@
 Z_{i,C} \rvert \quad \text{and} \quad \lvert V_{i,C} + \tilde V_{i,C}
-\rvert \leq 2 C \sqrt{b_T/P} \quad \text{a.s.}\] 
+\rvert \leq 2 \ZTrunc \quad \text{a.s.}\] 
 It follows that
@@
  \leq 2 \ZTrunc \SumOuterBlock{i} \lVert Z_i - \tilde Z_i \rVert_2 \\
- \leq \frac{2 C \sqrt{b_T}}{P}\SumOuterBlock{i} \SumInnerBlock{s}{i} \lVert \wall \ZSummand \\
+ \leq 2 \frac{b_T}{P}\SumOuterBlock{i} \SumInnerBlock{s}{i} \lVert \wall \ZSummand \\
   - (\tilde D_s - \E_R \tilde D_s) \rVert_2 \return \\ 
@@
 \begin{equation}\label{EQ-thetaconvg1}
-\resConvgEstDiff{1} = O_p(\sqrt{P/T})
+\resConvgEstDiff{1} = O_p(\sqrt{\frac PT})
 \end{equation}
@@
 \begin{equation}\label{EQ-thetaconvg2}
-\resConvgEstDiff{1} = O_p(\sqrt{P/T})
+\resConvgEstDiff{1} = O_p(\sqrt{\frac PT})
 \end{equation}
@@
 
-To prove (\ref{EQ-oosaverage1}), define $\tilde D_t$ for each $t = R+1,\dots,T-\h$ as
+To prove (\ref{EQ-oosaverage1}), define $\tilde D_t$ for each $t > 0$ as
 in Lemma \ref{lem-basic-coupling} so that
 \[
-\lVert \tilde D_t - D_{tR} \rVert_2 \leq \couplingBound{t-R}
-\]
-and 
+\lVert \tilde D_t - D_{tR} \rVert_2 \leq \couplingBound{t-R}.
+\]
+Notice that 
 \[
@@
 \[
-\lVert \E_R \bar D_1 - \wall \resConvgRHS{R} \rVert_2  \\
+\lVert \E_R \bar D_1 - \resConvgRHS{R} \rVert_2 \wall 
 \leq \frac1P \oosSum{t}{1} \lVert \E_R (D_{tR} - \tilde D_t) \rVert_2 \\
@@
 Equations (\ref{EQ-thetaconvg1}) and (\ref{EQ-thetaconvg2}) both
-follow the same argument, so we'll just prove (\ref{EQ-thetaconvg1}).
+follow the same argument, so we'll only prove (\ref{EQ-thetaconvg1}).
 Since 
-\[ \lVert \resConvgEstDiff{1} \rVert_1 \\ \quad= \| \E(L(y^{*} -
-x_1^{*\prime} \hat{\theta}_{1R}) - L(y^{*} - x_2^{*\prime}
-\hat{\theta}_{dR}) \mid \hat{\theta}_{1R}, \hat{\theta}_{1T}) \|_1 \\
-\quad\leq \lVert \resConvgEstDiffRV{1} \rVert_1, \] it suffices to
-prove
-\[ \resConvgEstDiffRV{1} = O_p(\sqrt{P/T}). \]
+\[ \lVert \resConvgEstDiff{1} \rVert_1 \leq \lVert
+\resConvgEstDiffRV{1} \rVert_1, \]
+it suffices to prove
+\[ \resConvgEstDiffRV{1} = O_p(\sqrt{\frac PT}). \]
 Moreover, smoothness of the loss function ensures that
@@
 \begin{equation*}
-  \lVert x_1^{*\prime}(\bh{1R} - \bh{1T}) \rVert_2 = O(\sqrt{P/T}).
+  \lVert x_1^{*\prime}(\bh{1R} - \bh{1T}) \rVert_2 = O(\sqrt{\frac PT}).
 \end{equation*}
@@
 \begin{equation} \label{eq-theta-convergence-1}
-\lVert x_1^{*\prime} (\bh{1R} - \bh{1T}) \rVert_2 \wall \leq
+\lVert x_1^{*\prime} (\bh{1R} - \bh{1T}) \rVert_2 \leq
 \lVert x_1^{*\prime} [(X_{1R}'X_{1R})^{-1} - (X_{1T}'X_{1T})]
-X_{1T}'\ep{1T} \rVert_2  \\ \quad +
+X_{1T}'\ep{1T} \rVert_2  +
 \lVert x_1^{*\prime} (X_{1R}'X_{1R})^{-1}\oosSum{t}{1} x_{1t}\varepsilon_{i,t+\h}
@@
 X_{1T}'\ep{1T} \rVert_2^2 \\ = O(1)
-\E\{\lambda_{\max}(X_{1T}' \ep{1T} \ep{1T}'
+\E\{\lambda_{max}(X_{1T}' \ep{1T} \ep{1T}'
     X_{1T}) \sum_{i=1}^{K_1}
-    \lambda_i^2([X_{1R}'X_{1R}]^{-1} -
-        [X_{1T}'X_{1T}]^{-1} )\}.
-\]
-By assumption, $\lambda_{\max}(X_{1T}'\ep{1T} \ep{1T}' X_{1T}) =
+    \lambda_i([X_{1R}'X_{1R}]^{-1} -
+        [X_{1T}'X_{1T}]^{-1} )^2\}.
+\]
+By assumption, $\lambda_{max}(X_{1T}'\ep{1T} \ep{1T}' X_{1T}) =
 O_p(T)$.  The matrix $(X_{1R}'X_{1R})^{-1} - (X_{1T}'X_{1T})^{-1}$ has
@@
 $(X_{1R}'X_{1R})^{-1}$, so
-  \[\sum_{i=1}^{K_1}\lambda_i^2((X_{1R}'X_{1R})^{-1} -
-  (X_{1T}'X_{1T})^{-1} )  \wall \leq
-  \sum_{i=K_1 - P + 1}^{K_1}\lambda_i^2((X_{1R}'X_{1R})^{-1})  \\ = O_p(P/T^2).
-  \]
+  \[
+    \sum_{i=1}^{K_1}
+    \lambda_i((X_{1R}'X_{1R})^{-1} -
+        (X_{1T}'X_{1T})^{-1} )^2 = O_p(\frac{P}{T^2}).
+  \]
+
 The moment bounds in Assumption~\ref{asmp-2} guarantee that
@@
         (X_{1T}'X_{1T})^{-1} ]
-      X_{1T}'\ep{1T} \rVert_2 = O(\sqrt{P/T}).
-  \]
-  A similar argument shows that
+      X_{1T}'\ep{1T} \rVert_2 = O(\sqrt{\frac PT}).
+  \]
+  A similar argument shows that that the second term in
+  \eqref{eq-theta-convergence-1} satisfies the relationship
   \[
     \lVert x_1^{*\prime} (X_{1R}'X_{1R})^{-1}\oosSum{t}{1} x_{1t}\varepsilon_{1T}
-    \rVert_2 =   O(\sqrt{P/T}),
+    \rVert_2 =   O(\sqrt{\frac PT}),
   \]
@@
   The proof follows \citepos{de_jong_consistency_2000} Theorem 2.1
-  closely.  We start by defining similar quantities to theirs,
-  borrowing their notation when possible to make the similarities
-  apparent.  For positive $\delta$, define $b_T \equiv \lfloor
-  \frac\gamma\delta \rfloor$,
+  closely.  We start by defining similar quantities to theirs.  For
+  positive $\delta$, define $b_T \equiv \lfloor \frac\gamma\delta
+  \rfloor$,
 \begin{equation*}
@@
 \begin{equation*}
-  \varianceTermII \equiv \vtSum \wall \varianceTermIIa\\ \times
-  \varianceTermIIb,\return
-\end{equation*}
-\begin{equation*}
-  \varianceTermIII \equiv \vtSum \wall \varianceTermIIIa\\ 
-  \times \varianceTermIIb, \return 
-\end{equation*}
-\begin{equation*}
-  \varianceTermIV \equiv \vtSum \wall \varianceTermIIIa \\
-  \times \varianceTermIVb, \return
-\end{equation*}
-giving us the inequalities
+  \varianceTermII \equiv \vtSum \wall (\varianceTermIIa)\\ \times
+  (\varianceTermIIb),\return
+\end{equation*}
+\begin{equation*}
+  \varianceTermIII \equiv \vtSum \wall (\varianceTermIIIa) \\ 
+  \times (\varianceTermIIb), \return 
+\end{equation*}
+\begin{equation*}
+  \varianceTermIV \equiv \vtSum \wall (\varianceTermIIIa) \\
+  \times (\varianceTermIVb), \return
+\end{equation*}
+and we have the inequalities
 \begin{equation*}
@@
 Their proofs of \eqref{dd1}--\eqref{dd4} use the fact that \ned\
-functions of mixing processes are also mixingale processes, and do not
-use any properties specific to \ned\ processes, so they hold here as
-well.  We do need to modify their proofs that
+functions of mixing processes are also Mixingale processes, and do not
+use any features that require \ned.  We do need to modify
+their proofs that
 \begin{equation}
@@
 \end{equation}
-though, since their proofs exploit \ned\ properties.
+though, since those proofs exploit \ned\ properties.
 
@@
 \varianceDiffA \\ +
-\frac1{P} \oosSum{s,t}{1} \lvert (D_{tR} - \bar D_1)(\E_R D_{sR} - \bar D_1) \rvert
+\frac1{P} \oosSum{s,t}{1} \lvert (\E_{R} D_{tR} - D_{tR})(\E_R D_{sR} - \bar D_1) \rvert
 \vWeight,
@@
 \[
-\varianceDiffA \\ \quad \leq O(1) [\varianceDiffAii]^{\frac12} [\varianceDiffAi]^{\frac12}.
-\]
-Now,
+\varianceDiffA \\ \leq O(1) [\varianceDiffAi]^{\frac12} [\varianceDiffAii]^{\frac12}.
+\]
+Since $D_{sR}^2$ is uniformly integrable, 
 $\frac1P \oosSum{s}{1}(D_{sR} - \E_R D_{sR})^2 = O_p(1)$, and it suffices to prove
-that \[\varianceDiffAi = o_p(1).\]  Observe that
+that $\varianceDiffAi = o_p(1)$.  Observe that
 \[
 \varianceDiffAi \wall =  O_p(\frac1P \oosSum{s}{1}(\E_{R}D_{sR} -
-\E_R\bar D_1)^2) \\
-\quad + O_p(\bar D_1 - \E_R\bar D_1)^{2} \\
+\E_R\bar D_1)^2)
++ O_p(\bar D_1 - \E_R\bar D_1)^{2} \\
 = O_p(\frac1P \oosSum{s}{1} (\E_RD_{sR})^2 - (\E_R\bar D_1)^2) + o_p(1),    \return
@@
 with the second term vanishing by Lemma \ref{res-mixingale} and
-\citepos{davidson_l1-convergence_1993} mixingale \lln.
-
-Now define $\tilde D_s$, $s = R+1,\dots,T-\h$, as in Lemma
-\ref{lem-basic-coupling} so that $\E_{s-1} \tilde D_s = \E_R \tilde
-D_s$ almost surely.  Note that we also have the almost sure equality
-$\E_R \tilde D_s = \E_R \tilde D_{R+1}$ almost surely for all $s\geq R+1$,
-and so
+\citepos{davidson_l1-convergence_1993} Mixingale \lln.
+
+Now define $\tilde D_s$ as in Lemma \ref{lem-basic-coupling} so that
+$\E_{s-1} \tilde D_s = \E_R \tilde D_s$ almost surely.  Note that we
+also have the almost sure equality $\E_R \tilde D_t = \E_R \tilde D_1$
+almost surely for all $t\geq1$, and so
 \[
 \frac1P \oosSum{s}{1} (\E_R \tilde D_s)^2 = (\frac1P \oosSum{s}{1} \E_R
-\tilde D_s)^2 \quad \text{a.s..}
+\tilde D_s)^2 \quad \text{a.s.}
 \]
@@
 \[
-\lVert \frac1P \wall\oosSum{s}{1} [(\E_RD_{sR})^2 - (\E_R \tilde D_s)^2] \rVert_1
-\\ \leq \frac1P \oosSum{s}{1} \lVert \E_RD_{sR} - \E_R \tilde D_s \rVert_2 \lVert
+\lVert \frac1P \oosSum{s}{1} [(\E_RD_{sR})^2 - (\E_R \tilde D_s)^2] \rVert_1
+\wall \leq \frac1P \oosSum{s}{1} \lVert \E_RD_{sR} - \E_R \tilde D_s \rVert_2 \lVert
 \E_RD_{sR} + \E_R \tilde D_s \rVert_2
@@
 \end{equation*}
-and note that $\{Z_{1t}^2 \frac{P\gamma}{b_T}\}$ and $\{Z_{2t}^2
-\frac{P\gamma}{b_T}\}$ are uniformly integrable.  As in the proof of Theorem
+and note that $\{Z_{1t}^2 \frac{P\gamma}{b}\}$ and $\{Z_{2t}^2
+\frac{P\gamma}{b}\}$ are uniformly integrable.  As in the proof of Theorem
 \ref{res-confidence-intervals}, we can assume that there is a constant
 $C$ such that $Z_{1t}$ and $Z_{2t}$ are bounded in absolute value by
-$C\sqrt{\frac{b_T}{P\gamma}}$; uniform integrability ensures that the
+$C\sqrt{\frac{b}{P\gamma}}$; uniform integrability ensures that the
 difference between the unbounded random variables and these truncated
@@
 \end{equation*}
-The proof then holds if we can show that both $U_i$ and $U_i'$ obey
-\lln s.  We'll do so by proving that $\{U_i -\E_R U_i,
-\UFiltration{2i-1}\}$ and $\{U_i' - \E_R U_i', \UFiltration{2i}\}$ are
-$L_2$-mixingales of size $-1/2$ and using the bound $E(\vtSumr (U_i -
-\E_R U_i))^2 = O(\vtSumr c_i^2)$ where the $c_i$ are the mixingale
-magnitude indices \citep{mcleish_maximal_1975}.
+The proof then holds if we can show that both $U_i$ and $U_i'$ obey \lln
+s.  We'll do so by proving that $\{U_i -\E_R U_i, \UFiltration{2i-1}\}$
+and $\{U_i' - \E_R U_i', \UFiltration{2i}\}$ are $L_2$-mixingales; the
+result then follows from \citepos{davidson_l1-convergence_1993}
+mixingale \lln.  The proof is the same for both, so we'll just present
+it for $U_i$.
 
@@
 \end{equation*}
-establishing part of the mixingale result trivially.  Now fix $i$ and $m >
-0$ and use Lemma \ref{lem-basic-coupling} to define $\tilde{D}_{ts}$
-for each $t =(2i-2)b_T-P+1,\dots,(2i-1)b_T-P$ and $s =
-\max(t+R-b_T,R-\h+1),\dots,\min(t+R+b_T,T)$ such that
+so it suffices to prove that there are constants $c_t$ and $\zeta_m$
+such that $\zeta_m = O(m^{-1/2 - u})$ as $m \to \infty$ for some
+positive $u$, and
+\begin{equation*}
+  \lVert \E( U_i - \E_R U_i \mid \UFiltration{2i-2m-1}) \rVert_2 \leq c_t \zeta_m.
+\end{equation*}
+
+Fix $i$ and $m > 0$ and use Lemma \ref{lem-basic-coupling} to define
+% $\tilde{D}_{ts}$ for each ${t =(2i-2)b_T-P+1},\dots,{(2i-1)b_T-P}$ and $s =
+% \max(t+R-b_T,R+1),\dots,\min(t+R+b_T,T)$
+such that 
 \begin{equation*}
@@
   \tilde Z_{1t} = \frac1{\sqrt{P\gamma}} \sum_{l=\vttLower}^{\vttUpper}
-  (\tilde D_{t,t+l+R} - \E_R\tilde D_{t,t+l+R})\ W(l/\gamma), \\
+  (\tilde D_{t,t+l+R} - \E_R\tilde D_{t,t+l+R}) W(\frac{l}{\gamma}), \\
 \end{equation*}
@@
 \tilde Z_{2t} = \frac1{\sqrt{P\gamma}} \sum_{j=\vttLower}^{\vttUpper}
-    (\tilde D_{t,t+l+R} - \E_R\tilde D_{t,t+l+R})\ \kernelB{j/\gamma}.
+    (\tilde D_{t,t+l+R} - \E_R\tilde D_{t,t+l+R})\kernelB{\frac{j}{\gamma}}.
 \end{equation*}
@@
   - \E_R Z_{1t}Z_{2t} \rVert_2 \return \\
-%  \leq \vtSuma (\wall \lVert \wall \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
-%  - \E(\tilde{Z}_{1t}\tilde{Z}_{2t} \mid \UFiltration{2i-2m-1}) \rVert_2\return
-%  \\ + \lVert \E_R Z_{1t}Z_{2t} - \E_R \tilde{Z}_{1t}\tilde{Z}_{2t}
-%  \rVert_2)\return \\
+  \leq \vtSuma (\wall \lVert \wall \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
+  - \E(\tilde{Z}_{1t}\tilde{Z}_{2t} \mid \UFiltration{2i-2m-1}) \rVert_2\return
+  \\ + \lVert \E_R Z_{1t}Z_{2t} - \E_R \tilde{Z}_{1t}\tilde{Z}_{2t}
+  \rVert_2)\return \\
   \leq 2 \vtSuma \lVert Z_{1t} Z_{2t} - \tilde Z_{1t} \tilde{Z}_{2t}
@@
 \begin{equation*}
-  2 C \wall \sqrt{\frac{b_T}{P \gamma}} \vtSuma \lVert Z_{1t} - \tilde{Z}_{1t} \rVert_2 \\ \leq
-  \frac{4C \sqrt{b_T}}{P\gamma} \vtSuma \sum_{l=\vttLower}^{\vttUpper} \lVert
-  D_{t+l+R,R} - \tilde{D}_{t,t+l+R} \rVert_2 W(l/\gamma) \\
-  \leq O(\frac{\sqrt{b_T}}{P\gamma}) \vtSuma
-  \sum_{l=\vttLower}^{\vttUpper} \couplingBeta{t+l-(2i-2m-1)b_T+P}\\
-  = O(\frac{\sqrt{b_T}}{P\gamma}) O(b_T^{\frac32-u}\, m^{-\frac12-u})
-\end{equation*}
-for some positive $u$.  The same argument holds for $Z_{2t}$.
-As a result,
-\[
-E(\vtSumr (U_i - \E_R U_i))^2 = o(\vtSumr \frac{b_T^2}{P\gamma}) =
-o(\frac{3P}{2b_T} \frac{b^2}{P\gamma}) = o(\frac{b_T}{\gamma}) \to 0,
-\]
-as required.
+  \vtSuma \lVert Z_{1t} - \tilde{Z}_{1t} \rVert_2 \\ \leq
+  \frac2{\sqrt{P\gamma}} \vtSuma \sum_{l=\vttLower}^{\vttUpper} \lVert
+  D_{t+l+R,R} - \tilde{D}_{t,t+l+R} \rVert_2 W(\frac{l}{\gamma}) \\
+  \leq O(\frac1{\sqrt{P\gamma}}) \vtSuma
+  \sum_{l=\vttLower}^{\vttUpper} \couplingBeta{t+l-(2i-2m-1)b+P}.
+\end{equation*}
+The double summation is $O(b_T^{\frac32} \, m^{-\frac12-u})$ for some
+positive $u$ by construction.  The same argument holds for $Z_{2t}$,
+completing the proof.
 \end{proof}
-
-\begin{proof}[Proof of Theorem~\ref{res:ftest}]
-  To clean up the notation, we'll write $\theta_1$ as $\theta$ and
-  $q_{K_2-K_1,T-K_2}(1-\alpha)$ as $q_\alpha$.  Let
-  $(\hat{\theta}, \hat{\psi})$ denote the \ols\ coefficient estimator
-  using the full model and let 
-  \[\hat\tau^2 = \frac{1}{T-K_2}\sum_{t=0}^{T-1} (y_{t+1} - x_{1t}'\hat{\theta} -
-  x_{2t}'\hat{\psi})^2. \] Since the regressors are orthogonal,
-  $\hat\theta$ also is the \ols\ estimator of $\theta$ using the
-  restricted model.  The difference between the two models'
-  generalization error is
-\[
-E_T \bar D_2 = \sum_{j=K_1+1}^{K_2} [\psi_j^2 - (\hat{\psi}_j - \psi_j)^2]
-\]
-For any $\hat{\theta}$, $E_T \bar D_2$ equals zero when
-$\hat{\psi}$ lies on the surface of the hypersphere centered at
-$\psi$ with radius $|\psi|_2$, and $E_T \bar D_2$ and is greater
-than zero when $\hat{\psi}$ lies outside that sphere.
-Also, the rejection region in $\Re^{K_2}$ for is the set of values of $\hat{\psi}$
-on or beyond the sphere
-\[
-\hat{\psi}'\hat{\psi} = \hat{\tau}^2 q_\alpha \frac{K_2-K_1}{T}.
-\]
-
-We can get a lower bound for the probability
-\[\Pr[F \geq q_\alpha \mid E_T \bar{D}_2 \leq 0]\]
-by rewriting $\hat{\psi}$ in spherical coordinates re-centered at
-$\psi$: $(\hat{r}, \hat{\omega}_1, \dots,
-\hat{\omega}_{K_2-K_1-1})$, with 
-\[\hat{r} = |\hat{\psi} - \psi|_2 \\
-\hat{\omega}_{i} = \tan^{-1}(\frac{(\sum\nolimits_{j=K_1+i+1}^{K_2}(\hat{\psi}_j -
-    \psi_j)^2)^{\frac12}}{\hat{\psi}_{K_1+i} - \psi_{K_1+i}}), \quad
-  i=1,\dots,K_2-K_1-2, \\
-\hat{\omega}_{K_2-K_1-1} =\atan(\hat{\psi}_{K_2-K_1} - \psi_{K_2-K_1},
-  \hat{\psi}_{K_2-K_1-1}- \psi_{K_2-K_1-1} )
-\]
-and
-\[
-\atan(a, b) \equiv 
-\begin{cases}
-\tan^{-1}(a/b) & a > 0 \\
-\pi + \tan^{-1}(a/b) & a < 0, b \geq 0 \\
--\pi + \tan^{-1}(a/b) & a < 0, b < 0 \\
-\pi/2 & a = 0, b > 0 \\
-- \pi/2 & a = 0, b < 0 \\
-\text{undefined} & a = 0, b = 0.
-\end{cases}
-\]
-Note that $\hat{\omega}_1,\dots,\hat{\omega}_{K_2-K_1 - 2} \sim
-\operatorname{uniform}(-\pi/2, \pi/2)$ and
-$\hat{\omega}_{K_2-K_1-1}\sim \operatorname{uniform}(-\pi, \pi)$.
-Under this coordinate system, the acceptance region is centered at
-$(|\psi|_2, \tilde{\omega}_1, \dots, \tilde{\omega}_{K_2-K_1-1})$ with
-\[
-\tilde{\omega}_i = \tan^{-1}([\sum_{j=i+1}^{K_2-K_1}
-  (\psi_j/\psi_i)^2]^{\frac12}) \quad \text{for } i = 1,\dots,K_2-2,\\
-\tilde{\omega}_{K_2-K_1-1} = \atan(\psi_{K_2-K_1}, \psi_{K_2-K_1-1}).
-\]
-
-If $\psi$ lies outside the acceptance region of the F-test, that
-acceptance region is contained in the cone
-\[\{(r, \omega_1,\dots,\omega_{K_2-1}) : r \geq 0,\, \tilde{\omega}_{i}
-- \xi \leq \omega_i \leq \tilde{\omega}_i + \xi\}\]
-with
-\[
- \xi = \sin^{-1}(\frac{\hat{\tau}}{|\psi|_2}\sqrt{\frac{q_\alpha (K_2-K_1)}{T}})
-\] 
-for $\hat{\tau}^2$ given.\footnote{This setup assumes that
-  $[\tilde\omega_i - \xi, \tilde\omega_i + \xi] \subset
-  [-\pi/2,\pi/2]$ for each $i$.  If not, the region can be rotated
-  without changing the results.}
-
-As a result,
-\[
-\Pr[F \geq q_{\alpha}\wall \mid E_T \bar{D}_2 \leq 0] = 
-\Pr[\hat{\psi}'\hat{\psi} \geq \hat \tau^2 q_\alpha \frac{K_2 - K_1}{T}
-\mid |\hat{\psi}-\psi|_2 \geq |\psi|_2] \\
-\geq 1 - \E(\Pr\{ \hat{\omega}_i \in [\tilde{\omega}_i - \xi, \tilde{\omega}_i +
-\xi] \ \forall i  \mid \hat{\tau}^2,
-|\hat{\psi}-\psi|_2 \geq |\psi|_2\} 
-\mid |\hat{\psi}-\psi|_2 \geq |\psi|_2)\quad a.s. \\ 
-= 1 - \frac12 E ((2\xi / \pi)^{K_2-K_1-1}\mid
-|\hat{\psi}-\psi|_2 \geq |\psi|_2)\quad a.s. \\
-= 1 - \frac12 E (2\xi/\pi)^{K_2-K_1-1} \quad a.s..
-\]
-The second equality holds because the $\hat{\omega}_i$s are uniform
-and the third holds because $\hat{\tau}$ is independent of
-$\hat{\psi}$ under normality.
-
-Now~\eqref{eq:ftestreject1} holds since $\xi \to 0$ almost surely as
-$\phi_2 \to \infty.$  Moreover, as
-$T\to\infty$, $\hat{\tau}^2\to^p\tau^2$ and $q_{\alpha}\to 1$, so
-$\plim \xi < \frac{\pi}{2}$.  Consequently,
-$(\frac{2\xi}{\pi})^{K_2-K_1-1}\to^p0$, proving~\eqref{eq:ftestreject2}.
-\end{proof}
-\bibliographystyle{abbrvnat}
 \bibliography{../../texlibrary.bzr/main}
-
-\begin{table}[b]
- \begin{multicols}{2}
+\clearpage
+
+\begin{table}
+  \centering
   \begin{itemize}
@@
   \end{itemize}
- \end{multicols}
   \caption{Variables used in Section \ref{sec:empirics} and by Goyal
-   and Welch (2008) to predict the equity premium.  Please see Goyal
-   and Welch's original paper
-   for a detailed description of each variable.}
+    and Welch (2008) to predict the equity premium.  Please see their
+    original paper for a detailed description of each variable.}
   \label{tab:equity}
 \end{table}
-
-\begin{table}[!tbp]
- \begin{center}
- \begin{tabular}{lrrrr}\hline\hline
-\multicolumn{1}{l}{waldtest}&\multicolumn{1}{c}{Res.Df}&\multicolumn{1}{c}{Df}&\multicolumn{1}{c}{F}&\multicolumn{1}{c}{Pr(\textgreaterF)}\tabularnewline
-\hline
-1&69&&&\\
-2&81&$-$12&3.4&0.00066 \\
-\hline
+\input{empirics/tables/coeftest}
+\input{empirics/tables/waldtest}
+
+\begin{table}
+  \centering
+  \begin{tabular}{c|r|r|r|r|r}
+  Variable & \multicolumn{5}{l}{Values}
+  \\\hline
+  $T$   & 120 & 160 & 240 & 600 & 1200 \\
+  $k_0$ &   2 & \multicolumn{1}{c}{$T/20$} \\
+  $k$   &   3 &  10 & \multicolumn{1}{c}{$T/10$} \\
+  $\thetanorm$ & 0.0 & 0.1 & 0.2
   \end{tabular}
-\caption{Wald test for the null hypothesis that all of the
-  coefficients in Goyal and Welch's (2008) ``kitchen sink'' model are
-  zero, except for the intercept, using the Newey-West
-  variance-covariance matrix.  The p-value is calculated from the $F$
-  distribution.\label{tab:gwinsample}}
-\end{center}
+  \caption{Parameters for Monte Carlo design.}
+  \label{tab:mc-parameters}
 \end{table}
-
 \clearpage
@@
 \centering
-\textbf{\large{Simulated Coverage of One-Sided DMW Interval for $E_R\bar D_1$}}
-\includegraphics{mc/plots/interval-testerror1}
-\textbf{\large{Simulated Coverage of Two-Sided DMW Interval for $E_R\bar D_1$}}
-\includegraphics{mc/plots/interval-testerror2}
+\includegraphics{mc/plots/interval-002}
 \caption{Simulated coverage of $E_R \bar D_1$ at 90\% confidence using
-a one- and two-sided intervals based on the \protect\textsc{dmw} \protect\textsc{oos}
-test, plotted as a function of the fraction of observations used in
-the test sample, $P/T$.  The solid horizontal line denotes the
-intervals' nominal coverage.}
- \label{fig:interval-R}
+a one-sided interval the naive \oos $t$ distribution.}
 \end{figure}
@@
 \centering
-\textbf{\large{Simulated Coverage of One-Sided DMW Interval for $E_T\bar D_2$}}
-\includegraphics{mc/plots/interval-generror1}
-\textbf{\large{Simulated Coverage of Two-Sided DMW Interval for $E_T\bar D_2$}}
-\includegraphics{mc/plots/interval-generror2}
-\caption{Simulated coverage of $E_T \bar D_2$ at 90\% confidence using
-a one- and two-sided intervals based on the \protect\textsc{dmw} \protect\textsc{oos}
-test, plotted as a function of the fraction of observations used in
-the test sample, $P/T$.  The solid horizontal line denotes the
-intervals' nominal coverage.}
-\label{fig:interval-T}
+\includegraphics{mc/plots/interval-003}
+\caption{Simulated coverage of $E_R \bar D_1$ at 90\% confidence using
+a two-sided interval based on the naive \oos $t$ distribution.}
 \end{figure}
 \clearpage
-
 \begin{figure}
 \centering
-  \textbf{\large{Simulated Rejection Probability of F-test Under $E_T
-      \bar{D}_2 \leq 0$}}
+\includegraphics{mc/plots/interval-004}
+\caption{Simulated coverage of $E_T \bar D_2$ at 90\% confidence using
+a one-sided interval the naive \oos $t$ distribution.}
+\end{figure}
+\clearpage
+\begin{figure}
+\centering
+\includegraphics{mc/plots/interval-004}
+\caption{Simulated coverage of $E_T \bar D_2$ at 90\% confidence using
+a two-sided interval based on the naive \oos $t$ distribution.}
+\end{figure}
+\clearpage
+\begin{figure}
+\centering
+\includegraphics{mc/plots/interval-005}
+\caption{Simulated coverage of $E_T \bar D_2$ at 90\% confidence using
+a two-sided interval based on the naive \oos $t$ distribution.}
+\end{figure}
+\clearpage
+
+\setkeys{Gin}{width=5.5in}
+\begin{figure}
+\centering
+\includegraphics{empirics/plots/oos-mse-1}
+\label{fig:oosmseI}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{empirics/plots/oos-mse-1b}
+\label{fig:oosmseII}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{empirics/plots/oos-mse-2}
+\label{fig:oosmseIII}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{empirics/plots/oos-mse-2b}
+\label{fig:oosmseIV}
+\end{figure}
+
+\newcommand{\circlefig}[2]{
+  \begin{tikzpicture}
+    % rejection region for F-test
+    \draw (0,0) circle (#1);
+    % circle of equal generalization error
+    \draw (1,1) let \p1=(1,1) in circle({veclen(\x1,\y1)});
+    \fill [black] (1,1) circle (2pt) node[right] {$(\theta_1,\theta_2)$};
+    \draw (1,1)--(0,0);
+    % axes
+    \draw[->] (0,0)--(#2,0) node[right] {$\hat\theta_1$};
+    \draw[->] (0,0)--(0,#2) node[above] {$\hat\theta_2$};
+  \end{tikzpicture}
+}
+
+\begin{figure}
+  \centering
+  \begin{tabular}{cc}
+  \subfloat[]{\circlefig{3}{2.5}\label{fig:circleO}} &
+  \subfloat[]{\circlefig{2}{2.5}\label{fig:circleA}}  \\
+  \subfloat[]{\circlefig{1}{2.5}\label{fig:circleB}}  &
+  \subfloat[]{\circlefig{.3}{2.5}\label{fig:circleC}} 
+  \end{tabular}
+\caption{Curves indicating the rejection region and region of equal
+  generalization error for the models dicsussed in Section
+  \ref{sec:insample}.  The smaller model has no estimated parameters
+  and the larger has two coefficients.}\label{fig:rreject}
+\end{figure}
+
+\setkeys{Gin}{width=6.5in}
+\begin{figure}
+  \centering
   \includegraphics{mc/plots/ftest-001}
-  \caption{Simulated rejection probabilities for the F-test given
-    $\E_T \bar{D}_2 \leq 0$ with nominal size 10\%.  Values greater
-    than 10\% indicate that the test rejects the benchmark model too
-    often.  See Section~\ref{sec:simulation-design} for a discussion
-    of the simulation design.}
+  \caption{Simulated rejection probabilities for the F-test given $\E_T
+    \bar{D}_2 \leq 0$ with nominal size 10\%.  Values greater than
+    10\% indicate that the test is rejecting the benchmark model too
+    often.  See Section~\ref{sec:simulation-design} for a discussion of
+    the simulation design.}
   \label{fig:ftest}
@@
   \centering
-  \textbf{\large{Simulated Rejection Probability of DMW Test Under $E_T
-      \bar{D}_2 \leq 0$}}
-  \includegraphics{mc/plots/size-dmwsize}  
-  \caption{Simulated rejection probabilities for the \protect\textsc{dmw}
-    \protect\textsc{oos} $t$-test given $\E_T \bar{D}_2 \leq 0$ with nominal
-    size 10\%.  Values greater than 10\% indicate that the test
-    rejects the benchmark model too often.  The solid horizontal line
-    indicates the nominal rejection probability.  See
-    Section~\ref{sec:simulation-design} for a discussion of the
-    simulation design.}
-  \label{fig:ttest-size}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \textbf{\large{Simulated Rejection Probability of Clark and West
-      (2006, 2007) Test Under $E_T \bar{D}_2 \leq 0$}}
-  \includegraphics{mc/plots/size-clarkwest}
-  \caption{Simulated rejection probabilities for Clark and West's
-    (2006, 2007) \protect\textsc{oos} test statistic given $\E_T \bar{D}_2
-    \leq 0$ with nominal size 10\%.  Values greater than 10\% indicate
-    that the test rejects the benchmark model too often.  The solid
-    horizontal line indicates the nominal rejection probability.  See
+  \includegraphics{mc/plots/size-002}
+   \caption{Simulated rejection probabilities for
+     Clark and West's (2006, 2007) test
+     statistic given $\E_T \bar{D}_2 \leq 0$ with nominal size 10\%.
+     Values greater than 10\% indicate that the test is rejecting the
+     benchmark model too often.  See
      Section~\ref{sec:simulation-design} for a discussion of the
@@
   \centering
-  \textbf{\large{Simulated Rejection Probability of McCracken (2007)
-      Test \\ Under $E_T \bar{D}_2 \leq 0$}}
-  \includegraphics{mc/plots/size-mccracken}
-  \caption{Simulated rejection probabilities for McCracken's (2007)
-    \protect \textsc{oos} test statistic given $\E_T \bar{D}_2 \leq 0$ with
-    nominal size 10\%.  Values greater than 10\% indicate that the
-    test rejects the benchmark model too often.  The solid horizontal
-    line indicates the nominal rejection probability.  See
-    Section~\ref{sec:simulation-design} for a discussion of the
-    simulation design.}
+  \includegraphics{mc/plots/size-003}
+   \caption{Simulated rejection probabilities for the \oost\ statistic
+     with McCracken's (2007) critical values, given
+     $\E_T \bar{D}_2 \leq 0$ with nominal size 10\%.  Values greater
+     than 10\% indicate that the test is rejecting the benchmark model
+     too often.  See Section~\ref{sec:simulation-design} for a
+   discussion of the simulation design.}
   \label{fig:mccracken}
@@
   \centering
-  \textbf{\large{Simulated Rejection Probability of DMW Test Under $E_T
-      \bar{D}_2 > 0$}}
-  \includegraphics{mc/plots/size-dmwpower}
-  \caption{Simulated rejection probabilities for the \protect \textsc{dmw}
-    \protect\textsc{oos} $t$-test given $\E_T \bar{D}_2 > 0$ with nominal
-    size 10\%.  Values greater than 10\% indicate that the test
-    rejects the benchmark model too often.  The solid horizontal line
-    indicates the nominal rejection probability.  See
+  \includegraphics{mc/plots/size-004}  
+  \caption{Simulated rejection probabilities for the naive \oost\
+    statistic given $\E_T
+    \bar{D}_2 \leq 0$ with nominal size 10\%.  Values greater than
+    10\% indicate that the test is rejecting the benchmark model too
+    often.  See Section~\ref{sec:simulation-design} for a discussion of
+    the simulation design.}
+  \label{fig:ttest-size}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics{mc/plots/size-005}
+  \caption{Simulated rejection probabilities for the naive \oost\
+    statistic given $\E_T \bar{D}_2 > 0$ with nominal size 10\%.
+    Values less than 10\% indicate that the test does not reject the
+    benchmark model often enough.  See
     Section~\ref{sec:simulation-design} for a discussion of the
@@
 
-\begin{figure}
-\centering
-\textbf{\large{Difference in OOS MSE of Prevailing Mean and\\ Kitchen
-    Sink Models of Equity Premium (OLS)}}
-\includegraphics{empirics/plots/oos-mse-1}
-\includegraphics{empirics/plots/oos-mse-1b}
-\caption{\protect \textsc{oos} difference in the \protect\textsc{mse}
-  of the prevailing mean benchmark and the kitchen sink model as a
-  function of the test sample size, $R$.  Both models forecast the
-  equity premium using annual data from 1928--2008.  The solid line
-  gives the \protect \textsc{oos} average, and the shaded region indicates the
-  one-sided 95\% confidence interval implied by the \protect
-  \textsc{dmw} test.  The bottom panel is a detailed view of the top
-  panel for $R \geq 50$.}
-\label{fig:empirics1}
-\end{figure}
-
-\begin{figure}
-\centering
-\textbf{\large{Difference in OOS MSE of Prevailing Mean and\\ Kitchen
-    Sink Models of Equity Premium (CT)}}
-\includegraphics{empirics/plots/oos-mse-2}
-\includegraphics{empirics/plots/oos-mse-2b}
-\caption{\protect \textsc{oos} difference in the \protect\textsc{mse}
-  of the prevailing mean benchmark and the kitchen sink model as a
-  function of the test sample size, $R$.  Both models forecast the
-  equity premium using annual data from 1928--2008.  The solid line
-  gives the \protect \textsc{oos} average, and the shaded region indicates the
-  one-sided 95\% confidence interval implied by the \protect
-  \textsc{dmw} test.  The bottom panel is a detailed view of the top
-  panel for $R \geq 50$.}
-\label{fig:empirics2}
-\end{figure}
-
-\begin{figure}
-\centering
-\textbf{\large{OOS MSE of Individual Forecasts of Equity Premium}}
-\includegraphics{empirics/plots/oos-ind-ks}
-\includegraphics{empirics/plots/oos-ind-pm}
-\caption{\protect{\textsc{oos} \textsc{mse} of the Prevailing Mean (\textsc{pm}) and
-    Kitchen Sink (\textsc{ks}) models for equity premium prediction as
-    a function of the size of the training sample, $R$.  Please note
-    that the vertical scales are different in the two plots.}}
-\label{fig:empirics3}
-\end{figure}
-
 \end{document}
@@
 
-% LocalWords: LM clark meese diebold chao corradi mccracken giacomini lm jel iR
-% analyses inoue datasets huber efron anova akritas
-% calhoun iR berbee th de nondifferentiable jong
-% mixingales mcleish AIC Berbee's merlevede Heyde's ib
-% mixingaleR TP eq dx dy tex tR tS tT iT sR sw tw vw
-% reestimate davidson over-reject anatolyev Anatolyev's iS izx
-% coefpart normalpart Jong's jt oos underrejects cltvar Scwarz JEL
-% hansen lm McCracken's jel RSQLite elemstatlearning rproject rsqlite
-% LocalWords:  McCracken's kilian anatolyev rossi REStud JAppliedEconometrics
-% LocalWords:  goyal welch rfs reputational calhoun Berbee's mixingales tR tS
-% LocalWords:  Heteroskedasticity Autocorrelation tT iT th berbee iS de dx ixz
-% LocalWords:  DMW mcleish sR eq ftestreject lightgray veclen RSQLite zeileis
-% LocalWords:  heteroskedasticity hothorn RNews JStatSoftware harrell campbell
-% LocalWords:  thompson bivariate Welch's multicollinearity Newey newey tw vw
-% LocalWords:  merlevede cltvar dR Scwarz davidson indices lrrrr waldtest Df
-% LocalWords:  dmw McCracken MSE OLS mse
+% LocalWords:  LM clark meese diebold chao corradi mccracken giacomini analyses
+% LocalWords:  inoue datasets huber efron anova akritas calhoun iR berbee th de
+% LocalWords:  nondifferentiable jong mixingales mcleish AIC Berbee's merlevede
+% LocalWords:  Heyde's ib mixingaleR mixingaleT TP eq dx dy tex tR tS tT iT sR
+% LocalWords:  sw tw vw reestimate davidson overreject anatolyev Anatolyev's iS
+% LocalWords:  izx coefpart normalpart Jong's jt oos overrejects overrejection
+% LocalWords:  underrejects cltvar Scwarz JEL hansen lm McCracken's jel RSQLite
+% LocalWords:  elemstatlearning rproject rsqlite

### 2012-03-30 R/ResultsFrame.R

@@ -1,0 +1,22 @@
+## The function 'ResultsFrame' takes a string that contains the text
+## for an SQL query and returns a dataframe giving its results and
+## adding ordered factors that label the coefficient values, number of
+## observations, and number of regressors.
+setGeneric("ResultsFrame", function(object,...) standardGeneric("ResultsFrame"))
+setMethod("ResultsFrame", "character",
+          function(object,...) {
+            nlabel <- dbGetQuery(dbc, "select distinct nlabel from nobs order by n;")$nlabel
+            altlabel <- dbGetQuery(dbc, "select distinct altlabel from nobs order by kAlt;")$altlabel
+            nulllabel <- dbGetQuery(dbc, "select distinct nulllabel from nobs order by kNull;")$nulllabel
+            normlabel <- dbGetQuery(dbc, "select distinct normlabel from coefficients order by norm;")$normlabel
+            d <- dbGetQuery(dbc, paste("select * from (", object, ") s, pars p ",
+                                       "on s.isim = p.isim and s.idgp = p.idgp;"))
+            d$ntotal <- d$n
+            k0 <- ordered(d$nulllabel, nulllabel)
+            ka <- ordered(d$altlabel, altlabel)
+            d$k <- k0:ka
+            d$b <- ordered(d$normlabel, normlabel)
+            d$n <- ordered(d$nlabel, nlabel)
+            subset(d, select = c(-isim, -idgp, -nlabel, -kNull, -nulllabel, -kAlt, 
+                        -altlabel, -norm, -normlabel))
+          })

### 2012-03-30 empirics/goyal-code/CalcOOS.m

@@ -1,0 +1,43 @@
+function OOS=CalcOOS(N,Eunc,Eols,K,dBeg,dEnd,fBeg)
+% function OOS=CalcOOS(Eunc,Eols,dBeg,dEnd,fBeg)
+% -------------------------------------------------------------------------
+% Inputs
+% N is the regression lag-1 for next period prediction, more for multi-year
+% Eunc and Eols are errors
+% dBeg, dEnd, and fBeg should be numbers like 50, 89, and 123
+% K is the number of variables in X
+% -------------------------------------------------------------------------
+% Outputs
+% OOS is output
+% -------------------------------------------------------------------------
+
+load CrtVal; % Diebold Marianno
+E1=Eunc; E2=Eols;
+E1sq=E1.^2; E2sq=E2.^2;
+R=fBeg-dBeg; P=dEnd-fBeg+1; pi=P/R;
+
+d=E1sq-E2sq;
+dbar=mean(d);
+Q2=0;
+for ii=-(N-1):(N-1)
+    absii=abs(ii);
+    Q2=Q2+(N-absii)/N*sum((d(absii+1:end)-dbar).*(d(1:end-absii)-dbar));
+end
+Q2=Q2/P;
+OOS_T=sqrt(P+1-2*N+N*(N-1)/P)*dbar/sqrt(Q2);
+%OOS_T=sqrt(P-N+1)*dbar/sqrt(Q2);
+OOS_F=(P-N+1)*(mean(E1sq)-mean(E2sq))/mean(E2sq);
+ENC_NEW=(P-N+1)*(mean(E1sq)-mean(E1.*E2))/mean(E2sq);
+lambd=(Eunc-Eols)\Eunc;
+
+CrtVals=[interp1(Crtpi,OOS_T_90(K,:),pi) ...
+        interp1(Crtpi,OOS_T_95(K,:),pi)  ...
+        interp1(Crtpi,OOS_T_99(K,:),pi)  ...
+        interp1(Crtpi,OOS_F_90(K,:),pi) ...
+        interp1(Crtpi,OOS_F_95(K,:),pi) ...
+        interp1(Crtpi,OOS_F_99(K,:),pi) ...
+        interp1(Crtpi,ENC_NEW_90(K,:),pi) ...
+        interp1(Crtpi,ENC_NEW_95(K,:),pi) ...
+        interp1(Crtpi,ENC_NEW_99(K,:),pi)];
+OOS=[OOS_T OOS_F ENC_NEW lambd CrtVals];
+return;

### 2012-03-30 empirics/goyal-code/myols.m

@@ -1,0 +1,22 @@
+function [bols,varOls,varNwest,adjr2,var_e]=myols(x,y)
+% function [bols,varOls,varNwest,adjr2,var_e]=myols(x,y)
+
+[T k]=size(x);
+bols=x\y;
+e=y-x*bols;
+Q=inv(x'*x);
+lag=floor(4*((T/100)^(2/9)));
+v=e.^2;
+v=x'*(x.*v(:,ones(k,1)));
+for i=1:lag
+   v1=e(1+i:T).*e(1:T-i);
+   v1=x(1+i:T,:)'*(x(1:T-i,:).*v1(:,ones(k,1)));
+   v=(1-i/(lag+1))*(v1+v1') + v;
+end
+varNwest=Q*v*Q*T/(T-k); 
+varOls=((e'*e)/(T-k))*Q;
+
+r2=1-var(e)/var(y);
+adjr2=(1-k)/(T-k)+(T-1)*r2/(T-k);
+var_e=(e'*e)/(T-k);
+return;

### 2012-03-30 mc/confidenceIntervals-pop.R

@@ -1,73 +1,0 @@
-### Simulation to calculate probability of choosing worse-forecasting larger model.
-
-### initialize
-rm(list = ls())
-set.seed(5700)
-library(lattice)
-library(fixedWindow)
-
-### set coefficient values to use for simulation
-rootVCV <- matrix(c(sqrt(10.505), 0, 1.036 / sqrt(10.505),
-                    sqrt(0.366 - 1.036^2 / 10.505)), 2, 2)
-B <- matrix(c(2.237, 0.261, 3.363, 0.000,-0.633, 0.000,-0.377, 0.000,-0.529,
-              0.000, 0.000, 0.804, 0.000,-0.221, 0.000, 0.226, 0.000,-0.205), 
-            byrow = T, nrow = 2)
-
-levelvec <- c(0.90, 0.95, 0.99)
-## column 1 - R values
-## column 2 - P values
-windowmat <- matrix(c(50,  50, 100, 100, 100, 200, 200, 200,
-                      25,  50,  25,  50, 100,  25,  50, 100), ncol=2)
-evalwindow <- 30
-ndraw <- evalwindow + max(rowSums(windowmat))
-
-realPerformance <- rep(NA, (nsims <- 1500) * dim(windowmat)[1])
-ciCal <- ciCW <- ciMc <-
-  matrix(NA, length(realPerformance), length(levelvec))
-
-for (i in 1:nsims) {
-  cat("Simulation", i, "of", nsims, "\n")
-  ## draw a random dataset
-  d.i <- rData1(ndraw, B, rootVCV)
-  ## loop over values of R and P
-  for (j in 1:dim(windowmat)[1]) {
-    ij <- j + (i-1) * dim(windowmat)[1]
-
-    R.ij <- windowmat[j,1]
-    P.ij <- windowmat[j,2]
-
-    preds0.ij <- forecast0(R.ij, P.ij, d.i)
-    predsA.ij <- forecastA(R.ij, P.ij, d.i)
-    target.ij <- d.i[1:P.ij + R.ij,1]
-
-    realPerformance[ij] <- mean((d.i[R.ij+P.ij + 1:evalwindow,1] -
-                                 forecast0(R.ij+P.ij, evalwindow, d.i))^2 -
-                                (d.i[R.ij+P.ij + 1:evalwindow,1] -
-                                 forecastA(R.ij+P.ij, evalwindow, d.i))^2)
-
-    ## loop over confidence levels
[…]

### 2012-03-30 mc/cw_eloss.R

@@ -1,18 +1,0 @@
-cw.eloss <- function(coef) {
-  F <- matrix(0, 10, 10)
-  F[1,1] <- 0.261
-  F[2:5,1:4] <- diag(4)
-  F[6,6] <- 0.804
-  F[6,7] <- -0.221
-  F[6,8] <- 0.226
-  F[6,9] <- -0.205
-  F[7:10,6:9] <- diag(4)
-
-  mu <- 2.237 / (1 - 0.261)
-  
-  Q <- matrix(0, 10, 10)
-  Q[c(1,6),c(1,6)] <- c(10.505, 1.036, 1.036, 0.366)
-  S <- matrix(solve(diag(100) - kronecker(F, F), c(Q)), 10, 10)
-  c(1, - coef[2:5], 0, -coef[6:9]) %*% S %*% c(1, - coef[2:5], 0, -coef[6:9]) +
-    (coef[1] - (1 - sum(coef[2:5])) * mu)^2
-}

### 2012-03-30 mc/experiment1.R

@@ -1,44 +1,0 @@
-library(lattice)
-rm(list = ls())
-
-rootVCV <- matrix(c(sqrt(10.505), 0, 1.036 / sqrt(10.505),
-sqrt(0.366 - 1.036^2 / 10.505)), 2, 2)
-B <- matrix(c(2.237, 0.261, 3.363, 0.000,-0.633, 0.000,-0.377, 0.000,-0.529,
-              0.000, 0.000, 0.804, 0.000,-0.221, 0.000, 0.226, 0.000,-0.205), 
-            byrow = T, nrow = 2)
-
-set.seed(5343)
-source("mcFunctions.R")
-n <- c(80, 120, 240, 480)
-Rratio <- c(1/4, 1/2, 3/4, 9/10)
-
-minwindow <- 20
-lossFrame <- cbind(expand.grid(R = paste(Rratio,"n"), sim = 1:(nsims <- 400), n = n),
-                   mFull1 = NA, mFull2 = NA, mTrain1 = NA, mTrain2 = NA)
-
-for (j in seq(along.with = n)) {
-  for (i in 1:nsims) {
-    cat(n[j], "--", i, "of", nsims, "\n")
-    d.ni <- rData1(n[j], B, rootVCV)
-    lossFrame[(j-1) * nsims * length(Rratio) + (i-1) * length(Rratio) + 1:length(Rratio),
-              c("mFull1", "mFull2")] <- rep(marginalLoss(makeb1(d.ni), makeb2(d.ni), B, rootVCV),
-                                            each = length(Rratio))
-    for (r in seq(along.with = Rratio)) {
-      lossFrame[(j-1) * nsims * length(Rratio) + (i-1) * length(Rratio) + r,
-                c("mTrain1", "mTrain2")] <- marginalLoss(makeb1(d.ni[1:round(Rratio[r] * n[j]),]),
-                                                         makeb2(d.ni[1:round(Rratio[r] * n[j]),]),
-                                                         B, rootVCV)
-    }
-  }
-}
-
-lims1 <- c(2.3, 3)
-xyplot(log(mFull1) ~ log(mTrain1) | n * Rratio, data = lossFrame,
-       xlim = lims1, ylim = lims1, aspect = "fill", pch = 19, cex = 0.1)
-
-histogram(~ log(mFull1) - log(mTrain1) | n * Rratio, data = lossFrame, nint = 180,
[…]

### 2012-03-30 mc/experiment2.R

@@ -1,47 +1,0 @@
-### Runs simulation to generate QQ plots --- examine whether out-of-sample averages are normal.
-
-library(lattice)
-rm(list = ls())
-
-rootVCV <- matrix(c(sqrt(10.505), 0, 1.036 / sqrt(10.505),
-                    sqrt(0.366 - 1.036^2 / 10.505)), 2, 2)
-B <- matrix(c(2.237, 0.261, 0.000, 0.000, 0.000, 0.000, 0.000, 0.000, 0.000,
-              0.000, 0.000, 0.804, 0.000,-0.221, 0.000, 0.226, 0.000,-0.205), 
-            byrow = T, nrow = 2)
-
-set.seed(5343)
-source("mcFunctions.R")
-n <- c(80, 120, 240, 480)
-Rratio <- c(1/4, 1/2, 3/4, 9/10)
-
-calStat <- cbind(expand.grid(R = paste(Rratio,"n"), sim = 1:(nsims <- 400), n = n), rvT = NA, rvR = NA, recT = NA)
-
-for (j in seq(along.with = n)) {
-  Rvec.j <- round(Rratio * n[j])
-  for (i in 1:nsims) {
-    cat(n[j], "-", i, "of", nsims, "\n")
-    d.ji <- rData1(n[j], B, rootVCV)
-    
-    normalStats.ji <- calPop(Rvec.j, d.ji, B, rootVCV)
-    expanding.ji <- recPop(Rvec.j, d.ji, B, rootVCV)
-
-    calStat[(j-1) * nsims * length(Rvec.j) + (i-1) * length(Rvec.j) + 1:length(Rvec.j), "rvT"] <- normalStats.ji[,"T"]
-    calStat[(j-1) * nsims * length(Rvec.j) + (i-1) * length(Rvec.j) + 1:length(Rvec.j), "rvR"] <- normalStats.ji[,"R"]
-
-    calStat[(j-1) * nsims * length(Rvec.j) + (i-1) * length(Rvec.j) + 1:length(Rvec.j), "recT"] <- expanding.ji[,"T"]
-    calStat[(j-1) * nsims * length(Rvec.j) + (i-1) * length(Rvec.j) + 1:length(Rvec.j), "recR"] <- expanding.ji[,"R"]
-  }
-}
-
-qqmath( ~ rvR | n + R, data = calStat, type = "l")
-qqmath( ~ rvT | n + R, data = calStat, type = "l")
[…]

### 2012-03-30 mc/main_table.R

@@ -1,26 +1,0 @@
-source("../R/cw_prederrors.R")
-source("../R/rcw.R")
-library(sandwich)
-
-rvec <- c(80, 120)
-pvec <- c(40, 80, 120, 160)
-
-n <- 1
-n <- 3000
-maxn <- max(rvec) + max(pvec)
-minr <- min(rvec)
-
-teststat <- matrix(NA, n, length(rvec) * length(pvec))
-muR <- matrix(NA, n, length(rvec))
-
-k <- 0
-for (i in 1:n) {
-  d.i <- cw.prederrors(rcw(maxn), R = minr)^2 %*% c(1, -1)
-  for (r in rvec) {
-    for (p in pvec) {
-      stat.irp <- lm(d.i ~ 1, subset = r - minr + 1:p)
-      nw.irp <- NeweyWest(stat.irp)
-    teststat[i,k] <- stat.ik$coef / nw.ik
-  }
-  print(paste("done simulation", i, "of", n))
-}clear

### 2012-03-30 mc/main_table2.R

@@ -1,35 +1,0 @@
-source("../R/cw_prederrors.R")
-source("../R/rcw.R")
-library(sandwich)
-
-rvec <- c(80, 120)
-pvec <- c(40, 80, 120, 160)
-tvec <- unique(c(outer(rvec, pvec, "+")))
-
-n <- 10
-maxn <- max(rvec) + max(pvec)
-minr <- min(rvec)
-
-teststat <- matrix(NA, n * length(rvec) * length(pvec))
-
-j <- 0
-k <- 0
-i <- 1
-mur <- rep(0, length(tvec))
-
-while (i <= n) {
-  d.i <- cw.prederrors(rcw(maxn), R = minr, Tvec = tvec)
-  for (tt in tvec) {
-    
-  for (r in rvec) {
-    ##    mur[j <- j+1] <- 
-    for (p in pvec) {
-      stat.irp <- lm(d.i ~ 1, subset = r - minr + 1:p)
-      teststat[k <- k+1] <- stat.irp$coef / NeweyWest(stat.irp)
-    }
-  }
-  print(paste("done simulation", i, "of", n))
-}
-
-results <- data.frame(t1 = teststat > 1.282
-                      t2 = teststat)

### 2012-03-30 mc/mc-engelwest.R

@@ -1,60 +1,0 @@
-library(fixedWindow)
-set.seed(92)
-
-fstat <- function(y, xo, xa) {
-### xo contains the regressors of the null model (including a constant)
-### xa contains the regressors for the alternative (including a constant).
-  d <- getDimensions(xo, xa)
-
-  eo <- lm.fit(y = y, x = xo)$resid
-  ea <- lm.fit(y = y, x = xa)$resid
-  sum((eo^2 - ea^2)/d$m) / sum(ea^2/(d$n-d$ka))
-}
-
-getDimensions <- function(xo, xa) {
-  if (!is.matrix(xo)) stop("the predictors of the null model must be a matrix")
-  if (!is.matrix(xa)) stop("the predictors of the alternative model must be a matrix")
-  if (! (dim(xa)[1] == dim(xo)[1])) stop("both matrices must have the same number of observations")
-  if (dim(xa)[2] < dim(xo)[2]) stop("the null model must have fewer variables than the alternative.")
-  r <- list(n = dim(xa)[1], ko = dim(xo)[2], ka = dim(xa)[2], m = dim(xa)[2] - dim(xo)[2],
-            cn = (dim(xa)[2] - dim(xo)[2])/(dim(xa)[1] - dim(xa)[2]))
-}
-
-b <- 0.9
-phi <- 0.5
-gam <- 0.5
-
-n <- 100
-nburn <- 1000
-### generate dm_t and dp_t
-
-dm <- rep(0, n + nburn)
-dp <- rep(0, n + nburn)
-ds <- rep(0, n + nburn)
-
-ep <- rnorm(n + nburn)
-em <- rnorm(n + nburn)
-
-for (t in 1:(n+nburn)) {
-  dm[t+1] <- phi * dm[t] + em[t]
-  dp[t+1] <- gam * dp[t] + ep[t]
-
-  ds[t+1] <- phi*(1-b)/(1-b*phi) * dm[t] + 1/(1-b*phi) * em[t] +
-    b*gam/(1-b*gam) * dp[t] + b/((1-b)*(1-b*gam)) * ep[t]
-}
-
-ds    <- ds[nburn + 1:n]
-dmLag <- dm[nburn + 1:n - 1]
-dpLag <- dp[nburn + 1:n - 1]
-
-R <- 50
-P <- n-R
-
-calhounCI(pred0 = mean(ds[1:R]),
[…]

### 2012-03-30 mc/paper_intro.R

@@ -1,36 +1,0 @@
-r2 <- function(n){
-  y <- arima.sim(model = list(ar = 0.1), n + 4, n.start = 500)
-  x <- arima.sim(model = list(ar = 0.3), n + 4, n.start = 500)
-  data.frame(y = y[4 + 1:n], y1 = y[3 + 1:n], y2 = y[2 + 1:n], y3 = y[1 + 1:n], y4 = y[1:n],
-             x = x[4 + 1:n], x1 = x[3 + 1:n], x2 = x[2 + 1:n], x3 = x[1 + 1:n], x4 = x[1:n])
-}
-
-makeerrors <- function(dataset, k, R) {
-  P <- length(dataset$y) - R
-  varmodel <- switch(k,
-                     lm(data = dataset, subset = 1:R, y ~ 1),
-                     lm(data = dataset, subset = 1:R, y ~ y1),
-                     lm(data = dataset, subset = 1:R, y ~ y1 + x1),
-                     lm(data = dataset, subset = 1:R, y ~ y1 + x1 + y2),
-                     lm(data = dataset, subset = 1:R, y ~ y1 + x1 + y2 + x2),
-                     lm(data = dataset, subset = 1:R, y ~ y1 + x1 + y2 + x2 + y3),
-                     lm(data = dataset, subset = 1:R, y ~ y1 + x1 + y2 + x2 + y3 + x3),
-                     lm(data = dataset, subset = 1:R, y ~ y1 + x1 + y2 + x2 + y3 + x3 + y4),
-                     lm(data = dataset, subset = 1:R, y ~ y1 + x1 + y2 + x2 + y3 + x3 + y4 + x4))
-  dataset[R + 1:P, "y"] - predict(varmodel, newdata = dataset[R + 1:P,])
-}
-
-R <- 4 * 20
-P <- 4 * 30
-nsims <- 1000
-ncoefs <- 9
-pmse <- rep(NA, nsims * (ncoefs - 1))
-stat.i <- 0
-for (s in 1:nsims) {
-  vardata.s <- r2(R + P)
-  for (k in 2:9) {
-    stat.i <- stat.i + 1
-    pmse[stat.i] <- mean(makeerrors(vardata.s, k, R)^2)
-  }
-}
-mcresults <- data.frame(pmse = pmse, zstat = (pmse - 1) / (2 / sqrt(P)), k = rep(2:9))

### 2012-03-30 mc/rTestStat.R

@@ -1,32 +1,0 @@
-rTestStat <- function(d = rcw(P+R), R, P) {
-  ret <- list(avg = NA, mR = NA, mT = NA, CE = NA)
-  
-  r1 <- 1:(R-1)
-  r2 <- 1:(R-4)
-  t1 <- R+P - 1
-  t2 <- R+P - 4
-  
-  predictors1 <- cbind(1, d$y[1:t1])
-  predictors2 <- cbind(1, matrix(d$y[outer(1:t2, 3:0, "+")], t2, 4),
-                       matrix(d$z[outer(1:t2, 3:0, "+")], t2, 4))
-
-  model1 <- lm.fit(y = d$y[r1 + 1], x = predictors1[r1,])
-  model2 <- lm.fit(y = d$y[r2 + 4], x = predictors2[r2,])
-  model1Full <- lm.fit(y = d$y[1:t1 + 1], x = predictors1)
-  model2Full <- lm.fit(y = d$y[1:t2 + 4], x = predictors2)
-
-  lossDiff = (d$y[seq(length = P, to = R+P)] - predictors1[-r1,] %*% model1$coef)^2 -
-    (d$y[seq(length = P, to = R+P)] - predictors2[-r2,] %*% model2$coef)^2
-
-  avgLoss <- lm(lossDiff ~ 1)
-  stdAvg <- sqrt(NeweyWest(avgLoss)[1,1])
-  
-  ## studentized value around period-R models
-  ret$avg <- as.numeric(avgLoss$coef)
-  ret$std <- as.numeric(stdAvg)
-  ret$mR <- (avgLoss$coef - (cw.eloss(c(model1$coef, rep(0,7))) - cw.eloss(model2$coef))) / stdAvg
-  ret$mT <- (avgLoss$coef - (cw.eloss(c(model1Full$coef, rep(0,7))) - cw.eloss(model2$coef))) / stdAvg
-  ret$CE <- (avgLoss$coef - ((predictors1[t1,] %*% (model1Full$coef - c(2.237, 0.261)))^2 -
-                             (predictors2[t2,] %*% (model2Full$coef - c(2.237, 0.261, rep(0,7))))^2)) / stdAvg
-  ret
-}

### 2012-03-30 mc/rcw.R

@@ -1,24 +1,0 @@
-rcw <- function(n, v = 1, edist = rnorm) {
-### Generates dataframe of matrix of n observations y_t, z_t
-### from Clark and West's (2007) DGP 1
-### v is a scalar that multiplies the covariance matrix for debugging 
-
-  burn <- 3500
-  n <- n + burn
-
-  vcv <- v * matrix(c(sqrt(10.505), 0, 1.036 / sqrt(10.505),
-                      sqrt(0.366 - 1.036^2 / 10.505)), 2, 2)
-  
-  z <- rep(NA,n)
-  y <- rep(NA,n)
-  y[1:4] <- 0
-  z[1:4] <- 0
-
-  innovations <- crossprod(vcv, matrix(edist(n * 2), 2, n))
-  for (s in 5:n) {
-    y[s] <- 2.237 + 0.261 * y[s-1] + innovations[1,s]
-    z[s] <- 0.804 * z[s-1] - 0.221 * z[s-2] + 0.226 * z[s-3] - 0.205 * z[s-4] +
-      innovations[2, s]
-  }
-  data.frame(y = y[-(1:burn)], z = z[-(1:burn)])
-}

### 2012-03-30 mc/sec2_table.R

@@ -1,24 +1,0 @@
-source("../R/cw_prederrors.R")
-source("../R/rcw.R")
-
-cw.table <- matrix(byrow = TRUE, c(80, 40, NA,  80, 80, NA,  80, 120, NA,
-                     80, 160, NA, 120, 40, NA, 120, 80, NA, 120, 120, NA,
-                     120,160, NA), 8, 3)
-nstats <- dim(cw.table)[1]
-
-n <- 3000
-maxn <- max(rowSums(cw.table[,1:2]))
-minR <- min(cw.table[,1])
-teststat <- matrix(NA, n, dim(cw.table)[1])
-for (i in 1:n) {
-  d.i <- cw.prederrors(rcw(maxn), R = minR)[,2]^2
-  for (k in 1:nstats) {
-    R <- cw.table[k,1]
-    P <- cw.table[k,2]
-    teststat[i,k] <- (sqrt(P) * (mean(d.i[(R - minR) + 1:P]) - 10.505)
-                      / sd(d.i[(R - minR) + 1:P])) > 1.282
-  }
-  print(paste("done simulation", i, "of", n))
-}
-
-cw.table[,3] <- colMeans(teststat)

### 2012-03-30 mc/secMC_table1.R

@@ -1,37 +1,0 @@
-library(sandwich)
-source("../R/cw_prederrors.R")
-source("../R/rcw.R")
-
-edist <- function(n) {
-  e1 <- rnorm(n, -1)
-  e2 <- rnorm(n, 2, 4)
-  r <- ifelse(rbinom(n, size = 1, p = 0.5), e1, e2)
-  r <- (r - 1/2) / sqrt(11)
-}
-
-mc.T <- c(100, 200, 300)
-mc.ratio <- c(1/3, 1/2, 2/3, 4/5)
-
-n <- 1000
-teststat <- matrix(NA, n, length(mc.T) * (1 + length(mc.ratio)))
-minR <- round(min(mc.T) * min(mc.ratio))
-for (i in 1:n) {
-  data.i <- rcw(max(mc.T), edist = edist)
-  d.i <- c(cw.prederrors(data.i, R = round(min(mc.ratio) *  min(mc.T)))^2 %*% c(1,-1))
-  k <- 0
-  for (nobs in mc.T) {
-    s2 <- 5:nobs
-    m1 <- lm(data.i$y[s2] ~ data.i$y[s2 - 1])
-    m2 <- lm(data.i$y[s2] ~ data.i$y[s2-1] + data.i$y[s2-2] + data.i$y[s2-3] + data.i$y[s2-4]
-             + data.i$z[s2-1] + data.i$z[s2-2] + data.i$z[s2-3] + data.i$z[s2-4])
-    teststat[i, k <- k+1] <- (anova(m1, m2)$Pr[2] < 0.10)
-    for (ratio in mc.ratio) {
-      d.subset <- (round(ratio * nobs) - minR) + 1:(nobs - round(ratio * nobs))
-      avgdiff <- lm(d.i[d.subset] ~ 1)
-      teststat[i, k <- k+1] <- avgdiff$coef / NeweyWest(avgdiff)[1,1] > 1.282
-    }
-  }
-  print(paste("done simulation", i, "of", n))
-}
-
-tabby <- matrix(colMeans(teststat), length(mc.T), byrow = T)

### 2012-03-30 mc/secMC_table2.R

@@ -1,45 +1,0 @@
-source("../R/cw_prederrors.R")
-source("../R/cw_eloss.R")
-
-
-i1 <- 2:maxn
-i2 <- 5:maxn
-
-for (i in 1:n) {
-
-  dataMatrix1.i$dep <- data.i$y[i1]
-  dataMatrix2.i$dep <- data.i$y[i2]
-  dataMatrix1.i$ylag <- data.i$y[i1-1]
-  for (j in 1:4) {
-    dataMatrix2.i[,paste("y",j, sep="")] <- data.i$y[i2 - j]
-    dataMatrix2.i[,paste("z",j, sep="")] <- data.i$z[i2 - j]
-  }
-  for (k in 1:nstats) {
-    R <- cw.table[k,1]
-    P <- cw.table[k,2]
-
-    lastPredictors.i <- c(1, as.matrix(dataMatrix2.i[R+P-3,-1]))
-    model1.ik <- lm(dep ~ ylag, data = dataMatrix1.i, subset = 1:(R-1))
-    model2.ik <- lm(dep ~ y1 + y2 + y3 + y4 + z1 + z2 + z3 + z4,
-                    data = dataMatrix2.i, subset = 1:(R-4))
- 
-    fullCoef1.ik <- c(lm(dep ~ ylag, data = dataMatrix1.i, subset = 1:(R+P-1))$coef, rep(0, 7))
-    fullCoef2.ik <- lm(dep ~ y1 + y2 + y3 + y4 + z1 + z2 + z3 + z4,
-                       data = dataMatrix2.i, subset = 1:(R+P-4))$coef
-    
-    diffCE.ik <- (lastPredictors.i %*% (fullCoef1.ik - pseudoTrue))^2 - 
-      (lastPredictors.i %*% (fullCoef2.ik - pseudoTrue))^2
-    diffFull.ik <- cw.eloss(fullCoef1.ik) - cw.eloss(fullCoef2.ik)
-    diffSubsample.ik <- 
-
-    loss.ik <- (dataMatrix1.i$dep[R-1 + 1:P] - predict(model1.ik, dataMatrix1.i[R-1 + 1:P,]))^2 -
-      (dataMatrix2.i$dep[R-4 + 1:P] - predict(model2.ik, dataMatrix2.i[R-1 + 1:P,]))^2
-    
-    avg.ik <- lm(loss.ik ~ 1)
-
[…]

### 2012-03-30 notes/slides-cv/outOfSampleMC.R

@@ -1,23 +1,0 @@
-load("mcGlobal.Rdata")
-
-set.seed(30)
-
-mcQuad    <- rep(NA, nsims)
-mcOverfit <- rep(NA, nsims)
-
-for (i in 1:nsims) {
-  d.i <- rmc()
-  
-  modelQuad    <- lm(y ~ poly(x, 2), data = d.i, subset = estimationWindow)
-  modelOverfit <- lm(y ~ poly(x, K), data = d.i, subset = estimationWindow)
-
-  errQuad    <- d.i$y[-estimationWindow] - predict(modelQuad,    data.frame(x = d.i$x[-estimationWindow]))
-  errOverfit <- d.i$y[-estimationWindow] - predict(modelOverfit, data.frame(x = d.i$x[-estimationWindow]))
-
-  mcQuad[i]    <- mean(errQuad^2)
-  mcOverfit[i] <- mean(errOverfit^2)
-
-  print(i)
-}
-
-save.image("simulations.Rdata")

### 2012-03-30 notes/slides-cv/quadQQ.R

@@ -1,18 +1,0 @@
-library(lattice)
-load("mcGlobal.Rdata")
-load("simulations.Rdata")
-
-muQuad <- 1/3
-varQuad <- (1/5 - muQuad^2) / n
-
-## generate qq-plot for simulations vs. theoretical quantiles
-png("quadQQ.png")
-qqmath(mcQuad, col = "black", ylab = "Simulated Values", xlab = "Theoretical Values (West 1996)",
-       distribution = function(p) qnorm(p = p, mean = muQuad, sd = sqrt(varQuad)), aspect = "1")
-dev.off()
-
-png("quadHist.png")
-hist(mcQuad, 70, freq = F, ylim = c(0, 20), xlab = "Simulated Value", main = "")
-curve(dnorm(x, mean = muQuad, sd = sqrt(varQuad)), from = 0.25, to = 0.45, n = 1000, col = "red", add = T,
-      lwd = 2)
-dev.off()

### 2012-03-30 paper/_point.pl

@@ -1,94 +1,0 @@
-open MASTER, "<calhoun_fixed_window.tex" or die "Can't even start!";
-open BIGBOY, ">calhoun_outline.tex" or die "can't open to write!";
-open TEMP, ">temp.txt";
-
-chomp($line = <MASTER>);
-until ($line =~ /\\section/) {
-    chomp($line = <MASTER>);
-}
-
-print BIGBOY "\\documentclass[11pt]{article} \n" .
-    "\\usepackage{amssymb,amsmath,amsthm,harvard,graphicx} \n" .
-    "\\setcounter{MaxMatrixCols}{10} \n" .
-    "\\setlength{\\voffset}{0.22in} \n" .
-    "\\setlength{\\hoffset}{-0.06in} \n ".
-    "\\setlength{\\topmargin}{0in} \n" .
-    "\\setlength{\\headheight}{0in}\n" .
-    "\\setlength{\\headsep}{0in}\n" .
-    "\\setlength{\\textheight}{7.33in}\n" .
-    "\\setlength{\\oddsidemargin}{0in}\n" .
-    "\\setlength{\\textwidth}{5.67in}\n" .
-    "\\input{../bib/definitions}\n" .
-    "\\input{def}\n" . 
-    "\\newcommand{\\pp}[1]{\\textbf{#1}}\n";
-
-print BIGBOY "\\begin{document}";
-print BIGBOY $line . "\\begin{itemize}\n";
-while (<MASTER>) {
-    chomp;
-    if (/\\(\w)*section/) {
-	print BIGBOY "\\end{itemize}\n" . $_ . "\n\\begin{itemize}\n";
-    } elsif (/\\context/) {
-	print BIGBOY "\\end{itemize}\n " .
-	    "\\subsection{Shared Context} \n\\begin{itemize}\n";
-    } elsif (/\\problem/) {
-	print BIGBOY "\\end{itemize}\n " .
-	    "\\subsection{Statement of Problem} \n\\begin{itemize}\n";
-    } elsif (/\\sowhat/) {
-	print BIGBOY "\\end{itemize}\n " .
-	    "\\subsection{So What?} \n\\begin{itemize}\n";
-    } elsif (/\\solution/) {
-	print BIGBOY "\\end{itemize}\n " .
-	    "\\subsection{Statement of Solution} \n\\begin{itemize}\n";
-    } elsif (/\\begin{(thm|lem|asmp)}/) {
[…]

### 2012-03-30 test/cw_eloss.R

@@ -1,11 +1,0 @@
-source("../R/cw_eloss.R")
-
-if (! isTRUE(all.equal(cw.eloss(c(2.237, 0.261, rep(0, 7))), 10.505)))
-  stop("Does not return correct value at true parameters")
-
-if (! isTRUE(all.equal(optim(c(2.237, 0.261, rep(0, 7)),
-                             cw.eloss,
-                             control = list(maxit = 10000),
-                             method = "SANN")$value, 10.505)))
-  stop("Optimization does not return correct value at true parameters")
-

### 2012-03-30 test/cw_prederrors.R

@@ -1,16 +1,0 @@
-source("../R/cw_prederrors.R")
-source("../R/rcw.R")
-n <- 50
-R <- 30
-
-### check that west_prederror returns the right number of prediction errors.
-
-terr <- cw.prederrors(rcw(n = n), R)
-if (! is.data.frame(terr))
-  stop("cw.prederrors does not return a dta frame")
-if (! isTRUE(all.equal(dim(terr), c(n - R, 2))))
-  stop("cw.prederrors returns the wrong size data frame")
-
-### check that the forecast errors are plausible
-if (isTRUE(all.equal(terr, rep(0, 2 * (n - R)), check.arguments = FALSE)))
-  stop("cw.prederrors should NOT return zero forecast error.")

### 2012-03-30 test/cw_table.R

@@ -1,33 +1,0 @@
-source("../R/cw_prederrors.R")
-source("../R/rcw.R")
-
-
-### test that cw.prederrors can reproduce Clark and West's (2007) Table 1
-### - for DGP 2 recursive regressions.
-
-cw.table <- matrix(byrow = TRUE, c( 80, 40, 0.024,  80, 80, 0.010,  80, 120, 0.006,  80, 160, 0.002,
-                                   120, 40, 0.030, 120, 80, 0.013, 120, 120, 0.008, 120, 160, 0.006), 8, 3)
-nstats <- dim(cw.table)[1]
-
-n <- 3000
-maxn <- max(rowSums(cw.table[,1:2]))
-minR <- min(cw.table[,1])
-teststat <- matrix(NA, n, dim(cw.table)[1])
-for (i in 1:n) {
-  d.i <- as.matrix(cw.prederrors(rcw(maxn), R = minR)^2) %*% c(1, -1)
-  for (k in 1:nstats) {
-    R <- cw.table[k,1]
-    P <- cw.table[k,2]
-    teststat[i,k] <- (sqrt(P) * mean(d.i[(R - minR) + 1:P]) / sd(d.i[(R - minR) + 1:P])) > 1.282
-  }
-  print(paste("done simulation", i, "of", n))
-}
-
-for (k in 1:nstats) {
-  bt <- binom.test(x = sum(teststat[,k]), n, p = cw.table[k,3],
-                   alternative = "t")
-  if (bt$p.value < 0.001) 
-    stop("Monte Carlo inconsistent with Clark and West --- R ", cw.table[k,1],
-         " P ", cw.table[k,2], " CI = ", signif(bt$conf[1], 2), " to ",
-         signif(bt$conf[2], 2), " but should be ", cw.table[k,3])
-}

### 2012-03-30 test/makeDataMatrices.R

@@ -1,10 +1,0 @@
-source("../empirics/makeDataMatrices.R")
-
-y <- 1:30
-x <- 301:330
-
-r <- makeDataMatrices(y,x)
-if (!(isTRUE(all.equal(r$target, 25:30))))
-  stop("incorrect target")
-if (!(isTRUE(all.equal(r$predictorMatrix, cbind(1, outer(1:6,12:1,"+"), outer(301:306,12:1,"+"))))))
-  stop("incorrect predictor matrix")

### 2012-03-30 test/rcw.R

@@ -1,12 +1,0 @@
-source("../mc/rcw.R")
-n <- 30
-
-### first check that it returns the right number of series and observations
-
-td <- rcw(n)
-if (! is.data.frame(td))
-  stop("rcw does not return a data frame.")
-if (! isTRUE(all.equal(dim(td), c(n, 2)))) {
-  stop("rcw does not return the correct dimension")
-}
-

### 2012-03-30 mc/plot-interval.Rnw
Removed Goyal's code and data from online zip file

--- 2011-02-24 mc/plot-interval.Rnw
@@
                panel = function(x,y,...) {
+                 panel.xyplot(x,y,...,type = "l")
                  panel.lines(c(0,2/3),c(.9,.9), col = "gray")
-                 panel.xyplot(x,y,...,type = "l")
                },

### 2012-03-30 paper.tex
Removed Goyal's code and data from online zip file

--- 2012-03-30 paper.tex
@@
 \documentclass[11pt]{article}
+%\linespread{1.2}\selectfont
 \usepackage{tikz}
@@
 \usepackage{setspace,amsmath,amssymb,amsthm,ifthen,subfig,url,multicol}
-\onehalfspacing\frenchspacing
+\usepackage{fancyhdr}
+\pagestyle{fancy}
+\lhead{\thepage}\chead{}\rhead{}
+\lfoot{}\cfoot{}\rfoot{}
+\renewcommand\headrulewidth{0pt}
+\onehalfspacing
 \usepackage[margin=1in]{geometry}
+\usepackage{nath}
 
@@
 \newcommand{\Citepos}[1]{\Citeauthor{#1}'s \citeyearpar{#1}}
-\newcommand{\clws}{\citeauthor{ClW:06}'s \citeyearpar{ClW:06,ClW:07}}
 
@@
 
-\newcommand{\oosA}{\bar{D}_{R}}
-\newcommand{\oosB}{\bar{D}_{T}}
+\newcommand{\oosA}{\bar{D}_a}
+\newcommand{\oosB}{\bar{D}_b}
 
 \newcommand{\oost}{\ensuremath{\operatorname{oos-t}}}
-\newcommand{\oosSum}[2]{\ensuremath{\sum_{#1=R+#2}^{T-\h}}}
+\newcommand{\oosSum}[2]{\ensuremath{\sum_{#1=R-\h+#2}^{T-\h}}}
 
@@
 \newcommand{\CEOuterBlock}[2]{\ensuremath{\E_{\InnerBlockU{(#2-1)}} #1}}
+
+\newcommand{\CenteredAverage}{\frac{\oosA - \E_T\oosT}{\hat\sigma / \sqrt{P}}}
+\newcommand{\CenteredAverageI}{\ensuremath{\frac{1}{\hat\sigma
+    \sqrt{P}}\oosSum{t}{1} (D_{tR} - \E_R D_{tR})}}
+\newcommand{\CenteredAverageII}{\ensuremath{\frac{\sqrt{P}}{\hat\sigma}
+    (\E_R\oosA - \E_T\oosB)}}
+
+\newcommand{\MixingaleArray}[1]{\ensuremath{}}
 
@@
 
-\newcommand{\couplingConstant}{\ensuremath{2^{(1+\rho)/\rho} B_L}}
-\newcommand{\couplingBeta}[1]{\ensuremath{\beta^{(\rho-2)/2\rho}_{#1}}}
-\newcommand{\couplingBetaSq}[1]{\ensuremath{\beta^{(\rho-2)/\rho}_{#1}}}
+\newcommand{\couplingConstant}{\ensuremath{2^{\frac{1+\rho}{\rho}} B_L}}
+\newcommand{\couplingBeta}[1]{\ensuremath{\beta^{\frac{\rho-2}{2\rho}}_{#1}}}
+\newcommand{\couplingBetaSq}[1]{\ensuremath{\beta^{\frac{\rho-2}{\rho}}_{#1}}}
 \newcommand{\couplingBound}[1]{\couplingConstant \couplingBeta{#1}}
@@
     would like to thank Julian Betts, Helle Bunzel, Marjorie Flavin,
-    Nir Jaimovich, Lutz Kilian, Ivana Komunjer, Michael McCracken,
-    Seth Pruitt, Ross Starr, Jim Stock, Yixiao Sun, Allan Timmermann,
-    Hal White, several anonymous referees, participants at the 2010
-    Midwest Economics Association Annual Meetings, the 2010
-    International Symposium on Forecasting, the 2010 Joint Statistical
-    Meetings, and in many seminars at \textsc{ucsd}, and espeically
-    Graham Elliott for their valuable suggestions, feedback and advice
-    in writing this paper.  I would also like to thank Amit Goyal for
-    providing computer code and data for his 2008 RFS paper with Ivo
-    Welch \citep{GoW:08}.} \\ Iowa State University}
+    Nir Jaimovich, Lutz Kilian, Michael McCracken, Seth Pruitt, Ross
+    Starr, Yixiao Sun, Allan Timmermann, participants at the 2010
+    Midwest Economics Association Annual Meetings, the 2010 Joint
+    Statistical Meetings, and in many seminars at \textsc{ucsd}, and
+    espeically Graham Elliott for their valuable suggestions, feedback
+    and advice in writing this paper.  I would also like to thank Amit
+    Goyal for providing computer code and data for his 2008 RFS paper
+    with Ivo Welch \citep{GoW:08}.} \\ Iowa State University,
+  Economics Department}
 \date{October 24, 2011}
@@
   positive.  Under this limit theory, the naive Diebold-Mariano-West
-  out-of-sample test can test hypotheses about the models'
-  generalization error, a key quantity for evaluating forecasting
-  models.  Moreover, tests that are designed to reject if the larger
-  model is true, such as the usual in-sample Wald and \textsc{lm}
-  tests and also Clark and McCracken's (2001, 2005a),
-  \citepos{Mcc:07}, and Clark and West's (2006, 2007) out-of-sample
-  statistics, will choose the larger model too often when the smaller
-  model is more accurate.
-
-\noindent \textsc{jel} Classification: C12, C22, C52, C53
+  out-of-sample test can test hypotheses about a key quantity for
+  evaluating forecasting models---a time series analogue to the
+  generalization error---as long as the out-of-sample period is small
+  relative to the total sample size.  Moreover, tests that are
+  designed to reject if the larger model is true, such as the usual
+  in-sample Wald and \textsc{lm} tests and also Clark and McCracken's
+  (2001, 2005a), \citepos{Mcc:07} and Clark and West's (2006, 2007)
+  out-of-sample statistics, will choose the larger model too often
+  when the smaller model is more accurate.
+
+\noindent \textsc{jel} Classification: C01, C12, C22, C52, C53
 
@@
 \end{abstract}
-\newpage
 
@@
 models is overfit.  In doing so, we provide a theoretical
-justification for forecasters to use \oos\ instead of in-sample
-comparisons and discover a practical limitation in existing statistics.
+justification for forecasters to use \oos\ instead of
+in-sample comparisons.
 
@@
   coefficients are consistent and asymptotically normal.}
-\citet{GiW:06} and \citet{GiR:09, GiR:10} are exceptions.  Instead of
+\citet{GiW:06}, and \citet{GiR:09, GiR:10} are exceptions.  Instead of
 focusing on hypotheses that can be tested by in-sample comparisons,
@@
 papers focus on a particular \oos\ estimation strategy and do not
-address why \oos\ comparisons might be useful as a general strategy.
+address why naive \oos\ comparisons might be generally useful.
 
@@
 increases with the number of observations so that their ratio remains
-positive.  Although overfit is sometimes used to describe the
-situation where a forecaster chooses from many different models, we
-view that as a separate issue.  Procedures that account for the
-presence of many models are being developed \citep[see, for
-example,][]{Whi:00,RoW:05}, but there is still disagreement about
-whether those procedures should themselves use in-sample or \oos\
-comparisons.  Understanding this issue in the context of a simple
-comparison between two models is necessary before resolving any new
-issues that arise with multiple comparisons.
-
-We focus on linear regression models for simplicity, but our basic
-conclusions should be true for other estimation strategies and models
-as well.  Under this asymptotic theory, the \ols\ coefficient
-estimator is no longer consistent or asymptotically normal
-\citep{Hub:73} and has positive variance in the limit.  Even so, we
-show that the usual \oos\ average is asymptotically normal and can
-consistently estimate the difference between the models'
-generalization error, the expected loss in the future conditional on
-the on the data available in period $T$.\footnote{See, for example,
+positive.  We focus on linear regression models estimated with a fixed
+training window, but our basic conclusions should be true for other
+estimation strategies and models as well.  Under this asymptotic
+theory, the \ols\ coefficient estimator is no longer consistent or
+asymptotically normal \citep{Hub:73} and has positive variance in the
+limit.  Even so, we show that the usual \oos\ average is
+asymptotically normal and can consistently estimate the difference
+between the models' expected loss in periods $T+1,T+2,\dots$
+conditional on the on the data available in period $T$, a time-series
+analogue to the generalization error.\footnote{See, for example,
   \citet{HTF:08}.}  Under these asymptotics, the generalization error
@@
 the model that is closer to the true \dgp\ in population can forecast
-worse.  In such a situation, a standard in-sample comparison would
-correctly reject the null hypothesis that the benchmark is true, and
-an \oos\ comparison would correctly fail to reject the null that the
-benchmark is more accurate.\footnote{In a pair of papers similar to
-  ours, \citet{ClM:09,ClM:09b} study in-sample and \oos\ tests that
-  the larger model has nonzero coefficients that are too close to zero
-  to expect the model to forecast more accurately.  Like this paper,
-  they argue that the larger model can be true but less accurate.
-  However, they focus on an aspect of the \dgp\ that makes this
-  phenomenon likely, while we focus on the coefficient estimates that
-  produce less accurate forecasts.}
+worse.  In such a situation, an in-sample comparison would correctly
+reject the null hypothesis that the benchmark is true, and an \oos\
+comparison would correctly fail to reject the null that the benchmark
+is more accurate.\footnote{In a pair of papers similar to ours,
+  \citet{ClM:09,ClM:09b} study in-sample and \oos\ tests that the
+  larger model has nonzero coefficients that are too close to zero to
+  expect the model to forecast more accurately.  Like this paper, they
+  argue that the larger model can be true but less accurate.  However,
+  they focus on an aspect of the \dgp\ that makes this phenomenon
+  likely, while we focus on the coefficient estimates that produce
+  less accurate forecasts.}
 
@@
 alternative model is higher than the cost of incorrectly failing to
-switch to a more accurate alternative.\footnote{Because we focus on
-  testing relative to a benchmark, rather than model selection with
-  now benchmark, we will not discuss in-sample statistics with
-  penalties for overparametrization, e.g. the \textsc{aic} or adjusted
-  R-square.  \citet{Lee:08} discusses similar issues to ours related
-  to model selection.}
+switch to a more accurate alternative.\footnote{These costs can be
+  monetary, in the form of computer upgrades, software installation,
+  and training, or they can be reputational costs.}
 We show that the \dmw\ test lets the forecaster control the
@@
 Since the models' coefficients are imprecisely estimated in the limit,
-the test sample must be small enough that the model estimated over
+the test sample must be small to ensure that the model estimated over
 the training sample is similar to the one that will be estimated over
@@
 shown by \citet{BoB:95}, \citet{AkA:00}, \citet{AkP:04}, and
-\citet{Ana:12}, \citet{Cal:11c}, among others.  Such results establish
-that hypotheses about the parameters of the \dgp\ can be tested
-in-sample even if one or both models are overfit.  For that very
-reason, these tests can not reliably choose a model for forecasting
-and will reject the benchmark too often.  We show this analytically in
-Section~\ref{sec:insample}.  Moreover, under this asymptotic theory,
-many recent \oos\ test statistics, such as those derived by
-\cite{ClM:01,ClM:05}, \citet{Mcc:07}, and \citet{ClW:06,ClW:07} should
-behave like the F-test.\footnote{Our theoretical results apply
-  directly to \citepos{Mcc:07} \oost test, since it simply proposes
-  more liberal critical values for the same test statistic.  Since
-  \citet{ClW:06,ClW:07} use a finite length estimation window, our
-  asymptotics are incompatible with theirs and prevent us from
-  studying their test directly, as well as \citepos{GiW:06} and other
-  similar tests.  But \clws\ test can be viewed as a stochastic
-  adjustment to the critical values of the usual \oost test, so our
-  theoretical results should apply informally as well.  Specifically,
-  we show that the \dmw\ test rejects probability equal to nominal
-  size, so more liberal critical values result in over-rejection.}
-These tests are also designed to reject the benchmark when the
-alternative model is true, and so they may reject too often when the
-benchmark is false but more accurate.  Obviously, since the
+\citet{Cal:10}, among others.  Such results establish that hypotheses
+about the parameters of the \dgp\ can be tested in-sample even if one
+or both models are overfit.  For that very reason, these tests can not
+reliably choose a model for forecasting and will reject the benchmark
+too often.  We show this analytically in Section~\ref{sec:insample}.
+Moreover, under this asymptotic theory, many recent \oos\ test
+statistics, such as those derived by \cite{ClM:01,ClM:05},
+\citet{Mcc:07}, and \citet{ClW:06,ClW:07} should behave like the
+F-test.  These tests are also designed to reject the benchmark when
+the alternative model is true, and so they may reject too often when
+the benchmark is false but more accurate.  Obviously, since the
 distribution of these statistics converges to the normal when $P/T \to
@@
 functions of mixing processes can be used for these \oos\ processes
-with only slight modification.
+with only slight modification.  Although we only present a proof that
+this mixingale result holds for the fixed-window scheme, it is simple
+to extend it to other estimation windows.
 
@@
 \[
-y_{t+\h} = x_{1t}'\theta_1 + \varepsilon_{1,t+h}, \quad\text{and}\quad
+y_{t+\h} = x_{1t}'\theta_1 + \varepsilon_{1,t+h}
+\]
+and
+\[
 y_{t+\h} = x_{2t}'\theta_2 + \varepsilon_{2,t+h};
 \]
-$t = 1,\dots,T-h$, $\h$ is the forecast horizon, and the
-variables $y_t$, $x_{1t}$, and $x_{2t}$ are all known in period $t$.
-Let
+$\h$ is the forecast horizon, and the variables $y_t$, $x_{1t}$, and
+$x_{2t}$ are all known in period $t$.  Let
 \begin{equation*}
@@
 
-We assume the following forecasting environment: the forecaster
-observs the data $(y_t,x_t)$ for periods 1 through $T$ and divides
-them into an estimation sample of the first $R+h$ observations and a
-test sample of the remaining $P$ observations.  After choosing one of
-the models, the forecaster will use that model to make predictions for
-periods $T + h$ through $T + h + Q$, where $Q$ is a known positive
-integer.  The forecaster's goal is to choose the model that will have
-lower average loss over periods $T+h$ through $T+h+Q$, evaluated by
-the known loss function $L$.
-
-Both models are estimated using \ols\ with a recursive, fixed, or
-rolling window:
-\[
-\hat y_{i,t+\h} = x_{it}'\bh{iR}, \qquad i=1,2, \qquad t = R+1,\dots,T-h
+Although our theory can apply to many different \oos\ statistics,
+we'll only present results for the \dmw\ \oos\ $t$-test.  Both models
+are estimated using \ols\ over the training sample:
+\[
+\hat y_{i,t+\h} = x_{it}'\bh{iR}, \quad i=1,2, \quad t = R+1,\dots,T-h
 \]
 with
-\begin{equation*}
-\bh{it}^{R} = \begin{cases} \big(\sum_{s=1}^{t-\h} x_{is}x_{is}'\big)^{-1}
-\sum_{s=1}^{t-\h} x_{is} y_{s+\h} & \text{recursive window}\\
- \big(\sum_{s=t - \h - R}^{t-\h} x_{is}x_{is}'\big)^{-1}
-\sum_{s=t - \h - R}^{t-\h} x_{is} y_{s+\h} & \text{rolling window} \\
- \big(\sum_{s=1}^{R-\h} x_{is}x_{is}'\big)^{-1} 
-\sum_{s=1}^{R-\h} x_{is} y_{s+\h} & \text{fixed window}
-\end{cases}
-\end{equation*}
-The observed \oos\ average is denoted $\oosA$: \[\oosA \equiv P^{-1}
-\oosSum{t}{1} D_{Rt}\]  with
-\[
-D_{Rt} \equiv L(y_{t+\h} - x_{1t}'\bh{1t}^R) - L(y_{t+\h}
-  - x_{2t}'\bh{2t}^R).
-\]
-The \oos\ statistic of interest is $\oost \equiv \sqrt{P} \oosA /
-\hat\sigma$, for $\hat\sigma^2$ some (possibly Heteroskedasticity- and
+\[
+\bh{it} = (\sum_{s=1}^{t-\h} x_{is}x_{is}')^{-1} \sum_{s=1}^{t-\h} x_{is} y_{s+\h},
+\quad i=1,2.
+\]
+The \oos\ average is denoted $\oosA$:
+\[
+\oosA \equiv P^{-1} \oosSum{t}{1} D_{tR}
+\quad \text{with} \quad D_{tS} \equiv L(y_{t+\h} - x_{1t}'\bh{1S}) -
+L(y_{t+\h} - x_{2t}'\bh{2S}),
+\]
+$P = T - R$ and $L$ a known loss function.  The \oos\ statistic
+of interest is 
+\[
+\oost \equiv \frac{\sqrt{P} \oosA}{\hat\sigma},
+\]
+for $\hat\sigma^2$ some (possibly Heteroskedasticity- and
 Autocorrelation-Consistent, or \hac) estimator of the asymptotic
@@
 
-As discussed above, the forecaster's goal is to choose the model with
-lower average future loss; i.e. to determine whether $\oosB$ is
-positive or negative,with
-\[
-\oosB \equiv Q^{-1} \sum_{t=T+1}^{T+Q} D_{Tt},
-\]
-with
-\[
-D_{Tt} \equiv L(y_{t+h} - x_{1t}' \bh{1t}^T) - L(y_{t+h} - x_{2t}' \bh{2t}^T)
-\]
-and 
-\begin{equation*}
-\bh{it}^{T} = \begin{cases} \big(\sum_{s=1}^{t-\h} x_{is}x_{is}'\big)^{-1}
-\sum_{s=1}^{t-\h} x_{is} y_{s+\h} & \text{recursive window}\\
- \big(\sum_{s=t - \h - T}^{t-\h} x_{is}x_{is}'\big)^{-1}
-\sum_{s=t - \h - T}^{t-\h} x_{is} y_{s+\h} & \text{rolling window} \\
- \big(\sum_{s=1}^{T-\h} x_{is}x_{is}'\big)^{-1} 
-\sum_{s=1}^{T-\h} x_{is} y_{s+\h} & \text{fixed window}.
-\end{cases}
-\end{equation*}
-Note that the coefficients are reestimated with a larger dataset for
-the fixed and rolling windows.  Since the forecaster's information
-set, $\mathcal{F}_T$, does not contain $\oosB$, he or she should
-decide between the models based on the conditional expectation, $\E_T
-\oosB$. If this quantity is positive, the first model is expected to
-perform worse in the future, and if it is negative the second is.
-
-This random variable is related to several well known measures of
-model performance.  As $Q \to \infty$, it converges to the difference
-in the models' generalization error and equals it for i.i.d. data.
-Moreover, if the data are i.i.d., the expectation of $\E_T \oosB$
-equals \citepos{Aka:69} Final Prediction Error (\textsc{fpe}).  Both
-generalization error and \textsc{fpe} are defined as teh performance
-on a new, independent, data set; here the new data is not
-independent.  Since $Q \to \infty$ in our asymptotic theory, though,
-we will call $\E_T \oosB$ the difference in generalization error
-throughout the paper with hopefully no risk of confusion.
+We'll show that \oost\ can be used to test whether the models will
+forecast equally accurately in the future.  Specifically, assume that
+whichever model is chosen will be used for an additional $Q$ periods
+in the future and let $\oosB$ denote the difference in average
+performance over those periods:
+\[
+\oosB \equiv Q^{-1} \sum_{t=T+1}^{T+Q} D_{tT}.
+\]
+Note that $\oosA$ depends on the training sample estimators,
+$\hat\theta_{iR}$, and $\oosB$ depends on the full sample
+estimators, $\hat\theta_{iT}$.  A forecaster has access to the
+information set $\mathcal{F}_T$ when deciding between the two
+forecasting models, but $\mathcal{F}_T$ does not contain $\oosB$.
+So a forecaster should decide between the models based on the
+conditional expectation, $\E_T \oosB$. If this quantity is
+positive, the first model is expected to perform worse in the future,
+and if it is negative the second is.
+
+When the underlying series is i.i.d., this random variable, $\E_T
+\oosB$, is equal to the difference in the models' generalization
+error.  The generalization error of model $i$ is defined as
+\begin{equation*}
+  \E_{T} L(y_{T+\h}^{*} - x_{iT}^{*\prime}\hat{\theta}_{iT})
+\end{equation*}
+where $(y_{T+\h}^{*},x_{iT}^{*})$ has the same joint distribution as
+$(y_{T+\h}, x_{iT})$ but is independent of $\mathcal{F}_T$.  Note that
+$\hat{\theta}_{iT}$ is known in period $T$, so the generalization
+error conditions on the observed coefficient estimates.  With
+dependence, the coefficient estimates may be informative about future
+values of $y_{t+\h}$ and $x_{it}$, but this influence dies out as $Q$
+grows.  Conditional performance measures like these are especially
+appropriate in areas like time-series economics where the forecaster
+knows the coefficient values when choosing a model, but would be less
+appropriate if the models will be re-estimated over an entirely new
+dataset before forecasting.
 
@@
 \begin{asmp}\label{asmp-1} 
-  The random array $\{y_t,x_t\}$ is stationary and absolutely regular
-  with coefficients $\beta_j$ of size $-\rho/(\rho-2)$; $\rho$ is
-  greater than two and discussed further in Assumption \ref{asmp-3}.
-  Also, $K_1$ and $K_2$ are less than $R$, and $K_2/T$ and
-  $(K_2-K_0)/T$ are uniformly positive; $K_0$ is the number of
-  regressors shared by the two models ($K_1/T$ can be uniformly
-  positive as well, but is not required to be).
+  The random array $\{y_t,x_t\}$ is stationary and
+  absolutely regular with coefficients $\beta_j$ of size
+  $-\rho/(\rho-2)$; $\rho$ is greater than two and discussed further
+  in Assumption \ref{asmp-3}.  Also, $K_1$ and $K_2$ are less than $R$,
+  and $\frac{K_2}{T}$ and $\frac{K_2-K_0}{T}$ are uniformly positive;
+  $K_0$ is the number of regressors shared by the two models ($K_1/T$
+  can be uniformly positive as well, but is not required to be).
 \end{asmp}
@@
   Moreover, there exist a $\delta > 0$ and finite $\Delta$ such that
-  \begin{align*}
+  \begin{equation*}
     \lVert \lambda_{\max}(X_{iS_{T}}'X_{iS_{T}}) \rVert_{3+\delta}
-    &\leq S_{T}\, \Delta, &
+    \leq S_{T}\, \Delta \\
     \lVert
     \lambda_{\max}(X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})
-    \rVert_{3+\delta} &\leq S_{T}\, \Delta, \\
-    \lVert \lambda_{\max}((X_{iS_{T}}'X_{iS_{T}})^{-1}) \rVert_{3+\delta} &\leq \Delta/S_{T}, &
+    \rVert_{3+\delta} \leq S_{T}\, \Delta \\
+    \lVert \lambda_{\max}((X_{iS_{T}}'X_{iS_{T}})^{-1}) \rVert_{3+\delta} \leq \Delta/S_{T} \\
     \lVert
     \lambda_{\max}((X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})^{-1})\rVert_{3+\delta}
-    &\leq \Delta/S_{T},
-  \end{align*}
+    \leq \Delta/S_{T}
+  \end{equation*}
   for all $S_{T} \geq K_{2T}$ and large enough $T$, with $i =
@@
   \begin{equation*}
-    \|D_{R,R+j}\|_\rho \leq B_L \quad\text{and}\quad
-    \|D_{T,T+j}\|_\rho \leq B_L.
-  \end{equation*}
-  for all $j \geq 1$; $\rho$ is defined in Assumption~\ref{asmp-1}.
+    \|D_{R+j,R}\|_\rho \leq B_L \quad\text{and}\quad
+    \|D_{T+j,T}\|_\rho \leq B_L.
+  \end{equation*}
+  for all $j \geq 1$.
 \end{asmp}
@@
 
-\begin{asmp} \label{asmp-4} $P\to\infty$, $R\to\infty$, $Q\to\infty$,
-  $P = o(T^{1/2}) + O(Q)$ as $T \to \infty$.  For the rolling and
-  recursive windows, $Q = o(T^{1/2})$ as well.
+\begin{asmp} \label{asmp-4} $P\to\infty$,
+  $R\to\infty$, $Q\to\infty$, $P^2/T \to 0$, and $P = O(Q)$ as $T \to \infty$.
 \end{asmp}
@@
 consider.  We use the same class of estimators studied by
-\citet{JoD:00} (their class $\mathcal{K}$); see
+\citet{DeD:00} (their class $\mathcal{K}$); see
 their paper for further discussion.
@@
 related---allowing for complex models requires tighter constraints on
-the size of the test sample.  West allows more general estimation
-methods, while we restrict attention to \ols; the advantage of using
-\ols\ is that it gives a necessary bound, $\| x_{it}' \theta_{it}^{R} - x_{it}'
-\theta_{iR}^R \|_2 \leq O(P/T^{1/2})$.  Our main results will hold for
-other models as long as a similar inequality exists, but proving such
-inequalities for other models is left for future research.
+the size of the test sample.
 
 Our other assumptions are similar.  The loss function must be smooth
-almost everywhere, which is less restrictive than \citet{Wes:96}
-requires but is not new; \citet{Mcc:00} extends West's results to
-cover a similar case.\footnote{Our assumptions allow for discontinuous
-  loss functions, such as that proposed by \citet{PeT:92}.
-  \citet{Mcc:07} does not allow for such loss functions, but it
-  appears that his conclusions hold for them under the restriction
-  $P/T \to 0$.}  We assume full stationarity and absolute regularity
-of the underlying random array, while West assumes covariance
-stationarity and strong mixing of the transformed forecast errors; and
-the details our moment conditions are different, but seem that they
-would hold in similar environment to West's.  Finally, since West's is
-a more standard environment, he assumes the existence of a consistent
-estimator of the variance, while we construct it explicitly.  Only
-West's assumptions governing model complexity and the size of the test
-sample are substantially different than ours.
+almost everywhere, which is slightly less restrictive than
+\citet{Wes:96} requires but is not new; \citet{Mcc:00} extends West's
+results to cover a similar case.  West relaxes our assumption that the
+forecasts come from a linear regression model; we could relax our
+assumption to include other linear estimators, but there would be
+little new insight.  We assume full stationarity and absolute
+regularity of the underlying random array, while West assumes
+covariance stationarity and strong mixing of the transformed forecast
+errors; and the details our moment conditions are different, but seem
+that they would hold in similar environment to West's.  Finally, since
+West's is a more standard environment, he assumes the existence of a
+consistent estimator of the variance, while we construct it
+explicitly.  Only West's assumptions governing model complexity and
+the size of the test sample are substantially different than ours.
 
@@
 hypotheses about $E_{T} \oosB$ when the models are overfit.  In
-fact, in the limit it rejects a more accurate but false benchmark
+fact, in the limit it rejects a more-accurate but false benchmark
 model almost surely.
@@
   Consequently, each of the usual Gaussian confidence intervals,
-  \begin{gather}
-  [\oosA - z_{\alpha/2} \, \hat\sigma /
+  \begin{eqnarray}
+  &&[\oosA - z_{\alpha/2} \, \hat\sigma /
       \sqrt{P}, \oosA + z_{\alpha/2} \hat\sigma / \sqrt{P}],\label{interval-twosided} \\
-  [\oosA - z_{\alpha} \, \hat\sigma / \sqrt{P}, +\infty), \label{interval-greater}
-  \intertext{and}
-(-\infty, \oosA + z_{\alpha}
+  &&[\oosA - z_{\alpha} \, \hat\sigma / \sqrt{P}, +\infty), \label{interval-greater}
+  \end{eqnarray}
+  and
+  \begin{equation} (-\infty, \oosA + z_{\alpha}
       \, \hat\sigma / \sqrt{P}],
-    \end{gather}
+  \end{equation}
   contains $\E_T\oosB$ with probability $\alpha$ in the limit,
@@
 models give different forecasts even if they both nest the \dgp.  This
-is intuitively similar to \citepos{GiW:06} rolling-window result, but
-comes from different asymptotics; Giacomini and White keep the
-variance of the \oos\ average positive by letting $P \to \infty$ with
-$R$ fixed; in this paper, $R \to \infty$ but the variance remains
-positive since $K \to \infty$ (quickly) as well.
+is similar to \citepos{GiW:06} rolling-window result, but comes from
+different asymptotics.
 
@@
 \begin{equation}
-  \Pr[P^{1/2}\oosA/\hat\sigma \geq z_{\alpha} \mid \E_{T}
+  \Pr[\sqrt{P}\oosA/\hat\sigma \geq z_{\alpha} \mid \E_{T}
   \oosB \leq 0] \to^p \alpha.
@@
 so Theorem~\ref{res-confidence-intervals} holds if
+\begin{equation}\label{normalpart}
+  \sqrt{P}\frac{\oosA - \E_R \oosA}{\sigma} \to^d N(0,1)
+\end{equation}
+and
 \begin{equation}\label{coefpart}
@@
 \end{equation}
-and
-\begin{equation}\label{normalpart}
-  \sqrt{P}\frac{\oosA - \E_R \oosA}{\sigma} \to^d N(0,1)
-\end{equation}
-The first Lemma shows that the rolling and recirsive window statistics
-can be approximated by the fixed widnow statistic and that
-that~\eqref{coefpart} holds for the fixed window.  The second Lemma
-shows that the process $\{D_{Rt} - \E_R \oosA\}$ is an $L_2$-mixingale
-of size $-1/2$ that satisfies a \clt\ for the fixed window statistic,
-ensuring~\eqref{normalpart}.
+The first Lemma first shows that the process $\{D_{tR} - \E_R \oosA\}$
+is an $L_2$-mixingale of size $-1/2$ that satisfies a \clt,
+ensuring~\eqref{normalpart}.  The second shows that~\eqref{coefpart}
+holds under Assumption~\ref{asmp-4}.
+
+\begin{lem}\label{res-mixingale}
+  Part 1: If Assumptions~\ref{asmp-1}--\ref{asmp-3} hold then the inequality
+  \begin{equation}\label{mixingaleR}
+    \lVert \E_{R+j-l}(D_{R+j,R} - \E_R D_{R+j,R}) \rVert_2 \leq
+    \couplingConstant \;
+    \zeta_l
+  \end{equation}
+  with $\zeta_l = O(l^{-\frac12 - \delta})$ holds for some positive
+  $\delta$, any positive $j$, and any $l$ between 0 and $j$.  As a
+  consequence, $\{D_{t,R} - \E_R D_{t,R}, \mathcal F_t\}$ is an
+  $L_2$-mixingales of size $-1/2$.
+
+  \noindent Part
+  2: Moreover,~\eqref{normalpart} holds under
+  Assumptions~\ref{asmp-1}--\ref{asmp-3} if $P \to \infty$ as $T \to
+  \infty$ and $\sigma^2$ is a.s. uniformly positive.
+\end{lem}
+
+Mixingales satisfies a weak-dependence condition similar to \mds es
+and were introduced and studied extensively by
+\citet{Mcl:74,Mcl:75,Mcl:75b,Mcl:77}.  This lemma shows that the
+estimation uncertainty introduces dependence into the \oos\ forecast
+errors, but that additional dependence is contained in the term $\E_R
+\oosA$ and can be effectively removed by subtraction.  The second
+part of the Lemma shows that the basic mixingale \clt\ established by
+\citet{Dej:97} applies in this setting.\footnote{De Jong proves two
+  \clt s: one for mixingales and one for \ned\ functions of mixing
+  processes.  His mixingale result makes assumptions about the
+  behavior of the sample second moment that arise as consequences of
+  \ned.  The proof of Lemma~\ref{res-mixingale} shows that the
+  arguments used for de Jong's \ned\ \clt\ continue to hold for our
+  \oos\ process---in effect, that the \oos\ process has slightly more
+  structure than required for it to be a mixingale.}
 
 \begin{lem} \label{res-convergence} Suppose that Assumptions
-  \ref{asmp-1}--\ref{asmp-4} hold, let $D_{Rt}'$ and $D_{Tt}'$ denote
-  the loss differences associated with the rolling or recursive
-  window, and let $D_{Rt}$ and $D_{Tt}$ those of the fixed window.  Then
-  \begin{equation}
-    \label{eq:8}
-    P^{1/2} \oosA' = P^{1/2} \oosA + o_p, \qquad Q^{1/2} \oosB' =
-    Q^{1/2} \oosB + o_p,
-  \end{equation}
-  and
-  \begin{equation}\label{eq:7}
+  \ref{asmp-1}--\ref{asmp-4} hold.  Then
+\begin{equation*}
   \E_T \oosB - \E_R \oosA =  O_p(\sqrt{P/T}) +
   o_p(P^{-\frac12}) + o_p(Q^{-\frac12}).
-  \end{equation}
+\end{equation*}
 \end{lem}
 
-There is an intuitive reason that Lemma~\ref{res-convergence} holds.
-In the limit, the difference between $\E_T \oosB$ and $\E_R \oosA$
+The justification for Lemma~\ref{res-convergence} is intuitive.  In
+the limit, the difference between $\E_T \oosB$ and $\E_R \oosA$
 comes from the coefficient estimators used: $\E_T\oosB$ is the
@@
 $\mathcal{F}_R$ and $\mathcal{F}_T$.  Since $L$ is smooth, the
-difference between $\E_R \oosA$ and $\E_T \oosB$ is of order $\lvert
-\hat\theta_R - \hat\theta_T \rvert_2$, which itself is of order
-$\sqrt{P/T}$.  The logic behind approximating the rolling and
-recursive window statistics with the fixed window statistic is the
-same.
-
-\begin{lem}\label{res-mixingale}
-  Part 1: If Assumptions~\ref{asmp-1}--\ref{asmp-3} hold and the fixed
-  window estimation window is used, then the inequality
-  \begin{equation}\label{mixingaleR}
-    \lVert \E_{R+j-l}(D_{R,R+j} - \E_R D_{R,R+j}) \rVert_2 \leq
-    \couplingConstant \;
-    \zeta_l
-  \end{equation}
-  with $\zeta_l = O(l^{-1/2 - \delta})$ holds for some positive
-  $\delta$, any positive $j$, and any $l$ between 0 and $j$.  As a
-  consequence, $\{D_{Rt} - \E_R D_{Rt}, \mathcal F_t\}$ is an
-  $L_2$-mixingale of size $-1/2$.
-
-  \noindent Part 2: Moreover,~\eqref{normalpart} holds under the
-  conditions of Part 1 if $P \to \infty$ as $T \to \infty$ and
-  $\sigma^2$ is a.s. uniformly positive.
-\end{lem}
-
-Mixingales satisfies a weak-dependence condition similar to \mds es
-and were introduced and studied extensively by
-\citet{Mcl:74,Mcl:75,Mcl:75b,Mcl:77}.  This lemma shows that the
-estimation uncertainty introduces dependence into the \oos\ forecast
-errors, but that additional dependence is contained in the term $\E_R
-\oosA$ and can be effectively removed by subtraction.  The second
-part of the Lemma shows that the basic mixingale \clt\ established by
-\citet{Jon:97} applies in this setting.\footnote{De Jong proves two
-  \clt s: one for mixingales and one for \ned\ functions of mixing
-  processes.  His mixingale result makes assumptions about the
-  behavior of the sample second moment that arise as consequences of
-  \ned.  The proof of Lemma~\ref{res-mixingale} shows that the
-  arguments used for de Jong's \ned\ \clt\ continue to hold for our
-  \oos\ process---in effect, that the \oos\ process has slightly more
-  structure than required for it to be a mixingale.}
+difference between $\E_R \oosA$ and $\E_T \oosB$ is of order
+$\lvert \hat\theta_R - \hat\theta_T \rvert_2$, which itself is of
+order $\sqrt{\frac{P}{T}}$.
 
@@
       Lemma~\ref{res-mixingale}, the proof of this lemma takes
-      \citepos{JoD:00} existing consistency results
+      \citepos{DeD:00} existing consistency results
       for \ned\ processes and shows that the same arguments can be
@@
   \ref{asmp-2}, \ref{asmp-3}, and \ref{asmp-5} hold, that $\gamma, P$
-  and $R \to \infty$ as $T \to \infty$, and that $\gamma = o(P)$.
-  Then
-  \begin{equation*}
-    P^{-1} \oosSum{s,t}{1} (D_{Rt} - \oosA)(D_{Rs} - \oosA)
+  and $R \to \infty$ as $T \to \infty$, and that $\gamma = o(P)$.  Then
+  \begin{equation*}
+    \frac1P \oosSum{s,t}{1} (D_{tR} - \oosA)(D_{sR} - \oosA)
     \vWeight = \sigma^2 + o_p(1).
@@
 \end{lem}
-
-\subsection{An Example}\label{sec:example}
 
@@
 This subsection establishes that the F-test can over-reject when the
-benchmark is more accurate than the alternative.  The issue explored
-here is different than that of \citet{Ana:12} and \citet{Cal:11c}; in
-those papers, the authors demonstrate that full sample Wald and $F$
-tests can be invalid under these asymptotics.  But in this subsection,
-we make stronger assumptions than elsewhere in the paper to guarantee
-that the $F$-test is valid; we assume the models are nested, the loss
-function is squared-error, the regressors are fixed, and the errors
-are i.i.d. normal, so the exact finite sample distribution of the
-$F$-test is known.\footnote{These assumptions are made to ensure the
-  most favorable conditions for the full-sample test.  The proof of
-  this section's main result relies only on their implication that the
-  acceptence region of the test is an ellipse centered at the origin
-  and the conclusions of Theorem~\ref{res:ftest} should hold
-  qualitatively for any test statistic that has such an acceptance
-  region, including \oos\ tests.} Even so, the $F$-test can not test
-the hypotheses discussed in the previous subsection; under these
-conditions, the probability that it rejects converges to one under the
-null that the benchmark is more accurate.
-
-Theorem~\ref{res:ftest} presents the details.
+benchmark is more accurate than the alternative.  We use stronger
+assumptions than before, i.i.d. data, normal errors, \mse\ loss, and
+nested models to ensure that the F-test performs as well as possible.
+Indeed, we know its exact distribution.  But the basic idea of this
+argument is much more general and should apply to other related tests,
+including \oos\ tests.
+
 \begin{thm}\label{res:ftest}
@@
 as $\phi_2 \to \infty$, \eqref{eq:ftestreject1} is not an immediate
-consequence of the power of the $F$-test increasing with $\phi_2$.
-
-The first result,~\eqref{eq:ftestreject1}, can be understood through
-the case $K_2 = 2$ and $K_1 = 0$, so
+consequence of the power of the F-test increasing with $\phi_2$.
+
+The first result,~\eqref{eq:ftestreject1}, can be understood through the case $K_2 = 2$ and
+$K_1 = 0$, so
 \begin{equation*}
@@
 It is important to remember that the F-test is valid for the null
-$\psi = 0$ in this analysis, so previous research, such as
-\citet{Ana:12} and \citet{Cal:11c}, does not predict these results.
-However, the $F$-test is poorly suited for choosing an accurate
-forecasting model, and performs worse when the larger model is overfit
-or explains more of the variation of the dependent variable.  Other
-asymptotically valid, unbiased tests of the null hypothesis that $\psi
-= 0$ will suffer the same problem.
+$\psi = 0$ in this analysis.  However, the F-test is poorly suited for
+choosing an accurate forecasting model, and performs worse when the
+larger model is overfit or explains more of the variation of the
+dependent variable.  Other valid unbiased tests of the null hypothesis
+that $\psi = 0$ will suffer the same problem.
 
@@
 \begin{equation*}
-  E_R \oosA = \Bigg[\sum_{i=1}^{K_1} (\tilde{\theta}_{iR} - \theta_i)^2 +
-  \sum_{i=K_1+1}^{K_2}\theta_i^2\Bigg] - \sum_{i=1}^{K_2} (\hat{\theta}_{iR} -
+  E_R \oosA = [\sum_{i=1}^{K_1} (\tilde{\theta}_{iR} - \theta_i)^2 +
+  \sum_{i=K_1+1}^{K_2}\theta_i^2] - \sum_{i=1}^{K_2} (\hat{\theta}_{iR} -
   \theta_i)^2
@@
 \begin{equation*}
-  E_T \oosB = \Bigg[\sum_{i=1}^{K_1} (\tilde{\theta}_{iT} - \theta_i)^2 +
-  \sum_{i=K_1+1}^{K_2}\theta_i^2\Bigg] - \sum_{i=1}^{K_2} (\hat{\theta}_{iT} -
+  E_T \oosB = [\sum_{i=1}^{K_1} (\tilde{\theta}_{iT} - \theta_i)^2 +
+  \sum_{i=K_1+1}^{K_2}\theta_i^2] - \sum_{i=1}^{K_2} (\hat{\theta}_{iT} -
   \theta_i)^2
@@
 modifications of existing results for \ned\ functions of mixing
-processes by \citet{Jon:97} and
-\citet{JoD:00}; this coupling argument is used to
+processes by \citet{Dej:97} and
+\citet{DeD:00}; this coupling argument is used to
 explicitly derive inequalities that arise naturally for \ned\
@@
 
-\begin{lem}
-  Suppose the conditions of Lemma~\ref{res-variance-estimator} hold
-  and let $D_{Rt}$ denote the fixed window statistic and $D_{Rt}'$ the
-  recursive or rolling window statsitics.  Then
-  \begin{multline*}P^{-1} \oosSum{s,t}{1} (D_{Rt}' - \oosA')(D_{Rs}' -
-    \oosA') \vWeight = \\ P^{-1} \oosSum{s,t}{1} (D_{Rt} - \oosA)(D_{Rs}
-    - \oosA) \vWeight + o_p.
-  \end{multline*}
-\end{lem}
-
-\begin{proof}
-  yeah!
-\end{proof}
-
 \section{Proofs of results in main text}
@@
 centered \oos\ average as
-
-\[
-\frac{\bar{D}_{R} - \E_T \bar{D}_T}{\hat\sigma / \sqrt{P}} =
-\frac{1}{\hat\sigma \sqrt{P}}\oosSum{t}{1} (D_{Rt} - \E_R D_{Rt}) +
-\frac{\sqrt{P}}{\hat\sigma} (\E_R\oosA - \E_T\oosB).
+  \[
+    \CenteredAverage = \CenteredAverageI + \CenteredAverageII.
   \]
@@
 Then
-\begin{align*}
-\lVert \E_{R+j-l} D_{R+j,R} - \E_R D_{R+j,R} \rVert_2 & \leq 
+\[
+\lVert \E_{R+j-l} D_{R+j,R} - \E_R D_{R+j,R} \rVert_2 \wall \leq 
 \lVert \E_{R+j-l} D_{R+j,R} - \E_{R+j-l} \tilde{D}_{R+j} \rVert_2 \\
-&\quad + \lVert
+\quad + \lVert
 \E_{R+j-l} \tilde{D}_{R+j} - \E_R D_{R+j,R} \rVert_2 \\
-&\leq 2 \lVert D_{R+j,R} - \tilde D_{R+j} \rVert_2 \\
-&\leq 2^{2 + 1/\rho}\ B_L\ \couplingBeta{l}.
-\end{align*}
+\leq 2 \lVert D_{R+j,R} - \tilde D_{R+j} \rVert_2 \\
+\leq 2^{2 + \frac1\rho}\ B_L\ \couplingBeta{l}.\return
+\]
 Now $\couplingBeta{l} = O(l^{-\frac12 - \delta})$ for some
@@
 \begin{proof}[Proof of Lemma \ref{res-mixingale}, Part 2.]
-  A modification of \citepos{Jon:97} \clt s for
+  A modification of \citepos{Dej:97} \clt s for
   mixingale and \ned\ arrays will complete the proof.
@@
 $b_T\to\infty$, and $b_T/P\to 0$.  The same arguments used in
-\citepos{Jon:97} Theorem 1 show that
-\begin{equation*}
-   \SumOuterBlock{i} Z_i = \frac1{\sqrt{P}} \oosSum{s}{1} (D_{Rt} - \E_R D_{Rt}) + o_p(1).
+\citepos{Dej:97} Theorem 1 show that
+\begin{equation*}
+   \SumOuterBlock{i} Z_i = \frac1{\sqrt{P}} \oosSum{s}{1} (D_{tR} - \E_R D_{tR}) + o_p(1).
 \end{equation*}
@@
 \end{equation}
-Equation (\ref{eq:cltvar2}) holds as in \citet{Jon:97} (see the proof
+Equation (\ref{eq:cltvar2}) holds as in \citet{Dej:97} (see the proof
 of his Theorem 2); to see that (\ref{eq:cltvar1}) holds, we'll use an
@@
 \[
-\lVert \tilde D_s - D_{Rs} \rVert_2 \leq 2^{1 + \frac1\rho} B_L \beta_{s -
+\lVert \tilde D_s - D_{sR} \rVert_2 \leq 2^{1 + \frac1\rho} B_L \beta_{s -
   (i-1)b_T + R}^{\rhoExp}, \quad s = R+(i-1)b_T + 1,\dots,R+i b_T
@@
 giving the inequality
-\begin{align*}
-  \lVert \ZSqCE - \E_R Z_i^2 \rVert_1 &= \lVert
-  \CEOuterBlock{(Z_i^2 - \tilde Z_i^2)}{i} - (\E_R Z_i^2 -
-  \CEOuterBlock{\tilde Z_i^2}{i}) \rVert_1 \\ & \leq 2 \lVert Z_i^2 -
-  \tilde Z_i^2 \rVert_1.
-\end{align*}
+\[
+\lVert \ZSqCE - \E_R Z_i^2 \rVert_1 \wall= \lVert \wall\CEOuterBlock{(Z_i^2 -
+  \tilde Z_i^2)}{i} \\ - (\E_R Z_i^2 - \CEOuterBlock{\tilde Z_i^2}{i})
+\rVert_1 \return\\
+\leq 2 \lVert Z_i^2 - \tilde Z_i^2 \rVert_1.
+\return
+\]
 
@@
 It follows that
-\begin{align*}
-  \SumOuterBlock{i} \lVert V_{i,C}^2 - \tilde V_{i,C}^2 \rVert_1 &
+\[
+\SumOuterBlock{i} \lVert V_{i,C}^2 - \tilde V_{i,C}^2 \rVert_1 
+\wall
  \leq 2 \ZTrunc \SumOuterBlock{i} \lVert Z_i - \tilde Z_i \rVert_2 \\
-  & \leq \frac{2 C \sqrt{b_T}}{P}\SumOuterBlock{i} \SumInnerBlock{s}{i} \lVert \ZSummand
-  - (\tilde D_s - \E_R \tilde D_s) \rVert_2 \\
-  & = O(\frac{\sqrt{b_T}}{P}) \SumOuterBlock{i} \SumInnerBlock{s}{i} \lVert D_{Rs} - \tilde D_s \rVert_2 \\
-  & = O(b_T^{-\frac12}) \sum_{s=1}^{b_T} \couplingBeta{s} 
-\end{align*}
+ \leq \frac{2 C \sqrt{b_T}}{P}\SumOuterBlock{i} \SumInnerBlock{s}{i} \lVert \wall \ZSummand \\
+  - (\tilde D_s - \E_R \tilde D_s) \rVert_2 \return \\ 
+ = O(\frac{\sqrt{b_T}}{P}) \SumOuterBlock{i} \SumInnerBlock{s}{i} \lVert D_{sR} - \tilde D_s \rVert_2 \\
+ = O(b_T^{-\frac12}) \sum_{s=1}^{b_T} \couplingBeta{s}
+ \return
+ \]
 Finally, $\couplingBeta{s} = O(s^{-1/2-\delta})$ for some positive
@@
 \[
-\lVert \tilde D_t - D_{Rt} \rVert_2 \leq \couplingBound{t-R}
+\lVert \tilde D_t - D_{tR} \rVert_2 \leq \couplingBound{t-R}
 \]
@@
 for all $t$.  Then 
-\begin{align*}
-\lVert \E_R \oosA - & \resConvgRHS{R} \rVert_2  \\
-& \leq \frac1P \oosSum{t}{1} \lVert \E_R (D_{Rt} - \tilde D_t) \rVert_2 \\
-& \leq \frac{\couplingConstant}{P} \oosSum{s}{1} \couplingBeta{s} \\
-& = o(P^{-\frac12}).
-\end{align*}
+\[
+\lVert \E_R \oosA - \wall \resConvgRHS{R} \rVert_2  \\
+\leq \frac1P \oosSum{t}{1} \lVert \E_R (D_{tR} - \tilde D_t) \rVert_2 \\
+\leq \frac{\couplingConstant}{P} \oosSum{s}{1} \couplingBeta{s} \\
+= o(P^{-\frac12}).
+\return
+\]
 The proof of (\ref{EQ-oosaverage2}) is identical.
@@
 Manipulating the formula for the \ols\ estimator gives us
-\begin{multline} \label{eq-theta-convergence-1}
-\lVert x_1^{*\prime} (\bh{1R} - \bh{1T}) \rVert_2  \leq\\
+\begin{equation} \label{eq-theta-convergence-1}
+\lVert x_1^{*\prime} (\bh{1R} - \bh{1T}) \rVert_2 \wall \leq
 \lVert x_1^{*\prime} [(X_{1R}'X_{1R})^{-1} - (X_{1T}'X_{1T})]
-X_{1T}'\ep{1T} \rVert_2  +
+X_{1T}'\ep{1T} \rVert_2  \\ \quad +
 \lVert x_1^{*\prime} (X_{1R}'X_{1R})^{-1}\oosSum{t}{1} x_{1t}\varepsilon_{i,t+\h}
 \rVert_2.
-\end{multline}
+\end{equation}
 The first term on the right side of \eqref{eq-theta-convergence-1}
 satisfies the relationship
-\begin{multline*}
-  \lVert x_{1}^{*\prime}[(X_{1R}'X_{1R})^{-1} - (X_{1T}'X_{1T})^{-1} ]
-  X_{1T}'\ep{1T} \rVert_2^2 = \\ O(1) \E\{\lambda_{\max}(X_{1T}'
-  \ep{1T} \ep{1T}' X_{1T}) \sum_{i=1}^{K_1}
-  \lambda_i^2([X_{1R}'X_{1R}]^{-1} - [X_{1T}'X_{1T}]^{-1} )\}.
-\end{multline*}
+\[
+\lVert x_{1}^{*\prime}[(X_{1R}'X_{1R})^{-1} -
+(X_{1T}'X_{1T})^{-1} ]
+X_{1T}'\ep{1T} \rVert_2^2 \\ = O(1)
+\E\{\lambda_{\max}(X_{1T}' \ep{1T} \ep{1T}'
+    X_{1T}) \sum_{i=1}^{K_1}
+    \lambda_i^2([X_{1R}'X_{1R}]^{-1} -
+        [X_{1T}'X_{1T}]^{-1} )\}.
+\]
 By assumption, $\lambda_{\max}(X_{1T}'\ep{1T} \ep{1T}' X_{1T}) =
@@
   \[\sum_{i=1}^{K_1}\lambda_i^2((X_{1R}'X_{1R})^{-1} -
-  (X_{1T}'X_{1T})^{-1} ) \leq
+  (X_{1T}'X_{1T})^{-1} )  \wall \leq
   \sum_{i=K_1 - P + 1}^{K_1}\lambda_i^2((X_{1R}'X_{1R})^{-1})  \\ = O_p(P/T^2).
@@
 \begin{proof}[Proof of Lemma \ref{res-variance-estimator}]
-  The proof follows \citepos{JoD:00} Theorem 2.1 closely.  We start by
-  defining similar quantities to theirs, borrowing their notation when
-  possible to make the similarities apparent.  For positive $\delta$,
-  define $b_T \equiv \lfloor \frac\gamma\delta \rfloor$, $\kernelB{x}
-  \equiv \kernelBDefn{x}$, and
-\begin{align*}
-  \varianceTermI &\equiv
-  \varianceTermIDefn,\\ \varianceTermII &\equiv \vtSum
-  \varianceTermIIa\\& \quad \times \varianceTermIIb,\\
-  \varianceTermIII &\equiv \vtSum \varianceTermIIIa\\
-  &\quad \times \varianceTermIIb,\\
-  \varianceTermIV &\equiv \vtSum \varianceTermIIIa \\
-  &\quad\times \varianceTermIVb,
-\end{align*}
+  The proof follows \citepos{DeD:00} Theorem 2.1
+  closely.  We start by defining similar quantities to theirs,
+  borrowing their notation when possible to make the similarities
+  apparent.  For positive $\delta$, define $b_T \equiv \lfloor
+  \frac\gamma\delta \rfloor$,
+\begin{equation*}
+  \kernelB{x} \equiv \kernelBDefn{x},
+\end{equation*}
+\begin{equation*}
+  \varianceTermI \equiv \varianceTermIDefn,
+\end{equation*}
+\begin{equation*}
+  \varianceTermII \equiv \vtSum \wall \varianceTermIIa\\ \times
+  \varianceTermIIb,\return
+\end{equation*}
+\begin{equation*}
+  \varianceTermIII \equiv \vtSum \wall \varianceTermIIIa\\ 
+  \times \varianceTermIIb, \return 
+\end{equation*}
+\begin{equation*}
+  \varianceTermIV \equiv \vtSum \wall \varianceTermIIIa \\
+  \times \varianceTermIVb, \return
+\end{equation*}
 giving us the inequalities
-\begin{align*}
-  \lVert \hat\sigma^2 - \sigma^2 \rVert_1 &
+\begin{equation*}
+  \lVert \hat\sigma^2 - \sigma^2 \rVert_1 \wall 
   \leq \lVert \hat\sigma^2 - \varianceTermI \rVert_1 
@@
   + \lVert \varianceTermII - \varianceTermIII \rVert_1 
-  + \lVert \varianceTermIII - \varianceTermIV \rVert_1\\ & \quad
+  + \lVert \varianceTermIII - \varianceTermIV \rVert_1\\\quad
   + \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1 
   + \lVert \E_R\varianceTermIII - \E_R\varianceTermIV \rVert_1
-  + \lVert \E_R\varianceTermII - \E_R\varianceTermIII \rVert_1\\ & \quad 
+  + \lVert \E_R\varianceTermII - \E_R\varianceTermIII \rVert_1\\\quad 
   + \lVert \E_R\varianceTermI - \E_R\varianceTermII \rVert_1 
   + \lVert \E_R \varianceTermI - \sigma^2 \rVert_1
-  \\ &
+  \\ 
   \leq  \lVert \hat\sigma^2 - \varianceTermI \rVert_1 
@@
       + \lVert \varianceTermIII - \varianceTermIV \rVert_1) \\ 
-  & \quad + \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1 
+  \quad + \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1 
   + \lVert \E_R \varianceTermI - \sigma^2 \rVert_1.
-\end{align*}
+\end{equation*}
 De Jong and Davidson (2000) prove that
@@
 We'll start with (\ref{eq:4}). It follows from simple algebra that
-\begin{align*}
-  \lvert \hat\sigma^2 - \varianceTermI \rvert & \leq  
-  \varianceDiffA \\ & \quad + \frac1{P} \oosSum{s,t}{1} \lvert (D_{Rt} -
-  \oosA)(\E_R D_{Rs} - \oosA) \rvert \vWeight,
-\end{align*}
+\[
+\lvert \hat\sigma^2 - \varianceTermI \rvert \leq \wall
+\varianceDiffA \\ +
+\frac1{P} \oosSum{s,t}{1} \lvert (D_{tR} - \oosA)(\E_R D_{sR} - \oosA) \rvert
+\vWeight,
+\]
 so we'll show that each summation is $o_p(1)$.  The two
@@
 upper bound
-\begin{multline*}
-\varianceDiffA \\ \leq O(1) [\varianceDiffAii]^{\frac12} [\varianceDiffAi]^{\frac12}.
-\end{multline*}
+\[
+\varianceDiffA \\ \quad \leq O(1) [\varianceDiffAii]^{\frac12} [\varianceDiffAi]^{\frac12}.
+\]
 Now,
-$\frac1P \oosSum{s}{1}(D_{Rs} - \E_R D_{Rs})^2 = O_p(1)$, and it suffices to prove
+$\frac1P \oosSum{s}{1}(D_{sR} - \E_R D_{sR})^2 = O_p(1)$, and it suffices to prove
 that \[\varianceDiffAi = o_p(1).\]  Observe that
-\begin{align*}
-  \varianceDiffAi & = O_p\Big(P^{-1} \oosSum{s}{1}(\E_{R}D_{Rs} -
-  \E_R\oosA)^2\Big) + O_p(\oosA - \E_R\oosA)^{2} \\
-  &= O_p\Big(P^{-1} \oosSum{s}{1} (\E_RD_{Rs})^2 - (\E_R\oosA)\Big) +
-  o_p(1),
-\end{align*}
+\[
+\varianceDiffAi \wall =  O_p(\frac1P \oosSum{s}{1}(\E_{R}D_{sR} -
+\E_R\oosA)^2) \\
+\quad + O_p(\oosA - \E_R\oosA)^{2} \\
+= O_p(\frac1P \oosSum{s}{1} (\E_RD_{sR})^2 - (\E_R\oosA)^2) + o_p(1),    \return
+\]
 with the second term vanishing by Lemma \ref{res-mixingale} and
@@
 Consequently,
-\begin{align*}
-\frac1P \oosSum{s}{1} (\E_R D_{Rs})^2 - (\E_R\oosA)^2 & = 
-\frac1P \oosSum{s}{1} [(\E_R D_{Rs})^2 - (\E_R\tilde D_s)^2]\\
-&\quad+ \Big(P^{-1} \oosSum{s}{1} \E_R \tilde D_s\Big)^2 - (\E_R\oosA)^2 \quad \text{a.s}.\\
-&= O_p\Big(P^{-1} \oosSum{s}{1} [(\E_R D_{Rs})^2 - (\E_R \tilde D_s)^2]\Big).
-\end{align*}
+\[
+\frac1P \oosSum{s}{1} (\E_R D_{sR})^2 - (\E_R\oosA)^2 \wall = 
+\frac1P \oosSum{s}{1} [(\E_R D_{sR})^2 - (\E_R\tilde D_s)^2]\\
+\quad+ (\frac1P \oosSum{s}{1} \E_R \tilde D_s)^2 - (\E_R\oosA)^2 \quad \text{a.s}.\\
+= O_p(\frac1P \oosSum{s}{1} [(\E_R D_{sR})^2 - (\E_R \tilde D_s)^2]).
+\]
 Finally, 
-\begin{align*}
-\lVert \frac1P \oosSum{s}{1} [(\E_RD_{Rs})^2 - (\E_R \tilde D_s)^2] \rVert_1
-&\leq \frac1P \oosSum{s}{1} \lVert \E_RD_{Rs} - \E_R \tilde D_s \rVert_2 \lVert
-\E_RD_{Rs} + \E_R \tilde D_s \rVert_2
-\\ &\leq \frac{4 B_L}P \oosSum{s}{1} \lVert \E_RD_{Rs} - \E_R \tilde D_s \rVert_2,
-\end{align*}
+\[
+\lVert \frac1P \wall\oosSum{s}{1} [(\E_RD_{sR})^2 - (\E_R \tilde D_s)^2] \rVert_1
+\\ \leq \frac1P \oosSum{s}{1} \lVert \E_RD_{sR} - \E_R \tilde D_s \rVert_2 \lVert
+\E_RD_{sR} + \E_R \tilde D_s \rVert_2
+\\ \leq \frac{4 B_L}P \oosSum{s}{1} \lVert \E_RD_{sR} - \E_R \tilde D_s \rVert_2,
+\return
+\]
 and this last term vanishes as in the proof of Lemma
@@
 \newcommand{\UFiltration}[1]{\ensuremath{\mathcal{F}_{(#1)b_{T}+R-P}}}%
-Next, we'll prove (\ref{eq:5}). As in \citet{JoD:00}, let
+Next, we'll prove (\ref{eq:5}). As in \citet{DeD:00}, let
 \begin{equation*}
@@
 \lfloor \frac{3P}{2b} \rfloor$ and rewrite the summation as
-\begin{align*}
-  \vtSum \vtIIIsummand &= \vtSumr \vtSuma \vtIIIsummand \\
-  &\quad+ \vtSumr \vtSumb \vtIIIsummand \\
-  &\quad+ \sum_{t=r b - P + 1}^{2P} \vtIIIsummand \\
-  &\equiv \vtSumr (U_i - \E_R U_i) + \vtSumr (U_i' - \E_R U_i') + o_{L_1}(1).
-\end{align*}
+\begin{equation*}
+  \vtSum \vtIIIsummand \wall= \vtSumr \vtSuma \vtIIIsummand \\
+  \quad+ \vtSumr \vtSumb \vtIIIsummand \\
+  \quad+ \sum_{t=r b - P + 1}^{2P} \vtIIIsummand \\
+  \equiv \vtSumr (U_i - \E_R U_i) + \vtSumr (U_i' - \E_R U_i') + o_{L_1}(1).\return
+\end{equation*}
 The proof then holds if we can show that both $U_i$ and $U_i'$ obey
@@
 \begin{equation*}
-  \lVert \tilde D_{ts} - D_{Rs} \rVert_2 \leq \couplingBound{s - (2i-2m-1)b_T-R+P}.
+  \lVert \tilde D_{ts} - D_{sR} \rVert_2 \leq \couplingBound{s - (2i-2m-1)b_T-R+P}.
 \end{equation*}
@@
 Now, we have the inequalities
-\begin{align*}
-  \lVert \E( U_i - \E_R U_i \mid \UFiltration{2i-2m-1}) \rVert_2
-  &\leq
+\begin{equation*}
+  \lVert \E( U_i - \wall \E_R U_i \mid \UFiltration{2i-2m-1}) \rVert_2
+  \\ \leq
   \vtSuma \lVert \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) - \E_R
   Z_{1t}Z_{2t} \rVert_2 \\
-  &= \vtSuma \lVert \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
-  &\quad - \E(\tilde{Z}_{1t}\tilde{Z}_{2t} \mid \UFiltration{2i-2m-1}) \\
-  &\quad + \E(\tilde{Z}_{1t}\tilde{Z}_{2t} \mid \UFiltration{2i-2m-1})
-  - \E_R Z_{1t}Z_{2t} \rVert_2 \\
+  = \vtSuma \lVert \wall \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
+  - \E(\tilde{Z}_{1t}\tilde{Z}_{2t} \mid \UFiltration{2i-2m-1}) \\
+  + \E(\tilde{Z}_{1t}\tilde{Z}_{2t} \mid \UFiltration{2i-2m-1})
+  - \E_R Z_{1t}Z_{2t} \rVert_2 \return \\
 %  \leq \vtSuma (\wall \lVert \wall \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
@@
 %  \rVert_2)\return \\
-  &\leq 2 \vtSuma \lVert Z_{1t} Z_{2t} - \tilde Z_{1t} \tilde{Z}_{2t}
+  \leq 2 \vtSuma \lVert Z_{1t} Z_{2t} - \tilde Z_{1t} \tilde{Z}_{2t}
   \rVert_2 \\
-  &\leq 2 \vtSuma (\lVert Z_{1t} - \tilde{Z}_{1t} \rVert_2 \lVert
+  \leq 2 \vtSuma (\lVert Z_{1t} - \tilde{Z}_{1t} \rVert_2 \lVert
   Z_{2t} \rVert_{\infty}
   + \lVert Z_{2t} - \tilde{Z}_{2t} \rVert_2 \lVert \tilde{Z}_{1t} \rVert_{\infty}) \\
-  &\leq 2 C \sqrt{\frac{b_T}{P\gamma}} \vtSuma (\lVert Z_{1t} - \tilde{Z}_{1t} \rVert_2 
+  \leq 2 C \sqrt{\frac{b_T}{P\gamma}} \vtSuma (\lVert Z_{1t} - \tilde{Z}_{1t} \rVert_2 
   + \lVert Z_{2t} - \tilde{Z}_{2t} \rVert_2).
-\end{align*}
+  \return
+\end{equation*}
 
 And we can finish the proof with the following inequalities:
-\begin{align*}
-  2 C \sqrt{\frac{b_T}{P \gamma}} \vtSuma & \lVert Z_{1t} - \tilde{Z}_{1t} \rVert_2 \\& \leq
+\begin{equation*}
+  2 C \wall \sqrt{\frac{b_T}{P \gamma}} \vtSuma \lVert Z_{1t} - \tilde{Z}_{1t} \rVert_2 \\ \leq
   \frac{4C \sqrt{b_T}}{P\gamma} \vtSuma \sum_{l=\vttLower}^{\vttUpper} \lVert
-  D_{t+l+R,R} - \tilde{D}_{t,t+l+R} \rVert_2 W(l/\gamma) \\&
+  D_{t+l+R,R} - \tilde{D}_{t,t+l+R} \rVert_2 W(l/\gamma) \\
   \leq O(\frac{\sqrt{b_T}}{P\gamma}) \vtSuma
-  \sum_{l=\vttLower}^{\vttUpper} \couplingBeta{t+l-(2i-2m-1)b_T+P}\\&
+  \sum_{l=\vttLower}^{\vttUpper} \couplingBeta{t+l-(2i-2m-1)b_T+P}\\
   = O(\frac{\sqrt{b_T}}{P\gamma}) O(b_T^{\frac32-u}\, m^{-\frac12-u})
-\end{align*}
+\end{equation*}
 for some positive $u$.  The same argument holds for $Z_{2t}$.
@@
 \[
-E_T \oosB = \sum_{j=K_1+1}^{K_2} [\psi_j^2 - (\hat{\psi}_j - \psi_j)^2].
-\]
-For any $\hat{\theta}$, $E_T \oosB$ equals zero when $\hat{\psi}$ lies
-on the surface of the hypersphere centered at $\psi$ with radius
-$|\psi|_2$, and $E_T \oosB$ and is greater than zero when $\hat{\psi}$
-lies outside that sphere.  Also, the rejection region in $\Re^{K_2}$
-for the F-test is the set of values of $\hat{\psi}$ on or beyond the
-sphere
+E_T \oosB = \sum_{j=K_1+1}^{K_2} [\psi_j^2 - (\hat{\psi}_j - \psi_j)^2]
+\]
+For any $\hat{\theta}$, $E_T \oosB$ equals zero when
+$\hat{\psi}$ lies on the surface of the hypersphere centered at
+$\psi$ with radius $|\psi|_2$, and $E_T \oosB$ and is greater
+than zero when $\hat{\psi}$ lies outside that sphere.
+Also, the rejection region in $\Re^{K_2}$ for is the set of values of $\hat{\psi}$
+on or beyond the sphere
 \[
@@
 As a result,
-\begin{align*}
-  \Pr[F \geq q_{\alpha} \mid E_T \oosB \leq 0] &=
-  \Pr[\hat{\psi}'\hat{\psi} \geq \hat \tau^2 q_\alpha \frac{K_2 -
-    K_1}{T}
+\[
+\Pr[F \geq q_{\alpha}\wall \mid E_T \oosB \leq 0] = 
+\Pr[\hat{\psi}'\hat{\psi} \geq \hat \tau^2 q_\alpha \frac{K_2 - K_1}{T}
 \mid |\hat{\psi}-\psi|_2 \geq |\psi|_2] \\
-  &\geq 1 - \E(\;\Pr[ \hat{\omega}_i \in [\tilde{\omega}_i - \xi,
-  \tilde{\omega}_i + \xi] \ \forall i \mid \hat{\tau}^2,
-  |\hat{\psi}-\psi|_2 \geq |\psi|_2] \\
-  &\qquad\qquad \mid |\hat{\psi}-\psi|_2 \geq |\psi|_2)\quad a.s. \\
-  &= 1 - \frac12 E ((2\xi / \pi)^{K_2-K_1-1}\mid
+\geq 1 - \E(\Pr\{ \hat{\omega}_i \in [\tilde{\omega}_i - \xi, \tilde{\omega}_i +
+\xi] \ \forall i  \mid \hat{\tau}^2,
+|\hat{\psi}-\psi|_2 \geq |\psi|_2\} 
+\mid |\hat{\psi}-\psi|_2 \geq |\psi|_2)\quad a.s. \\ 
+= 1 - \frac12 E ((2\xi / \pi)^{K_2-K_1-1}\mid
 |\hat{\psi}-\psi|_2 \geq |\psi|_2)\quad a.s. \\
-  &= 1 - \frac12 E (2\xi/\pi)^{K_2-K_1-1} \quad a.s..
-\end{align*}
+= 1 - \frac12 E (2\xi/\pi)^{K_2-K_1-1} \quad a.s..
+\]
 The second equality holds because the $\hat{\omega}_i$s are uniform
@@
 
-\begin{table}[h]
+\begin{table}[b]
  \begin{multicols}{2}
@@
 
-\begin{table}[b]
+\begin{table}[!tbp]
  \begin{center}
  \begin{tabular}{lrrrr}\hline\hline
-   \multicolumn{1}{l}{waldtest}&\multicolumn{1}{c}{Res.Df}&\multicolumn{1}{c}{Df}&\multicolumn{1}{c}{F}&\multicolumn{1}{c}{Pr(\textgreater
-     F)}\tabularnewline
+\multicolumn{1}{l}{waldtest}&\multicolumn{1}{c}{Res.Df}&\multicolumn{1}{c}{Df}&\multicolumn{1}{c}{F}&\multicolumn{1}{c}{Pr(\textgreaterF)}\tabularnewline
 \hline
@@
   \large{Simulated Rejection Probability of Clark and West
-      (2006, 2007) Test \\ Under $E_T \oosB \leq 0$}
+      (2006, 2007) Test Under $E_T \oosB \leq 0$}
   \includegraphics{mc/plots/size-clarkwest}
@@
 
+% LocalWords: LM clark meese diebold chao corradi mccracken giacomini lm jel iR
+% analyses inoue datasets huber efron anova akritas
+% calhoun iR berbee th de nondifferentiable jong
+% mixingales mcleish AIC Berbee's merlevede Heyde's ib
+% mixingaleR TP eq dx dy tex tR tS tT iT sR sw tw vw
+% reestimate davidson over-reject anatolyev Anatolyev's iS izx
+% coefpart normalpart Jong's jt oos underrejects cltvar Scwarz JEL
+% hansen lm McCracken's jel RSQLite elemstatlearning rproject rsqlite
 % LocalWords:  McCracken's kilian anatolyev rossi REStud JAppliedEconometrics
-% LocalWords:  goyal welch rfs reputational calhoun Berbee's mixingales Rt tS
-% LocalWords:  Heteroskedasticity Autocorrelation Tt iT th berbee iS de dx ixz
-% LocalWords:  DMW mcleish Rs eq ftestreject lightgray veclen RSQLite zeileis
+% LocalWords:  goyal welch rfs reputational calhoun Berbee's mixingales tR tS
+% LocalWords:  Heteroskedasticity Autocorrelation tT iT th berbee iS de dx ixz
+% LocalWords:  DMW mcleish sR eq ftestreject lightgray veclen RSQLite zeileis
 % LocalWords:  heteroskedasticity hothorn RNews JStatSoftware harrell campbell
@@
 % LocalWords:  anova akritas jong normalpart coefpart Jong's rproject rsqlite
-% LocalWords:  unrestrictive datasets Heyde's ib oos Mcc MeR StW InK DiM CCS
-% LocalWords:  ClM CoS ClW GiW GiR GoW Cla HTF Efr BoB AkA AkP DeD Mcl Dej Rde
-% LocalWords:  Sar Zeh Zei Har CaT NeW MeP HaH AllRefs
+% LocalWords:  unrestrictive datasets Heyde's ib oos

### 2012-03-30 empirics/goyal-code/CalcOOS.m

@@ -1,43 +1,0 @@
-function OOS=CalcOOS(N,Eunc,Eols,K,dBeg,dEnd,fBeg)
-% function OOS=CalcOOS(Eunc,Eols,dBeg,dEnd,fBeg)
-% -------------------------------------------------------------------------
-% Inputs
-% N is the regression lag-1 for next period prediction, more for multi-year
-% Eunc and Eols are errors
-% dBeg, dEnd, and fBeg should be numbers like 50, 89, and 123
-% K is the number of variables in X
-% -------------------------------------------------------------------------
-% Outputs
-% OOS is output
-% -------------------------------------------------------------------------
-
-load CrtVal; % Diebold Marianno
-E1=Eunc; E2=Eols;
-E1sq=E1.^2; E2sq=E2.^2;
-R=fBeg-dBeg; P=dEnd-fBeg+1; pi=P/R;
-
-d=E1sq-E2sq;
-dbar=mean(d);
-Q2=0;
-for ii=-(N-1):(N-1)
-    absii=abs(ii);
-    Q2=Q2+(N-absii)/N*sum((d(absii+1:end)-dbar).*(d(1:end-absii)-dbar));
-end
-Q2=Q2/P;
-OOS_T=sqrt(P+1-2*N+N*(N-1)/P)*dbar/sqrt(Q2);
-%OOS_T=sqrt(P-N+1)*dbar/sqrt(Q2);
-OOS_F=(P-N+1)*(mean(E1sq)-mean(E2sq))/mean(E2sq);
-ENC_NEW=(P-N+1)*(mean(E1sq)-mean(E1.*E2))/mean(E2sq);
-lambd=(Eunc-Eols)\Eunc;
-
-CrtVals=[interp1(Crtpi,OOS_T_90(K,:),pi) ...
-        interp1(Crtpi,OOS_T_95(K,:),pi)  ...
-        interp1(Crtpi,OOS_T_99(K,:),pi)  ...
-        interp1(Crtpi,OOS_F_90(K,:),pi) ...
-        interp1(Crtpi,OOS_F_95(K,:),pi) ...
-        interp1(Crtpi,OOS_F_99(K,:),pi) ...
-        interp1(Crtpi,ENC_NEW_90(K,:),pi) ...
-        interp1(Crtpi,ENC_NEW_95(K,:),pi) ...
-        interp1(Crtpi,ENC_NEW_99(K,:),pi)];
-OOS=[OOS_T OOS_F ENC_NEW lambd CrtVals];
-return;

### 2012-03-30 empirics/goyal-code/Forecast.m

@@ -1,32 +1,0 @@
-function [Eunc,Eols]=Forecast(N,R,X,dBeg,dEnd,fBeg,IncludeCAY,CAYALL)
-% function [Eunc,Eols]=Forecast(N,R,X,dBeg,dEnd,fBeg)
-% -------------------------------------------------------------------------
-% Inputs
-% N is the regression lag-1 for next period prediction, more for multi-year
-% dBeg, dEnd, and fBeg should be numbers like 50, 89, and 123
-% IncludeCAY==1 is cay is to re-estimated
-% CAYALL is the re-estimated cay
-% -------------------------------------------------------------------------
-% Outputs
-% Eunc and Eols are computed for the sample period fBeg:dEnd (not dBeg:dEnd)
-% -------------------------------------------------------------------------
-
-[T k]=size(X);
-Runc=R; Rols=R;
-for t=fBeg-N:dEnd-N
-    y=R(dBeg+N:t);
-    T=length(y);
-    x=[ones(T,1) X(dBeg:t-N,:)];
-    xx=[1 X(t,:)];  
-    if IncludeCAY==1
-        x=[x(:,1:end-1) CAYALL(dBeg:t-N,t)];
-        xx=[xx(1:end-1) CAYALL(t,t)];
-    end
-    bols=x\y;
-    bunc=mean(R(dBeg+N:t));
-    Rols(t+N)=xx*bols;
-    Runc(t+N)=bunc;
-end
-Eunc=Runc(fBeg:dEnd)-R(fBeg:dEnd);
-Eols=Rols(fBeg:dEnd)-R(fBeg:dEnd);
-return;

### 2012-03-30 empirics/goyal-code/InSampleFun.m

@@ -1,62 +1,0 @@
-function [mae,rmse,adjr2,fpval1,fpval2,dmae,drmse,adjr2B,dmaeB,drmseB]=InSampleFun(N,R,X,dBeg,dEnd,fBeg)
-% function [mae,rmse,adjr2,fpval1,fpval2,dmae,drmse,adjr2B,dmaeB,drmseB]=InSampleFun(N,R,X,dBeg,dEnd,fBeg)
-% -------------------------------------------------------------------------
-% Inputs
-% N is the regression lag-1 for next period prediction, more for multi-year
-% dBeg, dEnd, and fBeg should be numbers like 50, 89, and 123
-% -------------------------------------------------------------------------
-% Outputs
-% mae and rmse are computed for the sample period fBeg:dEnd (not dBeg:dEnd)
-% adjr2 is the r2 for the actual sample dBeg:dEnd
-% fpval1 is computed based on OLS errors 
-% fpval2 is computed based on NW errors 
-% dmae is Delta MAE (B is for OOS period)
-% drmse is Delta RMSE (B is for OOS period)
-% -------------------------------------------------------------------------
-
-y=R(dBeg+N:dEnd);
-T=length(y);
-x=[ones(T,1) X(dBeg:dEnd-N,:)];
-[T k]=size(x);
-
-[bols,varOls,varNwest,adjr2,var_e]=myols(x,y);
-eols=y-x*bols;
-bols=bols(2:end);
-varOls=varOls(2:end,2:end);
-varNwest=varNwest(2:end,2:end);
-fstat1=bols'*inv(varOls)*bols/(k-1); % F(K-1,T-K) large values reject the null that all betas are zero
-fstat2=bols'*inv(varNwest)*bols/(k-1); % F(K-1,T-K) large values reject the null that all betas are zero
-fpval1=1-fcdf(fstat1,k-1,T-k);
-fpval2=1-fcdf(fstat2,k-1,T-k);
-
-y=R(dBeg+N:dEnd);
-eunc=y-mean(y);
-
-% in-sample period
-ee=eols;
-rmse=mean(ee.^2).^.5;
-mae=mean(abs(ee));
-
-ee=eunc;
-maeuncond=mean(abs(ee));
-rmseuncond=mean(ee.^2).^.5;
-
[…]

### 2012-03-30 empirics/goyal-code/Main7Annual.m

@@ -1,182 +1,0 @@
-clear;clc;pack;
-DoModelSel=0;
-load Data_Annual;
-r=[NaN; (Index(2:end)+D12(2:end))./Index(1:end-1)-1]; % simple return
-R1=log(1+r)-log(1+Rfree); % continuosly compounded
-R3=filter(ones(3,1),1,R1); R5=filter(ones(5,1),1,R1);
-R=cell(5,1); R{1}=R1; R{3}=R3; R{5}=R5;
-
-load cay_a cayall; CAYALL=cayall;
-
-adata=cell(19,1); XBEG=zeros(19,1); XEND=zeros(19,1);
-i=0;
-i=i+1; adata{i,1}=dp;     XBEG(i)=1872; XEND(i)=2009;
-i=i+1; adata{i,1}=dy;     XBEG(i)=1872; XEND(i)=2009;
-i=i+1; adata{i,1}=ep;     XBEG(i)=1872; XEND(i)=2009;
-i=i+1; adata{i,1}=de;     XBEG(i)=1872;	XEND(i)=2009;
-i=i+1; adata{i,1}=svar;   XBEG(i)=1885;	XEND(i)=2009;
-i=i+1; adata{i,1}=btom;   XBEG(i)=1921;	XEND(i)=2009;
-i=i+1; adata{i,1}=ntis;   XBEG(i)=1927;	XEND(i)=2009;
-i=i+1; adata{i,1}=eqis;   XBEG(i)=1927;	XEND(i)=2009;
-i=i+1; adata{i,1}=tbl;    XBEG(i)=1920;	XEND(i)=2009;
-i=i+1; adata{i,1}=lty;    XBEG(i)=1919;	XEND(i)=2009;
-i=i+1; adata{i,1}=ltr;    XBEG(i)=1926;	XEND(i)=2009;
-i=i+1; adata{i,1}=tms;    XBEG(i)=1920;	XEND(i)=2009;
-i=i+1; adata{i,1}=dfy;    XBEG(i)=1919;	XEND(i)=2009;
-i=i+1; adata{i,1}=dfr;    XBEG(i)=1926;	XEND(i)=2009;
-i=i+1; adata{i,1}=infl;   XBEG(i)=1919;	XEND(i)=2009;
-i=i+1; adata{i,1}=ik;     XBEG(i)=1947;	XEND(i)=2009;
-i=i+1; adata{i,1}=cay;    XBEG(i)=1945;	XEND(i)=2009;
[…]

### 2012-03-30 oldnotes/slides-cv/approximationMC.R

@@ -1,19 +1,0 @@
-load("mcGlobal.Rdata")
-
-set.seed(30)
-
-mc <- rep(NA, nsims)
-integralMC <- rmc(n = 100000)
-
-for (i in 1:nsims) {
-  d.i <- rmc()
-  
-  model <- lm(y ~ poly(x, K), data = d.i, subset = estimationWindow)
-  err <- d.i$y[-estimationWindow] - predict(model, data.frame(x = d.i$x[-estimationWindow]))
-
-  mc[i] <- sqrt(100) * (mean(err^2) - mean((integralMC$y - predict(model, integralMC))^2)) / sd(err^2)
-  print(i)
-}
-## change
-
-save.image("approximation.Rdata")

### 2012-03-30 oldnotes/slides-cv/approximationQQ.R

@@ -1,13 +1,0 @@
-library(lattice)
-load("mcGlobal.Rdata")
-load("approximation.Rdata")
-
-## generate qq-plot for simulations vs. theoretical quantiles
-png("approximationQQ.png")
-qqmath(mc, col = "black", ylab = "Simulated Values", xlab = "Theoretical Values", aspect = "1")
-dev.off()
-
-png("approximationHist.png")
-hist(mc, 70, freq = F, xlab = "Standardized Simulated Value", main = "")
-curve(dnorm(x), n = 1000, from = -4, to = 4, col = "red", add = T, lwd = 2)
-dev.off()

### 2012-03-30 oldnotes/slides-cv/makeMCGlobal.R

@@ -1,17 +1,0 @@
-maxx <- 3
-K <- 10
-
-nsims <- 1500
-
-n <- 200
-estimationWindow <- 1:100
-
-
-rmc <- function(n = 200) {
-  x <- runif(n, max = maxx)
-  e <- runif(n, min = -1, max = 1)
-  y <- x^2 + e
-  data.frame(y, x)
-}
-
-save.image("mcGlobal.Rdata")

### 2012-03-30 oldnotes/slides-cv/overfitQQ.R

@@ -1,18 +1,0 @@
-library(lattice)
-load("mcGlobal.Rdata")
-load("simulations.Rdata")
-
-muOverfit <- 1/3
-varOverfit <- (1/5 - muOverfit^2) / n
-
-## generate qq-plot for simulations vs. theoretical quantiles
-png("overfitQQ.png")
-qqmath(mcOverfit, col = "black", ylab = "Simulated Values", xlab = "Theoretical Values (West 1996)",
-       distribution = function(p) qnorm(p = p, mean = muOverfit, sd = sqrt(varOverfit)), aspect = "1")
-dev.off()
-
-png("overfitHist.png")
-hist(mcOverfit[mcOverfit < 1], 70, freq = F, ylim = c(0, 20), xlab = "Simulated Value", main = "")
-curve(dnorm(x, mean = muOverfit, sd = sqrt(varOverfit)), from = 0.25, to = 0.45, n = 1000, col = "red", add = T,
-      lwd = 2)
-dev.off()

### 2012-03-30 mc/plot-insample-size.Rnw
Typed up changes to paper

--- 2010-10-18 mc/plot-insample-size.Rnw
@@
 \usepackage[margin=1in]{geometry}
+\usepackage{tikz}
 
@@
 
-<<fig=TRUE,width=5.5, height=4>>=
+<<fig=TRUE,width=5.5, height=4, eps=F, pdf=T>>=
 library(fwPackage)
+library(pgfSweave)
 library(lattice)
@@
               },
-              par.strip.text = list(cex = .65),
+              par.strip.text = list(cex = .55),
               layout = c(2,4),

### 2012-03-30 mc/plot-interval.Rnw
Typed up changes to paper

@@
 library(lattice)
+library(pgfSweave)
 ltheme <- canonical.theme(color = FALSE)     ## in-built B&W theme  
@@
 
-doxyplot <- function(dplot, ...) {
+doxyplot <- function(dplot,...) {
   print(xyplot(I(1 - reject) ~ I(ntest/n) | interaction(nlabel, altlabel, normlabel, sep = ", "),
                data = dplot,
-               ylab = "Coverage", xlab = "P/T",
+               ylab = "Coverage", xlab = "$P/T$",
                panel = function(x,y,...) {
+                 panel.lines(c(0,2/3),c(.9,.9), col = "gray")
                  panel.xyplot(x,y,...,type = "l")
-                 panel.lines(c(0,2/3),c(.9,.9), col = "gray")
                },
                layout = c(4,4),
-               par.strip.text = list(cex = .65),
+               par.strip.text = list(cex = .55),
                index.cond = list(c(13,15,16,14,9,11,12,10,5,7,8,6,1,3,4,2))))
@@
 naive out-of-sample t-test-based interval.
-<<testerror1, fig=TRUE, height = 3.5, width=6>>=
+<<testerror1, fig=TRUE, width=6, eps=F, pdf=T>>=
 d <- dbGetQuery(dbc, sprintf(dstring, 'test.error.1', 500))
@@
 
-Check empirical coverage of $E_{R} \bar{D}_{1}$ for the two-sided
+% Check empirical coverage of $E_{R} \bar{D}_{1}$ for the two-sided
+% naive out-of-sample t-test-based interval.
+% <<testerror2, fig=TRUE, width=6, tikz=T, eps=F, pdf=T>>=
+% d <- dbGetQuery(dbc, sprintf(dstring, 'test.error.2', 500))
+% d$nlabel <- sprintf("T=%d", d$n)
+% d$normlabel <- sprintf("c=%d", d$norm)
+% doxyplot(d)
+% @
+
+Check empirical coverage of $E_{T} \bar{D}_{2}$ for the one-sided
 naive out-of-sample t-test-based interval.
-<<testerror2, fig=TRUE, height = 3.5, width=6>>=
-d <- dbGetQuery(dbc, sprintf(dstring, 'test.error.2', 500))
+<<generror1, fig=TRUE, width=6, eps=F, pdf=T>>=
+d <- dbGetQuery(dbc, sprintf(dstring, 'gen.error.1', 500))
 d$nlabel <- sprintf("T=%d", d$n)
@@
 
-Check empirical coverage of $E_{T} \bar{D}_{2}$ for the one-sided
-naive out-of-sample t-test-based interval.
-<<generror1, fig=TRUE, height = 3.5, width=6>>=
-d <- dbGetQuery(dbc, sprintf(dstring, 'gen.error.1', 500))
-d$nlabel <- sprintf("T=%d", d$n)
-d$normlabel <- sprintf("c=%d", d$norm)
-doxyplot(d) #Empirical coverage of one-sided interval
-@
-
-Check empirical coverage of $E_{T} \bar{D}_{2}$ for the two-sided
-naive out-of-sample t-test-based interval.
-<<generror2, fig=TRUE, height = 3.5, width=6>>=
-d <- dbGetQuery(dbc, sprintf(dstring, 'gen.error.2', 500))
-d$nlabel <- sprintf("T=%d", d$n)
-d$normlabel <- sprintf("c=%d", d$norm)
-doxyplot(d) #Empirical coverage of two-sided interval
-@
+% Check empirical coverage of $E_{T} \bar{D}_{2}$ for the two-sided
+% naive out-of-sample t-test-based interval.  <<generror2, fig=TRUE,
+% width=6, tikz=T, eps=F, pdf=T>>= d <- dbGetQuery(dbc,
+% sprintf(dstring, 'gen.error.2', 500)) d$nlabel <-
+% sprintf("T=%d", d$n)
+% d$normlabel <- sprintf("c=%d", d$norm)
+% doxyplot(d) #Empirical coverage of two-sided interval @
 

### 2012-03-30 mc/plot-oos-size.Rnw
Typed up changes to paper

--- 2010-10-18 mc/plot-oos-size.Rnw
@@
 \usepackage[margin=1in]{geometry}
-
+\usepackage{tikz}
+\input{../macros}
 \begin{document}
@@
 library(lattice)
+library(pgfSweave)
+options(tikzLatexPackages = c(getOption("tikzLatexPackages"),
+          "\\input{../macros.tex}"))
+
 ltheme <- canonical.theme(color = FALSE)     ## in-built B&W theme  
@@
                data = dframe,
-               ylab = "Rejection Probability", xlab = "P/T",
+               ylab = "Rejection Probability", xlab = "$P/T$",
                panel = function(x,y,...) {
@@
                layout = c(4,4),
-               par.strip.text = list(cex = .65),
+               par.strip.text = list(cex = .55),
                index.cond = list(c(13,15,16,14,9,11,12,10,5,7,8,6,1,3,4,2))))
@@
 Empirical size of Clark and West test at 90\% confidence
-<<clarkwest, fig=TRUE, width=6>>=
+<<clarkwest, fig=TRUE, width=6, tikz=T, eps=F, pdf=T, tikz=T>>=
 doxyplot(d[d$transform == "clarkwest",])
@@
 Empirical size of McCracken test at 90\% confidence
-<<mccracken, fig=TRUE, width=6, height=3.5>>=
+<<mccracken, fig=TRUE, width=6, height=3.5, eps=F, pdf=T, tikz=T>>=
   print(xyplot(reject ~ I(ntest/n) | interaction(nlabel,altlabel,normlabel, sep = ", "),
                data = d[d$altlabel=="K=3" & d$transform == "mccracken",],
-               ylab = "Rejection Probability", xlab = "P/T",
+               ylab = "Rejection Probability", xlab = "$P/T$",
                panel = function(x,y,...) {
@@
                  panel.xyplot(x,y,...,type = "l")
-               },
-               layout = c(4,2),
-               par.strip.text = list(cex = .65),
+               }, layout = c(4,2),
+               par.strip.text = list(cex = .55),
                index.cond = list(c(5,7,8,6,1,3,4,2))))
@@
 Empirical size of Naive OOS test at 90\% confidence
-<<dmwsize, fig=TRUE, width=6>>=
+<<dmwsize, fig=TRUE, width=6, eps=F, pdf=T, tikz=T>>=
 doxyplot(d[d$transform == "difference",])
@@
 Empirical power of Naive oos test at 90\% confidence
-<<dmwpower, fig=TRUE, width=6>>=
+<<dmwpower, fig=TRUE, width=6, eps=F, pdf=T, tikz=T>>=
 doxyplot(dpower[dpower$transform == "difference",])

### 2012-03-30 paper.tex
Typed up changes to paper

@@
 \documentclass[11pt]{article}
-%\linespread{1.2}\selectfont
-\usepackage{tikz}
+\usepackage{tikz,setspace}
 \usetikzlibrary{calc}
 \usetikzlibrary{fit}
-\usepackage{graphicx}
-\usepackage{wrapfig}
-\usepackage[round,comma]{natbib}
-\usepackage{setspace,amsmath,amssymb,amsthm,ifthen,subfig,url,multicol}
-\usepackage{fancyhdr}
-\pagestyle{fancy}
-\lhead{\thepage}\chead{}\rhead{}
-\lfoot{}\cfoot{}\rfoot{}
-\renewcommand\headrulewidth{0pt}
+\usepackage[round]{natbib}
+\usepackage[margin=1in]{geometry}
 \onehalfspacing
-\usepackage[margin=1in]{geometry}
-\usepackage{nath}
+
+\input{macros}
 
@@
 
-\DeclareMathOperator{\E}{E}
-\DeclareMathOperator{\var}{var}
-\DeclareMathOperator*{\plim}{plim}
-\DeclareMathOperator{\tr}{tr}
-\DeclareMathOperator{\atan}{atan*}
-
 \newcommand{\citepos}[1]{\citeauthor{#1}'s \citeyearpar{#1}}
 \newcommand{\Citepos}[1]{\Citeauthor{#1}'s \citeyearpar{#1}}
+\newcommand{\clws}{\citeauthor{ClW:06}'s \citeyearpar{ClW:06,ClW:07}}
 
@@
 % command \ols
-\newcommand{\newacronym}[3]{%
-\expandafter\newcommand\expandafter{\csname #1\endcsname}{#2 \textsc{(\MakeLowercase{#3})}%
-\expandafter\renewcommand\expandafter{\csname #1\endcsname}{\textsc{\MakeLowercase{#3}}}}}
-
-\newcommand{\oosA}{\bar{D}_a}
-\newcommand{\oosB}{\bar{D}_b}
-
-\newcommand{\oost}{\ensuremath{\operatorname{oos-t}}}
-\newcommand{\oosSum}[2]{\ensuremath{\sum_{#1=R-\h+#2}^{T-\h}}}
-
-\newcommand{\h}{h}
-\newcommand{\InnerBlockL}[1]{\ensuremath{R+(#1-1)b_T + 1}}
-\newcommand{\InnerBlockU}[1]{\ensuremath{R+#1 b_T}}
-\newcommand{\OuterBlockU}{\lfloor \frac P{b_T} \rfloor}
-\newcommand{\SumOuterBlock}[1]{\ensuremath{\sum_{#1=1}^{\OuterBlockU}}}
-\newcommand{\SumInnerBlock}[2]{\ensuremath{\sum_{#1=\InnerBlockL{#2}}^{\InnerBlockU{#2}}}}
-
-\newcommand{\CEOuterBlock}[2]{\ensuremath{\E_{\InnerBlockU{(#2-1)}} #1}}
-
-\newcommand{\CenteredAverage}{\frac{\oosA - \E_T\oosT}{\hat\sigma / \sqrt{P}}}
-\newcommand{\CenteredAverageI}{\ensuremath{\frac{1}{\hat\sigma
-    \sqrt{P}}\oosSum{t}{1} (D_{tR} - \E_R D_{tR})}}
-\newcommand{\CenteredAverageII}{\ensuremath{\frac{\sqrt{P}}{\hat\sigma}
-    (\E_R\oosA - \E_T\oosB)}}
-
-\newcommand{\MixingaleArray}[1]{\ensuremath{}}
-
-\newcommand{\ZSummand}{D_{sR} - \E_R D_{sR}}
-\newcommand{\ZDef}{ \frac1{\sqrt{P}} \SumInnerBlock{s}{i} [\ZSummand]}
-\newcommand{\ZSqCE}{\ensuremath{\CEOuterBlock{Z_i^2}{i}}}
-\newcommand{\ZTrunc}{\ensuremath{C\sqrt{b_{T}/P}}}
-\newcommand{\PScaleTerm}{\ensuremath{\frac{C \sqrt{b_T}}{P}}}
-
-\newcommand{\vWeight}{W((t-s)/\gamma)}
-\newcommand{\vSummand}{\ensuremath{(D_{tR} - \E_R D_{tR})(D_{sR} - \E_R D_{sR}) \vWeight}}
-\newcommand{\kernelBDefn}[1]{\ensuremath{\frac1{\delta\sqrt{2\pi}}e^{-\frac{#1^2}{2\delta^2}}}}
-\newcommand{\kernelB}[1]{\ensuremath{\eta_{\delta}(#1)}}
-
-\newcommand{\vtSum}{\ensuremath{\sum_{t=-P+1}^{2P}}}
-\newcommand{\vtSumr}{\ensuremath{\sum_{i=1}^r}}
-\newcommand{\vtSuma}{\ensuremath{\sum_{t=(2i-2)b_T-P+1}^{(2i-1)b_T-P}}}
-\newcommand{\vtSumb}{\ensuremath{\sum_{t=(2i-1)b_T-P+1}^{2ib_T-P}}}
-\newcommand{\vttLower}{\ensuremath{\max(1-t,-b_T)}}
-\newcommand{\vttUpper}{\ensuremath{\min(P-t,b_T)}}
-
-\newcommand{\varianceTermIDefn}{\ensuremath{\frac1{P}\oosSum{s,t}{1}
-    \vSummand}}
-\newcommand{\varianceTermI}{\ensuremath{\sigma_{0\delta}^2}}
-\newcommand{\varianceTermII}{\ensuremath{\sigma_{1\delta}^2}}
-\newcommand{\varianceTermIIa}{\ensuremath{\frac1{\sqrt{P\gamma}}
-    \sum_{l=\max(1-t,-P)}^{\min(P-t,P)} (D_{t+l+R,R} - \E_R D_{t+l+R,R})
-    W(l/\gamma)}}
-\newcommand{\varianceTermIIb}{\ensuremath{\frac1{\sqrt{P\gamma}}
-    \sum_{j=1-t}^{P-t} (D_{t+j+R,R} - \E_R D_{t+j+R,R})
-    \kernelB{j/\gamma}}}
-\newcommand{\varianceTermIII}{\ensuremath{\sigma_{2\delta}^{2}}}
-\newcommand{\varianceTermIIIa}{\ensuremath{\frac1{\sqrt{P\gamma}}
-    \sum_{l=\vttLower}^{\vttUpper} (D_{t+l+R,R} - \E_R D_{t+l+R,R})
-    W(l/\gamma)}}
-\newcommand{\varianceTermIV}{\ensuremath{\sigma_{3\delta}^{2}}}
-\newcommand{\varianceTermIVb}{\ensuremath{\frac1{\sqrt{P\gamma}}
-    \sum_{j=\vttLower}^{\vttUpper} (D_{t+j+R,R} - \E_R D_{t+j+R,R})
-    \kernelB{j/\gamma}}}
-\newcommand{\vtIIIsummand}{\ensuremath{(Z_{1t}Z_{2t} - \E_RZ_{1t}Z_{2t})}}
-
-\newcommand{\varianceDiffA}{\ensuremath{\frac1{P} \oosSum{s,t}{1}
-    \lvert (D_{tR} - \E_R D_{tR})(\E_R D_{sR} - \oosA) \rvert
-    \vWeight}}
-\newcommand{\varianceDiffAi}{\ensuremath{\frac1P \oosSum{s}{1}(\E_R
-    D_{sR} - \oosA )^2}}
-\newcommand{\varianceDiffAii}{\ensuremath{\frac1P \oosSum{s}{1}
-    (D_{sR} - \E_R D_{sR})^2}}
-
-\newcommand{\rhoExp}{\ensuremath{\frac{\rho-2}{2\rho}}}
-\newcommand{\absReg}{\ensuremath{\frac\rho{\rho-2}}}
-
-\newcommand{\couplingConstant}{\ensuremath{2^{\frac{1+\rho}{\rho}} B_L}}
-\newcommand{\couplingBeta}[1]{\ensuremath{\beta^{\frac{\rho-2}{2\rho}}_{#1}}}
-\newcommand{\couplingBetaSq}[1]{\ensuremath{\beta^{\frac{\rho-2}{\rho}}_{#1}}}
-\newcommand{\couplingBound}[1]{\couplingConstant \couplingBeta{#1}}
-
-\newcommand{\OCoef}{\ensuremath{O_p(\frac{\sqrt{P}}{T})}}
-
-\newcommand{\bh}[1]{\ensuremath{\hat\theta_{#1}}}
-\newcommand{\ep}[1]{\ensuremath{\boldsymbol{\varepsilon}_{#1}}}
-
-\newcommand{\olsMatrix}[2]{\ensuremath{(#1'#1)^{-1}#1'#2}}
-
-\newcommand{\dmw}{\textsc{dmw}}
-\newcommand{\ols}{\textsc{ols}}
-\newcommand{\mds}{\textsc{mds}}
-\newcommand{\clt}{\textsc{clt}}
-\newcommand{\lln}{\textsc{lln}}
-\newacronym{VAR}{Vector Autoregression}{VAR}
-\newacronym{oos}{out-of-sample}{OOS}
-\newcommand{\dgp}{\textsc{dgp}}
-\newcommand{\hac}{\textsc{hac}}
-\newacronym{ned}{Near Epoch Dependent}{NED}
-\newacronym{mse}{Mean Squared Error}{MSE}
-\newcommand{\sfield}{$\sigma$-field}
-\newcommand{\sfields}{\sfield s}
-\renewcommand{\Re}{\ensuremath{\mathbb{R}}}
-
-\frenchspacing \title{Out-of-Sample Comparisons of Overfit Models}
+
+\title{Out-of-Sample Comparisons of Overfit Models}
 \author{Gray Calhoun\thanks{email: \texttt{gcalhoun@iastate.edu}. I
     would like to thank Julian Betts, Helle Bunzel, Marjorie Flavin,
-    Nir Jaimovich, Lutz Kilian, Michael McCracken, Seth Pruitt, Ross
-    Starr, Yixiao Sun, Allan Timmermann, participants at the 2010
-    Midwest Economics Association Annual Meetings, the 2010 Joint
-    Statistical Meetings, and in many seminars at \textsc{ucsd}, and
-    espeically Graham Elliott for their valuable suggestions, feedback
-    and advice in writing this paper.  I would also like to thank Amit
-    Goyal for providing computer code and data for his 2008 RFS paper
-    with Ivo Welch \citep{GoW:08}.} \\ Iowa State University,
-  Economics Department}
+    Nir Jaimovich, Lutz Kilian, Ivana Komunjer, Michael McCracken,
+    Seth Pruitt, Ross Starr, Jim Stock, Yixiao Sun, Allan Timmermann,
+    Hal White, several anonymous referees, participants at the 2010
+    Midwest Economics Association Annual Meetings, the 2010
+    International Symposium on Forecasting, the 2010 Joint Statistical
+    Meetings, the 2011 \textsc{nber}/\textsc{nsf} Time-Series
+    Conference, and in many seminars at \textsc{ucsd}, and espeically
+    Graham Elliott for their valuable suggestions, feedback and advice
+    in writing this paper.  I would also like to thank Amit Goyal for
+    providing computer code and data for his 2008 \textsc{rfs} paper
+    with Ivo Welch \citep{GoW:08}.} \\ Iowa State University}
 \date{October 24, 2011}
@@
   number of observations so that their ratio remains uniformly
-  positive.  Under this limit theory, the naive Diebold-Mariano-West
-  out-of-sample test can test hypotheses about a key quantity for
-  evaluating forecasting models---a time series analogue to the
-  generalization error---as long as the out-of-sample period is small
-  relative to the total sample size.  Moreover, tests that are
-  designed to reject if the larger model is true, such as the usual
-  in-sample Wald and \textsc{lm} tests and also Clark and McCracken's
-  (2001, 2005a), \citepos{Mcc:07} and Clark and West's (2006, 2007)
-  out-of-sample statistics, will choose the larger model too often
-  when the smaller model is more accurate.
-
-\noindent \textsc{jel} Classification: C01, C12, C22, C52, C53
+  positive.  Even under this limit theory, the naive
+  Diebold-Mariano-West out-of-sample test can test hypotheses about
+  the models' generalization error, a key quantity for evaluating
+  forecasting models.  Moreover, tests that are designed to reject if
+  the larger model is true, such as the usual in-sample Wald and
+  \textsc{lm} tests and also Clark and McCracken's (2001, 2005a),
+  \citepos{Mcc:07}, and Clark and West's (2006, 2007) out-of-sample
+  statistics, will choose the larger model too often when the smaller
+  model is more accurate. Similar results hold for statistics used for
+  in-sample model selection, such as the \aic, \bic, and adjusted
+  $R$-square.
+
+\noindent \textsc{jel} Classification: C12, C22, C52, C53
 
 \noindent Keywords: Generalization Error, Forecasting, Model
-Selection, t-test, Dimension Asymptotics
+Selection, $t$-test, Dimension Asymptotics
 \end{abstract}
+\newpage
 
@@
 models is overfit.  In doing so, we provide a theoretical
-justification for forecasters to use \oos\ instead of
-in-sample comparisons.
-
-Although \oos\ comparisons have been popular in macroeconomics and
-finance since \citepos{MeR:83} seminal study of exchange rate models,
+justification for forecasters to use \oos\ instead of in-sample
+comparisons and discover a practical limitation of existing statistics.
+
+Although \oos\ comparisons have been popular in Macroeconomics and
+Finance since \citepos{MeR:83} seminal study of exchange rate models,
 it is unclear from a theoretical perspective whether or not the
@@
 instability or overfit and allow a researcher to use a conventional
-in-sample comparison---a variation of the F-test, for example.  As
+in-sample comparison---a variation of the $F$-test, for example.  As
 \citet{InK:04} argue, the statistics themselves are designed to test
@@
 and West's assumptions, but maintains the stationarity and dependence
-conditions that permit in-sample comparisons.\footnote{Like us,
-  \citet{Ana:07} allows the number of regressors to increase with $T$.
-  But in that paper, they increase slowly enough that the \ols\
-  coefficients are consistent and asymptotically normal.}
-\citet{GiW:06}, and \citet{GiR:09, GiR:10} are exceptions.  Instead of
-focusing on hypotheses that can be tested by in-sample comparisons,
-\citet{GiW:06} derive an \oos\ test for the null hypothesis that the
-difference between two models' \oos\ forecasting performance is
-unpredictable, a martingale difference sequence; \citet{GiR:09} test
-whether the \oos\ forecasting performance of a model suffers from a
-breakdown relative to its in-sample performance; and \citet{GiR:10}
-test whether the forecasting performance is stable. However, those
-papers focus on a particular \oos\ estimation strategy and do not
-address why naive \oos\ comparisons might be generally useful.
+conditions that permit in-sample comparisons \citep[see][for a recent
+review of this literature]{Wes:06}.\footnote{Like us, \citet{Ana:07}
+  allows the number of regressors to increase with $T$.  But in that
+  paper, they increase slowly enough that the \ols\ coefficients are
+  consistent and asymptotically normal.}  \citet{GiW:06} and
+\citet{GiR:09, GiR:10} are exceptions.  Instead of focusing on
+hypotheses that can be tested by in-sample comparisons, \citet{GiW:06}
+derive an \oos\ test for the null hypothesis that the difference
+between two models' \oos\ forecasting performance is unpredictable, a
+martingale difference sequence; \citet{GiR:09} test whether the \oos\
+forecasting performance of a model suffers from a breakdown relative
+to its in-sample performance; and \citet{GiR:10} test whether the
+forecasting performance is stable. However, those papers focus on a
+particular \oos\ estimation strategy and do not address why \oos\
+comparisons might be useful as a general strategy.
 
@@
 increases with the number of observations so that their ratio remains
-positive.  We focus on linear regression models estimated with a fixed
-training window, but our basic conclusions should be true for other
-estimation strategies and models as well.  Under this asymptotic
-theory, the \ols\ coefficient estimator is no longer consistent or
-asymptotically normal \citep{Hub:73} and has positive variance in the
-limit.  Even so, we show that the usual \oos\ average is
-asymptotically normal and can consistently estimate the difference
-between the models' expected loss in periods $T+1,T+2,\dots$
-conditional on the on the data available in period $T$, a time-series
-analogue to the generalization error.\footnote{See, for example,
-  \citet{HTF:08}.}  Under these asymptotics, the generalization error
-does not converge to the expected performance of the pseudo-true
-models, so the in-sample and \oos\ comparisons measure different
+positive.  Although overfit is sometimes used to describe the
+situation where a forecaster chooses from many different models,
+i.e. \textit{data-mining} or \textit{data-snooping}, we view these as
+separate issues.  Procedures that account for the presence of many
+models have been, and are continuing to be, developed \citep[see, for
+example,][]{Whi:00,Han:05,RoW:05,HHK:10,ClM:11}, but it is unclear
+whether those procedures should themselves use in-sample or \oos\
+comparisons.  Understanding the difference between in-sample and \oos\
+comparisons in the context of a simple comparison between two models
+is necessary before resolving any new issues that arise with multiple
+comparisons.\footnote{Moreover, the empirical research that motivates
+  this paper uses \textit{pseudo} \oos\ comparisons and not
+  \textit{true} \oos\ comparisons.  Even if a true \oos\ comparison
+  could account for some forms of data-snooping better than
+  \citepos{Whi:00} \textsc{brc} or its extensions, in-sample and
+  pseudo \oos\ comparisons would both be affected by the data-snooping.
+  This point is also made by \citet{InK:04}.}
+
+We focus on linear regression models for simplicity, but our basic
+conclusions should be true for other models as well.  Under this
+asymptotic theory, the \ols\ coefficient estimator is no longer
+consistent or asymptotically normal \citep{Hub:73} and has positive
+variance in the limit.  Even so, we show that the usual \oos\ average
+is asymptotically normal and can consistently estimate the difference
+between the models' generalization error, the expected loss in the
+future conditional on the on the data available in period
+$T$.\footnote{See, for example, \citet{HTF:08} for a discussion of
+  generalization error.}  Under these asymptotics, the generalization
+error does not converge to the expected performance of the pseudo-true
+models, so existing in-sample and \oos\ comparisons measure different
 quantities and should be expected to give different results for
@@
 the model that is closer to the true \dgp\ in population can forecast
-worse.  In such a situation, an in-sample comparison would correctly
-reject the null hypothesis that the benchmark is true, and an \oos\
-comparison would correctly fail to reject the null that the benchmark
-is more accurate.\footnote{In a pair of papers similar to ours,
-  \citet{ClM:09,ClM:09b} study in-sample and \oos\ tests that the
-  larger model has nonzero coefficients that are too close to zero to
-  expect the model to forecast more accurately.  Like this paper, they
-  argue that the larger model can be true but less accurate.  However,
-  they focus on an aspect of the \dgp\ that makes this phenomenon
-  likely, while we focus on the coefficient estimates that produce
-  less accurate forecasts.}
+worse.  In such a situation, a standard in-sample comparison would
+correctly reject the null hypothesis that the benchmark is true, and
+an \oos\ comparison would correctly fail to reject the null that the
+benchmark is more accurate.\footnote{In a pair of papers similar to
+  ours, \citet{ClM:09b,ClM:12} study in-sample and \oos\ tests that
+  the larger model has nonzero coefficients that are too close to zero
+  to expect the model to forecast more accurately.  Like this paper,
+  they argue that the larger model can be true but less accurate.
+  However, they focus on an aspect of the \dgp\ that makes this
+  phenomenon likely, while we focus on the coefficient estimates that
+  produce less accurate forecasts.  Moreover, the implications of our
+  asymptotic theories are different and their paper does not provide a
+  reason to do \oos\ comparisons.}
 
@@
 alternative model is higher than the cost of incorrectly failing to
-switch to a more accurate alternative.\footnote{These costs can be
-  monetary, in the form of computer upgrades, software installation,
-  and training, or they can be reputational costs.}
-We show that the \dmw\ test lets the forecaster control the
-probability of the first error, just as with conventional hypothesis
-testing.
+switch to a more accurate alternative.  We show that the \dmw\ test
+lets the forecaster control the probability of the first error, just
+as with conventional hypothesis testing.
 
 Since the models' coefficients are imprecisely estimated in the limit,
-the test sample must be small to ensure that the model estimated over
-the training sample is similar to the one that will be estimated over
-the full sample.  In particular, $P/T \to 0$ is required for
-consistent estimation, and $P^2/T \to 0$ is required for valid
-confidence intervals and inference.  For larger $P$, the \oos\
-comparisons remain asymptotically normal, but are centered on the
-forecasting performance associated with the period-$R$ estimates.  In
-practice, researchers typically use large values of $P$, so these
-studies may be too pessimistic about their models' future accuracy if
-they use the \dmw\ test.  Section~\ref{sec:oostheory} lays out the
-asymptotic behavior of the \dmw\ test under this limit theory.
+the test sample must be small enough that the model estimated over the
+training sample is similar to the one that will be estimated over the
+full sample.  In particular, $P/T \to 0$ is required for consistent
+estimation, and $P^2/T \to 0$ is required for valid confidence
+intervals and inference.  For larger $P$, the \oos\ comparisons remain
+asymptotically normal, but are centered on the forecasting performance
+associated with the period-$R$ estimates.  In practice, researchers
+typically use large values of $P$, so these studies may be too
+pessimistic about their models' future accuracy if they use the \dmw\
+test.  Section~\ref{sec:oostheory} lays out the asymptotic behavior of
+the \dmw\ test under this limit theory.
 
 Since the \ols\ coefficient estimator is no longer consistent or
-asymptotically normal, the F-test and Wald tests are no longer
+asymptotically normal, the $F$-test and Wald tests are no longer
 asymptotically valid.  Moreover, \citet{Efr:86,Efr:04} shows that
 naive comparisons of in-sample loss overestimate models' accuracy by a
-factor proportional to $K/T$, $K$ being the number of regressors.  But
-modifications of the F-test are valid under this asymptotic theory, as
-shown by \citet{BoB:95}, \citet{AkA:00}, \citet{AkP:04}, and
-\citet{Cal:10}, among others.  Such results establish that hypotheses
-about the parameters of the \dgp\ can be tested in-sample even if one
-or both models are overfit.  For that very reason, these tests can not
-reliably choose a model for forecasting and will reject the benchmark
-too often.  We show this analytically in Section~\ref{sec:insample}.
-Moreover, under this asymptotic theory, many recent \oos\ test
-statistics, such as those derived by \cite{ClM:01,ClM:05},
-\citet{Mcc:07}, and \citet{ClW:06,ClW:07} should behave like the
-F-test.  These tests are also designed to reject the benchmark when
-the alternative model is true, and so they may reject too often when
-the benchmark is false but more accurate.  Obviously, since the
+factor proportional to $K/T$; $K$ is the number of regressors.  But
+modifications of the $F$-test are valid under this asymptotic theory,
+as shown by \citet{BoB:95}, \citet{AkA:00}, \citet{AkP:04},
+\citet{Cal:11c}, and \citet{Ana:12}, among others.  These results
+establish that hypotheses about the parameters of the \dgp\ can be
+tested in-sample even if one or both models are overfit.  For that
+very reason, these tests can not reliably choose a model for
+forecasting and will reject the benchmark too often.  We show this
+analytically in Section~\ref{sec:insample} and present analogous
+results for model selection.  Moreover, under this asymptotic theory,
+many recent \oos\ test statistics, such as those derived by
+\cite{ClM:01,ClM:05}, \citet{Mcc:07}, and \citet{ClW:06,ClW:07} should
+have the same problems as in-sample tests.\footnote{Our theoretical
+  results apply directly to \citepos{Mcc:07} \oos\ $t$-test, since it
+  simply proposes more liberal critical values for the same test
+  statistic that we study.  Since \citet{ClW:06,ClW:07} use a finite
+  length estimation window, our asymptotics are incompatible with
+  theirs and prevent us from studying their test directly, as well as
+  \citepos{GiW:06} and other tests based on \citepos{GiW:06}
+  asymptotics.  But \clws\ test can be viewed as a stochastic
+  adjustment to the critical values of the usual \oos\ $t$ test, so
+  our conclusions should apply informally as well.  Specifically, we
+  show that the \dmw\ test rejects with probability equal to nominal
+  size when the estimated benchmark model is expected to be more
+  accurate, so more liberal critical values result in overrejection.}
+These tests are also designed to reject the benchmark when the
+alternative model is true, and so they may reject too often when the
+benchmark is false but more accurate.  Obviously, since the
 distribution of these statistics converges to the normal when $P/T \to
 0$ (with the number of regressors fixed), these statistics behave like
-the \dmw\ test when $P$ is small, but should over-reject the benchmark
+the \dmw\ test when $P$ is small, but should overreject the benchmark
 when $P$ is large.  Section~\ref{sec:mc} presents simulations that
@@
 Section~\ref{sec:theory} gives the main theoretical results for the
-\dmw\ \oos\ test and shows that the F-test rejects the benchmark model
-too often when it is false but more accurate than the
-alternative. Section~\ref{sec:mc} presents a Monte Carlo study
-supporting our theoretical results.  Section~\ref{sec:empirics}
-applies the \oos\ statistic to \citepos{GoW:08} dataset
-for equity premium prediction, and Section~\ref{sec:conclusion}
-concludes.  Proofs and supporting results are listed in the Appendix.
+\dmw\ \oos\ test, shows that standard in-sample tests reject the
+benchmark model too often when it is false but more accurate than the
+alternative, and shows that standard model selection methods choose the
+larger model too often under similar conditions. Section~\ref{sec:mc}
+presents a Monte Carlo study supporting our theoretical results.
+Section~\ref{sec:empirics} applies the \oos\ statistic to
+\citepos{GoW:08} dataset for equity premium prediction, and
+Section~\ref{sec:conclusion} concludes.  Proofs and supporting results
+are listed in the Appendix.
 
@@
 We will set up our models and notation first, then list the assumptions
-required for our results.  There are two competing linear models that
-give forecasts for the target, $y_{t+\h}$:
+required for our results.
+
+\subsection{Notation and Forecasting Environment}
+We assume the following forecasting environment. There are two
+competing linear models that give forecasts for the target,
+$y_{t+\h}$:
 \[
-y_{t+\h} = x_{1t}'\theta_1 + \varepsilon_{1,t+h}
-\]
-and
-\[
+y_{t+\h} = x_{1t}'\theta_1 + \varepsilon_{1,t+h}, \quad\text{and}\quad
 y_{t+\h} = x_{2t}'\theta_2 + \varepsilon_{2,t+h};
 \]
-$\h$ is the forecast horizon, and the variables $y_t$, $x_{1t}$, and
-$x_{2t}$ are all known in period $t$.  Let
+$t = 1,\dots,T-h$, $\h$ is the forecast horizon, and the
+variables $y_t$, $x_{1t}$, and $x_{2t}$ are all known in period $t$.
+Let
 \begin{equation*}
@@
 to vary with $T$, so a stochastic array underlies all of our
-asymptotic theory, but we suppress that notation to make the
-presentation more clear.
-
-Although our theory can apply to many different \oos\ statistics,
-we'll only present results for the \dmw\ \oos\ $t$-test.  Both models
-are estimated using \ols\ over the training sample:
+asymptotic theory, but we suppress that notation to simplify the
+presentation.
+
+The forecaster observes the data $(y_t,x_t)$ for periods 1 through $T$
+and divides them into an estimation sample of the first $R$
+observations and a test sample of the remaining $P$ observations.
+After choosing one of the models, the forecaster will use that model
+to make predictions for periods $T + h + 1$ through $T + h + Q$, where
+$Q$ is a known positive integer.  The forecaster's goal is to choose
+the model that will have lower average loss over periods $T+h$ through
+$T+h+Q$, evaluated by the known loss function $L$.  We allow $Q = 1$,
+so this setup generalizes the problem of choosing a model for a single
+prediction.
+
+Both models are estimated using \ols\ with a recursive, fixed, or
+rolling window:
 \[
-\hat y_{i,t+\h} = x_{it}'\bh{iR}, \quad i=1,2, \quad t = R+1,\dots,T-h
+\hat y_{i,t+\h} = x_{it}'\hat{\theta}_{it}^{R}, \qquad i=1,2, \qquad t
+= R+1,\dots,T-h
 \]
 with
+\begin{equation*}
+  \bh{it}^{R} =  
+  \begin{cases}\big(\sum_{s=1}^{t-\h} x_{is}x_{is}'\big)^{-1}
+    \sum_{s=1}^{t-\h} x_{is} y_{s+\h} & \text{recursive window}\\
+    \big(\sum_{s=t - \h - R}^{t-\h} x_{is}x_{is}'\big)^{-1}
+    \sum_{s=t - \h - R}^{t-\h} x_{is} y_{s+\h} & \text{rolling window}\\
+    \big(\sum_{s=1}^{R-\h} x_{is}x_{is}'\big)^{-1} \sum_{s=1}^{R-\h}
+    x_{is} y_{s+\h} & \text{fixed window}
+  \end{cases}
+\end{equation*}
+The observed \oos\ average is denoted $\oosA$: \[\oosA \equiv P^{-1}
+\oosSum{t}{1} D_{Rt}\]  with
 \[
-\bh{it} = (\sum_{s=1}^{t-\h} x_{is}x_{is}')^{-1} \sum_{s=1}^{t-\h} x_{is} y_{s+\h},
-\quad i=1,2.
+D_{Rt} \equiv L(y_{t+\h} - x_{1t}'\bh{1t}^R) - L(y_{t+\h}
+  - x_{2t}'\bh{2t}^R).
 \]
-The \oos\ average is denoted $\oosA$:
-\[
-\oosA \equiv P^{-1} \oosSum{t}{1} D_{tR}
-\quad \text{with} \quad D_{tS} \equiv L(y_{t+\h} - x_{1t}'\bh{1S}) -
-L(y_{t+\h} - x_{2t}'\bh{2S}),
-\]
-$P = T - R$ and $L$ a known loss function.  The \oos\ statistic
-of interest is 
-\[
-\oost \equiv \frac{\sqrt{P} \oosA}{\hat\sigma},
-\]
-for $\hat\sigma^2$ some (possibly Heteroskedasticity- and
+The \oos\ statistic of interest is $\oost \equiv \sqrt{P} \oosA /
+\hat\sigma_R$, for $\hat\sigma_R^2$ some (possibly Heteroskedasticity- and
 Autocorrelation-Consistent, or \hac) estimator of the asymptotic
@@
 
-We'll show that \oost\ can be used to test whether the models will
-forecast equally accurately in the future.  Specifically, assume that
-whichever model is chosen will be used for an additional $Q$ periods
-in the future and let $\oosB$ denote the difference in average
-performance over those periods:
+As discussed above, the forecaster's goal is to choose the model with
+lower average future loss; i.e. to determine whether $\oosB$ is
+positive or negative,with
 \[
-\oosB \equiv Q^{-1} \sum_{t=T+1}^{T+Q} D_{tT}.
+\oosB \equiv Q^{-1} \sum_{t=T+1}^{T+Q} D_{Tt}, \quad 
+D_{Tt} \equiv L(y_{t+h} - x_{1t}' \bh{1t}^T) - L(y_{t+h} - x_{2t}' \bh{2t}^T)
 \]
-Note that $\oosA$ depends on the training sample estimators,
-$\hat\theta_{iR}$, and $\oosB$ depends on the full sample
-estimators, $\hat\theta_{iT}$.  A forecaster has access to the
-information set $\mathcal{F}_T$ when deciding between the two
-forecasting models, but $\mathcal{F}_T$ does not contain $\oosB$.
-So a forecaster should decide between the models based on the
-conditional expectation, $\E_T \oosB$. If this quantity is
-positive, the first model is expected to perform worse in the future,
-and if it is negative the second is.
-
-When the underlying series is i.i.d., this random variable, $\E_T
-\oosB$, is equal to the difference in the models' generalization
-error.  The generalization error of model $i$ is defined as
-\begin{equation*}
-  \E_{T} L(y_{T+\h}^{*} - x_{iT}^{*\prime}\hat{\theta}_{iT})
-\end{equation*}
-where $(y_{T+\h}^{*},x_{iT}^{*})$ has the same joint distribution as
-$(y_{T+\h}, x_{iT})$ but is independent of $\mathcal{F}_T$.  Note that
-$\hat{\theta}_{iT}$ is known in period $T$, so the generalization
-error conditions on the observed coefficient estimates.  With
-dependence, the coefficient estimates may be informative about future
-values of $y_{t+\h}$ and $x_{it}$, but this influence dies out as $Q$
-grows.  Conditional performance measures like these are especially
-appropriate in areas like time-series economics where the forecaster
-knows the coefficient values when choosing a model, but would be less
-appropriate if the models will be re-estimated over an entirely new
-dataset before forecasting.
-
-Before stating the main theoretical assumptions, we define some more
-notation.  The $l_v$-norm for vectors in $\Re^p$ (with $p$ arbitrary)
-is denoted $\lvert \cdot \rvert_v$, and the $L_v$-norm for
-$L_v$-integrable random variables is $\lVert \cdot \rVert_v$.  The
-functions $\lambda_i(\cdot)$ take a square-matrix argument and return
-its $i$th eigenvalue (with $\lambda_{i}(A) \leq \lambda_{i+1}(A)$ for
-any matrix $A$).
-All limits are taken as $T \to \infty$ unless stated otherwise.
+and 
+\begin{equation*}
+  \bh{it}^{T} = 
+  \begin{cases} \big(\sum_{s=1}^{t-\h} x_{is}x_{is}'\big)^{-1}
+    \sum_{s=1}^{t-\h} x_{is} y_{s+\h} & \text{recursive window} \\
+    \big(\sum_{s=t - \h - T}^{t-\h} x_{is}x_{is}'\big)^{-1}
+    \sum_{s=t - \h - T}^{t-\h} x_{is} y_{s+\h} & \text{rolling window} \\
+    \big(\sum_{s=1}^{T-\h} x_{is}x_{is}'\big)^{-1} 
+    \sum_{s=1}^{T-\h} x_{is} y_{s+\h} & \text{fixed window}.
+  \end{cases}
+\end{equation*}
+Note that the coefficients are reestimated with the full dataset.
+Since the forecaster's information set, $\mathcal{F}_T$, does not
+contain $\oosB$, he or she should decide between the models based on
+the conditional expectation, $\E_T \oosB$. If this quantity is
+positive, the first model is expected to perform the worst in the
+future, and if it is negative the second is.
+
+This conditional expectation is related to several well known measures
+of model performance.  In the limit, $\E_{T} \bar{D}_{T}$ converges to
+the difference in the models' generalization error and the two are
+equal in finite samples for i.i.d. data.  Moreover, if the data are
+i.i.d., the expectation of $\E_T \oosB$ equals \citepos{Aka:69} Final
+Prediction Error (\textsc{fpe}).  Both generalization error and
+\textsc{fpe} are defined by the model's performance on a new,
+independent, data set; here the new data are not independent in finite
+samples, but are asymptotically independent.  For the rest of the
+paper, we will call $\E_T \oosB$ the difference in generalization
+error with hopefully no risk of confusion.
+
+Finally, define the following notation.  The $l_v$-norm for vectors in
+$\Re^p$ (with $p$ arbitrary) is denoted $\lvert \cdot \rvert_v$, and
+the $L_v$-norm for $L_v$-integrable random variables is $\lVert \cdot
+\rVert_v$.  The functions $\lambda_i(\cdot)$ take a square-matrix
+argument and return its $i$th eigenvalue (with $\lambda_{i}(A) \leq
+\lambda_{i+1}(A)$ for any matrix $A$).  All limits are taken as $T \to
+\infty$ unless stated otherwise.
+
+\subsection{Assumptions}
 
@@
 difference in the models' performance; the fourth assumption describes
-the behavior of the estimation and test windows.  The last assumption
-describes the kernel used to estimate the \oos\ average's asymptotic
-variance.
+the behavior of the estimation and test windows.  And the last
+assumption describes the kernel used to estimate the \oos\ average's
+asymptotic variance.
 
 \begin{asmp}\label{asmp-1} 
-  The random array $\{y_t,x_t\}$ is stationary and
-  absolutely regular with coefficients $\beta_j$ of size
-  $-\rho/(\rho-2)$; $\rho$ is greater than two and discussed further
-  in Assumption \ref{asmp-3}.  Also, $K_1$ and $K_2$ are less than $R$,
-  and $\frac{K_2}{T}$ and $\frac{K_2-K_0}{T}$ are uniformly positive;
-  $K_0$ is the number of regressors shared by the two models ($K_1/T$
-  can be uniformly positive as well, but is not required to be).
+  The random array $\{y_t,x_t\}$ is stationary and absolutely regular
+  with coefficients $\beta_j$ of size $-\rho/(\rho-2)$; $\rho$ is
+  greater than two and discussed further in Assumption \ref{asmp-3}.
+  Also, $K_1$ and $K_2$ are less than $R$, and $K_2/T$ and
+  $(K_2-K_0)/T$ are uniformly positive; $K_0$ is the number of
+  regressors shared by the two models ($K_1/T$ can be uniformly
+  positive as well, but is not required to be).
 \end{asmp}
@@
 econometrics, because absolute regularity admits a particular coupling
-argument \citep{Ber:79} that is unavailable for strong mixing
-sequences.  Please see, for example, \citet{Dav:94} for a discussion
-of these mixing conditions.
+argument \citep[reproduced in this paper as Lemma A.1]{Ber:79} that is
+unavailable for strong mixing sequences.  Please see, for example,
+\citet{Dav:94} for a discussion of these mixing conditions.
 
@@
   $\theta_2$, satisfy $|\theta_1|_2 = O(1)$ and $|\theta_2|_2 = O(1)$.
-  Moreover, there exist a $\delta > 0$ and finite $\Delta$ such that
-  \begin{equation*}
-    \lVert \lambda_{\max}(X_{iS_{T}}'X_{iS_{T}}) \rVert_{3+\delta}
-    \leq S_{T}\, \Delta \\
-    \lVert
+  Moreover, there exists a finite $\Delta$ such that $\| x_{it}'x_{it}
+  \|_3 \leq K_i \Delta$,
+  \begin{align*}
+    \lVert \lambda_{\max}(X_{iS_{T}}'X_{iS_{T}}) \rVert_{3} &\leq
+    S_{T}\, \Delta, & \lVert
     \lambda_{\max}(X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})
-    \rVert_{3+\delta} \leq S_{T}\, \Delta \\
-    \lVert \lambda_{\max}((X_{iS_{T}}'X_{iS_{T}})^{-1}) \rVert_{3+\delta} \leq \Delta/S_{T} \\
-    \lVert
-    \lambda_{\max}((X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})^{-1})\rVert_{3+\delta}
-    \leq \Delta/S_{T}
-  \end{equation*}
+    \rVert_{3} &\leq S_{T}\, \Delta, \\
+    \lVert \lambda_{\max}((X_{iS_{T}}'X_{iS_{T}})^{-1})
+    \rVert_{3} &\leq \Delta/S_{T}, & \lVert
+    \lambda_{\max}((X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})^{-1})\rVert_{3}
+    &\leq \Delta/S_{T},
+  \end{align*}
   for all $S_{T} \geq K_{2T}$ and large enough $T$, with $i =
   1,2$,
-  \[ X_{iT} \equiv [x_{i1} \quad \dots \quad x_{i,T-\h}]' \]
-  and
-  \[ \ep{iT} = (\varepsilon_{i,1+\h}, \dots, \varepsilon_{i,T})'.\]
+  \[ X_{iT} \equiv [x_{i1} \quad \dots \quad x_{i,T-\h}]' \qquad
+  \text{and} \qquad
+  \ep{iT} = (\varepsilon_{i,1+\h}, \dots, \varepsilon_{i,T})'.\]
 \end{asmp}
@@
   derivatives almost everywhere.  Also, $L(0) = 0$, and there is a
-  constant $B_L$ such that
-  \begin{equation*}
-    \|D_{R+j,R}\|_\rho \leq B_L \quad\text{and}\quad
-    \|D_{T+j,T}\|_\rho \leq B_L.
-  \end{equation*}
-  for all $j \geq 1$.
+  constant $B_L$ such that $\|D_{R,R+j}\|_\rho \leq B_L$ and
+  $\|D_{T,T+j}\|_\rho \leq B_L$ for all $j \geq 1$ ($\rho$ is defined
+  in Assumption~\ref{asmp-1}); $\| x_{it}' \hat{\theta}_{is}^R \|_2 \leq
+  B_L$ and $\| x_{it}' \hat{\theta}_{is}^T \|_2 \leq B_L$; and
+  \begin{equation*}
+    \| L'(y_{t+h} - x_{it}'\tilde{\theta}_{it}) \|_2 \leq B_L
+  \end{equation*}
+  for $\tilde{\theta}_{it}$ a weighted average of any two estimates
+  $\hat{\theta}_{is}^R$ and $\hat{\theta}_{is'}^R$ or
+  $\hat{\theta}_{is}^T$ and $\hat{\theta}_{is'}^T$ with $s, s' \leq t$.
 \end{asmp}
@@
 This third assumption establishes basic moment and smoothness
-conditions for the \oos\ loss.  The differentiability
+conditions for the \oos\ loss and forecasts.  The differentiability
 condition is weak and allows the loss function itself to be
-non-differentiable; for example, absolute error and many asymmetric loss functions
-satisfy this assumption.
-
-\begin{asmp} \label{asmp-4} $P\to\infty$,
-  $R\to\infty$, $Q\to\infty$, $P^2/T \to 0$, and $P = O(Q)$ as $T \to \infty$.
+non-differentiable or even discontinuous; for example, absolute error
+and many asymmetric loss functions satisfy this assumption.
+
+\begin{asmp} \label{asmp-4} $P\to\infty$, $R\to\infty$, and  $P =
+  o(T^{1/2}$) as $T \to \infty$.  For the rolling and recursive
+  windows, $Q = o(T^{1/2})$ as well.
 \end{asmp}
@@
 implications.  In practical terms, this assumption requires that the
-forecaster plan to use the model for many periods in the future, that
-the test sample be large, and that the training sample be much larger,
-by enough that including or excluding the test sample does not affect
-the estimates of $\theta_1$ or $\theta_2$ very much.
+test sample be large and that the training sample be much larger, by
+enough that including or excluding the test sample does not affect the
+estimates of $\theta_1$ or $\theta_2$ very much.
 
@@
 \end{equation*}
-and $W(\cdot)$ is continuous at 0 and all but a finite number of
+and $W(\cdot)$ is continuous at zero and all but a finite number of
 points.
@@
 related---allowing for complex models requires tighter constraints on
-the size of the test sample.
+the size of the test sample.  West allows more general estimation
+methods, while we restrict attention to \ols; the advantage of using
+\ols\ is that we can derive the inequality, $$\| x_{it}'
+\theta_{it}^{R} - x_{it}' \theta_{iR}^R \|_2 \leq O(P/T)^{1/2}.$$  Our
+main results will hold for other models as long as a similar
+inequality exists, but proving such inequalities for other models is
+left for future research.
 
 Our other assumptions are similar.  The loss function must be smooth
-almost everywhere, which is slightly less restrictive than
-\citet{Wes:96} requires but is not new; \citet{Mcc:00} extends West's
-results to cover a similar case.  West relaxes our assumption that the
-forecasts come from a linear regression model; we could relax our
-assumption to include other linear estimators, but there would be
-little new insight.  We assume full stationarity and absolute
+almost everywhere, which is less restrictive than \citet{Wes:96}
+requires but is not new; \citet{Mcc:00} extends West's results to
+cover a similar case.\footnote{Our assumptions allow for discontinuous
+  loss functions, such as those proposed by \citet{PeT:92}.
+  \citet{Mcc:00} does not explicitly allow for such loss functions,
+  but it appears that his conclusions hold for them as well under the
+  restriction $P/T \to 0$.}  We assume full stationarity and absolute
 regularity of the underlying random array, while West assumes
@@
 \ref{res-confidence-intervals}, which shows that the \oos\ average is
-asymptotically normal and centered on $E_T \oosB$.  This result
-holds even for nested models and can be used to construct confidence
+asymptotically normal and centered on $\E_T \oosB$.  This result holds
+even for nested models and can be used to construct confidence
 intervals or test hypotheses.  After presenting Theorem
@@
 used to consistently estimate the asymptotic variance of the \oos\
-average.  We then show that the F-test does not let researchers test
-hypotheses about $E_{T} \oosB$ when the models are overfit.  In
-fact, in the limit it rejects a more-accurate but false benchmark
-model almost surely.
-
-\subsection{Behavior of DMW Test with Overfit}\label{sec:oostheory}
+average.  We next present an example that illustrates some of these
+concepts, and then show that typical full-sample tests do not let
+researchers test hypotheses about $\E_{T} \oosB$ when the models are
+overfit.  In fact, in the limit they can reject a more accurate but
+false benchmark model almost surely.
+
+\subsection{Behavior of the DMW Test with Overfit}\label{sec:oostheory}
 Our first theorem justifies using the \dmw\ $t$-test with a a short
@@
   Suppose that Assumptions \ref{asmp-1}--\ref{asmp-4} hold, that
-  $\hat\sigma$ is an estimator satisfying
+  $\hat\sigma_R^2$ is an estimator satisfying
   \[
-    \hat\sigma^2 = \sigma^2 + o_p(1), \quad \text{with}\quad 
-    \sigma^2 \equiv \var_R(\sqrt{P} \oosA),
+    \hat\sigma_R^2 - \sigma_R^2 \to^p 0 \quad \text{with}\quad 
+    \sigma_R^2 \equiv \var_R(\sqrt{P} \oosA) \equiv P \E_R(\bar{D}_R -
+    \E_R \bar{D}_R)^2,
   \]
-  and that $\sigma^2$ is uniformly a.s. positive.  Then
+  and that $\sigma_R^2$ is uniformly a.s. positive.  Then
   \[
-  \frac{\oosA - \E_T\oosB}{\hat\sigma / \sqrt{P}}
+  \frac{\oosA - \E_T\oosB}{\hat\sigma_R / \sqrt{P}}
   \to^d N(0,1).
@@
   Consequently, each of the usual Gaussian confidence intervals,
-  \begin{eqnarray}
-  &&[\oosA - z_{\alpha/2} \, \hat\sigma /
-      \sqrt{P}, \oosA + z_{\alpha/2} \hat\sigma / \sqrt{P}],\label{interval-twosided} \\
-  &&[\oosA - z_{\alpha} \, \hat\sigma / \sqrt{P}, +\infty), \label{interval-greater}
-  \end{eqnarray}
-  and
-  \begin{equation} (-\infty, \oosA + z_{\alpha}
-      \, \hat\sigma / \sqrt{P}],
-  \end{equation}
+  \begin{gather}
+  [\oosA - z_{\alpha/2} \, \hat\sigma_R /
+      \sqrt{P}, \oosA + z_{\alpha/2} \hat\sigma_R / \sqrt{P}],\label{interval-twosided} \\
+  [\oosA - z_{\alpha} \, \hat\sigma_R / \sqrt{P}, +\infty), \label{interval-greater}
+  \intertext{and}
+(-\infty, \oosA + z_{\alpha}
+      \, \hat\sigma_R / \sqrt{P}],
+    \end{gather}
     contains $\E_T\oosB$ with probability $\alpha$ in the limit,
@@
 \end{thm}
-The requirement that $\sigma^2$ be uniformly a.s. positive is not
+The requirement that $\sigma_R^2$ be uniformly a.s. positive is not
 restrictive under our asymptotic theory.  Since the models'
@@
 models give different forecasts even if they both nest the \dgp.  This
-is similar to \citepos{GiW:06} rolling-window result, but comes from
-different asymptotics.
+is intuitively similar to \citepos{GiW:06} rolling-window result, but
+comes from different asymptotic theory; Giacomini and White keep the
+variance of the \oos\ average positive by letting $P \to \infty$ with
+$R$ fixed; in this paper, $R \to \infty$ but the variance remains
+positive since $K \to \infty$ (quickly) as well.
 
@@
 inference about the models' accuracy.  Since the \oos\ average,
-$\oosA$, is asymptotically normal and centered on the expected
-future performance, $t$-tests constructed from the \oos\ errors
-necessarily test hypotheses about $\E_T \oosB$ and not the
-performance of the pseudo-true models or the unconditional
-performance of the models.
-
-The application to testing can be expressed as a corollary:
+$\oosA$, is asymptotically normal and centered on the expected future
+performance, $t$-tests constructed from the \oos\ errors necessarily
+test hypotheses about $\E_T \oosB$ and not the performance of the
+pseudo-true models or the unconditional performance of the models.
+This application to testing can be expressed as a corollary:
 \begin{cor}\label{res:oostest}
@@
 \begin{equation}
-  \Pr[\sqrt{P}\oosA/\hat\sigma \geq z_{\alpha} \mid \E_{T}
-  \oosB \leq 0] \to^p \alpha.
+  \lim \Pr[P^{1/2}\oosA/\hat\sigma_R \geq z_{\alpha} \mid \E_{T}
+  \oosB \leq 0] \leq \alpha.
 \end{equation}
@@
 so Theorem~\ref{res-confidence-intervals} holds if
+\begin{equation}\label{coefpart}
+  \E_R \oosA = \E_T \oosB + o_p(P^{-1/2}).
+\end{equation}
+and
 \begin{equation}\label{normalpart}
-  \sqrt{P}\frac{\oosA - \E_R \oosA}{\sigma} \to^d N(0,1)
+  \sqrt{P}\frac{\oosA - \E_R \oosA}{\sigma_R} \to^d N(0,1)
+\end{equation}
+The first Lemma shows that the rolling and recursive window statistics
+can be approximated by the fixed window statistic and that
+that~\eqref{coefpart} holds for the fixed window.  The second Lemma
+shows that the process $\{D_{Rt} - \E_R \oosA\}$ is an $L_2$-mixingale
+of size $-1/2$ that satisfies a \clt\ for the fixed window statistic,
+ensuring~\eqref{normalpart}.
+
+\begin{lem} \label{res-convergence} Suppose that Assumptions
+  \ref{asmp-1}--\ref{asmp-4} hold, let $D_{Rt}'$ and $D_{Tt}'$ denote
+  the loss differences associated with the rolling or recursive
+  window, and let $D_{Rt}$ and $D_{Tt}$ those of the fixed window.  Then
+  \begin{equation}
+    \label{eq:8}
+    P^{1/2} (\oosA' - \oosA) \to^p 0, \qquad P^{1/2} (\oosB' - \oosB)
+    \to^p 0,
   \end{equation}
   and
-\begin{equation}\label{coefpart}
-  \E_R \oosA = \E_T \oosB + o_p(P^{-\frac12}).
-\end{equation}
-The first Lemma first shows that the process $\{D_{tR} - \E_R \oosA\}$
-is an $L_2$-mixingale of size $-1/2$ that satisfies a \clt,
-ensuring~\eqref{normalpart}.  The second shows that~\eqref{coefpart}
-holds under Assumption~\ref{asmp-4}.
+  \begin{equation}\label{eq:7}
+    \E_T \oosB - \E_R \oosA =  O_p(\sqrt{P/T}) +
+    o_p(P^{-1/2}).
+  \end{equation}
+\end{lem}
+
+Note that $\E_T \oosB - \E_R \oosA$ is noise introduced by
+approximating the performance of the full-sample estimates with that
+of the partial-sample estimates.  Moreover, the $O_p(\sqrt{P/T})$ term
+is binding; it is straightforward to find examples for which
+$\sqrt{T/P}(\E_T \oosB - \E_R \oosA)$ does not converge to
+zero.\footnote{Notice that, if the observations are i.i.d. and
+  $(y_{t+h}, x_{it}) \sim N(0,I)$, $(\hat{\theta}_{iR}^R -
+  \hat{\theta}_{iT}^T) \sim N(0, (X_{iR}'X_{iR})^{-1} -
+  (X_{iT}'X_{iT})^{-1})$ given $X_{iT}$, and so
+  $\var(x_{i,T+1}'\hat{\theta}_{iR}^R - x_{i,T+1}'
+  \hat{\theta}_{iT}^T) \gg P K_i / (R - K_2)(T - K_2)$.}
+Consequently, there is little scope to relax our assumption that
+$P^2/T \to 0$.  If $\lim P^2/T$ is positive and finite then there is
+the possibility of adjusting the asymptotic distribution of the test
+statistic to account for this noise term as in \citet{Wes:96}, but we
+leave that to future research.  If $P^2/T \to \infty$, which is
+closest to common practice in applied research, the noise term
+dominates the asymptotic distribution of the \oos\ $t$-test, so the
+test has only trivial power in the limit if it has correct size.
 
 \begin{lem}\label{res-mixingale}
-  Part 1: If Assumptions~\ref{asmp-1}--\ref{asmp-3} hold then the inequality
+  Part 1: If Assumptions~\ref{asmp-1}--\ref{asmp-3} hold then the
+  inequality
   \begin{equation}\label{mixingaleR}
-    \lVert \E_{R+j-l}(D_{R+j,R} - \E_R D_{R+j,R}) \rVert_2 \leq
+    \lVert \E_{R+j-l}(D_{R,R+j} - \E_R D_{R,R+j}) \rVert_2 \leq
     \couplingConstant \;
@@
   \end{equation}
-  with $\zeta_l = O(l^{-\frac12 - \delta})$ holds for some positive
+  with $\zeta_l = O(l^{-1/2 - \delta})$ holds for some positive
   $\delta$, any positive $j$, and any $l$ between 0 and $j$.  As a
-  consequence, $\{D_{t,R} - \E_R D_{t,R}, \mathcal F_t\}$ is an
-  $L_2$-mixingales of size $-1/2$.
-
-  \noindent Part
-  2: Moreover,~\eqref{normalpart} holds under
-  Assumptions~\ref{asmp-1}--\ref{asmp-3} if $P \to \infty$ as $T \to
-  \infty$ and $\sigma^2$ is a.s. uniformly positive.
+  consequence, $\{D_{Rt} - \E_R D_{Rt}, \mathcal F_t\}$ is an
+  $L_2$-mixingale of size $-1/2$.
+
+  \noindent Part 2: Moreover,~\eqref{normalpart} holds under the
+  conditions of Part 1 if $P \to \infty$ as $T \to \infty$ and
+  $\sigma_R^2$ is a.s. uniformly positive.
 \end{lem}
 
-Mixingales satisfies a weak-dependence condition similar to \mds es
-and were introduced and studied extensively by
+Mixingales satisfy a weak-dependence condition similar to \mds es and
+were introduced and studied extensively by
 \citet{Mcl:74,Mcl:75,Mcl:75b,Mcl:77}.  This lemma shows that the
 estimation uncertainty introduces dependence into the \oos\ forecast
-errors, but that additional dependence is contained in the term $\E_R
-\oosA$ and can be effectively removed by subtraction.  The second
-part of the Lemma shows that the basic mixingale \clt\ established by
-\citet{Dej:97} applies in this setting.\footnote{De Jong proves two
+errors, but the additional dependence is contained in the term $\E_R
+\oosA$ and can be effectively removed by subtraction.  The second part
+of the Lemma shows that the basic mixingale \clt\ established by
+\citet{Jon:97} applies in this setting.\footnote{De Jong proves two
   \clt s: one for mixingales and one for \ned\ functions of mixing
@@
   \oos\ process---in effect, that the \oos\ process has slightly more
-  structure than required for it to be a mixingale.}
-
-\begin{lem} \label{res-convergence} Suppose that Assumptions
-  \ref{asmp-1}--\ref{asmp-4} hold.  Then
-\begin{equation*}
-  \E_T \oosB - \E_R \oosA =  O_p(\sqrt{P/T}) +
-  o_p(P^{-\frac12}) + o_p(Q^{-\frac12}).
-\end{equation*}
-\end{lem}
-
-The justification for Lemma~\ref{res-convergence} is intuitive.  In
-the limit, the difference between $\E_T \oosB$ and $\E_R \oosA$
-comes from the coefficient estimators used: $\E_T\oosB$ is the
-expected performance using the full-sample estimate, $\hat{\theta}_T$,
-and $\E_R \oosA$ is the performance using the period-$R$ estimate,
-$\hat{\theta}_R$.  When $P$ and $Q$ are large, the dependence between
-the test and training samples vanishes, so the estimators of $\theta$
-are the only variables affected by the conditioning $\sigma$-fields,
-$\mathcal{F}_R$ and $\mathcal{F}_T$.  Since $L$ is smooth, the
-difference between $\E_R \oosA$ and $\E_T \oosB$ is of order
-$\lvert \hat\theta_R - \hat\theta_T \rvert_2$, which itself is of
-order $\sqrt{\frac{P}{T}}$.
+  structure than required for it to be a mixingale.}  Note that
+Lemma~\ref{res-mixingale} does not require $P^2/T \to 0$.
 
 Finally, for Theorem \ref{res-confidence-intervals} to be useful, we
-need a consistent estimator of $\sigma^2$. Lemma
+need a consistent estimator of $\sigma_R^2$. Lemma
 \ref{res-variance-estimator} establishes that the usual \oos\ \hac\
@@
   \label{res-variance-estimator} Suppose Assumptions \ref{asmp-1},
-  \ref{asmp-2}, \ref{asmp-3}, and \ref{asmp-5} hold, that $\gamma, P$
-  and $R \to \infty$ as $T \to \infty$, and that $\gamma = o(P)$.  Then
-  \begin{equation*}
-    \frac1P \oosSum{s,t}{1} (D_{tR} - \oosA)(D_{sR} - \oosA)
-    \vWeight = \sigma^2 + o_p(1).
-  \end{equation*}
+  \ref{asmp-2}, \ref{asmp-3}, and \ref{asmp-5} hold, that $\gamma$,
+  $P$, and $R \to \infty$ as $T \to \infty$, and that $\gamma = o(P)$
+  and define
+  \begin{equation*}
+    \hat{\sigma}_R^2 \equiv P^{-1} \oosSum{s,t}{1} (D_{Rt} - \oosA)(D_{Rs} - \oosA)
+    \vWeight.
+  \end{equation*}
+  Then $\hat{\sigma}_R^2 - \sigma_R^2 \to^p 0$.
 \end{lem}
 
+The next subsection presents an example that clarifies the previous
+results.
+
+\subsection{An Example}\label{sec:example}
+
+Consider the fixed-window estimation scheme, let $L(e) = e^2$, let $h
+= 1$, let the benchmark model have no regressors (i.e. $y_{t+1} \sim$
+white noise), suppose that $(y_{t}, x_{2t}) \sim i.i.d.\ N(0,I)$, and
+assume that $R > 2K_2 + 4$.\footnote{The restriction $R > 2 K_2 + 4$
+  allows us to use a convenient formula for moments of the
+  Inverse-Wishart distribution.}  Under these conditions,
+\begin{align*}
+  D_{Rt} &= 2 y_{t+1} x_{2t}'\hat{\theta}_{2R}^R -
+  \hat{\theta}_{2R}^{R\prime} (x_{2t} x_{2t}') \hat{\theta}_{2R}^R \\
+  D_{Tt} &= 2 y_{t+1} x_{2t}'\hat{\theta}_{2T}^T -
+  \hat{\theta}_{2T}^{T\prime} (x_{2t} x_{2t}') \hat{\theta}_{2T}^T.
+\end{align*}
+
+The first two moments of $D_{Rt}$ for $t > R$ (conditional
+on $\mathcal{F}_R$) are straightforward to derive:
+$\E_R D_{Rt} = - \hat{\theta}_{2R}^{R\prime} \hat{\theta}_{2R}^R$
+and
+\begin{equation*}
+  \sigma_R^2 \equiv \E_R(D_{Rt} - \E_R D_{Rt})^2 = 4
+  \hat{\theta}_{2R}^{R\prime} \hat{\theta}_{2R}^{R} +
+  \E_R(\hat{\theta}_{2R}^{R\prime} (I - x_{2t} x_{2t}')
+  \hat{\theta}_{2R}^{R})^2   \geq 4 \hat{\theta}_{2R}^{R\prime}
+  \hat{\theta}_{2R}^R \quad a.s.
+\end{equation*}
+Now, $\hat{\theta}_{2R}^{R\prime} \hat{\theta}_{2R}^R$ is
+a.s. positive and uniformly integrable with mean $4 K_2 / (R - K_2 -
+1)$ (since $(X_{2R}'X_{2R})^{-1}$ is Inverse-Wishart$(I_{K_2}, R)$),
+making $\sigma_R^2$ uniformly a.s. positive and ensuring that the
+distribution of the \oos\ average is not $P^{1/2}$-degenerate.  The
+natural \oos\ variance estimator is consistent for $\sigma_R^2$:
+\begin{align*}
+  \hat{\sigma}_R^2 &= P^{-1} \sum_{t=R+1}^{T-1} (D_{Rt} - \oosA)^2 \\
+  &= 4 \hat{\theta}_{2R}^{R\prime} \Big[P^{-1} \sum_{t=R+1}^{T-1}
+  \Big(y_{t+1} x_{2t} - P^{-1} \sum_{s=R+1}^{T-1} y_s x_{2s}\Big)
+  \Big(y_{t+1} x_{2t} - P^{-1} \sum_{s=R+1}^{T-1} y_s
+  x_{2s}\Big)'\Big] \hat{\theta}_{2R}^{R\prime} \\ & \quad - 4
+  \Big[P^{-1} \sum_{t=R+1}^{T-1} \Big(y_{t+1} x_{2t} - P^{-1}
+  \sum_{s=R+1}^{T-1} y_s x_{2s}\Big)' \hat{\theta}_{2R}^{R}
+  \hat{\theta}_{2R}^{R\prime} \Big(x_{2t} x_{2t}' - P^{-1}
+  \sum_{s=R+1}^{T-1} x_{2s} x_{2s}' \Big) \hat{\theta}_{2R}^{R} \Big]
+  \\ &\quad + P^{-1} \sum_{t=R+1}^{T-1}
+  \Big[\hat{\theta}_{2R}^{R\prime} \Big(x_{2t} x_{2t}' - P^{-1}
+  \sum_{s=R+1}^{T-1} x_{2s} x_{2s}' \Big) \hat{\theta}_{2R}^{R}  \Big]^{2}.
+\end{align*}
+As $P \to \infty$, the first term converges in probability to
+$\hat{\theta}_{2R}^{R\prime} \hat{\theta}_{2R}^R$, the second to zero,
+and the third to $\E_R(\hat{\theta}_{2R}^{R\prime}(I - x_{2t}x_{2t}')
+\hat{\theta}_{2R}^R)^2$.  Since the number of regressors prevents
+$\hat{\theta}_{2R}^R$ from converging i.p. to zero (its expected
+value), $\hat{\sigma}_R^2$ does not converge to the unconditional
+variance.
+
+We can see that the \oos\ average obeys a \clt\ when centered at $\E_R
+\bar{D}_R$.  The centered and scaled \oos\ differences satisfy
+\begin{equation*}
+  \frac{D_{Rt} - \E_R D_{Rt}}{\sigma_R} =
+  \frac{2 y_{t} x_{2t}' \hat{\theta}_{2R} +
+    \hat{\theta}_{2R}' (I - x_t x_t') \hat{\theta}_{2R}}{\sqrt{4
+    \hat{\theta}_{2R}' \hat{\theta}_{2R} +
+    \E_R(\hat{\theta}_{2R}'(I - x_{2t} x_{2t}') \hat{\theta}_{2R})^2}}.
+\end{equation*}
+This sequence is not i.i.d. and we can not replace $\hat{\theta}_{2R}$
+with a sequence of constants $\theta_{2R}$ since $\hat{\theta}_{2R}$
+does not converge to a deterministic limit.  But $\sigma_R^{-1}
+\E_t(\oosA - \E_R\oosA) = 0$, making this sequence an
+\mds,\footnote{The sequence is actually exchangeable, but \mds\ is
+  enough to establish the \clt.} so it obeys a \clt\ as long as
+$\sigma_R^2$ is uniformly a.s. positive, which we have already
+established.  Lemma~\ref{res-mixingale} ensures that the \clt\ holds
+more generally.
+
+Finally, we can look at the difference $\E_R \bar{D}_R - \E_T
+\bar{D}_T$.  We can write this as
+\begin{align*}
+  \E_R \oosA - \E_T \oosB &= \hat{\theta}_{2R}^{R\prime}
+  \hat{\theta}_{2R}^R - \hat{\theta}_{2T}^{T\prime}
+  \hat{\theta}_{2T}^T \\ &=
+  \mathbf{\varepsilon}_T'[\tilde{X}_{2R}(X_{2R}'X_{2R})^{-2}
+  \tilde{X}_{2R} - X_{2T}(X_{2T}'X_{2T})^{-2} X_{2T} ] \mathbf{\varepsilon}_T
+\end{align*}
+with $\tilde{X}_{2R}$ the $T \times K_2$ matrix $[X_{2R}'\ 0]'$.
+Standard results for the moments of quadratic forms and of the
+Inverse-Wishart distribution \citep{Haf:79} imply that
+\begin{equation*}
+  \E(\E_R \oosA - \E_T \oosB) = \frac{K_2 P}{(T - K_2 - 1)(R - K_2 - 1)}
+\end{equation*}
+and
+\begin{align*}
+  \var(\E_R & \oosA - \E_T \oosB) \\ &= \E
+  \big[\tr((X_{2R}'X_{2R})^{-1} - (X_{2T}'X_{2T})^{-1})\big]^2 + 2 \tr
+  \E\big((X_{2R}'X_{2R})^{-2} - (X_{2T}'X_{2T})^{-2}\big) \\ &\quad - \big[\tr
+  \E((X_{2R}'X_{2R})^{-1} - (X_{2T}'X_{2T})^{-1}) \big]^2 \\ &=
+  O(P/T)^2.
+\end{align*}
+So, in this example, $P^{1/2}(\E_R \oosA - \E_T \oosB) \to^p 0$ only
+if $P^3/T^2 \to 0$, which is slightly weaker than the general
+requirement that $P^2/T \to 0$.  If $\lim P^3/T^2 > 0$ the \oos\ average
+still obeys the \mds\ \clt, but it is not centered correctly at $\E_T
+\oosB$.
+
 \subsection{Failure of In-Sample Tests}\label{sec:insample}
-This subsection establishes that the F-test can over-reject when the
-benchmark is more accurate than the alternative.  We use stronger
-assumptions than before, i.i.d. data, normal errors, \mse\ loss, and
-nested models to ensure that the F-test performs as well as possible.
-Indeed, we know its exact distribution.  But the basic idea of this
-argument is much more general and should apply to other related tests,
-including \oos\ tests.
-
+This subsection establishes that in-sample tests like the $F$-test can
+overreject when the benchmark is more accurate than the alternative.
+The issue explored here is different than that of \citet{Cal:11c} and
+\citet{Ana:12}; in those papers, the authors demonstrate that full
+sample Wald and $F$-tests can be invalid under increasing-$k$
+asymptotics,\footnote{\citet{Ana:12} shows that the Wald test is
+  invalid in general and gives an adjustment that corrects the
+  critical values; he also shows that the $F$-test is asymptotically
+  valid under certain conditions on the distribution of the
+  regressors.  \citet{Cal:11c} shows that the $F$-test is
+  asymptotically invalid without Anatolyev's constraint, and provides
+  a correction that gives valid tests.  Both papers only consider
+  independent observations.} e.g. they can overreject when testing the
+null hypotheses that a set of the coefficients is zero.  This paper,
+though, looks at the behavior when the coefficients are non-zero but
+the estimated restricted model is more accurate.  In this setting,
+these tests reject the benchmark too often---more than their nominal
+size---and for most coefficient values will reject almost surely in
+the limit.  We also look at some common model selection statistics and
+find the same conclusion---they choose the larger model with high
+probability regardless of which model will forecast better.  To
+simplify the presentation, we'll only present results for nested
+models.
+
+Theorem~\ref{res:ftest} presents results for in-sample hypothesis
+tests.
 \begin{thm}\label{res:ftest}
-  Let $\h = 1$ and suppose that $x_{1t}$ and $x_{2t}$ are
-  deterministic vectors such that $x_{2t} = (x_{1t}, z_t)$ and
-\[
-T^{-1} \sum_{t=1}^T x_{2t} x_{2t}'  = Q^{-1} \sum_{t=T+1}^{T+Q} x_{2t} x_{2t}' =
-I.
+  Suppose Assumptions 1--3 hold, that the models are nested, and that
+  $L(e) = e^2$.  Also, let $\Lambda$ be a test statistic with nominal
+  size $\alpha$ that has acceptance region contained in the set
+  \[\{\hat{\theta}_T \mid (\hat{\theta}_T -
+  \theta_0)'V_T(\hat{\theta}_T - \theta_0) < c \}\] for large enough
+  $T$ and some $\theta_0$, $c$, and $V_T$, with $V_T$ a possibly
+  random matrix with all eigenvalues uniformly bounded in probability
+  and rank satisfying $\lim \rank(V_T)/T > 0$.  Then there exist
+  distributions for $(x_t, \varepsilon_{t+h})$ such that
+  \begin{equation}
+    \label{eq:11}
+    \Pr[\Lambda \text{ rejects} \mid \E_T \oosB \leq 0] \to^p 1
+    \quad \text{as} \quad
+    \theta'V_T\theta \to^p \infty \quad \text{($T$ is fixed)}
+  \end{equation}
+  for almost every sequence $\theta$ (a.e. with respect to Lebesgue
+  measure) and 
+  \begin{equation}
+    \label{eq:15}
+    \plim_{T \to \infty} \Pr[\Lambda \text{ rejects} \mid
+    \E_T \oosB \leq 0] \geq \plim_{T \to \infty} \Pr[c + \delta < (\theta - \theta_0)' V_{T}
+    (\theta - \theta_0) \mid \E_T \bar{D}_T \leq 0]
+  \end{equation}
+  for any $\delta > 0$.
+\end{thm}
+Note that, if $V_T$ is nonstochastic or converges in probability,
+there are distributions on $(x_t, \varepsilon_{t+h})$ that are
+compatible with~\eqref{eq:15} such that
+\[\Pr[c + \delta < (\theta - \theta_0)'V_T (\theta - \theta_0) \mid
+E_T \bar{D}_T \leq 0] \to^p 1
 \]
-Also, suppose that $\theta_2 = (\theta_1, \psi)$, 
-$\varepsilon_{2,t+1} \sim i.i.d.\ N(0,\tau^2)$,
-$|\theta_1|_2 = \phi_1$, $|\psi|_2 = \phi_2$, $K_1/T = c_1 > 0$,
-$K_2/T = c_2 > 0$, and $K_2 \geq 2$, and let $F$ be the F-statistic
-for the test of the null hypothesis that $\psi = 0.$
-Then 
-\begin{equation}\label{eq:ftestreject1}
-  \Pr[F \geq q_{K_2 - K_1, T - K_2}(1-\alpha) \mid E_T \oosB \leq 0
-  ] \to 1\mbox{ as $\phi_2 \to \infty$ ($T$ fixed)}
-\end{equation}
-and if $\phi_2 \geq \tau \sqrt{c_2 - c_1}$, then
-\begin{equation}\label{eq:ftestreject2}
-  \Pr[F \geq q_{K_2 - K_1, T - K_2}(1-\alpha) \mid E_T \oosB \leq 0
-  ] \to 1 \text{ as $T \to \infty$},
-\end{equation}
-where $q_{K_2-K_1, T-K_2}(1-\alpha)$ is the
-$(1-\alpha)$-quantile of the $F_{K_2-K_1, T-K_2}$ distribution.
-\end{thm}
-The conditions on the regressors simplify the proof but can be
-relaxed.  As in Corollary~\ref{res:oostest}, the event that we are
-conditioning on in~\eqref{eq:ftestreject1} and~\eqref{eq:ftestreject2}
-is the event that the benchmark model is expected to be more accurate
-in the future.  Since the probability of this event converges to zero
-as $\phi_2 \to \infty$, \eqref{eq:ftestreject1} is not an immediate
-consequence of the power of the F-test increasing with $\phi_2$.
-
-The first result,~\eqref{eq:ftestreject1}, can be understood through the case $K_2 = 2$ and
-$K_1 = 0$, so
-\begin{equation*}
-  E_T \oosB = \psi_1^2 + \psi_2^2 - (\hat{\psi}_1 - \psi_1)^2 - (\hat\psi_2 - \psi_2)^2,
-\end{equation*}
-where $\hat{\psi}$ is the \ols\ estimator.  Under these conditions,
-the F-test rejects if $\hat{\psi}$ lies outside the circle centered at
-the origin with radius $\hat{\tau} (c_2 - c_1)^{0.5} q_{K_2-K_1,
-  T-K_2}^{0.5}(1-\alpha)$, and $E_T \oosB \leq 0$ holds for $\hat\psi$
-on or outside a circle centered at $\psi$ passing through the origin;
-$\hat{\tau}^2$ is the usual estimator of $\tau^2$.
+for any $\theta \neq \theta_0$.  Otherwise, the rejection probability
+will still depend on $\theta$ and $V_T$ and will typically be higher
+than the nominal size of the test.
+
+Theorem~\ref{res:ftest} covers a broad class of test statistics and
+allows the in-sample test to be valid or invalid in finite samples or
+asymptotically.  It implies that a large class of in-sample tests will
+reject if $\theta$ is nonzero, whether or not the alternative model is
+more accurate.  As an example, consider the $F$-test of the null
+hypothesis $A \theta =0$ with deterministic regressors and
+i.i.d. Normal errors where $\rank A = J$ and $\lim J/T > 0$.  Simple
+algebra reveals that the test rejects if $\hat{\theta}_T' V_T
+\hat{\theta}_T \geq 1$ with
+\begin{equation*}
+  V_T = (T/ J \hat{\xi}^{2}) A' (A (T^{-1}X_T'X_T)^{-1} A')^{-1} A;
+\end{equation*}
+$\xi^2$ is the variance of the model's innovations and $\hat{\xi}^2$ is
+the usual estimator based on the squared residuals.  Note that $\rank
+V_T = \rank A$ as long as $X_T'X_T$ is full rank.  Under the null $A
+\theta = 0$,
+\begin{equation*}
+  \hat{\theta}_T' V_T
+  \hat{\theta}_T =^d   (\xi^2/ J \hat{\xi}^2) \chi_J^2 =^d 1 + J^{-1/2} Z
+  + o_p(T^{-1/2}),
+\end{equation*}
+where $\chi_J^2$ is an independent $\chi^2$ random variable with $J$
+degrees of freedom and $Z \sim N(0,1)$.  Consequently, the $F$-test
+accepts whenever $\hat{\theta}_T$ is in a neighborhood of the cylinder
+defined by $\hat{\theta}_T' V_T \hat{\theta}_T = 1$ and rejects for
+$\hat{\theta}_T$ outside the neighborhood.\footnote{If $V_T$ is full
+  rank, this equation defines an ellipsoid in $\mathbb{R}^K$;
+  otherwise the equation defines an ellipsoid in a subspace of
+  $\mathbb{R}^K$.}  The neighborhood shrinks as $T \to \infty$, so the
+$F$-test satisfies the conditions of Theorem~\ref{res:ftest} with
+$V_T$ as given above and $c = 1 + \delta$ for any $\delta > 0$.
+Notice that $c$ does not depend on the nominal size of the test and
+that the exact finite sample distribution of the $F$-test is known in
+this example, so the test is valid by conventional measures but the
+conclusions of Theorem~\ref{res:ftest} still hold.
+
+The intuition behind Equation~\eqref{eq:11} can be understood by
+simplifying further to the case $K_2 = 2$ and $K_1 = 0$, deterministic
+orthonormal regressors, and $V_T = I$, so
+\begin{equation*}
+  E_T \oosB = \theta_{1}^2 + \theta_{2}^2 - (\hat{\theta}_{T,1} -
+  \theta_{1})^2 - (\hat\theta_{T,2} - \theta_2)^2.
+\end{equation*}
+Under these conditions, the test rejects if $\hat{\theta}_{T}$ lies
+outside the circle centered at the origin with radius $c^{1/2}$ and
+$\E_T \oosB \leq 0$ holds for $\hat\theta_{T}$ on or outside a circle
+centered at $\theta$ passing through the origin.
 Figure~\ref{fig:rreject} depicts these regions.  Since the \ols\
-estimator $\hat\psi$ is normal with mean $\psi$, the probability that
-$\hat{\psi}$ falls in the acceptance region given $E_T \oosB \leq 0$
-vanishes as $\phi_2 \to \infty$, even though the full model will give
-worse forecasts than the restricted model.
+estimator is normal with mean $\theta$, the probability that
+$\hat{\theta}_{T}$ falls in the acceptance region given $\E_T \oosB
+\leq 0$ vanishes as $\theta'\theta \to \infty$, even though the full
+model will give worse forecasts than the restricted model.
 
@@
     \draw (1,1) let \p1=(1,1) in circle({veclen(\x1,\y1)});
-    \fill [black] (1,1) circle (2pt) node[right] {$(\psi_1,\psi_2)$};
+    \fill [black] (1,1) circle (2pt) node[right] {$(\theta_1,\theta_2)$};
     \draw (0,0) circle (#1);
@@
     % axes
-    \draw[->] (0,0)--(#2,0) node[right] {$\hat\psi_1$};
-    \draw[->] (0,0)--(0,#2) node[above] {$\hat\psi_2$};
+    \draw[->] (0,0)--(#2,0) node[right] {$\hat\theta_{T,1}$};
+    \draw[->] (0,0)--(0,#2) node[above] {$\hat\theta_{T,2}$};
   \end{tikzpicture}
@@
     \draw (1,1) let \p1=(1,1) in circle({veclen(\x1,\y1)});
-    \fill [black] (1,1) circle (2pt) node[right] {$(\psi_1,\psi_2)$};
+    \fill [black] (1,1) circle (2pt) node[right] {$(\theta_1,\theta_2)$};
     \draw (1,1)--(0,0);
     % axes
-    \draw[->] (0,0)--(#2,0) node[right] {$\hat\psi_1$};
-    \draw[->] (0,0)--(0,#2) node[above] {$\hat\psi_2$};
+    \draw[->] (0,0)--(#2,0) node[right] {$\hat\theta_{T,1}$};
+    \draw[->] (0,0)--(0,#2) node[above] {$\hat\theta_{T,2}$};
   \end{tikzpicture}
@@
     Figures (a) and (b) show the rejection region and the acceptance
-    region respectively of the F-test given $E_T \oosB \leq 0$ when
-    the true elements of $\psi$ are moderately small.  Figures (c) and (d)
-    show the same regions when the true $\psi$ is large.}
+    region respectively of the full-sample test given $\E_T \oosB \leq
+    0$ when the true elements of $\theta$ are moderately small.  Figures
+    (c) and (d) show the same regions when the true $\theta$ is large.}
 \label{fig:rreject}
@@
 
-The second part of Theorem \ref{res:ftest},~\eqref{eq:ftestreject2},
-is more interesting and implies that the F-test rejects the benchmark
-too often for forecasting whenever we have an overfit model (unless,
-of course, $\psi = 0$).  The intuition is similar to the previous
-case.  As $K_2$ increases, the volume that $\hat{\psi}$ can occupy
-increases as well.  So the probability that $\hat{\psi}$ is close to
-the origin and therefore inside the acceptance region of the F-test
-decreases.  In the limit, the probability that $\hat{\psi}$ is outside
-the acceptance region is one.\footnote{If $\phi_2 \geq \tau \sqrt{c_2
-    - c_1}$ does not hold, then $\psi$ lies inside the acceptance
-  region of the F-test for large enough $T$.  In that case, the
-  rejection probability does not converge to one, but will converge to
-  a probability greater than $\alpha$.}
-
-It is important to remember that the F-test is valid for the null
-$\psi = 0$ in this analysis.  However, the F-test is poorly suited for
-choosing an accurate forecasting model, and performs worse when the
-larger model is overfit or explains more of the variation of the
-dependent variable.  Other valid unbiased tests of the null hypothesis
-that $\psi = 0$ will suffer the same problem.
+Equation~\eqref{eq:15} is more interesting and implies that these
+tests will almost surely reject the benchmark whenever we have a true
+but overfit and less accurate alternative.  The intuition is similar
+to the previous case.  As $K_2$ increases, the volume that
+$\hat{\theta}_{T}$ can occupy increases as well.  If $\theta$ is
+outside the acceptance region, the probability that $\hat{\theta}_{T}$
+is close to the origin and therefore inside the acceptance region of
+the test decreases.  In the limit, the probability that
+$\hat{\theta}_{T}$ is outside the acceptance region is one.
+
+A similar result for model selection follows as a Corollary to
+Theorem~\ref{res:ftest}.  Consistent model selection in this context
+is different than in the finite-$K$ case.  Here we want the
+probability of selecting a model given that it is more accurate to
+converge to one.  Formally, a model selection procedure is useful if
+\begin{gather}\label{eq:13}
+  \Pr[\text{model $1$ selected} \mid \E_T \oosB \leq 0] \to 1
+  \intertext{and} \Pr[\text{model $2$ selected} \mid \E_T \oosB > 0]
+  \to 1.\label{eq:14}
+\end{gather}
+Note that the conditioning event in~\eqref{eq:14} is different than in
+the testing results presented earlier, but otherwise they are similar.
+Theorem~\ref{res:ftest} implies that~\eqref{eq:13} will typically fail
+for overfit models for many common model selection methods, including
+adjusted $R^2$, the \aic, and the \bic.  Corollary~\ref{res:ic}
+contains the details.
+
+\begin{cor}\label{res:ic}
+  Suppose the conditions of Theorem~\ref{res:ftest} hold but that the
+  statistic $\Lambda'$ is used for model selection; $\Lambda'$ selects
+  the benchmark model for all $\hat{\theta}_T$ contained in a subset
+  of the region
+  \begin{equation*}
+    \{\hat{\theta}_T \mid \hat{\theta}_T'V_T \hat{\theta}_T < c\}
+  \end{equation*}
+  and selects the alternative for all $\hat{\theta}_T$ outside that
+  region.  Then there exist distributions on $x_t,\varepsilon_t$ such
+  that
+  \begin{equation}
+    \label{eq:17}
+    \plim \Pr[\Lambda' \text{ selects model 1} \mid \E_T \bar{D}_T \leq 0]
+    \leq \plim \Pr[\theta_0'V_T \theta_0 < c \mid \E_T \bar{D}_T].
+  \end{equation}
+\end{cor}
+As before, we often have 
+\begin{equation*}
+  \Pr[\theta_0'V_T \theta_0 < c \mid \E_T \bar{D}_T] \to^p 0.
+\end{equation*}
+Just as we saw with the $F$-test, adjusted $R$-squared, the \aic\ and
+the \bic\ will only choose the benchmark model if $\hat{\theta}_T$
+lies in the neighborhood of the cylinder defined by $\hat{\theta}_T
+V_{T} \hat{\theta}_T = c$, regardless of which model is expected to
+forecast better.  These statistics differ in how they determine the
+size of the neighborhood, with the neighborhood shrinking slower for
+the \bic\ than the \aic.
+
+It is important to remember that the tests considered do not need to
+have correct size for the null $\theta = \theta_0$, but are allowed to
+in this analysis, so previous research, such as \citet{Cal:11c} and
+\citet{Ana:12}, does not predict these results.  However, these tests
+are poorly suited for choosing an accurate forecasting model and
+perform worse when the larger model is overfit or explains more of the
+variation of the dependent variable.  Essentially, for forecasting we
+want to know if the coefficient estimates are close to their true
+values, but in-sample statistics tell us only whether the estimates
+are close to a particular hypothesized value (usually zero).  There
+are lots of estimates that are both far from zero and far from their
+true values which cause in-sample statistics to incorrectly choose the
+alternative model.
 
@@
 theory in small samples.\footnote{Simulations were conducted in R
-  \citep{Rde:10} using the Lattice \citep{Sar:10} and RSQLite
-  \citep{Jam:10} packages for graphics and data management
-  respectively.}  The first looks at the asymptotic normality of the
-\dmw\ statistic centered on either $E_R \oosA$ or $E_T \oosB$.
-The previous section's results imply that centering on the first
-should give an approximately normal statistic and centering on the
-second should give a normal statistic when $P$ is small relative to
-$T$.  The second simulation looks at the size and power of several
-statistics when conducting inference about the difference in the
-models' generalization error.
+  \citep{Rde:10} using Sweave \citep{Lei:02} and the Lattice
+  \citep{Sar:10}, RSQLite \citep{Jam:10}, tikzDevice
+  \citep{ShB:11:0.6.1}, and pgfSweave \citep{BrS:11:1.2.1} packages.}
+The first looks at the asymptotic normality of the \dmw\ statistic
+centered on either $\E_R \oosA$ or $\E_T \oosB$.  The previous
+section's results imply that centering on the first should give an
+approximately normal statistic and centering on the second should give
+a normal statistic when $P$ is small relative to $T$.  The second
+simulation looks at the size and power of several statistics when
+conducting inference about the difference in the models'
+generalization error.  For all of the simulations, we look at
+fixed-window \oos\ tests to speed up computation time.
 
@@
 \end{equation*}
-with $c=0$ or 1.  When $c$ is large, we're more likely to draw
-values of $X$ and $Y$ that make the estimated larger model more
+with $c$ equal to zero or one.  When $c$ is one, we're more likely to
+draw values of $X$ and $Y$ that make the estimated larger model more
 accurate than the benchmark, and when $c$ is zero we're unlikely to
@@
 Section~\ref{sec:oostheory} works in practice.  For each draw of $X$
-and $Y$, we construct a one-sided and two-sided \oos\ interval of the
+and $Y$, we construct a one-sided \oos\ interval of the
 form
 \begin{equation*}
-  [ \oosA - 1.28 \hat{\sigma}, \infty) \quad\text{and}\quad
-  [ \oosA - 1.64 \hat{\sigma}, \oosA + 1.64\ \hat{\sigma}], \\
-  \hat\sigma^2 = \frac1P \sum_{t=R+1}^T (D_t - \oosA)^{2}
-\end{equation*}
-for $P$ set to every 10th value between $T$ and $\frac{2T}{3}$.  We
-calculate the percentage of these intervals that contain $E_R \oosA$
-and that contain $E_T \oosB$.  Since the data are i.i.d., both of
-these quantities are easy to calculate:
-\begin{equation*}
-  E_R \oosA = [\sum_{i=1}^{K_1} (\tilde{\theta}_{iR} - \theta_i)^2 +
-  \sum_{i=K_1+1}^{K_2}\theta_i^2] - \sum_{i=1}^{K_2} (\hat{\theta}_{iR} -
+  [ \oosA - 1.28 \hat{\sigma_R}, \infty) \quad\text{with}\quad
+  \hat\sigma_R^2 = \frac1P \sum_{t=R+1}^T (D_t - \oosA)^{2}
+\end{equation*}
+for $P$ set to every 10th value between 1 and $2T/3$.  We calculate
+the percentage of these intervals that contain $\E_R \oosA$ and that
+contain $\E_T \oosB$.  Since the data are i.i.d., both of these
+quantities are easy to calculate:
+\begin{equation*}
+  E_R \oosA = \Bigg[\sum_{i=1}^{K_1} (\tilde{\theta}_{iR} - \theta_i)^2 +
+  \sum_{i=K_1+1}^{K_2}\theta_i^2\Bigg] - \sum_{i=1}^{K_2} (\hat{\theta}_{iR} -
   \theta_i)^2
@@
 \end{equation}
-We look at four different statistics---the full-sample F-test, the
+We look at four different statistics---the full-sample $F$-test, the
 \dmw\ $t$-test, the
@@
 statistic, but with a fixed window scheme.}
-For the F-test, we simply test whether the coefficients on the larger
+For the $F$-test, we simply test whether the coefficients on the larger
 model are nonzero.  For the out-of-sample tests, we conduct a
@@
 \subsection{Results}
-We next discuss results for the confidence intervals first.
+We discuss results for the confidence intervals first.
 Figures~\ref{fig:interval-R} and~\ref{fig:interval-T} show the
@@
 displays the coverage for a different choice of interval, centering
-term ($E_R \oosA$ or $E_T \oosB$) and combination of design
+term ($\E_R \oosA$ or $\E_T \oosB$) and combination of design
 parameters.
 
-Figure~\ref{fig:interval-R} gives the results for $E_R \oosA$.  For
-both the one and two-sided intervals, the actual coverage is very
-close to the nominal coverage except when $P$ is small.  The poor
-behavior for small $P$ is unsurprising, as it simply means that the
-\clt\ is a poor approximation when the test sample is small.  The
-intervals' good coverage holds even for the parsimonious models
-($K_1=1$ and $K_2= 3$) which our theory does not necessarily apply to.
-
-Figure~\ref{fig:interval-T} gives the results for $E_T \oosB$.  In
-rows 2, 4, 6, and 8, the overfit models, the coverage is near nominal
-coverage for moderately small values of $P$.  As $P$ increases to $2T/3$, the
-coverage either increases to 1 (for the one-sided interval) or fall to
-zero (the two-sided).  With the parsimonious model, the coverage is near
-nominal coverage for all $P$ for the one-sided interval with $c=1$,
-but only for moderately small $P$ for the two-sided interval or when
-$c=0$.
+Figure~\ref{fig:interval-R} gives the results for $\E_R \oosA$.  The
+actual coverage is very close to the nominal coverage except when $P$
+is very small.  The poor behavior for small $P$ is unsurprising, as it
+simply means that the \clt\ is a poor approximation when the test
+sample is small.  The intervals' good coverage holds even for the
+parsimonious models ($K_1=1$ and $K_2= 3$) which our theory does not
+necessarily apply to.
+
+Figure~\ref{fig:interval-T} gives the results for $\E_T \oosB$.  In
+rows 2, 4, 6, and 8---the overfit models---the coverage is near
+nominal coverage for moderately small values of $P$.  As $P$ increases
+to $2T/3$, the coverage increases to 1.  With the parsimonious model,
+the coverage is near nominal coverage for all $P$ for the one-sided
+interval with $c=1$, but only for moderately small $P$ when $c=0$.
 
@@
 When $P^2/T$ is small, the coverage is near nominal levels.  The
-behavior as $P$ increases, combined with the results for $E_R
-\oosA$, indicate that $E_T \oosB \geq E_R \oosA$ in general.
+behavior as $P$ increases, combined with the results for $\E_R
+\oosA$, indicate that $\E_T \oosB \geq E_R \oosA$ in general.
 Since
 \[E_{T} \oosB = E_{R} \oosA + (E_{T} \oosB - E_{R} \oosA), \] and the
-interval is approximately centered at $E_R \oosA$, the difference
-$E_{T} \oosB - E_{R} \oosA$ adds a substantial positive quantity when
+interval is approximately centered at $\E_R \oosA$, the difference
+$\E_{T} \oosB - E_{R} \oosA$ adds a substantial positive quantity when
 $P^2/T$ is not near zero, increasing the coverage of the one-sided
-interval but taking $E_T \oosB$ outside the two-sided interval.
+interval.
 
@@
 the conditional rejection probability is plotted for each combination
-of $T$, $K_1$, $K_2$, and $c$ as a function of $P$.  The F-test does
+of $T$, $K_1$, $K_2$, and $c$ as a function of $P$.  The $F$-test does
 not depend on $P$, so a single value is presented for each
@@
 
-We'll look at the F-test first.  To make comparisons easier, the size
+We'll look at the $F$-test first.  To make comparisons easier, the size
 is displayed as a dot plot in Figure~\ref{fig:ftest}.  Different
@@
 We see immediately that the actual and nominal size are essentially
-equal for $c = 0$, which is unsurprising.  For $c = 0$, the F-test is
+equal for $c = 0$, which is unsurprising.  For $c = 0$, the $F$-test is
 exact; moreover, the larger model will almost always be less accurate
 than the smaller one, so conditioning on $\E_T \oosB \leq 0$ is
-almost unrestrictive.  When $c$ increases, though, the F-test
-over-rejects badly---rejecting at roughly 50\% when $c = 1$ for the
+almost unrestrictive.  When $c$ increases, though, the $F$-test
+overrejects badly---rejecting at roughly 50\% when $c = 1$ for the
 parsimonious model and from 70\% to 100\% for the overfit model.  As
@@
 $P/T$ for $c=0$, under-rejecting by about 5pp when $P/T = 2/3$, and
-rises with $P/T$ for $c=1$, over-rejecting by about 10pp when
+rises with $P/T$ for $c=1$, overrejecting by about 10pp when
 $P/T=2/3$.  For small $P$, the rejection probability is near 10\% for
@@
 test is correctly sized for both the overfit and parsimonious studies,
-as we saw for the F-test.  When $c=1$, the rejection probability
+as we saw for the $F$-test.  When $c=1$, the rejection probability
 increases rapidly with $P/T$.  For $K_2=3$, the rejection probability
@@
 small to over 25\% when $P/T = 2/3$.  Note that all of the simulations
-use the parsimonious model.  McCracken's statistic over-rejects here
+use the parsimonious model.  McCracken's statistic overrejects here
 by slightly less than Clark and West's, but still by a substantial
@@
 simulating from \eqref{eq:1} with $c = 1$ or 2 subject to the
-constraint that $E_T \oosB > 0$.\footnote{Draws of $X$ and $Y$ with
-  $E_T \oosB > 0$ are very rare when $c=0$, so we do not present
+constraint that $\E_T \oosB > 0$.\footnote{Draws of $X$ and $Y$ with
+  $\E_T \oosB > 0$ are very rare when $c=0$, so we do not present
   results for that value of $c$.}  Figure~\ref{fig:ttest-power} plots
 the power for the \dmw\ test; since the other test statistics greatly
-over-reject, we do not present their power.  For $c=1$, the power is
+overreject, we do not present their power.  For $c=1$, the power is
 never greater than nominal size and decreases to zero as $P/T$
@@
 Both sets of simulations support our theoretical results.  The first
-simulation confirms that the \dmw\ \oos\ $t$-test is centered at $E_R
-\oosA$ for all choices of $P$ and $R$ and is centered on $E_T \oosB$
+simulation confirms that the \dmw\ \oos\ $t$-test is centered at $\E_R
+\oosA$ for all choices of $P$ and $R$ and is centered on $\E_T \oosB$
 only when $P$ is small.  The second simulation confirms that the \dmw\
-test has correct size for the null hypothesis that $E_T \oosB \leq 0$
+test has correct size for the null hypothesis that $\E_T \oosB \leq 0$
 when $P$ is small and that tests designed to test whether the
-benchmark is true, like the F-test and Clark and West's (2006, 2007)
+benchmark is true, like the $F$-test and Clark and West's (2006, 2007)
 and McCracken's (2007) \oos\ tests can reject by much more than their
-nominal size when testing the null $E_T \oosB \leq 0$.  Moreover,
+nominal size when testing the null $\E_T \oosB \leq 0$.  Moreover,
 these simulations demonstrate that the restriction $P^2/T \to 0$ is
@@
   section are done in R \citep{Rde:10}.  We also use code provided by
-  \citet{Zeh:02}, \citet{Zei:04}, and \citet{Har:10}.}  We estimate
-the expected forecasting performance of the largest model they
-consider, a model with 13 regressors, using 81 observations (annual
-data from 1928 to 2009).  We construct confidence intervals for the
-difference in performance between this model and a prevailing mean
-benchmark, and do so for different values of $R$ and $P$ to examine
-the effect of the training and test sample choice on this \oos\
-statistic.  We find that the estimate of the larger model's \mse\
-decreases relative to the benchmark as $R$ increases, but it is never
-smaller than the benchmark's.  This result, combined with the larger
-model's in-sample significance, suggests that there may be a real
-relationship between the equity premium and some of these predictors,
-but that the relationship can not be estimated accurately enough to be
-useful for forecasting and supports \citepos{GoW:08}
-conclusions.  These results hold even when imposing
-\citepos{CaT:08} restriction that the equity
+  \citet{Zeh:02}, \citet{Zei:04}, \citet{Har:10}, and
+  \citet{ShB:11:0.6.1}.}  We estimate the expected forecasting
+performance of the largest model they consider, a model with 13
+regressors, using 81 observations (annual data from 1928 to 2009).  We
+construct confidence intervals for the difference in performance
+between this model and a prevailing mean benchmark, and do so for
+different values of $R$ and $P$ to examine the effect of the training
+and test sample choice on this \oos\ statistic.  We find that the
+estimate of the larger model's \mse\ decreases relative to the
+benchmark as $R$ increases, but it is never smaller than the
+benchmark's.  This result, combined with the larger model's in-sample
+significance, suggests that there may be a real relationship between
+the equity premium and some of these predictors, but that the
+relationship can not be estimated accurately enough to be useful for
+forecasting and supports \citepos{GoW:08} conclusions.  These results
+hold even when imposing \citepos{CaT:08} restriction that the equity
 premium forecast be non-negative.
@@
 To study the effect of the training sample size on the \dmw\ statistic, we
-calculate the one-sided confidence interval for $E_T \oosB$ given
+calculate the one-sided confidence interval for $\E_T \oosB$ given
 by \eqref{interval-greater} corresponding to the null and alternative
@@
 \]
-for each value of $R$ between 20 and $T-10$.  The standard deviation
-is estimated using a Newey-West estimator with $\lfloor
-P^{\frac14}\rfloor$ lags.  For small values of $R$, the \oos\ average
-is expected to underestimate the performance of the larger model
-relative to the smaller, but this may not hold in this particular
-dataset.
+using the fixed-window scheme for each value of $R$ between 20 and
+$T-10$.  The standard deviation is estimated using a Newey-West
+estimator with $\lfloor P^{1/4}\rfloor$ lags.  For small values of
+$R$, the \oos\ average is expected to underestimate the performance of
+the larger model relative to the smaller, but this may not hold in
+this particular dataset.
 
@@
 parameter uncertainty---the full sample results indicate that the
-larger model could predict better than the benchmark with enough data.
+larger model could predict better than the benchmark with enough
+data.\footnote{\citet{BWB:10} make a similar point about exchange rate
+models, but see also \citet{Chi:10} and \citet{Gia:10}.}
 Obviously, this is an illustrative exercise only and is not meant to
@@
 instability that we have not addressed, and we have not dealt with
-variable persistence at all.
+variable persistence at all.  However, as we mention earlier, our
+requirement that $P$ be small should let our theoretical results
+extend to moderate instability, and the fact that we do not rely on
+the asymptotic distribution of the coefficient estimates should
+mitigate the effect of persistence as well.
 \section{Conclusion}\label{sec:conclusion}
@@
 the expected future accuracy of his or her models when one or both is
-overfit.  We show analytically and through Monte Carlo that existing
-in-sample test statistics can not test hypotheses about this
+overfit.  We show analytically and through Monte Carlo that standard
+full-sample test statistics can not test hypotheses about this
 performance.
@@
 Our paper also shows that popular test and training sample sizes may
-give misleading results if researchers are concerned about
-overfit.\footnote{As we mention in the introduction, forecasters also
-  use these statistics if they are concerned about unmodeled
-  instability, which this paper does not address.}  We show that
-$P^2/T$ must converge to zero for the \dmw\ test to give valid
-inference about the expected forecast accuracy, otherwise the test
-measures the accuracy of the estimates constructed using only the
+give misleading results if researchers are concerned about overfit.
+We show that $P^2/T$ must converge to zero for the \dmw\ test to give
+valid inference about the expected forecast accuracy, otherwise the
+test measures the accuracy of the estimates constructed using only the
 training sample.  In empirical research, $P$ is typically much larger
@@
 
-More work remains.  Our requirement that $\frac{P^2}{T}$ converge to
-zero is limiting, as it implies that in typical macroeconomic
-datasets, only a handful of observations should be used for testing.
-This restriction could be addressed by directly estimating $\E_R \oosA
-- \E_T \oosB$ or by deriving its asymptotic distribution, which would
-allow larger values of $P$.  It could also be mitigated by extending
-our results to cross-validation or other resampling strategies.  It
-would also be useful to extend our results to other estimation windows
-and forecasting models, and to explore how stationarity could be
-relaxed.
+More work remains.  The requirement that $P^2/T$ converge to zero is
+limiting, as it implies that in typical macroeconomic datasets, only a
+handful of observations should be used for testing.  This requirement
+can be relaxed only slightly; $P = O(T^{1/2})$ is required for the
+\oos\ test to have nontrivial power in general, but there are loss
+functions and \dgp s for which some relaxation is possible.  This
+constraint could be mitigated by extending our results to
+cross-validation or other resampling strategies, or by constructing
+full-sample statistics that allow inference about $\E_T \bar{D}_T$.
+It would also be useful to extend our results to other forecasting
+models and to explore how stationarity could be relaxed, but such
+extensions are less important than improving the available statistics.
 
 \appendix
-\section{Supporting results}
+\section*{Appendix: Mathematical Details}
+\setcounter{section}{1}
+
+\subsection*{Supporting Results}
 The results in this paper rely heavily on a coupling argument for
-absolutely regular sequences, Berbee's Lemma \citep{Ber:79}.  In fact,
-many of the results of this paper (\ref{res-confidence-intervals},
-\ref{res-mixingale}, and \ref{res-variance-estimator}) are
-modifications of existing results for \ned\ functions of mixing
-processes by \citet{Dej:97} and
-\citet{DeD:00}; this coupling argument is used to
-explicitly derive inequalities that arise naturally for \ned\
-processes.  Lemma \ref{lem-basic-coupling} establishes these
-inequalities, which are based on a proposition of
-\citet{MeP:02}.
+absolutely regular sequences, Berbee's Lemma \citep{Ber:79}.  Many of
+the results of this paper (Lemmas \ref{res-mixingale} and
+\ref{res-variance-estimator}) are modifications of existing results
+for \ned\ functions of mixing processes by \citet{Jon:97} and
+\citet{JoD:00}; this coupling argument is used to explicitly derive
+inequalities that arise naturally for \ned\ processes.  Lemma
+\ref{lem-basic-coupling} establishes these inequalities, which are
+based on a proposition of \citet{MeP:02}.
 
@@
 \]
-\begin{quotation}
-\begin{lem}\label{lem-berbee}
+\begin{lem}\label{lem-berbee}\quad
+
+\begin{quotation}\noindent
   Let $X$ and $Y$ be random variables defined on a probability space
-  $(\Omega, \mathcal{T}, \mathbf{P})$ with values in a Polish space
+  $(\Omega, \mathcal{T}, \Pr)$ with values in a Polish space
   $S$.  Let $\sigma(X)$ be a $\sigma$-algebra generated by $X$ and let
@@
   \sigma(U)$, independent of $X$ and distributed as $Y$, and such that
-  $\mathbf{P}(Y \neq Y^{*}) = \beta(X,Y)$.
-\end{lem}
+  $\Pr(Y \neq Y^{*}) = \beta(X,Y)$.
+
   \noindent\citep{MeP:02}
 \end{quotation}
+\end{lem}
 
@@
 dimension of $Y$, which makes them unsuitable for our applications.
-The remaining results in this section use Berbee's Lemma to establish
-some basic inequalities.
 
@@
   expectations are finite, where 
-  \[ \mathbf{x} = (x_{s}', \dots, x_{t}')', \\
-  \mathbf{y} = (y_{s+\h},\dots,y_{t+\h})'\] and $f$ is the
+  \[ \mathbf{x} = (x_{s}', \dots, x_{t}')', \qquad
+  \mathbf{y} = (y_{s+\h},\dots,y_{t+\h})',\] and $f$ is the
   joint density of $(\mathbf{x}, \mathbf{y})$.  Moreover,
@@
    \| \tilde D_v - D_{vw} \|_2 \leq 2^{1+1/\rho} B_L
-   \beta_{s-u}^\rhoExp, \qquad v = s,\dots,t.
+   \beta_{s-u}^{\rhoExp}, \qquad v = s,\dots,t.
  \end{equation}
@@
   Now define
-  \[ \tilde D_v \equiv L(y_{v+\h}^* - x_{1v}^* \cdot
-  \hat{\theta}_w) - L(y_{v+\h}^* - x_{2v}^* \cdot
-  \hat{\theta}_w), \quad v = s,\dotsc, t,
+  \[ \tilde D_v \equiv L(y_{v+\h}^* - x_{1v}^{*\prime} \hat{\theta}_w)
+  - L(y_{v+\h}^* - x_{2v}^{*\prime} \hat{\theta}_w), \quad v =
+  s,\dotsc, t,
   \]
@@
 
-\section{Proofs of results in main text}
-\begin{proof}[Proof of Theorem \ref{res-confidence-intervals}]
-It suffices to prove asymptotic normality.  We can rewrite the
-centered \oos\ average as
+\begin{lem}\label{lem:a2}
+  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-3} and that the fixed
+  window scheme is used.  Let $b_T$ be a sequence such that $b_T \to
+  \infty$ and $b_T = o(P)$ and define
+  \begin{equation*}
+    Z_i = \ZDef.
+  \end{equation*}
+  Then
+  \begin{equation}
+    \label{eq:10}
+    \sum_{i=1}^{\lfloor P/b_T \rfloor} (\E_R Z_i^2 - \E_{R+(i-1) b_T}
+    Z_i^2) \to^p 0.
+  \end{equation}
+  If Assumptions~\ref{asmp-4} and \ref{asmp-5} also hold and we define
+  \begin{gather*}
+    Z_{1t} = \varianceTermIIIa, \intertext{and} Z_{2t} =
+    \varianceTermIVb,
+  \end{gather*}
+  then
+  \begin{equation}
+    \label{eq:12}
+    \sum_{t=-P+1}^{2P} (Z_{1t} Z_{2t} - \E_R Z_{1t} Z_{2t}) \to^p 0.
+  \end{equation}
+\end{lem}
+\begin{proof}
+\newcommand{\UFiltration}[1]{\ensuremath{\mathcal{F}_{(#1)b_{T}+R-P}}}%
+The first result,~\eqref{eq:10}, follows a similar argument to Lemma~5
+of \citet{Jon:97} and~\eqref{eq:12} to Lemma~A.4 of \citet{JoD:00}.
+Since these arguments are similar and our modification is the same for
+both, we'll just present the more complicated version,~\eqref{eq:12}.
+
+Note that $\{Z_{1t}^2 P\gamma/b_T\}$ and $\{Z_{2t}^2 P\gamma/b_T\}$
+are uniformly integrable.  As in~\citet[Lemma A.4]{JoD:00}, we can
+assume that there is a constant $C$ such that $Z_{1t}$ and $Z_{2t}$
+are bounded in absolute value by $C\sqrt{b_T/P\gamma}$; uniform
+integrability ensures that the difference between the unbounded random
+variables and these truncated versions is negligible for large enough
+values of $C$.
+
+Let $r = \lfloor 3P/2b_T \rfloor$ and rewrite the summation as
+\begin{align*}
+  \vtSum \vtIIIsummand &= \vtSumr \vtSuma \vtIIIsummand \\
+  &\quad+ \vtSumr \vtSumb \vtIIIsummand \\
+  &\quad+ \sum_{t=r b - P + 1}^{2P} \vtIIIsummand \\
+  &\equiv \vtSumr (U_i - \E_R U_i) + \vtSumr (U_i' - \E_R U_i') + o_{L_1}(1).
+\end{align*}
+The proof then holds if we can show that both $U_i$ and $U_i'$ obey
+\lln s.  We'll do so by proving that $\{U_i -\E_R U_i,
+\UFiltration{2i-1}\}$ and $\{U_i' - \E_R U_i', \UFiltration{2i}\}$ are
+$L_2$-mixingales of size $-1/2$ and using the bound $\E(\vtSumr (U_i -
+\E_R U_i))^2 = O(\vtSumr c_i^2)$ where the $c_i$ are the mixingale
+magnitude indices \citep{Mcl:75}.
+
+For non-negative $m$, we have 
+\begin{equation*}
+U_i - \E_R U_i \in \UFiltration{2i+2m-1},
+\end{equation*}
+establishing half of the mixingale result trivially.  Now fix $i$ and $m >
+0$ and use Lemma \ref{lem-basic-coupling} to define $\tilde{D}_{ts}$
+for each $t =(2i-2)b_T-P+1,\dots,(2i-1)b_T-P$ and $s =
+\max(t+R-b_T,R-\h+1),\dots,\min(t+R+b_T,T)$ such that
+\begin{equation*}
+ \E_R \tilde D_{ts} = \E_{(2i-2m-1)b_T+R-P} \tilde D_{ts} \quad a.s.
+\end{equation*}
+and
+\begin{equation*}
+  \lVert \tilde D_{ts} - D_{Rs} \rVert_2 \leq \couplingBound{s - (2i-2m-1)b_T-R+P}.
+\end{equation*}
+Also define
+\begin{equation*}
+  \tilde Z_{1t} = 1/\sqrt{P\gamma} \sum_{l=\vttLower}^{\vttUpper}
+  (\tilde D_{t,t+l+R} - \E_R\tilde D_{t,t+l+R})\ W(l/\gamma), \\
+\end{equation*}
+and
+\begin{equation*}
+\tilde Z_{2t} = 1/\sqrt{P\gamma} \sum_{j=\vttLower}^{\vttUpper}
+    (\tilde D_{t,t+l+R} - \E_R\tilde D_{t,t+l+R})\ \kernelB{j/\gamma}.
+\end{equation*}
+
+Now, we have the inequalities
+\begin{align*}
+  \lVert \E( U_i - \E_R U_i & \mid \UFiltration{2i-2m-1}) \rVert_2
+  \\ &\leq
+  \vtSuma \lVert \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) - \E_R
+  Z_{1t}Z_{2t} \rVert_2 \\
+  &= \vtSuma \lVert \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
+  &\quad - \E(\tilde{Z}_{1t}\tilde{Z}_{2t} \mid \UFiltration{2i-2m-1}) \\
+  &\quad + \E(\tilde{Z}_{1t}\tilde{Z}_{2t} \mid \UFiltration{2i-2m-1})
+  - \E_R Z_{1t}Z_{2t} \rVert_2 \\
+%  \leq \vtSuma (\wall \lVert \wall \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
+%  - \E(\tilde{Z}_{1t}\tilde{Z}_{2t} \mid \UFiltration{2i-2m-1}) \rVert_2\return
+%  \\ + \lVert \E_R Z_{1t}Z_{2t} - \E_R \tilde{Z}_{1t}\tilde{Z}_{2t}
+%  \rVert_2)\return \\
+  &\leq 2 \vtSuma \lVert Z_{1t} Z_{2t} - \tilde Z_{1t} \tilde{Z}_{2t}
+  \rVert_2 \\
+  &\leq 2 \vtSuma (\lVert Z_{1t} - \tilde{Z}_{1t} \rVert_2 \lVert
+  Z_{2t} \rVert_{\infty}
+  + \lVert Z_{2t} - \tilde{Z}_{2t} \rVert_2 \lVert \tilde{Z}_{1t} \rVert_{\infty}) \\
+  &\leq \frac{2 C b_T^{1/2}}{(P\gamma)^{1/2}} \vtSuma (\lVert Z_{1t} - \tilde{Z}_{1t} \rVert_2 
+  + \lVert Z_{2t} - \tilde{Z}_{2t} \rVert_2).
+\end{align*}
+
+And we can finish the proof with the following inequalities:
+\begin{align*}
+  \frac{2 C b_T^{1/2}}{(P \gamma)^{1/2}} &\vtSuma \lVert Z_{1t} - \tilde{Z}_{1t} \rVert_2 \\& \leq
+  \frac{4C b_T^{1/2}}{P\gamma} \vtSuma \sum_{l=\vttLower}^{\vttUpper} \lVert
+  D_{t+l+R,R} - \tilde{D}_{t,t+l+R} \rVert_2 W(l/\gamma) \\&
+  \leq O\Bigg(\frac{b_T^{1/2}}{P\gamma}\Bigg) \vtSuma
+  \sum_{l=\vttLower}^{\vttUpper} \couplingBeta{t+l-(2i-2m-1)b_T+P}\\&
+  = O\Bigg(\frac{b_T^{1/2}}{P\gamma}\Bigg) O(b_T^{3/2-u}\, m^{-1/2-u})
+\end{align*}
+for some positive $u$.  The same argument holds for $Z_{2t}$.
+As a result,
 \[
-    \CenteredAverage = \CenteredAverageI + \CenteredAverageII.
+E\Big(\vtSumr (U_i - \E_R U_i)\Big)^2 = o\Big(\vtSumr b_T^2/P\gamma\Big) =
+ o(b_T/\gamma) \to 0,
+\]
+as required.
+\end{proof}
+
+\begin{lem}\label{lem:a3}
+  Suppose that $D_{Rt}'$ denotes loss differences using a rolling or
+  recursive window, and $D_{Rt}$ those using the fixed window and
+  define $\oosA' = P^{-1} \sum_{t=R+1}^{T-h} D_{Rt}'$.  
+  \begin{enumerate}
+  \item Under the assumptions of Theorem~\ref{sec:oostheory},
+    $\var_R(P^{1/2} \oosA') - \var_R(P^{1/2} \oosA) \to^p 0$.
+  \item Under the assumptions of Lemma~\ref{res-variance-estimator},
+    \begin{multline*}
+      P^{-1} \sum_{s,t=R+1}^{T-h} (D_{Rt}' - \oosA') (D_{Rs}' -
+      \oosA') W((t-s)/\gamma) - \\ P^{-1} \sum_{s,t=R+1}^{T-h}
+      (D_{Rt} - \oosA) (D_{Rs} - \oosA) W((t-s)/\gamma) \to^p 0.
+    \end{multline*}
+  \end{enumerate}
+\end{lem}
+\begin{proof}
+  Both follow from Equation~\eqref{eq:8} of Lemma~\ref{res-convergence}.
+\end{proof}
+
+\begin{lem}\label{lem:a6}
+  Suppose the conditions of Lemma~\ref{res-variance-estimator} hold
+  and that $D_{Rt}$ uses the fixed window.  Then
+  \begin{equation*}
+    \hat{\sigma}_R^2 - P^{-1} \sum_{s,t=R+1}^{T-h} (D_{Rs} - \E_R
+    D_{Rs}) (D_{Rt} - \E_R D_{Rt}) W((t-s)/\gamma) \to^{L_1} 0.
+  \end{equation*}
+\end{lem}
+
+\begin{proof}
+   It follows from simple algebra that
+\begin{multline*}
+  \Big| \hat\sigma_R^2 -  P^{-1} \sum_{s,t=R+1}^{T-h} (D_{Rs} - \E_R
+    D_{Rs}) (D_{Rt} - \E_R D_{Rt}) W((t-s)/\gamma) \Big| \leq\\
+  \varianceDiffA \\ + P^{-1} \oosSum{s,t}{1} \lvert (D_{Rs} -
+  \oosA)(\E_R D_{Rt} - \oosA) \rvert \vWeight + o_p(1).
+\end{multline*}
+We'll prove that these two sums are $o_p(1)$; uniform integrability
+then implies convergence in $L_1$.  The arguments are $o_p(1)$ are
+almost identical, so we'll only present the first.
+
+Applying the Cauchy-Scwarz inequality twice and simplifying gives the
+upper bound
+\begin{multline*}
+\varianceDiffA \\ \leq O(1) \Big[\varianceDiffAii\Big]^{1/2} \Big[\varianceDiffAi\Big]^{1/2}.
+\end{multline*}
+Now,
+$P^{-1} \oosSum{s}{1}(D_{Rs} - \E_R D_{Rs})^2 = O_p(1)$, and it suffices to prove
+that \[\varianceDiffAi = o_p(1).\]  Observe that
+\begin{align*}
+  \varianceDiffAi & = O_p\Big(P^{-1} \oosSum{s}{1}(\E_{R}D_{Rs} -
+  \E_R\oosA)^2\Big) + O_p(\oosA - \E_R\oosA)^{2} \\
+  &= O_p\Big(P^{-1} \oosSum{s}{1} (\E_RD_{Rs})^2 - (\E_R\oosA)^2\Big) +
+  o_p(1),
+\end{align*}
+with the second term vanishing by Lemma \ref{res-mixingale} and
+\citepos{Dav:93} mixingale \lln.
+
+Now define $\tilde D_s$, $s = R+1,\dots,T-\h$, as in Lemma
+\ref{lem-basic-coupling} so that $\E_{s-1} \tilde D_s = \E_R \tilde
+D_s$ almost surely.  Note that we also have the equality $\E_R \tilde
+D_s = \E_R \tilde D_{R+1}$ almost surely for all $s\geq R+1$, and so
+\[
+P^{-1} \oosSum{s}{1} (\E_R \tilde D_s)^2 = \Big(P^{-1} \oosSum{s}{1} \E_R
+\tilde D_s\Big)^2 \quad \text{a.s..}
+\]
+
+Consequently,
+\begin{align*}
+P^{-1} \oosSum{s}{1} (\E_R D_{Rs})^2 - (\E_R\oosA)^2 & = 
+P^{-1} \oosSum{s}{1} [(\E_R D_{Rs})^2 - (\E_R\tilde D_s)^2]\\
+&\quad+ \Big(P^{-1} \oosSum{s}{1} \E_R \tilde D_s\Big)^2 - (\E_R\oosA)^2 \quad \text{a.s}.\\
+&= O_p\Big(P^{-1} \oosSum{s}{1} [(\E_R D_{Rs})^2 - (\E_R \tilde D_s)^2]\Big).
+\end{align*}
+Finally, 
+\begin{align*}
+\Big\lVert P^{-1} \oosSum{s}{1} [(\E_RD_{Rs})^2 - (\E_R \tilde D_s)^2] \Big\rVert_1
+&\leq P^{-1} \oosSum{s}{1} \lVert \E_RD_{Rs} - \E_R \tilde D_s \rVert_2 \lVert
+\E_RD_{Rs} + \E_R \tilde D_s \rVert_2
+\\ &\leq (4 B_L/P) \oosSum{s}{1} \lVert \E_RD_{Rs} - \E_R \tilde D_s \rVert_2,
+\end{align*}
+and this last term vanishes as in the proof of Lemma~\ref{lem:a2}.
+\end{proof}
+
+\subsection*{Proof of Theorem \ref{res-confidence-intervals}}
+
+It suffices to prove asymptotic normality.  Lemma~\ref{lem:a3} and
+Equation~\eqref{eq:8} of Lemma~\ref{res-convergence} let us restrict
+attention to the fixed window statistic.  We can rewrite the centered
+\oos\ average as
+\[
+\frac{\bar{D}_{R} - \E_T \bar{D}_T}{\hat\sigma_R / \sqrt{P}} =
+\frac{1}{\hat\sigma_R \sqrt{P}}\oosSum{t}{1} (D_{Rt} - \E_R D_{Rt}) +
+\frac{\sqrt{P}}{\hat\sigma_R} (\E_R\oosA - \E_T\oosB).
 \]
@@
 \ref{res-convergence} ensure that the first term is asymptotically
-normal and the second term vanishes.
-\end{proof}
-
-\begin{proof}[Proof of Lemma \ref{res-mixingale}, Part 1.]
-Fix $R$, $j$ and $l$ and use Lemma
-\ref{lem-basic-coupling} to define $\tilde{D}_{R+j}$ so that
-\[\E_R\tilde D_{R+j} = \E_{R+j-l} \tilde D_{R+j} \quad a.s. \]
-and
-\[\lVert D_{R+j,R} - \tilde D_{R+j} \rVert_2 \leq \couplingBound{l}.\]
-Then
-\[
-\lVert \E_{R+j-l} D_{R+j,R} - \E_R D_{R+j,R} \rVert_2 \wall \leq 
-\lVert \E_{R+j-l} D_{R+j,R} - \E_{R+j-l} \tilde{D}_{R+j} \rVert_2 \\
-\quad + \lVert
-\E_{R+j-l} \tilde{D}_{R+j} - \E_R D_{R+j,R} \rVert_2 \\
-\leq 2 \lVert D_{R+j,R} - \tilde D_{R+j} \rVert_2 \\
-\leq 2^{2 + \frac1\rho}\ B_L\ \couplingBeta{l}.\return
-\]
-Now $\couplingBeta{l} = O(l^{-\frac12 - \delta})$ for some
-positive $\delta$, completing the proof.
-\end{proof}
-
-\begin{proof}[Proof of Lemma \ref{res-mixingale}, Part 2.]
-  A modification of \citepos{Dej:97} \clt s for
-  mixingale and \ned\ arrays will complete the proof.
-
-Define
-\[\label{eq:z1}
-  Z_i = \ZDef
-\]
-where $b_T$ is a sequence that satisfies $b_T\leq P$,
-$b_T\to\infty$, and $b_T/P\to 0$.  The same arguments used in
-\citepos{Dej:97} Theorem 1 show that
-\begin{equation*}
-   \SumOuterBlock{i} Z_i = \frac1{\sqrt{P}} \oosSum{s}{1} (D_{tR} - \E_R D_{tR}) + o_p(1).
-\end{equation*}
-and
-\begin{equation*}
-  \SumOuterBlock{i} Z_i = \SumOuterBlock{i} (Z_i - E_{R + (i-1)b_T}
-  Z_i) + o_p(1).
-\end{equation*}
-Note that $\{Z_i - E_{R + (i-1)b_T},\mathcal{F}_{R + i b_T}\}_i$ is an
-\mds\ by construction, so \citepos{HaH:80} Theorem 3.2 and Corollary
-3.1 ensure that\footnote{Note that $\sigma^2 \in \mathcal{F}_t$ for
-  all $t \geq R$, so Hall and Heyde's condition (3.21) is
-  unnecessary---see the remarks after their result.}
-\[
-\frac1{\sigma} \SumOuterBlock{i} Z_i \to^p
-N(0,1)
-\]
-as long as
-\begin{equation}\label{eq:cltvar2}
-  \sigma^2 - \SumOuterBlock{i} \E_R Z_i^2 \to^p 0,
-\end{equation}
-and
-\begin{equation}\label{eq:cltvar1}
-  \SumOuterBlock{i} \E_R Z_i^2 - \SumOuterBlock{i} \ZSqCE \to^p 0.
-\end{equation}
-Equation (\ref{eq:cltvar2}) holds as in \citet{Dej:97} (see the proof
-of his Theorem 2); to see that (\ref{eq:cltvar1}) holds, we'll use an
-argument based on his Lemma 5.  Define
-\[
-\tilde Z_i = \frac1{\sqrt{P}} \SumInnerBlock{s}{i} \tilde D_s -
-\E_R \tilde D_s,
-\]
-with $\tilde D_{R+(i-1)b_T + 1},\dots,\tilde D_{R+ib_T}$ new random
-variables that satisfy
-\[
-\lVert \tilde D_s - D_{sR} \rVert_2 \leq 2^{1 + \frac1\rho} B_L \beta_{s -
-  (i-1)b_T + R}^{\rhoExp}, \quad s = R+(i-1)b_T + 1,\dots,R+i b_T
-\]
-and
-\[
-\E_R \phi(\tilde D_s) = \E_{R+(i-1)b_T} \phi(\tilde D_s) \quad \text{a.s.}, \quad s = R+(i-1)b_T + 1,\dots,R+i b_T
-\]
-for all measurable $\phi$ such that the expectations are finite; the
-existence of these variables is ensured by Lemma
-\ref{lem-basic-coupling}.  Then $\tilde Z_i$ satisfies
-\[
-\E_R \tilde Z_i^2 = \CEOuterBlock{\tilde Z_i^2}{i} \quad \text{a.s.},
-\]
-giving the inequality
-\[
-\lVert \ZSqCE - \E_R Z_i^2 \rVert_1 \wall= \lVert \wall\CEOuterBlock{(Z_i^2 -
-  \tilde Z_i^2)}{i} \\ - (\E_R Z_i^2 - \CEOuterBlock{\tilde Z_i^2}{i})
-\rVert_1 \return\\
-\leq 2 \lVert Z_i^2 - \tilde Z_i^2 \rVert_1.
-\return
-\]
-
-Also define 
-\[
-V_{i,C} = \begin{cases} Z_i & \text{if } |Z_i| < \ZTrunc \\ 
-  \ZTrunc & \text{if } Z_i \geq \ZTrunc \\
-- \ZTrunc & \text{if } Z_i \leq -\ZTrunc
-  \end{cases}
-\]
-and
-\[
-\tilde V_{i,C} = \begin{cases} 
- \tilde Z_i & \text{if } |\tilde Z_i| < \ZTrunc \\ 
-  \ZTrunc & \text{if } \tilde Z_i \geq \ZTrunc \\
-- \ZTrunc & \text{if } \tilde Z_i \leq -\ZTrunc.
-\end{cases} 
-\]
-Both $Z_i\sqrt{\frac{P}{b_T}}$ and $\tilde Z_i\sqrt{\frac{P}{b_T}}$
-are uniformly integrable, so $C$ can be chosen to make
-\[
-\lVert \SumOuterBlock{i} [(Z_i^2 - \tilde Z_i^2) - (V_{i,C}^2 - \tilde V_{i,C}^2)] \rVert_1
-\]
-arbitrarily small.  As a result, \eqref{eq:cltvar1} holds if we can
-prove that
-\[
-\lVert \SumOuterBlock{i} (V_{i,C}^2 - \tilde V_{i,C}^2) \rVert_1 \to 0
-\]
-for arbitrary $C$, which we will show next.
-
-Note that 
-\[\lvert V_{i,C} - \tilde V_{i,C} \rvert \leq \lvert Z_{i,C} - \tilde
-Z_{i,C} \rvert \quad \text{and} \quad \lvert V_{i,C} + \tilde V_{i,C}
-\rvert \leq 2 C \sqrt{b_T/P} \quad \text{a.s.}\] 
-It follows that
-\[
-\SumOuterBlock{i} \lVert V_{i,C}^2 - \tilde V_{i,C}^2 \rVert_1 
-\wall
- \leq 2 \ZTrunc \SumOuterBlock{i} \lVert Z_i - \tilde Z_i \rVert_2 \\
- \leq \frac{2 C \sqrt{b_T}}{P}\SumOuterBlock{i} \SumInnerBlock{s}{i} \lVert \wall \ZSummand \\
-  - (\tilde D_s - \E_R \tilde D_s) \rVert_2 \return \\ 
- = O(\frac{\sqrt{b_T}}{P}) \SumOuterBlock{i} \SumInnerBlock{s}{i} \lVert D_{sR} - \tilde D_s \rVert_2 \\
- = O(b_T^{-\frac12}) \sum_{s=1}^{b_T} \couplingBeta{s}
- \return
- \]
-Finally, $\couplingBeta{s} = O(s^{-1/2-\delta})$ for some positive
-$\delta$, making the last term $o(1)$ and completing the proof.
-\end{proof}
-
-\begin{proof}[Proof of Lemma \ref{res-convergence}]
+normal and the second term vanishes.\qed
+
+\subsection*{Proof of Lemma \ref{res-convergence}}
 \newcommand{\resConvgRHS}[1]{\ensuremath{\E(L(y^* - x_1^{*\prime}\bh{1#1}) - L(y^{*} -
@@
     x_{#1}^{*\prime}\bh{#1R}) - L(y^{*} - x_{#1}^{*\prime}\bh{#1T})}}
-We'll first show that 
-\begin{equation}\label{EQ-oosaverage1}
-\E_R \oosA = \resConvgRHS{R} + o_p(P^{-\frac12})
-\end{equation}
-and
-\begin{equation}\label{EQ-oosaverage2}
-\E_T \oosB = \resConvgRHS{T} + o_p(Q^{-\frac12})
-\end{equation}
+We'll first prove that $P^{1/2} \bar{D}_R' = P^{1/2} \bar{D}_R + o_p$.
+Use Lemma~\ref{lem-berbee} to define $(y_{t+h}^{*}, x_{t}^{*})$ for
+each $t$ so be independent of $\mathcal{F}_R$ and that
+$\Pr[(y_{t+h}^{*}, x_{t}^{*}) \neq (y_{t+h}, x_t)] = \beta_{t-R}$.
+Then
+\begin{multline*}
+  \Big\| P^{-1/2} \sum_{t=R+1}^{T-h} (D_{Rt}' - D_{Rt}) \Big\|_1 = \\
+  \sum_{i=1,2} \Big\| P^{-1/2} \sum_{t=R+1}^{T-h} L(y_{t+h}^{*} -
+  x_{it}^{*\prime} \hat{\theta}_{it}^R) - L(y_{t+h}^{*} -
+  x_{it}^{*\prime} \hat{\theta}_{iR}^R) \Big\|_1  + O\Big(P^{-1/2}
+  \sum_{t=R+1}^{T-h} \beta_{t-R}^{(\rho-2)/2\rho}\Big).
+\end{multline*}
+
+By assumption, $P^{-1/2} \sum_{t=R+1}^{T-h}
+\beta_{t-R}^{(\rho-2)/2\rho} \to 0$.  Smoothness of $L$ and the
+formula for the \ols\ estimator ensures that
+\begin{align*}
+  \Big\|P^{-1/2} \sum_{t=R+1}^{T-h} L(y_{t+h}^{*} - x_{it}^{*\prime}
+  \hat{\theta}_{it}^R) - & L(y_{t+h}^{*} - x_{it}^{*\prime}
+  \hat{\theta}_{iR}^R)\Big\|_1 \\ &\leq B_{L} P^{-1/2}
+  \sum_{t=R+1}^{T-h} \| x_{it}^{*\prime} (\hat{\theta}_{it}^R -
+  \hat{\theta}_{iR}^R) \|_2 \\ &\leq B_{L} P^{-1/2} \sum_{t=R+1}^{T-h}
+  \Big(\big\| x_{it}^{*\prime} [(X_{it}'X_{it})^{-1} -
+  (X_{iR}'X_{iR})^{-1}] X_{it}' \mathbf{\varepsilon}_{it} \big\|_2 \\
+  &\quad + \big\| x_{it}^{*\prime}
+  (X_{iR}'X_{iR})^{-1}[X_{it}'\mathbf{\varepsilon}_{it} - X_{iR}
+  \mathbf{\varepsilon}_{iR} ] \big\|_2 \Big).
+\end{align*}
+  Moreover,
+\begin{align*}
+  \big\| x_{it}^{*\prime} [(X_{it}'X_{it})^{-1} &-
+  (X_{iR}'X_{iR})^{-1}] X_{it}' \mathbf{\varepsilon}_{it} \big\|_2 \\
+  &\leq \E \Big| \lambda_{K_i}(X_{it}' \mathbf{\varepsilon}_{it}
+  \mathbf{\varepsilon}_{it}' X_{it})\sum_{t=R+1}^{T-h}
+  \sum_{j=1}^{K_i} \lambda_j^2((X_{iR}'X_{iR})^{-1} -
+  (X_{it}'X_{it})^{-1}) \lambda_{\pi_j}(x_{it}^{*} x_{it}^{*\prime})
+  \Big| \\ &\leq \Delta T \Big\| \sum_{t=R+1}^{T-h} \sum_{j=1}^{t-R}
+  \lambda_j^{-2}(X_{iR}'X_{iR}) \lambda_{\pi_j}(x_{it}^{*}
+  x_{it}^{*\prime}) \Big\|_{3/2} \\ &\leq \Delta^3 P^2/R
+\end{align*}
+where $\pi_i,\dots,\pi_{K_i}$ is a permutation of $1,\dots,K_i$.  The
+first equality holds because $\lambda_{\max}(X_{it}'
+\mathbf{\varepsilon}_{it} \mathbf{\varepsilon}_{it} X_{it}) =
+O_{L_{3}}(T)$ by assumption and $(X_{iR}'X_{iR})^{-1} -
+(X_{it}'X_{it})^{-1}$ has rank $t-R$ with eigenvalues bounded by those
+of $(X_{iR}'X_{iR})^{-1}$.  The second holds by independence of
+$x_{it}^{*}$ and $X_{iR}$.  A similar argument proves that
+\begin{equation*}
+  \big\| x_{it}^{*\prime}
+  (X_{iR}'X_{iR})^{-1}[X_{it}'\mathbf{\varepsilon}_{it} - X_{iR}
+  \mathbf{\varepsilon}_{iR} ] \big\|_2 \leq \Delta^3 P^2/R
+\end{equation*}
+as well, so 
+\begin{equation*}
+  \Big\|P^{-1/2} \sum_{t=R+1}^{T-h} L(y_{t+h}^{*} - x_{it}^{*\prime}
+  \hat{\theta}_{it}^R) -  L(y_{t+h}^{*} - x_{it}^{*\prime}
+  \hat{\theta}_{iR}^R)\Big\|_1 \leq B_L \Delta^{3/2} P / R^{1/2},
+\end{equation*}
+completing the proof. The proof that $P^{1/2} (\bar{D}_T' - \bar{D}_T)
+\to^p 0$ is similar.\footnote{In this proof, $(y_{t+h}^{*}, x_t^{*})$
+  should be defined to be independent of $\mathcal{F}_R$ even for $t >
+  T$.}
+
+Now,~\eqref{eq:7} follows from showing
+\begin{gather*}
+\E_R \oosA = \resConvgRHS{R} + o_p(P^{-1/2}),\\
+\E_T \oosB = \resConvgRHS{T} + o_p(P^{-1/2}),\\
+\resConvgEstDiff{i} = O_p(P^{1/2}/T^{1/2}),
+\intertext{and}
+\resConvgEstDiff{i} = O_p(P^{1/2}/T^{1/2}),
+\end{gather*}
 where $\hat\theta_R = (\hat\theta_{1R}, \hat\theta_{2R})$,
@@
 distribution of $(y_{t+\h},x_{1t},x_{2t})$ independently of
-$\mathcal{F}_T$.  We'll then show that
-\begin{equation}\label{EQ-thetaconvg1}
-\resConvgEstDiff{1} = O_p(\sqrt{P/T})
-\end{equation}
+$\mathcal{F}_T$.  The arguments are the same as in the preceding
+proof.\qed
+
+\subsection*{Proof of Lemma \ref{res-mixingale}}
+We'll only present proofs for the fixed-window; the arguments for the
+rolling and recursive windows are essentially the same.
+
+\noindent \textit{Part 1.} Fix $R$, $j$ and $l$ and use Lemma
+\ref{lem-basic-coupling} to define $\tilde{D}_{R+j}$ so that
+\[\E_R\tilde D_{R+j} = \E_{R+j-l} \tilde D_{R+j} \quad a.s. \]
 and
-\begin{equation}\label{EQ-thetaconvg2}
-\resConvgEstDiff{1} = O_p(\sqrt{P/T})
-\end{equation}
-to complete the proof.
-
-To prove (\ref{EQ-oosaverage1}), define $\tilde D_t$ for each $t = R+1,\dots,T-\h$ as
-in Lemma \ref{lem-basic-coupling} so that
-\[
-\lVert \tilde D_t - D_{tR} \rVert_2 \leq \couplingBound{t-R}
+\[\lVert D_{R+j,R} - \tilde D_{R+j} \rVert_2 \leq \couplingBound{l}.\]
+Then
+\begin{align*}
+\lVert \E_{R+j-l} D_{R+j,R} - \E_R D_{R+j,R} \rVert_2 & \leq 
+\lVert \E_{R+j-l} D_{R+j,R} - \E_{R+j-l} \tilde{D}_{R+j} \rVert_2 \\
+&\quad + \lVert
+\E_{R+j-l} \tilde{D}_{R+j} - \E_R D_{R+j,R} \rVert_2 \\
+&\leq 2 \lVert D_{R+j,R} - \tilde D_{R+j} \rVert_2 \\
+&\leq 2^{2 + 1/\rho}\ B_L\ \couplingBeta{l}.
+\end{align*}
+Now $\couplingBeta{l} = O(l^{-1/2 - \delta})$ for some
+positive $\delta$, completing the proof.\qed
+
+\vspace{\baselineskip}
+\noindent\textit{Part 2.}  A modification of \citepos{Jon:97} \clt s for
+mixingale and \ned\ arrays will complete the proof.  Define
+\[\label{eq:z1}
+  Z_i = \ZDef
 \]
+where $b_T$ is a sequence that satisfies $b_T\leq P$,
+$b_T\to\infty$, and $b_T/P\to 0$.  The same arguments used in
+\citepos{Jon:97} Theorem 1 show that
+\begin{equation*}
+   \SumOuterBlock{i} Z_i = P^{-1/2} \oosSum{s}{1} (D_{Rt} - \E_R D_{Rt}) + o_p(1).
+\end{equation*}
 and
-\[
-\E_R \tilde D_t = \resConvgRHS{R} \quad\text{a.s.}
-\]
-for all $t$.  Then 
-\[
-\lVert \E_R \oosA - \wall \resConvgRHS{R} \rVert_2  \\
-\leq \frac1P \oosSum{t}{1} \lVert \E_R (D_{tR} - \tilde D_t) \rVert_2 \\
-\leq \frac{\couplingConstant}{P} \oosSum{s}{1} \couplingBeta{s} \\
-= o(P^{-\frac12}).
-\return
-\]
-The proof of (\ref{EQ-oosaverage2}) is identical.
-
-Equations (\ref{EQ-thetaconvg1}) and (\ref{EQ-thetaconvg2}) both
-follow the same argument, so we'll just prove (\ref{EQ-thetaconvg1}).
-Since 
-\[ \lVert \resConvgEstDiff{1} \rVert_1 \\ \quad= \| \E(L(y^{*} -
-x_1^{*\prime} \hat{\theta}_{1R}) - L(y^{*} - x_2^{*\prime}
-\hat{\theta}_{dR}) \mid \hat{\theta}_{1R}, \hat{\theta}_{1T}) \|_1 \\
-\quad\leq \lVert \resConvgEstDiffRV{1} \rVert_1, \] it suffices to
-prove
-\[ \resConvgEstDiffRV{1} = O_p(\sqrt{P/T}). \]
-Moreover, smoothness of the loss function ensures that
-\[ \resConvgEstDiffRV{1} = O_p(1) x_1^{*\prime} (\bh{1R} -
-\bh{1T}), \]
-and it suffices to show that
-\begin{equation*}
-  \lVert x_1^{*\prime}(\bh{1R} - \bh{1T}) \rVert_2 = O(\sqrt{P/T}).
-\end{equation*}
-
-Manipulating the formula for the \ols\ estimator gives us
-\begin{equation} \label{eq-theta-convergence-1}
-\lVert x_1^{*\prime} (\bh{1R} - \bh{1T}) \rVert_2 \wall \leq
-\lVert x_1^{*\prime} [(X_{1R}'X_{1R})^{-1} - (X_{1T}'X_{1T})]
-X_{1T}'\ep{1T} \rVert_2  \\ \quad +
-\lVert x_1^{*\prime} (X_{1R}'X_{1R})^{-1}\oosSum{t}{1} x_{1t}\varepsilon_{i,t+\h}
-\rVert_2.
-\end{equation}
-The first term on the right side of \eqref{eq-theta-convergence-1}
-satisfies the relationship
-\[
-\lVert x_{1}^{*\prime}[(X_{1R}'X_{1R})^{-1} -
-(X_{1T}'X_{1T})^{-1} ]
-X_{1T}'\ep{1T} \rVert_2^2 \\ = O(1)
-\E\{\lambda_{\max}(X_{1T}' \ep{1T} \ep{1T}'
-    X_{1T}) \sum_{i=1}^{K_1}
-    \lambda_i^2([X_{1R}'X_{1R}]^{-1} -
-        [X_{1T}'X_{1T}]^{-1} )\}.
-\]
-By assumption, $\lambda_{\max}(X_{1T}'\ep{1T} \ep{1T}' X_{1T}) =
-O_p(T)$.  The matrix $(X_{1R}'X_{1R})^{-1} - (X_{1T}'X_{1T})^{-1}$ has
-rank $P$ and its eigenvalues are bounded by those of
-$(X_{1R}'X_{1R})^{-1}$, so
-  \[\sum_{i=1}^{K_1}\lambda_i^2((X_{1R}'X_{1R})^{-1} -
-  (X_{1T}'X_{1T})^{-1} )  \wall \leq
-  \sum_{i=K_1 - P + 1}^{K_1}\lambda_i^2((X_{1R}'X_{1R})^{-1})  \\ = O_p(P/T^2).
-  \]
-The moment bounds in Assumption~\ref{asmp-2} guarantee that
-convergence in probability implies convergence in $L_2$, so
-  \[
-    \lVert x_1^{*\prime} [(X_{1R}'X_{1R})^{-1} -
-        (X_{1T}'X_{1T})^{-1} ]
-      X_{1T}'\ep{1T} \rVert_2 = O(\sqrt{P/T}).
-  \]
-  A similar argument shows that
-  \[
-    \lVert x_1^{*\prime} (X_{1R}'X_{1R})^{-1}\oosSum{t}{1} x_{1t}\varepsilon_{1T}
-    \rVert_2 =   O(\sqrt{P/T}),
-  \]
-  completing the proof.
-\end{proof}
-
-\begin{proof}[Proof of Lemma \ref{res-variance-estimator}]
-  The proof follows \citepos{DeD:00} Theorem 2.1
-  closely.  We start by defining similar quantities to theirs,
-  borrowing their notation when possible to make the similarities
-  apparent.  For positive $\delta$, define $b_T \equiv \lfloor
-  \frac\gamma\delta \rfloor$,
-\begin{equation*}
-  \kernelB{x} \equiv \kernelBDefn{x},
-\end{equation*}
-\begin{equation*}
-  \varianceTermI \equiv \varianceTermIDefn,
-\end{equation*}
-\begin{equation*}
-  \varianceTermII \equiv \vtSum \wall \varianceTermIIa\\ \times
-  \varianceTermIIb,\return
-\end{equation*}
-\begin{equation*}
-  \varianceTermIII \equiv \vtSum \wall \varianceTermIIIa\\ 
-  \times \varianceTermIIb, \return 
-\end{equation*}
-\begin{equation*}
-  \varianceTermIV \equiv \vtSum \wall \varianceTermIIIa \\
-  \times \varianceTermIVb, \return
-\end{equation*}
+\begin{equation*}
+  \SumOuterBlock{i} Z_i = \SumOuterBlock{i} (Z_i - E_{R + (i-1)b_T}
+  Z_i) + o_p(1).
+\end{equation*}
+Note that $\{Z_i - E_{R + (i-1)b_T},\mathcal{F}_{R + i b_T}\}_i$ is an
+\mds\ by construction, so \citepos{HaH:80} Theorem 3.2 and Corollary
+3.1 ensure that $\sigma_R^{-1} \SumOuterBlock{i} Z_i \to^d N(0,1) $ as
+long as
+\begin{equation}\label{eq:cltvar2}
+  \sigma_R^2 - \SumOuterBlock{i} \E_R Z_i^2 \to^p 0,
+\end{equation}
+and
+\begin{equation}\label{eq:cltvar1}
+  \SumOuterBlock{i} \E_R Z_i^2 - \SumOuterBlock{i} \ZSqCE \to^p 0.\footnote{Note that $\sigma_R^2 \in \mathcal{F}_t$ for
+    all $t \geq R$, so Hall and Heyde's condition (3.21) is
+    unnecessary---see the remarks after their result.} 
+\end{equation}
+Equation (\ref{eq:cltvar2}) holds as in \citet{Jon:97} (see the proof
+of his Theorem 2); (\ref{eq:cltvar1}) is ensured by
+Lemma~\ref{lem:a2}. \qed
+
+\subsection*{Proof of Lemma \ref{res-variance-estimator}}
+Lemma~\ref{lem:a3} lets us prove the results for the fixed window
+only.  The proof follows \citepos{JoD:00} Theorem 2.1 closely.  We
+start by defining similar quantities to theirs, borrowing their
+notation when possible to make the similarities apparent.  For
+positive $\delta$, define $b_T \equiv \lfloor \gamma/\delta \rfloor$,
+$\kernelB{x} \equiv \kernelBDefn{x}$, and
+\begin{align*}
+  \varianceTermI &\equiv
+  \varianceTermIDefn,\\ \varianceTermII &\equiv \vtSum
+  \varianceTermIIa\\& \quad \times \varianceTermIIb,\\
+  \varianceTermIII &\equiv \vtSum \varianceTermIIIa\\
+  &\quad \times \varianceTermIIb,\\
+  \varianceTermIV &\equiv \vtSum \varianceTermIIIa \\
+  &\quad\times \varianceTermIVb,
+\end{align*}
 giving us the inequalities
-\begin{equation*}
-  \lVert \hat\sigma^2 - \sigma^2 \rVert_1 \wall 
-  \leq \lVert \hat\sigma^2 - \varianceTermI \rVert_1 
+\begin{align*}
+  \lVert \hat\sigma_R^2 - \sigma_R^2 \rVert_1 &
+  \leq \lVert \hat\sigma_R^2 - \varianceTermI \rVert_1 
   + \lVert \varianceTermI - \varianceTermII \rVert_1 
   + \lVert \varianceTermII - \varianceTermIII \rVert_1 
-  + \lVert \varianceTermIII - \varianceTermIV \rVert_1\\\quad
+  + \lVert \varianceTermIII - \varianceTermIV \rVert_1\\ & \quad
   + \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1 
   + \lVert \E_R\varianceTermIII - \E_R\varianceTermIV \rVert_1
-  + \lVert \E_R\varianceTermII - \E_R\varianceTermIII \rVert_1\\\quad 
+  + \lVert \E_R\varianceTermII - \E_R\varianceTermIII \rVert_1\\ & \quad 
   + \lVert \E_R\varianceTermI - \E_R\varianceTermII \rVert_1 
-  + \lVert \E_R \varianceTermI - \sigma^2 \rVert_1
-  \\ 
-  \leq  \lVert \hat\sigma^2 - \varianceTermI \rVert_1 
+  + \lVert \E_R \varianceTermI - \sigma_R^2 \rVert_1
+  \\ &
+  \leq  \lVert \hat\sigma_R^2 - \varianceTermI \rVert_1 
   + 2(\lVert \varianceTermI - \varianceTermII \rVert_1 
@@
       + \lVert \varianceTermIII - \varianceTermIV \rVert_1) \\ 
-  \quad + \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1 
-  + \lVert \E_R \varianceTermI - \sigma^2 \rVert_1.
-\end{equation*}
+  & \quad + \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1 
+  + \lVert \E_R \varianceTermI - \sigma_R^2 \rVert_1.
+\end{align*}
 De Jong and Davidson (2000) prove that
@@
 \begin{equation} \label{dd4}
-\lim \lVert \E_R \varianceTermI - \sigma^2 \rVert_1 = 0.
+\lim \lVert \E_R \varianceTermI - \sigma_R^2 \rVert_1 = 0.
 \end{equation}
@@
 functions of mixing processes are also mixingale processes, and do not
-use any properties specific to \ned\ processes, so they hold here as
-well.  We do need to modify their proofs that
+use any other properties specific to \ned\ processes, so they hold
+here as well.  We do need to modify their proofs that
 \begin{equation}
-  \label{eq:4} \lVert \hat{\sigma}^2 - \varianceTermI \rVert_1 \to 0
+  \label{eq:4} \lVert \hat{\sigma}_R^2 - \varianceTermI \rVert_1 \to 0
 \end{equation}
@@
 \end{equation}
-though, since their proofs exploit \ned\ properties.
-
-We'll start with (\ref{eq:4}). It follows from simple algebra that
-\[
-\lvert \hat\sigma^2 - \varianceTermI \rvert \leq \wall
-\varianceDiffA \\ +
-\frac1{P} \oosSum{s,t}{1} \lvert (D_{tR} - \oosA)(\E_R D_{sR} - \oosA) \rvert
-\vWeight,
-\]
-so we'll show that each summation is $o_p(1)$.  The two
-arguments are almost identical, so we'll only present the first.
-
-Applying the Cauchy-Scwarz inequality twice and simplifying gives the
-upper bound
-\[
-\varianceDiffA \\ \quad \leq O(1) [\varianceDiffAii]^{\frac12} [\varianceDiffAi]^{\frac12}.
-\]
-Now,
-$\frac1P \oosSum{s}{1}(D_{sR} - \E_R D_{sR})^2 = O_p(1)$, and it suffices to prove
-that \[\varianceDiffAi = o_p(1).\]  Observe that
-\[
-\varianceDiffAi \wall =  O_p(\frac1P \oosSum{s}{1}(\E_{R}D_{sR} -
-\E_R\oosA)^2) \\
-\quad + O_p(\oosA - \E_R\oosA)^{2} \\
-= O_p(\frac1P \oosSum{s}{1} (\E_RD_{sR})^2 - (\E_R\oosA)^2) + o_p(1),    \return
-\]
-with the second term vanishing by Lemma \ref{res-mixingale} and
-\citepos{Dav:93} mixingale \lln.
-
-Now define $\tilde D_s$, $s = R+1,\dots,T-\h$, as in Lemma
-\ref{lem-basic-coupling} so that $\E_{s-1} \tilde D_s = \E_R \tilde
-D_s$ almost surely.  Note that we also have the almost sure equality
-$\E_R \tilde D_s = \E_R \tilde D_{R+1}$ almost surely for all $s\geq R+1$,
-and so
-\[
-\frac1P \oosSum{s}{1} (\E_R \tilde D_s)^2 = (\frac1P \oosSum{s}{1} \E_R
-\tilde D_s)^2 \quad \text{a.s..}
-\]
-
-Consequently,
-\[
-\frac1P \oosSum{s}{1} (\E_R D_{sR})^2 - (\E_R\oosA)^2 \wall = 
-\frac1P \oosSum{s}{1} [(\E_R D_{sR})^2 - (\E_R\tilde D_s)^2]\\
-\quad+ (\frac1P \oosSum{s}{1} \E_R \tilde D_s)^2 - (\E_R\oosA)^2 \quad \text{a.s}.\\
-= O_p(\frac1P \oosSum{s}{1} [(\E_R D_{sR})^2 - (\E_R \tilde D_s)^2]).
-\]
-Finally, 
-\[
-\lVert \frac1P \wall\oosSum{s}{1} [(\E_RD_{sR})^2 - (\E_R \tilde D_s)^2] \rVert_1
-\\ \leq \frac1P \oosSum{s}{1} \lVert \E_RD_{sR} - \E_R \tilde D_s \rVert_2 \lVert
-\E_RD_{sR} + \E_R \tilde D_s \rVert_2
-\\ \leq \frac{4 B_L}P \oosSum{s}{1} \lVert \E_RD_{sR} - \E_R \tilde D_s \rVert_2,
-\return
-\]
-and this last term vanishes as in the proof of Lemma
-\ref{res-mixingale}.
-
-\newcommand{\UFiltration}[1]{\ensuremath{\mathcal{F}_{(#1)b_{T}+R-P}}}%
-Next, we'll prove (\ref{eq:5}). As in \citet{DeD:00}, let
-\begin{equation*}
-  Z_{1t} = \varianceTermIIIa,
-\end{equation*}
-and
-\begin{equation*}
-  Z_{2t} = \varianceTermIVb,
-\end{equation*}
-so
-\begin{equation*}
-  \varianceTermIV - \E_R \varianceTermIV = \vtSum (Z_{1t}Z_{2t} - \E_R Z_{1t}Z_{2t}),
-\end{equation*}
-and note that $\{Z_{1t}^2 \frac{P\gamma}{b_T}\}$ and $\{Z_{2t}^2
-\frac{P\gamma}{b_T}\}$ are uniformly integrable.  As in the proof of Theorem
-\ref{res-confidence-intervals}, we can assume that there is a constant
-$C$ such that $Z_{1t}$ and $Z_{2t}$ are bounded in absolute value by
-$C\sqrt{\frac{b_T}{P\gamma}}$; uniform integrability ensures that the
-difference between the unbounded random variables and these truncated
-versions is negligible for large enough values of $C$.  Let $r =
-\lfloor \frac{3P}{2b} \rfloor$ and rewrite the summation as
-\begin{equation*}
-  \vtSum \vtIIIsummand \wall= \vtSumr \vtSuma \vtIIIsummand \\
-  \quad+ \vtSumr \vtSumb \vtIIIsummand \\
-  \quad+ \sum_{t=r b - P + 1}^{2P} \vtIIIsummand \\
-  \equiv \vtSumr (U_i - \E_R U_i) + \vtSumr (U_i' - \E_R U_i') + o_{L_1}(1).\return
-\end{equation*}
-The proof then holds if we can show that both $U_i$ and $U_i'$ obey
-\lln s.  We'll do so by proving that $\{U_i -\E_R U_i,
-\UFiltration{2i-1}\}$ and $\{U_i' - \E_R U_i', \UFiltration{2i}\}$ are
-$L_2$-mixingales of size $-1/2$ and using the bound $E(\vtSumr (U_i -
-\E_R U_i))^2 = O(\vtSumr c_i^2)$ where the $c_i$ are the mixingale
-magnitude indices \citep{Mcl:75}.
-
-For non-negative $m$, we have 
-\begin{equation*}
-U_i - \E_R U_i \in \UFiltration{2i+2m-1},
-\end{equation*}
-establishing part of the mixingale result trivially.  Now fix $i$ and $m >
-0$ and use Lemma \ref{lem-basic-coupling} to define $\tilde{D}_{ts}$
-for each $t =(2i-2)b_T-P+1,\dots,(2i-1)b_T-P$ and $s =
-\max(t+R-b_T,R-\h+1),\dots,\min(t+R+b_T,T)$ such that
-\begin{equation*}
- \E_R \tilde D_{ts} = \E_{(2i-2m-1)b_T+R-P} \tilde D_{ts} \quad a.s.
-\end{equation*}
-and
-\begin{equation*}
-  \lVert \tilde D_{ts} - D_{sR} \rVert_2 \leq \couplingBound{s - (2i-2m-1)b_T-R+P}.
-\end{equation*}
-Also define
-\begin{equation*}
-  \tilde Z_{1t} = \frac1{\sqrt{P\gamma}} \sum_{l=\vttLower}^{\vttUpper}
-  (\tilde D_{t,t+l+R} - \E_R\tilde D_{t,t+l+R})\ W(l/\gamma), \\
-\end{equation*}
-and
-\begin{equation*}
-\tilde Z_{2t} = \frac1{\sqrt{P\gamma}} \sum_{j=\vttLower}^{\vttUpper}
-    (\tilde D_{t,t+l+R} - \E_R\tilde D_{t,t+l+R})\ \kernelB{j/\gamma}.
-\end{equation*}
-
-Now, we have the inequalities
-\begin{equation*}
-  \lVert \E( U_i - \wall \E_R U_i \mid \UFiltration{2i-2m-1}) \rVert_2
-  \\ \leq
-  \vtSuma \lVert \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) - \E_R
-  Z_{1t}Z_{2t} \rVert_2 \\
-  = \vtSuma \lVert \wall \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
-  - \E(\tilde{Z}_{1t}\tilde{Z}_{2t} \mid \UFiltration{2i-2m-1}) \\
-  + \E(\tilde{Z}_{1t}\tilde{Z}_{2t} \mid \UFiltration{2i-2m-1})
-  - \E_R Z_{1t}Z_{2t} \rVert_2 \return \\
-%  \leq \vtSuma (\wall \lVert \wall \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
-%  - \E(\tilde{Z}_{1t}\tilde{Z}_{2t} \mid \UFiltration{2i-2m-1}) \rVert_2\return
-%  \\ + \lVert \E_R Z_{1t}Z_{2t} - \E_R \tilde{Z}_{1t}\tilde{Z}_{2t}
-%  \rVert_2)\return \\
-  \leq 2 \vtSuma \lVert Z_{1t} Z_{2t} - \tilde Z_{1t} \tilde{Z}_{2t}
-  \rVert_2 \\
-  \leq 2 \vtSuma (\lVert Z_{1t} - \tilde{Z}_{1t} \rVert_2 \lVert
-  Z_{2t} \rVert_{\infty}
-  + \lVert Z_{2t} - \tilde{Z}_{2t} \rVert_2 \lVert \tilde{Z}_{1t} \rVert_{\infty}) \\
-  \leq 2 C \sqrt{\frac{b_T}{P\gamma}} \vtSuma (\lVert Z_{1t} - \tilde{Z}_{1t} \rVert_2 
-  + \lVert Z_{2t} - \tilde{Z}_{2t} \rVert_2).
-  \return
-\end{equation*}
-
-And we can finish the proof with the following inequalities:
-\begin{equation*}
-  2 C \wall \sqrt{\frac{b_T}{P \gamma}} \vtSuma \lVert Z_{1t} - \tilde{Z}_{1t} \rVert_2 \\ \leq
-  \frac{4C \sqrt{b_T}}{P\gamma} \vtSuma \sum_{l=\vttLower}^{\vttUpper} \lVert
-  D_{t+l+R,R} - \tilde{D}_{t,t+l+R} \rVert_2 W(l/\gamma) \\
-  \leq O(\frac{\sqrt{b_T}}{P\gamma}) \vtSuma
-  \sum_{l=\vttLower}^{\vttUpper} \couplingBeta{t+l-(2i-2m-1)b_T+P}\\
-  = O(\frac{\sqrt{b_T}}{P\gamma}) O(b_T^{\frac32-u}\, m^{-\frac12-u})
-\end{equation*}
-for some positive $u$.  The same argument holds for $Z_{2t}$.
-As a result,
-\[
-E(\vtSumr (U_i - \E_R U_i))^2 = o(\vtSumr \frac{b_T^2}{P\gamma}) =
-o(\frac{3P}{2b_T} \frac{b^2}{P\gamma}) = o(\frac{b_T}{\gamma}) \to 0,
-\]
-as required.
-\end{proof}
-
-\begin{proof}[Proof of Theorem~\ref{res:ftest}]
-  To clean up the notation, we'll write $\theta_1$ as $\theta$ and
-  $q_{K_2-K_1,T-K_2}(1-\alpha)$ as $q_\alpha$.  Let
-  $(\hat{\theta}, \hat{\psi})$ denote the \ols\ coefficient estimator
-  using the full model and let 
-  \[\hat\tau^2 = \frac{1}{T-K_2}\sum_{t=0}^{T-1} (y_{t+1} - x_{1t}'\hat{\theta} -
-  x_{2t}'\hat{\psi})^2. \] Since the regressors are orthogonal,
-  $\hat\theta$ also is the \ols\ estimator of $\theta$ using the
-  restricted model.  The difference between the two models'
-  generalization error is
-\[
-E_T \oosB = \sum_{j=K_1+1}^{K_2} [\psi_j^2 - (\hat{\psi}_j - \psi_j)^2]
-\]
-For any $\hat{\theta}$, $E_T \oosB$ equals zero when
-$\hat{\psi}$ lies on the surface of the hypersphere centered at
-$\psi$ with radius $|\psi|_2$, and $E_T \oosB$ and is greater
-than zero when $\hat{\psi}$ lies outside that sphere.
-Also, the rejection region in $\Re^{K_2}$ for is the set of values of $\hat{\psi}$
-on or beyond the sphere
-\[
-\hat{\psi}'\hat{\psi} = \hat{\tau}^2 q_\alpha \frac{K_2-K_1}{T}.
-\]
-
-We can get a lower bound for the probability
-\[\Pr[F \geq q_\alpha \mid E_T \oosB \leq 0]\]
-by rewriting $\hat{\psi}$ in spherical coordinates re-centered at
-$\psi$: $(\hat{r}, \hat{\omega}_1, \dots,
-\hat{\omega}_{K_2-K_1-1})$, with 
-\[\hat{r} = |\hat{\psi} - \psi|_2 \\
-\hat{\omega}_{i} = \tan^{-1}(\frac{(\sum\nolimits_{j=K_1+i+1}^{K_2}(\hat{\psi}_j -
-    \psi_j)^2)^{\frac12}}{\hat{\psi}_{K_1+i} - \psi_{K_1+i}}), \quad
-  i=1,\dots,K_2-K_1-2, \\
-\hat{\omega}_{K_2-K_1-1} =\atan(\hat{\psi}_{K_2-K_1} - \psi_{K_2-K_1},
-  \hat{\psi}_{K_2-K_1-1}- \psi_{K_2-K_1-1} )
-\]
-and
-\[
-\atan(a, b) \equiv 
-\begin{cases}
-\tan^{-1}(a/b) & a > 0 \\
-\pi + \tan^{-1}(a/b) & a < 0, b \geq 0 \\
--\pi + \tan^{-1}(a/b) & a < 0, b < 0 \\
-\pi/2 & a = 0, b > 0 \\
-- \pi/2 & a = 0, b < 0 \\
-\text{undefined} & a = 0, b = 0.
-\end{cases}
-\]
-Note that $\hat{\omega}_1,\dots,\hat{\omega}_{K_2-K_1 - 2} \sim
-\operatorname{uniform}(-\pi/2, \pi/2)$ and
-$\hat{\omega}_{K_2-K_1-1}\sim \operatorname{uniform}(-\pi, \pi)$.
-Under this coordinate system, the acceptance region is centered at
-$(|\psi|_2, \tilde{\omega}_1, \dots, \tilde{\omega}_{K_2-K_1-1})$ with
-\[
-\tilde{\omega}_i = \tan^{-1}([\sum_{j=i+1}^{K_2-K_1}
-  (\psi_j/\psi_i)^2]^{\frac12}) \quad \text{for } i = 1,\dots,K_2-2,\\
-\tilde{\omega}_{K_2-K_1-1} = \atan(\psi_{K_2-K_1}, \psi_{K_2-K_1-1}).
-\]
-
-If $\psi$ lies outside the acceptance region of the F-test, that
-acceptance region is contained in the cone
-\[\{(r, \omega_1,\dots,\omega_{K_2-1}) : r \geq 0,\, \tilde{\omega}_{i}
-- \xi \leq \omega_i \leq \tilde{\omega}_i + \xi\}\]
-with
-\[
- \xi = \sin^{-1}(\frac{\hat{\tau}}{|\psi|_2}\sqrt{\frac{q_\alpha (K_2-K_1)}{T}})
-\] 
-for $\hat{\tau}^2$ given.\footnote{This setup assumes that
-  $[\tilde\omega_i - \xi, \tilde\omega_i + \xi] \subset
-  [-\pi/2,\pi/2]$ for each $i$.  If not, the region can be rotated
-  without changing the results.}
-
-As a result,
-\[
-\Pr[F \geq q_{\alpha}\wall \mid E_T \oosB \leq 0] = 
-\Pr[\hat{\psi}'\hat{\psi} \geq \hat \tau^2 q_\alpha \frac{K_2 - K_1}{T}
-\mid |\hat{\psi}-\psi|_2 \geq |\psi|_2] \\
-\geq 1 - \E(\Pr\{ \hat{\omega}_i \in [\tilde{\omega}_i - \xi, \tilde{\omega}_i +
-\xi] \ \forall i  \mid \hat{\tau}^2,
-|\hat{\psi}-\psi|_2 \geq |\psi|_2\} 
-\mid |\hat{\psi}-\psi|_2 \geq |\psi|_2)\quad a.s. \\ 
-= 1 - \frac12 E ((2\xi / \pi)^{K_2-K_1-1}\mid
-|\hat{\psi}-\psi|_2 \geq |\psi|_2)\quad a.s. \\
-= 1 - \frac12 E (2\xi/\pi)^{K_2-K_1-1} \quad a.s..
-\]
-The second equality holds because the $\hat{\omega}_i$s are uniform
-and the third holds because $\hat{\tau}$ is independent of
-$\hat{\psi}$ under normality.
-
-Now~\eqref{eq:ftestreject1} holds since $\xi \to 0$ almost surely as
-$\phi_2 \to \infty.$  Moreover, as
-$T\to\infty$, $\hat{\tau}^2\to^p\tau^2$ and $q_{\alpha}\to 1$, so
-$\plim \xi < \frac{\pi}{2}$.  Consequently,
-$(\frac{2\xi}{\pi})^{K_2-K_1-1}\to^p0$, proving~\eqref{eq:ftestreject2}.
-\end{proof}
+though, since their proofs exploit \ned\ properties.  The proofs
+follow from Lemmas~\ref{lem:a2} and~\ref{lem:a6}, since
+\begin{equation*}
+  \varianceTermIV - \E_R \varianceTermIV = \vtSum (Z_{1t}Z_{2t} - \E_R Z_{1t}Z_{2t});
+\end{equation*}
+$Z_{1t}$ and $Z_{2t}$ are defined in Lemma~\ref{lem:a2}.
+\qed
+
+\subsection*{Proof of Theorem~\ref{res:ftest}}
+
+\textit{Equation~\eqref{eq:11}}: Note that a necessary condition for
+$(\hat{\theta}_T - \theta_0)'V_T (\hat{\theta}_T - \theta_0) < c$
+as $\theta'V_T\theta \to \infty$ is for all of the mass of
+$\hat{\theta}_T$ to concentrate on the line joining $\theta$ and
+$\theta_0$.  For any distribution of $(\varepsilon_{t+h}, x_t')$ such
+that $\hat{\theta}_T$ depends on $\theta$ only through its mean, the
+Lebesgue measure of parameter sequences satisfying this condition is
+zero. \qed
+
+\vspace{\baselineskip}
+\noindent\textit{Equation~\eqref{eq:15}}:  Suppose that
+$(\varepsilon_{t+h}, x_t) \sim i.i.d. N(0,I)$ and condition on $X_T$.
+Then the distribution of $\hat{\theta}_{T}$ concentrates uniformly on
+the ellipsoid
+\begin{equation*}
+  (\hat{\theta}_T - \theta)'(\hat{\theta}_T - \theta) = \theta'\theta.
+\end{equation*}
+Now, for $\theta$ and $V_T$ such that 
+\begin{equation*}
+  (\theta-\theta_0)' V_T (\theta-\theta_0) > c + \delta,
+\end{equation*}
+the probability that $\hat{\theta}_T$ is inside the acceptance region
+of the test is less than $(1/2)^{K_2}$, which converges to zero as $T
+\to \infty$. \qed
+
 \bibliographystyle{abbrvnat}
@@
 
-\begin{table}[b]
+\begin{table}[h]
  \begin{multicols}{2}
@@
 
-\begin{table}[!tbp]
+\begin{table}[b]
  \begin{center}
  \begin{tabular}{lrrrr}\hline\hline
-\multicolumn{1}{l}{waldtest}&\multicolumn{1}{c}{Res.Df}&\multicolumn{1}{c}{Df}&\multicolumn{1}{c}{F}&\multicolumn{1}{c}{Pr(\textgreaterF)}\tabularnewline
+   \multicolumn{1}{l}{waldtest}&\multicolumn{1}{c}{Res.Df}&\multicolumn{1}{c}{Df}&\multicolumn{1}{c}{F}&\multicolumn{1}{c}{Pr(\textgreater
+     F)}\tabularnewline
    \hline
@@
 \begin{figure}
-\centering
-\large{Simulated Coverage of One-Sided DMW Interval for $E_R\oosA$}
-\includegraphics{mc/plots/interval-testerror1}
-\large{Simulated Coverage of Two-Sided DMW Interval for $E_R\oosA$}
-\includegraphics{mc/plots/interval-testerror2}
-\caption{Simulated coverage of $E_R \oosA$ at 90\% confidence using a
-  one- and two-sided intervals based on the \protect\textsc{dmw}
+  \centering {\large Simulated Coverage of One-Sided DMW Interval for
+    $\E_R\oosA$} \input{mc/plots/interval-testerror1.tikz}
+\caption{Simulated coverage of $\E_R \oosA$ at 90\% confidence using a
+  one-sided interval based on the \protect\textsc{dmw}
   \protect\textsc{oos} test, plotted as a function of the fraction of
@@
 \begin{figure}
-\centering
-\large{Simulated Coverage of One-Sided DMW Interval for $E_T\oosB$}
-\includegraphics{mc/plots/interval-generror1}
-\large{Simulated Coverage of Two-Sided DMW Interval for $E_T\oosB$}
-\includegraphics{mc/plots/interval-generror2}
-\caption{Simulated coverage of $E_T \oosB$ at 90\% confidence using a
-  one- and two-sided intervals based on the \protect\textsc{dmw}
+  \centering {\large Simulated Coverage of One-Sided DMW Interval for
+    $\E_T\oosB$} \input{mc/plots/interval-generror1.tikz}
+\caption{Simulated coverage of $\E_T \oosB$ at 90\% confidence using a
+  one-sided interval based on the \protect\textsc{dmw}
   \protect\textsc{oos} test, plotted as a function of the fraction of
@@
 \begin{figure}
-  \centering
-\large{Simulated Rejection Probability of F-test Under $E_T
-      \oosB \leq 0$}
-  \includegraphics{mc/plots/ftest-001}
-  \caption{Simulated rejection probabilities for the F-test given
+  \centering {\large Simulated Rejection Probability of $F$-test Under
+    $\E_T \oosB \leq 0$}
+  \input{mc/plots/ftest-001.tikz}
+  \caption{Simulated rejection probabilities for the $F$-test given
     $\E_T \oosB \leq 0$ with nominal size 10\%.  Values greater than
@@
 \begin{figure}
-  \centering
-  \large{Simulated Rejection Probability of DMW Test Under $E_T
-      \oosB \leq 0$}
-  \includegraphics{mc/plots/size-dmwsize}  
+  \centering {\large Simulated Rejection Probability of DMW Test Under
+    $\E_T \oosB \leq 0$)} \input{mc/plots/size-dmwsize.tikz}
   \caption{Simulated rejection probabilities for the \protect\textsc{dmw}
@@
 \begin{figure}
-  \centering
-  \large{Simulated Rejection Probability of Clark and West
-      (2006, 2007) Test Under $E_T \oosB \leq 0$}
-  \includegraphics{mc/plots/size-clarkwest}
+  \centering {\large Simulated Rejection Probability of Clark and West
+    (2006, 2007) \\ Test Under $\E_T \oosB \leq 0$}
+  \input{mc/plots/size-clarkwest.tikz}
   \caption{Simulated rejection probabilities for Clark and West's
@@
 \begin{figure}
-  \centering
-  \large{Simulated Rejection Probability of McCracken (2007)
-      Test \\ Under $E_T \oosB \leq 0$}
-  \includegraphics{mc/plots/size-mccracken}
+  \centering {\large Simulated Rejection Probability of McCracken
+    (2007) Test \\ Under $\E_T \oosB \leq 0$}
+  \input{mc/plots/size-mccracken.tikz}
   \caption{Simulated rejection probabilities for McCracken's (2007)
@@
 \begin{figure}
-  \centering
-  \large{Simulated Rejection Probability of DMW Test Under $E_T
-      \oosB > 0$}
-  \includegraphics{mc/plots/size-dmwpower}
+  \centering {\large Simulated Rejection Probability of DMW Test Under
+    $\E_T \oosB > 0$} \input{mc/plots/size-dmwpower.tikz}
   \caption{Simulated rejection probabilities for the \protect \textsc{dmw}
@@
     Sink Models of Equity Premium (OLS)}
-\includegraphics{empirics/plots/oos-mse-1}
-\includegraphics{empirics/plots/oos-mse-1b}
+\input{empirics/plots/oos-mse-1.tikz}
+\input{empirics/plots/oos-mse-1b.tikz}
 \caption{\protect \textsc{oos} difference in the \protect\textsc{mse}
@@
     Sink Models of Equity Premium (CT)}
-\includegraphics{empirics/plots/oos-mse-2}
-\includegraphics{empirics/plots/oos-mse-2b}
+\input{empirics/plots/oos-mse-2.tikz}
+\input{empirics/plots/oos-mse-2b.tikz}
 \caption{\protect \textsc{oos} difference in the \protect\textsc{mse}
@@
 \large{OOS MSE of Individual Forecasts of Equity Premium}
-\includegraphics{empirics/plots/oos-ind-ks}
-\includegraphics{empirics/plots/oos-ind-pm}
+\input{empirics/plots/oos-ind-ks.tikz}
+\input{empirics/plots/oos-ind-pm.tikz}
 \caption{\protect{\textsc{oos} \textsc{mse} of the Prevailing Mean (\textsc{pm}) and
@@
 % LocalWords:  anova akritas jong normalpart coefpart Jong's rproject rsqlite
-% LocalWords:  unrestrictive datasets Heyde's ib oos
+% LocalWords:  unrestrictive datasets Heyde's ib oos Mcc MeR StW InK DiM CCS lm
+% LocalWords:  ClM CoS ClW GiW GiR GoW Cla HTF Efr BoB AkA AkP DeD Mcl Dej Rde
+% LocalWords:  Sar Zeh Zei Har CaT NeW MeP HaH AllRefs Diebold jel Whi RoW brc
+% LocalWords:  overrejection overreject fpe JoD iR PeT Giacomini WN Wishart T'V
+% LocalWords:  premultiply const overrejects overrejecting BWB Gia Schwarz HHK
+% LocalWords:  Haf Anatolyev's nonstochastic T'X Sweave tikzDevice pgfSweave

### 2012-03-30 empirics/oos-analysis.R

@@ -2,6 +2,7 @@ library(lattice)
 library(sandwich)
 library(lmtest)
 library(Hmisc)
+library(tikzDevice)
 
 dfull <- ts(read.csv("AllData2009.csv")[,-1],
             start = 1871, frequency = 1)
@@ -95,7 +96,7 @@ oos.ct <- oosStats(tstats.ct)
 
 indplot <- function(name, series, file, height = 2, width = 5.5, xlabel = "",
                     ticks = NULL, labels = TRUE,...) {
-  pdf(file = file, height = height, width = width)
+  tikz(file = file, height = height, width = width)
   par(mar = c(5.1, 4.2, 1.1, 0))
   plot(cbind(series, 0), yaxt = "n", ylab = name,
        plot.type = "single", bty = "n",
@@ -106,16 +107,16 @@ indplot <- function(name, series, file, height = 2, width = 5.5, xlabel = "",
   dev.off()  
 }
 
-indplot(name = "KS", oos[,"KS"], file = "plots/oos-ind-ks.pdf")
-indplot(name = "PM", oos[,"PM"], file = "plots/oos-ind-pm.pdf", xlabel = "R",
+indplot(name = "KS", oos[,"KS"], file = "plots/oos-ind-ks.tikz")
+indplot(name = "PM", oos[,"PM"], file = "plots/oos-ind-pm.tikz", xlabel = "$R$",
         ticks = c(0, .01, .02, .03, .04, 0.05),
         labels = c("0", "", "", "", "", "0.05"))
 
 ## make plots of out-of-sample mse
-## set parameters for pdf images
+## set parameters for  images
 oosplot <- function(series, file, height = 2, width = 5.5, xlabel = "",
                     ticks = NULL, labels = TRUE,...) {
-  pdf(file = file, height = height, width = width)
+  tikz(file = file, height = height, width = width)
   x1 <- sum(is.na(series[,1])) + start(series)[1]
   xn <- end(series)[1]
   par(mar = c(5.1, 4.2, 1.1, 0))
@@ -132,22 +133,22 @@ oosplot <- function(series, file, height = 2, width = 5.5, xlabel = "",
 }
 
 ##Average OOS MSE Difference\nfor OLS Equity Premium Forecasts
[…]

### 2012-03-30 mc-setup.py

@@ -4,9 +4,9 @@
 # makefile, so it might be easiest to just look at its output.
 
 nsims = 2000 # this is the number of simulations
-njobs = 4   # I set this to equal the number of processors on my 
-            # computer.  Changing its value will change the results
-            # of the simulations, since they'll be seeded differently.
+njobs = 7    # I set this to equal the number of processors on my 
+             # computer.  Changing its value will change the results
+             # of the simulations, since they'll be seeded differently.
 def maindb(sql):
     print("\t$(sqlite) $(sqliteFlags) mc/simulations.db \"" + sql + ";\"")
 
@@ -17,7 +17,6 @@ def maindb(sql):
 # corresponding file name.
 dbnames = ["oosstats" + str(i + 1) + "of" + str(njobs) for i in range(njobs)]
 dbfiles = ["mc/db/" + d + ".db" for d in dbnames]
-seeds = range(307, 307 + njobs)
 
 intervaltable = "interval"
 difftable     = "diff"
@@ -64,15 +63,17 @@ makeindex("intervalIndex", "interval (label, idgp)")
 makeview(intervaltable, "select ntest, isim, idgp, transform, label, avg(reject) as reject " +
          "from " + intervaltable + " group by ntest, isim, idgp, transform, label")
 makeview(difftable, "select * from " + difftable)
-makeview(ftesttable, "select isim, idgp, label, avg(reject) as reject from " + ftesttable + " group by isim, idgp, label")
+makeview(ftesttable, "select isim, idgp, label, avg(reject) as reject from " 
+         + ftesttable + " group by isim, idgp, label")
 print "\ttouch $@"
 
 # This is the set of make commands to create the temporary databases.
-for (db, s, n, j) in zip(dbnames, seeds, jsims, range(njobs)):
+for (db, n, j) in zip(dbnames, jsims, range(njobs)):
     print ("mc/db/" + db + ".db: mc/db/oosstats.R mc/db/nobs.created mc/db/coefficients.created\n"
-           + "\techo 'dbname <- \"$@\"; set.seed(" + str(s) + "); "
+           + "\techo 'dbname <- \"$@\"; "
            + "nsim <- " + str(n) + "; " 
-           + ".jobnumber <- " + str(j) + "; "
+           + "jobnumber <- " + str(j+1) + "; "
+           + "njobs <- " + str(njobs) + "; "
            + "intervaltable <- \"" + intervaltable + "\"; "
[…]

### 2012-03-30 mc/db/oosstats.R

@@ -1,7 +1,14 @@
-## The variables nsim and dbname are appended to the beginning of this
-## file before execution.
+## The variables nsim, njobs, jobnumber, and dbname are appended to
+## the beginning of this file before execution.  This code *should*
+## set up random number generation for the parallel processes
+## correctly.
+require(rlecuyer)
+.lec.SetPackageSeed(c(4586, 8197, 5954,   15, 2896, 1839))
+jobnames <- LETTERS[1:njobs]
+.lec.CreateStream(jobnames)
+.lec.CurrentStream(jobnames[jobnumber])
                
-library(fwPackage) ## look here for function definitions.
+require(fwPackage) ## look here for function definitions.
 
 dbmain <- dbConnect(dbDriver("SQLite"), "mc/simulations.db")
 
@@ -84,7 +91,7 @@ initTable <- function(db, tablename, tablefn, remove.table = TRUE) {
   retfn <- function() {
     dbWriteTable(db, tablename,
                  data.frame(do.call("tablefn", as.list(match.call())[-1L]),
-                            jobnumber = as.integer(.jobnumber)),
+                            jobnumber = as.integer(jobnumber)),
                  append = TRUE, row.names = FALSE)
   }
   formals(retfn) <- formals(tablefn)

### 2013-10-18 paper.tex
Move bibtex to external submodule
Add date generation to makefile
Added code to the makefile to display the date of the commit, the branch, and
the commit SHA (all automatically generated by `make ver`) in the date field
and as a running header on every page.
Update theorem and lemma numbering
Switches from Section.number to just number (at editor's request).
Prove testing result on conditional probability
This commit adds a proof of what was Corollary 1, that the conditional
probability of rejection given E_T D_T =< 0 is actually less than or
equal to alpha.  I've also changed it to be listed

@@
 
-\newtheorem{thm}{Theorem}[section]
-\newtheorem{lem}[thm]{Lemma}
-\newtheorem{claim}[thm]{Claim}
-\newtheorem{cor}[thm]{Corollary}
+\pagestyle{myheadings}
+\newtheorem{thm}{Theorem}
+\newtheorem{lem}{Lemma}
+\newtheorem{claim}{Claim}
+\newtheorem{cor}{Corollary}
 \newtheorem{asmp}{Assumption}
@@
 
-%% from http://blog.blubinc.net/
-% Define a command for a given term. This will create a command which gives
-% the long name, with a parenthesised acronym, on the first call.
-% Additionally it will redefine itself to call the acronym function instead
-% on subsequent executions.
-%
-% Takes:
-%	1, command name
-%	2, long name
-%	3, acronym
-% ie \newacronym{ols}{Ordinary Least Squares}{OLS} will define the
-% command \ols
-
+\input{VERSION.tex}
 \title{Out-of-Sample Comparisons of Overfit Models}
@@
     with Ivo Welch \citep{GoW:08}.} \\ Iowa State University}
-\date{October 24, 2011}
 
@@
 pseudo-true models or the unconditional performance of the models.
-This application to testing can be expressed as a corollary:
-\begin{cor}\label{res:oostest}
+This application to testing can be expressed as its own theorem:
+\begin{thm}\label{res:oostest}
 Suppose that the conditions of Theorem \ref{res-confidence-intervals}
-hold.  Then
+hold and that $\lim \Pr[\E_T \oosB \leq 0] > 0$.  Then
 \begin{equation}
-  \lim \Pr[P^{1/2}\oosA/\hat\sigma_R \geq z_{\alpha} \mid \E_{T}
+  \lim \Pr[P^{1/2}\oosA/\hat\sigma_R > z_{\alpha} \mid \E_T
   \oosB \leq 0] \leq \alpha.
 \end{equation}
-\end{cor}
+\end{thm}
 
@@
 \setcounter{section}{1}
+% Change lemma style to prepend 'A'
+\setcounter{lem}{0}
+\renewcommand{\thelem}{A\arabic{lem}}
 
@@
 normal and the second term vanishes.\qed
+
+\subsection*{Proof of Theorem \ref{res:oostest}}
+By Lemma~\ref{res-convergence}, we know that
+\begin{equation*}
+  \Pr[\E_R \oosA \leq 0] - \Pr[\E_T \oosB \leq 0] \to 0
+\end{equation*}
+and
+\begin{equation*}
+  \Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha \text{ and } \E_R \oosA \leq 0]
+  - \Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha \text{ and } 
+  \E_T \oosB \leq 0] \to 0.
+\end{equation*}
+For large enough $T$, both $\Pr[\E_R \oosA \leq 0]$ and $\Pr[\E_T
+\oosB \leq 0]$ are positive, so
+\begin{equation*}
+  \Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha
+  \mid \E_R \oosA \leq 0] = 
+  \frac{\Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha \text{ and }
+    \E_R \oosA \leq 0]}{\Pr[\E_R \oosA \leq 0]}
+\end{equation*}
+and
+\begin{equation*}
+  \Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha
+  \mid \E_T \oosB \leq 0] = 
+  \frac{\Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha \text{ and }
+    \E_T \oosB \leq 0]}{\Pr[\E_T \oosB \leq 0]}
+\end{equation*}
+almost surely and consequently
+\begin{equation*}
+  \Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha
+  \mid \E_T \oosB \leq 0]
+  - \Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha
+  \mid \E_R \oosA \leq 0] \to^p 0.
+\end{equation*}
+Finally,
+\begin{align*}
+  \Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha \mid \E_R \oosA \leq 0]
+  &\leq \Pr[P^{1/2} (\oosA - \E_R \oosA) / \hat\sigma > z_\alpha 
+  \mid \E_R \oosA \leq 0] \\
+  &= \E( \Pr[P^{1/2} (\oosA - \E_R \oosA) / \hat\sigma > z_\alpha 
+  \mid \mathcal{F}_R] \mid \E_R \oosA \leq 0) \\
+  &= \E(\alpha \mid \E_R \oosA \leq 0) \\
+  &= \alpha
+\end{align*}
+where the second equality holds by Lemma~\ref{res-mixingale} and
+Theorem~\ref{res-variance-estimator}, completing the proof.
+\qed
 
@@
 \bibliographystyle{abbrvnat}
-\bibliography{AllRefs}
+\bibliography{texextra/AllRefs}
 

### 2013-10-18 paper.tex
Rewrite introduction of paper
This commit rewrites the introduction as suggested by referee 2 and
by the editor.  Hopefully it is more clear.

@@
   number of observations so that their ratio remains uniformly
-  positive.  Even under this limit theory, the naive
-  Diebold-Mariano-West out-of-sample test can test hypotheses about
-  the models' generalization error, a key quantity for evaluating
-  forecasting models.  Moreover, tests that are designed to reject if
-  the larger model is true, such as the usual in-sample Wald and
-  \textsc{lm} tests and also Clark and McCracken's (2001, 2005a),
-  \citepos{Mcc:07}, and Clark and West's (2006, 2007) out-of-sample
-  statistics, will choose the larger model too often when the smaller
-  model is more accurate. Similar results hold for statistics used for
-  in-sample model selection, such as the \aic, \bic, and adjusted
-  $R$-square.
+  positive.  Our analysis gives a theoretical motivation for using
+  \oos\ comparisons: the \dmw\ \oos\ test allows a forecaster to
+  conduct inference about the expected future accuracy of his or her
+  models when one or both is overfit.  We show analytically and
+  through Monte Carlo that standard full-sample test statistics can
+  not test hypotheses about this performance.  Our paper also shows
+  that popular test and training sample sizes may give misleading
+  results if researchers are concerned about overfit.  We show that
+  $P^2/T$ must converge to zero for the \dmw\ test to give valid
+  inference about the expected forecast accuracy, otherwise the test
+  measures the accuracy of the estimates constructed using only the
+  training sample.  In empirical research, $P$ is typically much
+  larger than this.  Our simulations indicate that using large values
+  of $P$ with the \dmw\ test gives undersized tests with low power, so
+  this practice may favor simple benchmark models too much.
 
@@
 justification for forecasters to use \oos\ instead of in-sample
-comparisons and discover a practical limitation of existing statistics.
+comparisons: the \dmw\ \oos\ test\footnote{In this paper, we will
+  refer to the basic \oos\ $t$-test studied by \citet{DiM:95} and
+  \citet{Wes:96} as the \dmw\ test.} allows a forecaster to conduct
+inference about the expected future accuracy of his or her models when
+one or both is overfit.  We show analytically and through Monte Carlo
+that standard full-sample test statistics can not test hypotheses
+about this performance.
+
+Our paper also shows that popular test and training sample sizes may
+give misleading results if researchers are concerned about overfit.
+We show that $P^2/T$ must converge to zero for the \dmw\ test to give
+valid inference about the expected forecast accuracy, otherwise the
+test measures the accuracy of the estimates constructed using only the
+training sample.  In empirical research, $P$ is typically much larger
+than this.  Our simulations indicate that using large values of $P$
+with the \dmw\ test gives undersized tests with low power, so this
+practice may favor simple benchmark models too much.  Existing
+corrections, proposed by \citet{ClM:01,ClM:05}, \citet{Mcc:07} and
+\citet{ClW:06,ClW:07}, seem to correct too much, though, and reject
+too often when the benchmark model is more accurate.
 
@@
 Finance since \citepos{MeR:83} seminal study of exchange rate models,
-it is unclear from a theoretical perspective whether or not the
+it has been unclear from a theoretical perspective whether or not the
 statistics are useful.  Empirical researchers often cite ``overfit''
@@
 distributions of many popular \oos\ test statistics under conditions
-that would justify these full-sample tests.\footnote{In this paper, we
-  will refer to their basic \oos\ $t$-test as the \dmw\ test.}  Much
+that would justify these full-sample tests.  Much
 of the subsequent research by \citet{Mcc:00, Mcc:07}, \citet{CCS:01},
@@
 and West's assumptions, but maintains the stationarity and dependence
-conditions that permit in-sample comparisons \citep[see][for a recent
+conditions that permit in-sample comparisons \citep[see][for a
 review of this literature]{Wes:06}.\footnote{Like us, \citet{Ana:07}
@@
 asymptotics to study the behavior of \oos\ comparisons when at least
-one of the models is overfit---when the number of its regressors
+one of the models is overfit---the number of its regressors
 increases with the number of observations so that their ratio remains
@@
 models have been, and are continuing to be, developed \citep[see, for
-example,][]{Whi:00,Han:05,RoW:05,HHK:10,ClM:11}, but it is unclear
+example,][]{Whi:00,Han:05,RoW:05,HHK:10,ClM:12b}, but it is unclear
 whether those procedures should themselves use in-sample or \oos\
@@
 conclusions should be true for other models as well.  Under this
-asymptotic theory, the \ols\ coefficient estimator is no longer
+asymptotic theory, where the number of regressors $k$ increases with $T$
+so that $\lim k/T$ is positive,
+the \ols\ coefficient estimator is no longer
 consistent or asymptotically normal \citep{Hub:73} and has positive
-variance in the limit.  Even so, we show that the usual \oos\ average
+variance in the limit.  We show that, even so, the usual \oos\ average
 is asymptotically normal and can consistently estimate the difference
@@
 quantities and should be expected to give different results for
-reasons beyond simple size and power comparisons.  Under our theory,
+reasons beyond simple size and power comparisons.  Under our limit theory,
 the model that is closer to the true \dgp\ in population can forecast
@@
 benchmark is more accurate.\footnote{In a pair of papers similar to
-  ours, \citet{ClM:09b,ClM:12} study in-sample and \oos\ tests that
+  ours, \citet{ClM:12,ClM:12b} study in-sample and \oos\ tests that
   the larger model has nonzero coefficients that are too close to zero
@@
   produce less accurate forecasts.  Moreover, the implications of our
-  asymptotic theories are different and their paper does not provide a
-  reason to do \oos\ comparisons.}
-
-This result justifies \oos\ comparisons when researchers want to
+  asymptotic theories are different and their papers do not provide
+  reasons to do \oos\ comparisons.}
+Also note that, in this situation, a model that performs well
+in-sample can perform badly out-of-sample \emph{even if there are no
+structural breaks or other forms of instability.}  Researchers
+have argued that a breakdown of in-sample forecasting ability
+indicates a structural break (see \citealp{BoH:99} and
+\citealp{StW:03}), but this breakdown can be caused by overfit as
+well.
+
+Our results can justify \oos\ comparisons when researchers want to
 choose a model for forecasting.  Although there has been little
@@
 full sample.  In particular, $P/T \to 0$ is required for consistent
-estimation, and $P^2/T \to 0$ is required for valid confidence
+estimation of the difference in the two models' performance,
+and $P^2/T \to 0$ is required for valid confidence
 intervals and inference.  For larger $P$, the \oos\ comparisons remain
@@
 on non-convergent estimators.  Moreover, transformations of these
-processes also behave like mixingales, so asymptotic results for \ned\
-functions of mixing processes can be used for these \oos\ processes
-with only slight modification.
+processes also behave like mixingales when recentered, so asymptotic
+results for \ned\ functions of mixing processes can be used for these
+\oos\ processes with only slight modification.
 

### 2013-10-23 paper.tex
Make extremly minor tweak to wording in introduction
Add \ep and \eigen macros
This commit introduces some new macros that were helpful in editing Lemma 1's
proof.
- replaces the explicit use of \lambda with an \eigen operator.
- \varepsilon and bolded \varepsilon are pains to type, so we  introduces
  macros for them both.

@@
 \input{macros}
+
+\newcommand{\e}{\varepsilon}
+\newcommand{\eb}{\mathbf{\e}}
+\DeclareMathOperator{\eigen}{\lambda}
 
@@
 indicates a structural break (see \citealp{BoH:99} and
-\citealp{StW:03}), but this breakdown can be caused by overfit as
+\citealp{StW:03} among others), but this breakdown can be caused by overfit as
 well.
@@
 \[
-y_{t+\h} = x_{1t}'\theta_1 + \varepsilon_{1,t+h}, \quad\text{and}\quad
-y_{t+\h} = x_{2t}'\theta_2 + \varepsilon_{2,t+h};
+y_{t+\h} = x_{1t}'\theta_1 + \e_{1,t+h}, \quad\text{and}\quad
+y_{t+\h} = x_{2t}'\theta_2 + \e_{2,t+h};
 \]
@@
 the $L_v$-norm for $L_v$-integrable random variables is $\lVert \cdot
-\rVert_v$.  The functions $\lambda_i(\cdot)$ take a square-matrix
-argument and return its $i$th eigenvalue (with $\lambda_{i}(A) \leq
-\lambda_{i+1}(A)$ for any matrix $A$).  All limits are taken as $T \to
+\rVert_v$.  The functions $\eigen_i(\cdot)$ take a square-matrix
+argument and return its $i$th eigenvalue (with $\eigen_{i}(A) \leq
+\eigen_{i+1}(A)$ for any matrix $A$).  All limits are taken as $T \to
 \infty$ unless stated otherwise.
@@
   \begin{align*}
-    \lVert \lambda_{\max}(X_{iS_{T}}'X_{iS_{T}}) \rVert_{3} &\leq
+    \lVert \eigen_{\max}(X_{iS_{T}}'X_{iS_{T}}) \rVert_{3} &\leq
     S_{T}\, \Delta, & \lVert
-    \lambda_{\max}(X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})
+    \eigen_{\max}(X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})
     \rVert_{3} &\leq S_{T}\, \Delta, \\
-    \lVert \lambda_{\max}((X_{iS_{T}}'X_{iS_{T}})^{-1})
+    \lVert \eigen_{\max}((X_{iS_{T}}'X_{iS_{T}})^{-1})
     \rVert_{3} &\leq \Delta/S_{T}, & \lVert
-    \lambda_{\max}((X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})^{-1})\rVert_{3}
+    \eigen_{\max}((X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})^{-1})\rVert_{3}
     &\leq \Delta/S_{T},
@@
   \text{and} \qquad
-  \ep{iT} = (\varepsilon_{i,1+\h}, \dots, \varepsilon_{i,T})'.\]
+  \ep{iT} = (\e_{i,1+\h}, \dots, \e_{i,T})'.\]
 \end{asmp}
@@
   \hat{\theta}_{2T}^T \\ &=
-  \mathbf{\varepsilon}_T'[\tilde{X}_{2R}(X_{2R}'X_{2R})^{-2}
-  \tilde{X}_{2R} - X_{2T}(X_{2T}'X_{2T})^{-2} X_{2T} ] \mathbf{\varepsilon}_T
+  \eb_T'[\tilde{X}_{2R}(X_{2R}'X_{2R})^{-2}
+  \tilde{X}_{2R} - X_{2T}(X_{2T}'X_{2T})^{-2} X_{2T} ] \eb_T
 \end{align*}
@@
   and rank satisfying $\lim \rank(V_T)/T > 0$.  Then there exist
-  distributions for $(x_t, \varepsilon_{t+h})$ such that
+  distributions for $(x_t, \e_{t+h})$ such that
   \begin{equation}
@@
 Note that, if $V_T$ is nonstochastic or converges in probability,
-there are distributions on $(x_t, \varepsilon_{t+h})$ that are
+there are distributions on $(x_t, \e_{t+h})$ that are
 compatible with~\eqref{eq:15} such that
@@
   and selects the alternative for all $\hat{\theta}_T$ outside that
-  region.  Then there exist distributions on $x_t,\varepsilon_t$ such
+  region.  Then there exist distributions on $x_t,\e_t$ such
   that
@@
 \begin{equation}\label{eq:6}
-  y_t = x_t'\theta + \varepsilon_t,\quad \varepsilon_t \sim N(0,1),
+  y_t = x_t'\theta + \e_t,\quad \e_t \sim N(0,1),
   \quad t=1,\dots,T.
@@
   \label{eq:1}
-  y_{1t} = \sum_{j=1}^{K_1} x_{jt}\theta_j + \varepsilon_t
+  y_{1t} = \sum_{j=1}^{K_1} x_{jt}\theta_j + \e_t
 \end{equation}
@@
 \[
-r_{t+1} = \beta_0 + \beta_1 x_t + \varepsilon_{t+1}
+r_{t+1} = \beta_0 + \beta_1 x_t + \e_{t+1}
 \]
@@
   \label{eq:3}
-  r_{t+1} &=& \mu + \varepsilon_{1,t+1} \\
+  r_{t+1} &=& \mu + \e_{1,t+1} \\
   \label{eq:2}
-r_{t+1} &=& \beta_0 + \sum_{i=1}^K \beta_{i} x_{it} + \varepsilon_{2,t+1}  
+r_{t+1} &=& \beta_0 + \sum_{i=1}^K \beta_{i} x_{it} + \e_{2,t+1}  
 \end{eqnarray}
@@
   \Big(\big\| x_{it}^{*\prime} [(X_{it}'X_{it})^{-1} -
-  (X_{iR}'X_{iR})^{-1}] X_{it}' \mathbf{\varepsilon}_{it} \big\|_2 \\
+  (X_{iR}'X_{iR})^{-1}] X_{it}' \eb_{it} \big\|_2 \\
   &\quad + \big\| x_{it}^{*\prime}
-  (X_{iR}'X_{iR})^{-1}[X_{it}'\mathbf{\varepsilon}_{it} - X_{iR}
-  \mathbf{\varepsilon}_{iR} ] \big\|_2 \Big).
+  (X_{iR}'X_{iR})^{-1}[X_{it}'\eb_{it} - X_{iR}
+  \eb_{iR} ] \big\|_2 \Big).
 \end{align*}
@@
   \big\| x_{it}^{*\prime} [(X_{it}'X_{it})^{-1} &-
-  (X_{iR}'X_{iR})^{-1}] X_{it}' \mathbf{\varepsilon}_{it} \big\|_2 \\
-  &\leq \E \Big| \lambda_{K_i}(X_{it}' \mathbf{\varepsilon}_{it}
-  \mathbf{\varepsilon}_{it}' X_{it})\sum_{t=R+1}^{T-h}
-  \sum_{j=1}^{K_i} \lambda_j^2((X_{iR}'X_{iR})^{-1} -
-  (X_{it}'X_{it})^{-1}) \lambda_{\pi_j}(x_{it}^{*} x_{it}^{*\prime})
+  (X_{iR}'X_{iR})^{-1}] X_{it}' \eb_{it} \big\|_2 \\
+  &\leq \E \Big| \eigen_{K_i}(X_{it}' \eb_{it}
+  \eb_{it}' X_{it})\sum_{t=R+1}^{T-h}
+  \sum_{j=1}^{K_i} \eigen_j^2((X_{iR}'X_{iR})^{-1} -
+  (X_{it}'X_{it})^{-1}) \eigen_{\pi_j}(x_{it}^{*} x_{it}^{*\prime})
   \Big| \\ &\leq \Delta T \Big\| \sum_{t=R+1}^{T-h} \sum_{j=1}^{t-R}
-  \lambda_j^{-2}(X_{iR}'X_{iR}) \lambda_{\pi_j}(x_{it}^{*}
+  \eigen_j^{-2}(X_{iR}'X_{iR}) \eigen_{\pi_j}(x_{it}^{*}
   x_{it}^{*\prime}) \Big\|_{3/2} \\ &\leq \Delta^3 P^2/R
@@
 where $\pi_i,\dots,\pi_{K_i}$ is a permutation of $1,\dots,K_i$.  The
-first equality holds because $\lambda_{\max}(X_{it}'
-\mathbf{\varepsilon}_{it} \mathbf{\varepsilon}_{it} X_{it}) =
+first equality holds because $\eigen_{\max}(X_{it}'
+\eb_{it} \eb_{it} X_{it}) =
 O_{L_{3}}(T)$ by assumption and $(X_{iR}'X_{iR})^{-1} -
@@
   \big\| x_{it}^{*\prime}
-  (X_{iR}'X_{iR})^{-1}[X_{it}'\mathbf{\varepsilon}_{it} - X_{iR}
-  \mathbf{\varepsilon}_{iR} ] \big\|_2 \leq \Delta^3 P^2/R
+  (X_{iR}'X_{iR})^{-1}[X_{it}'\eb_{it} - X_{iR}
+  \eb_{iR} ] \big\|_2 \leq \Delta^3 P^2/R
 \end{equation*}
@@
 $\hat{\theta}_T$ to concentrate on the line joining $\theta$ and
-$\theta_0$.  For any distribution of $(\varepsilon_{t+h}, x_t')$ such
+$\theta_0$.  For any distribution of $(\e_{t+h}, x_t')$ such
 that $\hat{\theta}_T$ depends on $\theta$ only through its mean, the
@@
 \noindent\textit{Equation~\eqref{eq:15}}:  Suppose that
-$(\varepsilon_{t+h}, x_t) \sim i.i.d. N(0,I)$ and condition on $X_T$.
+$(\e_{t+h}, x_t) \sim i.i.d. N(0,I)$ and condition on $X_T$.
 Then the distribution of $\hat{\theta}_{T}$ concentrates uniformly on

### 2013-10-23 paper.tex
Remove references and theory for rolling and recursive windows
The rolling and recursive arguments in the paper are wrong---there is
an eigenvector that shows up when constructing the forecasts associated
with the estimators the blows up and prevents convergence.  This commit
removes that material from the paper.

@@
 
-Both models are estimated using \ols\ with a recursive, fixed, or
-rolling window:
+Both models are estimated using \ols\ with a fixed window:
 \[
-\hat y_{i,t+\h} = x_{it}'\hat{\theta}_{it}^{R}, \qquad i=1,2, \qquad t
+\hat y_{i,t+\h} = x_{it}'\hat{\theta}_{it}, \qquad i=1,2, \qquad t
 = R+1,\dots,T-h
@@
 \begin{equation*}
-  \bh{it}^{R} =  
-  \begin{cases}\big(\sum_{s=1}^{t-\h} x_{is}x_{is}'\big)^{-1}
-    \sum_{s=1}^{t-\h} x_{is} y_{s+\h} & \text{recursive window}\\
-    \big(\sum_{s=t - \h - R}^{t-\h} x_{is}x_{is}'\big)^{-1}
-    \sum_{s=t - \h - R}^{t-\h} x_{is} y_{s+\h} & \text{rolling window}\\
+  \bh{it} =
+  \begin{cases}
     \big(\sum_{s=1}^{R-\h} x_{is}x_{is}'\big)^{-1} \sum_{s=1}^{R-\h}
-    x_{is} y_{s+\h} & \text{fixed window}
+    x_{is} y_{s+\h} & t \leq T \\
+    \big(\sum_{s=1}^{T-\h} x_{is}x_{is}'\big)^{-1}
+    \sum_{s=1}^{T-\h} x_{is} y_{s+\h} & t > T.
   \end{cases}
@@
 \[
-D_{Rt} \equiv L(y_{t+\h} - x_{1t}'\bh{1t}^R) - L(y_{t+\h}
-  - x_{2t}'\bh{2t}^R).
+D_{Rt} \equiv L(y_{t+\h} - x_{1t}'\bh{1t}) - L(y_{t+\h} - x_{2t}'\bh{2t}).
 \]
@@
 \oosB \equiv Q^{-1} \sum_{t=T+1}^{T+Q} D_{Tt}, \quad 
-D_{Tt} \equiv L(y_{t+h} - x_{1t}' \bh{1t}^T) - L(y_{t+h} - x_{2t}' \bh{2t}^T)
+D_{Tt} \equiv L(y_{t+h} - x_{1t}' \bh{1t}) - L(y_{t+h} - x_{2t}' \bh{2t}).
 \]
-and 
-\begin{equation*}
-  \bh{it}^{T} = 
-  \begin{cases} \big(\sum_{s=1}^{t-\h} x_{is}x_{is}'\big)^{-1}
-    \sum_{s=1}^{t-\h} x_{is} y_{s+\h} & \text{recursive window} \\
-    \big(\sum_{s=t - \h - T}^{t-\h} x_{is}x_{is}'\big)^{-1}
-    \sum_{s=t - \h - T}^{t-\h} x_{is} y_{s+\h} & \text{rolling window} \\
-    \big(\sum_{s=1}^{T-\h} x_{is}x_{is}'\big)^{-1} 
-    \sum_{s=1}^{T-\h} x_{is} y_{s+\h} & \text{fixed window}.
-  \end{cases}
-\end{equation*}
 Note that the coefficients are reestimated with the full dataset.
@@
 
-\begin{asmp} \label{asmp-4} $P\to\infty$, $R\to\infty$, and  $P =
-  o(T^{1/2}$) as $T \to \infty$.  For the rolling and recursive
-  windows, $Q = o(T^{1/2})$ as well.
+\begin{asmp} \label{asmp-4} $P, R, Q \to\infty$ and $P^2/T \to 0$ as
+  $T \to \infty$.
 \end{asmp}
@@
 with
-\begin{equation*} \psi(x) = \frac1{\sqrt{2\pi}} \int_{-\infty}^{\infty} W(z) e^{ixz}dz,
+\begin{equation*} 
+  \psi(x) = \frac1{\sqrt{2\pi}} \int_{-\infty}^{\infty} W(z) e^{ixz}dz,
 \end{equation*}
@@
 methods, while we restrict attention to \ols; the advantage of using
-\ols\ is that we can derive the inequality, $$\| x_{it}'
-\theta_{it}^{R} - x_{it}' \theta_{iR}^R \|_2 \leq O(P/T)^{1/2}.$$  Our
-main results will hold for other models as long as a similar
-inequality exists, but proving such inequalities for other models is
+\ols\ is that we can derive the inequality, 
+\begin{equation*}
+  \| x_{it}'\theta_{i,T+1} - x_{it}'\theta_{iR} \|_2 \leq O(P/T)^{1/2}.
+\end{equation*}
+Our main results will hold for other models and estimation windows as
+long as a similar inequality exists, but proving such inequalities is
 left for future research.
@@
 \end{equation}
-The first Lemma shows that the rolling and recursive window statistics
-can be approximated by the fixed window statistic and that
-that~\eqref{coefpart} holds for the fixed window.  The second Lemma
-shows that the process $\{D_{Rt} - \E_R \oosA\}$ is an $L_2$-mixingale
-of size $-1/2$ that satisfies a \clt\ for the fixed window statistic,
-ensuring~\eqref{normalpart}.
-
-\begin{lem} \label{res-convergence} Suppose that Assumptions
-  \ref{asmp-1}--\ref{asmp-4} hold, let $D_{Rt}'$ and $D_{Tt}'$ denote
-  the loss differences associated with the rolling or recursive
-  window, and let $D_{Rt}$ and $D_{Tt}$ those of the fixed window.  Then
-  \begin{equation}
-    \label{eq:8}
-    P^{1/2} (\oosA' - \oosA) \to^p 0, \qquad P^{1/2} (\oosB' - \oosB)
-    \to^p 0,
-  \end{equation}
-  and
+The first Lemma establishes~\eqref{coefpart} and the second shows that
+the process $\{D_{Rt} - \E_R \oosA\}$ is an $L_2$-mixingale of size
+$-1/2$ that satisfies a \clt, ensuring~\eqref{normalpart}.
+
+\begin{lem} \label{res-convergence}
+  Under Assumptions \ref{asmp-1}--\ref{asmp-4},
   \begin{equation}\label{eq:7}
-    \E_T \oosB - \E_R \oosA =  O_p(\sqrt{P/T}) +
-    o_p(P^{-1/2}).
+    \E_T \oosB - \E_R \oosA = O_p(\sqrt{P/T}) + o_p(P^{-1/2} + Q^{-1/2}).
   \end{equation}
@@
 closest to common practice in applied research, the noise term
-dominates the asymptotic distribution of the \oos\ $t$-test, so the
+dominates the asymptotic distribution of the \oos\ $t$-test and the
 test has only trivial power in the limit if it has correct size.
@@
 
-  \noindent Part 2: Moreover,~\eqref{normalpart} holds under the
-  conditions of Part 1 if $P \to \infty$ as $T \to \infty$ and
-  $\sigma_R^2$ is a.s. uniformly positive.
+  \noindent Part 2: Moreover,~\eqref{normalpart} holds under
+  Assumptions~\ref{asmp-1}--\ref{asmp-4} if $\sigma_R^2$ is
+  a.s. uniformly positive.
 \end{lem}
@@
 \begin{lem}
-  \label{res-variance-estimator} Suppose Assumptions \ref{asmp-1},
-  \ref{asmp-2}, \ref{asmp-3}, and \ref{asmp-5} hold, that $\gamma$,
-  $P$, and $R \to \infty$ as $T \to \infty$, and that $\gamma = o(P)$
-  and define
+  \label{res-variance-estimator} Suppose Assumptions
+  \ref{asmp-1}--\ref{asmp-5} hold and that $\gamma \to \infty$ and 
+  $\gamma/P \to 0$ as $T \to \infty$, and define
   \begin{equation*}
@@
 
-Consider the fixed-window estimation scheme, let $L(e) = e^2$, let $h
+Let $L(e) = e^2$, let $h
 = 1$, let the benchmark model have no regressors (i.e. $y_{t+1} \sim$
@@
   Inverse-Wishart distribution.}  Under these conditions,
-\begin{align*}
-  D_{Rt} &= 2 y_{t+1} x_{2t}'\hat{\theta}_{2R}^R -
-  \hat{\theta}_{2R}^{R\prime} (x_{2t} x_{2t}') \hat{\theta}_{2R}^R \\
-  D_{Tt} &= 2 y_{t+1} x_{2t}'\hat{\theta}_{2T}^T -
-  \hat{\theta}_{2T}^{T\prime} (x_{2t} x_{2t}') \hat{\theta}_{2T}^T.
-\end{align*}
-
-The first two moments of $D_{Rt}$ for $t > R$ (conditional
-on $\mathcal{F}_R$) are straightforward to derive:
-$\E_R D_{Rt} = - \hat{\theta}_{2R}^{R\prime} \hat{\theta}_{2R}^R$
-and
+\begin{equation*}
+  D_t =
+  \begin{cases}
+    2 y_{t+1} x_{2t}'\hat{\theta}_{2R} -
+    \hat{\theta}_{2R}' x_{2t} x_{2t}' \hat{\theta}_{2R} & t \leq T \\
+    2 y_{t+1} x_{2t}'\hat{\theta}_{2T} -
+    \hat{\theta}_{2T}' x_{2t} x_{2t}' \hat{\theta}_{2T} & t > T.
+  \end{cases}
+\end{equation*}
+
+The first two conditional moments of $D_t$ for $t > R$ (given
+$\mathcal{F}_R$) are straightforward to derive: $\E_R D_{Rt} = -
+\hat{\theta}_{2R}' \hat{\theta}_{2R}$ and
 \begin{equation*}
@@
 \end{equation*}
-Now, $\hat{\theta}_{2R}^{R\prime} \hat{\theta}_{2R}^R$ is
+Now, $\hat{\theta}_{2R}' \hat{\theta}_{2R}$ is
 a.s. positive and uniformly integrable with mean $4 K_2 / (R - K_2 -
@@
   \Big(y_{t+1} x_{2t} - P^{-1} \sum_{s=R+1}^{T-1} y_s
-  x_{2s}\Big)'\Big] \hat{\theta}_{2R}^{R\prime} \\ & \quad - 4
+  x_{2s}\Big)'\Big] \hat{\theta}_{2R}' \\ & \quad - 4
   \Big[P^{-1} \sum_{t=R+1}^{T-1} \Big(y_{t+1} x_{2t} - P^{-1}
-  \sum_{s=R+1}^{T-1} y_s x_{2s}\Big)' \hat{\theta}_{2R}^{R}
-  \hat{\theta}_{2R}^{R\prime} \Big(x_{2t} x_{2t}' - P^{-1}
-  \sum_{s=R+1}^{T-1} x_{2s} x_{2s}' \Big) \hat{\theta}_{2R}^{R} \Big]
+  \sum_{s=R+1}^{T-1} y_s x_{2s}\Big)' \hat{\theta}_{2R}
+  \hat{\theta}_{2R}' \Big(x_{2t} x_{2t}' - P^{-1}
+  \sum_{s=R+1}^{T-1} x_{2s} x_{2s}' \Big) \hat{\theta}_{2R} \Big]
   \\ &\quad + P^{-1} \sum_{t=R+1}^{T-1}
-  \Big[\hat{\theta}_{2R}^{R\prime} \Big(x_{2t} x_{2t}' - P^{-1}
-  \sum_{s=R+1}^{T-1} x_{2s} x_{2s}' \Big) \hat{\theta}_{2R}^{R}  \Big]^{2}.
+  \Big[\hat{\theta}_{2R}' \Big(x_{2t} x_{2t}' - P^{-1}
+  \sum_{s=R+1}^{T-1} x_{2s} x_{2s}' \Big) \hat{\theta}_{2R}'  \Big]^{2}.
 \end{align*}
@@
 \begin{align*}
-  \E_R \oosA - \E_T \oosB &= \hat{\theta}_{2R}^{R\prime}
-  \hat{\theta}_{2R}^R - \hat{\theta}_{2T}^{T\prime}
-  \hat{\theta}_{2T}^T \\ &=
+  \E_R \oosA - \E_T \oosB &= \hat{\theta}_{2R}'
+  \hat{\theta}_{2R} - \hat{\theta}_{2T}' \hat{\theta}_{2T} \\ &=
   \eb_T'[\tilde{X}_{2R}(X_{2R}'X_{2R})^{-2}
@@
   Suppose Assumptions \ref{asmp-1}--\ref{asmp-3} hold.  Then, for any
-  T, $s$, $t$, $u$, and $w$, with $t \geq s > u \geq w$, there exist random
-  variables $\tilde D_s,\dots,\tilde D_t$ such that
+  T, $s$, and $t$ with $t \geq s$, there exist random variables
+  $\tilde D_s,\dots,\tilde D_t$ such that
   \begin{equation}\label{eq:coupling1}
-    P[(\tilde D_s,\dots,\tilde D_t) \neq (D_{sw},\dots,D_{tw})] \leq \beta_{s-u}
+    P[(\tilde D_s,\dots,\tilde D_t) \neq (D_s,\dots,D_t)] \leq \beta_{s-u}
   \end{equation}
@@
     \int
-    \phi(D_{sw},\dots,D_{tw}) f(\mathbf{x}, \mathbf{y})\ d\mathbf{x}\ d\mathbf{y}
+    \phi(D_s,\dots,D_t) f(\mathbf{x}, \mathbf{y})\ d\mathbf{x}\ d\mathbf{y}
   \end{equation}
@@
  \begin{equation}\label{eq:coupling3}
-   \| \tilde D_v - D_{vw} \|_2 \leq 2^{1+1/\rho} B_L
+   \| \tilde D_v - D_v \|_2 \leq 2^{1+1/\rho} B_L
    \beta_{s-u}^{\rhoExp}, \qquad v = s,\dots,t.
@@
   Now define
-  \[ \tilde D_v \equiv L(y_{v+\h}^* - x_{1v}^{*\prime} \hat{\theta}_w)
-  - L(y_{v+\h}^* - x_{2v}^{*\prime} \hat{\theta}_w), \quad v =
-  s,\dotsc, t,
-  \]
+  \begin{equation*}
+    \tilde D_v =
+    \begin{cases}
+      L(y_{v+\h}^* - x_{1v}^{*\prime} \hat{\theta}_{1R}) - L(y_{v+\h}^* -
+      x_{2v}^{*\prime} \hat{\theta}_{2R}) & v \leq T \\
+      L(y_{v+\h}^* - x_{1v}^{*\prime} \hat{\theta}_{1T}) - L(y_{v+\h}^* -
+      x_{2v}^{*\prime} \hat{\theta}_{2T}) & v > T
+    \end{cases}
+  \end{equation*}
   with $y_{v+\h}^*$ and $x_{iv}^*$ denoting the elements of $V^*$
@@
 \begin{lem}\label{lem:a2}
-  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-3} and that the fixed
-  window scheme is used.  Let $b_T$ be a sequence such that $b_T \to
-  \infty$ and $b_T = o(P)$ and define
+  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-3} hold.  Let $b_T$ be a
+  sequence such that $b_T \to \infty$ and $b_T = o(P)$ and define
   \begin{equation*}
@@
 
-\begin{lem}\label{lem:a3}
-  Suppose that $D_{Rt}'$ denotes loss differences using a rolling or
-  recursive window, and $D_{Rt}$ those using the fixed window and
-  define $\oosA' = P^{-1} \sum_{t=R+1}^{T-h} D_{Rt}'$.  
-  \begin{enumerate}
-  \item Under the assumptions of Theorem~\ref{sec:oostheory},
-    $\var_R(P^{1/2} \oosA') - \var_R(P^{1/2} \oosA) \to^p 0$.
-  \item Under the assumptions of Lemma~\ref{res-variance-estimator},
-    \begin{multline*}
-      P^{-1} \sum_{s,t=R+1}^{T-h} (D_{Rt}' - \oosA') (D_{Rs}' -
-      \oosA') W((t-s)/\gamma) - \\ P^{-1} \sum_{s,t=R+1}^{T-h}
-      (D_{Rt} - \oosA) (D_{Rs} - \oosA) W((t-s)/\gamma) \to^p 0.
-    \end{multline*}
-  \end{enumerate}
-\end{lem}
-\begin{proof}
-  Both follow from Equation~\eqref{eq:8} of Lemma~\ref{res-convergence}.
-\end{proof}
+%\newcommand{\DD}[2][{}]{(D_{#2}^{#1} - \E_R D_{#2}^{#1})}
+%\newcommand{\ovg}[1]{\tfrac{1}{P} \sum_{#1=R+1}^{T-h}}
 
 \begin{lem}\label{lem:a6}
-  Suppose the conditions of Lemma~\ref{res-variance-estimator} hold
-  and that $D_{Rt}$ uses the fixed window.  Then
+  Suppose the conditions of Lemma~\ref{res-variance-estimator} hold.
+  Then
   \begin{equation*}
@@
 \begin{align*}
-P^{-1} \oosSum{s}{1} (\E_R D_{Rs})^2 - (\E_R\oosA)^2 & = 
-P^{-1} \oosSum{s}{1} [(\E_R D_{Rs})^2 - (\E_R\tilde D_s)^2]\\
+P^{-1} \oosSum{s}{1} (\E_R D_s)^2 - (\E_R\oosA)^2 & = 
+P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R\tilde D_s)^2]\\
 &\quad+ \Big(P^{-1} \oosSum{s}{1} \E_R \tilde D_s\Big)^2 - (\E_R\oosA)^2 \quad \text{a.s}.\\
-&= O_p\Big(P^{-1} \oosSum{s}{1} [(\E_R D_{Rs})^2 - (\E_R \tilde D_s)^2]\Big).
+&= O_p\Big(P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R \tilde D_s)^2]\Big).
 \end{align*}
@@
 \begin{align*}
-\Big\lVert P^{-1} \oosSum{s}{1} [(\E_RD_{Rs})^2 - (\E_R \tilde D_s)^2] \Big\rVert_1
-&\leq P^{-1} \oosSum{s}{1} \lVert \E_RD_{Rs} - \E_R \tilde D_s \rVert_2 \lVert
-\E_RD_{Rs} + \E_R \tilde D_s \rVert_2
-\\ &\leq (4 B_L/P) \oosSum{s}{1} \lVert \E_RD_{Rs} - \E_R \tilde D_s \rVert_2,
+\Big\lVert P^{-1} \oosSum{s}{1} [(\E_RD_s)^2 - (\E_R \tilde D_s)^2] \Big\rVert_1
+&\leq P^{-1} \oosSum{s}{1} \lVert \E_RD_s - \E_R \tilde D_s \rVert_2 \lVert
+\E_RD_s + \E_R \tilde D_s \rVert_2
+\\ &\leq (4 B_L/P) \oosSum{s}{1} \lVert \E_RD_s - \E_R \tilde D_s \rVert_2,
 \end{align*}
@@
 
-It suffices to prove asymptotic normality.  Lemma~\ref{lem:a3} and
-Equation~\eqref{eq:8} of Lemma~\ref{res-convergence} let us restrict
-attention to the fixed window statistic.  We can rewrite the centered
-\oos\ average as
+It suffices to prove asymptotic normality.  We can rewrite the
+centered \oos\ average as
 \[
@@
     x_{#1}^{*\prime}\bh{#1R}) - L(y^{*} - x_{#1}^{*\prime}\bh{#1T})}}
-We'll first prove that $P^{1/2} \bar{D}_R' = P^{1/2} \bar{D}_R + o_p$.
-Use Lemma~\ref{lem-berbee} to define $(y_{t+h}^{*}, x_{t}^{*})$ for
-each $t$ so be independent of $\mathcal{F}_R$ and that
-$\Pr[(y_{t+h}^{*}, x_{t}^{*}) \neq (y_{t+h}, x_t)] = \beta_{t-R}$.
-Then
-\begin{multline*}
-  \Big\| P^{-1/2} \sum_{t=R+1}^{T-h} (D_{Rt}' - D_{Rt}) \Big\|_1 = \\
-  \sum_{i=1,2} \Big\| P^{-1/2} \sum_{t=R+1}^{T-h} L(y_{t+h}^{*} -
-  x_{it}^{*\prime} \hat{\theta}_{it}^R) - L(y_{t+h}^{*} -
-  x_{it}^{*\prime} \hat{\theta}_{iR}^R) \Big\|_1  + O\Big(P^{-1/2}
-  \sum_{t=R+1}^{T-h} \beta_{t-R}^{(\rho-2)/2\rho}\Big).
-\end{multline*}
-
-By assumption, $P^{-1/2} \sum_{t=R+1}^{T-h}
-\beta_{t-R}^{(\rho-2)/2\rho} \to 0$.  Smoothness of $L$ and the
-formula for the \ols\ estimator ensures that
-\begin{align*}
-  \Big\|P^{-1/2} \sum_{t=R+1}^{T-h} L(y_{t+h}^{*} - x_{it}^{*\prime}
-  \hat{\theta}_{it}^R) - & L(y_{t+h}^{*} - x_{it}^{*\prime}
-  \hat{\theta}_{iR}^R)\Big\|_1 \\ &\leq B_{L} P^{-1/2}
-  \sum_{t=R+1}^{T-h} \| x_{it}^{*\prime} (\hat{\theta}_{it}^R -
-  \hat{\theta}_{iR}^R) \|_2 \\ &\leq B_{L} P^{-1/2} \sum_{t=R+1}^{T-h}
-  \Big(\big\| x_{it}^{*\prime} [(X_{it}'X_{it})^{-1} -
-  (X_{iR}'X_{iR})^{-1}] X_{it}' \eb_{it} \big\|_2 \\
-  &\quad + \big\| x_{it}^{*\prime}
-  (X_{iR}'X_{iR})^{-1}[X_{it}'\eb_{it} - X_{iR}
-  \eb_{iR} ] \big\|_2 \Big).
-\end{align*}
-  Moreover,
-\begin{align*}
-  \big\| x_{it}^{*\prime} [(X_{it}'X_{it})^{-1} &-
-  (X_{iR}'X_{iR})^{-1}] X_{it}' \eb_{it} \big\|_2 \\
-  &\leq \E \Big| \eigen_{K_i}(X_{it}' \eb_{it}
-  \eb_{it}' X_{it})\sum_{t=R+1}^{T-h}
-  \sum_{j=1}^{K_i} \eigen_j^2((X_{iR}'X_{iR})^{-1} -
-  (X_{it}'X_{it})^{-1}) \eigen_{\pi_j}(x_{it}^{*} x_{it}^{*\prime})
-  \Big| \\ &\leq \Delta T \Big\| \sum_{t=R+1}^{T-h} \sum_{j=1}^{t-R}
-  \eigen_j^{-2}(X_{iR}'X_{iR}) \eigen_{\pi_j}(x_{it}^{*}
-  x_{it}^{*\prime}) \Big\|_{3/2} \\ &\leq \Delta^3 P^2/R
-\end{align*}
-where $\pi_i,\dots,\pi_{K_i}$ is a permutation of $1,\dots,K_i$.  The
-first equality holds because $\eigen_{\max}(X_{it}'
-\eb_{it} \eb_{it} X_{it}) =
-O_{L_{3}}(T)$ by assumption and $(X_{iR}'X_{iR})^{-1} -
-(X_{it}'X_{it})^{-1}$ has rank $t-R$ with eigenvalues bounded by those
-of $(X_{iR}'X_{iR})^{-1}$.  The second holds by independence of
-$x_{it}^{*}$ and $X_{iR}$.  A similar argument proves that
-\begin{equation*}
-  \big\| x_{it}^{*\prime}
-  (X_{iR}'X_{iR})^{-1}[X_{it}'\eb_{it} - X_{iR}
-  \eb_{iR} ] \big\|_2 \leq \Delta^3 P^2/R
-\end{equation*}
-as well, so 
-\begin{equation*}
-  \Big\|P^{-1/2} \sum_{t=R+1}^{T-h} L(y_{t+h}^{*} - x_{it}^{*\prime}
-  \hat{\theta}_{it}^R) -  L(y_{t+h}^{*} - x_{it}^{*\prime}
-  \hat{\theta}_{iR}^R)\Big\|_1 \leq B_L \Delta^{3/2} P / R^{1/2},
-\end{equation*}
-completing the proof. The proof that $P^{1/2} (\bar{D}_T' - \bar{D}_T)
-\to^p 0$ is similar.\footnote{In this proof, $(y_{t+h}^{*}, x_t^{*})$
-  should be defined to be independent of $\mathcal{F}_R$ even for $t >
-  T$.}
-
-Now,~\eqref{eq:7} follows from showing
-\begin{gather*}
-\E_R \oosA = \resConvgRHS{R} + o_p(P^{-1/2}),\\
-\E_T \oosB = \resConvgRHS{T} + o_p(P^{-1/2}),\\
-\resConvgEstDiff{i} = O_p(P^{1/2}/T^{1/2}),
+
+Equation~\eqref{eq:7} holds if we show
+\begin{gather}
+\E_R \oosA = \resConvgRHS{R} + o_p(P^{-1/2}),\label{eq:18}\\
+\E_T \oosB = \resConvgRHS{T} + o_p(Q^{-1/2}),\label{eq:19}
 \intertext{and}
-\resConvgEstDiff{i} = O_p(P^{1/2}/T^{1/2}),
-\end{gather*}
+\resConvgEstDiff{i} = O_p(\sqrt{P/T}),\label{eq:20}
+\end{gather}
 where $\hat\theta_R = (\hat\theta_{1R}, \hat\theta_{2R})$,
@@
 distribution of $(y_{t+\h},x_{1t},x_{2t})$ independently of
-$\mathcal{F}_T$.  The arguments are the same as in the preceding
-proof.\qed
+$\mathcal{F}_T$.
+
+For~\eqref{eq:18}, define $D_t^*$ for each $t=R+1,R+2,\dots,T-h$ so
+that
+\begin{equation*}
+  \| D_t^* - D_{Rt} \|_2 \leq 2^{(1+\rho)/\rho} B_L \beta_{t-R}^{(\rho-2)/2\rho}
+\end{equation*}
+and
+\begin{equation*}
+  \E_R D_t^* = \E(L(y^* - x_1^{*\prime}\hat\theta_{1R}) -
+  L(y^* - x_2^{*\prime}\hat\theta_{2R}) \mid \hat\theta_R) \qquad a.s.
+\end{equation*}
+Lemma~\ref{lem-basic-coupling} ensures that these $D_t^*$ exist.
+Now,
+\begin{align*}
+  \Big\lVert \E_R \oosA - \E\Big(P^{-1} \sum_{t=R+1}^{T-h} D_t^* \mid
+  \hat\theta_R\Big) \Big\rVert_2
+  &= \Big\lVert \E_R\Big( \oosA - P^{-1} \sum_{t=R+1}^{T-h} D_t^*
+  \Big) \Big\rVert_2 \\
+  &= P^{-1} \sum_{t=R+1}^{T-h} \lVert D_{Rt} - D_t^* \rVert_2\\
+  &= O(P^{-1}) \sum_{t=R+1}^{T-h} \beta_{t-R}^{(\rho-2)/2\rho}
+\end{align*}
+and this last term is $o(P^{-1/2})$ by assumption.  Essentially the
+same argument proves~\eqref{eq:19} as well.
+
+For~\eqref{eq:20}, observe that
+\begin{align*}
+  \|L(y^{*} -  x_i^{*\prime} \hat{\theta}_{iR}) -
+  L(y^{*} - x_i^{*\prime} \hat{\theta}_{iT}) \|_1
+  &\leq B_{L} P^{-1/2} \| x_i^{*\prime} (\hat{\theta}_{iR} - \hat{\theta}_{iT}) \|_2 \\
+  &\leq B_{L} P^{-1/2}\big(\| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
+  (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2 \\
+  &\quad+ \| x_i^{*\prime}
+  (X_{iR}'X_{iR})^{-1}[X_{iT}'\eb_{iT} - X_{iR}
+  \eb_{iR} ] \|_2 \big).
+\end{align*}
+The first term in the upper bound satisfies
+\begin{align*}
+  \| x_i^{*\prime} &[(X_{iT}'X_{iT})^{-1} -
+  (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2^2 =\\
+  &= \E \tr\big( x_i^* x_i^{*\prime} X_{iT}'\eb_{iT} \eb_{iT}X_{iT}
+   [(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}]^2 \big) \\
+  &\leq \eigen_{K_i}(\E x_i x_i') \E \Big|  \eigen_{K_i}(X_{iT}' \eb_{iT}
+  \eb_{iT}' X_{iT}) \sum_{j=1}^{K_i} \eigen_j^2((X_{iR}'X_{iR})^{-1} -
+  (X_{iT}'X_{iT})^{-1}) \Big| \\
+  &= O(T) \, \Big\| \sum_{j=1}^{t-R} \eigen_j^{-2}(X_{iR}'X_{iR}) \Big\|_{3/2} \\
+  &= O(P^2/R)
+\end{align*}
+The second equality holds because $\eigen_{K_i}(X_{iT}' \eb_{iT}
+\eb_{iT} X_{iT}) = O_{L_{3}}(T)$ by assumption and
+$(X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}$ has rank $t-R$ with
+eigenvalues bounded by those of $(X_{iR}'X_{iR})^{-1}$.
+
+A similar argument proves that
+\begin{equation*}
+  \big\| x_i^{*\prime} (X_{iR}'X_{iR})^{-1}
+  [X_{iT}'\eb_{iT} - X_{iR} \eb_{iR} ] \big\|_2 \leq \Delta^3 P^2/R
+\end{equation*}
+as well, completing the proof.
+\qed
 
 \subsection*{Proof of Lemma \ref{res-mixingale}}
-We'll only present proofs for the fixed-window; the arguments for the
-rolling and recursive windows are essentially the same.
-
 \noindent \textit{Part 1.} Fix $R$, $j$ and $l$ and use Lemma
@@
 \subsection*{Proof of Lemma \ref{res-variance-estimator}}
-Lemma~\ref{lem:a3} lets us prove the results for the fixed window
-only.  The proof follows \citepos{JoD:00} Theorem 2.1 closely.  We
+The proof follows \citepos{JoD:00} Theorem 2.1 closely.  We
 start by defining similar quantities to theirs, borrowing their
@@
 Their proofs of \eqref{dd1}--\eqref{dd4} use the fact that \ned\
-functions of mixing processes are also mixingale processes, and do not
+functions of mixing processes are also mixingale processes and do not
 use any other properties specific to \ned\ processes, so they hold

### 2013-10-23 paper.tex
Correct assumption on eigenvalues
This commit changes the assumption on the eigenvalues of X'ee'X to focus
on the conditional expectation of the random matrix and not the matrix
itself.

This commit fixes bug #24

@@
 \onehalfspacing
-
 \input{macros}
@@
 The observed \oos\ average is denoted $\oosA$: \[\oosA \equiv P^{-1}
-\oosSum{t}{1} D_{Rt}\]  with
+\oosSum{t}{1} D_t\]  with
 \[
-D_{Rt} \equiv L(y_{t+\h} - x_{1t}'\bh{1t}) - L(y_{t+\h} - x_{2t}'\bh{2t}).
+D_t \equiv L(y_{t+\h} - x_{1t}'\bh{1t}) - L(y_{t+\h} - x_{2t}'\bh{2t}).
 \]
 The \oos\ statistic of interest is $\oost \equiv \sqrt{P} \oosA /
-\hat\sigma_R$, for $\hat\sigma_R^2$ some (possibly Heteroskedasticity- and
+\sh$, for $\sh^2$ some (possibly Heteroskedasticity- and
 Autocorrelation-Consistent, or \hac) estimator of the asymptotic
@@
 \[
-\oosB \equiv Q^{-1} \sum_{t=T+1}^{T+Q} D_{Tt}, \quad 
-D_{Tt} \equiv L(y_{t+h} - x_{1t}' \bh{1t}) - L(y_{t+h} - x_{2t}' \bh{2t}).
+\oosB \equiv Q^{-1} \sum_{t=T+1}^{T+Q} D_t.
 \]
@@
   positive and finite, and all of the eigenvalues of the covariance
-  matrix of $x_t$ are uniformly positive and finite as well.  The
-  Euclidean norms of the pseudo-true coefficients, $\theta_1$ and
-  $\theta_2$, satisfy $|\theta_1|_2 = O(1)$ and $|\theta_2|_2 = O(1)$.
-  Moreover, there exists a finite $\Delta$ such that $\| x_{it}'x_{it}
-  \|_3 \leq K_i \Delta$,
+  matrix of $x_t$ are uniformly positive and finite as well.
+  Moreover,
   \begin{align*}
-    \lVert \eigen_{\max}(X_{iS_{T}}'X_{iS_{T}}) \rVert_{3} &\leq
-    S_{T}\, \Delta, & \lVert
-    \eigen_{\max}(X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})
-    \rVert_{3} &\leq S_{T}\, \Delta, \\
-    \lVert \eigen_{\max}((X_{iS_{T}}'X_{iS_{T}})^{-1})
-    \rVert_{3} &\leq \Delta/S_{T}, & \lVert
-    \eigen_{\max}((X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})^{-1})\rVert_{3}
-    &\leq \Delta/S_{T},
+    &\eigen_{\max}(X_{iS}'X_{iS}) = O_{L_3}(S),&
+    &\eigen_{\max}(\E(X_{iT}'\ep{iT}\ep{iT}'X_{iT}
+    \mid X_{iR}'X_{iR}, X_{iT}'X_{iT})) = O_{L_3}(S),\\
+    &\eigen_{\max}((X_{iS}'X_{iS})^{-1}) = O_{L_3}(1/S),&
+    &\eigen_{\max}\Big(\E\Big( \sum_{s,t=R+1}^{T-h} \e_{is} \e_{it} x_{is}x_{it}'
+    \,\Big|\, X_{iR}'X_{iR} \Big)\Big) = O_{L_3}(P),
   \end{align*}
-  for all $S_{T} \geq K_{2T}$ and large enough $T$, with $i =
-  1,2$,
+  for large enough $T$, where $S = R,T$, $i = 1,2$,
   \[ X_{iT} \equiv [x_{i1} \quad \dots \quad x_{i,T-\h}]' \qquad
-  \text{and} \qquad
-  \ep{iT} = (\e_{i,1+\h}, \dots, \e_{i,T})'.\]
+  \text{and} \qquad \ep{iT} = (\e_{i,1+\h}, \dots, \e_{i,T})'.\]
+  Additionally, the Euclidean norms of the pseudo-true coefficients,
+  $\theta_1$ and $\theta_2$, satisfy $|\theta_1|_2 = O(1)$ and
+  $|\theta_2|_2 = O(1)$.
 \end{asmp}
@@
 
+We can see that these conditions are trivially satisfied when the
+underlying series are i.i.d.\ Normal and the regression includes a
+constant.
+\begin{example}
+  If $(x_{t}, y_t)$ are i.i.d. $N(0, \Sigma)$ where $\Sigma$ is
+  uniformly positive definite, then
+  \begin{equation*}
+    \theta = \cov(y_t, x_t) \var(x_t)^{-1}
+  \end{equation*}
+  and the regression constant is
+  \begin{equation*}
+    \theta_0 = \E y_t - \cov(y_t, x_t) \var(x_t)^{-1} \E x_t
+  \end{equation*}
+  where both of these terms follow directly from the normality
+  assumption.  Then $|\theta|_2 = O(1)$ as a consequence of uniform
+  positive definiteness of $\Sigma$ and $\varepsilon_t \sim i.i.d.\
+  N(0, v^2)$ (independent of $x_t$) with
+  \begin{equation*}
+    v^2 = \var(y_t) - \cov(y_t, x_t) \var(x_t)^{-1} \cov(y_t, x_t)'.
+  \end{equation*}
+  Then we have
+  \begin{equation*}
+    \E(X_{T}'\ep{T}\ep{T}'X_T \mid X_{R}'X_{R}, X_{T}'X_{T})
+    = v^2 X_{T}'X_{T}
+  \end{equation*}
+  and
+  \begin{equation*}
+    \E\Big( \sum_{s,t=R+1}^{T-h} \e_s \e_t x_s x_t'
+    \,\Big|\, X_{R}'X_{R} \Big)\Big) = P v^2 \E x_t x_t'.
+  \end{equation*}
+
+  So the conditions amount to restrictions on the eigenvalues of
+  $X_T'X_T$, which are familiar from general \ols.
+\end{example}
+
 \begin{asmp}\label{asmp-3}
@@
   derivatives almost everywhere.  Also, $L(0) = 0$, and there is a
-  constant $B_L$ such that $\|D_{R,R+j}\|_\rho \leq B_L$ and
-  $\|D_{T,T+j}\|_\rho \leq B_L$ for all $j \geq 1$ ($\rho$ is defined
-  in Assumption~\ref{asmp-1}); $\| x_{it}' \hat{\theta}_{is}^R \|_2 \leq
-  B_L$ and $\| x_{it}' \hat{\theta}_{is}^T \|_2 \leq B_L$; and
+  constant $B_L$ such that $\|D_t\|_\rho \leq B_L$ for all $t$ ($\rho$ is defined
+  in Assumption~\ref{asmp-1}); $\| x_{it}' \hat{\theta}_{it} \|_2 \leq
+  B_L$ and $\| x_{it}' \hat{\theta}_{it} \|_2 \leq B_L$; and
   \begin{equation*}
@@
   for $\tilde{\theta}_{it}$ a weighted average of any two estimates
-  $\hat{\theta}_{is}^R$ and $\hat{\theta}_{is'}^R$ or
-  $\hat{\theta}_{is}^T$ and $\hat{\theta}_{is'}^T$ with $s, s' \leq t$.
+  $\hat{\theta}_{it}$ and $\hat{\theta}_{it'}$.
 \end{asmp}
@@
   Suppose that Assumptions \ref{asmp-1}--\ref{asmp-4} hold, that
-  $\hat\sigma_R^2$ is an estimator satisfying
+  $\sh^2$ is an estimator satisfying
   \[
-    \hat\sigma_R^2 - \sigma_R^2 \to^p 0 \quad \text{with}\quad 
-    \sigma_R^2 \equiv \var_R(\sqrt{P} \oosA) \equiv P \E_R(\bar{D}_R -
+    \sh^2 - \sigma^2 \to^p 0 \quad \text{with}\quad
+    \sigma^2 \equiv \var_R(\sqrt{P} \oosA) \equiv P \E_R(\bar{D}_R -
     \E_R \bar{D}_R)^2,
   \]
-  and that $\sigma_R^2$ is uniformly a.s. positive.  Then
+  and that $\sigma^2$ is uniformly a.s. positive.  Then
   \[
-  \frac{\oosA - \E_T\oosB}{\hat\sigma_R / \sqrt{P}}
+  \frac{\oosA - \E_T\oosB}{\sh / \sqrt{P}}
   \to^d N(0,1).
@@
   \begin{gather}
-  [\oosA - z_{\alpha/2} \, \hat\sigma_R /
-      \sqrt{P}, \oosA + z_{\alpha/2} \hat\sigma_R / \sqrt{P}],\label{interval-twosided} \\
-  [\oosA - z_{\alpha} \, \hat\sigma_R / \sqrt{P}, +\infty), \label{interval-greater}
+  [\oosA - z_{\alpha/2} \, \sh /
+      \sqrt{P}, \oosA + z_{\alpha/2} \sh / \sqrt{P}],\label{interval-twosided} \\
+  [\oosA - z_{\alpha} \, \sh / \sqrt{P}, +\infty), \label{interval-greater}
   \intertext{and}
 (-\infty, \oosA + z_{\alpha}
-      \, \hat\sigma_R / \sqrt{P}],
+      \, \sh / \sqrt{P}],
     \end{gather}
@@
 \end{thm}
-The requirement that $\sigma_R^2$ be uniformly a.s. positive is not
+The requirement that $\sigma^2$ be uniformly a.s. positive is not
 restrictive under our asymptotic theory.  Since the models'
@@
 \begin{equation}
-  \lim \Pr[P^{1/2}\oosA/\hat\sigma_R > z_{\alpha} \mid \E_T
+  \lim \Pr[P^{1/2}\oosA/\sh > z_{\alpha} \mid \E_T
   \oosB \leq 0] \leq \alpha.
@@
 \begin{equation}\label{normalpart}
-  \sqrt{P}\frac{\oosA - \E_R \oosA}{\sigma_R} \to^d N(0,1)
+  \sqrt{P}\frac{\oosA - \E_R \oosA}{\sigma} \to^d N(0,1)
 \end{equation}
 The first Lemma establishes~\eqref{coefpart} and the second shows that
-the process $\{D_{Rt} - \E_R \oosA\}$ is an $L_2$-mixingale of size
+the process $\{D_t - \E_R \oosA\}$ is an $L_2$-mixingale of size
 $-1/2$ that satisfies a \clt, ensuring~\eqref{normalpart}.
@@
 zero.\footnote{Notice that, if the observations are i.i.d. and
-  $(y_{t+h}, x_{it}) \sim N(0,I)$, $(\hat{\theta}_{iR}^R -
-  \hat{\theta}_{iT}^T) \sim N(0, (X_{iR}'X_{iR})^{-1} -
+  $(y_{t+h}, x_{it}) \sim N(0,I)$, $(\hat{\theta}_{iR} -
+  \hat{\theta}_{iT}) \sim N(0, (X_{iR}'X_{iR})^{-1} -
   (X_{iT}'X_{iT})^{-1})$ given $X_{iT}$, and so
-  $\var(x_{i,T+1}'\hat{\theta}_{iR}^R - x_{i,T+1}'
-  \hat{\theta}_{iT}^T) \gg P K_i / (R - K_2)(T - K_2)$.}
+  $\var(x_{i,T+1}'\hat{\theta}_{iR} - x_{i,T+1}'
+  \hat{\theta}_{iT}) \gg P K_i / (R - K_2)(T - K_2)$.}
 Consequently, there is little scope to relax our assumption that
@@
   \begin{equation}\label{mixingaleR}
-    \lVert \E_{R+j-l}(D_{R,R+j} - \E_R D_{R,R+j}) \rVert_2 \leq
-    \couplingConstant \;
-    \zeta_l
+    \lVert \E_{R+j-l}(D_{R+j} - \E_R D_{R+j}) \rVert_2 \leq
+    \couplingConstant \; \zeta_l
   \end{equation}
@@
   $\delta$, any positive $j$, and any $l$ between 0 and $j$.  As a
-  consequence, $\{D_{Rt} - \E_R D_{Rt}, \mathcal F_t\}$ is an
+  consequence, $\{D_t - \E_R D_t, \mathcal F_t\}$ is an
   $L_2$-mixingale of size $-1/2$.
@@
   \noindent Part 2: Moreover,~\eqref{normalpart} holds under
-  Assumptions~\ref{asmp-1}--\ref{asmp-4} if $\sigma_R^2$ is
+  Assumptions~\ref{asmp-1}--\ref{asmp-4} if $\sigma^2$ is
   a.s. uniformly positive.
@@
 Finally, for Theorem \ref{res-confidence-intervals} to be useful, we
-need a consistent estimator of $\sigma_R^2$. Lemma
+need a consistent estimator of $\sigma^2$. Lemma
 \ref{res-variance-estimator} establishes that the usual \oos\ \hac\
@@
   \begin{equation*}
-    \hat{\sigma}_R^2 \equiv P^{-1} \oosSum{s,t}{1} (D_{Rt} - \oosA)(D_{Rs} - \oosA)
+    \sh^2 \equiv P^{-1} \oosSum{s,t}{1} (D_t - \oosA)(D_{Rs} - \oosA)
     \vWeight.
   \end{equation*}
-  Then $\hat{\sigma}_R^2 - \sigma_R^2 \to^p 0$.
+  Then $\sh^2 - \sigma^2 \to^p 0$.
 \end{lem}
@@
 The first two conditional moments of $D_t$ for $t > R$ (given
-$\mathcal{F}_R$) are straightforward to derive: $\E_R D_{Rt} = -
+$\mathcal{F}_R$) are straightforward to derive: $\E_R D_t = -
 \hat{\theta}_{2R}' \hat{\theta}_{2R}$ and
 \begin{equation*}
-  \sigma_R^2 \equiv \E_R(D_{Rt} - \E_R D_{Rt})^2 = 4
-  \hat{\theta}_{2R}^{R\prime} \hat{\theta}_{2R}^{R} +
-  \E_R(\hat{\theta}_{2R}^{R\prime} (I - x_{2t} x_{2t}')
-  \hat{\theta}_{2R}^{R})^2   \geq 4 \hat{\theta}_{2R}^{R\prime}
-  \hat{\theta}_{2R}^R \quad a.s.
+  \sigma^2 \equiv \E_R(D_t - \E_R D_t)^2 = 4
+  \hat{\theta}_{2R}' \hat{\theta}_{2R} +
+  \E_R(\hat{\theta}_{2R}' (I - x_{2t} x_{2t}')
+  \hat{\theta}_{2R})^2   \geq 4 \hat{\theta}_{2R}'
+  \hat{\theta}_{2R} \quad a.s.
 \end{equation*}
@@
 1)$ (since $(X_{2R}'X_{2R})^{-1}$ is Inverse-Wishart$(I_{K_2}, R)$),
-making $\sigma_R^2$ uniformly a.s. positive and ensuring that the
+making $\sigma^2$ uniformly a.s. positive and ensuring that the
 distribution of the \oos\ average is not $P^{1/2}$-degenerate.  The
-natural \oos\ variance estimator is consistent for $\sigma_R^2$:
+natural \oos\ variance estimator is consistent for $\sigma^2$:
 \begin{align*}
-  \hat{\sigma}_R^2 &= P^{-1} \sum_{t=R+1}^{T-1} (D_{Rt} - \oosA)^2 \\
-  &= 4 \hat{\theta}_{2R}^{R\prime} \Big[P^{-1} \sum_{t=R+1}^{T-1}
+  \sh^2 &= P^{-1} \sum_{t=R+1}^{T-1} (D_t - \oosA)^2 \\
+  &= 4 \hat{\theta}_{2R}' \Big[P^{-1} \sum_{t=R+1}^{T-1}
   \Big(y_{t+1} x_{2t} - P^{-1} \sum_{s=R+1}^{T-1} y_s x_{2s}\Big)
@@
   \Big[\hat{\theta}_{2R}' \Big(x_{2t} x_{2t}' - P^{-1}
-  \sum_{s=R+1}^{T-1} x_{2s} x_{2s}' \Big) \hat{\theta}_{2R}'  \Big]^{2}.
+  \sum_{s=R+1}^{T-1} x_{2s} x_{2s}' \Big) \hat{\theta}_{2R}  \Big]^{2}.
 \end{align*}
 As $P \to \infty$, the first term converges in probability to
-$\hat{\theta}_{2R}^{R\prime} \hat{\theta}_{2R}^R$, the second to zero,
-and the third to $\E_R(\hat{\theta}_{2R}^{R\prime}(I - x_{2t}x_{2t}')
-\hat{\theta}_{2R}^R)^2$.  Since the number of regressors prevents
-$\hat{\theta}_{2R}^R$ from converging i.p. to zero (its expected
-value), $\hat{\sigma}_R^2$ does not converge to the unconditional
+$\hat{\theta}_{2R}' \hat{\theta}_{2R}$, the second to zero,
+and the third to $\E_R(\hat{\theta}_{2R}'(I - x_{2t}x_{2t}')
+\hat{\theta}_{2R})^2$.  Since the number of regressors prevents
+$\hat{\theta}_{2R}$ from converging i.p. to zero (its expected
+value), $\sh^2$ does not converge to the unconditional
 variance.
@@
 \begin{equation*}
-  \frac{D_{Rt} - \E_R D_{Rt}}{\sigma_R} =
+  \frac{D_t - \E_R D_t}{\sigma} =
   \frac{2 y_{t} x_{2t}' \hat{\theta}_{2R} +
@@
 with a sequence of constants $\theta_{2R}$ since $\hat{\theta}_{2R}$
-does not converge to a deterministic limit.  But $\sigma_R^{-1}
+does not converge to a deterministic limit.  But $\sigma^{-1}
 \E_t(\oosA - \E_R\oosA) = 0$, making this sequence an
@@
   enough to establish the \clt.} so it obeys a \clt\ as long as
-$\sigma_R^2$ is uniformly a.s. positive, which we have already
+$\sigma^2$ is uniformly a.s. positive, which we have already
 established.  Lemma~\ref{res-mixingale} ensures that the \clt\ holds
@@
 \begin{equation*}
-  [ \oosA - 1.28 \hat{\sigma_R}, \infty) \quad\text{with}\quad
-  \hat\sigma_R^2 = \frac1P \sum_{t=R+1}^T (D_t - \oosA)^{2}
+  [ \oosA - 1.28 \hat{\sigma}, \infty) \quad\text{with}\quad
+  \sh^2 = \frac1P \sum_{t=R+1}^T (D_t - \oosA)^{2}
 \end{equation*}
@@
   T, $s$, and $t$ with $t \geq s$, there exist random variables
-  $\tilde D_s,\dots,\tilde D_t$ such that
+  $D_s^*,\dots,D_t^*$ such that
   \begin{equation}\label{eq:coupling1}
-    P[(\tilde D_s,\dots,\tilde D_t) \neq (D_s,\dots,D_t)] \leq \beta_{s-u}
+    P[(D_s^*,\dots,D_t^*) \neq (D_s,\dots,D_t)] \leq \beta_{s-u}
   \end{equation}
@@
   \begin{equation}\label{eq:coupling2}
-    \E(\phi(\tilde D_s,\dots, \tilde D_t) \mid \mathcal{F}_u ) = 
+    \E(\phi(D_s^*,\dots, D_t^*) \mid \mathcal{F}_u ) =
     \int
@@
  \begin{equation}\label{eq:coupling3}
-   \| \tilde D_v - D_v \|_2 \leq 2^{1+1/\rho} B_L
+   \| D_v^* - D_v \|_2 \leq 2^{1+1/\rho} B_L
    \beta_{s-u}^{\rhoExp}, \qquad v = s,\dots,t.
@@
   \begin{equation*}
-    \tilde D_v =
+    D_v^* =
     \begin{cases}
@@
 establishing half of the mixingale result trivially.  Now fix $i$ and $m >
-0$ and use Lemma \ref{lem-basic-coupling} to define $\tilde{D}_{ts}$
+0$ and use Lemma \ref{lem-basic-coupling} to define $D_{ts}^*$
 for each $t =(2i-2)b_T-P+1,\dots,(2i-1)b_T-P$ and $s =
@@
 \begin{equation*}
- \E_R \tilde D_{ts} = \E_{(2i-2m-1)b_T+R-P} \tilde D_{ts} \quad a.s.
+ \E_R D_{ts}^* = \E_{(2i-2m-1)b_T+R-P} D_{ts}^* \quad a.s.
 \end{equation*}
@@
 \begin{equation*}
-  \lVert \tilde D_{ts} - D_{Rs} \rVert_2 \leq \couplingBound{s - (2i-2m-1)b_T-R+P}.
+  \lVert D_{ts}^* - D_s \rVert_2 \leq \couplingBound{s - (2i-2m-1)b_T-R+P}.
 \end{equation*}
@@
 \begin{equation*}
-  \tilde Z_{1t} = 1/\sqrt{P\gamma} \sum_{l=\vttLower}^{\vttUpper}
-  (\tilde D_{t,t+l+R} - \E_R\tilde D_{t,t+l+R})\ W(l/\gamma), \\
+  Z_{1t}^* = 1/\sqrt{P\gamma} \sum_{l=\vttLower}^{\vttUpper}
+  (D_{t,t+l+R}^* - \E_R D_{t,t+l+R}^*)\ W(l/\gamma), \\
 \end{equation*}
@@
 \begin{equation*}
-\tilde Z_{2t} = 1/\sqrt{P\gamma} \sum_{j=\vttLower}^{\vttUpper}
-    (\tilde D_{t,t+l+R} - \E_R\tilde D_{t,t+l+R})\ \kernelB{j/\gamma}.
+Z_{2t}^* = 1/\sqrt{P\gamma} \sum_{j=\vttLower}^{\vttUpper}
+    (D_{t,t+l+R}^* - \E_R D_{t,t+l+R}^*)\ \kernelB{j/\gamma}.
 \end{equation*}
@@
   &= \vtSuma \lVert \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
-  &\quad - \E(\tilde{Z}_{1t}\tilde{Z}_{2t} \mid \UFiltration{2i-2m-1}) \\
-  &\quad + \E(\tilde{Z}_{1t}\tilde{Z}_{2t} \mid \UFiltration{2i-2m-1})
+  &\quad - \E(Z_{1t}^* Z_{2t}^* \mid \UFiltration{2i-2m-1}) \\
+  &\quad + \E(Z_{1t}^* Z_{2t}^* \mid \UFiltration{2i-2m-1})
   - \E_R Z_{1t}Z_{2t} \rVert_2 \\
 %  \leq \vtSuma (\wall \lVert \wall \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
-%  - \E(\tilde{Z}_{1t}\tilde{Z}_{2t} \mid \UFiltration{2i-2m-1}) \rVert_2\return
-%  \\ + \lVert \E_R Z_{1t}Z_{2t} - \E_R \tilde{Z}_{1t}\tilde{Z}_{2t}
+%  - \E(Z_{1t}^*Z_{2t}^* \mid \UFiltration{2i-2m-1}) \rVert_2\return
+%  \\ + \lVert \E_R Z_{1t}Z_{2t} - \E_R Z_{1t}^*Z_{2t}^*
 %  \rVert_2)\return \\
-  &\leq 2 \vtSuma \lVert Z_{1t} Z_{2t} - \tilde Z_{1t} \tilde{Z}_{2t}
+  &\leq 2 \vtSuma \lVert Z_{1t} Z_{2t} - Z_{1t}^* Z_{2t}^*
   \rVert_2 \\
-  &\leq 2 \vtSuma (\lVert Z_{1t} - \tilde{Z}_{1t} \rVert_2 \lVert
+  &\leq 2 \vtSuma (\lVert Z_{1t} - Z_{1t}^* \rVert_2 \lVert
   Z_{2t} \rVert_{\infty}
-  + \lVert Z_{2t} - \tilde{Z}_{2t} \rVert_2 \lVert \tilde{Z}_{1t} \rVert_{\infty}) \\
-  &\leq \frac{2 C b_T^{1/2}}{(P\gamma)^{1/2}} \vtSuma (\lVert Z_{1t} - \tilde{Z}_{1t} \rVert_2 
-  + \lVert Z_{2t} - \tilde{Z}_{2t} \rVert_2).
+  + \lVert Z_{2t} - Z_{2t}^* \rVert_2 \lVert Z_{1t}^* \rVert_{\infty}) \\
+  &\leq \frac{2 C b_T^{1/2}}{(P\gamma)^{1/2}} \vtSuma (\lVert Z_{1t} - Z_{1t}^* \rVert_2
+  + \lVert Z_{2t} - Z_{2t}^* \rVert_2).
 \end{align*}
@@
 \begin{align*}
-  \frac{2 C b_T^{1/2}}{(P \gamma)^{1/2}} &\vtSuma \lVert Z_{1t} - \tilde{Z}_{1t} \rVert_2 \\& \leq
+  \frac{2 C b_T^{1/2}}{(P \gamma)^{1/2}} &\vtSuma \lVert Z_{1t} - Z_{1t}^* \rVert_2 \\& \leq
   \frac{4C b_T^{1/2}}{P\gamma} \vtSuma \sum_{l=\vttLower}^{\vttUpper} \lVert
-  D_{t+l+R,R} - \tilde{D}_{t,t+l+R} \rVert_2 W(l/\gamma) \\&
+  D_{t+l+R,R} - D_{t,t+l+R}^* \rVert_2 W(l/\gamma) \\&
   \leq O\Bigg(\frac{b_T^{1/2}}{P\gamma}\Bigg) \vtSuma
@@
   \begin{equation*}
-    \hat{\sigma}_R^2 - P^{-1} \sum_{s,t=R+1}^{T-h} (D_{Rs} - \E_R
-    D_{Rs}) (D_{Rt} - \E_R D_{Rt}) W((t-s)/\gamma) \to^{L_1} 0.
+    \sh^2 - P^{-1} \sum_{s,t=R+1}^{T-h} (D_s - \E_R
+    D_s) (D_t - \E_R D_t) W((t-s)/\gamma) \to^{L_1} 0.
   \end{equation*}
@@
 \begin{multline*}
-  \Big| \hat\sigma_R^2 -  P^{-1} \sum_{s,t=R+1}^{T-h} (D_{Rs} - \E_R
-    D_{Rs}) (D_{Rt} - \E_R D_{Rt}) W((t-s)/\gamma) \Big| \leq\\
-  \varianceDiffA \\ + P^{-1} \oosSum{s,t}{1} \lvert (D_{Rs} -
-  \oosA)(\E_R D_{Rt} - \oosA) \rvert \vWeight + o_p(1).
+  \Big| \sh^2 -  P^{-1} \sum_{s,t=R+1}^{T-h} (D_s - \E_R
+    D_s) (D_t - \E_R D_t) W((t-s)/\gamma) \Big| \leq\\
+  \varianceDiffA \\ + P^{-1} \oosSum{s,t}{1} \lvert (D_s -
+  \oosA)(\E_R D_t - \oosA) \rvert \vWeight + o_p(1).
 \end{multline*}
@@
 Now,
-$P^{-1} \oosSum{s}{1}(D_{Rs} - \E_R D_{Rs})^2 = O_p(1)$, and it suffices to prove
+$P^{-1} \oosSum{s}{1}(D_s - \E_R D_s)^2 = O_p(1)$, and it suffices to prove
 that \[\varianceDiffAi = o_p(1).\]  Observe that
 \begin{align*}
-  \varianceDiffAi & = O_p\Big(P^{-1} \oosSum{s}{1}(\E_{R}D_{Rs} -
+  \varianceDiffAi & = O_p\Big(P^{-1} \oosSum{s}{1}(\E_{R}D_s -
   \E_R\oosA)^2\Big) + O_p(\oosA - \E_R\oosA)^{2} \\
-  &= O_p\Big(P^{-1} \oosSum{s}{1} (\E_RD_{Rs})^2 - (\E_R\oosA)^2\Big) +
+  &= O_p\Big(P^{-1} \oosSum{s}{1} (\E_RD_s)^2 - (\E_R\oosA)^2\Big) +
   o_p(1),
@@
 
-Now define $\tilde D_s$, $s = R+1,\dots,T-\h$, as in Lemma
-\ref{lem-basic-coupling} so that $\E_{s-1} \tilde D_s = \E_R \tilde
-D_s$ almost surely.  Note that we also have the equality $\E_R \tilde
-D_s = \E_R \tilde D_{R+1}$ almost surely for all $s\geq R+1$, and so
+Now define $D_s^*$, $s = R+1,\dots,T-\h$, as in Lemma
+\ref{lem-basic-coupling} so that $\E_{s-1} D_s^* = \E_R D_s^*$ almost
+surely.  Note that we also have the equality $\E_R D_s^* = \E_R
+D_{R+1}^*$ almost surely for all $s\geq R+1$, and so
 \[
-P^{-1} \oosSum{s}{1} (\E_R \tilde D_s)^2 = \Big(P^{-1} \oosSum{s}{1} \E_R
-\tilde D_s\Big)^2 \quad \text{a.s..}
+P^{-1} \oosSum{s}{1} (\E_R D_s^*)^2 = \Big(P^{-1} \oosSum{s}{1} \E_R
+D_s^*\Big)^2 \quad \text{a.s..}
 \]
@@
 P^{-1} \oosSum{s}{1} (\E_R D_s)^2 - (\E_R\oosA)^2 & =
-P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R\tilde D_s)^2]\\
-&\quad+ \Big(P^{-1} \oosSum{s}{1} \E_R \tilde D_s\Big)^2 - (\E_R\oosA)^2 \quad \text{a.s}.\\
-&= O_p\Big(P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R \tilde D_s)^2]\Big).
+P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R D_s^*)^2]\\
+&\quad+ \Big(P^{-1} \oosSum{s}{1} \E_R D_s^*\Big)^2 - (\E_R\oosA)^2 \quad \text{a.s}.\\
+&= O_p\Big(P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R D_s^*)^2]\Big).
 \end{align*}
@@
 \begin{align*}
-\Big\lVert P^{-1} \oosSum{s}{1} [(\E_RD_s)^2 - (\E_R \tilde D_s)^2] \Big\rVert_1
-&\leq P^{-1} \oosSum{s}{1} \lVert \E_RD_s - \E_R \tilde D_s \rVert_2 \lVert
-\E_RD_s + \E_R \tilde D_s \rVert_2
-\\ &\leq (4 B_L/P) \oosSum{s}{1} \lVert \E_RD_s - \E_R \tilde D_s \rVert_2,
+\Big\lVert P^{-1} \oosSum{s}{1} [(\E_RD_s)^2 - (\E_R D_s^*)^2] \Big\rVert_1
+&\leq P^{-1} \oosSum{s}{1} \lVert \E_RD_s - \E_R D_s^* \rVert_2 \lVert
+\E_RD_s + \E_R D_s^* \rVert_2
+\\ &\leq (4 B_L/P) \oosSum{s}{1} \lVert \E_RD_s - \E_R D_s^* \rVert_2,
 \end{align*}
@@
 \[
-\frac{\bar{D}_{R} - \E_T \bar{D}_T}{\hat\sigma_R / \sqrt{P}} =
-\frac{1}{\hat\sigma_R \sqrt{P}}\oosSum{t}{1} (D_{Rt} - \E_R D_{Rt}) +
-\frac{\sqrt{P}}{\hat\sigma_R} (\E_R\oosA - \E_T\oosB).
+\frac{\bar{D}_{R} - \E_T \bar{D}_T}{\sh / \sqrt{P}} =
+\frac{1}{\sh \sqrt{P}}\oosSum{t}{1} (D_t - \E_R D_t) +
+\frac{\sqrt{P}}{\sh} (\E_R\oosA - \E_T\oosB).
 \]
@@
 \begin{equation*}
-  \Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha \text{ and } \E_R \oosA \leq 0]
-  - \Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha \text{ and } 
+  \Pr[P^{1/2} \oosA / \sh > z_\alpha \text{ and } \E_R \oosA \leq 0]
+  - \Pr[P^{1/2} \oosA / \sh > z_\alpha \text{ and }
   \E_T \oosB \leq 0] \to 0.
@@
 \begin{equation*}
-  \Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha
+  \Pr[P^{1/2} \oosA / \sh > z_\alpha
   \mid \E_R \oosA \leq 0] =
-  \frac{\Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha \text{ and }
+  \frac{\Pr[P^{1/2} \oosA / \sh > z_\alpha \text{ and }
     \E_R \oosA \leq 0]}{\Pr[\E_R \oosA \leq 0]}
@@
 \begin{equation*}
-  \Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha
+  \Pr[P^{1/2} \oosA / \sh > z_\alpha
   \mid \E_T \oosB \leq 0] =
-  \frac{\Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha \text{ and }
+  \frac{\Pr[P^{1/2} \oosA / \sh > z_\alpha \text{ and }
     \E_T \oosB \leq 0]}{\Pr[\E_T \oosB \leq 0]}
@@
 \begin{equation*}
-  \Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha
+  \Pr[P^{1/2} \oosA / \sh > z_\alpha
   \mid \E_T \oosB \leq 0]
-  - \Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha
+  - \Pr[P^{1/2} \oosA / \sh > z_\alpha
   \mid \E_R \oosA \leq 0] \to^p 0.
@@
 \begin{align*}
-  \Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha \mid \E_R \oosA \leq 0]
-  &\leq \Pr[P^{1/2} (\oosA - \E_R \oosA) / \hat\sigma > z_\alpha 
+  \Pr[P^{1/2} \oosA / \sh > z_\alpha \mid \E_R \oosA \leq 0]
+  &\leq \Pr[P^{1/2} (\oosA - \E_R \oosA) / \sh > z_\alpha
   \mid \E_R \oosA \leq 0] \\
-  &= \E( \Pr[P^{1/2} (\oosA - \E_R \oosA) / \hat\sigma > z_\alpha 
+  &= \E( \Pr[P^{1/2} (\oosA - \E_R \oosA) / \sh > z_\alpha
   \mid \mathcal{F}_R] \mid \E_R \oosA \leq 0) \\
@@
 \begin{equation*}
-  \| D_t^* - D_{Rt} \|_2 \leq 2^{(1+\rho)/\rho} B_L \beta_{t-R}^{(\rho-2)/2\rho}
+  \| D_t^* - D_t \|_2 \leq 2^{(1+\rho)/\rho} B_L \beta_{t-R}^{(\rho-2)/2\rho}
 \end{equation*}
@@
   \Big) \Big\rVert_2 \\
-  &= P^{-1} \sum_{t=R+1}^{T-h} \lVert D_{Rt} - D_t^* \rVert_2\\
+  &= P^{-1} \sum_{t=R+1}^{T-h} \lVert D_t - D_t^* \rVert_2\\
   &= O(P^{-1}) \sum_{t=R+1}^{T-h} \beta_{t-R}^{(\rho-2)/2\rho}
@@
   L(y^{*} - x_i^{*\prime} \hat{\theta}_{iT}) \|_1
-  &\leq B_{L} P^{-1/2} \| x_i^{*\prime} (\hat{\theta}_{iR} - \hat{\theta}_{iT}) \|_2 \\
-  &\leq B_{L} P^{-1/2}\big(\| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
+  &\leq B_{L} \| x_i^{*\prime} (\hat{\theta}_{iR} - \hat{\theta}_{iT}) \|_2 \\
+  &\leq B_{L} \big(\| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
   (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2 \\
@@
   (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2^2 =\\
-  &= \E \tr\big( x_i^* x_i^{*\prime} X_{iT}'\eb_{iT} \eb_{iT}X_{iT}
-   [(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}]^2 \big) \\
-  &\leq \eigen_{K_i}(\E x_i x_i') \E \Big|  \eigen_{K_i}(X_{iT}' \eb_{iT}
-  \eb_{iT}' X_{iT}) \sum_{j=1}^{K_i} \eigen_j^2((X_{iR}'X_{iR})^{-1} -
-  (X_{iT}'X_{iT})^{-1}) \Big| \\
-  &= O(T) \, \Big\| \sum_{j=1}^{t-R} \eigen_j^{-2}(X_{iR}'X_{iR}) \Big\|_{3/2} \\
-  &= O(P^2/R)
+  &= \E \tr\big( x_i^* x_i^{*\prime}
+   [(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}] X_{iT}'\eb_{iT} \eb_{iT}X_{iT}
+   [(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}] \big) \\
+  &\leq \eigen_{K_i}(\E x_i x_i')
+  \, \| \eigen_{K_i}(\E(X_{iT}' \eb_{iT} \eb_{iT}' X_{iT} \mid
+  X_{iR}'X_{iR}, X_{iT}'X_{iT})) \|_3 \\
+  & \quad \times \Big\|\sum_{j=1}^{K_i}
+  \eigen_j^2((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}) \Big\|_{3/2}
 \end{align*}
-The second equality holds because $\eigen_{K_i}(X_{iT}' \eb_{iT}
-\eb_{iT} X_{iT}) = O_{L_{3}}(T)$ by assumption and
-$(X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}$ has rank $t-R$ with
-eigenvalues bounded by those of $(X_{iR}'X_{iR})^{-1}$.
+
+By Assumption~\ref{asmp-2},
+\begin{equation*}
+  \eigen_{K_i}(\E(X_{iT}' \eb_{iT} \eb_{iT}' X_{iT} \mid
+  X_{iR}'X_{iR}, X_{iT}'X_{iT})) = O_{L_3}(T).
+\end{equation*}
+Also, $(X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}$ has rank $P$ and
+its eigenvalues are bounded by those of $(X_{iR}'X_{iR})^{-1}$, which
+are $O_{L_2}(1/R)$ by Assumption~\ref{asmp-2} as well, so
+\begin{align*}
+  \Big\|\sum_{j=1}^{K_i}
+  \eigen_j^2\big((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}\big)\Big\|_{3/2}
+  &\leq \Big\|\sum_{j=K_i - P+1}^{K_i}
+  \eigen_j^2\big((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}\big) \Big\|_{3/2} \\
+  &= O(P/R^2)
+\end{align*}
+proving that
+\begin{equation*}
+  \| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
+  (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2 = O(\sqrt{P/R}).
+\end{equation*}
 
@@
   \big\| x_i^{*\prime} (X_{iR}'X_{iR})^{-1}
-  [X_{iT}'\eb_{iT} - X_{iR} \eb_{iR} ] \big\|_2 \leq \Delta^3 P^2/R
-\end{equation*}
-as well, completing the proof.
+  [X_{iT}'\eb_{iT} - X_{iR} \eb_{iR} ] \big\|_2 =  O(\sqrt{P/R}),
+\end{equation*}
+completing the proof.
 \qed
@@
 \noindent \textit{Part 1.} Fix $R$, $j$ and $l$ and use Lemma
-\ref{lem-basic-coupling} to define $\tilde{D}_{R+j}$ so that
-\[\E_R\tilde D_{R+j} = \E_{R+j-l} \tilde D_{R+j} \quad a.s. \]
+\ref{lem-basic-coupling} to define $D_{R+j}^*$ so that
+\[\E_RD_{R+j}^* = \E_{R+j-l} D_{R+j}^* \quad a.s. \]
 and
-\[\lVert D_{R+j,R} - \tilde D_{R+j} \rVert_2 \leq \couplingBound{l}.\]
+\[\lVert D_{R+j} - D_{R+j}^* \rVert_2 \leq \couplingBound{l}.\]
 Then
 \begin{align*}
-\lVert \E_{R+j-l} D_{R+j,R} - \E_R D_{R+j,R} \rVert_2 & \leq 
-\lVert \E_{R+j-l} D_{R+j,R} - \E_{R+j-l} \tilde{D}_{R+j} \rVert_2 \\
+\lVert \E_{R+j-l} D_{R+j} - \E_R D_{R+j} \rVert_2 & \leq
+\lVert \E_{R+j-l} D_{R+j} - \E_{R+j-l} D_{R+j}^* \rVert_2 \\
 &\quad + \lVert
-\E_{R+j-l} \tilde{D}_{R+j} - \E_R D_{R+j,R} \rVert_2 \\
-&\leq 2 \lVert D_{R+j,R} - \tilde D_{R+j} \rVert_2 \\
+\E_{R+j-l} D_{R+j}^* - \E_R D_{R+j} \rVert_2 \\
+&\leq 2 \lVert D_{R+j} - D_{R+j}^* \rVert_2 \\
 &\leq 2^{2 + 1/\rho}\ B_L\ \couplingBeta{l}.
@@
 \begin{equation*}
-   \SumOuterBlock{i} Z_i = P^{-1/2} \oosSum{s}{1} (D_{Rt} - \E_R D_{Rt}) + o_p(1).
+   \SumOuterBlock{i} Z_i = P^{-1/2} \oosSum{s}{1} (D_t - \E_R D_t) + o_p(1).
 \end{equation*}
@@
 \mds\ by construction, so \citepos{HaH:80} Theorem 3.2 and Corollary
-3.1 ensure that $\sigma_R^{-1} \SumOuterBlock{i} Z_i \to^d N(0,1) $ as
+3.1 ensure that $\sigma^{-1} \SumOuterBlock{i} Z_i \to^d N(0,1) $ as
 long as
 \begin{equation}\label{eq:cltvar2}
-  \sigma_R^2 - \SumOuterBlock{i} \E_R Z_i^2 \to^p 0,
+  \sigma^2 - \SumOuterBlock{i} \E_R Z_i^2 \to^p 0,
 \end{equation}
@@
 \begin{equation}\label{eq:cltvar1}
-  \SumOuterBlock{i} \E_R Z_i^2 - \SumOuterBlock{i} \ZSqCE \to^p 0.\footnote{Note that $\sigma_R^2 \in \mathcal{F}_t$ for
+  \SumOuterBlock{i} \E_R Z_i^2 - \SumOuterBlock{i} \ZSqCE \to^p 0.\footnote{Note that $\sigma^2 \in \mathcal{F}_t$ for
     all $t \geq R$, so Hall and Heyde's condition (3.21) is
@@
 \begin{align*}
-  \lVert \hat\sigma_R^2 - \sigma_R^2 \rVert_1 &
-  \leq \lVert \hat\sigma_R^2 - \varianceTermI \rVert_1 
+  \lVert \sh^2 - \sigma^2 \rVert_1 &
+  \leq \lVert \sh^2 - \varianceTermI \rVert_1
   + \lVert \varianceTermI - \varianceTermII \rVert_1
@@
   + \lVert \E_R\varianceTermI - \E_R\varianceTermII \rVert_1
-  + \lVert \E_R \varianceTermI - \sigma_R^2 \rVert_1
+  + \lVert \E_R \varianceTermI - \sigma^2 \rVert_1
   \\ &
-  \leq  \lVert \hat\sigma_R^2 - \varianceTermI \rVert_1 
+  \leq  \lVert \sh^2 - \varianceTermI \rVert_1
   + 2(\lVert \varianceTermI - \varianceTermII \rVert_1
@@
   & \quad + \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1
-  + \lVert \E_R \varianceTermI - \sigma_R^2 \rVert_1.
+  + \lVert \E_R \varianceTermI - \sigma^2 \rVert_1.
 \end{align*}
@@
 \begin{equation} \label{dd4}
-\lim \lVert \E_R \varianceTermI - \sigma_R^2 \rVert_1 = 0.
+\lim \lVert \E_R \varianceTermI - \sigma^2 \rVert_1 = 0.
 \end{equation}
@@
 \begin{equation}
-  \label{eq:4} \lVert \hat{\sigma}_R^2 - \varianceTermI \rVert_1 \to 0
+  \label{eq:4} \lVert \sh^2 - \varianceTermI \rVert_1 \to 0
 \end{equation}

### 2013-10-23 paper.tex
Fix scale factor in proof of convergence of centering terms
The exisitng proof of Lemma 1, convergence of the centering terms, has
an incorrect scale term P^{-1/2}; this commit removes it.

@@
   positive and finite, and all of the eigenvalues of the covariance
-  matrix of $x_t$ are uniformly positive and finite as well.
-  Moreover,
+  matrix of $x_t$ are uniformly positive and finite as well.  The
+  Euclidean norms of the pseudo-true coefficients, $\theta_1$ and
+  $\theta_2$, satisfy $|\theta_1|_2 = O(1)$ and $|\theta_2|_2 = O(1)$.
+  Moreover, there exists a finite $\Delta$ such that $\| x_{it}'x_{it}
+  \|_3 \leq K_i \Delta$,
   \begin{align*}
-    &\eigen_{\max}(X_{iS}'X_{iS}) = O_{L_3}(S),&
-    &\eigen_{\max}(\E(X_{iT}'\ep{iT}\ep{iT}'X_{iT}
-    \mid X_{iR}'X_{iR}, X_{iT}'X_{iT})) = O_{L_3}(S),\\
-    &\eigen_{\max}((X_{iS}'X_{iS})^{-1}) = O_{L_3}(1/S),&
-    &\eigen_{\max}\Big(\E\Big( \sum_{s,t=R+1}^{T-h} \e_{is} \e_{it} x_{is}x_{it}'
-    \,\Big|\, X_{iR}'X_{iR} \Big)\Big) = O_{L_3}(P),
+    \lVert \eigen_{\max}(X_{iS_{T}}'X_{iS_{T}}) \rVert_{3} &\leq
+    S_{T}\, \Delta, & \lVert
+    \eigen_{\max}(X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})
+    \rVert_{3} &\leq S_{T}\, \Delta, \\
+    \lVert \eigen_{\max}((X_{iS_{T}}'X_{iS_{T}})^{-1})
+    \rVert_{3} &\leq \Delta/S_{T}, & \lVert
+    \eigen_{\max}((X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})^{-1})\rVert_{3}
+    &\leq \Delta/S_{T},
   \end{align*}
-  for large enough $T$, where $S = R,T$, $i = 1,2$,
+  for all $S_{T} \geq K_{2T}$ and large enough $T$, with $i =
+  1,2$,
   \[ X_{iT} \equiv [x_{i1} \quad \dots \quad x_{i,T-\h}]' \qquad
-  \text{and} \qquad \ep{iT} = (\e_{i,1+\h}, \dots, \e_{i,T})'.\]
-  Additionally, the Euclidean norms of the pseudo-true coefficients,
-  $\theta_1$ and $\theta_2$, satisfy $|\theta_1|_2 = O(1)$ and
-  $|\theta_2|_2 = O(1)$.
+  \text{and} \qquad
+  \ep{iT} = (\e_{i,1+\h}, \dots, \e_{i,T})'.\]
 \end{asmp}
@@
 variance of $y_{t+\h}$ in the limit.
-
-We can see that these conditions are trivially satisfied when the
-underlying series are i.i.d.\ Normal and the regression includes a
-constant.
-\begin{example}
-  If $(x_{t}, y_t)$ are i.i.d. $N(0, \Sigma)$ where $\Sigma$ is
-  uniformly positive definite, then
-  \begin{equation*}
-    \theta = \cov(y_t, x_t) \var(x_t)^{-1}
-  \end{equation*}
-  and the regression constant is
-  \begin{equation*}
-    \theta_0 = \E y_t - \cov(y_t, x_t) \var(x_t)^{-1} \E x_t
-  \end{equation*}
-  where both of these terms follow directly from the normality
-  assumption.  Then $|\theta|_2 = O(1)$ as a consequence of uniform
-  positive definiteness of $\Sigma$ and $\varepsilon_t \sim i.i.d.\
-  N(0, v^2)$ (independent of $x_t$) with
-  \begin{equation*}
-    v^2 = \var(y_t) - \cov(y_t, x_t) \var(x_t)^{-1} \cov(y_t, x_t)'.
-  \end{equation*}
-  Then we have
-  \begin{equation*}
-    \E(X_{T}'\ep{T}\ep{T}'X_T \mid X_{R}'X_{R}, X_{T}'X_{T})
-    = v^2 X_{T}'X_{T}
-  \end{equation*}
-  and
-  \begin{equation*}
-    \E\Big( \sum_{s,t=R+1}^{T-h} \e_s \e_t x_s x_t'
-    \,\Big|\, X_{R}'X_{R} \Big)\Big) = P v^2 \E x_t x_t'.
-  \end{equation*}
-
-  So the conditions amount to restrictions on the eigenvalues of
-  $X_T'X_T$, which are familiar from general \ols.
-\end{example}
 
@@
   (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2^2 =\\
-  &= \E \tr\big( x_i^* x_i^{*\prime}
-   [(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}] X_{iT}'\eb_{iT} \eb_{iT}X_{iT}
-   [(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}] \big) \\
-  &\leq \eigen_{K_i}(\E x_i x_i')
-  \, \| \eigen_{K_i}(\E(X_{iT}' \eb_{iT} \eb_{iT}' X_{iT} \mid
-  X_{iR}'X_{iR}, X_{iT}'X_{iT})) \|_3 \\
-  & \quad \times \Big\|\sum_{j=1}^{K_i}
-  \eigen_j^2((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}) \Big\|_{3/2}
+  &= \E \tr\big( x_i^* x_i^{*\prime} X_{iT}'\eb_{iT} \eb_{iT}X_{iT}
+   [(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}]^2 \big) \\
+  &\leq \eigen_{K_i}(\E x_i x_i') \E \Big|  \eigen_{K_i}(X_{iT}' \eb_{iT}
+  \eb_{iT}' X_{iT}) \sum_{j=1}^{K_i} \eigen_j^2((X_{iR}'X_{iR})^{-1} -
+  (X_{iT}'X_{iT})^{-1}) \Big| \\
+  &= O(T) \, \Big\| \sum_{j=1}^{t-R} \eigen_j^{-2}(X_{iR}'X_{iR}) \Big\|_{3/2} \\
+  &= O(P^2/R)
 \end{align*}
-
-By Assumption~\ref{asmp-2},
-\begin{equation*}
-  \eigen_{K_i}(\E(X_{iT}' \eb_{iT} \eb_{iT}' X_{iT} \mid
-  X_{iR}'X_{iR}, X_{iT}'X_{iT})) = O_{L_3}(T).
-\end{equation*}
-Also, $(X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}$ has rank $P$ and
-its eigenvalues are bounded by those of $(X_{iR}'X_{iR})^{-1}$, which
-are $O_{L_2}(1/R)$ by Assumption~\ref{asmp-2} as well, so
-\begin{align*}
-  \Big\|\sum_{j=1}^{K_i}
-  \eigen_j^2\big((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}\big)\Big\|_{3/2}
-  &\leq \Big\|\sum_{j=K_i - P+1}^{K_i}
-  \eigen_j^2\big((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}\big) \Big\|_{3/2} \\
-  &= O(P/R^2)
-\end{align*}
-proving that
-\begin{equation*}
-  \| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
-  (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2 = O(\sqrt{P/R}).
-\end{equation*}
+The second equality holds because $\eigen_{K_i}(X_{iT}' \eb_{iT}
+\eb_{iT} X_{iT}) = O_{L_{3}}(T)$ by assumption and
+$(X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}$ has rank $t-R$ with
+eigenvalues bounded by those of $(X_{iR}'X_{iR})^{-1}$.
 
@@
   \big\| x_i^{*\prime} (X_{iR}'X_{iR})^{-1}
-  [X_{iT}'\eb_{iT} - X_{iR} \eb_{iR} ] \big\|_2 =  O(\sqrt{P/R}),
-\end{equation*}
-completing the proof.
+  [X_{iT}'\eb_{iT} - X_{iR} \eb_{iR} ] \big\|_2 \leq \Delta^3 P^2/R
+\end{equation*}
+as well, completing the proof.
 \qed

### 2013-11-04 paper.tex
Clean up and edit notation for the paper

@@
   L(y^{*} - x_i^{*\prime} \hat{\theta}_{iT}) \|_1
-  &\leq B_{L} \| x_i^{*\prime} (\hat{\theta}_{iR} - \hat{\theta}_{iT}) \|_2 \\
-  &\leq B_{L} \big(\| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
+  &\leq B_{L} P^{-1/2} \| x_i^{*\prime} (\hat{\theta}_{iR} - \hat{\theta}_{iT}) \|_2 \\
+  &\leq B_{L} P^{-1/2}\big(\| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
   (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2 \\

### 2013-12-16 paper.tex
Clean up proof of Lemma 1
This commit makes a few changes to Lemma 1 to make it easier to read; it may
fix a few minor typos as well.

--- 2013-10-23 paper.tex
@@
 
+\begin{proof}[Proof of~\eqref{eq:18} and~\eqref{eq:19}]
 For~\eqref{eq:18}, define $D_t^*$ for each $t=R+1,R+2,\dots,T-h$ so
@@
   \Big) \Big\rVert_2 \\
-  &= P^{-1} \sum_{t=R+1}^{T-h} \lVert D_t - D_t^* \rVert_2\\
+  &\leq P^{-1} \sum_{t=R+1}^{T-h} \lVert D_t - D_t^* \rVert_2\\
   &= O(P^{-1}) \sum_{t=R+1}^{T-h} \beta_{t-R}^{(\rho-2)/2\rho}
 \end{align*}
-and this last term is $o(P^{-1/2})$ by assumption.  Essentially the
-same argument proves~\eqref{eq:19} as well.
-
-For~\eqref{eq:20}, observe that
+and this last term is $o(P^{-1/2})$ by assumption.
+
+Essentially the same argument proves~\eqref{eq:19} as well.
+\end{proof}
+
+\begin{proof}[Proof of~\eqref{eq:20}]
+Observe that
 \begin{align*}
@@
   &\leq B_{L} \| x_i^{*\prime} (\hat{\theta}_{iR} - \hat{\theta}_{iT}) \|_2 \\
-  &\leq B_{L} \big(\| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
+  &\leq B_{L} \, \| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
   (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2 \\
-  &\quad+ \| x_i^{*\prime}
+  &\quad+ B_L \, \| x_i^{*\prime}
   (X_{iR}'X_{iR})^{-1}[X_{iT}'\eb_{iT} - X_{iR}
-  \eb_{iR} ] \|_2 \big).
+  \eb_{iR} ] \|_2 .
 \end{align*}
-The first term in the upper bound satisfies
+The first term in the upper bound\,---\,$\| x_i^{*\prime}
+[(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2$\,---\,satisfies
 \begin{align*}
@@
    [(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}] X_{iT}'\eb_{iT} \eb_{iT}X_{iT}
-   [(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}] \big) \\
-  &\leq \eigen_{K_i}(\E x_i x_i')
+   [(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}] \big) \\ \label{eq:8}
+  \begin{split}&\leq
+    \eigen_{K_i}(\E x_i x_i')
     \, \| \eigen_{K_i}(\E(X_{iT}' \eb_{iT} \eb_{iT}' X_{iT} \mid
@@
     & \quad \times \Big\|\sum_{j=1}^{K_i}
-  \eigen_j^2((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}) \Big\|_{3/2}
+    \eigen_j^2((X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}) \Big\|_{3/2}
+  \end{split} \\
+  &= O(T) \Big\|\sum_{j=1}^{K_i}
+    \eigen_j^2((X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}) \Big\|_{3/2}
 \end{align*}
-
-By Assumption~\ref{asmp-2},
-\begin{equation*}
-  \eigen_{K_i}(\E(X_{iT}' \eb_{iT} \eb_{iT}' X_{iT} \mid
-  X_{iR}'X_{iR}, X_{iT}'X_{iT})) = O_{L_3}(T).
-\end{equation*}
-Also, $(X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}$ has rank $P$ and
-its eigenvalues are bounded by those of $(X_{iR}'X_{iR})^{-1}$, which
-are $O_{L_2}(1/R)$ by Assumption~\ref{asmp-2} as well, so
+with the second to last inequality a consequence of Holder's
+inequality and the last bound holding by Assumption~\ref{asmp-2}.
+
+Now, $(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}$ has rank $P$ and
+each of its nonzero eigenvalues are bounded in absolute value by the
+eivenvalues of $(X_{iR}'X_{iR})^{-1}$. The eivenvalues of
+$(X_{iR}'X_{iR})^{-1}$ are $O_{L_3}(1/R)$ by Assumption~\ref{asmp-2}, so
 \begin{align*}
@@
   \eigen_j^2\big((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}\big) \Big\|_{3/2} \\
-  &= O(P/R^2)
+  &= O(P/R^2),
 \end{align*}
@@
 completing the proof.
-\qed
+\end{proof}
 

### 2013-12-16 paper.tex
Remove end-of-line whitespace

--- 2013-11-04 paper.tex
@@
 The observed \oos\ average is denoted $\oosA$: \[\oosA \equiv P^{-1}
-\oosSum{t}{1} D_t\]  with
+\oosSum{t}{1} D_{Rt}\]  with
 \[
-D_t \equiv L(y_{t+\h} - x_{1t}'\bh{1t}) - L(y_{t+\h} - x_{2t}'\bh{2t}).
+D_{Rt} \equiv L(y_{t+\h} - x_{1t}'\bh{1t}) - L(y_{t+\h} - x_{2t}'\bh{2t}).
 \]
 The \oos\ statistic of interest is $\oost \equiv \sqrt{P} \oosA /
-\sh$, for $\sh^2$ some (possibly Heteroskedasticity- and
+\hat\sigma_R$, for $\hat\sigma_R^2$ some (possibly Heteroskedasticity- and
 Autocorrelation-Consistent, or \hac) estimator of the asymptotic
@@
 \[
-\oosB \equiv Q^{-1} \sum_{t=T+1}^{T+Q} D_t.
+\oosB \equiv Q^{-1} \sum_{t=T+1}^{T+Q} D_{Tt}, \quad
+D_{Tt} \equiv L(y_{t+h} - x_{1t}' \bh{1t}) - L(y_{t+h} - x_{2t}' \bh{2t}).
 \]
@@
   derivatives almost everywhere.  Also, $L(0) = 0$, and there is a
-  constant $B_L$ such that $\|D_t\|_\rho \leq B_L$ for all $t$ ($\rho$ is defined
-  in Assumption~\ref{asmp-1}); $\| x_{it}' \hat{\theta}_{it} \|_2 \leq
-  B_L$ and $\| x_{it}' \hat{\theta}_{it} \|_2 \leq B_L$; and
+  constant $B_L$ such that $\|D_{R,R+j}\|_\rho \leq B_L$ and
+  $\|D_{T,T+j}\|_\rho \leq B_L$ for all $j \geq 1$ ($\rho$ is defined
+  in Assumption~\ref{asmp-1}); $\| x_{it}' \hat{\theta}_{is}^R \|_2 \leq
+  B_L$ and $\| x_{it}' \hat{\theta}_{is}^T \|_2 \leq B_L$; and
   \begin{equation*}
@@
   for $\tilde{\theta}_{it}$ a weighted average of any two estimates
-  $\hat{\theta}_{it}$ and $\hat{\theta}_{it'}$.
+  $\hat{\theta}_{is}^R$ and $\hat{\theta}_{is'}^R$ or
+  $\hat{\theta}_{is}^T$ and $\hat{\theta}_{is'}^T$ with $s, s' \leq t$.
 \end{asmp}
@@
   Suppose that Assumptions \ref{asmp-1}--\ref{asmp-4} hold, that
-  $\sh^2$ is an estimator satisfying
+  $\hat\sigma_R^2$ is an estimator satisfying
   \[
-    \sh^2 - \sigma^2 \to^p 0 \quad \text{with}\quad
-    \sigma^2 \equiv \var_R(\sqrt{P} \oosA) \equiv P \E_R(\bar{D}_R -
+    \hat\sigma_R^2 - \sigma_R^2 \to^p 0 \quad \text{with}\quad
+    \sigma_R^2 \equiv \var_R(\sqrt{P} \oosA) \equiv P \E_R(\bar{D}_R -
     \E_R \bar{D}_R)^2,
   \]
-  and that $\sigma^2$ is uniformly a.s. positive.  Then
+  and that $\sigma_R^2$ is uniformly a.s. positive.  Then
   \[
-  \frac{\oosA - \E_T\oosB}{\sh / \sqrt{P}}
+  \frac{\oosA - \E_T\oosB}{\hat\sigma_R / \sqrt{P}}
   \to^d N(0,1).
@@
   \begin{gather}
-  [\oosA - z_{\alpha/2} \, \sh /
-      \sqrt{P}, \oosA + z_{\alpha/2} \sh / \sqrt{P}],\label{interval-twosided} \\
-  [\oosA - z_{\alpha} \, \sh / \sqrt{P}, +\infty), \label{interval-greater}
+  [\oosA - z_{\alpha/2} \, \hat\sigma_R /
+      \sqrt{P}, \oosA + z_{\alpha/2} \hat\sigma_R / \sqrt{P}],\label{interval-twosided} \\
+  [\oosA - z_{\alpha} \, \hat\sigma_R / \sqrt{P}, +\infty), \label{interval-greater}
   \intertext{and}
 (-\infty, \oosA + z_{\alpha}
-      \, \sh / \sqrt{P}],
+      \, \hat\sigma_R / \sqrt{P}],
     \end{gather}
@@
 \begin{equation}
-  \lim \Pr[P^{1/2}\oosA/\sh > z_{\alpha} \mid \E_T
+  \lim \Pr[P^{1/2}\oosA/\hat\sigma_R > z_{\alpha} \mid \E_T
   \oosB \leq 0] \leq \alpha.
@@
 \begin{equation}\label{normalpart}
-  \sqrt{P}\frac{\oosA - \E_R \oosA}{\sigma} \to^d N(0,1)
+  \sqrt{P}\frac{\oosA - \E_R \oosA}{\sigma_R} \to^d N(0,1)
 \end{equation}
 The first Lemma establishes~\eqref{coefpart} and the second shows that
-the process $\{D_t - \E_R \oosA\}$ is an $L_2$-mixingale of size
+the process $\{D_{Rt} - \E_R \oosA\}$ is an $L_2$-mixingale of size
 $-1/2$ that satisfies a \clt, ensuring~\eqref{normalpart}.
@@
 zero.\footnote{Notice that, if the observations are i.i.d. and
-  $(y_{t+h}, x_{it}) \sim N(0,I)$, $(\hat{\theta}_{iR} -
-  \hat{\theta}_{iT}) \sim N(0, (X_{iR}'X_{iR})^{-1} -
+  $(y_{t+h}, x_{it}) \sim N(0,I)$, $(\hat{\theta}_{iR}^R -
+  \hat{\theta}_{iT}^T) \sim N(0, (X_{iR}'X_{iR})^{-1} -
   (X_{iT}'X_{iT})^{-1})$ given $X_{iT}$, and so
-  $\var(x_{i,T+1}'\hat{\theta}_{iR} - x_{i,T+1}'
-  \hat{\theta}_{iT}) \gg P K_i / (R - K_2)(T - K_2)$.}
+  $\var(x_{i,T+1}'\hat{\theta}_{iR}^R - x_{i,T+1}'
+  \hat{\theta}_{iT}^T) \gg P K_i / (R - K_2)(T - K_2)$.}
 Consequently, there is little scope to relax our assumption that
@@
   \begin{equation}\label{mixingaleR}
-    \lVert \E_{R+j-l}(D_{R+j} - \E_R D_{R+j}) \rVert_2 \leq
-    \couplingConstant \; \zeta_l
+    \lVert \E_{R+j-l}(D_{R,R+j} - \E_R D_{R,R+j}) \rVert_2 \leq
+    \couplingConstant \;
+    \zeta_l
   \end{equation}
@@
   $\delta$, any positive $j$, and any $l$ between 0 and $j$.  As a
-  consequence, $\{D_t - \E_R D_t, \mathcal F_t\}$ is an
+  consequence, $\{D_{Rt} - \E_R D_{Rt}, \mathcal F_t\}$ is an
   $L_2$-mixingale of size $-1/2$.
@@
   \noindent Part 2: Moreover,~\eqref{normalpart} holds under
-  Assumptions~\ref{asmp-1}--\ref{asmp-4} if $\sigma^2$ is
+  Assumptions~\ref{asmp-1}--\ref{asmp-4} if $\sigma_R^2$ is
   a.s. uniformly positive.
@@
 Finally, for Theorem \ref{res-confidence-intervals} to be useful, we
-need a consistent estimator of $\sigma^2$. Lemma
+need a consistent estimator of $\sigma_R^2$. Lemma
 \ref{res-variance-estimator} establishes that the usual \oos\ \hac\
@@
   \begin{equation*}
-    \sh^2 \equiv P^{-1} \oosSum{s,t}{1} (D_t - \oosA)(D_{Rs} - \oosA)
+    \hat{\sigma}_R^2 \equiv P^{-1} \oosSum{s,t}{1} (D_{Rt} - \oosA)(D_{Rs} - \oosA)
     \vWeight.
   \end{equation*}
-  Then $\sh^2 - \sigma^2 \to^p 0$.
+  Then $\hat{\sigma}_R^2 - \sigma_R^2 \to^p 0$.
 \end{lem}
@@
 The first two conditional moments of $D_t$ for $t > R$ (given
-$\mathcal{F}_R$) are straightforward to derive: $\E_R D_t = -
+$\mathcal{F}_R$) are straightforward to derive: $\E_R D_{Rt} = -
 \hat{\theta}_{2R}' \hat{\theta}_{2R}$ and
 \begin{equation*}
-  \sigma^2 \equiv \E_R(D_t - \E_R D_t)^2 = 4
-  \hat{\theta}_{2R}' \hat{\theta}_{2R} +
-  \E_R(\hat{\theta}_{2R}' (I - x_{2t} x_{2t}')
-  \hat{\theta}_{2R})^2   \geq 4 \hat{\theta}_{2R}'
-  \hat{\theta}_{2R} \quad a.s.
+  \sigma_R^2 \equiv \E_R(D_{Rt} - \E_R D_{Rt})^2 = 4
+  \hat{\theta}_{2R}^{R\prime} \hat{\theta}_{2R}^{R} +
+  \E_R(\hat{\theta}_{2R}^{R\prime} (I - x_{2t} x_{2t}')
+  \hat{\theta}_{2R}^{R})^2   \geq 4 \hat{\theta}_{2R}^{R\prime}
+  \hat{\theta}_{2R}^R \quad a.s.
 \end{equation*}
@@
 1)$ (since $(X_{2R}'X_{2R})^{-1}$ is Inverse-Wishart$(I_{K_2}, R)$),
-making $\sigma^2$ uniformly a.s. positive and ensuring that the
+making $\sigma_R^2$ uniformly a.s. positive and ensuring that the
 distribution of the \oos\ average is not $P^{1/2}$-degenerate.  The
-natural \oos\ variance estimator is consistent for $\sigma^2$:
+natural \oos\ variance estimator is consistent for $\sigma_R^2$:
 \begin{align*}
-  \sh^2 &= P^{-1} \sum_{t=R+1}^{T-1} (D_t - \oosA)^2 \\
-  &= 4 \hat{\theta}_{2R}' \Big[P^{-1} \sum_{t=R+1}^{T-1}
+  \hat{\sigma}_R^2 &= P^{-1} \sum_{t=R+1}^{T-1} (D_{Rt} - \oosA)^2 \\
+  &= 4 \hat{\theta}_{2R}^{R\prime} \Big[P^{-1} \sum_{t=R+1}^{T-1}
   \Big(y_{t+1} x_{2t} - P^{-1} \sum_{s=R+1}^{T-1} y_s x_{2s}\Big)
@@
   \Big[\hat{\theta}_{2R}' \Big(x_{2t} x_{2t}' - P^{-1}
-  \sum_{s=R+1}^{T-1} x_{2s} x_{2s}' \Big) \hat{\theta}_{2R}  \Big]^{2}.
+  \sum_{s=R+1}^{T-1} x_{2s} x_{2s}' \Big) \hat{\theta}_{2R}'  \Big]^{2}.
 \end{align*}
 As $P \to \infty$, the first term converges in probability to
-$\hat{\theta}_{2R}' \hat{\theta}_{2R}$, the second to zero,
-and the third to $\E_R(\hat{\theta}_{2R}'(I - x_{2t}x_{2t}')
-\hat{\theta}_{2R})^2$.  Since the number of regressors prevents
-$\hat{\theta}_{2R}$ from converging i.p. to zero (its expected
-value), $\sh^2$ does not converge to the unconditional
+$\hat{\theta}_{2R}^{R\prime} \hat{\theta}_{2R}^R$, the second to zero,
+and the third to $\E_R(\hat{\theta}_{2R}^{R\prime}(I - x_{2t}x_{2t}')
+\hat{\theta}_{2R}^R)^2$.  Since the number of regressors prevents
+$\hat{\theta}_{2R}^R$ from converging i.p. to zero (its expected
+value), $\hat{\sigma}_R^2$ does not converge to the unconditional
 variance.
@@
 \begin{equation*}
-  \frac{D_t - \E_R D_t}{\sigma} =
+  \frac{D_{Rt} - \E_R D_{Rt}}{\sigma_R} =
   \frac{2 y_{t} x_{2t}' \hat{\theta}_{2R} +
@@
 with a sequence of constants $\theta_{2R}$ since $\hat{\theta}_{2R}$
-does not converge to a deterministic limit.  But $\sigma^{-1}
+does not converge to a deterministic limit.  But $\sigma_R^{-1}
 \E_t(\oosA - \E_R\oosA) = 0$, making this sequence an
@@
   enough to establish the \clt.} so it obeys a \clt\ as long as
-$\sigma^2$ is uniformly a.s. positive, which we have already
+$\sigma_R^2$ is uniformly a.s. positive, which we have already
 established.  Lemma~\ref{res-mixingale} ensures that the \clt\ holds
@@
 \begin{equation*}
-  [ \oosA - 1.28 \hat{\sigma}, \infty) \quad\text{with}\quad
-  \sh^2 = \frac1P \sum_{t=R+1}^T (D_t - \oosA)^{2}
+  [ \oosA - 1.28 \hat{\sigma_R}, \infty) \quad\text{with}\quad
+  \hat\sigma_R^2 = \frac1P \sum_{t=R+1}^T (D_t - \oosA)^{2}
 \end{equation*}
@@
   T, $s$, and $t$ with $t \geq s$, there exist random variables
-  $D_s^*,\dots,D_t^*$ such that
+  $\tilde D_s,\dots,\tilde D_t$ such that
   \begin{equation}\label{eq:coupling1}
-    P[(D_s^*,\dots,D_t^*) \neq (D_s,\dots,D_t)] \leq \beta_{s-u}
+    P[(\tilde D_s,\dots,\tilde D_t) \neq (D_s,\dots,D_t)] \leq \beta_{s-u}
   \end{equation}
@@
   \begin{equation}\label{eq:coupling2}
-    \E(\phi(D_s^*,\dots, D_t^*) \mid \mathcal{F}_u ) =
+    \E(\phi(\tilde D_s,\dots, \tilde D_t) \mid \mathcal{F}_u ) =
     \int
@@
  \begin{equation}\label{eq:coupling3}
-   \| D_v^* - D_v \|_2 \leq 2^{1+1/\rho} B_L
+   \| \tilde D_v - D_v \|_2 \leq 2^{1+1/\rho} B_L
    \beta_{s-u}^{\rhoExp}, \qquad v = s,\dots,t.
@@
   \begin{equation*}
-    D_v^* =
+    \tilde D_v =
     \begin{cases}
@@
 establishing half of the mixingale result trivially.  Now fix $i$ and $m >
-0$ and use Lemma \ref{lem-basic-coupling} to define $D_{ts}^*$
+0$ and use Lemma \ref{lem-basic-coupling} to define $\tilde{D}_{ts}$
 for each $t =(2i-2)b_T-P+1,\dots,(2i-1)b_T-P$ and $s =
@@
 \begin{equation*}
- \E_R D_{ts}^* = \E_{(2i-2m-1)b_T+R-P} D_{ts}^* \quad a.s.
+ \E_R \tilde D_{ts} = \E_{(2i-2m-1)b_T+R-P} \tilde D_{ts} \quad a.s.
 \end{equation*}
@@
 \begin{equation*}
-  \lVert D_{ts}^* - D_s \rVert_2 \leq \couplingBound{s - (2i-2m-1)b_T-R+P}.
+  \lVert \tilde D_{ts} - D_{Rs} \rVert_2 \leq \couplingBound{s - (2i-2m-1)b_T-R+P}.
 \end{equation*}
@@
 \begin{equation*}
-  Z_{1t}^* = 1/\sqrt{P\gamma} \sum_{l=\vttLower}^{\vttUpper}
-  (D_{t,t+l+R}^* - \E_R D_{t,t+l+R}^*)\ W(l/\gamma), \\
+  \tilde Z_{1t} = 1/\sqrt{P\gamma} \sum_{l=\vttLower}^{\vttUpper}
+  (\tilde D_{t,t+l+R} - \E_R\tilde D_{t,t+l+R})\ W(l/\gamma), \\
 \end{equation*}
@@
 \begin{equation*}
-Z_{2t}^* = 1/\sqrt{P\gamma} \sum_{j=\vttLower}^{\vttUpper}
-    (D_{t,t+l+R}^* - \E_R D_{t,t+l+R}^*)\ \kernelB{j/\gamma}.
+\tilde Z_{2t} = 1/\sqrt{P\gamma} \sum_{j=\vttLower}^{\vttUpper}
+    (\tilde D_{t,t+l+R} - \E_R\tilde D_{t,t+l+R})\ \kernelB{j/\gamma}.
 \end{equation*}
@@
   &= \vtSuma \lVert \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
-  &\quad - \E(Z_{1t}^* Z_{2t}^* \mid \UFiltration{2i-2m-1}) \\
-  &\quad + \E(Z_{1t}^* Z_{2t}^* \mid \UFiltration{2i-2m-1})
+  &\quad - \E(\tilde{Z}_{1t}\tilde{Z}_{2t} \mid \UFiltration{2i-2m-1}) \\
+  &\quad + \E(\tilde{Z}_{1t}\tilde{Z}_{2t} \mid \UFiltration{2i-2m-1})
   - \E_R Z_{1t}Z_{2t} \rVert_2 \\
 %  \leq \vtSuma (\wall \lVert \wall \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
-%  - \E(Z_{1t}^*Z_{2t}^* \mid \UFiltration{2i-2m-1}) \rVert_2\return
-%  \\ + \lVert \E_R Z_{1t}Z_{2t} - \E_R Z_{1t}^*Z_{2t}^*
+%  - \E(\tilde{Z}_{1t}\tilde{Z}_{2t} \mid \UFiltration{2i-2m-1}) \rVert_2\return
+%  \\ + \lVert \E_R Z_{1t}Z_{2t} - \E_R \tilde{Z}_{1t}\tilde{Z}_{2t}
 %  \rVert_2)\return \\
-  &\leq 2 \vtSuma \lVert Z_{1t} Z_{2t} - Z_{1t}^* Z_{2t}^*
+  &\leq 2 \vtSuma \lVert Z_{1t} Z_{2t} - \tilde Z_{1t} \tilde{Z}_{2t}
   \rVert_2 \\
-  &\leq 2 \vtSuma (\lVert Z_{1t} - Z_{1t}^* \rVert_2 \lVert
+  &\leq 2 \vtSuma (\lVert Z_{1t} - \tilde{Z}_{1t} \rVert_2 \lVert
   Z_{2t} \rVert_{\infty}
-  + \lVert Z_{2t} - Z_{2t}^* \rVert_2 \lVert Z_{1t}^* \rVert_{\infty}) \\
-  &\leq \frac{2 C b_T^{1/2}}{(P\gamma)^{1/2}} \vtSuma (\lVert Z_{1t} - Z_{1t}^* \rVert_2
-  + \lVert Z_{2t} - Z_{2t}^* \rVert_2).
+  + \lVert Z_{2t} - \tilde{Z}_{2t} \rVert_2 \lVert \tilde{Z}_{1t} \rVert_{\infty}) \\
+  &\leq \frac{2 C b_T^{1/2}}{(P\gamma)^{1/2}} \vtSuma (\lVert Z_{1t} - \tilde{Z}_{1t} \rVert_2
+  + \lVert Z_{2t} - \tilde{Z}_{2t} \rVert_2).
 \end{align*}
@@
 \begin{align*}
-  \frac{2 C b_T^{1/2}}{(P \gamma)^{1/2}} &\vtSuma \lVert Z_{1t} - Z_{1t}^* \rVert_2 \\& \leq
+  \frac{2 C b_T^{1/2}}{(P \gamma)^{1/2}} &\vtSuma \lVert Z_{1t} - \tilde{Z}_{1t} \rVert_2 \\& \leq
   \frac{4C b_T^{1/2}}{P\gamma} \vtSuma \sum_{l=\vttLower}^{\vttUpper} \lVert
-  D_{t+l+R,R} - D_{t,t+l+R}^* \rVert_2 W(l/\gamma) \\&
+  D_{t+l+R,R} - \tilde{D}_{t,t+l+R} \rVert_2 W(l/\gamma) \\&
   \leq O\Bigg(\frac{b_T^{1/2}}{P\gamma}\Bigg) \vtSuma
@@
   \begin{equation*}
-    \sh^2 - P^{-1} \sum_{s,t=R+1}^{T-h} (D_s - \E_R
-    D_s) (D_t - \E_R D_t) W((t-s)/\gamma) \to^{L_1} 0.
+    \hat{\sigma}_R^2 - P^{-1} \sum_{s,t=R+1}^{T-h} (D_{Rs} - \E_R
+    D_{Rs}) (D_{Rt} - \E_R D_{Rt}) W((t-s)/\gamma) \to^{L_1} 0.
   \end{equation*}
@@
 \begin{multline*}
-  \Big| \sh^2 -  P^{-1} \sum_{s,t=R+1}^{T-h} (D_s - \E_R
-    D_s) (D_t - \E_R D_t) W((t-s)/\gamma) \Big| \leq\\
-  \varianceDiffA \\ + P^{-1} \oosSum{s,t}{1} \lvert (D_s -
-  \oosA)(\E_R D_t - \oosA) \rvert \vWeight + o_p(1).
+  \Big| \hat\sigma_R^2 -  P^{-1} \sum_{s,t=R+1}^{T-h} (D_{Rs} - \E_R
+    D_{Rs}) (D_{Rt} - \E_R D_{Rt}) W((t-s)/\gamma) \Big| \leq\\
+  \varianceDiffA \\ + P^{-1} \oosSum{s,t}{1} \lvert (D_{Rs} -
+  \oosA)(\E_R D_{Rt} - \oosA) \rvert \vWeight + o_p(1).
 \end{multline*}
@@
 Now,
-$P^{-1} \oosSum{s}{1}(D_s - \E_R D_s)^2 = O_p(1)$, and it suffices to prove
+$P^{-1} \oosSum{s}{1}(D_{Rs} - \E_R D_{Rs})^2 = O_p(1)$, and it suffices to prove
 that \[\varianceDiffAi = o_p(1).\]  Observe that
 \begin{align*}
-  \varianceDiffAi & = O_p\Big(P^{-1} \oosSum{s}{1}(\E_{R}D_s -
+  \varianceDiffAi & = O_p\Big(P^{-1} \oosSum{s}{1}(\E_{R}D_{Rs} -
   \E_R\oosA)^2\Big) + O_p(\oosA - \E_R\oosA)^{2} \\
-  &= O_p\Big(P^{-1} \oosSum{s}{1} (\E_RD_s)^2 - (\E_R\oosA)^2\Big) +
+  &= O_p\Big(P^{-1} \oosSum{s}{1} (\E_RD_{Rs})^2 - (\E_R\oosA)^2\Big) +
   o_p(1),
@@
 
-Now define $D_s^*$, $s = R+1,\dots,T-\h$, as in Lemma
-\ref{lem-basic-coupling} so that $\E_{s-1} D_s^* = \E_R D_s^*$ almost
-surely.  Note that we also have the equality $\E_R D_s^* = \E_R
-D_{R+1}^*$ almost surely for all $s\geq R+1$, and so
+Now define $\tilde D_s$, $s = R+1,\dots,T-\h$, as in Lemma
+\ref{lem-basic-coupling} so that $\E_{s-1} \tilde D_s = \E_R \tilde
+D_s$ almost surely.  Note that we also have the equality $\E_R \tilde
+D_s = \E_R \tilde D_{R+1}$ almost surely for all $s\geq R+1$, and so
 \[
-P^{-1} \oosSum{s}{1} (\E_R D_s^*)^2 = \Big(P^{-1} \oosSum{s}{1} \E_R
-D_s^*\Big)^2 \quad \text{a.s..}
+P^{-1} \oosSum{s}{1} (\E_R \tilde D_s)^2 = \Big(P^{-1} \oosSum{s}{1} \E_R
+\tilde D_s\Big)^2 \quad \text{a.s..}
 \]
@@
 P^{-1} \oosSum{s}{1} (\E_R D_s)^2 - (\E_R\oosA)^2 & =
-P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R D_s^*)^2]\\
-&\quad+ \Big(P^{-1} \oosSum{s}{1} \E_R D_s^*\Big)^2 - (\E_R\oosA)^2 \quad \text{a.s}.\\
-&= O_p\Big(P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R D_s^*)^2]\Big).
+P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R\tilde D_s)^2]\\
+&\quad+ \Big(P^{-1} \oosSum{s}{1} \E_R \tilde D_s\Big)^2 - (\E_R\oosA)^2 \quad \text{a.s}.\\
+&= O_p\Big(P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R \tilde D_s)^2]\Big).
 \end{align*}
@@
 \begin{align*}
-\Big\lVert P^{-1} \oosSum{s}{1} [(\E_RD_s)^2 - (\E_R D_s^*)^2] \Big\rVert_1
-&\leq P^{-1} \oosSum{s}{1} \lVert \E_RD_s - \E_R D_s^* \rVert_2 \lVert
-\E_RD_s + \E_R D_s^* \rVert_2
-\\ &\leq (4 B_L/P) \oosSum{s}{1} \lVert \E_RD_s - \E_R D_s^* \rVert_2,
+\Big\lVert P^{-1} \oosSum{s}{1} [(\E_RD_s)^2 - (\E_R \tilde D_s)^2] \Big\rVert_1
+&\leq P^{-1} \oosSum{s}{1} \lVert \E_RD_s - \E_R \tilde D_s \rVert_2 \lVert
+\E_RD_s + \E_R \tilde D_s \rVert_2
+\\ &\leq (4 B_L/P) \oosSum{s}{1} \lVert \E_RD_s - \E_R \tilde D_s \rVert_2,
 \end{align*}
@@
 \[
-\frac{\bar{D}_{R} - \E_T \bar{D}_T}{\sh / \sqrt{P}} =
-\frac{1}{\sh \sqrt{P}}\oosSum{t}{1} (D_t - \E_R D_t) +
-\frac{\sqrt{P}}{\sh} (\E_R\oosA - \E_T\oosB).
+\frac{\bar{D}_{R} - \E_T \bar{D}_T}{\hat\sigma_R / \sqrt{P}} =
+\frac{1}{\hat\sigma_R \sqrt{P}}\oosSum{t}{1} (D_{Rt} - \E_R D_{Rt}) +
+\frac{\sqrt{P}}{\hat\sigma_R} (\E_R\oosA - \E_T\oosB).
 \]
@@
 \begin{equation*}
-  \Pr[P^{1/2} \oosA / \sh > z_\alpha \text{ and } \E_R \oosA \leq 0]
-  - \Pr[P^{1/2} \oosA / \sh > z_\alpha \text{ and }
+  \Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha \text{ and } \E_R \oosA \leq 0]
+  - \Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha \text{ and }
   \E_T \oosB \leq 0] \to 0.
@@
 \begin{equation*}
-  \Pr[P^{1/2} \oosA / \sh > z_\alpha
+  \Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha
   \mid \E_R \oosA \leq 0] =
-  \frac{\Pr[P^{1/2} \oosA / \sh > z_\alpha \text{ and }
+  \frac{\Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha \text{ and }
     \E_R \oosA \leq 0]}{\Pr[\E_R \oosA \leq 0]}
@@
 \begin{equation*}
-  \Pr[P^{1/2} \oosA / \sh > z_\alpha
+  \Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha
   \mid \E_T \oosB \leq 0] =
-  \frac{\Pr[P^{1/2} \oosA / \sh > z_\alpha \text{ and }
+  \frac{\Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha \text{ and }
     \E_T \oosB \leq 0]}{\Pr[\E_T \oosB \leq 0]}
@@
 \begin{equation*}
-  \Pr[P^{1/2} \oosA / \sh > z_\alpha
+  \Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha
   \mid \E_T \oosB \leq 0]
-  - \Pr[P^{1/2} \oosA / \sh > z_\alpha
+  - \Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha
   \mid \E_R \oosA \leq 0] \to^p 0.
@@
 \begin{align*}
-  \Pr[P^{1/2} \oosA / \sh > z_\alpha \mid \E_R \oosA \leq 0]
-  &\leq \Pr[P^{1/2} (\oosA - \E_R \oosA) / \sh > z_\alpha
+  \Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha \mid \E_R \oosA \leq 0]
+  &\leq \Pr[P^{1/2} (\oosA - \E_R \oosA) / \hat\sigma > z_\alpha
   \mid \E_R \oosA \leq 0] \\
-  &= \E( \Pr[P^{1/2} (\oosA - \E_R \oosA) / \sh > z_\alpha
+  &= \E( \Pr[P^{1/2} (\oosA - \E_R \oosA) / \hat\sigma > z_\alpha
   \mid \mathcal{F}_R] \mid \E_R \oosA \leq 0) \\
@@
 \begin{equation*}
-  \| D_t^* - D_t \|_2 \leq 2^{(1+\rho)/\rho} B_L \beta_{t-R}^{(\rho-2)/2\rho}
+  \| D_t^* - D_{Rt} \|_2 \leq 2^{(1+\rho)/\rho} B_L \beta_{t-R}^{(\rho-2)/2\rho}
 \end{equation*}
@@
   \Big) \Big\rVert_2 \\
-  &= P^{-1} \sum_{t=R+1}^{T-h} \lVert D_t - D_t^* \rVert_2\\
+  &= P^{-1} \sum_{t=R+1}^{T-h} \lVert D_{Rt} - D_t^* \rVert_2\\
   &= O(P^{-1}) \sum_{t=R+1}^{T-h} \beta_{t-R}^{(\rho-2)/2\rho}
@@
 \noindent \textit{Part 1.} Fix $R$, $j$ and $l$ and use Lemma
-\ref{lem-basic-coupling} to define $D_{R+j}^*$ so that
-\[\E_RD_{R+j}^* = \E_{R+j-l} D_{R+j}^* \quad a.s. \]
+\ref{lem-basic-coupling} to define $\tilde{D}_{R+j}$ so that
+\[\E_R\tilde D_{R+j} = \E_{R+j-l} \tilde D_{R+j} \quad a.s. \]
 and
-\[\lVert D_{R+j} - D_{R+j}^* \rVert_2 \leq \couplingBound{l}.\]
+\[\lVert D_{R+j,R} - \tilde D_{R+j} \rVert_2 \leq \couplingBound{l}.\]
 Then
 \begin{align*}
-\lVert \E_{R+j-l} D_{R+j} - \E_R D_{R+j} \rVert_2 & \leq
-\lVert \E_{R+j-l} D_{R+j} - \E_{R+j-l} D_{R+j}^* \rVert_2 \\
+\lVert \E_{R+j-l} D_{R+j,R} - \E_R D_{R+j,R} \rVert_2 & \leq
+\lVert \E_{R+j-l} D_{R+j,R} - \E_{R+j-l} \tilde{D}_{R+j} \rVert_2 \\
 &\quad + \lVert
-\E_{R+j-l} D_{R+j}^* - \E_R D_{R+j} \rVert_2 \\
-&\leq 2 \lVert D_{R+j} - D_{R+j}^* \rVert_2 \\
+\E_{R+j-l} \tilde{D}_{R+j} - \E_R D_{R+j,R} \rVert_2 \\
+&\leq 2 \lVert D_{R+j,R} - \tilde D_{R+j} \rVert_2 \\
 &\leq 2^{2 + 1/\rho}\ B_L\ \couplingBeta{l}.
@@
 \begin{equation*}
-   \SumOuterBlock{i} Z_i = P^{-1/2} \oosSum{s}{1} (D_t - \E_R D_t) + o_p(1).
+   \SumOuterBlock{i} Z_i = P^{-1/2} \oosSum{s}{1} (D_{Rt} - \E_R D_{Rt}) + o_p(1).
 \end{equation*}
@@
 \mds\ by construction, so \citepos{HaH:80} Theorem 3.2 and Corollary
-3.1 ensure that $\sigma^{-1} \SumOuterBlock{i} Z_i \to^d N(0,1) $ as
+3.1 ensure that $\sigma_R^{-1} \SumOuterBlock{i} Z_i \to^d N(0,1) $ as
 long as
 \begin{equation}\label{eq:cltvar2}
-  \sigma^2 - \SumOuterBlock{i} \E_R Z_i^2 \to^p 0,
+  \sigma_R^2 - \SumOuterBlock{i} \E_R Z_i^2 \to^p 0,
 \end{equation}
@@
 \begin{equation}\label{eq:cltvar1}
-  \SumOuterBlock{i} \E_R Z_i^2 - \SumOuterBlock{i} \ZSqCE \to^p 0.\footnote{Note that $\sigma^2 \in \mathcal{F}_t$ for
+  \SumOuterBlock{i} \E_R Z_i^2 - \SumOuterBlock{i} \ZSqCE \to^p 0.\footnote{Note that $\sigma_R^2 \in \mathcal{F}_t$ for
     all $t \geq R$, so Hall and Heyde's condition (3.21) is
@@
 \begin{align*}
-  \lVert \sh^2 - \sigma^2 \rVert_1 &
-  \leq \lVert \sh^2 - \varianceTermI \rVert_1
+  \lVert \hat\sigma_R^2 - \sigma_R^2 \rVert_1 &
+  \leq \lVert \hat\sigma_R^2 - \varianceTermI \rVert_1
   + \lVert \varianceTermI - \varianceTermII \rVert_1
@@
   + \lVert \E_R\varianceTermI - \E_R\varianceTermII \rVert_1
-  + \lVert \E_R \varianceTermI - \sigma^2 \rVert_1
+  + \lVert \E_R \varianceTermI - \sigma_R^2 \rVert_1
   \\ &
-  \leq  \lVert \sh^2 - \varianceTermI \rVert_1
+  \leq  \lVert \hat\sigma_R^2 - \varianceTermI \rVert_1
   + 2(\lVert \varianceTermI - \varianceTermII \rVert_1
@@
   & \quad + \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1
-  + \lVert \E_R \varianceTermI - \sigma^2 \rVert_1.
+  + \lVert \E_R \varianceTermI - \sigma_R^2 \rVert_1.
 \end{align*}
@@
 \begin{equation}
-  \label{eq:4} \lVert \sh^2 - \varianceTermI \rVert_1 \to 0
+  \label{eq:4} \lVert \hat{\sigma}_R^2 - \varianceTermI \rVert_1 \to 0
 \end{equation}

### 2013-12-19 paper.tex
Correct typo in mixignale proof
Rewrite assumption 3 - moments and smoothness
This commit changes the assumption on moments and
smoothness of the loss function (assumption 3) to
give the needed conditions for Lemma 1.

--- 2013-12-16 paper.tex
@@
 \begin{asmp}\label{asmp-3}
-  The loss function $L$ is continuous and has finite left and right
-  derivatives almost everywhere.  Also, $L(0) = 0$, and there is a
-  constant $B_L$ such that $\|D_t\|_\rho \leq B_L$ for all $t$ ($\rho$ is defined
-  in Assumption~\ref{asmp-1}); $\| x_{it}' \hat{\theta}_{it} \|_2 \leq
-  B_L$ and $\| x_{it}' \hat{\theta}_{it} \|_2 \leq B_L$; and
-  \begin{equation*}
-    \| L'(y_{t+h} - x_{it}'\tilde{\theta}_{it}) \|_2 \leq B_L
-  \end{equation*}
-  for $\tilde{\theta}_{it}$ a weighted average of any two estimates
-  $\hat{\theta}_{it}$ and $\hat{\theta}_{it'}$.
+  The loss function $L$ is continuous, has finite left and right
+  derivatives almost everywhere, and $L(0) = 0$.  There is a constant
+  $B_L$ and a function $L'$ that bounds the left and right derivative
+  of $L$ such that $\|D_t\|_\rho \leq B_L$; $\|D_t^*\|_\rho \leq B_L$
+  for all $t$, where
+  \begin{equation*}
+    D_t^* = L(y^* - x_1^{*\prime}\hat\theta_{1t})
+    - L(y^* - x_2^{*\prime}\hat\theta_{2t})
+  \end{equation*}
+  and $(y^*, x_1^*, x_2^*)$ equals $(y_t, x_{1t}, x_{2t})$ in
+  distribution but is independent of $\mathcal{F}_T$ ($\rho$ is defined
+  in Assumption~\ref{asmp-1}); and
+  \begin{equation*}
+    \| L'(y^* - x_{i}^{*\prime}
+    (\alpha \hat{\theta}_{iR} + (1-\alpha) \hat{\theta}_{iT})) \|_2
+    \leq B_L
+  \end{equation*}
+  for any $\alpha \in [0,1]$.
 \end{asmp}
@@
 \end{equation*}
-Note that $\{Z_i - E_{R + (i-1)b_T},\mathcal{F}_{R + i b_T}\}_i$ is an
+Note that $\{Z_i - E_{R + (i-1)b_T} Z_i,\mathcal{F}_{R + i b_T}\}_i$ is an
 \mds\ by construction, so \citepos{HaH:80} Theorem 3.2 and Corollary

### 2013-12-20 paper.tex
Tweak a few sentences in the introduction

@@
 is necessary before resolving any new issues that arise with multiple
-comparisons.\footnote{Moreover, the empirical research that motivates
+comparisons. Moreover, the empirical research that motivates
 this paper uses \textit{pseudo} \oos\ comparisons and not
@@
 could account for some forms of data-snooping better than
-  \citepos{Whi:00} \textsc{brc} or its extensions, in-sample and
-  pseudo \oos\ comparisons would both be affected by the data-snooping.
-  This point is also made by \citet{InK:04}.}
-
-We focus on linear regression models for simplicity, but our basic
+\citepos{Whi:00} \textsc{brc} or its extensions, in-sample and pseudo
+\oos\ comparisons would both be affected by the data-snooping, a
+point also made by \citet{InK:04}.
+
+We focus on linear regression models estimated with a fixed window
+for simplicity, but our basic
 conclusions should be true for other models as well.  Under this
 asymptotic theory, where the number of regressors $k$ increases with $T$
-so that $\lim k/T$ is positive,
+so that $\lim k/T$ is positive and less than one,
 the \ols\ coefficient estimator is no longer
@@
 Also note that, in this situation, a model that performs well
-in-sample can perform badly out-of-sample \emph{even if there are no
-structural breaks or other forms of instability.}  Researchers
+in-sample can perform badly out-of-sample even if there are no
+structural breaks or other forms of instability.  Researchers
 have argued that a breakdown of in-sample forecasting ability
@@
 on non-convergent estimators.  Moreover, transformations of these
-processes also behave like mixingales when recentered, so asymptotic
+processes also behave like mixingales when recentered, so 
+the arguments used to prove asymptotic
 results for \ned\ functions of mixing processes can be used for these

### 2013-12-20 paper.tex
Tweak a few statements in setup section

@@
 $Q$ is a known positive integer.  The forecaster's goal is to choose
-the model that will have lower average loss over periods $T+h$ through
+the model that will have lower average loss over periods $T+h+1$ through
 $T+h+Q$, evaluated by the known loss function $L$.  We allow $Q = 1$,

### 2013-12-20 paper.tex
Fix typo in extended example

@@
 \end{align*}
-So, in this example, $P^{1/2}(\E_R \oosA - \E_T \oosB) \to^p 0$ only
+So, in this example, $P^{1/2}(\E_R \oosA - \E_T \oosB) \to^p 0$
 if $P^3/T^2 \to 0$, which is slightly weaker than the general

### 2014-01-08 paper.tex
Fix typo in index of D_t
Move version info from Makefile to git hooks
This commit removes a script from the Makefile that generates
the commit date and version number and stores them in the file
VERSION.tex (which then is included in the main document). This
information is now generated by the git hooks:
- post-commit
- post-merge
- post-checkout

This approach is motivated by Brent Longborough's gitinfo package.
Redo indexing in Lemma A3
This commit rearranges the indexing in Lemma A3 so that alphabetical
order corresponds to temporal order. It also adds a missing index and
closes #29.

@@
 
-\input{VERSION.tex}
+% VERSION is generated by a post-commit hook and contains the git
+% version info
+\IfFileExists{VERSION}{
+  \input{VERSION}
+  \date{\dinfo\ (version \hinfo)}
+  \markright{\dinfo\ (version \hinfo)}
+}{}
+
 \title{Out-of-Sample Comparisons of Overfit Models}
@@
   Suppose Assumptions \ref{asmp-1}--\ref{asmp-3} hold.  Then, for any
-  T, $s$, and $t$ with $t \geq s$, there exist random variables
-  $D_s^*,\dots,D_t^*$ such that
+  T, $s$, $t$, and $u$ with $s < t \leq u$, there exist random
+  variables $D_t^*,\dots,D_u^*$ such that
   \begin{equation}\label{eq:coupling1}
-    P[(D_s^*,\dots,D_t^*) \neq (D_s,\dots,D_t)] \leq \beta_{s-u}
+    P[(D_{t}^*,\dots,D_u^*) \neq (D_{t},\dots,D_u)] \leq \beta_{t-s}
   \end{equation}
@@
   \begin{equation}\label{eq:coupling2}
-    \E(\phi(D_s^*,\dots, D_t^*) \mid \mathcal{F}_u ) =
+    \E(\phi(D_{t}^*,\dots, D_u^*) \mid \mathcal{F}_s ) =
     \int
-    \phi(D_s,\dots,D_t) f(\mathbf{x}, \mathbf{y})\ d\mathbf{x}\ d\mathbf{y}
+    \phi(D_{t},\dots,D_u) f(\mathbf{x}, \mathbf{y})\ d\mathbf{x}\ d\mathbf{y}
   \end{equation}
@@
   expectations are finite, where
-  \[ \mathbf{x} = (x_{s}', \dots, x_{t}')', \qquad
-  \mathbf{y} = (y_{s+\h},\dots,y_{t+\h})',\] and $f$ is the
+  \[ \mathbf{x} = (x_{t}', \dots, x_{u}')', \qquad
+  \mathbf{y} = (y_{t+\h},\dots,y_{u+\h})',\] and $f$ is the
   joint density of $(\mathbf{x}, \mathbf{y})$.  Moreover,
@@
    \| D_v^* - D_v \|_2 \leq 2^{1+1/\rho} B_L
-   \beta_{s-u}^{\rhoExp}, \qquad v = s,\dots,t.
+   \beta_{t-s}^{\rhoExp}, \qquad v = t,\dots,u.
  \end{equation}
@@
   The proof follows as a consequence of Lemmas \ref{lem-berbee} and
-  \ref{lem-extend-mp}.  Let $l = t-s$.  For any fixed values of $l$
+  \ref{lem-extend-mp}.  Let $l = u-t$.  For any fixed values of $l$
   and $T$, the sequence of vectors
-  \[ V_s = (y_{s+\h}, x_{s}', \dots, y_{s+l+\h}, x_{s+l}') \] is
+  \[ V_{t} = (y_{t+\h}, x_{t}', \dots, y_{t+l+\h}, x_{t+l}') \] is
   absolutely regular of size $\rho/(\rho-2)$.  Berbee's Lemma implies
   that there is a random vector $V^*$ that is independent of
-  $\mathcal{F}_u$, equal to $V_s$ in distribution, and satisfies
-  \[\Pr[V^* \neq V_s] = \beta_{s-u}.\]
+  $\mathcal{F}_s$, equal to $V_{t}$ in distribution, and satisfies
+  \[\Pr[V^* \neq V_{t}] = \beta_{t-s}.\]
 
@@
   with $y_{v+\h}^*$ and $x_{iv}^*$ denoting the elements of $V^*$
-  corresponding to $y_{v+\h}$ and $x_{iv}$ in $V_s$.  Equations
+  corresponding to $y_{v+\h}$ and $x_{iv}$ in $V_{t}$.  Equations
   (\ref{eq:coupling1}) and (\ref{eq:coupling2}) are satisfied by
@@
   \frac{4C b_T^{1/2}}{P\gamma} \vtSuma \sum_{l=\vttLower}^{\vttUpper} \lVert
-  D_{t+l+R,R} - D_{t,t+l+R}^* \rVert_2 W(l/\gamma) \\&
+  D_{t+l+R} - D_{t,t+l+R}^* \rVert_2 W(l/\gamma) \\&
   \leq O\Bigg(\frac{b_T^{1/2}}{P\gamma}\Bigg) \vtSuma

### 2014-01-09 paper.tex
Tweak commit references in date field
Finesse summation indices in Lemma A4
This commit tweaks the summation indices in Lemma A4 to make them
easier to follow and closes #30.

@@
   \input{VERSION}
-  \date{\dinfo\ (version \hinfo)}
-  \markright{\dinfo\ (version \hinfo)}
+  \date{\dinfo\ (commit \hinfo)}
+  \markright{\dinfo\ (commit \hinfo)}
 }{}
@@
   Suppose Assumptions~\ref{asmp-1}--\ref{asmp-3} hold.  Let $b_T$ be a
-  sequence such that $b_T \to \infty$ and $b_T = o(P)$ and define
+  sequence of integers such that $b_T \to \infty$ and $b_T = o(P)$ and define
   \begin{equation*}
@@
     \label{eq:12}
-    \sum_{t=-P+1}^{2P} (Z_{1t} Z_{2t} - \E_R Z_{1t} Z_{2t}) \to^p 0.
+    \vtSum (Z_{1t} Z_{2t} - \E_R Z_{1t} Z_{2t}) \to^p 0.
   \end{equation}
@@
   &\quad+ \vtSumr \vtSumb \vtIIIsummand \\
-  &\quad+ \sum_{t=r b - P + 1}^{2P} \vtIIIsummand \\
+  &\quad+ \sum_{t=r b_T - P + R + 1}^{2P+R} \vtIIIsummand \\
   &\equiv \vtSumr (U_i - \E_R U_i) + \vtSumr (U_i' - \E_R U_i') + o_{L_1}(1).
@@
 0$ and use Lemma \ref{lem-basic-coupling} to define $D_{ts}^*$
-for each $t =(2i-2)b_T-P+1,\dots,(2i-1)b_T-P$ and $s =
-\max(t+R-b_T,R-\h+1),\dots,\min(t+R+b_T,T)$ such that
+for each $t =(2i-2)b_T-P+R+1,\dots,(2i-1)b_T-P+R$ and $s =
+\max(t-b_T,R+1),\dots,\min(t+b_T,T-\h)$ such that
 \begin{equation*}
@@
 \begin{equation*}
-  \lVert D_{ts}^* - D_s \rVert_2 \leq \couplingBound{s - (2i-2m-1)b_T-R+P}.
+  \lVert D_{ts}^* - D_s \rVert_2 \leq \couplingBound{s - (2i-2m-1)b_T+P}.
 \end{equation*}
@@
 \begin{equation*}
-  Z_{1t}^* = 1/\sqrt{P\gamma} \sum_{l=\vttLower}^{\vttUpper}
-  (D_{t,t+l+R}^* - \E_R D_{t,t+l+R}^*)\ W(l/\gamma), \\
+  Z_{1t}^* = (P\gamma)^{-1/2} \sum_{l=\vttLower}^{\vttUpper}
+  (D_{t,t+l}^* - \E_R D_{t,t+l}^*)\ W(l/\gamma), \\
 \end{equation*}
@@
 \begin{equation*}
-Z_{2t}^* = 1/\sqrt{P\gamma} \sum_{j=\vttLower}^{\vttUpper}
-    (D_{t,t+l+R}^* - \E_R D_{t,t+l+R}^*)\ \kernelB{j/\gamma}.
+Z_{2t}^* = (P\gamma)^{-1/2} \sum_{j=\vttLower}^{\vttUpper}
+    (D_{t,t+l}^* - \E_R D_{t,t+l}^*)\ \kernelB{j/\gamma}.
 \end{equation*}
@@
   \frac{4C b_T^{1/2}}{P\gamma} \vtSuma \sum_{l=\vttLower}^{\vttUpper} \lVert
-  D_{t+l+R} - D_{t,t+l+R}^* \rVert_2 W(l/\gamma) \\&
+  D_{t+l} - D_{t,t+l}^* \rVert_2 W(l/\gamma) \\&
   \leq O\Bigg(\frac{b_T^{1/2}}{P\gamma}\Bigg) \vtSuma

### 2014-01-09 paper.tex
Add definition of gamma and eta to Lemma A4
This commit add some definitions to the proof of lemma A4:
- gamma
- delta
- eta
and changes the gamma notation to gamma_T for the proof.
Those terms are used in the proof but had not been defined.

This commit closes #31.

@@
   \end{gather*}
-  then
+  with $\delta > 0$, $\eta_\delta$ defined in the proof of
+  Lemma~\ref{res-variance-estimator}, and $\gamma_T = b_T/\delta$, then
   \begin{equation}
@@
 
-Note that $\{Z_{1t}^2 P\gamma/b_T\}$ and $\{Z_{2t}^2 P\gamma/b_T\}$
+Note that $\{Z_{1t}^2 P\gamma_T/b_T\}$ and $\{Z_{2t}^2 P\gamma_T/b_T\}$
 are uniformly integrable.  As in~\citet[Lemma A.4]{JoD:00}, we can
 assume that there is a constant $C$ such that $Z_{1t}$ and $Z_{2t}$
-are bounded in absolute value by $C\sqrt{b_T/P\gamma}$; uniform
+are bounded in absolute value by $C\sqrt{b_T/P\gamma_T}$; uniform
 integrability ensures that the difference between the unbounded random
@@
 \begin{equation*}
-  Z_{1t}^* = (P\gamma)^{-1/2} \sum_{l=\vttLower}^{\vttUpper}
-  (D_{t,t+l}^* - \E_R D_{t,t+l}^*)\ W(l/\gamma), \\
+  Z_{1t}^* = (P\gamma_T)^{-1/2} \sum_{l=\vttLower}^{\vttUpper}
+  (D_{t,t+l}^* - \E_R D_{t,t+l}^*)\ W(l/\gamma_T), \\
 \end{equation*}
@@
 \begin{equation*}
-Z_{2t}^* = (P\gamma)^{-1/2} \sum_{j=\vttLower}^{\vttUpper}
-    (D_{t,t+l}^* - \E_R D_{t,t+l}^*)\ \kernelB{j/\gamma}.
+Z_{2t}^* = (P\gamma_T)^{-1/2} \sum_{j=\vttLower}^{\vttUpper}
+    (D_{t,t+l}^* - \E_R D_{t,t+l}^*)\ \kernelB{j/\gamma_T}.
 \end{equation*}
@@
   + \lVert Z_{2t} - Z_{2t}^* \rVert_2 \lVert Z_{1t}^* \rVert_{\infty}) \\
-  &\leq \frac{2 C b_T^{1/2}}{(P\gamma)^{1/2}} \vtSuma (\lVert Z_{1t} - Z_{1t}^* \rVert_2
+  &\leq \frac{2 C b_T^{1/2}}{(P\gamma_T)^{1/2}} \vtSuma (\lVert Z_{1t} - Z_{1t}^* \rVert_2
   + \lVert Z_{2t} - Z_{2t}^* \rVert_2).
@@
 \begin{align*}
-  \frac{2 C b_T^{1/2}}{(P \gamma)^{1/2}} &\vtSuma \lVert Z_{1t} - Z_{1t}^* \rVert_2 \\& \leq
-  \frac{4C b_T^{1/2}}{P\gamma} \vtSuma \sum_{l=\vttLower}^{\vttUpper} \lVert
-  D_{t+l} - D_{t,t+l}^* \rVert_2 W(l/\gamma) \\&
-  \leq O\Bigg(\frac{b_T^{1/2}}{P\gamma}\Bigg) \vtSuma
+  \frac{2 C b_T^{1/2}}{(P \gamma_T)^{1/2}} &\vtSuma \lVert Z_{1t} - Z_{1t}^* \rVert_2 \\& \leq
+  \frac{4C b_T^{1/2}}{P\gamma_T} \vtSuma \sum_{l=\vttLower}^{\vttUpper} \lVert
+  D_{t+l} - D_{t,t+l}^* \rVert_2 W(l/\gamma_T) \\&
+  \leq O\Bigg(\frac{b_T^{1/2}}{P\gamma_T}\Bigg) \vtSuma
   \sum_{l=\vttLower}^{\vttUpper} \couplingBeta{t+l-(2i-2m-1)b_T+P}\\&
-  = O\Bigg(\frac{b_T^{1/2}}{P\gamma}\Bigg) O(b_T^{3/2-u}\, m^{-1/2-u})
+  = O\Bigg(\frac{b_T^{1/2}}{P\gamma_T}\Bigg) O(b_T^{3/2-u}\, m^{-1/2-u})
 \end{align*}
@@
 \[
-E\Big(\vtSumr (U_i - \E_R U_i)\Big)^2 = o\Big(\vtSumr b_T^2/P\gamma\Big) =
- o(b_T/\gamma) \to 0,
+E\Big(\vtSumr (U_i - \E_R U_i)\Big)^2 = o\Big(\vtSumr b_T^2/P\gamma_T\Big) =
+ o(b_T/\gamma_T) \to 0,
 \]

### 2014-01-30 paper.tex
Clean up end of Lemma A5
This commit makes a few statements at the end of Lemma A5
explicit and closes #32.
Add definition of pseudo-true model parameters
This commit adds a definition of \theta_1 and \theta_2. This commit
closes #1.
Clear up confusing sentence about what the oos test *doesn't* measure
This commit tries to clear up a point of confusion for one of the
referees and closes #13

@@
 variables $y_t$, $x_{1t}$, and $x_{2t}$ are all known in period $t$.
-Let
+The coefficients $\theta_1$ and $\theta_2$ minimize the population
+Mean Square Error, so
+\begin{equation*}
+  \theta_i = \argmin_\theta \sum_{t=1}^{T-\h} \E (y_{t+\h} - x_{it}'\theta)^2,
+\end{equation*}
+making $\e_{i,t+\h}$ uncorrelated with $x_{i,t}$. Let
 \begin{equation*}
@@
 test hypotheses about $\E_T \oosB$ and not the performance of the
-pseudo-true models or the unconditional performance of the models.
+pseudo-true models or the unconditional performance of the
+models.\footnote{i.e. $\E L(\e_{1,t+\h}) - \E  L(\e_{2,t+\h})$ or $\E \oosB$.
+Note that the expectation of $\E_T \oosB$ equals $\E \oosB$ but that
+$\sqrt{P} (\E_T \oosB - \E \oosB)$ may not be asymptotically normal,
+which would be necessary for testing.}
 This application to testing can be expressed as its own theorem:
@@
 P^{-1} \oosSum{s}{1} (\E_R D_s^*)^2 = \Big(P^{-1} \oosSum{s}{1} \E_R
-D_s^*\Big)^2 \quad \text{a.s..}
+D_s^*\Big)^2 \quad \text{a.s.}
 \]
-
 Consequently,
 \begin{align*}
-P^{-1} \oosSum{s}{1} (\E_R D_s)^2 - (\E_R\oosA)^2 & =
-P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R D_s^*)^2]\\
-&\quad+ \Big(P^{-1} \oosSum{s}{1} \E_R D_s^*\Big)^2 - (\E_R\oosA)^2 \quad \text{a.s}.\\
-&= O_p\Big(P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R D_s^*)^2]\Big).
+P^{-1} \oosSum{s}{1}& (\E_R D_s)^2 - (\E_R\oosA)^2 \\
+&= P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R D_s^*)^2]
+ + \Big(P^{-1} \oosSum{s}{1} \E_R D_s^*\Big)^2 - (\E_R\oosA)^2 \quad \text{a.s}.\\
+&= O_p\Big(P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R D_s^*)^2]\Big)
+ + O_p\Big(P^{-1} \oosSum{s}{1} \E_R (D_s - D_s^*)\Big).
 \end{align*}
@@
 \Big\lVert P^{-1} \oosSum{s}{1} [(\E_RD_s)^2 - (\E_R D_s^*)^2] \Big\rVert_1
-&\leq P^{-1} \oosSum{s}{1} \lVert \E_RD_s - \E_R D_s^* \rVert_2 \lVert
-\E_RD_s + \E_R D_s^* \rVert_2
-\\ &\leq (4 B_L/P) \oosSum{s}{1} \lVert \E_RD_s - \E_R D_s^* \rVert_2,
+&\leq P^{-1} \oosSum{s}{1} \lVert \E_R (D_s - D_s^*) \rVert_2 \lVert
+\E_R (D_s + D_s^*) \rVert_2
+\\ &\leq (4 B_L/P) \oosSum{s}{1} \lVert \E_R (D_s - D_s^*) \rVert_2,
 \end{align*}
-and this last term vanishes as in the proof of Lemma~\ref{lem:a2}.
+and this last term vanishes as in the proof of Lemma~\ref{lem:a2},
+completing the proof.
 \end{proof}

### 2014-02-18 paper.tex
Edit introduction

@@
 corrections, proposed by \citet{ClM:01,ClM:05}, \citet{Mcc:07} and
-\citet{ClW:06,ClW:07}, seem to correct too much, though, and reject
+\citet{ClW:06,ClW:07}, seem to overcorrect for this problem, though, and reject
 too often when the benchmark model is more accurate.
@@
   allows the number of regressors to increase with $T$.  But in that
-  paper, they increase slowly enough that the \ols\ coefficients are
-  consistent and asymptotically normal.}  \citet{GiW:06} and
+  paper, the number of regressors increases slowly enough that the \ols\
+  coefficients are consistent and asymptotically normal.} \citet{GiW:06} and
 \citet{GiR:09, GiR:10} are exceptions.  Instead of focusing on
@@
 test similar hypotheses, one might expect that they would give similar
-results.  They do not.  Generally in-sample analysis supports more
-complicated theoretical models and \oos\ analysis supports simple
+results.  They do not.  In-sample analyses tend to support more
+complicated theoretical models and \oos\ analyses support simple
 benchmarks, as seen in \citet{MeR:83}, \citet{StW:03}, and
@@
 
+But we also identify new practical limitations for applying the \dmw\
+test to overfit models.
 Since the models' coefficients are imprecisely estimated in the limit,
@@
 
-Since the \ols\ coefficient estimator is no longer consistent or
-asymptotically normal, the $F$-test and Wald tests are no longer
-asymptotically valid.  Moreover, \citet{Efr:86,Efr:04} shows that
-naive comparisons of in-sample loss overestimate models' accuracy by a
-factor proportional to $K/T$; $K$ is the number of regressors.  But
-modifications of the $F$-test are valid under this asymptotic theory,
-as shown by \citet{BoB:95}, \citet{AkA:00}, \citet{AkP:04},
-\citet{Cal:11c}, and \citet{Ana:12}, among others.  These results
-establish that hypotheses about the parameters of the \dgp\ can be
-tested in-sample even if one or both models are overfit.  For that
-very reason, these tests can not reliably choose a model for
-forecasting and will reject the benchmark too often.  We show this
-analytically in Section~\ref{sec:insample} and present analogous
-results for model selection.  Moreover, under this asymptotic theory,
-many recent \oos\ test statistics, such as those derived by
-\cite{ClM:01,ClM:05}, \citet{Mcc:07}, and \citet{ClW:06,ClW:07} should
-have the same problems as in-sample tests.\footnote{Our theoretical
-  results apply directly to \citepos{Mcc:07} \oos\ $t$-test, since it
-  simply proposes more liberal critical values for the same test
-  statistic that we study.  Since \citet{ClW:06,ClW:07} use a finite
-  length estimation window, our asymptotics are incompatible with
-  theirs and prevent us from studying their test directly, as well as
+Popular in-sample tests and model selection criteria, like the Wald
+test, AIC, and BIC, do not help forecasters in this setting. We show
+that these statistics can no pick out the more accurate model. For
+many \dgp s they will choose a larger alternative model over a small
+benchmark model with probability approaching one, regardless of which
+model is more accurate.\footnote{Our result holds for a broad class of
+  full-sample statistics, but there may be other potential statistics
+  that mimic the \oos\ test and remain valid. Exploring such
+  statistics is left for future research.}
+This result holds even though modifications of the $F$-test are valid
+under this asymptotic theory, as shown by \citet{BoB:95},
+\citet{AkA:00}, \citet{AkP:04}, \citet{Cal:11c}, and \citet{Ana:12},
+among others.\footnote{Also see \citet{Efr:86,Efr:04} for a discussion
+  of naive in-sample loss comparisons.}
+Moreover, under this asymptotic theory, many recent \oos\ test
+statistics, such as those derived by \cite{ClM:01,ClM:05},
+\citet{Mcc:07}, and \citet{ClW:06,ClW:07} should have the same
+problems as in-sample tests.\footnote{Our theoretical results apply
+  directly to \citepos{Mcc:07} \oos\ $t$-test, since it simply
+  proposes more liberal critical values for the same test statistic
+  that we study.  Since \citet{ClW:06,ClW:07} use a finite length
+  estimation window, our asymptotics are incompatible with theirs and
+  prevent us from studying their test directly, as well as
   \citepos{GiW:06} and other tests based on \citepos{GiW:06}
@@
 the \dmw\ test when $P$ is small, but should overreject the benchmark
-when $P$ is large.  Section~\ref{sec:mc} presents simulations that
-support these claims.
+when $P$ is large. Section~\ref{sec:insample} presents our theoretical
+results for full-sample statistics and Section~\ref{sec:mc} presents
+Monte Carlo evidence to support these claims.
 

### 2014-02-18 paper.tex
Edit introduction to setup/assumptions section

@@
 \section{Setup and Assumptions}\label{sec:assumptions}
-We will set up our models and notation first, then list the assumptions
-required for our results.
+The first part of this section will describe the environment in detail
+and set up our models and notation. The second part will list the
+assumptions underlying our theoretical results.
 
@@
 \]
-$t = 1,\dots,T-h$, $\h$ is the forecast horizon, and the
+$t = 1,\dots,T-h$, $\h$ is the forecast horizon and the
 variables $y_t$, $x_{1t}$, and $x_{2t}$ are all known in period $t$.
@@
 \end{equation*}
-making $\e_{i,t+\h}$ uncorrelated with $x_{i,t}$. Let
-\begin{equation*}
-  \mathcal{F}_t = \sigma(y_1, x_1, \dots, y_t, x_t)
-\end{equation*}
-with $x_t$ the vector of all elements of $x_{1t}$ and $x_{2t}$ after
+making $\e_{i,t+\h}$ uncorrelated with $x_{i,t}$; $\e_{i,t+\h}$ may exhibit
+serial correlation so both of the linear models may be misspecified.
+Let $\mathcal{F}_t = \sigma(y_1, x_1, \dots, y_t, x_t)$ be the information
+set available to the forecaster in period $t$,
+with $x_t$ the vector of all stochastic elements of $x_{1t}$ and $x_{2t}$ after
 removing duplicates, and let $\E_t$ and $\var_t$ denote the

### 2014-02-18 paper.tex
Remove incorrect line about allowing Q = 1
Rewrite setup section of paper

@@
 uses $K_1$ regressors, and the second uses $K_2$.  Without loss of
-generality, assume that $K_1 \leq K_2$.  We will allow $K_1$ and $K_2$
-to vary with $T$, so a stochastic array underlies all of our
-asymptotic theory, but we suppress that notation to simplify the
-presentation.
-
-The forecaster observes the data $(y_t,x_t)$ for periods 1 through $T$
-and divides them into an estimation sample of the first $R$
-observations and a test sample of the remaining $P$ observations.
-After choosing one of the models, the forecaster will use that model
-to make predictions for periods $T + h + 1$ through $T + h + Q$, where
-$Q$ is a known positive integer.  The forecaster's goal is to choose
-the model that will have lower average loss over periods $T+h+1$ through
-$T+h+Q$, evaluated by the known loss function $L$.  We allow $Q = 1$,
-so this setup generalizes the problem of choosing a model for a single
-prediction.
-
-Both models are estimated using \ols\ with a fixed window:
-\[
-\hat y_{i,t+\h} = x_{it}'\hat{\theta}_{it}, \qquad i=1,2, \qquad t
-= R+1,\dots,T-h
-\]
-with
-\begin{equation*}
-  \bh{it} =
-  \begin{cases}
-    \big(\sum_{s=1}^{R-\h} x_{is}x_{is}'\big)^{-1} \sum_{s=1}^{R-\h}
-    x_{is} y_{s+\h} & t \leq T \\
-    \big(\sum_{s=1}^{T-\h} x_{is}x_{is}'\big)^{-1}
-    \sum_{s=1}^{T-\h} x_{is} y_{s+\h} & t > T.
-  \end{cases}
-\end{equation*}
-The observed \oos\ average is denoted $\oosA$: \[\oosA \equiv P^{-1}
-\oosSum{t}{1} D_t\]  with
-\[
-D_t \equiv L(y_{t+\h} - x_{1t}'\bh{1t}) - L(y_{t+\h} - x_{2t}'\bh{2t}).
-\]
-The \oos\ statistic of interest is $\oost \equiv \sqrt{P} \oosA /
-\sh$, for $\sh^2$ some (possibly Heteroskedasticity- and
-Autocorrelation-Consistent, or \hac) estimator of the asymptotic
-variance of $\oosA$.
-
-As discussed above, the forecaster's goal is to choose the model with
-lower average future loss; i.e. to determine whether $\oosB$ is
-positive or negative,with
-\[
-\oosB \equiv Q^{-1} \sum_{t=T+1}^{T+Q} D_t.
-\]
-Note that the coefficients are reestimated with the full dataset.
-Since the forecaster's information set, $\mathcal{F}_T$, does not
-contain $\oosB$, he or she should decide between the models based on
-the conditional expectation, $\E_T \oosB$. If this quantity is
-positive, the first model is expected to perform the worst in the
-future, and if it is negative the second is.
-
-This conditional expectation is related to several well known measures
-of model performance.  In the limit, $\E_{T} \bar{D}_{T}$ converges to
-the difference in the models' generalization error and the two are
-equal in finite samples for i.i.d. data.  Moreover, if the data are
-i.i.d., the expectation of $\E_T \oosB$ equals \citepos{Aka:69} Final
-Prediction Error (\textsc{fpe}).  Both generalization error and
-\textsc{fpe} are defined by the model's performance on a new,
-independent, data set; here the new data are not independent in finite
-samples, but are asymptotically independent.  For the rest of the
-paper, we will call $\E_T \oosB$ the difference in generalization
-error with hopefully no risk of confusion.
+generality, assume that $K_1 \leq K_2$. At least one of the models is
+overfit, which we represent asymptotically by letting $K_2$ grow with
+$T$ quickly enough that $\lim K_2/T$ is positive; $K_1$ may grow with
+$T$ as well. Since the number of regressors changes with $T$, a
+stochastic array underlies all of our asymptotic theory, but we
+suppress that notation to simplify the presentation.
+
+In the settings we are interested in, a forecaster observes the data
+$(y_t,x_t)$ for periods 1 through $T$ and divides the observations
+into an estimation sample of the first $R$ observations and a test
+sample of the remaining $P$ observations. The forecaster then compares
+the models' performance over the test sample, which entails
+constructing two sequences of forecasts, (using a fixed-window
+estimation strategy)
+\begin{equation}
+\hat y_{i,t+\h} = x_{it}'\hat{\theta}_{it}, \qquad \text{for } i=1,2;
+\ t = R+1,\dots,T-h,
+\end{equation}
+where
+\begin{equation}
+  \bh{it} = \Big(\sum_{s=1}^{R-\h} x_{is}x_{is}'\Big)^{-1} \sum_{s=1}^{R-\h}
+  x_{is} y_{s+\h}, \qquad \text{for } i=1,2;\ t = R+1,\dots, T - \h.\footnote{It
+    may not be clear why we are using a $t$ index in $\bh{it}$,
+    since $\bh{it} = \bh{iR}$ almost surely for all $t \leq T-h$.
+    We need this index because $\bh{it}$ will be defined for $t > T-\h$
+    soon, and will not equal $\bh{iR}$ for those values of $t$.}
+\end{equation}
+
+The models are then compared by their forecast errors over the test
+sample.  There are many statistics that could be used to make this
+comparison, but we focus on perhaps the most natural, the \dmw\ \oost\
+test \citep{DiM:95,Wes:96}.\footnote{The core insights of our paper
+  apply to other \oos\ statistics as well.} This statistic is based on
+the difference in the models' loss over the test sample, $\oosA$,
+defined as
+\begin{equation}
+  \oosA \equiv P^{-1} \oosSum{t}{1} D_t
+\end{equation}
+where
+\begin{equation}\label{eq:16}
+  D_t = L(y_{t+\h} - x_{1t}'\bh{1t}) - L(y_{t+\h} - x_{2t}'\bh{2t}),
+\end{equation}
+and $L$ is a known loss function. Now the \oost\ test is defined as
+$\sqrt{P} \oosA / \sh$, where $\sh^2$ is an estimator of the
+asymptotic variance of $\oosA$. (Possibly a Heteroskedasticity- and
+Autocorrelation-Consistent, or \hac, estimator.)
+
+There are several hypotheses that the \oost\ test has been used
+for. Most theoretical work, such as \citet{DiM:95}, \citet{Wes:96},
+and \cite{Mcc:07}, has focused on using these statistics to test
+hypotheses about the pseudo-true values $\theta_1$ and $\theta_2$.  In
+particular, that research focuses on testing the null hypothesis that
+\begin{equation}
+  \E L(y_{t+\h} - x_{1t}'\theta_{1}) = \E L(y_{t+\h} - x_{2t}'\theta_{2}).
+\end{equation}
+Another possibility is that the forecaster will use one of the models
+to make a number of predictions in the future---call the number of
+predictions $Q$---in which case the quantity of interest is
+\begin{equation}
+  \E_T \oosB \equiv Q^{-1} \sum_{t=T+1}^{T+Q} \E_T D_t,
+\end{equation}
+where $D_t$ is defined in Equation~\eqref{eq:16} but here uses the
+full-sample estimates of the models' parameters,
+\begin{equation}
+  \bh{it} = \Big(\sum_{s=1}^{T-\h} x_{is}x_{is}'\Big)^{-1} \sum_{s=1}^{T-\h}
+  x_{is} y_{s+\h}, \qquad \text{for } i=1,2;\ t = T+1,\dots, T + Q.
+\end{equation}
+If $\E_T \oosB$ is positive, the second model is expected to forecast
+better than the first over the next $Q$ periods, and if $\E_T \oosB$
+is negative then the first model is better. We use a conditional
+expectation because the coefficient estimates in $\oosB$ are
+stochastic but known in period $T$, and their values will determine
+the performance of the two models.
+
+Under conventional fixed-$K$ asymptotic theory, $\E_T \oosB$ would
+converge in probability to the difference in the expected loss
+associated with the pseudo-true models,\footnote{Under appropriate
+  stationarity, moment, and weak-dependence conditions, obviously.}
+\begin{equation}\label{eq:22}
+  \E L(y_{t+\h} - x_{1t}'\theta_{1}) - \E L(y_{t+\h} - x_{2t}'\theta_{2}).
+\end{equation}
+But if $K_2$ increases with $T$ these quantities can have different
+limits. For a simple example, assume squared-error loss, let $x_{1,t}
+= 1$ for all $t$, and let $(y_{t+\h},x_{2,t})$ be i.i.d. $N(0,
+\Sigma)$.  Then
+\begin{align*}
+  \E_T \oosB - & \big(\E L(y_{t+\h} - x_{1t}'\theta_{1}) - \E L(y_{t+\h} - x_{2t}'\theta_{2})\big) \\
+  &= \big(\E_T (y_{T+\h+1} - \bh{1,T})^2 - \E_T (y_{T+\h+1} - x_{T+1}'\bh{2,T})^2\big) -
+  \big(\E y_{T+\h+1}^2 - \E (y_{T+\h+1} - x_{T+1}'\theta_2)^2 \big)\\
+  &= (\bh{2,t} - \theta_2)' \Sigma_x (\bh{2,t} - \theta_2) + o_p(1).
+\end{align*}
+This last term has expectation $\var(y_T) \frac{K_2}{T - K_2 - 1}$ and
+would converge to zero if $K_2$ were fixed, but does not when $\lim
+K_2 / T > 0$. In Section~\ref{sec:oostheory} we show that the \oost\
+statistic can estimate $\E_T \oosB$ under our increasing $K$
+asymptotics and does not estimate the expected loss in~\eqref{eq:22}.
+
+Our conditional expectation has been studied heavily in
+cross-sectional settings with independent observations. In such a
+setting, $\E_T \oosB$ is equal to the difference in the models'
+\emph{generalization error}, which has been used widely in the machine
+learning literature \citep[see][for further discussion]{HTF:08}.
+Moreover, with i.i.d. observations, the expectation of $\E_T \oosB$
+equals \citepos{Aka:69} Final Prediction Error (\textsc{fpe}). Both
+generalization error and \textsc{fpe} are defined by a model's
+performance on a new, independent, data set, but, for lack of a better
+term, we will call $\E_T \oosB$ the difference in generalization error
+for the rest of the paper with hopefully no risk of confusion.
 
@@
 \bibliographystyle{abbrvnat}
-\bibliography{texextra/AllRefs}
+\bibliography{references}
 

### 2014-02-19 paper.tex
Change bibliography database
More revisions to notation and environment section

@@
 $y_{t+\h}$:
-\[
+\begin{equation}
 y_{t+\h} = x_{1t}'\theta_1 + \e_{1,t+h}, \quad\text{and}\quad
 y_{t+\h} = x_{2t}'\theta_2 + \e_{2,t+h};
-\]
+\end{equation}
 $t = 1,\dots,T-h$, $\h$ is the forecast horizon and the
@@
 Mean Square Error, so
-\begin{equation*}
+\begin{equation}
   \theta_i = \argmin_\theta \sum_{t=1}^{T-\h} \E (y_{t+\h} - x_{it}'\theta)^2,
-\end{equation*}
-making $\e_{i,t+\h}$ uncorrelated with $x_{i,t}$; $\e_{i,t+\h}$ may exhibit
+\end{equation}
+making $\e_{i,t+\h}$ uncorrelated with $x_{i,t}$; $\e_{i,t+\h}$ can exhibit
 serial correlation so both of the linear models may be misspecified.
 Let $\mathcal{F}_t = \sigma(y_1, x_1, \dots, y_t, x_t)$ be the information
-set available to the forecaster in period $t$,
+set available in period $t$,
 with $x_t$ the vector of all stochastic elements of $x_{1t}$ and $x_{2t}$ after
@@
 $T$ quickly enough that $\lim K_2/T$ is positive; $K_1$ may grow with
-$T$ as well. Since the number of regressors changes with $T$, a
+$T$ as well. Since the models change with $T$, a
 stochastic array underlies all of our asymptotic theory, but we
@@
     since $\bh{it} = \bh{iR}$ almost surely for all $t \leq T-h$.
-    We need this index because $\bh{it}$ will be defined for $t > T-\h$
-    soon, and will not equal $\bh{iR}$ for those values of $t$.}
+    But $\bh{it}$ will be defined for $t > T-\h$
+    soon and will not equal $\bh{iR}$ for those values of $t$.}
 \end{equation}
@@
 The models are then compared by their forecast errors over the test
-sample.  There are many statistics that could be used to make this
-comparison, but we focus on perhaps the most natural, the \dmw\ \oost\
+sample.  There are many statistics that have been considered in the
+literature, but we focus on perhaps the most natural, the \dmw\ \oost\
 test \citep{DiM:95,Wes:96}.\footnote{The core insights of our paper
@@
 \end{equation}
-and $L$ is a known loss function. Now the \oost\ test is defined as
+and $L$ is a known loss function. The \oost\ test is defined as
 $\sqrt{P} \oosA / \sh$, where $\sh^2$ is an estimator of the
@@
 
-There are several hypotheses that the \oost\ test has been used
-for. Most theoretical work, such as \citet{DiM:95}, \citet{Wes:96},
-and \cite{Mcc:07}, has focused on using these statistics to test
+Most theoretical research, such as \citet{DiM:95}, \citet{Wes:96},
+and \cite{Mcc:07}, has focused on using the \oost\ statistic to test
 hypotheses about the pseudo-true values $\theta_1$ and $\theta_2$.  In
 particular, that research focuses on testing the null hypothesis that
-\begin{equation}
-  \E L(y_{t+\h} - x_{1t}'\theta_{1}) = \E L(y_{t+\h} - x_{2t}'\theta_{2}).
-\end{equation}
-Another possibility is that the forecaster will use one of the models
-to make a number of predictions in the future---call the number of
-predictions $Q$---in which case the quantity of interest is
+\begin{equation}\label{eq:21}
+  \E L(y_{t+\h} - x_{1t}'\theta_{1}) - \E L(y_{t+\h} - x_{2t}'\theta_{2}) = 0.
+\end{equation}
+But the population quantities in \eqref{eq:21} do not determine which
+model is more accurate in finite samples and, under our asymptotics,
+in the limit when models are allowed to be overfit. The models'
+accuracy will also depend on the specific estimates of $\theta_1$ and
+$\theta_2$ used to produce the forecasts. In this setting, where the
+forecaster will use one of the models to make a number of predictions
+in the future---call the number of predictions $Q$---the quantity of
+interest becomes
 \begin{equation}
@@
 converge in probability to the difference in the expected loss
-associated with the pseudo-true models,\footnote{Under appropriate
-  stationarity, moment, and weak-dependence conditions, obviously.}
+associated with the pseudo-true models,\footnote{Under standard
+  stationarity, moment, and weak-dependence conditions.}
+
+i.e. the LHS of~\eqref{eq:21}.
 \begin{equation}\label{eq:22}
@@
 statistic can estimate $\E_T \oosB$ under our increasing $K$
-asymptotics and does not estimate the expected loss in~\eqref{eq:22}.
-
-Our conditional expectation has been studied heavily in
+asymptotics and does not estimate the expected loss associated with
+the pseudo-true coefficients.
+
+The conditional expectation $\E_T \oosB$ has been studied heavily in
 cross-sectional settings with independent observations. In such a
 setting, $\E_T \oosB$ is equal to the difference in the models'
-\emph{generalization error}, which has been used widely in the machine
+\emph{generalization error}, which has been used widely as a measure
+of model accuracy in the machine
 learning literature \citep[see][for further discussion]{HTF:08}.

### 2014-02-19 paper.tex
Fix extra parenthesis in caption
Begin to rewrite assumptions

@@
 
-We assume the next conditions hold throughout the paper.  The first
+The next conditions are assumed to hold throughout the paper.  The first
 assumption controls the dependence of the underlying random array.
-The second prevents the sequence of experiments from becoming
-degenerate as $T$ increases.  The third assumption controls the
+The second layes out the details of our asymptotic approximation.
+The third assumption controls the
 smoothness of the loss function and bounds the moments of the
@@
   greater than two and discussed further in Assumption \ref{asmp-3}.
-  Also, $K_1$ and $K_2$ are less than $R$, and $K_2/T$ and
-  $(K_2-K_0)/T$ are uniformly positive; $K_0$ is the number of
-  regressors shared by the two models ($K_1/T$ can be uniformly
-  positive as well, but is not required to be).
 \end{asmp}
 
-The first assumption is a standard condition on the dependence of the
-underlying stochastic array.  We assume that the array is absolutely
-regular instead of strong mixing, which is more common in
-econometrics, because absolute regularity admits a particular coupling
-argument \citep[reproduced in this paper as Lemma A.1]{Ber:79} that is
-unavailable for strong mixing sequences.  Please see, for example,
-\citet{Dav:94} for a discussion of these mixing conditions.
-
-Assumption \ref{asmp-2} rules out uninteresting cases where the
-forecast error vanishes.
+This assumption is a standard condition on the dependence of the
+underlying stochastic array. The only novelty is that we use
+absolute regularity instead of strong or uniform mixing as our
+weak dependence condition; absolute regularity admits a paricular
+coupling argument, ``Berbee's Lemma'' \citep[reproduced in this
+paper as Lemma A.1 for reference]{Ber:79} that is
+unavailable for strong mixing sequences; absolute regularity
+implies uniform mixing, so this assumption is not unduly strong.
+For a detailed discussion of these weak dependence conditions,
+please see, for example, \citet{Dav:94}.
+
+Our strict stationarity assumption is also somewhat stronger than is
+typically used; \citet{Wes:96} and \citet{Mcc:07}, for example,
+present results assuming covariance stationarity of the loss
+associated with the pseudo-true models. We need to make a stronger
+assumption because we will need to prove asymptotic results where the
+$\bh{it}$ remain random---so we would need covariance stationarity to
+hold for almost all estimates of $\theta_i$, and not just for the
+pseudo-true value.
+
+The next assumption describes our asymptotic experiment.
 \begin{asmp}\label{asmp-2}
+  The number of regressors for each model, $K_1$ and $K_2$, are less
+  than $R$, and $K_2/T$ and $(K_2-K_0)/T$ are uniformly positive;
+  $K_0$ is the number of regressors shared by the two models ($K_1/T$
+  can be uniformly positive as well, but is not required to be).
+
   The variance of $y_{t+\h}$ given $\mathcal{F}_t$ is uniformly
@@
   \text{and} \qquad \ep{iT} = (\e_{i,1+\h}, \dots, \e_{i,T})'.\]
+
   Additionally, the Euclidean norms of the pseudo-true coefficients,
@@
     \E\Big( \sum_{s,t=R+1}^{T-h} \e_s \e_t x_s x_t'
-    \,\Big|\, X_{R}'X_{R} \Big)\Big) = P v^2 \E x_t x_t'.
+    \,\Big|\, X_{R}'X_{R} \Big) = P v^2 \E x_t x_t'.
   \end{equation*}
@@
   \centering {\large Simulated Rejection Probability of DMW Test Under
-    $\E_T \oosB \leq 0$)} \input{mc/plots/size-dmwsize.tikz}
+    $\E_T \oosB \leq 0$} \input{mc/plots/size-dmwsize.tikz}
   \caption{Simulated rejection probabilities for the \protect\textsc{dmw}

### 2014-02-25 paper.tex
Edit assumptions

@@
 
+The next assumption establishes moment conditions for the \oos\ loss
+process and smoothness conditions for the loss function itself. The
+moment conditions are standard and apply to $D_t$, and the smoothness
+conditions are relatively weak.
+
 \begin{asmp}\label{asmp-3}
   The loss function $L$ is continuous, has finite left and right
-  derivatives almost everywhere, and $L(0) = 0$.  There is a constant
-  $B_L$ and a function $L'$ that bounds the left and right derivative
-  of $L$ such that $\|D_t\|_\rho \leq B_L$; $\|D_t^*\|_\rho \leq B_L$
-  for all $t$, where
+  derivatives, and $L(0) = 0$.  There is a constant $B_L$ and a
+  function $L'$ that bounds the left and right derivative of $L$ at
+  every point such that $\|D_t\|_\rho \leq B_L$; $\|D_t^*\|_\rho \leq
+  B_L$ for all $t$, where
   \begin{equation*}
@@
 
-This third assumption establishes basic moment and smoothness
-conditions for the \oos\ loss and forecasts.  The differentiability
-condition is weak and allows the loss function itself to be
-non-differentiable or even discontinuous; for example, absolute error
-and many asymmetric loss functions satisfy this assumption.
-
+The differentiability condition in Assumption~\ref{asmp-3} is weak and
+allows the loss function itself to be non-differentiable; for example,
+absolute error and many asymmetric loss functions satisfy this
+assumption.
+
+Assumption~\ref{asmp-4} controls the growth of the test and training
+samples.
 \begin{asmp} \label{asmp-4} $P, R, Q \to\infty$ and $P^2/T \to 0$ as
@@
 the assumption are new, in particular the requirement that $P^2/T \to
-0$.  See Lemma \ref{res-convergence} for a discussion of its
+0$.  See Lemma~\ref{res-convergence} for a discussion of its
 implications.  In practical terms, this assumption requires that the

### 2014-02-25 paper.tex
Change font to bitstream charter
Remove small caps

@@
 \input{macros}
+\usepackage[charter]{mathdesign}
 
@@
 \title{Out-of-Sample Comparisons of Overfit Models}
-\author{Gray Calhoun\thanks{email: \texttt{gcalhoun@iastate.edu}. I
+\author{Gray Calhoun\thanks{email: gcalhoun@iastate.edu. I
     would like to thank Julian Betts, Helle Bunzel, Marjorie Flavin,
@@
     International Symposium on Forecasting, the 2010 Joint Statistical
-    Meetings, the 2011 \textsc{nber}/\textsc{nsf} Time-Series
-    Conference, and in many seminars at \textsc{ucsd}, and espeically
+    Meetings, the 2011 NBER-NSF Time-Series
+    Conference, and in many seminars at UCSD, and espeically
     Graham Elliott for their valuable suggestions, feedback and advice
     in writing this paper.  I would also like to thank Amit Goyal for
-    providing computer code and data for his 2008 \textsc{rfs} paper
+    providing computer code and data for his 2008 RFS paper
     with Ivo Welch \citep{GoW:08}.} \\ Iowa State University}
@@
   positive.  Our analysis gives a theoretical motivation for using
-  \oos\ comparisons: the \dmw\ \oos\ test allows a forecaster to
+  out-of-sample (OOS) comparisons: the DMW OOS test allows a forecaster to
   conduct inference about the expected future accuracy of his or her
@@
   results if researchers are concerned about overfit.  We show that
-  $P^2/T$ must converge to zero for the \dmw\ test to give valid
+  $P^2/T$ must converge to zero for the DMW test to give valid
   inference about the expected forecast accuracy, otherwise the test
@@
   larger than this.  Our simulations indicate that using large values
-  of $P$ with the \dmw\ test gives undersized tests with low power, so
+  of $P$ with the DMW test gives undersized tests with low power, so
   this practice may favor simple benchmark models too much.
 
-\noindent \textsc{jel} Classification: C12, C22, C52, C53
+\noindent JEL Classification: C12, C22, C52, C53
 
@@
 models is overfit.  In doing so, we provide a theoretical
-justification for forecasters to use \oos\ instead of in-sample
-comparisons: the \dmw\ \oos\ test\footnote{In this paper, we will
-  refer to the basic \oos\ $t$-test studied by \citet{DiM:95} and
-  \citet{Wes:96} as the \dmw\ test.} allows a forecaster to conduct
+justification for forecasters to use OOS instead of in-sample
+comparisons: the DMW OOS test\footnote{In this paper, we will
+  refer to the basic OOS $t$-test studied by \citet{DiM:95} and
+  \citet{Wes:96} as the DMW test.} allows a forecaster to conduct
 inference about the expected future accuracy of his or her models when
@@
 give misleading results if researchers are concerned about overfit.
-We show that $P^2/T$ must converge to zero for the \dmw\ test to give
+We show that $P^2/T$ must converge to zero for the DMW test to give
 valid inference about the expected forecast accuracy, otherwise the
@@
 than this.  Our simulations indicate that using large values of $P$
-with the \dmw\ test gives undersized tests with low power, so this
+with the DMW test gives undersized tests with low power, so this
 practice may favor simple benchmark models too much.  Existing
@@
 
-Although \oos\ comparisons have been popular in Macroeconomics and
+Although OOS comparisons have been popular in Macroeconomics and
 Finance since \citepos{MeR:83} seminal study of exchange rate models,
@@
 statistics are useful.  Empirical researchers often cite ``overfit''
-or ``instability'' as reasons for using \oos\ comparisons, as in
+or ``instability'' as reasons for using OOS comparisons, as in
 \citet{StW:03}, but neither term is precisely defined or formalized.
@@
 example, \citet{DiM:95} and \citet{Wes:96} derive the limiting
-distributions of many popular \oos\ test statistics under conditions
+distributions of many popular OOS test statistics under conditions
 that would justify these full-sample tests.  Much
@@
   allows the number of regressors to increase with $T$.  But in that
-  paper, the number of regressors increases slowly enough that the \ols\
+  paper, the number of regressors increases slowly enough that the OLS
   coefficients are consistent and asymptotically normal.} \citet{GiW:06} and
@@
 hypotheses that can be tested by in-sample comparisons, \citet{GiW:06}
-derive an \oos\ test for the null hypothesis that the difference
-between two models' \oos\ forecasting performance is unpredictable, a
-martingale difference sequence; \citet{GiR:09} test whether the \oos\
+derive an OOS test for the null hypothesis that the difference
+between two models' OOS forecasting performance is unpredictable, a
+martingale difference sequence; \citet{GiR:09} test whether the OOS
 forecasting performance of a model suffers from a breakdown relative
@@
 forecasting performance is stable. However, those papers focus on a
-particular \oos\ estimation strategy and do not address why \oos\
+particular OOS estimation strategy and do not address why OOS
 comparisons might be useful as a general strategy.
 
-Since in-sample and \oos\ statistics require similar assumptions and
+Since in-sample and OOS statistics require similar assumptions and
 test similar hypotheses, one might expect that they would give similar
 results.  They do not.  In-sample analyses tend to support more
-complicated theoretical models and \oos\ analyses support simple
+complicated theoretical models and OOS analyses support simple
 benchmarks, as seen in \citet{MeR:83}, \citet{StW:03}, and
@@
 the outcome of research, it is important to know when each is
-appropriate.  The explanations in favor of \oos\ comparisons claim
+appropriate.  The explanations in favor of OOS comparisons claim
 that they should be more robust to unmodeled instability
@@
 \citep{Mcc:98,Cla:04}.  Both explanations presume that the in-sample
-comparison is invalid and the \oos\ comparisons are more reliable.  Of
-course, as \citet{InK:04,InK:06} point out, both in-sample and \oos\
-methods could be valid, but the \oos\ methods could have lower power.
+comparison is invalid and the OOS comparisons are more reliable.  Of
+course, as \citet{InK:04,InK:06} point out, both in-sample and OOS
+methods could be valid, but the OOS methods could have lower power.
 
@@
 ``instability'' to future research. This paper uses dimension
-asymptotics to study the behavior of \oos\ comparisons when at least
+asymptotics to study the behavior of OOS comparisons when at least
 one of the models is overfit---the number of its regressors
@@
 example,][]{Whi:00,Han:05,RoW:05,HHK:10,ClM:12b}, but it is unclear
-whether those procedures should themselves use in-sample or \oos\
-comparisons.  Understanding the difference between in-sample and \oos\
+whether those procedures should themselves use in-sample or OOS
+comparisons.  Understanding the difference between in-sample and OOS
 comparisons in the context of a simple comparison between two models
@@
 comparisons. Moreover, the empirical research that motivates
-this paper uses \textit{pseudo} \oos\ comparisons and not
-\textit{true} \oos\ comparisons.  Even if a true \oos\ comparison
+this paper uses \textit{pseudo} OOS comparisons and not
+\textit{true} OOS comparisons.  Even if a true OOS comparison
 could account for some forms of data-snooping better than
-\citepos{Whi:00} \textsc{brc} or its extensions, in-sample and pseudo
-\oos\ comparisons would both be affected by the data-snooping, a
+\citepos{Whi:00} BRC or its extensions, in-sample and pseudo
+OOS comparisons would both be affected by the data-snooping, a
 point also made by \citet{InK:04}.
@@
 so that $\lim k/T$ is positive and less than one,
-the \ols\ coefficient estimator is no longer
+the OLS coefficient estimator is no longer
 consistent or asymptotically normal \citep{Hub:73} and has positive
-variance in the limit.  We show that, even so, the usual \oos\ average
+variance in the limit.  We show that, even so, the usual OOS average
 is asymptotically normal and can consistently estimate the difference
@@
 error does not converge to the expected performance of the pseudo-true
-models, so existing in-sample and \oos\ comparisons measure different
+models, so existing in-sample and OOS comparisons measure different
 quantities and should be expected to give different results for
 reasons beyond simple size and power comparisons.  Under our limit theory,
-the model that is closer to the true \dgp\ in population can forecast
+the model that is closer to the true DGP in population can forecast
 worse.  In such a situation, a standard in-sample comparison would
 correctly reject the null hypothesis that the benchmark is true, and
-an \oos\ comparison would correctly fail to reject the null that the
+an OOS comparison would correctly fail to reject the null that the
 benchmark is more accurate.\footnote{In a pair of papers similar to
-  ours, \citet{ClM:12,ClM:12b} study in-sample and \oos\ tests that
+  ours, \citet{ClM:12,ClM:12b} study in-sample and OOS tests that
   the larger model has nonzero coefficients that are too close to zero
@@
   they argue that the larger model can be true but less accurate.
-  However, they focus on an aspect of the \dgp\ that makes this
+  However, they focus on an aspect of the DGP that makes this
   phenomenon likely, while we focus on the coefficient estimates that
@@
   asymptotic theories are different and their papers do not provide
-  reasons to do \oos\ comparisons.}
+  reasons to do OOS comparisons.}
 Also note that, in this situation, a model that performs well
@@
 
-Our results can justify \oos\ comparisons when researchers want to
+Our results can justify OOS comparisons when researchers want to
 choose a model for forecasting.  Although there has been little
@@
 alternative model is higher than the cost of incorrectly failing to
-switch to a more accurate alternative.  We show that the \dmw\ test
+switch to a more accurate alternative.  We show that the DMW test
 lets the forecaster control the probability of the first error, just
@@
 
-But we also identify new practical limitations for applying the \dmw\
+But we also identify new practical limitations for applying the DMW
 test to overfit models.
@@
 and $P^2/T \to 0$ is required for valid confidence
-intervals and inference.  For larger $P$, the \oos\ comparisons remain
+intervals and inference.  For larger $P$, the OOS comparisons remain
 asymptotically normal, but are centered on the forecasting performance
@@
 typically use large values of $P$, so these studies may be too
-pessimistic about their models' future accuracy if they use the \dmw\
+pessimistic about their models' future accuracy if they use the DMW
 test.  Section~\ref{sec:oostheory} lays out the asymptotic behavior of
-the \dmw\ test under this limit theory.
+the DMW test under this limit theory.
 
@@
 that these statistics can no pick out the more accurate model. For
-many \dgp s they will choose a larger alternative model over a small
+many DGPs they will choose a larger alternative model over a small
 benchmark model with probability approaching one, regardless of which
@@
   full-sample statistics, but there may be other potential statistics
-  that mimic the \oos\ test and remain valid. Exploring such
+  that mimic the OOS test and remain valid. Exploring such
   statistics is left for future research.}
@@
   of naive in-sample loss comparisons.}
-Moreover, under this asymptotic theory, many recent \oos\ test
+Moreover, under this asymptotic theory, many recent OOS test
 statistics, such as those derived by \cite{ClM:01,ClM:05},
@@
 problems as in-sample tests.\footnote{Our theoretical results apply
-  directly to \citepos{Mcc:07} \oos\ $t$-test, since it simply
+  directly to \citepos{Mcc:07} OOS $t$-test, since it simply
   proposes more liberal critical values for the same test statistic
@@
   asymptotics.  But \clws\ test can be viewed as a stochastic
-  adjustment to the critical values of the usual \oos\ $t$ test, so
+  adjustment to the critical values of the usual OOS $t$ test, so
   our conclusions should apply informally as well.  Specifically, we
-  show that the \dmw\ test rejects with probability equal to nominal
+  show that the DMW test rejects with probability equal to nominal
   size when the estimated benchmark model is expected to be more
@@
 0$ (with the number of regressors fixed), these statistics behave like
-the \dmw\ test when $P$ is small, but should overreject the benchmark
+the DMW test when $P$ is small, but should overreject the benchmark
 when $P$ is large. Section~\ref{sec:insample} presents our theoretical
@@
 
-Finally, this paper also introduces a new method of proof for \oos\
+Finally, this paper also introduces a new method of proof for OOS
 statistics.  We use a coupling argument (Berbee's Lemma, 1979) to show
-that sequences of \oos\ loss behave like mixingales when the
+that sequences of OOS loss behave like mixingales when the
 underlying series are absolutely regular, even if the forecasts depend
@@
 the arguments used to prove asymptotic
-results for \ned\ functions of mixing processes can be used for these
-\oos\ processes with only slight modification.
+results for Near Epoch Dependent (NED) functions of mixing processes
+can be used for these OOS processes with only slight modification.
 
@@
 Section~\ref{sec:theory} gives the main theoretical results for the
-\dmw\ \oos\ test, shows that standard in-sample tests reject the
+DMW OOS test, shows that standard in-sample tests reject the
 benchmark model too often when it is false but more accurate than the
@@
 presents a Monte Carlo study supporting our theoretical results.
-Section~\ref{sec:empirics} applies the \oos\ statistic to
+Section~\ref{sec:empirics} applies the OOS statistic to
 \citepos{GoW:08} dataset for equity premium prediction, and
@@
 sample.  There are many statistics that have been considered in the
-literature, but we focus on perhaps the most natural, the \dmw\ \oost\
+literature, but we focus on perhaps the most natural, the DMW \oost\
 test \citep{DiM:95,Wes:96}.\footnote{The core insights of our paper
-  apply to other \oos\ statistics as well.} This statistic is based on
+  apply to other OOS statistics as well.} This statistic is based on
 the difference in the models' loss over the test sample, $\oosA$,
@@
 asymptotic variance of $\oosA$. (Possibly a Heteroskedasticity- and
-Autocorrelation-Consistent, or \hac, estimator.)
+Autocorrelation-Consistent, or HAC, estimator.)
 
@@
 Moreover, with i.i.d. observations, the expectation of $\E_T \oosB$
-equals \citepos{Aka:69} Final Prediction Error (\textsc{fpe}). Both
-generalization error and \textsc{fpe} are defined by a model's
+equals \citepos{Aka:69} Final Prediction Error (FPE). Both
+generalization error and FPE are defined by a model's
 performance on a new, independent, data set, but, for lack of a better
@@
 assumption controls the dependence of the underlying random array.
-The second layes out the details of our asymptotic approximation.
+The second lays out the details of our asymptotic approximation.
 The third assumption controls the
@@
 the behavior of the estimation and test windows.  And the last
-assumption describes the kernel used to estimate the \oos\ average's
+assumption describes the kernel used to estimate the OOS average's
 asymptotic variance.
@@
 absolute regularity instead of strong or uniform mixing as our
-weak dependence condition; absolute regularity admits a paricular
+weak dependence condition; absolute regularity admits a particular
 coupling argument, ``Berbee's Lemma'' \citep[reproduced in this
@@
 variance is straightforward.  The conditions on the eigenvalues are
-technical and control the behavior of the \ols\ estimator as the
+technical and control the behavior of the OLS estimator as the
 number of regressors gets large.  The restrictions on the pseudo-true
@@
   So the conditions amount to restrictions on the eigenvalues of
-  $X_T'X_T$, which are familiar from general \ols.
+  $X_T'X_T$, which are familiar from general OLS.
 \end{example}
 
-The next assumption establishes moment conditions for the \oos\ loss
+The next assumption establishes moment conditions for the OOS loss
 process and smoothness conditions for the loss function itself. The
@@
 absolute error and many asymmetric loss functions satisfy this
-assumption.
-
-Assumption~\ref{asmp-4} controls the growth of the test and training
-samples.
+assumption.  The next assumption controls the growth of the test and
+training samples.
 \begin{asmp} \label{asmp-4} $P, R, Q \to\infty$ and $P^2/T \to 0$ as
@@
 
-The next assumption restricts the class of variance estimators we will
+A final assumption restricts the class of variance estimators we will
 consider.  We use the same class of estimators studied by
@@
 (Assumption~\ref{asmp-4}).\footnote{\citet{Wes:96} does not have a
-  second \oos\ period, so there is no analogue in his paper to our
+  second OOS period, so there is no analogue in his paper to our
   restriction on $Q$.}  Obviously, these differences are
@@
 the size of the test sample.  West allows more general estimation
-methods, while we restrict attention to \ols; the advantage of using
-\ols\ is that we can derive the inequality,
-\begin{equation*}
-  \| x_{it}'\theta_{i,T+1} - x_{it}'\theta_{iR} \|_2 \leq O(P/T)^{1/2}.
+methods, while we restrict attention to OLS; the advantage of using
+OLS is that we can derive the inequality,
+\begin{equation*}
+  \| x_{it}'\bh{i,T+1} - x_{it}'\bh{iR} \|_2 \leq O(P/T)^{1/2}.
 \end{equation*}
@@
 The main result of the paper is Theorem
-\ref{res-confidence-intervals}, which shows that the \oos\ average is
+\ref{res-confidence-intervals}, which shows that the OOS average is
 asymptotically normal and centered on $\E_T \oosB$.  This result holds
@@
 \ref{res-confidence-intervals}, we explain and present two key Lemmas
-used in its proof that add some insight into the nature of \oos\
-comparisons, and then show that standard \hac\ \oos\ estimators can be
-used to consistently estimate the asymptotic variance of the \oos\
+used in its proof that add some insight into the nature of OOS
+comparisons, and then show that standard HAC OOS estimators can be
+used to consistently estimate the asymptotic variance of the OOS
 average.  We next present an example that illustrates some of these
@@
 \subsection{Behavior of the DMW Test with Overfit}\label{sec:oostheory}
-Our first theorem justifies using the \dmw\ $t$-test with a a short
+Our first theorem justifies using the DMW $t$-test with a a short
 test sample.
@@
 coefficients are estimated with uncertainty in the limit, the two
-models give different forecasts even if they both nest the \dgp.  This
+models give different forecasts even if they both nest the DGP.  This
 is intuitively similar to \citepos{GiW:06} rolling-window result, but
 comes from different asymptotic theory; Giacomini and White keep the
-variance of the \oos\ average positive by letting $P \to \infty$ with
+variance of the OOS average positive by letting $P \to \infty$ with
 $R$ fixed; in this paper, $R \to \infty$ but the variance remains
@@
 
-This result allows forecasters to use the \dmw\ test to conduct
-inference about the models' accuracy.  Since the \oos\ average,
+This result allows forecasters to use the DMW test to conduct
+inference about the models' accuracy.  Since the OOS average,
 $\oosA$, is asymptotically normal and centered on the expected future
-performance, $t$-tests constructed from the \oos\ errors necessarily
+performance, $t$-tests constructed from the OOS errors necessarily
 test hypotheses about $\E_T \oosB$ and not the performance of the
@@
 the process $\{D_t - \E_R \oosA\}$ is an $L_2$-mixingale of size
-$-1/2$ that satisfies a \clt, ensuring~\eqref{normalpart}.
+$-1/2$ that satisfies a CLT, ensuring~\eqref{normalpart}.
 
@@
 closest to common practice in applied research, the noise term
-dominates the asymptotic distribution of the \oos\ $t$-test and the
+dominates the asymptotic distribution of the OOS $t$-test and the
 test has only trivial power in the limit if it has correct size.
@@
 
-Mixingales satisfy a weak-dependence condition similar to \mds es and
+Mixingales satisfy a weak-dependence condition similar to MDSes and
 were introduced and studied extensively by
 \citet{Mcl:74,Mcl:75,Mcl:75b,Mcl:77}.  This lemma shows that the
-estimation uncertainty introduces dependence into the \oos\ forecast
+estimation uncertainty introduces dependence into the OOS forecast
 errors, but the additional dependence is contained in the term $\E_R
 \oosA$ and can be effectively removed by subtraction.  The second part
-of the Lemma shows that the basic mixingale \clt\ established by
+of the Lemma shows that the basic mixingale CLT established by
 \citet{Jon:97} applies in this setting.\footnote{De Jong proves two
-  \clt s: one for mixingales and one for \ned\ functions of mixing
+  CLTs: one for mixingales and one for NED functions of mixing
   processes.  His mixingale result makes assumptions about the
   behavior of the sample second moment that arise as consequences of
-  \ned.  The proof of Lemma~\ref{res-mixingale} shows that the
-  arguments used for de Jong's \ned\ \clt\ continue to hold for our
-  \oos\ process---in effect, that the \oos\ process has slightly more
+  NED.  The proof of Lemma~\ref{res-mixingale} shows that the
+  arguments used for de Jong's NED CLT continue to hold for our
+  OOS process---in effect, that the OOS process has slightly more
   structure than required for it to be a mixingale.}  Note that
@@
 need a consistent estimator of $\sigma^2$. Lemma
-\ref{res-variance-estimator} establishes that the usual \oos\ \hac\
+\ref{res-variance-estimator} establishes that the usual OOS HAC
 variance estimators are consistent.\footnote{As with
@@
       \citepos{JoD:00} existing consistency results
-      for \ned\ processes and shows that the same arguments can be
-      applied to our \oos\ mixingale.}
+      for NED processes and shows that the same arguments can be
+      applied to our OOS mixingale.}
 
@@
 making $\sigma^2$ uniformly a.s. positive and ensuring that the
-distribution of the \oos\ average is not $P^{1/2}$-degenerate.  The
-natural \oos\ variance estimator is consistent for $\sigma^2$:
+distribution of the OOS average is not $P^{1/2}$-degenerate.  The
+natural OOS variance estimator is consistent for $\sigma^2$:
 \begin{align*}
@@
 
-We can see that the \oos\ average obeys a \clt\ when centered at $\E_R
-\bar{D}_R$.  The centered and scaled \oos\ differences satisfy
+We can see that the OOS average obeys a CLT when centered at $\E_R
+\bar{D}_R$.  The centered and scaled OOS differences satisfy
 \begin{equation*}
@@
 \E_t(\oosA - \E_R\oosA) = 0$, making this sequence an
-\mds,\footnote{The sequence is actually exchangeable, but \mds\ is
-  enough to establish the \clt.} so it obeys a \clt\ as long as
+MDS,\footnote{The sequence is actually exchangeable, but MDS is
+  enough to establish the CLT.} so it obeys a CLT as long as
 $\sigma^2$ is uniformly a.s. positive, which we have already
-established.  Lemma~\ref{res-mixingale} ensures that the \clt\ holds
+established.  Lemma~\ref{res-mixingale} ensures that the CLT holds
 more generally.
@@
 if $P^3/T^2 \to 0$, which is slightly weaker than the general
-requirement that $P^2/T \to 0$.  If $\lim P^3/T^2 > 0$ the \oos\ average
-still obeys the \mds\ \clt, but it is not centered correctly at $\E_T
+requirement that $P^2/T \to 0$.  If $\lim P^3/T^2 > 0$ the OOS average
+still obeys the MDS CLT, but it is not centered correctly at $\E_T
 \oosB$.
@@
 centered at $\theta$ passing through the origin.
-Figure~\ref{fig:rreject} depicts these regions.  Since the \ols\
+Figure~\ref{fig:rreject} depicts these regions.  Since the OLS
 estimator is normal with mean $\theta$, the probability that
@@
 for overfit models for many common model selection methods, including
-adjusted $R^2$, the \aic, and the \bic.  Corollary~\ref{res:ic}
+adjusted $R^2$, the AIC, and the BIC.  Corollary~\ref{res:ic}
 contains the details.
@@
 \end{equation*}
-Just as we saw with the $F$-test, adjusted $R$-squared, the \aic\ and
-the \bic\ will only choose the benchmark model if $\hat{\theta}_T$
+Just as we saw with the $F$-test, adjusted $R$-squared, the AIC and
+the BIC will only choose the benchmark model if $\hat{\theta}_T$
 lies in the neighborhood of the cylinder defined by $\hat{\theta}_T
@@
 size of the neighborhood, with the neighborhood shrinking slower for
-the \bic\ than the \aic.
+the BIC than the AIC.
 
@@
   \citep{ShB:11:0.6.1}, and pgfSweave \citep{BrS:11:1.2.1} packages.}
-The first looks at the asymptotic normality of the \dmw\ statistic
+The first looks at the asymptotic normality of the DMW statistic
 centered on either $\E_R \oosA$ or $\E_T \oosB$.  The previous
@@
 generalization error.  For all of the simulations, we look at
-fixed-window \oos\ tests to speed up computation time.
+fixed-window OOS tests to speed up computation time.
 
@@
 environments---serial dependence, heteroskedasticity, and complicated
-\dgp s.  We simulate data for both studies from the equation
+DGPs.  We simulate data for both studies from the equation
 \begin{equation}\label{eq:6}
@@
 \end{equation}
-and the alternative model is the \dgp\ \eqref{eq:6}.  We let
+and the alternative model is the DGP \eqref{eq:6}.  We let
 $(K_1,K_2)$ equal either $(2,3)$ or $(T/20,T/10)$ to study our theory
@@
 Section~\ref{sec:oostheory} works in practice.  For each draw of $X$
-and $Y$, we construct a one-sided \oos\ interval of the
+and $Y$, we construct a one-sided OOS interval of the
 form
@@
 We look at four different statistics---the full-sample $F$-test, the
-\dmw\ $t$-test, the
-\oos\ $t$-test using McCracken's (2007)
+DMW $t$-test, the
+OOS $t$-test using McCracken's (2007)
 critical values,\footnote{These critical values are not published for
@@
 To estimate each test's size for the hypothesis \eqref{eq:9}, we draw
-samples from the \dgp\ and discard those for which \eqref{eq:9} does
+samples from the DGP and discard those for which \eqref{eq:9} does
 not hold, until we have 2000 for each choice of the design parameters.
@@
 is very small.  The poor behavior for small $P$ is unsurprising, as it
-simply means that the \clt\ is a poor approximation when the test
+simply means that the CLT is a poor approximation when the test
 sample is small.  The intervals' good coverage holds even for the
@@
 We next present the size simulations,
-Figures~\ref{fig:ftest}--\ref{fig:ttest-power}.  For the \oos\ tests,
+Figures~\ref{fig:ftest}--\ref{fig:ttest-power}.  For the OOS tests,
 the conditional rejection probability is plotted for each combination
@@
 
-Figure~\ref{fig:ttest-size} presents the size estimates for the \dmw\
+Figure~\ref{fig:ttest-size} presents the size estimates for the DMW
 $t$-test.  Again, different panels display results for different
@@
 We observe the following patterns.  The
-\dmw\ test has close to nominal size when $P$ is small for every
+DMW test has close to nominal size when $P$ is small for every
 combination of design parameters.  In most cases, the rejection
@@
 
-Since the \dmw\ test tends to have low rejection probability, the
+Since the DMW test tends to have low rejection probability, the
 test's power is a concern.  We'll present some power results,
@@
   results for that value of $c$.}  Figure~\ref{fig:ttest-power} plots
-the power for the \dmw\ test; since the other test statistics greatly
+the power for the DMW test; since the other test statistics greatly
 overreject, we do not present their power.  For $c=1$, the power is
@@
 Both sets of simulations support our theoretical results.  The first
-simulation confirms that the \dmw\ \oos\ $t$-test is centered at $\E_R
+simulation confirms that the DMW OOS $t$-test is centered at $\E_R
 \oosA$ for all choices of $P$ and $R$ and is centered on $\E_T \oosB$
-only when $P$ is small.  The second simulation confirms that the \dmw\
+only when $P$ is small.  The second simulation confirms that the DMW
 test has correct size for the null hypothesis that $\E_T \oosB \leq 0$
@@
 benchmark is true, like the $F$-test and Clark and West's (2006, 2007)
-and McCracken's (2007) \oos\ tests can reject by much more than their
+and McCracken's (2007) OOS tests can reject by much more than their
 nominal size when testing the null $\E_T \oosB \leq 0$.  Moreover,
 these simulations demonstrate that the restriction $P^2/T \to 0$ is
-binding in practice, as the \dmw\ test under-rejects and has very low
+binding in practice, as the DMW test under-rejects and has very low
 power when it is not satisfied.
@@
 different values of $R$ and $P$ to examine the effect of the training
-and test sample choice on this \oos\ statistic.  We find that the
-estimate of the larger model's \mse\ decreases relative to the
+and test sample choice on this OOS statistic.  We find that the
+estimate of the larger model's Mean Squared Error (MSE) decreases relative to the
 benchmark as $R$ increases, but it is never smaller than the
@@
 We'll start with a very brief review.  \citet{GoW:08}
-study the \oos\ forecasting performance of different variables thought
+study the OOS forecasting performance of different variables thought
 to predict the equity premium (calculated as the difference between
@@
   because the variables are linear combinations of other variables.}
-\citet{GoW:08} estimate the \oos\ forecasting
+\citet{GoW:08} estimate the OOS forecasting
 performance of bivariate models of the form
@@
 \]
-using \ols\ with a recursive window, where $r_{t+1}$ is the equity
+using OLS with a recursive window, where $r_{t+1}$ is the equity
 premium and $x_t$ is a generic predictor, as well as some larger
@@
 \end{eqnarray}
-respectively and are estimated by \ols\ using the fixed-window scheme.
+respectively and are estimated by OLS using the fixed-window scheme.
 The predictors are listed in Table~\ref{tab:equity}; for a detailed
@@
 \eqref{eq:3} and \eqref{eq:2}, but impose that $\hat r_{t+1}$ be
-non-negative for each forecast.  We then calculate the \oos\ test just
+non-negative for each forecast.  We then calculate the OOS test just
 as for the unconstrained model.
@@
 
-To study the effect of the training sample size on the \dmw\ statistic, we
+To study the effect of the training sample size on the DMW statistic, we
 calculate the one-sided confidence interval for $\E_T \oosB$ given
@@
 estimator with $\lfloor P^{1/4}\rfloor$ lags.  For small values of
-$R$, the \oos\ average is expected to underestimate the performance of
+$R$, the OOS average is expected to underestimate the performance of
 the larger model relative to the smaller, but this may not hold in
@@
 
-Figures~\ref{fig:empirics1} plots the \ols\ results and
+Figures~\ref{fig:empirics1} plots the OLS results and
 Figure~\ref{fig:empirics2} imposes \citepos{CaT:08} restriction.  The
-solid line in each figure shows the \oos\ average, $\oosA$, and the
+solid line in each figure shows the OOS average, $\oosA$, and the
 shaded region indicates the 95\% one-sided confidence interval implied
-by the \dmw\ test.  Negative numbers indicate that the kitchen sink
+by the DMW test.  Negative numbers indicate that the kitchen sink
 model has higher out-of-sample loss.  We can see that the same
@@
 \section{Conclusion}\label{sec:conclusion}
-This paper gives a theoretical motivation for using \oos\ comparisons:
-the \dmw\ \oos\ test allows a forecaster to conduct inference about
+This paper gives a theoretical motivation for using OOS comparisons:
+the DMW OOS test allows a forecaster to conduct inference about
 the expected future accuracy of his or her models when one or both is
@@
 can be relaxed only slightly; $P = O(T^{1/2})$ is required for the
-\oos\ test to have nontrivial power in general, but there are loss
-functions and \dgp s for which some relaxation is possible.  This
+OOS test to have nontrivial power in general, but there are loss
+functions and DGPs for which some relaxation is possible.  This
 constraint could be mitigated by extending our results to
@@
 \ref{res-variance-estimator}) are modifications of existing results
-for \ned\ functions of mixing processes by \citet{Jon:97} and
+for NED functions of mixing processes by \citet{Jon:97} and
 \citet{JoD:00}; this coupling argument is used to explicitly derive
-inequalities that arise naturally for \ned\ processes.  Lemma
+inequalities that arise naturally for NED processes.  Lemma
 \ref{lem-basic-coupling} establishes these inequalities, which are
@@
 The proof then holds if we can show that both $U_i$ and $U_i'$ obey
-\lln s.  We'll do so by proving that $\{U_i -\E_R U_i,
+LLNs.  We'll do so by proving that $\{U_i -\E_R U_i,
 \UFiltration{2i-1}\}$ and $\{U_i' - \E_R U_i', \UFiltration{2i}\}$ are
@@
 with the second term vanishing by Lemma \ref{res-mixingale} and
-\citepos{Dav:93} mixingale \lln.
+\citepos{Dav:93} mixingale LLN.
 
@@
 It suffices to prove asymptotic normality.  We can rewrite the
-centered \oos\ average as
+centered OOS average as
 \[
@@
 each of its nonzero eigenvalues are bounded in absolute value by the
-eivenvalues of $(X_{iR}'X_{iR})^{-1}$. The eivenvalues of
+eigenvalues of $(X_{iR}'X_{iR})^{-1}$. The eivenvalues of
 $(X_{iR}'X_{iR})^{-1}$ are $O_{L_3}(1/R)$ by Assumption~\ref{asmp-2}, so
@@
 \vspace{\baselineskip}
-\noindent\textit{Part 2.}  A modification of \citepos{Jon:97} \clt s for
-mixingale and \ned\ arrays will complete the proof.  Define
+\noindent\textit{Part 2.}  A modification of \citepos{Jon:97} CLTs for
+mixingale and NED arrays will complete the proof.  Define
 \[\label{eq:z1}
@@
 Note that $\{Z_i - E_{R + (i-1)b_T} Z_i,\mathcal{F}_{R + i b_T}\}_i$ is an
-\mds\ by construction, so \citepos{HaH:80} Theorem 3.2 and Corollary
+MDS by construction, so \citepos{HaH:80} Theorem 3.2 and Corollary
 3.1 ensure that $\sigma^{-1} \SumOuterBlock{i} Z_i \to^d N(0,1) $ as
@@
 \end{equation}
-Their proofs of \eqref{dd1}--\eqref{dd4} use the fact that \ned\
+Their proofs of \eqref{dd1}--\eqref{dd4} use the fact that NED
 functions of mixing processes are also mixingale processes and do not
-use any other properties specific to \ned\ processes, so they hold
+use any other properties specific to NED processes, so they hold
 here as well.  We do need to modify their proofs that
@@
 \end{equation}
-though, since their proofs exploit \ned\ properties.  The proofs
+though, since their proofs exploit NED properties.  The proofs
 follow from Lemmas~\ref{lem:a2} and~\ref{lem:a6}, since
@@
 \caption{Simulated coverage of $\E_R \oosA$ at 90\% confidence using a
-  one-sided interval based on the \protect\textsc{dmw}
-  \protect\textsc{oos} test, plotted as a function of the fraction of
+  one-sided interval based on the DMW
+  OOS test, plotted as a function of the fraction of
   observations used in the test sample, $P/T$.  The solid horizontal
@@
 \caption{Simulated coverage of $\E_T \oosB$ at 90\% confidence using a
-  one-sided interval based on the \protect\textsc{dmw}
-  \protect\textsc{oos} test, plotted as a function of the fraction of
+  one-sided interval based on the DMW
+  OOS, plotted as a function of the fraction of
   observations used in the test sample, $P/T$.  The solid horizontal
@@
     $\E_T \oosB \leq 0$} \input{mc/plots/size-dmwsize.tikz}
-  \caption{Simulated rejection probabilities for the \protect\textsc{dmw}
-    \protect\textsc{oos} $t$-test given $\E_T \oosB \leq 0$ with nominal
+  \caption{Simulated rejection probabilities for the DMW
+    OOS $t$-test given $\E_T \oosB \leq 0$ with nominal
     size 10\%.  Values greater than 10\% indicate that the test
@@
   \caption{Simulated rejection probabilities for Clark and West's
-    (2006, 2007) \protect\textsc{oos} test statistic given $\E_T \oosB
+    (2006, 2007) OOS test statistic given $\E_T \oosB
     \leq 0$ with nominal size 10\%.  Values greater than 10\% indicate
@@
   \caption{Simulated rejection probabilities for McCracken's (2007)
-    \protect \textsc{oos} test statistic given $\E_T \oosB \leq 0$ with
+    OOS test statistic given $\E_T \oosB \leq 0$ with
     nominal size 10\%.  Values greater than 10\% indicate that the
@@
     $\E_T \oosB > 0$} \input{mc/plots/size-dmwpower.tikz}
-  \caption{Simulated rejection probabilities for the \protect \textsc{dmw}
-    \protect\textsc{oos} $t$-test given $\E_T \oosB > 0$ with nominal
+  \caption{Simulated rejection probabilities for the DMW
+    OOS $t$-test given $\E_T \oosB > 0$ with nominal
     size 10\%.  Values greater than 10\% indicate that the test
@@
 \input{empirics/plots/oos-mse-1b.tikz}
-\caption{\protect \textsc{oos} difference in the \protect\textsc{mse}
+\caption{OOS difference in the MSE
   of the prevailing mean benchmark and the kitchen sink model as a
@@
   equity premium using annual data from 1928--2008.  The solid line
-  gives the \protect \textsc{oos} average, and the shaded region indicates the
-  one-sided 95\% confidence interval implied by the \protect
-  \textsc{dmw} test.  The bottom panel is a detailed view of the top
+  gives the OOS average, and the shaded region indicates the
+  one-sided 95\% confidence interval implied by the
+  DMW test.  The bottom panel is a detailed view of the top
   panel for $R \geq 50$.}
@@
 \input{empirics/plots/oos-mse-2b.tikz}
-\caption{\protect \textsc{oos} difference in the \protect\textsc{mse}
+\caption{OOS difference in the MSE
   of the prevailing mean benchmark and the kitchen sink model as a
@@
   equity premium using annual data from 1928--2008.  The solid line
-  gives the \protect \textsc{oos} average, and the shaded region indicates the
-  one-sided 95\% confidence interval implied by the \protect
-  \textsc{dmw} test.  The bottom panel is a detailed view of the top
+  gives the OOS average, and the shaded region indicates the
+  one-sided 95\% confidence interval implied by the 
+  DMW test.  The bottom panel is a detailed view of the top
   panel for $R \geq 50$.}
@@
 \input{empirics/plots/oos-ind-pm.tikz}
-\caption{\protect{\textsc{oos} \textsc{mse} of the Prevailing Mean (\textsc{pm}) and
-    Kitchen Sink (\textsc{ks}) models for equity premium prediction as
+\caption{OOS MSE of the Prevailing Mean (PM) and
+    Kitchen Sink (KS) models for equity premium prediction as
     a function of the size of the training sample, $R$.  Please note
-    that the vertical scales are different in the two plots.}}
+    that the vertical scales are different in the two plots.}
 \label{fig:empirics3}

### 2014-02-25 paper.tex
Tweak footnote source to make line-wrap work better

@@
 justification for forecasters to use OOS instead of in-sample
-comparisons: the DMW OOS test\footnote{In this paper, we will
-  refer to the basic OOS $t$-test studied by \citet{DiM:95} and
-  \citet{Wes:96} as the DMW test.} allows a forecaster to conduct
+comparisons: the DMW OOS test%
+\footnote{In this paper, we will refer to the basic OOS $t$-test
+  studied by \citet{DiM:95} and \citet{Wes:96} as the DMW test.} %
+allows a forecaster to conduct
 inference about the expected future accuracy of his or her models when
@@
 conditions that permit in-sample comparisons \citep[see][for a
-review of this literature]{Wes:06}.\footnote{Like us, \citet{Ana:07}
-  allows the number of regressors to increase with $T$.  But in that
-  paper, the number of regressors increases slowly enough that the OLS
-  coefficients are consistent and asymptotically normal.} \citet{GiW:06} and
+review of this literature]{Wes:06}.%
+\footnote{Like us, \citet{Ana:07} allows the number of regressors to
+  increase with $T$.  But in that paper, the number of regressors
+  increases slowly enough that the OLS coefficients are consistent and
+  asymptotically normal.} %
+\citet{GiW:06} and
 \citet{GiR:09, GiR:10} are exceptions.  Instead of focusing on
@@
 future conditional on the on the data available in period
-$T$.\footnote{See, for example, \citet{HTF:08} for a discussion of
-  generalization error.}  Under these asymptotics, the generalization
+$T$.%
+\footnote{See, for example, \citet{HTF:08} for a discussion of
+  generalization error.} %
+Under these asymptotics, the generalization
 error does not converge to the expected performance of the pseudo-true
@@
 an OOS comparison would correctly fail to reject the null that the
-benchmark is more accurate.\footnote{In a pair of papers similar to
+benchmark is more accurate.%
+\footnote{In a pair of papers similar to
   ours, \citet{ClM:12,ClM:12b} study in-sample and OOS tests that
@@
   asymptotic theories are different and their papers do not provide
-  reasons to do OOS comparisons.}
+  reasons to do OOS comparisons.} %
 Also note that, in this situation, a model that performs well
@@
 benchmark model with probability approaching one, regardless of which
-model is more accurate.\footnote{Our result holds for a broad class of
+model is more accurate.%
+\footnote{Our result holds for a broad class of
   full-sample statistics, but there may be other potential statistics
   that mimic the OOS test and remain valid. Exploring such
-  statistics is left for future research.}
+  statistics is left for future research.} %
 This result holds even though modifications of the $F$-test are valid
@@
 \citet{AkA:00}, \citet{AkP:04}, \citet{Cal:11c}, and \citet{Ana:12},
-among others.\footnote{Also see \citet{Efr:86,Efr:04} for a discussion
-  of naive in-sample loss comparisons.}
+among others.%
+\footnote{Also see \citet{Efr:86,Efr:04} for a discussion
+  of naive in-sample loss comparisons.} %
 Moreover, under this asymptotic theory, many recent OOS test
@@
 \citet{Mcc:07}, and \citet{ClW:06,ClW:07} should have the same
-problems as in-sample tests.\footnote{Our theoretical results apply
+problems as in-sample tests.%
+\footnote{Our theoretical results apply
   directly to \citepos{Mcc:07} OOS $t$-test, since it simply
@@
   size when the estimated benchmark model is expected to be more
-  accurate, so more liberal critical values result in overrejection.}
+  accurate, so more liberal critical values result in overrejection.} %
 These tests are also designed to reject the benchmark when the
@@
 
-\section{Setup and Assumptions}\label{sec:assumptions}
+\section{Setup and assumptions}\label{sec:assumptions}
+
 The first part of this section will describe the environment in detail
@@
 
-\subsection{Notation and Forecasting Environment}
+\subsection{Notation and forecasting environment}
 We assume the following forecasting environment. There are two
@@
   \bh{it} = \Big(\sum_{s=1}^{R-\h} x_{is}x_{is}'\Big)^{-1} \sum_{s=1}^{R-\h}
-  x_{is} y_{s+\h}, \qquad \text{for } i=1,2;\ t = R+1,\dots, T - \h.\footnote{It
-    may not be clear why we are using a $t$ index in $\bh{it}$,
+  x_{is} y_{s+\h}, \qquad \text{for } i=1,2;\ t = R+1,\dots, T - \h.%
+\footnote{It may not be clear why we are using a $t$ index in $\bh{it}$,
     since $\bh{it} = \bh{iR}$ almost surely for all $t \leq T-h$.
     But $\bh{it}$ will be defined for $t > T-\h$
-    soon and will not equal $\bh{iR}$ for those values of $t$.}
+    soon and will not equal $\bh{iR}$ for those values of $t$.} %
 \end{equation}
@@
 literature, but we focus on perhaps the most natural, the DMW \oost\
-test \citep{DiM:95,Wes:96}.\footnote{The core insights of our paper
-  apply to other OOS statistics as well.} This statistic is based on
+test \citep{DiM:95,Wes:96}.%
+\footnote{The core insights of our paper apply to other OOS statistics
+  as well.} %
+This statistic is based on
 the difference in the models' loss over the test sample, $\oosA$,
@@
 converge in probability to the difference in the expected loss
-associated with the pseudo-true models,\footnote{Under standard
-  stationarity, moment, and weak-dependence conditions.}
-
+associated with the pseudo-true models,%
+\footnote{Under standard stationarity, moment, and weak-dependence
+  conditions.} %
 i.e. the LHS of~\eqref{eq:21}.
@@
 in $[0,\infty]$, while we require $P^2/R \to 0$
-(Assumption~\ref{asmp-4}).\footnote{\citet{Wes:96} does not have a
+(Assumption~\ref{asmp-4}).%
+\footnote{\citet{Wes:96} does not have a
   second OOS period, so there is no analogue in his paper to our
-  restriction on $Q$.}  Obviously, these differences are
+  restriction on $Q$.} %
+Obviously, these differences are
 related---allowing for complex models requires tighter constraints on
@@
 
-\subsection{Failure of In-Sample Tests}\label{sec:insample}
+\subsection{Failure of in-sample forecast evaluation}\label{sec:insample}
 This subsection establishes that in-sample tests like the $F$-test can
@@
 sample Wald and $F$-tests can be invalid under increasing-$k$
-asymptotics,\footnote{\citet{Ana:12} shows that the Wald test is
+asymptotics,%
+\footnote{\citet{Ana:12} shows that the Wald test is
   invalid in general and gives an adjustment that corrects the
@@
   a correction that gives valid tests.  Both papers only consider
-  independent observations.} e.g. they can overreject when testing the
+  independent observations.} %
+e.g. they can overreject when testing the
 null hypotheses that a set of the coefficients is zero.  This paper,
@@
 defined by $\hat{\theta}_T' V_T \hat{\theta}_T = 1$ and rejects for
-$\hat{\theta}_T$ outside the neighborhood.\footnote{If $V_T$ is full
+$\hat{\theta}_T$ outside the neighborhood.%
+\footnote{If $V_T$ is full
   rank, this equation defines an ellipsoid in $\mathbb{R}^K$;
   otherwise the equation defines an ellipsoid in a subspace of
-  $\mathbb{R}^K$.}  The neighborhood shrinks as $T \to \infty$, so the
+  $\mathbb{R}^K$.} %
+The neighborhood shrinks as $T \to \infty$, so the
 $F$-test satisfies the conditions of Theorem~\ref{res:ftest} with
@@
 OOS $t$-test using McCracken's (2007)
-critical values,\footnote{These critical values are not published for
-  $K_2-K_1>10$, so we do not report them for $K_2 = T/10$.}
+critical values,%
+\footnote{These critical values are not published for
+  $K_2-K_1>10$, so we do not report them for $K_2 = T/10$.} %
 and Clark and West's (2006, 2007) Gaussian out-of-sample
-statistic.\footnote{Clark and West (2006, 2007) derive their statistic
+statistic.%
+\footnote{Clark and West (2006, 2007) derive their statistic
 using the rolling window estimation scheme.  Here we use the same
-statistic, but with a fixed window scheme.}
+statistic, but with a fixed window scheme.} %
 For the $F$-test, we simply test whether the coefficients on the larger
@@
 simulating from \eqref{eq:1} with $c = 1$ or 2 subject to the
-constraint that $\E_T \oosB > 0$.\footnote{Draws of $X$ and $Y$ with
+constraint that $\E_T \oosB > 0$.%
+\footnote{Draws of $X$ and $Y$ with
   $\E_T \oosB > 0$ are very rare when $c=0$, so we do not present
-  results for that value of $c$.}  Figure~\ref{fig:ttest-power} plots
+  results for that value of $c$.} %
+Figure~\ref{fig:ttest-power} plots
 the power for the DMW test; since the other test statistics greatly
@@
 power when it is not satisfied.
-\section{Empirical Exercise}\label{sec:empirics}
+\section{Empirical exercise}\label{sec:empirics}
 This section presents an analysis of equity premium predictability
-similar to \citet{GoW:08}.\footnote{All of the calculations in this
+similar to \citet{GoW:08}.%
+\footnote{All of the calculations in this
   section are done in R \citep{Rde:10}.  We also use code provided by
   \citet{Zeh:02}, \citet{Zei:04}, \citet{Har:10}, and
-  \citet{ShB:11:0.6.1}.}  We estimate the expected forecasting
+  \citet{ShB:11:0.6.1}.} %
+We estimate the expected forecasting
 performance of the largest model they consider, a model with 13
@@
 variables are listed in
-Table~\ref{tab:equity}.\footnote{Table~\ref{tab:equity} only lists the
+Table~\ref{tab:equity}.%
+\footnote{Table~\ref{tab:equity} only lists the
   variables used in \citepos{GoW:08} ``kitchen sink''
@@
   excluded from this model either because the series are too short or
-  because the variables are linear combinations of other variables.}
+  because the variables are linear combinations of other variables.} %
 \citet{GoW:08} estimate the OOS forecasting
@@
 regression for Equation~\eqref{eq:2}, using Newey-West standard errors
-with two lags \citep{NeW:87}.\footnote{We compare the test statistic
-  to critical values from the $F$-distribution.}  The $p$-value is
+with two lags \citep{NeW:87}.%
+\footnote{We compare the test statistic
+  to critical values from the $F$-distribution.} %
+The $p$-value is
 very small (less than 0.01), indicating that the coefficients are
@@
 larger model could predict better than the benchmark with enough
-data.\footnote{\citet{BWB:10} make a similar point about exchange rate
-models, but see also \citet{Chi:10} and \citet{Gia:10}.}
+data.%
+\footnote{\citet{BWB:10} make a similar point about exchange rate
+models, but see also \citet{Chi:10} and \citet{Gia:10}.} %
 Obviously, this is an illustrative exercise only and is not meant to
@@
 \appendix
-\section*{Appendix: Mathematical Details}
+\section*{Appendix: mathematical details}
 \setcounter{section}{1}
@@
 
-\subsection*{Supporting Results}
+\subsection*{Supporting results}
 The results in this paper rely heavily on a coupling argument for
@@
 \begin{equation}\label{eq:cltvar1}
-  \SumOuterBlock{i} \E_R Z_i^2 - \SumOuterBlock{i} \ZSqCE \to^p 0.\footnote{Note that $\sigma^2 \in \mathcal{F}_t$ for
+  \SumOuterBlock{i} \E_R Z_i^2 - \SumOuterBlock{i} \ZSqCE \to^p 0.%
+\footnote{Note that $\sigma^2 \in \mathcal{F}_t$ for
     all $t \geq R$, so Hall and Heyde's condition (3.21) is
-    unnecessary---see the remarks after their result.}
+    unnecessary---see the remarks after their result.} %
 \end{equation}

### 2014-02-26 paper.tex
Change fonts to charter and source code pro
This commit changes the main font in the paper to Bitstream Charter
and changes the monospaced font (where it's used) to Adobe's Source
Code Pro.

@@
 \usepackage[charter]{mathdesign}
+\usepackage[osf]{sourcecodepro}
+% This will make copy and pasting easier, and will prevent the
+% abomination that is monospace font ligatures.  Sorry, everyone who
+% really likes ligatures.  Don't worry, the Bitstream Charter font
+% has very, very few ligatures anyway.
+\DisableLigatures{family = tt*}
+\urlstyle{same}
 
@@
 \newcommand{\clws}{\citeauthor{ClW:06}'s \citeyearpar{ClW:06,ClW:07}}
+
+\usepackage[bitstream]{mathdesign}
 
@@
   \centering {\large Simulated Coverage of One-Sided DMW Interval for
-    $\E_R\oosA$} \input{mc/plots/interval-testerror1.tikz}
+    $\E_R\oosA$} \input{floats/mc-interval-testerror1.tex}
 \caption{Simulated coverage of $\E_R \oosA$ at 90\% confidence using a
@@
   \centering {\large Simulated Coverage of One-Sided DMW Interval for
-    $\E_T\oosB$} \input{mc/plots/interval-generror1.tikz}
+    $\E_T\oosB$} \input{floats/mc-interval-generror1.tex}
 \caption{Simulated coverage of $\E_T \oosB$ at 90\% confidence using a
@@
     $\E_T \oosB \leq 0$}
-  \input{mc/plots/ftest-001.tikz}
+  \input{floats/mc-ftest.tex}
   \caption{Simulated rejection probabilities for the $F$-test given
@@
   \centering {\large Simulated Rejection Probability of DMW Test Under
-    $\E_T \oosB \leq 0$} \input{mc/plots/size-dmwsize.tikz}
+    $\E_T \oosB \leq 0$} \input{floats/mc-dmwsize.tex}
   \caption{Simulated rejection probabilities for the DMW
@@
     (2006, 2007) \\ Test Under $\E_T \oosB \leq 0$}
-  \input{mc/plots/size-clarkwest.tikz}
+  \input{floats/mc-clarkwestsize.tex}
   \caption{Simulated rejection probabilities for Clark and West's
@@
     (2007) Test \\ Under $\E_T \oosB \leq 0$}
-  \input{mc/plots/size-mccracken.tikz}
+  \input{floats/mc-mccrackensize.tex}
   \caption{Simulated rejection probabilities for McCracken's (2007)
@@
   \centering {\large Simulated Rejection Probability of DMW Test Under
-    $\E_T \oosB > 0$} \input{mc/plots/size-dmwpower.tikz}
+    $\E_T \oosB > 0$} \input{floats/mc-dmwpower.tex}
   \caption{Simulated rejection probabilities for the DMW
@@
     Sink Models of Equity Premium (OLS)}
-\input{empirics/plots/oos-mse-1.tikz}
-\input{empirics/plots/oos-mse-1b.tikz}
+\input{floats/empirics-oos-mse-1.tex}
+\input{floats/empirics-oos-mse-1b.tex}
 \caption{OOS difference in the MSE
@@
     Sink Models of Equity Premium (CT)}
-\input{empirics/plots/oos-mse-2.tikz}
-\input{empirics/plots/oos-mse-2b.tikz}
+\input{floats/empirics-oos-mse-2.tex}
+\input{floats/empirics-oos-mse-2b.tex}
 \caption{OOS difference in the MSE
@@
 \large{OOS MSE of Individual Forecasts of Equity Premium}
-\input{empirics/plots/oos-ind-ks.tikz}
-\input{empirics/plots/oos-ind-pm.tikz}
+\input{floats/empirics-oos-ind-ks.tex}
+\input{floats/empirics-oos-ind-pm.tex}
 \caption{OOS MSE of the Prevailing Mean (PM) and

### 2014-03-03 paper.tex
Add 'tryinput' to input graphs only if they exist
This commit adds the \tryinput macro which will \input the file
if it exists, but silently pass if it doesn't. This can make
compiling the pdf file in intermediate steps easier.

@@
 \IfFileExists{VERSION}{
-  \input{VERSION}
+  \tryinput{VERSION}
   \date{\dinfo\ (commit \hinfo)}
@@
   \centering {\large Simulated Coverage of One-Sided DMW Interval for
-    $\E_R\oosA$} \input{floats/mc-interval-testerror1.tex}
+    $\E_R\oosA$} \tryinput{floats/mc-interval-testerror1.tex}
 \caption{Simulated coverage of $\E_R \oosA$ at 90\% confidence using a
@@
   \centering {\large Simulated Coverage of One-Sided DMW Interval for
-    $\E_T\oosB$} \input{floats/mc-interval-generror1.tex}
+    $\E_T\oosB$} \tryinput{floats/mc-interval-generror1.tex}
 \caption{Simulated coverage of $\E_T \oosB$ at 90\% confidence using a
@@
     $\E_T \oosB \leq 0$}
-  \input{floats/mc-ftest.tex}
+  \tryinput{floats/mc-ftest.tex}
   \caption{Simulated rejection probabilities for the $F$-test given
@@
   \centering {\large Simulated Rejection Probability of DMW Test Under
-    $\E_T \oosB \leq 0$} \input{floats/mc-dmwsize.tex}
+    $\E_T \oosB \leq 0$} \tryinput{floats/mc-dmwsize.tex}
   \caption{Simulated rejection probabilities for the DMW
@@
     (2006, 2007) \\ Test Under $\E_T \oosB \leq 0$}
-  \input{floats/mc-clarkwestsize.tex}
+  \tryinput{floats/mc-clarkwestsize.tex}
   \caption{Simulated rejection probabilities for Clark and West's
@@
     (2007) Test \\ Under $\E_T \oosB \leq 0$}
-  \input{floats/mc-mccrackensize.tex}
+  \tryinput{floats/mc-mccrackensize.tex}
   \caption{Simulated rejection probabilities for McCracken's (2007)
@@
   \centering {\large Simulated Rejection Probability of DMW Test Under
-    $\E_T \oosB > 0$} \input{floats/mc-dmwpower.tex}
+    $\E_T \oosB > 0$} \tryinput{floats/mc-dmwpower.tex}
   \caption{Simulated rejection probabilities for the DMW
@@
     Sink Models of Equity Premium (OLS)}
-\input{floats/empirics-oos-mse-1.tex}
-\input{floats/empirics-oos-mse-1b.tex}
+\tryinput{floats/empirics-oos-mse-1.tex}
+\tryinput{floats/empirics-oos-mse-1b.tex}
 \caption{OOS difference in the MSE
@@
     Sink Models of Equity Premium (CT)}
-\input{floats/empirics-oos-mse-2.tex}
-\input{floats/empirics-oos-mse-2b.tex}
+\tryinput{floats/empirics-oos-mse-2.tex}
+\tryinput{floats/empirics-oos-mse-2b.tex}
 \caption{OOS difference in the MSE
@@
 \large{OOS MSE of Individual Forecasts of Equity Premium}
-\input{floats/empirics-oos-ind-ks.tex}
-\input{floats/empirics-oos-ind-pm.tex}
+\tryinput{floats/empirics-oos-ind-ks.tex}
+\tryinput{floats/empirics-oos-ind-pm.tex}
 \caption{OOS MSE of the Prevailing Mean (PM) and

### 2014-03-14 R/empirics-coeftest.R
Reorganize code (big!)
This commit is a massive code reorganization. There are several reasons
for it:
- R 3.0x came out and my old packages weren't valid any more
- The pgfSweave package is obsolete, and so I've unbundled
  the sweave files that were using it.
- It seemed like an opportunistic time to make a few other
  changes.

@@ -1,0 +1,8 @@
+library(sandwich)
+library(lmtest)
+library(Hmisc)
+load("data/empirical-results.RData")
+
+devnull <-
+  latex(coeftest(fullmod, vcov=NeweyWest(fullmod, prewhite=FALSE, lag=2)),
+        file = "floats/empirics-coeftest.tex", digits = 2)

### 2014-03-14 R/empirics-oos-ind-ks.R

@@ -1,0 +1,8 @@
+library(sandwich)
+library(lmtest)
+library(Hmisc)
+library(tikzDevice)
+load("data/empirical-results.RData")
+
+indplot(name = "KS", oos[,"KS"],
+        file = "floats/empirics-oos-ind-ks.tex")

### 2014-03-14 R/empirics-oos-ind-pm.R

@@ -1,0 +1,10 @@
+library(sandwich)
+library(lmtest)
+library(Hmisc)
+library(tikzDevice)
+load("data/empirical-results.RData")
+
+indplot(name = "PM", oos[,"PM"],
+        file = "floats/empirics-oos-ind-pm.tex", xlabel = "$R$",
+        ticks = c(0, .01, .02, .03, .04, 0.05),
+        labels = c("0", "", "", "", "", "0.05"))

### 2014-03-14 R/empirics-oos-mse-1.R

@@ -1,0 +1,11 @@
+library(sandwich)
+library(lmtest)
+library(Hmisc)
+library(tikzDevice)
+load("data/empirical-results.RData")
+
+##Average OOS MSE Difference\nfor OLS Equity Premium Forecasts
+oosplot(oos[,c("interval", "average")],
+        file = "floats/empirics-oos-mse-1.tex",
+        ticks = c(0, -1, -2, -3, -4),
+        labels = c("0", "", "-2", "", "-4"))

### 2014-03-14 R/empirics-oos-mse-1b.R

@@ -1,0 +1,15 @@
+library(sandwich)
+library(lmtest)
+library(Hmisc)
+library(tikzDevice)
+load("data/empirical-results.RData")
+
+oos.subset <- oos
+window(oos.subset, end = 49) <- NA
+## Subset of Average OOS MSE Difference\nfor OLS Equity Premium
+## Forecasts
+oosplot(oos.subset[,c("interval", "average")],
+        file = "floats/empirics-oos-mse-1b.tex",
+        xlabel = "$R$", ticks = c(0, -0.025, -.05, -0.075, -.1),
+        labels = c("0", "", "-0.5", "", "-.10"))
+

### 2014-03-14 R/empirics-oos-mse-2b.R

@@ -1,0 +1,16 @@
+library(sandwich)
+library(lmtest)
+library(Hmisc)
+library(tikzDevice)
+load("data/empirical-results.RData")
+
+oos.subset <- oos.ct
+window(oos.subset, end = 49) <- NA
+
+# Subset of Average OOS MSE Difference for Restricted OLS Equity
+# Premium Forecasts
+oosplot(oos.subset[,c("interval", "average")],
+        file = "floats/empirics-oos-mse-2b.tex",
+        xlabel = "$R$",
+        ticks = c(0, - 0.015/2, -.015, -(0.015 + 0.03)/2, -.03),
+        labels = c("0", "", "", "", "-.03"))

### 2014-03-14 R/empirics-waldtest.R

@@ -1,0 +1,13 @@
+library(sandwich)
+library(lmtest)
+library(Hmisc)
+load("data/empirical-results.RData")
+
+devnull <-
+  latex(waldtest(fullmod, vcov=NeweyWest(fullmod, prewhite=FALSE, lag=2), test="F"),
+        file = "floats/empirics-waldtest.tex", digits = 2,
+        caption = "Wald test for the null hypothesis that all of the coefficients
+                   in Goyal and Welch's (2008) ``kitchen sink'' model are zero,
+                   except for the intercept.",
+        label = "tab:gwinsample")
+

### 2014-03-14 R/empirics.R

@@ -1,10 +1,7 @@
-library(lattice)
 library(sandwich)
 library(lmtest)
-library(Hmisc)
-library(tikzDevice)
 
-dfull <- ts(read.csv("AllData2009.csv")[,-1],
+dfull <- ts(read.csv("data/goyalwelch2009.csv")[,-1],
             start = 1871, frequency = 1)
 stock.returns <- (dfull[,"price"] + dfull[,"dividend"]) / lag(dfull[,"price"], -1) - 1
 startyear <- 1928
@@ -77,11 +74,6 @@ tstats.ct <- lapply(RStart:REnd, function(R) oosT(R, fullmodel, dframe, TRUE))
 
 ## make table assessing full-sample model
 fullmod <- lm(fullmodel, data = dframe)
-## assignment prevents display
-temp <- latex(coeftest(fullmod, vcov=NeweyWest(fullmod, prewhite=FALSE, lag=2)),
-              file = "tables/coeftest.tex", digits = 2)
-temp <- latex(waldtest(fullmod, vcov=NeweyWest(fullmod, prewhite=FALSE, lag=2), test="F"),
-              file = "tables/waldtest.tex", digits = 2, caption = "Wald test for the null hypothesis that all of the coefficients in Goyal and Welch's (2008) ``kitchen sink'' model are zero, except for the intercept.", label = "tab:gwinsample")
 
 oosStats <- function(tstats) 
   ts(cbind(PM = sapply(tstats, function(x) x$avg1),
@@ -107,11 +99,6 @@ indplot <- function(name, series, file, height = 2, width = 5.5, xlabel = "",
   dev.off()  
 }
 
-indplot(name = "KS", oos[,"KS"], file = "plots/oos-ind-ks.tikz")
-indplot(name = "PM", oos[,"PM"], file = "plots/oos-ind-pm.tikz", xlabel = "$R$",
-        ticks = c(0, .01, .02, .03, .04, 0.05),
-        labels = c("0", "", "", "", "", "0.05"))
-
 ## make plots of out-of-sample mse
 ## set parameters for  images
 oosplot <- function(series, file, height = 2, width = 5.5, xlabel = "",
@@ -125,30 +112,13 @@ oosplot <- function(series, file, height = 2, width = 5.5, xlabel = "",
        ylab = "MSE Diff.", xlab = xlabel,
        lwd = 0.8,
        col = c("white", "white"))
[…]

### 2014-03-14 R/mc-clarkwestsize.R

@@ -1,0 +1,32 @@
+library(fwPackage, lib.loc = "package")
+library(lattice)
+library(tikzDevice)
+
+ltheme <- canonical.theme(color = FALSE)     ## in-built B&W theme  
+ltheme$strip.background$col <- "transparent" ## change strip bg  
+lattice.options(default.theme = ltheme)      ## set as default  
+
+dbc <- dbConnect(dbDriver("SQLite"), dbname = "data/simulations.db")
+
+d <- dbGetQuery(dbc, "
+select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
+from interval 
+where label='size' and idgp in (1,2) and transform = 'clarkwest'
+group by ntest, isim, idgp, transform, label) s 
+join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp")
+d$nlabel <- sprintf("T=%d", d$n)
+d$normlabel <- sprintf("c=%d", d$norm)
+
+tikz(file = "floats/mc-clarkwestsize.tex", width = 6)
+xyplot(reject ~ I(ntest/n) | interaction(nlabel,altlabel,normlabel, sep = ", "),
+       data = d,
+       ylab = "Rejection Probability", xlab = "$P/T$",
+       panel = function(x,y,...) {
+         panel.lines(c(0,2/3),c(.1,.1), col = "lightgray")
+         panel.xyplot(x,y,...,type = "l")
+       },
+       layout = c(4,4),
+       par.strip.text = list(cex = .55),
+       index.cond = list(c(13,15,16,14,9,11,12,10,5,7,8,6,1,3,4,2)))
+dev.off()
+dbDisconnect(dbc)

### 2014-03-14 R/mc-dmwpower.R

@@ -1,0 +1,32 @@
+library(fwPackage, lib.loc = "package")
+library(lattice)
+library(tikzDevice)
+
+ltheme <- canonical.theme(color = FALSE)     ## in-built B&W theme  
+ltheme$strip.background$col <- "transparent" ## change strip bg  
+lattice.options(default.theme = ltheme)      ## set as default  
+
+dbc <- dbConnect(dbDriver("SQLite"), dbname = "data/simulations.db")
+
+d <- dbGetQuery(dbc, "
+select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
+from interval 
+where label='power' and idgp in (2,3) and transform='difference'
+group by ntest, isim, idgp, transform, label) s 
+join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp")
+d$nlabel <- sprintf("T=%d", d$n)
+d$normlabel <- sprintf("c=%d", d$norm)
+
+tikz(file = "floats/mc-dmwpower.tex", width = 6)
+xyplot(reject ~ I(ntest/n) | interaction(nlabel,altlabel,normlabel, sep = ", "),
+       data = d,
+       ylab = "Rejection Probability", xlab = "$P/T$",
+       panel = function(x,y,...) {
+         panel.lines(c(0,2/3),c(.1,.1), col = "lightgray")
+         panel.xyplot(x,y,...,type = "l")
+       },
+       layout = c(4,4),
+       par.strip.text = list(cex = .55),
+       index.cond = list(c(13,15,16,14,9,11,12,10,5,7,8,6,1,3,4,2)))
+dev.off()
+dbDisconnect(dbc)

### 2014-03-14 R/mc-dmwsize.R

@@ -1,0 +1,32 @@
+library(fwPackage, lib.loc = "package")
+library(lattice)
+library(tikzDevice)
+
+ltheme <- canonical.theme(color = FALSE)     ## in-built B&W theme  
+ltheme$strip.background$col <- "transparent" ## change strip bg  
+lattice.options(default.theme = ltheme)      ## set as default  
+
+dbc <- dbConnect(dbDriver("SQLite"), dbname = "data/simulations.db")
+
+d <- dbGetQuery(dbc, "
+select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
+from interval 
+where label='size' and idgp in (1,2) and transform = 'difference'
+group by ntest, isim, idgp, transform, label) s 
+join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp")
+d$nlabel <- sprintf("T=%d", d$n)
+d$normlabel <- sprintf("c=%d", d$norm)
+
+tikz(file = "floats/mc-dmwsize.tex", width = 6)
+xyplot(reject ~ I(ntest/n) | interaction(nlabel,altlabel,normlabel, sep = ", "),
+       data = d,
+       ylab = "Rejection Probability", xlab = "$P/T$",
+       panel = function(x,y,...) {
+         panel.lines(c(0,2/3),c(.1,.1), col = "lightgray")
+         panel.xyplot(x,y,...,type = "l")
+       },
+       layout = c(4,4),
+       par.strip.text = list(cex = .55),
+       index.cond = list(c(13,15,16,14,9,11,12,10,5,7,8,6,1,3,4,2)))
+dev.off()
+dbDisconnect(dbc)

### 2014-03-14 R/mc-ftest.R

@@ -1,0 +1,28 @@
+library(fwPackage, lib.loc="package")
+library(tikzDevice)
+library(lattice)
+
+ltheme <- canonical.theme(color = FALSE)     ## in-built B&W theme  
+ltheme$strip.background$col <- "transparent" ## change strip bg  
+lattice.options(default.theme = ltheme)      ## set as default  
+
+dbc <- dbConnect(dbDriver("SQLite"), dbname = "data/simulations.db")
+d <- dbGetQuery(dbc,
+                "select reject, 'T=' || n as nlabel, altlabel, norm from viewftest 
+                 where label='size' and norm in (0,1)")
+d$norm <- as.factor(d$norm)
+
+tikz(file = "floats/mc-ftest.tex", width = 5.5, height = 4)
+dotplot(norm ~ reject | interaction(altlabel,nlabel, sep = ", "),
+              dat = d, las = 1,
+              xlab = "Rejection Probability", ylab = "c",
+              xlim = c(-.1, 1.1),
+              panel = function(x, y, ...) {
+                panel.dotplot(x, y, ..., type = "n")
+                panel.text(x, as.numeric(y), labels = sprintf("%.2f", x))
+              },
+              par.strip.text = list(cex = .55),
+              layout = c(2,4),
+              index.cond = list(c(3,4,7,8,5,6,1,2)))
+dev.off()
+dbDisconnect(dbc)

### 2014-03-14 R/mc-interval-generror1.R

@@ -1,0 +1,36 @@
+library(fwPackage, lib.loc="package")
+library(lattice)
+library(tikzDevice)
+
+ltheme <- canonical.theme(color = FALSE)     ## in-built B&W theme  
+ltheme$strip.background$col <- "transparent" ## change strip bg  
+lattice.options(default.theme = ltheme)      ## set as default  
+
+dbc <- dbConnect(dbDriver("SQLite"), dbname = "data/simulations.db")
+
+mcpars <- dbGetQuery(dbc, "select count(jobnumber) as njobs from interval")
+dstring <- "
+select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
+from interval 
+where label='%s' and simIndex <= %d and transform = 'difference'
+group by ntest, isim, idgp, transform, label) s 
+join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp"
+
+d <- dbGetQuery(dbc, sprintf(dstring, 'gen.error.1', 500))
+d$nlabel <- sprintf("T=%d", d$n)
+d$normlabel <- sprintf("c=%d", d$norm)
+
+tikz(file = "floats/mc-interval-generror1.tex", width=6)
+xyplot(I(1 - reject) ~ I(ntest/n)
+         | interaction(nlabel, altlabel, normlabel, sep = ", "),
+       data = d,
+       ylab = "Coverage", xlab = "$P/T$",
+       panel = function(x,y,...) {
+         panel.lines(c(0,2/3),c(.9,.9), col = "gray")
+         panel.xyplot(x,y,...,type = "l")
+       },
+       layout = c(4,4),
+       par.strip.text = list(cex = .55),
+       index.cond = list(c(13,15,16,14,9,11,12,10,5,7,8,6,1,3,4,2)))
+dev.off()
+dbDisconnect(dbc)

### 2014-03-14 R/mc-interval-testerror1.R

@@ -1,0 +1,36 @@
+library(fwPackage, lib.loc="package")
+library(lattice)
+library(tikzDevice)
+
+ltheme <- canonical.theme(color = FALSE)     ## in-built B&W theme  
+ltheme$strip.background$col <- "transparent" ## change strip bg  
+lattice.options(default.theme = ltheme)      ## set as default  
+
+dbc <- dbConnect(dbDriver("SQLite"), dbname = "data/simulations.db")
+
+mcpars <- dbGetQuery(dbc, "select count(jobnumber) as njobs from interval")
+dstring <- "
+select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
+from interval 
+where label='%s' and simIndex <= %d and transform = 'difference'
+group by ntest, isim, idgp, transform, label) s 
+join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp"
+
+d <- dbGetQuery(dbc, sprintf(dstring, 'test.error.1', 500))
+d$nlabel <- sprintf("T=%d", d$n)
+d$normlabel <- sprintf("c=%d", d$norm)
+
+tikz(file = "floats/mc-interval-testerror1.tex", width=6)
+xyplot(I(1 - reject) ~ I(ntest/n)
+         | interaction(nlabel, altlabel, normlabel, sep = ", "),
+       data = d,
+       ylab = "Coverage", xlab = "$P/T$",
+       panel = function(x,y,...) {
+         panel.lines(c(0,2/3),c(.9,.9), col = "gray")
+         panel.xyplot(x,y,...,type = "l")
+       },
+       layout = c(4,4),
+       par.strip.text = list(cex = .55),
+       index.cond = list(c(13,15,16,14,9,11,12,10,5,7,8,6,1,3,4,2)))
+dev.off()
+dbDisconnect(dbc)

### 2014-03-14 R/mc-mccrackensize.R

@@ -1,0 +1,31 @@
+library(fwPackage, lib.loc = "package")
+library(lattice)
+library(tikzDevice)
+
+ltheme <- canonical.theme(color = FALSE)     ## in-built B&W theme  
+ltheme$strip.background$col <- "transparent" ## change strip bg  
+lattice.options(default.theme = ltheme)      ## set as default  
+
+dbc <- dbConnect(dbDriver("SQLite"), dbname = "data/simulations.db")
+
+d <- dbGetQuery(dbc, "
+select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
+from interval 
+where label='size' and idgp in (1,2) and transform = 'mccracken'
+group by ntest, isim, idgp, transform, label) s 
+join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp")
+d$nlabel <- sprintf("T=%d", d$n)
+d$normlabel <- sprintf("c=%d", d$norm)
+
+tikz(file = "floats/mc-mccrackensize.tex", w = 6)
+xyplot(reject ~ I(ntest/n) | interaction(nlabel,altlabel,normlabel, sep = ", "),
+       data = d[d$altlabel=="K=3" & d$transform == "mccracken",],
+       ylab = "Rejection Probability", xlab = "$P/T$",
+       panel = function(x,y,...) {
+         panel.lines(c(0,2/3),c(.1,.1), col = "lightgray")
+         panel.xyplot(x,y,...,type = "l")
+       }, layout = c(4,2),
+       par.strip.text = list(cex = .55),
+       index.cond = list(c(5,7,8,6,1,3,4,2)))
+dev.off()
+dbDisconnect(dbc)

### 2014-03-14 R/simulations.R

@@ -8,9 +8,9 @@ jobnames <- LETTERS[1:njobs]
 .lec.CreateStream(jobnames)
 .lec.CurrentStream(jobnames[jobnumber])
                
-require(fwPackage) ## look here for function definitions.
+require(fwPackage, lib.loc = "package") ## look here for function definitions.
 
-dbmain <- dbConnect(dbDriver("SQLite"), "mc/simulations.db")
+dbmain <- dbConnect(dbDriver("SQLite"), "data/simulations.db")
 
 mcDesign <- dbGetQuery(dbmain,
 "select nobs.i as isim, n, kNull, kAlt, norm, coefficients.i as idgp from nobs cross join coefficients")

### 2014-03-19 appendix.tex
Add recursive window simulations for separate appendix

--- 2014-02-25 paper.tex
@@
 \documentclass[11pt]{article}
-\usepackage{tikz,setspace}
-\usetikzlibrary{calc}
-\usetikzlibrary{fit}
-\usepackage[round]{natbib}
-\usepackage[margin=1in]{geometry}
-\onehalfspacing
-\input{macros}
-\usepackage[charter]{mathdesign}
+\input{setup}
 
-\newcommand{\e}{\varepsilon}
-\newcommand{\eb}{\mathbf{\e}}
-\DeclareMathOperator{\eigen}{\lambda}
-
-\pagestyle{myheadings}
-\newtheorem{thm}{Theorem}
-\newtheorem{lem}{Lemma}
-\newtheorem{claim}{Claim}
-\newtheorem{cor}{Corollary}
-\newtheorem{asmp}{Assumption}
-\newtheorem{example}{Example}
-\newtheorem{defn}{Definition}
-
-\newcommand{\citepos}[1]{\citeauthor{#1}'s \citeyearpar{#1}}
-\newcommand{\Citepos}[1]{\Citeauthor{#1}'s \citeyearpar{#1}}
-\newcommand{\clws}{\citeauthor{ClW:06}'s \citeyearpar{ClW:06,ClW:07}}
-
-% VERSION is generated by a post-commit hook and contains the git
-% version info
-\IfFileExists{VERSION}{
-  \input{VERSION}
-  \date{\dinfo\ (commit \hinfo)}
-  \markright{\dinfo\ (commit \hinfo)}
-}{}
-
-\title{Out-of-Sample Comparisons of Overfit Models}
-\author{Gray Calhoun\thanks{email: gcalhoun@iastate.edu. I
-    would like to thank Julian Betts, Helle Bunzel, Marjorie Flavin,
-    Nir Jaimovich, Lutz Kilian, Ivana Komunjer, Michael McCracken,
-    Seth Pruitt, Ross Starr, Jim Stock, Yixiao Sun, Allan Timmermann,
-    Hal White, several anonymous referees, participants at the 2010
-    Midwest Economics Association Annual Meetings, the 2010
-    International Symposium on Forecasting, the 2010 Joint Statistical
-    Meetings, the 2011 NBER-NSF Time-Series
-    Conference, and in many seminars at UCSD, and espeically
-    Graham Elliott for their valuable suggestions, feedback and advice
-    in writing this paper.  I would also like to thank Amit Goyal for
-    providing computer code and data for his 2008 RFS paper
-    with Ivo Welch \citep{GoW:08}.} \\ Iowa State University}
+\title{Supplamental Appendix for Out-of-Sample Comparisons of Overfit
+  Models}
+\author{Gray Calhoun\thanks{email: gcalhoun@iastate.edu} \\
+  Iowa State University}
 
@@
 
-\begin{abstract}\thispagestyle{empty}\noindent
-  This paper uses dimension asymptotics to study why overfit linear
-  regression models should be compared out-of-sample; we let the
-  number of predictors used by the larger model increase with the
-  number of observations so that their ratio remains uniformly
-  positive.  Our analysis gives a theoretical motivation for using
-  out-of-sample (OOS) comparisons: the DMW OOS test allows a forecaster to
-  conduct inference about the expected future accuracy of his or her
-  models when one or both is overfit.  We show analytically and
-  through Monte Carlo that standard full-sample test statistics can
-  not test hypotheses about this performance.  Our paper also shows
-  that popular test and training sample sizes may give misleading
-  results if researchers are concerned about overfit.  We show that
-  $P^2/T$ must converge to zero for the DMW test to give valid
-  inference about the expected forecast accuracy, otherwise the test
-  measures the accuracy of the estimates constructed using only the
-  training sample.  In empirical research, $P$ is typically much
-  larger than this.  Our simulations indicate that using large values
-  of $P$ with the DMW test gives undersized tests with low power, so
-  this practice may favor simple benchmark models too much.
-
-\noindent JEL Classification: C12, C22, C52, C53
-
-\noindent Keywords: Generalization Error, Forecasting, Model
-Selection, $t$-test, Dimension Asymptotics
-\end{abstract}
-\newpage
-
-\section{Introduction}\label{sec:introduction}
-Consider two sequences of length $P$ of prediction errors, the result
-of forecasting the same variable with two different estimated models.
-Both models are estimated with $R$ observations, collectively called
-the {\em estimation window}, and are used to forecast an additional
-$P$ observations, called the {\em test sample}.  There are $T$
-observations in all, and $R+P=T$.  This paper introduces a new limit
-theory for statistics constructed from these prediction errors
-designed to approximate the behavior of the statistics when one of the
-models is overfit.  In doing so, we provide a theoretical
-justification for forecasters to use OOS instead of in-sample
-comparisons: the DMW OOS test%
-\footnote{In this paper, we will refer to the basic OOS $t$-test
-  studied by \citet{DiM:95} and \citet{Wes:96} as the DMW test.} %
-allows a forecaster to conduct
-inference about the expected future accuracy of his or her models when
-one or both is overfit.  We show analytically and through Monte Carlo
-that standard full-sample test statistics can not test hypotheses
-about this performance.
-
-Our paper also shows that popular test and training sample sizes may
-give misleading results if researchers are concerned about overfit.
-We show that $P^2/T$ must converge to zero for the DMW test to give
-valid inference about the expected forecast accuracy, otherwise the
-test measures the accuracy of the estimates constructed using only the
-training sample.  In empirical research, $P$ is typically much larger
-than this.  Our simulations indicate that using large values of $P$
-with the DMW test gives undersized tests with low power, so this
-practice may favor simple benchmark models too much.  Existing
-corrections, proposed by \citet{ClM:01,ClM:05}, \citet{Mcc:07} and
-\citet{ClW:06,ClW:07}, seem to overcorrect for this problem, though, and reject
-too often when the benchmark model is more accurate.
-
-Although OOS comparisons have been popular in Macroeconomics and
-Finance since \citepos{MeR:83} seminal study of exchange rate models,
-it has been unclear from a theoretical perspective whether or not the
-statistics are useful.  Empirical researchers often cite ``overfit''
-or ``instability'' as reasons for using OOS comparisons, as in
-\citet{StW:03}, but neither term is precisely defined or formalized.
-Compounding this problem, the asymptotic distributions of these
-statistics are derived under conditions that rule out either
-instability or overfit and allow a researcher to use a conventional
-in-sample comparison---a variation of the $F$-test, for example.  As
-\citet{InK:04} argue, the statistics themselves are designed to test
-hypotheses that can be tested by these in-sample statistics.  For
-example, \citet{DiM:95} and \citet{Wes:96} derive the limiting
-distributions of many popular OOS test statistics under conditions
-that would justify these full-sample tests.  Much
-of the subsequent research by \citet{Mcc:00, Mcc:07}, \citet{CCS:01},
-\citet{ClM:01,ClM:05}, \citet{CoS:02,CoS:04}, \citet{ClW:06,ClW:07},
-\citet{Ana:07}, and others relaxes several of Diebold and Mariano's
-and West's assumptions, but maintains the stationarity and dependence
-conditions that permit in-sample comparisons \citep[see][for a
-review of this literature]{Wes:06}.%
-\footnote{Like us, \citet{Ana:07} allows the number of regressors to
-  increase with $T$.  But in that paper, the number of regressors
-  increases slowly enough that the OLS coefficients are consistent and
-  asymptotically normal.} %
-\citet{GiW:06} and
-\citet{GiR:09, GiR:10} are exceptions.  Instead of focusing on
-hypotheses that can be tested by in-sample comparisons, \citet{GiW:06}
-derive an OOS test for the null hypothesis that the difference
-between two models' OOS forecasting performance is unpredictable, a
-martingale difference sequence; \citet{GiR:09} test whether the OOS
-forecasting performance of a model suffers from a breakdown relative
-to its in-sample performance; and \citet{GiR:10} test whether the
-forecasting performance is stable. However, those papers focus on a
-particular OOS estimation strategy and do not address why OOS
-comparisons might be useful as a general strategy.
-
-Since in-sample and OOS statistics require similar assumptions and
-test similar hypotheses, one might expect that they would give similar
-results.  They do not.  In-sample analyses tend to support more
-complicated theoretical models and OOS analyses support simple
-benchmarks, as seen in \citet{MeR:83}, \citet{StW:03}, and
-\citet{GoW:08}.  Since these different approaches strongly influence
-the outcome of research, it is important to know when each is
-appropriate.  The explanations in favor of OOS comparisons claim
-that they should be more robust to unmodeled instability
-\citep{ClM:05,GiW:06,GiR:09,GiR:10} or to overfit
-\citep{Mcc:98,Cla:04}.  Both explanations presume that the in-sample
-comparison is invalid and the OOS comparisons are more reliable.  Of
-course, as \citet{InK:04,InK:06} point out, both in-sample and OOS
-methods could be valid, but the OOS methods could have lower power.
-
-In this paper, we study the ``overfit'' possibility and leave
-``instability'' to future research. This paper uses dimension
-asymptotics to study the behavior of OOS comparisons when at least
-one of the models is overfit---the number of its regressors
-increases with the number of observations so that their ratio remains
-positive.  Although overfit is sometimes used to describe the
-situation where a forecaster chooses from many different models,
-i.e. \textit{data-mining} or \textit{data-snooping}, we view these as
-separate issues.  Procedures that account for the presence of many
-models have been, and are continuing to be, developed \citep[see, for
-example,][]{Whi:00,Han:05,RoW:05,HHK:10,ClM:12b}, but it is unclear
-whether those procedures should themselves use in-sample or OOS
-comparisons.  Understanding the difference between in-sample and OOS
-comparisons in the context of a simple comparison between two models
-is necessary before resolving any new issues that arise with multiple
-comparisons. Moreover, the empirical research that motivates
-this paper uses \textit{pseudo} OOS comparisons and not
-\textit{true} OOS comparisons.  Even if a true OOS comparison
-could account for some forms of data-snooping better than
-\citepos{Whi:00} BRC or its extensions, in-sample and pseudo
-OOS comparisons would both be affected by the data-snooping, a
-point also made by \citet{InK:04}.
-
-We focus on linear regression models estimated with a fixed window
-for simplicity, but our basic
-conclusions should be true for other models as well.  Under this
-asymptotic theory, where the number of regressors $k$ increases with $T$
-so that $\lim k/T$ is positive and less than one,
-the OLS coefficient estimator is no longer
-consistent or asymptotically normal \citep{Hub:73} and has positive
-variance in the limit.  We show that, even so, the usual OOS average
-is asymptotically normal and can consistently estimate the difference
-between the models' generalization error, the expected loss in the
-future conditional on the on the data available in period
-$T$.%
-\footnote{See, for example, \citet{HTF:08} for a discussion of
-  generalization error.} %
-Under these asymptotics, the generalization
-error does not converge to the expected performance of the pseudo-true
-models, so existing in-sample and OOS comparisons measure different
-quantities and should be expected to give different results for
-reasons beyond simple size and power comparisons.  Under our limit theory,
-the model that is closer to the true DGP in population can forecast
-worse.  In such a situation, a standard in-sample comparison would
-correctly reject the null hypothesis that the benchmark is true, and
-an OOS comparison would correctly fail to reject the null that the
-benchmark is more accurate.%
-\footnote{In a pair of papers similar to
-  ours, \citet{ClM:12,ClM:12b} study in-sample and OOS tests that
-  the larger model has nonzero coefficients that are too close to zero
-  to expect the model to forecast more accurately.  Like this paper,
-  they argue that the larger model can be true but less accurate.
-  However, they focus on an aspect of the DGP that makes this
-  phenomenon likely, while we focus on the coefficient estimates that
-  produce less accurate forecasts.  Moreover, the implications of our
-  asymptotic theories are different and their papers do not provide
-  reasons to do OOS comparisons.} %
-Also note that, in this situation, a model that performs well
-in-sample can perform badly out-of-sample even if there are no
-structural breaks or other forms of instability.  Researchers
-have argued that a breakdown of in-sample forecasting ability
-indicates a structural break (see \citealp{BoH:99} and
-\citealp{StW:03} among others), but this breakdown can be caused by overfit as
-well.
-
-Our results can justify OOS comparisons when researchers want to
-choose a model for forecasting.  Although there has been little
-emphasis on hypothesis testing in this setting, testing is usually
-appropriate: there is usually a familiar benchmark model in place, and
-the cost of incorrectly abandoning the benchmark for a less accurate
-alternative model is higher than the cost of incorrectly failing to
-switch to a more accurate alternative.  We show that the DMW test
-lets the forecaster control the probability of the first error, just
-as with conventional hypothesis testing.
-
-But we also identify new practical limitations for applying the DMW
-test to overfit models.
-Since the models' coefficients are imprecisely estimated in the limit,
-the test sample must be small enough that the model estimated over the
-training sample is similar to the one that will be estimated over the
-full sample.  In particular, $P/T \to 0$ is required for consistent
-estimation of the difference in the two models' performance,
-and $P^2/T \to 0$ is required for valid confidence
-intervals and inference.  For larger $P$, the OOS comparisons remain
-asymptotically normal, but are centered on the forecasting performance
-associated with the period-$R$ estimates.  In practice, researchers
-typically use large values of $P$, so these studies may be too
-pessimistic about their models' future accuracy if they use the DMW
-test.  Section~\ref{sec:oostheory} lays out the asymptotic behavior of
-the DMW test under this limit theory.
-
-Popular in-sample tests and model selection criteria, like the Wald
-test, AIC, and BIC, do not help forecasters in this setting. We show
-that these statistics can no pick out the more accurate model. For
-many DGPs they will choose a larger alternative model over a small
-benchmark model with probability approaching one, regardless of which
-model is more accurate.%
-\footnote{Our result holds for a broad class of
-  full-sample statistics, but there may be other potential statistics
-  that mimic the OOS test and remain valid. Exploring such
-  statistics is left for future research.} %
-This result holds even though modifications of the $F$-test are valid
-under this asymptotic theory, as shown by \citet{BoB:95},
-\citet{AkA:00}, \citet{AkP:04}, \citet{Cal:11c}, and \citet{Ana:12},
-among others.%
-\footnote{Also see \citet{Efr:86,Efr:04} for a discussion
-  of naive in-sample loss comparisons.} %
-Moreover, under this asymptotic theory, many recent OOS test
-statistics, such as those derived by \cite{ClM:01,ClM:05},
-\citet{Mcc:07}, and \citet{ClW:06,ClW:07} should have the same
-problems as in-sample tests.%
-\footnote{Our theoretical results apply
-  directly to \citepos{Mcc:07} OOS $t$-test, since it simply
-  proposes more liberal critical values for the same test statistic
-  that we study.  Since \citet{ClW:06,ClW:07} use a finite length
-  estimation window, our asymptotics are incompatible with theirs and
-  prevent us from studying their test directly, as well as
-  \citepos{GiW:06} and other tests based on \citepos{GiW:06}
-  asymptotics.  But \clws\ test can be viewed as a stochastic
-  adjustment to the critical values of the usual OOS $t$ test, so
-  our conclusions should apply informally as well.  Specifically, we
-  show that the DMW test rejects with probability equal to nominal
-  size when the estimated benchmark model is expected to be more
-  accurate, so more liberal critical values result in overrejection.} %
-These tests are also designed to reject the benchmark when the
-alternative model is true, and so they may reject too often when the
-benchmark is false but more accurate.  Obviously, since the
-distribution of these statistics converges to the normal when $P/T \to
-0$ (with the number of regressors fixed), these statistics behave like
-the DMW test when $P$ is small, but should overreject the benchmark
-when $P$ is large. Section~\ref{sec:insample} presents our theoretical
-results for full-sample statistics and Section~\ref{sec:mc} presents
-Monte Carlo evidence to support these claims.
-
-Finally, this paper also introduces a new method of proof for OOS
-statistics.  We use a coupling argument (Berbee's Lemma, 1979) to show
-that sequences of OOS loss behave like mixingales when the
-underlying series are absolutely regular, even if the forecasts depend
-on non-convergent estimators.  Moreover, transformations of these
-processes also behave like mixingales when recentered, so 
-the arguments used to prove asymptotic
-results for Near Epoch Dependent (NED) functions of mixing processes
-can be used for these OOS processes with only slight modification.
-
-The rest of the paper proceeds as follows.
-Section~\ref{sec:assumptions} introduces our notation and assumptions.
-Section~\ref{sec:theory} gives the main theoretical results for the
-DMW OOS test, shows that standard in-sample tests reject the
-benchmark model too often when it is false but more accurate than the
-alternative, and shows that standard model selection methods choose the
-larger model too often under similar conditions. Section~\ref{sec:mc}
-presents a Monte Carlo study supporting our theoretical results.
-Section~\ref{sec:empirics} applies the OOS statistic to
-\citepos{GoW:08} dataset for equity premium prediction, and
-Section~\ref{sec:conclusion} concludes.  Proofs and supporting results
-are listed in the Appendix.
-
-\section{Setup and assumptions}\label{sec:assumptions}
-
-The first part of this section will describe the environment in detail
-and set up our models and notation. The second part will list the
-assumptions underlying our theoretical results.
-
-\subsection{Notation and forecasting environment}
-We assume the following forecasting environment. There are two
-competing linear models that give forecasts for the target,
-$y_{t+\h}$:
-\begin{equation}
-y_{t+\h} = x_{1t}'\theta_1 + \e_{1,t+h}, \quad\text{and}\quad
-y_{t+\h} = x_{2t}'\theta_2 + \e_{2,t+h};
-\end{equation}
-$t = 1,\dots,T-h$, $\h$ is the forecast horizon and the
-variables $y_t$, $x_{1t}$, and $x_{2t}$ are all known in period $t$.
-The coefficients $\theta_1$ and $\theta_2$ minimize the population
-Mean Square Error, so
-\begin{equation}
-  \theta_i = \argmin_\theta \sum_{t=1}^{T-\h} \E (y_{t+\h} - x_{it}'\theta)^2,
-\end{equation}
-making $\e_{i,t+\h}$ uncorrelated with $x_{i,t}$; $\e_{i,t+\h}$ can exhibit
-serial correlation so both of the linear models may be misspecified.
-Let $\mathcal{F}_t = \sigma(y_1, x_1, \dots, y_t, x_t)$ be the information
-set available in period $t$,
-with $x_t$ the vector of all stochastic elements of $x_{1t}$ and $x_{2t}$ after
-removing duplicates, and let $\E_t$ and $\var_t$ denote the
-conditional mean and variance given $\mathcal{F}_t$.  The first model
-uses $K_1$ regressors, and the second uses $K_2$.  Without loss of
-generality, assume that $K_1 \leq K_2$. At least one of the models is
-overfit, which we represent asymptotically by letting $K_2$ grow with
-$T$ quickly enough that $\lim K_2/T$ is positive; $K_1$ may grow with
-$T$ as well. Since the models change with $T$, a
-stochastic array underlies all of our asymptotic theory, but we
-suppress that notation to simplify the presentation.
-
-In the settings we are interested in, a forecaster observes the data
-$(y_t,x_t)$ for periods 1 through $T$ and divides the observations
-into an estimation sample of the first $R$ observations and a test
-sample of the remaining $P$ observations. The forecaster then compares
-the models' performance over the test sample, which entails
-constructing two sequences of forecasts, (using a fixed-window
-estimation strategy)
-\begin{equation}
-\hat y_{i,t+\h} = x_{it}'\hat{\theta}_{it}, \qquad \text{for } i=1,2;
-\ t = R+1,\dots,T-h,
-\end{equation}
-where
-\begin{equation}
-  \bh{it} = \Big(\sum_{s=1}^{R-\h} x_{is}x_{is}'\Big)^{-1} \sum_{s=1}^{R-\h}
-  x_{is} y_{s+\h}, \qquad \text{for } i=1,2;\ t = R+1,\dots, T - \h.%
-\footnote{It may not be clear why we are using a $t$ index in $\bh{it}$,
-    since $\bh{it} = \bh{iR}$ almost surely for all $t \leq T-h$.
-    But $\bh{it}$ will be defined for $t > T-\h$
-    soon and will not equal $\bh{iR}$ for those values of $t$.} %
-\end{equation}
-
-The models are then compared by their forecast errors over the test
-sample.  There are many statistics that have been considered in the
-literature, but we focus on perhaps the most natural, the DMW \oost\
-test \citep{DiM:95,Wes:96}.%
-\footnote{The core insights of our paper apply to other OOS statistics
-  as well.} %
-This statistic is based on
-the difference in the models' loss over the test sample, $\oosA$,
-defined as
-\begin{equation}
-  \oosA \equiv P^{-1} \oosSum{t}{1} D_t
-\end{equation}
-where
-\begin{equation}\label{eq:16}
-  D_t = L(y_{t+\h} - x_{1t}'\bh{1t}) - L(y_{t+\h} - x_{2t}'\bh{2t}),
-\end{equation}
-and $L$ is a known loss function. The \oost\ test is defined as
-$\sqrt{P} \oosA / \sh$, where $\sh^2$ is an estimator of the
-asymptotic variance of $\oosA$. (Possibly a Heteroskedasticity- and
-Autocorrelation-Consistent, or HAC, estimator.)
-
-Most theoretical research, such as \citet{DiM:95}, \citet{Wes:96},
-and \cite{Mcc:07}, has focused on using the \oost\ statistic to test
-hypotheses about the pseudo-true values $\theta_1$ and $\theta_2$.  In
-particular, that research focuses on testing the null hypothesis that
-\begin{equation}\label{eq:21}
-  \E L(y_{t+\h} - x_{1t}'\theta_{1}) - \E L(y_{t+\h} - x_{2t}'\theta_{2}) = 0.
-\end{equation}
-But the population quantities in \eqref{eq:21} do not determine which
-model is more accurate in finite samples and, under our asymptotics,
-in the limit when models are allowed to be overfit. The models'
-accuracy will also depend on the specific estimates of $\theta_1$ and
-$\theta_2$ used to produce the forecasts. In this setting, where the
-forecaster will use one of the models to make a number of predictions
-in the future---call the number of predictions $Q$---the quantity of
-interest becomes
-\begin{equation}
-  \E_T \oosB \equiv Q^{-1} \sum_{t=T+1}^{T+Q} \E_T D_t,
-\end{equation}
-where $D_t$ is defined in Equation~\eqref{eq:16} but here uses the
-full-sample estimates of the models' parameters,
-\begin{equation}
-  \bh{it} = \Big(\sum_{s=1}^{T-\h} x_{is}x_{is}'\Big)^{-1} \sum_{s=1}^{T-\h}
-  x_{is} y_{s+\h}, \qquad \text{for } i=1,2;\ t = T+1,\dots, T + Q.
-\end{equation}
-If $\E_T \oosB$ is positive, the second model is expected to forecast
-better than the first over the next $Q$ periods, and if $\E_T \oosB$
-is negative then the first model is better. We use a conditional
-expectation because the coefficient estimates in $\oosB$ are
-stochastic but known in period $T$, and their values will determine
-the performance of the two models.
-
-Under conventional fixed-$K$ asymptotic theory, $\E_T \oosB$ would
-converge in probability to the difference in the expected loss
-associated with the pseudo-true models,%
-\footnote{Under standard stationarity, moment, and weak-dependence
-  conditions.} %
-i.e. the LHS of~\eqref{eq:21}.
-\begin{equation}\label{eq:22}
-  \E L(y_{t+\h} - x_{1t}'\theta_{1}) - \E L(y_{t+\h} - x_{2t}'\theta_{2}).
-\end{equation}
-But if $K_2$ increases with $T$ these quantities can have different
-limits. For a simple example, assume squared-error loss, let $x_{1,t}
-= 1$ for all $t$, and let $(y_{t+\h},x_{2,t})$ be i.i.d. $N(0,
-\Sigma)$.  Then
-\begin{align*}
-  \E_T \oosB - & \big(\E L(y_{t+\h} - x_{1t}'\theta_{1}) - \E L(y_{t+\h} - x_{2t}'\theta_{2})\big) \\
-  &= \big(\E_T (y_{T+\h+1} - \bh{1,T})^2 - \E_T (y_{T+\h+1} - x_{T+1}'\bh{2,T})^2\big) -
-  \big(\E y_{T+\h+1}^2 - \E (y_{T+\h+1} - x_{T+1}'\theta_2)^2 \big)\\
-  &= (\bh{2,t} - \theta_2)' \Sigma_x (\bh{2,t} - \theta_2) + o_p(1).
-\end{align*}
-This last term has expectation $\var(y_T) \frac{K_2}{T - K_2 - 1}$ and
-would converge to zero if $K_2$ were fixed, but does not when $\lim
-K_2 / T > 0$. In Section~\ref{sec:oostheory} we show that the \oost\
-statistic can estimate $\E_T \oosB$ under our increasing $K$
-asymptotics and does not estimate the expected loss associated with
-the pseudo-true coefficients.
-
-The conditional expectation $\E_T \oosB$ has been studied heavily in
-cross-sectional settings with independent observations. In such a
-setting, $\E_T \oosB$ is equal to the difference in the models'
-\emph{generalization error}, which has been used widely as a measure
-of model accuracy in the machine
-learning literature \citep[see][for further discussion]{HTF:08}.
-Moreover, with i.i.d. observations, the expectation of $\E_T \oosB$
-equals \citepos{Aka:69} Final Prediction Error (FPE). Both
-generalization error and FPE are defined by a model's
-performance on a new, independent, data set, but, for lack of a better
-term, we will call $\E_T \oosB$ the difference in generalization error
-for the rest of the paper with hopefully no risk of confusion.
-
-Finally, define the following notation.  The $l_v$-norm for vectors in
-$\Re^p$ (with $p$ arbitrary) is denoted $\lvert \cdot \rvert_v$, and
-the $L_v$-norm for $L_v$-integrable random variables is $\lVert \cdot
-\rVert_v$.  The functions $\eigen_i(\cdot)$ take a square-matrix
-argument and return its $i$th eigenvalue (with $\eigen_{i}(A) \leq
-\eigen_{i+1}(A)$ for any matrix $A$).  All limits are taken as $T \to
-\infty$ unless stated otherwise.
-
-\subsection{Assumptions}
-
-The next conditions are assumed to hold throughout the paper.  The first
-assumption controls the dependence of the underlying random array.
-The second lays out the details of our asymptotic approximation.
-The third assumption controls the
-smoothness of the loss function and bounds the moments of the
-difference in the models' performance; the fourth assumption describes
-the behavior of the estimation and test windows.  And the last
-assumption describes the kernel used to estimate the OOS average's
-asymptotic variance.
-
-\begin{asmp}\label{asmp-1}
-  The random array $\{y_t,x_t\}$ is stationary and absolutely regular
-  with coefficients $\beta_j$ of size $-\rho/(\rho-2)$; $\rho$ is
-  greater than two and discussed further in Assumption \ref{asmp-3}.
-\end{asmp}
-
-This assumption is a standard condition on the dependence of the
-underlying stochastic array. The only novelty is that we use
-absolute regularity instead of strong or uniform mixing as our
-weak dependence condition; absolute regularity admits a particular
-coupling argument, ``Berbee's Lemma'' \citep[reproduced in this
-paper as Lemma A.1 for reference]{Ber:79} that is
-unavailable for strong mixing sequences; absolute regularity
-implies uniform mixing, so this assumption is not unduly strong.
-For a detailed discussion of these weak dependence conditions,
-please see, for example, \citet{Dav:94}.
-
-Our strict stationarity assumption is also somewhat stronger than is
-typically used; \citet{Wes:96} and \citet{Mcc:07}, for example,
-present results assuming covariance stationarity of the loss
-associated with the pseudo-true models. We need to make a stronger
-assumption because we will need to prove asymptotic results where the
-$\bh{it}$ remain random---so we would need covariance stationarity to
-hold for almost all estimates of $\theta_i$, and not just for the
-pseudo-true value.
-
-The next assumption describes our asymptotic experiment.
-\begin{asmp}\label{asmp-2}
-  The number of regressors for each model, $K_1$ and $K_2$, are less
-  than $R$, and $K_2/T$ and $(K_2-K_0)/T$ are uniformly positive;
-  $K_0$ is the number of regressors shared by the two models ($K_1/T$
-  can be uniformly positive as well, but is not required to be).
-
-  The variance of $y_{t+\h}$ given $\mathcal{F}_t$ is uniformly
-  positive and finite, and all of the eigenvalues of the covariance
-  matrix of $x_t$ are uniformly positive and finite as well.
-  Moreover,
-  \begin{align*}
-    &\eigen_{\max}(X_{iS}'X_{iS}) = O_{L_3}(S),&
-    &\eigen_{\max}(\E(X_{iT}'\ep{iT}\ep{iT}'X_{iT}
-    \mid X_{iR}'X_{iR}, X_{iT}'X_{iT})) = O_{L_3}(S),\\
-    &\eigen_{\max}((X_{iS}'X_{iS})^{-1}) = O_{L_3}(1/S),&
-    &\eigen_{\max}\Big(\E\Big( \sum_{s,t=R+1}^{T-h} \e_{is} \e_{it} x_{is}x_{it}'
-    \,\Big|\, X_{iR}'X_{iR} \Big)\Big) = O_{L_3}(P),
-  \end{align*}
-  for large enough $T$, where $S = R,T$, $i = 1,2$,
-  \[ X_{iT} \equiv [x_{i1} \quad \dots \quad x_{i,T-\h}]' \qquad
-  \text{and} \qquad \ep{iT} = (\e_{i,1+\h}, \dots, \e_{i,T})'.\]
-
-  Additionally, the Euclidean norms of the pseudo-true coefficients,
-  $\theta_1$ and $\theta_2$, satisfy $|\theta_1|_2 = O(1)$ and
-  $|\theta_2|_2 = O(1)$.
-\end{asmp}
-
-The assumption that $y_{t+\h}$ and $x_t$ have positive and finite
-variance is straightforward.  The conditions on the eigenvalues are
-technical and control the behavior of the OLS estimator as the
-number of regressors gets large.  The restrictions on the pseudo-true
-coefficients ensure that the regression model doesn't dominate the
-variance of $y_{t+\h}$ in the limit.
-
-We can see that these conditions are trivially satisfied when the
-underlying series are i.i.d.\ Normal and the regression includes a
-constant.
-\begin{example}
-  If $(x_{t}, y_t)$ are i.i.d. $N(0, \Sigma)$ where $\Sigma$ is
-  uniformly positive definite, then
-  \begin{equation*}
-    \theta = \cov(y_t, x_t) \var(x_t)^{-1}
-  \end{equation*}
-  and the regression constant is
-  \begin{equation*}
-    \theta_0 = \E y_t - \cov(y_t, x_t) \var(x_t)^{-1} \E x_t
-  \end{equation*}
-  where both of these terms follow directly from the normality
-  assumption.  Then $|\theta|_2 = O(1)$ as a consequence of uniform
-  positive definiteness of $\Sigma$ and $\varepsilon_t \sim i.i.d.\
-  N(0, v^2)$ (independent of $x_t$) with
-  \begin{equation*}
-    v^2 = \var(y_t) - \cov(y_t, x_t) \var(x_t)^{-1} \cov(y_t, x_t)'.
-  \end{equation*}
-  Then we have
-  \begin{equation*}
-    \E(X_{T}'\ep{T}\ep{T}'X_T \mid X_{R}'X_{R}, X_{T}'X_{T})
-    = v^2 X_{T}'X_{T}
-  \end{equation*}
-  and
-  \begin{equation*}
-    \E\Big( \sum_{s,t=R+1}^{T-h} \e_s \e_t x_s x_t'
-    \,\Big|\, X_{R}'X_{R} \Big) = P v^2 \E x_t x_t'.
-  \end{equation*}
-
-  So the conditions amount to restrictions on the eigenvalues of
-  $X_T'X_T$, which are familiar from general OLS.
-\end{example}
-
-The next assumption establishes moment conditions for the OOS loss
-process and smoothness conditions for the loss function itself. The
-moment conditions are standard and apply to $D_t$, and the smoothness
-conditions are relatively weak.
-
-\begin{asmp}\label{asmp-3}
-  The loss function $L$ is continuous, has finite left and right
-  derivatives, and $L(0) = 0$.  There is a constant $B_L$ and a
-  function $L'$ that bounds the left and right derivative of $L$ at
-  every point such that $\|D_t\|_\rho \leq B_L$; $\|D_t^*\|_\rho \leq
-  B_L$ for all $t$, where
-  \begin{equation*}
-    D_t^* = L(y^* - x_1^{*\prime}\hat\theta_{1t})
-    - L(y^* - x_2^{*\prime}\hat\theta_{2t})
-  \end{equation*}
-  and $(y^*, x_1^*, x_2^*)$ equals $(y_t, x_{1t}, x_{2t})$ in
-  distribution but is independent of $\mathcal{F}_T$ ($\rho$ is defined
-  in Assumption~\ref{asmp-1}); and
-  \begin{equation*}
-    \| L'(y^* - x_{i}^{*\prime}
-    (\alpha \hat{\theta}_{iR} + (1-\alpha) \hat{\theta}_{iT})) \|_2
-    \leq B_L
-  \end{equation*}
-  for any $\alpha \in [0,1]$.
-\end{asmp}
-
-The differentiability condition in Assumption~\ref{asmp-3} is weak and
-allows the loss function itself to be non-differentiable; for example,
-absolute error and many asymmetric loss functions satisfy this
-assumption.  The next assumption controls the growth of the test and
-training samples.
-\begin{asmp} \label{asmp-4} $P, R, Q \to\infty$ and $P^2/T \to 0$ as
-  $T \to \infty$.
-\end{asmp}
-
-The requirements that $P$ and $R$ grow with $T$ are common. Parts of
-the assumption are new, in particular the requirement that $P^2/T \to
-0$.  See Lemma~\ref{res-convergence} for a discussion of its
-implications.  In practical terms, this assumption requires that the
-test sample be large and that the training sample be much larger, by
-enough that including or excluding the test sample does not affect the
-estimates of $\theta_1$ or $\theta_2$ very much.
-
-A final assumption restricts the class of variance estimators we will
-consider.  We use the same class of estimators studied by
-\citet{JoD:00} (their class $\mathcal{K}$); see
-their paper for further discussion.
-
-\begin{asmp}
-  \label{asmp-5} $W$ is a kernel from
-$\Re$ to $[-1,1]$ such that $W(0) = 1$, $W(x) = W(-x)$ for all $x$,
-\begin{equation*}
-  \int_{-\infty}^{\infty} \lvert W(x) \rvert dx < \infty, \quad
-  \int_{-\infty}^{\infty} \lvert \psi(x) \rvert dx < \infty
-\end{equation*}
-with
-\begin{equation*}
-  \psi(x) = \frac1{\sqrt{2\pi}} \int_{-\infty}^{\infty} W(z) e^{ixz}dz,
-\end{equation*}
-and $W(\cdot)$ is continuous at zero and all but a finite number of
-points.
-\end{asmp}
-
-Assumptions~\ref{asmp-1}--\ref{asmp-5} are broadly similar to
-\citepos{Wes:96} assumptions, except with regard to model complexity
-and the size of the test sample.  West assumes that $K_1$ and $K_2$
-are both finite, while we let them grow rapidly with $T$
-(Assumption~\ref{asmp-1}), and West lets $P/R$ converge to any value
-in $[0,\infty]$, while we require $P^2/R \to 0$
-(Assumption~\ref{asmp-4}).%
-\footnote{\citet{Wes:96} does not have a
-  second OOS period, so there is no analogue in his paper to our
-  restriction on $Q$.} %
-Obviously, these differences are
-related---allowing for complex models requires tighter constraints on
-the size of the test sample.  West allows more general estimation
-methods, while we restrict attention to OLS; the advantage of using
-OLS is that we can derive the inequality,
-\begin{equation*}
-  \| x_{it}'\bh{i,T+1} - x_{it}'\bh{iR} \|_2 \leq O(P/T)^{1/2}.
-\end{equation*}
-Our main results will hold for other models and estimation windows as
-long as a similar inequality exists, but proving such inequalities is
-left for future research.
-
-Our other assumptions are similar.  The loss function must be smooth
-almost everywhere, which is less restrictive than \citet{Wes:96}
-requires but is not new; \citet{Mcc:00} extends West's results to
-cover a similar case.\footnote{Our assumptions allow for discontinuous
-  loss functions, such as those proposed by \citet{PeT:92}.
-  \citet{Mcc:00} does not explicitly allow for such loss functions,
-  but it appears that his conclusions hold for them as well under the
-  restriction $P/T \to 0$.}  We assume full stationarity and absolute
-regularity of the underlying random array, while West assumes
-covariance stationarity and strong mixing of the transformed forecast
-errors; and the details our moment conditions are different, but seem
-that they would hold in similar environment to West's.  Finally, since
-West's is a more standard environment, he assumes the existence of a
-consistent estimator of the variance, while we construct it
-explicitly.  Only West's assumptions governing model complexity and
-the size of the test sample are substantially different than ours.
-
-\section{Theoretical Results}\label{sec:theory}
-The main result of the paper is Theorem
-\ref{res-confidence-intervals}, which shows that the OOS average is
-asymptotically normal and centered on $\E_T \oosB$.  This result holds
-even for nested models and can be used to construct confidence
-intervals or test hypotheses.  After presenting Theorem
-\ref{res-confidence-intervals}, we explain and present two key Lemmas
-used in its proof that add some insight into the nature of OOS
-comparisons, and then show that standard HAC OOS estimators can be
-used to consistently estimate the asymptotic variance of the OOS
-average.  We next present an example that illustrates some of these
-concepts, and then show that typical full-sample tests do not let
-researchers test hypotheses about $\E_{T} \oosB$ when the models are
-overfit.  In fact, in the limit they can reject a more accurate but
-false benchmark model almost surely.
-
-\subsection{Behavior of the DMW Test with Overfit}\label{sec:oostheory}
-Our first theorem justifies using the DMW $t$-test with a a short
-test sample.
-
-\begin{thm}\label{res-confidence-intervals}
-  Suppose that Assumptions \ref{asmp-1}--\ref{asmp-4} hold, that
-  $\sh^2$ is an estimator satisfying
-  \[
-    \sh^2 - \sigma^2 \to^p 0 \quad \text{with}\quad
-    \sigma^2 \equiv \var_R(\sqrt{P} \oosA) \equiv P \E_R(\bar{D}_R -
-    \E_R \bar{D}_R)^2,
-  \]
-  and that $\sigma^2$ is uniformly a.s. positive.  Then
-  \[
-  \frac{\oosA - \E_T\oosB}{\sh / \sqrt{P}}
-  \to^d N(0,1).
-  \]
-  Consequently, each of the usual Gaussian confidence intervals,
-  \begin{gather}
-  [\oosA - z_{\alpha/2} \, \sh /
-      \sqrt{P}, \oosA + z_{\alpha/2} \sh / \sqrt{P}],\label{interval-twosided} \\
-  [\oosA - z_{\alpha} \, \sh / \sqrt{P}, +\infty), \label{interval-greater}
-  \intertext{and}
-(-\infty, \oosA + z_{\alpha}
-      \, \sh / \sqrt{P}],
-    \end{gather}
-    contains $\E_T\oosB$ with probability $\alpha$ in the limit,
-  with $z_{\alpha}$ the $1-\alpha$ quantile of the standard normal
-  distribution.
-\end{thm}
-The requirement that $\sigma^2$ be uniformly a.s. positive is not
-restrictive under our asymptotic theory.  Since the models'
-coefficients are estimated with uncertainty in the limit, the two
-models give different forecasts even if they both nest the DGP.  This
-is intuitively similar to \citepos{GiW:06} rolling-window result, but
-comes from different asymptotic theory; Giacomini and White keep the
-variance of the OOS average positive by letting $P \to \infty$ with
-$R$ fixed; in this paper, $R \to \infty$ but the variance remains
-positive since $K \to \infty$ (quickly) as well.
-
-This result allows forecasters to use the DMW test to conduct
-inference about the models' accuracy.  Since the OOS average,
-$\oosA$, is asymptotically normal and centered on the expected future
-performance, $t$-tests constructed from the OOS errors necessarily
-test hypotheses about $\E_T \oosB$ and not the performance of the
-pseudo-true models or the unconditional performance of the
-models.\footnote{i.e. $\E L(\e_{1,t+\h}) - \E  L(\e_{2,t+\h})$ or $\E \oosB$.
-Note that the expectation of $\E_T \oosB$ equals $\E \oosB$ but that
-$\sqrt{P} (\E_T \oosB - \E \oosB)$ may not be asymptotically normal,
-which would be necessary for testing.}
-This application to testing can be expressed as its own theorem:
-\begin{thm}\label{res:oostest}
-Suppose that the conditions of Theorem \ref{res-confidence-intervals}
-hold and that $\lim \Pr[\E_T \oosB \leq 0] > 0$.  Then
-\begin{equation}
-  \lim \Pr[P^{1/2}\oosA/\sh > z_{\alpha} \mid \E_T
-  \oosB \leq 0] \leq \alpha.
-\end{equation}
-\end{thm}
-
-Two intermediate Lemmas will help us understand Theorem
-\ref{res-confidence-intervals} better.  Its proof consists of two
-steps: we can write
-\begin{equation}
-  \sqrt{P} (\oosA - \E_T \oosB) = \sqrt{P} (\oosA - \E_R
-  \oosA) + \sqrt{P} (\E_R \oosA - \E_T \oosB),
-\end{equation}
-so Theorem~\ref{res-confidence-intervals} holds if
-\begin{equation}\label{coefpart}
-  \E_R \oosA = \E_T \oosB + o_p(P^{-1/2}).
-\end{equation}
-and
-\begin{equation}\label{normalpart}
-  \sqrt{P}\frac{\oosA - \E_R \oosA}{\sigma} \to^d N(0,1)
-\end{equation}
-The first Lemma establishes~\eqref{coefpart} and the second shows that
-the process $\{D_t - \E_R \oosA\}$ is an $L_2$-mixingale of size
-$-1/2$ that satisfies a CLT, ensuring~\eqref{normalpart}.
-
-\begin{lem} \label{res-convergence}
-  Under Assumptions \ref{asmp-1}--\ref{asmp-4},
-  \begin{equation}\label{eq:7}
-    \E_T \oosB - \E_R \oosA = O_p(\sqrt{P/T}) + o_p(P^{-1/2} + Q^{-1/2}).
-  \end{equation}
-\end{lem}
-
-Note that $\E_T \oosB - \E_R \oosA$ is noise introduced by
-approximating the performance of the full-sample estimates with that
-of the partial-sample estimates.  Moreover, the $O_p(\sqrt{P/T})$ term
-is binding; it is straightforward to find examples for which
-$\sqrt{T/P}(\E_T \oosB - \E_R \oosA)$ does not converge to
-zero.\footnote{Notice that, if the observations are i.i.d. and
-  $(y_{t+h}, x_{it}) \sim N(0,I)$, $(\hat{\theta}_{iR} -
-  \hat{\theta}_{iT}) \sim N(0, (X_{iR}'X_{iR})^{-1} -
-  (X_{iT}'X_{iT})^{-1})$ given $X_{iT}$, and so
-  $\var(x_{i,T+1}'\hat{\theta}_{iR} - x_{i,T+1}'
-  \hat{\theta}_{iT}) \gg P K_i / (R - K_2)(T - K_2)$.}
-Consequently, there is little scope to relax our assumption that
-$P^2/T \to 0$.  If $\lim P^2/T$ is positive and finite then there is
-the possibility of adjusting the asymptotic distribution of the test
-statistic to account for this noise term as in \citet{Wes:96}, but we
-leave that to future research.  If $P^2/T \to \infty$, which is
-closest to common practice in applied research, the noise term
-dominates the asymptotic distribution of the OOS $t$-test and the
-test has only trivial power in the limit if it has correct size.
-
-\begin{lem}\label{res-mixingale}
-  Part 1: If Assumptions~\ref{asmp-1}--\ref{asmp-3} hold then the
-  inequality
-  \begin{equation}\label{mixingaleR}
-    \lVert \E_{R+j-l}(D_{R+j} - \E_R D_{R+j}) \rVert_2 \leq
-    \couplingConstant \; \zeta_l
-  \end{equation}
-  with $\zeta_l = O(l^{-1/2 - \delta})$ holds for some positive
-  $\delta$, any positive $j$, and any $l$ between 0 and $j$.  As a
-  consequence, $\{D_t - \E_R D_t, \mathcal F_t\}$ is an
-  $L_2$-mixingale of size $-1/2$.
-
-  \noindent Part 2: Moreover,~\eqref{normalpart} holds under
-  Assumptions~\ref{asmp-1}--\ref{asmp-4} if $\sigma^2$ is
-  a.s. uniformly positive.
-\end{lem}
-
-Mixingales satisfy a weak-dependence condition similar to MDSes and
-were introduced and studied extensively by
-\citet{Mcl:74,Mcl:75,Mcl:75b,Mcl:77}.  This lemma shows that the
-estimation uncertainty introduces dependence into the OOS forecast
-errors, but the additional dependence is contained in the term $\E_R
-\oosA$ and can be effectively removed by subtraction.  The second part
-of the Lemma shows that the basic mixingale CLT established by
-\citet{Jon:97} applies in this setting.\footnote{De Jong proves two
-  CLTs: one for mixingales and one for NED functions of mixing
-  processes.  His mixingale result makes assumptions about the
-  behavior of the sample second moment that arise as consequences of
-  NED.  The proof of Lemma~\ref{res-mixingale} shows that the
-  arguments used for de Jong's NED CLT continue to hold for our
-  OOS process---in effect, that the OOS process has slightly more
-  structure than required for it to be a mixingale.}  Note that
-Lemma~\ref{res-mixingale} does not require $P^2/T \to 0$.
-
-Finally, for Theorem \ref{res-confidence-intervals} to be useful, we
-need a consistent estimator of $\sigma^2$. Lemma
-\ref{res-variance-estimator} establishes that the usual OOS HAC
-variance estimators are consistent.\footnote{As with
-      Lemma~\ref{res-mixingale}, the proof of this lemma takes
-      \citepos{JoD:00} existing consistency results
-      for NED processes and shows that the same arguments can be
-      applied to our OOS mixingale.}
-
-\begin{lem}
-  \label{res-variance-estimator} Suppose Assumptions
-  \ref{asmp-1}--\ref{asmp-5} hold and that $\gamma \to \infty$ and
-  $\gamma/P \to 0$ as $T \to \infty$, and define
-  \begin{equation*}
-    \sh^2 \equiv P^{-1} \oosSum{s,t}{1} (D_t - \oosA)(D_{Rs} - \oosA)
-    \vWeight.
-  \end{equation*}
-  Then $\sh^2 - \sigma^2 \to^p 0$.
-\end{lem}
-
-The next subsection presents an example that clarifies the previous
-results.
-
-\subsection{An Example}\label{sec:example}
-
-Let $L(e) = e^2$, let $h
-= 1$, let the benchmark model have no regressors (i.e. $y_{t+1} \sim$
-white noise), suppose that $(y_{t}, x_{2t}) \sim i.i.d.\ N(0,I)$, and
-assume that $R > 2K_2 + 4$.\footnote{The restriction $R > 2 K_2 + 4$
-  allows us to use a convenient formula for moments of the
-  Inverse-Wishart distribution.}  Under these conditions,
-\begin{equation*}
-  D_t =
-  \begin{cases}
-    2 y_{t+1} x_{2t}'\hat{\theta}_{2R} -
-    \hat{\theta}_{2R}' x_{2t} x_{2t}' \hat{\theta}_{2R} & t \leq T \\
-    2 y_{t+1} x_{2t}'\hat{\theta}_{2T} -
-    \hat{\theta}_{2T}' x_{2t} x_{2t}' \hat{\theta}_{2T} & t > T.
-  \end{cases}
-\end{equation*}
-
-The first two conditional moments of $D_t$ for $t > R$ (given
-$\mathcal{F}_R$) are straightforward to derive: $\E_R D_t = -
-\hat{\theta}_{2R}' \hat{\theta}_{2R}$ and
-\begin{equation*}
-  \sigma^2 \equiv \E_R(D_t - \E_R D_t)^2 = 4
-  \hat{\theta}_{2R}' \hat{\theta}_{2R} +
-  \E_R(\hat{\theta}_{2R}' (I - x_{2t} x_{2t}')
-  \hat{\theta}_{2R})^2   \geq 4 \hat{\theta}_{2R}'
-  \hat{\theta}_{2R} \quad a.s.
-\end{equation*}
-Now, $\hat{\theta}_{2R}' \hat{\theta}_{2R}$ is
-a.s. positive and uniformly integrable with mean $4 K_2 / (R - K_2 -
-1)$ (since $(X_{2R}'X_{2R})^{-1}$ is Inverse-Wishart$(I_{K_2}, R)$),
-making $\sigma^2$ uniformly a.s. positive and ensuring that the
-distribution of the OOS average is not $P^{1/2}$-degenerate.  The
-natural OOS variance estimator is consistent for $\sigma^2$:
-\begin{align*}
-  \sh^2 &= P^{-1} \sum_{t=R+1}^{T-1} (D_t - \oosA)^2 \\
-  &= 4 \hat{\theta}_{2R}' \Big[P^{-1} \sum_{t=R+1}^{T-1}
-  \Big(y_{t+1} x_{2t} - P^{-1} \sum_{s=R+1}^{T-1} y_s x_{2s}\Big)
-  \Big(y_{t+1} x_{2t} - P^{-1} \sum_{s=R+1}^{T-1} y_s
-  x_{2s}\Big)'\Big] \hat{\theta}_{2R}' \\ & \quad - 4
-  \Big[P^{-1} \sum_{t=R+1}^{T-1} \Big(y_{t+1} x_{2t} - P^{-1}
-  \sum_{s=R+1}^{T-1} y_s x_{2s}\Big)' \hat{\theta}_{2R}
-  \hat{\theta}_{2R}' \Big(x_{2t} x_{2t}' - P^{-1}
-  \sum_{s=R+1}^{T-1} x_{2s} x_{2s}' \Big) \hat{\theta}_{2R} \Big]
-  \\ &\quad + P^{-1} \sum_{t=R+1}^{T-1}
-  \Big[\hat{\theta}_{2R}' \Big(x_{2t} x_{2t}' - P^{-1}
-  \sum_{s=R+1}^{T-1} x_{2s} x_{2s}' \Big) \hat{\theta}_{2R}  \Big]^{2}.
-\end{align*}
-As $P \to \infty$, the first term converges in probability to
-$\hat{\theta}_{2R}' \hat{\theta}_{2R}$, the second to zero,
-and the third to $\E_R(\hat{\theta}_{2R}'(I - x_{2t}x_{2t}')
-\hat{\theta}_{2R})^2$.  Since the number of regressors prevents
-$\hat{\theta}_{2R}$ from converging i.p. to zero (its expected
-value), $\sh^2$ does not converge to the unconditional
-variance.
-
-We can see that the OOS average obeys a CLT when centered at $\E_R
-\bar{D}_R$.  The centered and scaled OOS differences satisfy
-\begin{equation*}
-  \frac{D_t - \E_R D_t}{\sigma} =
-  \frac{2 y_{t} x_{2t}' \hat{\theta}_{2R} +
-    \hat{\theta}_{2R}' (I - x_t x_t') \hat{\theta}_{2R}}{\sqrt{4
-    \hat{\theta}_{2R}' \hat{\theta}_{2R} +
-    \E_R(\hat{\theta}_{2R}'(I - x_{2t} x_{2t}') \hat{\theta}_{2R})^2}}.
-\end{equation*}
-This sequence is not i.i.d. and we can not replace $\hat{\theta}_{2R}$
-with a sequence of constants $\theta_{2R}$ since $\hat{\theta}_{2R}$
-does not converge to a deterministic limit.  But $\sigma^{-1}
-\E_t(\oosA - \E_R\oosA) = 0$, making this sequence an
-MDS,\footnote{The sequence is actually exchangeable, but MDS is
-  enough to establish the CLT.} so it obeys a CLT as long as
-$\sigma^2$ is uniformly a.s. positive, which we have already
-established.  Lemma~\ref{res-mixingale} ensures that the CLT holds
-more generally.
-
-Finally, we can look at the difference $\E_R \bar{D}_R - \E_T
-\bar{D}_T$.  We can write this as
-\begin{align*}
-  \E_R \oosA - \E_T \oosB &= \hat{\theta}_{2R}'
-  \hat{\theta}_{2R} - \hat{\theta}_{2T}' \hat{\theta}_{2T} \\ &=
-  \eb_T'[\tilde{X}_{2R}(X_{2R}'X_{2R})^{-2}
-  \tilde{X}_{2R} - X_{2T}(X_{2T}'X_{2T})^{-2} X_{2T} ] \eb_T
-\end{align*}
-with $\tilde{X}_{2R}$ the $T \times K_2$ matrix $[X_{2R}'\ 0]'$.
-Standard results for the moments of quadratic forms and of the
-Inverse-Wishart distribution \citep{Haf:79} imply that
-\begin{equation*}
-  \E(\E_R \oosA - \E_T \oosB) = \frac{K_2 P}{(T - K_2 - 1)(R - K_2 - 1)}
-\end{equation*}
-and
-\begin{align*}
-  \var(\E_R & \oosA - \E_T \oosB) \\ &= \E
-  \big[\tr((X_{2R}'X_{2R})^{-1} - (X_{2T}'X_{2T})^{-1})\big]^2 + 2 \tr
-  \E\big((X_{2R}'X_{2R})^{-2} - (X_{2T}'X_{2T})^{-2}\big) \\ &\quad - \big[\tr
-  \E((X_{2R}'X_{2R})^{-1} - (X_{2T}'X_{2T})^{-1}) \big]^2 \\ &=
-  O(P/T)^2.
-\end{align*}
-So, in this example, $P^{1/2}(\E_R \oosA - \E_T \oosB) \to^p 0$
-if $P^3/T^2 \to 0$, which is slightly weaker than the general
-requirement that $P^2/T \to 0$.  If $\lim P^3/T^2 > 0$ the OOS average
-still obeys the MDS CLT, but it is not centered correctly at $\E_T
-\oosB$.
-
-\subsection{Failure of in-sample forecast evaluation}\label{sec:insample}
-This subsection establishes that in-sample tests like the $F$-test can
-overreject when the benchmark is more accurate than the alternative.
-The issue explored here is different than that of \citet{Cal:11c} and
-\citet{Ana:12}; in those papers, the authors demonstrate that full
-sample Wald and $F$-tests can be invalid under increasing-$k$
-asymptotics,%
-\footnote{\citet{Ana:12} shows that the Wald test is
-  invalid in general and gives an adjustment that corrects the
-  critical values; he also shows that the $F$-test is asymptotically
-  valid under certain conditions on the distribution of the
-  regressors.  \citet{Cal:11c} shows that the $F$-test is
-  asymptotically invalid without Anatolyev's constraint, and provides
-  a correction that gives valid tests.  Both papers only consider
-  independent observations.} %
-e.g. they can overreject when testing the
-null hypotheses that a set of the coefficients is zero.  This paper,
-though, looks at the behavior when the coefficients are non-zero but
-the estimated restricted model is more accurate.  In this setting,
-these tests reject the benchmark too often---more than their nominal
-size---and for most coefficient values will reject almost surely in
-the limit.  We also look at some common model selection statistics and
-find the same conclusion---they choose the larger model with high
-probability regardless of which model will forecast better.  To
-simplify the presentation, we'll only present results for nested
-models.
-
-Theorem~\ref{res:ftest} presents results for in-sample hypothesis
-tests.
-\begin{thm}\label{res:ftest}
-  Suppose Assumptions 1--3 hold, that the models are nested, and that
-  $L(e) = e^2$.  Also, let $\Lambda$ be a test statistic with nominal
-  size $\alpha$ that has acceptance region contained in the set
-  \[\{\hat{\theta}_T \mid (\hat{\theta}_T -
-  \theta_0)'V_T(\hat{\theta}_T - \theta_0) < c \}\] for large enough
-  $T$ and some $\theta_0$, $c$, and $V_T$, with $V_T$ a possibly
-  random matrix with all eigenvalues uniformly bounded in probability
-  and rank satisfying $\lim \rank(V_T)/T > 0$.  Then there exist
-  distributions for $(x_t, \e_{t+h})$ such that
-  \begin{equation}
-    \label{eq:11}
-    \Pr[\Lambda \text{ rejects} \mid \E_T \oosB \leq 0] \to^p 1
-    \quad \text{as} \quad
-    \theta'V_T\theta \to^p \infty \quad \text{($T$ is fixed)}
-  \end{equation}
-  for almost every sequence $\theta$ (a.e. with respect to Lebesgue
-  measure) and
-  \begin{equation}
-    \label{eq:15}
-    \plim_{T \to \infty} \Pr[\Lambda \text{ rejects} \mid
-    \E_T \oosB \leq 0] \geq \plim_{T \to \infty} \Pr[c + \delta < (\theta - \theta_0)' V_{T}
-    (\theta - \theta_0) \mid \E_T \bar{D}_T \leq 0]
-  \end{equation}
-  for any $\delta > 0$.
-\end{thm}
-Note that, if $V_T$ is nonstochastic or converges in probability,
-there are distributions on $(x_t, \e_{t+h})$ that are
-compatible with~\eqref{eq:15} such that
-\[\Pr[c + \delta < (\theta - \theta_0)'V_T (\theta - \theta_0) \mid
-E_T \bar{D}_T \leq 0] \to^p 1
-\]
-for any $\theta \neq \theta_0$.  Otherwise, the rejection probability
-will still depend on $\theta$ and $V_T$ and will typically be higher
-than the nominal size of the test.
-
-Theorem~\ref{res:ftest} covers a broad class of test statistics and
-allows the in-sample test to be valid or invalid in finite samples or
-asymptotically.  It implies that a large class of in-sample tests will
-reject if $\theta$ is nonzero, whether or not the alternative model is
-more accurate.  As an example, consider the $F$-test of the null
-hypothesis $A \theta =0$ with deterministic regressors and
-i.i.d. Normal errors where $\rank A = J$ and $\lim J/T > 0$.  Simple
-algebra reveals that the test rejects if $\hat{\theta}_T' V_T
-\hat{\theta}_T \geq 1$ with
-\begin{equation*}
-  V_T = (T/ J \hat{\xi}^{2}) A' (A (T^{-1}X_T'X_T)^{-1} A')^{-1} A;
-\end{equation*}
-$\xi^2$ is the variance of the model's innovations and $\hat{\xi}^2$ is
-the usual estimator based on the squared residuals.  Note that $\rank
-V_T = \rank A$ as long as $X_T'X_T$ is full rank.  Under the null $A
-\theta = 0$,
-\begin{equation*}
-  \hat{\theta}_T' V_T
-  \hat{\theta}_T =^d   (\xi^2/ J \hat{\xi}^2) \chi_J^2 =^d 1 + J^{-1/2} Z
-  + o_p(T^{-1/2}),
-\end{equation*}
-where $\chi_J^2$ is an independent $\chi^2$ random variable with $J$
-degrees of freedom and $Z \sim N(0,1)$.  Consequently, the $F$-test
-accepts whenever $\hat{\theta}_T$ is in a neighborhood of the cylinder
-defined by $\hat{\theta}_T' V_T \hat{\theta}_T = 1$ and rejects for
-$\hat{\theta}_T$ outside the neighborhood.%
-\footnote{If $V_T$ is full
-  rank, this equation defines an ellipsoid in $\mathbb{R}^K$;
-  otherwise the equation defines an ellipsoid in a subspace of
-  $\mathbb{R}^K$.} %
-The neighborhood shrinks as $T \to \infty$, so the
-$F$-test satisfies the conditions of Theorem~\ref{res:ftest} with
-$V_T$ as given above and $c = 1 + \delta$ for any $\delta > 0$.
-Notice that $c$ does not depend on the nominal size of the test and
-that the exact finite sample distribution of the $F$-test is known in
-this example, so the test is valid by conventional measures but the
-conclusions of Theorem~\ref{res:ftest} still hold.
-
-The intuition behind Equation~\eqref{eq:11} can be understood by
-simplifying further to the case $K_2 = 2$ and $K_1 = 0$, deterministic
-orthonormal regressors, and $V_T = I$, so
-\begin{equation*}
-  E_T \oosB = \theta_{1}^2 + \theta_{2}^2 - (\hat{\theta}_{T,1} -
-  \theta_{1})^2 - (\hat\theta_{T,2} - \theta_2)^2.
-\end{equation*}
-Under these conditions, the test rejects if $\hat{\theta}_{T}$ lies
-outside the circle centered at the origin with radius $c^{1/2}$ and
-$\E_T \oosB \leq 0$ holds for $\hat\theta_{T}$ on or outside a circle
-centered at $\theta$ passing through the origin.
-Figure~\ref{fig:rreject} depicts these regions.  Since the OLS
-estimator is normal with mean $\theta$, the probability that
-$\hat{\theta}_{T}$ falls in the acceptance region given $\E_T \oosB
-\leq 0$ vanishes as $\theta'\theta \to \infty$, even though the full
-model will give worse forecasts than the restricted model.
-
-\newcommand{\circlefigA}[4]{
-  \begin{tikzpicture}
-    \fill[lightgray] (-#3,-#3) rectangle (#4,#4);
-    % rejection region for F-test
-    \filldraw[fill=white,draw=black] (0,0) circle (#1);
-    % circle of equal generalization error
-    \filldraw[fill=white,draw=black] (1,1) let \p1=(1,1) in circle({veclen(\x1,\y1)});
-    \draw (1,1) let \p1=(1,1) in circle({veclen(\x1,\y1)});
-    \fill [black] (1,1) circle (2pt) node[right] {$(\theta_1,\theta_2)$};
-    \draw (0,0) circle (#1);
-    \draw (1,1)--(0,0);
-    % axes
-    \draw[->] (0,0)--(#2,0) node[right] {$\hat\theta_{T,1}$};
-    \draw[->] (0,0)--(0,#2) node[above] {$\hat\theta_{T,2}$};
-  \end{tikzpicture}
-}
-\newcommand{\circlefigB}[4]{
-  \begin{tikzpicture}
-    \fill[white] (-#3,-#3) rectangle (#4,#4);
-    % rejection region for F-test
-    \fill[lightgray] (0,0) circle (#1);
-    % circle of equal generalization error
-    \fill[white] (1,1) let \p1=(1,1) in circle({veclen(\x1,\y1)});
-    \draw (0,0) circle (#1);
-    \draw (1,1) let \p1=(1,1) in circle({veclen(\x1,\y1)});
-    \fill [black] (1,1) circle (2pt) node[right] {$(\theta_1,\theta_2)$};
-    \draw (1,1)--(0,0);
-    % axes
-    \draw[->] (0,0)--(#2,0) node[right] {$\hat\theta_{T,1}$};
-    \draw[->] (0,0)--(0,#2) node[above] {$\hat\theta_{T,2}$};
-  \end{tikzpicture}
-}
+Fill in the text...
 
 \begin{figure}
-  \centering
-  \begin{tabular}{cc}
-  \subfloat[]{\circlefigA{1}{2.5}{1.4}{3.2}\label{fig:circleA}} &
-  \subfloat[]{\circlefigB{1}{2.5}{1.4}{3.2}\label{fig:circleB}}  \\
-  \subfloat[]{\circlefigA{.3}{2.5}{1.4}{3.2}\label{fig:circleC}}  &
-  \subfloat[]{\circlefigB{.3}{2.5}{1.4}{3.2}\label{fig:circleD}}
-  \end{tabular}
-  \caption{Graphs indicating the rejection region and region of equal
-    generalization error for the models discussed in Section
-    \ref{sec:insample}.  The smaller model has no estimated parameters
-    and the larger has two coefficients.  The shaded regions in
-    Figures (a) and (b) show the rejection region and the acceptance
-    region respectively of the full-sample test given $\E_T \oosB \leq
-    0$ when the true elements of $\theta$ are moderately small.  Figures
-    (c) and (d) show the same regions when the true $\theta$ is large.}
-\label{fig:rreject}
-\end{figure}
-
-Equation~\eqref{eq:15} is more interesting and implies that these
-tests will almost surely reject the benchmark whenever we have a true
-but overfit and less accurate alternative.  The intuition is similar
-to the previous case.  As $K_2$ increases, the volume that
-$\hat{\theta}_{T}$ can occupy increases as well.  If $\theta$ is
-outside the acceptance region, the probability that $\hat{\theta}_{T}$
-is close to the origin and therefore inside the acceptance region of
-the test decreases.  In the limit, the probability that
-$\hat{\theta}_{T}$ is outside the acceptance region is one.
-
-A similar result for model selection follows as a Corollary to
-Theorem~\ref{res:ftest}.  Consistent model selection in this context
-is different than in the finite-$K$ case.  Here we want the
-probability of selecting a model given that it is more accurate to
-converge to one.  Formally, a model selection procedure is useful if
-\begin{gather}\label{eq:13}
-  \Pr[\text{model $1$ selected} \mid \E_T \oosB \leq 0] \to 1
-  \intertext{and} \Pr[\text{model $2$ selected} \mid \E_T \oosB > 0]
-  \to 1.\label{eq:14}
-\end{gather}
-Note that the conditioning event in~\eqref{eq:14} is different than in
-the testing results presented earlier, but otherwise they are similar.
-Theorem~\ref{res:ftest} implies that~\eqref{eq:13} will typically fail
-for overfit models for many common model selection methods, including
-adjusted $R^2$, the AIC, and the BIC.  Corollary~\ref{res:ic}
-contains the details.
-
-\begin{cor}\label{res:ic}
-  Suppose the conditions of Theorem~\ref{res:ftest} hold but that the
-  statistic $\Lambda'$ is used for model selection; $\Lambda'$ selects
-  the benchmark model for all $\hat{\theta}_T$ contained in a subset
-  of the region
-  \begin{equation*}
-    \{\hat{\theta}_T \mid \hat{\theta}_T'V_T \hat{\theta}_T < c\}
-  \end{equation*}
-  and selects the alternative for all $\hat{\theta}_T$ outside that
-  region.  Then there exist distributions on $x_t,\e_t$ such
-  that
-  \begin{equation}
-    \label{eq:17}
-    \plim \Pr[\Lambda' \text{ selects model 1} \mid \E_T \bar{D}_T \leq 0]
-    \leq \plim \Pr[\theta_0'V_T \theta_0 < c \mid \E_T \bar{D}_T].
-  \end{equation}
-\end{cor}
-As before, we often have
-\begin{equation*}
-  \Pr[\theta_0'V_T \theta_0 < c \mid \E_T \bar{D}_T] \to^p 0.
-\end{equation*}
-Just as we saw with the $F$-test, adjusted $R$-squared, the AIC and
-the BIC will only choose the benchmark model if $\hat{\theta}_T$
-lies in the neighborhood of the cylinder defined by $\hat{\theta}_T
-V_{T} \hat{\theta}_T = c$, regardless of which model is expected to
-forecast better.  These statistics differ in how they determine the
-size of the neighborhood, with the neighborhood shrinking slower for
-the BIC than the AIC.
-
-It is important to remember that the tests considered do not need to
-have correct size for the null $\theta = \theta_0$, but are allowed to
-in this analysis, so previous research, such as \citet{Cal:11c} and
-\citet{Ana:12}, does not predict these results.  However, these tests
-are poorly suited for choosing an accurate forecasting model and
-perform worse when the larger model is overfit or explains more of the
-variation of the dependent variable.  Essentially, for forecasting we
-want to know if the coefficient estimates are close to their true
-values, but in-sample statistics tell us only whether the estimates
-are close to a particular hypothesized value (usually zero).  There
-are lots of estimates that are both far from zero and far from their
-true values which cause in-sample statistics to incorrectly choose the
-alternative model.
-
-\section{Monte Carlo}\label{sec:mc}
-\newcommand{\thetanorm}{\ensuremath{\lvert \theta \rvert_2}} This
-section presents two simulations that investigate the accuracy of our
-theory in small samples.\footnote{Simulations were conducted in R
-  \citep{Rde:10} using Sweave \citep{Lei:02} and the Lattice
-  \citep{Sar:10}, RSQLite \citep{Jam:10}, tikzDevice
-  \citep{ShB:11:0.6.1}, and pgfSweave \citep{BrS:11:1.2.1} packages.}
-The first looks at the asymptotic normality of the DMW statistic
-centered on either $\E_R \oosA$ or $\E_T \oosB$.  The previous
-section's results imply that centering on the first should give an
-approximately normal statistic and centering on the second should give
-a normal statistic when $P$ is small relative to $T$.  The second
-simulation looks at the size and power of several statistics when
-conducting inference about the difference in the models'
-generalization error.  For all of the simulations, we look at
-fixed-window OOS tests to speed up computation time.
-
-\subsection{Setup}\label{sec:simulation-design}
-The Monte Carlo experiment is intentionally very simple so that we can
-isolate the influence of the models' complexity.  In particular, we do
-not include some features that are common in forecasting
-environments---serial dependence, heteroskedasticity, and complicated
-DGPs.  We simulate data for both studies from the equation
-\begin{equation}\label{eq:6}
-  y_t = x_t'\theta + \e_t,\quad \e_t \sim N(0,1),
-  \quad t=1,\dots,T.
-\end{equation}
-The first element of $x_t$ is 1 and the remaining $K_2-1$ elements are
-independent Standard Normal.  The benchmark model is
-\begin{equation}
-  \label{eq:1}
-  y_{1t} = \sum_{j=1}^{K_1} x_{jt}\theta_j + \e_t
-\end{equation}
-and the alternative model is the DGP \eqref{eq:6}.  We let
-$(K_1,K_2)$ equal either $(2,3)$ or $(T/20,T/10)$ to study our theory
-in its intended application as well as for more parsimonious models.
-We let $T$ equal 100, 250, 500, or 1000.  We also vary $\theta$, and do
-so giving the benchmark and the alternative model comparable weight in
-predicting $y_t$.  Specifically, we set
-\begin{equation*}
-  \theta_j =
-\begin{cases} \frac{c}{\sqrt{K_1}} & j = 1,\dots,K_1 \\
-\frac{c}{\sqrt{K_2 - K_1}} & j = K_1 + 1,\dots,K_2 \end{cases}
-\end{equation*}
-with $c$ equal to zero or one.  When $c$ is one, we're more likely to
-draw values of $X$ and $Y$ that make the estimated larger model more
-accurate than the benchmark, and when $c$ is zero we're unlikely to
-draw such values of $X$ and $Y$.  For all of the studies, $L(x) =
-x^2$.
-
-The first set of simulations study how well the theory in
-Section~\ref{sec:oostheory} works in practice.  For each draw of $X$
-and $Y$, we construct a one-sided OOS interval of the
-form
-\begin{equation*}
-  [ \oosA - 1.28 \hat{\sigma}, \infty) \quad\text{with}\quad
-  \sh^2 = \frac1P \sum_{t=R+1}^T (D_t - \oosA)^{2}
-\end{equation*}
-for $P$ set to every 10th value between 1 and $2T/3$.  We calculate
-the percentage of these intervals that contain $\E_R \oosA$ and that
-contain $\E_T \oosB$.  Since the data are i.i.d., both of these
-quantities are easy to calculate:
-\begin{equation*}
-  E_R \oosA = \Bigg[\sum_{i=1}^{K_1} (\tilde{\theta}_{iR} - \theta_i)^2 +
-  \sum_{i=K_1+1}^{K_2}\theta_i^2\Bigg] - \sum_{i=1}^{K_2} (\hat{\theta}_{iR} -
-  \theta_i)^2
-\end{equation*}
-and
-\begin{equation*}
-  E_T \oosB = \Bigg[\sum_{i=1}^{K_1} (\tilde{\theta}_{iT} - \theta_i)^2 +
-  \sum_{i=K_1+1}^{K_2}\theta_i^2\Bigg] - \sum_{i=1}^{K_2} (\hat{\theta}_{iT} -
-  \theta_i)^2
-\end{equation*}
-where $\tilde{\theta}$ indicates that the coefficient is estimated
-using only the regressors in the benchmark model and $\hat{\theta}$
-the full model.  We draw 2000 samples for each combination of the
-design parameters.
-
-The second simulation looks at the size and power of the test
-statistics when conducting inference about the models' generalization
-error.  The null hypothesis we test is
-\begin{equation}\label{eq:9}
-  H_0:\quad E_T \oosB \leq 0,
-\end{equation}
-We look at four different statistics---the full-sample $F$-test, the
-DMW $t$-test, the
-OOS $t$-test using McCracken's (2007)
-critical values,%
-\footnote{These critical values are not published for
-  $K_2-K_1>10$, so we do not report them for $K_2 = T/10$.} %
-and Clark and West's (2006, 2007) Gaussian out-of-sample
-statistic.%
-\footnote{Clark and West (2006, 2007) derive their statistic
-using the rolling window estimation scheme.  Here we use the same
-statistic, but with a fixed window scheme.} %
-For the $F$-test, we simply test whether the coefficients on the larger
-model are nonzero.  For the out-of-sample tests, we conduct a
-one-sided test of out-of-sample performance for every 10th value of
-$P$ as before.
-
-To estimate each test's size for the hypothesis \eqref{eq:9}, we draw
-samples from the DGP and discard those for which \eqref{eq:9} does
-not hold, until we have 2000 for each choice of the design parameters.
-The estimated size is the fraction of those samples in which the test
-statistic rejects.
-\subsection{Results}
-We discuss results for the confidence intervals first.
-Figures~\ref{fig:interval-R} and~\ref{fig:interval-T} show the
-coverage probability of these intervals as a function of $P$ for each
-combination of $T$, $K_1$ and $K_2$, and $c$.  The gray horizontal
-line shows the intervals' nominal coverage probability.  Each panel
-displays the coverage for a different choice of interval, centering
-term ($\E_R \oosA$ or $\E_T \oosB$) and combination of design
-parameters.
-
-Figure~\ref{fig:interval-R} gives the results for $\E_R \oosA$.  The
-actual coverage is very close to the nominal coverage except when $P$
-is very small.  The poor behavior for small $P$ is unsurprising, as it
-simply means that the CLT is a poor approximation when the test
-sample is small.  The intervals' good coverage holds even for the
-parsimonious models ($K_1=1$ and $K_2= 3$) which our theory does not
-necessarily apply to.
-
-Figure~\ref{fig:interval-T} gives the results for $\E_T \oosB$.  In
-rows 2, 4, 6, and 8---the overfit models---the coverage is near
-nominal coverage for moderately small values of $P$.  As $P$ increases
-to $2T/3$, the coverage increases to 1.  With the parsimonious model,
-the coverage is near nominal coverage for all $P$ for the one-sided
-interval with $c=1$, but only for moderately small $P$ when $c=0$.
-
-The behavior for $K_2 = T/10$ is exactly what our theory predicts.
-When $P^2/T$ is small, the coverage is near nominal levels.  The
-behavior as $P$ increases, combined with the results for $\E_R
-\oosA$, indicate that $\E_T \oosB \geq E_R \oosA$ in general.
-Since
-\[E_{T} \oosB = E_{R} \oosA + (E_{T} \oosB - E_{R} \oosA), \] and the
-interval is approximately centered at $\E_R \oosA$, the difference
-$\E_{T} \oosB - E_{R} \oosA$ adds a substantial positive quantity when
-$P^2/T$ is not near zero, increasing the coverage of the one-sided
-interval.
-
-We next present the size simulations,
-Figures~\ref{fig:ftest}--\ref{fig:ttest-power}.  For the OOS tests,
-the conditional rejection probability is plotted for each combination
-of $T$, $K_1$, $K_2$, and $c$ as a function of $P$.  The $F$-test does
-not depend on $P$, so a single value is presented for each
-combination.
-
-We'll look at the $F$-test first.  To make comparisons easier, the size
-is displayed as a dot plot in Figure~\ref{fig:ftest}.  Different
-panels display a different combination of $K_1$, $K_2$, and $T$, and
-each individual plot shows the empirical size for each choice of $c$.
-We see immediately that the actual and nominal size are essentially
-equal for $c = 0$, which is unsurprising.  For $c = 0$, the $F$-test is
-exact; moreover, the larger model will almost always be less accurate
-than the smaller one, so conditioning on $\E_T \oosB \leq 0$ is
-almost unrestrictive.  When $c$ increases, though, the $F$-test
-overrejects badly---rejecting at roughly 50\% when $c = 1$ for the
-parsimonious model and from 70\% to 100\% for the overfit model.  As
-our discussion in Section~\ref{sec:insample} predicts, the rejection
-probability increases with $T$ for the overfit model but does not
-depend on $T$ for the small model.
-
-Figure~\ref{fig:ttest-size} presents the size estimates for the DMW
-$t$-test.  Again, different panels display results for different
-combinations of the design parameters.  Each graph plots the rejection
-probability against $P/T$.  For $K/T=10$, the rejection probability
-falls as $P/T$ increases, from near nominal size when $P/T$ is small
-to zero when $P/T$ is near $2/3$.  Moreover, the rejection probability
-falls faster when $T$ is large, as our theory predicts.  When $K=3$,
-the rejection probability stays closer to nominal size, but falls with
-$P/T$ for $c=0$, under-rejecting by about 5pp when $P/T = 2/3$, and
-rises with $P/T$ for $c=1$, overrejecting by about 10pp when
-$P/T=2/3$.  For small $P$, the rejection probability is near 10\% for
-all simulations (the farthest is $K=T/10$, $c=0$, where the rejection
-probability is about 5\%; the other simulations are much closer).
-
-We observe the following patterns.  The
-DMW test has close to nominal size when $P$ is small for every
-combination of design parameters.  In most cases, the rejection
-probability decreases as $P/T$ increases---the exception is for $K_2 =
-3$ and $c=1$.  For the large-$K$ simulations, the rejection
-probability drops to zero for most of the simulations as $P/T$
-increases.  The rejection probability increases with $c$, but the
-rejection probability still is near nominal probability for small $P$
-with $c=1$.
-
-Clark and West's (2006, 2007) statistic, presented in
-Figure~\ref{fig:clarkwest}, behaves quite differently.  For $c=0$ the
-test is correctly sized for both the overfit and parsimonious studies,
-as we saw for the $F$-test.  When $c=1$, the rejection probability
-increases rapidly with $P/T$.  For $K_2=3$, the rejection probability
-is near 10\% when $P$ is small but about 40\% when $P/T = 2/3$.  For
-$K=T/10$, the rejection probability is even higher and increases with
-$T$ as well, from a maximum over 50\% when $T=100$ to a maximum of
-nearly 100\% when $T=1000$.
-
-Results using \citepos{Mcc:07} critical values are
-presented in Figure~\ref{fig:mccracken} and are similar to those using
-Clark and West's test.  For $c=0$ the rejection probability is nearly
-the test's nominal size.  For $c=1$, the rejection probability
-increases with $P/T$, from close to the nominal size when $P/T$ is
-small to over 25\% when $P/T = 2/3$.  Note that all of the simulations
-use the parsimonious model.  McCracken's statistic overrejects here
-by slightly less than Clark and West's, but still by a substantial
-amount.
-
-Since the DMW test tends to have low rejection probability, the
-test's power is a concern.  We'll present some power results,
-simulating from \eqref{eq:1} with $c = 1$ or 2 subject to the
-constraint that $\E_T \oosB > 0$.%
-\footnote{Draws of $X$ and $Y$ with
-  $\E_T \oosB > 0$ are very rare when $c=0$, so we do not present
-  results for that value of $c$.} %
-Figure~\ref{fig:ttest-power} plots
-the power for the DMW test; since the other test statistics greatly
-overreject, we do not present their power.  For $c=1$, the power is
-never greater than nominal size and decreases to zero as $P/T$
-increases for the overfit model.  For $c=2$ the power is better,
-increasing with $P/T$ for a stretch and then decreasing as $P/T$ grows
-beyond approximately 1/4 for the overfit model.  Larger values of $T$
-give a higher peak and greater power overall, but the power still
-falls to nearly zero if $P/T$ is too large (approximately 2/3 in our
-simulations).  The power with the parsimonious model is typically
-quite low but greater than nominal size for $c = 2$.
-
-Both sets of simulations support our theoretical results.  The first
-simulation confirms that the DMW OOS $t$-test is centered at $\E_R
-\oosA$ for all choices of $P$ and $R$ and is centered on $\E_T \oosB$
-only when $P$ is small.  The second simulation confirms that the DMW
-test has correct size for the null hypothesis that $\E_T \oosB \leq 0$
-when $P$ is small and that tests designed to test whether the
-benchmark is true, like the $F$-test and Clark and West's (2006, 2007)
-and McCracken's (2007) OOS tests can reject by much more than their
-nominal size when testing the null $\E_T \oosB \leq 0$.  Moreover,
-these simulations demonstrate that the restriction $P^2/T \to 0$ is
-binding in practice, as the DMW test under-rejects and has very low
-power when it is not satisfied.
-\section{Empirical exercise}\label{sec:empirics}
-This section presents an analysis of equity premium predictability
-similar to \citet{GoW:08}.%
-\footnote{All of the calculations in this
-  section are done in R \citep{Rde:10}.  We also use code provided by
-  \citet{Zeh:02}, \citet{Zei:04}, \citet{Har:10}, and
-  \citet{ShB:11:0.6.1}.} %
-We estimate the expected forecasting
-performance of the largest model they consider, a model with 13
-regressors, using 81 observations (annual data from 1928 to 2009).  We
-construct confidence intervals for the difference in performance
-between this model and a prevailing mean benchmark, and do so for
-different values of $R$ and $P$ to examine the effect of the training
-and test sample choice on this OOS statistic.  We find that the
-estimate of the larger model's Mean Squared Error (MSE) decreases relative to the
-benchmark as $R$ increases, but it is never smaller than the
-benchmark's.  This result, combined with the larger model's in-sample
-significance, suggests that there may be a real relationship between
-the equity premium and some of these predictors, but that the
-relationship can not be estimated accurately enough to be useful for
-forecasting and supports \citepos{GoW:08} conclusions.  These results
-hold even when imposing \citepos{CaT:08} restriction that the equity
-premium forecast be non-negative.
-
-We'll start with a very brief review.  \citet{GoW:08}
-study the OOS forecasting performance of different variables thought
-to predict the equity premium (calculated as the difference between
-the return on the S\&P 500 index and the T-bill rate).  Some of these
-variables are listed in
-Table~\ref{tab:equity}.%
-\footnote{Table~\ref{tab:equity} only lists the
-  variables used in \citepos{GoW:08} ``kitchen sink''
-  model.  Some of the variables that they use in bivariate models are
-  excluded from this model either because the series are too short or
-  because the variables are linear combinations of other variables.} %
-\citet{GoW:08} estimate the OOS forecasting
-performance of bivariate models of the form
-\[
-r_{t+1} = \beta_0 + \beta_1 x_t + \e_{t+1}
-\]
-using OLS with a recursive window, where $r_{t+1}$ is the equity
-premium and $x_t$ is a generic predictor, as well as some larger
-models.  They find that these models forecast no better than the
-prevailing mean of the equity premium.
-\citet{CaT:08} find that nonlinear extensions of
-Goyal and Welch's models are more accurate, either imposing sign
-restrictions on the estimated coefficients or imposing that the
-forecast be non-negative, but do not test for significance.
-
-Obviously, \citepos{GoW:08} bivariate models do not
-match the asymptotic theory of this paper, so we restrict our
-attention here to their ``kitchen sink'' model, which includes all of
-the variables, except for a few dropped because of data availability or
-(perfect) multicollinearity.  Formally, the benchmark and alternative models are
-\begin{eqnarray}
-  \label{eq:3}
-  r_{t+1} &=& \mu + \e_{1,t+1} \\
-  \label{eq:2}
-r_{t+1} &=& \beta_0 + \sum_{i=1}^K \beta_{i} x_{it} + \e_{2,t+1}
-\end{eqnarray}
-respectively and are estimated by OLS using the fixed-window scheme.
-The predictors are listed in Table~\ref{tab:equity}; for a detailed
-description of each predictor, please see Goyal and Welch's original
-paper.  In this model, there are 13 regressors (including the constant
-term) and we estimate the coefficients using annual data from 1928 to
-2009.  This makes the ratio $K/T$ equal to about 0.16.  We also
-present results for one of \citepos{CaT:08}
-restricted forecasting models.  For this model, we estimate
-\eqref{eq:3} and \eqref{eq:2}, but impose that $\hat r_{t+1}$ be
-non-negative for each forecast.  We then calculate the OOS test just
-as for the unconstrained model.
-
-Table~\ref{tab:gwinsample} gives the results of the full sample
-regression for Equation~\eqref{eq:2}, using Newey-West standard errors
-with two lags \citep{NeW:87}.%
-\footnote{We compare the test statistic
-  to critical values from the $F$-distribution.} %
-The $p$-value is
-very small (less than 0.01), indicating that the coefficients are
-nonzero in population and at least one of these predictors is
-correlated with the equity premium.  As we argue earlier, this result
-does not imply that the model will forecast well, which we look at
-next.
-
-To study the effect of the training sample size on the DMW statistic, we
-calculate the one-sided confidence interval for $\E_T \oosB$ given
-by \eqref{interval-greater} corresponding to the null and alternative
-hypotheses
-\[ H_0: \quad E_T \oosB \leq 0 \qquad
-H_A: \quad E_T \oosB > 0
-\]
-using the fixed-window scheme for each value of $R$ between 20 and
-$T-10$.  The standard deviation is estimated using a Newey-West
-estimator with $\lfloor P^{1/4}\rfloor$ lags.  For small values of
-$R$, the OOS average is expected to underestimate the performance of
-the larger model relative to the smaller, but this may not hold in
-this particular dataset.
-
-Figures~\ref{fig:empirics1} plots the OLS results and
-Figure~\ref{fig:empirics2} imposes \citepos{CaT:08} restriction.  The
-solid line in each figure shows the OOS average, $\oosA$, and the
-shaded region indicates the 95\% one-sided confidence interval implied
-by the DMW test.  Negative numbers indicate that the kitchen sink
-model has higher out-of-sample loss.  We can see that the same
-patterns hold for both models: the performance difference decreases as
-$R$ grows, but the kitchen sink model is never more accurate.  We also
-see that the performance difference decreases suddenly over the period
-$R=29$ to $R=34$ (corresponding to the years 1956--1961).
-Figure~\ref{fig:empirics3} plots the accuracy of the individual
-forecasts (only for the linear models) and shows that this change is
-the result of a sudden improvement in the kitchen sink model.  This
-change may indicate instability in the underlying relationship, as
-\citet{GoW:08} propose.
-
-In summary, we fail to reject the null that the benchmark prevailing
-mean model is more accurate than \citepos{GoW:08} kitchen sink.  This
-result is consistent with Goyal and Welch's original analysis.  Unlike
-Goyal and Welch, we attribute this result, at least in part, to
-parameter uncertainty---the full sample results indicate that the
-larger model could predict better than the benchmark with enough
-data.%
-\footnote{\citet{BWB:10} make a similar point about exchange rate
-models, but see also \citet{Chi:10} and \citet{Gia:10}.} %
-Obviously, this is an illustrative exercise only and is not meant to
-be comprehensive.  In this dataset, there is likely parameter
-instability that we have not addressed, and we have not dealt with
-variable persistence at all.  However, as we mention earlier, our
-requirement that $P$ be small should let our theoretical results
-extend to moderate instability, and the fact that we do not rely on
-the asymptotic distribution of the coefficient estimates should
-mitigate the effect of persistence as well.
-\section{Conclusion}\label{sec:conclusion}
-This paper gives a theoretical motivation for using OOS comparisons:
-the DMW OOS test allows a forecaster to conduct inference about
-the expected future accuracy of his or her models when one or both is
-overfit.  We show analytically and through Monte Carlo that standard
-full-sample test statistics can not test hypotheses about this
-performance.
-
-Our paper also shows that popular test and training sample sizes may
-give misleading results if researchers are concerned about overfit.
-We show that $P^2/T$ must converge to zero for the DMW test to give
-valid inference about the expected forecast accuracy, otherwise the
-test measures the accuracy of the estimates constructed using only the
-training sample.  In empirical research, $P$ is typically much larger
-than this.  Our simulations indicate that using large values of $P$
-with the DMW test gives undersized tests with low power, so this
-practice may favor simple benchmark models too much.  Existing
-corrections, proposed by \citet{ClM:01,ClM:05}, \citet{Mcc:07} and
-\citet{ClW:06,ClW:07}, seem to correct too much, though, and reject
-too often when the benchmark model is more accurate.
-
-More work remains.  The requirement that $P^2/T$ converge to zero is
-limiting, as it implies that in typical macroeconomic datasets, only a
-handful of observations should be used for testing.  This requirement
-can be relaxed only slightly; $P = O(T^{1/2})$ is required for the
-OOS test to have nontrivial power in general, but there are loss
-functions and DGPs for which some relaxation is possible.  This
-constraint could be mitigated by extending our results to
-cross-validation or other resampling strategies, or by constructing
-full-sample statistics that allow inference about $\E_T \bar{D}_T$.
-It would also be useful to extend our results to other forecasting
-models and to explore how stationarity could be relaxed, but such
-extensions are less important than improving the available statistics.
-
-\appendix
-\section*{Appendix: mathematical details}
-\setcounter{section}{1}
-% Change lemma style to prepend 'A'
-\setcounter{lem}{0}
-\renewcommand{\thelem}{A\arabic{lem}}
-
-\subsection*{Supporting results}
-The results in this paper rely heavily on a coupling argument for
-absolutely regular sequences, Berbee's Lemma \citep{Ber:79}.  Many of
-the results of this paper (Lemmas \ref{res-mixingale} and
-\ref{res-variance-estimator}) are modifications of existing results
-for NED functions of mixing processes by \citet{Jon:97} and
-\citet{JoD:00}; this coupling argument is used to explicitly derive
-inequalities that arise naturally for NED processes.  Lemma
-\ref{lem-basic-coupling} establishes these inequalities, which are
-based on a proposition of \citet{MeP:02}.
-
-We present \citeauthor{MeP:02}'s
-(\citeyear{MeP:02}) statement of Berbee's Lemma for
-the reader's reference.  In the following Lemma, $\beta(X,Y)$ is the
-coefficient of absolute regularity:
-\[
-\beta(X,Y) = \sup_{A \in \sigma(Y)} \E \lvert \Pr(A \mid \sigma(X))
-  - \Pr(A) \rvert.
-\]
-\begin{lem}\label{lem-berbee}\quad
-
-\begin{quotation}\noindent
-  Let $X$ and $Y$ be random variables defined on a probability space
-  $(\Omega, \mathcal{T}, \Pr)$ with values in a Polish space
-  $S$.  Let $\sigma(X)$ be a $\sigma$-algebra generated by $X$ and let
-  $U$ be a random variable uniformly distributed on $[0,1]$
-  independent of $(X,Y)$.  Then there exists a random variable $Y^{*}$
-  measurable with respect to $\sigma(X) \vee \sigma(Y) \vee
-  \sigma(U)$, independent of $X$ and distributed as $Y$, and such that
-  $\Pr(Y \neq Y^{*}) = \beta(X,Y)$.
-
-  \noindent\citep{MeP:02}
-\end{quotation}
-\end{lem}
-
-The advantage of this result over coupling arguments that use other
-forms of weak dependence is that the difference between the original
-variable, $Y$, and the new variable, $Y^{*}$, does not depend on their
-dimension.  Similar results for strong mixing sequences depend on the
-dimension of $Y$, which makes them unsuitable for our applications.
-
-\begin{lem}\label{lem-extend-mp}
-  Suppose that $X$ and $X^*$ are $L_p$-bounded random variables, with
-  $p > 2$, that satisfy ${\Pr[X \neq X^*] = c}$.  Then
-  \[
-    \lVert X - X^* \rVert_2 \leq 2^{1/p} (\lVert X \rVert_p + \lVert
-    X^* \rVert_p) c^{(p-2)/2p}
-  \]
-\end{lem}
-
-The proof is virtually identical to the proof of Proposition 2.3 in
-\citet{MeP:02} and is omitted.
-
-\begin{lem}\label{lem-basic-coupling}
-  Suppose Assumptions \ref{asmp-1}--\ref{asmp-3} hold.  Then, for any
-  T, $s$, $t$, and $u$ with $s < t \leq u$, there exist random
-  variables $D_t^*,\dots,D_u^*$ such that
-  \begin{equation}\label{eq:coupling1}
-    P[(D_{t}^*,\dots,D_u^*) \neq (D_{t},\dots,D_u)] \leq \beta_{t-s}
-  \end{equation}
-  and
-  \begin{equation}\label{eq:coupling2}
-    \E(\phi(D_{t}^*,\dots, D_u^*) \mid \mathcal{F}_s ) =
-    \int
-    \phi(D_{t},\dots,D_u) f(\mathbf{x}, \mathbf{y})\ d\mathbf{x}\ d\mathbf{y}
-  \end{equation}
-  almost surely for all measurable functions $\phi$ such that the
-  expectations are finite, where
-  \[ \mathbf{x} = (x_{t}', \dots, x_{u}')', \qquad
-  \mathbf{y} = (y_{t+\h},\dots,y_{u+\h})',\] and $f$ is the
-  joint density of $(\mathbf{x}, \mathbf{y})$.  Moreover,
- \begin{equation}\label{eq:coupling3}
-   \| D_v^* - D_v \|_2 \leq 2^{1+1/\rho} B_L
-   \beta_{t-s}^{\rhoExp}, \qquad v = t,\dots,u.
- \end{equation}
-\end{lem}
-
-\begin{proof}
-  The proof follows as a consequence of Lemmas \ref{lem-berbee} and
-  \ref{lem-extend-mp}.  Let $l = u-t$.  For any fixed values of $l$
-  and $T$, the sequence of vectors
-  \[ V_{t} = (y_{t+\h}, x_{t}', \dots, y_{t+l+\h}, x_{t+l}') \] is
-  absolutely regular of size $\rho/(\rho-2)$.  Berbee's Lemma implies
-  that there is a random vector $V^*$ that is independent of
-  $\mathcal{F}_s$, equal to $V_{t}$ in distribution, and satisfies
-  \[\Pr[V^* \neq V_{t}] = \beta_{t-s}.\]
-
-  Now define
-  \begin{equation*}
-    D_v^* =
-    \begin{cases}
-      L(y_{v+\h}^* - x_{1v}^{*\prime} \hat{\theta}_{1R}) - L(y_{v+\h}^* -
-      x_{2v}^{*\prime} \hat{\theta}_{2R}) & v \leq T \\
-      L(y_{v+\h}^* - x_{1v}^{*\prime} \hat{\theta}_{1T}) - L(y_{v+\h}^* -
-      x_{2v}^{*\prime} \hat{\theta}_{2T}) & v > T
-    \end{cases}
-  \end{equation*}
-  with $y_{v+\h}^*$ and $x_{iv}^*$ denoting the elements of $V^*$
-  corresponding to $y_{v+\h}$ and $x_{iv}$ in $V_{t}$.  Equations
-  (\ref{eq:coupling1}) and (\ref{eq:coupling2}) are satisfied by
-  construction, and (\ref{eq:coupling3}) follows from Lemma
-  \ref{lem-extend-mp}.
-\end{proof}
-
-\begin{lem}\label{lem:a2}
-  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-3} hold.  Let $b_T$ be a
-  sequence of integers such that $b_T \to \infty$ and $b_T = o(P)$ and define
-  \begin{equation*}
-    Z_i = \ZDef.
-  \end{equation*}
-  Then
-  \begin{equation}
-    \label{eq:10}
-    \sum_{i=1}^{\lfloor P/b_T \rfloor} (\E_R Z_i^2 - \E_{R+(i-1) b_T}
-    Z_i^2) \to^p 0.
-  \end{equation}
-  If Assumptions~\ref{asmp-4} and \ref{asmp-5} also hold and we define
-  \begin{gather*}
-    Z_{1t} = \varianceTermIIIa, \intertext{and} Z_{2t} =
-    \varianceTermIVb,
-  \end{gather*}
-  with $\delta > 0$, $\eta_\delta$ defined in the proof of
-  Lemma~\ref{res-variance-estimator}, and $\gamma_T = b_T/\delta$, then
-  \begin{equation}
-    \label{eq:12}
-    \vtSum (Z_{1t} Z_{2t} - \E_R Z_{1t} Z_{2t}) \to^p 0.
-  \end{equation}
-\end{lem}
-\begin{proof}
-\newcommand{\UFiltration}[1]{\ensuremath{\mathcal{F}_{(#1)b_{T}+R-P}}}%
-The first result,~\eqref{eq:10}, follows a similar argument to Lemma~5
-of \citet{Jon:97} and~\eqref{eq:12} to Lemma~A.4 of \citet{JoD:00}.
-Since these arguments are similar and our modification is the same for
-both, we'll just present the more complicated version,~\eqref{eq:12}.
-
-Note that $\{Z_{1t}^2 P\gamma_T/b_T\}$ and $\{Z_{2t}^2 P\gamma_T/b_T\}$
-are uniformly integrable.  As in~\citet[Lemma A.4]{JoD:00}, we can
-assume that there is a constant $C$ such that $Z_{1t}$ and $Z_{2t}$
-are bounded in absolute value by $C\sqrt{b_T/P\gamma_T}$; uniform
-integrability ensures that the difference between the unbounded random
-variables and these truncated versions is negligible for large enough
-values of $C$.
-
-Let $r = \lfloor 3P/2b_T \rfloor$ and rewrite the summation as
-\begin{align*}
-  \vtSum \vtIIIsummand &= \vtSumr \vtSuma \vtIIIsummand \\
-  &\quad+ \vtSumr \vtSumb \vtIIIsummand \\
-  &\quad+ \sum_{t=r b_T - P + R + 1}^{2P+R} \vtIIIsummand \\
-  &\equiv \vtSumr (U_i - \E_R U_i) + \vtSumr (U_i' - \E_R U_i') + o_{L_1}(1).
-\end{align*}
-The proof then holds if we can show that both $U_i$ and $U_i'$ obey
-LLNs.  We'll do so by proving that $\{U_i -\E_R U_i,
-\UFiltration{2i-1}\}$ and $\{U_i' - \E_R U_i', \UFiltration{2i}\}$ are
-$L_2$-mixingales of size $-1/2$ and using the bound $\E(\vtSumr (U_i -
-\E_R U_i))^2 = O(\vtSumr c_i^2)$ where the $c_i$ are the mixingale
-magnitude indices \citep{Mcl:75}.
-
-For non-negative $m$, we have
-\begin{equation*}
-U_i - \E_R U_i \in \UFiltration{2i+2m-1},
-\end{equation*}
-establishing half of the mixingale result trivially.  Now fix $i$ and $m >
-0$ and use Lemma \ref{lem-basic-coupling} to define $D_{ts}^*$
-for each $t =(2i-2)b_T-P+R+1,\dots,(2i-1)b_T-P+R$ and $s =
-\max(t-b_T,R+1),\dots,\min(t+b_T,T-\h)$ such that
-\begin{equation*}
- \E_R D_{ts}^* = \E_{(2i-2m-1)b_T+R-P} D_{ts}^* \quad a.s.
-\end{equation*}
-and
-\begin{equation*}
-  \lVert D_{ts}^* - D_s \rVert_2 \leq \couplingBound{s - (2i-2m-1)b_T+P}.
-\end{equation*}
-Also define
-\begin{equation*}
-  Z_{1t}^* = (P\gamma_T)^{-1/2} \sum_{l=\vttLower}^{\vttUpper}
-  (D_{t,t+l}^* - \E_R D_{t,t+l}^*)\ W(l/\gamma_T), \\
-\end{equation*}
-and
-\begin{equation*}
-Z_{2t}^* = (P\gamma_T)^{-1/2} \sum_{j=\vttLower}^{\vttUpper}
-    (D_{t,t+l}^* - \E_R D_{t,t+l}^*)\ \kernelB{j/\gamma_T}.
-\end{equation*}
-
-Now, we have the inequalities
-\begin{align*}
-  \lVert \E( U_i - \E_R U_i & \mid \UFiltration{2i-2m-1}) \rVert_2
-  \\ &\leq
-  \vtSuma \lVert \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) - \E_R
-  Z_{1t}Z_{2t} \rVert_2 \\
-  &= \vtSuma \lVert \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
-  &\quad - \E(Z_{1t}^* Z_{2t}^* \mid \UFiltration{2i-2m-1}) \\
-  &\quad + \E(Z_{1t}^* Z_{2t}^* \mid \UFiltration{2i-2m-1})
-  - \E_R Z_{1t}Z_{2t} \rVert_2 \\
-%  \leq \vtSuma (\wall \lVert \wall \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
-%  - \E(Z_{1t}^*Z_{2t}^* \mid \UFiltration{2i-2m-1}) \rVert_2\return
-%  \\ + \lVert \E_R Z_{1t}Z_{2t} - \E_R Z_{1t}^*Z_{2t}^*
-%  \rVert_2)\return \\
-  &\leq 2 \vtSuma \lVert Z_{1t} Z_{2t} - Z_{1t}^* Z_{2t}^*
-  \rVert_2 \\
-  &\leq 2 \vtSuma (\lVert Z_{1t} - Z_{1t}^* \rVert_2 \lVert
-  Z_{2t} \rVert_{\infty}
-  + \lVert Z_{2t} - Z_{2t}^* \rVert_2 \lVert Z_{1t}^* \rVert_{\infty}) \\
-  &\leq \frac{2 C b_T^{1/2}}{(P\gamma_T)^{1/2}} \vtSuma (\lVert Z_{1t} - Z_{1t}^* \rVert_2
-  + \lVert Z_{2t} - Z_{2t}^* \rVert_2).
-\end{align*}
-
-And we can finish the proof with the following inequalities:
-\begin{align*}
-  \frac{2 C b_T^{1/2}}{(P \gamma_T)^{1/2}} &\vtSuma \lVert Z_{1t} - Z_{1t}^* \rVert_2 \\& \leq
-  \frac{4C b_T^{1/2}}{P\gamma_T} \vtSuma \sum_{l=\vttLower}^{\vttUpper} \lVert
-  D_{t+l} - D_{t,t+l}^* \rVert_2 W(l/\gamma_T) \\&
-  \leq O\Bigg(\frac{b_T^{1/2}}{P\gamma_T}\Bigg) \vtSuma
-  \sum_{l=\vttLower}^{\vttUpper} \couplingBeta{t+l-(2i-2m-1)b_T+P}\\&
-  = O\Bigg(\frac{b_T^{1/2}}{P\gamma_T}\Bigg) O(b_T^{3/2-u}\, m^{-1/2-u})
-\end{align*}
-for some positive $u$.  The same argument holds for $Z_{2t}$.
-As a result,
-\[
-E\Big(\vtSumr (U_i - \E_R U_i)\Big)^2 = o\Big(\vtSumr b_T^2/P\gamma_T\Big) =
- o(b_T/\gamma_T) \to 0,
-\]
-as required.
-\end{proof}
-
-%\newcommand{\DD}[2][{}]{(D_{#2}^{#1} - \E_R D_{#2}^{#1})}
-%\newcommand{\ovg}[1]{\tfrac{1}{P} \sum_{#1=R+1}^{T-h}}
-
-\begin{lem}\label{lem:a6}
-  Suppose the conditions of Lemma~\ref{res-variance-estimator} hold.
-  Then
-  \begin{equation*}
-    \sh^2 - P^{-1} \sum_{s,t=R+1}^{T-h} (D_s - \E_R
-    D_s) (D_t - \E_R D_t) W((t-s)/\gamma) \to^{L_1} 0.
-  \end{equation*}
-\end{lem}
-
-\begin{proof}
-   It follows from simple algebra that
-\begin{multline*}
-  \Big| \sh^2 -  P^{-1} \sum_{s,t=R+1}^{T-h} (D_s - \E_R
-    D_s) (D_t - \E_R D_t) W((t-s)/\gamma) \Big| \leq\\
-  \varianceDiffA \\ + P^{-1} \oosSum{s,t}{1} \lvert (D_s -
-  \oosA)(\E_R D_t - \oosA) \rvert \vWeight + o_p(1).
-\end{multline*}
-We'll prove that these two sums are $o_p(1)$; uniform integrability
-then implies convergence in $L_1$.  The arguments are $o_p(1)$ are
-almost identical, so we'll only present the first.
-
-Applying the Cauchy-Scwarz inequality twice and simplifying gives the
-upper bound
-\begin{multline*}
-\varianceDiffA \\ \leq O(1) \Big[\varianceDiffAii\Big]^{1/2} \Big[\varianceDiffAi\Big]^{1/2}.
-\end{multline*}
-Now,
-$P^{-1} \oosSum{s}{1}(D_s - \E_R D_s)^2 = O_p(1)$, and it suffices to prove
-that \[\varianceDiffAi = o_p(1).\]  Observe that
-\begin{align*}
-  \varianceDiffAi & = O_p\Big(P^{-1} \oosSum{s}{1}(\E_{R}D_s -
-  \E_R\oosA)^2\Big) + O_p(\oosA - \E_R\oosA)^{2} \\
-  &= O_p\Big(P^{-1} \oosSum{s}{1} (\E_RD_s)^2 - (\E_R\oosA)^2\Big) +
-  o_p(1),
-\end{align*}
-with the second term vanishing by Lemma \ref{res-mixingale} and
-\citepos{Dav:93} mixingale LLN.
-
-Now define $D_s^*$, $s = R+1,\dots,T-\h$, as in Lemma
-\ref{lem-basic-coupling} so that $\E_{s-1} D_s^* = \E_R D_s^*$ almost
-surely.  Note that we also have the equality $\E_R D_s^* = \E_R
-D_{R+1}^*$ almost surely for all $s\geq R+1$, and so
-\[
-P^{-1} \oosSum{s}{1} (\E_R D_s^*)^2 = \Big(P^{-1} \oosSum{s}{1} \E_R
-D_s^*\Big)^2 \quad \text{a.s.}
-\]
-Consequently,
-\begin{align*}
-P^{-1} \oosSum{s}{1}& (\E_R D_s)^2 - (\E_R\oosA)^2 \\
-&= P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R D_s^*)^2]
- + \Big(P^{-1} \oosSum{s}{1} \E_R D_s^*\Big)^2 - (\E_R\oosA)^2 \quad \text{a.s}.\\
-&= O_p\Big(P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R D_s^*)^2]\Big)
- + O_p\Big(P^{-1} \oosSum{s}{1} \E_R (D_s - D_s^*)\Big).
-\end{align*}
-Finally,
-\begin{align*}
-\Big\lVert P^{-1} \oosSum{s}{1} [(\E_RD_s)^2 - (\E_R D_s^*)^2] \Big\rVert_1
-&\leq P^{-1} \oosSum{s}{1} \lVert \E_R (D_s - D_s^*) \rVert_2 \lVert
-\E_R (D_s + D_s^*) \rVert_2
-\\ &\leq (4 B_L/P) \oosSum{s}{1} \lVert \E_R (D_s - D_s^*) \rVert_2,
-\end{align*}
-and this last term vanishes as in the proof of Lemma~\ref{lem:a2},
-completing the proof.
-\end{proof}
-
-\subsection*{Proof of Theorem \ref{res-confidence-intervals}}
-
-It suffices to prove asymptotic normality.  We can rewrite the
-centered OOS average as
-\[
-\frac{\bar{D}_{R} - \E_T \bar{D}_T}{\sh / \sqrt{P}} =
-\frac{1}{\sh \sqrt{P}}\oosSum{t}{1} (D_t - \E_R D_t) +
-\frac{\sqrt{P}}{\sh} (\E_R\oosA - \E_T\oosB).
-\]
-Lemmas \ref{res-mixingale} and
-\ref{res-convergence} ensure that the first term is asymptotically
-normal and the second term vanishes.\qed
-
-\subsection*{Proof of Theorem \ref{res:oostest}}
-By Lemma~\ref{res-convergence}, we know that
-\begin{equation*}
-  \Pr[\E_R \oosA \leq 0] - \Pr[\E_T \oosB \leq 0] \to 0
-\end{equation*}
-and
-\begin{equation*}
-  \Pr[P^{1/2} \oosA / \sh > z_\alpha \text{ and } \E_R \oosA \leq 0]
-  - \Pr[P^{1/2} \oosA / \sh > z_\alpha \text{ and }
-  \E_T \oosB \leq 0] \to 0.
-\end{equation*}
-For large enough $T$, both $\Pr[\E_R \oosA \leq 0]$ and $\Pr[\E_T
-\oosB \leq 0]$ are positive, so
-\begin{equation*}
-  \Pr[P^{1/2} \oosA / \sh > z_\alpha
-  \mid \E_R \oosA \leq 0] =
-  \frac{\Pr[P^{1/2} \oosA / \sh > z_\alpha \text{ and }
-    \E_R \oosA \leq 0]}{\Pr[\E_R \oosA \leq 0]}
-\end{equation*}
-and
-\begin{equation*}
-  \Pr[P^{1/2} \oosA / \sh > z_\alpha
-  \mid \E_T \oosB \leq 0] =
-  \frac{\Pr[P^{1/2} \oosA / \sh > z_\alpha \text{ and }
-    \E_T \oosB \leq 0]}{\Pr[\E_T \oosB \leq 0]}
-\end{equation*}
-almost surely and consequently
-\begin{equation*}
-  \Pr[P^{1/2} \oosA / \sh > z_\alpha
-  \mid \E_T \oosB \leq 0]
-  - \Pr[P^{1/2} \oosA / \sh > z_\alpha
-  \mid \E_R \oosA \leq 0] \to^p 0.
-\end{equation*}
-Finally,
-\begin{align*}
-  \Pr[P^{1/2} \oosA / \sh > z_\alpha \mid \E_R \oosA \leq 0]
-  &\leq \Pr[P^{1/2} (\oosA - \E_R \oosA) / \sh > z_\alpha
-  \mid \E_R \oosA \leq 0] \\
-  &= \E( \Pr[P^{1/2} (\oosA - \E_R \oosA) / \sh > z_\alpha
-  \mid \mathcal{F}_R] \mid \E_R \oosA \leq 0) \\
-  &= \E(\alpha \mid \E_R \oosA \leq 0) \\
-  &= \alpha
-\end{align*}
-where the second equality holds by Lemma~\ref{res-mixingale} and
-Theorem~\ref{res-variance-estimator}, completing the proof.
-\qed
-
-\subsection*{Proof of Lemma \ref{res-convergence}}
-\newcommand{\resConvgRHS}[1]{\ensuremath{\E(L(y^* - x_1^{*\prime}\bh{1#1}) - L(y^{*} -
-x_2^{*\prime}\bh{2#1}) \mid \bh{#1})}}
-\newcommand{\resConvgEstDiff}[1]{\ensuremath{\E(L(y^{*} -
-    x_{#1}^{*\prime}\bh{#1R}) \mid \bh{R}) -
-\E(L(y^{*} - x_{#1}^{*\prime}\bh{#1T}) \mid \bh{T})}}
-\newcommand{\resConvgEstDiffRV}[1]{\ensuremath{L(y^{*} -
-    x_{#1}^{*\prime}\bh{#1R}) - L(y^{*} - x_{#1}^{*\prime}\bh{#1T})}}
-
-Equation~\eqref{eq:7} holds if we show
-\begin{gather}
-\E_R \oosA = \resConvgRHS{R} + o_p(P^{-1/2}),\label{eq:18}\\
-\E_T \oosB = \resConvgRHS{T} + o_p(Q^{-1/2}),\label{eq:19}
-\intertext{and}
-\resConvgEstDiff{i} = O_p(\sqrt{P/T}),\label{eq:20}
-\end{gather}
-where $\hat\theta_R = (\hat\theta_{1R}, \hat\theta_{2R})$,
-$\hat\theta_T = (\hat\theta_{1T}, \hat\theta_{2T})$, and $y^{*}$,
-$x_1^{*}$ and $x_2^{*}$ are random variables drawn from the joint
-distribution of $(y_{t+\h},x_{1t},x_{2t})$ independently of
-$\mathcal{F}_T$.
-
-\begin{proof}[Proof of~\eqref{eq:18} and~\eqref{eq:19}]
-For~\eqref{eq:18}, define $D_t^*$ for each $t=R+1,R+2,\dots,T-h$ so
-that
-\begin{equation*}
-  \| D_t^* - D_t \|_2 \leq 2^{(1+\rho)/\rho} B_L \beta_{t-R}^{(\rho-2)/2\rho}
-\end{equation*}
-and
-\begin{equation*}
-  \E_R D_t^* = \E(L(y^* - x_1^{*\prime}\hat\theta_{1R}) -
-  L(y^* - x_2^{*\prime}\hat\theta_{2R}) \mid \hat\theta_R) \qquad a.s.
-\end{equation*}
-Lemma~\ref{lem-basic-coupling} ensures that these $D_t^*$ exist.
-Now,
-\begin{align*}
-  \Big\lVert \E_R \oosA - \E\Big(P^{-1} \sum_{t=R+1}^{T-h} D_t^* \mid
-  \hat\theta_R\Big) \Big\rVert_2
-  &= \Big\lVert \E_R\Big( \oosA - P^{-1} \sum_{t=R+1}^{T-h} D_t^*
-  \Big) \Big\rVert_2 \\
-  &\leq P^{-1} \sum_{t=R+1}^{T-h} \lVert D_t - D_t^* \rVert_2\\
-  &= O(P^{-1}) \sum_{t=R+1}^{T-h} \beta_{t-R}^{(\rho-2)/2\rho}
-\end{align*}
-and this last term is $o(P^{-1/2})$ by assumption.
-
-Essentially the same argument proves~\eqref{eq:19} as well.
-\end{proof}
-
-\begin{proof}[Proof of~\eqref{eq:20}]
-Observe that
-\begin{align*}
-  \|L(y^{*} -  x_i^{*\prime} \hat{\theta}_{iR}) -
-  L(y^{*} - x_i^{*\prime} \hat{\theta}_{iT}) \|_1
-  &\leq B_{L} \| x_i^{*\prime} (\hat{\theta}_{iR} - \hat{\theta}_{iT}) \|_2 \\
-  &\leq B_{L} \, \| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
-  (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2 \\
-  &\quad+ B_L \, \| x_i^{*\prime}
-  (X_{iR}'X_{iR})^{-1}[X_{iT}'\eb_{iT} - X_{iR}
-  \eb_{iR} ] \|_2 .
-\end{align*}
-The first term in the upper bound\,---\,$\| x_i^{*\prime}
-[(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2$\,---\,satisfies
-\begin{align*}
-  \| x_i^{*\prime} &[(X_{iT}'X_{iT})^{-1} -
-  (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2^2 =\\
-  &= \E \tr\big( x_i^* x_i^{*\prime}
-   [(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}] X_{iT}'\eb_{iT} \eb_{iT}X_{iT}
-   [(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}] \big) \\ \label{eq:8}
-  \begin{split}&\leq
-    \eigen_{K_i}(\E x_i x_i')
-    \, \| \eigen_{K_i}(\E(X_{iT}' \eb_{iT} \eb_{iT}' X_{iT} \mid
-    X_{iR}'X_{iR}, X_{iT}'X_{iT})) \|_3 \\
-    & \quad \times \Big\|\sum_{j=1}^{K_i}
-    \eigen_j^2((X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}) \Big\|_{3/2}
-  \end{split} \\
-  &= O(T) \Big\|\sum_{j=1}^{K_i}
-    \eigen_j^2((X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}) \Big\|_{3/2}
-\end{align*}
-with the second to last inequality a consequence of Holder's
-inequality and the last bound holding by Assumption~\ref{asmp-2}.
-
-Now, $(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}$ has rank $P$ and
-each of its nonzero eigenvalues are bounded in absolute value by the
-eigenvalues of $(X_{iR}'X_{iR})^{-1}$. The eivenvalues of
-$(X_{iR}'X_{iR})^{-1}$ are $O_{L_3}(1/R)$ by Assumption~\ref{asmp-2}, so
-\begin{align*}
-  \Big\|\sum_{j=1}^{K_i}
-  \eigen_j^2\big((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}\big)\Big\|_{3/2}
-  &\leq \Big\|\sum_{j=K_i - P+1}^{K_i}
-  \eigen_j^2\big((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}\big) \Big\|_{3/2} \\
-  &= O(P/R^2),
-\end{align*}
-proving that
-\begin{equation*}
-  \| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
-  (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2 = O(\sqrt{P/R}).
-\end{equation*}
-
-A similar argument proves that
-\begin{equation*}
-  \big\| x_i^{*\prime} (X_{iR}'X_{iR})^{-1}
-  [X_{iT}'\eb_{iT} - X_{iR} \eb_{iR} ] \big\|_2 =  O(\sqrt{P/R}),
-\end{equation*}
-completing the proof.
-\end{proof}
-
-\subsection*{Proof of Lemma \ref{res-mixingale}}
-\noindent \textit{Part 1.} Fix $R$, $j$ and $l$ and use Lemma
-\ref{lem-basic-coupling} to define $D_{R+j}^*$ so that
-\[\E_RD_{R+j}^* = \E_{R+j-l} D_{R+j}^* \quad a.s. \]
-and
-\[\lVert D_{R+j} - D_{R+j}^* \rVert_2 \leq \couplingBound{l}.\]
-Then
-\begin{align*}
-\lVert \E_{R+j-l} D_{R+j} - \E_R D_{R+j} \rVert_2 & \leq
-\lVert \E_{R+j-l} D_{R+j} - \E_{R+j-l} D_{R+j}^* \rVert_2 \\
-&\quad + \lVert
-\E_{R+j-l} D_{R+j}^* - \E_R D_{R+j} \rVert_2 \\
-&\leq 2 \lVert D_{R+j} - D_{R+j}^* \rVert_2 \\
-&\leq 2^{2 + 1/\rho}\ B_L\ \couplingBeta{l}.
-\end{align*}
-Now $\couplingBeta{l} = O(l^{-1/2 - \delta})$ for some
-positive $\delta$, completing the proof.\qed
-
-\vspace{\baselineskip}
-\noindent\textit{Part 2.}  A modification of \citepos{Jon:97} CLTs for
-mixingale and NED arrays will complete the proof.  Define
-\[\label{eq:z1}
-  Z_i = \ZDef
-\]
-where $b_T$ is a sequence that satisfies $b_T\leq P$,
-$b_T\to\infty$, and $b_T/P\to 0$.  The same arguments used in
-\citepos{Jon:97} Theorem 1 show that
-\begin{equation*}
-   \SumOuterBlock{i} Z_i = P^{-1/2} \oosSum{s}{1} (D_t - \E_R D_t) + o_p(1).
-\end{equation*}
-and
-\begin{equation*}
-  \SumOuterBlock{i} Z_i = \SumOuterBlock{i} (Z_i - E_{R + (i-1)b_T}
-  Z_i) + o_p(1).
-\end{equation*}
-Note that $\{Z_i - E_{R + (i-1)b_T} Z_i,\mathcal{F}_{R + i b_T}\}_i$ is an
-MDS by construction, so \citepos{HaH:80} Theorem 3.2 and Corollary
-3.1 ensure that $\sigma^{-1} \SumOuterBlock{i} Z_i \to^d N(0,1) $ as
-long as
-\begin{equation}\label{eq:cltvar2}
-  \sigma^2 - \SumOuterBlock{i} \E_R Z_i^2 \to^p 0,
-\end{equation}
-and
-\begin{equation}\label{eq:cltvar1}
-  \SumOuterBlock{i} \E_R Z_i^2 - \SumOuterBlock{i} \ZSqCE \to^p 0.%
-\footnote{Note that $\sigma^2 \in \mathcal{F}_t$ for
-    all $t \geq R$, so Hall and Heyde's condition (3.21) is
-    unnecessary---see the remarks after their result.} %
-\end{equation}
-Equation (\ref{eq:cltvar2}) holds as in \citet{Jon:97} (see the proof
-of his Theorem 2); (\ref{eq:cltvar1}) is ensured by
-Lemma~\ref{lem:a2}. \qed
-
-\subsection*{Proof of Lemma \ref{res-variance-estimator}}
-The proof follows \citepos{JoD:00} Theorem 2.1 closely.  We
-start by defining similar quantities to theirs, borrowing their
-notation when possible to make the similarities apparent.  For
-positive $\delta$, define $b_T \equiv \lfloor \gamma/\delta \rfloor$,
-$\kernelB{x} \equiv \kernelBDefn{x}$, and
-\begin{align*}
-  \varianceTermI &\equiv
-  \varianceTermIDefn,\\ \varianceTermII &\equiv \vtSum
-  \varianceTermIIa\\& \quad \times \varianceTermIIb,\\
-  \varianceTermIII &\equiv \vtSum \varianceTermIIIa\\
-  &\quad \times \varianceTermIIb,\\
-  \varianceTermIV &\equiv \vtSum \varianceTermIIIa \\
-  &\quad\times \varianceTermIVb,
-\end{align*}
-giving us the inequalities
-\begin{align*}
-  \lVert \sh^2 - \sigma^2 \rVert_1 &
-  \leq \lVert \sh^2 - \varianceTermI \rVert_1
-  + \lVert \varianceTermI - \varianceTermII \rVert_1
-  + \lVert \varianceTermII - \varianceTermIII \rVert_1
-  + \lVert \varianceTermIII - \varianceTermIV \rVert_1\\ & \quad
-  + \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1
-  + \lVert \E_R\varianceTermIII - \E_R\varianceTermIV \rVert_1
-  + \lVert \E_R\varianceTermII - \E_R\varianceTermIII \rVert_1\\ & \quad
-  + \lVert \E_R\varianceTermI - \E_R\varianceTermII \rVert_1
-  + \lVert \E_R \varianceTermI - \sigma^2 \rVert_1
-  \\ &
-  \leq  \lVert \sh^2 - \varianceTermI \rVert_1
-  + 2(\lVert \varianceTermI - \varianceTermII \rVert_1
-      + \lVert \varianceTermII - \varianceTermIII \rVert_1
-      + \lVert \varianceTermIII - \varianceTermIV \rVert_1) \\
-  & \quad + \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1
-  + \lVert \E_R \varianceTermI - \sigma^2 \rVert_1.
-\end{align*}
-De Jong and Davidson (2000) prove that
-\begin{equation} \label{dd1}
-\lim_{\delta\to0} \limsup_{T\to\infty} \lVert \varianceTermI -
-\varianceTermII\rVert_1 = 0,
-\end{equation}
-\begin{equation} \label{dd2}
-\lim_{\delta\to0} \limsup_{T\to\infty} \lVert \varianceTermII - \varianceTermIII
-\rVert_1 = 0,
-\end{equation}
-\begin{equation} \label{dd3}
-\lim_{\delta\to0} \limsup_{T\to\infty} \lVert \varianceTermIII - \varianceTermIV
-\rVert_1 = 0,
-\end{equation}
-and
-\begin{equation} \label{dd4}
-\lim \lVert \E_R \varianceTermI - \sigma^2 \rVert_1 = 0.
-\end{equation}
-Their proofs of \eqref{dd1}--\eqref{dd4} use the fact that NED
-functions of mixing processes are also mixingale processes and do not
-use any other properties specific to NED processes, so they hold
-here as well.  We do need to modify their proofs that
-\begin{equation}
-  \label{eq:4} \lVert \sh^2 - \varianceTermI \rVert_1 \to 0
-\end{equation}
-and
-\begin{equation}
-  \label{eq:5} \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1
-  \to 0 \quad \text{for all positive $\delta$},
-\end{equation}
-though, since their proofs exploit NED properties.  The proofs
-follow from Lemmas~\ref{lem:a2} and~\ref{lem:a6}, since
-\begin{equation*}
-  \varianceTermIV - \E_R \varianceTermIV = \vtSum (Z_{1t}Z_{2t} - \E_R Z_{1t}Z_{2t});
-\end{equation*}
-$Z_{1t}$ and $Z_{2t}$ are defined in Lemma~\ref{lem:a2}.
-\qed
-
-\subsection*{Proof of Theorem~\ref{res:ftest}}
-
-\textit{Equation~\eqref{eq:11}}: Note that a necessary condition for
-$(\hat{\theta}_T - \theta_0)'V_T (\hat{\theta}_T - \theta_0) < c$
-as $\theta'V_T\theta \to \infty$ is for all of the mass of
-$\hat{\theta}_T$ to concentrate on the line joining $\theta$ and
-$\theta_0$.  For any distribution of $(\e_{t+h}, x_t')$ such
-that $\hat{\theta}_T$ depends on $\theta$ only through its mean, the
-Lebesgue measure of parameter sequences satisfying this condition is
-zero. \qed
-
-\vspace{\baselineskip}
-\noindent\textit{Equation~\eqref{eq:15}}:  Suppose that
-$(\e_{t+h}, x_t) \sim i.i.d. N(0,I)$ and condition on $X_T$.
-Then the distribution of $\hat{\theta}_{T}$ concentrates uniformly on
-the ellipsoid
-\begin{equation*}
-  (\hat{\theta}_T - \theta)'(\hat{\theta}_T - \theta) = \theta'\theta.
-\end{equation*}
-Now, for $\theta$ and $V_T$ such that
-\begin{equation*}
-  (\theta-\theta_0)' V_T (\theta-\theta_0) > c + \delta,
-\end{equation*}
-the probability that $\hat{\theta}_T$ is inside the acceptance region
-of the test is less than $(1/2)^{K_2}$, which converges to zero as $T
-\to \infty$. \qed
-
-\bibliographystyle{abbrvnat}
-\bibliography{references}
-
-\begin{table}[h]
- \begin{multicols}{2}
-  \begin{itemize}
-  \item log Dividend Price Ratio
-  \item log Earnings Price Ratio
-  \item Stock Market Variance
-  \item Book to Market Ratio
-  \item Net Equity Expansion
-  \item Percent Equity Issuing
-  \item Treasury Bill
-  \item Long Term Yield
-  \item Long Term Rate
-  \item Default Return Spread
-  \item Default Yield Spread
-  \item Inflation
-  \end{itemize}
- \end{multicols}
- \caption{Variables used in Section \ref{sec:empirics} and by Goyal
-   and Welch (2008) to predict the equity premium.  Please see Goyal
-   and Welch's original paper
-   for a detailed description of each variable.}
- \label{tab:equity}
-\end{table}
-
-\begin{table}[b]
- \begin{center}
- \begin{tabular}{lrrrr}\hline\hline
-   \multicolumn{1}{l}{waldtest}&\multicolumn{1}{c}{Res.Df}&\multicolumn{1}{c}{Df}&\multicolumn{1}{c}{F}&\multicolumn{1}{c}{Pr(\textgreater
-     F)}\tabularnewline
-   \hline
-   1&69&&&\\
-   2&81&$-$12&3.4&0.00066 \\
-   \hline
-\end{tabular}
-\caption{Wald test for the null hypothesis that all of the
-  coefficients in Goyal and Welch's (2008) ``kitchen sink'' model are
-  zero, except for the intercept, using the Newey-West
-  variance-covariance matrix.  The p-value is calculated from the $F$
-  distribution.\label{tab:gwinsample}}
-\end{center}
-\end{table}
-
-\clearpage
-\begin{figure}
-  \centering {\large Simulated Coverage of One-Sided DMW Interval for
-    $\E_R\oosA$} \input{mc/plots/interval-testerror1.tikz}
-\caption{Simulated coverage of $\E_R \oosA$ at 90\% confidence using a
-  one-sided interval based on the DMW
-  OOS test, plotted as a function of the fraction of
-  observations used in the test sample, $P/T$.  The solid horizontal
-  line denotes the intervals' nominal coverage.}
- \label{fig:interval-R}
-\end{figure}
-\clearpage
-\begin{figure}
-  \centering {\large Simulated Coverage of One-Sided DMW Interval for
-    $\E_T\oosB$} \input{mc/plots/interval-generror1.tikz}
+  \centering {\large Simulated Coverage of Recursive One-Sided DMW Interval for
+    $\E_T\oosB$} \input{floats/mc-interval-generror1-rec.tex}
 \caption{Simulated coverage of $\E_T \oosB$ at 90\% confidence using a
@@
 \begin{figure}
-  \centering {\large Simulated Rejection Probability of $F$-test Under
-    $\E_T \oosB \leq 0$}
-  \input{mc/plots/ftest-001.tikz}
-  \caption{Simulated rejection probabilities for the $F$-test given
-    $\E_T \oosB \leq 0$ with nominal size 10\%.  Values greater than
-    10\% indicate that the test rejects the benchmark model too often.
-    See Section~\ref{sec:simulation-design} for a discussion of the
-    simulation design.}
-  \label{fig:ftest}
-\end{figure}
-\clearpage
-\begin{figure}
-  \centering {\large Simulated Rejection Probability of DMW Test Under
-    $\E_T \oosB \leq 0$} \input{mc/plots/size-dmwsize.tikz}
+  \centering {\large Simulated Rejection Probability of Recursive DMW Test Under
+    $\E_T \oosB \leq 0$} \input{floats/mc-dmwsize-rec.tex}
   \caption{Simulated rejection probabilities for the DMW
@@
 \begin{figure}
-  \centering {\large Simulated Rejection Probability of Clark and West
+  \centering {\large Simulated Rejection Probability of Recursive Clark and West
     (2006, 2007) \\ Test Under $\E_T \oosB \leq 0$}
-  \input{mc/plots/size-clarkwest.tikz}
+  \input{floats/mc-clarkwestsize-rec.tex}
   \caption{Simulated rejection probabilities for Clark and West's
@@
 \begin{figure}
-  \centering {\large Simulated Rejection Probability of McCracken
+  \centering {\large Simulated Rejection Probability of Recursive McCracken
     (2007) Test \\ Under $\E_T \oosB \leq 0$}
-  \input{mc/plots/size-mccracken.tikz}
+  \input{floats/mc-mccrackensize-rec.tex}
   \caption{Simulated rejection probabilities for McCracken's (2007)
@@
 \begin{figure}
-  \centering {\large Simulated Rejection Probability of DMW Test Under
-    $\E_T \oosB > 0$} \input{mc/plots/size-dmwpower.tikz}
+  \centering {\large Simulated Rejection Probability of Recursive DMW Test Under
+    $\E_T \oosB > 0$} \input{floats/mc-dmwpower-rec.tex}
   \caption{Simulated rejection probabilities for the DMW
@@
   \label{fig:ttest-power}
-\end{figure}
-
-\begin{figure}
-\centering
-\large{Difference in OOS MSE of Prevailing Mean and\\ Kitchen
-    Sink Models of Equity Premium (OLS)}
-\input{empirics/plots/oos-mse-1.tikz}
-\input{empirics/plots/oos-mse-1b.tikz}
-\caption{OOS difference in the MSE
-  of the prevailing mean benchmark and the kitchen sink model as a
-  function of the test sample size, $R$.  Both models forecast the
-  equity premium using annual data from 1928--2008.  The solid line
-  gives the OOS average, and the shaded region indicates the
-  one-sided 95\% confidence interval implied by the
-  DMW test.  The bottom panel is a detailed view of the top
-  panel for $R \geq 50$.}
-\label{fig:empirics1}
-\end{figure}
-
-\begin{figure}
-\centering
-\large{Difference in OOS MSE of Prevailing Mean and\\ Kitchen
-    Sink Models of Equity Premium (CT)}
-\input{empirics/plots/oos-mse-2.tikz}
-\input{empirics/plots/oos-mse-2b.tikz}
-\caption{OOS difference in the MSE
-  of the prevailing mean benchmark and the kitchen sink model as a
-  function of the test sample size, $R$.  Both models forecast the
-  equity premium using annual data from 1928--2008.  The solid line
-  gives the OOS average, and the shaded region indicates the
-  one-sided 95\% confidence interval implied by the 
-  DMW test.  The bottom panel is a detailed view of the top
-  panel for $R \geq 50$.}
-\label{fig:empirics2}
-\end{figure}
-
-\begin{figure}
-\centering
-\large{OOS MSE of Individual Forecasts of Equity Premium}
-\input{empirics/plots/oos-ind-ks.tikz}
-\input{empirics/plots/oos-ind-pm.tikz}
-\caption{OOS MSE of the Prevailing Mean (PM) and
-    Kitchen Sink (KS) models for equity premium prediction as
-    a function of the size of the training sample, $R$.  Please note
-    that the vertical scales are different in the two plots.}
-\label{fig:empirics3}
 \end{figure}

### 2014-03-19 R/mc-clarkwestsize-rec.R

@@ -1,4 +1,4 @@
-library(fwPackage, lib.loc="package")
+library(fwPackage, lib.loc = "package")
 library(lattice)
 library(tikzDevice)
 
@@ -10,25 +10,24 @@ dbc <- dbConnect(dbDriver("SQLite"), dbname = "data/simulations.db")
 
 d <- dbGetQuery(dbc, "
 select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
-               from interval 
-               where label='gen.error.1'
+               from interval
+               where label='size'
                  and ntest >= 10
-                 and simIndex <= 500
-                 and transform = 'difference'
-                 and scheme = 'fix'
+                 and idgp in (1,2)
+                 and transform = 'clarkwest'
+                 and scheme = 'rec'
                group by ntest, isim, idgp, transform, label) s 
 join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp")
 
 d$nlabel <- sprintf("T=%d", d$n)
 d$normlabel <- sprintf("c=%d", d$norm)
 
-tikz(file = "floats/mc-interval-generror1.tex", width=6)
-xyplot(I(1 - reject) ~ I(ntest/n)
-         | interaction(nlabel, altlabel, normlabel, sep = ", "),
+tikz(file = "floats/mc-clarkwestsize-rec.tex", width = 6)
+xyplot(reject ~ I(ntest/n) | interaction(nlabel,altlabel,normlabel, sep = ", "),
        data = d,
-       ylab = "Coverage", xlab = "$P/T$",
+       ylab = "Rejection Probability", xlab = "$P/T$",
        panel = function(x,y,...) {
-         panel.lines(c(0,2/3),c(.9,.9), col = "gray")
+         panel.lines(c(0,2/3),c(.1,.1), col = "lightgray")
          panel.xyplot(x,y,...,type = "l")
        },
        layout = c(4,4),

### 2014-03-19 R/mc-clarkwestsize.R

@@ -10,10 +10,15 @@ dbc <- dbConnect(dbDriver("SQLite"), dbname = "data/simulations.db")
 
 d <- dbGetQuery(dbc, "
 select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
-from interval 
-where label='size' and idgp in (1,2) and transform = 'clarkwest'
-group by ntest, isim, idgp, transform, label) s 
+               from interval 
+               where label='size'
+                 and ntest >= 10
+                 and idgp in (1,2)
+                 and transform = 'clarkwest'
+                 and scheme = 'fix'
+               group by ntest, isim, idgp, transform, label) s 
 join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp")
+
 d$nlabel <- sprintf("T=%d", d$n)
 d$normlabel <- sprintf("c=%d", d$norm)
 

### 2014-03-19 R/mc-dmwpower-rec.R

@@ -1,4 +1,4 @@
-library(fwPackage, lib.loc="package")
+library(fwPackage, lib.loc = "package")
 library(lattice)
 library(tikzDevice)
 
@@ -11,24 +11,23 @@ dbc <- dbConnect(dbDriver("SQLite"), dbname = "data/simulations.db")
 d <- dbGetQuery(dbc, "
 select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
                from interval 
-               where label='gen.error.1'
-                 and ntest >= 10
-                 and simIndex <= 500
-                 and transform = 'difference'
-                 and scheme = 'fix'
+               where label='power'
+                 and ntest <= 10
+                 and idgp in (2,3)
+                 and transform='difference'
+                 and scheme='rec'
                group by ntest, isim, idgp, transform, label) s 
 join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp")
 
 d$nlabel <- sprintf("T=%d", d$n)
 d$normlabel <- sprintf("c=%d", d$norm)
 
-tikz(file = "floats/mc-interval-generror1.tex", width=6)
-xyplot(I(1 - reject) ~ I(ntest/n)
-         | interaction(nlabel, altlabel, normlabel, sep = ", "),
+tikz(file = "floats/mc-dmwpower-rec.tex", width = 6)
+xyplot(reject ~ I(ntest/n) | interaction(nlabel,altlabel,normlabel, sep = ", "),
        data = d,
-       ylab = "Coverage", xlab = "$P/T$",
+       ylab = "Rejection Probability", xlab = "$P/T$",
        panel = function(x,y,...) {
-         panel.lines(c(0,2/3),c(.9,.9), col = "gray")
+         panel.lines(c(0,2/3),c(.1,.1), col = "lightgray")
          panel.xyplot(x,y,...,type = "l")
        },
        layout = c(4,4),

### 2014-03-19 R/mc-dmwsize-rec.R

@@ -1,4 +1,4 @@
-library(fwPackage, lib.loc="package")
+library(fwPackage, lib.loc = "package")
 library(lattice)
 library(tikzDevice)
 
@@ -11,24 +11,23 @@ dbc <- dbConnect(dbDriver("SQLite"), dbname = "data/simulations.db")
 d <- dbGetQuery(dbc, "
 select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
                from interval 
-               where label='gen.error.1'
+               where label='size'
                  and ntest >= 10
-                 and simIndex <= 500
+                 and idgp in (1,2)
                  and transform = 'difference'
-                 and scheme = 'fix'
+                 and scheme='rec'
                group by ntest, isim, idgp, transform, label) s 
 join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp")
 
 d$nlabel <- sprintf("T=%d", d$n)
 d$normlabel <- sprintf("c=%d", d$norm)
 
-tikz(file = "floats/mc-interval-generror1.tex", width=6)
-xyplot(I(1 - reject) ~ I(ntest/n)
-         | interaction(nlabel, altlabel, normlabel, sep = ", "),
+tikz(file = "floats/mc-dmwsize-rec.tex", width = 6)
+xyplot(reject ~ I(ntest/n) | interaction(nlabel,altlabel,normlabel, sep = ", "),
        data = d,
-       ylab = "Coverage", xlab = "$P/T$",
+       ylab = "Rejection Probability", xlab = "$P/T$",
        panel = function(x,y,...) {
-         panel.lines(c(0,2/3),c(.9,.9), col = "gray")
+         panel.lines(c(0,2/3),c(.1,.1), col = "lightgray")
          panel.xyplot(x,y,...,type = "l")
        },
        layout = c(4,4),

### 2014-03-19 R/mc-dmwsize.R

@@ -10,10 +10,15 @@ dbc <- dbConnect(dbDriver("SQLite"), dbname = "data/simulations.db")
 
 d <- dbGetQuery(dbc, "
 select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
-from interval 
-where label='size' and idgp in (1,2) and transform = 'difference'
-group by ntest, isim, idgp, transform, label) s 
+               from interval
+               where label='size'
+                 and ntest >= 10
+                 and idgp in (1,2)
+                 and transform = 'difference'
+                 and scheme='fix'
+               group by ntest, isim, idgp, transform, label) s
 join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp")
+
 d$nlabel <- sprintf("T=%d", d$n)
 d$normlabel <- sprintf("c=%d", d$norm)
 

### 2014-03-19 R/mc-interval-generror1-rec.R

@@ -15,14 +15,14 @@ select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
                  and ntest >= 10
                  and simIndex <= 500
                  and transform = 'difference'
-                 and scheme = 'fix'
-               group by ntest, isim, idgp, transform, label) s 
+                 and scheme = 'rec'
+               group by ntest, isim, idgp, transform, label) s
 join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp")
 
 d$nlabel <- sprintf("T=%d", d$n)
 d$normlabel <- sprintf("c=%d", d$norm)
 
-tikz(file = "floats/mc-interval-generror1.tex", width=6)
+tikz(file = "floats/mc-interval-generror1-rec.tex", width=6)
 xyplot(I(1 - reject) ~ I(ntest/n)
          | interaction(nlabel, altlabel, normlabel, sep = ", "),
        data = d,

### 2014-03-19 R/mc-interval-testerror1.R

@@ -8,15 +8,17 @@ lattice.options(default.theme = ltheme)      ## set as default
 
 dbc <- dbConnect(dbDriver("SQLite"), dbname = "data/simulations.db")
 
-mcpars <- dbGetQuery(dbc, "select count(jobnumber) as njobs from interval")
-dstring <- "
+d <- dbGetQuery(dbc, "
 select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
-from interval 
-where label='%s' and simIndex <= %d and transform = 'difference'
-group by ntest, isim, idgp, transform, label) s 
-join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp"
+               from interval 
+               where label = 'test.error.1'
+                 and ntest >= 10
+                 and simIndex <= 500
+                 and transform = 'difference'
+                 and scheme = 'fix'
+               group by ntest, isim, idgp, transform, label) s
+join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp")
 
-d <- dbGetQuery(dbc, sprintf(dstring, 'test.error.1', 500))
 d$nlabel <- sprintf("T=%d", d$n)
 d$normlabel <- sprintf("c=%d", d$norm)
 

### 2014-03-19 R/simulations.R

@@ -2,6 +2,11 @@
 ## the beginning of this file before execution.  This code *should*
 ## set up random number generation for the parallel processes
 ## correctly.
+
+## I apologize to all future readers about the quality of this code. I
+## have no idea why I thought these ideas were good, but there's no
+## time to do anything about it now...
+
 require(rlecuyer)
 .lec.SetPackageSeed(c(4586, 8197, 5954,   15, 2896, 1839))
 jobnames <- LETTERS[1:njobs]
@@ -29,48 +34,53 @@ varfn <- new.env(hash=TRUE)
 ##
 ## where L[1] and L[2] are something like the average out-of-sample loss
 
-locfn[["difference"]] <-      function(L) L[1] - L[2]
-varfn[["difference"]] <-      function(L, vcv) calcvar(vcv, c(1, -1))
+locfn[["difference"]] <- function(L) L[1] - L[2]
+varfn[["difference"]] <- function(L, vcv) calcvar(vcv, c(1, -1))
 
-locfn[["ratio"]] <-           function(L) L[1] / L[2]
-varfn[["ratio"]] <-           function(L, vcv) calcvar(vcv, c(1/L[2], -L[1]/L[2]^2))
+locfn[["ratio"]] <- function(L) L[1] / L[2]
+varfn[["ratio"]] <- function(L, vcv) calcvar(vcv, c(1/L[2], -L[1]/L[2]^2))
 
 locfn[["rmse.difference"]] <- function(L) sqrt(L[1]) - sqrt(L[2])
-varfn[["rmse.difference"]] <- function(L, vcv) calcvar(vcv, c(0.5/sqrt(L[1]), -0.5/sqrt(L[2])))
+varfn[["rmse.difference"]] <-
+  function(L, vcv) calcvar(vcv, c(0.5/sqrt(L[1]), -0.5/sqrt(L[2])))
 
-locfn[["rmse.ratio"]] <-      function(L) sqrt(L[1] / L[2])
-varfn[["rmse.ratio"]] <-      function(L, vcv) calcvar(vcv, c(0.5/sqrt(L[1]*L[2]), -0.5*sqrt(L[1]/(L[2]^3))))
+locfn[["rmse.ratio"]] <- function(L) sqrt(L[1] / L[2])
+varfn[["rmse.ratio"]] <-
[…]

### 2014-03-19 package/fwPackage_1.0_source/R/AllClasses.R

@@ -5,7 +5,17 @@ setClass("oos.forecast",
                         target               = "numeric",
                         nreg                 = "integer"))
 
-forecasts <- function(object,...) object@forecasts
+forecasts <- function(object, scheme = "fix",...) {
+  switch(scheme,
+         fix = object@forecasts,
+         rec = {
+           rforecasts <- sapply(object@forecasts, function(f) f[1])
+           n <- length(rforecasts)
+           lapply(seq_along(rforecasts),
+                  function(i) rforecasts[seq.int(i, n, 1)])
+         },
+         stop("The window scheme is not supported"))
+}
 
 setClass("oos.pair",
          representation(model.null = "oos.forecast",

### 2014-03-19 package/fwPackage_1.0_source/R/qmccracken.R

@@ -1,4 +1,4 @@
-qmccracken <- function(kextra, PRratio) {
+qmccracken <- function(kextra, PRratio, scheme = "fix") {
   if (any(kextra > 10 || kextra < 1))
     stop("kextra must be between 1 and 10")
   if (any(PRratio > 2 || PRratio < 0))
@@ -17,7 +17,11 @@ qmccracken <- function(kextra, PRratio) {
   }
   else if (PRratio.length < kextra.length)
     PRratio <- rep(PRratio, length.out = kextra.length)
-  
-  .C("qmccracken", 0L, as.integer(kextra), as.double(PRratio),
-     as.integer(kextra.length), q = double(kextra.length))$q
+
+  switch(scheme,
+         fix = .C("qmccrackenfix", 0L, as.integer(kextra), as.double(PRratio),
+           as.integer(kextra.length), q = double(kextra.length))$q,
+         rec = .C("qmccrackenrec", 0L, as.integer(kextra), as.double(PRratio),
+           as.integer(kextra.length), q = double(kextra.length))$q,
+         stop("That window scheme is unsupported."))
 }

### 2014-03-19 package/fwPackage_1.0_source/src/qmccracken.c

@@ -1,7 +1,7 @@
 #include <R.h>
 #include <math.h>
 
-void qmccracken(int *whichquantile, int *k, double *pr, int *n, double *q) {
+void qmccrackenfix(int *whichquantile, int *k, double *pr, int *n, double *q) {
   // *whichquantile indicates which table we're using:
   // 0 = .90 -- this is the only one implemented right now.
   // 1 = .95
@@ -22,6 +22,44 @@ void qmccracken(int *whichquantile, int *k, double *pr, int *n, double *q) {
     {1.280,  0.868,  0.663,  0.467,  0.247,  0.153, -0.029, -0.115, -0.227, -0.343, -0.440, -0.502},
     {1.280,  0.844,  0.655,  0.396,  0.182,  0.034, -0.111, -0.224, -0.303, -0.437, -0.543, -0.625},
     {1.280,  0.797,  0.616,  0.348,  0.125, -0.055, -0.210, -0.305, -0.398, -0.559, -0.645, -0.729}
+  };
+  int i, j;
+  double wL, wU;
+  for (j = 0; j < *n; j++) {
+    i = 0;
+    while (pr[j] > PRs[i] && i < 11) {
+      i++;
+    }
+    wL = 1 - (pr[j] - PRs[i-1]) / (PRs[i] - PRs[i-1]);
+    wU = 1 - (PRs[i] - pr[j])   / (PRs[i] - PRs[i-1]);
+    // interpolate between the two nearest critical values.
+    q[j] = (wL * cv[k[j]-1][i-1]) + (wU * cv[k[j]-1][i]);
+  }
+}
+
+// The next function was largely copy and pasted from the previous
+// function. Sorry, brah.
+void qmccrackenrec(int *whichquantile, int *k, double *pr, int *n, double *q) {
+  // *whichquantile indicates which table we're using:
+  // 0 = .90 -- this is the only one implemented right now.
+  // 1 = .95
+  // 2 = .99
+  // *nelem 
+  double PRs[12] = {0.0, 0.1, 0.2, 0.4, 0.6, 0.8, 1.0, 1.2, 1.4, 1.6, 1.8, 2.0};
+  // First index indicates the number of excess regressors;
+  // second index indicates the ratio P/R;
+  // Values are from McCracken's 2001 paper
+  double cv[10][12] = {
[…]

### 2014-03-20 paper.tex
Reorganize code (big!)
This commit is a massive code reorganization. There are several reasons
for it:
- R 3.0x came out and my old packages weren't valid any more
- The pgfSweave package is obsolete, and so I've unbundled
  the sweave files that were using it.
- It seemed like an opportunistic time to make a few other
  changes.
Try to resolve problems in pdf fonts
Consolidate header LaTeX into its own file
This commit does some bookkeeping and cleans up the input, usepakage
etc commands. It also puts package loading and macro definitions into
a single LaTeX file.
Styling: tweak spacing and f

@@
-\documentclass[11pt]{article}
-\usepackage{tikz,setspace}
-\usetikzlibrary{calc}
-\usetikzlibrary{fit}
-\usepackage[round]{natbib}
-\usepackage[margin=1in]{geometry}
-\onehalfspacing
-\input{macros}
-\usepackage[charter]{mathdesign}
-\usepackage[osf]{sourcecodepro}
-% This will make copy and pasting easier, and will prevent the
-% abomination that is monospace font ligatures.  Sorry, everyone who
-% really likes ligatures.  Don't worry, the Bitstream Charter font
-% has very, very few ligatures anyway.
-\DisableLigatures{family = tt*}
-\urlstyle{same}
-
-\newcommand{\e}{\varepsilon}
-\newcommand{\eb}{\mathbf{\e}}
-\DeclareMathOperator{\eigen}{\lambda}
-
-\pagestyle{myheadings}
-\newtheorem{thm}{Theorem}
-\newtheorem{lem}{Lemma}
-\newtheorem{claim}{Claim}
-\newtheorem{cor}{Corollary}
-\newtheorem{asmp}{Assumption}
-\newtheorem{example}{Example}
-\newtheorem{defn}{Definition}
-
-\newcommand{\citepos}[1]{\citeauthor{#1}'s \citeyearpar{#1}}
-\newcommand{\Citepos}[1]{\Citeauthor{#1}'s \citeyearpar{#1}}
-\newcommand{\clws}{\citeauthor{ClW:06}'s \citeyearpar{ClW:06,ClW:07}}
-
-\usepackage[bitstream]{mathdesign}
-
-% VERSION is generated by a post-commit hook and contains the git
-% version info
-\IfFileExists{VERSION}{
-  \tryinput{VERSION}
-  \date{\dinfo\ (commit \hinfo)}
-  \markright{\dinfo\ (commit \hinfo)}
-}{}
+\documentclass[12pt]{article}
+\input{setup}
 
@@
 
-\begin{abstract}\thispagestyle{empty}\noindent
+\begin{abstract}\noindent
   This paper uses dimension asymptotics to study why overfit linear
@@
 
-\section{Introduction}\label{sec:introduction}
+\section{Introduction}
+\label{sec:introduction}
+
 Consider two sequences of length $P$ of prediction errors, the result
@@
 between two models' OOS forecasting performance is unpredictable, a
-martingale difference sequence; \citet{GiR:09} test whether the OOS
+martingale difference sequence (MDS); \citet{GiR:09} test whether the OOS
 forecasting performance of a model suffers from a breakdown relative
@@
 situation where a forecaster chooses from many different models,
-i.e. \textit{data-mining} or \textit{data-snooping}, we view these as
+i.e. \emph{data-mining} or \emph{data-snooping}, we view these as
 separate issues.  Procedures that account for the presence of many
@@
 comparisons. Moreover, the empirical research that motivates
-this paper uses \textit{pseudo} OOS comparisons and not
-\textit{true} OOS comparisons.  Even if a true OOS comparison
+this paper uses \emph{pseudo} OOS comparisons and not
+true OOS comparisons.  Even if a true OOS comparison
 could account for some forms of data-snooping better than
@@
 We focus on linear regression models estimated with a fixed window
-for simplicity, but our basic
-conclusions should be true for other models as well.  Under this
+for simplicity, but our basic conclusions should be true for other
+models and estimation strategies as well.  Under this
 asymptotic theory, where the number of regressors $k$ increases with $T$
@@
 Under these asymptotics, the generalization
-error does not converge to the expected performance of the pseudo-true
+error does not converge to the expected performance of the pseudotrue
 models, so existing in-sample and OOS comparisons measure different
@@
 have argued that a breakdown of in-sample forecasting ability
-indicates a structural break (see \citealp{BoH:99} and
-\citealp{StW:03} among others), but this breakdown can be caused by overfit as
-well.
-
-Our results can justify OOS comparisons when researchers want to
+indicates a structural break (see \citealp{BoH:99}, and
+\citealp{StW:03}, among others), but this breakdown can be caused by
+overfit as well.
+
+These theoretical results partially justify OOS comparisons when
+researchers want to
 choose a model for forecasting.  Although there has been little
@@
 Popular in-sample tests and model selection criteria, like the Wald
-test, AIC, and BIC, do not help forecasters in this setting. We show
-that these statistics can no pick out the more accurate model. For
-many DGPs they will choose a larger alternative model over a small
-benchmark model with probability approaching one, regardless of which
-model is more accurate.%
+test and the AIC, do not help forecasters in this setting. We show
+that these statistics do not select the more accurate model when
+choosing between overfit models. For many DGPs the Wald test and the
+AIC will choose a larger alternative model over a small benchmark
+model with probability approaching one, regardless of which model is
+more accurate, while the BIC chooses the benchmark model with
+probability approaching one.%
 \footnote{Our result holds for a broad class of
@@
 
-Finally, this paper also introduces a new method of proof for OOS
+Finally, this paper introduces a new method of proof for OOS
 statistics.  We use a coupling argument (Berbee's Lemma, 1979) to show
@@
 benchmark model too often when it is false but more accurate than the
-alternative, and shows that standard model selection methods choose the
-larger model too often under similar conditions. Section~\ref{sec:mc}
+alternative, and shows that standard model selection methods can run
+into similar problems. Section~\ref{sec:mc}
 presents a Monte Carlo study supporting our theoretical results.
@@
 
-\section{Setup and assumptions}\label{sec:assumptions}
+\section{Setup and assumptions}
+\label{sec:assumptions}
 
 The first part of this section will describe the environment in detail
-and set up our models and notation. The second part will list the
+and set up our models and notation. The second part lists the
 assumptions underlying our theoretical results.
@@
 \subsection{Notation and forecasting environment}
+
 We assume the following forecasting environment. There are two
@@
   x_{is} y_{s+\h}, \qquad \text{for } i=1,2;\ t = R+1,\dots, T - \h.%
-\footnote{It may not be clear why we are using a $t$ index in $\bh{it}$,
+\footnote{It may not be clear why we are using the index $t$ in $\bh{it}$,
     since $\bh{it} = \bh{iR}$ almost surely for all $t \leq T-h$.
@@
 
-The models are then compared by their forecast errors over the test
+The models are then compared by their forecast performance over the test
 sample. There are many statistics that have been considered in the
@@
 
-Most theoretical research, such as \citet{DiM:95}, \citet{Wes:96},
+Statistics like $\oost$ have a long history in empirical economics
+because they capture an intuitive idea of modeling: that a good model
+should be able to forecast well when given new data and not only when
+used to fit the same data that were used to estimate it. \cite{MeR:83}
+use such a statistic to study exchange rate models and find that none
+of the models that existed at the time of the study outperformed a
+random walk. This finding has been remarkably durable and has spawned
+an enormous literature; see \cite{Mar:95}, \cite{KiT:03},
+\cite{CCP:05}, \cite{EnW:05}, \cite{Ros:05}, and \cite{BWB:10}, among
+many others.
+
+Most theoretical research on these statistics, such as \citet{DiM:95}, \citet{Wes:96},
 and \cite{Mcc:07}, has focused on using the \oost\ statistic to test
-hypotheses about the pseudo-true values $\theta_1$ and $\theta_2$.  In
+hypotheses about the pseudotrue values $\theta_1$ and $\theta_2$.  In
 particular, that research focuses on testing the null hypothesis that
@@
 But the population quantities in \eqref{eq:21} do not determine which
-model is more accurate in finite samples and, under our asymptotics,
-in the limit when models are allowed to be overfit. The models'
+model is more accurate in practice. The models'
 accuracy will also depend on the specific estimates of $\theta_1$ and
@@
 \begin{equation}
-  \E_T \oosB \equiv Q^{-1} \sum_{t=T+1}^{T+Q} \E_T D_t,
+  \E_T \oosB = Q^{-1} \sum_{t=T+1}^{T+Q} \E_T D_t,
 \end{equation}
@@
 converge in probability to the difference in the expected loss
-associated with the pseudo-true models,%
-\footnote{Under standard stationarity, moment, and weak-dependence
-  conditions.} %
+associated with the pseudotrue models,%
+\footnote{This statement is subject to the usual assumptions: some
+  form of stationarity, bounded moments, and weak dependence.} %
 i.e. the LHS of~\eqref{eq:21}.
@@
 = 1$ for all $t$, and let $(y_{t+\h},x_{2,t})$ be i.i.d. $N(0,
-\Sigma)$.  Then
+\Sigma)$.  Then the difference between $\E_T \oosB$ and
+quantity~\eqref{eq:22} is
 \begin{align*}
@@
   \big(\E y_{T+\h+1}^2 - \E (y_{T+\h+1} - x_{T+1}'\theta_2)^2 \big)\\
-  &= (\bh{2,t} - \theta_2)' \Sigma_x (\bh{2,t} - \theta_2) + o_p(1).
+  &= (\bh{2,t} - \theta_2)' \Sigma (\bh{2,t} - \theta_2) + o_p(1).
 \end{align*}
-This last term has expectation $\var(y_T) \frac{K_2}{T - K_2 - 1}$ and
-would converge to zero if $K_2$ were fixed, but does not when $\lim
+This last term has expectation equal to $\var(y_T) \frac{K_2}{T - K_2 - 1}$ and
+would converge to zero in probability if $K_2$ were fixed, but does not when $\lim
 K_2 / T > 0$. In Section~\ref{sec:oostheory} we show that the \oost\
@@
 asymptotics and does not estimate the expected loss associated with
-the pseudo-true coefficients.
+the pseudotrue coefficients.
 
@@
 \subsection{Assumptions}
+\label{sec:asmp}
 
@@
 weak dependence condition; absolute regularity admits a particular
-coupling argument, ``Berbee's Lemma'' \citep[reproduced in this
+coupling argument, \emph{Berbee's Lemma} \citep[reproduced in this
 paper as Lemma A.1 for reference]{Ber:79} that is
-unavailable for strong mixing sequences; absolute regularity
+unavailable for strong mixing sequences. Absolute regularity
 implies uniform mixing, so this assumption is not unduly strong.
 For a detailed discussion of these weak dependence conditions,
-please see, for example, \citet{Dav:94}.
+please see \citet{Dav:94} or \citet{Dou:94}.
 
@@
 present results assuming covariance stationarity of the loss
-associated with the pseudo-true models. We need to make a stronger
-assumption because we will need to prove asymptotic results where the
+associated with the pseudotrue models. We need to make a stronger
+assumption because we will need to prove asymptotic results when the
 $\bh{it}$ remain random---so we would need covariance stationarity to
-hold for almost all estimates of $\theta_i$, and not just for the
-pseudo-true value.
+hold for almost all estimates of $\theta_i$ and not just for the
+pseudotrue value. The only way to guarantee that condition is to
+assume strict stationarity for the underlying stochastic processes.
 
@@
   The number of regressors for each model, $K_1$ and $K_2$, are less
-  than $R$, and $K_2/T$ and $(K_2-K_0)/T$ are uniformly positive;
-  $K_0$ is the number of regressors shared by the two models ($K_1/T$
-  can be uniformly positive as well, but is not required to be).
+  than $R$ and $(K_2-K_0)/T$ is uniformly positive;
+  $K_0$ is the number of regressors shared by the two models ($(K_1 - K_0)/T$
+  may be uniformly positive as well, but is not required to be).
 
   The variance of $y_{t+\h}$ given $\mathcal{F}_t$ is uniformly
-  positive and finite, and all of the eigenvalues of the covariance
+  positive and finite and all of the eigenvalues of the covariance
   matrix of $x_t$ are uniformly positive and finite as well.
@@
   \begin{align*}
-    &\eigen_{\max}(X_{iS}'X_{iS}) = O_{L_3}(S),&
-    &\eigen_{\max}(\E(X_{iT}'\ep{iT}\ep{iT}'X_{iT}
-    \mid X_{iR}'X_{iR}, X_{iT}'X_{iT})) = O_{L_3}(S),\\
-    &\eigen_{\max}((X_{iS}'X_{iS})^{-1}) = O_{L_3}(1/S),&
-    &\eigen_{\max}\Big(\E\Big( \sum_{s,t=R+1}^{T-h} \e_{is} \e_{it} x_{is}x_{it}'
-    \,\Big|\, X_{iR}'X_{iR} \Big)\Big) = O_{L_3}(P),
+    &\eigen_{\max}(X_{iS}'X_{iS}) = O_{L_3}(S), \\
+    &\eigen_{\max}((X_{iS}'X_{iS})^{-1}) = O_{L_3}(1/S), \\
+    \intertext{and}%
+    &\eigen_{\max}\Bigg(\E\Big( \sum_{s,t=U}^{S-h} \e_{i,s+\h} \e_{i,t+\h} x_{is}x_{it}'
+    \,\Big|\, X_{iS}'X_{iS} \Big)\Bigg) = O_{L_3}(S-U),
   \end{align*}
-  for large enough $T$, where $S = R,T$, $i = 1,2$,
-  \[ X_{iT} \equiv [x_{i1} \quad \dots \quad x_{i,T-\h}]' \qquad
-  \text{and} \qquad \ep{iT} = (\e_{i,1+\h}, \dots, \e_{i,T})'.\]
-
-  Additionally, the Euclidean norms of the pseudo-true coefficients,
+  for large enough $T$, where $S = R,\dots,T$, $U=1,\dots,S-\h$,
+  $i = 1,2$,
+  \[ X_{iS} \equiv [x_{i1} \quad \dots \quad x_{i,S-\h}]' \qquad
+  \text{and} \qquad \ep{iS} = (\e_{i,1+\h}, \dots, \e_{i,S})'.\]
+
+  Additionally, the Euclidean norms of the pseudotrue coefficients,
   $\theta_1$ and $\theta_2$, satisfy $|\theta_1|_2 = O(1)$ and
@@
 variance is straightforward. The conditions on the eigenvalues are
-technical and control the behavior of the OLS estimator as the
-number of regressors gets large.  The restrictions on the pseudo-true
-coefficients ensure that the regression model doesn't dominate the
-variance of $y_{t+\h}$ in the limit.
-
-We can see that these conditions are trivially satisfied when the
-underlying series are i.i.d.\ Normal and the regression includes a
-constant.
-\begin{example}
-  If $(x_{t}, y_t)$ are i.i.d. $N(0, \Sigma)$ where $\Sigma$ is
-  uniformly positive definite, then
-  \begin{equation*}
-    \theta = \cov(y_t, x_t) \var(x_t)^{-1}
-  \end{equation*}
-  and the regression constant is
-  \begin{equation*}
-    \theta_0 = \E y_t - \cov(y_t, x_t) \var(x_t)^{-1} \E x_t
-  \end{equation*}
-  where both of these terms follow directly from the normality
-  assumption.  Then $|\theta|_2 = O(1)$ as a consequence of uniform
-  positive definiteness of $\Sigma$ and $\varepsilon_t \sim i.i.d.\
-  N(0, v^2)$ (independent of $x_t$) with
-  \begin{equation*}
-    v^2 = \var(y_t) - \cov(y_t, x_t) \var(x_t)^{-1} \cov(y_t, x_t)'.
-  \end{equation*}
-  Then we have
-  \begin{equation*}
-    \E(X_{T}'\ep{T}\ep{T}'X_T \mid X_{R}'X_{R}, X_{T}'X_{T})
-    = v^2 X_{T}'X_{T}
-  \end{equation*}
-  and
-  \begin{equation*}
-    \E\Big( \sum_{s,t=R+1}^{T-h} \e_s \e_t x_s x_t'
-    \,\Big|\, X_{R}'X_{R} \Big) = P v^2 \E x_t x_t'.
-  \end{equation*}
-
-  So the conditions amount to restrictions on the eigenvalues of
-  $X_T'X_T$, which are familiar from general OLS.
-\end{example}
+technical and control the behavior of the OLS estimator as the number
+of regressors gets large---the third assumption is nonstandard but can
+be easily verified under independence, for example. The restrictions
+on the pseudotrue coefficients ensure that the regression model
+doesn't dominate the variance of $y_{t+\h}$ in the limit.
 
@@
   \begin{equation*}
-    \| L'(y^* - x_{i}^{*\prime}
-    (\alpha \hat{\theta}_{iR} + (1-\alpha) \hat{\theta}_{iT})) \|_2
+    \| L'(y^* - x_{i}^{*\prime} (\alpha \bh{iR} + (1-\alpha) \bh{iT})) \|_2
     \leq B_L
@@
 absolute error and many asymmetric loss functions satisfy this
-assumption.  The next assumption controls the growth of the test and
+assumption. The Assumption makes use of both $(y_{t+\h}, x_{1t},
+x_{2t})$ and $(y^*, x_1^*, x_2^*)$ because the period $t$ observations
+can be dependent on $\bh{iT}$ in complicated ways. When the underlying
+observations are independent these assumptions can simplify
+considerably.
+
+The next assumption controls the growth of the test and
 training samples.
-\begin{asmp} \label{asmp-4} $P, R, Q \to\infty$ and $P^2/T \to 0$ as
-  $T \to \infty$.
+\begin{asmp} \label{asmp-4} (a) $P, R, Q \to\infty$ as $T \to
+  \infty$. (b) $P^2/T \to 0$ as $T \to \infty$.
 \end{asmp}
@@
 requires but is not new; \citet{Mcc:00} extends West's results to
-cover a similar case.\footnote{Our assumptions allow for discontinuous
-  loss functions, such as those proposed by \citet{PeT:92}.
-  \citet{Mcc:00} does not explicitly allow for such loss functions,
-  but it appears that his conclusions hold for them as well under the
-  restriction $P/T \to 0$.}  We assume full stationarity and absolute
+cover a similar case. We assume full stationarity and absolute
 regularity of the underlying random array, while West assumes
@@
 
-\section{Theoretical Results}\label{sec:theory}
-The main result of the paper is Theorem
-\ref{res-confidence-intervals}, which shows that the OOS average is
-asymptotically normal and centered on $\E_T \oosB$.  This result holds
-even for nested models and can be used to construct confidence
-intervals or test hypotheses.  After presenting Theorem
-\ref{res-confidence-intervals}, we explain and present two key Lemmas
-used in its proof that add some insight into the nature of OOS
-comparisons, and then show that standard HAC OOS estimators can be
-used to consistently estimate the asymptotic variance of the OOS
-average.  We next present an example that illustrates some of these
-concepts, and then show that typical full-sample tests do not let
-researchers test hypotheses about $\E_{T} \oosB$ when the models are
-overfit.  In fact, in the limit they can reject a more accurate but
-false benchmark model almost surely.
-
-\subsection{Behavior of the DMW Test with Overfit}\label{sec:oostheory}
-Our first theorem justifies using the DMW $t$-test with a a short
-test sample.
-
-\begin{thm}\label{res-confidence-intervals}
-  Suppose that Assumptions \ref{asmp-1}--\ref{asmp-4} hold, that
-  $\sh^2$ is an estimator satisfying
-  \[
-    \sh^2 - \sigma^2 \to^p 0 \quad \text{with}\quad
-    \sigma^2 \equiv \var_R(\sqrt{P} \oosA) \equiv P \E_R(\bar{D}_R -
-    \E_R \bar{D}_R)^2,
-  \]
-  and that $\sigma^2$ is uniformly a.s. positive.  Then
-  \[
-  \frac{\oosA - \E_T\oosB}{\sh / \sqrt{P}}
-  \to^d N(0,1).
-  \]
-  Consequently, each of the usual Gaussian confidence intervals,
-  \begin{gather}
-  [\oosA - z_{\alpha/2} \, \sh /
-      \sqrt{P}, \oosA + z_{\alpha/2} \sh / \sqrt{P}],\label{interval-twosided} \\
-  [\oosA - z_{\alpha} \, \sh / \sqrt{P}, +\infty), \label{interval-greater}
-  \intertext{and}
-(-\infty, \oosA + z_{\alpha}
-      \, \sh / \sqrt{P}],
-    \end{gather}
-    contains $\E_T\oosB$ with probability $\alpha$ in the limit,
-  with $z_{\alpha}$ the $1-\alpha$ quantile of the standard normal
-  distribution.
+\section{Theoretical results}
+\label{sec:theory}
+
+This section lays out our theoretical results. The first subsection
+presents results for the DMW $t$-test; we show that it is
+asymptotically normal when one or both forecasting models is overfit.
+(i.e., under our increasing-$K$ asymptotic approximation.) We also
+present a new limitation on these statistics---OOS comparisons heavily
+penalize overfit models unless the size of the test sample is a very
+small proportion of the total sample size, which will not be practical
+in much applied research. The second subsection presents results for
+full-sample statistics and shows that widely used test statistics and
+model selection criteria are misleading when choosing a model for
+forecasting. In contrast to OOS comparisons, these full-sample
+criteria choose overfit models too often, even when they are less
+accurate than simple benchmark models. These results are somewhat
+abstract, so the third subsection works through an example DGP in
+detail.
+
+\subsection{Asymptotic normality of the DMW test}
+\label{sec:oostheory}
+
+This section has two main conceptual results. The first,
+Lemma~\ref{res-mixingale}, shows that the OOS average, $\oosA$, is
+asymptotically normal as the size of the test sample grows, even when
+the models are overfit. But $\oosA$ is centered at $\E_R \oosA$, the
+difference in the generalization error of the models estimated over
+the \emph{training sample}, which is not the quantity of interest to
+forecasters. Forecasters will generally want to estimate or test
+hypotheses about the difference in the generalization error of the
+models estimated with the full sample, $\E_T \oosB$. Our second
+result, Lemma~\ref{res-convergence}, shows that these quantities are
+approximately equal only when the test sample is very small relative
+to the total sample size. In particular, we show that $\oosA$ is a
+consistent estimator of $\E_T \oosB$ when $P/T \to 0$ and is
+asymptotically normal with mean $\E_T \oosB$ when $P^2/T \to 0$. After
+establishing these Lemmas, we then show that the \oost\ test is
+asymptotically standard normal and can be used to test hypotheses
+about $\E_T \oosB$, which requires the two Lemmas as well as a
+consistent estimator of the variance of the OOS average.
+
+In the first result, we show that
+$\sqrt{P} (\oosA - \E_R \oosA)$ is asymptotically normal as $P \to
+\infty$. This application of the CLT is complicated by a hidden source
+of dependence---the training sample estimators $\bh{iR}$. Under
+conventional asymptotic theory, we would replace each $\bh{iR}$ with
+its pseudotrue value $\theta_i$ and apply the CLT to $\sqrt{P}
+L(y_{t+\h} - x_{it}'\theta_i)$, with some complications potentially
+arising from the replacement (as in \citealp{Wes:96},
+\citealp{ClM:01}, or \citealp{Mcc:07}, for example). But we can not
+make that replacement here, because our asymptotic approximation
+prevents $x_{it}'\bh{iR}$ from converging to $x_{it}'\theta_i$.
+
+Instead, we show that $D_t - \E_R D_t$ is an $L_2$-mixingale that
+satisfies the CLT. Mixingales satisfy a weak-dependence condition
+similar to MDSes,%
+\footnote{An array $Z_{n,t}$ and an increasing sequence of \sfields
+  $\Gs_{n,t}$ is an \emph{$L_2$-mixingale of size $-1/2$} if there is
+  an array of constants $\{c_{n,t}\}$ and a sequence of constants
+  $\zeta_l = O(l^{-1/2 - \delta})$ for some $\delta > 0$ such that
+  \begin{equation*}
+    \lVert \E(Z_{n,t} \mid \Gs_{n,t-l}) \rVert_2
+    \leq c_{n,t} \zeta_l
+    \qquad\text{and}\qquad
+    \lVert Z_{n,t} - \E(Z_{n,t} \mid \Gs_{n,t+l}) \rVert_2
+    \leq c_{n,t} \zeta_{l+1}.
+  \end{equation*}
+  Mixingales were introduced and developed by
+  \citet{Mcl:74,Mcl:75,Mcl:75b,Mcl:77}.} %
+but they have some limitations. Transformations of mixingales are
+typically not themselves mixingales, which means that CLTs for
+mixingale processes require additional assumptions to hold beyond the
+mixingale property.%
+\footnote{See \citet{Jon:97} for an illustration. We will borrow
+  heavily from his results in our proofs.} %
+This is in contrast to Near Epoch Dependent (NED) processes, which
+retain the NED property after transformations. \citep[See chapter 17
+of][for further discussion of these properties.]{Dav:94} But the OOS
+loss has more structure than most mixingales and behaves like an NED
+process in important respects.
+
+\begin{lem}\label{res-mixingale}
+  If Assumptions~\ref{asmp-1}--\ref{asmp-3} hold then $\{D_t - \E_R
+  D_t, \mathcal F_t\}$ is an $L_2$-mixingale of size $-1/2$.
+  Moreover
+  \begin{equation}\label{normalpart}
+    \sqrt{P}(\oosA - \E_R \oosA)/\sigma \to^d N(0,1)
+  \end{equation}
+  as $P \to \infty$ if $\sigma^2$ is uniformly almost surely positive,
+  where $\sigma^2 = \var_R(\sqrt{P} \oosA)$ (which is equal to $P
+  \E_R(\bar{D}_R - \E_R \bar{D}_R)^2$).
+\end{lem}
+
+It may be helpful to compare Lemma~\ref{res-mixingale} to the method
+of proof in \citet{GiW:06}. \citet{GiW:06} show that the OOS average
+is asymptotically normal when the forecasts are estimated with a fixed
+length rolling window. In that case, each $\bh{it}$ depends on only
+the most recent $R$ observations and, since $R$ is fixed in their
+theory, the forecast errors $y_{t+\h} - x_{it}'\bh{it}$ are themselves
+mixing processes. Transformations of their forecast errors are
+still obviously mixing processes and obey the CLT.
+
+In our paper, $R$ is not fixed and the forecast errors are not a
+convenient weakly-dependent process, since the estimation error in
+$\bh{it}$ introduces strong dependence. Consequently,
+transformations of the forecast errors are not weakly dependent
+either. But this additional dependence has a special form and can be
+removed by subtracting the conditional mean; this means that $g(y_{t+\h} -
+x_{it}'\bh{it})$ is not weakly dependent but $g(y_{t+\h} -
+x_{it}'\bh{it}) - \E_R g(y_{t+\h} - x_{it}'\bh{it})$ is, as long as
+the new process satisfies standard moment
+restrictions. Assumptions~\ref{asmp-1}--\ref{asmp-3} ensure that these
+restrictions are satisfied for $D_t - \E_R D_t$.
+
+The form of the dependence introduced by $\bh{it}$ also allows the CLT
+to hold without additional restrictions---the proof rests on showing
+that a process like $D_t^2 - \E_R D_t^2$ is also a mixingale, using a
+similar argument to the one used by \citet{Jon:97} for NED
+processes. This property needs to be established on its own because it
+does not follow from the behavior of $D_t - \E_R D_t$.
+Lemma~\ref{lem:a2} presents the details of this part of the proof.
+
+The next Lemma connects $E_R \oosA$ to $\E_T \oosB$, the difference in
+the models' generalization error. Under conventional asymptotics,
+these quantities are generally close. But they are not for overfit
+models, and the models will tend to forecast better when estimated over the
+full sample than over the training sample. Consequently, OOS
+comparisons will penalize overfit models too much unless the test
+sample is small relative to the total data set.
+
+\begin{lem} \label{res-convergence}
+  Under Assumptions \ref{asmp-1}--\ref{asmp-4}a,
+  \begin{equation}\label{eq:7}
+    \E_T \oosB - \E_R \oosA = O_p(\sqrt{P/T}) + o_p(P^{-1/2} + Q^{-1/2}).
+  \end{equation}
+  Moreover, there exist processes and loss functions that satisfy
+  Assumptions \ref{asmp-1}--\ref{asmp-4}a but $\E_T \oosB - \E_R \oosA
+  \neq O_p(1)$ unless $P/T \to 0$.
+\end{lem}
+
+We can view $\E_T \oosB - \E_R \oosA$ as noise introduced by
+approximating the performance of the full-sample estimates with that
+of the partial-sample estimates. The second part of
+Lemma~\ref{res-convergence} shows that the $O_p(\sqrt{P/T})$ term
+is generally binding; using $\oosA$ to estimate $\E_T \oosB$ requires
+$P/T \to 0$ for consistency and using $\sqrt{P} \oosA$ to test
+hypotheses about $\E_T \oosB$ requires $P^2/T \to 0$.
+
+Finally, we can use Lemmas~\ref{res-mixingale}
+and~\ref{res-convergence} to show that the DMW test is asymptotically
+normal and centered at $\E_T \oosB$, as long as
+Assumption~\ref{asmp-4}b holds. This theorem justifies using the DMW
+$t$-test with a short test sample, which may not be feasible in some
+applications.
+
+\begin{thm}\label{res-oost}
+  Suppose that Assumptions \ref{asmp-1}--\ref{asmp-5} hold (including
+  \ref{asmp-4}b), that $\gamma \to \infty$ and $\gamma/P \to 0$ as $T
+  \to \infty$, and that $\sigma^2$ is uniformly a.s. positive. Define
+  $\sh^2$ to be the usual OOS HAC estimator of the asymptotic variance
+  of $\oosA$,
+  \begin{equation}
+    \sh^2 \equiv P^{-1} \oosSum{s,t}{1} (D_t - \oosA)(D_s - \oosA)
+    \vWeight.
+  \end{equation}
+  Then
+  \begin{equation}
+    \sqrt{P}(\oosA - \E_T\oosB)/\sh \to^d N(0,1).
+  \end{equation}
 \end{thm}
+
 The requirement that $\sigma^2$ be uniformly a.s. positive is not
@@
 
-This result allows forecasters to use the DMW test to conduct
-inference about the models' accuracy.  Since the OOS average,
-$\oosA$, is asymptotically normal and centered on the expected future
-performance, $t$-tests constructed from the OOS errors necessarily
-test hypotheses about $\E_T \oosB$ and not the performance of the
-pseudo-true models or the unconditional performance of the
-models.\footnote{i.e. $\E L(\e_{1,t+\h}) - \E  L(\e_{2,t+\h})$ or $\E \oosB$.
-Note that the expectation of $\E_T \oosB$ equals $\E \oosB$ but that
-$\sqrt{P} (\E_T \oosB - \E \oosB)$ may not be asymptotically normal,
-which would be necessary for testing.}
-This application to testing can be expressed as its own theorem:
+Finally, we establish that the DMW test can be use to construct
+confidence intervals for $\E_T \oosB$ or test hypotheses about $\E_T
+\oosB$. In particular, forecasters will often want to test the null
+hypothesis that $\E_T \oosB \leq 0$, meaning that the benchmark model
+is expected to be more accurate than the alternative model in the
+future.
+
 \begin{thm}\label{res:oostest}
-Suppose that the conditions of Theorem \ref{res-confidence-intervals}
-hold and that $\lim \Pr[\E_T \oosB \leq 0] > 0$.  Then
-\begin{equation}
+  Suppose that the conditions of Theorem
+  \ref{res-oost} hold. Then each of the usual Gaussian
+  confidence intervals,
+  \begin{gather}
+    [\oosA - z_{\alpha/2} \, \sh /
+    \sqrt{P}, \oosA + z_{\alpha/2} \sh / \sqrt{P}],\label{interval-twosided} \\
+    [\oosA - z_{\alpha} \, \sh / \sqrt{P}, +\infty), \label{interval-greater}
+    \intertext{and}
+    (-\infty, \oosA + z_{\alpha} \, \sh / \sqrt{P}],
+  \end{gather}
+  contains $\E_T\oosB$ with probability $\alpha$ in the limit, with
+  $z_{\alpha}$ the $1-\alpha$ quantile of the standard normal
+  distribution. If $\lim \Pr[\E_T \oosB \leq 0] > 0$ in addition then
+  \begin{equation}\label{eq:23}
     \lim \Pr[P^{1/2}\oosA/\sh > z_{\alpha} \mid \E_T
@@
 \end{thm}
-
-Two intermediate Lemmas will help us understand Theorem
-\ref{res-confidence-intervals} better.  Its proof consists of two
-steps: we can write
+The results for confidence intervals in Theorem~\ref{res:oostest}
+follow immediately from Theorem~\ref{res-oost},
+but~\eqref{eq:23} requires additional steps.
+
+\subsection{Failure of in-sample statistics for forecast evaluation}
+\label{sec:insample}
+
+In this subsection we look at the behavior of some full-sample
+statistics under the same asymptotic theory as before.  We show that
+these statistics, which include common tests such as the Wald test as
+well as model selection criteria such as the AIC, do not measure the
+models' generalization error and consequently do not indicate which
+model will be more accurate in the future. Some of these statistics
+will tend to choose the larger model regardless of which model will be
+more accurate in the future, whereas others tend to choose the smaller
+model.  This is a different issue than whether or not full-sample
+tests are valid for testing hypotheses about the pseudotrue
+coefficients of the models; as \citet{Cal:11c} and \citet{Ana:12}
+demonstrate, variations of the Wald test can be valid for those
+hypotheses under increasing-$K$ asymptotics.%
+\footnote{\citet{Ana:12} shows that the Wald test is invalid in
+  general and gives an adjustment that corrects the critical values;
+  he also shows that the $F$-test is asymptotically valid under
+  certain conditions on the distribution of the regressors.
+  \citet{Cal:11c} shows that the $F$-test is asymptotically invalid
+  without Anatolyev's constraint, even under homoskedasticity, and
+  provides a correction that gives valid tests.  Both papers only
+  consider independent observations.} %
+To simplify the presentation we only derive results for nested models
+but the conclusions hold more generally.
+
+The full-sample statistics we study in this paper share a common
+property. They choose the alternative model when the distance between
+a subset of their coefficient estimates and the origin exceeds a
+threshold, and choose the benchmark otherwise. For the Wald test, for
+example, this threshold is chosen so that the test has correct size
+when those coefficients are zero in population. For small models that
+can be consistently estimated, these coefficient estimates are close
+to their true values and so this criterion can be a reasonable proxy
+for the relative accuracy of the larger model.
+
+But for overfit models, the estimates will typically be far from both
+their pseudotrue values and from zero. In that case, the Wald test and
+the AIC will both tend to choose the larger model even when it is less
+accurate than the smaller benchmark model. This phenomenon is driven
+by the dimensionality of the alternative model, since there are more
+potential values of the coefficient estimator that are far from zero
+when it has many elements. The threshold for the Wald test and the AIC
+is set by construction to be a bounded distance from the origin.
+Every other statistic that shares this property has the same behavior,
+since the probability that the coefficient estimators of a
+less-accurate but true alternative model fall inside a bounded
+threshold are arbitrarily small in the limit. This behavior is
+formalized by Theorem~\ref{res:insample1}.
+\begin{thm}\label{res:insample1}
+  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-4} hold and let
+  $\Lambda$ be a model selection statistic that takes the values zero
+  or one; $\Lambda = 0$ indicates that the benchmark model is chosen
+  and $\Lambda = 1$ indicates the alternative.  Moreover, assume that
+  $L(e) = e^2$ and that there exist a deterministic scalar $c$ and a
+  sequence of possibly random matrices $V_T$ such that
+  \begin{equation}\label{eq:25}
+    \Pr[\Lambda > \1\{\bh{2T}' V_T \bh{2T} > c \}] \to 0
+    \quad \text{as } T \to \infty
+  \end{equation}
+  where the eigenvalues of $V_T$ are uniformly bounded in probability
+  and $\plim \rank(V_T)/T > 0$.
+
+  Then there exist DGPs satisfing these assumptions such that
+  \begin{equation}\label{eq:11}
+    \E( \Lambda \mid \E_T \oosB \leq 0 ) \to^p 1.
+  \end{equation}
+\end{thm}
+As we state above,~\eqref{eq:11} means that, with probability
+approaching 1, the benchmark model is rejected even when it is more
+accurate. The DGPs and statistics used in Theorem~\ref{res:insample1}
+are simple and common. The DGPs include correctly specified linear
+models with normal and homoskedastic errors. The statistics that meet
+the restrictions on $\Lambda$ include the $F$-test and AIC.
+
+For example, the $F$-statistic to test the null that all of the
+coefficients unique to the larger model is known to have the form
+\begin{equation}\label{eq:17}
+  F = \frac{\bh{2T}' M_2' ( M_2 (X_{2T}'X_{2T})^{-1} M_2' )^{-1} M_2
+    \bh{2T}}{s^2 (K_2 - K_1)}
+\end{equation}
+where $s^2$ is the usual estimator of the variance of the regression
+error and $M = (0_{K_2 - K_1, K_1}\ \ I_{K_2 - K_1})$. Then let $c$ be any number
+greater than 1 and define
+\begin{equation*}
+  V_T = M_2' \big( M_2 \big(\tfrac{1}{s^2 (K_2 - K_1)} X_{2T}'X_{2T}\big)^{-1}
+  M_2' \big)^{-1} M_2'.
+\end{equation*}
+If Assumption~\ref{asmp-2} holds and $s^2$ is consistent then $V_T$
+has uniformly bounded eigenvalues and has rank $K_2 - K_1$, so it
+satisfies~\eqref{eq:25}.%
+\footnote{If it is surprising that these conditions hold for any $c >
+  1$, remember that the $F$ random variable converges to 1 in
+  probability as both degrees of freedom diverge to $\infty$ since its
+  numerator and denominator both obey the LLN.} %
+Robust variations of the Wald test can obviously satisfy~\eqref{eq:25}
+for similar reasons, and the AIC for nested linear models is
+equivalent to using the $F$-test with the critical value %
+$(e^{2 (K_2 - K_1) / T} - 1) \cdot (T - K_2) / (K_2 - K_1)$, %
+which converges to a finite limit, so the AIC satisfies~\eqref{eq:25}
+as well.
+
+For statistics that don't satisfy~\eqref{eq:25}, the behavior can be
+quite different. The BIC, for example, can also be written in terms of
+the $F$-statistic and is equivalent to using the critical value $(T \,
+e^{2 (K_2 - K_1) / T} - 1) \cdot (T - K_2) / (K_2 - K_1)$. This
+critical value diverges as $T \to \infty$, ensuring that~\eqref{eq:25}
+fails for any $c$. For this statistic, we have the opposite problem as
+before: when the alternative model is \emph{more} accurate, the
+coefficient estimates of the larger model are contained in a bounded
+region of the parameter space. Since the acceptance region of the BIC
+grows, it eventually contains \emph{any} bounded region of the
+parameter space. For large enough $T$, the BIC will always choose the
+\emph{smaller model}, even when the larger model is more accurate.
+
+Theorem~\ref{res:insample2} describes this behavior in detail.
+
+\begin{thm}\label{res:insample2}
+  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-4} hold, let $L(e) =
+  e^2$, and let $\Lambda$ be a model selection statistic as in
+  Theorem~\ref{res:insample1}. Also assume that, for any finite scalar
+  $c$,
+  \begin{equation}\label{eq:27}
+    \Pr[\Lambda > \1\{\bh{2T}' V_T \bh{2T} > c \}] \to 1
+    \quad \text{as } T \to \infty,
+  \end{equation}
+  where $V_T$ is a sequence of possibly random matrices with with
+  eigenvalues uniformly bounded in probability and $\plim \rank(V_T)/T
+  > 0$. Then there exist DGPs satisfing these assumptions such that
+  \begin{equation}\label{eq:15}
+    \E( \Lambda \mid \E_T \oosB \geq 0 ) \to^p 0.
+  \end{equation}
+\end{thm}
+
+Again,~\eqref{eq:15} implies that statistics like the BIC will always
+choose the smaller model, even when the larger model will give more
+accurate forecasts. Both models may be overfit, in that both $K_1/T$
+and $K_2/T$ may both be positive in the limit; the key is that $(K_2 -
+K_1)/T$ is also positive in the limit.
+
+It is important to remember that, when $\Lambda$ represents a test
+statistic, the test may have correct size for the null hypothesis that
+the additional coefficients on the larger model are zero. So previous
+research, such as \citet{Cal:11c} and \citet{Ana:12}, does not predict
+these results. Any statistic that uses the distance of the models'
+estimated coefficients from a set point (the origin being the most
+common) is poorly suited for choosing between overfit models. These
+models only forecast well when their coefficient estimates are close
+to their pseudotrue values, which can be far from any prespecified
+point. Depending on the statistic, it can be biased towards choosing
+the larger model or the smaller model. Formal in-sample tests will
+likely be biased towards the larger model, as we show for the $F$-test
+in Theorem~\ref{res:insample1}.
+
+\subsection{An extended but simple example}
+\label{sec:example}
+
+This subsection illustrates the previous theoretical results with a
+concrete, extremely simple, example. Let $L(e) = e^2$ and $h =
+1$. Suppose that $\e_{t+1} \sim i.i.d.\ N(0,1)$, that the benchmark
+model is nested in the alternative, and let
 \begin{equation}
-  \sqrt{P} (\oosA - \E_T \oosB) = \sqrt{P} (\oosA - \E_R
-  \oosA) + \sqrt{P} (\E_R \oosA - \E_T \oosB),
-\end{equation}
-so Theorem~\ref{res-confidence-intervals} holds if
-\begin{equation}\label{coefpart}
-  \E_R \oosA = \E_T \oosB + o_p(P^{-1/2}).
-\end{equation}
-and
-\begin{equation}\label{normalpart}
-  \sqrt{P}\frac{\oosA - \E_R \oosA}{\sigma} \to^d N(0,1)
-\end{equation}
-The first Lemma establishes~\eqref{coefpart} and the second shows that
-the process $\{D_t - \E_R \oosA\}$ is an $L_2$-mixingale of size
-$-1/2$ that satisfies a CLT, ensuring~\eqref{normalpart}.
-
-\begin{lem} \label{res-convergence}
-  Under Assumptions \ref{asmp-1}--\ref{asmp-4},
-  \begin{equation}\label{eq:7}
-    \E_T \oosB - \E_R \oosA = O_p(\sqrt{P/T}) + o_p(P^{-1/2} + Q^{-1/2}).
-  \end{equation}
-\end{lem}
-
-Note that $\E_T \oosB - \E_R \oosA$ is noise introduced by
-approximating the performance of the full-sample estimates with that
-of the partial-sample estimates.  Moreover, the $O_p(\sqrt{P/T})$ term
-is binding; it is straightforward to find examples for which
-$\sqrt{T/P}(\E_T \oosB - \E_R \oosA)$ does not converge to
-zero.\footnote{Notice that, if the observations are i.i.d. and
-  $(y_{t+h}, x_{it}) \sim N(0,I)$, $(\hat{\theta}_{iR} -
-  \hat{\theta}_{iT}) \sim N(0, (X_{iR}'X_{iR})^{-1} -
-  (X_{iT}'X_{iT})^{-1})$ given $X_{iT}$, and so
-  $\var(x_{i,T+1}'\hat{\theta}_{iR} - x_{i,T+1}'
-  \hat{\theta}_{iT}) \gg P K_i / (R - K_2)(T - K_2)$.}
-Consequently, there is little scope to relax our assumption that
-$P^2/T \to 0$.  If $\lim P^2/T$ is positive and finite then there is
-the possibility of adjusting the asymptotic distribution of the test
-statistic to account for this noise term as in \citet{Wes:96}, but we
-leave that to future research.  If $P^2/T \to \infty$, which is
-closest to common practice in applied research, the noise term
-dominates the asymptotic distribution of the OOS $t$-test and the
-test has only trivial power in the limit if it has correct size.
-
-\begin{lem}\label{res-mixingale}
-  Part 1: If Assumptions~\ref{asmp-1}--\ref{asmp-3} hold then the
-  inequality
-  \begin{equation}\label{mixingaleR}
-    \lVert \E_{R+j-l}(D_{R+j} - \E_R D_{R+j}) \rVert_2 \leq
-    \couplingConstant \; \zeta_l
-  \end{equation}
-  with $\zeta_l = O(l^{-1/2 - \delta})$ holds for some positive
-  $\delta$, any positive $j$, and any $l$ between 0 and $j$.  As a
-  consequence, $\{D_t - \E_R D_t, \mathcal F_t\}$ is an
-  $L_2$-mixingale of size $-1/2$.
-
-  \noindent Part 2: Moreover,~\eqref{normalpart} holds under
-  Assumptions~\ref{asmp-1}--\ref{asmp-4} if $\sigma^2$ is
-  a.s. uniformly positive.
-\end{lem}
-
-Mixingales satisfy a weak-dependence condition similar to MDSes and
-were introduced and studied extensively by
-\citet{Mcl:74,Mcl:75,Mcl:75b,Mcl:77}.  This lemma shows that the
-estimation uncertainty introduces dependence into the OOS forecast
-errors, but the additional dependence is contained in the term $\E_R
-\oosA$ and can be effectively removed by subtraction.  The second part
-of the Lemma shows that the basic mixingale CLT established by
-\citet{Jon:97} applies in this setting.\footnote{De Jong proves two
-  CLTs: one for mixingales and one for NED functions of mixing
-  processes.  His mixingale result makes assumptions about the
-  behavior of the sample second moment that arise as consequences of
-  NED.  The proof of Lemma~\ref{res-mixingale} shows that the
-  arguments used for de Jong's NED CLT continue to hold for our
-  OOS process---in effect, that the OOS process has slightly more
-  structure than required for it to be a mixingale.}  Note that
-Lemma~\ref{res-mixingale} does not require $P^2/T \to 0$.
-
-Finally, for Theorem \ref{res-confidence-intervals} to be useful, we
-need a consistent estimator of $\sigma^2$. Lemma
-\ref{res-variance-estimator} establishes that the usual OOS HAC
-variance estimators are consistent.\footnote{As with
-      Lemma~\ref{res-mixingale}, the proof of this lemma takes
-      \citepos{JoD:00} existing consistency results
-      for NED processes and shows that the same arguments can be
-      applied to our OOS mixingale.}
-
-\begin{lem}
-  \label{res-variance-estimator} Suppose Assumptions
-  \ref{asmp-1}--\ref{asmp-5} hold and that $\gamma \to \infty$ and
-  $\gamma/P \to 0$ as $T \to \infty$, and define
-  \begin{equation*}
-    \sh^2 \equiv P^{-1} \oosSum{s,t}{1} (D_t - \oosA)(D_{Rs} - \oosA)
-    \vWeight.
-  \end{equation*}
-  Then $\sh^2 - \sigma^2 \to^p 0$.
-\end{lem}
-
-The next subsection presents an example that clarifies the previous
-results.
-
-\subsection{An Example}\label{sec:example}
-
-Let $L(e) = e^2$, let $h
-= 1$, let the benchmark model have no regressors (i.e. $y_{t+1} \sim$
-white noise), suppose that $(y_{t}, x_{2t}) \sim i.i.d.\ N(0,I)$, and
-assume that $R > 2K_2 + 4$.\footnote{The restriction $R > 2 K_2 + 4$
-  allows us to use a convenient formula for moments of the
-  Inverse-Wishart distribution.}  Under these conditions,
-\begin{equation*}
+  y_{t+1} = x_{2t}'\theta_2 + \e_{t+1}.
+\end{equation}
+be the DGP. We also assume for simplicity that the full-sample design
+matrix $X_{2T}$ satisfies $X_{2T}'X_{2T} = T \times I$ and that
+$x_{T+1} \sim N(0, I)$, which violates our assumptions on the
+regressors but simplifies this treatment considerably.
+
+The first part shows how the assumptions in Section~\ref{sec:asmp} are
+satisfied in this example and the second demonstrates asymptotic
+normality of the DMW OOS $t$-test. The third part explicitly shows
+that $\E_R \oosA$ converges to $\E_T \oosB$ only when the test sample
+is small. And the last part demonstrates that the $F$-test, AIC, and
+BIC do not indicate which model will be more accurate in the future,
+even in this simple example.
+
+\subsubsection*{Fulfillment of the assumptions}
+
+\subsubsection*{Asymptotic normality of the OOS average}
+
+Under these conditions, we have
+\begin{equation}
   D_t =
   \begin{cases}
-    2 y_{t+1} x_{2t}'\hat{\theta}_{2R} -
-    \hat{\theta}_{2R}' x_{2t} x_{2t}' \hat{\theta}_{2R} & t \leq T \\
-    2 y_{t+1} x_{2t}'\hat{\theta}_{2T} -
-    \hat{\theta}_{2T}' x_{2t} x_{2t}' \hat{\theta}_{2T} & t > T.
+    2 \e_{t+1} (x_{2t}'\bh{2R} - x_{1t}'\bh{1R})
+    + (x_{2t}'\theta_2 - x_{1t}'\bh{1R})^2
+    - (x_{2t}'\theta_2 - x_{2t}'\bh{2R})^2
+    & \text{if } t < T \\
+    2 \e_{t+1} (x_{2t}'\bh{2T} - x_{1t}'\bh{1T})
+    + (x_{2t}'\theta_2 - x_{1t}'\bh{1T})^2
+    - (x_{2t}'\theta_2 - x_{2t}'\bh{2T})^2
+    & \text{if } t > T
   \end{cases}
-\end{equation*}
-
-The first two conditional moments of $D_t$ for $t > R$ (given
-$\mathcal{F}_R$) are straightforward to derive: $\E_R D_t = -
-\hat{\theta}_{2R}' \hat{\theta}_{2R}$ and
-\begin{equation*}
-  \sigma^2 \equiv \E_R(D_t - \E_R D_t)^2 = 4
-  \hat{\theta}_{2R}' \hat{\theta}_{2R} +
-  \E_R(\hat{\theta}_{2R}' (I - x_{2t} x_{2t}')
-  \hat{\theta}_{2R})^2   \geq 4 \hat{\theta}_{2R}'
-  \hat{\theta}_{2R} \quad a.s.
-\end{equation*}
-Now, $\hat{\theta}_{2R}' \hat{\theta}_{2R}$ is
-a.s. positive and uniformly integrable with mean $4 K_2 / (R - K_2 -
-1)$ (since $(X_{2R}'X_{2R})^{-1}$ is Inverse-Wishart$(I_{K_2}, R)$),
-making $\sigma^2$ uniformly a.s. positive and ensuring that the
-distribution of the OOS average is not $P^{1/2}$-degenerate.  The
-natural OOS variance estimator is consistent for $\sigma^2$:
-\begin{align*}
-  \sh^2 &= P^{-1} \sum_{t=R+1}^{T-1} (D_t - \oosA)^2 \\
-  &= 4 \hat{\theta}_{2R}' \Big[P^{-1} \sum_{t=R+1}^{T-1}
-  \Big(y_{t+1} x_{2t} - P^{-1} \sum_{s=R+1}^{T-1} y_s x_{2s}\Big)
-  \Big(y_{t+1} x_{2t} - P^{-1} \sum_{s=R+1}^{T-1} y_s
-  x_{2s}\Big)'\Big] \hat{\theta}_{2R}' \\ & \quad - 4
-  \Big[P^{-1} \sum_{t=R+1}^{T-1} \Big(y_{t+1} x_{2t} - P^{-1}
-  \sum_{s=R+1}^{T-1} y_s x_{2s}\Big)' \hat{\theta}_{2R}
-  \hat{\theta}_{2R}' \Big(x_{2t} x_{2t}' - P^{-1}
-  \sum_{s=R+1}^{T-1} x_{2s} x_{2s}' \Big) \hat{\theta}_{2R} \Big]
-  \\ &\quad + P^{-1} \sum_{t=R+1}^{T-1}
-  \Big[\hat{\theta}_{2R}' \Big(x_{2t} x_{2t}' - P^{-1}
-  \sum_{s=R+1}^{T-1} x_{2s} x_{2s}' \Big) \hat{\theta}_{2R}  \Big]^{2}.
-\end{align*}
-As $P \to \infty$, the first term converges in probability to
-$\hat{\theta}_{2R}' \hat{\theta}_{2R}$, the second to zero,
-and the third to $\E_R(\hat{\theta}_{2R}'(I - x_{2t}x_{2t}')
-\hat{\theta}_{2R})^2$.  Since the number of regressors prevents
-$\hat{\theta}_{2R}$ from converging i.p. to zero (its expected
-value), $\sh^2$ does not converge to the unconditional
-variance.
-
-We can see that the OOS average obeys a CLT when centered at $\E_R
-\bar{D}_R$.  The centered and scaled OOS differences satisfy
-\begin{equation*}
-  \frac{D_t - \E_R D_t}{\sigma} =
-  \frac{2 y_{t} x_{2t}' \hat{\theta}_{2R} +
-    \hat{\theta}_{2R}' (I - x_t x_t') \hat{\theta}_{2R}}{\sqrt{4
-    \hat{\theta}_{2R}' \hat{\theta}_{2R} +
-    \E_R(\hat{\theta}_{2R}'(I - x_{2t} x_{2t}') \hat{\theta}_{2R})^2}}.
-\end{equation*}
-This sequence is not i.i.d. and we can not replace $\hat{\theta}_{2R}$
-with a sequence of constants $\theta_{2R}$ since $\hat{\theta}_{2R}$
-does not converge to a deterministic limit.  But $\sigma^{-1}
-\E_t(\oosA - \E_R\oosA) = 0$, making this sequence an
-MDS,\footnote{The sequence is actually exchangeable, but MDS is
-  enough to establish the CLT.} so it obeys a CLT as long as
-$\sigma^2$ is uniformly a.s. positive, which we have already
-established.  Lemma~\ref{res-mixingale} ensures that the CLT holds
-more generally.
-
-Finally, we can look at the difference $\E_R \bar{D}_R - \E_T
-\bar{D}_T$.  We can write this as
-\begin{align*}
-  \E_R \oosA - \E_T \oosB &= \hat{\theta}_{2R}'
-  \hat{\theta}_{2R} - \hat{\theta}_{2T}' \hat{\theta}_{2T} \\ &=
-  \eb_T'[\tilde{X}_{2R}(X_{2R}'X_{2R})^{-2}
-  \tilde{X}_{2R} - X_{2T}(X_{2T}'X_{2T})^{-2} X_{2T} ] \eb_T
-\end{align*}
-with $\tilde{X}_{2R}$ the $T \times K_2$ matrix $[X_{2R}'\ 0]'$.
-Standard results for the moments of quadratic forms and of the
-Inverse-Wishart distribution \citep{Haf:79} imply that
-\begin{equation*}
-  \E(\E_R \oosA - \E_T \oosB) = \frac{K_2 P}{(T - K_2 - 1)(R - K_2 - 1)}
-\end{equation*}
+\end{equation}
+and so we can explicitly derive the components of
+Lemma~\ref{res-mixingale}:
+\begin{multline}\label{eq:17}
+  D_t - \E_R D_t
+  = 2 \e_{t+1} (x_{2t}'\bh{2R} - x_{1t}'\bh{1R})
+  + \Big\{(x_{2t}'\theta_2 - x_{1t}'\bh{1R})^2
+          - \E_R (x_{2t}'\theta_2 - x_{1t}'\bh{1R})^2 \Big\} \\
+  - \Big\{(x_{2t}'\theta_2 - x_{2t}'\bh{2R})^2
+          - \E_R (x_{2t}'\theta_2 - x_{2t}'\bh{2R})^2 \Big\}
+\end{multline}
+for $t < T$. Since the underlying observations are i.i.d., $\E_{t-1}
+D_t = \E_R D_t$ a.s.\ and $\{D_t - \E_R D_t, \Fs_{t};
+t=R+1,\dots,T-1\}$ is an MDS. Even in this simple example, the
+estimation error in $\bh{1R}$ and $\bh{2R}$ introduces strong
+persistance into the OOS forecast errors, but this persistence is
+predetermined so we can continue to apply basic asymptotic theory.
+
+Although transformations of $D_t - \E_R D_t$ will obviously not be
+MDSes in general, it should be clear that transformations of $D_t$
+will be MDSes after subtracting their conditional mean; i.e.
+\begin{equation}
+  \{g(D_t) - \E_R g(D_t); \Fs_t; t = R+1,\dots,T-1\}
+\end{equation}
+is an MDS as long as
+$g(D_t)$ has finite mean, but $g(D_t - \E_R D_t)$ is not. This MDS
+result holds because $x_t$ and $y_{t+1}$ are independent of $\bh{1R}$
+and $\bh{2R}$, so
+\begin{equation}\begin{split}
+  \E_R g(D_t)
+  &= \int g\Big((x_1'\bh{1R})^2 - (x_1'\bh{2R})^2
+       + 2 y (x'\bh{2R} - x'\bh{1R})\Big) \, f(y, x) \, dx \, dy \\
+  &= \E_{t-1} g(D_t)
+\end{split}\end{equation}
+a.s., where $f$ is the density of $(y_{t+1}, x_{2t})$ and $x_1$
+denotes the first $K_1$ elements of $x$.
+
+These MDS results imply that $\oosA$ and $(1/P) \sum_{t=R+1}^{T-1}
+D_t^2$ both obey LLNs: $\oosA \to^p \E_R \oosA$ and
+\begin{equation}
+  (1/P) \sum_{t=R+1}^{T-1} D_t^2 \to^p \E_R D_T^2.
+\end{equation}
+Moreover, these convergence results imply that $\sh^2 - \var_R
+\sqrt{P} \oosA \to^p 0$, where $\sh^2$ is the OOS variance estimator
+\begin{equation}
+  \sh^2 = (1/P) \sum_{t=R+1}^{T-1} (D_t - \oosA)^2.
+\end{equation}
+(In the general dependent case, we would need to use a HAC estimator
+for consistency.)
+
+Finally, we can apply the MDS CLT to $\oosA$ as long as $\Pr[\lim
+\var_R \sqrt{P} \oosA > 0] = 1$. \citep[Theorem 3.2.]{HaH:80} In our
+main results, we assume that this condition holds, but it is
+straightforward to verify here. Equation~\eqref{eq:17} implies that
+\begin{equation}
+  \begin{split}
+    \var_R \sqrt{P} \oosA &= \E_R(D_t - \E_R D_t)^2 \\
+    &\geq 4 \E_R (x_{2t}' \bh{2R} - x_{1t}' \bh{1R})^2
+    \quad a.s.
+  \end{split}
+\end{equation}
+and...
+
+\subsubsection*{Convergence of $\E_R \oosA$ to $\E_T \oosB$}
+
+We can also use this example to study Lemma~\ref{res-convergence}.
+Under this section's assumptions, $\E_R \oosA$ and $\E_T \oosB$ can be
+worked with directly, and their difference is equal to
+\begin{equation}
+  \begin{split}
+    \E_R \oosA - \E_T \oosB &= \Big\{(\bh{1R} - \theta_1)'(\bh{1R} -
+    \theta_1) -
+    (\bh{2R} - \theta_2)'(\bh{2R} - \theta_2)\Big\} \\
+    & \quad - \Big\{(\bh{1T} - \theta_1)'(\bh{1T} - \theta_1) -
+    (\bh{2T} - \theta_2)'(\bh{2T} - \theta_2)\Big\} \\
+    &\begin{split}
+      =\ep{T}'\Big\{
+      & \tilde{X}_{1R}(X_{1R}'X_{1R})^{-2} \tilde{X}_{1R}'
+      - X_{1T}(X_{1T}'X_{1T})^{-2} X_{1T}' \\
+      & - \tilde{X}_{2R}(X_{2R}'X_{2R})^{-2} \tilde{X}_{2R}'
+      + X_{2T}(X_{2T}'X_{2T})^{-2} X_{2T}'
+      \Big\}\ep{T}.
+    \end{split}
+  \end{split}
+\end{equation}
+with $\tilde{X}_{iR}$ the $T \times K_i$ matrix $[X_{iR}'\ 0]'$.
+
+This last term is a quadratic form and the regressors are assumed to
+be normal, so its first two moments are easy to calculate. The mean
+difference is
+\begin{equation}
+  \begin{split}
+  \E(\E_R \oosA - \E_T \oosB)
+      &=\E \tr \Big\{
+        \tilde{X}_{1R}(X_{1R}'X_{1R})^{-2} \tilde{X}_{1R}
+      - X_{1T}(X_{1T}'X_{1T})^{-2} X_{1T} \\
+      & \qquad\qquad- \tilde{X}_{2R}(X_{2R}'X_{2R})^{-2} \tilde{X}_{2R}
+      + X_{2T}(X_{2T}'X_{2T})^{-2} X_{2T} \Big\} \\
+      &= \tr \Big\{\E (X_{1R}'X_{1R})^{-1}
+         - \E (X_{1T}'X_{1T})^{-1} \Big\}
+         - \tr \Big\{\E (X_{2R}'X_{2R})^{-1}
+         - \E (X_{2T}'X_{2T})^{-1} \Big\}, \\
+      &= \tfrac{K_1 P}{(R-K_1-1)(T-K_1-1)} - \tfrac{K_2 P}{(R-K_2-1)(T-K_2-1)}.
+    \end{split}
+\end{equation}
+The variance of the difference is
+and
+
 and
@@
 
-\subsection{Failure of in-sample forecast evaluation}\label{sec:insample}
-This subsection establishes that in-sample tests like the $F$-test can
-overreject when the benchmark is more accurate than the alternative.
-The issue explored here is different than that of \citet{Cal:11c} and
-\citet{Ana:12}; in those papers, the authors demonstrate that full
-sample Wald and $F$-tests can be invalid under increasing-$k$
-asymptotics,%
-\footnote{\citet{Ana:12} shows that the Wald test is
-  invalid in general and gives an adjustment that corrects the
-  critical values; he also shows that the $F$-test is asymptotically
-  valid under certain conditions on the distribution of the
-  regressors.  \citet{Cal:11c} shows that the $F$-test is
-  asymptotically invalid without Anatolyev's constraint, and provides
-  a correction that gives valid tests.  Both papers only consider
-  independent observations.} %
-e.g. they can overreject when testing the
-null hypotheses that a set of the coefficients is zero.  This paper,
-though, looks at the behavior when the coefficients are non-zero but
-the estimated restricted model is more accurate.  In this setting,
-these tests reject the benchmark too often---more than their nominal
-size---and for most coefficient values will reject almost surely in
-the limit.  We also look at some common model selection statistics and
-find the same conclusion---they choose the larger model with high
-probability regardless of which model will forecast better.  To
-simplify the presentation, we'll only present results for nested
-models.
-
-Theorem~\ref{res:ftest} presents results for in-sample hypothesis
-tests.
-\begin{thm}\label{res:ftest}
-  Suppose Assumptions 1--3 hold, that the models are nested, and that
-  $L(e) = e^2$.  Also, let $\Lambda$ be a test statistic with nominal
-  size $\alpha$ that has acceptance region contained in the set
-  \[\{\hat{\theta}_T \mid (\hat{\theta}_T -
-  \theta_0)'V_T(\hat{\theta}_T - \theta_0) < c \}\] for large enough
-  $T$ and some $\theta_0$, $c$, and $V_T$, with $V_T$ a possibly
-  random matrix with all eigenvalues uniformly bounded in probability
-  and rank satisfying $\lim \rank(V_T)/T > 0$.  Then there exist
-  distributions for $(x_t, \e_{t+h})$ such that
+\subsubsection*{Behavior of the F-test}
+
+[no, just assume that the regressors are deterministic]
+
+This example illustrates the problems with in-sample forecast
+evaulation especially well, because we have finite sample
+distributions of the test statistics of interest, the $F$-test, AIC,
+and BIC.
+
+[text]
+
+\begin{equation*}
+  M_2 \bh{2T} \sim
+  N(M_2 \theta_2, \sigma^2/T)
+\end{equation*}
+where $M_2 = (0\ I)$. Given $\E_T \oosB = 0$ as well as the previous
+information set, and the density of $M_2 \bh{2T}$ concentrates
+uniformly on the surface of the sphere centered at $M_2 \theta_2$ and
+passing through the origin:
+\begin{equation*}
+  (M_2 \bh{2T} - M_2 \theta_2)'(M_2 \bh{2T} - M_2 \theta_2) =
+  \theta_2'M_2' M_2 \theta_2.
+\end{equation*}
+We can also represent the null $\E_T \oosB \leq 0$ by conditioning on
+$\E_T \oosB = -c$ for a fixed positive constant $c$. In that case, the
+density of $M_2 \bh{2T}$ concentrates on the sphere
+\begin{equation*}
+  (M_2 \bh{2T} - M_2 \theta_2)'(M_2 \bh{2T} - M_2 \theta_2) =
+  \theta_2'M_2' M_2 \theta_2 + c
+\end{equation*}
+which has the same center but larger radius. What makes both
+distributions relatively easy to work with is that the estimators are
+uniformly distributed on the surface of each sphere.
+For other (stochastic) design matrices, the distribution of $M_2
+\bh{2T}$ is not uniform on the sphere and its location may be
+different, but the same general argument will hold.
+
+For the $F$-test we have, just as in Equation~\eqref{eq:17}
 \begin{equation}
-    \label{eq:11}
-    \Pr[\Lambda \text{ rejects} \mid \E_T \oosB \leq 0] \to^p 1
-    \quad \text{as} \quad
-    \theta'V_T\theta \to^p \infty \quad \text{($T$ is fixed)}
-  \end{equation}
-  for almost every sequence $\theta$ (a.e. with respect to Lebesgue
-  measure) and
-  \begin{equation}
-    \label{eq:15}
-    \plim_{T \to \infty} \Pr[\Lambda \text{ rejects} \mid
-    \E_T \oosB \leq 0] \geq \plim_{T \to \infty} \Pr[c + \delta < (\theta - \theta_0)' V_{T}
-    (\theta - \theta_0) \mid \E_T \bar{D}_T \leq 0]
-  \end{equation}
-  for any $\delta > 0$.
-\end{thm}
-Note that, if $V_T$ is nonstochastic or converges in probability,
-there are distributions on $(x_t, \e_{t+h})$ that are
-compatible with~\eqref{eq:15} such that
-\[\Pr[c + \delta < (\theta - \theta_0)'V_T (\theta - \theta_0) \mid
-E_T \bar{D}_T \leq 0] \to^p 1
-\]
-for any $\theta \neq \theta_0$.  Otherwise, the rejection probability
-will still depend on $\theta$ and $V_T$ and will typically be higher
-than the nominal size of the test.
-
-Theorem~\ref{res:ftest} covers a broad class of test statistics and
-allows the in-sample test to be valid or invalid in finite samples or
-asymptotically.  It implies that a large class of in-sample tests will
-reject if $\theta$ is nonzero, whether or not the alternative model is
-more accurate.  As an example, consider the $F$-test of the null
-hypothesis $A \theta =0$ with deterministic regressors and
-i.i.d. Normal errors where $\rank A = J$ and $\lim J/T > 0$.  Simple
-algebra reveals that the test rejects if $\hat{\theta}_T' V_T
-\hat{\theta}_T \geq 1$ with
-\begin{equation*}
-  V_T = (T/ J \hat{\xi}^{2}) A' (A (T^{-1}X_T'X_T)^{-1} A')^{-1} A;
-\end{equation*}
-$\xi^2$ is the variance of the model's innovations and $\hat{\xi}^2$ is
-the usual estimator based on the squared residuals.  Note that $\rank
-V_T = \rank A$ as long as $X_T'X_T$ is full rank.  Under the null $A
-\theta = 0$,
-\begin{equation*}
-  \hat{\theta}_T' V_T
-  \hat{\theta}_T =^d   (\xi^2/ J \hat{\xi}^2) \chi_J^2 =^d 1 + J^{-1/2} Z
-  + o_p(T^{-1/2}),
-\end{equation*}
-where $\chi_J^2$ is an independent $\chi^2$ random variable with $J$
-degrees of freedom and $Z \sim N(0,1)$.  Consequently, the $F$-test
-accepts whenever $\hat{\theta}_T$ is in a neighborhood of the cylinder
-defined by $\hat{\theta}_T' V_T \hat{\theta}_T = 1$ and rejects for
-$\hat{\theta}_T$ outside the neighborhood.%
-\footnote{If $V_T$ is full
-  rank, this equation defines an ellipsoid in $\mathbb{R}^K$;
-  otherwise the equation defines an ellipsoid in a subspace of
-  $\mathbb{R}^K$.} %
-The neighborhood shrinks as $T \to \infty$, so the
-$F$-test satisfies the conditions of Theorem~\ref{res:ftest} with
-$V_T$ as given above and $c = 1 + \delta$ for any $\delta > 0$.
-Notice that $c$ does not depend on the nominal size of the test and
-that the exact finite sample distribution of the $F$-test is known in
-this example, so the test is valid by conventional measures but the
-conclusions of Theorem~\ref{res:ftest} still hold.
-
-The intuition behind Equation~\eqref{eq:11} can be understood by
-simplifying further to the case $K_2 = 2$ and $K_1 = 0$, deterministic
-orthonormal regressors, and $V_T = I$, so
-\begin{equation*}
-  E_T \oosB = \theta_{1}^2 + \theta_{2}^2 - (\hat{\theta}_{T,1} -
-  \theta_{1})^2 - (\hat\theta_{T,2} - \theta_2)^2.
-\end{equation*}
-Under these conditions, the test rejects if $\hat{\theta}_{T}$ lies
-outside the circle centered at the origin with radius $c^{1/2}$ and
-$\E_T \oosB \leq 0$ holds for $\hat\theta_{T}$ on or outside a circle
-centered at $\theta$ passing through the origin.
-Figure~\ref{fig:rreject} depicts these regions.  Since the OLS
-estimator is normal with mean $\theta$, the probability that
-$\hat{\theta}_{T}$ falls in the acceptance region given $\E_T \oosB
-\leq 0$ vanishes as $\theta'\theta \to \infty$, even though the full
-model will give worse forecasts than the restricted model.
-
-\newcommand{\circlefigA}[4]{
-  \begin{tikzpicture}
-    \fill[lightgray] (-#3,-#3) rectangle (#4,#4);
-    % rejection region for F-test
-    \filldraw[fill=white,draw=black] (0,0) circle (#1);
-    % circle of equal generalization error
-    \filldraw[fill=white,draw=black] (1,1) let \p1=(1,1) in circle({veclen(\x1,\y1)});
-    \draw (1,1) let \p1=(1,1) in circle({veclen(\x1,\y1)});
-    \fill [black] (1,1) circle (2pt) node[right] {$(\theta_1,\theta_2)$};
-    \draw (0,0) circle (#1);
-    \draw (1,1)--(0,0);
-    % axes
-    \draw[->] (0,0)--(#2,0) node[right] {$\hat\theta_{T,1}$};
-    \draw[->] (0,0)--(0,#2) node[above] {$\hat\theta_{T,2}$};
-  \end{tikzpicture}
-}
-\newcommand{\circlefigB}[4]{
-  \begin{tikzpicture}
-    \fill[white] (-#3,-#3) rectangle (#4,#4);
-    % rejection region for F-test
-    \fill[lightgray] (0,0) circle (#1);
-    % circle of equal generalization error
-    \fill[white] (1,1) let \p1=(1,1) in circle({veclen(\x1,\y1)});
-    \draw (0,0) circle (#1);
-    \draw (1,1) let \p1=(1,1) in circle({veclen(\x1,\y1)});
-    \fill [black] (1,1) circle (2pt) node[right] {$(\theta_1,\theta_2)$};
-    \draw (1,1)--(0,0);
-    % axes
-    \draw[->] (0,0)--(#2,0) node[right] {$\hat\theta_{T,1}$};
-    \draw[->] (0,0)--(0,#2) node[above] {$\hat\theta_{T,2}$};
-  \end{tikzpicture}
-}
-
-\begin{figure}
-  \centering
-  \begin{tabular}{cc}
-  \subfloat[]{\circlefigA{1}{2.5}{1.4}{3.2}\label{fig:circleA}} &
-  \subfloat[]{\circlefigB{1}{2.5}{1.4}{3.2}\label{fig:circleB}}  \\
-  \subfloat[]{\circlefigA{.3}{2.5}{1.4}{3.2}\label{fig:circleC}}  &
-  \subfloat[]{\circlefigB{.3}{2.5}{1.4}{3.2}\label{fig:circleD}}
-  \end{tabular}
-  \caption{Graphs indicating the rejection region and region of equal
-    generalization error for the models discussed in Section
-    \ref{sec:insample}.  The smaller model has no estimated parameters
-    and the larger has two coefficients.  The shaded regions in
-    Figures (a) and (b) show the rejection region and the acceptance
-    region respectively of the full-sample test given $\E_T \oosB \leq
-    0$ when the true elements of $\theta$ are moderately small.  Figures
-    (c) and (d) show the same regions when the true $\theta$ is large.}
-\label{fig:rreject}
-\end{figure}
-
-Equation~\eqref{eq:15} is more interesting and implies that these
-tests will almost surely reject the benchmark whenever we have a true
-but overfit and less accurate alternative.  The intuition is similar
-to the previous case.  As $K_2$ increases, the volume that
-$\hat{\theta}_{T}$ can occupy increases as well.  If $\theta$ is
-outside the acceptance region, the probability that $\hat{\theta}_{T}$
-is close to the origin and therefore inside the acceptance region of
-the test decreases.  In the limit, the probability that
-$\hat{\theta}_{T}$ is outside the acceptance region is one.
-
-A similar result for model selection follows as a Corollary to
-Theorem~\ref{res:ftest}.  Consistent model selection in this context
-is different than in the finite-$K$ case.  Here we want the
-probability of selecting a model given that it is more accurate to
-converge to one.  Formally, a model selection procedure is useful if
-\begin{gather}\label{eq:13}
-  \Pr[\text{model $1$ selected} \mid \E_T \oosB \leq 0] \to 1
-  \intertext{and} \Pr[\text{model $2$ selected} \mid \E_T \oosB > 0]
-  \to 1.\label{eq:14}
-\end{gather}
-Note that the conditioning event in~\eqref{eq:14} is different than in
-the testing results presented earlier, but otherwise they are similar.
-Theorem~\ref{res:ftest} implies that~\eqref{eq:13} will typically fail
-for overfit models for many common model selection methods, including
-adjusted $R^2$, the AIC, and the BIC.  Corollary~\ref{res:ic}
-contains the details.
-
-\begin{cor}\label{res:ic}
-  Suppose the conditions of Theorem~\ref{res:ftest} hold but that the
-  statistic $\Lambda'$ is used for model selection; $\Lambda'$ selects
-  the benchmark model for all $\hat{\theta}_T$ contained in a subset
-  of the region
-  \begin{equation*}
-    \{\hat{\theta}_T \mid \hat{\theta}_T'V_T \hat{\theta}_T < c\}
-  \end{equation*}
-  and selects the alternative for all $\hat{\theta}_T$ outside that
-  region.  Then there exist distributions on $x_t,\e_t$ such
-  that
-  \begin{equation}
-    \label{eq:17}
-    \plim \Pr[\Lambda' \text{ selects model 1} \mid \E_T \bar{D}_T \leq 0]
-    \leq \plim \Pr[\theta_0'V_T \theta_0 < c \mid \E_T \bar{D}_T].
-  \end{equation}
-\end{cor}
-As before, we often have
-\begin{equation*}
-  \Pr[\theta_0'V_T \theta_0 < c \mid \E_T \bar{D}_T] \to^p 0.
-\end{equation*}
-Just as we saw with the $F$-test, adjusted $R$-squared, the AIC and
-the BIC will only choose the benchmark model if $\hat{\theta}_T$
-lies in the neighborhood of the cylinder defined by $\hat{\theta}_T
-V_{T} \hat{\theta}_T = c$, regardless of which model is expected to
-forecast better.  These statistics differ in how they determine the
-size of the neighborhood, with the neighborhood shrinking slower for
-the BIC than the AIC.
-
-It is important to remember that the tests considered do not need to
-have correct size for the null $\theta = \theta_0$, but are allowed to
-in this analysis, so previous research, such as \citet{Cal:11c} and
-\citet{Ana:12}, does not predict these results.  However, these tests
-are poorly suited for choosing an accurate forecasting model and
-perform worse when the larger model is overfit or explains more of the
-variation of the dependent variable.  Essentially, for forecasting we
-want to know if the coefficient estimates are close to their true
-values, but in-sample statistics tell us only whether the estimates
-are close to a particular hypothesized value (usually zero).  There
-are lots of estimates that are both far from zero and far from their
-true values which cause in-sample statistics to incorrectly choose the
-alternative model.
-
-\section{Monte Carlo}\label{sec:mc}
-\newcommand{\thetanorm}{\ensuremath{\lvert \theta \rvert_2}} This
-section presents two simulations that investigate the accuracy of our
-theory in small samples.\footnote{Simulations were conducted in R
-  \citep{Rde:10} using Sweave \citep{Lei:02} and the Lattice
-  \citep{Sar:10}, RSQLite \citep{Jam:10}, tikzDevice
-  \citep{ShB:11:0.6.1}, and pgfSweave \citep{BrS:11:1.2.1} packages.}
+  F = \tfrac{T}{s^2 (K_2 - K_1)} \bh{2T}' M_2' M_2 \bh{2T}.
+\end{equation}
+We know that $\sqrt{T}(F - 1)$ is asymptotically normal
+\citep{Cal:11c} so the test accepts if
+\begin{equation}\label{eq:26}
+  \tfrac{T}{s^2 (K_2 - K_1)} \bh{2T}' M_2' M_2 \bh{2T}
+  \leq 1 + \delta / \sqrt{T},
+\end{equation}
+where $\delta$ is chosen to determine the size of the test. In other
+words, the test accepts if $M_2 \bh{2T}$ falls in the sphere centered
+at the origin with radius $s ((K_2 - K_1) / T)^{1/2} +
+O_p(1/\sqrt{T})$.
+
+So if the unknown coeficients satisfy
+\begin{equation*}
+\theta_2'M_2'M_2\theta_2 > \var(\e_t)^{1/2} ((K_2 - K_1) / T)^{1/2}
+\end{equation*}
+for large enough $T$, then the probability of rejecting the null
+hypothesis when it is at least as accurate as the altenative is
+equivalent to the probability that $\bh{2T}$ violates~\eqref{eq:26}
+given that it is uniformly distributed on the sphere
+\begin{equation*}
+  (M_2 \bh{2T} - M_2 \theta_2)'(M_2 \bh{2T} - M_2 \theta_2) =
+  \theta_2'M_2' M_2 \theta_2 + c
+\end{equation*}
+for some positive $c$. Each individual element of $M_2 \bh{2T}$
+independently has probability less than $1/2$ of falling in the
+acceptance region, so the probability that at least one doesn't (all
+that is needed for rejection) is bounded (for large enough $T$)
+\begin{equation*}
+  1 - (1/2)^{K_2 - K_1}
+\end{equation*}
+which obviously converges to 1 as $K_2 - K_1 \to \infty$. The same
+bound also holds under the alternative $\E_T \oosB > 0$, so the
+$F$-test rejects with probability approaching 1 for these values of
+$\theta_2$, regardless of which model is more accurate.
+
+\section{Monte Carlo}
+\label{sec:mc}
+
+This section presents two simulations that investigate the accuracy of
+our theory in small samples.%
+\footnote{Simulations were conducted in R \citep{Rde:10} using the
+  MASS \citep{VeR:02}, Matrix \citep{BM:13}, rlecuyer \citep{SR:12},
+  and RSQLite \citep{Jam:10} packages. Graphs were produced in R using
+  Lattice \citep{Sar:10} and tikzDevice \citep{ShB:11:0.6.1} as well
+  as the TikZ and PGF LaTeX packages \citep{Tan:10}} %
 The first looks at the asymptotic normality of the DMW statistic
@@
 
-\subsection{Setup}\label{sec:simulation-design}
+\subsection{Setup}
+\label{sec:simulation-design}
+
 The Monte Carlo experiment is intentionally very simple so that we can
@@
 statistic rejects.
+
 \subsection{Results}
+
 We discuss results for the confidence intervals first.
@@
 power when it is not satisfied.
-\section{Empirical exercise}\label{sec:empirics}
+
+\section{Empirical analysis of equity premium predictability}
+\label{sec:empirics}
+
 This section presents an analysis of equity premium predictability
 similar to \citet{GoW:08}.%
-\footnote{All of the calculations in this
-  section are done in R \citep{Rde:10}.  We also use code provided by
-  \citet{Zeh:02}, \citet{Zei:04}, \citet{Har:10}, and
-  \citet{ShB:11:0.6.1}.} %
+\footnote{Calculations in this section are done in R \citep{Rde:10}
+  using the lmtest \citep{ZeH:02} and sandwich \citep{Zei:04}
+  packages. Tables and grapsh were prepared with the Hmsic
+  \citep{Har:10} and tikzDevice \citep{ShB:11:0.6.1} R packages as
+  well as the TikZ and PGF LaTeX packages \citep{Tan:10}} %
 We estimate the expected forecasting
@@
 mitigate the effect of persistence as well.
-\section{Conclusion}\label{sec:conclusion}
+
+\section{Conclusion}
+\label{sec:conclusion}
+
 This paper gives a theoretical motivation for using OOS comparisons:
@@
 absolutely regular sequences, Berbee's Lemma \citep{Ber:79}.  Many of
-the results of this paper (Lemmas \ref{res-mixingale} and
-\ref{res-variance-estimator}) are modifications of existing results
+the results of this paper (Lemma \ref{res-mixingale} and
+Theorem~\ref{res-oost}) use modifications of existing results
 for NED functions of mixing processes by \citet{Jon:97} and
@@
 dimension.  Similar results for strong mixing sequences depend on the
-dimension of $Y$, which makes them unsuitable for our applications.
+dimension of $Y$, which makes them unsuitable for this paper.
 
@@
     \sum_{i=1}^{\lfloor P/b_T \rfloor} (\E_R Z_i^2 - \E_{R+(i-1) b_T}
-    Z_i^2) \to^p 0.
-  \end{equation}
-  If Assumptions~\ref{asmp-4} and \ref{asmp-5} also hold and we define
-  \begin{gather*}
-    Z_{1t} = \varianceTermIIIa, \intertext{and} Z_{2t} =
-    \varianceTermIVb,
-  \end{gather*}
-  with $\delta > 0$, $\eta_\delta$ defined in the proof of
-  Lemma~\ref{res-variance-estimator}, and $\gamma_T = b_T/\delta$, then
+    Z_i^2) \to^p 0 \quad\text{ as } P \to \infty.
+  \end{equation}
+
+  If the assumptions of Theorem~\ref{res-oost} also hold, $b_T$ is
+  restricted further so that $b_T \equiv \lfloor \gamma/\delta
+  \rfloor$ for some positive scalar $\delta$, and we define
+  \begin{equation}\label{eq:13}
+    \kernelB{x} \equiv \kernelBDefn{x},
+  \end{equation}
+  then
   \begin{equation}
@@
   \end{equation}
+  where
+  \begin{gather}
+    Z_{1t} = \varianceTermIIIa,%
+    \intertext{and}%
+    Z_{2t} = \varianceTermIVb.
+  \end{gather}
 \end{lem}
@@
 
-%\newcommand{\DD}[2][{}]{(D_{#2}^{#1} - \E_R D_{#2}^{#1})}
-%\newcommand{\ovg}[1]{\tfrac{1}{P} \sum_{#1=R+1}^{T-h}}
-
 \begin{lem}\label{lem:a6}
-  Suppose the conditions of Lemma~\ref{res-variance-estimator} hold.
+  Suppose the conditions of Theorem~\ref{res-oost} hold.
   Then
@@
 We'll prove that these two sums are $o_p(1)$; uniform integrability
-then implies convergence in $L_1$.  The arguments are $o_p(1)$ are
-almost identical, so we'll only present the first.
+then implies convergence in $L_1$.  The arguments for each are almost
+identical, so we'll only present the first.
 
@@
 \end{align*}
-with the second term vanishing by Lemma \ref{res-mixingale} and
+with the second term $o_p(1)$ by Lemma \ref{res-mixingale} and
 \citepos{Dav:93} mixingale LLN.
@@
 
-\subsection*{Proof of Theorem \ref{res-confidence-intervals}}
-
-It suffices to prove asymptotic normality.  We can rewrite the
-centered OOS average as
+\subsection*{Proof of Lemma \ref{res-mixingale}}
+We will start by proving that $\{D_t - \E_R D_t, \Fs_t\}$ is an
+$L_2$-mixingale of size $-1/2$; $D_t$ is $\Fs_t$-measurable and so it
+suffices to prove that
+\begin{equation}\label{eq:24}
+  \| \E_{t-l} D_t  - \E_R D_t \|_2 \leq 2^{2 + 1/\rho} B_L \, \couplingBeta{l}
+\end{equation}
+for $l = 1,\dots,t-R$, since $\couplingBeta{l} = O(l^{-1/2 - \delta})$
+for some $\delta > 0$ by assumption. Fix $R$, $t$ and $l$ and use
+Lemma \ref{lem-basic-coupling} to define $D_t^*$ so that
 \[
-\frac{\bar{D}_{R} - \E_T \bar{D}_T}{\sh / \sqrt{P}} =
-\frac{1}{\sh \sqrt{P}}\oosSum{t}{1} (D_t - \E_R D_t) +
-\frac{\sqrt{P}}{\sh} (\E_R\oosA - \E_T\oosB).
+\E_R D_t^* = \E_{t-l} D_t^* \quad a.s.
 \]
-Lemmas \ref{res-mixingale} and
-\ref{res-convergence} ensure that the first term is asymptotically
-normal and the second term vanishes.\qed
-
-\subsection*{Proof of Theorem \ref{res:oostest}}
-By Lemma~\ref{res-convergence}, we know that
-\begin{equation*}
-  \Pr[\E_R \oosA \leq 0] - \Pr[\E_T \oosB \leq 0] \to 0
-\end{equation*}
 and
-\begin{equation*}
-  \Pr[P^{1/2} \oosA / \sh > z_\alpha \text{ and } \E_R \oosA \leq 0]
-  - \Pr[P^{1/2} \oosA / \sh > z_\alpha \text{ and }
-  \E_T \oosB \leq 0] \to 0.
-\end{equation*}
-For large enough $T$, both $\Pr[\E_R \oosA \leq 0]$ and $\Pr[\E_T
-\oosB \leq 0]$ are positive, so
-\begin{equation*}
-  \Pr[P^{1/2} \oosA / \sh > z_\alpha
-  \mid \E_R \oosA \leq 0] =
-  \frac{\Pr[P^{1/2} \oosA / \sh > z_\alpha \text{ and }
-    \E_R \oosA \leq 0]}{\Pr[\E_R \oosA \leq 0]}
+\[
+\lVert D_t - D_t^* \rVert_2 \leq \couplingBound{l}.
+\]
+Then
+\begin{align*}
+\lVert \E_{t-l} D_t - \E_R D_t \rVert_2 & \leq
+\lVert \E_{t-l} D_t - \E_{t-l} D_t^* \rVert_2  + \lVert \E_{t-l} D_t^* - \E_R D_t \rVert_2 \\
+&\leq 2 \lVert D_t - D_t^* \rVert_2 \\
+&\leq 2^{2 + 1/\rho}\ B_L\ \couplingBeta{l}.\tag*{\qed}
+\end{align*}
+
+\noindent Asymptotic normality follows from~\eqref{eq:24} using a
+modification of \citepos{Jon:97} CLTs for mixingale and NED arrays.
+Define
+\[\label{eq:z1}
+  Z_i = \ZDef
+\]
+where $b_T$ is a sequence that satisfies $b_T\leq P$,
+$b_T\to\infty$, and $b_T/P\to 0$.  The same arguments used in
+\citepos{Jon:97} Theorem 1 show that
+\begin{equation*}
+   \SumOuterBlock{i} Z_i = P^{-1/2} \oosSum{s}{1} (D_t - \E_R D_t) + o_p(1).
 \end{equation*}
@@
 \begin{equation*}
-  \Pr[P^{1/2} \oosA / \sh > z_\alpha
-  \mid \E_T \oosB \leq 0] =
-  \frac{\Pr[P^{1/2} \oosA / \sh > z_\alpha \text{ and }
-    \E_T \oosB \leq 0]}{\Pr[\E_T \oosB \leq 0]}
-\end{equation*}
-almost surely and consequently
-\begin{equation*}
-  \Pr[P^{1/2} \oosA / \sh > z_\alpha
-  \mid \E_T \oosB \leq 0]
-  - \Pr[P^{1/2} \oosA / \sh > z_\alpha
-  \mid \E_R \oosA \leq 0] \to^p 0.
-\end{equation*}
-Finally,
-\begin{align*}
-  \Pr[P^{1/2} \oosA / \sh > z_\alpha \mid \E_R \oosA \leq 0]
-  &\leq \Pr[P^{1/2} (\oosA - \E_R \oosA) / \sh > z_\alpha
-  \mid \E_R \oosA \leq 0] \\
-  &= \E( \Pr[P^{1/2} (\oosA - \E_R \oosA) / \sh > z_\alpha
-  \mid \mathcal{F}_R] \mid \E_R \oosA \leq 0) \\
-  &= \E(\alpha \mid \E_R \oosA \leq 0) \\
-  &= \alpha
-\end{align*}
-where the second equality holds by Lemma~\ref{res-mixingale} and
-Theorem~\ref{res-variance-estimator}, completing the proof.
-\qed
+  \SumOuterBlock{i} Z_i = \SumOuterBlock{i} (Z_i - E_{R + (i-1)b_T}
+  Z_i) + o_p(1).
+\end{equation*}
+Note that $\{Z_i - E_{R + (i-1)b_T} Z_i,\mathcal{F}_{R + i b_T}\}_i$ is an
+MDS by construction, so \citepos{HaH:80} Theorem 3.2 and Corollary
+3.1 ensure that $\sigma^{-1} \SumOuterBlock{i} Z_i \to^d N(0,1) $ as
+long as
+\begin{equation}\label{eq:cltvar2}
+  \sigma^2 - \SumOuterBlock{i} \E_R Z_i^2 \to^p 0,
+\end{equation}
+and
+\begin{equation}\label{eq:cltvar1}
+  \SumOuterBlock{i} \E_R Z_i^2 - \SumOuterBlock{i} \ZSqCE \to^p 0.%
+\footnote{Note that $\sigma^2 \in \mathcal{F}_t$ for
+    all $t \geq R$, so Hall and Heyde's condition (3.21) is
+    unnecessary---see the remarks after their result.} %
+\end{equation}
+Equation (\ref{eq:cltvar2}) holds as in \citet{Jon:97} (see the proof
+of his Theorem 2); (\ref{eq:cltvar1}) is ensured by
+Lemma~\ref{lem:a2}. \qed
 
@@
     x_{#1}^{*\prime}\bh{#1R}) - L(y^{*} - x_{#1}^{*\prime}\bh{#1T})}}
+
+For the second part:
+\begin{quotation}
+  Notice that, if the observations are i.i.d. and $(y_{t+h}, x_{it})
+  \sim N(0,I)$, $(\hat{\theta}_{iR} - \hat{\theta}_{iT}) \sim N(0,
+  (X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1})$ given $X_{iT}$, and so
+  $\var(x_{i,T+1}'\hat{\theta}_{iR} - x_{i,T+1}' \hat{\theta}_{iT})
+  \gg P K_i / (R - K_2)(T - K_2)$.
+\end{quotation}
 
@@
 and this last term is $o(P^{-1/2})$ by assumption.
-
 Essentially the same argument proves~\eqref{eq:19} as well.
@@
 \begin{proof}[Proof of~\eqref{eq:20}]
-Observe that
+Assumption~\ref{asmp-3} and the definition of the OLS estimator
+ensure that
 \begin{align*}
-  \|L(y^{*} -  x_i^{*\prime} \hat{\theta}_{iR}) -
-  L(y^{*} - x_i^{*\prime} \hat{\theta}_{iT}) \|_1
-  &\leq B_{L} \| x_i^{*\prime} (\hat{\theta}_{iR} - \hat{\theta}_{iT}) \|_2 \\
+  \|L(y^{*} -  x_i^{*\prime} \bh{iR}) - L(y^{*} - x_i^{*\prime} \bh{iT}) \|_1
+  &\leq B_{L} \| x_i^{*\prime} (\bh{iR} - \bh{iT}) \|_2 \\
   &\leq B_{L} \, \| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
-  (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2 \\
+  (X_{iR}'X_{iR})^{-1}] X_{iR}' \eb_{iR} \|_2 \\
   &\quad+ B_L \, \| x_i^{*\prime}
-  (X_{iR}'X_{iR})^{-1}[X_{iT}'\eb_{iT} - X_{iR}
+  (X_{iT}'X_{iT})^{-1}[X_{iT}'\eb_{iT} - X_{iR}
   \eb_{iR} ] \|_2 .
 \end{align*}
-The first term in the upper bound\,---\,$\| x_i^{*\prime}
-[(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2$\,---\,satisfies
-\begin{align*}
-  \| x_i^{*\prime} &[(X_{iT}'X_{iT})^{-1} -
-  (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2^2 =\\
-  &= \E \tr\big( x_i^* x_i^{*\prime}
-   [(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}] X_{iT}'\eb_{iT} \eb_{iT}X_{iT}
-   [(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}] \big) \\ \label{eq:8}
-  \begin{split}&\leq
-    \eigen_{K_i}(\E x_i x_i')
-    \, \| \eigen_{K_i}(\E(X_{iT}' \eb_{iT} \eb_{iT}' X_{iT} \mid
-    X_{iR}'X_{iR}, X_{iT}'X_{iT})) \|_3 \\
-    & \quad \times \Big\|\sum_{j=1}^{K_i}
-    \eigen_j^2((X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}) \Big\|_{3/2}
-  \end{split} \\
-  &= O(T) \Big\|\sum_{j=1}^{K_i}
-    \eigen_j^2((X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}) \Big\|_{3/2}
-\end{align*}
-with the second to last inequality a consequence of Holder's
-inequality and the last bound holding by Assumption~\ref{asmp-2}.
-
-Now, $(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}$ has rank $P$ and
+
+Define $V = (X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}$ and $W =
+X_{iR}'\eb_{iR} \eb_{iR}X_{iR}$. The first term in the upper bound
+satisfies
+\begin{align}
+  \| x_i^{*\prime} V X_{iR}' \eb_{iR} \|_2^2
+  &= O(1) \cdot \E \tr\big( V^2 W \big) \\
+  \label{eq:14}
+  &= O(1) \big( \E \tr\{ V^2 \E(W \mid X_{iR}'X_{iR})\}
+  + \E \tr\{ V^2 (W - \E(W \mid X_{iR}'X_{iR}))\}\big)
+\end{align}
+since $\eigen_{K_i}(\E x_i x_i') = O(1)$ by assumption.
+
+To show that the first term in~\eqref{eq:14} converges to zero at the
+right rate, observe that
+\begin{equation}
+  \E \tr\{ V^2 \E(W \mid X_{iR}'X_{iR})\}
+  \leq \bigg\rVert
+  \eigen_{K_i}(\E(W \mid X_{iR}'X_{iR})) \bigg\rVert_3
+  \bigg\rVert \sum_{i=1}^{K_i} \eigen_i^2 \big(V\big) \bigg\rVert_{3/2}.
+\end{equation}
+The first term in this product is $O(R)$ by
+Assumption~\ref{asmp-2}. For the second term, observe that
+$(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}$ has rank $P$ and
 each of its nonzero eigenvalues are bounded in absolute value by the
@@
 $(X_{iR}'X_{iR})^{-1}$ are $O_{L_3}(1/R)$ by Assumption~\ref{asmp-2}, so
+\begin{equation*}
+  \Big\|\sum_{j=1}^{K_i}
+  \eigen_j^2(V)\Big\|_{3/2}
+  \leq \Big\|\sum_{j=K_i - P+1}^{K_i} \eigen_j^2(V) \Big\|_{3/2}
+  = O(P/R^2)
+\end{equation*}
+and, consequently,
+\begin{equation*}
+  \E \tr\bigg\{
+  [(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}]^2
+  \E(X_{iR}'\eb_{iR} \eb_{iR}X_{iR} \mid X_{iR}'X_{iR})\bigg\} = O(P/R).
+\end{equation*}
+
+For the second term in~\eqref{eq:14}, define for each $s=\h+1,\dots,R$,
+\begin{equation*}
+  w_{is} = x_{i,s-\h} x_{i,s-\h}' \e_{i,s}^2 + \1\{s > \h+1\}
+  \sum_{t=\h+1}^{s-1} (x_{i,s-\h} x_{i,t-\h}' + x_{i,t-\h} x_{i,s-\h}')
+  \e_{i,s} \e_{i,t}
+\end{equation*}
+and observe that $W = \sum_{s=\h+1}^{R} w_{is}$. Now use
+Lemma~\ref{lem-berbee} to define new random variables $w_{is}^*$ for
+each $s$ that are independent of $\sigma(x_{R+1},\dots,x_{T-\h})$ and
+satisfy
+\begin{equation*}
+  \Pr[w_{is} \neq w_{is}^*] \leq \beta_{R -\h + 1- s}.
+\end{equation*}
+By construction,
+\begin{equation*}
+  \E\bigg(\sum_{t=\h+1}^R w_{it}^*\ \big|\ X_{iR}'X_{iR}, X_{iT}'X_{iT}\bigg)
+  =  \E\bigg(\sum_{t=\h+1}^R w_{it}^*\ \big|\ X_{iR}'X_{iR}\bigg) \quad\text{a.s.}
+\end{equation*}
+and we can rewrite the second term in~\eqref{eq:14} as
 \begin{align*}
-  \Big\|\sum_{j=1}^{K_i}
-  \eigen_j^2\big((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}\big)\Big\|_{3/2}
-  &\leq \Big\|\sum_{j=K_i - P+1}^{K_i}
-  \eigen_j^2\big((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}\big) \Big\|_{3/2} \\
-  &= O(P/R^2),
+  \E \tr&\{ V^2 (W - \E(W \mid X_{iR}'X_{iR}))\}\big) \\
+  &= \E \tr\bigg\{V^2 \sum_{t=\h+1}^R \big(\E(w_{it} - w_{it}^* \mid
+  X_{iR}'X_{iR}, X_{iT}'X_{iT}) - \E(w_{it} - w_{it}^* \mid
+  X_{iR}'X_{iR})\big) \Bigg\} \\
+  &= \E \sum_{t=\h+1}^R \big(\tr\{V^2 (w_{it} - w_{it}^*)\}
+  - \E(\tr\{\E(V^2 \mid X_{iR}'X_{iR}) (w_{it} - w_{it}^*)\} \mid
+  X_{iR}'X_{iR}) \big) \\
+  &= \E \sum_{t=\h+1}^R \big(\tr\{(w_{it} - w_{it}^*)
+  (V^2 - \E(V^2 \mid X_{iR}'X_{iR})\} \big)
 \end{align*}
-proving that
-\begin{equation*}
-  \| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
-  (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2 = O(\sqrt{P/R}).
-\end{equation*}
+where these results come from repeated use of the LIE along with
+linearity of the trace and expectation operators. By construction,
+\begin{equation*}
+  \Pr\big[\tr\{w_{it} (V^2 - \E(V^2 \mid X_{iR}'X_{iR}))\}
+  \neq \tr\{w_{it}^* (V^2 - \E(V^2 \mid X_{iR}'X_{iR}))\}\big]
+  \leq  \beta_{R -\h + 1- s}.
+\end{equation*}
+
+[NEED TO FINISH HERE]
 
@@
 
-\subsection*{Proof of Lemma \ref{res-mixingale}}
-\noindent \textit{Part 1.} Fix $R$, $j$ and $l$ and use Lemma
-\ref{lem-basic-coupling} to define $D_{R+j}^*$ so that
-\[\E_RD_{R+j}^* = \E_{R+j-l} D_{R+j}^* \quad a.s. \]
-and
-\[\lVert D_{R+j} - D_{R+j}^* \rVert_2 \leq \couplingBound{l}.\]
-Then
-\begin{align*}
-\lVert \E_{R+j-l} D_{R+j} - \E_R D_{R+j} \rVert_2 & \leq
-\lVert \E_{R+j-l} D_{R+j} - \E_{R+j-l} D_{R+j}^* \rVert_2 \\
-&\quad + \lVert
-\E_{R+j-l} D_{R+j}^* - \E_R D_{R+j} \rVert_2 \\
-&\leq 2 \lVert D_{R+j} - D_{R+j}^* \rVert_2 \\
-&\leq 2^{2 + 1/\rho}\ B_L\ \couplingBeta{l}.
-\end{align*}
-Now $\couplingBeta{l} = O(l^{-1/2 - \delta})$ for some
-positive $\delta$, completing the proof.\qed
-
-\vspace{\baselineskip}
-\noindent\textit{Part 2.}  A modification of \citepos{Jon:97} CLTs for
-mixingale and NED arrays will complete the proof.  Define
-\[\label{eq:z1}
-  Z_i = \ZDef
+\subsection*{Proof of Theorem \ref{res-oost}}
+We can rewrite the centered \oost\ statistic as
+\[
+\sqrt{P}(\oosA - \E_T \oosB)/\sh
+= \frac{\sigma}{\sh}\, \Big( \sqrt{P}(\oosA - \E_R \oosA)/\sigma
++ \sqrt{P}(\E_R \oosA - \E_T \oosB)/\sigma \Big)
 \]
-where $b_T$ is a sequence that satisfies $b_T\leq P$,
-$b_T\to\infty$, and $b_T/P\to 0$.  The same arguments used in
-\citepos{Jon:97} Theorem 1 show that
-\begin{equation*}
-   \SumOuterBlock{i} Z_i = P^{-1/2} \oosSum{s}{1} (D_t - \E_R D_t) + o_p(1).
-\end{equation*}
-and
-\begin{equation*}
-  \SumOuterBlock{i} Z_i = \SumOuterBlock{i} (Z_i - E_{R + (i-1)b_T}
-  Z_i) + o_p(1).
-\end{equation*}
-Note that $\{Z_i - E_{R + (i-1)b_T} Z_i,\mathcal{F}_{R + i b_T}\}_i$ is an
-MDS by construction, so \citepos{HaH:80} Theorem 3.2 and Corollary
-3.1 ensure that $\sigma^{-1} \SumOuterBlock{i} Z_i \to^d N(0,1) $ as
-long as
-\begin{equation}\label{eq:cltvar2}
-  \sigma^2 - \SumOuterBlock{i} \E_R Z_i^2 \to^p 0,
-\end{equation}
-and
-\begin{equation}\label{eq:cltvar1}
-  \SumOuterBlock{i} \E_R Z_i^2 - \SumOuterBlock{i} \ZSqCE \to^p 0.%
-\footnote{Note that $\sigma^2 \in \mathcal{F}_t$ for
-    all $t \geq R$, so Hall and Heyde's condition (3.21) is
-    unnecessary---see the remarks after their result.} %
-\end{equation}
-Equation (\ref{eq:cltvar2}) holds as in \citet{Jon:97} (see the proof
-of his Theorem 2); (\ref{eq:cltvar1}) is ensured by
-Lemma~\ref{lem:a2}. \qed
-
-\subsection*{Proof of Lemma \ref{res-variance-estimator}}
-The proof follows \citepos{JoD:00} Theorem 2.1 closely.  We
-start by defining similar quantities to theirs, borrowing their
-notation when possible to make the similarities apparent.  For
-positive $\delta$, define $b_T \equiv \lfloor \gamma/\delta \rfloor$,
-$\kernelB{x} \equiv \kernelBDefn{x}$, and
+so Lemma \ref{res-mixingale} and \ref{res-convergence} ensure that
+this term is asymptotically standard normal as long as $\sigma/\sh
+\to^p 1$. Since $\sigma$ is almost surely positive, this convergence
+is equivalent to $\sigma^2 - \sh^2 \to^p 0$.
+
+The proof that $\sigma^2 - \sh^2 \to^p 0$ follows \citepos{JoD:00}
+Theorem 2.1 closely.  We start by defining similar quantities to
+theirs, borrowing their notation when possible to make the
+similarities apparent. Let $b_T \equiv \lfloor \gamma/\delta \rfloor$,
+define $\kernelB{x}$ as in \eqref{eq:13}, and define the following
+terms as in \citet{JoD:00}:
 \begin{align*}
@@
   \varianceTermIIa\\& \quad \times \varianceTermIIb,\\
-  \varianceTermIII &\equiv \vtSum \varianceTermIIIa\\
+  \varianceTermIII &\equiv \vtSum \varianceTermIIIa\\\displaybreak
   &\quad \times \varianceTermIIb,\\
   \varianceTermIV &\equiv \vtSum \varianceTermIIIa \\
-  &\quad\times \varianceTermIVb,
+  &\quad\times \varianceTermIVb.
 \end{align*}
-giving us the inequalities
+These definitions give the inequalities
 \begin{align*}
@@
 functions of mixing processes are also mixingale processes and do not
-use any other properties specific to NED processes, so they hold
-here as well.  We do need to modify their proofs that
-\begin{equation}
-  \label{eq:4} \lVert \sh^2 - \varianceTermI \rVert_1 \to 0
+use any other properties specific to NED processes, so their results
+hold here as well.  We do need to modify their proofs that
+\begin{equation}\label{eq:5}
+  \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1 \to 0
 \end{equation}
 and
-\begin{equation}
-  \label{eq:5} \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1
-  \to 0 \quad \text{for all positive $\delta$},
-\end{equation}
-though, since their proofs exploit NED properties.  The proofs
-follow from Lemmas~\ref{lem:a2} and~\ref{lem:a6}, since
-\begin{equation*}
-  \varianceTermIV - \E_R \varianceTermIV = \vtSum (Z_{1t}Z_{2t} - \E_R Z_{1t}Z_{2t});
-\end{equation*}
-$Z_{1t}$ and $Z_{2t}$ are defined in Lemma~\ref{lem:a2}.
+\begin{equation}\label{eq:4}
+  \lVert \sh^2 - \varianceTermI \rVert_1 \to 0
+\end{equation}
+for all positive $\delta$, though, since those proofs exploit NED
+properties. These results are presented as Lemmas~\ref{lem:a2}
+and~\ref{lem:a6} respectively.  \qed
+
+\subsection*{Proof of Theorem \ref{res:oostest}}
+Coverage of the confidence intervals is immediate from
+Theorem~\ref{res-oost}, so we will present a proof of~\eqref{eq:23}.
+By Lemma~\ref{res-convergence}, we know that
+\begin{equation*}
+  \Pr[\E_R \oosA \leq 0] - \Pr[\E_T \oosB \leq 0] \to 0
+\end{equation*}
+and
+\begin{equation*}
+  \Pr[P^{1/2} \oosA / \sh > z_\alpha \text{ and } \E_R \oosA \leq 0]
+  - \Pr[P^{1/2} \oosA / \sh > z_\alpha \text{ and }
+  \E_T \oosB \leq 0] \to 0.
+\end{equation*}
+For large enough $T$, both $\Pr[\E_R \oosA \leq 0]$ and $\Pr[\E_T
+\oosB \leq 0]$ are positive, so
+\begin{equation*}
+  \Pr[P^{1/2} \oosA / \sh > z_\alpha
+  \mid \E_R \oosA \leq 0] =
+  \frac{\Pr[P^{1/2} \oosA / \sh > z_\alpha \text{ and }
+    \E_R \oosA \leq 0]}{\Pr[\E_R \oosA \leq 0]}
+\end{equation*}
+and
+\begin{equation*}
+  \Pr[P^{1/2} \oosA / \sh > z_\alpha
+  \mid \E_T \oosB \leq 0] =
+  \frac{\Pr[P^{1/2} \oosA / \sh > z_\alpha \text{ and }
+    \E_T \oosB \leq 0]}{\Pr[\E_T \oosB \leq 0]}
+\end{equation*}
+almost surely and consequently
+\begin{equation*}
+  \Pr[P^{1/2} \oosA / \sh > z_\alpha
+  \mid \E_T \oosB \leq 0]
+  - \Pr[P^{1/2} \oosA / \sh > z_\alpha
+  \mid \E_R \oosA \leq 0] \to^p 0.
+\end{equation*}
+Finally,
+\begin{align*}
+  \Pr[P^{1/2} \oosA / \sh > z_\alpha \mid \E_R \oosA \leq 0]
+  &\leq \Pr[P^{1/2} (\oosA - \E_R \oosA) / \sh > z_\alpha
+  \mid \E_R \oosA \leq 0] \\
+  &= \E( \Pr[P^{1/2} (\oosA - \E_R \oosA) / \sh > z_\alpha
+  \mid \mathcal{F}_R] \mid \E_R \oosA \leq 0) \\
+  &= \E(\alpha \mid \E_R \oosA \leq 0) \\
+  &= \alpha
+\end{align*}
+completing the proof.
 \qed
 
-\subsection*{Proof of Theorem~\ref{res:ftest}}
-
-\textit{Equation~\eqref{eq:11}}: Note that a necessary condition for
-$(\hat{\theta}_T - \theta_0)'V_T (\hat{\theta}_T - \theta_0) < c$
-as $\theta'V_T\theta \to \infty$ is for all of the mass of
-$\hat{\theta}_T$ to concentrate on the line joining $\theta$ and
-$\theta_0$.  For any distribution of $(\e_{t+h}, x_t')$ such
-that $\hat{\theta}_T$ depends on $\theta$ only through its mean, the
-Lebesgue measure of parameter sequences satisfying this condition is
-zero. \qed
-
-\vspace{\baselineskip}
-\noindent\textit{Equation~\eqref{eq:15}}:  Suppose that
-$(\e_{t+h}, x_t) \sim i.i.d. N(0,I)$ and condition on $X_T$.
-Then the distribution of $\hat{\theta}_{T}$ concentrates uniformly on
-the ellipsoid
-\begin{equation*}
-  (\hat{\theta}_T - \theta)'(\hat{\theta}_T - \theta) = \theta'\theta.
-\end{equation*}
-Now, for $\theta$ and $V_T$ such that
-\begin{equation*}
-  (\theta-\theta_0)' V_T (\theta-\theta_0) > c + \delta,
-\end{equation*}
-the probability that $\hat{\theta}_T$ is inside the acceptance region
-of the test is less than $(1/2)^{K_2}$, which converges to zero as $T
-\to \infty$. \qed
+\subsection*{Proof of Theorem~\ref{res:insample1}}
+
+For both parts, let $(\e_{t+h}, x_{t}) \sim i.i.d. N(0,I)$ and let
+$\theta_1 = 0$.
+
+\noindent
+\emph{Proof of (\ref{eq:11})}. $\E_T \oosB = 0$ implies that
+\begin{equation*}
+  \E_T (y_{T+\h+1} - x_{1T+1}'\bh{1T})^2
+  = \E_T (y_{T+\h+1} - x_{2T+1}'\bh{2T})^2
+\end{equation*}
+almost surely, which can be expressed as
+\begin{equation*}
+  \bh{1T}'\bh{1T} = (\bh{2T} - \theta_2)'(\bh{2T} - \theta_2)
+\end{equation*}
+almost surely. So, given $\bh{1T}$,
+
+, where $\tilde\theta_{1T}$ is the first $K_1$ elements
+of $\bh{2T}$ and $\tilde\theta_{2T}$ is the remaining $K_2 - K_1$, and
+$\theta_2^*$ is the corresponding elements of the pseudotrue $\theta_2$.
+
+distribution of $\bh{2T}$ concentrates on and outside the sphere
+defined by
+\begin{equation*}
+  (\bh{2T} - \theta_2)' A (\bh{2T} - \theta_2) = \theta_2' A \theta_2.
+\end{equation*}
+This sphere is centered at the
+
+If $\theta_2$ and $V_T$ satisfy
+\begin{equation*}
+  \Pr[\theta_2' V_T \theta_2 > 2 c] \to 1
+\end{equation*}
+the acceptance region of $\Lambda$ is contained in a cube with
+
+then
+\begin{align*}
+  \E(\Lambda \mid \E_T \oosB \leq 0)
+  &\leq \Pr[ \bh{2T}' V_T \bh{2T} < c \mid \E_T \oosB \leq 0] \\
+  &\leq (1/2)^{K_2},
+\end{align*}
+which converges to zero as $T \to \infty$.
+
+\qed
 

### 2014-03-21 paper.tex
Preamble: remove headers and clean up unused commands

--- 2014-03-03 paper.tex
@@
 
-\section{Monte Carlo}\label{sec:mc}
-\newcommand{\thetanorm}{\ensuremath{\lvert \theta \rvert_2}} This
-section presents two simulations that investigate the accuracy of our
-theory in small samples.\footnote{Simulations were conducted in R
-  \citep{Rde:10} using Sweave \citep{Lei:02} and the Lattice
-  \citep{Sar:10}, RSQLite \citep{Jam:10}, tikzDevice
-  \citep{ShB:11:0.6.1}, and pgfSweave \citep{BrS:11:1.2.1} packages.}
+\section{Monte Carlo}
+\label{sec:mc}
+
+This section presents two simulations that investigate the accuracy of
+our theory in small samples.%
+\footnote{Simulations were conducted in R \citep{Rde:10} using Sweave
+  \citep{Lei:02} and the Lattice \citep{Sar:10}, RSQLite
+  \citep{Jam:10}, and tikzDevice \citep{ShB:11:0.6.1} packages.} %
 The first looks at the asymptotic normality of the DMW statistic

### 2014-03-21 paper.tex
Revise Monte Carlo presentation
This commit edits the presentation of the Monte Carlo results,
hopefully making them seem more important and making them
easier to follow.

It also fixes several bugs in the graphs and converts the
presentation of the F-test results to a table.

--- 2014-03-20 paper.tex
@@
 inference about the expected future accuracy of his or her models when
-one or both is overfit.  We show analytically and through Monte Carlo
+one or both is overfit.  We show analytically and through Monte Carlo simulations
 that standard full-sample test statistics can not test hypotheses
@@
 models and estimation strategies as well.  Under this
-asymptotic theory, where the number of regressors $k$ increases with $T$
-so that $\lim k/T$ is positive and less than one,
+asymptotic theory, where the number of regressors $K$ increases with $T$
+so that $\lim K/T$ is positive and less than one,
 the OLS coefficient estimator is no longer
@@
 indicates a structural break (see \citealp{BoH:99}, and
-\citealp{StW:03}, among others), but this breakdown can be caused by
-overfit as well.
-
-These theoretical results partially justify OOS comparisons when
+\citealp{StW:03}, among others), but we show that this breakdown
+can be caused by overfit as well.
+
+It is important to realize that we are not \emph{advocating} linear
+regression for highly overparametrized models. If $K$ is very large
+relative to $T$, researchers will often want to use some form of
+shrinkage forecast, for example the LASSO \citep{Tib:96} or a factor
+model \citep{StW:02,BaN:02}. Our main focus in practice is settings
+where $K$ is \emph{moderately} large and it is not clear whether
+overfit will dominate the results. In such settings that, it is
+important to understand the behavior of different evaluation criteria
+when $K$ is large, in case overfit is a concern, and to have reliable
+methods for estimating the models' performance, which is the goal of
+this paper.
+
+Our theoretical results partially justify OOS comparisons when
 researchers want to
@@
 choosing between overfit models. For many DGPs the Wald test and the
-AIC will choose a larger alternative model over a small benchmark
-model with probability approaching one, regardless of which model is
-more accurate, while the BIC chooses the benchmark model with
-probability approaching one.%
-\footnote{Our result holds for a broad class of
-  full-sample statistics, but there may be other potential statistics
-  that mimic the OOS test and remain valid. Exploring such
-  statistics is left for future research.} %
+will choose the larger alternative model over a small benchmark model
+with probability much greater than its nominal size, regardless of
+which model is more accurate, and the AIC behaves similarly. The BIC,
+however, chooses the benchmark model with probability approaching one
+even when the \emph{alternative} model is more accurate.%
+\footnote{Our result holds for a broad class of full-sample
+  statistics, but there may be other potential statistics that mimic
+  the OOS test and remain valid. Exploring such statistics is left for
+  future research.} %
 This result holds even though modifications of the $F$-test are valid
@@
 among others.%
-\footnote{Also see \citet{Efr:86,Efr:04} for a discussion
-  of naive in-sample loss comparisons.} %
+\footnote{Also see \citet{Efr:86,Efr:04} for a discussion of naive
+  in-sample loss comparisons.} %
 Moreover, under this asymptotic theory, many recent OOS test
@@
 problems as in-sample tests.%
-\footnote{Our theoretical results apply
-  directly to \citepos{Mcc:07} OOS $t$-test, since it simply
-  proposes more liberal critical values for the same test statistic
-  that we study.  Since \citet{ClW:06,ClW:07} use a finite length
-  estimation window, our asymptotics are incompatible with theirs and
-  prevent us from studying their test directly, as well as
-  \citepos{GiW:06} and other tests based on \citepos{GiW:06}
-  asymptotics.  But \clws\ test can be viewed as a stochastic
-  adjustment to the critical values of the usual OOS $t$ test, so
-  our conclusions should apply informally as well.  Specifically, we
-  show that the DMW test rejects with probability equal to nominal
-  size when the estimated benchmark model is expected to be more
-  accurate, so more liberal critical values result in overrejection.} %
+\footnote{Our theoretical results apply directly to \citepos{Mcc:07}
+  OOS $t$-test, since it simply proposes more liberal critical values
+  for the same test statistic that we study.  Since
+  \citet{ClW:06,ClW:07} use a finite length estimation window, our
+  asymptotics are incompatible with theirs and prevent us from
+  studying their test directly, as well as \citepos{GiW:06} and other
+  tests based on \citepos{GiW:06} asymptotics.  But \clws\ test can be
+  viewed as a stochastic adjustment to the critical values of the
+  usual \oost\ test, so our conclusions should apply informally as
+  well.  Specifically, we show that the DMW test rejects with
+  probability equal to nominal size when the estimated benchmark model
+  is expected to be more accurate, so more liberal critical values
+  result in overrejection.} %
 These tests are also designed to reject the benchmark when the
 alternative model is true, and so they may reject too often when the
-benchmark is false but more accurate.  Obviously, since the
+benchmark is misspecified but more accurate.  Obviously, since the
 distribution of these statistics converges to the normal when $P/T \to
@@
 processes also behave like mixingales when recentered, so 
-the arguments used to prove asymptotic
+many arguments used to prove asymptotic
 results for Near Epoch Dependent (NED) functions of mixing processes
@@
 DMW OOS test, shows that standard in-sample tests reject the
-benchmark model too often when it is false but more accurate than the
+benchmark model too often when it is misspecified but more accurate than the
 alternative, and shows that standard model selection methods can run
@@
 $y_{t+\h}$:
-\begin{equation}
+\begin{equation*}
 y_{t+\h} = x_{1t}'\theta_1 + \e_{1,t+h}, \quad\text{and}\quad
 y_{t+\h} = x_{2t}'\theta_2 + \e_{2,t+h};
-\end{equation}
+\end{equation*}
 $t = 1,\dots,T-h$, $\h$ is the forecast horizon and the
@@
 Mean Square Error, so
-\begin{equation}
+\begin{equation*}
   \theta_i = \argmin_\theta \sum_{t=1}^{T-\h} \E (y_{t+\h} - x_{it}'\theta)^2,
-\end{equation}
+\end{equation*}
 making $\e_{i,t+\h}$ uncorrelated with $x_{i,t}$; $\e_{i,t+\h}$ can exhibit
@@
 In the settings we are interested in, a forecaster observes the data
-$(y_t,x_t)$ for periods 1 through $T$ and divides the observations
+$(y_t,x_t)$ for periods 1 through $T$ and divides these observations
 into an estimation sample of the first $R$ observations and a test
@@
 the models' performance over the test sample, which entails
-constructing two sequences of forecasts, (using a fixed-window
-estimation strategy)
-\begin{equation}
+constructing two sequences of forecasts with a fixed-window
+estimation strategy,
+\begin{equation*}
 \hat y_{i,t+\h} = x_{it}'\hat{\theta}_{it}, \qquad \text{for } i=1,2;
 \ t = R+1,\dots,T-h,
-\end{equation}
+\end{equation*}
 where
-\begin{equation}
+\begin{equation*}
   \bh{it} = \Big(\sum_{s=1}^{R-\h} x_{is}x_{is}'\Big)^{-1} \sum_{s=1}^{R-\h}
@@
     soon and will not equal $\bh{iR}$ for those values of $t$.} %
-\end{equation}
+\end{equation*}
 
@@
 defined as
-\begin{equation}
+\begin{equation*}
   \oosA \equiv P^{-1} \oosSum{t}{1} D_t
-\end{equation}
+\end{equation*}
 where
-\begin{equation}\label{eq:16}
+\begin{equation*}
   D_t = L(y_{t+\h} - x_{1t}'\bh{1t}) - L(y_{t+\h} - x_{2t}'\bh{2t}),
-\end{equation}
+\end{equation*}
 and $L$ is a known loss function. The \oost\ test is defined as
@@
 Statistics like $\oost$ have a long history in empirical economics
-because they capture an intuitive idea of modeling: that a good model
-should be able to forecast well when given new data and not only when
-used to fit the same data that were used to estimate it. \cite{MeR:83}
+because they capture an intuitive idea of model fit: that a good model
+should be able to forecast well on new data. \cite{MeR:83}
 use such a statistic to study exchange rate models and find that none
-of the models that existed at the time of the study outperformed a
+of the models that existed at the time of their study outperform a
 random walk. This finding has been remarkably durable and has spawned
@@
 particular, that research focuses on testing the null hypothesis that
-\begin{equation}\label{eq:21}
-  \E L(y_{t+\h} - x_{1t}'\theta_{1}) - \E L(y_{t+\h} - x_{2t}'\theta_{2}) = 0.
-\end{equation}
-But the population quantities in \eqref{eq:21} do not determine which
+\begin{equation*}
+  \E L(y_{t+\h} - x_{1t}'\theta_{1}) = \E L(y_{t+\h} - x_{2t}'\theta_{2}).
+\end{equation*}
+But the population quantities in this equation do not determine which
 model is more accurate in practice. The models'
 accuracy will also depend on the specific estimates of $\theta_1$ and
-$\theta_2$ used to produce the forecasts. In this setting, where the
-forecaster will use one of the models to make a number of predictions
-in the future---call the number of predictions $Q$---the quantity of
-interest becomes
-\begin{equation}
+$\theta_2$ used to produce the forecasts.
+
+When the forecaster will use one of the models to make a number of
+predictions (call it $Q$) in the future, the quantity of interest
+becomes
+\begin{equation*}
   \E_T \oosB = Q^{-1} \sum_{t=T+1}^{T+Q} \E_T D_t,
-\end{equation}
-where $D_t$ is defined in Equation~\eqref{eq:16} but here uses the
-full-sample estimates of the models' parameters,
-\begin{equation}
+\end{equation*}
+where $D_t$ is defined as before,
+\begin{equation*}
+  D_t = L(y_{t+\h} - x_{1t}'\bh{1t}) - L(y_{t+\h} - x_{2t}'\bh{2t}),
+\end{equation*}
+but now uses the full-sample estimates of the models' parameters,
+\begin{equation*}
   \bh{it} = \Big(\sum_{s=1}^{T-\h} x_{is}x_{is}'\Big)^{-1} \sum_{s=1}^{T-\h}
   x_{is} y_{s+\h}, \qquad \text{for } i=1,2;\ t = T+1,\dots, T + Q.
-\end{equation}
+\end{equation*}
 If $\E_T \oosB$ is positive, the second model is expected to forecast
@@
   form of stationarity, bounded moments, and weak dependence.} %
-i.e. the LHS of~\eqref{eq:21}.
 \begin{equation}\label{eq:22}
@@
 \Sigma)$.  Then the difference between $\E_T \oosB$ and
-quantity~\eqref{eq:22} is
+the in quantity~\eqref{eq:22} is
 \begin{align*}
-  \E_T \oosB - & \big(\E L(y_{t+\h} - x_{1t}'\theta_{1}) - \E L(y_{t+\h} - x_{2t}'\theta_{2})\big) \\
-  &= \big(\E_T (y_{T+\h+1} - \bh{1,T})^2 - \E_T (y_{T+\h+1} - x_{T+1}'\bh{2,T})^2\big) -
-  \big(\E y_{T+\h+1}^2 - \E (y_{T+\h+1} - x_{T+1}'\theta_2)^2 \big)\\
-  &= (\bh{2,t} - \theta_2)' \Sigma (\bh{2,t} - \theta_2) + o_p(1).
+  \E_T \oosB - \big(\E L(y_{t+\h} - x_{1t}'\theta_{1}&) - \E L(y_{t+\h} - x_{2t}'\theta_{2})\big) \\
+  &= \big(\E_T (y_{T+\h+1} - \bh{1,T})^2 -
+     \E_T (y_{T+\h+1} - x_{T+1}'\bh{2,T})^2\big) \\
+     &\quad - \big(\E y_{T+\h+1}^2 - \E (y_{T+\h+1} - x_{T+1}'\theta_2)^2 \big)\\
+  &= (\bh{2,t} - \theta_2)' \var(x_{2,t})\, (\bh{2,t} - \theta_2) + o_p(1).
 \end{align*}
@@
 performance on a new, independent, data set, but, for lack of a better
-term, we will call $\E_T \oosB$ the difference in generalization error
+term, we will call $\E_T \oosB$ the ``difference in generalization error''
 for the rest of the paper with hopefully no risk of confusion.
@@
 unavailable for strong mixing sequences. Absolute regularity
-implies uniform mixing, so this assumption is not unduly strong.
+implies uniform mixing but is more restrictive than strong mixing,
+so this assumption is not unduly strong.
 For a detailed discussion of these weak dependence conditions,
@@
   Moreover,
-  \begin{align*}
-    &\eigen_{\max}(X_{iS}'X_{iS}) = O_{L_3}(S), \\
-    &\eigen_{\max}((X_{iS}'X_{iS})^{-1}) = O_{L_3}(1/S), \\
-    \intertext{and}%
-    &\eigen_{\max}\Bigg(\E\Big( \sum_{s,t=U}^{S-h} \e_{i,s+\h} \e_{i,t+\h} x_{is}x_{it}'
-    \,\Big|\, X_{iS}'X_{iS} \Big)\Bigg) = O_{L_3}(S-U),
-  \end{align*}
-  for large enough $T$, where $S = R,\dots,T$, $U=1,\dots,S-\h$,
-  $i = 1,2$,
+  \begin{equation}
+    \eigen_{\max}(X_{iS}'X_{iS}) = O_{L_3}(S),
+  \end{equation}
+  \begin{equation}
+    \eigen_{\max}((X_{iS}'X_{iS})^{-1}) = O_{L_3}(1/S),
+  \end{equation}
+  \begin{multline}\label{eq:28}
+    \eigen_{\max}\Bigg(\E\Big(
+    \sum_{s,t=U}^{V-\h} \e_{i,s+\h} \e_{i,t+\h} x_{is}x_{it}'
+    \mBig
+    x_{i1},\dots,x_{i,U-1};
+    \sum_{s=U}^{V-\h} x_{is} x_{is}';
+    x_{i,V-\h+1},\dots,x_{i,T-\h}
+    \Big)\Bigg) \\
+    = O_{L_3}(\max(V-U, K_i)),
+  \end{multline}
+  and
+  \begin{multline}\label{eq:8}
+    \tr \E\Big(
+    \sum_{s,t=U}^{V-\h} \e_{i,s+\h} \e_{i,t+\h} x_{is}x_{it}'
+    \mBig
+    x_{i1},\dots,x_{i,U-1};
+    \sum_{s=U}^{V-\h} x_{is} x_{is}';
+    x_{i,V-\h+1},\dots,x_{i,T-\h}
+    \Big)\Bigg) \\
+    = O_{L_3}((V-U) \times K_i)
+  \end{multline}
+  for large enough $T$, where $S = R,\dots,T$, $1 \leq U \leq V - \h
+  \leq T - \h$, $i = 1,2$,
   \[ X_{iS} \equiv [x_{i1} \quad \dots \quad x_{i,S-\h}]' \qquad
@@
 
+The assumption on $K_1$ and $K_2$ is crucial to the paper; we assume
+that the model complexity grows with $T$ fast enough to break
+consistency. This assumption is how we derive an asymptotic
+concept of ``overfit.''
+
 The assumption that $y_{t+\h}$ and $x_t$ have positive and finite
@@
 technical and control the behavior of the OLS estimator as the number
-of regressors gets large---the third assumption is nonstandard but can
-be easily verified under independence, for example. The restrictions
-on the pseudotrue coefficients ensure that the regression model
-doesn't dominate the variance of $y_{t+\h}$ in the limit.
+of regressors gets large---the third and fourth assumptions are
+nonstandard but can be easily verified under, for example,
+independence. Section~\ref{sec:example} contains such an example. The
+restrictions on the pseudotrue coefficients ensure that the regression
+model doesn't dominate the variance of $y_{t+\h}$ in the limit.
 
@@
   B_L$ for all $t$, where
-  \begin{equation*}
+  \begin{equation}
     D_t^* = L(y^* - x_1^{*\prime}\hat\theta_{1t})
     - L(y^* - x_2^{*\prime}\hat\theta_{2t})
-  \end{equation*}
+  \end{equation}
   and $(y^*, x_1^*, x_2^*)$ equals $(y_t, x_{1t}, x_{2t})$ in
@@
   in Assumption~\ref{asmp-1}); and
-  \begin{equation*}
+  \begin{equation}\label{eq:29}
     \| L'(y^* - x_{i}^{*\prime} (\alpha \bh{iR} + (1-\alpha) \bh{iT})) \|_2
     \leq B_L
-  \end{equation*}
+  \end{equation}
   for any $\alpha \in [0,1]$.
@@
 absolute error and many asymmetric loss functions satisfy this
-assumption. The Assumption makes use of both $(y_{t+\h}, x_{1t},
+assumption. The assumption makes use of both $(y_{t+\h}, x_{1t},
 x_{2t})$ and $(y^*, x_1^*, x_2^*)$ because the period $t$ observations
@@
 \begin{asmp} \label{asmp-4} (a) $P, R, Q \to\infty$ as $T \to
-  \infty$. (b) $P^2/T \to 0$ as $T \to \infty$.
+  \infty$. (b) $P^2/T \to 0$ and $P/Q \to 0$ as $T \to \infty$.
 \end{asmp}
@@
 $\Re$ to $[-1,1]$ such that $W(0) = 1$, $W(x) = W(-x)$ for all $x$,
-\begin{equation*}
+\begin{equation}
   \int_{-\infty}^{\infty} \lvert W(x) \rvert dx < \infty, \quad
   \int_{-\infty}^{\infty} \lvert \psi(x) \rvert dx < \infty
-\end{equation*}
+\end{equation}
 with
-\begin{equation*}
+\begin{equation}
   \psi(x) = \frac1{\sqrt{2\pi}} \int_{-\infty}^{\infty} W(z) e^{ixz}dz,
-\end{equation*}
+\end{equation}
 and $W(\cdot)$ is continuous at zero and all but a finite number of
@@
 
-Assumptions~\ref{asmp-1}--\ref{asmp-5} are broadly similar to
-\citepos{Wes:96} assumptions, except with regard to model complexity
-and the size of the test sample.  West assumes that $K_1$ and $K_2$
-are both finite, while we let them grow rapidly with $T$
-(Assumption~\ref{asmp-1}), and West lets $P/R$ converge to any value
-in $[0,\infty]$, while we require $P^2/R \to 0$
-(Assumption~\ref{asmp-4}).%
-\footnote{\citet{Wes:96} does not have a
-  second OOS period, so there is no analogue in his paper to our
-  restriction on $Q$.} %
-Obviously, these differences are
-related---allowing for complex models requires tighter constraints on
-the size of the test sample.  West allows more general estimation
-methods, while we restrict attention to OLS; the advantage of using
-OLS is that we can derive the inequality,
-\begin{equation*}
-  \| x_{it}'\bh{i,T+1} - x_{it}'\bh{iR} \|_2 \leq O(P/T)^{1/2}.
-\end{equation*}
-Our main results will hold for other models and estimation windows as
-long as a similar inequality exists, but proving such inequalities is
-left for future research.
-
-Our other assumptions are similar.  The loss function must be smooth
-almost everywhere, which is less restrictive than \citet{Wes:96}
-requires but is not new; \citet{Mcc:00} extends West's results to
-cover a similar case. We assume full stationarity and absolute
-regularity of the underlying random array, while West assumes
-covariance stationarity and strong mixing of the transformed forecast
-errors; and the details our moment conditions are different, but seem
-that they would hold in similar environment to West's.  Finally, since
-West's is a more standard environment, he assumes the existence of a
-consistent estimator of the variance, while we construct it
-explicitly.  Only West's assumptions governing model complexity and
-the size of the test sample are substantially different than ours.
+These assumptions are broadly similar to those existing in the
+literature, with some differences in our assumptions relating the
+estimated coefficients to future values of the DGP.
+Section~\ref{sec:example} contains an extended example that shows how
+these assumptions are satisfied in a simple setting.
 
@@
 This section lays out our theoretical results. The first subsection
-presents results for the DMW $t$-test; we show that it is
+presents results for the DMW \oost\ test; we show that it is
 asymptotically normal when one or both forecasting models is overfit.
@@
 loss has more structure than most mixingales and behaves like an NED
-process in important respects.
+process in important respects. (The key result here is
+Lemma~\ref{lem:a2} in the Appendix.) Lemma~\ref{res-mixingale} presents the
+CLT that we use later, and Section~\ref{sec:example} works through an
+i.i.d. example in detail. For i.i.d. observations, the OOS loss is an
+MDS and is easier to work with.
 
@@
   Moreover
-  \begin{equation}\label{normalpart}
+  \begin{equation}
     \sqrt{P}(\oosA - \E_R \oosA)/\sigma \to^d N(0,1)
@@
 either. But this additional dependence has a special form and can be
-removed by subtracting the conditional mean; this means that $g(y_{t+\h} -
+removed by subtracting the conditional mean; specifically $g(y_{t+\h} -
 x_{it}'\bh{it})$ is not weakly dependent but $g(y_{t+\h} -
-x_{it}'\bh{it}) - \E_R g(y_{t+\h} - x_{it}'\bh{it})$ is, as long as
-the new process satisfies standard moment
-restrictions. Assumptions~\ref{asmp-1}--\ref{asmp-3} ensure that these
-restrictions are satisfied for $D_t - \E_R D_t$.
-
-The form of the dependence introduced by $\bh{it}$ also allows the CLT
-to hold without additional restrictions---the proof rests on showing
-that a process like $D_t^2 - \E_R D_t^2$ is also a mixingale, using a
-similar argument to the one used by \citet{Jon:97} for NED
-processes. This property needs to be established on its own because it
-does not follow from the behavior of $D_t - \E_R D_t$.
-Lemma~\ref{lem:a2} presents the details of this part of the proof.
+x_{it}'\bh{it}) - \E_R g(y_{t+\h} - x_{it}'\bh{it})$ is.
+Assumptions~\ref{asmp-1}--\ref{asmp-3} allow us to show directly
+that $D_t - \E_R D_t$ and (crucially) $D^2_t - \E_R D_t^2$ are both
+weakly dependent mixingales, ensuring Lemma~\ref{res-mixingale}.
 
@@
   \begin{equation}\label{eq:7}
-    \E_T \oosB - \E_R \oosA = O_p(\sqrt{P/T}) + o_p(P^{-1/2} + Q^{-1/2}).
-  \end{equation}
-  Moreover, there exist processes and loss functions that satisfy
-  Assumptions \ref{asmp-1}--\ref{asmp-4}a but $\E_T \oosB - \E_R \oosA
-  \neq O_p(1)$ unless $P/T \to 0$.
+    \E_T \oosB - \E_R \oosA = O_p(\sqrt{P/T}) + o_p(P^{-1/2})
+    + o_p(Q^{-1/2}).
+  \end{equation}
 \end{lem}
-
 We can view $\E_T \oosB - \E_R \oosA$ as noise introduced by
 approximating the performance of the full-sample estimates with that
-of the partial-sample estimates. The second part of
-Lemma~\ref{res-convergence} shows that the $O_p(\sqrt{P/T})$ term
-is generally binding; using $\oosA$ to estimate $\E_T \oosB$ requires
-$P/T \to 0$ for consistency and using $\sqrt{P} \oosA$ to test
-hypotheses about $\E_T \oosB$ requires $P^2/T \to 0$.
+of the partial-sample estimates. The key term on the RHS
+of~\eqref{eq:7} in practice is $O_p(\sqrt{P/T})$---unless $P/T$ is
+small, this noise dominates the OOS average, making it an inconsistent
+estimator of $\E_T \oosB$. The $o_p(P^{-1/2})$ term is completely
+unrestrictive in our applications because we will multiply the OOS
+average by at most $\sqrt{P}$ (for the CLT). And the $o_p(Q^{-1/2})$
+term has some implications for interpreting these results: we can only
+measure the average performance of the forecasting models for an
+extended period in the future, long enough that the future
+observations are essentially independent of the current
+information. For $Q=1$, for example, the dependence between
+$y_{T+\h+1}$ and the current information set $\Fs_T$ may be very
+strong.
 
@@
 normal and centered at $\E_T \oosB$, as long as
-Assumption~\ref{asmp-4}b holds. This theorem justifies using the DMW
-$t$-test with a short test sample, which may not be feasible in some
-applications.
+Assumption~\ref{asmp-4}b holds. This theorem only establishes the
+asymptotic distribution, though.
 
@@
 
-Finally, we establish that the DMW test can be use to construct
-confidence intervals for $\E_T \oosB$ or test hypotheses about $\E_T
-\oosB$. In particular, forecasters will often want to test the null
-hypothesis that $\E_T \oosB \leq 0$, meaning that the benchmark model
-is expected to be more accurate than the alternative model in the
-future.
+When $K_1$ and $K_2$ are fixed, West's (1996) and McCracken's (2007)
+asymptotic theories apply and the \oost\ test remains normal as long
+as $P/T \to 0$, even if $\sigma^2 \to 0$. Under that asymptotic
+approximation, the variance will converge to zero whenever the true
+DGP is nested in both of the forecasting models. The same principles
+may apply in our setting if $K_1$ and $K_2$ grow slowly, so $K_2/T \to
+0$. It is likely that a second order expansion along the lines of
+\citet{Mcc:07} would lead to asymptotic normality for that
+intermediate case, but we leave that issue to future research.
+
+Finally, Theorem~\ref{res:oostest} establishes that the DMW test can be
+use to construct confidence intervals for $\E_T \oosB$ and test
+hypotheses about $\E_T \oosB$. In particular, forecasters will often
+want to test the null hypothesis that $\E_T \oosB \leq 0$, meaning
+that the benchmark model is expected to be more accurate than the
+alternative model in the future.
 
@@
   $z_{\alpha}$ the $1-\alpha$ quantile of the standard normal
-  distribution. If $\lim \Pr[\E_T \oosB \leq 0] > 0$ in addition then
+  distribution. If, in addition, $\lim \Pr[\E_T \oosB \leq 0]$ is
+  positive then
   \begin{equation}\label{eq:23}
@@
 \end{thm}
+\noindent
 The results for confidence intervals in Theorem~\ref{res:oostest}
@@
   consider independent observations.} %
-To simplify the presentation we only derive results for nested models
-but the conclusions hold more generally.
+To simplify the presentation and the intuition we only derive results
+for nested models and for MSE loss, but the conclusions hold much more
+generally.%
+\footnote{Also, define $M_1 = [I_{K_1} \ 0_{K_1 \times (K_2 - K_1)}]$
+  and $M_2 = [0_{(K_2 - K_1) \times K_2} \ I_{K_2 - K_1}]$ as the
+  selection matrices that return the first $K_1$ and the last $K_2 -
+  K_1$ elements of $\theta_2$, and assume that the regressors are
+  ordered so that the first $K_1$ elements of $x_{2,t}$ correspond to
+  $x_{1,t}$.} %
 
@@
 But for overfit models, the estimates will typically be far from both
-their pseudotrue values and from zero. In that case, the Wald test and
+their pseudotrue values and also from zero. In that case, the Wald test and
 the AIC will both tend to choose the larger model even when it is less
@@
 when it has many elements. The threshold for the Wald test and the AIC
-is set by construction to be a bounded distance from the origin.
-Every other statistic that shares this property has the same behavior,
-since the probability that the coefficient estimators of a
-less-accurate but true alternative model fall inside a bounded
-threshold are arbitrarily small in the limit. This behavior is
-formalized by Theorem~\ref{res:insample1}.
+is set by construction to be a bounded distance from the origin, and
+every other statistic that shares this property has the same behavior
+and can reject the benchmark model with high probability, even when
+it is more accurate. This behavior is
+formalized in Theorem~\ref{res:insample1}.
+
 \begin{thm}\label{res:insample1}
@@
   and $\Lambda = 1$ indicates the alternative.  Moreover, assume that
-  $L(e) = e^2$ and that there exist a deterministic scalar $c$ and a
-  sequence of possibly random matrices $V_T$ such that
+  $L(e) = e^2$ and that there exist deterministic scalars $c$ and
+  $\delta$ and a sequence of matrices $V_T$ such that
   \begin{equation}\label{eq:25}
-    \Pr[\Lambda > \1\{\bh{2T}' V_T \bh{2T} > c \}] \to 0
-    \quad \text{as } T \to \infty
-  \end{equation}
-  where the eigenvalues of $V_T$ are uniformly bounded in probability
-  and $\plim \rank(V_T)/T > 0$.
-
-  Then there exist DGPs satisfing these assumptions such that
+    \limsup_{T \to \infty}
+    \Pr[\Lambda \geq \1\{\bh{2T}'M_2' V_T M_2\bh{2T} > c \}]
+    \leq \delta
+  \end{equation}
+  where the eigenvalues of $V_T$ are uniformly bounded, and $\lim
+  \rank(V_T)/T > 0$.
+
+  Then there exist DGPs satisfying these assumptions such that
   \begin{equation}\label{eq:11}
-    \E( \Lambda \mid \E_T \oosB \leq 0 ) \to^p 1.
+    \liminf_{T \to \infty} \E( \Lambda \mid \E_T \oosB \leq 0 )
+    \to^p \gamma > 1/2 - \delta.
   \end{equation}
 \end{thm}
-As we state above,~\eqref{eq:11} means that, with probability
-approaching 1, the benchmark model is rejected even when it is more
-accurate. The DGPs and statistics used in Theorem~\ref{res:insample1}
-are simple and common. The DGPs include correctly specified linear
-models with normal and homoskedastic errors. The statistics that meet
-the restrictions on $\Lambda$ include the $F$-test and AIC.
-
-For example, the $F$-statistic to test the null that all of the
-coefficients unique to the larger model is known to have the form
-\begin{equation}\label{eq:17}
+
+As we state above,~\eqref{eq:11} means that, with high probability,
+the benchmark model is rejected even when it is more accurate. In
+general, $\delta$ can be made arbitrarily small by increasing the
+region enclosed by $\1\{\bh{2T}'M_2' V_T M_2\bh{2T}\}$ and DGPs can be
+chosen to put $\gamma$ arbitrarily close to 1 while still satisfying
+the assumptions of the Theorem.  The DGPs and
+statistics used in Theorem~\ref{res:insample1} are simple and
+common. They include correctly specified linear models with normal and
+homoskedastic errors; and the statistics that meet the restrictions on
+$\Lambda$ include the $F$-test and AIC.
+
+For example, the $F$-statistic to test the null hypothesis that the
+benchmark model is correctly specified is known to have the form
+\begin{equation*}
   F = \frac{\bh{2T}' M_2' ( M_2 (X_{2T}'X_{2T})^{-1} M_2' )^{-1} M_2
     \bh{2T}}{s^2 (K_2 - K_1)}
-\end{equation}
+\end{equation*}
 where $s^2$ is the usual estimator of the variance of the regression
-error and $M = (0_{K_2 - K_1, K_1}\ \ I_{K_2 - K_1})$. Then let $c$ be any number
-greater than 1 and define
+error. Then let $c$ be any number greater than 1 and define
 \begin{equation*}
@@
 
-Theorem~\ref{res:insample2} describes this behavior in detail.
-
+This behavior is formalized in Theorem~\ref{res:insample2}.
 \begin{thm}\label{res:insample2}
@@
   \begin{equation}\label{eq:27}
-    \Pr[\Lambda > \1\{\bh{2T}' V_T \bh{2T} > c \}] \to 1
+    \Pr[\Lambda \leq \1\{\bh{2T}'M_2' V_T M_2\bh{2T} > c \}] \to 1
     \quad \text{as } T \to \infty,
   \end{equation}
-  where $V_T$ is a sequence of possibly random matrices with with
-  eigenvalues uniformly bounded in probability and $\plim \rank(V_T)/T
-  > 0$. Then there exist DGPs satisfing these assumptions such that
+  where $V_T$ is a sequence of deterministic matrices with uniformly
+  bounded eigenvalues and $\lim \rank(V_T)/T > 0$. Then there exist
+  DGPs satisfying these assumptions such that
   \begin{equation}\label{eq:15}
@@
 
-Again,~\eqref{eq:15} implies that statistics like the BIC will always
-choose the smaller model, even when the larger model will give more
-accurate forecasts. Both models may be overfit, in that both $K_1/T$
-and $K_2/T$ may both be positive in the limit; the key is that $(K_2 -
-K_1)/T$ is also positive in the limit.
-
-It is important to remember that, when $\Lambda$ represents a test
-statistic, the test may have correct size for the null hypothesis that
-the additional coefficients on the larger model are zero. So previous
-research, such as \citet{Cal:11c} and \citet{Ana:12}, does not predict
-these results. Any statistic that uses the distance of the models'
-estimated coefficients from a set point (the origin being the most
-common) is poorly suited for choosing between overfit models. These
+The condition~\label{eq:27} requires that the acceptance region of
+$\Lambda$ eventually contains any finite cylindar centered at the
+origin. Again,~\eqref{eq:15} implies that statistics like the BIC
+will always choose the smaller model for some DGPs, even when the
+larger model will give more accurate forecasts. Both models may be
+overfit, in that both $K_1/T$ and $K_2/T$ may both be positive in the
+limit; the key is that $(K_2 - K_1)/T$ is also positive in the limit.
+
+It is important to remember that previous research, such as
+\citet{Cal:11c} and \citet{Ana:12}, does not predict these
+results. When $\Lambda$ represents a test statistic, the test may have
+correct size for the null hypothesis that the additional coefficients
+on the larger model are zero. The results in this subsection are being
+driven by the full-sample statistics' behavior when the smaller model
+is misspecified but more accurate.
+
+Any statistic that uses the distance of the models' estimated
+coefficients from a set point (the origin being the most common) is
+poorly suited for choosing between overfit forecasting models. These
 models only forecast well when their coefficient estimates are close
-to their pseudotrue values, which can be far from any prespecified
+to their pseudotrue values, which can be far from the origin or any
+other prespecified
 point. Depending on the statistic, it can be biased towards choosing
-the larger model or the smaller model. Formal in-sample tests will
-likely be biased towards the larger model, as we show for the $F$-test
-in Theorem~\ref{res:insample1}.
-
-\subsection{An extended but simple example}
+the larger model or the smaller model. Formal in-sample \emph{tests}
+will likely be biased towards the larger model, as we show for the
+$F$-test and Wald test in Theorem~\ref{res:insample1}.
+
+\subsection{An extended simple example}
 \label{sec:example}
@@
 This subsection illustrates the previous theoretical results with a
-concrete, extremely simple, example. Let $L(e) = e^2$ and $h =
-1$. Suppose that $\e_{t+1} \sim i.i.d.\ N(0,1)$, that the benchmark
-model is nested in the alternative, and let
-\begin{equation}
-  y_{t+1} = x_{2t}'\theta_2 + \e_{t+1}.
-\end{equation}
-be the DGP. We also assume for simplicity that the full-sample design
-matrix $X_{2T}$ satisfies $X_{2T}'X_{2T} = T \times I$ and that
-$x_{T+1} \sim N(0, I)$, which violates our assumptions on the
-regressors but simplifies this treatment considerably.
-
-The first part shows how the assumptions in Section~\ref{sec:asmp} are
-satisfied in this example and the second demonstrates asymptotic
-normality of the DMW OOS $t$-test. The third part explicitly shows
-that $\E_R \oosA$ converges to $\E_T \oosB$ only when the test sample
-is small. And the last part demonstrates that the $F$-test, AIC, and
-BIC do not indicate which model will be more accurate in the future,
-even in this simple example.
-
-\subsubsection*{Fulfillment of the assumptions}
-
-\subsubsection*{Asymptotic normality of the OOS average}
-
-Under these conditions, we have
-\begin{equation}
+concrete Let $L(e) = e^2$ and $h = 1$. Suppose that the benchmark is
+nested in the alternative and $(x_{2t}, \e_{2,t+1}) \sim i.i.d.\
+N(0,I)$, and let $y_{t+1} = x_{2t}'\theta_2 + \e_{2,t+1}$
+be the DGP. Also assume that $K_2/T \to c_2$ and $K_1 / T \to c_1 <
+c_2$.
+
+The first part of this subsection shows how the assumptions in
+Section~\ref{sec:asmp} are satisfied and the second part
+demonstrates asymptotic normality of the DMW OOS $t$-test. The third
+part explicitly shows that $\E_R \oosA$ converges to $\E_T \oosB$ only
+when the test sample is small. And the last part demonstrates that the
+$F$-test, AIC, and BIC do not indicate which model will be more
+accurate in the future, even in this simple example.
+
+\subsubsection*{Fulfillment of Assumptions 1--5}
+
+We will go through the assumptions one by one. The first Assumption is
+a condition on the dependence and moments of the process. Since the
+DGP is i.i.d. Normal, these conditions are satisfied trivially.
+
+Assumption~\ref{asmp-2} deals with the design matrix. In this example,
+we directly assume that $K_2$ and $K_1$ grow at the correct rates so
+the the assumption is satisfied. The variance of $y_{t+1}$ given
+$\Fs_t$ is simply the unconditional variance of $\e_{2,t+1}$, which is
+1; and the eigenvalues of $\E x_{2t} x_{2t}$ all equal 1 as well; and
+so they are all uniformly positive and finite as required.
+
+Assumption~\ref{asmp-2} also requires the eigenvalues of $S^{-1}
+X_{iS}'X_{iS}$ to be positive and finite, and for the largest
+eigenvalue of $S^{-1} X_{iS}'X_{iS}$ to be bounded in $L_3$.  These
+results follow from developments in random matrix theory.
+\citet{Gem:80} establishes that the largest eigenvalue of
+$X_{iS}'X_{iS}$ is of order $S + K_i$ and \citet{Joh:01} shows that it
+converges in distribution to the Tracy-Widom law of order 1
+\citep{TrW:96}, which has finite 3rd moments. \citet{Sil:85} and
+\citet{BFP:98} prove similar results for the smallest eigenvalue.
+Assumption~\ref{asmp-2} also requires the largest eigenvalue of
+$(X_{iS}'X_{iS})^{-1}$ be bounded in $L_3$; this should follow from a
+similar argument, but we are unaware of any papers that explicitly
+derive moments for this eigenvalue.
+
+For the conditional expectation of %
+$\sum_{s,t=U}^{V-\h} \e_{i,t+\h} \e_{i,s+\h} x_{i,s} x_{i,t}'$,
+independence implies that
+\begin{equation*}
+  \E\Big(
+  \sum_{s,t=U}^{V-\h} \e_{i,s+\h} \e_{i,t+\h} x_{is}x_{it}'
+  \mBig
+  x_{i1},\dots,x_{i,U-1};
+  \sum_{s=U}^{V-\h} x_{is} x_{is}';
+  x_{i,V-\h+1},\dots,x_{i,T-\h}
+  \Big)
+  = \sum_{s=U}^{V-\h} x_{is} x_{is}'.
+\end{equation*}
+The largest eigenvalue of this last matrix is of order $K_i + V - U$,
+as discussed, and it has at most $V-\h - U + 1$ nonzero eigenvalues,
+ensuring that both~\eqref{eq:28} and~\eqref{eq:8} hold.
+
+Assumption~\ref{asmp-3} restricts the loss function and the realized
+OOS loss. In this example, we have
+\begin{equation*}
+  D_t^* =^d D_t = (e_{2,t+1} + x_{2t}'\theta_2 - x_{1t}'\bh{1t})^2
+  - (e_{2,t+1} + x_{2t}'(\theta_2 - \bh{2t}))^2
+\end{equation*}
+which has bounded $\rho$th moments by construction. The loss function
+is differentiable and $L'(e) = 2 e$, so \eqref{eq:29} holds as well.
+
+Finally, Assumption~\ref{asmp-4} deals with the choice of test and
+training sample and holds automatically. And Assumption~\ref{asmp-5}
+requires the kernel of the HAC variance estimator to be continuous at
+zero; it is straightforward to construct an estimator that satisfies
+this condition. However, in this section we will use the estimator
+\begin{equation*}
+  \sh^2 = \frac{1}{n} \sum_{t=R+1}^{T-1} (D_t - \oosA)^2
+\end{equation*}
+which does not satisfy Assumption~\ref{asmp-5} but nevertheless is
+consistent for the conditional variance of $\oosA$ because the
+underlying observations are independent.
+
+\subsubsection*{Asymptotic normality of the OOS average, Lemma 1}
+
+This subsection walks through Lemma 1's CLT. Since the observations in
+this example are i.i.d., we do not need to use mixingale theory to
+derive the results, but the OOS process is still affected by the
+estimation error in $\bh{1t}$ and $\bh{2t}$ and has a high degree of
+dependence. This dependence makes the OOS process an MDS, and MDS
+asymptotic theory replaces mixingale theory in this example.
+
+By construction, we have
+\begin{equation*}
   D_t =
@@
   \end{cases}
-\end{equation}
+\end{equation*}
 and so we can explicitly derive the components of
-Lemma~\ref{res-mixingale}:
-\begin{multline}\label{eq:17}
+Lemma~\ref{res-mixingale}. First,
+\begin{multline*}
   D_t - \E_R D_t
@@
           - \E_R (x_{2t}'\theta_2 - x_{2t}'\bh{2R})^2 \Big\}
-\end{multline}
+\end{multline*}
 for $t < T$. Since the underlying observations are i.i.d., $\E_{t-1}
-D_t = \E_R D_t$ a.s.\ and $\{D_t - \E_R D_t, \Fs_{t};
-t=R+1,\dots,T-1\}$ is an MDS. Even in this simple example, the
-estimation error in $\bh{1R}$ and $\bh{2R}$ introduces strong
-persistance into the OOS forecast errors, but this persistence is
-predetermined so we can continue to apply basic asymptotic theory.
+D_t = \E_R D_t$ a.s.\ and consequently $\{D_t - \E_R D_t, \Fs_{t};
+t=R+1,\dots,T-1\}$ is an MDS.
 
@@
 will be MDSes after subtracting their conditional mean; i.e.
-\begin{equation}
+\begin{equation*}
   \{g(D_t) - \E_R g(D_t); \Fs_t; t = R+1,\dots,T-1\}
-\end{equation}
+\end{equation*}
 is an MDS as long as
@@
 and $\bh{2R}$, so
-\begin{equation}\begin{split}
+\begin{equation*}\begin{split}
   \E_R g(D_t)
-  &= \int g\Big((x_1'\bh{1R})^2 - (x_1'\bh{2R})^2
+  &= \int g\Big((x_1'\bh{1R})^2 - (x_2'\bh{2R})^2
        + 2 y (x'\bh{2R} - x'\bh{1R})\Big) \, f(y, x) \, dx \, dy \\
   &= \E_{t-1} g(D_t)
-\end{split}\end{equation}
+\end{split}\end{equation*}
 a.s., where $f$ is the density of $(y_{t+1}, x_{2t})$ and $x_1$
-denotes the first $K_1$ elements of $x$.
-
-These MDS results imply that $\oosA$ and $(1/P) \sum_{t=R+1}^{T-1}
-D_t^2$ both obey LLNs: $\oosA \to^p \E_R \oosA$ and
-\begin{equation}
+denotes the first $K_1$ elements of $x$. This result parallels our
+results for mixingales in the general case.
+
+As a result, $\oosA$ and $(1/P) \sum_{t=R+1}^{T-1} D_t^2$ both obey
+LLNs: $\oosA \to^p \E_R \oosA$ and
+\begin{equation*}
   (1/P) \sum_{t=R+1}^{T-1} D_t^2 \to^p \E_R D_T^2.
-\end{equation}
+\end{equation*}
 Moreover, these convergence results imply that $\sh^2 - \var_R
-\sqrt{P} \oosA \to^p 0$, where $\sh^2$ is the OOS variance estimator
-\begin{equation}
-  \sh^2 = (1/P) \sum_{t=R+1}^{T-1} (D_t - \oosA)^2.
-\end{equation}
-(In the general dependent case, we would need to use a HAC estimator
-for consistency.)
-
-Finally, we can apply the MDS CLT to $\oosA$ as long as $\Pr[\lim
-\var_R \sqrt{P} \oosA > 0] = 1$. \citep[Theorem 3.2.]{HaH:80} In our
-main results, we assume that this condition holds, but it is
-straightforward to verify here. Equation~\eqref{eq:17} implies that
-\begin{equation}
-  \begin{split}
-    \var_R \sqrt{P} \oosA &= \E_R(D_t - \E_R D_t)^2 \\
-    &\geq 4 \E_R (x_{2t}' \bh{2R} - x_{1t}' \bh{1R})^2
-    \quad a.s.
-  \end{split}
-\end{equation}
-and...
-
-\subsubsection*{Convergence of $\E_R \oosA$ to $\E_T \oosB$}
-
-We can also use this example to study Lemma~\ref{res-convergence}.
-Under this section's assumptions, $\E_R \oosA$ and $\E_T \oosB$ can be
-worked with directly, and their difference is equal to
-\begin{equation}
+\sqrt{P} \oosA \to^p 0$. And so
+\begin{equation*}
+  \sqrt{P} \oosA/\sh \to N(0,1)
+\end{equation*}
+by the MDS CLT.
+
+\subsubsection*{Convergence of $\E_R \oosA$ to $\E_T \oosB$, Lemma 2}
+
+This subsection works through Lemma~\ref{res-convergence}. In this
+example, the difference between $\E_R \oosA$ and $\E_T \oosB$ equals
+\begin{equation*}
   \begin{split}
@@
   \end{split}
-\end{equation}
-with $\tilde{X}_{iR}$ the $T \times K_i$ matrix $[X_{iR}'\ 0]'$.
-
-This last term is a quadratic form and the regressors are assumed to
-be normal, so its first two moments are easy to calculate. The mean
-difference is
-\begin{equation}
+\end{equation*}
+with $\tilde{X}_{iR}$ the $T \times K_i$ matrix $[X_{iR}'\ 0]'$. This
+last term is a quadratic form and the regressors and errors are
+assumed to be normal, so we can find the rate that the difference
+converges to zero in probability by calculating its first two moments.
+
+The mean difference is
+\begin{equation*}
   \begin{split}
   \E(\E_R \oosA - \E_T \oosB)
-      &=\E \tr \Big\{
-        \tilde{X}_{1R}(X_{1R}'X_{1R})^{-2} \tilde{X}_{1R}
-      - X_{1T}(X_{1T}'X_{1T})^{-2} X_{1T} \\
-      & \qquad\qquad- \tilde{X}_{2R}(X_{2R}'X_{2R})^{-2} \tilde{X}_{2R}
-      + X_{2T}(X_{2T}'X_{2T})^{-2} X_{2T} \Big\} \\
-      &= \tr \Big\{\E (X_{1R}'X_{1R})^{-1}
-         - \E (X_{1T}'X_{1T})^{-1} \Big\}
-         - \tr \Big\{\E (X_{2R}'X_{2R})^{-1}
-         - \E (X_{2T}'X_{2T})^{-1} \Big\}, \\
-      &= \tfrac{K_1 P}{(R-K_1-1)(T-K_1-1)} - \tfrac{K_2 P}{(R-K_2-1)(T-K_2-1)}.
+      &=O\Big(\max_i \E \tr \big\{
+        \tilde{X}_{iR}(X_{iR}'X_{iR})^{-2} \tilde{X}_{iR}
+        - X_{iT}(X_{iT}'X_{iT})^{-2} X_{iT} \big\} \Big) \\
+      &=O\Big(\max_i \tr \big\{\E (X_{1R}'X_{1R})^{-1}
+         - \E (X_{1T}'X_{1T})^{-1} \big\}\Big) \\
+      &=O( K_1 P / (R-K_1)(T-K_1)) \\
+      &=O(P/T)
     \end{split}
-\end{equation}
-The variance of the difference is
-and
-
-and
+\end{equation*}
+The first equality follows from the expectation of a quadratic form,
+the second from routine manipulations of the trace operator, and the
+third from the moments of the inverse Wishart distribution.
+
+Similarly, the variance of the difference is
 \begin{align*}
-  \var(\E_R & \oosA - \E_T \oosB) \\ &= \E
-  \big[\tr((X_{2R}'X_{2R})^{-1} - (X_{2T}'X_{2T})^{-1})\big]^2 + 2 \tr
-  \E\big((X_{2R}'X_{2R})^{-2} - (X_{2T}'X_{2T})^{-2}\big) \\ &\quad - \big[\tr
-  \E((X_{2R}'X_{2R})^{-1} - (X_{2T}'X_{2T})^{-1}) \big]^2 \\ &=
-  O(P/T)^2.
+  \var(\E_R & \oosA - \E_T \oosB) \\ &=
+  O\Big(\max_i \E\big[\tr((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1})\big]^2
+  + 2 \tr \E\big((X_{iR}'X_{iR})^{-2} - (X_{iT}'X_{iT})^{-2}\big) \\
+  &\qquad - \big[\tr \E((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}) \big]^2 \Big)\\
+  &= O(P/T)^2.
 \end{align*}
@@
 
-[no, just assume that the regressors are deterministic]
-
-This example illustrates the problems with in-sample forecast
-evaulation especially well, because we have finite sample
-distributions of the test statistics of interest, the $F$-test, AIC,
-and BIC.
-
-[text]
-
+This part illustrates the behavior of full-sample statistics in our
+simple example. To simplify the presentation even more, assume that
+the full-sample design matrix is orthogonal in-sample, not just in
+population, so $X_{2T}'X_{2T} = T \cdot I_{K_2 \times K_2}$, and again
+let $M_1$ and $M_2$ be the selection matrices for the first $K_1$ and
+the last $K_2-K_1$ elements of $\theta_2$. In this example,
 \begin{equation*}
   M_2 \bh{2T} \sim
-  N(M_2 \theta_2, \sigma^2/T)
-\end{equation*}
-where $M_2 = (0\ I)$. Given $\E_T \oosB = 0$ as well as the previous
-information set, and the density of $M_2 \bh{2T}$ concentrates
-uniformly on the surface of the sphere centered at $M_2 \theta_2$ and
-passing through the origin:
+  N(M_2 \theta_2, (1/T) \, I_{K_2-K_1})
+\end{equation*}
+and, conditional on $\E_T \oosB = 0$, the density of $M_2 \bh{2T}$
+concentrates uniformly on the surface of the sphere centered at $M_2
+\theta_2$ and passing through the origin:
 \begin{equation*}
@@
 \end{equation*}
-We can also represent the null $\E_T \oosB \leq 0$ by conditioning on
-$\E_T \oosB = -c$ for a fixed positive constant $c$. In that case, the
+To see intuitively that it must pass through the origin, note that the
+two models will give identical forecasts when $\bh{2T} = 0$ since the
+regressors are orthogonal. (Identical forecasts obviously have the
+same MSE.)
+
+This region is a cylinder in the original space, $\Re^{K_2}$.  We can
+also represent the null $\E_T \oosB \leq 0$ by conditioning on $\E_T
+\oosB = -d$ for a fixed positive constant $c$. In that case, the
 density of $M_2 \bh{2T}$ concentrates on the sphere
@@
   (M_2 \bh{2T} - M_2 \theta_2)'(M_2 \bh{2T} - M_2 \theta_2) =
-  \theta_2'M_2' M_2 \theta_2 + c
-\end{equation*}
-which has the same center but larger radius. What makes both
-distributions relatively easy to work with is that the estimators are
-uniformly distributed on the surface of each sphere.
-For other (stochastic) design matrices, the distribution of $M_2
-\bh{2T}$ is not uniform on the sphere and its location may be
-different, but the same general argument will hold.
-
-For the $F$-test we have, just as in Equation~\eqref{eq:17}
-\begin{equation}
+  \theta_2'M_2' M_2 \theta_2 + d
+\end{equation*}
+which has the same center but larger radius.
+
+For the $F$-test we have, as before,
+\begin{equation*}
   F = \tfrac{T}{s^2 (K_2 - K_1)} \bh{2T}' M_2' M_2 \bh{2T}.
-\end{equation}
+\end{equation*}
 We know that $\sqrt{T}(F - 1)$ is asymptotically normal
@@
 
-So if the unknown coeficients satisfy
+\input{floats/circles}
+\begin{figure}
+  \centering
+  \begin{tabular}{cc}
+  \subfloat[]{\circlefigA{1}{2.5}{1.4}{4.5}\label{fig:circleA}} &
+  \subfloat[]{\circlefigB{1}{2.5}{1.4}{4.5}\label{fig:circleB}}
+  \end{tabular}
+  \caption{Graphs indicating the rejection region and region of equal
+    generalization error for the models discussed in Section
+    \ref{sec:insample}.  The smaller model has no estimated parameters
+    and the larger has two coefficients.  The shaded regions in
+    Figures (a) and (b) show the rejection region and the acceptance
+    region respectively of the full-sample test given $\E_T \oosB \leq
+    0$. Here $e_1 = (1,0)$ and $e_2 = (0,1)$ are the first and second
+    selection vectors, so the horizontal axes represent changes in the
+    first unique element of $\bh{2T}$ and the vertical axes represent
+    changes in the second unique element.}
+\label{fig:rreject}
+\end{figure}
+
+This is perhaps best illustrated with a picture.
+Figure~\ref{fig:rreject} plots these quantities when $K_2 - K_1 =
+2$. The circle centered at the origin plots the threshold for the
+$F$-test; when $M_2 \bh{iT}$ falls outside this circle, the $F$-test
+rejects. The circle centered at $M_2 \theta_2$ plots the set of points
+for which $\E_T \oosB = 0$. The shaded region in
+Figure~\ref{fig:rreject}~(a) plots the rejection region given $\E_T
+\oosB \leq 0$ and the shaded region in Figure~\ref{fig:rreject}~(b)
+plots the acceptance region given $\E_T \oosB \leq 0$.
+
+In the picture, the unknown coefficients satisfy
 \begin{equation*}
@@
 \end{equation*}
-for large enough $T$, then the probability of rejecting the null
-hypothesis when it is at least as accurate as the altenative is
-equivalent to the probability that $\bh{2T}$ violates~\eqref{eq:26}
-given that it is uniformly distributed on the sphere
+so the center of the conditional distribution of $\bh{2T}$ given $\E_T
+\oosB \leq 0$ is outside the acceptance region of the $F$-test. When
+this is the case, the conditional probability that $\bh{2T}$ falls in
+the rejection region is less than 1/2, since $M_2 \bh{2T}$ is
+uniformly distributed on the cylindar
 \begin{equation*}
   (M_2 \bh{2T} - M_2 \theta_2)'(M_2 \bh{2T} - M_2 \theta_2) =
-  \theta_2'M_2' M_2 \theta_2 + c
-\end{equation*}
-for some positive $c$. Each individual element of $M_2 \bh{2T}$
-independently has probability less than $1/2$ of falling in the
-acceptance region, so the probability that at least one doesn't (all
-that is needed for rejection) is bounded (for large enough $T$)
-\begin{equation*}
-  1 - (1/2)^{K_2 - K_1}
-\end{equation*}
-which obviously converges to 1 as $K_2 - K_1 \to \infty$. The same
-bound also holds under the alternative $\E_T \oosB > 0$, so the
-$F$-test rejects with probability approaching 1 for these values of
-$\theta_2$, regardless of which model is more accurate.
-
+  \theta_2'M_2' M_2 \theta_2 + d
+\end{equation*}
+for some positive $d$.
+
+The AIC behaves essentially the same way. For the BIC, the radius of
+the cylander centered at the origin increases with $T$ and eventually
+encompasses the cylander centered at $M_2 \theta_2$, so it never
+selects the alternative once $T$ is large enough.
 \section{Monte Carlo}
@@
 This section presents two simulations that investigate the accuracy of
-our theory in small samples.%
-\footnote{Simulations were conducted in R \citep{Rde:10} using the
-  MASS \citep{VeR:02}, Matrix \citep{BM:13}, rlecuyer \citep{SR:12},
-  and RSQLite \citep{Jam:10} packages. Graphs were produced in R using
-  Lattice \citep{Sar:10} and tikzDevice \citep{ShB:11:0.6.1} as well
-  as the TikZ and PGF LaTeX packages \citep{Tan:10}} %
-The first looks at the asymptotic normality of the DMW statistic
-centered on either $\E_R \oosA$ or $\E_T \oosB$.  The previous
-section's results imply that centering on the first should give an
-approximately normal statistic and centering on the second should give
-a normal statistic when $P$ is small relative to $T$.  The second
-simulation looks at the size and power of several statistics when
-conducting inference about the difference in the models'
-generalization error.  For all of the simulations, we look at
-fixed-window OOS tests to speed up computation time.
+our theory in small samples.
+We do several Monte Carlo exercises. The first looks at wheather our
+theoretical results for the OOS average are accuarate: whether or not
+the OOS average is approximately normal, and whether it is centered on
+$\E_R \oosA$, $\E_T \oosB$, or somewhere else entierely. The second
+issue is whether or not the \oost\ test is \emph{useful} for
+conducting inference about $\E_T \oosB$. Our theoretical results
+suggest that it may not be, because we require $P^2/T \to 0$ for
+inference about $\E_T \oosB$ to be valid. A highly related issue is
+whether other statistics are useful for conducting inference about
+$\E_T \oosB$---again, our theoretical results suggest that they are
+not.
+
+We use the same DGP for all of these simulations, and it is described
+in the next subsection. Results are presented in the subsection after
+that. Simulations were conducted in R \citep{Rde:10} using the
+\emph{MASS} \citep{VeR:02}, \emph{Matrix} \citep{BM:13}, and
+\emph{rlecuyer} \citep{SR:12} and graphs are produced using
+\emph{Lattice} \citep{Sar:10}. In this paper, we present results for
+the fixed window, but recursive window results are available in a
+separate Appendix and are broadly similary.
 
@@
 environments---serial dependence, heteroskedasticity, and complicated
-DGPs.  We simulate data for both studies from the equation
+DGPs. The DGP we use is given by the equation
 \begin{equation}\label{eq:6}
@@
 in its intended application as well as for more parsimonious models.
-We let $T$ equal 100, 250, 500, or 1000.  We also vary $\theta$, and do
+We let $T$ equal 100, 250, or 500.  We also vary $\theta$, and do
 so giving the benchmark and the alternative model comparable weight in
@@
 accurate than the benchmark, and when $c$ is zero we're unlikely to
-draw such values of $X$ and $Y$.  For all of the studies, $L(x) =
-x^2$.
-
-The first set of simulations study how well the theory in
-Section~\ref{sec:oostheory} works in practice.  For each draw of $X$
-and $Y$, we construct a one-sided OOS interval of the
-form
+draw such values of $X$ and $Y$.  For all of the studies, $L(e) =
+e^2$.
+
+To study the accuracy of our theoretical approximations, we first
+estmate the coverage probabilities of OOS confidence intervals for
+$\E_R \oosA$ and $\E_T \oosB$. For each draw of $X$ and $Y$, we
+construct the one-sided OOS interval defined in
+Theorem~\ref{res:oostest}:
 \begin{equation*}
@@
 \end{equation*}
-for $P$ set to every 10th value between 1 and $2T/3$.  We calculate
-the percentage of these intervals that contain $\E_R \oosA$ and that
-contain $\E_T \oosB$.  Since the data are i.i.d., both of these
-quantities are easy to calculate:
-\begin{equation*}
-  E_R \oosA = \Bigg[\sum_{i=1}^{K_1} (\tilde{\theta}_{iR} - \theta_i)^2 +
-  \sum_{i=K_1+1}^{K_2}\theta_i^2\Bigg] - \sum_{i=1}^{K_2} (\hat{\theta}_{iR} -
-  \theta_i)^2
-\end{equation*}
-and
-\begin{equation*}
-  E_T \oosB = \Bigg[\sum_{i=1}^{K_1} (\tilde{\theta}_{iT} - \theta_i)^2 +
-  \sum_{i=K_1+1}^{K_2}\theta_i^2\Bigg] - \sum_{i=1}^{K_2} (\hat{\theta}_{iT} -
-  \theta_i)^2
-\end{equation*}
-where $\tilde{\theta}$ indicates that the coefficient is estimated
-using only the regressors in the benchmark model and $\hat{\theta}$
-the full model.  We draw 2000 samples for each combination of the
-design parameters.
-
-The second simulation looks at the size and power of the test
-statistics when conducting inference about the models' generalization
-error.  The null hypothesis we test is
-\begin{equation}\label{eq:9}
+for $P = 10,\dots,2T/3$; we then calculate the percentage of
+simulations where these intervals contain $\E_R \oosA$ and the
+percentage that contain $\E_T \oosB$.  Since the data are i.i.d., both
+of these quantities are easy to calculate (see
+Section~\ref{sec:example}). For these calculations, we draw 2000
+samples for each combination of the design parameters.
+
+Our second set of results studies whether these different OOS and
+in-sample statistics are valid for testing the null hypothesis
+\begin{equation*}
   H_0:\quad E_T \oosB \leq 0,
-\end{equation}
+\end{equation*}
+namely that the benchmark model is expected to be more accurate in the
+future than the alternative. Informally, we are interested in whether
+the conditional probability
+\begin{equation*}
+  \Pr[\text{test rejects} \mid E_T \oosB \leq 0] \leq \alpha
+\end{equation*}
+where $\alpha$ is the nominal size of the test. If this inequality
+does not hold, the test statistic is rejecting the benchmark model too
+often.
+
 We look at four different statistics---the full-sample $F$-test, the
-DMW $t$-test, the
-OOS $t$-test using McCracken's (2007)
-critical values,%
-\footnote{These critical values are not published for
-  $K_2-K_1>10$, so we do not report them for $K_2 = T/10$.} %
-and Clark and West's (2006, 2007) Gaussian out-of-sample
-statistic.%
-\footnote{Clark and West (2006, 2007) derive their statistic
-using the rolling window estimation scheme.  Here we use the same
-statistic, but with a fixed window scheme.} %
-For the $F$-test, we simply test whether the coefficients on the larger
-model are nonzero.  For the out-of-sample tests, we conduct a
-one-sided test of out-of-sample performance for every 10th value of
-$P$ as before.
-
-To estimate each test's size for the hypothesis \eqref{eq:9}, we draw
-samples from the DGP and discard those for which \eqref{eq:9} does
-not hold, until we have 2000 for each choice of the design parameters.
-The estimated size is the fraction of those samples in which the test
-statistic rejects.
+DMW $t$-test, the OOS $t$-test using McCracken's (2007) critical
+values,%
+\footnote{These critical values are not published for $K_2-K_1>10$, so
+  we do not report them for $K_2 = T/10$.} %
+and Clark and West's (2006, 2007) Gaussian out-of-sample statistic.%
+\footnote{Clark and West (2006, 2007) derive their statistic using the
+  rolling window estimation scheme. Here we use the same statistic,
+  but with a fixed window scheme. A supplemental appendix presents
+  results for their statistic, using the recursive window.} %
+For the $F$-test, we simply test whether the coefficients on the
+larger model are nonzero.  For the out-of-sample tests, we conduct a
+one-sided test of out-of-sample performance for every value of $P$ as
+before. For each of these simulations, we discard draws from the DGP
+that violate the null hypothesis $E_T \oosB \leq 0$ and then use the
+remaining samples to calculate the conditional probability that each
+test rejects. The simulations end when 2000 draws have been retained
+for each choice of the design parameters.
 
@@
 coverage probability of these intervals as a function of $P$ for each
-combination of $T$, $K_1$ and $K_2$, and $c$.  The gray horizontal
-line shows the intervals' nominal coverage probability.  Each panel
-displays the coverage for a different choice of interval, centering
-term ($\E_R \oosA$ or $\E_T \oosB$) and combination of design
-parameters.
+combination of $T$, $K_1$ and $K_2$, and $c$.  The nominal coverage is
+90\%.  The gray horizontal line shows the intervals' nominal coverage
+probability.  Each panel displays the coverage for a different choice
+of design parameters.
 
@@
 is very small.  The poor behavior for small $P$ is unsurprising, as it
-simply means that the CLT is a poor approximation when the test
-sample is small.  The intervals' good coverage holds even for the
-parsimonious models ($K_1=1$ and $K_2= 3$) which our theory does not
-necessarily apply to.
+simply means that the CLT is a poor approximation when the test sample
+is small. The inteval for $T = 100$, $K = T/10$, and $c = 0$ is the
+worst, with actual coverage near 85\% for most values of $P/T$. But
+the others are much closer to nominal coverage, even for the
+parsimonious models ($K_1=1$ and $K_2= 3$) where one might expect
+the theoretical results to break down.
 
 Figure~\ref{fig:interval-T} gives the results for $\E_T \oosB$.  In
-rows 2, 4, 6, and 8---the overfit models---the coverage is near
-nominal coverage for moderately small values of $P$.  As $P$ increases
-to $2T/3$, the coverage increases to 1.  With the parsimonious model,
-the coverage is near nominal coverage for all $P$ for the one-sided
-interval with $c=1$, but only for moderately small $P$ when $c=0$.
+columns 2 and 4---the overfit models---the coverage is near nominal
+coverage for moderately small values of $P$.  As $P$ increases to
+$2T/3$, the coverage increases above nominal size; near 100\% for some
+DGPs.  With the parsimonious model, the coverage is near nominal
+coverage for all $P$ for the one-sided interval with $c=1$, but only
+for moderately small $P$ when $c=0$.
 
 The behavior for $K_2 = T/10$ is exactly what our theory predicts.
-When $P^2/T$ is small, the coverage is near nominal levels.  The
-behavior as $P$ increases, combined with the results for $\E_R
-\oosA$, indicate that $\E_T \oosB \geq E_R \oosA$ in general.
-Since
-\[E_{T} \oosB = E_{R} \oosA + (E_{T} \oosB - E_{R} \oosA), \] and the
-interval is approximately centered at $\E_R \oosA$, the difference
-$\E_{T} \oosB - E_{R} \oosA$ adds a substantial positive quantity when
-$P^2/T$ is not near zero, increasing the coverage of the one-sided
-interval.
-
-We next present the size simulations,
-Figures~\ref{fig:ftest}--\ref{fig:ttest-power}.  For the OOS tests,
-the conditional rejection probability is plotted for each combination
-of $T$, $K_1$, $K_2$, and $c$ as a function of $P$.  The $F$-test does
-not depend on $P$, so a single value is presented for each
-combination.
-
-We'll look at the $F$-test first.  To make comparisons easier, the size
-is displayed as a dot plot in Figure~\ref{fig:ftest}.  Different
-panels display a different combination of $K_1$, $K_2$, and $T$, and
-each individual plot shows the empirical size for each choice of $c$.
-We see immediately that the actual and nominal size are essentially
-equal for $c = 0$, which is unsurprising.  For $c = 0$, the $F$-test is
-exact; moreover, the larger model will almost always be less accurate
-than the smaller one, so conditioning on $\E_T \oosB \leq 0$ is
-almost unrestrictive.  When $c$ increases, though, the $F$-test
-overrejects badly---rejecting at roughly 50\% when $c = 1$ for the
-parsimonious model and from 70\% to 100\% for the overfit model.  As
-our discussion in Section~\ref{sec:insample} predicts, the rejection
-probability increases with $T$ for the overfit model but does not
-depend on $T$ for the small model.
+When $P^2/T$ is small, the coverage is close to nominal levels.  The
+behavior as $P$ increases, combined with the results for $\E_R \oosA$,
+indicate that typically $\E_T \oosB \geq E_R \oosA$.  Since
+\begin{equation*}
+  E_{T} \oosB = E_{R} \oosA + (E_{T} \oosB - E_{R} \oosA),
+\end{equation*}
+and the interval is approximately centered at $\E_R \oosA$, the
+difference $\E_{T} \oosB - E_{R} \oosA$ adds a substantial positive
+quantity when $P^2/T$ is not near zero, increasing the coverage of the
+one-sided interval.
+
+We present the size simulations next, in
+Figures~\ref{fig:ftest}--\ref{fig:ttest-power}.  For the OOS tests
+We plot each OOS test's conditional rejection probability,
+\begin{equation*}
+  \Pr[\text{test rejects} \mid E_T \oosB \leq 0],
+\end{equation*}
+for each combination of $T$, $K_1$, $K_2$, and $c$ as a function of
+$P$.  The $F$-test does not depend on $P$, so we calculate and
+tabluate it's conditional rejection probability as a single value for
+each combination of design parameters.
+
+Table~\ref{fig:ftest} summarizes the simulation results for the
+$F$-test. For $c = 0$, the estimated conditional rejection probability
+is almost exactly equal to the test's nominal size (10\%), which is
+unsurprising.  For $c = 0$, the $F$-test is exact; moreover, the
+larger model will almost always be less accurate than the smaller one,
+so conditioning on $\E_T \oosB \leq 0$ is almost unrestrictive.  When
+$c$ increases, though, the $F$-test overrejects badly---rejecting at
+roughly 50\% when $c = 1$ for the parsimonious model and from 70\% to
+100\% for the overfit model. This agrees with our
+Section~\ref{sec:insample} results and matches results seen in
+empirical practice: the $F$-test rejects the benchmark with very high
+probability, even though it is, by construction, more accurate than
+the alternative model.
 
 Figure~\ref{fig:ttest-size} presents the size estimates for the DMW
-$t$-test.  Again, different panels display results for different
+\oost\ test.  Again, different panels display results for different
 combinations of the design parameters.  Each graph plots the rejection
@@
 
-Results using \citepos{Mcc:07} critical values are
-presented in Figure~\ref{fig:mccracken} and are similar to those using
-Clark and West's test.  For $c=0$ the rejection probability is nearly
-the test's nominal size.  For $c=1$, the rejection probability
-increases with $P/T$, from close to the nominal size when $P/T$ is
-small to over 25\% when $P/T = 2/3$.  Note that all of the simulations
-use the parsimonious model.  McCracken's statistic overrejects here
-by slightly less than Clark and West's, but still by a substantial
-amount.
-
-Since the DMW test tends to have low rejection probability, the
-test's power is a concern.  We'll present some power results,
-simulating from \eqref{eq:1} with $c = 1$ or 2 subject to the
-constraint that $\E_T \oosB > 0$.%
-\footnote{Draws of $X$ and $Y$ with
-  $\E_T \oosB > 0$ are very rare when $c=0$, so we do not present
-  results for that value of $c$.} %
-Figure~\ref{fig:ttest-power} plots
-the power for the DMW test; since the other test statistics greatly
-overreject, we do not present their power.  For $c=1$, the power is
-never greater than nominal size and decreases to zero as $P/T$
-increases for the overfit model.  For $c=2$ the power is better,
-increasing with $P/T$ for a stretch and then decreasing as $P/T$ grows
-beyond approximately 1/4 for the overfit model.  Larger values of $T$
-give a higher peak and greater power overall, but the power still
-falls to nearly zero if $P/T$ is too large (approximately 2/3 in our
-simulations).  The power with the parsimonious model is typically
-quite low but greater than nominal size for $c = 2$.
+Results using \citepos{Mcc:07} critical values are presented in
+Figure~\ref{fig:mccracken} and are similar to those using Clark and
+West's test.  For $c=0$ the rejection probability is nearly the test's
+nominal size.  For $c=1$, the rejection probability increases with
+$P/T$, from close to the nominal size when $P/T$ is small to over 25\%
+when $P/T = 2/3$.  Note that all of the simulations use the
+parsimonious model.  McCracken's statistic overrejects here by
+slightly less than Clark and West's, but still by a substantial
+amount. Note that we are unable to plot results for McCracken's
+statistic when $K/T = 10$, which is where the brakdown in Clark and
+West's test is most pronounced.
+
+Since the DMW test tends to have low rejection probability, the test's
+power is a concern.  Figure~\ref{fig:ttest-power} power results for
+the DMW test, simulating from \eqref{eq:1} with $c = 1$ or 2 subject
+to the constraint that $\E_T \oosB > 0$.%
+\footnote{Draws of $X$ and $Y$ with $\E_T \oosB > 0$ are very rare
+  when $c=0$, so we do not present results for that value of $c$.} %
+Since the other test statistics greatly overreject, we do not present
+their power.  For $c=1$, the power is never greater than nominal size
+and decreases to zero as $P/T$ increases for the overfit model.  For
+$c=2$ the power is better, increasing with $P/T$ at first stretch and
+then decreasing as $P/T$ grows beyond approximately 1/4 for the
+overfit model.  Larger values of $T$ give a higher peak and greater
+power overall, but the power still falls to nearly zero if $P/T$ is
+too large (approximately 2/3 in our simulations).  The power with the
+parsimonious model is typically quite low but greater than nominal
+size for $c = 2$.
 
@@
 nominal size when testing the null $\E_T \oosB \leq 0$.  Moreover,
-these simulations demonstrate that the restriction $P^2/T \to 0$ is
-binding in practice, as the DMW test under-rejects and has very low
-power when it is not satisfied.
+these simulations demonstrate that the restriction that $P$ be small
+is binding in practice, as the DMW test under-rejects and has very low
+power when $P$ is too large.
 
@@
 
-This section presents an analysis of equity premium predictability
-similar to \citet{GoW:08}.%
-\footnote{Calculations in this section are done in R \citep{Rde:10}
-  using the lmtest \citep{ZeH:02} and sandwich \citep{Zei:04}
-  packages. Tables and grapsh were prepared with the Hmsic
-  \citep{Har:10} and tikzDevice \citep{ShB:11:0.6.1} R packages as
-  well as the TikZ and PGF LaTeX packages \citep{Tan:10}} %
-We estimate the expected forecasting
-performance of the largest model they consider, a model with 13
-regressors, using 81 observations (annual data from 1928 to 2009).  We
-construct confidence intervals for the difference in performance
-between this model and a prevailing mean benchmark, and do so for
-different values of $R$ and $P$ to examine the effect of the training
-and test sample choice on this OOS statistic.  We find that the
-estimate of the larger model's Mean Squared Error (MSE) decreases relative to the
-benchmark as $R$ increases, but it is never smaller than the
-benchmark's.  This result, combined with the larger model's in-sample
-significance, suggests that there may be a real relationship between
-the equity premium and some of these predictors, but that the
-relationship can not be estimated accurately enough to be useful for
-forecasting and supports \citepos{GoW:08} conclusions.  These results
-hold even when imposing \citepos{CaT:08} restriction that the equity
-premium forecast be non-negative.
-
-We'll start with a very brief review.  \citet{GoW:08}
-study the OOS forecasting performance of different variables thought
-to predict the equity premium (calculated as the difference between
-the return on the S\&P 500 index and the T-bill rate).  Some of these
-variables are listed in
-Table~\ref{tab:equity}.%
-\footnote{Table~\ref{tab:equity} only lists the
-  variables used in \citepos{GoW:08} ``kitchen sink''
-  model.  Some of the variables that they use in bivariate models are
-  excluded from this model either because the series are too short or
-  because the variables are linear combinations of other variables.} %
-\citet{GoW:08} estimate the OOS forecasting
-performance of bivariate models of the form
+This section presents a study of equity premium predictability based
+on \citet{GoW:08}. Goyal and Welch conduct an out of sample analysis
+of 18 different variables thought, based on previous research, to
+predict the equity premium (calculated as the difference between the
+return on the S\&P 500 index and the T-bill rate).%
+\footnote{\citet{GoW:08} builds on previous research by \citet{BoH:99}
+  and \cite{GoW:03}.} %
+Their analysis has two notable features: they compare different
+predictors across the same time periods and frequency as much as
+possible, making the accuracy of these predictors directly comparable;
+many of the papers that originally proposed these predictors used
+different time periods, methods, or observational frequencies so their
+results were not directly comparable. And Goyal and Welch compare
+these predictors out-of-sample; many of the original studies found
+in-sample evidence of equity premium predictability but did not look
+at out-of-sample evidence.
+
+Goyal and Welch consider many different models; most of them are very
+simple---regression onto a constant and a single stochastic
+predictor---but some are more complicated. They find that essentially
+none of the models outperform a simple benchmark, the prevailing mean
+of the equity premium, and conclude that these variables do not
+predict the equity premium. A large literature has subsequently sought
+to explain or rebut these results, including several responses to
+Goyal and Welch's original working paper published in the same special
+issue of \textit{The Review of Financial Studies} as \citet{GoW:08}.%
+\footnote{Those papers are \citet{CaT:08}, \citet{Coc:08},
+  \citet{BRW:08}, and \citet{LeN:08}.} %
+
+\citet{GoW:08}, as well as \citet{BoH:99}, \citet{LeN:08}, and many
+other authors, propose that instability could explain the OOS failure
+of these models. However, we have shown in this paper that overfit can
+also explain this pattern, significant in-sample results that do not
+hold up out of sample. In this section, we explore the extent to which
+overfit is a potential concern in this data set and estimate the
+expected forecasting performance of the largest model they consider, a
+model with 13 regressors, using 81 observations (annual data from 1928
+to 2009). The predictors are listed in Table~\ref{tab:equity}; please
+see Goyal and Welch's original paper for detailed information about
+these variables.%
+\footnote{Table~\ref{tab:equity} only lists the variables used in
+  \citepos{GoW:08} ``kitchen sink'' model.  Some of the variables that
+  they use are excluded from this model either
+  because the series are too short or because the variables are linear
+  combinations of other variables.} %
+
+\citet{GoW:08} focus primarily on univariate regression models of the
+form
 \[
-r_{t+1} = \beta_0 + \beta_1 x_t + \e_{t+1}
+r_{t+1} = \beta_0 + \beta_1 x_{it} + \e_{t+1}
 \]
 using OLS with a recursive window, where $r_{t+1}$ is the equity
-premium and $x_t$ is a generic predictor, as well as some larger
-models.  They find that these models forecast no better than the
-prevailing mean of the equity premium.
-\citet{CaT:08} find that nonlinear extensions of
-Goyal and Welch's models are more accurate, either imposing sign
-restrictions on the estimated coefficients or imposing that the
-forecast be non-negative, but do not test for significance.
-
-Obviously, \citepos{GoW:08} bivariate models do not
-match the asymptotic theory of this paper, so we restrict our
-attention here to their ``kitchen sink'' model, which includes all of
-the variables, except for a few dropped because of data availability or
-(perfect) multicollinearity.  Formally, the benchmark and alternative models are
-\begin{eqnarray}
-  \label{eq:3}
-  r_{t+1} &=& \mu + \e_{1,t+1} \\
-  \label{eq:2}
-r_{t+1} &=& \beta_0 + \sum_{i=1}^K \beta_{i} x_{it} + \e_{2,t+1}
-\end{eqnarray}
-respectively and are estimated by OLS using the fixed-window scheme.
-The predictors are listed in Table~\ref{tab:equity}; for a detailed
-description of each predictor, please see Goyal and Welch's original
-paper.  In this model, there are 13 regressors (including the constant
-term) and we estimate the coefficients using annual data from 1928 to
-2009.  This makes the ratio $K/T$ equal to about 0.16.  We also
-present results for one of \citepos{CaT:08}
-restricted forecasting models.  For this model, we estimate
-\eqref{eq:3} and \eqref{eq:2}, but impose that $\hat r_{t+1}$ be
-non-negative for each forecast.  We then calculate the OOS test just
-as for the unconstrained model.
-
-Table~\ref{tab:gwinsample} gives the results of the full sample
-regression for Equation~\eqref{eq:2}, using Newey-West standard errors
-with two lags \citep{NeW:87}.%
-\footnote{We compare the test statistic
-  to critical values from the $F$-distribution.} %
-The $p$-value is
-very small (less than 0.01), indicating that the coefficients are
-nonzero in population and at least one of these predictors is
-correlated with the equity premium.  As we argue earlier, this result
-does not imply that the model will forecast well, which we look at
-next.
-
+premium and $x_{it}$ is one of the predictors listed in
+Table~\ref{tab:equity}.%
+\footnote{To make it easier to compare coefficients across variables
+  and models, all of the regressors are studentized before our
+  analysis and the equity premium is reported in basis points.} %
+This focus is consistent with much of the rest of the literature. But
+it is not clear that this approach---using a large number of
+restricted models---is any more reliable than using a single, large
+model. Very few papers in the equity-premium predictability literature
+explicitly account for the multiplicity of model comparisons%
+\footnote{\citet{RaW:06}, \citet{RaZ:12}, and \citet{Cal:13b} are
+  exceptions.} %
+and most widely-used statistics for multiple comparisons are
+derived under the assumption that there is a finite number of
+hypotheses or models (as is the case in \citealp{STW:99c},
+\citealp{Whi:00}, \citealp{Han:05}, and \citealp{LeR:05}), so there is
+little theoretical evidence that they are any more reliable than a
+regression model that encompasses all of the smaller models. Moreover,
+since \citet{GoW:08} (along with most of the rest of the literature)
+want to interpret these univariate regressions as meaningful
+statements about the true relationships between the equity premium and
+the regressors, omitted variable bias is a serious potential issue.
+
+For example, Table~\ref{tab:gwinsample} presents two full-sample
+coefficient estimates for each of the 12 predictors we consider.%
+\footnote{For all of our full sample results, we studentize the
+  regressors to make it easier to compare coefficient estimates and we
+  express the equity premium in basis points.} %
+The first column is the estimator of the coefficient on the listed
+variable in the full regression,
+\begin{equation*}
+  r_{t+1} = \beta_0 + \sum_{i=1}^{12} \beta_{i} x_{it} + \e_{t+1},
+\end{equation*}
+and the third column is the $p$-value associated with a two-sided
+$t$-test that the coefficient is zero in population. The second column
+is the estimator of the coefficient from the univariate regression
+\begin{equation*}
+  r_{t+1} = \alpha_i + \gamma_{i} x_{it} + \e_{t+1},
+\end{equation*}
+and the fourth column is the $p$-value associated with its $t$-test.%
+\footnote{All of the standard errors were calculated using a
+  Newey-West kernel with two lags.} %
+Some of the coefficient estimates agree, but some do not. The
+coefficient estimate for the \emph{default yield spread}, for example,
+is substantially and significantly negative in the full model ($-7.79$
+with $p$-value $0.042$), but is near zero in the univariate regression
+($0.79$ with $p$-value $0.720$). This pair of results implies that the
+the default yield spread contains information about the equity premium
+but is also correlated with other poor predictors, and that this
+additional correlation adds noise to the univariate regression
+and masks the true relationship. Similarly, \emph{net equity expansion}
+is significant at 10\% in the univariate regression but not in the
+full model ($p$-values of $0.060$ and $0.626$ respectively), which is
+likely attributable to omitted variable bias. So there is merit to
+studying a large model that includes all of the variables.
+
+Results for the full sample estimates of these models are in
+Table~\ref{tab:gwinsample}.%
+\footnote{Calculations in this section are done in R \citep{Rde:10}
+  using the \emph{lmtest} \citep{ZeH:02} and \emph{sandwich}
+  \citep{Zei:04} packages. Tables and graphs were prepared with the
+  \emph{dbframe} \citep{Cal:10b}, \emph{Hmsic} \citep{Har:10},
+  \emph{tikzDevice} \citep{ShB:11:0.6.1}, and \emph{xtable}
+  \citep{Dah:09} R packages as well as the \emph{booktabs}
+  \citep{FeE:05} and \emph{TikZ and PGF} LaTeX packages
+  \citep{Tan:10}}%
+\footnote{We compare the test statistic to critical values from the
+  $F$-distribution, which has been shown to be more reliable when
+  there are many regressors \citep{Ana:12,Cal:11c}.} %
+The last rows of the table list measures of the full-model fit.  The
+$p$-value for the test of full model fit is very small (less than
+0.01), indicating that the coefficients are nonzero in population and
+at least one of these predictors is correlated with the equity
+premium.%
+\footnote{We have done additional analysis to try to identify which
+  predictors were correlated with the equity premium, but none of the
+  individual regressors were significant after correcting for
+  multiplicity. The Bonferroni correction, for example, suggests that
+  an individual $p$-value would need to be less than $0.10/12 \approx
+  0.0083$ for its corresponding coefficient to be significant at the
+  10\% level, but the smallest $p$-value is $0.035$. One can improve
+  on the Bonferroni correction, but a comprehensive analysis is beyond
+  the scope of this paper.} %
+As we argue throughout the paper, this result does not imply that the
+model will forecast well.
+
+To determine whether the full model can forecast well, we use the DMW
+\oost\ test to compare it to a sample mean benchmark,
+\begin{equation*}
+r_{t+1} = \mu + \e_{1,t+1}.
+\end{equation*}
+Both models are estimated by OLS using the fixed-window scheme. We
+also present results for a restricted model proposed by
+\citet{CaT:08} that imposes that $\hat r_{t+1}$ be non-negative for
+each forecast.
 To study the effect of the training sample size on the DMW statistic, we
@@
 the larger model relative to the smaller, but this may not hold in
-this particular dataset.
-
-Figures~\ref{fig:empirics1} plots the OLS results and
+this particular dataset. For the OOS results, we express the equity
+premium in percentage points.
+
+Figure~\ref{fig:empirics1} plots the OLS results and
 Figure~\ref{fig:empirics2} imposes \citepos{CaT:08} restriction. The
@@
 shaded region indicates the 95\% one-sided confidence interval implied
-by the DMW test.  Negative numbers indicate that the kitchen sink
-model has higher out-of-sample loss.  We can see that the same
-patterns hold for both models: the performance difference decreases as
-$R$ grows, but the kitchen sink model is never more accurate.  We also
-see that the performance difference decreases suddenly over the period
-$R=29$ to $R=34$ (corresponding to the years 1956--1961).
+by the DMW test.  Negative numbers indicate that the full model has
+higher out-of-sample loss.  We can see that the same patterns hold for
+both models: the performance difference decreases as $R$ grows, but
+the full model is never more accurate.  We also see that the
+performance difference decreases suddenly over the period $R=29$ to
+$R=34$ (corresponding to the years 1956--1961).
 Figure~\ref{fig:empirics3} plots the accuracy of the individual
 forecasts (only for the linear models) and shows that this change is
-the result of a sudden improvement in the kitchen sink model.  This
-change may indicate instability in the underlying relationship, as
-\citet{GoW:08} propose.
+the result of a sudden improvement in the full model.  This change may
+indicate instability in the underlying relationship, as proposed by
+\citet{GoW:08}.
 
 In summary, we fail to reject the null that the benchmark prevailing
-mean model is more accurate than \citepos{GoW:08} kitchen sink.  This
-result is consistent with Goyal and Welch's original analysis.  Unlike
-Goyal and Welch, we attribute this result, at least in part, to
-parameter uncertainty---the full sample results indicate that the
-larger model could predict better than the benchmark with enough
-data.%
+mean model is more accurate than the full model including all of
+\citepos{GoW:08} predictors.  This result is consistent with Goyal and
+Welch's original analysis.  Unlike Goyal and Welch, we attribute this
+result, at least in part, to parameter uncertainty---the full sample
+results indicate that there is a true predictive relationship between
+some of these variables and the equity premium and the larger model
+could predict better than the benchmark with enough data.%
 \footnote{\citet{BWB:10} make a similar point about exchange rate
   models, but see also \citet{Chi:10} and \citet{Gia:10}.} %
-Obviously, this is an illustrative exercise only and is not meant to
-be comprehensive.  In this dataset, there is likely parameter
-instability that we have not addressed, and we have not dealt with
-variable persistence at all.  However, as we mention earlier, our
-requirement that $P$ be small should let our theoretical results
-extend to moderate instability, and the fact that we do not rely on
-the asymptotic distribution of the coefficient estimates should
-mitigate the effect of persistence as well.
+These also indicate that combination or shrinkage estimators of the
+full model could significantly improve on the benchmark.%
+\footnote{See \citet{RaZ:12} for a recent review of this
+  literature.} %
 
@@
 coefficient of absolute regularity:
-\[
+\begin{equation}
 \beta(X,Y) = \sup_{A \in \sigma(Y)} \E \lvert \Pr(A \mid \sigma(X))
   - \Pr(A) \rvert.
-\]
+\end{equation}
+
 \begin{lem}\label{lem-berbee}\quad
@@
   $p > 2$, that satisfy ${\Pr[X \neq X^*] = c}$.  Then
-  \[
+  \begin{equation}
     \lVert X - X^* \rVert_2 \leq 2^{1/p} (\lVert X \rVert_p + \lVert
     X^* \rVert_p) c^{(p-2)/2p}
-  \]
+  \end{equation}
 \end{lem}
@@
   sequence of integers such that $b_T \to \infty$ and $b_T = o(P)$ and define
-  \begin{equation*}
+  \begin{equation}
     Z_i = \ZDef.
-  \end{equation*}
+  \end{equation}
   Then
@@
   Then
-  \begin{equation*}
+  \begin{equation}
     \sh^2 - P^{-1} \sum_{s,t=R+1}^{T-h} (D_s - \E_R
     D_s) (D_t - \E_R D_t) W((t-s)/\gamma) \to^{L_1} 0.
-  \end{equation*}
+  \end{equation}
 \end{lem}
@@
 
-Applying the Cauchy-Scwarz inequality twice and simplifying gives the
+Applying the Cauchy-Schwarz inequality twice and simplifying gives the
 upper bound
@@
 Define
-\[\label{eq:z1}
+\begin{equation*}
   Z_i = \ZDef
-\]
+\end{equation*}
 where $b_T$ is a sequence that satisfies $b_T\leq P$,
@@
 long as
-\begin{equation}\label{eq:cltvar2}
+\begin{equation*}
   \sigma^2 - \SumOuterBlock{i} \E_R Z_i^2 \to^p 0,
-\end{equation}
+\end{equation*}
 and
-\begin{equation}\label{eq:cltvar1}
+\begin{equation*}
   \SumOuterBlock{i} \E_R Z_i^2 - \SumOuterBlock{i} \ZSqCE \to^p 0.%
@@
     unnecessary---see the remarks after their result.} %
-\end{equation}
-Equation (\ref{eq:cltvar2}) holds as in \citet{Jon:97} (see the proof
-of his Theorem 2); (\ref{eq:cltvar1}) is ensured by
+\end{equation*}
+The first equation holds as in \citet{Jon:97} (see the proof
+of his Theorem 2); the second is ensured by
 Lemma~\ref{lem:a2}. \qed
@@
     x_{#1}^{*\prime}\bh{#1R}) - L(y^{*} - x_{#1}^{*\prime}\bh{#1T})}}
-
-For the second part:
-\begin{quotation}
-  Notice that, if the observations are i.i.d. and $(y_{t+h}, x_{it})
-  \sim N(0,I)$, $(\hat{\theta}_{iR} - \hat{\theta}_{iT}) \sim N(0,
-  (X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1})$ given $X_{iT}$, and so
-  $\var(x_{i,T+1}'\hat{\theta}_{iR} - x_{i,T+1}' \hat{\theta}_{iT})
-  \gg P K_i / (R - K_2)(T - K_2)$.
-\end{quotation}
 
@@
 
-Define $V = (X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}$ and $W =
-X_{iR}'\eb_{iR} \eb_{iR}X_{iR}$. The first term in the upper bound
-satisfies
-\begin{align}
+To simplify notation, define $V = (X_{iT}'X_{iT})^{-1} -
+(X_{iR}'X_{iR})^{-1}$ and $W = X_{iR}'\eb_{iR} \eb_{iR}'X_{iR}$. The
+first term in the upper bound satisfies
+\begin{align*}
   \| x_i^{*\prime} V X_{iR}' \eb_{iR} \|_2^2
-  &= O(1) \cdot \E \tr\big( V^2 W \big) \\
-  \label{eq:14}
-  &= O(1) \big( \E \tr\{ V^2 \E(W \mid X_{iR}'X_{iR})\}
-  + \E \tr\{ V^2 (W - \E(W \mid X_{iR}'X_{iR}))\}\big)
-\end{align}
-since $\eigen_{K_i}(\E x_i x_i') = O(1)$ by assumption.
-
-To show that the first term in~\eqref{eq:14} converges to zero at the
-right rate, observe that
-\begin{equation}
-  \E \tr\{ V^2 \E(W \mid X_{iR}'X_{iR})\}
-  \leq \bigg\rVert
-  \eigen_{K_i}(\E(W \mid X_{iR}'X_{iR})) \bigg\rVert_3
-  \bigg\rVert \sum_{i=1}^{K_i} \eigen_i^2 \big(V\big) \bigg\rVert_{3/2}.
-\end{equation}
-The first term in this product is $O(R)$ by
-Assumption~\ref{asmp-2}. For the second term, observe that
+  &\leq \eigen_{K_i}(\E x_i^* x_i^{*\prime}) \cdot \E \tr\big( V^2 W \big) \\
+  &= O(1) \cdot \E \tr\{ V^2 \E(W \mid
+  X_{iR}'X_{iR}, x_{i,R-\h+1} x_{i,R-\h+1}',\dots, x_{i,T-\h} x_{i,T-\h}')\}
+\end{align*}
+by assumption. Observe that
+\begin{multline*}
+  \E \tr\{ V^2 \E(W \mid X_{iR}'X_{iR}, x_{i,R-\h+1} x_{i,R-\h+1}',\dots, x_{i,T-\h} x_{i,T-\h}')\}
+  \\ \leq
+  \Big\rVert \sum_{i=1}^{K_i} \eigen_i^2 \big(V\big) \Big\rVert_{3/2}
+  \big\rVert \eigen_{K_i}(\E(W \mid
+  X_{iR}'X_{iR}, x_{i,R-\h+1} x_{i,R-\h+1}',\dots, x_{i,T-\h} x_{i,T-\h}')) \big\rVert_3.
+\end{multline*}
+The second term in this product is $O(R)$ by
+Assumption~\ref{asmp-2}. To bound the first term, note that
 $(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}$ has rank $P$ and
-each of its nonzero eigenvalues are bounded in absolute value by the
-eigenvalues of $(X_{iR}'X_{iR})^{-1}$. The eivenvalues of
+each of its nonzero eigenvalues is bounded in absolute value by the
+eigenvalues of $(X_{iR}'X_{iR})^{-1}$. The eigenvalues of
 $(X_{iR}'X_{iR})^{-1}$ are $O_{L_3}(1/R)$ by Assumption~\ref{asmp-2}, so
@@
   \leq \Big\|\sum_{j=K_i - P+1}^{K_i} \eigen_j^2(V) \Big\|_{3/2}
-  = O(P/R^2)
-\end{equation*}
-and, consequently,
-\begin{equation*}
-  \E \tr\bigg\{
-  [(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}]^2
-  \E(X_{iR}'\eb_{iR} \eb_{iR}X_{iR} \mid X_{iR}'X_{iR})\bigg\} = O(P/R).
-\end{equation*}
-
-For the second term in~\eqref{eq:14}, define for each $s=\h+1,\dots,R$,
-\begin{equation*}
-  w_{is} = x_{i,s-\h} x_{i,s-\h}' \e_{i,s}^2 + \1\{s > \h+1\}
-  \sum_{t=\h+1}^{s-1} (x_{i,s-\h} x_{i,t-\h}' + x_{i,t-\h} x_{i,s-\h}')
-  \e_{i,s} \e_{i,t}
-\end{equation*}
-and observe that $W = \sum_{s=\h+1}^{R} w_{is}$. Now use
-Lemma~\ref{lem-berbee} to define new random variables $w_{is}^*$ for
-each $s$ that are independent of $\sigma(x_{R+1},\dots,x_{T-\h})$ and
-satisfy
-\begin{equation*}
-  \Pr[w_{is} \neq w_{is}^*] \leq \beta_{R -\h + 1- s}.
-\end{equation*}
-By construction,
-\begin{equation*}
-  \E\bigg(\sum_{t=\h+1}^R w_{it}^*\ \big|\ X_{iR}'X_{iR}, X_{iT}'X_{iT}\bigg)
-  =  \E\bigg(\sum_{t=\h+1}^R w_{it}^*\ \big|\ X_{iR}'X_{iR}\bigg) \quad\text{a.s.}
-\end{equation*}
-and we can rewrite the second term in~\eqref{eq:14} as
-\begin{align*}
-  \E \tr&\{ V^2 (W - \E(W \mid X_{iR}'X_{iR}))\}\big) \\
-  &= \E \tr\bigg\{V^2 \sum_{t=\h+1}^R \big(\E(w_{it} - w_{it}^* \mid
-  X_{iR}'X_{iR}, X_{iT}'X_{iT}) - \E(w_{it} - w_{it}^* \mid
-  X_{iR}'X_{iR})\big) \Bigg\} \\
-  &= \E \sum_{t=\h+1}^R \big(\tr\{V^2 (w_{it} - w_{it}^*)\}
-  - \E(\tr\{\E(V^2 \mid X_{iR}'X_{iR}) (w_{it} - w_{it}^*)\} \mid
-  X_{iR}'X_{iR}) \big) \\
-  &= \E \sum_{t=\h+1}^R \big(\tr\{(w_{it} - w_{it}^*)
-  (V^2 - \E(V^2 \mid X_{iR}'X_{iR})\} \big)
-\end{align*}
-where these results come from repeated use of the LIE along with
-linearity of the trace and expectation operators. By construction,
-\begin{equation*}
-  \Pr\big[\tr\{w_{it} (V^2 - \E(V^2 \mid X_{iR}'X_{iR}))\}
-  \neq \tr\{w_{it}^* (V^2 - \E(V^2 \mid X_{iR}'X_{iR}))\}\big]
-  \leq  \beta_{R -\h + 1- s}.
-\end{equation*}
-
-[NEED TO FINISH HERE]
+  = O(P/R^2).
+\end{equation*}
+Consequently,
+\begin{equation*}
+  \E \tr\bigg\{[(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}]^2
+  X_{iR}'\eb_{iR} \eb_{iR}X_{iR} \bigg\} = O(P/R)
+\end{equation*}
+and so
+\begin{equation*}
+  \| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
+  (X_{iR}'X_{iR})^{-1}] X_{iR}' \eb_{iR} \|_2 = O(\sqrt{P/R}).
+\end{equation*}
 
@@
 similarities apparent. Let $b_T \equiv \lfloor \gamma/\delta \rfloor$,
-define $\kernelB{x}$ as in \eqref{eq:13}, and define the following
+define $\kernelB{x}$ as in Equation \eqref{eq:13}, and define the following
 terms as in \citet{JoD:00}:
@@
   \varianceTermIIa\\& \quad \times \varianceTermIIb,\\
-  \varianceTermIII &\equiv \vtSum \varianceTermIIIa\\\displaybreak
+  \varianceTermIII &\equiv \vtSum \varianceTermIIIa\\
   &\quad \times \varianceTermIIb,\\
@@
 De Jong and Davidson (2000) prove that
-\begin{equation} \label{dd1}
+\begin{equation*}
 \lim_{\delta\to0} \limsup_{T\to\infty} \lVert \varianceTermI -
 \varianceTermII\rVert_1 = 0,
-\end{equation}
-\begin{equation} \label{dd2}
+\end{equation*}
+\begin{equation*}
 \lim_{\delta\to0} \limsup_{T\to\infty} \lVert \varianceTermII - \varianceTermIII
 \rVert_1 = 0,
-\end{equation}
-\begin{equation} \label{dd3}
+\end{equation*}
+\begin{equation*}
 \lim_{\delta\to0} \limsup_{T\to\infty} \lVert \varianceTermIII - \varianceTermIV
 \rVert_1 = 0,
-\end{equation}
+\end{equation*}
 and
-\begin{equation} \label{dd4}
+\begin{equation*}
 \lim \lVert \E_R \varianceTermI - \sigma^2 \rVert_1 = 0.
-\end{equation}
-Their proofs of \eqref{dd1}--\eqref{dd4} use the fact that NED
+\end{equation*}
+Their proofs of these four convergence results use the fact that NED
 functions of mixing processes are also mixingale processes and do not
@@
 hold here as well.  We do need to modify their proofs that
-\begin{equation}\label{eq:5}
+\begin{equation*}
   \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1 \to 0
-\end{equation}
+\end{equation*}
 and
-\begin{equation}\label{eq:4}
+\begin{equation*}
   \lVert \sh^2 - \varianceTermI \rVert_1 \to 0
-\end{equation}
+\end{equation*}
 for all positive $\delta$, though, since those proofs exploit NED
@@
 Theorem~\ref{res-oost}, so we will present a proof of~\eqref{eq:23}.
-By Lemma~\ref{res-convergence}, we know that
-\begin{equation*}
-  \Pr[\E_R \oosA \leq 0] - \Pr[\E_T \oosB \leq 0] \to 0
-\end{equation*}
-and
-\begin{equation*}
-  \Pr[P^{1/2} \oosA / \sh > z_\alpha \text{ and } \E_R \oosA \leq 0]
-  - \Pr[P^{1/2} \oosA / \sh > z_\alpha \text{ and }
+By Lemma~\ref{res-convergence}, we know that $\E_R \oosA - \E_T \oosB
+\to^p 0$, so
+\begin{equation*}
+  \Pr[\E_R \oosA \leq 0] - \Pr[\E_T \oosB \leq 0] \to 0.
+\end{equation*}
+Now we can use Lemma~\ref{lem-basic-coupling} to define $D_t^*$ as in
+the proofs of Lemma~\ref{res-mixingale} and~\ref{res-convergence} so
+that $\E_R D_t^* = \E_{t-l} D_t^*$ a.s. and
+\[
+\lVert D_t - D_t^* \rVert_2 \leq \couplingBound{l}
+\]
+and define $\oosA^* = P^{-1} \sum_{t=R+1}^{T-\h} D_t^*$. Then
+\begin{equation*}
+  \lVert \sqrt{P} \oosA - \sqrt{P} \oosA^* \rVert_2
+  \leq P^{-1/2} \sum_{t=R+1}^{T-\h} \lVert \oosA - \oosA^* \rVert_2
+  = o(1),
+\end{equation*}
+and, consequently, we have convergence in probability of the following
+vectors:
+\begin{equation*}
+  (\sqrt{P} \oosA^*/\sigma,\ \E_R \oosA) -
+  (\sqrt{P} \oosA/\sh,\ \E_T \oosB) \to^p 0,
+\end{equation*}
+where we are implicitly using consistency of $\sh^2$ for $\sigma^2$.
+More importantly, this implies convergence in distribution of these
+vectors, so
+\begin{equation*}
+  \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha
+  \text{ and } \E_R \oosA \leq 0]
+  - \Pr[\sqrt{P} \oosA / \sh > z_\alpha \text{ and }
   \E_T \oosB \leq 0] \to 0.
 \end{equation*}
+
 For large enough $T$, both $\Pr[\E_R \oosA \leq 0]$ and $\Pr[\E_T
-\oosB \leq 0]$ are positive, so
-\begin{equation*}
-  \Pr[P^{1/2} \oosA / \sh > z_\alpha
-  \mid \E_R \oosA \leq 0] =
-  \frac{\Pr[P^{1/2} \oosA / \sh > z_\alpha \text{ and }
+\oosB \leq 0]$ are positive (the second by assumption, the first by
+convergence to the second) so (for these $T$)
+\begin{align}\label{eq:31}
+  \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha
+  \mid \E_R \oosA \leq 0] &=
+  \frac{\Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha \text{ and }
     \E_R \oosA \leq 0]}{\Pr[\E_R \oosA \leq 0]}
-\end{equation*}
-and
-\begin{equation*}
-  \Pr[P^{1/2} \oosA / \sh > z_\alpha
-  \mid \E_T \oosB \leq 0] =
-  \frac{\Pr[P^{1/2} \oosA / \sh > z_\alpha \text{ and }
+\intertext{and}\label{eq:32}
+  \Pr[\sqrt{P} \oosA / \sh > z_\alpha
+  \mid \E_T \oosB \leq 0] &=
+  \frac{\Pr[\sqrt{P} \oosA / \sh > z_\alpha \text{ and }
     \E_T \oosB \leq 0]}{\Pr[\E_T \oosB \leq 0]}
-\end{equation*}
-almost surely and consequently
-\begin{equation*}
-  \Pr[P^{1/2} \oosA / \sh > z_\alpha
-  \mid \E_T \oosB \leq 0]
-  - \Pr[P^{1/2} \oosA / \sh > z_\alpha
-  \mid \E_R \oosA \leq 0] \to^p 0.
-\end{equation*}
-Finally,
+\end{align}
+almost surely. Since the terms on the RHS of Equations~\eqref{eq:31}
+and~\eqref{eq:32} converge to the same limit in probability, we have
+\begin{equation*}
+  \Pr[\sqrt{P} \oosA / \sh > z_\alpha  \mid \E_T \oosB \leq 0]
+  - \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha \mid \E_R \oosA \leq 0]
+  \to^p 0
+\end{equation*}
+and it suffices to show that
+\begin{equation*}
+  \plim \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha \mid \E_R \oosA \leq 0]
+  \leq \alpha.
+\end{equation*}
+
+To establish this inequality, we have
 \begin{align*}
-  \Pr[P^{1/2} \oosA / \sh > z_\alpha \mid \E_R \oosA \leq 0]
-  &\leq \Pr[P^{1/2} (\oosA - \E_R \oosA) / \sh > z_\alpha
+  \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha \mid \E_R \oosA \leq 0]
+  &\leq \Pr[\sqrt{P} (\oosA^* - \E_R \oosA) / \sigma > z_\alpha
   \mid \E_R \oosA \leq 0] \\
-  &= \E( \Pr[P^{1/2} (\oosA - \E_R \oosA) / \sh > z_\alpha
-  \mid \mathcal{F}_R] \mid \E_R \oosA \leq 0) \\
-  &= \E(\alpha \mid \E_R \oosA \leq 0) \\
-  &= \alpha
+  &\leq \E\big(
+  \Pr[\sqrt{P} (\oosA^* - \E_R \oosA) / \sigma > z_\alpha \mid \Fs_R]
+  \mid \E_R \oosA \leq 0\big).
 \end{align*}
-completing the proof.
+By construction,
+\begin{equation*}
+  \Pr[\sqrt{P} (\oosA^* - \E_R \oosA) / \sigma > z_\alpha \mid \Fs_R]
+  \to \alpha
+\end{equation*}
+since generated pseudo OOS observations in each $D_t^*$ are
+independent of $\Fs_R$, completing the proof.
 \qed
@@
 
-For both parts, let $(\e_{t+h}, x_{t}) \sim i.i.d. N(0,I)$ and let
-$\theta_1 = 0$.
-
-\noindent
-\emph{Proof of (\ref{eq:11})}. $\E_T \oosB = 0$ implies that
+Let $(\e_{t+h}, x_{t}) \sim i.i.d.\ N(0,I)$ and let $\theta_1 = 0$.
+For any $d \geq 0$, the event $\E_T \oosB = -d$ implies that
 \begin{equation*}
   \E_T (y_{T+\h+1} - x_{1T+1}'\bh{1T})^2
-  = \E_T (y_{T+\h+1} - x_{2T+1}'\bh{2T})^2
-\end{equation*}
-almost surely, which can be expressed as
-\begin{equation*}
-  \bh{1T}'\bh{1T} = (\bh{2T} - \theta_2)'(\bh{2T} - \theta_2)
-\end{equation*}
-almost surely. So, given $\bh{1T}$,
-
-, where $\tilde\theta_{1T}$ is the first $K_1$ elements
-of $\bh{2T}$ and $\tilde\theta_{2T}$ is the remaining $K_2 - K_1$, and
-$\theta_2^*$ is the corresponding elements of the pseudotrue $\theta_2$.
-
-distribution of $\bh{2T}$ concentrates on and outside the sphere
-defined by
-\begin{equation*}
-  (\bh{2T} - \theta_2)' A (\bh{2T} - \theta_2) = \theta_2' A \theta_2.
-\end{equation*}
-This sphere is centered at the
-
-If $\theta_2$ and $V_T$ satisfy
-\begin{equation*}
-  \Pr[\theta_2' V_T \theta_2 > 2 c] \to 1
-\end{equation*}
-the acceptance region of $\Lambda$ is contained in a cube with
-
-then
+  = \E_T (y_{T+\h+1} - x_{2T+1}'\bh{2T})^2 - d \quad a.s.
+\end{equation*}
+which can be expressed as
+\begin{equation}\label{eq:34}
+  d + \bh{1T}'\bh{1T} - \bh{2T}'M_1'M_1\bh{2T}
+  = (\bh{2T} - \theta_2)' M_2'M_2 (\bh{2T} - \theta_2) \quad a.s.
+\end{equation}
+Now, $M_2 \bh{2T}$ is normally distributed conditional
+on $\bh{1T}$ and $M_1 \bh{2T}$, and is distributed on the surface of
+the sphere defined by~\eqref{eq:34} conditional on $\bh{1T}$, $M_1
+\bh{2T}$, and the event $\E_T \oosB = -d$.
+
+Since $M_2 \bh{2T}$ is normal, this conditional distribution is
+invariant to reflection across the axes defined by the eigenvectors of
+its covariance matrix. So when $\theta_2$ lies outside the cylindar
+that contains the acceptance region of $\Lambda$, ie.e. $\theta_2'M_2'
+V_T M_2 \theta_2 > c$, we have
 \begin{align*}
+  \Pr[ \bh{2T}'M_2' V_T M_2 &\bh{2T} \leq c \mid \E_T \oosB \leq 0] \\
+  &= \E\Big( \Pr[ \bh{2T}'M_2' V_T M_2 \bh{2T} \leq c
+  \mid \E_T \oosB \leq 0, \bh{1T}, M_1 \bh{2T}]
+  \mid \E_T \oosB \leq 0 \Big) \\
+  & < 1/2
+\end{align*}
+since the inner conditional probability is less than 1/2.
+
+Then
+\begin{equation*}
   \E(\Lambda \mid \E_T \oosB \leq 0)
-  &\leq \Pr[ \bh{2T}' V_T \bh{2T} < c \mid \E_T \oosB \leq 0] \\
-  &\leq (1/2)^{K_2},
-\end{align*}
-which converges to zero as $T \to \infty$.
+  =   \E(\Lambda \mid \E_T \oosB \leq 0)
+\end{equation*}
+
+and magick...
+\qed
+
+\subsection*{Proof of Theorem~\ref{res:insample2}}
+As in the proof of Theorem~\ref{res:insample1}, let $(\e_{t+h}, x_{t})
+\sim i.i.d.\ N(0,I)$ and let $\theta_1 = 0$. The event $\E_T \oosB
+\geq 0$ implies that
+\begin{equation*}
+  \E_T (y_{T+\h+1} - x_{1T+1}'\bh{1T})^2
+  \geq \E_T (y_{T+\h+1} - x_{2T+1}'\bh{2T})^2 \quad a.s.
+\end{equation*}
+which can be expressed as
+\begin{equation}\label{eq:34}
+  \bh{1T}'\bh{1T} - \bh{2T}'M_1'M_1\bh{2T}
+  \geq (\bh{2T} - \theta_2)' M_2'M_2 (\bh{2T} - \theta_2) \quad a.s.
+\end{equation}
+$M_2 \bh{2T}$ is normally distributed conditional on $\bh{1T}$ and
+$M_1 \bh{2T}$, and is a.s. contained in the sphere defined
+by~\eqref{eq:34} conditional on $\bh{1T}$, $M_1 \bh{2T}$, and the
+event $\E_T \oosB \geq 0$.
+
+Then
+\begin{equation*}
+  \E( \Lambda \mid \E_T \oosB \geq 0 )
+\end{equation*}
 
@@
 \bibliography{references}
-
-\begin{table}[h]
- \begin{multicols}{2}
-  \begin{itemize}
-  \item log Dividend Price Ratio
-  \item log Earnings Price Ratio
-  \item Stock Market Variance
-  \item Book to Market Ratio
-  \item Net Equity Expansion
-  \item Percent Equity Issuing
-  \item Treasury Bill
-  \item Long Term Yield
-  \item Long Term Rate
-  \item Default Return Spread
-  \item Default Yield Spread
-  \item Inflation
-  \end{itemize}
- \end{multicols}
- \caption{Variables used in Section \ref{sec:empirics} and by Goyal
-   and Welch (2008) to predict the equity premium.  Please see Goyal
-   and Welch's original paper
+\clearpage
+
+\begin{table}[tb]
+  \begin{tabularx}{\linewidth}{XX}
+    \toprule
+    Category & Variable \\
+    \midrule
+    Stock market variables
+    & Dividend to price ratio (log) \\
+    & Earnings to price ratio (log) \\
+    & Stock market variance \\
+    & Book to market ratio \\
+    & Net equity expansion \\
+    & Percent equity issuing \\\\
+    Interest rate variables
+    & Treasury Bill rate (3 month) \\
+    & Long term yield \\
+    & Long term rate \\
+    & Default return spread \\
+    & Default yield spread \\
+    & Inflation rate \\
+    \bottomrule
+  \end{tabularx}
+  \caption{Variables used to predict the equity premium
+    (Section~\ref{sec:empirics}).
+    Please see Goyal and Welch's original paper \citep{GoW:08}
     for a detailed description of each variable.}
@@
 
-\begin{table}[b]
- \begin{center}
- \begin{tabular}{lrrrr}\hline\hline
-   \multicolumn{1}{l}{waldtest}&\multicolumn{1}{c}{Res.Df}&\multicolumn{1}{c}{Df}&\multicolumn{1}{c}{F}&\multicolumn{1}{c}{Pr(\textgreater
-     F)}\tabularnewline
-   \hline
-   1&69&&&\\
-   2&81&$-$12&3.4&0.00066 \\
-   \hline
-\end{tabular}
-\caption{Wald test for the null hypothesis that all of the
-  coefficients in Goyal and Welch's (2008) ``kitchen sink'' model are
-  zero, except for the intercept, using the Newey-West
-  variance-covariance matrix.  The p-value is calculated from the $F$
-  distribution.\label{tab:gwinsample}}
-\end{center}
-\end{table}
-
-\clearpage
-\begin{figure}
-  \centering {\large Simulated Coverage of One-Sided DMW Interval for
-    $\E_R\oosA$} \tryinput{floats/mc-interval-testerror1.tex}
-\caption{Simulated coverage of $\E_R \oosA$ at 90\% confidence using a
-  one-sided interval based on the DMW
-  OOS test, plotted as a function of the fraction of
-  observations used in the test sample, $P/T$.  The solid horizontal
-  line denotes the intervals' nominal coverage.}
+\tryinput{floats/empirics-insample.tex}
+\tryinput{floats/empirics-insample-tuned.tex}
+% These macros create tables. They are defined in
+% floats/empirics-insample.tex and possibly overwritten in the next
+% file.
+\insamplecoefs
+\insampletests
+
+\tryinput{floats/mc-ftest.tex}
+
+\begin{figure}\centering
+  {\large Coverage of DMW OOS interval for $\E_R\oosA$ in simulations}
+  \tryinput{floats/mc-interval-testerror1.tex}
+  \caption{Simulated coverage of $\E_R \oosA$ at 90\% confidence using
+    a one-sided interval based on the DMW \oost\ test, plotted as a
+    function of the fraction of observations used in the test sample,
+    $P/T$. The solid horizontal line denotes the intervals' nominal
+    coverage.}
  \label{fig:interval-R}
@@
 \clearpage
-\begin{figure}
-  \centering {\large Simulated Coverage of One-Sided DMW Interval for
-    $\E_T\oosB$} \tryinput{floats/mc-interval-generror1.tex}
-\caption{Simulated coverage of $\E_T \oosB$ at 90\% confidence using a
-  one-sided interval based on the DMW
-  OOS, plotted as a function of the fraction of
-  observations used in the test sample, $P/T$.  The solid horizontal
-  line denotes the intervals' nominal coverage.}
+
+\begin{figure}\centering
+  {\large Coverage of DMW OOS interval for $\E_T\oosB$ in simulations}
+  \tryinput{floats/mc-interval-generror1.tex}
+  \caption{Simulated coverage of $\E_T \oosB$ at 90\% confidence using
+    a one-sided interval based on the DMW \oost\ test, plotted as a
+    function of the fraction of observations used in the test sample,
+    $P/T$.  The solid horizontal line denotes the intervals' nominal
+    coverage.}
   \label{fig:interval-T}
@@
 
-\begin{figure}
-  \centering {\large Simulated Rejection Probability of $F$-test Under
-    $\E_T \oosB \leq 0$}
-  \tryinput{floats/mc-ftest.tex}
-  \caption{Simulated rejection probabilities for the $F$-test given
-    $\E_T \oosB \leq 0$ with nominal size 10\%.  Values greater than
-    10\% indicate that the test rejects the benchmark model too often.
-    See Section~\ref{sec:simulation-design} for a discussion of the
-    simulation design.}
-  \label{fig:ftest}
-\end{figure}
-\clearpage
-\begin{figure}
-  \centering {\large Simulated Rejection Probability of DMW Test Under
-    $\E_T \oosB \leq 0$} \tryinput{floats/mc-dmwsize.tex}
-  \caption{Simulated rejection probabilities for the DMW
-    OOS $t$-test given $\E_T \oosB \leq 0$ with nominal
-    size 10\%.  Values greater than 10\% indicate that the test
-    rejects the benchmark model too often.  The solid horizontal line
-    indicates the nominal rejection probability.  See
+\begin{figure}\centering
+  {\large Size of DMW \oost\ test in simulations}
+  \tryinput{floats/mc-dmwsize.tex}
+  \caption{Simulated rejection probabilities for the DMW \oost\ test
+    under the null hypothesis that the benchmark model will forecast
+    better, $\E_T \oosB \leq 0$. The nominal size is 10\% and is
+    marked with a solid horizontal line. Values greater than 10\%
+    indicate that the test rejects the benchmark model too often. See
     Section~\ref{sec:simulation-design} for a discussion of the
@@
 \end{figure}
-
-\begin{figure}
-  \centering {\large Simulated Rejection Probability of Clark and West
-    (2006, 2007) \\ Test Under $\E_T \oosB \leq 0$}
+\clearpage
+
+\begin{figure}\centering
+  {\large Size of Clark-West OOS test in simulations}
   \tryinput{floats/mc-clarkwestsize.tex}
   \caption{Simulated rejection probabilities for Clark and West's
-    (2006, 2007) OOS test statistic given $\E_T \oosB
-    \leq 0$ with nominal size 10\%.  Values greater than 10\% indicate
-    that the test rejects the benchmark model too often.  The solid
-    horizontal line indicates the nominal rejection probability.  See
-    Section~\ref{sec:simulation-design} for a discussion of the
-    simulation design.}
+    (2006, 2007) OOS test statistic under the null hypothesis that the
+    benchmark will forecast better, $\E_T \oosB \leq 0$. The nominal
+    size is 10\% and is marked with a solid horizontal line. Values
+    greater than 10\% indicate that the test rejects the benchmark
+    model too often. See Section~\ref{sec:simulation-design} for a
+    discussion of the simulation design.}
    \label{fig:clarkwest}
 \end{figure}
-
-\begin{figure}
-  \centering {\large Simulated Rejection Probability of McCracken
-    (2007) Test \\ Under $\E_T \oosB \leq 0$}
+\clearpage
+
+\begin{figure}\centering
+  {\large Size of McCracken \oost\ test in simulations}
   \tryinput{floats/mc-mccrackensize.tex}
   \caption{Simulated rejection probabilities for McCracken's (2007)
-    OOS test statistic given $\E_T \oosB \leq 0$ with
-    nominal size 10\%.  Values greater than 10\% indicate that the
-    test rejects the benchmark model too often.  The solid horizontal
-    line indicates the nominal rejection probability.  See
+    \oost\ test under the null hypothesis that the benchmark model is
+    more accurate, $\E_T \oosB \leq 0$. Nominal size is 10\% and is
+    marked with a solid horizontal line. Values greater than 10\%
+    indicate that the test rejects the benchmark model too often. See
     Section~\ref{sec:simulation-design} for a discussion of the
@@
 \end{figure}
-
-\begin{figure}
-  \centering {\large Simulated Rejection Probability of DMW Test Under
-    $\E_T \oosB > 0$} \tryinput{floats/mc-dmwpower.tex}
-  \caption{Simulated rejection probabilities for the DMW
-    OOS $t$-test given $\E_T \oosB > 0$ with nominal
-    size 10\%.  Values greater than 10\% indicate that the test
-    rejects the benchmark model too often.  The solid horizontal line
-    indicates the nominal rejection probability.  See
+\clearpage
+
+\begin{figure}\centering
+  {\large Power of DMW \oost\ test in simulations}
+  \tryinput{floats/mc-dmwpower.tex}
+  \caption{Simulated rejection probabilities for the DMW \oost\ test
+    under the alternative that the benchmark model is less accurate,
+    $\E_T \oosB > 0$. Nominal size is 10\% and is marked with a solid
+    horizontal line. Values greater than 10\% indicate that the test
+    rejects the benchmark model too often. See
     Section~\ref{sec:simulation-design} for a discussion of the
@@
 \end{figure}
+\clearpage
 
@@
 
-% LocalWords:  McCracken's kilian anatolyev rossi REStud JAppliedEconometrics
-% LocalWords:  goyal welch rfs reputational calhoun Berbee's mixingales Rt tS
-% LocalWords:  Heteroskedasticity Autocorrelation Tt iT th berbee iS de dx ixz
-% LocalWords:  DMW mcleish Rs eq ftestreject lightgray veclen RSQLite zeileis
-% LocalWords:  heteroskedasticity hothorn RNews JStatSoftware harrell campbell
-% LocalWords:  thompson bivariate Welch's multicollinearity Newey newey tw vw
-% LocalWords:  merlevede cltvar dR Scwarz davidson indices lrrrr waldtest Df jt
-% LocalWords:  dmw McCracken MSE OLS mse inoue huber elemstatlearning efron sw
-% LocalWords:  anova akritas jong normalpart coefpart Jong's rproject rsqlite
-% LocalWords:  unrestrictive datasets Heyde's ib oos Mcc MeR StW InK DiM CCS lm
-% LocalWords:  ClM CoS ClW GiW GiR GoW Cla HTF Efr BoB AkA AkP DeD Mcl Dej Rde
-% LocalWords:  Sar Zeh Zei Har CaT NeW MeP HaH AllRefs Diebold jel Whi RoW brc
-% LocalWords:  overrejection overreject fpe JoD iR PeT Giacomini WN Wishart T'V
-% LocalWords:  premultiply const overrejects overrejecting BWB Gia Schwarz HHK
-% LocalWords:  Haf Anatolyev's nonstochastic T'X Sweave tikzDevice pgfSweave
+%  LocalWords:  ClM Mcc ClW MeR StW InK CCS CoS GiW GiR BRC HTF BoH
+%  LocalWords:  Tib BaN AIC BoB AkA AkP Efr iR eq FPE th Dou iS iT dx
+%  LocalWords:  JoD ixz Mcl RHS MSE homoskedastic Joh Widom TrW Sil
+%  LocalWords:  BFP dy LLNs VeR rlecuyer RSQLite Sar tikzDevice TikZ
+%  LocalWords:  PGF LaTeX jt test's CaT Coc BRW LeN RaW RaZ LeR ZeH
+%  LocalWords:  lmtest Zei dbframe Hmsic Har xtable Dah booktabs FeE
+%  LocalWords:  Bonferroni BWB Gia MeP indices Schwarz HaH Jong

### 2014-03-21 R/mc-clarkwestsize-rec.R

@@ -18,11 +18,12 @@ select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
                  and scheme = 'rec'
                group by ntest, isim, idgp, transform, label) s 
 join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp")
+dbDisconnect(dbc)
 
 d$nlabel <- sprintf("T=%d", d$n)
 d$normlabel <- sprintf("c=%d", d$norm)
 
-tikz(file = "floats/mc-clarkwestsize-rec.tex", width = 6)
+tikz(file = "floats/mc-clarkwestsize-rec.tex", width = 6, height = 4.5)
 xyplot(reject ~ I(ntest/n) | interaction(nlabel,altlabel,normlabel, sep = ", "),
        data = d,
        ylab = "Rejection Probability", xlab = "$P/T$",
@@ -30,8 +31,7 @@ xyplot(reject ~ I(ntest/n) | interaction(nlabel,altlabel,normlabel, sep = ", "),
          panel.lines(c(0,2/3),c(.1,.1), col = "lightgray")
          panel.xyplot(x,y,...,type = "l")
        },
-       layout = c(4,4),
+       layout = c(4,3),
        par.strip.text = list(cex = .55),
-       index.cond = list(c(13,15,16,14,9,11,12,10,5,7,8,6,1,3,4,2)))
+       index.cond = list(c(3, 6, 9, 12, 2, 5, 8, 11, 1, 4, 7, 10)))
 dev.off()
-dbDisconnect(dbc)

### 2014-03-21 R/mc-clarkwestsize.R

@@ -18,11 +18,12 @@ select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
                  and scheme = 'fix'
                group by ntest, isim, idgp, transform, label) s 
 join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp")
+dbDisconnect(dbc)
 
 d$nlabel <- sprintf("T=%d", d$n)
 d$normlabel <- sprintf("c=%d", d$norm)
 
-tikz(file = "floats/mc-clarkwestsize.tex", width = 6)
+tikz(file = "floats/mc-clarkwestsize.tex", width = 6, height = 4.5)
 xyplot(reject ~ I(ntest/n) | interaction(nlabel,altlabel,normlabel, sep = ", "),
        data = d,
        ylab = "Rejection Probability", xlab = "$P/T$",
@@ -30,8 +31,7 @@ xyplot(reject ~ I(ntest/n) | interaction(nlabel,altlabel,normlabel, sep = ", "),
          panel.lines(c(0,2/3),c(.1,.1), col = "lightgray")
          panel.xyplot(x,y,...,type = "l")
        },
-       layout = c(4,4),
+       layout = c(4,3),
        par.strip.text = list(cex = .55),
-       index.cond = list(c(13,15,16,14,9,11,12,10,5,7,8,6,1,3,4,2)))
+       index.cond = list(c(3, 6, 9, 12, 2, 5, 8, 11, 1, 4, 7, 10)))
 dev.off()
-dbDisconnect(dbc)

### 2014-03-21 R/mc-dmwpower-rec.R

@@ -7,22 +7,22 @@ ltheme$strip.background$col <- "transparent" ## change strip bg
 lattice.options(default.theme = ltheme)      ## set as default  
 
 dbc <- dbConnect(dbDriver("SQLite"), dbname = "data/simulations.db")
-
 d <- dbGetQuery(dbc, "
 select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
                from interval 
                where label='power'
-                 and ntest <= 10
+                 and ntest >= 10
                  and idgp in (2,3)
                  and transform='difference'
                  and scheme='rec'
-               group by ntest, isim, idgp, transform, label) s 
+               group by ntest, isim, idgp, transform, label) s
 join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp")
+dbDisconnect(dbc)
 
 d$nlabel <- sprintf("T=%d", d$n)
 d$normlabel <- sprintf("c=%d", d$norm)
 
-tikz(file = "floats/mc-dmwpower-rec.tex", width = 6)
+tikz(file = "floats/mc-dmwpower-rec.tex", width = 6, height = 4.5)
 xyplot(reject ~ I(ntest/n) | interaction(nlabel,altlabel,normlabel, sep = ", "),
        data = d,
        ylab = "Rejection Probability", xlab = "$P/T$",
@@ -30,8 +30,7 @@ xyplot(reject ~ I(ntest/n) | interaction(nlabel,altlabel,normlabel, sep = ", "),
          panel.lines(c(0,2/3),c(.1,.1), col = "lightgray")
          panel.xyplot(x,y,...,type = "l")
        },
-       layout = c(4,4),
+       layout = c(4,3),
        par.strip.text = list(cex = .55),
-       index.cond = list(c(13,15,16,14,9,11,12,10,5,7,8,6,1,3,4,2)))
+       index.cond = list(c(3, 6, 9, 12, 2, 5, 8, 11, 1, 4, 7, 10)))
 dev.off()
-dbDisconnect(dbc)

### 2014-03-21 R/mc-dmwpower.R

@@ -18,11 +18,12 @@ select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
                  and scheme='fix'
                group by ntest, isim, idgp, transform, label) s 
 join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp")
+dbDisconnect(dbc)
 
 d$nlabel <- sprintf("T=%d", d$n)
 d$normlabel <- sprintf("c=%d", d$norm)
 
-tikz(file = "floats/mc-dmwpower.tex", width = 6)
+tikz(file = "floats/mc-dmwpower.tex", width = 6, height = 4.5)
 xyplot(reject ~ I(ntest/n) | interaction(nlabel,altlabel,normlabel, sep = ", "),
        data = d,
        ylab = "Rejection Probability", xlab = "$P/T$",
@@ -30,8 +31,7 @@ xyplot(reject ~ I(ntest/n) | interaction(nlabel,altlabel,normlabel, sep = ", "),
          panel.lines(c(0,2/3),c(.1,.1), col = "lightgray")
          panel.xyplot(x,y,...,type = "l")
        },
-       layout = c(4,4),
+       layout = c(4,3),
        par.strip.text = list(cex = .55),
-       index.cond = list(c(13,15,16,14,9,11,12,10,5,7,8,6,1,3,4,2)))
+       index.cond = list(c(3, 6, 9, 12, 2, 5, 8, 11, 1, 4, 7, 10)))
 dev.off()
-dbDisconnect(dbc)

### 2014-03-21 R/mc-dmwsize-rec.R

@@ -18,11 +18,12 @@ select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
                  and scheme='rec'
                group by ntest, isim, idgp, transform, label) s 
 join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp")
+dbDisconnect(dbc)
 
 d$nlabel <- sprintf("T=%d", d$n)
 d$normlabel <- sprintf("c=%d", d$norm)
 
-tikz(file = "floats/mc-dmwsize-rec.tex", width = 6)
+tikz(file = "floats/mc-dmwsize-rec.tex", width = 6, height = 4.5)
 xyplot(reject ~ I(ntest/n) | interaction(nlabel,altlabel,normlabel, sep = ", "),
        data = d,
        ylab = "Rejection Probability", xlab = "$P/T$",
@@ -30,8 +31,7 @@ xyplot(reject ~ I(ntest/n) | interaction(nlabel,altlabel,normlabel, sep = ", "),
          panel.lines(c(0,2/3),c(.1,.1), col = "lightgray")
          panel.xyplot(x,y,...,type = "l")
        },
-       layout = c(4,4),
+       layout = c(4,3),
        par.strip.text = list(cex = .55),
-       index.cond = list(c(13,15,16,14,9,11,12,10,5,7,8,6,1,3,4,2)))
+       index.cond = list(c(3, 6, 9, 12, 2, 5, 8, 11, 1, 4, 7, 10)))
 dev.off()
-dbDisconnect(dbc)

### 2014-03-21 R/mc-dmwsize.R

@@ -18,11 +18,12 @@ select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
                  and scheme='fix'
                group by ntest, isim, idgp, transform, label) s
 join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp")
+dbDisconnect(dbc)
 
 d$nlabel <- sprintf("T=%d", d$n)
 d$normlabel <- sprintf("c=%d", d$norm)
 
-tikz(file = "floats/mc-dmwsize.tex", width = 6)
+tikz(file = "floats/mc-dmwsize.tex", width = 6, height = 4.5)
 xyplot(reject ~ I(ntest/n) | interaction(nlabel,altlabel,normlabel, sep = ", "),
        data = d,
        ylab = "Rejection Probability", xlab = "$P/T$",
@@ -30,8 +31,7 @@ xyplot(reject ~ I(ntest/n) | interaction(nlabel,altlabel,normlabel, sep = ", "),
          panel.lines(c(0,2/3),c(.1,.1), col = "lightgray")
          panel.xyplot(x,y,...,type = "l")
        },
-       layout = c(4,4),
+       layout = c(4,3),
        par.strip.text = list(cex = .55),
-       index.cond = list(c(13,15,16,14,9,11,12,10,5,7,8,6,1,3,4,2)))
+       index.cond = list(c(3, 6, 9, 12, 2, 5, 8, 11, 1, 4, 7, 10)))
 dev.off()
-dbDisconnect(dbc)

### 2014-03-21 R/mc-ftest.R

@@ -1,28 +1,41 @@
 library(fwPackage, lib.loc="package")
 library(tikzDevice)
 library(lattice)
+library(dbframe)
 
 ltheme <- canonical.theme(color = FALSE)     ## in-built B&W theme  
 ltheme$strip.background$col <- "transparent" ## change strip bg  
 lattice.options(default.theme = ltheme)      ## set as default  
 
 dbc <- dbConnect(dbDriver("SQLite"), dbname = "data/simulations.db")
-d <- dbGetQuery(dbc,
-                "select reject, 'T=' || n as nlabel, altlabel, norm from viewftest 
-                 where label='size' and norm in (0,1)")
-d$norm <- as.factor(d$norm)
-
-tikz(file = "floats/mc-ftest.tex", width = 5.5, height = 4)
-dotplot(norm ~ reject | interaction(altlabel,nlabel, sep = ", "),
-              dat = d, las = 1,
-              xlab = "Rejection Probability", ylab = "c",
-              xlim = c(-.1, 1.1),
-              panel = function(x, y, ...) {
-                panel.dotplot(x, y, ..., type = "n")
-                panel.text(x, as.numeric(y), labels = sprintf("%.2f", x))
-              },
-              par.strip.text = list(cex = .55),
-              layout = c(2,4),
-              index.cond = list(c(3,4,7,8,5,6,1,2)))
-dev.off()
+d <- dbGetQuery(dbc, "select reject, n, kNull, nulllabel, altlabel, norm
+                      from viewftest where label = 'size'")
 dbDisconnect(dbc)
+
+d$nulllabel[d$nulllabel == "K0=2"] <- "$2$"
+d$nulllabel[d$nulllabel == "K0=n/50"] <- "$T/50$"
+d$altlabel[d$altlabel == "K=3"] <- "$3$"
+d$altlabel[d$altlabel == "K=T/10"] <- "$T/10$"
+
+dl <- lapply(unique(d$norm), function(dnorm) d[d$norm == dnorm,])
+dd <- dl[[1]][, c("nulllabel", "altlabel", "n", "reject")]
+names(dd) <- c("$K_1$", "$K_2$", "$T$", "$| \\theta_2 |_2 = 0$")
+dd[,"$| \\theta_2 |_2 = 1$"] <- dl[[2]]$reject
+
+tabscode <- booktabs(dd,
+                     align = c("l", "l", "C", "C", "C"),
+                     digits = c(0, 0, 0, 3, 3),
[…]

### 2014-03-21 R/mc-interval-generror1-rec.R

@@ -18,21 +18,22 @@ select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
                  and scheme = 'rec'
                group by ntest, isim, idgp, transform, label) s
 join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp")
+dbDisconnect(dbc)
 
 d$nlabel <- sprintf("T=%d", d$n)
 d$normlabel <- sprintf("c=%d", d$norm)
 
-tikz(file = "floats/mc-interval-generror1-rec.tex", width=6)
+tikz(file = "floats/mc-interval-generror1-rec.tex", width=6, height = 4.5)
 xyplot(I(1 - reject) ~ I(ntest/n)
          | interaction(nlabel, altlabel, normlabel, sep = ", "),
        data = d,
        ylab = "Coverage", xlab = "$P/T$",
+       ylim = c(.8, 1),
        panel = function(x,y,...) {
          panel.lines(c(0,2/3),c(.9,.9), col = "gray")
          panel.xyplot(x,y,...,type = "l")
        },
-       layout = c(4,4),
+       layout = c(4,3),
        par.strip.text = list(cex = .55),
-       index.cond = list(c(13,15,16,14,9,11,12,10,5,7,8,6,1,3,4,2)))
+       index.cond = list(c(3, 6, 9, 12, 2, 5, 8, 11, 1, 4, 7, 10)))
 dev.off()
-dbDisconnect(dbc)

### 2014-03-21 R/mc-interval-generror1.R

@@ -18,21 +18,22 @@ select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
                  and scheme = 'fix'
                group by ntest, isim, idgp, transform, label) s 
 join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp")
+dbDisconnect(dbc)
 
 d$nlabel <- sprintf("T=%d", d$n)
 d$normlabel <- sprintf("c=%d", d$norm)
 
-tikz(file = "floats/mc-interval-generror1.tex", width=6)
+tikz(file = "floats/mc-interval-generror1.tex", width=6, height = 4.5)
 xyplot(I(1 - reject) ~ I(ntest/n)
          | interaction(nlabel, altlabel, normlabel, sep = ", "),
        data = d,
+       ylim = c(.8, 1),
        ylab = "Coverage", xlab = "$P/T$",
        panel = function(x,y,...) {
          panel.lines(c(0,2/3),c(.9,.9), col = "gray")
          panel.xyplot(x,y,...,type = "l")
        },
-       layout = c(4,4),
+       layout = c(4,3),
        par.strip.text = list(cex = .55),
-       index.cond = list(c(13,15,16,14,9,11,12,10,5,7,8,6,1,3,4,2)))
+       index.cond = list(c(3, 6, 9, 12, 2, 5, 8, 11, 1, 4, 7, 10)))
 dev.off()
-dbDisconnect(dbc)

### 2014-03-21 paper.tex
Empirics: clean up table listing Goyal and Welch variables
This commit adds the booktabs and tabularx packages to the
preamble and moves the list of Goyal Welch variables to
a booktabs table.

The first table was smushed into the bibliography; that's been fixed
now and it's on its own page.

--- 2014-03-20 paper.tex
@@
 \bibliography{references}
-
-\begin{table}[h]
- \begin{multicols}{2}
-  \begin{itemize}
-  \item log Dividend Price Ratio
-  \item log Earnings Price Ratio
-  \item Stock Market Variance
-  \item Book to Market Ratio
-  \item Net Equity Expansion
-  \item Percent Equity Issuing
-  \item Treasury Bill
-  \item Long Term Yield
-  \item Long Term Rate
-  \item Default Return Spread
-  \item Default Yield Spread
-  \item Inflation
-  \end{itemize}
- \end{multicols}
- \caption{Variables used in Section \ref{sec:empirics} and by Goyal
-   and Welch (2008) to predict the equity premium.  Please see Goyal
-   and Welch's original paper
+\clearpage
+
+\begin{table}[tb]
+  \begin{tabularx}{\linewidth}{XX}
+    \toprule
+    Category & Variable \\
+    \midrule
+    Stock market variables
+    & Dividend Price ratio (log) \\
+    & Earnings Price ratio (log) \\
+    & Stock Market Variance \\
+    & Book to Market Ratio \\
+    & Net Equity Expansion \\
+    & Percent Equity Issuing \\\\
+    Interest rate variables
+    & Treasury Bill rate (3 month) \\
+    & Long Term Yield \\
+    & Long Term Rate \\
+    & Default Return Spread \\
+    & Default Yield Spread \\
+    & Inflation \\
+    \bottomrule
+  \end{tabularx}
+  \caption{Variables used to predict the equity premium.
+    Please see Goyal and Welch's original paper \citep{GoW:08}
     for a detailed description of each variable.}

### 2014-03-25 paper.tex
References: Add reference for TikZ and PGF
Conflicts:
	paper.tex

--- 2014-03-21 paper.tex
@@
 our theory in small samples.%
-\footnote{Simulations were conducted in R \citep{Rde:10} using Sweave
-  \citep{Lei:02} and the Lattice \citep{Sar:10}, RSQLite
-  \citep{Jam:10}, and tikzDevice \citep{ShB:11:0.6.1} packages.} %
+\footnote{Simulations were conducted in R \citep{Rde:10} using the
+  MASS \citep{VeR:02}, Matrix \citep{BM:13}, rlecuyer \citep{SR:12},
+  and RSQLite \citep{Jam:10} packages. Graphs were produced in R using
+  Lattice \citep{Sar:10} and tikzDevice \citep{ShB:11:0.6.1} as well
+  as the TikZ and PGF LaTeX packages \citep{Tan:10}} %
 The first looks at the asymptotic normality of the DMW statistic

### 2014-03-25 appendix.tex
Styling: tweak spacing and font size
- changes the font to 12pt charter instead of 11pt
- changes the margins to 1.25in instead of 1in
- changes to single spacing instead of 1 and a half spacing.

Hopefully these all make the document easier to read; I'll probably
undo them before submission though.

@@
-\documentclass[11pt]{article}
+\documentclass[12pt]{article}
 \input{setup}
 
-\title{Supplamental Appendix for Out-of-Sample Comparisons of Overfit
-  Models}
-\author{Gray Calhoun\thanks{email: gcalhoun@iastate.edu} \\
+\title{Supplamental Appendix for ``Out-of-Sample Comparisons of
+  Overfit Models''}
+\author{Gray Calhoun\thanks{email: \protect\url{gcalhoun@iastate.edu}} \\
   Iowa State University}
@@
 
-Fill in the text...
+This appendix presents simulation results that accompany
+\cite{Cal:14}. As in the main paper, these simulations were conducted
+in R \citep{Rde:10} using the MASS \citep{VeR:02}, Matrix
+\citep{BM:13}, rlecuyer \citep{SR:12}, and RSQLite \citep{Jam:10}
+packages. Graphs were produced in R using Lattice \citep{Sar:10} and
+tikzDevice \citep{ShB:11:0.6.1}.
 
-\begin{figure}
-  \centering {\large Simulated Coverage of Recursive One-Sided DMW Interval for
-    $\E_T\oosB$} \input{floats/mc-interval-generror1-rec.tex}
-\caption{Simulated coverage of $\E_T \oosB$ at 90\% confidence using a
-  one-sided interval based on the DMW
-  OOS, plotted as a function of the fraction of
-  observations used in the test sample, $P/T$.  The solid horizontal
-  line denotes the intervals' nominal coverage.}
+\nocite{DiM:95,Wes:96,Mcc:07,ClW:06,ClW:07}
+\bibliographystyle{abbrvnat}
+\bibliography{references}
+
+\begin{figure}\centering
+  {\large Coverage of recursive DMW OOS interval in simulations}
+  \input{floats/mc-interval-generror1-rec.tex}
+  \caption{Simulated coverage of $\E_T \oosB$ at 90\% confidence using
+    a one-sided interval based on the recursive DMW \oost\ test,
+    plotted as a function of the fraction of observations used in the
+    test sample, $P/T$.  The solid horizontal line denotes the
+    intervals' nominal coverage.}
   \label{fig:interval-T}
 \end{figure}
-\clearpage
 
-\begin{figure}
-  \centering {\large Simulated Rejection Probability of Recursive DMW Test Under
-    $\E_T \oosB \leq 0$} \input{floats/mc-dmwsize-rec.tex}
-  \caption{Simulated rejection probabilities for the DMW
-    OOS $t$-test given $\E_T \oosB \leq 0$ with nominal
-    size 10\%.  Values greater than 10\% indicate that the test
-    rejects the benchmark model too often.  The solid horizontal line
-    indicates the nominal rejection probability.  See
-    Section~\ref{sec:simulation-design} for a discussion of the
-    simulation design.}
+\begin{figure}\centering
+  {\large Size of recursive DMW \oost\ test in simulations}
+  \input{floats/mc-dmwsize-rec.tex}
+  \caption{Simulated rejection probabilities for the recursive DMW
+    \oost\ test under the null hypothesis that the benchmark model is
+    more accurate, $\E_T \oosB \leq 0$. Nominal size is 10\% and is
+    marked with a solid horizontal line. Values greater than 10\%
+    indicate that the test rejects the benchmark model too often.}
   \label{fig:ttest-size}
@@
 
-\begin{figure}
-  \centering {\large Simulated Rejection Probability of Recursive Clark and West
-    (2006, 2007) \\ Test Under $\E_T \oosB \leq 0$}
+\begin{figure}\centering
+  {\large Size of recursive Clark-West OOS test in simulations}
   \input{floats/mc-clarkwestsize-rec.tex}
   \caption{Simulated rejection probabilities for Clark and West's
-    (2006, 2007) OOS test statistic given $\E_T \oosB
-    \leq 0$ with nominal size 10\%.  Values greater than 10\% indicate
-    that the test rejects the benchmark model too often.  The solid
-    horizontal line indicates the nominal rejection probability.  See
-    Section~\ref{sec:simulation-design} for a discussion of the
-    simulation design.}
+    (2006, 2007) recursive OOS test statistic under the null
+    hypothesis that the benchmark model is more accurate, $\E_T \oosB
+    \leq 0$. Nominal size is 10\% and is marked with a solid
+    horizontal line. Values greater than 10\% indicate that the test
+    rejects the benchmark model too often.}
   \label{fig:clarkwest}
@@
 
-\begin{figure}
-  \centering {\large Simulated Rejection Probability of Recursive McCracken
-    (2007) Test \\ Under $\E_T \oosB \leq 0$}
+\begin{figure}\centering
+  {\large Size of recursive McCracken \oost\ test in simulations}
   \input{floats/mc-mccrackensize-rec.tex}
   \caption{Simulated rejection probabilities for McCracken's (2007)
-    OOS test statistic given $\E_T \oosB \leq 0$ with
-    nominal size 10\%.  Values greater than 10\% indicate that the
-    test rejects the benchmark model too often.  The solid horizontal
-    line indicates the nominal rejection probability.  See
-    Section~\ref{sec:simulation-design} for a discussion of the
-    simulation design.}
+    recursive \oost\ test under the null hypothesis that the benchmark
+    model is more accurate, $\E_T \oosB \leq 0$. Nominal size is 10\%
+    and is marked with a solid horizontal line. Values greater than
+    10\% indicate that the test rejects the benchmark model too
+    often.}
   \label{fig:mccracken}
@@
 
-\begin{figure}
-  \centering {\large Simulated Rejection Probability of Recursive DMW Test Under
-    $\E_T \oosB > 0$} \input{floats/mc-dmwpower-rec.tex}
-  \caption{Simulated rejection probabilities for the DMW
-    OOS $t$-test given $\E_T \oosB > 0$ with nominal
-    size 10\%.  Values greater than 10\% indicate that the test
-    rejects the benchmark model too often.  The solid horizontal line
-    indicates the nominal rejection probability.  See
-    Section~\ref{sec:simulation-design} for a discussion of the
-    simulation design.}
+\begin{figure}\centering
+  {\large Power of recursive DMW \oost\ test in simulations}
+  \input{floats/mc-dmwpower-rec.tex}
+  \caption{Simulated rejection probabilities for the recursive DMW
+    \oost\ test under the alternative that the benchmark model is less
+    accurate, $\E_T \oosB > 0$. Nominal size is 10\% and is marked
+    with a solid horizontal line. Values greater than 10\% indicate
+    that the test rejects the benchmark model too often.}
   \label{fig:ttest-power}
 \end{figure}
-
 \end{document}
@@
 %%% mode: latex
-%%% TeX-master: "paper"
+%%% TeX-master: "appendix"
 %%% End:
-
-% LocalWords:  McCracken's kilian anatolyev rossi REStud JAppliedEconometrics
-% LocalWords:  goyal welch rfs reputational calhoun Berbee's mixingales Rt tS
-% LocalWords:  Heteroskedasticity Autocorrelation Tt iT th berbee iS de dx ixz
-% LocalWords:  DMW mcleish Rs eq ftestreject lightgray veclen RSQLite zeileis
-% LocalWords:  heteroskedasticity hothorn RNews JStatSoftware harrell campbell
-% LocalWords:  thompson bivariate Welch's multicollinearity Newey newey tw vw
-% LocalWords:  merlevede cltvar dR Scwarz davidson indices lrrrr waldtest Df jt
-% LocalWords:  dmw McCracken MSE OLS mse inoue huber elemstatlearning efron sw
-% LocalWords:  anova akritas jong normalpart coefpart Jong's rproject rsqlite
-% LocalWords:  unrestrictive datasets Heyde's ib oos Mcc MeR StW InK DiM CCS lm
-% LocalWords:  ClM CoS ClW GiW GiR GoW Cla HTF Efr BoB AkA AkP DeD Mcl Dej Rde
-% LocalWords:  Sar Zeh Zei Har CaT NeW MeP HaH AllRefs Diebold jel Whi RoW brc
-% LocalWords:  overrejection overreject fpe JoD iR PeT Giacomini WN Wishart T'V
-% LocalWords:  premultiply const overrejects overrejecting BWB Gia Schwarz HHK
-% LocalWords:  Haf Anatolyev's nonstochastic T'X Sweave tikzDevice pgfSweave

### 2014-03-25 floats/empirics-insample-tuned.tex

\renewcommand\insampletests\relax

\renewcommand\insamplecoefs{%
  \begin{table}[tb]
    \begin{tabularx}{\textwidth}{lCCCC}
      \toprule
      & \multicolumn{2}{c}{Coefficient estimates}
      & \multicolumn{2}{c}{$p$-values} \\
      \cmidrule(lr){2-3} \cmidrule(l){4-5}
      & Full & Univariate & Full & Univariate \\
      \midrule Stock market variance & $\enskip4.61$ & $\enskip0.36$ & $0.081$ & $0.870$ \\
      Book to market ratio & $\enskip4.46$ & $\enskip4.81$ & $0.251$ & $0.027$ \\
      Dividend to price ratio (log) & $\enskip4.40$ & $\enskip3.91$ & $0.400$ & $0.073$ \\
      Long term rate & $\enskip3.78$ & $\enskip2.91$ & $0.035$ & $0.184$ \\
      Long term yield & $\enskip3.23$ & $\!\!-1.25$ & $0.438$ & $0.569$ \\
      Earnings to price ratio (log) & $\enskip0.79$ & $\enskip3.50$ & $0.849$ & $0.109$ \\
      Inflation rate & $\enskip0.63$ & $\enskip0.69$ & $0.696$ & $0.754$ \\
      Default return spread & $\enskip0.53$ & $\!\!-1.74$ & $0.795$ & $0.429$ \\
      Net equity expansion & $\!\!-1.88$ & $\!\!-4.10$ & $0.626$ & $0.060$ \\
      Treasury Bill rate & $\!\!-4.38$ & $\!\!-2.47$ & $0.316$ & $0.260$ \\
      Percent equity issuing & $\!\!-5.56$ & $\!\!-5.10$ & $0.040$ & $0.019$ \\
      Default yield spread & $\!\!-7.79$ & $\enskip0.79$ & $0.042$ & $0.720$ \\
      \\
      Robust $F$-statistic ($12$/$69$ df) & \enskip $3.37$ & & $0.001$ \\
      $R^2$ & $\enskip 0.23$ \\
      Adjusted $R^2$ & $\enskip 0.10$ \\
      \bottomrule \end{tabularx}
    \caption{Coefficient estimates and model fit for the univariate and full
      models described in Section \ref{sec:empirics}. The ``Full'' column
      lists the coefficient estimates from regressing the equity premium on
      all of the variables listed; the ``Univariate'' column lists the
      coefficient estimates from a univariate regression of the equity premium
      on the variable alone. All of the regressions include a constant, but
      its estimate is not listed. The equity premium is expressed in basis
      points and all of the regressors are studentized.
      These models are estimated using U.S. annual data from 1928--2009
      (81 observations). The standard errors and robust $F$-statistic
      are calculated using a Newey-West HAC estimator with two lags,
      implemented in the \emph{sandwich} and \emph{lmtest} R packages
      \protect\citep{NeW:87,ZeH:02,Zei:04}.}
    \label{tab:gwinsample}
  \end{table}
}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../paper"
%%% End:

### 2014-03-25 paper.tex

--- 2014-03-21 paper.tex
@@
 
-This section presents an analysis of equity premium predictability
-similar to \citet{GoW:08}.%
-\footnote{Calculations in this section are done in R \citep{Rde:10}
-  using the lmtest \citep{ZeH:02} and sandwich \citep{Zei:04}
-  packages. Tables and grapsh were prepared with the Hmsic
-  \citep{Har:10} and tikzDevice \citep{ShB:11:0.6.1} R packages as
-  well as the TikZ and PGF LaTeX packages \citep{Tan:10}} %
-We estimate the expected forecasting
-performance of the largest model they consider, a model with 13
-regressors, using 81 observations (annual data from 1928 to 2009).  We
-construct confidence intervals for the difference in performance
-between this model and a prevailing mean benchmark, and do so for
-different values of $R$ and $P$ to examine the effect of the training
-and test sample choice on this OOS statistic.  We find that the
-estimate of the larger model's Mean Squared Error (MSE) decreases relative to the
-benchmark as $R$ increases, but it is never smaller than the
-benchmark's.  This result, combined with the larger model's in-sample
-significance, suggests that there may be a real relationship between
-the equity premium and some of these predictors, but that the
-relationship can not be estimated accurately enough to be useful for
-forecasting and supports \citepos{GoW:08} conclusions.  These results
-hold even when imposing \citepos{CaT:08} restriction that the equity
-premium forecast be non-negative.
-
-We'll start with a very brief review.  \citet{GoW:08}
-study the OOS forecasting performance of different variables thought
-to predict the equity premium (calculated as the difference between
-the return on the S\&P 500 index and the T-bill rate).  Some of these
-variables are listed in
-Table~\ref{tab:equity}.%
-\footnote{Table~\ref{tab:equity} only lists the
-  variables used in \citepos{GoW:08} ``kitchen sink''
-  model.  Some of the variables that they use in bivariate models are
-  excluded from this model either because the series are too short or
-  because the variables are linear combinations of other variables.} %
-\citet{GoW:08} estimate the OOS forecasting
-performance of bivariate models of the form
+This section presents a study of equity premium predictability based
+on \citet{GoW:08}. Goyal and Welch conduct an out of sample analysis
+of 18 different variables thought, based on previous research, to
+predict the equity premium (calculated as the difference between the
+return on the S\&P 500 index and the T-bill rate).%
+\footnote{\citet{GoW:08} builds on previous research by \citet{BoH:99}
+  and \cite{GoW:03}.} %
+Their analysis has two notable features: they compare different
+predictors across the same time periods and frequency as much as
+possible, making the accuracy of these predictors directly comparable;
+many of the papers that originally proposed these predictors used
+different time periods, methods, or observational frequencies so their
+results were not directly comparable. And Goyal and Welch compare
+these predictors out-of-sample; many of the original studies found
+in-sample evidence of equity premium predictability but did not look
+at out-of-sample evidence.
+
+Goyal and Welch consider many different models; most of them are very
+simple---regression onto a constant and a single stochastic
+predictor---but some are more complicated. They find that essentially
+none of the models outperform a simple benchmark, the prevailing mean
+of the equity premium, and conclude that these variables do not
+predict the equity premium. A large literature has subsequently sought
+to explain or rebut these results, including several responses to
+Goyal and Welch's original working paper published in the same special
+issue of \textit{The Review of Financial Studies} as \citet{GoW:08}.%
+\footnote{Those papers are \citet{CaT:08}, \citet{Coc:08},
+  \citet{BRW:08}, and \citet{LeN:08}.} %
+
+\citet{GoW:08}, as well as \citet{BoH:99}, \citet{LeN:08}, and many
+other authors, propose that instability could explain the OOS failure
+of these models. However, we have shown in this paper that overfit can
+also explain this pattern, significant in-sample results that do not
+hold up out of sample. In this section, we explore the extent to which
+overfit is a potential concern in this data set and estimate the
+expected forecasting performance of the largest model they consider, a
+model with 13 regressors, using 81 observations (annual data from 1928
+to 2009). The predictors are listed in Table~\ref{tab:equity}; please
+see Goyal and Welch's original paper for detailed information about
+these variables.%
+\footnote{Table~\ref{tab:equity} only lists the variables used in
+  \citepos{GoW:08} ``kitchen sink'' model.  Some of the variables that
+  they use are excluded from this model either
+  because the series are too short or because the variables are linear
+  combinations of other variables.} %
+
+\citet{GoW:08} focus primarily on univariate regression models of the
+form
 \[
-r_{t+1} = \beta_0 + \beta_1 x_t + \e_{t+1}
+r_{t+1} = \beta_0 + \beta_1 x_{it} + \e_{t+1}
 \]
 using OLS with a recursive window, where $r_{t+1}$ is the equity
-premium and $x_t$ is a generic predictor, as well as some larger
-models.  They find that these models forecast no better than the
-prevailing mean of the equity premium.
-\citet{CaT:08} find that nonlinear extensions of
-Goyal and Welch's models are more accurate, either imposing sign
-restrictions on the estimated coefficients or imposing that the
-forecast be non-negative, but do not test for significance.
-
-Obviously, \citepos{GoW:08} bivariate models do not
-match the asymptotic theory of this paper, so we restrict our
-attention here to their ``kitchen sink'' model, which includes all of
-the variables, except for a few dropped because of data availability or
-(perfect) multicollinearity.  Formally, the benchmark and alternative models are
-\begin{eqnarray}
-  \label{eq:3}
-  r_{t+1} &=& \mu + \e_{1,t+1} \\
-  \label{eq:2}
-r_{t+1} &=& \beta_0 + \sum_{i=1}^K \beta_{i} x_{it} + \e_{2,t+1}
-\end{eqnarray}
-respectively and are estimated by OLS using the fixed-window scheme.
-The predictors are listed in Table~\ref{tab:equity}; for a detailed
-description of each predictor, please see Goyal and Welch's original
-paper.  In this model, there are 13 regressors (including the constant
-term) and we estimate the coefficients using annual data from 1928 to
-2009.  This makes the ratio $K/T$ equal to about 0.16.  We also
-present results for one of \citepos{CaT:08}
-restricted forecasting models.  For this model, we estimate
-\eqref{eq:3} and \eqref{eq:2}, but impose that $\hat r_{t+1}$ be
-non-negative for each forecast.  We then calculate the OOS test just
-as for the unconstrained model.
-
-Table~\ref{tab:gwinsample} gives the results of the full sample
-regression for Equation~\eqref{eq:2}, using Newey-West standard errors
-with two lags \citep{NeW:87}.%
-\footnote{We compare the test statistic
-  to critical values from the $F$-distribution.} %
-The $p$-value is
-very small (less than 0.01), indicating that the coefficients are
-nonzero in population and at least one of these predictors is
-correlated with the equity premium.  As we argue earlier, this result
-does not imply that the model will forecast well, which we look at
-next.
-
+premium and $x_{it}$ is one of the predictors listed in
+Table~\ref{tab:equity}.%
+\footnote{To make it easier to compare coefficients across variables
+  and models, all of the regressors are studentized before our
+  analysis and the equity premium is reported in basis points.} %
+This focus is consistent with much of the rest of the literature. But
+it is not clear that this approach---using a large number of
+restricted models---is any more reliable than using a single, large
+model. Very few papers in the equity-premium predictability literature
+explicitly account for the multiplicity of model comparisons%
+\footnote{\citet{RaW:06}, \citet{RaZ:12}, and \citet{Cal:13b} are
+  exceptions.} %
+and most widely-used statistics for multiple comparisons are
+derived under the assumption that there is a finite number of
+hypotheses or models (as is the case in \citealp{STW:99c},
+\citealp{Whi:00}, \citealp{Han:05}, and \citealp{LeR:05}), so there is
+little theoretical evidence that they are any more reliable than a
+regression model that encompasses all of the smaller models. Moreover,
+since \citet{GoW:08} (along with most of the rest of the literature)
+want to interpret these univariate regressions as meaningful
+statements about the true relationships between the equity premium and
+the regressors, omitted variable bias is a serious potential issue.
+
+For example, Table~\ref{tab:gwinsample} presents two full-sample
+coefficient estimates for each of the 12 predictors we consider.%
+\footnote{For all of our full sample results, we studentize the
+  regressors to make it easier to compare coefficient estimates and we
+  express the equity premium in basis points.} %
+The first column is the estimator of the coefficient on the listed
+variable in the full regression,
+\begin{equation}\label{eq:30}
+  r_{t+1} = \beta_0 + \sum_{i=1}^{12} \beta_{i} x_{it} + \e_{t+1},
+\end{equation}
+and the third column is the $p$-value associated with a two-sided
+$t$-test that the coefficient is zero in population. The second column
+is the estimator of the coefficient from the univariate regression
+\begin{equation}
+  r_{t+1} = \alpha_i + \gamma_{i} x_{it} + \e_{t+1},
+\end{equation}
+and the fourth column is the $p$-value associated with its $t$-test.%
+\footnote{All of the standard errors were calculated using a
+  Newey-West kernel with two lags.} %
+Some of the coefficient estimates agree, but some do not. The
+coefficient estimate for the \emph{default yield spread}, for example,
+is substantially and significantly negative in the full model ($-7.79$
+with $p$-value $0.042$), but is near zero in the univariate regression
+($0.79$ with $p$-value $0.720$). This pair of results implies that the
+the default yield spread contains information about the equity premium
+but is also correlated with other poor predictors, and that this
+additional correlation adds noise to the univariate regression
+and masks the true relationship. Similarly, \emph{net equity expansion}
+is significant at 10\% in the univariate regression but not in the
+full model ($p$-values of $0.060$ and $0.626$ respectively), which is
+likely attributable to omitted variable bias. So there is merit to
+studying a large model that includes all of the variables.
+
+Results for the full sample estimates of Equation~\eqref{eq:2} are in
+Table~\ref{tab:gwinsample}.%
+\footnote{Calculations in this section are done in R \citep{Rde:10}
+  using the \emph{lmtest} \citep{ZeH:02} and \emph{sandwich}
+  \citep{Zei:04} packages. Tables and graphs were prepared with the
+  \emph{dbframe} \citep{Cal:10b}, \emph{Hmsic} \citep{Har:10},
+  \emph{tikzDevice} \citep{ShB:11:0.6.1}, and \emph{xtable}
+  \citep{Dah:09} R packages as well as the \emph{booktabs}
+  \citep{FeE:05} and \emph{TikZ and PGF} LaTeX packages
+  \citep{Tan:10}}%
+\footnote{We compare the test statistic to critical values from the
+  $F$-distribution, which has been shown to be more reliable when
+  there are many regressors \citep{Ana:12,Cal:11c}.} %
+The last rows of the table list measures of the full-model fit.  The
+$p$-value for the test of full model fit is very small (less than
+0.01), indicating that the coefficients are nonzero in population and
+at least one of these predictors is correlated with the equity
+premium.%
+\footnote{We have done additional analysis to try to identify which
+  predictors were correlated with the equity premium, but none of the
+  individual regressors were significant after correcting for
+  multiplicity. The Bonferroni correction, for example, suggests that
+  an individual $p$-value would need to be less than $0.10/12 \approx
+  0.0083$ for its corresponding coefficint to be significant at the
+  10\% level, but the smallest $p$-value is $0.035$. One can improve
+  on the Bonferroni correction, but a comprehensive analysis is beyond
+  the scope of this paper.} %
+As we argue throughout the paper, this result does not imply that the
+model will forecast well.
+
+To determine whether the full model can forecast well, we use the DMW
+\oost\ test to compare it to a sample mean benchmark,
+\begin{equation}\label{eq:2}
+r_{t+1} = \mu + \e_{1,t+1}.
+\end{equation}
+Both models are estimated by OLS using the fixed-window scheme. We
+also present results for a restricted model proposed by
+\citet{CaT:08} that imposes that $\hat r_{t+1}$ be non-negative for
+each forecast.
 To study the effect of the training sample size on the DMW statistic, we
@@
 the larger model relative to the smaller, but this may not hold in
-this particular dataset.
-
-Figures~\ref{fig:empirics1} plots the OLS results and
+this particular dataset. For the OOS results, we express the equity
+premium in perecentage points.
+
+Figure~\ref{fig:empirics1} plots the OLS results and
 Figure~\ref{fig:empirics2} imposes \citepos{CaT:08} restriction. The
@@
     Stock market variables
-    & Dividend Price ratio (log) \\
-    & Earnings Price ratio (log) \\
-    & Stock Market Variance \\
-    & Book to Market Ratio \\
-    & Net Equity Expansion \\
-    & Percent Equity Issuing \\\\
+    & Dividend to price ratio (log) \\
+    & Earnings to price ratio (log) \\
+    & Stock market variance \\
+    & Book to market ratio \\
+    & Net equity expansion \\
+    & Percent equity issuing \\\\
     Interest rate variables
     & Treasury Bill rate (3 month) \\
-    & Long Term Yield \\
-    & Long Term Rate \\
-    & Default Return Spread \\
-    & Default Yield Spread \\
-    & Inflation \\
+    & Long term yield \\
+    & Long term rate \\
+    & Default return spread \\
+    & Default yield spread \\
+    & Inflation rate \\
     \bottomrule
   \end{tabularx}
-  \caption{Variables used to predict the equity premium.
+  \caption{Variables used to predict the equity premium
+    (Section~\ref{sec:empirics}).
     Please see Goyal and Welch's original paper \citep{GoW:08}
@@
 \end{table}
-
-\begin{table}[b]
- \begin{center}
- \begin{tabular}{lrrrr}\hline\hline
-   \multicolumn{1}{l}{waldtest}&\multicolumn{1}{c}{Res.Df}&\multicolumn{1}{c}{Df}&\multicolumn{1}{c}{F}&\multicolumn{1}{c}{Pr(\textgreater
-     F)}\tabularnewline
-   \hline
-   1&69&&&\\
-   2&81&$-$12&3.4&0.00066 \\
-   \hline
-\end{tabular}
-\caption{Wald test for the null hypothesis that all of the
-  coefficients in Goyal and Welch's (2008) ``kitchen sink'' model are
-  zero, except for the intercept, using the Newey-West
-  variance-covariance matrix.  The p-value is calculated from the $F$
-  distribution.\label{tab:gwinsample}}
-\end{center}
-\end{table}
+\clearpage
+
+\tryinput{floats/empirics-insample.tex}
+\tryinput{floats/empirics-insample-tuned.tex}
+% These macros create tables. They are defined in
+% floats/empirics-insample.tex and possibly overwritten in the next
+% file.
+\insamplecoefs
+\insampletests
 

### 2014-03-27 paper.tex
Extensive rewrite of the paper's theoretical component
This commit is a major rewrite of the paper's theoretical component,
including both the in-sample and out-of-sample results. The in-sample
proofs still need to be completed, but otherwise this part of the
paper is more or less ready to go.

@@
 error.  The null hypothesis we test is
-\begin{equation}\label{eq:9}
+\begin{equation*}
   H_0:\quad E_T \oosB \leq 0,
-\end{equation}
+\end{equation*}
 We look at four different statistics---the full-sample $F$-test, the
@@
 
-To estimate each test's size for the hypothesis \eqref{eq:9}, we draw
-samples from the DGP and discard those for which \eqref{eq:9} does
+To estimate each test's size for the null hypothesis, we draw
+samples from the DGP and discard those for which the null does
 not hold, until we have 2000 for each choice of the design parameters.
@@
 variable in the full regression,
-\begin{equation}\label{eq:30}
+\begin{equation*}
   r_{t+1} = \beta_0 + \sum_{i=1}^{12} \beta_{i} x_{it} + \e_{t+1},
-\end{equation}
+\end{equation*}
 and the third column is the $p$-value associated with a two-sided
@@
 is the estimator of the coefficient from the univariate regression
-\begin{equation}
+\begin{equation*}
   r_{t+1} = \alpha_i + \gamma_{i} x_{it} + \e_{t+1},
-\end{equation}
+\end{equation*}
 and the fourth column is the $p$-value associated with its $t$-test.%
@@
 
-Results for the full sample estimates of Equation~\eqref{eq:2} are in
+Results for the full sample estimates of these models are in
 Table~\ref{tab:gwinsample}.%
@@
   an individual $p$-value would need to be less than $0.10/12 \approx
-  0.0083$ for its corresponding coefficint to be significant at the
+  0.0083$ for its corresponding coefficient to be significant at the
   10\% level, but the smallest $p$-value is $0.035$. One can improve
@@
 \oost\ test to compare it to a sample mean benchmark,
-\begin{equation}\label{eq:2}
+\begin{equation*}
 r_{t+1} = \mu + \e_{1,t+1}.
-\end{equation}
+\end{equation*}
 Both models are estimated by OLS using the fixed-window scheme. We
@@
 this particular dataset. For the OOS results, we express the equity
-premium in perecentage points.
+premium in percentage points.
 

### 2014-03-27 paper.tex
Revise empirical write-up
This commit makes several minor changes to the empirical section.

@@
 \end{equation*}
-for $P$ set to every 10th value between 1 and $2T/3$.  We calculate
-the percentage of these intervals that contain $\E_R \oosA$ and that
-contain $\E_T \oosB$.  Since the data are i.i.d., both of these
-quantities are easy to calculate:
-\begin{equation*}
-  E_R \oosA = \Bigg[\sum_{i=1}^{K_1} (\tilde{\theta}_{iR} - \theta_i)^2 +
-  \sum_{i=K_1+1}^{K_2}\theta_i^2\Bigg] - \sum_{i=1}^{K_2} (\hat{\theta}_{iR} -
-  \theta_i)^2
-\end{equation*}
-and
-\begin{equation*}
-  E_T \oosB = \Bigg[\sum_{i=1}^{K_1} (\tilde{\theta}_{iT} - \theta_i)^2 +
-  \sum_{i=K_1+1}^{K_2}\theta_i^2\Bigg] - \sum_{i=1}^{K_2} (\hat{\theta}_{iT} -
-  \theta_i)^2
-\end{equation*}
-where $\tilde{\theta}$ indicates that the coefficient is estimated
-using only the regressors in the benchmark model and $\hat{\theta}$
-the full model.  We draw 2000 samples for each combination of the
-design parameters.
-
-The second simulation looks at the size and power of the test
-statistics when conducting inference about the models' generalization
-error.  The null hypothesis we test is
+for $P = 10,\dots,2T/3$; we then calculate the percentage of
+simulations where these intervals contain $\E_R \oosA$ and the
+percentage that contain $\E_T \oosB$.  Since the data are i.i.d., both
+of these quantities are easy to calculate (see
+Section~\ref{sec:example}). For these calculations, we draw 2000
+samples for each combination of the design parameters.
+
+Our second set of results studies whether these different OOS and
+in-sample statistics are valid for testing the null hypothesis
 \begin{equation*}
@@
 \end{equation*}
+namely that the benchmark model is expected to be more accurate in the
+future than the alternative. Informally, we are interested in whether
+the conditional probability
+\begin{equation*}
+  \Pr[\text{test rejects} \mid E_T \oosB \leq 0] \leq \alpha
+\end{equation*}
+where $\alpha$ is the nominal size of the test. If this inequality
+does not hold, the test statistic is rejecting the benchmark model too
+often.
+
 We look at four different statistics---the full-sample $F$-test, the
-DMW $t$-test, the
-OOS $t$-test using McCracken's (2007)
-critical values,%
-\footnote{These critical values are not published for
-  $K_2-K_1>10$, so we do not report them for $K_2 = T/10$.} %
-and Clark and West's (2006, 2007) Gaussian out-of-sample
-statistic.%
-\footnote{Clark and West (2006, 2007) derive their statistic
-using the rolling window estimation scheme.  Here we use the same
-statistic, but with a fixed window scheme.} %
-For the $F$-test, we simply test whether the coefficients on the larger
-model are nonzero.  For the out-of-sample tests, we conduct a
-one-sided test of out-of-sample performance for every 10th value of
-$P$ as before.
-
-To estimate each test's size for the null hypothesis, we draw
-samples from the DGP and discard those for which the null does
-not hold, until we have 2000 for each choice of the design parameters.
-The estimated size is the fraction of those samples in which the test
-statistic rejects.
+DMW $t$-test, the OOS $t$-test using McCracken's (2007) critical
+values,%
+\footnote{These critical values are not published for $K_2-K_1>10$, so
+  we do not report them for $K_2 = T/10$.} %
+and Clark and West's (2006, 2007) Gaussian out-of-sample statistic.%
+\footnote{Clark and West (2006, 2007) derive their statistic using the
+  rolling window estimation scheme. Here we use the same statistic,
+  but with a fixed window scheme. A supplemental appendix presents
+  results for their statistic, using the recursive window.} %
+For the $F$-test, we simply test whether the coefficients on the
+larger model are nonzero.  For the out-of-sample tests, we conduct a
+one-sided test of out-of-sample performance for every value of $P$ as
+before. For each of these simulations, we discard draws from the DGP
+that violate the null hypothesis $E_T \oosB \leq 0$ and then use the
+remaining samples to calculate the conditional probability that each
+test rejects. The simulations end when 2000 draws have been retained
+for each choice of the design parameters.
 
@@
   and \cite{GoW:03}.} %
-Their analysis has two notable features: they compare different
+Their analysis has two notable features: Goyal and Welch compare different
 predictors across the same time periods and frequency as much as
@@
 premium and $x_{it}$ is one of the predictors listed in
-Table~\ref{tab:equity}.%
-\footnote{To make it easier to compare coefficients across variables
-  and models, all of the regressors are studentized before our
-  analysis and the equity premium is reported in basis points.} %
+Table~\ref{tab:equity}.
 This focus is consistent with much of the rest of the literature. But
@@
   express the equity premium in basis points.} %
-The first column is the estimator of the coefficient on the listed
+The first column is the estimator of the coefficient on the
 variable in the full regression,
@@
   using the \emph{lmtest} \citep{ZeH:02} and \emph{sandwich}
-  \citep{Zei:04} packages. Tables and graphs were prepared with the
-  \emph{dbframe} \citep{Cal:10b}, \emph{Hmsic} \citep{Har:10},
-  \emph{tikzDevice} \citep{ShB:11:0.6.1}, and \emph{xtable}
-  \citep{Dah:09} R packages as well as the \emph{booktabs}
-  \citep{FeE:05} and \emph{TikZ and PGF} LaTeX packages
-  \citep{Tan:10}}%
+  \citep{Zei:04} packages.}%
 \footnote{We compare the test statistic to critical values from the
-  $F$-distribution, which has been shown to be more reliable when
-  there are many regressors \citep{Ana:12,Cal:11c}.} %
+  $F$-distribution, which have been shown to be more reliable than
+  Chi-squared critical values when there are many regressors
+  \citep{Ana:12,Cal:11c}.} %
 The last rows of the table list measures of the full-model fit.  The
 $p$-value for the test of full model fit is very small (less than
-0.01), indicating that the coefficients are nonzero in population and
-at least one of these predictors is correlated with the equity
-premium.%
+0.01), indicating that some of the coefficients are nonzero in
+population and at least one of these predictors is correlated with the
+equity premium.%
 \footnote{We have done additional analysis to try to identify which
@@
   10\% level, but the smallest $p$-value is $0.035$. One can improve
-  on the Bonferroni correction, but a comprehensive analysis is beyond
-  the scope of this paper.} %
+  on the Bonferroni correction, of course, but a comprehensive
+  analysis is beyond the scope of this paper.} %
 As we argue throughout the paper, this result does not imply that the
@@
 These also indicate that combination or shrinkage estimators of the
-full model could significantly improve on the benchmark.%
+full model have the potential to significantly improve on the benchmark.%
 \footnote{See \citet{RaZ:12} for a recent review of this
@@
 \end{table}
-\clearpage
 
@@
 
-\clearpage
-\begin{figure}
-  \centering {\large Simulated Coverage of One-Sided DMW Interval for
-    $\E_R\oosA$} \tryinput{floats/mc-interval-testerror1.tex}
-\caption{Simulated coverage of $\E_R \oosA$ at 90\% confidence using a
-  one-sided interval based on the DMW
-  OOS test, plotted as a function of the fraction of
-  observations used in the test sample, $P/T$.  The solid horizontal
-  line denotes the intervals' nominal coverage.}
+\tryinput{floats/mc-ftest.tex}
+
+\begin{figure}\centering
+  {\large Coverage of DMW OOS interval for $\E_R\oosA$ in simulations}
+  \tryinput{floats/mc-interval-testerror1.tex}
+  \caption{Simulated coverage of $\E_R \oosA$ at 90\% confidence using
+    a one-sided interval based on the DMW \oost\ test, plotted as a
+    function of the fraction of observations used in the test sample,
+    $P/T$. The solid horizontal line denotes the intervals' nominal
+    coverage.}
  \label{fig:interval-R}

### 2014-03-27 appendix.tex
Tweak intro to appendix

@@
 This appendix presents simulation results that accompany
-\cite{Cal:14}. As in the main paper, these simulations were conducted
-in R \citep{Rde:10} using the MASS \citep{VeR:02}, Matrix
-\citep{BM:13}, rlecuyer \citep{SR:12}, and RSQLite \citep{Jam:10}
-packages. Graphs were produced in R using Lattice \citep{Sar:10} and
-tikzDevice \citep{ShB:11:0.6.1}.
+\citet{Cal:14}. The Monte Carlo here is exactly the same as presented
+in \citet{Cal:14}, except that a recursive window is used. Please read
+the original paper for further details.
+
+\begin{itemize}
+
+\item Figure 1 in this Appendix corresponds to Figure 3 in the
+  original paper.
+\item Figure 2 corresponds to Figure 4 in the paper.
+\item Figure 3 corresponds to Figure 5 in the paper.
+\item Figure 4 corresponds to Figure 6 in the paper.
+\item Figure 5 corresponds to Figure 7 in the paper.
+
+\end{itemize}
 

### 2014-03-28 paper.tex
Rough version of proof for in-sample statistics

@@
   and $\Lambda = 1$ indicates the alternative.  Moreover, assume that
-  $L(e) = e^2$ and that there exist deterministic scalars $c$ and
-  $\delta$ and a sequence of matrices $V_T$ such that
+  $L(e) = e^2$ and that there exist a deterministic scalar $c$
+  and a sequence of possibly random matrices $V_T$ such that
   \begin{equation}\label{eq:25}
@@
     \Pr[\Lambda \geq \1\{\bh{2T}'M_2' V_T M_2\bh{2T} > c \}]
-    \leq \delta
-  \end{equation}
-  where the eigenvalues of $V_T$ are uniformly bounded, and $\lim
-  \rank(V_T)/T > 0$.
+    \to 0
+  \end{equation}
+  where the eigenvalues of $V_T$ are uniformly bounded in probability,
+  $\plim \rank(V_T)/T > 0$, and neither $V_T$ nor $c$ depend on
+  $\theta$ or the value of $\bh{2T}$.
 
@@
   \begin{equation}\label{eq:27}
-    \Pr[\Lambda \leq \1\{\bh{2T}'M_2' V_T M_2\bh{2T} > c \}] \to 1
-    \quad \text{as } T \to \infty,
-  \end{equation}
-  where $V_T$ is a sequence of deterministic matrices with uniformly
-  bounded eigenvalues and $\lim \rank(V_T)/T > 0$. Then there exist
-  DGPs satisfying these assumptions such that
+    \Pr[\Lambda \leq \1\{\bh{2T}'M_2' M_2\bh{2T} > c \}] \to 1
+    \quad \text{as } T \to \infty.
+  \end{equation}
+
+  Then there exist DGPs satisfying these assumptions such that
   \begin{equation}\label{eq:15}
@@
 \end{equation}
-Now, $M_2 \bh{2T}$ is normally distributed conditional
-on $\bh{1T}$ and $M_1 \bh{2T}$, and is distributed on the surface of
-the sphere defined by~\eqref{eq:34} conditional on $\bh{1T}$, $M_1
-\bh{2T}$, and the event $\E_T \oosB = -d$.
+$M_2 \bh{2T}$ is normally distributed conditional on $\bh{1T}$ and
+$M_1 \bh{2T}$, and is distributed on the surface of the sphere defined
+by~\eqref{eq:34} conditional on $\bh{1T}$, $M_1 \bh{2T}$, and the
+event $\E_T \oosB = -d$.
 
@@
 its covariance matrix. So when $\theta_2$ lies outside the cylindar
-that contains the acceptance region of $\Lambda$, ie.e. $\theta_2'M_2'
-V_T M_2 \theta_2 > c$, we have
+that contains the acceptance region of $\Lambda$, i.e. when
+$\theta_2'M_2' V_T M_2 \theta_2 > c$, we have%
+\footnote{To keep the notation in these equations managable, define
+  the information set $\Gs = \sigma(\E_T \oosB \leq 0,~ \theta_2'M_2'
+  V_T M_2 \theta_2 > c)$.} %
 \begin{align*}
-  \Pr[ \bh{2T}'M_2' V_T M_2 &\bh{2T} \leq c \mid \E_T \oosB \leq 0] \\
-  &= \E\Big( \Pr[ \bh{2T}'M_2' V_T M_2 \bh{2T} \leq c
-  \mid \E_T \oosB \leq 0, \bh{1T}, M_1 \bh{2T}]
-  \mid \E_T \oosB \leq 0 \Big) \\
+  \Pr[ \bh{2T}' M_2' V_T M_2 \bh{2T} \leq c \mid \Gs]
+  &= \E\Big( \Pr[ \bh{2T}'M_2' V_T M_2 \bh{2T} \leq c \mid \Gs,~\bh{1T},~M_1 \bh{2T}] \mid \Gs \Big) \\
   & < 1/2
@@
 
-Then
-\begin{equation*}
-  \E(\Lambda \mid \E_T \oosB \leq 0)
-  =   \E(\Lambda \mid \E_T \oosB \leq 0)
-\end{equation*}
-
-and magick...
+Now let $\delta > 0$ be an arbitrary but small constant, and choose
+$\theta_2$ far enough from the origin to ensure that
+\begin{equation*}
+  \Pr[\theta_2'M_2' V_T M_2 \theta_2 \leq c] \leq \delta
+\end{equation*}
+for large enough $T$. Then
+\begin{align*}
+  \E(\Lambda \mid \E_T \oosB \leq 0) &
+  \geq \Pr[\bh{2T}' M_2' V_T M_2 \bh{2T} > c \mid \E_T \oosB \leq 0] \\
+  &= \Pr[\bh{2T}' M_2' V_T M_2 \bh{2T} > c \text{~~and~~}
+  \theta_2'M_2' V_T M_2 \theta_2 > c \mid \E_T \oosB  \leq 0] \\
+  & \quad + \Pr[\bh{2T}' V_T M_2 \bh{2T} > c \text{~~and~~ }
+  \theta_2'M_2' V_T M_2 \theta_2 \leq c \mid \E_T \oosB \leq 0].
+\end{align*}
+
+The second term is nonnegative by design. By conditioning on
+$\theta_2'M_2' V_T M_2 \theta_2 > c$ our earlier argument shows that
+the first term is greater than or equal to $(1 - \delta) / 2$. Since
+$\delta$ is arbitrarily small, this completes the proof.
 \qed
@@
 
-Then
-\begin{equation*}
-  \E( \Lambda \mid \E_T \oosB \geq 0 )
-\end{equation*}
+Let $\delta$ be a small arbitrary constant, define $\theta^*$ as
+\begin{gather*}
+  \theta^* = \argmax_\theta \theta' M_2' M_2 \theta \\
+  s.t.\ \bh{1T}'\bh{1T} - \bh{2T}'M_1'M_1\bh{2T} = (\theta - \theta_2)' M_2'M_2 (\theta - \theta_2)
+\end{gather*}
+($\theta^*$ depends on $\bh{1T}$ and $M_1 \bh{2T}$) and choose $c$ so
+that
+\begin{equation*}
+  \Pr[ \theta^{* \prime} M_2 M_2 \theta^* > c] < \delta.
+\end{equation*}
+
+Then, we have for large enough $T$
+\begin{align*}
+  \E(\Lambda \mid \E_T \oosB \geq 0) &\leq
+  \Pr[\bh{2T}'M_2'M_2\bh{2T} > c \mid \E_T \oosB \geq 0) \\
+  &\leq \delta
+\end{align*}
+Since $\delta$ is arbitrarily close to zero, this completes the proof.
 

### 2014-03-28 paper.tex
Minor tweaks to in-sample results

@@
 
-The condition~\label{eq:27} requires that the acceptance region of
+The condition~\ref{eq:27} requires that the acceptance region of
 $\Lambda$ eventually contains any finite cylindar centered at the
@@
 \end{equation*}
-We know that $\sqrt{T}(F - 1)$ is asymptotically normal
-\citep{Cal:11c} so the test accepts if
+We know that $\sqrt{T}(F - 1)$ is asymptotically normal since its
+numerator is Chi-squared with $K_2-K_1$ degrees of freedom and obeys a
+CLT.  The test accepts if
 \begin{equation}\label{eq:26}
@@
 
-In the picture, the unknown coefficients satisfy
+In the picture, the true coefficients $\theta_2$ satisfy
 \begin{equation*}
@@
 \begin{equation}\label{eq:34}
-  d + \bh{1T}'\bh{1T} - \bh{2T}'M_1'M_1\bh{2T}
+  d + \theta_2'M_2' M_2 \theta_2 + \bh{1T}'\bh{1T} - \bh{2T}'M_1'M_1\bh{2T}
   = (\bh{2T} - \theta_2)' M_2'M_2 (\bh{2T} - \theta_2) \quad a.s.
@@
 \end{align*}
-
 The second term is nonnegative by design. By conditioning on
@@
 which can be expressed as
-\begin{equation}\label{eq:34}
-  \bh{1T}'\bh{1T} - \bh{2T}'M_1'M_1\bh{2T}
+\begin{equation}\label{eq:2}
+  \theta_2'M_2 M_2'\theta_2 + \bh{1T}'\bh{1T} - \bh{2T}'M_1'M_1\bh{2T}
   \geq (\bh{2T} - \theta_2)' M_2'M_2 (\bh{2T} - \theta_2) \quad a.s.
@@
 $M_1 \bh{2T}$, and is a.s. contained in the sphere defined
-by~\eqref{eq:34} conditional on $\bh{1T}$, $M_1 \bh{2T}$, and the
+by~\eqref{eq:2} conditional on $\bh{1T}$, $M_1 \bh{2T}$, and the
 event $\E_T \oosB \geq 0$.
@@
   \theta^* = \argmax_\theta \theta' M_2' M_2 \theta \\
-  s.t.\ \bh{1T}'\bh{1T} - \bh{2T}'M_1'M_1\bh{2T} = (\theta - \theta_2)' M_2'M_2 (\theta - \theta_2)
+  s.t.\quad \theta_2'M_2'M_2\theta_2 +  \bh{1T}'\bh{1T} - \bh{2T}'M_1'M_1\bh{2T} = (\theta - \theta_2)' M_2'M_2 (\theta - \theta_2)
 \end{gather*}
-($\theta^*$ depends on $\bh{1T}$ and $M_1 \bh{2T}$) and choose $c$ so
-that
+($\theta^*$ is stochastic and depends on $\bh{1T}$ and $M_1 \bh{2T}$)
+and choose $c$ so that
 \begin{equation*}

### 2014-03-28 paper.tex
Spellcheck paper

@@
 The condition~\ref{eq:27} requires that the acceptance region of
-$\Lambda$ eventually contains any finite cylindar centered at the
+$\Lambda$ eventually contains any finite cylinder centered at the
 origin. Again,~\eqref{eq:15} implies that statistics like the BIC
@@
 the rejection region is less than 1/2, since $M_2 \bh{2T}$ is
-uniformly distributed on the cylindar
+uniformly distributed on the cylinder
 \begin{equation*}
@@
 The AIC behaves essentially the same way. For the BIC, the radius of
-the cylander centered at the origin increases with $T$ and eventually
-encompasses the cylander centered at $M_2 \theta_2$, so it never
+the cylinder centered at the origin increases with $T$ and eventually
+encompasses the cylinder centered at $M_2 \theta_2$, so it never
 selects the alternative once $T$ is large enough.
@@
 our theory in small samples.
-We do several Monte Carlo exercises. The first looks at wheather our
-theoretical results for the OOS average are accuarate: whether or not
+We do several Monte Carlo exercises. The first looks at whether our
+theoretical results for the OOS average are accurate: whether or not
 the OOS average is approximately normal, and whether it is centered on
-$\E_R \oosA$, $\E_T \oosB$, or somewhere else entierely. The second
+$\E_R \oosA$, $\E_T \oosB$, or somewhere else entirely. The second
 issue is whether or not the \oost\ test is \emph{useful} for
@@
 the fixed window, but recursive window results are available in a
-separate Appendix and are broadly similary.
+separate Appendix and are broadly similar.
 
@@
 To study the accuracy of our theoretical approximations, we first
-estmate the coverage probabilities of OOS confidence intervals for
+estimate the coverage probabilities of OOS confidence intervals for
 $\E_R \oosA$ and $\E_T \oosB$. For each draw of $X$ and $Y$, we
@@
 simply means that the CLT is a poor approximation when the test sample
-is small. The inteval for $T = 100$, $K = T/10$, and $c = 0$ is the
+is small. The interval for $T = 100$, $K = T/10$, and $c = 0$ is the
 worst, with actual coverage near 85\% for most values of $P/T$. But
@@
 $P$.  The $F$-test does not depend on $P$, so we calculate and
-tabluate it's conditional rejection probability as a single value for
+tabulate it's conditional rejection probability as a single value for
 each combination of design parameters.
@@
 amount. Note that we are unable to plot results for McCracken's
-statistic when $K/T = 10$, which is where the brakdown in Clark and
+statistic when $K/T = 10$, which is where the breakdown in Clark and
 West's test is most pronounced.
@@
 invariant to reflection across the axes defined by the eigenvectors of
-its covariance matrix. So when $\theta_2$ lies outside the cylindar
+its covariance matrix. So when $\theta_2$ lies outside the cylinder
 that contains the acceptance region of $\Lambda$, i.e. when
 $\theta_2'M_2' V_T M_2 \theta_2 > c$, we have%
-\footnote{To keep the notation in these equations managable, define
+\footnote{To keep the notation in these equations manageable, define
   the information set $\Gs = \sigma(\E_T \oosB \leq 0,~ \theta_2'M_2'
@@
 
-%  LocalWords:  ClM Mcc ClW MeR StW InK CCS CoS GiW GiR BRC HTF BoH
+%  LocalWords:  ClM Mcc ClW MeR StW InK CCS CoS GiW GiR BRC HTF BoH '
 %  LocalWords:  Tib BaN AIC BoB AkA AkP Efr iR eq FPE th Dou iS iT dx
@@
 %  LocalWords:  lmtest Zei dbframe Hmsic Har xtable Dah booktabs FeE
-%  LocalWords:  Bonferroni BWB Gia MeP indices Schwarz HaH Jong
+%  LocalWords:  Bonferroni BWB Gia MeP indices Schwarz HaH Jong i1 1R
+%  LocalWords:  overcorrect 'X 's 2P i' 2i 2m 4C De eigenvectors 'M
+%  LocalWords:  2'M 1'M

### 2014-09-22 appendix.tex
Correct stupid spelling mistake in title of appendix
Minor tweaks to paper

@@
 
-\title{Supplamental Appendix for ``Out-of-Sample Comparisons of
+\title{Supplemental Appendix for ``Out-of-Sample Comparisons of
   Overfit Models''}
@@
 
-\begin{figure}\centering
+\begin{figure}[b]\centering
   {\large Coverage of recursive DMW OOS interval in simulations}

### 2014-09-22 paper.tex
Minor tweaks to paper

@@
 \author{Gray Calhoun\thanks{email: gcalhoun@iastate.edu. I
-    would like to thank Julian Betts, Helle Bunzel, Marjorie Flavin,
+    would like to thank Julian Betts, Helle Bunzel,
+    St\'ephane Bonhomme, Marjorie Flavin,
     Nir Jaimovich, Lutz Kilian, Ivana Komunjer, Michael McCracken,
@@
     Meetings, the 2011 NBER-NSF Time-Series
-    Conference, and in many seminars at UCSD, and espeically
+    Conference, and in many seminars at UCSD, and especially
     Graham Elliott for their valuable suggestions, feedback and advice
@@
 asymptotic theory, where the number of regressors $K$ increases with $T$
-so that $\lim K/T$ is positive and less than one,
+so that the limit of $K/T$ is positive and less than one,
 the OLS coefficient estimator is no longer
@@
 shrinkage forecast, for example the LASSO \citep{Tib:96} or a factor
-model \citep{StW:02,BaN:02}. Our main focus in practice is settings
+model \citep{StW:02,BaN:02}. Our main focus is practical settings
 where $K$ is \emph{moderately} large and it is not clear whether
-overfit will dominate the results. In such settings that, it is
-important to understand the behavior of different evaluation criteria
-when $K$ is large, in case overfit is a concern, and to have reliable
-methods for estimating the models' performance, which is the goal of
+overfit will dominate the results. In these settings it is
+crucial to understand the behavior of different evaluation criteria
+when $K$ is large, in case overfit does turn out to be a concern, and to have reliable
+methods for estimating these overfit models' performance. This is the goal of
 this paper.
@@
 asymptotically normal, but are centered on the forecasting performance
-associated with the period-$R$ estimates.  In practice, researchers
+associated with the period $R$ estimates.  In practice, researchers
 typically use large values of $P$, so these studies may be too
@@
 that these statistics do not select the more accurate model when
-choosing between overfit models. For many DGPs the Wald test and the
-will choose the larger alternative model over a small benchmark model
+choosing between overfit models. For many DGPs the Wald test
+will choose the larger model over a small benchmark
 with probability much greater than its nominal size, regardless of
@@
 underlying series are absolutely regular, even if the forecasts depend
-on non-convergent estimators.  Moreover, transformations of these
-processes also behave like mixingales when recentered, so 
+on non-convergent estimators.  Moreover, we also show that transformations of these
+processes behave like mixingales after they are appropriately recentered, so
 many arguments used to prove asymptotic
@@
 alternative, and shows that standard model selection methods can run
-into similar problems. Section~\ref{sec:mc}
+into similar problems. Section~\ref{sec:theory} also presents an
+example DGP that illustrates these results. Section~\ref{sec:mc}
 presents a Monte Carlo study supporting our theoretical results.
@@
 \cite{CCP:05}, \cite{EnW:05}, \cite{Ros:05}, and \cite{BWB:10}, among
-many others.
+many others. Research in financial markets has found a similar pattern,
+e.g. \cite{BoH:99}, \citet{GoW:08,GoW:03}, and \citet{Tim:08}.
 
@@
 conventional asymptotic theory, we would replace each $\bh{iR}$ with
-its pseudotrue value $\theta_i$ and apply the CLT to $\sqrt{P}
-L(y_{t+\h} - x_{it}'\theta_i)$, with some complications potentially
+its pseudotrue value $\theta_i$ and apply the CLT to
+$L(y_{t+\h} - x_{it}'\theta_i)$, with some complications potentially
 arising from the replacement (as in \citealp{Wes:96},
@@
 these quantities are generally close. But they are not for overfit
-models, and the models will tend to forecast better when estimated over the
+models and the models will tend to forecast better when estimated over the
 full sample than over the training sample. Consequently, OOS
@@
 normal and centered at $\E_T \oosB$, as long as
-Assumption~\ref{asmp-4}b holds. This theorem only establishes the
-asymptotic distribution, though.
+Assumption~\ref{asmp-4}b holds.
 
@@
 
-When $K_1$ and $K_2$ are fixed, West's (1996) and McCracken's (2007)
-asymptotic theories apply and the \oost\ test remains normal as long
+If $K_1$ and $K_2$ were finite, West's (1996) and McCracken's (2007)
+asymptotic theories would apply and the \oost\ test would remain normal as long
 as $P/T \to 0$, even if $\sigma^2 \to 0$. Under that asymptotic
@@
 DGP is nested in both of the forecasting models. The same principles
-may apply in our setting if $K_1$ and $K_2$ grow slowly, so $K_2/T \to
+may also apply if $K_1$ and $K_2$ grow slowly, with $K_2/T \to
 0$. It is likely that a second order expansion along the lines of
@@
 follow immediately from Theorem~\ref{res-oost},
-but~\eqref{eq:23} requires additional steps.
+but~\eqref{eq:23} requires additional proof.
 
@@
 generally.%
-\footnote{Also, define $M_1 = [I_{K_1} \ 0_{K_1 \times (K_2 - K_1)}]$
+\footnote{In this section, we define $M_1 = [I_{K_1} \ 0_{K_1 \times (K_2 - K_1)}]$
   and $M_2 = [0_{(K_2 - K_1) \times K_2} \ I_{K_2 - K_1}]$ as the
@@
   \begin{equation}\label{eq:11}
-    \liminf_{T \to \infty} \E( \Lambda \mid \E_T \oosB \leq 0 )
-    \to^p \gamma > 1/2 - \delta.
+    \liminf_{T \to \infty} \E( \Lambda \mid \E_T \oosB \leq 0 ) \geq 1/2.
   \end{equation}
@@
 region enclosed by $\1\{\bh{2T}'M_2' V_T M_2\bh{2T}\}$ and DGPs can be
-chosen to put $\gamma$ arbitrarily close to 1 while still satisfying
+chosen to put the limiting quantity in~\eqref{eq:11}
+arbitrarily close to 1 while still satisfying
 the assumptions of the Theorem.  The DGPs and
@@
 
-For example, the $F$-statistic to test the null hypothesis that the
+For example, the $F$-statistic for the null hypothesis that the
 benchmark model is correctly specified is known to have the form
@@
 has uniformly bounded eigenvalues and has rank $K_2 - K_1$, so it
-satisfies~\eqref{eq:25}.%
-\footnote{If it is surprising that these conditions hold for any $c >
-  1$, remember that the $F$ random variable converges to 1 in
-  probability as both degrees of freedom diverge to $\infty$ since its
-  numerator and denominator both obey the LLN.} %
+satisfies~\eqref{eq:25}.
 Robust variations of the Wald test can obviously satisfy~\eqref{eq:25}
@@
   \begin{equation}\label{eq:27}
-    \Pr[\Lambda \leq \1\{\bh{2T}'M_2' M_2\bh{2T} > c \}] \to 1
+    \Pr[\Lambda \leq \1\{\bh{2T}'M_2'J M_2\bh{2T} > c \}] \to 1
     \quad \text{as } T \to \infty.
@@
 
-The condition~\ref{eq:27} requires that the acceptance region of
+The condition~\eqref{eq:27} requires that the acceptance region of
 $\Lambda$ eventually contains any finite cylinder centered at the
@@
 This subsection illustrates the previous theoretical results with a
-concrete Let $L(e) = e^2$ and $h = 1$. Suppose that the benchmark is
+concrete example. Let $L(e) = e^2$ and $h = 1$. Suppose that the benchmark is
 nested in the alternative and $(x_{2t}, \e_{2,t+1}) \sim i.i.d.\
@@
 Section~\ref{sec:asmp} are satisfied and the second part
-demonstrates asymptotic normality of the DMW OOS $t$-test. The third
+demonstrates asymptotic normality of the DMW \oost\ test. The third
 part explicitly shows that $\E_R \oosA$ converges to $\E_T \oosB$ only
 when the test sample is small. And the last part demonstrates that the
-$F$-test, AIC, and BIC do not indicate which model will be more
+$F$-test does not indicate which model will be more
 accurate in the future, even in this simple example.
@@
 
-We will go through the assumptions one by one. The first Assumption is
+We will go through the assumptions one by one. The first is
 a condition on the dependence and moments of the process. Since the
@@
 For the conditional expectation of %
-$\sum_{s,t=U}^{V-\h} \e_{i,t+\h} \e_{i,s+\h} x_{i,s} x_{i,t}'$,
+$\sum_{s,t=U}^{V-1} \e_{i,t+1} \e_{i,s+1} x_{i,s} x_{i,t}'$,
 independence implies that
@@
   \E\Big(
-  \sum_{s,t=U}^{V-\h} \e_{i,s+\h} \e_{i,t+\h} x_{is}x_{it}'
+  \sum_{s,t=U}^{V-1} \e_{i,s+1} \e_{i,t+1} x_{is}x_{it}'
   \mBig
   x_{i1},\dots,x_{i,U-1};
-  \sum_{s=U}^{V-\h} x_{is} x_{is}';
-  x_{i,V-\h+1},\dots,x_{i,T-\h}
+  \sum_{s=U}^{V-1} x_{is} x_{is}';
+  x_{i,V},\dots,x_{i,T-1}
   \Big)
-  = \sum_{s=U}^{V-\h} x_{is} x_{is}'.
+  = \sum_{s=U}^{V-1} x_{is} x_{is}'.
 \end{equation*}
 The largest eigenvalue of this last matrix is of order $K_i + V - U$,
-as discussed, and it has at most $V-\h - U + 1$ nonzero eigenvalues,
+as discussed, and it has at most $V - U$ nonzero eigenvalues,
 ensuring that both~\eqref{eq:28} and~\eqref{eq:8} hold.
@@
 \begin{equation*}
-  \sh^2 = \frac{1}{n} \sum_{t=R+1}^{T-1} (D_t - \oosA)^2
+  \sh^2 = \frac{1}{P} \sum_{t=R+1}^{T-1} (D_t - \oosA)^2
 \end{equation*}
@@
 the fixed window, but recursive window results are available in a
-separate Appendix and are broadly similar.
+separate Appendix and are similar.
 
@@
 combination of $T$, $K_1$ and $K_2$, and $c$.  The nominal coverage is
-90\%.  The gray horizontal line shows the intervals' nominal coverage
-probability.  Each panel displays the coverage for a different choice
-of design parameters.
+90\% and is represented with a gray horizontal line. Each panel
+displays the coverage for a different choice of design parameters.
 
@@
 Figures~\ref{fig:ftest}--\ref{fig:ttest-power}.  For the OOS tests
-We plot each OOS test's conditional rejection probability,
+we plot each OOS test's conditional rejection probability,
 \begin{equation*}
@@
 
-\bibliographystyle{abbrvnat}
-\bibliography{references}
 \clearpage
+
+\tryinput{floats/mc-ftest.tex}
 
@@
 
-\tryinput{floats/mc-ftest.tex}
-
 \begin{figure}\centering
@@
 
+\clearpage
+
+\bibliographystyle{abbrvnat}
+\bibliography{references}
+
 \end{document}
@@
 %  LocalWords:  overcorrect 'X 's 2P i' 2i 2m 4C De eigenvectors 'M
-%  LocalWords:  2'M 1'M
+%  LocalWords:  2'M 1'M DiM GoW Cla Whi RoW HHK Rde

### 2016-01-23 paper.tex
[#47] Remove repeated use of "on the" in the paper
This commit fixes a minor typo that a referee pointed out.

@@
 between the models' generalization error, the expected loss in the
-future conditional on the on the data available in period
+future conditional on the data available in period
 $T$.%

### 2016-01-23 paper.tex
[#36] Clarify that we use *strict* stationarity in Assumption 1
One of the referees found the statement of "stationarity" without any
modification a bit confusing and initially assumed *weak* stationarity.
This commit removes that confusion.

@@
 \begin{asmp}\label{asmp-1}
-  The random array $\{y_t,x_t\}$ is stationary and absolutely regular
+  The random array $\{y_t,x_t\}$ is strictly stationary and absolutely regular
   with coefficients $\beta_j$ of size $-\rho/(\rho-2)$; $\rho$ is

### 2016-01-23 paper.tex
[#34] Add definition of 'OOS' to body of the paper
This addresses a concern of one of the referees.
[#33] Revise abstract
This commit addresses a point raised by one of the referees about
defining $P$, but it also rewrites the abstract substantially to
try to make it more clear.

@@
 \begin{abstract}\noindent
-  This paper uses dimension asymptotics to study why overfit linear
-  regression models should be compared out-of-sample; we let the
-  number of predictors used by the larger model increase with the
+  This paper uses dimension asymptotics to study the behavior of
+  out-of-sample (OOS) test statistics when they are used to compare
+  ``overfit'' linear regression models. Under these asymptotics, the
+  number of predictors used by the larger model increases with the
   number of observations so that their ratio remains uniformly
-  positive.  Our analysis gives a theoretical motivation for using
-  out-of-sample (OOS) comparisons: the DMW OOS test allows a forecaster to
-  conduct inference about the expected future accuracy of his or her
-  models when one or both is overfit.  We show analytically and
-  through Monte Carlo that standard full-sample test statistics can
-  not test hypotheses about this performance.  Our paper also shows
-  that popular test and training sample sizes may give misleading
-  results if researchers are concerned about overfit.  We show that
-  $P^2/T$ must converge to zero for the DMW test to give valid
-  inference about the expected forecast accuracy, otherwise the test
-  measures the accuracy of the estimates constructed using only the
-  training sample.  In empirical research, $P$ is typically much
-  larger than this.  Our simulations indicate that using large values
-  of $P$ with the DMW test gives undersized tests with low power, so
-  this practice may favor simple benchmark models too much.
+  positive. This analysis gives a theoretical motivation for using
+  out-of-sample (OOS) comparisons: the Diebold-Mariano-West OOS $t$-test
+  (Diebold and Mariano, 1995, \textit{JBES}, and West, 1996,
+  \textit{Econometrica}) allows a forecaster to conduct inference
+  about the models' generalization error, an important measure of
+  forecast accuracy that conditions on the models' parameter estimates.
+  We show analytically and through Monte Carlo that standard full-sample
+  test statistics can not test hypotheses about this measure of performance.
+  Our paper also suggests that comparisons of overfit models require small
+  OOS test samples. If $P$ denotes the number of observations used for the
+  OOS comparison and $T$ the total number of observations, $P^2/T$ must
+  converge to zero for the OOS $t$-test to be centered on the model's
+  generalization error.
 
@@
 models is overfit.  In doing so, we provide a theoretical
-justification for forecasters to use OOS instead of in-sample
+justification for forecasters to use out-of-sample (OOS) instead of in-sample
 comparisons: the DMW OOS test%

### 2016-01-31 latex-tools-0.2.1/version_git.sh
[#49] Import latex-tools repository as subdirectory
We're going to use the version_git bash script and makefile snippet
to automatically generate a version and commit stamp for the pdfs
produced in this repository. To make life easier for potential
researchers not familiar with Git, I'm just going to add the current
version of the latex-tools repository as a subdirectory instead of
using a submodule. This commit adds that subdirectory.

@@ -1,0 +1,44 @@
+# This file is a simplified version of
+# <https://github.com/JuliaLang/julia/blob/95ee26932b9cd0ed748e18853c6bf5de769edb06/base/version_git.sh>
+# which is a part of Julia. License is MIT:
+# <http://julialang.org/license>
+
+last_tag=$(git describe --tags --abbrev=0)
+git_time=$(git log -1 --pretty=format:%ct)
+
+#collect the contents
+commit=$(git rev-parse HEAD)
+commit_short=$(git rev-parse --short HEAD)
+if [ -n "$(git status --porcelain)" ]; then
+    # append dirty mark '*' if the repository has uncommited changes
+    commit_short="$commit_short"*
+fi
+branch=$(git branch | sed -n '/\* /s///p')
+# Some versions of wc (eg on OS X) add extra whitespace to their output.
+# The sed(1) call stops this from breaking the generated Julia's indentation by
+# stripping all non-digits.
+build_number=$(git rev-list HEAD ^$last_tag | wc -l | sed -e 's/[^[:digit:]]//g')
+# Check for errrors and emit default value for missing numbers.
+if [ -z "$build_number" ]; then
+    build_number="0"
+fi
+
+date_string=$git_time
+case $(uname) in
+  Darwin | FreeBSD)
+    date_string="$(/bin/date -jr $git_time -u '+%Y-%m-%d')"
+    ;;
+  MINGW*)
+    git_time=$(git log -1 --pretty=format:%ci)
+    date_string="$(/bin/date --date="$git_time" -u '+%Y-%m-%d')"
+    ;;
+  *)
+    date_string="$(/bin/date --date="@$git_time" -u '+%Y-%m-%d')"
+    ;;
+esac
+
+if [ $(git describe --tags --exact-match 2> /dev/null) ]; then
+    echo $(git describe --tags --exact-match)
+else
+    echo "$date_string, commit $commit_short"
+fi

### 2016-01-31 paper.tex
[#51] Switch BibTeX database to latex-tools version
This switch adds records for a few papers and (probably more important)
updates the records of a few of my papers in the BibTeX database. The
bibtex keys change for those papers, so the files need to be updated
in the LaTeX files as well.

@@
-\documentclass[12pt]{article}
+\documentclass[12pt,draft]{article}
+\input{VERSION}
 \input{setup}
@@
 explicitly account for the multiplicity of model comparisons%
-\footnote{\citet{RaW:06}, \citet{RaZ:12}, and \citet{Cal:13b} are
+\footnote{\citet{RaW:06}, \citet{RaZ:12}, and \citet{Cal:15} are
   exceptions.} %
@@
 \bibliographystyle{abbrvnat}
-\bibliography{references}
+\bibliography{latex-tools-0.2.1/references}
 

### 2016-03-09 appendix.tex
[#51] Switch BibTeX database to latex-tools version
This switch adds records for a few papers and (probably more important)
updates the records of a few of my papers in the BibTeX database. The
bibtex keys change for those papers, so the files need to be updated
in the LaTeX files as well.
[#49] Add code to generate and import Git info into LaTeX files
This commit adds code to the makefile to generate a (short) new file VERSION.tex
with information on the repository version (if the commit is tagged) or commit.
That imformation is included as the date and header of the final pdfs.
Include appen

--- 2014-03-25 appendix.tex
@@
-\documentclass[12pt]{article}
+\documentclass[12pt,draft]{article}
 \input{setup}
 
-\title{Supplamental Appendix for ``Out-of-Sample Comparisons of
+\title{Supplemental Appendix for ``Out-of-Sample Comparisons of
   Overfit Models''}
@@
 
+\date{\VERSION}
+
 \begin{document}
@@
 
-This appendix presents simulation results that accompany
-\cite{Cal:14}. As in the main paper, these simulations were conducted
-in R \citep{Rde:10} using the MASS \citep{VeR:02}, Matrix
-\citep{BM:13}, rlecuyer \citep{SR:12}, and RSQLite \citep{Jam:10}
-packages. Graphs were produced in R using Lattice \citep{Sar:10} and
-tikzDevice \citep{ShB:11:0.6.1}.
+\input{appendix_contents.tex}
 
-\nocite{DiM:95,Wes:96,Mcc:07,ClW:06,ClW:07}
 \bibliographystyle{abbrvnat}
-\bibliography{references}
-
-\begin{figure}\centering
-  {\large Coverage of recursive DMW OOS interval in simulations}
-  \input{floats/mc-interval-generror1-rec.tex}
-  \caption{Simulated coverage of $\E_T \oosB$ at 90\% confidence using
-    a one-sided interval based on the recursive DMW \oost\ test,
-    plotted as a function of the fraction of observations used in the
-    test sample, $P/T$.  The solid horizontal line denotes the
-    intervals' nominal coverage.}
-  \label{fig:interval-T}
-\end{figure}
-
-\begin{figure}\centering
-  {\large Size of recursive DMW \oost\ test in simulations}
-  \input{floats/mc-dmwsize-rec.tex}
-  \caption{Simulated rejection probabilities for the recursive DMW
-    \oost\ test under the null hypothesis that the benchmark model is
-    more accurate, $\E_T \oosB \leq 0$. Nominal size is 10\% and is
-    marked with a solid horizontal line. Values greater than 10\%
-    indicate that the test rejects the benchmark model too often.}
-  \label{fig:ttest-size}
-\end{figure}
-
-\begin{figure}\centering
-  {\large Size of recursive Clark-West OOS test in simulations}
-  \input{floats/mc-clarkwestsize-rec.tex}
-  \caption{Simulated rejection probabilities for Clark and West's
-    (2006, 2007) recursive OOS test statistic under the null
-    hypothesis that the benchmark model is more accurate, $\E_T \oosB
-    \leq 0$. Nominal size is 10\% and is marked with a solid
-    horizontal line. Values greater than 10\% indicate that the test
-    rejects the benchmark model too often.}
-  \label{fig:clarkwest}
-\end{figure}
-
-\begin{figure}\centering
-  {\large Size of recursive McCracken \oost\ test in simulations}
-  \input{floats/mc-mccrackensize-rec.tex}
-  \caption{Simulated rejection probabilities for McCracken's (2007)
-    recursive \oost\ test under the null hypothesis that the benchmark
-    model is more accurate, $\E_T \oosB \leq 0$. Nominal size is 10\%
-    and is marked with a solid horizontal line. Values greater than
-    10\% indicate that the test rejects the benchmark model too
-    often.}
-  \label{fig:mccracken}
-\end{figure}
-
-\begin{figure}\centering
-  {\large Power of recursive DMW \oost\ test in simulations}
-  \input{floats/mc-dmwpower-rec.tex}
-  \caption{Simulated rejection probabilities for the recursive DMW
-    \oost\ test under the alternative that the benchmark model is less
-    accurate, $\E_T \oosB > 0$. Nominal size is 10\% and is marked
-    with a solid horizontal line. Values greater than 10\% indicate
-    that the test rejects the benchmark model too often.}
-  \label{fig:ttest-power}
-\end{figure}
+\bibliography{latex-tools-0.2.1/references}
 \end{document}
@@
 %%% mode: latex
-%%% TeX-master: "appendix"
+%%% TeX-master: "appendix.tex"
+%%% TeX-command-extra-options: "-shell-escape"
 %%% End:

### 2016-03-09 appendix_contents.tex
Include appendix with main paper for convenience to referees

This appendix presents simulation results that accompany
\citet{Cal:15b}. The Monte Carlo here is exactly the same as presented
in \citet{Cal:15b}, except that a recursive window is used. Please read
the original paper for further details.

\begin{itemize}

\item Figure 1 in this Appendix corresponds to Figure 3 in the
  original paper.
\item Figure 2 corresponds to Figure 4 in the paper.
\item Figure 3 corresponds to Figure 5 in the paper.
\item Figure 4 corresponds to Figure 6 in the paper.
\item Figure 5 corresponds to Figure 7 in the paper.

\end{itemize}

\nocite{DiM:95,Wes:96,Mcc:07,ClW:06,ClW:07}
\begin{figure}[b]\centering
  {\large Coverage of recursive DMW OOS interval in simulations}
  \input{floats/mc-interval-generror1-rec.tex}
  \caption{Simulated coverage of $\E_T \oosB$ at 90\% confidence using
    a one-sided interval based on the recursive DMW \oost\ test,
    plotted as a function of the fraction of observations used in the
    test sample, $P/T$.  The solid horizontal line denotes the
    intervals' nominal coverage.}
  \label{fig:interval-T}
\end{figure}

\begin{figure}\centering
  {\large Size of recursive DMW \oost\ test in simulations}
  \input{floats/mc-dmwsize-rec.tex}
  \caption{Simulated rejection probabilities for the recursive DMW
    \oost\ test under the null hypothesis that the benchmark model is
    more accurate, $\E_T \oosB \leq 0$. Nominal size is 10\% and is
    marked with a solid horizontal line. Values greater than 10\%
    indicate that the test rejects the benchmark model too often.}
  \label{fig:ttest-size}
\end{figure}

\begin{figure}\centering
  {\large Size of recursive Clark-West OOS test in simulations}
  \input{floats/mc-clarkwestsize-rec.tex}
  \caption{Simulated rejection probabilities for Clark and West's
    (2006, 2007) recursive OOS test statistic under the null
    hypothesis that the benchmark model is more accurate, $\E_T \oosB
    \leq 0$. Nominal size is 10\% and is marked with a solid
    horizontal line. Values greater than 10\% indicate that the test
    rejects the benchmark model too often.}
  \label{fig:clarkwest}
\end{figure}

\begin{figure}\centering
  {\large Size of recursive McCracken \oost\ test in simulations}
  \input{floats/mc-mccrackensize-rec.tex}
  \caption{Simulated rejection probabilities for McCracken's (2007)
    recursive \oost\ test under the null hypothesis that the benchmark
    model is more accurate, $\E_T \oosB \leq 0$. Nominal size is 10\%
    and is marked with a solid horizontal line. Values greater than
    10\% indicate that the test rejects the benchmark model too
    often.}
  \label{fig:mccracken}
\end{figure}

\begin{figure}\centering
  {\large Power of recursive DMW \oost\ test in simulations}
  \input{floats/mc-dmwpower-rec.tex}
  \caption{Simulated rejection probabilities for the recursive DMW
    \oost\ test under the alternative that the benchmark model is less
    accurate, $\E_T \oosB > 0$. Nominal size is 10\% and is marked
    with a solid horizontal line. Values greater than 10\% indicate
    that the test rejects the benchmark model too often.}
  \label{fig:ttest-power}
\end{figure}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "appendix"
%%% End:

### 2016-03-09 paper.tex
[#49] Add code to generate and import Git info into LaTeX files
This commit adds code to the makefile to generate a (short) new file VERSION.tex
with information on the repository version (if the commit is tagged) or commit.
That imformation is included as the date and header of the final pdfs.
[#49] Tweak formatting and display of Git commit info
The commit information (date and hash) is posted in the header
of each page.
Include appendix with main paper for convenience to referees

@@
 \documentclass[12pt,draft]{article}
-\input{VERSION}
 \input{setup}
@@
     with Ivo Welch \citep{GoW:08}.} \\ Iowa State University}
+
+\date{\VERSION}
 
@@
 justification for forecasters to use out-of-sample (OOS) instead of in-sample
-comparisons: the DMW OOS test%
-\footnote{In this paper, we will refer to the basic OOS $t$-test
-  studied by \citet{DiM:95} and \citet{Wes:96} as the DMW test.} %
+comparisons: the DMW OOS test\footnote{%
+  In this paper, we will refer to the basic OOS $t$-test studied by
+  \citet{DiM:95} and \citet{Wes:96} as the DMW test.} %
 allows a forecaster to conduct
@@
 conditions that permit in-sample comparisons \citep[see][for a
-review of this literature]{Wes:06}.%
-\footnote{Like us, \citet{Ana:07} allows the number of regressors to
-  increase with $T$.  But in that paper, the number of regressors
-  increases slowly enough that the OLS coefficients are consistent and
+review of this literature]{Wes:06}.\footnote{%
+  Like us, \citet{Ana:07} allows the number of regressors to increase
+  with $T$.  But in that paper, the number of regressors increases
+  slowly enough that the OLS coefficients are consistent and
   asymptotically normal.} %
@@
 future conditional on the data available in period
-$T$.%
-\footnote{See, for example, \citet{HTF:08} for a discussion of
-  generalization error.} %
+$T$.\footnote{%
+  See, for example, \citet{HTF:08} for a discussion of generalization
+  error.} %
 Under these asymptotics, the generalization
@@
 an OOS comparison would correctly fail to reject the null that the
-benchmark is more accurate.%
-\footnote{In a pair of papers similar to
-  ours, \citet{ClM:12,ClM:12b} study in-sample and OOS tests that
-  the larger model has nonzero coefficients that are too close to zero
-  to expect the model to forecast more accurately.  Like this paper,
-  they argue that the larger model can be true but less accurate.
-  However, they focus on an aspect of the DGP that makes this
-  phenomenon likely, while we focus on the coefficient estimates that
-  produce less accurate forecasts.  Moreover, the implications of our
-  asymptotic theories are different and their papers do not provide
-  reasons to do OOS comparisons.} %
+benchmark is more accurate.\footnote{%
+  In a pair of papers similar to ours, \citet{ClM:12,ClM:12b} study
+  in-sample and OOS tests that the larger model has nonzero
+  coefficients that are too close to zero to expect the model to
+  forecast more accurately.  Like this paper, they argue that the
+  larger model can be true but less accurate.  However, they focus on
+  an aspect of the DGP that makes this phenomenon likely, while we
+  focus on the coefficient estimates that produce less accurate
+  forecasts.  Moreover, the implications of our asymptotic theories
+  are different and their papers do not provide reasons to do OOS
+  comparisons.} %
 Also note that, in this situation, a model that performs well
@@
 however, chooses the benchmark model with probability approaching one
-even when the \emph{alternative} model is more accurate.%
-\footnote{Our result holds for a broad class of full-sample
-  statistics, but there may be other potential statistics that mimic
-  the OOS test and remain valid. Exploring such statistics is left for
-  future research.} %
+even when the \emph{alternative} model is more accurate.\footnote{%
+  Our result holds for a broad class of full-sample statistics, but
+  there may be other potential statistics that mimic the OOS test and
+  remain valid. Exploring such statistics is left for future
+  research.} %
 This result holds even though modifications of the $F$-test are valid
@@
 \citet{AkA:00}, \citet{AkP:04}, \citet{Cal:11c}, and \citet{Ana:12},
-among others.%
-\footnote{Also see \citet{Efr:86,Efr:04} for a discussion of naive
-  in-sample loss comparisons.} %
+among others.\footnote{%
+  Also see \citet{Efr:86,Efr:04} for a discussion of naive in-sample
+  loss comparisons.} %
 Moreover, under this asymptotic theory, many recent OOS test
@@
 \citet{Mcc:07}, and \citet{ClW:06,ClW:07} should have the same
-problems as in-sample tests.%
-\footnote{Our theoretical results apply directly to \citepos{Mcc:07}
-  OOS $t$-test, since it simply proposes more liberal critical values
-  for the same test statistic that we study.  Since
-  \citet{ClW:06,ClW:07} use a finite length estimation window, our
-  asymptotics are incompatible with theirs and prevent us from
-  studying their test directly, as well as \citepos{GiW:06} and other
-  tests based on \citepos{GiW:06} asymptotics.  But \clws\ test can be
-  viewed as a stochastic adjustment to the critical values of the
-  usual \oost\ test, so our conclusions should apply informally as
-  well.  Specifically, we show that the DMW test rejects with
-  probability equal to nominal size when the estimated benchmark model
-  is expected to be more accurate, so more liberal critical values
-  result in overrejection.} %
+problems as in-sample tests.\footnote{%
+  Our theoretical results apply directly to \citepos{Mcc:07} OOS
+  $t$-test, since it simply proposes more liberal critical values for
+  the same test statistic that we study.  Since \citet{ClW:06,ClW:07}
+  use a finite length estimation window, our asymptotics are
+  incompatible with theirs and prevent us from studying their test
+  directly, as well as \citepos{GiW:06} and other tests based on
+  \citepos{GiW:06} asymptotics.  But \clws\ test can be viewed as a
+  stochastic adjustment to the critical values of the usual \oost\
+  test, so our conclusions should apply informally as well.
+  Specifically, we show that the DMW test rejects with probability
+  equal to nominal size when the estimated benchmark model is expected
+  to be more accurate, so more liberal critical values result in
+  overrejection.} %
 These tests are also designed to reject the benchmark when the
@@
   \bh{it} = \Big(\sum_{s=1}^{R-\h} x_{is}x_{is}'\Big)^{-1} \sum_{s=1}^{R-\h}
-  x_{is} y_{s+\h}, \qquad \text{for } i=1,2;\ t = R+1,\dots, T - \h.%
-\footnote{It may not be clear why we are using the index $t$ in $\bh{it}$,
+  x_{is} y_{s+\h}, \qquad
+  \text{for } i=1,2;\ t = R+1,\dots, T - \h.\footnote{%
+    It may not be clear why we are using the index $t$ in $\bh{it}$,
     since $\bh{it} = \bh{iR}$ almost surely for all $t \leq T-h$.
@@
 literature, but we focus on perhaps the most natural, the DMW \oost\
-test \citep{DiM:95,Wes:96}.%
-\footnote{The core insights of our paper apply to other OOS statistics
-  as well.} %
+test \citep{DiM:95,Wes:96}.\footnote{%
+  The core insights of our paper apply to other OOS statistics as
+  well.} %
 This statistic is based on
@@
 Autocorrelation-Consistent, or HAC, estimator.)
-
-Statistics like $\oost$ have a long history in empirical economics
-because they capture an intuitive idea of model fit: that a good model
-should be able to forecast well on new data. \cite{MeR:83}
-use such a statistic to study exchange rate models and find that none
-of the models that existed at the time of their study outperform a
-random walk. This finding has been remarkably durable and has spawned
-an enormous literature; see \cite{Mar:95}, \cite{KiT:03},
-\cite{CCP:05}, \cite{EnW:05}, \cite{Ros:05}, and \cite{BWB:10}, among
-many others. Research in financial markets has found a similar pattern,
-e.g. \cite{BoH:99}, \citet{GoW:08,GoW:03}, and \citet{Tim:08}.
 
@@
 converge in probability to the difference in the expected loss
-associated with the pseudotrue models,%
-\footnote{This statement is subject to the usual assumptions: some
-  form of stationarity, bounded moments, and weak dependence.} %
+associated with the pseudotrue models,\footnote{%
+  This statement is subject to the usual assumptions: some form of
+  stationarity, bounded moments, and weak dependence.} %
 \begin{equation}\label{eq:22}
@@
 satisfies the CLT. Mixingales satisfy a weak-dependence condition
-similar to MDSes,%
-\footnote{An array $Z_{n,t}$ and an increasing sequence of \sfields
+similar to MDSes,\footnote{%
+  An array $Z_{n,t}$ and an increasing sequence of \sfields
   $\Gs_{n,t}$ is an \emph{$L_2$-mixingale of size $-1/2$} if there is
@@
 mixingale processes require additional assumptions to hold beyond the
-mixingale property.%
-\footnote{See \citet{Jon:97} for an illustration. We will borrow
-  heavily from his results in our proofs.} %
+mixingale property.\footnote{%
+  See \citet{Jon:97} for an illustration. We will borrow heavily from
+  his results in our proofs.} %
 This is in contrast to Near Epoch Dependent (NED) processes, which
@@
 demonstrate, variations of the Wald test can be valid for those
-hypotheses under increasing-$K$ asymptotics.%
-\footnote{\citet{Ana:12} shows that the Wald test is invalid in
-  general and gives an adjustment that corrects the critical values;
-  he also shows that the $F$-test is asymptotically valid under
-  certain conditions on the distribution of the regressors.
-  \citet{Cal:11c} shows that the $F$-test is asymptotically invalid
-  without Anatolyev's constraint, even under homoskedasticity, and
-  provides a correction that gives valid tests.  Both papers only
-  consider independent observations.} %
+hypotheses under increasing-$K$ asymptotics.\footnote{%
+  \citet{Ana:12} shows that the Wald test is invalid in general and
+  gives an adjustment that corrects the critical values; he also shows
+  that the $F$-test is asymptotically valid under certain conditions
+  on the distribution of the regressors.  \citet{Cal:11c} shows that
+  the $F$-test is asymptotically invalid without Anatolyev's
+  constraint, even under homoskedasticity, and provides a correction
+  that gives valid tests.  Both papers only consider independent
+  observations.} %
 To simplify the presentation and the intuition we only derive results
 for nested models and for MSE loss, but the conclusions hold much more
-generally.%
-\footnote{In this section, we define $M_1 = [I_{K_1} \ 0_{K_1 \times (K_2 - K_1)}]$
-  and $M_2 = [0_{(K_2 - K_1) \times K_2} \ I_{K_2 - K_1}]$ as the
-  selection matrices that return the first $K_1$ and the last $K_2 -
-  K_1$ elements of $\theta_2$, and assume that the regressors are
-  ordered so that the first $K_1$ elements of $x_{2,t}$ correspond to
-  $x_{1,t}$.} %
+generally.\footnote{%
+  In this section, we define
+  $M_1 = [I_{K_1} \ 0_{K_1 \times (K_2 - K_1)}]$ and
+  $M_2 = [0_{(K_2 - K_1) \times K_2} \ I_{K_2 - K_1}]$ as the
+  selection matrices that return the first $K_1$ and the last
+  $K_2 - K_1$ elements of $\theta_2$, and assume that the regressors
+  are ordered so that the first $K_1$ elements of $x_{2,t}$ correspond
+  to $x_{1,t}$.} %
 
@@
 DMW $t$-test, the OOS $t$-test using McCracken's (2007) critical
-values,%
-\footnote{These critical values are not published for $K_2-K_1>10$, so
-  we do not report them for $K_2 = T/10$.} %
-and Clark and West's (2006, 2007) Gaussian out-of-sample statistic.%
-\footnote{Clark and West (2006, 2007) derive their statistic using the
-  rolling window estimation scheme. Here we use the same statistic,
-  but with a fixed window scheme. A supplemental appendix presents
-  results for their statistic, using the recursive window.} %
+values,\footnote{%
+  These critical values are not published for $K_2-K_1>10$, so we do
+  not report them for $K_2 = T/10$.} %
+and Clark and West's (2006, 2007) Gaussian out-of-sample
+statistic.\footnote{%
+  Clark and West (2006, 2007) derive their statistic using the rolling
+  window estimation scheme. Here we use the same statistic, but with a
+  fixed window scheme. A supplemental appendix presents results for
+  their statistic, using the recursive window.} %
 For the $F$-test, we simply test whether the coefficients on the
@@
 the DMW test, simulating from \eqref{eq:1} with $c = 1$ or 2 subject
-to the constraint that $\E_T \oosB > 0$.%
-\footnote{Draws of $X$ and $Y$ with $\E_T \oosB > 0$ are very rare
-  when $c=0$, so we do not present results for that value of $c$.} %
+to the constraint that $\E_T \oosB > 0$.\footnote{%
+  Draws of $X$ and $Y$ with $\E_T \oosB > 0$ are very rare when $c=0$,
+  so we do not present results for that value of $c$.} %
 Since the other test statistics greatly overreject, we do not present
@@
 predict the equity premium (calculated as the difference between the
-return on the S\&P 500 index and the T-bill rate).%
-\footnote{\citet{GoW:08} builds on previous research by \citet{BoH:99}
-  and \cite{GoW:03}.} %
+return on the S\&P 500 index and the T-bill rate).\footnote{%
+  \citet{GoW:08} builds on previous research by \citet{BoH:99} and
+  \cite{GoW:03}.} %
 Their analysis has two notable features: Goyal and Welch compare different
@@
 Goyal and Welch's original working paper published in the same special
-issue of \textit{The Review of Financial Studies} as \citet{GoW:08}.%
-\footnote{Those papers are \citet{CaT:08}, \citet{Coc:08},
-  \citet{BRW:08}, and \citet{LeN:08}.} %
+issue of \textit{The Review of Financial Studies} as
+\citet{GoW:08}.\footnote{%
+  Those papers are \citet{CaT:08}, \citet{Coc:08}, \citet{BRW:08}, and
+  \citet{LeN:08}.} %
 
@@
 see Goyal and Welch's original paper for detailed information about
-these variables.%
-\footnote{Table~\ref{tab:equity} only lists the variables used in
+these variables.\footnote{%
+  Table~\ref{tab:equity} only lists the variables used in
   \citepos{GoW:08} ``kitchen sink'' model.  Some of the variables that
-  they use are excluded from this model either
-  because the series are too short or because the variables are linear
-  combinations of other variables.} %
+  they use are excluded from this model either because the series are
+  too short or because the variables are linear combinations of other
+  variables.} %
 
@@
 model. Very few papers in the equity-premium predictability literature
-explicitly account for the multiplicity of model comparisons%
-\footnote{\citet{RaW:06}, \citet{RaZ:12}, and \citet{Cal:15} are
+explicitly account for the multiplicity of model comparisons\footnote{%
+  \citet{RaW:06}, \citet{RaZ:12}, and \citet{Cal:15} are
   exceptions.} %
@@
 For example, Table~\ref{tab:gwinsample} presents two full-sample
-coefficient estimates for each of the 12 predictors we consider.%
-\footnote{For all of our full sample results, we studentize the
+coefficient estimates for each of the 12 predictors we
+consider.\footnote{%
+  For all of our full sample results, we studentize the
   regressors to make it easier to compare coefficient estimates and we
@@
 \end{equation*}
-and the fourth column is the $p$-value associated with its $t$-test.%
-\footnote{All of the standard errors were calculated using a
-  Newey-West kernel with two lags.} %
+and the fourth column is the $p$-value associated with its
+$t$-test.\footnote{%
+  All of the standard errors were calculated using a Newey-West kernel
+  with two lags.} %
 Some of the coefficient estimates agree, but some do not. The
@@
 Results for the full sample estimates of these models are in
-Table~\ref{tab:gwinsample}.%
-\footnote{Calculations in this section are done in R \citep{Rde:10}
-  using the \emph{lmtest} \citep{ZeH:02} and \emph{sandwich}
-  \citep{Zei:04} packages.}%
-\footnote{We compare the test statistic to critical values from the
+Table~\ref{tab:gwinsample}.\footnote{%
+  Calculations in this section are done in R \citep{Rde:10} using the
+  \emph{lmtest} \citep{ZeH:02} and \emph{sandwich} \citep{Zei:04}
+  packages.}\footnote{%
+  We compare the test statistic to critical values from the
   $F$-distribution, which have been shown to be more reliable than
@@
 population and at least one of these predictors is correlated with the
-equity premium.%
-\footnote{We have done additional analysis to try to identify which
-  predictors were correlated with the equity premium, but none of the
-  individual regressors were significant after correcting for
-  multiplicity. The Bonferroni correction, for example, suggests that
-  an individual $p$-value would need to be less than $0.10/12 \approx
-  0.0083$ for its corresponding coefficient to be significant at the
-  10\% level, but the smallest $p$-value is $0.035$. One can improve
-  on the Bonferroni correction, of course, but a comprehensive
-  analysis is beyond the scope of this paper.} %
+equity premium.\footnote{%
+  We have done additional analysis to try to identify which predictors
+  were correlated with the equity premium, but none of the individual
+  regressors were significant after correcting for multiplicity. The
+  Bonferroni correction, for example, suggests that an individual
+  $p$-value would need to be less than $0.10/12 \approx 0.0083$ for
+  its corresponding coefficient to be significant at the 10\% level,
+  but the smallest $p$-value is $0.035$. One can improve on the
+  Bonferroni correction, of course, but a comprehensive analysis is
+  beyond the scope of this paper.} %
 As we argue throughout the paper, this result does not imply that the
@@
 some of these variables and the equity premium and the larger model
-could predict better than the benchmark with enough data.%
-\footnote{\citet{BWB:10} make a similar point about exchange rate
-  models, but see also \citet{Chi:10} and \citet{Gia:10}.} %
+could predict better than the benchmark with enough data.\footnote{%
+  \citet{BWB:10} make a similar point about exchange rate models, but
+  see also \citet{Chi:10} and \citet{Gia:10}.} %
 These also indicate that combination or shrinkage estimators of the
-full model have the potential to significantly improve on the benchmark.%
-\footnote{See \citet{RaZ:12} for a recent review of this
-  literature.} %
+full model have the potential to significantly improve on the
+benchmark.\footnote{%
+  See \citet{RaZ:12} for a recent review of this literature.} %
 
@@
 \begin{equation*}
-  \SumOuterBlock{i} \E_R Z_i^2 - \SumOuterBlock{i} \ZSqCE \to^p 0.%
-\footnote{Note that $\sigma^2 \in \mathcal{F}_t$ for
+  \SumOuterBlock{i} \E_R Z_i^2 - \SumOuterBlock{i} \ZSqCE \to^p 0.\footnote{%
+    Note that $\sigma^2 \in \mathcal{F}_t$ for
     all $t \geq R$, so Hall and Heyde's condition (3.21) is
@@
 that contains the acceptance region of $\Lambda$, i.e. when
-$\theta_2'M_2' V_T M_2 \theta_2 > c$, we have%
-\footnote{To keep the notation in these equations manageable, define
-  the information set $\Gs = \sigma(\E_T \oosB \leq 0,~ \theta_2'M_2'
-  V_T M_2 \theta_2 > c)$.} %
+$\theta_2'M_2' V_T M_2 \theta_2 > c$, we have\footnote{%
+  To keep the notation in these equations manageable, define the
+  information set
+  $\Gs = \sigma(\E_T \oosB \leq 0,~ \theta_2'M_2' V_T M_2 \theta_2 >
+  c)$.} %
 \begin{align*}
@@
 \clearpage
-
+\markboth{}{}
 \tryinput{floats/mc-ftest.tex}
@@
 
+\clearpage
+\section{Supplemental appendix (not for publication)}
+\input{appendix_contents}
+
 \end{document}
@@
 %%% TeX-master: "paper"
+%%% TeX-command-extra-options: "-shell-escape"
 %%% End:

### 2016-12-22 paper.tex
[#52] Tweak date/version script to use bashful w/in the LaTeX paper
Closes #52

--- 2016-01-31 paper.tex
@@
 
-Statistics like $\oost$ have a long history in empirical economics
-because they capture an intuitive idea of model fit: that a good model
-should be able to forecast well on new data. \cite{MeR:83}
-use such a statistic to study exchange rate models and find that none
-of the models that existed at the time of their study outperform a
-random walk. This finding has been remarkably durable and has spawned
-an enormous literature; see \cite{Mar:95}, \cite{KiT:03},
-\cite{CCP:05}, \cite{EnW:05}, \cite{Ros:05}, and \cite{BWB:10}, among
-many others. Research in financial markets has found a similar pattern,
-e.g. \cite{BoH:99}, \citet{GoW:08,GoW:03}, and \citet{Tim:08}.
-
 Most theoretical research on these statistics, such as \citet{DiM:95}, \citet{Wes:96},

### 2017-04-21 floats/empirics-oos-ind-ks.tex
Add TeX files with simulation and empirical results to repo
I've decided to add _a few_ generated files to the main repository to
make my life easier; namely any graphics or tables that are included
in the main paper.

% Created by tikzDevice version 0.6.2-92-0ad2792 on 2014-03-27 04:41:27
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (397.48,144.54);
\begin{scope}
\path[clip] ( 50.40, 61.20) rectangle (397.48,131.34);
\definecolor[named]{drawColor}{rgb}{1.00,1.00,1.00}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] ( 63.25,128.74) --
	( 69.44,113.58) --
	( 75.62,116.70) --
	( 81.80,101.94) --
	( 87.98,102.92) --
	( 94.16,109.79) --
	(100.34,103.33) --
	(106.52,117.62) --
	(112.70,122.31) --
	(118.88,123.05) --
	(125.06,107.38) --
	(131.24,103.26) --
	(137.42,108.90) --
	(143.60, 81.56) --
	(149.78, 73.07) --
	(155.96, 70.30) --
	(162.14, 68.61) --
	(168.32, 68.52) --
	(174.50, 68.01) --
	(180.68, 66.99) --
	(186.86, 67.19) --
	(193.04, 68.04) --
	(199.22, 65.70) --
	(205.40, 65.82) --
	(211.58, 65.23) --
	(217.76, 65.25) --
	(223.94, 65.20) --
	(230.12, 65.91) --
	(236.30, 65.56) --
	(242.48, 65.28) --
	(248.66, 65.84) --
	(254.84, 65.68) --
	(261.02, 65.76) --
	(267.20, 65.83) --
	(273.38, 65.88) --
	(279.57, 64.78) --
	(285.75, 64.82) --
	(291.93, 64.59) --
	(298.11, 64.52) --
	(304.29, 64.56) --
	(310.47, 64.63) --
	(316.65, 64.48) --
	(322.83, 64.47) --
	(329.01, 64.52) --
	(335.19, 64.47) --
	(341.37, 64.51) --
	(347.55, 64.52) --
	(353.73, 64.57) --
	(359.91, 64.47) --
	(366.09, 64.51) --
	(372.27, 64.63) --
	(378.45, 64.81) --
	(384.63, 65.01);

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] ( 63.25, 63.80) --
	( 69.44, 63.80) --
	( 75.62, 63.80) --
	( 81.80, 63.80) --
	( 87.98, 63.80) --
	( 94.16, 63.80) --
	(100.34, 63.80) --
	(106.52, 63.80) --
	(112.70, 63.80) --
	(118.88, 63.80) --
	(125.06, 63.80) --
	(131.24, 63.80) --
	(137.42, 63.80) --
	(143.60, 63.80) --
	(149.78, 63.80) --
	(155.96, 63.80) --
	(162.14, 63.80) --
	(168.32, 63.80) --
	(174.50, 63.80) --
	(180.68, 63.80) --
	(186.86, 63.80) --
	(193.04, 63.80) --
	(199.22, 63.80) --
	(205.40, 63.80) --
	(211.58, 63.80) --
	(217.76, 63.80) --
	(223.94, 63.80) --
	(230.12, 63.80) --
	(236.30, 63.80) --
	(242.48, 63.80) --
	(248.66, 63.80) --
	(254.84, 63.80) --
	(261.02, 63.80) --
	(267.20, 63.80) --
	(273.38, 63.80) --
	(279.57, 63.80) --
	(285.75, 63.80) --
	(291.93, 63.80) --
	(298.11, 63.80) --
	(304.29, 63.80) --
	(310.47, 63.80) --
	(316.65, 63.80) --
	(322.83, 63.80) --
	(329.01, 63.80) --
	(335.19, 63.80) --
	(341.37, 63.80) --
	(347.55, 63.80) --
	(353.73, 63.80) --
	(359.91, 63.80) --
	(366.09, 63.80) --
	(372.27, 63.80) --
	(378.45, 63.80) --
	(384.63, 63.80);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,144.54);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 12.00, 96.27) {Full model};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,144.54);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 63.25, 61.20) -- (372.27, 61.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 63.25, 61.20) -- ( 63.25, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (125.06, 61.20) -- (125.06, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.86, 61.20) -- (186.86, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (248.66, 61.20) -- (248.66, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (310.47, 61.20) -- (310.47, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (372.27, 61.20) -- (372.27, 55.20);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.25, 39.60) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (125.06, 39.60) {30};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (186.86, 39.60) {40};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (248.66, 39.60) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (310.47, 39.60) {60};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (372.27, 39.60) {70};
\end{scope}
\begin{scope}
\path[clip] ( 50.40, 61.20) rectangle (397.48,131.34);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 63.25,128.74) --
	( 69.44,113.58) --
	( 75.62,116.70) --
	( 81.80,101.94) --
	( 87.98,102.92) --
	( 94.16,109.79) --
	(100.34,103.33) --
	(106.52,117.62) --
	(112.70,122.31) --
	(118.88,123.05) --
	(125.06,107.38) --
	(131.24,103.26) --
	(137.42,108.90) --
	(143.60, 81.56) --
	(149.78, 73.07) --
	(155.96, 70.30) --
	(162.14, 68.61) --
	(168.32, 68.52) --
	(174.50, 68.01) --
	(180.68, 66.99) --
	(186.86, 67.19) --
	(193.04, 68.04) --
	(199.22, 65.70) --
	(205.40, 65.82) --
	(211.58, 65.23) --
	(217.76, 65.25) --
	(223.94, 65.20) --
	(230.12, 65.91) --
	(236.30, 65.56) --
	(242.48, 65.28) --
	(248.66, 65.84) --
	(254.84, 65.68) --
	(261.02, 65.76) --
	(267.20, 65.83) --
	(273.38, 65.88) --
	(279.57, 64.78) --
	(285.75, 64.82) --
	(291.93, 64.59) --
	(298.11, 64.52) --
	(304.29, 64.56) --
	(310.47, 64.63) --
	(316.65, 64.48) --
	(322.83, 64.47) --
	(329.01, 64.52) --
	(335.19, 64.47) --
	(341.37, 64.51) --
	(347.55, 64.52) --
	(353.73, 64.57) --
	(359.91, 64.47) --
	(366.09, 64.51) --
	(372.27, 64.63) --
	(378.45, 64.81) --
	(384.63, 65.01);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,144.54);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 63.80) -- ( 50.40,119.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 63.80) -- ( 44.40, 63.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 77.75) -- ( 44.40, 77.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 91.71) -- ( 44.40, 91.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,105.66) -- ( 44.40,105.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,119.62) -- ( 44.40,119.62);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40, 61.04) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40, 75.00) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40, 88.95) {2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40,102.91) {3};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40,116.86) {4};
\end{scope}
\end{tikzpicture}

### 2017-04-21 floats/empirics-oos-ind-pm.tex
Add TeX files with simulation and empirical results to repo
I've decided to add _a few_ generated files to the main repository to
make my life easier; namely any graphics or tables that are included
in the main paper.

--- 2017-04-21 floats/empirics-oos-ind-ks.tex
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] ( 63.25,128.74) --
-	( 69.44,113.58) --
-	( 75.62,116.70) --
-	( 81.80,101.94) --
-	( 87.98,102.92) --
-	( 94.16,109.79) --
-	(100.34,103.33) --
-	(106.52,117.62) --
-	(112.70,122.31) --
-	(118.88,123.05) --
-	(125.06,107.38) --
-	(131.24,103.26) --
-	(137.42,108.90) --
-	(143.60, 81.56) --
-	(149.78, 73.07) --
-	(155.96, 70.30) --
-	(162.14, 68.61) --
-	(168.32, 68.52) --
-	(174.50, 68.01) --
-	(180.68, 66.99) --
-	(186.86, 67.19) --
-	(193.04, 68.04) --
-	(199.22, 65.70) --
-	(205.40, 65.82) --
-	(211.58, 65.23) --
-	(217.76, 65.25) --
-	(223.94, 65.20) --
-	(230.12, 65.91) --
-	(236.30, 65.56) --
-	(242.48, 65.28) --
-	(248.66, 65.84) --
-	(254.84, 65.68) --
-	(261.02, 65.76) --
-	(267.20, 65.83) --
-	(273.38, 65.88) --
-	(279.57, 64.78) --
-	(285.75, 64.82) --
-	(291.93, 64.59) --
-	(298.11, 64.52) --
-	(304.29, 64.56) --
-	(310.47, 64.63) --
-	(316.65, 64.48) --
-	(322.83, 64.47) --
-	(329.01, 64.52) --
-	(335.19, 64.47) --
-	(341.37, 64.51) --
-	(347.55, 64.52) --
-	(353.73, 64.57) --
-	(359.91, 64.47) --
-	(366.09, 64.51) --
-	(372.27, 64.63) --
-	(378.45, 64.81) --
-	(384.63, 65.01);
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] ( 63.25, 97.34) --
+	( 69.44, 97.88) --
+	( 75.62, 98.01) --
+	( 81.80, 97.62) --
+	( 87.98, 97.87) --
+	( 94.16, 98.41) --
+	(100.34, 98.76) --
+	(106.52, 97.50) --
+	(112.70, 97.95) --
+	(118.88, 98.43) --
+	(125.06, 97.50) --
+	(131.24, 97.26) --
+	(137.42, 97.93) --
+	(143.60, 98.08) --
+	(149.78, 98.74) --
+	(155.96, 97.99) --
+	(162.14, 98.74) --
+	(168.32, 99.59) --
+	(174.50,100.40) --
+	(180.68, 99.28) --
+	(186.86,100.08) --
+	(193.04,100.89) --
+	(199.22, 99.90) --
+	(205.40,100.40) --
+	(211.58,101.38) --
+	(217.76,102.37) --
+	(223.94,100.30) --
+	(230.12, 94.81) --
+	(236.30, 94.33) --
+	(242.48, 94.91) --
+	(248.66, 94.58) --
+	(254.84, 95.42) --
+	(261.02, 96.47) --
+	(267.20, 97.16) --
+	(273.38, 95.89) --
+	(279.57, 97.03) --
+	(285.75, 98.12) --
+	(291.93, 99.14) --
+	(298.11, 99.59) --
+	(304.29,101.00) --
+	(310.47,102.50) --
+	(316.65,104.29) --
+	(322.83,105.29) --
+	(329.01,105.81) --
+	(335.19,106.66) --
+	(341.37,109.14) --
+	(347.55,111.98) --
+	(353.73,114.58) --
+	(359.91,114.85) --
+	(366.09,118.06) --
+	(372.27,119.90) --
+	(378.45,123.28) --
+	(384.63,128.74);
 
@@
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 12.00, 96.27) {Full model};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (223.94, 15.60) {Observations used for training sample ($R$)};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 12.00, 96.27) {Benchmark};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 63.25,128.74) --
-	( 69.44,113.58) --
-	( 75.62,116.70) --
-	( 81.80,101.94) --
-	( 87.98,102.92) --
-	( 94.16,109.79) --
-	(100.34,103.33) --
-	(106.52,117.62) --
-	(112.70,122.31) --
-	(118.88,123.05) --
-	(125.06,107.38) --
-	(131.24,103.26) --
-	(137.42,108.90) --
-	(143.60, 81.56) --
-	(149.78, 73.07) --
-	(155.96, 70.30) --
-	(162.14, 68.61) --
-	(168.32, 68.52) --
-	(174.50, 68.01) --
-	(180.68, 66.99) --
-	(186.86, 67.19) --
-	(193.04, 68.04) --
-	(199.22, 65.70) --
-	(205.40, 65.82) --
-	(211.58, 65.23) --
-	(217.76, 65.25) --
-	(223.94, 65.20) --
-	(230.12, 65.91) --
-	(236.30, 65.56) --
-	(242.48, 65.28) --
-	(248.66, 65.84) --
-	(254.84, 65.68) --
-	(261.02, 65.76) --
-	(267.20, 65.83) --
-	(273.38, 65.88) --
-	(279.57, 64.78) --
-	(285.75, 64.82) --
-	(291.93, 64.59) --
-	(298.11, 64.52) --
-	(304.29, 64.56) --
-	(310.47, 64.63) --
-	(316.65, 64.48) --
-	(322.83, 64.47) --
-	(329.01, 64.52) --
-	(335.19, 64.47) --
-	(341.37, 64.51) --
-	(347.55, 64.52) --
-	(353.73, 64.57) --
-	(359.91, 64.47) --
-	(366.09, 64.51) --
-	(372.27, 64.63) --
-	(378.45, 64.81) --
-	(384.63, 65.01);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 63.25, 97.34) --
+	( 69.44, 97.88) --
+	( 75.62, 98.01) --
+	( 81.80, 97.62) --
+	( 87.98, 97.87) --
+	( 94.16, 98.41) --
+	(100.34, 98.76) --
+	(106.52, 97.50) --
+	(112.70, 97.95) --
+	(118.88, 98.43) --
+	(125.06, 97.50) --
+	(131.24, 97.26) --
+	(137.42, 97.93) --
+	(143.60, 98.08) --
+	(149.78, 98.74) --
+	(155.96, 97.99) --
+	(162.14, 98.74) --
+	(168.32, 99.59) --
+	(174.50,100.40) --
+	(180.68, 99.28) --
+	(186.86,100.08) --
+	(193.04,100.89) --
+	(199.22, 99.90) --
+	(205.40,100.40) --
+	(211.58,101.38) --
+	(217.76,102.37) --
+	(223.94,100.30) --
+	(230.12, 94.81) --
+	(236.30, 94.33) --
+	(242.48, 94.91) --
+	(248.66, 94.58) --
+	(254.84, 95.42) --
+	(261.02, 96.47) --
+	(267.20, 97.16) --
+	(273.38, 95.89) --
+	(279.57, 97.03) --
+	(285.75, 98.12) --
+	(291.93, 99.14) --
+	(298.11, 99.59) --
+	(304.29,101.00) --
+	(310.47,102.50) --
+	(316.65,104.29) --
+	(322.83,105.29) --
+	(329.01,105.81) --
+	(335.19,106.66) --
+	(341.37,109.14) --
+	(347.55,111.98) --
+	(353.73,114.58) --
+	(359.91,114.85) --
+	(366.09,118.06) --
+	(372.27,119.90) --
+	(378.45,123.28) --
+	(384.63,128.74);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 63.80) -- ( 50.40,119.62);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 63.80) -- ( 50.40,122.39);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 77.75) -- ( 44.40, 77.75);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 75.52) -- ( 44.40, 75.52);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 91.71) -- ( 44.40, 91.71);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 87.23) -- ( 44.40, 87.23);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,105.66) -- ( 44.40,105.66);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 98.95) -- ( 44.40, 98.95);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,119.62) -- ( 44.40,119.62);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,110.67) -- ( 44.40,110.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,122.39) -- ( 44.40,122.39);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40, 75.00) {1};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40, 88.95) {2};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40,102.91) {3};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40,116.86) {4};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40,119.63) {0.05};
 \end{scope}

### 2017-04-21 floats/empirics-oos-mse-1.tex
Add TeX files with simulation and empirical results to repo
I've decided to add _a few_ generated files to the main repository to
make my life easier; namely any graphics or tables that are included
in the main paper.

% Created by tikzDevice version 0.6.2-92-0ad2792 on 2014-03-27 04:41:27
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (397.48,144.54);
\begin{scope}
\path[clip] ( 50.40, 61.20) rectangle (397.48,131.34);
\definecolor[named]{drawColor}{rgb}{1.00,1.00,1.00}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] ( 63.25, 63.80) --
	( 69.44, 79.00) --
	( 75.62, 75.81) --
	( 81.80, 90.65) --
	( 87.98, 89.65) --
	( 94.16, 82.75) --
	(100.34, 89.24) --
	(106.52, 74.79) --
	(112.70, 70.07) --
	(118.88, 69.31) --
	(125.06, 85.04) --
	(131.24, 89.19) --
	(137.42, 83.50) --
	(143.60,111.13) --
	(149.78,119.75) --
	(155.96,122.55) --
	(162.14,124.28) --
	(168.32,124.38) --
	(174.50,124.90) --
	(180.68,125.93) --
	(186.86,125.73) --
	(193.04,124.88) --
	(199.22,127.25) --
	(205.40,127.14) --
	(211.58,127.74) --
	(217.76,127.73) --
	(223.94,127.76) --
	(230.12,126.96) --
	(236.30,127.32) --
	(242.48,127.60) --
	(248.66,127.03) --
	(254.84,127.21) --
	(261.02,127.14) --
	(267.20,127.07) --
	(273.38,127.01) --
	(279.57,128.12) --
	(285.75,128.10) --
	(291.93,128.34) --
	(298.11,128.42) --
	(304.29,128.39) --
	(310.47,128.33) --
	(316.65,128.52) --
	(322.83,128.54) --
	(329.01,128.49) --
	(335.19,128.54) --
	(341.37,128.53) --
	(347.55,128.56) --
	(353.73,128.53) --
	(359.91,128.64) --
	(366.09,128.64) --
	(372.27,128.53) --
	(378.45,128.38) --
	(384.63,128.25);

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] ( 63.25, 65.95) --
	( 69.44, 80.70) --
	( 75.62, 77.67) --
	( 81.80, 92.03) --
	( 87.98, 91.07) --
	( 94.16, 84.40) --
	(100.34, 90.69) --
	(106.52, 76.77) --
	(112.70, 72.21) --
	(118.88, 71.50) --
	(125.06, 86.73) --
	(131.24, 90.74) --
	(137.42, 85.25) --
	(143.60,111.86) --
	(149.78,120.13) --
	(155.96,122.81) --
	(162.14,124.47) --
	(168.32,124.56) --
	(174.50,125.07) --
	(180.68,126.05) --
	(186.86,125.86) --
	(193.04,125.05) --
	(199.22,127.31) --
	(205.40,127.20) --
	(211.58,127.78) --
	(217.76,127.77) --
	(223.94,127.80) --
	(230.12,127.04) --
	(236.30,127.38) --
	(242.48,127.66) --
	(248.66,127.11) --
	(254.84,127.28) --
	(261.02,127.21) --
	(267.20,127.15) --
	(273.38,127.09) --
	(279.57,128.17) --
	(285.75,128.14) --
	(291.93,128.38) --
	(298.11,128.46) --
	(304.29,128.43) --
	(310.47,128.38) --
	(316.65,128.55) --
	(322.83,128.57) --
	(329.01,128.53) --
	(335.19,128.58) --
	(341.37,128.57) --
	(347.55,128.60) --
	(353.73,128.58) --
	(359.91,128.68) --
	(366.09,128.68) --
	(372.27,128.58) --
	(378.45,128.44) --
	(384.63,128.32);

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] ( 63.25,128.74) --
	( 69.44,128.74) --
	( 75.62,128.74) --
	( 81.80,128.74) --
	( 87.98,128.74) --
	( 94.16,128.74) --
	(100.34,128.74) --
	(106.52,128.74) --
	(112.70,128.74) --
	(118.88,128.74) --
	(125.06,128.74) --
	(131.24,128.74) --
	(137.42,128.74) --
	(143.60,128.74) --
	(149.78,128.74) --
	(155.96,128.74) --
	(162.14,128.74) --
	(168.32,128.74) --
	(174.50,128.74) --
	(180.68,128.74) --
	(186.86,128.74) --
	(193.04,128.74) --
	(199.22,128.74) --
	(205.40,128.74) --
	(211.58,128.74) --
	(217.76,128.74) --
	(223.94,128.74) --
	(230.12,128.74) --
	(236.30,128.74) --
	(242.48,128.74) --
	(248.66,128.74) --
	(254.84,128.74) --
	(261.02,128.74) --
	(267.20,128.74) --
	(273.38,128.74) --
	(279.57,128.74) --
	(285.75,128.74) --
	(291.93,128.74) --
	(298.11,128.74) --
	(304.29,128.74) --
	(310.47,128.74) --
	(316.65,128.74) --
	(322.83,128.74) --
	(329.01,128.74) --
	(335.19,128.74) --
	(341.37,128.74) --
	(347.55,128.74) --
	(353.73,128.74) --
	(359.91,128.74) --
	(366.09,128.74) --
	(372.27,128.74) --
	(378.45,128.74) --
	(384.63,128.74);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,144.54);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 12.00, 96.27) {MSE Diff.};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,144.54);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 63.25, 61.20) -- (372.27, 61.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 63.25, 61.20) -- ( 63.25, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (125.06, 61.20) -- (125.06, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.86, 61.20) -- (186.86, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (248.66, 61.20) -- (248.66, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (310.47, 61.20) -- (310.47, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (372.27, 61.20) -- (372.27, 55.20);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.25, 39.60) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (125.06, 39.60) {30};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (186.86, 39.60) {40};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (248.66, 39.60) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (310.47, 39.60) {60};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (372.27, 39.60) {70};
\end{scope}
\begin{scope}
\path[clip] ( 50.40, 61.20) rectangle (397.48,131.34);
\definecolor[named]{fillColor}{rgb}{0.75,0.75,0.75}

\path[fill=fillColor] ( 63.25,128.74) --
	( 63.25, 63.80) --
	( 69.44, 79.00) --
	( 75.62, 75.81) --
	( 81.80, 90.65) --
	( 87.98, 89.65) --
	( 94.16, 82.75) --
	(100.34, 89.24) --
	(106.52, 74.79) --
	(112.70, 70.07) --
	(118.88, 69.31) --
	(125.06, 85.04) --
	(131.24, 89.19) --
	(137.42, 83.50) --
	(143.60,111.13) --
	(149.78,119.75) --
	(155.96,122.55) --
	(162.14,124.28) --
	(168.32,124.38) --
	(174.50,124.90) --
	(180.68,125.93) --
	(186.86,125.73) --
	(193.04,124.88) --
	(199.22,127.25) --
	(205.40,127.14) --
	(211.58,127.74) --
	(217.76,127.73) --
	(223.94,127.76) --
	(230.12,126.96) --
	(236.30,127.32) --
	(242.48,127.60) --
	(248.66,127.03) --
	(254.84,127.21) --
	(261.02,127.14) --
	(267.20,127.07) --
	(273.38,127.01) --
	(279.57,128.12) --
	(285.75,128.10) --
	(291.93,128.34) --
	(298.11,128.42) --
	(304.29,128.39) --
	(310.47,128.33) --
	(316.65,128.52) --
	(322.83,128.54) --
	(329.01,128.49) --
	(335.19,128.54) --
	(341.37,128.53) --
	(347.55,128.56) --
	(353.73,128.53) --
	(359.91,128.64) --
	(366.09,128.64) --
	(372.27,128.53) --
	(378.45,128.38) --
	(384.63,128.25) --
	(384.63,128.74) --
	cycle;
\definecolor[named]{drawColor}{rgb}{0.75,0.75,0.75}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 63.25,128.74) --
	(384.63,128.74);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 63.25, 65.95) --
	( 69.44, 80.70) --
	( 75.62, 77.67) --
	( 81.80, 92.03) --
	( 87.98, 91.07) --
	( 94.16, 84.40) --
	(100.34, 90.69) --
	(106.52, 76.77) --
	(112.70, 72.21) --
	(118.88, 71.50) --
	(125.06, 86.73) --
	(131.24, 90.74) --
	(137.42, 85.25) --
	(143.60,111.86) --
	(149.78,120.13) --
	(155.96,122.81) --
	(162.14,124.47) --
	(168.32,124.56) --
	(174.50,125.07) --
	(180.68,126.05) --
	(186.86,125.86) --
	(193.04,125.05) --
	(199.22,127.31) --
	(205.40,127.20) --
	(211.58,127.78) --
	(217.76,127.77) --
	(223.94,127.80) --
	(230.12,127.04) --
	(236.30,127.38) --
	(242.48,127.66) --
	(248.66,127.11) --
	(254.84,127.28) --
	(261.02,127.21) --
	(267.20,127.15) --
	(273.38,127.09) --
	(279.57,128.17) --
	(285.75,128.14) --
	(291.93,128.38) --
	(298.11,128.46) --
	(304.29,128.43) --
	(310.47,128.38) --
	(316.65,128.55) --
	(322.83,128.57) --
	(329.01,128.53) --
	(335.19,128.58) --
	(341.37,128.57) --
	(347.55,128.60) --
	(353.73,128.58) --
	(359.91,128.68) --
	(366.09,128.68) --
	(372.27,128.58) --
	(378.45,128.44) --
	(384.63,128.32);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,144.54);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 74.43) -- ( 50.40,128.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 74.43) -- ( 44.40, 74.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 88.01) -- ( 44.40, 88.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,101.59) -- ( 44.40,101.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,115.16) -- ( 44.40,115.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,128.74) -- ( 44.40,128.74);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40, 71.68) {-4};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40, 98.83) {-2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40,125.99) {0};
\end{scope}
\end{tikzpicture}

### 2017-04-21 floats/empirics-oos-mse-1b.tex
Add TeX files with simulation and empirical results to repo
I've decided to add _a few_ generated files to the main repository to
make my life easier; namely any graphics or tables that are included
in the main paper.

--- 2017-04-21 floats/empirics-oos-mse-1.tex
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] ( 63.25, 63.80) --
-	( 69.44, 79.00) --
-	( 75.62, 75.81) --
-	( 81.80, 90.65) --
-	( 87.98, 89.65) --
-	( 94.16, 82.75) --
-	(100.34, 89.24) --
-	(106.52, 74.79) --
-	(112.70, 70.07) --
-	(118.88, 69.31) --
-	(125.06, 85.04) --
-	(131.24, 89.19) --
-	(137.42, 83.50) --
-	(143.60,111.13) --
-	(149.78,119.75) --
-	(155.96,122.55) --
-	(162.14,124.28) --
-	(168.32,124.38) --
-	(174.50,124.90) --
-	(180.68,125.93) --
-	(186.86,125.73) --
-	(193.04,124.88) --
-	(199.22,127.25) --
-	(205.40,127.14) --
-	(211.58,127.74) --
-	(217.76,127.73) --
-	(223.94,127.76) --
-	(230.12,126.96) --
-	(236.30,127.32) --
-	(242.48,127.60) --
-	(248.66,127.03) --
-	(254.84,127.21) --
-	(261.02,127.14) --
-	(267.20,127.07) --
-	(273.38,127.01) --
-	(279.57,128.12) --
-	(285.75,128.10) --
-	(291.93,128.34) --
-	(298.11,128.42) --
-	(304.29,128.39) --
-	(310.47,128.33) --
-	(316.65,128.52) --
-	(322.83,128.54) --
-	(329.01,128.49) --
-	(335.19,128.54) --
-	(341.37,128.53) --
-	(347.55,128.56) --
-	(353.73,128.53) --
-	(359.91,128.64) --
-	(366.09,128.64) --
-	(372.27,128.53) --
-	(378.45,128.38) --
-	(384.63,128.25);
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (248.66, 64.79) --
+	(254.84, 71.45) --
+	(261.02, 68.74) --
+	(267.20, 66.28) --
+	(273.38, 63.80) --
+	(279.57,105.64) --
+	(285.75,104.73) --
+	(291.93,113.66) --
+	(298.11,116.70) --
+	(304.29,115.54) --
+	(310.47,113.47) --
+	(316.65,120.29) --
+	(322.83,121.13) --
+	(329.01,119.16) --
+	(335.19,121.19) --
+	(341.37,120.79) --
+	(347.55,121.75) --
+	(353.73,120.97) --
+	(359.91,125.03) --
+	(366.09,124.93) --
+	(372.27,120.92) --
+	(378.45,115.37) --
+	(384.63,110.14);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] ( 63.25, 65.95) --
-	( 69.44, 80.70) --
-	( 75.62, 77.67) --
-	( 81.80, 92.03) --
-	( 87.98, 91.07) --
-	( 94.16, 84.40) --
-	(100.34, 90.69) --
-	(106.52, 76.77) --
-	(112.70, 72.21) --
-	(118.88, 71.50) --
-	(125.06, 86.73) --
-	(131.24, 90.74) --
-	(137.42, 85.25) --
-	(143.60,111.86) --
-	(149.78,120.13) --
-	(155.96,122.81) --
-	(162.14,124.47) --
-	(168.32,124.56) --
-	(174.50,125.07) --
-	(180.68,126.05) --
-	(186.86,125.86) --
-	(193.04,125.05) --
-	(199.22,127.31) --
-	(205.40,127.20) --
-	(211.58,127.78) --
-	(217.76,127.77) --
-	(223.94,127.80) --
-	(230.12,127.04) --
-	(236.30,127.38) --
-	(242.48,127.66) --
-	(248.66,127.11) --
-	(254.84,127.28) --
-	(261.02,127.21) --
-	(267.20,127.15) --
-	(273.38,127.09) --
-	(279.57,128.17) --
-	(285.75,128.14) --
-	(291.93,128.38) --
-	(298.11,128.46) --
-	(304.29,128.43) --
-	(310.47,128.38) --
-	(316.65,128.55) --
-	(322.83,128.57) --
-	(329.01,128.53) --
-	(335.19,128.58) --
-	(341.37,128.57) --
-	(347.55,128.60) --
-	(353.73,128.58) --
-	(359.91,128.68) --
-	(366.09,128.68) --
-	(372.27,128.58) --
-	(378.45,128.44) --
-	(384.63,128.32);
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (248.66, 67.69) --
+	(254.84, 74.06) --
+	(261.02, 71.45) --
+	(267.20, 69.09) --
+	(273.38, 66.79) --
+	(279.57,107.26) --
+	(285.75,106.40) --
+	(291.93,115.08) --
+	(298.11,118.01) --
+	(304.29,116.97) --
+	(310.47,115.08) --
+	(316.65,121.60) --
+	(322.83,122.36) --
+	(329.01,120.66) --
+	(335.19,122.70) --
+	(341.37,122.44) --
+	(347.55,123.48) --
+	(353.73,122.73) --
+	(359.91,126.40) --
+	(366.09,126.32) --
+	(372.27,122.61) --
+	(378.45,117.59) --
+	(384.63,112.83);
 
@@
 
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (223.94, 15.60) {Observations used for training sample ($R$)};
+
 \node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 12.00, 96.27) {MSE Diff.};
@@
 
-\path[fill=fillColor] ( 63.25,128.74) --
-	( 63.25, 63.80) --
-	( 69.44, 79.00) --
-	( 75.62, 75.81) --
-	( 81.80, 90.65) --
-	( 87.98, 89.65) --
-	( 94.16, 82.75) --
-	(100.34, 89.24) --
-	(106.52, 74.79) --
-	(112.70, 70.07) --
-	(118.88, 69.31) --
-	(125.06, 85.04) --
-	(131.24, 89.19) --
-	(137.42, 83.50) --
-	(143.60,111.13) --
-	(149.78,119.75) --
-	(155.96,122.55) --
-	(162.14,124.28) --
-	(168.32,124.38) --
-	(174.50,124.90) --
-	(180.68,125.93) --
-	(186.86,125.73) --
-	(193.04,124.88) --
-	(199.22,127.25) --
-	(205.40,127.14) --
-	(211.58,127.74) --
-	(217.76,127.73) --
-	(223.94,127.76) --
-	(230.12,126.96) --
-	(236.30,127.32) --
-	(242.48,127.60) --
-	(248.66,127.03) --
-	(254.84,127.21) --
-	(261.02,127.14) --
-	(267.20,127.07) --
-	(273.38,127.01) --
-	(279.57,128.12) --
-	(285.75,128.10) --
-	(291.93,128.34) --
-	(298.11,128.42) --
-	(304.29,128.39) --
-	(310.47,128.33) --
-	(316.65,128.52) --
-	(322.83,128.54) --
-	(329.01,128.49) --
-	(335.19,128.54) --
-	(341.37,128.53) --
-	(347.55,128.56) --
-	(353.73,128.53) --
-	(359.91,128.64) --
-	(366.09,128.64) --
-	(372.27,128.53) --
-	(378.45,128.38) --
-	(384.63,128.25) --
+\path[fill=fillColor] (248.66,128.74) --
+	(248.66, 64.79) --
+	(254.84, 71.45) --
+	(261.02, 68.74) --
+	(267.20, 66.28) --
+	(273.38, 63.80) --
+	(279.57,105.64) --
+	(285.75,104.73) --
+	(291.93,113.66) --
+	(298.11,116.70) --
+	(304.29,115.54) --
+	(310.47,113.47) --
+	(316.65,120.29) --
+	(322.83,121.13) --
+	(329.01,119.16) --
+	(335.19,121.19) --
+	(341.37,120.79) --
+	(347.55,121.75) --
+	(353.73,120.97) --
+	(359.91,125.03) --
+	(366.09,124.93) --
+	(372.27,120.92) --
+	(378.45,115.37) --
+	(384.63,110.14) --
 	(384.63,128.74) --
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 63.25, 65.95) --
-	( 69.44, 80.70) --
-	( 75.62, 77.67) --
-	( 81.80, 92.03) --
-	( 87.98, 91.07) --
-	( 94.16, 84.40) --
-	(100.34, 90.69) --
-	(106.52, 76.77) --
-	(112.70, 72.21) --
-	(118.88, 71.50) --
-	(125.06, 86.73) --
-	(131.24, 90.74) --
-	(137.42, 85.25) --
-	(143.60,111.86) --
-	(149.78,120.13) --
-	(155.96,122.81) --
-	(162.14,124.47) --
-	(168.32,124.56) --
-	(174.50,125.07) --
-	(180.68,126.05) --
-	(186.86,125.86) --
-	(193.04,125.05) --
-	(199.22,127.31) --
-	(205.40,127.20) --
-	(211.58,127.78) --
-	(217.76,127.77) --
-	(223.94,127.80) --
-	(230.12,127.04) --
-	(236.30,127.38) --
-	(242.48,127.66) --
-	(248.66,127.11) --
-	(254.84,127.28) --
-	(261.02,127.21) --
-	(267.20,127.15) --
-	(273.38,127.09) --
-	(279.57,128.17) --
-	(285.75,128.14) --
-	(291.93,128.38) --
-	(298.11,128.46) --
-	(304.29,128.43) --
-	(310.47,128.38) --
-	(316.65,128.55) --
-	(322.83,128.57) --
-	(329.01,128.53) --
-	(335.19,128.58) --
-	(341.37,128.57) --
-	(347.55,128.60) --
-	(353.73,128.58) --
-	(359.91,128.68) --
-	(366.09,128.68) --
-	(372.27,128.58) --
-	(378.45,128.44) --
-	(384.63,128.32);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (248.66, 67.69) --
+	(254.84, 74.06) --
+	(261.02, 71.45) --
+	(267.20, 69.09) --
+	(273.38, 66.79) --
+	(279.57,107.26) --
+	(285.75,106.40) --
+	(291.93,115.08) --
+	(298.11,118.01) --
+	(304.29,116.97) --
+	(310.47,115.08) --
+	(316.65,121.60) --
+	(322.83,122.36) --
+	(329.01,120.66) --
+	(335.19,122.70) --
+	(341.37,122.44) --
+	(347.55,123.48) --
+	(353.73,122.73) --
+	(359.91,126.40) --
+	(366.09,126.32) --
+	(372.27,122.61) --
+	(378.45,117.59) --
+	(384.63,112.83);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 74.43) -- ( 50.40,128.74);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 77.95) -- ( 50.40,128.74);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 74.43) -- ( 44.40, 74.43);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 77.95) -- ( 44.40, 77.95);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 88.01) -- ( 44.40, 88.01);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 90.65) -- ( 44.40, 90.65);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,101.59) -- ( 44.40,101.59);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,103.34) -- ( 44.40,103.34);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,115.16) -- ( 44.40,115.16);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,116.04) -- ( 44.40,116.04);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40, 71.68) {-4};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40, 75.19) {-.10};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40, 98.83) {-2};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40,100.59) {-0.5};
 

### 2017-04-21 floats/empirics-oos-mse-2.tex
Add TeX files with simulation and empirical results to repo
I've decided to add _a few_ generated files to the main repository to
make my life easier; namely any graphics or tables that are included
in the main paper.

--- 2017-04-21 floats/empirics-oos-mse-1b.tex
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (248.66, 64.79) --
-	(254.84, 71.45) --
-	(261.02, 68.74) --
-	(267.20, 66.28) --
-	(273.38, 63.80) --
-	(279.57,105.64) --
-	(285.75,104.73) --
-	(291.93,113.66) --
-	(298.11,116.70) --
-	(304.29,115.54) --
-	(310.47,113.47) --
-	(316.65,120.29) --
-	(322.83,121.13) --
-	(329.01,119.16) --
-	(335.19,121.19) --
-	(341.37,120.79) --
-	(347.55,121.75) --
-	(353.73,120.97) --
-	(359.91,125.03) --
-	(366.09,124.93) --
-	(372.27,120.92) --
-	(378.45,115.37) --
-	(384.63,110.14);
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] ( 63.25, 63.80) --
+	( 69.44, 79.00) --
+	( 75.62, 75.65) --
+	( 81.80, 90.54) --
+	( 87.98, 89.54) --
+	( 94.16, 82.61) --
+	(100.34, 89.12) --
+	(106.52, 74.63) --
+	(112.70, 69.89) --
+	(118.88, 69.13) --
+	(125.06, 84.91) --
+	(131.24, 89.07) --
+	(137.42, 83.37) --
+	(143.60,111.11) --
+	(149.78,119.79) --
+	(155.96,122.58) --
+	(162.14,124.34) --
+	(168.32,124.44) --
+	(174.50,124.99) --
+	(180.68,126.15) --
+	(186.86,125.94) --
+	(193.04,125.01) --
+	(199.22,127.58) --
+	(205.40,127.46) --
+	(211.58,128.46) --
+	(217.76,128.40) --
+	(223.94,128.54) --
+	(230.12,128.70) --
+	(236.30,128.70) --
+	(242.48,128.68) --
+	(248.66,128.71) --
+	(254.84,128.72) --
+	(261.02,128.72) --
+	(267.20,128.71) --
+	(273.38,128.71) --
+	(279.57,128.69) --
+	(285.75,128.71) --
+	(291.93,128.71) --
+	(298.11,128.71) --
+	(304.29,128.70) --
+	(310.47,128.70) --
+	(316.65,128.70) --
+	(322.83,128.69) --
+	(329.01,128.70) --
+	(335.19,128.71) --
+	(341.37,128.71) --
+	(347.55,128.71) --
+	(353.73,128.70) --
+	(359.91,128.70) --
+	(366.09,128.68) --
+	(372.27,128.59) --
+	(378.45,128.44) --
+	(384.63,128.30);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (248.66, 67.69) --
-	(254.84, 74.06) --
-	(261.02, 71.45) --
-	(267.20, 69.09) --
-	(273.38, 66.79) --
-	(279.57,107.26) --
-	(285.75,106.40) --
-	(291.93,115.08) --
-	(298.11,118.01) --
-	(304.29,116.97) --
-	(310.47,115.08) --
-	(316.65,121.60) --
-	(322.83,122.36) --
-	(329.01,120.66) --
-	(335.19,122.70) --
-	(341.37,122.44) --
-	(347.55,123.48) --
-	(353.73,122.73) --
-	(359.91,126.40) --
-	(366.09,126.32) --
-	(372.27,122.61) --
-	(378.45,117.59) --
-	(384.63,112.83);
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] ( 63.25, 65.95) --
+	( 69.44, 80.71) --
+	( 75.62, 77.52) --
+	( 81.80, 91.92) --
+	( 87.98, 90.96) --
+	( 94.16, 84.27) --
+	(100.34, 90.58) --
+	(106.52, 76.61) --
+	(112.70, 72.04) --
+	(118.88, 71.33) --
+	(125.06, 86.60) --
+	(131.24, 90.62) --
+	(137.42, 85.12) --
+	(143.60,111.84) --
+	(149.78,120.17) --
+	(155.96,122.84) --
+	(162.14,124.53) --
+	(168.32,124.63) --
+	(174.50,125.16) --
+	(180.68,126.27) --
+	(186.86,126.07) --
+	(193.04,125.19) --
+	(199.22,127.64) --
+	(205.40,127.53) --
+	(211.58,128.47) --
+	(217.76,128.42) --
+	(223.94,128.55) --
+	(230.12,128.71) --
+	(236.30,128.71) --
+	(242.48,128.68) --
+	(248.66,128.72) --
+	(254.84,128.73) --
+	(261.02,128.72) --
+	(267.20,128.72) --
+	(273.38,128.71) --
+	(279.57,128.70) --
+	(285.75,128.72) --
+	(291.93,128.72) --
+	(298.11,128.72) --
+	(304.29,128.72) --
+	(310.47,128.71) --
+	(316.65,128.72) --
+	(322.83,128.70) --
+	(329.01,128.71) --
+	(335.19,128.72) --
+	(341.37,128.72) --
+	(347.55,128.72) --
+	(353.73,128.72) --
+	(359.91,128.72) --
+	(366.09,128.71) --
+	(372.27,128.62) --
+	(378.45,128.49) --
+	(384.63,128.37);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (223.94, 15.60) {Observations used for training sample ($R$)};
-
 \node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 12.00, 96.27) {MSE Diff.};
@@
 
-\path[fill=fillColor] (248.66,128.74) --
-	(248.66, 64.79) --
-	(254.84, 71.45) --
-	(261.02, 68.74) --
-	(267.20, 66.28) --
-	(273.38, 63.80) --
-	(279.57,105.64) --
-	(285.75,104.73) --
-	(291.93,113.66) --
-	(298.11,116.70) --
-	(304.29,115.54) --
-	(310.47,113.47) --
-	(316.65,120.29) --
-	(322.83,121.13) --
-	(329.01,119.16) --
-	(335.19,121.19) --
-	(341.37,120.79) --
-	(347.55,121.75) --
-	(353.73,120.97) --
-	(359.91,125.03) --
-	(366.09,124.93) --
-	(372.27,120.92) --
-	(378.45,115.37) --
-	(384.63,110.14) --
+\path[fill=fillColor] ( 63.25,128.74) --
+	( 63.25, 63.80) --
+	( 69.44, 79.00) --
+	( 75.62, 75.65) --
+	( 81.80, 90.54) --
+	( 87.98, 89.54) --
+	( 94.16, 82.61) --
+	(100.34, 89.12) --
+	(106.52, 74.63) --
+	(112.70, 69.89) --
+	(118.88, 69.13) --
+	(125.06, 84.91) --
+	(131.24, 89.07) --
+	(137.42, 83.37) --
+	(143.60,111.11) --
+	(149.78,119.79) --
+	(155.96,122.58) --
+	(162.14,124.34) --
+	(168.32,124.44) --
+	(174.50,124.99) --
+	(180.68,126.15) --
+	(186.86,125.94) --
+	(193.04,125.01) --
+	(199.22,127.58) --
+	(205.40,127.46) --
+	(211.58,128.46) --
+	(217.76,128.40) --
+	(223.94,128.54) --
+	(230.12,128.70) --
+	(236.30,128.70) --
+	(242.48,128.68) --
+	(248.66,128.71) --
+	(254.84,128.72) --
+	(261.02,128.72) --
+	(267.20,128.71) --
+	(273.38,128.71) --
+	(279.57,128.69) --
+	(285.75,128.71) --
+	(291.93,128.71) --
+	(298.11,128.71) --
+	(304.29,128.70) --
+	(310.47,128.70) --
+	(316.65,128.70) --
+	(322.83,128.69) --
+	(329.01,128.70) --
+	(335.19,128.71) --
+	(341.37,128.71) --
+	(347.55,128.71) --
+	(353.73,128.70) --
+	(359.91,128.70) --
+	(366.09,128.68) --
+	(372.27,128.59) --
+	(378.45,128.44) --
+	(384.63,128.30) --
 	(384.63,128.74) --
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (248.66, 67.69) --
-	(254.84, 74.06) --
-	(261.02, 71.45) --
-	(267.20, 69.09) --
-	(273.38, 66.79) --
-	(279.57,107.26) --
-	(285.75,106.40) --
-	(291.93,115.08) --
-	(298.11,118.01) --
-	(304.29,116.97) --
-	(310.47,115.08) --
-	(316.65,121.60) --
-	(322.83,122.36) --
-	(329.01,120.66) --
-	(335.19,122.70) --
-	(341.37,122.44) --
-	(347.55,123.48) --
-	(353.73,122.73) --
-	(359.91,126.40) --
-	(366.09,126.32) --
-	(372.27,122.61) --
-	(378.45,117.59) --
-	(384.63,112.83);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 63.25, 65.95) --
+	( 69.44, 80.71) --
+	( 75.62, 77.52) --
+	( 81.80, 91.92) --
+	( 87.98, 90.96) --
+	( 94.16, 84.27) --
+	(100.34, 90.58) --
+	(106.52, 76.61) --
+	(112.70, 72.04) --
+	(118.88, 71.33) --
+	(125.06, 86.60) --
+	(131.24, 90.62) --
+	(137.42, 85.12) --
+	(143.60,111.84) --
+	(149.78,120.17) --
+	(155.96,122.84) --
+	(162.14,124.53) --
+	(168.32,124.63) --
+	(174.50,125.16) --
+	(180.68,126.27) --
+	(186.86,126.07) --
+	(193.04,125.19) --
+	(199.22,127.64) --
+	(205.40,127.53) --
+	(211.58,128.47) --
+	(217.76,128.42) --
+	(223.94,128.55) --
+	(230.12,128.71) --
+	(236.30,128.71) --
+	(242.48,128.68) --
+	(248.66,128.72) --
+	(254.84,128.73) --
+	(261.02,128.72) --
+	(267.20,128.72) --
+	(273.38,128.71) --
+	(279.57,128.70) --
+	(285.75,128.72) --
+	(291.93,128.72) --
+	(298.11,128.72) --
+	(304.29,128.72) --
+	(310.47,128.71) --
+	(316.65,128.72) --
+	(322.83,128.70) --
+	(329.01,128.71) --
+	(335.19,128.72) --
+	(341.37,128.72) --
+	(347.55,128.72) --
+	(353.73,128.72) --
+	(359.91,128.72) --
+	(366.09,128.71) --
+	(372.27,128.62) --
+	(378.45,128.49) --
+	(384.63,128.37);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 77.95) -- ( 50.40,128.74);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 74.27) -- ( 50.40,128.74);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 77.95) -- ( 44.40, 77.95);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 74.27) -- ( 44.40, 74.27);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 90.65) -- ( 44.40, 90.65);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 87.89) -- ( 44.40, 87.89);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,103.34) -- ( 44.40,103.34);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,101.51) -- ( 44.40,101.51);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,116.04) -- ( 44.40,116.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,115.12) -- ( 44.40,115.12);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40, 75.19) {-.10};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40, 71.51) {-4};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40,100.59) {-0.5};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40, 98.75) {-2};
 

### 2017-04-21 floats/empirics-oos-mse-2b.tex
Add TeX files with simulation and empirical results to repo
I've decided to add _a few_ generated files to the main repository to
make my life easier; namely any graphics or tables that are included
in the main paper.

--- 2017-04-21 floats/empirics-oos-mse-1b.tex
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (248.66, 64.79) --
-	(254.84, 71.45) --
-	(261.02, 68.74) --
-	(267.20, 66.28) --
-	(273.38, 63.80) --
-	(279.57,105.64) --
-	(285.75,104.73) --
-	(291.93,113.66) --
-	(298.11,116.70) --
-	(304.29,115.54) --
-	(310.47,113.47) --
-	(316.65,120.29) --
-	(322.83,121.13) --
-	(329.01,119.16) --
-	(335.19,121.19) --
-	(341.37,120.79) --
-	(347.55,121.75) --
-	(353.73,120.97) --
-	(359.91,125.03) --
-	(366.09,124.93) --
-	(372.27,120.92) --
-	(378.45,115.37) --
-	(384.63,110.14);
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (248.66,124.54) --
+	(254.84,125.33) --
+	(261.02,125.15) --
+	(267.20,123.84) --
+	(273.38,123.35) --
+	(279.57,120.81) --
+	(285.75,124.16) --
+	(291.93,124.28) --
+	(298.11,123.31) --
+	(304.29,123.14) --
+	(310.47,122.78) --
+	(316.65,123.16) --
+	(322.83,120.87) --
+	(329.01,122.51) --
+	(335.19,123.70) --
+	(341.37,123.48) --
+	(347.55,123.46) --
+	(353.73,122.23) --
+	(359.91,123.13) --
+	(366.09,120.07) --
+	(372.27,106.08) --
+	(378.45, 84.32) --
+	(384.63, 63.80);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (248.66, 67.69) --
-	(254.84, 74.06) --
-	(261.02, 71.45) --
-	(267.20, 69.09) --
-	(273.38, 66.79) --
-	(279.57,107.26) --
-	(285.75,106.40) --
-	(291.93,115.08) --
-	(298.11,118.01) --
-	(304.29,116.97) --
-	(310.47,115.08) --
-	(316.65,121.60) --
-	(322.83,122.36) --
-	(329.01,120.66) --
-	(335.19,122.70) --
-	(341.37,122.44) --
-	(347.55,123.48) --
-	(353.73,122.73) --
-	(359.91,126.40) --
-	(366.09,126.32) --
-	(372.27,122.61) --
-	(378.45,117.59) --
-	(384.63,112.83);
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (248.66,125.42) --
+	(254.84,126.24) --
+	(261.02,126.11) --
+	(267.20,124.81) --
+	(273.38,124.31) --
+	(279.57,122.08) --
+	(285.75,125.43) --
+	(291.93,125.60) --
+	(298.11,124.74) --
+	(304.29,124.74) --
+	(310.47,124.48) --
+	(316.65,124.85) --
+	(322.83,122.60) --
+	(329.01,124.53) --
+	(335.19,125.81) --
+	(341.37,125.79) --
+	(347.55,125.98) --
+	(353.73,125.02) --
+	(359.91,125.98) --
+	(366.09,123.38) --
+	(372.27,111.40) --
+	(378.45, 91.89) --
+	(384.63, 73.27);
 
@@
 \path[fill=fillColor] (248.66,128.74) --
-	(248.66, 64.79) --
-	(254.84, 71.45) --
-	(261.02, 68.74) --
-	(267.20, 66.28) --
-	(273.38, 63.80) --
-	(279.57,105.64) --
-	(285.75,104.73) --
-	(291.93,113.66) --
-	(298.11,116.70) --
-	(304.29,115.54) --
-	(310.47,113.47) --
-	(316.65,120.29) --
-	(322.83,121.13) --
-	(329.01,119.16) --
-	(335.19,121.19) --
-	(341.37,120.79) --
-	(347.55,121.75) --
-	(353.73,120.97) --
-	(359.91,125.03) --
-	(366.09,124.93) --
-	(372.27,120.92) --
-	(378.45,115.37) --
-	(384.63,110.14) --
+	(248.66,124.54) --
+	(254.84,125.33) --
+	(261.02,125.15) --
+	(267.20,123.84) --
+	(273.38,123.35) --
+	(279.57,120.81) --
+	(285.75,124.16) --
+	(291.93,124.28) --
+	(298.11,123.31) --
+	(304.29,123.14) --
+	(310.47,122.78) --
+	(316.65,123.16) --
+	(322.83,120.87) --
+	(329.01,122.51) --
+	(335.19,123.70) --
+	(341.37,123.48) --
+	(347.55,123.46) --
+	(353.73,122.23) --
+	(359.91,123.13) --
+	(366.09,120.07) --
+	(372.27,106.08) --
+	(378.45, 84.32) --
+	(384.63, 63.80) --
 	(384.63,128.74) --
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (248.66, 67.69) --
-	(254.84, 74.06) --
-	(261.02, 71.45) --
-	(267.20, 69.09) --
-	(273.38, 66.79) --
-	(279.57,107.26) --
-	(285.75,106.40) --
-	(291.93,115.08) --
-	(298.11,118.01) --
-	(304.29,116.97) --
-	(310.47,115.08) --
-	(316.65,121.60) --
-	(322.83,122.36) --
-	(329.01,120.66) --
-	(335.19,122.70) --
-	(341.37,122.44) --
-	(347.55,123.48) --
-	(353.73,122.73) --
-	(359.91,126.40) --
-	(366.09,126.32) --
-	(372.27,122.61) --
-	(378.45,117.59) --
-	(384.63,112.83);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (248.66,125.42) --
+	(254.84,126.24) --
+	(261.02,126.11) --
+	(267.20,124.81) --
+	(273.38,124.31) --
+	(279.57,122.08) --
+	(285.75,125.43) --
+	(291.93,125.60) --
+	(298.11,124.74) --
+	(304.29,124.74) --
+	(310.47,124.48) --
+	(316.65,124.85) --
+	(322.83,122.60) --
+	(329.01,124.53) --
+	(335.19,125.81) --
+	(341.37,125.79) --
+	(347.55,125.98) --
+	(353.73,125.02) --
+	(359.91,125.98) --
+	(366.09,123.38) --
+	(372.27,111.40) --
+	(378.45, 91.89) --
+	(384.63, 73.27);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 77.95) -- ( 50.40,128.74);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 68.44) -- ( 50.40,128.74);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 77.95) -- ( 44.40, 77.95);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 68.44) -- ( 44.40, 68.44);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 90.65) -- ( 44.40, 90.65);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 83.51) -- ( 44.40, 83.51);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,103.34) -- ( 44.40,103.34);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 98.59) -- ( 44.40, 98.59);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,116.04) -- ( 44.40,116.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,113.67) -- ( 44.40,113.67);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40, 75.19) {-.10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40,100.59) {-0.5};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40, 65.68) {-.03};
 

### 2017-04-21 floats/mc-dmwpower-rec.tex
Add TeX files with simulation and empirical results to repo
I've decided to add _a few_ generated files to the main repository to
make my life easier; namely any graphics or tables that are included
in the main paper.

% Created by tikzDevice version 0.6.2-92-0ad2792 on 2014-03-27 14:58:15
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,325.21);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);

\path[] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (220.94, 12.05) {$P/T$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at ( 14.29,162.76) {Rejection Probability};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44, 54.31) -- ( 48.75, 54.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44, 66.59) -- ( 48.75, 66.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44, 78.87) -- ( 48.75, 78.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44, 91.15) -- ( 48.75, 91.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,103.43) -- ( 48.75,103.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,115.71) -- ( 48.75,115.71);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06, 51.00) {0.00};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06, 63.28) {0.05};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06, 75.56) {0.10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06, 87.85) {0.15};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06,100.13) {0.20};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06,112.41) {0.25};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 57.20, 50.02) -- ( 57.20, 44.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 80.76, 50.02) -- ( 80.76, 44.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.31, 50.02) -- (104.31, 44.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.87, 50.02) -- (127.87, 44.32);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 57.20, 32.02) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 80.76, 32.02) {0.2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (104.31, 32.02) {0.4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (127.87, 32.02) {0.6};
\end{scope}
\begin{scope}
\path[clip] ( 54.44, 50.02) rectangle (137.69,119.88);
\definecolor[named]{drawColor}{rgb}{0.83,0.83,0.83}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 57.20, 78.87) --
	(135.72, 78.87);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 59.56, 78.85) --
	( 59.79, 79.14) --
	( 60.03, 78.68) --
	( 60.26, 79.14) --
	( 60.50, 79.72) --
	( 60.73, 79.32) --
	( 60.97, 78.15) --
	( 61.20, 78.21) --
	( 61.44, 78.39) --
	( 61.68, 79.03) --
	( 61.91, 77.98) --
	( 62.15, 78.04) --
	( 62.38, 78.04) --
	( 62.62, 77.75) --
	( 62.85, 77.98) --
	( 63.09, 77.92) --
	( 63.32, 77.22) --
	( 63.56, 76.99) --
	( 63.80, 76.87) --
	( 64.03, 76.47) --
	( 64.27, 76.12) --
	( 64.50, 75.77) --
	( 64.74, 75.77) --
	( 64.97, 75.07) --
	( 65.21, 74.72) --
	( 65.44, 74.20) --
	( 65.68, 74.14) --
	( 65.92, 73.91) --
	( 66.15, 74.02) --
	( 66.39, 74.14) --
	( 66.62, 74.49) --
	( 66.86, 73.73) --
	( 67.09, 73.68) --
	( 67.33, 73.56) --
	( 67.56, 73.56) --
	( 67.80, 74.31) --
	( 68.04, 74.55) --
	( 68.27, 73.27) --
	( 68.51, 73.09) --
	( 68.74, 72.74) --
	( 68.98, 72.86) --
	( 69.21, 72.40) --
	( 69.45, 72.86) --
	( 69.69, 72.05) --
	( 69.92, 71.58) --
	( 70.16, 72.05) --
	( 70.39, 72.22) --
	( 70.63, 71.87) --
	( 70.86, 71.93) --
	( 71.10, 71.81) --
	( 71.33, 71.29) --
	( 71.57, 70.94) --
	( 71.81, 70.65) --
	( 72.04, 70.65) --
	( 72.28, 71.23) --
	( 72.51, 71.00) --
	( 72.75, 70.71) --
	( 72.98, 70.82) --
	( 73.22, 70.88) --
	( 73.45, 70.24) --
	( 73.69, 70.71) --
	( 73.93, 70.48) --
	( 74.16, 69.78) --
	( 74.40, 70.01) --
	( 74.63, 70.42) --
	( 74.87, 70.36) --
	( 75.10, 70.07) --
	( 75.34, 69.49) --
	( 75.57, 69.20) --
	( 75.81, 69.55) --
	( 76.05, 69.37) --
	( 76.28, 69.66) --
	( 76.52, 69.08) --
	( 76.75, 69.08) --
	( 76.99, 68.96) --
	( 77.22, 69.20) --
	( 77.46, 69.31) --
	( 77.69, 68.73) --
	( 77.93, 68.32) --
	( 78.17, 68.27) --
	( 78.40, 67.80) --
	( 78.64, 68.27) --
	( 78.87, 68.44) --
	( 79.11, 68.21) --
	( 79.34, 68.03) --
	( 79.58, 68.09) --
	( 79.81, 68.15) --
	( 80.05, 67.97) --
	( 80.29, 67.86) --
	( 80.52, 67.92) --
	( 80.76, 68.09) --
	( 80.99, 67.80) --
	( 81.23, 67.28) --
	( 81.46, 67.33) --
	( 81.70, 67.04) --
	( 81.93, 67.63) --
	( 82.17, 67.39) --
	( 82.41, 67.68) --
	( 82.64, 67.39) --
	( 82.88, 67.63) --
	( 83.11, 67.63) --
	( 83.35, 67.10) --
	( 83.58, 66.87) --
	( 83.82, 66.75) --
	( 84.05, 66.75) --
	( 84.29, 66.64) --
	( 84.53, 66.40) --
	( 84.76, 66.35) --
	( 85.00, 66.29) --
	( 85.23, 66.81) --
	( 85.47, 66.58) --
	( 85.70, 66.29) --
	( 85.94, 66.29) --
	( 86.17, 66.17) --
	( 86.41, 66.17) --
	( 86.65, 66.40) --
	( 86.88, 65.65) --
	( 87.12, 65.65) --
	( 87.35, 65.30) --
	( 87.59, 65.47) --
	( 87.82, 65.65) --
	( 88.06, 65.76) --
	( 88.29, 65.65) --
	( 88.53, 65.88) --
	( 88.77, 65.36) --
	( 89.00, 65.36) --
	( 89.24, 65.30) --
	( 89.47, 65.30) --
	( 89.71, 65.18) --
	( 89.94, 65.12) --
	( 90.18, 64.83) --
	( 90.41, 64.60) --
	( 90.65, 64.37) --
	( 90.89, 64.54) --
	( 91.12, 64.37) --
	( 91.36, 64.43) --
	( 91.59, 64.48) --
	( 91.83, 64.14) --
	( 92.06, 64.08) --
	( 92.30, 64.08) --
	( 92.53, 63.50) --
	( 92.77, 63.55) --
	( 93.01, 63.50) --
	( 93.24, 63.55) --
	( 93.48, 63.67) --
	( 93.71, 63.50) --
	( 93.95, 63.38) --
	( 94.18, 63.55) --
	( 94.42, 63.44) --
	( 94.66, 63.44) --
	( 94.89, 63.50) --
	( 95.13, 63.50) --
	( 95.36, 63.55) --
	( 95.60, 63.50) --
	( 95.83, 63.38) --
	( 96.07, 63.26) --
	( 96.30, 63.26) --
	( 96.54, 63.15) --
	( 96.78, 62.80) --
	( 97.01, 63.09) --
	( 97.25, 62.86) --
	( 97.48, 62.57) --
	( 97.72, 62.68) --
	( 97.95, 62.39) --
	( 98.19, 62.39) --
	( 98.42, 62.45) --
	( 98.66, 62.22) --
	( 98.90, 62.10) --
	( 99.13, 62.10) --
	( 99.37, 62.33) --
	( 99.60, 62.39) --
	( 99.84, 62.33) --
	(100.07, 61.93) --
	(100.31, 61.81) --
	(100.54, 61.69) --
	(100.78, 61.52) --
	(101.02, 61.29) --
	(101.25, 61.34) --
	(101.49, 61.58) --
	(101.72, 61.17) --
	(101.96, 60.88) --
	(102.19, 61.05) --
	(102.43, 61.23) --
	(102.66, 61.05) --
	(102.90, 60.82) --
	(103.14, 61.11) --
	(103.37, 61.05) --
	(103.61, 61.29) --
	(103.84, 61.05) --
	(104.08, 61.05) --
	(104.31, 60.94) --
	(104.55, 60.70) --
	(104.78, 60.82) --
	(105.02, 60.88) --
	(105.26, 60.99) --
	(105.49, 60.70) --
	(105.73, 60.70) --
	(105.96, 60.76) --
	(106.20, 60.53) --
	(106.43, 60.47) --
	(106.67, 60.47) --
	(106.90, 60.41) --
	(107.14, 60.30) --
	(107.38, 60.41) --
	(107.61, 60.30) --
	(107.85, 60.12) --
	(108.08, 60.24) --
	(108.32, 60.18) --
	(108.55, 60.12) --
	(108.79, 60.12) --
	(109.02, 60.24) --
	(109.26, 60.18) --
	(109.50, 60.06) --
	(109.73, 59.83) --
	(109.97, 59.89) --
	(110.20, 59.77) --
	(110.44, 59.54) --
	(110.67, 59.37) --
	(110.91, 59.25) --
	(111.14, 59.25) --
	(111.38, 59.13) --
	(111.62, 59.13) --
	(111.85, 59.02) --
	(112.09, 58.96) --
	(112.32, 58.84) --
	(112.56, 58.96) --
	(112.79, 58.96) --
	(113.03, 58.96) --
	(113.26, 58.96) --
	(113.50, 59.02) --
	(113.74, 58.96) --
	(113.97, 58.90) --
	(114.21, 58.84) --
	(114.44, 58.61) --
	(114.68, 58.67) --
	(114.91, 58.49) --
	(115.15, 58.44) --
	(115.38, 58.44) --
	(115.62, 58.38) --
	(115.86, 58.38) --
	(116.09, 58.38) --
	(116.33, 58.32) --
	(116.56, 58.67) --
	(116.80, 58.61) --
	(117.03, 58.26) --
	(117.27, 58.49) --
	(117.51, 58.44) --
	(117.74, 58.38) --
	(117.98, 58.38) --
	(118.21, 58.32) --
	(118.45, 58.20) --
	(118.68, 58.09) --
	(118.92, 58.09) --
	(119.15, 58.14) --
	(119.39, 58.20) --
	(119.63, 58.26) --
	(119.86, 58.26) --
	(120.10, 58.14) --
	(120.33, 57.97) --
	(120.57, 58.03) --
	(120.80, 58.09) --
	(121.04, 57.85) --
	(121.27, 57.97) --
	(121.51, 57.85) --
	(121.75, 57.80) --
	(121.98, 57.80) --
	(122.22, 57.56) --
	(122.45, 57.56) --
	(122.69, 57.45) --
	(122.92, 57.50) --
	(123.16, 57.33) --
	(123.39, 57.39) --
	(123.63, 57.33) --
	(123.87, 57.21) --
	(124.10, 57.27) --
	(124.34, 57.21) --
	(124.57, 56.98) --
	(124.81, 56.92) --
	(125.04, 56.98) --
	(125.28, 56.98) --
	(125.51, 56.81) --
	(125.75, 56.75) --
	(125.99, 56.86) --
	(126.22, 56.75) --
	(126.46, 56.81) --
	(126.69, 56.75) --
	(126.93, 56.75) --
	(127.16, 56.81) --
	(127.40, 56.75) --
	(127.63, 56.63) --
	(127.87, 56.52) --
	(128.11, 56.46) --
	(128.34, 56.46) --
	(128.58, 56.40) --
	(128.81, 56.34) --
	(129.05, 56.40) --
	(129.28, 56.17) --
	(129.52, 56.23) --
	(129.75, 56.11) --
	(129.99, 56.28) --
	(130.23, 56.17) --
	(130.46, 56.11) --
	(130.70, 56.17) --
	(130.93, 56.05) --
	(131.17, 55.93) --
	(131.40, 56.05) --
	(131.64, 55.88) --
	(131.87, 55.93) --
	(132.11, 55.99) --
	(132.35, 55.82) --
	(132.58, 55.93);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44, 50.02) rectangle (137.69,119.88);
\end{scope}
\begin{scope}
\path[clip] ( 54.44,119.88) rectangle (137.69,127.83);

\path[] ( 54.44,119.88) rectangle (137.69,127.83);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 69.67,121.58) {T=500, K=3, c=1};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,119.88) rectangle (137.69,127.83);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.45, 50.02) -- (140.45, 44.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (164.01, 50.02) -- (164.01, 44.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.56, 50.02) -- (187.56, 44.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.12, 50.02) -- (211.12, 44.32);
\end{scope}
\begin{scope}
\path[clip] (137.69, 50.02) rectangle (220.94,119.88);
\definecolor[named]{drawColor}{rgb}{0.83,0.83,0.83}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.45, 78.87) --
	(218.97, 78.87);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.80, 75.31) --
	(143.04, 74.32) --
	(143.28, 75.80) --
	(143.51, 75.80) --
	(143.75, 75.06) --
	(143.98, 75.18) --
	(144.22, 74.69) --
	(144.45, 74.32) --
	(144.69, 74.20) --
	(144.92, 73.10) --
	(145.16, 72.97) --
	(145.40, 71.75) --
	(145.63, 71.62) --
	(145.87, 71.38) --
	(146.10, 72.97) --
	(146.34, 74.45) --
	(146.57, 73.71) --
	(146.81, 73.34) --
	(147.05, 71.13) --
	(147.28, 69.90) --
	(147.52, 70.64) --
	(147.75, 71.62) --
	(147.99, 71.13) --
	(148.22, 71.13) --
	(148.46, 71.62) --
	(148.69, 70.64) --
	(148.93, 70.15) --
	(149.17, 70.76) --
	(149.40, 70.39) --
	(149.64, 71.13) --
	(149.87, 71.75) --
	(150.11, 69.66) --
	(150.34, 69.78) --
	(150.58, 69.66) --
	(150.81, 68.80) --
	(151.05, 69.29) --
	(151.29, 69.29) --
	(151.52, 68.92) --
	(151.76, 68.92) --
	(151.99, 68.92) --
	(152.23, 67.57) --
	(152.46, 68.18) --
	(152.70, 67.20) --
	(152.93, 67.69) --
	(153.17, 67.69) --
	(153.41, 68.18) --
	(153.64, 68.68) --
	(153.88, 68.55) --
	(154.11, 68.43) --
	(154.35, 68.43) --
	(154.58, 67.69) --
	(154.82, 67.32) --
	(155.05, 67.94) --
	(155.29, 68.06) --
	(155.53, 67.45) --
	(155.76, 67.20) --
	(156.00, 66.83) --
	(156.23, 66.34) --
	(156.47, 66.34) --
	(156.70, 66.71) --
	(156.94, 66.34) --
	(157.17, 66.59) --
	(157.41, 65.85) --
	(157.65, 65.60) --
	(157.88, 66.34) --
	(158.12, 65.48) --
	(158.35, 65.36) --
	(158.59, 65.85) --
	(158.82, 65.36) --
	(159.06, 66.59) --
	(159.29, 65.97) --
	(159.53, 65.60) --
	(159.77, 66.22) --
	(160.00, 65.85) --
	(160.24, 65.85) --
	(160.47, 64.99) --
	(160.71, 64.99) --
	(160.94, 65.60) --
	(161.18, 65.85) --
	(161.41, 65.11) --
	(161.65, 64.25) --
	(161.89, 63.89) --
	(162.12, 64.25) --
	(162.36, 64.01) --
	(162.59, 64.13) --
	(162.83, 64.75) --
	(163.06, 64.13) --
	(163.30, 64.13) --
	(163.53, 64.13) --
	(163.77, 64.38) --
	(164.01, 64.25) --
	(164.24, 64.01) --
	(164.48, 63.64) --
	(164.71, 63.64) --
	(164.95, 63.52) --
	(165.18, 63.76) --
	(165.42, 63.76) --
	(165.65, 63.27) --
	(165.89, 63.15) --
	(166.13, 63.76) --
	(166.36, 63.89) --
	(166.60, 63.03) --
	(166.83, 62.66) --
	(167.07, 62.29) --
	(167.30, 62.66) --
	(167.54, 61.92) --
	(167.77, 61.92) --
	(168.01, 61.67) --
	(168.25, 61.80) --
	(168.48, 61.92) --
	(168.72, 62.41) --
	(168.95, 62.41) --
	(169.19, 62.53) --
	(169.42, 62.41) --
	(169.66, 62.17) --
	(169.90, 61.80) --
	(170.13, 61.67) --
	(170.37, 61.80) --
	(170.60, 61.67) --
	(170.84, 61.80) --
	(171.07, 61.80) --
	(171.31, 60.94) --
	(171.54, 60.45) --
	(171.78, 60.32) --
	(172.02, 60.45) --
	(172.25, 60.20) --
	(172.49, 60.57) --
	(172.72, 61.18) --
	(172.96, 60.57) --
	(173.19, 60.08) --
	(173.43, 60.20) --
	(173.66, 60.08) --
	(173.90, 60.08) --
	(174.14, 60.08) --
	(174.37, 60.08) --
	(174.61, 59.34) --
	(174.84, 59.22) --
	(175.08, 59.22) --
	(175.31, 58.97) --
	(175.55, 58.73) --
	(175.78, 58.85) --
	(176.02, 58.85) --
	(176.26, 59.22) --
	(176.49, 59.22) --
	(176.73, 59.10) --
	(176.96, 59.10) --
	(177.20, 59.34) --
	(177.43, 58.85) --
	(177.67, 58.85) --
	(177.90, 58.85) --
	(178.14, 58.73) --
	(178.38, 58.36) --
	(178.61, 58.48) --
	(178.85, 57.99) --
	(179.08, 58.11) --
	(179.32, 57.99) --
	(179.55, 57.87) --
	(179.79, 57.74) --
	(180.02, 57.38) --
	(180.26, 57.25) --
	(180.50, 57.13) --
	(180.73, 57.50) --
	(180.97, 57.38) --
	(181.20, 57.13) --
	(181.44, 57.25) --
	(181.67, 57.62) --
	(181.91, 57.25) --
	(182.14, 57.25) --
	(182.38, 57.13) --
	(182.62, 56.76) --
	(182.85, 56.88) --
	(183.09, 56.52) --
	(183.32, 56.27) --
	(183.56, 56.27) --
	(183.79, 56.39) --
	(184.03, 56.15) --
	(184.26, 56.03) --
	(184.50, 56.39) --
	(184.74, 56.03) --
	(184.97, 56.27) --
	(185.21, 56.15) --
	(185.44, 56.27) --
	(185.68, 56.15) --
	(185.91, 56.39) --
	(186.15, 56.27) --
	(186.38, 56.52) --
	(186.62, 56.27) --
	(186.86, 56.15) --
	(187.09, 56.15) --
	(187.33, 55.90) --
	(187.56, 55.78) --
	(187.80, 55.53) --
	(188.03, 55.78) --
	(188.27, 55.66) --
	(188.50, 55.41) --
	(188.74, 55.29) --
	(188.98, 55.41) --
	(189.21, 55.66) --
	(189.45, 55.53) --
	(189.68, 55.29) --
	(189.92, 54.92) --
	(190.15, 55.04) --
	(190.39, 55.29) --
	(190.62, 55.41) --
	(190.86, 55.53) --
	(191.10, 55.29) --
	(191.33, 55.29) --
	(191.57, 55.04) --
	(191.80, 55.17) --
	(192.04, 55.29) --
	(192.27, 55.29) --
	(192.51, 55.04) --
	(192.74, 55.04) --
	(192.98, 55.04) --
	(193.22, 55.04) --
	(193.45, 55.17) --
	(193.69, 55.17) --
	(193.92, 55.29) --
	(194.16, 55.04) --
	(194.39, 54.92) --
	(194.63, 54.92) --
	(194.87, 54.92) --
	(195.10, 54.92) --
	(195.34, 54.67) --
	(195.57, 54.55) --
	(195.81, 54.55) --
	(196.04, 54.55) --
	(196.28, 54.55) --
	(196.51, 54.55) --
	(196.75, 54.55) --
	(196.99, 54.55) --
	(197.22, 54.55) --
	(197.46, 54.67) --
	(197.69, 54.80) --
	(197.93, 54.80) --
	(198.16, 54.92) --
	(198.40, 54.67) --
	(198.63, 54.80) --
	(198.87, 54.80) --
	(199.11, 54.67) --
	(199.34, 54.43) --
	(199.58, 54.55) --
	(199.81, 54.55) --
	(200.05, 54.55) --
	(200.28, 54.67) --
	(200.52, 54.55) --
	(200.75, 54.55) --
	(200.99, 54.55) --
	(201.23, 54.43) --
	(201.46, 54.55) --
	(201.70, 54.43) --
	(201.93, 54.55) --
	(202.17, 54.55) --
	(202.40, 54.43) --
	(202.64, 54.31) --
	(202.87, 54.31) --
	(203.11, 54.31) --
	(203.35, 54.31) --
	(203.58, 54.31) --
	(203.82, 54.31) --
	(204.05, 54.43) --
	(204.29, 54.55) --
	(204.52, 54.55) --
	(204.76, 54.43) --
	(204.99, 54.43) --
	(205.23, 54.43) --
	(205.47, 54.43) --
	(205.70, 54.43) --
	(205.94, 54.55) --
	(206.17, 54.55) --
	(206.41, 54.55) --
	(206.64, 54.31) --
	(206.88, 54.43) --
	(207.11, 54.55) --
	(207.35, 54.55) --
	(207.59, 54.55) --
	(207.82, 54.55) --
	(208.06, 54.55) --
	(208.29, 54.55) --
	(208.53, 54.43) --
	(208.76, 54.43) --
	(209.00, 54.43) --
	(209.23, 54.31) --
	(209.47, 54.43) --
	(209.71, 54.31) --
	(209.94, 54.31) --
	(210.18, 54.31) --
	(210.41, 54.43) --
	(210.65, 54.43) --
	(210.88, 54.31) --
	(211.12, 54.43) --
	(211.35, 54.31) --
	(211.59, 54.31) --
	(211.83, 54.31) --
	(212.06, 54.31) --
	(212.30, 54.31) --
	(212.53, 54.31) --
	(212.77, 54.31) --
	(213.00, 54.31) --
	(213.24, 54.31) --
	(213.47, 54.31) --
	(213.71, 54.31) --
	(213.95, 54.31) --
	(214.18, 54.31) --
	(214.42, 54.31) --
	(214.65, 54.31) --
	(214.89, 54.31) --
	(215.12, 54.31) --
	(215.36, 54.31) --
	(215.59, 54.31) --
	(215.83, 54.31);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.69, 50.02) rectangle (220.94,119.88);
\end{scope}
\begin{scope}
\path[clip] (137.69,119.88) rectangle (220.94,127.83);

\path[] (137.69,119.88) rectangle (220.94,127.83);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.66] at (147.24,121.58) {T=500, K=T/10, c=1};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.69,119.88) rectangle (220.94,127.83);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.70, 50.02) -- (223.70, 44.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (247.26, 50.02) -- (247.26, 44.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (270.81, 50.02) -- (270.81, 44.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (294.37, 50.02) -- (294.37, 44.32);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (223.70, 32.02) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (247.26, 32.02) {0.2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (270.81, 32.02) {0.4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (294.37, 32.02) {0.6};
\end{scope}
\begin{scope}
\path[clip] (220.94, 50.02) rectangle (304.19,119.88);
\definecolor[named]{drawColor}{rgb}{0.83,0.83,0.83}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.70, 78.87) --
	(302.22, 78.87);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.05, 81.08) --
	(226.29, 80.59) --
	(226.53, 83.54) --
	(226.76, 81.20) --
	(227.00, 81.94) --
	(227.23, 81.08) --
	(227.47, 81.45) --
	(227.70, 81.33) --
	(227.94, 82.55) --
	(228.17, 83.17) --
	(228.41, 82.43) --
	(228.65, 81.69) --
	(228.88, 83.29) --
	(229.12, 81.82) --
	(229.35, 83.05) --
	(229.59, 81.94) --
	(229.82, 81.33) --
	(230.06, 80.71) --
	(230.29, 80.71) --
	(230.53, 81.08) --
	(230.77, 82.19) --
	(231.00, 82.19) --
	(231.24, 82.06) --
	(231.47, 82.43) --
	(231.71, 82.06) --
	(231.94, 82.55) --
	(232.18, 81.94) --
	(232.41, 81.94) --
	(232.65, 80.71) --
	(232.89, 80.47) --
	(233.12, 80.59) --
	(233.36, 81.94) --
	(233.59, 81.45) --
	(233.83, 79.73) --
	(234.06, 79.73) --
	(234.30, 78.62) --
	(234.53, 80.47) --
	(234.77, 80.59) --
	(235.01, 80.96) --
	(235.24, 80.34) --
	(235.48, 80.47) --
	(235.71, 79.85) --
	(235.95, 79.97) --
	(236.18, 80.22) --
	(236.42, 79.11) --
	(236.65, 79.73) --
	(236.89, 78.87) --
	(237.13, 79.85) --
	(237.36, 79.73) --
	(237.60, 78.87) --
	(237.83, 78.87) --
	(238.07, 79.73) --
	(238.30, 79.24) --
	(238.54, 78.62) --
	(238.77, 78.87) --
	(239.01, 80.10) --
	(239.25, 79.97) --
	(239.48, 80.59) --
	(239.72, 80.34) --
	(239.95, 81.69) --
	(240.19, 81.45) --
	(240.42, 80.96) --
	(240.66, 80.96) --
	(240.89, 80.71) --
	(241.13, 80.59) --
	(241.37, 81.08) --
	(241.60, 80.59) --
	(241.84, 80.59) --
	(242.07, 80.22) --
	(242.31, 80.34) --
	(242.54, 80.47) --
	(242.78, 80.34) --
	(243.01, 80.10) --
	(243.25, 80.47) --
	(243.49, 79.85) --
	(243.72, 79.97) --
	(243.96, 80.22) --
	(244.19, 80.59) --
	(244.43, 81.08) --
	(244.66, 81.33) --
	(244.90, 81.57) --
	(245.13, 80.47) --
	(245.37, 79.97) --
	(245.61, 80.10) --
	(245.84, 80.34) --
	(246.08, 80.34) --
	(246.31, 79.97) --
	(246.55, 80.59) --
	(246.78, 80.59) --
	(247.02, 80.22) --
	(247.26, 79.48) --
	(247.49, 78.50) --
	(247.73, 78.01) --
	(247.96, 77.89) --
	(248.20, 77.64) --
	(248.43, 78.01) --
	(248.67, 78.26) --
	(248.90, 78.99) --
	(249.14, 79.24) --
	(249.38, 78.99) --
	(249.61, 78.50) --
	(249.85, 78.13) --
	(250.08, 78.01) --
	(250.32, 78.50) --
	(250.55, 78.13) --
	(250.79, 78.01) --
	(251.02, 78.26) --
	(251.26, 78.62) --
	(251.50, 78.87) --
	(251.73, 78.75) --
	(251.97, 78.38) --
	(252.20, 78.87) --
	(252.44, 78.26) --
	(252.67, 78.62) --
	(252.91, 77.15) --
	(253.14, 77.40) --
	(253.38, 77.64) --
	(253.62, 77.89) --
	(253.85, 77.40) --
	(254.09, 77.40) --
	(254.32, 77.15) --
	(254.56, 77.52) --
	(254.79, 76.78) --
	(255.03, 76.78) --
	(255.26, 76.66) --
	(255.50, 77.52) --
	(255.74, 77.52) --
	(255.97, 77.40) --
	(256.21, 77.03) --
	(256.44, 76.78) --
	(256.68, 76.90) --
	(256.91, 77.40) --
	(257.15, 77.64) --
	(257.38, 77.64) --
	(257.62, 77.89) --
	(257.86, 77.52) --
	(258.09, 76.90) --
	(258.33, 77.40) --
	(258.56, 76.54) --
	(258.80, 76.78) --
	(259.03, 77.15) --
	(259.27, 76.78) --
	(259.50, 76.66) --
	(259.74, 76.54) --
	(259.98, 76.17) --
	(260.21, 76.29) --
	(260.45, 75.43) --
	(260.68, 75.80) --
	(260.92, 76.17) --
	(261.15, 76.04) --
	(261.39, 75.68) --
	(261.62, 75.43) --
	(261.86, 75.68) --
	(262.10, 75.68) --
	(262.33, 75.31) --
	(262.57, 75.43) --
	(262.80, 75.18) --
	(263.04, 75.06) --
	(263.27, 74.94) --
	(263.51, 75.18) --
	(263.74, 74.45) --
	(263.98, 74.69) --
	(264.22, 74.08) --
	(264.45, 73.96) --
	(264.69, 74.45) --
	(264.92, 74.57) --
	(265.16, 74.08) --
	(265.39, 73.71) --
	(265.63, 73.71) --
	(265.86, 73.47) --
	(266.10, 73.83) --
	(266.34, 73.96) --
	(266.57, 73.71) --
	(266.81, 73.10) --
	(267.04, 73.59) --
	(267.28, 73.83) --
	(267.51, 73.96) --
	(267.75, 74.32) --
	(267.98, 74.32) --
	(268.22, 73.96) --
	(268.46, 73.47) --
	(268.69, 73.83) --
	(268.93, 73.71) --
	(269.16, 73.71) --
	(269.40, 73.47) --
	(269.63, 73.59) --
	(269.87, 73.47) --
	(270.11, 72.97) --
	(270.34, 72.73) --
	(270.58, 72.85) --
	(270.81, 72.48) --
	(271.05, 72.73) --
	(271.28, 72.85) --
	(271.52, 72.61) --
	(271.75, 72.36) --
	(271.99, 72.48) --
	(272.23, 72.36) --
	(272.46, 72.11) --
	(272.70, 72.24) --
	(272.93, 71.25) --
	(273.17, 71.25) --
	(273.40, 71.01) --
	(273.64, 71.01) --
	(273.87, 71.25) --
	(274.11, 71.38) --
	(274.35, 71.01) --
	(274.58, 70.39) --
	(274.82, 70.64) --
	(275.05, 71.13) --
	(275.29, 70.76) --
	(275.52, 70.52) --
	(275.76, 70.64) --
	(275.99, 70.27) --
	(276.23, 70.76) --
	(276.47, 70.64) --
	(276.70, 70.64) --
	(276.94, 71.38) --
	(277.17, 71.01) --
	(277.41, 71.01) --
	(277.64, 71.13) --
	(277.88, 71.38) --
	(278.11, 71.01) --
	(278.35, 70.76) --
	(278.59, 70.27) --
	(278.82, 70.64) --
	(279.06, 70.76) --
	(279.29, 71.25) --
	(279.53, 70.39) --
	(279.76, 70.76) --
	(280.00, 71.13) --
	(280.23, 70.39) --
	(280.47, 70.76) --
	(280.71, 70.76) --
	(280.94, 70.39) --
	(281.18, 70.27) --
	(281.41, 70.52) --
	(281.65, 70.39) --
	(281.88, 70.39) --
	(282.12, 70.52) --
	(282.35, 71.01) --
	(282.59, 70.52) --
	(282.83, 70.52) --
	(283.06, 69.90) --
	(283.30, 70.39) --
	(283.53, 69.90) --
	(283.77, 70.27) --
	(284.00, 70.39) --
	(284.24, 70.39) --
	(284.47, 70.27) --
	(284.71, 70.52) --
	(284.95, 70.03) --
	(285.18, 70.64) --
	(285.42, 70.27) --
	(285.65, 70.03) --
	(285.89, 69.90) --
	(286.12, 70.03) --
	(286.36, 70.03) --
	(286.59, 70.52) --
	(286.83, 70.27) --
	(287.07, 70.64) --
	(287.30, 70.64) --
	(287.54, 71.13) --
	(287.77, 70.89) --
	(288.01, 71.01) --
	(288.24, 70.39) --
	(288.48, 70.52) --
	(288.71, 70.89) --
	(288.95, 70.64) --
	(289.19, 70.39) --
	(289.42, 70.27) --
	(289.66, 69.66) --
	(289.89, 69.54) --
	(290.13, 69.41) --
	(290.36, 69.04) --
	(290.60, 69.17) --
	(290.83, 68.92) --
	(291.07, 68.80) --
	(291.31, 68.55) --
	(291.54, 68.68) --
	(291.78, 68.92) --
	(292.01, 69.04) --
	(292.25, 68.55) --
	(292.48, 68.06) --
	(292.72, 67.82) --
	(292.96, 67.57) --
	(293.19, 67.69) --
	(293.43, 67.32) --
	(293.66, 66.96) --
	(293.90, 66.96) --
	(294.13, 66.83) --
	(294.37, 66.83) --
	(294.60, 66.59) --
	(294.84, 66.34) --
	(295.08, 66.96) --
	(295.31, 66.83) --
	(295.55, 66.96) --
	(295.78, 67.08) --
	(296.02, 67.08) --
	(296.25, 66.83) --
	(296.49, 66.71) --
	(296.72, 66.96) --
	(296.96, 66.34) --
	(297.20, 66.46) --
	(297.43, 66.22) --
	(297.67, 66.34) --
	(297.90, 66.46) --
	(298.14, 66.34) --
	(298.37, 66.34) --
	(298.61, 66.10) --
	(298.84, 66.34) --
	(299.08, 66.71);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.94, 50.02) rectangle (304.19,119.88);
\end{scope}
\begin{scope}
\path[clip] (220.94,119.88) rectangle (304.19,127.83);

\path[] (220.94,119.88) rectangle (304.19,127.83);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.66] at (236.17,121.58) {T=500, K=3, c=2};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.94,119.88) rectangle (304.19,127.83);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (306.95, 50.02) -- (306.95, 44.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (330.50, 50.02) -- (330.50, 44.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.06, 50.02) -- (354.06, 44.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.62, 50.02) -- (377.62, 44.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.44, 54.31) -- (393.13, 54.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.44, 66.59) -- (393.13, 66.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.44, 78.87) -- (393.13, 78.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.44, 91.15) -- (393.13, 91.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.44,103.43) -- (393.13,103.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.44,115.71) -- (393.13,115.71);
\end{scope}
\begin{scope}
\path[clip] (304.19, 50.02) rectangle (387.44,119.88);
\definecolor[named]{drawColor}{rgb}{0.83,0.83,0.83}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (306.95, 78.87) --
	(385.47, 78.87);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (309.30, 89.92) --
	(309.54, 90.29) --
	(309.77, 90.17) --
	(310.01, 90.29) --
	(310.25, 89.31) --
	(310.48, 90.29) --
	(310.72, 91.64) --
	(310.95, 90.54) --
	(311.19, 91.52) --
	(311.42, 91.77) --
	(311.66, 92.62) --
	(311.89, 94.96) --
	(312.13, 96.06) --
	(312.37, 94.71) --
	(312.60, 96.43) --
	(312.84, 97.41) --
	(313.07, 98.52) --
	(313.31, 99.13) --
	(313.54, 98.77) --
	(313.78,100.49) --
	(314.01,100.36) --
	(314.25,100.61) --
	(314.49,101.35) --
	(314.72,102.33) --
	(314.96,101.59) --
	(315.19,101.10) --
	(315.43,101.10) --
	(315.66,100.61) --
	(315.90,102.20) --
	(316.13,102.33) --
	(316.37,102.33) --
	(316.61,102.82) --
	(316.84,104.17) --
	(317.08,104.17) --
	(317.31,103.68) --
	(317.55,104.91) --
	(317.78,103.68) --
	(318.02,104.54) --
	(318.25,105.03) --
	(318.49,105.28) --
	(318.73,105.40) --
	(318.96,105.03) --
	(319.20,104.78) --
	(319.43,103.80) --
	(319.67,104.91) --
	(319.90,106.87) --
	(320.14,107.49) --
	(320.37,107.49) --
	(320.61,107.61) --
	(320.85,107.98) --
	(321.08,107.98) --
	(321.32,108.10) --
	(321.55,108.47) --
	(321.79,107.98) --
	(322.02,108.35) --
	(322.26,108.71) --
	(322.50,107.98) --
	(322.73,109.21) --
	(322.97,108.22) --
	(323.20,108.71) --
	(323.44,109.70) --
	(323.67,109.70) --
	(323.91,110.68) --
	(324.14,109.94) --
	(324.38,110.31) --
	(324.62,109.33) --
	(324.85,108.84) --
	(325.09,110.07) --
	(325.32,109.45) --
	(325.56,109.57) --
	(325.79,110.80) --
	(326.03,110.43) --
	(326.26,110.31) --
	(326.50,111.78) --
	(326.74,110.68) --
	(326.97,111.29) --
	(327.21,111.91) --
	(327.44,111.29) --
	(327.68,111.17) --
	(327.91,110.56) --
	(328.15,110.31) --
	(328.38,110.80) --
	(328.62,110.43) --
	(328.86,111.78) --
	(329.09,111.42) --
	(329.33,111.66) --
	(329.56,113.01) --
	(329.80,112.64) --
	(330.03,112.77) --
	(330.27,112.89) --
	(330.50,113.87) --
	(330.74,114.12) --
	(330.98,112.15) --
	(331.21,111.54) --
	(331.45,113.50) --
	(331.68,113.50) --
	(331.92,114.98) --
	(332.15,115.22) --
	(332.39,115.59) --
	(332.62,114.73) --
	(332.86,115.35) --
	(333.10,113.75) --
	(333.33,114.24) --
	(333.57,113.50) --
	(333.80,114.98) --
	(334.04,115.10) --
	(334.27,113.87) --
	(334.51,114.24) --
	(334.74,114.36) --
	(334.98,114.24) --
	(335.22,113.01) --
	(335.45,113.87) --
	(335.69,113.87) --
	(335.92,114.61) --
	(336.16,115.22) --
	(336.39,114.00) --
	(336.63,114.36) --
	(336.86,113.75) --
	(337.10,114.61) --
	(337.34,113.38) --
	(337.57,112.89) --
	(337.81,112.77) --
	(338.04,113.14) --
	(338.28,112.03) --
	(338.51,111.66) --
	(338.75,112.77) --
	(338.98,112.52) --
	(339.22,111.66) --
	(339.46,111.66) --
	(339.69,111.42) --
	(339.93,111.17) --
	(340.16,112.28) --
	(340.40,111.29) --
	(340.63,109.45) --
	(340.87,110.31) --
	(341.10,110.43) --
	(341.34,111.17) --
	(341.58,110.80) --
	(341.81,110.92) --
	(342.05,111.29) --
	(342.28,110.80) --
	(342.52,111.17) --
	(342.75,110.92) --
	(342.99,111.66) --
	(343.22,111.54) --
	(343.46,111.54) --
	(343.70,110.92) --
	(343.93,111.54) --
	(344.17,110.92) --
	(344.40,111.17) --
	(344.64,111.05) --
	(344.87,110.68) --
	(345.11,109.82) --
	(345.35,110.92) --
	(345.58,110.68) --
	(345.82,111.54) --
	(346.05,110.56) --
	(346.29,110.19) --
	(346.52,110.80) --
	(346.76,110.92) --
	(346.99,111.29) --
	(347.23,111.05) --
	(347.47,110.68) --
	(347.70,110.19) --
	(347.94,110.31) --
	(348.17,110.19) --
	(348.41,110.07) --
	(348.64,110.31) --
	(348.88,109.70) --
	(349.11,108.71) --
	(349.35,109.57) --
	(349.59,108.96) --
	(349.82,109.57) --
	(350.06,109.45) --
	(350.29,109.45) --
	(350.53,108.35) --
	(350.76,107.85) --
	(351.00,107.85) --
	(351.23,108.35) --
	(351.47,108.96) --
	(351.71,108.96) --
	(351.94,107.85) --
	(352.18,108.84) --
	(352.41,108.47) --
	(352.65,108.71) --
	(352.88,107.98) --
	(353.12,107.49) --
	(353.35,106.63) --
	(353.59,106.99) --
	(353.83,105.15) --
	(354.06,105.40) --
	(354.30,104.42) --
	(354.53,103.68) --
	(354.77,103.43) --
	(355.00,103.80) --
	(355.24,104.17) --
	(355.47,103.56) --
	(355.71,103.19) --
	(355.95,103.31) --
	(356.18,103.06) --
	(356.42,102.45) --
	(356.65,101.59) --
	(356.89,101.84) --
	(357.12,102.08) --
	(357.36,101.22) --
	(357.59,102.20) --
	(357.83,101.71) --
	(358.07,101.71) --
	(358.30,100.73) --
	(358.54,100.24) --
	(358.77,101.47) --
	(359.01,101.10) --
	(359.24, 99.50) --
	(359.48, 99.38) --
	(359.71, 99.38) --
	(359.95, 99.75) --
	(360.19,100.85) --
	(360.42, 99.26) --
	(360.66, 99.01) --
	(360.89, 98.52) --
	(361.13, 98.52) --
	(361.36, 98.03) --
	(361.60, 96.80) --
	(361.83, 97.41) --
	(362.07, 95.94) --
	(362.31, 95.70) --
	(362.54, 96.80) --
	(362.78, 96.80) --
	(363.01, 96.06) --
	(363.25, 95.70) --
	(363.48, 95.20) --
	(363.72, 94.84) --
	(363.95, 95.20) --
	(364.19, 95.08) --
	(364.43, 93.85) --
	(364.66, 94.34) --
	(364.90, 94.10) --
	(365.13, 94.59) --
	(365.37, 93.48) --
	(365.60, 93.73) --
	(365.84, 94.22) --
	(366.07, 93.36) --
	(366.31, 93.36) --
	(366.55, 93.12) --
	(366.78, 93.24) --
	(367.02, 93.24) --
	(367.25, 93.61) --
	(367.49, 93.61) --
	(367.72, 92.26) --
	(367.96, 92.01) --
	(368.19, 90.41) --
	(368.43, 91.15) --
	(368.67, 90.91) --
	(368.90, 91.27) --
	(369.14, 91.03) --
	(369.37, 91.89) --
	(369.61, 91.27) --
	(369.84, 91.40) --
	(370.08, 91.03) --
	(370.32, 90.05) --
	(370.55, 89.80) --
	(370.79, 89.55) --
	(371.02, 89.19) --
	(371.26, 89.19) --
	(371.49, 88.45) --
	(371.73, 87.96) --
	(371.96, 87.96) --
	(372.20, 87.47) --
	(372.44, 87.84) --
	(372.67, 87.10) --
	(372.91, 86.98) --
	(373.14, 86.48) --
	(373.38, 85.50) --
	(373.61, 85.62) --
	(373.85, 84.40) --
	(374.08, 85.01) --
	(374.32, 84.64) --
	(374.56, 84.76) --
	(374.79, 84.89) --
	(375.03, 83.66) --
	(375.26, 83.90) --
	(375.50, 83.78) --
	(375.73, 83.41) --
	(375.97, 82.92) --
	(376.20, 81.82) --
	(376.44, 81.69) --
	(376.68, 81.20) --
	(376.91, 81.08) --
	(377.15, 80.71) --
	(377.38, 80.47) --
	(377.62, 79.48) --
	(377.85, 78.50) --
	(378.09, 78.99) --
	(378.32, 79.24) --
	(378.56, 78.87) --
	(378.80, 78.50) --
	(379.03, 78.26) --
	(379.27, 78.01) --
	(379.50, 77.52) --
	(379.74, 76.90) --
	(379.97, 77.15) --
	(380.21, 76.66) --
	(380.44, 76.66) --
	(380.68, 76.29) --
	(380.92, 76.29) --
	(381.15, 75.80) --
	(381.39, 75.31) --
	(381.62, 75.18) --
	(381.86, 74.94) --
	(382.09, 75.18) --
	(382.33, 74.69);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (304.19, 50.02) rectangle (387.44,119.88);
\end{scope}
\begin{scope}
\path[clip] (304.19,119.88) rectangle (387.44,127.83);

\path[] (304.19,119.88) rectangle (387.44,127.83);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.66] at (313.74,121.58) {T=500, K=T/10, c=2};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (304.19,119.88) rectangle (387.44,127.83);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,132.12) -- ( 48.75,132.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,144.40) -- ( 48.75,144.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,156.69) -- ( 48.75,156.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,168.97) -- ( 48.75,168.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,181.25) -- ( 48.75,181.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,193.53) -- ( 48.75,193.53);
\end{scope}
\begin{scope}
\path[clip] ( 54.44,127.83) rectangle (137.69,197.70);
\definecolor[named]{drawColor}{rgb}{0.83,0.83,0.83}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 57.20,156.69) --
	(135.72,156.69);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 61.91,156.44) --
	( 62.38,157.24) --
	( 62.85,157.35) --
	( 63.32,157.18) --
	( 63.80,157.47) --
	( 64.27,156.21) --
	( 64.74,156.38) --
	( 65.21,156.27) --
	( 65.68,156.38) --
	( 66.15,156.67) --
	( 66.62,155.87) --
	( 67.09,156.10) --
	( 67.56,155.53) --
	( 68.04,154.50) --
	( 68.51,154.62) --
	( 68.98,154.79) --
	( 69.45,154.39) --
	( 69.92,154.11) --
	( 70.39,154.16) --
	( 70.86,153.99) --
	( 71.33,153.71) --
	( 71.81,153.48) --
	( 72.28,153.42) --
	( 72.75,152.74) --
	( 73.22,152.23) --
	( 73.69,152.45) --
	( 74.16,153.14) --
	( 74.63,151.83) --
	( 75.10,151.66) --
	( 75.57,151.49) --
	( 76.05,151.49) --
	( 76.52,151.37) --
	( 76.99,151.03) --
	( 77.46,150.57) --
	( 77.93,150.63) --
	( 78.40,150.57) --
	( 78.87,150.00) --
	( 79.34,149.66) --
	( 79.81,150.00) --
	( 80.29,150.06) --
	( 80.76,149.38) --
	( 81.23,149.49) --
	( 81.70,148.87) --
	( 82.17,149.04) --
	( 82.64,149.09) --
	( 83.11,148.52) --
	( 83.58,148.24) --
	( 84.05,148.47) --
	( 84.53,148.41) --
	( 85.00,147.56) --
	( 85.47,147.27) --
	( 85.94,147.16) --
	( 86.41,146.64) --
	( 86.88,146.19) --
	( 87.35,146.36) --
	( 87.82,145.62) --
	( 88.29,145.90) --
	( 88.77,145.79) --
	( 89.24,146.19) --
	( 89.71,145.68) --
	( 90.18,144.82) --
	( 90.65,144.71) --
	( 91.12,145.11) --
	( 91.59,144.82) --
	( 92.06,144.59) --
	( 92.53,144.59) --
	( 93.01,143.97) --
	( 93.48,143.63) --
	( 93.95,143.17) --
	( 94.42,143.11) --
	( 94.89,143.28) --
	( 95.36,143.46) --
	( 95.83,143.23) --
	( 96.30,143.46) --
	( 96.78,143.40) --
	( 97.25,142.89) --
	( 97.72,142.71) --
	( 98.19,142.66) --
	( 98.66,142.20) --
	( 99.13,141.97) --
	( 99.60,141.97) --
	(100.07,141.75) --
	(100.54,141.52) --
	(101.02,141.41) --
	(101.49,141.12) --
	(101.96,141.06) --
	(102.43,140.89) --
	(102.90,140.84) --
	(103.37,140.61) --
	(103.84,140.55) --
	(104.31,140.84) --
	(104.78,140.78) --
	(105.26,140.84) --
	(105.73,140.61) --
	(106.20,140.38) --
	(106.67,140.78) --
	(107.14,140.49) --
	(107.61,140.38) --
	(108.08,140.27) --
	(108.55,140.10) --
	(109.02,139.87) --
	(109.50,139.92) --
	(109.97,139.70) --
	(110.44,139.35) --
	(110.91,139.07) --
	(111.38,138.61) --
	(111.85,138.61) --
	(112.32,138.56) --
	(112.79,138.61) --
	(113.26,138.44) --
	(113.74,138.27) --
	(114.21,138.04) --
	(114.68,138.22) --
	(115.15,138.33) --
	(115.62,137.87) --
	(116.09,137.99) --
	(116.56,137.65) --
	(117.03,137.59) --
	(117.51,137.48) --
	(117.98,137.59) --
	(118.45,137.42) --
	(118.92,137.36) --
	(119.39,136.96) --
	(119.86,136.68) --
	(120.33,136.68) --
	(120.80,136.62) --
	(121.27,136.34) --
	(121.75,135.94) --
	(122.22,136.05) --
	(122.69,135.71) --
	(123.16,135.65) --
	(123.63,135.71) --
	(124.10,135.60) --
	(124.57,135.54) --
	(125.04,135.48) --
	(125.51,135.54) --
	(125.99,135.48) --
	(126.46,135.43) --
	(126.93,135.25) --
	(127.40,135.20) --
	(127.87,135.14) --
	(128.34,135.14) --
	(128.81,135.03) --
	(129.28,134.80) --
	(129.75,134.80) --
	(130.23,134.74) --
	(130.70,134.51) --
	(131.17,134.34) --
	(131.64,134.12) --
	(132.11,134.23) --
	(132.58,134.06);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,127.83) rectangle (137.69,197.70);
\end{scope}
\begin{scope}
\path[clip] ( 54.44,197.70) rectangle (137.69,205.65);

\path[] ( 54.44,197.70) rectangle (137.69,205.65);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 69.67,199.40) {T=250, K=3, c=1};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,197.70) rectangle (137.69,205.65);
\end{scope}
\begin{scope}
\path[clip] (137.69,127.83) rectangle (220.94,197.70);
\definecolor[named]{drawColor}{rgb}{0.83,0.83,0.83}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.45,156.69) --
	(218.97,156.69);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.16,151.90) --
	(145.63,152.76) --
	(146.10,151.40) --
	(146.57,152.26) --
	(147.05,152.63) --
	(147.52,153.00) --
	(147.99,152.63) --
	(148.46,154.23) --
	(148.93,154.60) --
	(149.40,155.33) --
	(149.87,152.76) --
	(150.34,152.88) --
	(150.81,152.51) --
	(151.29,152.39) --
	(151.76,152.39) --
	(152.23,151.90) --
	(152.70,152.02) --
	(153.17,151.28) --
	(153.64,149.32) --
	(154.11,148.95) --
	(154.58,149.68) --
	(155.05,148.46) --
	(155.53,148.09) --
	(156.00,148.33) --
	(156.47,147.47) --
	(156.94,148.09) --
	(157.41,147.97) --
	(157.88,146.86) --
	(158.35,145.75) --
	(158.82,145.75) --
	(159.29,145.75) --
	(159.77,146.00) --
	(160.24,146.00) --
	(160.71,145.75) --
	(161.18,144.65) --
	(161.65,144.28) --
	(162.12,143.91) --
	(162.59,142.81) --
	(163.06,142.19) --
	(163.53,142.07) --
	(164.01,142.07) --
	(164.48,142.07) --
	(164.95,142.44) --
	(165.42,141.82) --
	(165.89,141.58) --
	(166.36,142.19) --
	(166.83,140.84) --
	(167.30,141.70) --
	(167.77,141.46) --
	(168.25,140.23) --
	(168.72,140.35) --
	(169.19,140.47) --
	(169.66,140.47) --
	(170.13,140.84) --
	(170.60,140.10) --
	(171.07,139.98) --
	(171.54,140.10) --
	(172.02,140.35) --
	(172.49,139.49) --
	(172.96,138.39) --
	(173.43,138.02) --
	(173.90,137.53) --
	(174.37,137.77) --
	(174.84,137.40) --
	(175.31,136.91) --
	(175.78,136.54) --
	(176.26,136.91) --
	(176.73,136.79) --
	(177.20,136.91) --
	(177.67,137.40) --
	(178.14,137.40) --
	(178.61,137.65) --
	(179.08,137.28) --
	(179.55,137.16) --
	(180.02,137.40) --
	(180.50,137.53) --
	(180.97,136.79) --
	(181.44,136.30) --
	(181.91,136.05) --
	(182.38,136.30) --
	(182.85,136.05) --
	(183.32,135.68) --
	(183.79,135.32) --
	(184.26,135.44) --
	(184.74,135.44) --
	(185.21,135.19) --
	(185.68,135.56) --
	(186.15,135.32) --
	(186.62,135.68) --
	(187.09,135.68) --
	(187.56,135.81) --
	(188.03,135.68) --
	(188.50,135.44) --
	(188.98,135.68) --
	(189.45,135.32) --
	(189.92,135.07) --
	(190.39,134.82) --
	(190.86,134.70) --
	(191.33,134.82) --
	(191.80,134.82) --
	(192.27,134.33) --
	(192.74,134.95) --
	(193.22,134.58) --
	(193.69,134.33) --
	(194.16,134.58) --
	(194.63,134.58) --
	(195.10,134.33) --
	(195.57,134.09) --
	(196.04,134.33) --
	(196.51,134.33) --
	(196.99,133.96) --
	(197.46,133.47) --
	(197.93,133.23) --
	(198.40,133.23) --
	(198.87,133.47) --
	(199.34,133.35) --
	(199.81,133.23) --
	(200.28,133.35) --
	(200.75,133.47) --
	(201.23,132.98) --
	(201.70,132.86) --
	(202.17,132.86) --
	(202.64,132.86) --
	(203.11,132.86) --
	(203.58,132.86) --
	(204.05,132.86) --
	(204.52,132.61) --
	(204.99,132.49) --
	(205.47,132.74) --
	(205.94,132.61) --
	(206.41,132.37) --
	(206.88,132.37) --
	(207.35,132.24) --
	(207.82,132.37) --
	(208.29,132.37) --
	(208.76,132.49) --
	(209.23,132.37) --
	(209.71,132.37) --
	(210.18,132.37) --
	(210.65,132.24) --
	(211.12,132.37) --
	(211.59,132.24) --
	(212.06,132.24) --
	(212.53,132.24) --
	(213.00,132.24) --
	(213.47,132.24) --
	(213.95,132.24) --
	(214.42,132.24) --
	(214.89,132.12) --
	(215.36,132.12) --
	(215.83,132.12);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.69,127.83) rectangle (220.94,197.70);
\end{scope}
\begin{scope}
\path[clip] (137.69,197.70) rectangle (220.94,205.65);

\path[] (137.69,197.70) rectangle (220.94,205.65);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.66] at (147.24,199.40) {T=250, K=T/10, c=1};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.69,197.70) rectangle (220.94,205.65);
\end{scope}
\begin{scope}
\path[clip] (220.94,127.83) rectangle (304.19,197.70);
\definecolor[named]{drawColor}{rgb}{0.83,0.83,0.83}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.70,156.69) --
	(302.22,156.69);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.41,162.09) --
	(228.88,160.49) --
	(229.35,160.62) --
	(229.82,160.00) --
	(230.29,161.11) --
	(230.77,160.00) --
	(231.24,158.53) --
	(231.71,159.14) --
	(232.18,159.88) --
	(232.65,157.79) --
	(233.12,157.91) --
	(233.59,159.14) --
	(234.06,158.77) --
	(234.53,157.79) --
	(235.01,158.53) --
	(235.48,159.39) --
	(235.95,159.26) --
	(236.42,158.53) --
	(236.89,158.65) --
	(237.36,159.39) --
	(237.83,159.88) --
	(238.30,159.14) --
	(238.77,157.30) --
	(239.25,156.93) --
	(239.72,156.44) --
	(240.19,156.56) --
	(240.66,157.18) --
	(241.13,157.05) --
	(241.60,158.16) --
	(242.07,157.18) --
	(242.54,157.55) --
	(243.01,156.56) --
	(243.49,157.05) --
	(243.96,157.05) --
	(244.43,156.32) --
	(244.90,156.56) --
	(245.37,155.83) --
	(245.84,156.93) --
	(246.31,157.30) --
	(246.78,157.30) --
	(247.26,156.44) --
	(247.73,156.81) --
	(248.20,157.67) --
	(248.67,157.30) --
	(249.14,157.30) --
	(249.61,156.93) --
	(250.08,156.81) --
	(250.55,156.69) --
	(251.02,157.05) --
	(251.50,156.56) --
	(251.97,156.32) --
	(252.44,155.83) --
	(252.91,156.69) --
	(253.38,156.07) --
	(253.85,156.32) --
	(254.32,156.07) --
	(254.79,156.19) --
	(255.26,156.44) --
	(255.74,155.83) --
	(256.21,154.72) --
	(256.68,155.09) --
	(257.15,155.09) --
	(257.62,155.83) --
	(258.09,155.95) --
	(258.56,154.84) --
	(259.03,155.09) --
	(259.50,156.19) --
	(259.98,155.46) --
	(260.45,155.46) --
	(260.92,153.61) --
	(261.39,153.74) --
	(261.86,154.47) --
	(262.33,154.11) --
	(262.80,153.86) --
	(263.27,154.11) --
	(263.74,154.23) --
	(264.22,154.47) --
	(264.69,154.72) --
	(265.16,153.74) --
	(265.63,154.84) --
	(266.10,154.23) --
	(266.57,154.84) --
	(267.04,154.11) --
	(267.51,153.74) --
	(267.98,153.74) --
	(268.46,154.47) --
	(268.93,155.21) --
	(269.40,154.47) --
	(269.87,154.35) --
	(270.34,154.11) --
	(270.81,153.37) --
	(271.28,152.76) --
	(271.75,153.12) --
	(272.23,152.88) --
	(272.70,152.88) --
	(273.17,153.00) --
	(273.64,152.51) --
	(274.11,152.88) --
	(274.58,151.90) --
	(275.05,151.90) --
	(275.52,151.28) --
	(275.99,151.53) --
	(276.47,151.40) --
	(276.94,151.16) --
	(277.41,151.16) --
	(277.88,151.04) --
	(278.35,150.67) --
	(278.82,151.40) --
	(279.29,150.79) --
	(279.76,150.91) --
	(280.23,150.79) --
	(280.71,150.30) --
	(281.18,150.18) --
	(281.65,150.42) --
	(282.12,149.81) --
	(282.59,149.81) --
	(283.06,149.44) --
	(283.53,149.32) --
	(284.00,149.19) --
	(284.47,148.70) --
	(284.95,148.70) --
	(285.42,148.95) --
	(285.89,149.07) --
	(286.36,149.44) --
	(286.83,149.68) --
	(287.30,149.07) --
	(287.77,149.19) --
	(288.24,149.32) --
	(288.71,148.58) --
	(289.19,148.83) --
	(289.66,149.32) --
	(290.13,148.09) --
	(290.60,148.09) --
	(291.07,147.97) --
	(291.54,148.09) --
	(292.01,148.09) --
	(292.48,147.47) --
	(292.96,148.09) --
	(293.43,147.60) --
	(293.90,147.60) --
	(294.37,147.35) --
	(294.84,147.47) --
	(295.31,146.86) --
	(295.78,146.86) --
	(296.25,146.98) --
	(296.72,145.63) --
	(297.20,145.51) --
	(297.67,145.26) --
	(298.14,145.02) --
	(298.61,145.14) --
	(299.08,146.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.94,127.83) rectangle (304.19,197.70);
\end{scope}
\begin{scope}
\path[clip] (220.94,197.70) rectangle (304.19,205.65);

\path[] (220.94,197.70) rectangle (304.19,205.65);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.66] at (236.17,199.40) {T=250, K=3, c=2};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.94,197.70) rectangle (304.19,205.65);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.44,132.12) -- (393.13,132.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.44,144.40) -- (393.13,144.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.44,156.69) -- (393.13,156.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.44,168.97) -- (393.13,168.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.44,181.25) -- (393.13,181.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.44,193.53) -- (393.13,193.53);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.96] at (398.82,128.82) {0.00};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.96] at (398.82,141.10) {0.05};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.96] at (398.82,153.38) {0.10};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.96] at (398.82,165.66) {0.15};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.96] at (398.82,177.94) {0.20};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.96] at (398.82,190.23) {0.25};
\end{scope}
\begin{scope}
\path[clip] (304.19,127.83) rectangle (387.44,197.70);
\definecolor[named]{drawColor}{rgb}{0.83,0.83,0.83}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (306.95,156.69) --
	(385.47,156.69);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (311.66,167.62) --
	(312.13,167.25) --
	(312.60,169.34) --
	(313.07,171.91) --
	(313.54,170.69) --
	(314.01,171.67) --
	(314.49,171.18) --
	(314.96,172.41) --
	(315.43,173.02) --
	(315.90,173.76) --
	(316.37,173.76) --
	(316.84,175.23) --
	(317.31,175.11) --
	(317.78,176.34) --
	(318.25,176.21) --
	(318.73,176.09) --
	(319.20,176.09) --
	(319.67,177.07) --
	(320.14,177.44) --
	(320.61,178.06) --
	(321.08,178.18) --
	(321.55,176.83) --
	(322.02,176.95) --
	(322.50,178.55) --
	(322.97,179.90) --
	(323.44,176.70) --
	(323.91,178.67) --
	(324.38,179.16) --
	(324.85,178.67) --
	(325.32,178.42) --
	(325.79,178.67) --
	(326.26,179.53) --
	(326.74,180.76) --
	(327.21,182.11) --
	(327.68,181.00) --
	(328.15,182.23) --
	(328.62,182.23) --
	(329.09,182.11) --
	(329.56,181.86) --
	(330.03,181.86) --
	(330.50,181.25) --
	(330.98,181.62) --
	(331.45,181.13) --
	(331.92,181.13) --
	(332.39,181.86) --
	(332.86,181.13) --
	(333.33,181.74) --
	(333.80,180.51) --
	(334.27,179.16) --
	(334.74,179.41) --
	(335.22,179.90) --
	(335.69,181.62) --
	(336.16,180.39) --
	(336.63,179.90) --
	(337.10,180.51) --
	(337.57,180.27) --
	(338.04,178.92) --
	(338.51,178.30) --
	(338.98,179.41) --
	(339.46,181.13) --
	(339.93,180.27) --
	(340.40,179.78) --
	(340.87,179.04) --
	(341.34,180.39) --
	(341.81,180.27) --
	(342.28,180.51) --
	(342.75,180.02) --
	(343.22,178.55) --
	(343.70,177.69) --
	(344.17,177.56) --
	(344.64,177.07) --
	(345.11,177.20) --
	(345.58,178.42) --
	(346.05,177.44) --
	(346.52,176.95) --
	(346.99,177.32) --
	(347.47,176.58) --
	(347.94,177.32) --
	(348.41,177.20) --
	(348.88,176.46) --
	(349.35,175.85) --
	(349.82,176.09) --
	(350.29,176.95) --
	(350.76,175.72) --
	(351.23,175.97) --
	(351.71,176.95) --
	(352.18,175.85) --
	(352.65,176.09) --
	(353.12,175.97) --
	(353.59,175.85) --
	(354.06,176.34) --
	(354.53,176.83) --
	(355.00,176.70) --
	(355.47,176.09) --
	(355.95,175.11) --
	(356.42,175.35) --
	(356.89,174.13) --
	(357.36,174.74) --
	(357.83,174.25) --
	(358.30,172.65) --
	(358.77,174.00) --
	(359.24,173.27) --
	(359.71,172.65) --
	(360.19,171.91) --
	(360.66,171.55) --
	(361.13,172.04) --
	(361.60,172.53) --
	(362.07,171.30) --
	(362.54,169.95) --
	(363.01,169.83) --
	(363.48,169.83) --
	(363.95,168.97) --
	(364.43,170.32) --
	(364.90,170.07) --
	(365.37,169.70) --
	(365.84,169.58) --
	(366.31,169.95) --
	(366.78,169.83) --
	(367.25,169.70) --
	(367.72,168.60) --
	(368.19,167.74) --
	(368.67,166.51) --
	(369.14,166.63) --
	(369.61,166.76) --
	(370.08,166.02) --
	(370.55,165.53) --
	(371.02,165.04) --
	(371.49,164.42) --
	(371.96,163.81) --
	(372.44,164.30) --
	(372.91,164.55) --
	(373.38,164.55) --
	(373.85,163.69) --
	(374.32,163.07) --
	(374.79,161.97) --
	(375.26,162.21) --
	(375.73,161.11) --
	(376.20,161.11) --
	(376.68,160.37) --
	(377.15,160.25) --
	(377.62,160.37) --
	(378.09,159.39) --
	(378.56,159.88) --
	(379.03,159.39) --
	(379.50,157.42) --
	(379.97,157.30) --
	(380.44,157.42) --
	(380.92,155.46) --
	(381.39,154.35) --
	(381.86,154.60) --
	(382.33,153.74);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (304.19,127.83) rectangle (387.44,197.70);
\end{scope}
\begin{scope}
\path[clip] (304.19,197.70) rectangle (387.44,205.65);

\path[] (304.19,197.70) rectangle (387.44,205.65);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.66] at (313.74,199.40) {T=250, K=T/10, c=2};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (304.19,197.70) rectangle (387.44,205.65);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 57.20,283.46) -- ( 57.20,289.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 80.76,283.46) -- ( 80.76,289.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.31,283.46) -- (104.31,289.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.87,283.46) -- (127.87,289.15);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,209.94) -- ( 48.75,209.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,222.22) -- ( 48.75,222.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,234.50) -- ( 48.75,234.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,246.78) -- ( 48.75,246.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,259.07) -- ( 48.75,259.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,271.35) -- ( 48.75,271.35);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06,206.63) {0.00};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06,218.91) {0.05};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06,231.20) {0.10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06,243.48) {0.15};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06,255.76) {0.20};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06,268.04) {0.25};
\end{scope}
\begin{scope}
\path[clip] ( 54.44,205.65) rectangle (137.69,275.51);
\definecolor[named]{drawColor}{rgb}{0.83,0.83,0.83}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 57.20,234.50) --
	(135.72,234.50);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.98,233.38) --
	( 70.16,233.69) --
	( 71.33,232.64) --
	( 72.51,232.40) --
	( 73.69,231.72) --
	( 74.87,231.17) --
	( 76.05,230.37) --
	( 77.22,229.51) --
	( 78.40,229.14) --
	( 79.58,228.72) --
	( 80.76,228.53) --
	( 81.93,228.10) --
	( 83.11,228.22) --
	( 84.29,227.49) --
	( 85.47,226.81) --
	( 86.65,226.20) --
	( 87.82,225.40) --
	( 89.00,225.46) --
	( 90.18,225.03) --
	( 91.36,224.60) --
	( 92.53,223.99) --
	( 93.71,223.32) --
	( 94.89,222.82) --
	( 96.07,222.33) --
	( 97.25,222.70) --
	( 98.42,222.09) --
	( 99.60,221.72) --
	(100.78,220.92) --
	(101.96,220.55) --
	(103.14,220.12) --
	(104.31,220.25) --
	(105.49,219.51) --
	(106.67,219.20) --
	(107.85,218.65) --
	(109.02,217.73) --
	(110.20,218.10) --
	(111.38,217.42) --
	(112.56,217.06) --
	(113.74,216.69) --
	(114.91,216.81) --
	(116.09,216.81) --
	(117.27,216.38) --
	(118.45,216.01) --
	(119.63,215.64) --
	(120.80,215.28) --
	(121.98,215.22) --
	(123.16,215.03) --
	(124.34,214.79) --
	(125.51,214.23) --
	(126.69,213.93) --
	(127.87,213.74);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,205.65) rectangle (137.69,275.51);
\end{scope}
\begin{scope}
\path[clip] ( 54.44,275.51) rectangle (137.69,283.46);

\path[] ( 54.44,275.51) rectangle (137.69,283.46);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 69.67,277.22) {T=100, K=3, c=1};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,275.51) rectangle (137.69,283.46);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.45,283.46) -- (140.45,289.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (164.01,283.46) -- (164.01,289.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.56,283.46) -- (187.56,289.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.12,283.46) -- (211.12,289.15);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (140.45,294.85) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (164.01,294.85) {0.2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (187.56,294.85) {0.4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (211.12,294.85) {0.6};
\end{scope}
\begin{scope}
\path[clip] (137.69,205.65) rectangle (220.94,275.51);
\definecolor[named]{drawColor}{rgb}{0.83,0.83,0.83}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.45,234.50) --
	(218.97,234.50);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (152.23,230.78) --
	(153.41,229.22) --
	(154.58,228.02) --
	(155.76,227.06) --
	(156.94,227.54) --
	(158.12,225.99) --
	(159.29,225.03) --
	(160.47,224.19) --
	(161.65,224.79) --
	(162.83,224.07) --
	(164.01,223.11) --
	(165.18,222.51) --
	(166.36,221.32) --
	(167.54,221.56) --
	(168.72,221.08) --
	(169.90,220.96) --
	(171.07,220.84) --
	(172.25,220.12) --
	(173.43,219.88) --
	(174.61,219.88) --
	(175.78,219.40) --
	(176.96,218.92) --
	(178.14,217.36) --
	(179.32,217.60) --
	(180.50,217.36) --
	(181.67,217.00) --
	(182.85,216.41) --
	(184.03,215.45) --
	(185.21,215.45) --
	(186.38,214.85) --
	(187.56,215.45) --
	(188.74,215.21) --
	(189.92,214.85) --
	(191.10,214.73) --
	(192.27,214.13) --
	(193.45,214.25) --
	(194.63,214.61) --
	(195.81,213.77) --
	(196.99,213.65) --
	(198.16,213.65) --
	(199.34,213.41) --
	(200.52,212.93) --
	(201.70,212.57) --
	(202.87,212.45) --
	(204.05,212.45) --
	(205.23,211.85) --
	(206.41,211.97) --
	(207.59,211.38) --
	(208.76,211.49) --
	(209.94,211.38) --
	(211.12,211.26);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.69,205.65) rectangle (220.94,275.51);
\end{scope}
\begin{scope}
\path[clip] (137.69,275.51) rectangle (220.94,283.46);

\path[] (137.69,275.51) rectangle (220.94,283.46);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.66] at (147.24,277.22) {T=100, K=T/10, c=1};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.69,275.51) rectangle (220.94,283.46);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.70,283.46) -- (223.70,289.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (247.26,283.46) -- (247.26,289.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (270.81,283.46) -- (270.81,289.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (294.37,283.46) -- (294.37,289.15);
\end{scope}
\begin{scope}
\path[clip] (220.94,205.65) rectangle (304.19,275.51);
\definecolor[named]{drawColor}{rgb}{0.83,0.83,0.83}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.70,234.50) --
	(302.22,234.50);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.48,244.20) --
	(236.65,239.29) --
	(237.83,237.69) --
	(239.01,238.43) --
	(240.19,237.57) --
	(241.37,237.94) --
	(242.54,238.92) --
	(243.72,235.98) --
	(244.90,234.62) --
	(246.08,234.62) --
	(247.26,235.85) --
	(248.43,234.38) --
	(249.61,234.99) --
	(250.79,235.61) --
	(251.97,235.48) --
	(253.14,236.10) --
	(254.32,234.01) --
	(255.50,234.13) --
	(256.68,233.89) --
	(257.86,233.27) --
	(259.03,233.15) --
	(260.21,232.05) --
	(261.39,232.41) --
	(262.57,232.90) --
	(263.74,231.31) --
	(264.92,231.31) --
	(266.10,231.43) --
	(267.28,230.94) --
	(268.46,230.33) --
	(269.63,231.68) --
	(270.81,231.06) --
	(271.99,231.31) --
	(273.17,231.06) --
	(274.35,230.08) --
	(275.52,229.34) --
	(276.70,229.71) --
	(277.88,228.36) --
	(279.06,228.73) --
	(280.23,227.75) --
	(281.41,228.61) --
	(282.59,226.89) --
	(283.77,226.76) --
	(284.95,226.40) --
	(286.12,225.78) --
	(287.30,225.17) --
	(288.48,225.41) --
	(289.66,225.04) --
	(290.83,224.68) --
	(292.01,224.43) --
	(293.19,224.31) --
	(294.37,223.94);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.94,205.65) rectangle (304.19,275.51);
\end{scope}
\begin{scope}
\path[clip] (220.94,275.51) rectangle (304.19,283.46);

\path[] (220.94,275.51) rectangle (304.19,283.46);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.66] at (236.17,277.22) {T=100, K=3, c=2};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.94,275.51) rectangle (304.19,283.46);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (306.95,283.46) -- (306.95,289.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (330.50,283.46) -- (330.50,289.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.06,283.46) -- (354.06,289.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.62,283.46) -- (377.62,289.15);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (306.95,294.85) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (330.50,294.85) {0.2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (354.06,294.85) {0.4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (377.62,294.85) {0.6};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.44,209.94) -- (393.13,209.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.44,222.22) -- (393.13,222.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.44,234.50) -- (393.13,234.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.44,246.78) -- (393.13,246.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.44,259.07) -- (393.13,259.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.44,271.35) -- (393.13,271.35);
\end{scope}
\begin{scope}
\path[clip] (304.19,205.65) rectangle (387.44,275.51);
\definecolor[named]{drawColor}{rgb}{0.83,0.83,0.83}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (306.95,234.50) --
	(385.47,234.50);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (318.73,245.19) --
	(319.90,243.84) --
	(321.08,246.54) --
	(322.26,247.27) --
	(323.44,246.78) --
	(324.62,247.15) --
	(325.79,246.66) --
	(326.97,246.42) --
	(328.15,245.56) --
	(329.33,245.92) --
	(330.50,246.91) --
	(331.68,245.80) --
	(332.86,244.70) --
	(334.04,245.06) --
	(335.22,246.05) --
	(336.39,246.17) --
	(337.57,244.94) --
	(338.75,244.45) --
	(339.93,246.17) --
	(341.10,244.45) --
	(342.28,243.47) --
	(343.46,243.34) --
	(344.64,241.75) --
	(345.82,241.50) --
	(346.99,241.38) --
	(348.17,242.48) --
	(349.35,241.87) --
	(350.53,240.77) --
	(351.71,240.77) --
	(352.88,240.40) --
	(354.06,239.91) --
	(355.24,239.29) --
	(356.42,237.82) --
	(357.59,238.68) --
	(358.77,238.31) --
	(359.95,237.94) --
	(361.13,239.05) --
	(362.31,238.06) --
	(363.48,236.47) --
	(364.66,235.98) --
	(365.84,236.47) --
	(367.02,234.62) --
	(368.19,233.64) --
	(369.37,232.05) --
	(370.55,231.68) --
	(371.73,232.05) --
	(372.91,231.92) --
	(374.08,232.05) --
	(375.26,231.92) --
	(376.44,230.20) --
	(377.62,229.83);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (304.19,205.65) rectangle (387.44,275.51);
\end{scope}
\begin{scope}
\path[clip] (304.19,275.51) rectangle (387.44,283.46);

\path[] (304.19,275.51) rectangle (387.44,283.46);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.66] at (313.74,277.22) {T=100, K=T/10, c=2};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,325.21);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (304.19,275.51) rectangle (387.44,283.46);
\end{scope}
\end{tikzpicture}

### 2017-04-21 floats/mc-ftest.tex
Add TeX files with simulation and empirical results to repo
I've decided to add _a few_ generated files to the main repository to
make my life easier; namely any graphics or tables that are included
in the main paper.

\begin{table}[tb]
 % latex table generated in R 3.0.2 by xtable 1.7-0 package
% Thu Mar 27 13:12:32 2014
\begin{tabularx}{\textwidth}{llCCC}
  \toprule &&&
 \multicolumn{2}{c}{Conditional rejection probability (size)} \\
 \cmidrule(l){4-5} $K_1$ & $K_2$ & $T$ & $| \theta_2 |_2 = 0$ & $| \theta_2 |_2 = 1$ \\ 
  \midrule $2$ & $3$ & $100$ & $0.104$ & $0.485$ \\ 
   &  & $250$ & $0.102$ & $0.528$ \\ 
   &  & $500$ & $0.096$ & $0.503$ \\ 
  $T/50$ & $T/10$ & $100$ & $0.106$ & $0.701$ \\ 
   &  & $250$ & $0.108$ & $0.904$ \\ 
   &  & $500$ & $0.104$ & $0.989$ \\ 
   \bottomrule \end{tabularx}
 \caption{Simulated rejection probabilities for the $F$-test under
the null hypothesis that the benchmark model will forecast better,
$\E_T \oosB \leq 0$. Nominal size is 10\% and values greater than
10\% indicate that the test rejects the benchmark model too often.
See Section~\ref{sec:simulation-design} for a discussion of the
simulation design.}
\label{fig:ftest}
\end{table}

### 2017-04-21 floats/mc-mccrackensize-rec.tex
Add TeX files with simulation and empirical results to repo
I've decided to add _a few_ generated files to the main repository to
make my life easier; namely any graphics or tables that are included
in the main paper.

% Created by tikzDevice version 0.6.2-92-0ad2792 on 2014-03-27 13:56:00
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (361.35,397.48);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);

\path[] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (184.81, 12.04) {$P/T$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at ( 14.29,198.90) {Rejection Probability};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44, 57.82) -- ( 48.75, 57.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44, 72.33) -- ( 48.75, 72.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44, 86.84) -- ( 48.75, 86.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,101.35) -- ( 48.75,101.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,115.86) -- ( 48.75,115.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,130.37) -- ( 48.75,130.37);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06, 54.51) {0.10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06, 69.02) {0.15};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06, 83.53) {0.20};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06, 98.04) {0.25};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06,112.55) {0.30};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06,127.06) {0.35};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.76, 50.02) -- ( 58.76, 44.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.65, 50.02) -- ( 95.65, 44.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (132.54, 50.02) -- (132.54, 44.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.42, 50.02) -- (169.42, 44.32);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 58.76, 32.02) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 95.65, 32.02) {0.2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (132.54, 32.02) {0.4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (169.42, 32.02) {0.6};
\end{scope}
\begin{scope}
\path[clip] ( 54.44, 50.02) rectangle (184.81,143.97);
\definecolor[named]{drawColor}{rgb}{0.83,0.83,0.83}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.76, 57.82) --
	(181.72, 57.82);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 62.45, 59.12) --
	( 62.82, 60.14) --
	( 63.19, 60.86) --
	( 63.56, 60.14) --
	( 63.92, 59.70) --
	( 64.29, 61.88) --
	( 64.66, 62.46) --
	( 65.03, 61.30) --
	( 65.40, 60.14) --
	( 65.77, 60.57) --
	( 66.14, 60.86) --
	( 66.51, 60.57) --
	( 66.88, 60.86) --
	( 67.24, 60.43) --
	( 67.61, 60.28) --
	( 67.98, 61.01) --
	( 68.35, 60.28) --
	( 68.72, 59.56) --
	( 69.09, 61.88) --
	( 69.46, 62.46) --
	( 69.83, 61.30) --
	( 70.20, 63.04) --
	( 70.56, 62.75) --
	( 70.93, 63.33) --
	( 71.30, 63.18) --
	( 71.67, 64.64) --
	( 72.04, 64.06) --
	( 72.41, 64.20) --
	( 72.78, 64.78) --
	( 73.15, 64.64) --
	( 73.52, 64.93) --
	( 73.88, 65.51) --
	( 74.25, 65.36) --
	( 74.62, 65.94) --
	( 74.99, 65.94) --
	( 75.36, 65.36) --
	( 75.73, 65.07) --
	( 76.10, 63.77) --
	( 76.47, 63.77) --
	( 76.84, 64.35) --
	( 77.20, 64.49) --
	( 77.57, 63.62) --
	( 77.94, 62.75) --
	( 78.31, 62.89) --
	( 78.68, 63.62) --
	( 79.05, 63.77) --
	( 79.42, 64.06) --
	( 79.79, 64.49) --
	( 80.16, 63.48) --
	( 80.52, 62.46) --
	( 80.89, 62.75) --
	( 81.26, 62.17) --
	( 81.63, 61.30) --
	( 82.00, 61.44) --
	( 82.37, 61.44) --
	( 82.74, 61.30) --
	( 83.11, 61.59) --
	( 83.48, 61.88) --
	( 83.84, 62.31) --
	( 84.21, 62.31) --
	( 84.58, 62.02) --
	( 84.95, 63.04) --
	( 85.32, 64.49) --
	( 85.69, 63.18) --
	( 86.06, 62.75) --
	( 86.43, 63.91) --
	( 86.79, 63.33) --
	( 87.16, 63.62) --
	( 87.53, 63.48) --
	( 87.90, 63.48) --
	( 88.27, 63.18) --
	( 88.64, 63.04) --
	( 89.01, 64.20) --
	( 89.38, 64.20) --
	( 89.75, 64.78) --
	( 90.11, 64.20) --
	( 90.48, 63.33) --
	( 90.85, 63.04) --
	( 91.22, 62.60) --
	( 91.59, 63.62) --
	( 91.96, 63.04) --
	( 92.33, 62.89) --
	( 92.70, 62.75) --
	( 93.07, 62.89) --
	( 93.43, 63.04) --
	( 93.80, 62.31) --
	( 94.17, 62.46) --
	( 94.54, 62.17) --
	( 94.91, 62.31) --
	( 95.28, 62.46) --
	( 95.65, 63.04) --
	( 96.02, 64.35) --
	( 96.39, 63.91) --
	( 96.75, 64.20) --
	( 97.12, 62.31) --
	( 97.49, 62.17) --
	( 97.86, 61.73) --
	( 98.23, 62.31) --
	( 98.60, 62.46) --
	( 98.97, 61.44) --
	( 99.34, 62.02) --
	( 99.71, 61.88) --
	(100.07, 62.31) --
	(100.44, 61.73) --
	(100.81, 61.44) --
	(101.18, 60.57) --
	(101.55, 60.86) --
	(101.92, 60.28) --
	(102.29, 60.28) --
	(102.66, 60.72) --
	(103.03, 61.44) --
	(103.39, 60.72) --
	(103.76, 60.72) --
	(104.13, 61.15) --
	(104.50, 61.44) --
	(104.87, 60.28) --
	(105.24, 59.99) --
	(105.61, 59.99) --
	(105.98, 60.86) --
	(106.35, 60.28) --
	(106.71, 61.01) --
	(107.08, 60.86) --
	(107.45, 59.70) --
	(107.82, 60.14) --
	(108.19, 60.14) --
	(108.56, 59.41) --
	(108.93, 59.12) --
	(109.30, 58.54) --
	(109.67, 59.12) --
	(110.03, 59.85) --
	(110.40, 59.70) --
	(110.77, 59.27) --
	(111.14, 59.41) --
	(111.51, 58.98) --
	(111.88, 58.54) --
	(112.25, 58.40) --
	(112.62, 58.54) --
	(112.99, 58.25) --
	(113.35, 59.70) --
	(113.72, 59.70) --
	(114.09, 59.85) --
	(114.46, 58.98) --
	(114.83, 58.83) --
	(115.20, 59.41) --
	(115.57, 58.69) --
	(115.94, 58.83) --
	(116.31, 58.54) --
	(116.67, 57.67) --
	(117.04, 58.11) --
	(117.41, 57.53) --
	(117.78, 58.40) --
	(118.15, 57.96) --
	(118.52, 58.25) --
	(118.89, 57.96) --
	(119.26, 58.25) --
	(119.63, 58.54) --
	(119.99, 59.70) --
	(120.36, 59.12) --
	(120.73, 59.41) --
	(121.10, 59.85) --
	(121.47, 59.56) --
	(121.84, 59.70) --
	(122.21, 58.83) --
	(122.58, 58.98) --
	(122.95, 59.12) --
	(123.31, 58.54) --
	(123.68, 59.27) --
	(124.05, 59.27) --
	(124.42, 58.69) --
	(124.79, 58.69) --
	(125.16, 58.40) --
	(125.53, 58.54) --
	(125.90, 57.82) --
	(126.27, 58.40) --
	(126.63, 58.69) --
	(127.00, 59.27) --
	(127.37, 58.83) --
	(127.74, 59.27) --
	(128.11, 59.41) --
	(128.48, 59.56) --
	(128.85, 59.12) --
	(129.22, 59.12) --
	(129.59, 58.25) --
	(129.95, 58.40) --
	(130.32, 58.69) --
	(130.69, 58.40) --
	(131.06, 58.83) --
	(131.43, 58.69) --
	(131.80, 58.83) --
	(132.17, 58.83) --
	(132.54, 59.27) --
	(132.91, 59.27) --
	(133.27, 58.69) --
	(133.64, 58.69) --
	(134.01, 59.41) --
	(134.38, 58.98) --
	(134.75, 58.83) --
	(135.12, 59.70) --
	(135.49, 59.27) --
	(135.86, 59.12) --
	(136.23, 58.54) --
	(136.59, 59.56) --
	(136.96, 58.98) --
	(137.33, 58.98) --
	(137.70, 59.56) --
	(138.07, 59.27) --
	(138.44, 59.56) --
	(138.81, 58.69) --
	(139.18, 59.27) --
	(139.55, 59.12) --
	(139.91, 58.83) --
	(140.28, 58.11) --
	(140.65, 57.82) --
	(141.02, 58.54) --
	(141.39, 58.69) --
	(141.76, 58.40) --
	(142.13, 57.82) --
	(142.50, 58.40) --
	(142.87, 58.11) --
	(143.23, 57.82) --
	(143.60, 57.53) --
	(143.97, 58.40) --
	(144.34, 58.54) --
	(144.71, 58.54) --
	(145.08, 58.54) --
	(145.45, 58.83) --
	(145.82, 57.96) --
	(146.19, 58.54) --
	(146.55, 58.40) --
	(146.92, 58.54) --
	(147.29, 58.69) --
	(147.66, 58.40) --
	(148.03, 59.12) --
	(148.40, 58.25) --
	(148.77, 58.40) --
	(149.14, 57.67) --
	(149.51, 57.96) --
	(149.87, 57.67) --
	(150.24, 56.51) --
	(150.61, 57.82) --
	(150.98, 57.96) --
	(151.35, 58.11) --
	(151.72, 57.67) --
	(152.09, 57.96) --
	(152.46, 58.11) --
	(152.83, 58.25) --
	(153.19, 57.53) --
	(153.56, 57.82) --
	(153.93, 57.24) --
	(154.30, 57.82) --
	(154.67, 57.82) --
	(155.04, 57.53) --
	(155.41, 56.51) --
	(155.78, 56.95) --
	(156.15, 57.96) --
	(156.51, 58.11) --
	(156.88, 58.11) --
	(157.25, 58.25) --
	(157.62, 58.40) --
	(157.99, 58.25) --
	(158.36, 58.25) --
	(158.73, 58.83) --
	(159.10, 57.96) --
	(159.47, 57.38) --
	(159.83, 57.24) --
	(160.20, 56.66) --
	(160.57, 56.80) --
	(160.94, 56.22) --
	(161.31, 56.66) --
	(161.68, 57.09) --
	(162.05, 56.95) --
	(162.42, 56.51) --
	(162.78, 56.66) --
	(163.15, 55.78) --
	(163.52, 55.93) --
	(163.89, 55.78) --
	(164.26, 56.22) --
	(164.63, 56.51) --
	(165.00, 56.66) --
	(165.37, 57.38) --
	(165.74, 57.24) --
	(166.10, 56.66) --
	(166.47, 56.80) --
	(166.84, 56.80) --
	(167.21, 56.80) --
	(167.58, 56.66) --
	(167.95, 56.37) --
	(168.32, 56.22) --
	(168.69, 56.07) --
	(169.06, 57.24) --
	(169.42, 56.66) --
	(169.79, 57.67) --
	(170.16, 57.53) --
	(170.53, 58.54) --
	(170.90, 58.25) --
	(171.27, 57.67) --
	(171.64, 58.40) --
	(172.01, 58.25) --
	(172.38, 58.54) --
	(172.74, 57.82) --
	(173.11, 57.96) --
	(173.48, 58.54) --
	(173.85, 58.54) --
	(174.22, 57.82) --
	(174.59, 57.96) --
	(174.96, 57.67) --
	(175.33, 58.25) --
	(175.70, 57.96) --
	(176.06, 57.82) --
	(176.43, 57.53) --
	(176.80, 56.80);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44, 50.02) rectangle (184.81,143.97);
\end{scope}
\begin{scope}
\path[clip] ( 54.44,143.97) rectangle (184.81,151.92);

\path[] ( 54.44,143.97) rectangle (184.81,151.92);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 93.23,145.67) {T=500, K=3, c=0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,143.97) rectangle (184.81,151.92);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.12, 50.02) -- (189.12, 44.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.01, 50.02) -- (226.01, 44.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (262.90, 50.02) -- (262.90, 44.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (299.79, 50.02) -- (299.79, 44.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17, 57.82) -- (320.86, 57.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17, 72.33) -- (320.86, 72.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17, 86.84) -- (320.86, 86.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17,101.35) -- (320.86,101.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17,115.86) -- (320.86,115.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17,130.37) -- (320.86,130.37);
\end{scope}
\begin{scope}
\path[clip] (184.81, 50.02) rectangle (315.17,143.97);
\definecolor[named]{drawColor}{rgb}{0.83,0.83,0.83}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.12, 57.82) --
	(312.08, 57.82);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.81, 64.06) --
	(193.18, 64.78) --
	(193.55, 64.49) --
	(193.92, 65.51) --
	(194.29, 64.06) --
	(194.66, 65.51) --
	(195.03, 64.35) --
	(195.39, 67.10) --
	(195.76, 66.96) --
	(196.13, 66.67) --
	(196.50, 65.22) --
	(196.87, 66.67) --
	(197.24, 67.54) --
	(197.61, 66.23) --
	(197.98, 66.09) --
	(198.35, 68.12) --
	(198.71, 67.10) --
	(199.08, 68.70) --
	(199.45, 68.55) --
	(199.82, 68.70) --
	(200.19, 69.28) --
	(200.56, 71.17) --
	(200.93, 72.76) --
	(201.30, 73.34) --
	(201.67, 73.05) --
	(202.03, 74.36) --
	(202.40, 74.79) --
	(202.77, 76.10) --
	(203.14, 77.11) --
	(203.51, 77.26) --
	(203.88, 78.13) --
	(204.25, 77.26) --
	(204.62, 79.15) --
	(204.99, 78.57) --
	(205.35, 80.02) --
	(205.72, 79.87) --
	(206.09, 81.18) --
	(206.46, 81.90) --
	(206.83, 81.03) --
	(207.20, 81.03) --
	(207.57, 80.89) --
	(207.94, 81.03) --
	(208.31, 81.61) --
	(208.67, 81.90) --
	(209.04, 81.61) --
	(209.41, 81.18) --
	(209.78, 82.48) --
	(210.15, 81.76) --
	(210.52, 82.19) --
	(210.89, 82.77) --
	(211.26, 82.19) --
	(211.63, 82.48) --
	(211.99, 82.19) --
	(212.36, 82.05) --
	(212.73, 82.34) --
	(213.10, 82.77) --
	(213.47, 83.50) --
	(213.84, 84.66) --
	(214.21, 84.66) --
	(214.58, 85.68) --
	(214.95, 85.39) --
	(215.31, 86.55) --
	(215.68, 86.11) --
	(216.05, 86.26) --
	(216.42, 85.24) --
	(216.79, 86.26) --
	(217.16, 86.84) --
	(217.53, 87.56) --
	(217.90, 86.40) --
	(218.27, 88.14) --
	(218.63, 88.72) --
	(219.00, 88.43) --
	(219.37, 89.45) --
	(219.74, 89.30) --
	(220.11, 89.45) --
	(220.48, 90.75) --
	(220.85, 90.90) --
	(221.22, 91.04) --
	(221.58, 90.90) --
	(221.95, 90.32) --
	(222.32, 91.48) --
	(222.69, 91.48) --
	(223.06, 91.19) --
	(223.43, 90.03) --
	(223.80, 89.45) --
	(224.17, 90.03) --
	(224.54, 90.46) --
	(224.90, 89.74) --
	(225.27, 90.61) --
	(225.64, 90.61) --
	(226.01, 90.46) --
	(226.38, 90.61) --
	(226.75, 92.35) --
	(227.12, 91.62) --
	(227.49, 91.33) --
	(227.86, 91.33) --
	(228.22, 91.04) --
	(228.59, 91.92) --
	(228.96, 92.35) --
	(229.33, 92.06) --
	(229.70, 91.77) --
	(230.07, 91.92) --
	(230.44, 92.79) --
	(230.81, 92.79) --
	(231.18, 93.22) --
	(231.54, 93.22) --
	(231.91, 93.22) --
	(232.28, 93.80) --
	(232.65, 94.09) --
	(233.02, 94.67) --
	(233.39, 95.11) --
	(233.76, 94.96) --
	(234.13, 94.38) --
	(234.50, 95.11) --
	(234.86, 95.54) --
	(235.23, 94.96) --
	(235.60, 95.69) --
	(235.97, 95.54) --
	(236.34, 96.56) --
	(236.71, 95.54) --
	(237.08, 95.54) --
	(237.45, 96.12) --
	(237.82, 97.43) --
	(238.18, 96.56) --
	(238.55, 95.98) --
	(238.92, 96.56) --
	(239.29, 96.85) --
	(239.66, 96.85) --
	(240.03, 97.14) --
	(240.40, 97.43) --
	(240.77, 97.14) --
	(241.14, 97.43) --
	(241.50, 97.57) --
	(241.87, 97.14) --
	(242.24, 97.28) --
	(242.61, 98.15) --
	(242.98, 98.74) --
	(243.35, 98.44) --
	(243.72, 99.61) --
	(244.09, 99.46) --
	(244.46, 99.61) --
	(244.82,100.48) --
	(245.19,100.48) --
	(245.56,100.19) --
	(245.93,101.06) --
	(246.30,101.64) --
	(246.67,101.49) --
	(247.04,102.36) --
	(247.41,101.49) --
	(247.78,101.78) --
	(248.14,102.65) --
	(248.51,103.09) --
	(248.88,103.23) --
	(249.25,103.96) --
	(249.62,103.67) --
	(249.99,103.09) --
	(250.36,103.38) --
	(250.73,103.52) --
	(251.10,103.67) --
	(251.46,103.09) --
	(251.83,103.96) --
	(252.20,103.09) --
	(252.57,104.10) --
	(252.94,103.52) --
	(253.31,103.09) --
	(253.68,103.23) --
	(254.05,102.94) --
	(254.42,102.94) --
	(254.78,104.25) --
	(255.15,104.10) --
	(255.52,104.83) --
	(255.89,103.81) --
	(256.26,106.28) --
	(256.63,105.70) --
	(257.00,105.41) --
	(257.37,105.85) --
	(257.74,106.43) --
	(258.10,106.43) --
	(258.47,105.26) --
	(258.84,105.99) --
	(259.21,105.85) --
	(259.58,106.86) --
	(259.95,106.72) --
	(260.32,107.30) --
	(260.69,107.15) --
	(261.06,106.72) --
	(261.42,108.02) --
	(261.79,107.44) --
	(262.16,107.15) --
	(262.53,106.86) --
	(262.90,107.01) --
	(263.27,108.75) --
	(263.64,109.04) --
	(264.01,109.18) --
	(264.38,110.05) --
	(264.74,109.91) --
	(265.11,109.76) --
	(265.48,110.49) --
	(265.85,111.07) --
	(266.22,111.07) --
	(266.59,111.36) --
	(266.96,111.65) --
	(267.33,110.34) --
	(267.70,110.34) --
	(268.06,110.49) --
	(268.43,110.92) --
	(268.80,110.78) --
	(269.17,111.79) --
	(269.54,111.94) --
	(269.91,113.25) --
	(270.28,113.25) --
	(270.65,113.10) --
	(271.02,113.83) --
	(271.38,114.41) --
	(271.75,114.99) --
	(272.12,114.12) --
	(272.49,113.68) --
	(272.86,114.70) --
	(273.23,114.84) --
	(273.60,114.12) --
	(273.97,114.55) --
	(274.34,115.57) --
	(274.70,114.99) --
	(275.07,116.00) --
	(275.44,116.29) --
	(275.81,115.71) --
	(276.18,116.44) --
	(276.55,117.16) --
	(276.92,117.74) --
	(277.29,118.90) --
	(277.66,118.90) --
	(278.02,118.76) --
	(278.39,119.48) --
	(278.76,119.48) --
	(279.13,118.76) --
	(279.50,120.21) --
	(279.87,120.50) --
	(280.24,120.21) --
	(280.61,120.94) --
	(280.98,121.23) --
	(281.34,121.37) --
	(281.71,121.95) --
	(282.08,120.94) --
	(282.45,121.23) --
	(282.82,120.94) --
	(283.19,122.24) --
	(283.56,121.95) --
	(283.93,122.39) --
	(284.30,121.66) --
	(284.66,121.66) --
	(285.03,121.08) --
	(285.40,122.39) --
	(285.77,122.24) --
	(286.14,122.68) --
	(286.51,121.95) --
	(286.88,122.97) --
	(287.25,122.68) --
	(287.62,122.24) --
	(287.98,123.26) --
	(288.35,123.11) --
	(288.72,123.84) --
	(289.09,123.98) --
	(289.46,124.42) --
	(289.83,124.56) --
	(290.20,125.00) --
	(290.57,125.29) --
	(290.94,125.29) --
	(291.30,125.29) --
	(291.67,125.43) --
	(292.04,125.00) --
	(292.41,124.85) --
	(292.78,123.40) --
	(293.15,123.98) --
	(293.52,124.27) --
	(293.89,124.42) --
	(294.26,125.00) --
	(294.62,125.14) --
	(294.99,124.71) --
	(295.36,125.72) --
	(295.73,124.85) --
	(296.10,124.85) --
	(296.47,125.29) --
	(296.84,126.45) --
	(297.21,126.01) --
	(297.58,125.43) --
	(297.94,125.72) --
	(298.31,127.03) --
	(298.68,127.47) --
	(299.05,126.45) --
	(299.42,126.74) --
	(299.79,126.59) --
	(300.16,126.16) --
	(300.53,126.74) --
	(300.89,126.88) --
	(301.26,127.18) --
	(301.63,127.61) --
	(302.00,128.34) --
	(302.37,127.76) --
	(302.74,129.06) --
	(303.11,129.50) --
	(303.48,128.19) --
	(303.85,130.51) --
	(304.21,130.66) --
	(304.58,129.93) --
	(304.95,131.09) --
	(305.32,131.38) --
	(305.69,131.09) --
	(306.06,132.69) --
	(306.43,132.25) --
	(306.80,131.24) --
	(307.17,131.53);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.81, 50.02) rectangle (315.17,143.97);
\end{scope}
\begin{scope}
\path[clip] (184.81,143.97) rectangle (315.17,151.92);

\path[] (184.81,143.97) rectangle (315.17,151.92);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.66] at (223.60,145.67) {T=500, K=3, c=1};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.81,143.97) rectangle (315.17,151.92);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,159.72) -- ( 48.75,159.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,174.23) -- ( 48.75,174.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,188.74) -- ( 48.75,188.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,203.25) -- ( 48.75,203.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,217.76) -- ( 48.75,217.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,232.27) -- ( 48.75,232.27);
\end{scope}
\begin{scope}
\path[clip] ( 54.44,151.92) rectangle (184.81,245.88);
\definecolor[named]{drawColor}{rgb}{0.83,0.83,0.83}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.76,159.72) --
	(181.72,159.72);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.14,163.79) --
	( 66.88,164.37) --
	( 67.61,163.64) --
	( 68.35,163.93) --
	( 69.09,163.64) --
	( 69.83,166.25) --
	( 70.56,167.85) --
	( 71.30,168.14) --
	( 72.04,170.90) --
	( 72.78,169.59) --
	( 73.52,169.30) --
	( 74.25,169.01) --
	( 74.99,168.14) --
	( 75.73,169.44) --
	( 76.47,170.46) --
	( 77.20,170.17) --
	( 77.94,170.46) --
	( 78.68,170.31) --
	( 79.42,169.30) --
	( 80.16,168.86) --
	( 80.89,167.41) --
	( 81.63,166.40) --
	( 82.37,166.69) --
	( 83.11,167.27) --
	( 83.84,166.25) --
	( 84.58,165.53) --
	( 85.32,166.54) --
	( 86.06,165.53) --
	( 86.79,166.25) --
	( 87.53,166.69) --
	( 88.27,167.41) --
	( 89.01,167.12) --
	( 89.75,169.01) --
	( 90.48,168.14) --
	( 91.22,168.14) --
	( 91.96,168.57) --
	( 92.70,166.40) --
	( 93.43,165.96) --
	( 94.17,165.53) --
	( 94.91,166.11) --
	( 95.65,166.11) --
	( 96.39,165.24) --
	( 97.12,165.53) --
	( 97.86,165.24) --
	( 98.60,165.38) --
	( 99.34,165.96) --
	(100.07,164.66) --
	(100.81,164.80) --
	(101.55,165.09) --
	(102.29,165.09) --
	(103.03,164.22) --
	(103.76,163.79) --
	(104.50,163.50) --
	(105.24,162.62) --
	(105.98,163.06) --
	(106.71,162.19) --
	(107.45,161.90) --
	(108.19,161.61) --
	(108.93,162.04) --
	(109.67,161.03) --
	(110.40,161.75) --
	(111.14,160.74) --
	(111.88,161.32) --
	(112.62,161.90) --
	(113.35,161.46) --
	(114.09,161.17) --
	(114.83,161.61) --
	(115.57,161.61) --
	(116.31,162.19) --
	(117.04,161.32) --
	(117.78,161.46) --
	(118.52,162.19) --
	(119.26,162.19) --
	(119.99,163.06) --
	(120.73,162.48) --
	(121.47,163.35) --
	(122.21,163.35) --
	(122.95,162.48) --
	(123.68,162.19) --
	(124.42,162.48) --
	(125.16,161.90) --
	(125.90,162.04) --
	(126.63,162.48) --
	(127.37,162.91) --
	(128.11,162.77) --
	(128.85,162.91) --
	(129.59,162.62) --
	(130.32,162.62) --
	(131.06,162.77) --
	(131.80,161.46) --
	(132.54,161.46) --
	(133.27,162.19) --
	(134.01,161.75) --
	(134.75,161.03) --
	(135.49,162.19) --
	(136.23,161.75) --
	(136.96,160.59) --
	(137.70,160.88) --
	(138.44,160.30) --
	(139.18,160.30) --
	(139.91,160.45) --
	(140.65,160.45) --
	(141.39,160.30) --
	(142.13,160.45) --
	(142.87,160.74) --
	(143.60,161.03) --
	(144.34,161.90) --
	(145.08,162.48) --
	(145.82,161.75) --
	(146.55,161.17) --
	(147.29,160.59) --
	(148.03,160.01) --
	(148.77,161.32) --
	(149.51,162.19) --
	(150.24,162.48) --
	(150.98,162.19) --
	(151.72,162.48) --
	(152.46,162.91) --
	(153.19,161.61) --
	(153.93,161.90) --
	(154.67,160.59) --
	(155.41,161.61) --
	(156.15,160.59) --
	(156.88,161.32) --
	(157.62,161.17) --
	(158.36,162.62) --
	(159.10,161.61) --
	(159.83,161.90) --
	(160.57,161.46) --
	(161.31,161.61) --
	(162.05,160.59) --
	(162.78,160.88) --
	(163.52,161.03) --
	(164.26,161.17) --
	(165.00,161.46) --
	(165.74,161.46) --
	(166.47,160.45) --
	(167.21,160.16) --
	(167.95,159.87) --
	(168.69,160.74) --
	(169.42,160.88) --
	(170.16,160.74) --
	(170.90,161.03) --
	(171.64,161.61) --
	(172.38,160.88) --
	(173.11,161.90) --
	(173.85,162.77) --
	(174.59,162.33) --
	(175.33,162.04) --
	(176.06,161.90) --
	(176.80,161.90);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,151.92) rectangle (184.81,245.88);
\end{scope}
\begin{scope}
\path[clip] ( 54.44,245.88) rectangle (184.81,253.83);

\path[] ( 54.44,245.88) rectangle (184.81,253.83);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 93.23,247.58) {T=250, K=3, c=0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,245.88) rectangle (184.81,253.83);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17,159.72) -- (320.86,159.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17,174.23) -- (320.86,174.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17,188.74) -- (320.86,188.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17,203.25) -- (320.86,203.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17,217.76) -- (320.86,217.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17,232.27) -- (320.86,232.27);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.96] at (326.55,156.42) {0.10};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.96] at (326.55,170.93) {0.15};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.96] at (326.55,185.44) {0.20};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.96] at (326.55,199.95) {0.25};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.96] at (326.55,214.46) {0.30};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.96] at (326.55,228.97) {0.35};
\end{scope}
\begin{scope}
\path[clip] (184.81,151.92) rectangle (315.17,245.88);
\definecolor[named]{drawColor}{rgb}{0.83,0.83,0.83}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.12,159.72) --
	(312.08,159.72);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.50,171.48) --
	(197.24,172.93) --
	(197.98,174.52) --
	(198.71,174.09) --
	(199.45,175.97) --
	(200.19,176.55) --
	(200.93,177.72) --
	(201.67,178.30) --
	(202.40,178.30) --
	(203.14,180.62) --
	(203.88,181.92) --
	(204.62,182.79) --
	(205.35,186.13) --
	(206.09,188.74) --
	(206.83,189.03) --
	(207.57,189.32) --
	(208.31,188.16) --
	(209.04,188.02) --
	(209.78,189.32) --
	(210.52,189.90) --
	(211.26,190.34) --
	(211.99,191.50) --
	(212.73,191.64) --
	(213.47,193.10) --
	(214.21,193.53) --
	(214.95,191.21) --
	(215.68,193.24) --
	(216.42,193.10) --
	(217.16,192.52) --
	(217.90,192.37) --
	(218.63,192.66) --
	(219.37,193.10) --
	(220.11,192.66) --
	(220.85,194.11) --
	(221.58,194.98) --
	(222.32,195.13) --
	(223.06,194.84) --
	(223.80,194.98) --
	(224.54,195.85) --
	(225.27,196.00) --
	(226.01,195.71) --
	(226.75,196.29) --
	(227.49,195.85) --
	(228.22,196.58) --
	(228.96,197.59) --
	(229.70,197.45) --
	(230.44,197.01) --
	(231.18,197.74) --
	(231.91,197.74) --
	(232.65,198.90) --
	(233.39,198.32) --
	(234.13,197.30) --
	(234.86,196.72) --
	(235.60,198.90) --
	(236.34,199.34) --
	(237.08,199.63) --
	(237.82,200.93) --
	(238.55,201.95) --
	(239.29,201.51) --
	(240.03,201.80) --
	(240.77,202.82) --
	(241.50,204.41) --
	(242.24,203.25) --
	(242.98,204.56) --
	(243.72,206.74) --
	(244.46,205.86) --
	(245.19,205.86) --
	(245.93,205.86) --
	(246.67,205.72) --
	(247.41,206.45) --
	(248.14,208.04) --
	(248.88,207.03) --
	(249.62,207.46) --
	(250.36,207.03) --
	(251.10,208.19) --
	(251.83,208.04) --
	(252.57,208.48) --
	(253.31,209.20) --
	(254.05,209.64) --
	(254.78,208.48) --
	(255.52,207.90) --
	(256.26,209.64) --
	(257.00,209.20) --
	(257.74,210.80) --
	(258.47,210.36) --
	(259.21,211.09) --
	(259.95,213.27) --
	(260.69,214.57) --
	(261.42,215.88) --
	(262.16,216.31) --
	(262.90,215.59) --
	(263.64,216.60) --
	(264.38,217.18) --
	(265.11,217.76) --
	(265.85,217.33) --
	(266.59,218.49) --
	(267.33,219.36) --
	(268.06,219.50) --
	(268.80,221.97) --
	(269.54,222.41) --
	(270.28,222.12) --
	(271.02,223.28) --
	(271.75,224.00) --
	(272.49,222.99) --
	(273.23,222.41) --
	(273.97,222.99) --
	(274.70,222.99) --
	(275.44,222.70) --
	(276.18,221.83) --
	(276.92,222.26) --
	(277.66,222.70) --
	(278.39,224.15) --
	(279.13,224.87) --
	(279.87,225.45) --
	(280.61,226.03) --
	(281.34,226.32) --
	(282.08,229.08) --
	(282.82,227.19) --
	(283.56,228.79) --
	(284.30,229.66) --
	(285.03,229.37) --
	(285.77,228.50) --
	(286.51,229.23) --
	(287.25,228.79) --
	(287.98,229.81) --
	(288.72,229.81) --
	(289.46,229.08) --
	(290.20,230.97) --
	(290.94,230.97) --
	(291.67,231.84) --
	(292.41,233.58) --
	(293.15,233.43) --
	(293.89,233.14) --
	(294.62,233.29) --
	(295.36,233.87) --
	(296.10,234.45) --
	(296.84,233.72) --
	(297.58,235.18) --
	(298.31,235.47) --
	(299.05,235.76) --
	(299.79,235.61) --
	(300.53,236.63) --
	(301.26,237.35) --
	(302.00,238.66) --
	(302.74,237.93) --
	(303.48,238.22) --
	(304.21,239.09) --
	(304.95,239.67) --
	(305.69,239.82) --
	(306.43,239.67) --
	(307.17,240.11);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.81,151.92) rectangle (315.17,245.88);
\end{scope}
\begin{scope}
\path[clip] (184.81,245.88) rectangle (315.17,253.83);

\path[] (184.81,245.88) rectangle (315.17,253.83);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.66] at (223.60,247.58) {T=250, K=3, c=1};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.81,245.88) rectangle (315.17,253.83);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.76,355.73) -- ( 58.76,361.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.65,355.73) -- ( 95.65,361.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (132.54,355.73) -- (132.54,361.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.42,355.73) -- (169.42,361.42);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,261.63) -- ( 48.75,261.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,276.14) -- ( 48.75,276.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,290.65) -- ( 48.75,290.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,305.16) -- ( 48.75,305.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,319.67) -- ( 48.75,319.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,334.18) -- ( 48.75,334.18);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06,258.32) {0.10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06,272.83) {0.15};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06,287.34) {0.20};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06,301.85) {0.25};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06,316.36) {0.30};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06,330.87) {0.35};
\end{scope}
\begin{scope}
\path[clip] ( 54.44,253.83) rectangle (184.81,347.78);
\definecolor[named]{drawColor}{rgb}{0.83,0.83,0.83}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.76,261.63) --
	(181.72,261.63);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 77.20,270.33) --
	( 79.05,271.21) --
	( 80.89,271.35) --
	( 82.74,270.04) --
	( 84.58,271.06) --
	( 86.43,270.04) --
	( 88.27,269.17) --
	( 90.11,268.30) --
	( 91.96,269.03) --
	( 93.80,266.56) --
	( 95.65,268.16) --
	( 97.49,267.00) --
	( 99.34,266.42) --
	(101.18,266.71) --
	(103.03,264.82) --
	(104.87,264.97) --
	(106.71,265.98) --
	(108.56,265.84) --
	(110.40,266.42) --
	(112.25,265.98) --
	(114.09,266.27) --
	(115.94,265.40) --
	(117.78,265.26) --
	(119.63,265.40) --
	(121.47,265.11) --
	(123.31,265.98) --
	(125.16,266.27) --
	(127.00,265.40) --
	(128.85,265.40) --
	(130.69,266.85) --
	(132.54,265.69) --
	(134.38,266.13) --
	(136.23,265.55) --
	(138.07,263.95) --
	(139.91,264.97) --
	(141.76,263.95) --
	(143.60,264.10) --
	(145.45,263.66) --
	(147.29,264.82) --
	(149.14,265.69) --
	(150.98,265.40) --
	(152.83,264.97) --
	(154.67,263.81) --
	(156.51,263.66) --
	(158.36,262.93) --
	(160.20,263.22) --
	(162.05,263.51) --
	(163.89,263.66) --
	(165.74,264.10) --
	(167.58,263.22) --
	(169.42,263.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,253.83) rectangle (184.81,347.78);
\end{scope}
\begin{scope}
\path[clip] ( 54.44,347.78) rectangle (184.81,355.73);

\path[] ( 54.44,347.78) rectangle (184.81,355.73);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 93.23,349.49) {T=100, K=3, c=0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,347.78) rectangle (184.81,355.73);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.12,355.73) -- (189.12,361.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.01,355.73) -- (226.01,361.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (262.90,355.73) -- (262.90,361.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (299.79,355.73) -- (299.79,361.42);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (189.12,367.12) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (226.01,367.12) {0.2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (262.90,367.12) {0.4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (299.79,367.12) {0.6};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17,261.63) -- (320.86,261.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17,276.14) -- (320.86,276.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17,290.65) -- (320.86,290.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17,305.16) -- (320.86,305.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17,319.67) -- (320.86,319.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17,334.18) -- (320.86,334.18);
\end{scope}
\begin{scope}
\path[clip] (184.81,253.83) rectangle (315.17,347.78);
\definecolor[named]{drawColor}{rgb}{0.83,0.83,0.83}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.12,261.63) --
	(312.08,261.63);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.57,289.20) --
	(209.41,287.31) --
	(211.26,288.76) --
	(213.10,287.46) --
	(214.95,288.91) --
	(216.79,292.10) --
	(218.63,293.26) --
	(220.48,293.99) --
	(222.32,294.42) --
	(224.17,295.73) --
	(226.01,296.31) --
	(227.86,296.89) --
	(229.70,299.21) --
	(231.54,299.94) --
	(233.39,300.52) --
	(235.23,301.39) --
	(237.08,302.26) --
	(238.92,302.84) --
	(240.77,305.16) --
	(242.61,306.47) --
	(244.46,305.74) --
	(246.30,306.03) --
	(248.14,306.32) --
	(249.99,307.63) --
	(251.83,308.21) --
	(253.68,307.19) --
	(255.52,309.37) --
	(257.37,309.80) --
	(259.21,310.38) --
	(261.06,312.85) --
	(262.90,312.99) --
	(264.74,315.61) --
	(266.59,316.62) --
	(268.43,318.36) --
	(270.28,318.51) --
	(272.12,320.25) --
	(273.97,319.81) --
	(275.81,320.83) --
	(277.66,320.98) --
	(279.50,322.57) --
	(281.34,324.60) --
	(283.19,324.31) --
	(285.03,324.75) --
	(286.88,326.92) --
	(288.72,325.76) --
	(290.57,326.92) --
	(292.41,326.49) --
	(294.26,327.80) --
	(296.10,327.80) --
	(297.94,329.10) --
	(299.79,332.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.81,253.83) rectangle (315.17,347.78);
\end{scope}
\begin{scope}
\path[clip] (184.81,347.78) rectangle (315.17,355.73);

\path[] (184.81,347.78) rectangle (315.17,355.73);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.66] at (223.60,349.49) {T=100, K=3, c=1};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.81,347.78) rectangle (315.17,355.73);
\end{scope}
\end{tikzpicture}

### 2017-04-21 floats/mc-mccrackensize.tex
Add TeX files with simulation and empirical results to repo
I've decided to add _a few_ generated files to the main repository to
make my life easier; namely any graphics or tables that are included
in the main paper.

% Created by tikzDevice version 0.6.2-92-0ad2792 on 2014-03-27 13:37:45
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (361.35,397.48);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);

\path[] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (184.81, 12.04) {$P/T$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at ( 14.29,198.90) {Rejection Probability};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44, 59.11) -- ( 48.75, 59.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44, 79.93) -- ( 48.75, 79.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,100.74) -- ( 48.75,100.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,121.55) -- ( 48.75,121.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,142.37) -- ( 48.75,142.37);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06, 55.81) {0.10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06, 76.62) {0.15};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06, 97.43) {0.20};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06,118.25) {0.25};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.76, 50.02) -- ( 58.76, 44.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.65, 50.02) -- ( 95.65, 44.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (132.54, 50.02) -- (132.54, 44.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.42, 50.02) -- (169.42, 44.32);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 58.76, 32.02) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 95.65, 32.02) {0.2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (132.54, 32.02) {0.4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (169.42, 32.02) {0.6};
\end{scope}
\begin{scope}
\path[clip] ( 54.44, 50.02) rectangle (184.81,143.97);
\definecolor[named]{drawColor}{rgb}{0.83,0.83,0.83}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.76, 59.11) --
	(181.72, 59.11);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 62.45, 61.40) --
	( 62.82, 62.65) --
	( 63.19, 63.90) --
	( 63.56, 61.40) --
	( 63.92, 61.61) --
	( 64.29, 64.73) --
	( 64.66, 66.19) --
	( 65.03, 63.49) --
	( 65.40, 64.53) --
	( 65.77, 62.24) --
	( 66.14, 63.69) --
	( 66.51, 60.78) --
	( 66.88, 64.94) --
	( 67.24, 62.24) --
	( 67.61, 63.69) --
	( 67.98, 66.19) --
	( 68.35, 62.65) --
	( 68.72, 61.61) --
	( 69.09, 63.49) --
	( 69.46, 66.40) --
	( 69.83, 63.28) --
	( 70.20, 63.90) --
	( 70.56, 66.19) --
	( 70.93, 64.94) --
	( 71.30, 66.82) --
	( 71.67, 68.06) --
	( 72.04, 66.61) --
	( 72.41, 68.48) --
	( 72.78, 67.44) --
	( 73.15, 66.40) --
	( 73.52, 66.40) --
	( 73.88, 66.19) --
	( 74.25, 64.94) --
	( 74.62, 66.19) --
	( 74.99, 65.57) --
	( 75.36, 65.15) --
	( 75.73, 64.53) --
	( 76.10, 62.03) --
	( 76.47, 63.28) --
	( 76.84, 64.11) --
	( 77.20, 63.28) --
	( 77.57, 60.78) --
	( 77.94, 59.95) --
	( 78.31, 61.61) --
	( 78.68, 63.49) --
	( 79.05, 62.86) --
	( 79.42, 62.44) --
	( 79.79, 61.40) --
	( 80.16, 61.82) --
	( 80.52, 62.86) --
	( 80.89, 63.49) --
	( 81.26, 61.40) --
	( 81.63, 62.86) --
	( 82.00, 63.69) --
	( 82.37, 62.65) --
	( 82.74, 63.49) --
	( 83.11, 65.98) --
	( 83.48, 65.15) --
	( 83.84, 63.28) --
	( 84.21, 63.28) --
	( 84.58, 65.36) --
	( 84.95, 65.15) --
	( 85.32, 66.19) --
	( 85.69, 66.19) --
	( 86.06, 66.19) --
	( 86.43, 65.77) --
	( 86.79, 67.86) --
	( 87.16, 66.40) --
	( 87.53, 67.65) --
	( 87.90, 69.10) --
	( 88.27, 68.90) --
	( 88.64, 69.10) --
	( 89.01, 67.44) --
	( 89.38, 67.02) --
	( 89.75, 68.48) --
	( 90.11, 67.44) --
	( 90.48, 67.44) --
	( 90.85, 68.90) --
	( 91.22, 68.90) --
	( 91.59, 68.27) --
	( 91.96, 68.69) --
	( 92.33, 69.73) --
	( 92.70, 69.52) --
	( 93.07, 69.31) --
	( 93.43, 67.65) --
	( 93.80, 67.44) --
	( 94.17, 68.06) --
	( 94.54, 67.23) --
	( 94.91, 66.19) --
	( 95.28, 65.15) --
	( 95.65, 65.15) --
	( 96.02, 66.19) --
	( 96.39, 65.36) --
	( 96.75, 67.65) --
	( 97.12, 66.40) --
	( 97.49, 65.57) --
	( 97.86, 65.15) --
	( 98.23, 65.15) --
	( 98.60, 63.69) --
	( 98.97, 62.44) --
	( 99.34, 63.69) --
	( 99.71, 63.69) --
	(100.07, 63.28) --
	(100.44, 62.24) --
	(100.81, 61.82) --
	(101.18, 59.95) --
	(101.55, 61.82) --
	(101.92, 62.44) --
	(102.29, 60.57) --
	(102.66, 61.40) --
	(103.03, 61.82) --
	(103.39, 62.24) --
	(103.76, 62.44) --
	(104.13, 62.03) --
	(104.50, 60.78) --
	(104.87, 59.11) --
	(105.24, 60.99) --
	(105.61, 62.03) --
	(105.98, 63.49) --
	(106.35, 61.61) --
	(106.71, 61.82) --
	(107.08, 59.74) --
	(107.45, 59.53) --
	(107.82, 60.57) --
	(108.19, 58.91) --
	(108.56, 61.40) --
	(108.93, 60.16) --
	(109.30, 60.16) --
	(109.67, 60.57) --
	(110.03, 61.82) --
	(110.40, 61.20) --
	(110.77, 61.40) --
	(111.14, 61.20) --
	(111.51, 61.20) --
	(111.88, 61.61) --
	(112.25, 61.61) --
	(112.62, 61.40) --
	(112.99, 60.57) --
	(113.35, 62.03) --
	(113.72, 61.61) --
	(114.09, 62.24) --
	(114.46, 62.24) --
	(114.83, 62.03) --
	(115.20, 64.11) --
	(115.57, 62.24) --
	(115.94, 59.74) --
	(116.31, 59.53) --
	(116.67, 58.28) --
	(117.04, 57.87) --
	(117.41, 58.49) --
	(117.78, 59.53) --
	(118.15, 59.95) --
	(118.52, 58.28) --
	(118.89, 59.32) --
	(119.26, 59.95) --
	(119.63, 59.53) --
	(119.99, 59.53) --
	(120.36, 59.53) --
	(120.73, 59.95) --
	(121.10, 59.53) --
	(121.47, 59.74) --
	(121.84, 59.74) --
	(122.21, 58.70) --
	(122.58, 56.41) --
	(122.95, 61.20) --
	(123.31, 60.57) --
	(123.68, 58.07) --
	(124.05, 59.11) --
	(124.42, 58.91) --
	(124.79, 58.49) --
	(125.16, 58.91) --
	(125.53, 59.32) --
	(125.90, 59.32) --
	(126.27, 59.53) --
	(126.63, 58.70) --
	(127.00, 60.78) --
	(127.37, 59.74) --
	(127.74, 58.49) --
	(128.11, 60.16) --
	(128.48, 58.91) --
	(128.85, 58.91) --
	(129.22, 59.32) --
	(129.59, 60.36) --
	(129.95, 60.78) --
	(130.32, 59.53) --
	(130.69, 59.11) --
	(131.06, 62.03) --
	(131.43, 62.86) --
	(131.80, 62.65) --
	(132.17, 63.49) --
	(132.54, 63.69) --
	(132.91, 62.86) --
	(133.27, 61.20) --
	(133.64, 60.16) --
	(134.01, 62.86) --
	(134.38, 62.65) --
	(134.75, 62.86) --
	(135.12, 62.86) --
	(135.49, 60.99) --
	(135.86, 59.74) --
	(136.23, 60.57) --
	(136.59, 61.82) --
	(136.96, 62.86) --
	(137.33, 63.28) --
	(137.70, 63.28) --
	(138.07, 63.69) --
	(138.44, 61.40) --
	(138.81, 60.57) --
	(139.18, 60.16) --
	(139.55, 59.95) --
	(139.91, 59.53) --
	(140.28, 60.16) --
	(140.65, 62.03) --
	(141.02, 60.78) --
	(141.39, 61.82) --
	(141.76, 61.20) --
	(142.13, 62.44) --
	(142.50, 61.40) --
	(142.87, 60.57) --
	(143.23, 59.53) --
	(143.60, 60.16) --
	(143.97, 59.74) --
	(144.34, 60.57) --
	(144.71, 60.78) --
	(145.08, 62.03) --
	(145.45, 60.36) --
	(145.82, 60.16) --
	(146.19, 61.20) --
	(146.55, 61.40) --
	(146.92, 59.95) --
	(147.29, 60.36) --
	(147.66, 59.53) --
	(148.03, 59.74) --
	(148.40, 56.62) --
	(148.77, 55.78) --
	(149.14, 56.41) --
	(149.51, 59.53) --
	(149.87, 58.28) --
	(150.24, 58.49) --
	(150.61, 57.87) --
	(150.98, 59.11) --
	(151.35, 58.49) --
	(151.72, 56.83) --
	(152.09, 56.41) --
	(152.46, 59.32) --
	(152.83, 59.32) --
	(153.19, 59.74) --
	(153.56, 57.87) --
	(153.93, 59.11) --
	(154.30, 58.70) --
	(154.67, 57.87) --
	(155.04, 58.07) --
	(155.41, 56.83) --
	(155.78, 57.03) --
	(156.15, 58.70) --
	(156.51, 60.36) --
	(156.88, 59.11) --
	(157.25, 62.03) --
	(157.62, 61.40) --
	(157.99, 60.57) --
	(158.36, 62.24) --
	(158.73, 61.61) --
	(159.10, 59.74) --
	(159.47, 61.61) --
	(159.83, 60.36) --
	(160.20, 61.61) --
	(160.57, 59.32) --
	(160.94, 61.20) --
	(161.31, 59.11) --
	(161.68, 58.28) --
	(162.05, 60.16) --
	(162.42, 60.16) --
	(162.78, 59.11) --
	(163.15, 57.66) --
	(163.52, 59.53) --
	(163.89, 58.91) --
	(164.26, 59.53) --
	(164.63, 59.11) --
	(165.00, 58.49) --
	(165.37, 59.32) --
	(165.74, 59.32) --
	(166.10, 58.91) --
	(166.47, 59.11) --
	(166.84, 57.66) --
	(167.21, 59.74) --
	(167.58, 59.95) --
	(167.95, 58.70) --
	(168.32, 59.32) --
	(168.69, 58.91) --
	(169.06, 58.49) --
	(169.42, 55.78) --
	(169.79, 56.83) --
	(170.16, 58.91) --
	(170.53, 58.07) --
	(170.90, 59.11) --
	(171.27, 57.66) --
	(171.64, 57.24) --
	(172.01, 57.66) --
	(172.38, 57.24) --
	(172.74, 55.99) --
	(173.11, 58.28) --
	(173.48, 55.99) --
	(173.85, 57.87) --
	(174.22, 59.95) --
	(174.59, 58.49) --
	(174.96, 59.32) --
	(175.33, 58.49) --
	(175.70, 59.74) --
	(176.06, 59.53) --
	(176.43, 62.65) --
	(176.80, 63.07);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44, 50.02) rectangle (184.81,143.97);
\end{scope}
\begin{scope}
\path[clip] ( 54.44,143.97) rectangle (184.81,151.92);

\path[] ( 54.44,143.97) rectangle (184.81,151.92);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 93.23,145.67) {T=500, K=3, c=0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,143.97) rectangle (184.81,151.92);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.12, 50.02) -- (189.12, 44.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.01, 50.02) -- (226.01, 44.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (262.90, 50.02) -- (262.90, 44.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (299.79, 50.02) -- (299.79, 44.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17, 59.11) -- (320.86, 59.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17, 79.93) -- (320.86, 79.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17,100.74) -- (320.86,100.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17,121.55) -- (320.86,121.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17,142.37) -- (320.86,142.37);
\end{scope}
\begin{scope}
\path[clip] (184.81, 50.02) rectangle (315.17,143.97);
\definecolor[named]{drawColor}{rgb}{0.83,0.83,0.83}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.12, 59.11) --
	(312.08, 59.11);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.81, 66.19) --
	(193.18, 66.61) --
	(193.55, 68.48) --
	(193.92, 66.82) --
	(194.29, 65.77) --
	(194.66, 67.44) --
	(195.03, 66.19) --
	(195.39, 69.73) --
	(195.76, 68.27) --
	(196.13, 66.61) --
	(196.50, 64.94) --
	(196.87, 67.02) --
	(197.24, 69.31) --
	(197.61, 68.69) --
	(197.98, 67.86) --
	(198.35, 69.52) --
	(198.71, 69.10) --
	(199.08, 67.65) --
	(199.45, 68.27) --
	(199.82, 67.44) --
	(200.19, 68.90) --
	(200.56, 70.98) --
	(200.93, 69.52) --
	(201.30, 73.48) --
	(201.67, 73.27) --
	(202.03, 72.85) --
	(202.40, 73.89) --
	(202.77, 75.35) --
	(203.14, 74.52) --
	(203.51, 74.93) --
	(203.88, 75.97) --
	(204.25, 76.60) --
	(204.62, 75.76) --
	(204.99, 77.64) --
	(205.35, 75.76) --
	(205.72, 77.01) --
	(206.09, 80.55) --
	(206.46, 80.55) --
	(206.83, 79.72) --
	(207.20, 81.80) --
	(207.57, 81.18) --
	(207.94, 77.43) --
	(208.31, 79.93) --
	(208.67, 80.34) --
	(209.04, 81.59) --
	(209.41, 80.97) --
	(209.78, 81.38) --
	(210.15, 80.55) --
	(210.52, 80.55) --
	(210.89, 81.80) --
	(211.26, 84.09) --
	(211.63, 83.67) --
	(211.99, 85.13) --
	(212.36, 85.13) --
	(212.73, 84.92) --
	(213.10, 84.09) --
	(213.47, 85.75) --
	(213.84, 84.51) --
	(214.21, 84.71) --
	(214.58, 86.80) --
	(214.95, 86.38) --
	(215.31, 87.84) --
	(215.68, 89.29) --
	(216.05, 87.00) --
	(216.42, 88.04) --
	(216.79, 89.29) --
	(217.16, 87.42) --
	(217.53, 87.21) --
	(217.90, 87.21) --
	(218.27, 89.50) --
	(218.63, 88.04) --
	(219.00, 85.96) --
	(219.37, 86.80) --
	(219.74, 86.80) --
	(220.11, 87.00) --
	(220.48, 85.75) --
	(220.85, 90.13) --
	(221.22, 92.83) --
	(221.58, 92.83) --
	(221.95, 92.62) --
	(222.32, 91.37) --
	(222.69, 90.33) --
	(223.06, 90.54) --
	(223.43, 92.41) --
	(223.80, 90.54) --
	(224.17, 88.88) --
	(224.54, 88.46) --
	(224.90, 87.42) --
	(225.27, 90.13) --
	(225.64, 90.13) --
	(226.01, 90.96) --
	(226.38, 92.41) --
	(226.75, 93.66) --
	(227.12, 90.13) --
	(227.49, 91.37) --
	(227.86, 94.29) --
	(228.22, 95.12) --
	(228.59, 93.04) --
	(228.96, 93.66) --
	(229.33, 93.87) --
	(229.70, 95.75) --
	(230.07, 94.29) --
	(230.44, 93.87) --
	(230.81, 94.29) --
	(231.18, 95.33) --
	(231.54, 93.25) --
	(231.91, 95.95) --
	(232.28, 94.91) --
	(232.65, 95.75) --
	(233.02, 93.66) --
	(233.39, 93.04) --
	(233.76, 94.29) --
	(234.13, 95.54) --
	(234.50, 97.20) --
	(234.86, 97.41) --
	(235.23, 97.41) --
	(235.60, 98.24) --
	(235.97, 97.41) --
	(236.34, 97.83) --
	(236.71, 98.24) --
	(237.08, 97.20) --
	(237.45, 98.45) --
	(237.82, 99.91) --
	(238.18, 98.45) --
	(238.55, 97.83) --
	(238.92, 95.95) --
	(239.29, 96.99) --
	(239.66, 97.41) --
	(240.03, 95.95) --
	(240.40, 97.41) --
	(240.77, 98.66) --
	(241.14, 98.66) --
	(241.50, 98.66) --
	(241.87, 99.08) --
	(242.24, 98.24) --
	(242.61, 97.83) --
	(242.98, 99.49) --
	(243.35, 97.83) --
	(243.72, 97.62) --
	(244.09, 96.79) --
	(244.46, 96.58) --
	(244.82, 97.41) --
	(245.19, 98.66) --
	(245.56, 98.24) --
	(245.93, 99.49) --
	(246.30, 99.49) --
	(246.67, 99.49) --
	(247.04, 99.08) --
	(247.41, 99.70) --
	(247.78, 99.91) --
	(248.14,101.78) --
	(248.51,101.78) --
	(248.88,104.49) --
	(249.25,102.82) --
	(249.62,103.65) --
	(249.99,103.65) --
	(250.36,103.45) --
	(250.73,105.53) --
	(251.10,102.61) --
	(251.46,105.53) --
	(251.83,105.11) --
	(252.20,104.07) --
	(252.57,105.53) --
	(252.94,103.65) --
	(253.31,103.24) --
	(253.68,103.65) --
	(254.05,103.65) --
	(254.42,103.45) --
	(254.78,105.32) --
	(255.15,106.78) --
	(255.52,105.94) --
	(255.89,106.15) --
	(256.26,106.78) --
	(256.63,107.19) --
	(257.00,107.61) --
	(257.37,106.78) --
	(257.74,107.40) --
	(258.10,107.40) --
	(258.47,108.44) --
	(258.84,109.07) --
	(259.21,111.56) --
	(259.58,110.94) --
	(259.95,109.07) --
	(260.32,111.98) --
	(260.69,110.52) --
	(261.06,109.69) --
	(261.42,110.73) --
	(261.79,110.73) --
	(262.16,112.19) --
	(262.53,111.98) --
	(262.90,110.94) --
	(263.27,110.73) --
	(263.64,110.94) --
	(264.01,111.77) --
	(264.38,112.81) --
	(264.74,112.81) --
	(265.11,111.98) --
	(265.48,111.77) --
	(265.85,111.56) --
	(266.22,111.56) --
	(266.59,112.81) --
	(266.96,113.85) --
	(267.33,114.27) --
	(267.70,114.06) --
	(268.06,115.73) --
	(268.43,115.73) --
	(268.80,117.60) --
	(269.17,119.26) --
	(269.54,116.35) --
	(269.91,116.35) --
	(270.28,116.97) --
	(270.65,117.39) --
	(271.02,115.31) --
	(271.38,114.89) --
	(271.75,114.06) --
	(272.12,114.68) --
	(272.49,115.31) --
	(272.86,116.77) --
	(273.23,113.23) --
	(273.60,115.73) --
	(273.97,116.77) --
	(274.34,115.73) --
	(274.70,116.35) --
	(275.07,118.01) --
	(275.44,119.68) --
	(275.81,120.10) --
	(276.18,119.26) --
	(276.55,119.89) --
	(276.92,120.93) --
	(277.29,122.18) --
	(277.66,122.39) --
	(278.02,122.59) --
	(278.39,122.39) --
	(278.76,124.05) --
	(279.13,122.39) --
	(279.50,122.18) --
	(279.87,122.18) --
	(280.24,123.01) --
	(280.61,123.63) --
	(280.98,125.09) --
	(281.34,125.92) --
	(281.71,127.59) --
	(282.08,125.51) --
	(282.45,125.09) --
	(282.82,124.88) --
	(283.19,127.38) --
	(283.56,125.51) --
	(283.93,126.96) --
	(284.30,126.34) --
	(284.66,125.72) --
	(285.03,124.88) --
	(285.40,125.30) --
	(285.77,125.51) --
	(286.14,125.09) --
	(286.51,122.80) --
	(286.88,122.39) --
	(287.25,122.59) --
	(287.62,124.67) --
	(287.98,124.67) --
	(288.35,125.72) --
	(288.72,126.55) --
	(289.09,126.96) --
	(289.46,126.76) --
	(289.83,125.09) --
	(290.20,124.47) --
	(290.57,126.55) --
	(290.94,127.59) --
	(291.30,126.76) --
	(291.67,126.76) --
	(292.04,126.96) --
	(292.41,128.00) --
	(292.78,129.46) --
	(293.15,128.63) --
	(293.52,127.17) --
	(293.89,128.21) --
	(294.26,129.05) --
	(294.62,128.42) --
	(294.99,127.59) --
	(295.36,127.17) --
	(295.73,128.42) --
	(296.10,129.88) --
	(296.47,128.21) --
	(296.84,126.96) --
	(297.21,127.17) --
	(297.58,124.88) --
	(297.94,124.47) --
	(298.31,124.05) --
	(298.68,124.47) --
	(299.05,127.17) --
	(299.42,124.88) --
	(299.79,125.72) --
	(300.16,126.13) --
	(300.53,124.47) --
	(300.89,127.38) --
	(301.26,126.13) --
	(301.63,124.67) --
	(302.00,125.51) --
	(302.37,124.05) --
	(302.74,122.80) --
	(303.11,125.72) --
	(303.48,127.38) --
	(303.85,128.21) --
	(304.21,129.25) --
	(304.58,125.72) --
	(304.95,125.72) --
	(305.32,125.92) --
	(305.69,127.17) --
	(306.06,127.38) --
	(306.43,128.42) --
	(306.80,129.46) --
	(307.17,128.63);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.81, 50.02) rectangle (315.17,143.97);
\end{scope}
\begin{scope}
\path[clip] (184.81,143.97) rectangle (315.17,151.92);

\path[] (184.81,143.97) rectangle (315.17,151.92);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.66] at (223.60,145.67) {T=500, K=3, c=1};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.81,143.97) rectangle (315.17,151.92);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,161.02) -- ( 48.75,161.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,181.83) -- ( 48.75,181.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,202.65) -- ( 48.75,202.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,223.46) -- ( 48.75,223.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,244.27) -- ( 48.75,244.27);
\end{scope}
\begin{scope}
\path[clip] ( 54.44,151.92) rectangle (184.81,245.88);
\definecolor[named]{drawColor}{rgb}{0.83,0.83,0.83}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.76,161.02) --
	(181.72,161.02);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.14,164.56) --
	( 66.88,165.39) --
	( 67.61,163.73) --
	( 68.35,164.14) --
	( 69.09,163.93) --
	( 69.83,168.10) --
	( 70.56,168.93) --
	( 71.30,168.31) --
	( 72.04,173.09) --
	( 72.78,171.01) --
	( 73.52,169.55) --
	( 74.25,168.72) --
	( 74.99,167.26) --
	( 75.73,169.35) --
	( 76.47,170.80) --
	( 77.20,171.22) --
	( 77.94,171.01) --
	( 78.68,169.76) --
	( 79.42,166.43) --
	( 80.16,167.47) --
	( 80.89,167.89) --
	( 81.63,165.39) --
	( 82.37,167.06) --
	( 83.11,167.47) --
	( 83.84,166.64) --
	( 84.58,166.43) --
	( 85.32,166.85) --
	( 86.06,168.51) --
	( 86.79,169.14) --
	( 87.53,169.76) --
	( 88.27,165.60) --
	( 89.01,167.47) --
	( 89.75,170.39) --
	( 90.48,168.31) --
	( 91.22,169.97) --
	( 91.96,170.39) --
	( 92.70,167.26) --
	( 93.43,167.47) --
	( 94.17,165.81) --
	( 94.91,165.39) --
	( 95.65,166.22) --
	( 96.39,166.64) --
	( 97.12,168.72) --
	( 97.86,166.85) --
	( 98.60,166.64) --
	( 99.34,166.85) --
	(100.07,167.06) --
	(100.81,168.72) --
	(101.55,167.47) --
	(102.29,167.26) --
	(103.03,165.60) --
	(103.76,164.35) --
	(104.50,163.93) --
	(105.24,164.35) --
	(105.98,165.60) --
	(106.71,166.22) --
	(107.45,165.18) --
	(108.19,162.89) --
	(108.93,164.35) --
	(109.67,163.52) --
	(110.40,163.31) --
	(111.14,162.06) --
	(111.88,163.10) --
	(112.62,164.14) --
	(113.35,163.10) --
	(114.09,162.27) --
	(114.83,163.52) --
	(115.57,162.89) --
	(116.31,163.31) --
	(117.04,162.69) --
	(117.78,164.35) --
	(118.52,163.73) --
	(119.26,162.89) --
	(119.99,162.06) --
	(120.73,162.89) --
	(121.47,163.10) --
	(122.21,162.89) --
	(122.95,161.65) --
	(123.68,164.14) --
	(124.42,164.56) --
	(125.16,162.69) --
	(125.90,163.10) --
	(126.63,162.27) --
	(127.37,161.85) --
	(128.11,162.27) --
	(128.85,162.69) --
	(129.59,162.48) --
	(130.32,163.73) --
	(131.06,162.69) --
	(131.80,160.60) --
	(132.54,163.52) --
	(133.27,161.44) --
	(134.01,159.77) --
	(134.75,161.44) --
	(135.49,162.06) --
	(136.23,162.48) --
	(136.96,162.69) --
	(137.70,160.40) --
	(138.44,160.81) --
	(139.18,164.14) --
	(139.91,164.56) --
	(140.65,164.14) --
	(141.39,162.69) --
	(142.13,160.40) --
	(142.87,162.06) --
	(143.60,161.44) --
	(144.34,161.23) --
	(145.08,162.27) --
	(145.82,162.48) --
	(146.55,161.85) --
	(147.29,162.48) --
	(148.03,162.48) --
	(148.77,163.73) --
	(149.51,164.35) --
	(150.24,166.43) --
	(150.98,167.68) --
	(151.72,164.77) --
	(152.46,166.22) --
	(153.19,165.18) --
	(153.93,166.85) --
	(154.67,168.72) --
	(155.41,166.85) --
	(156.15,165.81) --
	(156.88,163.73) --
	(157.62,163.31) --
	(158.36,162.89) --
	(159.10,162.27) --
	(159.83,162.06) --
	(160.57,164.14) --
	(161.31,164.35) --
	(162.05,163.10) --
	(162.78,163.93) --
	(163.52,164.56) --
	(164.26,161.65) --
	(165.00,162.89) --
	(165.74,166.43) --
	(166.47,162.69) --
	(167.21,164.35) --
	(167.95,163.52) --
	(168.69,161.65) --
	(169.42,160.81) --
	(170.16,162.27) --
	(170.90,161.44) --
	(171.64,161.44) --
	(172.38,160.81) --
	(173.11,162.06) --
	(173.85,161.85) --
	(174.59,162.06) --
	(175.33,165.60) --
	(176.06,163.73) --
	(176.80,165.60);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,151.92) rectangle (184.81,245.88);
\end{scope}
\begin{scope}
\path[clip] ( 54.44,245.88) rectangle (184.81,253.83);

\path[] ( 54.44,245.88) rectangle (184.81,253.83);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 93.23,247.58) {T=250, K=3, c=0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,245.88) rectangle (184.81,253.83);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17,161.02) -- (320.86,161.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17,181.83) -- (320.86,181.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17,202.65) -- (320.86,202.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17,223.46) -- (320.86,223.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17,244.27) -- (320.86,244.27);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.96] at (326.55,157.72) {0.10};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.96] at (326.55,178.53) {0.15};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.96] at (326.55,199.34) {0.20};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.96] at (326.55,220.15) {0.25};
\end{scope}
\begin{scope}
\path[clip] (184.81,151.92) rectangle (315.17,245.88);
\definecolor[named]{drawColor}{rgb}{0.83,0.83,0.83}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.12,161.02) --
	(312.08,161.02);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.50,170.80) --
	(197.24,171.64) --
	(197.98,172.88) --
	(198.71,172.26) --
	(199.45,174.76) --
	(200.19,176.21) --
	(200.93,177.67) --
	(201.67,179.34) --
	(202.40,180.58) --
	(203.14,179.75) --
	(203.88,178.09) --
	(204.62,180.58) --
	(205.35,182.46) --
	(206.09,185.79) --
	(206.83,187.24) --
	(207.57,189.12) --
	(208.31,189.53) --
	(209.04,187.66) --
	(209.78,189.12) --
	(210.52,189.74) --
	(211.26,189.33) --
	(211.99,192.24) --
	(212.73,191.20) --
	(213.47,194.11) --
	(214.21,195.57) --
	(214.95,195.57) --
	(215.68,196.40) --
	(216.42,194.95) --
	(217.16,193.28) --
	(217.90,190.37) --
	(218.63,193.07) --
	(219.37,191.20) --
	(220.11,193.07) --
	(220.85,193.90) --
	(221.58,194.11) --
	(222.32,197.03) --
	(223.06,197.44) --
	(223.80,196.40) --
	(224.54,198.07) --
	(225.27,197.23) --
	(226.01,197.03) --
	(226.75,197.03) --
	(227.49,197.86) --
	(228.22,198.48) --
	(228.96,198.48) --
	(229.70,199.94) --
	(230.44,199.94) --
	(231.18,204.94) --
	(231.91,204.52) --
	(232.65,203.06) --
	(233.39,201.40) --
	(234.13,201.19) --
	(234.86,197.65) --
	(235.60,198.69) --
	(236.34,199.11) --
	(237.08,199.52) --
	(237.82,199.73) --
	(238.55,199.94) --
	(239.29,200.98) --
	(240.03,200.77) --
	(240.77,202.65) --
	(241.50,204.10) --
	(242.24,206.18) --
	(242.98,207.85) --
	(243.72,210.35) --
	(244.46,209.31) --
	(245.19,209.31) --
	(245.93,209.93) --
	(246.67,208.89) --
	(247.41,210.14) --
	(248.14,210.76) --
	(248.88,211.80) --
	(249.62,210.56) --
	(250.36,210.76) --
	(251.10,212.01) --
	(251.83,211.39) --
	(252.57,209.72) --
	(253.31,210.56) --
	(254.05,211.18) --
	(254.78,212.01) --
	(255.52,212.84) --
	(256.26,213.89) --
	(257.00,213.47) --
	(257.74,214.51) --
	(258.47,214.93) --
	(259.21,218.46) --
	(259.95,218.05) --
	(260.69,221.79) --
	(261.42,218.88) --
	(262.16,219.30) --
	(262.90,219.71) --
	(263.64,221.17) --
	(264.38,223.04) --
	(265.11,222.00) --
	(265.85,224.08) --
	(266.59,224.92) --
	(267.33,226.79) --
	(268.06,227.83) --
	(268.80,225.54) --
	(269.54,227.62) --
	(270.28,229.08) --
	(271.02,228.45) --
	(271.75,228.87) --
	(272.49,229.49) --
	(273.23,230.33) --
	(273.97,229.49) --
	(274.70,231.37) --
	(275.44,229.70) --
	(276.18,229.91) --
	(276.92,229.91) --
	(277.66,230.33) --
	(278.39,230.33) --
	(279.13,230.74) --
	(279.87,230.54) --
	(280.61,231.37) --
	(281.34,231.16) --
	(282.08,232.20) --
	(282.82,233.66) --
	(283.56,232.62) --
	(284.30,234.28) --
	(285.03,234.70) --
	(285.77,234.28) --
	(286.51,233.03) --
	(287.25,233.03) --
	(287.98,233.03) --
	(288.72,235.11) --
	(289.46,233.87) --
	(290.20,232.62) --
	(290.94,234.07) --
	(291.67,234.70) --
	(292.41,234.28) --
	(293.15,232.62) --
	(293.89,235.53) --
	(294.62,234.91) --
	(295.36,235.95) --
	(296.10,234.91) --
	(296.84,236.57) --
	(297.58,235.11) --
	(298.31,235.53) --
	(299.05,233.03) --
	(299.79,235.11) --
	(300.53,234.28) --
	(301.26,233.45) --
	(302.00,232.62) --
	(302.74,230.95) --
	(303.48,233.03) --
	(304.21,234.49) --
	(304.95,235.95) --
	(305.69,238.44) --
	(306.43,240.11) --
	(307.17,238.86);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.81,151.92) rectangle (315.17,245.88);
\end{scope}
\begin{scope}
\path[clip] (184.81,245.88) rectangle (315.17,253.83);

\path[] (184.81,245.88) rectangle (315.17,253.83);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.66] at (223.60,247.58) {T=250, K=3, c=1};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.81,245.88) rectangle (315.17,253.83);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.76,355.73) -- ( 58.76,361.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.65,355.73) -- ( 95.65,361.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (132.54,355.73) -- (132.54,361.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.42,355.73) -- (169.42,361.42);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,262.93) -- ( 48.75,262.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,283.74) -- ( 48.75,283.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,304.55) -- ( 48.75,304.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,325.37) -- ( 48.75,325.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,346.18) -- ( 48.75,346.18);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06,259.62) {0.10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06,280.43) {0.15};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06,301.25) {0.20};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 43.06,322.06) {0.25};
\end{scope}
\begin{scope}
\path[clip] ( 54.44,253.83) rectangle (184.81,347.78);
\definecolor[named]{drawColor}{rgb}{0.83,0.83,0.83}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.76,262.93) --
	(181.72,262.93);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 77.20,265.63) --
	( 79.05,265.01) --
	( 80.89,268.13) --
	( 82.74,265.84) --
	( 84.58,267.71) --
	( 86.43,267.09) --
	( 88.27,266.47) --
	( 90.11,268.34) --
	( 91.96,268.55) --
	( 93.80,265.01) --
	( 95.65,267.71) --
	( 97.49,267.30) --
	( 99.34,265.63) --
	(101.18,263.76) --
	(103.03,264.38) --
	(104.87,263.97) --
	(106.71,265.84) --
	(108.56,264.59) --
	(110.40,265.22) --
	(112.25,265.84) --
	(114.09,267.09) --
	(115.94,263.14) --
	(117.78,265.01) --
	(119.63,264.18) --
	(121.47,263.97) --
	(123.31,265.84) --
	(125.16,263.55) --
	(127.00,262.72) --
	(128.85,262.93) --
	(130.69,264.80) --
	(132.54,267.09) --
	(134.38,267.51) --
	(136.23,268.13) --
	(138.07,269.17) --
	(139.91,268.34) --
	(141.76,269.38) --
	(143.60,267.30) --
	(145.45,264.59) --
	(147.29,267.30) --
	(149.14,266.47) --
	(150.98,269.80) --
	(152.83,266.05) --
	(154.67,265.63) --
	(156.51,266.47) --
	(158.36,269.80) --
	(160.20,269.80) --
	(162.05,270.21) --
	(163.89,269.80) --
	(165.74,267.09) --
	(167.58,266.47) --
	(169.42,264.59);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,253.83) rectangle (184.81,347.78);
\end{scope}
\begin{scope}
\path[clip] ( 54.44,347.78) rectangle (184.81,355.73);

\path[] ( 54.44,347.78) rectangle (184.81,355.73);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 93.23,349.49) {T=100, K=3, c=0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.44,347.78) rectangle (184.81,355.73);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.12,355.73) -- (189.12,361.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.01,355.73) -- (226.01,361.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (262.90,355.73) -- (262.90,361.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (299.79,355.73) -- (299.79,361.42);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (189.12,367.12) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (226.01,367.12) {0.2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (262.90,367.12) {0.4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (299.79,367.12) {0.6};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17,262.93) -- (320.86,262.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17,283.74) -- (320.86,283.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17,304.55) -- (320.86,304.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17,325.37) -- (320.86,325.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.17,346.18) -- (320.86,346.18);
\end{scope}
\begin{scope}
\path[clip] (184.81,253.83) rectangle (315.17,347.78);
\definecolor[named]{drawColor}{rgb}{0.83,0.83,0.83}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.12,262.93) --
	(312.08,262.93);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.57,284.78) --
	(209.41,283.12) --
	(211.26,284.36) --
	(213.10,286.86) --
	(214.95,287.28) --
	(216.79,290.40) --
	(218.63,289.78) --
	(220.48,291.44) --
	(222.32,294.15) --
	(224.17,294.56) --
	(226.01,294.98) --
	(227.86,297.89) --
	(229.70,299.14) --
	(231.54,299.77) --
	(233.39,297.89) --
	(235.23,299.35) --
	(237.08,301.43) --
	(238.92,306.84) --
	(240.77,307.05) --
	(242.61,307.26) --
	(244.46,306.63) --
	(246.30,306.84) --
	(248.14,309.96) --
	(249.99,310.80) --
	(251.83,311.21) --
	(253.68,311.42) --
	(255.52,313.50) --
	(257.37,311.84) --
	(259.21,312.67) --
	(261.06,314.13) --
	(262.90,316.00) --
	(264.74,319.75) --
	(266.59,321.83) --
	(268.43,319.75) --
	(270.28,322.24) --
	(272.12,321.20) --
	(273.97,320.58) --
	(275.81,322.24) --
	(277.66,325.99) --
	(279.50,326.61) --
	(281.34,330.36) --
	(283.19,331.19) --
	(285.03,329.11) --
	(286.88,329.94) --
	(288.72,328.28) --
	(290.57,329.53) --
	(292.41,329.94) --
	(294.26,329.53) --
	(296.10,332.03) --
	(297.94,330.98) --
	(299.79,332.44);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.81,253.83) rectangle (315.17,347.78);
\end{scope}
\begin{scope}
\path[clip] (184.81,347.78) rectangle (315.17,355.73);

\path[] (184.81,347.78) rectangle (315.17,355.73);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.66] at (223.60,349.49) {T=100, K=3, c=1};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,397.48);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.81,347.78) rectangle (315.17,355.73);
\end{scope}
\end{tikzpicture}

### 2017-04-21 1-intro.tex
[#40/move] Move extended example from Section 3.3 to appendix

--- 2016-03-09 paper.tex
@@
-\documentclass[12pt,draft]{article}
-\input{setup}
-
-\title{Out-of-Sample Comparisons of Overfit Models}
-\author{Gray Calhoun\thanks{email: gcalhoun@iastate.edu. I
-    would like to thank Julian Betts, Helle Bunzel,
-    St\'ephane Bonhomme, Marjorie Flavin,
-    Nir Jaimovich, Lutz Kilian, Ivana Komunjer, Michael McCracken,
-    Seth Pruitt, Ross Starr, Jim Stock, Yixiao Sun, Allan Timmermann,
-    Hal White, several anonymous referees, participants at the 2010
-    Midwest Economics Association Annual Meetings, the 2010
-    International Symposium on Forecasting, the 2010 Joint Statistical
-    Meetings, the 2011 NBER-NSF Time-Series
-    Conference, and in many seminars at UCSD, and especially
-    Graham Elliott for their valuable suggestions, feedback and advice
-    in writing this paper.  I would also like to thank Amit Goyal for
-    providing computer code and data for his 2008 RFS paper
-    with Ivo Welch \citep{GoW:08}.} \\ Iowa State University}
-
-\date{\VERSION}
-
-\begin{document}
-\maketitle
-
-\begin{abstract}\noindent
-  This paper uses dimension asymptotics to study the behavior of
-  out-of-sample (OOS) test statistics when they are used to compare
-  ``overfit'' linear regression models. Under these asymptotics, the
-  number of predictors used by the larger model increases with the
-  number of observations so that their ratio remains uniformly
-  positive. This analysis gives a theoretical motivation for using
-  out-of-sample (OOS) comparisons: the Diebold-Mariano-West OOS $t$-test
-  (Diebold and Mariano, 1995, \textit{JBES}, and West, 1996,
-  \textit{Econometrica}) allows a forecaster to conduct inference
-  about the models' generalization error, an important measure of
-  forecast accuracy that conditions on the models' parameter estimates.
-  We show analytically and through Monte Carlo that standard full-sample
-  test statistics can not test hypotheses about this measure of performance.
-  Our paper also suggests that comparisons of overfit models require small
-  OOS test samples. If $P$ denotes the number of observations used for the
-  OOS comparison and $T$ the total number of observations, $P^2/T$ must
-  converge to zero for the OOS $t$-test to be centered on the model's
-  generalization error.
-
-\noindent JEL Classification: C12, C22, C52, C53
-
-\noindent Keywords: Generalization Error, Forecasting, Model
-Selection, $t$-test, Dimension Asymptotics
-\end{abstract}
-\newpage
-
 \section{Introduction}
@@
 alternative, and shows that standard model selection methods can run
-into similar problems. Section~\ref{sec:theory} also presents an
-example DGP that illustrates these results. Section~\ref{sec:mc}
+into similar problems. Section~\ref{sec:mc}
 presents a Monte Carlo study supporting our theoretical results.
@@
 Section~\ref{sec:conclusion} concludes.  Proofs and supporting results
-are listed in the Appendix.
-
-\section{Setup and assumptions}
-\label{sec:assumptions}
-
-The first part of this section will describe the environment in detail
-and set up our models and notation. The second part lists the
-assumptions underlying our theoretical results.
-
-\subsection{Notation and forecasting environment}
-
-We assume the following forecasting environment. There are two
-competing linear models that give forecasts for the target,
-$y_{t+\h}$:
-\begin{equation*}
-y_{t+\h} = x_{1t}'\theta_1 + \e_{1,t+h}, \quad\text{and}\quad
-y_{t+\h} = x_{2t}'\theta_2 + \e_{2,t+h};
-\end{equation*}
-$t = 1,\dots,T-h$, $\h$ is the forecast horizon and the
-variables $y_t$, $x_{1t}$, and $x_{2t}$ are all known in period $t$.
-The coefficients $\theta_1$ and $\theta_2$ minimize the population
-Mean Square Error, so
-\begin{equation*}
-  \theta_i = \argmin_\theta \sum_{t=1}^{T-\h} \E (y_{t+\h} - x_{it}'\theta)^2,
-\end{equation*}
-making $\e_{i,t+\h}$ uncorrelated with $x_{i,t}$; $\e_{i,t+\h}$ can exhibit
-serial correlation so both of the linear models may be misspecified.
-Let $\mathcal{F}_t = \sigma(y_1, x_1, \dots, y_t, x_t)$ be the information
-set available in period $t$,
-with $x_t$ the vector of all stochastic elements of $x_{1t}$ and $x_{2t}$ after
-removing duplicates, and let $\E_t$ and $\var_t$ denote the
-conditional mean and variance given $\mathcal{F}_t$.  The first model
-uses $K_1$ regressors, and the second uses $K_2$.  Without loss of
-generality, assume that $K_1 \leq K_2$. At least one of the models is
-overfit, which we represent asymptotically by letting $K_2$ grow with
-$T$ quickly enough that $\lim K_2/T$ is positive; $K_1$ may grow with
-$T$ as well. Since the models change with $T$, a
-stochastic array underlies all of our asymptotic theory, but we
-suppress that notation to simplify the presentation.
-
-In the settings we are interested in, a forecaster observes the data
-$(y_t,x_t)$ for periods 1 through $T$ and divides these observations
-into an estimation sample of the first $R$ observations and a test
-sample of the remaining $P$ observations. The forecaster then compares
-the models' performance over the test sample, which entails
-constructing two sequences of forecasts with a fixed-window
-estimation strategy,
-\begin{equation*}
-\hat y_{i,t+\h} = x_{it}'\hat{\theta}_{it}, \qquad \text{for } i=1,2;
-\ t = R+1,\dots,T-h,
-\end{equation*}
-where
-\begin{equation*}
-  \bh{it} = \Big(\sum_{s=1}^{R-\h} x_{is}x_{is}'\Big)^{-1} \sum_{s=1}^{R-\h}
-  x_{is} y_{s+\h}, \qquad
-  \text{for } i=1,2;\ t = R+1,\dots, T - \h.\footnote{%
-    It may not be clear why we are using the index $t$ in $\bh{it}$,
-    since $\bh{it} = \bh{iR}$ almost surely for all $t \leq T-h$.
-    But $\bh{it}$ will be defined for $t > T-\h$
-    soon and will not equal $\bh{iR}$ for those values of $t$.} %
-\end{equation*}
-
-The models are then compared by their forecast performance over the test
-sample. There are many statistics that have been considered in the
-literature, but we focus on perhaps the most natural, the DMW \oost\
-test \citep{DiM:95,Wes:96}.\footnote{%
-  The core insights of our paper apply to other OOS statistics as
-  well.} %
-This statistic is based on
-the difference in the models' loss over the test sample, $\oosA$,
-defined as
-\begin{equation*}
-  \oosA \equiv P^{-1} \oosSum{t}{1} D_t
-\end{equation*}
-where
-\begin{equation*}
-  D_t = L(y_{t+\h} - x_{1t}'\bh{1t}) - L(y_{t+\h} - x_{2t}'\bh{2t}),
-\end{equation*}
-and $L$ is a known loss function. The \oost\ test is defined as
-$\sqrt{P} \oosA / \sh$, where $\sh^2$ is an estimator of the
-asymptotic variance of $\oosA$. (Possibly a Heteroskedasticity- and
-Autocorrelation-Consistent, or HAC, estimator.)
-
-Most theoretical research on these statistics, such as \citet{DiM:95}, \citet{Wes:96},
-and \cite{Mcc:07}, has focused on using the \oost\ statistic to test
-hypotheses about the pseudotrue values $\theta_1$ and $\theta_2$.  In
-particular, that research focuses on testing the null hypothesis that
-\begin{equation*}
-  \E L(y_{t+\h} - x_{1t}'\theta_{1}) = \E L(y_{t+\h} - x_{2t}'\theta_{2}).
-\end{equation*}
-But the population quantities in this equation do not determine which
-model is more accurate in practice. The models'
-accuracy will also depend on the specific estimates of $\theta_1$ and
-$\theta_2$ used to produce the forecasts.
-
-When the forecaster will use one of the models to make a number of
-predictions (call it $Q$) in the future, the quantity of interest
-becomes
-\begin{equation*}
-  \E_T \oosB = Q^{-1} \sum_{t=T+1}^{T+Q} \E_T D_t,
-\end{equation*}
-where $D_t$ is defined as before,
-\begin{equation*}
-  D_t = L(y_{t+\h} - x_{1t}'\bh{1t}) - L(y_{t+\h} - x_{2t}'\bh{2t}),
-\end{equation*}
-but now uses the full-sample estimates of the models' parameters,
-\begin{equation*}
-  \bh{it} = \Big(\sum_{s=1}^{T-\h} x_{is}x_{is}'\Big)^{-1} \sum_{s=1}^{T-\h}
-  x_{is} y_{s+\h}, \qquad \text{for } i=1,2;\ t = T+1,\dots, T + Q.
-\end{equation*}
-If $\E_T \oosB$ is positive, the second model is expected to forecast
-better than the first over the next $Q$ periods, and if $\E_T \oosB$
-is negative then the first model is better. We use a conditional
-expectation because the coefficient estimates in $\oosB$ are
-stochastic but known in period $T$, and their values will determine
-the performance of the two models.
-
-Under conventional fixed-$K$ asymptotic theory, $\E_T \oosB$ would
-converge in probability to the difference in the expected loss
-associated with the pseudotrue models,\footnote{%
-  This statement is subject to the usual assumptions: some form of
-  stationarity, bounded moments, and weak dependence.} %
-\begin{equation}\label{eq:22}
-  \E L(y_{t+\h} - x_{1t}'\theta_{1}) - \E L(y_{t+\h} - x_{2t}'\theta_{2}).
-\end{equation}
-But if $K_2$ increases with $T$ these quantities can have different
-limits. For a simple example, assume squared-error loss, let $x_{1,t}
-= 1$ for all $t$, and let $(y_{t+\h},x_{2,t})$ be i.i.d. $N(0,
-\Sigma)$.  Then the difference between $\E_T \oosB$ and
-the in quantity~\eqref{eq:22} is
-\begin{align*}
-  \E_T \oosB - \big(\E L(y_{t+\h} - x_{1t}'\theta_{1}&) - \E L(y_{t+\h} - x_{2t}'\theta_{2})\big) \\
-  &= \big(\E_T (y_{T+\h+1} - \bh{1,T})^2 -
-     \E_T (y_{T+\h+1} - x_{T+1}'\bh{2,T})^2\big) \\
-     &\quad - \big(\E y_{T+\h+1}^2 - \E (y_{T+\h+1} - x_{T+1}'\theta_2)^2 \big)\\
-  &= (\bh{2,t} - \theta_2)' \var(x_{2,t})\, (\bh{2,t} - \theta_2) + o_p(1).
-\end{align*}
-This last term has expectation equal to $\var(y_T) \frac{K_2}{T - K_2 - 1}$ and
-would converge to zero in probability if $K_2$ were fixed, but does not when $\lim
-K_2 / T > 0$. In Section~\ref{sec:oostheory} we show that the \oost\
-statistic can estimate $\E_T \oosB$ under our increasing $K$
-asymptotics and does not estimate the expected loss associated with
-the pseudotrue coefficients.
-
-The conditional expectation $\E_T \oosB$ has been studied heavily in
-cross-sectional settings with independent observations. In such a
-setting, $\E_T \oosB$ is equal to the difference in the models'
-\emph{generalization error}, which has been used widely as a measure
-of model accuracy in the machine
-learning literature \citep[see][for further discussion]{HTF:08}.
-Moreover, with i.i.d. observations, the expectation of $\E_T \oosB$
-equals \citepos{Aka:69} Final Prediction Error (FPE). Both
-generalization error and FPE are defined by a model's
-performance on a new, independent, data set, but, for lack of a better
-term, we will call $\E_T \oosB$ the ``difference in generalization error''
-for the rest of the paper with hopefully no risk of confusion.
-
-Finally, define the following notation.  The $l_v$-norm for vectors in
-$\Re^p$ (with $p$ arbitrary) is denoted $\lvert \cdot \rvert_v$, and
-the $L_v$-norm for $L_v$-integrable random variables is $\lVert \cdot
-\rVert_v$.  The functions $\eigen_i(\cdot)$ take a square-matrix
-argument and return its $i$th eigenvalue (with $\eigen_{i}(A) \leq
-\eigen_{i+1}(A)$ for any matrix $A$).  All limits are taken as $T \to
-\infty$ unless stated otherwise.
-
-\subsection{Assumptions}
-\label{sec:asmp}
-
-The next conditions are assumed to hold throughout the paper.  The first
-assumption controls the dependence of the underlying random array.
-The second lays out the details of our asymptotic approximation.
-The third assumption controls the
-smoothness of the loss function and bounds the moments of the
-difference in the models' performance; the fourth assumption describes
-the behavior of the estimation and test windows.  And the last
-assumption describes the kernel used to estimate the OOS average's
-asymptotic variance.
-
-\begin{asmp}\label{asmp-1}
-  The random array $\{y_t,x_t\}$ is strictly stationary and absolutely regular
-  with coefficients $\beta_j$ of size $-\rho/(\rho-2)$; $\rho$ is
-  greater than two and discussed further in Assumption \ref{asmp-3}.
-\end{asmp}
-
-This assumption is a standard condition on the dependence of the
-underlying stochastic array. The only novelty is that we use
-absolute regularity instead of strong or uniform mixing as our
-weak dependence condition; absolute regularity admits a particular
-coupling argument, \emph{Berbee's Lemma} \citep[reproduced in this
-paper as Lemma A.1 for reference]{Ber:79} that is
-unavailable for strong mixing sequences. Absolute regularity
-implies uniform mixing but is more restrictive than strong mixing,
-so this assumption is not unduly strong.
-For a detailed discussion of these weak dependence conditions,
-please see \citet{Dav:94} or \citet{Dou:94}.
-
-Our strict stationarity assumption is also somewhat stronger than is
-typically used; \citet{Wes:96} and \citet{Mcc:07}, for example,
-present results assuming covariance stationarity of the loss
-associated with the pseudotrue models. We need to make a stronger
-assumption because we will need to prove asymptotic results when the
-$\bh{it}$ remain random---so we would need covariance stationarity to
-hold for almost all estimates of $\theta_i$ and not just for the
-pseudotrue value. The only way to guarantee that condition is to
-assume strict stationarity for the underlying stochastic processes.
-
-The next assumption describes our asymptotic experiment.
-\begin{asmp}\label{asmp-2}
-  The number of regressors for each model, $K_1$ and $K_2$, are less
-  than $R$ and $(K_2-K_0)/T$ is uniformly positive;
-  $K_0$ is the number of regressors shared by the two models ($(K_1 - K_0)/T$
-  may be uniformly positive as well, but is not required to be).
-
-  The variance of $y_{t+\h}$ given $\mathcal{F}_t$ is uniformly
-  positive and finite and all of the eigenvalues of the covariance
-  matrix of $x_t$ are uniformly positive and finite as well.
-  Moreover,
-  \begin{equation}
-    \eigen_{\max}(X_{iS}'X_{iS}) = O_{L_3}(S),
-  \end{equation}
-  \begin{equation}
-    \eigen_{\max}((X_{iS}'X_{iS})^{-1}) = O_{L_3}(1/S),
-  \end{equation}
-  \begin{multline}\label{eq:28}
-    \eigen_{\max}\Bigg(\E\Big(
-    \sum_{s,t=U}^{V-\h} \e_{i,s+\h} \e_{i,t+\h} x_{is}x_{it}'
-    \mBig
-    x_{i1},\dots,x_{i,U-1};
-    \sum_{s=U}^{V-\h} x_{is} x_{is}';
-    x_{i,V-\h+1},\dots,x_{i,T-\h}
-    \Big)\Bigg) \\
-    = O_{L_3}(\max(V-U, K_i)),
-  \end{multline}
-  and
-  \begin{multline}\label{eq:8}
-    \tr \E\Big(
-    \sum_{s,t=U}^{V-\h} \e_{i,s+\h} \e_{i,t+\h} x_{is}x_{it}'
-    \mBig
-    x_{i1},\dots,x_{i,U-1};
-    \sum_{s=U}^{V-\h} x_{is} x_{is}';
-    x_{i,V-\h+1},\dots,x_{i,T-\h}
-    \Big)\Bigg) \\
-    = O_{L_3}((V-U) \times K_i)
-  \end{multline}
-  for large enough $T$, where $S = R,\dots,T$, $1 \leq U \leq V - \h
-  \leq T - \h$, $i = 1,2$,
-  \[ X_{iS} \equiv [x_{i1} \quad \dots \quad x_{i,S-\h}]' \qquad
-  \text{and} \qquad \ep{iS} = (\e_{i,1+\h}, \dots, \e_{i,S})'.\]
-
-  Additionally, the Euclidean norms of the pseudotrue coefficients,
-  $\theta_1$ and $\theta_2$, satisfy $|\theta_1|_2 = O(1)$ and
-  $|\theta_2|_2 = O(1)$.
-\end{asmp}
-
-The assumption on $K_1$ and $K_2$ is crucial to the paper; we assume
-that the model complexity grows with $T$ fast enough to break
-consistency. This assumption is how we derive an asymptotic
-concept of ``overfit.''
-
-The assumption that $y_{t+\h}$ and $x_t$ have positive and finite
-variance is straightforward. The conditions on the eigenvalues are
-technical and control the behavior of the OLS estimator as the number
-of regressors gets large---the third and fourth assumptions are
-nonstandard but can be easily verified under, for example,
-independence. Section~\ref{sec:example} contains such an example. The
-restrictions on the pseudotrue coefficients ensure that the regression
-model doesn't dominate the variance of $y_{t+\h}$ in the limit.
-
-The next assumption establishes moment conditions for the OOS loss
-process and smoothness conditions for the loss function itself. The
-moment conditions are standard and apply to $D_t$, and the smoothness
-conditions are relatively weak.
-
-\begin{asmp}\label{asmp-3}
-  The loss function $L$ is continuous, has finite left and right
-  derivatives, and $L(0) = 0$.  There is a constant $B_L$ and a
-  function $L'$ that bounds the left and right derivative of $L$ at
-  every point such that $\|D_t\|_\rho \leq B_L$; $\|D_t^*\|_\rho \leq
-  B_L$ for all $t$, where
-  \begin{equation}
-    D_t^* = L(y^* - x_1^{*\prime}\hat\theta_{1t})
-    - L(y^* - x_2^{*\prime}\hat\theta_{2t})
-  \end{equation}
-  and $(y^*, x_1^*, x_2^*)$ equals $(y_t, x_{1t}, x_{2t})$ in
-  distribution but is independent of $\mathcal{F}_T$ ($\rho$ is defined
-  in Assumption~\ref{asmp-1}); and
-  \begin{equation}\label{eq:29}
-    \| L'(y^* - x_{i}^{*\prime} (\alpha \bh{iR} + (1-\alpha) \bh{iT})) \|_2
-    \leq B_L
-  \end{equation}
-  for any $\alpha \in [0,1]$.
-\end{asmp}
-
-The differentiability condition in Assumption~\ref{asmp-3} is weak and
-allows the loss function itself to be non-differentiable; for example,
-absolute error and many asymmetric loss functions satisfy this
-assumption. The assumption makes use of both $(y_{t+\h}, x_{1t},
-x_{2t})$ and $(y^*, x_1^*, x_2^*)$ because the period $t$ observations
-can be dependent on $\bh{iT}$ in complicated ways. When the underlying
-observations are independent these assumptions can simplify
-considerably.
-
-The next assumption controls the growth of the test and
-training samples.
-\begin{asmp} \label{asmp-4} (a) $P, R, Q \to\infty$ as $T \to
-  \infty$. (b) $P^2/T \to 0$ and $P/Q \to 0$ as $T \to \infty$.
-\end{asmp}
-
-The requirements that $P$ and $R$ grow with $T$ are common. Parts of
-the assumption are new, in particular the requirement that $P^2/T \to
-0$.  See Lemma~\ref{res-convergence} for a discussion of its
-implications.  In practical terms, this assumption requires that the
-test sample be large and that the training sample be much larger, by
-enough that including or excluding the test sample does not affect the
-estimates of $\theta_1$ or $\theta_2$ very much.
-
-A final assumption restricts the class of variance estimators we will
-consider.  We use the same class of estimators studied by
-\citet{JoD:00} (their class $\mathcal{K}$); see
-their paper for further discussion.
-
-\begin{asmp}
-  \label{asmp-5} $W$ is a kernel from
-$\Re$ to $[-1,1]$ such that $W(0) = 1$, $W(x) = W(-x)$ for all $x$,
-\begin{equation}
-  \int_{-\infty}^{\infty} \lvert W(x) \rvert dx < \infty, \quad
-  \int_{-\infty}^{\infty} \lvert \psi(x) \rvert dx < \infty
-\end{equation}
-with
-\begin{equation}
-  \psi(x) = \frac1{\sqrt{2\pi}} \int_{-\infty}^{\infty} W(z) e^{ixz}dz,
-\end{equation}
-and $W(\cdot)$ is continuous at zero and all but a finite number of
-points.
-\end{asmp}
-
-These assumptions are broadly similar to those existing in the
-literature, with some differences in our assumptions relating the
-estimated coefficients to future values of the DGP.
-Section~\ref{sec:example} contains an extended example that shows how
-these assumptions are satisfied in a simple setting.
-
-\section{Theoretical results}
-\label{sec:theory}
-
-This section lays out our theoretical results. The first subsection
-presents results for the DMW \oost\ test; we show that it is
-asymptotically normal when one or both forecasting models is overfit.
-(i.e., under our increasing-$K$ asymptotic approximation.) We also
-present a new limitation on these statistics---OOS comparisons heavily
-penalize overfit models unless the size of the test sample is a very
-small proportion of the total sample size, which will not be practical
-in much applied research. The second subsection presents results for
-full-sample statistics and shows that widely used test statistics and
-model selection criteria are misleading when choosing a model for
-forecasting. In contrast to OOS comparisons, these full-sample
-criteria choose overfit models too often, even when they are less
-accurate than simple benchmark models. These results are somewhat
-abstract, so the third subsection works through an example DGP in
-detail.
-
-\subsection{Asymptotic normality of the DMW test}
-\label{sec:oostheory}
-
-This section has two main conceptual results. The first,
-Lemma~\ref{res-mixingale}, shows that the OOS average, $\oosA$, is
-asymptotically normal as the size of the test sample grows, even when
-the models are overfit. But $\oosA$ is centered at $\E_R \oosA$, the
-difference in the generalization error of the models estimated over
-the \emph{training sample}, which is not the quantity of interest to
-forecasters. Forecasters will generally want to estimate or test
-hypotheses about the difference in the generalization error of the
-models estimated with the full sample, $\E_T \oosB$. Our second
-result, Lemma~\ref{res-convergence}, shows that these quantities are
-approximately equal only when the test sample is very small relative
-to the total sample size. In particular, we show that $\oosA$ is a
-consistent estimator of $\E_T \oosB$ when $P/T \to 0$ and is
-asymptotically normal with mean $\E_T \oosB$ when $P^2/T \to 0$. After
-establishing these Lemmas, we then show that the \oost\ test is
-asymptotically standard normal and can be used to test hypotheses
-about $\E_T \oosB$, which requires the two Lemmas as well as a
-consistent estimator of the variance of the OOS average.
-
-In the first result, we show that
-$\sqrt{P} (\oosA - \E_R \oosA)$ is asymptotically normal as $P \to
-\infty$. This application of the CLT is complicated by a hidden source
-of dependence---the training sample estimators $\bh{iR}$. Under
-conventional asymptotic theory, we would replace each $\bh{iR}$ with
-its pseudotrue value $\theta_i$ and apply the CLT to
-$L(y_{t+\h} - x_{it}'\theta_i)$, with some complications potentially
-arising from the replacement (as in \citealp{Wes:96},
-\citealp{ClM:01}, or \citealp{Mcc:07}, for example). But we can not
-make that replacement here, because our asymptotic approximation
-prevents $x_{it}'\bh{iR}$ from converging to $x_{it}'\theta_i$.
-
-Instead, we show that $D_t - \E_R D_t$ is an $L_2$-mixingale that
-satisfies the CLT. Mixingales satisfy a weak-dependence condition
-similar to MDSes,\footnote{%
-  An array $Z_{n,t}$ and an increasing sequence of \sfields
-  $\Gs_{n,t}$ is an \emph{$L_2$-mixingale of size $-1/2$} if there is
-  an array of constants $\{c_{n,t}\}$ and a sequence of constants
-  $\zeta_l = O(l^{-1/2 - \delta})$ for some $\delta > 0$ such that
-  \begin{equation*}
-    \lVert \E(Z_{n,t} \mid \Gs_{n,t-l}) \rVert_2
-    \leq c_{n,t} \zeta_l
-    \qquad\text{and}\qquad
-    \lVert Z_{n,t} - \E(Z_{n,t} \mid \Gs_{n,t+l}) \rVert_2
-    \leq c_{n,t} \zeta_{l+1}.
-  \end{equation*}
-  Mixingales were introduced and developed by
-  \citet{Mcl:74,Mcl:75,Mcl:75b,Mcl:77}.} %
-but they have some limitations. Transformations of mixingales are
-typically not themselves mixingales, which means that CLTs for
-mixingale processes require additional assumptions to hold beyond the
-mixingale property.\footnote{%
-  See \citet{Jon:97} for an illustration. We will borrow heavily from
-  his results in our proofs.} %
-This is in contrast to Near Epoch Dependent (NED) processes, which
-retain the NED property after transformations. \citep[See chapter 17
-of][for further discussion of these properties.]{Dav:94} But the OOS
-loss has more structure than most mixingales and behaves like an NED
-process in important respects. (The key result here is
-Lemma~\ref{lem:a2} in the Appendix.) Lemma~\ref{res-mixingale} presents the
-CLT that we use later, and Section~\ref{sec:example} works through an
-i.i.d. example in detail. For i.i.d. observations, the OOS loss is an
-MDS and is easier to work with.
-
-\begin{lem}\label{res-mixingale}
-  If Assumptions~\ref{asmp-1}--\ref{asmp-3} hold then $\{D_t - \E_R
-  D_t, \mathcal F_t\}$ is an $L_2$-mixingale of size $-1/2$.
-  Moreover
-  \begin{equation}
-    \sqrt{P}(\oosA - \E_R \oosA)/\sigma \to^d N(0,1)
-  \end{equation}
-  as $P \to \infty$ if $\sigma^2$ is uniformly almost surely positive,
-  where $\sigma^2 = \var_R(\sqrt{P} \oosA)$ (which is equal to $P
-  \E_R(\bar{D}_R - \E_R \bar{D}_R)^2$).
-\end{lem}
-
-It may be helpful to compare Lemma~\ref{res-mixingale} to the method
-of proof in \citet{GiW:06}. \citet{GiW:06} show that the OOS average
-is asymptotically normal when the forecasts are estimated with a fixed
-length rolling window. In that case, each $\bh{it}$ depends on only
-the most recent $R$ observations and, since $R$ is fixed in their
-theory, the forecast errors $y_{t+\h} - x_{it}'\bh{it}$ are themselves
-mixing processes. Transformations of their forecast errors are
-still obviously mixing processes and obey the CLT.
-
-In our paper, $R$ is not fixed and the forecast errors are not a
-convenient weakly-dependent process, since the estimation error in
-$\bh{it}$ introduces strong dependence. Consequently,
-transformations of the forecast errors are not weakly dependent
-either. But this additional dependence has a special form and can be
-removed by subtracting the conditional mean; specifically $g(y_{t+\h} -
-x_{it}'\bh{it})$ is not weakly dependent but $g(y_{t+\h} -
-x_{it}'\bh{it}) - \E_R g(y_{t+\h} - x_{it}'\bh{it})$ is.
-Assumptions~\ref{asmp-1}--\ref{asmp-3} allow us to show directly
-that $D_t - \E_R D_t$ and (crucially) $D^2_t - \E_R D_t^2$ are both
-weakly dependent mixingales, ensuring Lemma~\ref{res-mixingale}.
-
-The next Lemma connects $E_R \oosA$ to $\E_T \oosB$, the difference in
-the models' generalization error. Under conventional asymptotics,
-these quantities are generally close. But they are not for overfit
-models and the models will tend to forecast better when estimated over the
-full sample than over the training sample. Consequently, OOS
-comparisons will penalize overfit models too much unless the test
-sample is small relative to the total data set.
-
-\begin{lem} \label{res-convergence}
-  Under Assumptions \ref{asmp-1}--\ref{asmp-4}a,
-  \begin{equation}\label{eq:7}
-    \E_T \oosB - \E_R \oosA = O_p(\sqrt{P/T}) + o_p(P^{-1/2})
-    + o_p(Q^{-1/2}).
-  \end{equation}
-\end{lem}
-We can view $\E_T \oosB - \E_R \oosA$ as noise introduced by
-approximating the performance of the full-sample estimates with that
-of the partial-sample estimates. The key term on the RHS
-of~\eqref{eq:7} in practice is $O_p(\sqrt{P/T})$---unless $P/T$ is
-small, this noise dominates the OOS average, making it an inconsistent
-estimator of $\E_T \oosB$. The $o_p(P^{-1/2})$ term is completely
-unrestrictive in our applications because we will multiply the OOS
-average by at most $\sqrt{P}$ (for the CLT). And the $o_p(Q^{-1/2})$
-term has some implications for interpreting these results: we can only
-measure the average performance of the forecasting models for an
-extended period in the future, long enough that the future
-observations are essentially independent of the current
-information. For $Q=1$, for example, the dependence between
-$y_{T+\h+1}$ and the current information set $\Fs_T$ may be very
-strong.
-
-Finally, we can use Lemmas~\ref{res-mixingale}
-and~\ref{res-convergence} to show that the DMW test is asymptotically
-normal and centered at $\E_T \oosB$, as long as
-Assumption~\ref{asmp-4}b holds.
-
-\begin{thm}\label{res-oost}
-  Suppose that Assumptions \ref{asmp-1}--\ref{asmp-5} hold (including
-  \ref{asmp-4}b), that $\gamma \to \infty$ and $\gamma/P \to 0$ as $T
-  \to \infty$, and that $\sigma^2$ is uniformly a.s. positive. Define
-  $\sh^2$ to be the usual OOS HAC estimator of the asymptotic variance
-  of $\oosA$,
-  \begin{equation}
-    \sh^2 \equiv P^{-1} \oosSum{s,t}{1} (D_t - \oosA)(D_s - \oosA)
-    \vWeight.
-  \end{equation}
-  Then
-  \begin{equation}
-    \sqrt{P}(\oosA - \E_T\oosB)/\sh \to^d N(0,1).
-  \end{equation}
-\end{thm}
-
-The requirement that $\sigma^2$ be uniformly a.s. positive is not
-restrictive under our asymptotic theory. Since the models'
-coefficients are estimated with uncertainty in the limit, the two
-models give different forecasts even if they both nest the DGP.  This
-is intuitively similar to \citepos{GiW:06} rolling-window result, but
-comes from different asymptotic theory; Giacomini and White keep the
-variance of the OOS average positive by letting $P \to \infty$ with
-$R$ fixed; in this paper, $R \to \infty$ but the variance remains
-positive since $K \to \infty$ (quickly) as well.
-
-If $K_1$ and $K_2$ were finite, West's (1996) and McCracken's (2007)
-asymptotic theories would apply and the \oost\ test would remain normal as long
-as $P/T \to 0$, even if $\sigma^2 \to 0$. Under that asymptotic
-approximation, the variance will converge to zero whenever the true
-DGP is nested in both of the forecasting models. The same principles
-may also apply if $K_1$ and $K_2$ grow slowly, with $K_2/T \to
-0$. It is likely that a second order expansion along the lines of
-\citet{Mcc:07} would lead to asymptotic normality for that
-intermediate case, but we leave that issue to future research.
-
-Finally, Theorem~\ref{res:oostest} establishes that the DMW test can be
-use to construct confidence intervals for $\E_T \oosB$ and test
-hypotheses about $\E_T \oosB$. In particular, forecasters will often
-want to test the null hypothesis that $\E_T \oosB \leq 0$, meaning
-that the benchmark model is expected to be more accurate than the
-alternative model in the future.
-
-\begin{thm}\label{res:oostest}
-  Suppose that the conditions of Theorem
-  \ref{res-oost} hold. Then each of the usual Gaussian
-  confidence intervals,
-  \begin{gather}
-    [\oosA - z_{\alpha/2} \, \sh /
-    \sqrt{P}, \oosA + z_{\alpha/2} \sh / \sqrt{P}],\label{interval-twosided} \\
-    [\oosA - z_{\alpha} \, \sh / \sqrt{P}, +\infty), \label{interval-greater}
-    \intertext{and}
-    (-\infty, \oosA + z_{\alpha} \, \sh / \sqrt{P}],
-  \end{gather}
-  contains $\E_T\oosB$ with probability $\alpha$ in the limit, with
-  $z_{\alpha}$ the $1-\alpha$ quantile of the standard normal
-  distribution. If, in addition, $\lim \Pr[\E_T \oosB \leq 0]$ is
-  positive then
-  \begin{equation}\label{eq:23}
-    \lim \Pr[P^{1/2}\oosA/\sh > z_{\alpha} \mid \E_T
-    \oosB \leq 0] \leq \alpha.
-  \end{equation}
-\end{thm}
-\noindent
-The results for confidence intervals in Theorem~\ref{res:oostest}
-follow immediately from Theorem~\ref{res-oost},
-but~\eqref{eq:23} requires additional proof.
-
-\subsection{Failure of in-sample statistics for forecast evaluation}
-\label{sec:insample}
-
-In this subsection we look at the behavior of some full-sample
-statistics under the same asymptotic theory as before.  We show that
-these statistics, which include common tests such as the Wald test as
-well as model selection criteria such as the AIC, do not measure the
-models' generalization error and consequently do not indicate which
-model will be more accurate in the future. Some of these statistics
-will tend to choose the larger model regardless of which model will be
-more accurate in the future, whereas others tend to choose the smaller
-model.  This is a different issue than whether or not full-sample
-tests are valid for testing hypotheses about the pseudotrue
-coefficients of the models; as \citet{Cal:11c} and \citet{Ana:12}
-demonstrate, variations of the Wald test can be valid for those
-hypotheses under increasing-$K$ asymptotics.\footnote{%
-  \citet{Ana:12} shows that the Wald test is invalid in general and
-  gives an adjustment that corrects the critical values; he also shows
-  that the $F$-test is asymptotically valid under certain conditions
-  on the distribution of the regressors.  \citet{Cal:11c} shows that
-  the $F$-test is asymptotically invalid without Anatolyev's
-  constraint, even under homoskedasticity, and provides a correction
-  that gives valid tests.  Both papers only consider independent
-  observations.} %
-To simplify the presentation and the intuition we only derive results
-for nested models and for MSE loss, but the conclusions hold much more
-generally.\footnote{%
-  In this section, we define
-  $M_1 = [I_{K_1} \ 0_{K_1 \times (K_2 - K_1)}]$ and
-  $M_2 = [0_{(K_2 - K_1) \times K_2} \ I_{K_2 - K_1}]$ as the
-  selection matrices that return the first $K_1$ and the last
-  $K_2 - K_1$ elements of $\theta_2$, and assume that the regressors
-  are ordered so that the first $K_1$ elements of $x_{2,t}$ correspond
-  to $x_{1,t}$.} %
-
-The full-sample statistics we study in this paper share a common
-property. They choose the alternative model when the distance between
-a subset of their coefficient estimates and the origin exceeds a
-threshold, and choose the benchmark otherwise. For the Wald test, for
-example, this threshold is chosen so that the test has correct size
-when those coefficients are zero in population. For small models that
-can be consistently estimated, these coefficient estimates are close
-to their true values and so this criterion can be a reasonable proxy
-for the relative accuracy of the larger model.
-
-But for overfit models, the estimates will typically be far from both
-their pseudotrue values and also from zero. In that case, the Wald test and
-the AIC will both tend to choose the larger model even when it is less
-accurate than the smaller benchmark model. This phenomenon is driven
-by the dimensionality of the alternative model, since there are more
-potential values of the coefficient estimator that are far from zero
-when it has many elements. The threshold for the Wald test and the AIC
-is set by construction to be a bounded distance from the origin, and
-every other statistic that shares this property has the same behavior
-and can reject the benchmark model with high probability, even when
-it is more accurate. This behavior is
-formalized in Theorem~\ref{res:insample1}.
-
-\begin{thm}\label{res:insample1}
-  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-4} hold and let
-  $\Lambda$ be a model selection statistic that takes the values zero
-  or one; $\Lambda = 0$ indicates that the benchmark model is chosen
-  and $\Lambda = 1$ indicates the alternative.  Moreover, assume that
-  $L(e) = e^2$ and that there exist a deterministic scalar $c$
-  and a sequence of possibly random matrices $V_T$ such that
-  \begin{equation}\label{eq:25}
-    \limsup_{T \to \infty}
-    \Pr[\Lambda \geq \1\{\bh{2T}'M_2' V_T M_2\bh{2T} > c \}]
-    \to 0
-  \end{equation}
-  where the eigenvalues of $V_T$ are uniformly bounded in probability,
-  $\plim \rank(V_T)/T > 0$, and neither $V_T$ nor $c$ depend on
-  $\theta$ or the value of $\bh{2T}$.
-
-  Then there exist DGPs satisfying these assumptions such that
-  \begin{equation}\label{eq:11}
-    \liminf_{T \to \infty} \E( \Lambda \mid \E_T \oosB \leq 0 ) \geq 1/2.
-  \end{equation}
-\end{thm}
-
-As we state above,~\eqref{eq:11} means that, with high probability,
-the benchmark model is rejected even when it is more accurate. In
-general, $\delta$ can be made arbitrarily small by increasing the
-region enclosed by $\1\{\bh{2T}'M_2' V_T M_2\bh{2T}\}$ and DGPs can be
-chosen to put the limiting quantity in~\eqref{eq:11}
-arbitrarily close to 1 while still satisfying
-the assumptions of the Theorem.  The DGPs and
-statistics used in Theorem~\ref{res:insample1} are simple and
-common. They include correctly specified linear models with normal and
-homoskedastic errors; and the statistics that meet the restrictions on
-$\Lambda$ include the $F$-test and AIC.
-
-For example, the $F$-statistic for the null hypothesis that the
-benchmark model is correctly specified is known to have the form
-\begin{equation*}
-  F = \frac{\bh{2T}' M_2' ( M_2 (X_{2T}'X_{2T})^{-1} M_2' )^{-1} M_2
-    \bh{2T}}{s^2 (K_2 - K_1)}
-\end{equation*}
-where $s^2$ is the usual estimator of the variance of the regression
-error. Then let $c$ be any number greater than 1 and define
-\begin{equation*}
-  V_T = M_2' \big( M_2 \big(\tfrac{1}{s^2 (K_2 - K_1)} X_{2T}'X_{2T}\big)^{-1}
-  M_2' \big)^{-1} M_2'.
-\end{equation*}
-If Assumption~\ref{asmp-2} holds and $s^2$ is consistent then $V_T$
-has uniformly bounded eigenvalues and has rank $K_2 - K_1$, so it
-satisfies~\eqref{eq:25}.
-Robust variations of the Wald test can obviously satisfy~\eqref{eq:25}
-for similar reasons, and the AIC for nested linear models is
-equivalent to using the $F$-test with the critical value %
-$(e^{2 (K_2 - K_1) / T} - 1) \cdot (T - K_2) / (K_2 - K_1)$, %
-which converges to a finite limit, so the AIC satisfies~\eqref{eq:25}
-as well.
-
-For statistics that don't satisfy~\eqref{eq:25}, the behavior can be
-quite different. The BIC, for example, can also be written in terms of
-the $F$-statistic and is equivalent to using the critical value $(T \,
-e^{2 (K_2 - K_1) / T} - 1) \cdot (T - K_2) / (K_2 - K_1)$. This
-critical value diverges as $T \to \infty$, ensuring that~\eqref{eq:25}
-fails for any $c$. For this statistic, we have the opposite problem as
-before: when the alternative model is \emph{more} accurate, the
-coefficient estimates of the larger model are contained in a bounded
-region of the parameter space. Since the acceptance region of the BIC
-grows, it eventually contains \emph{any} bounded region of the
-parameter space. For large enough $T$, the BIC will always choose the
-\emph{smaller model}, even when the larger model is more accurate.
-
-This behavior is formalized in Theorem~\ref{res:insample2}.
-\begin{thm}\label{res:insample2}
-  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-4} hold, let $L(e) =
-  e^2$, and let $\Lambda$ be a model selection statistic as in
-  Theorem~\ref{res:insample1}. Also assume that, for any finite scalar
-  $c$,
-  \begin{equation}\label{eq:27}
-    \Pr[\Lambda \leq \1\{\bh{2T}'M_2'J M_2\bh{2T} > c \}] \to 1
-    \quad \text{as } T \to \infty.
-  \end{equation}
-
-  Then there exist DGPs satisfying these assumptions such that
-  \begin{equation}\label{eq:15}
-    \E( \Lambda \mid \E_T \oosB \geq 0 ) \to^p 0.
-  \end{equation}
-\end{thm}
-
-The condition~\eqref{eq:27} requires that the acceptance region of
-$\Lambda$ eventually contains any finite cylinder centered at the
-origin. Again,~\eqref{eq:15} implies that statistics like the BIC
-will always choose the smaller model for some DGPs, even when the
-larger model will give more accurate forecasts. Both models may be
-overfit, in that both $K_1/T$ and $K_2/T$ may both be positive in the
-limit; the key is that $(K_2 - K_1)/T$ is also positive in the limit.
-
-It is important to remember that previous research, such as
-\citet{Cal:11c} and \citet{Ana:12}, does not predict these
-results. When $\Lambda$ represents a test statistic, the test may have
-correct size for the null hypothesis that the additional coefficients
-on the larger model are zero. The results in this subsection are being
-driven by the full-sample statistics' behavior when the smaller model
-is misspecified but more accurate.
-
-Any statistic that uses the distance of the models' estimated
-coefficients from a set point (the origin being the most common) is
-poorly suited for choosing between overfit forecasting models. These
-models only forecast well when their coefficient estimates are close
-to their pseudotrue values, which can be far from the origin or any
-other prespecified
-point. Depending on the statistic, it can be biased towards choosing
-the larger model or the smaller model. Formal in-sample \emph{tests}
-will likely be biased towards the larger model, as we show for the
-$F$-test and Wald test in Theorem~\ref{res:insample1}.
-
-\subsection{An extended simple example}
-\label{sec:example}
-
-This subsection illustrates the previous theoretical results with a
-concrete example. Let $L(e) = e^2$ and $h = 1$. Suppose that the benchmark is
-nested in the alternative and $(x_{2t}, \e_{2,t+1}) \sim i.i.d.\
-N(0,I)$, and let $y_{t+1} = x_{2t}'\theta_2 + \e_{2,t+1}$
-be the DGP. Also assume that $K_2/T \to c_2$ and $K_1 / T \to c_1 <
-c_2$.
-
-The first part of this subsection shows how the assumptions in
-Section~\ref{sec:asmp} are satisfied and the second part
-demonstrates asymptotic normality of the DMW \oost\ test. The third
-part explicitly shows that $\E_R \oosA$ converges to $\E_T \oosB$ only
-when the test sample is small. And the last part demonstrates that the
-$F$-test does not indicate which model will be more
-accurate in the future, even in this simple example.
-
-\subsubsection*{Fulfillment of Assumptions 1--5}
-
-We will go through the assumptions one by one. The first is
-a condition on the dependence and moments of the process. Since the
-DGP is i.i.d. Normal, these conditions are satisfied trivially.
-
-Assumption~\ref{asmp-2} deals with the design matrix. In this example,
-we directly assume that $K_2$ and $K_1$ grow at the correct rates so
-the the assumption is satisfied. The variance of $y_{t+1}$ given
-$\Fs_t$ is simply the unconditional variance of $\e_{2,t+1}$, which is
-1; and the eigenvalues of $\E x_{2t} x_{2t}$ all equal 1 as well; and
-so they are all uniformly positive and finite as required.
-
-Assumption~\ref{asmp-2} also requires the eigenvalues of $S^{-1}
-X_{iS}'X_{iS}$ to be positive and finite, and for the largest
-eigenvalue of $S^{-1} X_{iS}'X_{iS}$ to be bounded in $L_3$.  These
-results follow from developments in random matrix theory.
-\citet{Gem:80} establishes that the largest eigenvalue of
-$X_{iS}'X_{iS}$ is of order $S + K_i$ and \citet{Joh:01} shows that it
-converges in distribution to the Tracy-Widom law of order 1
-\citep{TrW:96}, which has finite 3rd moments. \citet{Sil:85} and
-\citet{BFP:98} prove similar results for the smallest eigenvalue.
-Assumption~\ref{asmp-2} also requires the largest eigenvalue of
-$(X_{iS}'X_{iS})^{-1}$ be bounded in $L_3$; this should follow from a
-similar argument, but we are unaware of any papers that explicitly
-derive moments for this eigenvalue.
-
-For the conditional expectation of %
-$\sum_{s,t=U}^{V-1} \e_{i,t+1} \e_{i,s+1} x_{i,s} x_{i,t}'$,
-independence implies that
-\begin{equation*}
-  \E\Big(
-  \sum_{s,t=U}^{V-1} \e_{i,s+1} \e_{i,t+1} x_{is}x_{it}'
-  \mBig
-  x_{i1},\dots,x_{i,U-1};
-  \sum_{s=U}^{V-1} x_{is} x_{is}';
-  x_{i,V},\dots,x_{i,T-1}
-  \Big)
-  = \sum_{s=U}^{V-1} x_{is} x_{is}'.
-\end{equation*}
-The largest eigenvalue of this last matrix is of order $K_i + V - U$,
-as discussed, and it has at most $V - U$ nonzero eigenvalues,
-ensuring that both~\eqref{eq:28} and~\eqref{eq:8} hold.
-
-Assumption~\ref{asmp-3} restricts the loss function and the realized
-OOS loss. In this example, we have
-\begin{equation*}
-  D_t^* =^d D_t = (e_{2,t+1} + x_{2t}'\theta_2 - x_{1t}'\bh{1t})^2
-  - (e_{2,t+1} + x_{2t}'(\theta_2 - \bh{2t}))^2
-\end{equation*}
-which has bounded $\rho$th moments by construction. The loss function
-is differentiable and $L'(e) = 2 e$, so \eqref{eq:29} holds as well.
-
-Finally, Assumption~\ref{asmp-4} deals with the choice of test and
-training sample and holds automatically. And Assumption~\ref{asmp-5}
-requires the kernel of the HAC variance estimator to be continuous at
-zero; it is straightforward to construct an estimator that satisfies
-this condition. However, in this section we will use the estimator
-\begin{equation*}
-  \sh^2 = \frac{1}{P} \sum_{t=R+1}^{T-1} (D_t - \oosA)^2
-\end{equation*}
-which does not satisfy Assumption~\ref{asmp-5} but nevertheless is
-consistent for the conditional variance of $\oosA$ because the
-underlying observations are independent.
-
-\subsubsection*{Asymptotic normality of the OOS average, Lemma 1}
-
-This subsection walks through Lemma 1's CLT. Since the observations in
-this example are i.i.d., we do not need to use mixingale theory to
-derive the results, but the OOS process is still affected by the
-estimation error in $\bh{1t}$ and $\bh{2t}$ and has a high degree of
-dependence. This dependence makes the OOS process an MDS, and MDS
-asymptotic theory replaces mixingale theory in this example.
-
-By construction, we have
-\begin{equation*}
-  D_t =
-  \begin{cases}
-    2 \e_{t+1} (x_{2t}'\bh{2R} - x_{1t}'\bh{1R})
-    + (x_{2t}'\theta_2 - x_{1t}'\bh{1R})^2
-    - (x_{2t}'\theta_2 - x_{2t}'\bh{2R})^2
-    & \text{if } t < T \\
-    2 \e_{t+1} (x_{2t}'\bh{2T} - x_{1t}'\bh{1T})
-    + (x_{2t}'\theta_2 - x_{1t}'\bh{1T})^2
-    - (x_{2t}'\theta_2 - x_{2t}'\bh{2T})^2
-    & \text{if } t > T
-  \end{cases}
-\end{equation*}
-and so we can explicitly derive the components of
-Lemma~\ref{res-mixingale}. First,
-\begin{multline*}
-  D_t - \E_R D_t
-  = 2 \e_{t+1} (x_{2t}'\bh{2R} - x_{1t}'\bh{1R})
-  + \Big\{(x_{2t}'\theta_2 - x_{1t}'\bh{1R})^2
-          - \E_R (x_{2t}'\theta_2 - x_{1t}'\bh{1R})^2 \Big\} \\
-  - \Big\{(x_{2t}'\theta_2 - x_{2t}'\bh{2R})^2
-          - \E_R (x_{2t}'\theta_2 - x_{2t}'\bh{2R})^2 \Big\}
-\end{multline*}
-for $t < T$. Since the underlying observations are i.i.d., $\E_{t-1}
-D_t = \E_R D_t$ a.s.\ and consequently $\{D_t - \E_R D_t, \Fs_{t};
-t=R+1,\dots,T-1\}$ is an MDS.
-
-Although transformations of $D_t - \E_R D_t$ will obviously not be
-MDSes in general, it should be clear that transformations of $D_t$
-will be MDSes after subtracting their conditional mean; i.e.
-\begin{equation*}
-  \{g(D_t) - \E_R g(D_t); \Fs_t; t = R+1,\dots,T-1\}
-\end{equation*}
-is an MDS as long as
-$g(D_t)$ has finite mean, but $g(D_t - \E_R D_t)$ is not. This MDS
-result holds because $x_t$ and $y_{t+1}$ are independent of $\bh{1R}$
-and $\bh{2R}$, so
-\begin{equation*}\begin{split}
-  \E_R g(D_t)
-  &= \int g\Big((x_1'\bh{1R})^2 - (x_2'\bh{2R})^2
-       + 2 y (x'\bh{2R} - x'\bh{1R})\Big) \, f(y, x) \, dx \, dy \\
-  &= \E_{t-1} g(D_t)
-\end{split}\end{equation*}
-a.s., where $f$ is the density of $(y_{t+1}, x_{2t})$ and $x_1$
-denotes the first $K_1$ elements of $x$. This result parallels our
-results for mixingales in the general case.
-
-As a result, $\oosA$ and $(1/P) \sum_{t=R+1}^{T-1} D_t^2$ both obey
-LLNs: $\oosA \to^p \E_R \oosA$ and
-\begin{equation*}
-  (1/P) \sum_{t=R+1}^{T-1} D_t^2 \to^p \E_R D_T^2.
-\end{equation*}
-Moreover, these convergence results imply that $\sh^2 - \var_R
-\sqrt{P} \oosA \to^p 0$. And so
-\begin{equation*}
-  \sqrt{P} \oosA/\sh \to N(0,1)
-\end{equation*}
-by the MDS CLT.
-
-\subsubsection*{Convergence of $\E_R \oosA$ to $\E_T \oosB$, Lemma 2}
-
-This subsection works through Lemma~\ref{res-convergence}. In this
-example, the difference between $\E_R \oosA$ and $\E_T \oosB$ equals
-\begin{equation*}
-  \begin{split}
-    \E_R \oosA - \E_T \oosB &= \Big\{(\bh{1R} - \theta_1)'(\bh{1R} -
-    \theta_1) -
-    (\bh{2R} - \theta_2)'(\bh{2R} - \theta_2)\Big\} \\
-    & \quad - \Big\{(\bh{1T} - \theta_1)'(\bh{1T} - \theta_1) -
-    (\bh{2T} - \theta_2)'(\bh{2T} - \theta_2)\Big\} \\
-    &\begin{split}
-      =\ep{T}'\Big\{
-      & \tilde{X}_{1R}(X_{1R}'X_{1R})^{-2} \tilde{X}_{1R}'
-      - X_{1T}(X_{1T}'X_{1T})^{-2} X_{1T}' \\
-      & - \tilde{X}_{2R}(X_{2R}'X_{2R})^{-2} \tilde{X}_{2R}'
-      + X_{2T}(X_{2T}'X_{2T})^{-2} X_{2T}'
-      \Big\}\ep{T}.
-    \end{split}
-  \end{split}
-\end{equation*}
-with $\tilde{X}_{iR}$ the $T \times K_i$ matrix $[X_{iR}'\ 0]'$. This
-last term is a quadratic form and the regressors and errors are
-assumed to be normal, so we can find the rate that the difference
-converges to zero in probability by calculating its first two moments.
-
-The mean difference is
-\begin{equation*}
-  \begin{split}
-  \E(\E_R \oosA - \E_T \oosB)
-      &=O\Big(\max_i \E \tr \big\{
-        \tilde{X}_{iR}(X_{iR}'X_{iR})^{-2} \tilde{X}_{iR}
-        - X_{iT}(X_{iT}'X_{iT})^{-2} X_{iT} \big\} \Big) \\
-      &=O\Big(\max_i \tr \big\{\E (X_{1R}'X_{1R})^{-1}
-         - \E (X_{1T}'X_{1T})^{-1} \big\}\Big) \\
-      &=O( K_1 P / (R-K_1)(T-K_1)) \\
-      &=O(P/T)
-    \end{split}
-\end{equation*}
-The first equality follows from the expectation of a quadratic form,
-the second from routine manipulations of the trace operator, and the
-third from the moments of the inverse Wishart distribution.
-
-Similarly, the variance of the difference is
-\begin{align*}
-  \var(\E_R & \oosA - \E_T \oosB) \\ &=
-  O\Big(\max_i \E\big[\tr((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1})\big]^2
-  + 2 \tr \E\big((X_{iR}'X_{iR})^{-2} - (X_{iT}'X_{iT})^{-2}\big) \\
-  &\qquad - \big[\tr \E((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}) \big]^2 \Big)\\
-  &= O(P/T)^2.
-\end{align*}
-So, in this example, $P^{1/2}(\E_R \oosA - \E_T \oosB) \to^p 0$
-if $P^3/T^2 \to 0$, which is slightly weaker than the general
-requirement that $P^2/T \to 0$.  If $\lim P^3/T^2 > 0$ the OOS average
-still obeys the MDS CLT, but it is not centered correctly at $\E_T
-\oosB$.
-
-\subsubsection*{Behavior of the F-test}
-
-This part illustrates the behavior of full-sample statistics in our
-simple example. To simplify the presentation even more, assume that
-the full-sample design matrix is orthogonal in-sample, not just in
-population, so $X_{2T}'X_{2T} = T \cdot I_{K_2 \times K_2}$, and again
-let $M_1$ and $M_2$ be the selection matrices for the first $K_1$ and
-the last $K_2-K_1$ elements of $\theta_2$. In this example,
-\begin{equation*}
-  M_2 \bh{2T} \sim
-  N(M_2 \theta_2, (1/T) \, I_{K_2-K_1})
-\end{equation*}
-and, conditional on $\E_T \oosB = 0$, the density of $M_2 \bh{2T}$
-concentrates uniformly on the surface of the sphere centered at $M_2
-\theta_2$ and passing through the origin:
-\begin{equation*}
-  (M_2 \bh{2T} - M_2 \theta_2)'(M_2 \bh{2T} - M_2 \theta_2) =
-  \theta_2'M_2' M_2 \theta_2.
-\end{equation*}
-To see intuitively that it must pass through the origin, note that the
-two models will give identical forecasts when $\bh{2T} = 0$ since the
-regressors are orthogonal. (Identical forecasts obviously have the
-same MSE.)
-
-This region is a cylinder in the original space, $\Re^{K_2}$.  We can
-also represent the null $\E_T \oosB \leq 0$ by conditioning on $\E_T
-\oosB = -d$ for a fixed positive constant $c$. In that case, the
-density of $M_2 \bh{2T}$ concentrates on the sphere
-\begin{equation*}
-  (M_2 \bh{2T} - M_2 \theta_2)'(M_2 \bh{2T} - M_2 \theta_2) =
-  \theta_2'M_2' M_2 \theta_2 + d
-\end{equation*}
-which has the same center but larger radius.
-
-For the $F$-test we have, as before,
-\begin{equation*}
-  F = \tfrac{T}{s^2 (K_2 - K_1)} \bh{2T}' M_2' M_2 \bh{2T}.
-\end{equation*}
-We know that $\sqrt{T}(F - 1)$ is asymptotically normal since its
-numerator is Chi-squared with $K_2-K_1$ degrees of freedom and obeys a
-CLT.  The test accepts if
-\begin{equation}\label{eq:26}
-  \tfrac{T}{s^2 (K_2 - K_1)} \bh{2T}' M_2' M_2 \bh{2T}
-  \leq 1 + \delta / \sqrt{T},
-\end{equation}
-where $\delta$ is chosen to determine the size of the test. In other
-words, the test accepts if $M_2 \bh{2T}$ falls in the sphere centered
-at the origin with radius $s ((K_2 - K_1) / T)^{1/2} +
-O_p(1/\sqrt{T})$.
-
-\input{floats/circles}
-\begin{figure}
-  \centering
-  \begin{tabular}{cc}
-  \subfloat[]{\circlefigA{1}{2.5}{1.4}{4.5}\label{fig:circleA}} &
-  \subfloat[]{\circlefigB{1}{2.5}{1.4}{4.5}\label{fig:circleB}}
-  \end{tabular}
-  \caption{Graphs indicating the rejection region and region of equal
-    generalization error for the models discussed in Section
-    \ref{sec:insample}.  The smaller model has no estimated parameters
-    and the larger has two coefficients.  The shaded regions in
-    Figures (a) and (b) show the rejection region and the acceptance
-    region respectively of the full-sample test given $\E_T \oosB \leq
-    0$. Here $e_1 = (1,0)$ and $e_2 = (0,1)$ are the first and second
-    selection vectors, so the horizontal axes represent changes in the
-    first unique element of $\bh{2T}$ and the vertical axes represent
-    changes in the second unique element.}
-\label{fig:rreject}
-\end{figure}
-
-This is perhaps best illustrated with a picture.
-Figure~\ref{fig:rreject} plots these quantities when $K_2 - K_1 =
-2$. The circle centered at the origin plots the threshold for the
-$F$-test; when $M_2 \bh{iT}$ falls outside this circle, the $F$-test
-rejects. The circle centered at $M_2 \theta_2$ plots the set of points
-for which $\E_T \oosB = 0$. The shaded region in
-Figure~\ref{fig:rreject}~(a) plots the rejection region given $\E_T
-\oosB \leq 0$ and the shaded region in Figure~\ref{fig:rreject}~(b)
-plots the acceptance region given $\E_T \oosB \leq 0$.
-
-In the picture, the true coefficients $\theta_2$ satisfy
-\begin{equation*}
-\theta_2'M_2'M_2\theta_2 > \var(\e_t)^{1/2} ((K_2 - K_1) / T)^{1/2}
-\end{equation*}
-so the center of the conditional distribution of $\bh{2T}$ given $\E_T
-\oosB \leq 0$ is outside the acceptance region of the $F$-test. When
-this is the case, the conditional probability that $\bh{2T}$ falls in
-the rejection region is less than 1/2, since $M_2 \bh{2T}$ is
-uniformly distributed on the cylinder
-\begin{equation*}
-  (M_2 \bh{2T} - M_2 \theta_2)'(M_2 \bh{2T} - M_2 \theta_2) =
-  \theta_2'M_2' M_2 \theta_2 + d
-\end{equation*}
-for some positive $d$.
-
-The AIC behaves essentially the same way. For the BIC, the radius of
-the cylinder centered at the origin increases with $T$ and eventually
-encompasses the cylinder centered at $M_2 \theta_2$, so it never
-selects the alternative once $T$ is large enough.
-\section{Monte Carlo}
-\label{sec:mc}
-
-This section presents two simulations that investigate the accuracy of
-our theory in small samples.
-We do several Monte Carlo exercises. The first looks at whether our
-theoretical results for the OOS average are accurate: whether or not
-the OOS average is approximately normal, and whether it is centered on
-$\E_R \oosA$, $\E_T \oosB$, or somewhere else entirely. The second
-issue is whether or not the \oost\ test is \emph{useful} for
-conducting inference about $\E_T \oosB$. Our theoretical results
-suggest that it may not be, because we require $P^2/T \to 0$ for
-inference about $\E_T \oosB$ to be valid. A highly related issue is
-whether other statistics are useful for conducting inference about
-$\E_T \oosB$---again, our theoretical results suggest that they are
-not.
-
-We use the same DGP for all of these simulations, and it is described
-in the next subsection. Results are presented in the subsection after
-that. Simulations were conducted in R \citep{Rde:10} using the
-\emph{MASS} \citep{VeR:02}, \emph{Matrix} \citep{BM:13}, and
-\emph{rlecuyer} \citep{SR:12} and graphs are produced using
-\emph{Lattice} \citep{Sar:10}. In this paper, we present results for
-the fixed window, but recursive window results are available in a
-separate Appendix and are similar.
-
-\subsection{Setup}
-\label{sec:simulation-design}
-
-The Monte Carlo experiment is intentionally very simple so that we can
-isolate the influence of the models' complexity.  In particular, we do
-not include some features that are common in forecasting
-environments---serial dependence, heteroskedasticity, and complicated
-DGPs. The DGP we use is given by the equation
-\begin{equation}\label{eq:6}
-  y_t = x_t'\theta + \e_t,\quad \e_t \sim N(0,1),
-  \quad t=1,\dots,T.
-\end{equation}
-The first element of $x_t$ is 1 and the remaining $K_2-1$ elements are
-independent Standard Normal.  The benchmark model is
-\begin{equation}
-  \label{eq:1}
-  y_{1t} = \sum_{j=1}^{K_1} x_{jt}\theta_j + \e_t
-\end{equation}
-and the alternative model is the DGP \eqref{eq:6}.  We let
-$(K_1,K_2)$ equal either $(2,3)$ or $(T/20,T/10)$ to study our theory
-in its intended application as well as for more parsimonious models.
-We let $T$ equal 100, 250, or 500.  We also vary $\theta$, and do
-so giving the benchmark and the alternative model comparable weight in
-predicting $y_t$.  Specifically, we set
-\begin{equation*}
-  \theta_j =
-\begin{cases} \frac{c}{\sqrt{K_1}} & j = 1,\dots,K_1 \\
-\frac{c}{\sqrt{K_2 - K_1}} & j = K_1 + 1,\dots,K_2 \end{cases}
-\end{equation*}
-with $c$ equal to zero or one.  When $c$ is one, we're more likely to
-draw values of $X$ and $Y$ that make the estimated larger model more
-accurate than the benchmark, and when $c$ is zero we're unlikely to
-draw such values of $X$ and $Y$.  For all of the studies, $L(e) =
-e^2$.
-
-To study the accuracy of our theoretical approximations, we first
-estimate the coverage probabilities of OOS confidence intervals for
-$\E_R \oosA$ and $\E_T \oosB$. For each draw of $X$ and $Y$, we
-construct the one-sided OOS interval defined in
-Theorem~\ref{res:oostest}:
-\begin{equation*}
-  [ \oosA - 1.28 \hat{\sigma}, \infty) \quad\text{with}\quad
-  \sh^2 = \frac1P \sum_{t=R+1}^T (D_t - \oosA)^{2}
-\end{equation*}
-for $P = 10,\dots,2T/3$; we then calculate the percentage of
-simulations where these intervals contain $\E_R \oosA$ and the
-percentage that contain $\E_T \oosB$.  Since the data are i.i.d., both
-of these quantities are easy to calculate (see
-Section~\ref{sec:example}). For these calculations, we draw 2000
-samples for each combination of the design parameters.
-
-Our second set of results studies whether these different OOS and
-in-sample statistics are valid for testing the null hypothesis
-\begin{equation*}
-  H_0:\quad E_T \oosB \leq 0,
-\end{equation*}
-namely that the benchmark model is expected to be more accurate in the
-future than the alternative. Informally, we are interested in whether
-the conditional probability
-\begin{equation*}
-  \Pr[\text{test rejects} \mid E_T \oosB \leq 0] \leq \alpha
-\end{equation*}
-where $\alpha$ is the nominal size of the test. If this inequality
-does not hold, the test statistic is rejecting the benchmark model too
-often.
-
-We look at four different statistics---the full-sample $F$-test, the
-DMW $t$-test, the OOS $t$-test using McCracken's (2007) critical
-values,\footnote{%
-  These critical values are not published for $K_2-K_1>10$, so we do
-  not report them for $K_2 = T/10$.} %
-and Clark and West's (2006, 2007) Gaussian out-of-sample
-statistic.\footnote{%
-  Clark and West (2006, 2007) derive their statistic using the rolling
-  window estimation scheme. Here we use the same statistic, but with a
-  fixed window scheme. A supplemental appendix presents results for
-  their statistic, using the recursive window.} %
-For the $F$-test, we simply test whether the coefficients on the
-larger model are nonzero.  For the out-of-sample tests, we conduct a
-one-sided test of out-of-sample performance for every value of $P$ as
-before. For each of these simulations, we discard draws from the DGP
-that violate the null hypothesis $E_T \oosB \leq 0$ and then use the
-remaining samples to calculate the conditional probability that each
-test rejects. The simulations end when 2000 draws have been retained
-for each choice of the design parameters.
-
-\subsection{Results}
-
-We discuss results for the confidence intervals first.
-Figures~\ref{fig:interval-R} and~\ref{fig:interval-T} show the
-coverage probability of these intervals as a function of $P$ for each
-combination of $T$, $K_1$ and $K_2$, and $c$.  The nominal coverage is
-90\% and is represented with a gray horizontal line. Each panel
-displays the coverage for a different choice of design parameters.
-
-Figure~\ref{fig:interval-R} gives the results for $\E_R \oosA$.  The
-actual coverage is very close to the nominal coverage except when $P$
-is very small.  The poor behavior for small $P$ is unsurprising, as it
-simply means that the CLT is a poor approximation when the test sample
-is small. The interval for $T = 100$, $K = T/10$, and $c = 0$ is the
-worst, with actual coverage near 85\% for most values of $P/T$. But
-the others are much closer to nominal coverage, even for the
-parsimonious models ($K_1=1$ and $K_2= 3$) where one might expect
-the theoretical results to break down.
-
-Figure~\ref{fig:interval-T} gives the results for $\E_T \oosB$.  In
-columns 2 and 4---the overfit models---the coverage is near nominal
-coverage for moderately small values of $P$.  As $P$ increases to
-$2T/3$, the coverage increases above nominal size; near 100\% for some
-DGPs.  With the parsimonious model, the coverage is near nominal
-coverage for all $P$ for the one-sided interval with $c=1$, but only
-for moderately small $P$ when $c=0$.
-
-The behavior for $K_2 = T/10$ is exactly what our theory predicts.
-When $P^2/T$ is small, the coverage is close to nominal levels.  The
-behavior as $P$ increases, combined with the results for $\E_R \oosA$,
-indicate that typically $\E_T \oosB \geq E_R \oosA$.  Since
-\begin{equation*}
-  E_{T} \oosB = E_{R} \oosA + (E_{T} \oosB - E_{R} \oosA),
-\end{equation*}
-and the interval is approximately centered at $\E_R \oosA$, the
-difference $\E_{T} \oosB - E_{R} \oosA$ adds a substantial positive
-quantity when $P^2/T$ is not near zero, increasing the coverage of the
-one-sided interval.
-
-We present the size simulations next, in
-Figures~\ref{fig:ftest}--\ref{fig:ttest-power}.  For the OOS tests
-we plot each OOS test's conditional rejection probability,
-\begin{equation*}
-  \Pr[\text{test rejects} \mid E_T \oosB \leq 0],
-\end{equation*}
-for each combination of $T$, $K_1$, $K_2$, and $c$ as a function of
-$P$.  The $F$-test does not depend on $P$, so we calculate and
-tabulate it's conditional rejection probability as a single value for
-each combination of design parameters.
-
-Table~\ref{fig:ftest} summarizes the simulation results for the
-$F$-test. For $c = 0$, the estimated conditional rejection probability
-is almost exactly equal to the test's nominal size (10\%), which is
-unsurprising.  For $c = 0$, the $F$-test is exact; moreover, the
-larger model will almost always be less accurate than the smaller one,
-so conditioning on $\E_T \oosB \leq 0$ is almost unrestrictive.  When
-$c$ increases, though, the $F$-test overrejects badly---rejecting at
-roughly 50\% when $c = 1$ for the parsimonious model and from 70\% to
-100\% for the overfit model. This agrees with our
-Section~\ref{sec:insample} results and matches results seen in
-empirical practice: the $F$-test rejects the benchmark with very high
-probability, even though it is, by construction, more accurate than
-the alternative model.
-
-Figure~\ref{fig:ttest-size} presents the size estimates for the DMW
-\oost\ test.  Again, different panels display results for different
-combinations of the design parameters.  Each graph plots the rejection
-probability against $P/T$.  For $K/T=10$, the rejection probability
-falls as $P/T$ increases, from near nominal size when $P/T$ is small
-to zero when $P/T$ is near $2/3$.  Moreover, the rejection probability
-falls faster when $T$ is large, as our theory predicts.  When $K=3$,
-the rejection probability stays closer to nominal size, but falls with
-$P/T$ for $c=0$, under-rejecting by about 5pp when $P/T = 2/3$, and
-rises with $P/T$ for $c=1$, overrejecting by about 10pp when
-$P/T=2/3$.  For small $P$, the rejection probability is near 10\% for
-all simulations (the farthest is $K=T/10$, $c=0$, where the rejection
-probability is about 5\%; the other simulations are much closer).
-
-We observe the following patterns.  The
-DMW test has close to nominal size when $P$ is small for every
-combination of design parameters.  In most cases, the rejection
-probability decreases as $P/T$ increases---the exception is for $K_2 =
-3$ and $c=1$.  For the large-$K$ simulations, the rejection
-probability drops to zero for most of the simulations as $P/T$
-increases.  The rejection probability increases with $c$, but the
-rejection probability still is near nominal probability for small $P$
-with $c=1$.
-
-Clark and West's (2006, 2007) statistic, presented in
-Figure~\ref{fig:clarkwest}, behaves quite differently.  For $c=0$ the
-test is correctly sized for both the overfit and parsimonious studies,
-as we saw for the $F$-test.  When $c=1$, the rejection probability
-increases rapidly with $P/T$.  For $K_2=3$, the rejection probability
-is near 10\% when $P$ is small but about 40\% when $P/T = 2/3$.  For
-$K=T/10$, the rejection probability is even higher and increases with
-$T$ as well, from a maximum over 50\% when $T=100$ to a maximum of
-nearly 100\% when $T=1000$.
-
-Results using \citepos{Mcc:07} critical values are presented in
-Figure~\ref{fig:mccracken} and are similar to those using Clark and
-West's test.  For $c=0$ the rejection probability is nearly the test's
-nominal size.  For $c=1$, the rejection probability increases with
-$P/T$, from close to the nominal size when $P/T$ is small to over 25\%
-when $P/T = 2/3$.  Note that all of the simulations use the
-parsimonious model.  McCracken's statistic overrejects here by
-slightly less than Clark and West's, but still by a substantial
-amount. Note that we are unable to plot results for McCracken's
-statistic when $K/T = 10$, which is where the breakdown in Clark and
-West's test is most pronounced.
-
-Since the DMW test tends to have low rejection probability, the test's
-power is a concern.  Figure~\ref{fig:ttest-power} power results for
-the DMW test, simulating from \eqref{eq:1} with $c = 1$ or 2 subject
-to the constraint that $\E_T \oosB > 0$.\footnote{%
-  Draws of $X$ and $Y$ with $\E_T \oosB > 0$ are very rare when $c=0$,
-  so we do not present results for that value of $c$.} %
-Since the other test statistics greatly overreject, we do not present
-their power.  For $c=1$, the power is never greater than nominal size
-and decreases to zero as $P/T$ increases for the overfit model.  For
-$c=2$ the power is better, increasing with $P/T$ at first stretch and
-then decreasing as $P/T$ grows beyond approximately 1/4 for the
-overfit model.  Larger values of $T$ give a higher peak and greater
-power overall, but the power still falls to nearly zero if $P/T$ is
-too large (approximately 2/3 in our simulations).  The power with the
-parsimonious model is typically quite low but greater than nominal
-size for $c = 2$.
-
-Both sets of simulations support our theoretical results.  The first
-simulation confirms that the DMW OOS $t$-test is centered at $\E_R
-\oosA$ for all choices of $P$ and $R$ and is centered on $\E_T \oosB$
-only when $P$ is small.  The second simulation confirms that the DMW
-test has correct size for the null hypothesis that $\E_T \oosB \leq 0$
-when $P$ is small and that tests designed to test whether the
-benchmark is true, like the $F$-test and Clark and West's (2006, 2007)
-and McCracken's (2007) OOS tests can reject by much more than their
-nominal size when testing the null $\E_T \oosB \leq 0$.  Moreover,
-these simulations demonstrate that the restriction that $P$ be small
-is binding in practice, as the DMW test under-rejects and has very low
-power when $P$ is too large.
-
-\section{Empirical analysis of equity premium predictability}
-\label{sec:empirics}
-
-This section presents a study of equity premium predictability based
-on \citet{GoW:08}. Goyal and Welch conduct an out of sample analysis
-of 18 different variables thought, based on previous research, to
-predict the equity premium (calculated as the difference between the
-return on the S\&P 500 index and the T-bill rate).\footnote{%
-  \citet{GoW:08} builds on previous research by \citet{BoH:99} and
-  \cite{GoW:03}.} %
-Their analysis has two notable features: Goyal and Welch compare different
-predictors across the same time periods and frequency as much as
-possible, making the accuracy of these predictors directly comparable;
-many of the papers that originally proposed these predictors used
-different time periods, methods, or observational frequencies so their
-results were not directly comparable. And Goyal and Welch compare
-these predictors out-of-sample; many of the original studies found
-in-sample evidence of equity premium predictability but did not look
-at out-of-sample evidence.
-
-Goyal and Welch consider many different models; most of them are very
-simple---regression onto a constant and a single stochastic
-predictor---but some are more complicated. They find that essentially
-none of the models outperform a simple benchmark, the prevailing mean
-of the equity premium, and conclude that these variables do not
-predict the equity premium. A large literature has subsequently sought
-to explain or rebut these results, including several responses to
-Goyal and Welch's original working paper published in the same special
-issue of \textit{The Review of Financial Studies} as
-\citet{GoW:08}.\footnote{%
-  Those papers are \citet{CaT:08}, \citet{Coc:08}, \citet{BRW:08}, and
-  \citet{LeN:08}.} %
-
-\citet{GoW:08}, as well as \citet{BoH:99}, \citet{LeN:08}, and many
-other authors, propose that instability could explain the OOS failure
-of these models. However, we have shown in this paper that overfit can
-also explain this pattern, significant in-sample results that do not
-hold up out of sample. In this section, we explore the extent to which
-overfit is a potential concern in this data set and estimate the
-expected forecasting performance of the largest model they consider, a
-model with 13 regressors, using 81 observations (annual data from 1928
-to 2009). The predictors are listed in Table~\ref{tab:equity}; please
-see Goyal and Welch's original paper for detailed information about
-these variables.\footnote{%
-  Table~\ref{tab:equity} only lists the variables used in
-  \citepos{GoW:08} ``kitchen sink'' model.  Some of the variables that
-  they use are excluded from this model either because the series are
-  too short or because the variables are linear combinations of other
-  variables.} %
-
-\citet{GoW:08} focus primarily on univariate regression models of the
-form
-\[
-r_{t+1} = \beta_0 + \beta_1 x_{it} + \e_{t+1}
-\]
-using OLS with a recursive window, where $r_{t+1}$ is the equity
-premium and $x_{it}$ is one of the predictors listed in
-Table~\ref{tab:equity}.
-This focus is consistent with much of the rest of the literature. But
-it is not clear that this approach---using a large number of
-restricted models---is any more reliable than using a single, large
-model. Very few papers in the equity-premium predictability literature
-explicitly account for the multiplicity of model comparisons\footnote{%
-  \citet{RaW:06}, \citet{RaZ:12}, and \citet{Cal:15} are
-  exceptions.} %
-and most widely-used statistics for multiple comparisons are
-derived under the assumption that there is a finite number of
-hypotheses or models (as is the case in \citealp{STW:99c},
-\citealp{Whi:00}, \citealp{Han:05}, and \citealp{LeR:05}), so there is
-little theoretical evidence that they are any more reliable than a
-regression model that encompasses all of the smaller models. Moreover,
-since \citet{GoW:08} (along with most of the rest of the literature)
-want to interpret these univariate regressions as meaningful
-statements about the true relationships between the equity premium and
-the regressors, omitted variable bias is a serious potential issue.
-
-For example, Table~\ref{tab:gwinsample} presents two full-sample
-coefficient estimates for each of the 12 predictors we
-consider.\footnote{%
-  For all of our full sample results, we studentize the
-  regressors to make it easier to compare coefficient estimates and we
-  express the equity premium in basis points.} %
-The first column is the estimator of the coefficient on the
-variable in the full regression,
-\begin{equation*}
-  r_{t+1} = \beta_0 + \sum_{i=1}^{12} \beta_{i} x_{it} + \e_{t+1},
-\end{equation*}
-and the third column is the $p$-value associated with a two-sided
-$t$-test that the coefficient is zero in population. The second column
-is the estimator of the coefficient from the univariate regression
-\begin{equation*}
-  r_{t+1} = \alpha_i + \gamma_{i} x_{it} + \e_{t+1},
-\end{equation*}
-and the fourth column is the $p$-value associated with its
-$t$-test.\footnote{%
-  All of the standard errors were calculated using a Newey-West kernel
-  with two lags.} %
-Some of the coefficient estimates agree, but some do not. The
-coefficient estimate for the \emph{default yield spread}, for example,
-is substantially and significantly negative in the full model ($-7.79$
-with $p$-value $0.042$), but is near zero in the univariate regression
-($0.79$ with $p$-value $0.720$). This pair of results implies that the
-the default yield spread contains information about the equity premium
-but is also correlated with other poor predictors, and that this
-additional correlation adds noise to the univariate regression
-and masks the true relationship. Similarly, \emph{net equity expansion}
-is significant at 10\% in the univariate regression but not in the
-full model ($p$-values of $0.060$ and $0.626$ respectively), which is
-likely attributable to omitted variable bias. So there is merit to
-studying a large model that includes all of the variables.
-
-Results for the full sample estimates of these models are in
-Table~\ref{tab:gwinsample}.\footnote{%
-  Calculations in this section are done in R \citep{Rde:10} using the
-  \emph{lmtest} \citep{ZeH:02} and \emph{sandwich} \citep{Zei:04}
-  packages.}\footnote{%
-  We compare the test statistic to critical values from the
-  $F$-distribution, which have been shown to be more reliable than
-  Chi-squared critical values when there are many regressors
-  \citep{Ana:12,Cal:11c}.} %
-The last rows of the table list measures of the full-model fit.  The
-$p$-value for the test of full model fit is very small (less than
-0.01), indicating that some of the coefficients are nonzero in
-population and at least one of these predictors is correlated with the
-equity premium.\footnote{%
-  We have done additional analysis to try to identify which predictors
-  were correlated with the equity premium, but none of the individual
-  regressors were significant after correcting for multiplicity. The
-  Bonferroni correction, for example, suggests that an individual
-  $p$-value would need to be less than $0.10/12 \approx 0.0083$ for
-  its corresponding coefficient to be significant at the 10\% level,
-  but the smallest $p$-value is $0.035$. One can improve on the
-  Bonferroni correction, of course, but a comprehensive analysis is
-  beyond the scope of this paper.} %
-As we argue throughout the paper, this result does not imply that the
-model will forecast well.
-
-To determine whether the full model can forecast well, we use the DMW
-\oost\ test to compare it to a sample mean benchmark,
-\begin{equation*}
-r_{t+1} = \mu + \e_{1,t+1}.
-\end{equation*}
-Both models are estimated by OLS using the fixed-window scheme. We
-also present results for a restricted model proposed by
-\citet{CaT:08} that imposes that $\hat r_{t+1}$ be non-negative for
-each forecast.
-To study the effect of the training sample size on the DMW statistic, we
-calculate the one-sided confidence interval for $\E_T \oosB$ given
-by \eqref{interval-greater} corresponding to the null and alternative
-hypotheses
-\[ H_0: \quad E_T \oosB \leq 0 \qquad
-H_A: \quad E_T \oosB > 0
-\]
-using the fixed-window scheme for each value of $R$ between 20 and
-$T-10$. The standard deviation is estimated using a Newey-West
-estimator with $\lfloor P^{1/4}\rfloor$ lags.  For small values of
-$R$, the OOS average is expected to underestimate the performance of
-the larger model relative to the smaller, but this may not hold in
-this particular dataset. For the OOS results, we express the equity
-premium in percentage points.
-
-Figure~\ref{fig:empirics1} plots the OLS results and
-Figure~\ref{fig:empirics2} imposes \citepos{CaT:08} restriction. The
-solid line in each figure shows the OOS average, $\oosA$, and the
-shaded region indicates the 95\% one-sided confidence interval implied
-by the DMW test.  Negative numbers indicate that the full model has
-higher out-of-sample loss.  We can see that the same patterns hold for
-both models: the performance difference decreases as $R$ grows, but
-the full model is never more accurate.  We also see that the
-performance difference decreases suddenly over the period $R=29$ to
-$R=34$ (corresponding to the years 1956--1961).
-Figure~\ref{fig:empirics3} plots the accuracy of the individual
-forecasts (only for the linear models) and shows that this change is
-the result of a sudden improvement in the full model.  This change may
-indicate instability in the underlying relationship, as proposed by
-\citet{GoW:08}.
-
-In summary, we fail to reject the null that the benchmark prevailing
-mean model is more accurate than the full model including all of
-\citepos{GoW:08} predictors.  This result is consistent with Goyal and
-Welch's original analysis.  Unlike Goyal and Welch, we attribute this
-result, at least in part, to parameter uncertainty---the full sample
-results indicate that there is a true predictive relationship between
-some of these variables and the equity premium and the larger model
-could predict better than the benchmark with enough data.\footnote{%
-  \citet{BWB:10} make a similar point about exchange rate models, but
-  see also \citet{Chi:10} and \citet{Gia:10}.} %
-These also indicate that combination or shrinkage estimators of the
-full model have the potential to significantly improve on the
-benchmark.\footnote{%
-  See \citet{RaZ:12} for a recent review of this literature.} %
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-This paper gives a theoretical motivation for using OOS comparisons:
-the DMW OOS test allows a forecaster to conduct inference about
-the expected future accuracy of his or her models when one or both is
-overfit.  We show analytically and through Monte Carlo that standard
-full-sample test statistics can not test hypotheses about this
-performance.
-
-Our paper also shows that popular test and training sample sizes may
-give misleading results if researchers are concerned about overfit.
-We show that $P^2/T$ must converge to zero for the DMW test to give
-valid inference about the expected forecast accuracy, otherwise the
-test measures the accuracy of the estimates constructed using only the
-training sample.  In empirical research, $P$ is typically much larger
-than this.  Our simulations indicate that using large values of $P$
-with the DMW test gives undersized tests with low power, so this
-practice may favor simple benchmark models too much.  Existing
-corrections, proposed by \citet{ClM:01,ClM:05}, \citet{Mcc:07} and
-\citet{ClW:06,ClW:07}, seem to correct too much, though, and reject
-too often when the benchmark model is more accurate.
-
-More work remains.  The requirement that $P^2/T$ converge to zero is
-limiting, as it implies that in typical macroeconomic datasets, only a
-handful of observations should be used for testing.  This requirement
-can be relaxed only slightly; $P = O(T^{1/2})$ is required for the
-OOS test to have nontrivial power in general, but there are loss
-functions and DGPs for which some relaxation is possible.  This
-constraint could be mitigated by extending our results to
-cross-validation or other resampling strategies, or by constructing
-full-sample statistics that allow inference about $\E_T \bar{D}_T$.
-It would also be useful to extend our results to other forecasting
-models and to explore how stationarity could be relaxed, but such
-extensions are less important than improving the available statistics.
-
-\appendix
-\section*{Appendix: mathematical details}
-\setcounter{section}{1}
-% Change lemma style to prepend 'A'
-\setcounter{lem}{0}
-\renewcommand{\thelem}{A\arabic{lem}}
-
-\subsection*{Supporting results}
-The results in this paper rely heavily on a coupling argument for
-absolutely regular sequences, Berbee's Lemma \citep{Ber:79}.  Many of
-the results of this paper (Lemma \ref{res-mixingale} and
-Theorem~\ref{res-oost}) use modifications of existing results
-for NED functions of mixing processes by \citet{Jon:97} and
-\citet{JoD:00}; this coupling argument is used to explicitly derive
-inequalities that arise naturally for NED processes.  Lemma
-\ref{lem-basic-coupling} establishes these inequalities, which are
-based on a proposition of \citet{MeP:02}.
-
-We present \citeauthor{MeP:02}'s
-(\citeyear{MeP:02}) statement of Berbee's Lemma for
-the reader's reference.  In the following Lemma, $\beta(X,Y)$ is the
-coefficient of absolute regularity:
-\begin{equation}
-\beta(X,Y) = \sup_{A \in \sigma(Y)} \E \lvert \Pr(A \mid \sigma(X))
-  - \Pr(A) \rvert.
-\end{equation}
-
-\begin{lem}\label{lem-berbee}\quad
-
-\begin{quotation}\noindent
-  Let $X$ and $Y$ be random variables defined on a probability space
-  $(\Omega, \mathcal{T}, \Pr)$ with values in a Polish space
-  $S$.  Let $\sigma(X)$ be a $\sigma$-algebra generated by $X$ and let
-  $U$ be a random variable uniformly distributed on $[0,1]$
-  independent of $(X,Y)$.  Then there exists a random variable $Y^{*}$
-  measurable with respect to $\sigma(X) \vee \sigma(Y) \vee
-  \sigma(U)$, independent of $X$ and distributed as $Y$, and such that
-  $\Pr(Y \neq Y^{*}) = \beta(X,Y)$.
-
-  \noindent\citep{MeP:02}
-\end{quotation}
-\end{lem}
-
-The advantage of this result over coupling arguments that use other
-forms of weak dependence is that the difference between the original
-variable, $Y$, and the new variable, $Y^{*}$, does not depend on their
-dimension.  Similar results for strong mixing sequences depend on the
-dimension of $Y$, which makes them unsuitable for this paper.
-
-\begin{lem}\label{lem-extend-mp}
-  Suppose that $X$ and $X^*$ are $L_p$-bounded random variables, with
-  $p > 2$, that satisfy ${\Pr[X \neq X^*] = c}$.  Then
-  \begin{equation}
-    \lVert X - X^* \rVert_2 \leq 2^{1/p} (\lVert X \rVert_p + \lVert
-    X^* \rVert_p) c^{(p-2)/2p}
-  \end{equation}
-\end{lem}
-
-The proof is virtually identical to the proof of Proposition 2.3 in
-\citet{MeP:02} and is omitted.
-
-\begin{lem}\label{lem-basic-coupling}
-  Suppose Assumptions \ref{asmp-1}--\ref{asmp-3} hold.  Then, for any
-  T, $s$, $t$, and $u$ with $s < t \leq u$, there exist random
-  variables $D_t^*,\dots,D_u^*$ such that
-  \begin{equation}\label{eq:coupling1}
-    P[(D_{t}^*,\dots,D_u^*) \neq (D_{t},\dots,D_u)] \leq \beta_{t-s}
-  \end{equation}
-  and
-  \begin{equation}\label{eq:coupling2}
-    \E(\phi(D_{t}^*,\dots, D_u^*) \mid \mathcal{F}_s ) =
-    \int
-    \phi(D_{t},\dots,D_u) f(\mathbf{x}, \mathbf{y})\ d\mathbf{x}\ d\mathbf{y}
-  \end{equation}
-  almost surely for all measurable functions $\phi$ such that the
-  expectations are finite, where
-  \[ \mathbf{x} = (x_{t}', \dots, x_{u}')', \qquad
-  \mathbf{y} = (y_{t+\h},\dots,y_{u+\h})',\] and $f$ is the
-  joint density of $(\mathbf{x}, \mathbf{y})$.  Moreover,
- \begin{equation}\label{eq:coupling3}
-   \| D_v^* - D_v \|_2 \leq 2^{1+1/\rho} B_L
-   \beta_{t-s}^{\rhoExp}, \qquad v = t,\dots,u.
- \end{equation}
-\end{lem}
-
-\begin{proof}
-  The proof follows as a consequence of Lemmas \ref{lem-berbee} and
-  \ref{lem-extend-mp}.  Let $l = u-t$.  For any fixed values of $l$
-  and $T$, the sequence of vectors
-  \[ V_{t} = (y_{t+\h}, x_{t}', \dots, y_{t+l+\h}, x_{t+l}') \] is
-  absolutely regular of size $\rho/(\rho-2)$.  Berbee's Lemma implies
-  that there is a random vector $V^*$ that is independent of
-  $\mathcal{F}_s$, equal to $V_{t}$ in distribution, and satisfies
-  \[\Pr[V^* \neq V_{t}] = \beta_{t-s}.\]
-
-  Now define
-  \begin{equation*}
-    D_v^* =
-    \begin{cases}
-      L(y_{v+\h}^* - x_{1v}^{*\prime} \hat{\theta}_{1R}) - L(y_{v+\h}^* -
-      x_{2v}^{*\prime} \hat{\theta}_{2R}) & v \leq T \\
-      L(y_{v+\h}^* - x_{1v}^{*\prime} \hat{\theta}_{1T}) - L(y_{v+\h}^* -
-      x_{2v}^{*\prime} \hat{\theta}_{2T}) & v > T
-    \end{cases}
-  \end{equation*}
-  with $y_{v+\h}^*$ and $x_{iv}^*$ denoting the elements of $V^*$
-  corresponding to $y_{v+\h}$ and $x_{iv}$ in $V_{t}$.  Equations
-  (\ref{eq:coupling1}) and (\ref{eq:coupling2}) are satisfied by
-  construction, and (\ref{eq:coupling3}) follows from Lemma
-  \ref{lem-extend-mp}.
-\end{proof}
-
-\begin{lem}\label{lem:a2}
-  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-3} hold.  Let $b_T$ be a
-  sequence of integers such that $b_T \to \infty$ and $b_T = o(P)$ and define
-  \begin{equation}
-    Z_i = \ZDef.
-  \end{equation}
-  Then
-  \begin{equation}
-    \label{eq:10}
-    \sum_{i=1}^{\lfloor P/b_T \rfloor} (\E_R Z_i^2 - \E_{R+(i-1) b_T}
-    Z_i^2) \to^p 0 \quad\text{ as } P \to \infty.
-  \end{equation}
-
-  If the assumptions of Theorem~\ref{res-oost} also hold, $b_T$ is
-  restricted further so that $b_T \equiv \lfloor \gamma/\delta
-  \rfloor$ for some positive scalar $\delta$, and we define
-  \begin{equation}\label{eq:13}
-    \kernelB{x} \equiv \kernelBDefn{x},
-  \end{equation}
-  then
-  \begin{equation}
-    \label{eq:12}
-    \vtSum (Z_{1t} Z_{2t} - \E_R Z_{1t} Z_{2t}) \to^p 0.
-  \end{equation}
-  where
-  \begin{gather}
-    Z_{1t} = \varianceTermIIIa,%
-    \intertext{and}%
-    Z_{2t} = \varianceTermIVb.
-  \end{gather}
-\end{lem}
-\begin{proof}
-\newcommand{\UFiltration}[1]{\ensuremath{\mathcal{F}_{(#1)b_{T}+R-P}}}%
-The first result,~\eqref{eq:10}, follows a similar argument to Lemma~5
-of \citet{Jon:97} and~\eqref{eq:12} to Lemma~A.4 of \citet{JoD:00}.
-Since these arguments are similar and our modification is the same for
-both, we'll just present the more complicated version,~\eqref{eq:12}.
-
-Note that $\{Z_{1t}^2 P\gamma_T/b_T\}$ and $\{Z_{2t}^2 P\gamma_T/b_T\}$
-are uniformly integrable.  As in~\citet[Lemma A.4]{JoD:00}, we can
-assume that there is a constant $C$ such that $Z_{1t}$ and $Z_{2t}$
-are bounded in absolute value by $C\sqrt{b_T/P\gamma_T}$; uniform
-integrability ensures that the difference between the unbounded random
-variables and these truncated versions is negligible for large enough
-values of $C$.
-
-Let $r = \lfloor 3P/2b_T \rfloor$ and rewrite the summation as
-\begin{align*}
-  \vtSum \vtIIIsummand &= \vtSumr \vtSuma \vtIIIsummand \\
-  &\quad+ \vtSumr \vtSumb \vtIIIsummand \\
-  &\quad+ \sum_{t=r b_T - P + R + 1}^{2P+R} \vtIIIsummand \\
-  &\equiv \vtSumr (U_i - \E_R U_i) + \vtSumr (U_i' - \E_R U_i') + o_{L_1}(1).
-\end{align*}
-The proof then holds if we can show that both $U_i$ and $U_i'$ obey
-LLNs.  We'll do so by proving that $\{U_i -\E_R U_i,
-\UFiltration{2i-1}\}$ and $\{U_i' - \E_R U_i', \UFiltration{2i}\}$ are
-$L_2$-mixingales of size $-1/2$ and using the bound $\E(\vtSumr (U_i -
-\E_R U_i))^2 = O(\vtSumr c_i^2)$ where the $c_i$ are the mixingale
-magnitude indices \citep{Mcl:75}.
-
-For non-negative $m$, we have
-\begin{equation*}
-U_i - \E_R U_i \in \UFiltration{2i+2m-1},
-\end{equation*}
-establishing half of the mixingale result trivially.  Now fix $i$ and $m >
-0$ and use Lemma \ref{lem-basic-coupling} to define $D_{ts}^*$
-for each $t =(2i-2)b_T-P+R+1,\dots,(2i-1)b_T-P+R$ and $s =
-\max(t-b_T,R+1),\dots,\min(t+b_T,T-\h)$ such that
-\begin{equation*}
- \E_R D_{ts}^* = \E_{(2i-2m-1)b_T+R-P} D_{ts}^* \quad a.s.
-\end{equation*}
-and
-\begin{equation*}
-  \lVert D_{ts}^* - D_s \rVert_2 \leq \couplingBound{s - (2i-2m-1)b_T+P}.
-\end{equation*}
-Also define
-\begin{equation*}
-  Z_{1t}^* = (P\gamma_T)^{-1/2} \sum_{l=\vttLower}^{\vttUpper}
-  (D_{t,t+l}^* - \E_R D_{t,t+l}^*)\ W(l/\gamma_T), \\
-\end{equation*}
-and
-\begin{equation*}
-Z_{2t}^* = (P\gamma_T)^{-1/2} \sum_{j=\vttLower}^{\vttUpper}
-    (D_{t,t+l}^* - \E_R D_{t,t+l}^*)\ \kernelB{j/\gamma_T}.
-\end{equation*}
-
-Now, we have the inequalities
-\begin{align*}
-  \lVert \E( U_i - \E_R U_i & \mid \UFiltration{2i-2m-1}) \rVert_2
-  \\ &\leq
-  \vtSuma \lVert \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) - \E_R
-  Z_{1t}Z_{2t} \rVert_2 \\
-  &= \vtSuma \lVert \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
-  &\quad - \E(Z_{1t}^* Z_{2t}^* \mid \UFiltration{2i-2m-1}) \\
-  &\quad + \E(Z_{1t}^* Z_{2t}^* \mid \UFiltration{2i-2m-1})
-  - \E_R Z_{1t}Z_{2t} \rVert_2 \\
-%  \leq \vtSuma (\wall \lVert \wall \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
-%  - \E(Z_{1t}^*Z_{2t}^* \mid \UFiltration{2i-2m-1}) \rVert_2\return
-%  \\ + \lVert \E_R Z_{1t}Z_{2t} - \E_R Z_{1t}^*Z_{2t}^*
-%  \rVert_2)\return \\
-  &\leq 2 \vtSuma \lVert Z_{1t} Z_{2t} - Z_{1t}^* Z_{2t}^*
-  \rVert_2 \\
-  &\leq 2 \vtSuma (\lVert Z_{1t} - Z_{1t}^* \rVert_2 \lVert
-  Z_{2t} \rVert_{\infty}
-  + \lVert Z_{2t} - Z_{2t}^* \rVert_2 \lVert Z_{1t}^* \rVert_{\infty}) \\
-  &\leq \frac{2 C b_T^{1/2}}{(P\gamma_T)^{1/2}} \vtSuma (\lVert Z_{1t} - Z_{1t}^* \rVert_2
-  + \lVert Z_{2t} - Z_{2t}^* \rVert_2).
-\end{align*}
-
-And we can finish the proof with the following inequalities:
-\begin{align*}
-  \frac{2 C b_T^{1/2}}{(P \gamma_T)^{1/2}} &\vtSuma \lVert Z_{1t} - Z_{1t}^* \rVert_2 \\& \leq
-  \frac{4C b_T^{1/2}}{P\gamma_T} \vtSuma \sum_{l=\vttLower}^{\vttUpper} \lVert
-  D_{t+l} - D_{t,t+l}^* \rVert_2 W(l/\gamma_T) \\&
-  \leq O\Bigg(\frac{b_T^{1/2}}{P\gamma_T}\Bigg) \vtSuma
-  \sum_{l=\vttLower}^{\vttUpper} \couplingBeta{t+l-(2i-2m-1)b_T+P}\\&
-  = O\Bigg(\frac{b_T^{1/2}}{P\gamma_T}\Bigg) O(b_T^{3/2-u}\, m^{-1/2-u})
-\end{align*}
-for some positive $u$.  The same argument holds for $Z_{2t}$.
-As a result,
-\[
-E\Big(\vtSumr (U_i - \E_R U_i)\Big)^2 = o\Big(\vtSumr b_T^2/P\gamma_T\Big) =
- o(b_T/\gamma_T) \to 0,
-\]
-as required.
-\end{proof}
-
-\begin{lem}\label{lem:a6}
-  Suppose the conditions of Theorem~\ref{res-oost} hold.
-  Then
-  \begin{equation}
-    \sh^2 - P^{-1} \sum_{s,t=R+1}^{T-h} (D_s - \E_R
-    D_s) (D_t - \E_R D_t) W((t-s)/\gamma) \to^{L_1} 0.
-  \end{equation}
-\end{lem}
-
-\begin{proof}
-   It follows from simple algebra that
-\begin{multline*}
-  \Big| \sh^2 -  P^{-1} \sum_{s,t=R+1}^{T-h} (D_s - \E_R
-    D_s) (D_t - \E_R D_t) W((t-s)/\gamma) \Big| \leq\\
-  \varianceDiffA \\ + P^{-1} \oosSum{s,t}{1} \lvert (D_s -
-  \oosA)(\E_R D_t - \oosA) \rvert \vWeight + o_p(1).
-\end{multline*}
-We'll prove that these two sums are $o_p(1)$; uniform integrability
-then implies convergence in $L_1$.  The arguments for each are almost
-identical, so we'll only present the first.
-
-Applying the Cauchy-Schwarz inequality twice and simplifying gives the
-upper bound
-\begin{multline*}
-\varianceDiffA \\ \leq O(1) \Big[\varianceDiffAii\Big]^{1/2} \Big[\varianceDiffAi\Big]^{1/2}.
-\end{multline*}
-Now,
-$P^{-1} \oosSum{s}{1}(D_s - \E_R D_s)^2 = O_p(1)$, and it suffices to prove
-that \[\varianceDiffAi = o_p(1).\]  Observe that
-\begin{align*}
-  \varianceDiffAi & = O_p\Big(P^{-1} \oosSum{s}{1}(\E_{R}D_s -
-  \E_R\oosA)^2\Big) + O_p(\oosA - \E_R\oosA)^{2} \\
-  &= O_p\Big(P^{-1} \oosSum{s}{1} (\E_RD_s)^2 - (\E_R\oosA)^2\Big) +
-  o_p(1),
-\end{align*}
-with the second term $o_p(1)$ by Lemma \ref{res-mixingale} and
-\citepos{Dav:93} mixingale LLN.
-
-Now define $D_s^*$, $s = R+1,\dots,T-\h$, as in Lemma
-\ref{lem-basic-coupling} so that $\E_{s-1} D_s^* = \E_R D_s^*$ almost
-surely.  Note that we also have the equality $\E_R D_s^* = \E_R
-D_{R+1}^*$ almost surely for all $s\geq R+1$, and so
-\[
-P^{-1} \oosSum{s}{1} (\E_R D_s^*)^2 = \Big(P^{-1} \oosSum{s}{1} \E_R
-D_s^*\Big)^2 \quad \text{a.s.}
-\]
-Consequently,
-\begin{align*}
-P^{-1} \oosSum{s}{1}& (\E_R D_s)^2 - (\E_R\oosA)^2 \\
-&= P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R D_s^*)^2]
- + \Big(P^{-1} \oosSum{s}{1} \E_R D_s^*\Big)^2 - (\E_R\oosA)^2 \quad \text{a.s}.\\
-&= O_p\Big(P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R D_s^*)^2]\Big)
- + O_p\Big(P^{-1} \oosSum{s}{1} \E_R (D_s - D_s^*)\Big).
-\end{align*}
-Finally,
-\begin{align*}
-\Big\lVert P^{-1} \oosSum{s}{1} [(\E_RD_s)^2 - (\E_R D_s^*)^2] \Big\rVert_1
-&\leq P^{-1} \oosSum{s}{1} \lVert \E_R (D_s - D_s^*) \rVert_2 \lVert
-\E_R (D_s + D_s^*) \rVert_2
-\\ &\leq (4 B_L/P) \oosSum{s}{1} \lVert \E_R (D_s - D_s^*) \rVert_2,
-\end{align*}
-and this last term vanishes as in the proof of Lemma~\ref{lem:a2},
-completing the proof.
-\end{proof}
-
-\subsection*{Proof of Lemma \ref{res-mixingale}}
-We will start by proving that $\{D_t - \E_R D_t, \Fs_t\}$ is an
-$L_2$-mixingale of size $-1/2$; $D_t$ is $\Fs_t$-measurable and so it
-suffices to prove that
-\begin{equation}\label{eq:24}
-  \| \E_{t-l} D_t  - \E_R D_t \|_2 \leq 2^{2 + 1/\rho} B_L \, \couplingBeta{l}
-\end{equation}
-for $l = 1,\dots,t-R$, since $\couplingBeta{l} = O(l^{-1/2 - \delta})$
-for some $\delta > 0$ by assumption. Fix $R$, $t$ and $l$ and use
-Lemma \ref{lem-basic-coupling} to define $D_t^*$ so that
-\[
-\E_R D_t^* = \E_{t-l} D_t^* \quad a.s.
-\]
-and
-\[
-\lVert D_t - D_t^* \rVert_2 \leq \couplingBound{l}.
-\]
-Then
-\begin{align*}
-\lVert \E_{t-l} D_t - \E_R D_t \rVert_2 & \leq
-\lVert \E_{t-l} D_t - \E_{t-l} D_t^* \rVert_2  + \lVert \E_{t-l} D_t^* - \E_R D_t \rVert_2 \\
-&\leq 2 \lVert D_t - D_t^* \rVert_2 \\
-&\leq 2^{2 + 1/\rho}\ B_L\ \couplingBeta{l}.\tag*{\qed}
-\end{align*}
-
-\noindent Asymptotic normality follows from~\eqref{eq:24} using a
-modification of \citepos{Jon:97} CLTs for mixingale and NED arrays.
-Define
-\begin{equation*}
-  Z_i = \ZDef
-\end{equation*}
-where $b_T$ is a sequence that satisfies $b_T\leq P$,
-$b_T\to\infty$, and $b_T/P\to 0$.  The same arguments used in
-\citepos{Jon:97} Theorem 1 show that
-\begin{equation*}
-   \SumOuterBlock{i} Z_i = P^{-1/2} \oosSum{s}{1} (D_t - \E_R D_t) + o_p(1).
-\end{equation*}
-and
-\begin{equation*}
-  \SumOuterBlock{i} Z_i = \SumOuterBlock{i} (Z_i - E_{R + (i-1)b_T}
-  Z_i) + o_p(1).
-\end{equation*}
-Note that $\{Z_i - E_{R + (i-1)b_T} Z_i,\mathcal{F}_{R + i b_T}\}_i$ is an
-MDS by construction, so \citepos{HaH:80} Theorem 3.2 and Corollary
-3.1 ensure that $\sigma^{-1} \SumOuterBlock{i} Z_i \to^d N(0,1) $ as
-long as
-\begin{equation*}
-  \sigma^2 - \SumOuterBlock{i} \E_R Z_i^2 \to^p 0,
-\end{equation*}
-and
-\begin{equation*}
-  \SumOuterBlock{i} \E_R Z_i^2 - \SumOuterBlock{i} \ZSqCE \to^p 0.\footnote{%
-    Note that $\sigma^2 \in \mathcal{F}_t$ for
-    all $t \geq R$, so Hall and Heyde's condition (3.21) is
-    unnecessary---see the remarks after their result.} %
-\end{equation*}
-The first equation holds as in \citet{Jon:97} (see the proof
-of his Theorem 2); the second is ensured by
-Lemma~\ref{lem:a2}. \qed
-
-\subsection*{Proof of Lemma \ref{res-convergence}}
-\newcommand{\resConvgRHS}[1]{\ensuremath{\E(L(y^* - x_1^{*\prime}\bh{1#1}) - L(y^{*} -
-x_2^{*\prime}\bh{2#1}) \mid \bh{#1})}}
-\newcommand{\resConvgEstDiff}[1]{\ensuremath{\E(L(y^{*} -
-    x_{#1}^{*\prime}\bh{#1R}) \mid \bh{R}) -
-\E(L(y^{*} - x_{#1}^{*\prime}\bh{#1T}) \mid \bh{T})}}
-\newcommand{\resConvgEstDiffRV}[1]{\ensuremath{L(y^{*} -
-    x_{#1}^{*\prime}\bh{#1R}) - L(y^{*} - x_{#1}^{*\prime}\bh{#1T})}}
-
-Equation~\eqref{eq:7} holds if we show
-\begin{gather}
-\E_R \oosA = \resConvgRHS{R} + o_p(P^{-1/2}),\label{eq:18}\\
-\E_T \oosB = \resConvgRHS{T} + o_p(Q^{-1/2}),\label{eq:19}
-\intertext{and}
-\resConvgEstDiff{i} = O_p(\sqrt{P/T}),\label{eq:20}
-\end{gather}
-where $\hat\theta_R = (\hat\theta_{1R}, \hat\theta_{2R})$,
-$\hat\theta_T = (\hat\theta_{1T}, \hat\theta_{2T})$, and $y^{*}$,
-$x_1^{*}$ and $x_2^{*}$ are random variables drawn from the joint
-distribution of $(y_{t+\h},x_{1t},x_{2t})$ independently of
-$\mathcal{F}_T$.
-
-\begin{proof}[Proof of~\eqref{eq:18} and~\eqref{eq:19}]
-For~\eqref{eq:18}, define $D_t^*$ for each $t=R+1,R+2,\dots,T-h$ so
-that
-\begin{equation*}
-  \| D_t^* - D_t \|_2 \leq 2^{(1+\rho)/\rho} B_L \beta_{t-R}^{(\rho-2)/2\rho}
-\end{equation*}
-and
-\begin{equation*}
-  \E_R D_t^* = \E(L(y^* - x_1^{*\prime}\hat\theta_{1R}) -
-  L(y^* - x_2^{*\prime}\hat\theta_{2R}) \mid \hat\theta_R) \qquad a.s.
-\end{equation*}
-Lemma~\ref{lem-basic-coupling} ensures that these $D_t^*$ exist.
-Now,
-\begin{align*}
-  \Big\lVert \E_R \oosA - \E\Big(P^{-1} \sum_{t=R+1}^{T-h} D_t^* \mid
-  \hat\theta_R\Big) \Big\rVert_2
-  &= \Big\lVert \E_R\Big( \oosA - P^{-1} \sum_{t=R+1}^{T-h} D_t^*
-  \Big) \Big\rVert_2 \\
-  &\leq P^{-1} \sum_{t=R+1}^{T-h} \lVert D_t - D_t^* \rVert_2\\
-  &= O(P^{-1}) \sum_{t=R+1}^{T-h} \beta_{t-R}^{(\rho-2)/2\rho}
-\end{align*}
-and this last term is $o(P^{-1/2})$ by assumption.
-Essentially the same argument proves~\eqref{eq:19} as well.
-\end{proof}
-
-\begin{proof}[Proof of~\eqref{eq:20}]
-Assumption~\ref{asmp-3} and the definition of the OLS estimator
-ensure that
-\begin{align*}
-  \|L(y^{*} -  x_i^{*\prime} \bh{iR}) - L(y^{*} - x_i^{*\prime} \bh{iT}) \|_1
-  &\leq B_{L} \| x_i^{*\prime} (\bh{iR} - \bh{iT}) \|_2 \\
-  &\leq B_{L} \, \| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
-  (X_{iR}'X_{iR})^{-1}] X_{iR}' \eb_{iR} \|_2 \\
-  &\quad+ B_L \, \| x_i^{*\prime}
-  (X_{iT}'X_{iT})^{-1}[X_{iT}'\eb_{iT} - X_{iR}
-  \eb_{iR} ] \|_2 .
-\end{align*}
-
-To simplify notation, define $V = (X_{iT}'X_{iT})^{-1} -
-(X_{iR}'X_{iR})^{-1}$ and $W = X_{iR}'\eb_{iR} \eb_{iR}'X_{iR}$. The
-first term in the upper bound satisfies
-\begin{align*}
-  \| x_i^{*\prime} V X_{iR}' \eb_{iR} \|_2^2
-  &\leq \eigen_{K_i}(\E x_i^* x_i^{*\prime}) \cdot \E \tr\big( V^2 W \big) \\
-  &= O(1) \cdot \E \tr\{ V^2 \E(W \mid
-  X_{iR}'X_{iR}, x_{i,R-\h+1} x_{i,R-\h+1}',\dots, x_{i,T-\h} x_{i,T-\h}')\}
-\end{align*}
-by assumption. Observe that
-\begin{multline*}
-  \E \tr\{ V^2 \E(W \mid X_{iR}'X_{iR}, x_{i,R-\h+1} x_{i,R-\h+1}',\dots, x_{i,T-\h} x_{i,T-\h}')\}
-  \\ \leq
-  \Big\rVert \sum_{i=1}^{K_i} \eigen_i^2 \big(V\big) \Big\rVert_{3/2}
-  \big\rVert \eigen_{K_i}(\E(W \mid
-  X_{iR}'X_{iR}, x_{i,R-\h+1} x_{i,R-\h+1}',\dots, x_{i,T-\h} x_{i,T-\h}')) \big\rVert_3.
-\end{multline*}
-The second term in this product is $O(R)$ by
-Assumption~\ref{asmp-2}. To bound the first term, note that
-$(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}$ has rank $P$ and
-each of its nonzero eigenvalues is bounded in absolute value by the
-eigenvalues of $(X_{iR}'X_{iR})^{-1}$. The eigenvalues of
-$(X_{iR}'X_{iR})^{-1}$ are $O_{L_3}(1/R)$ by Assumption~\ref{asmp-2}, so
-\begin{equation*}
-  \Big\|\sum_{j=1}^{K_i}
-  \eigen_j^2(V)\Big\|_{3/2}
-  \leq \Big\|\sum_{j=K_i - P+1}^{K_i} \eigen_j^2(V) \Big\|_{3/2}
-  = O(P/R^2).
-\end{equation*}
-Consequently,
-\begin{equation*}
-  \E \tr\bigg\{[(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}]^2
-  X_{iR}'\eb_{iR} \eb_{iR}X_{iR} \bigg\} = O(P/R)
-\end{equation*}
-and so
-\begin{equation*}
-  \| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
-  (X_{iR}'X_{iR})^{-1}] X_{iR}' \eb_{iR} \|_2 = O(\sqrt{P/R}).
-\end{equation*}
-
-A similar argument proves that
-\begin{equation*}
-  \big\| x_i^{*\prime} (X_{iR}'X_{iR})^{-1}
-  [X_{iT}'\eb_{iT} - X_{iR} \eb_{iR} ] \big\|_2 =  O(\sqrt{P/R}),
-\end{equation*}
-completing the proof.
-\end{proof}
-
-\subsection*{Proof of Theorem \ref{res-oost}}
-We can rewrite the centered \oost\ statistic as
-\[
-\sqrt{P}(\oosA - \E_T \oosB)/\sh
-= \frac{\sigma}{\sh}\, \Big( \sqrt{P}(\oosA - \E_R \oosA)/\sigma
-+ \sqrt{P}(\E_R \oosA - \E_T \oosB)/\sigma \Big)
-\]
-so Lemma \ref{res-mixingale} and \ref{res-convergence} ensure that
-this term is asymptotically standard normal as long as $\sigma/\sh
-\to^p 1$. Since $\sigma$ is almost surely positive, this convergence
-is equivalent to $\sigma^2 - \sh^2 \to^p 0$.
-
-The proof that $\sigma^2 - \sh^2 \to^p 0$ follows \citepos{JoD:00}
-Theorem 2.1 closely.  We start by defining similar quantities to
-theirs, borrowing their notation when possible to make the
-similarities apparent. Let $b_T \equiv \lfloor \gamma/\delta \rfloor$,
-define $\kernelB{x}$ as in Equation \eqref{eq:13}, and define the following
-terms as in \citet{JoD:00}:
-\begin{align*}
-  \varianceTermI &\equiv
-  \varianceTermIDefn,\\ \varianceTermII &\equiv \vtSum
-  \varianceTermIIa\\& \quad \times \varianceTermIIb,\\
-  \varianceTermIII &\equiv \vtSum \varianceTermIIIa\\
-  &\quad \times \varianceTermIIb,\\
-  \varianceTermIV &\equiv \vtSum \varianceTermIIIa \\
-  &\quad\times \varianceTermIVb.
-\end{align*}
-These definitions give the inequalities
-\begin{align*}
-  \lVert \sh^2 - \sigma^2 \rVert_1 &
-  \leq \lVert \sh^2 - \varianceTermI \rVert_1
-  + \lVert \varianceTermI - \varianceTermII \rVert_1
-  + \lVert \varianceTermII - \varianceTermIII \rVert_1
-  + \lVert \varianceTermIII - \varianceTermIV \rVert_1\\ & \quad
-  + \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1
-  + \lVert \E_R\varianceTermIII - \E_R\varianceTermIV \rVert_1
-  + \lVert \E_R\varianceTermII - \E_R\varianceTermIII \rVert_1\\ & \quad
-  + \lVert \E_R\varianceTermI - \E_R\varianceTermII \rVert_1
-  + \lVert \E_R \varianceTermI - \sigma^2 \rVert_1
-  \\ &
-  \leq  \lVert \sh^2 - \varianceTermI \rVert_1
-  + 2(\lVert \varianceTermI - \varianceTermII \rVert_1
-      + \lVert \varianceTermII - \varianceTermIII \rVert_1
-      + \lVert \varianceTermIII - \varianceTermIV \rVert_1) \\
-  & \quad + \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1
-  + \lVert \E_R \varianceTermI - \sigma^2 \rVert_1.
-\end{align*}
-De Jong and Davidson (2000) prove that
-\begin{equation*}
-\lim_{\delta\to0} \limsup_{T\to\infty} \lVert \varianceTermI -
-\varianceTermII\rVert_1 = 0,
-\end{equation*}
-\begin{equation*}
-\lim_{\delta\to0} \limsup_{T\to\infty} \lVert \varianceTermII - \varianceTermIII
-\rVert_1 = 0,
-\end{equation*}
-\begin{equation*}
-\lim_{\delta\to0} \limsup_{T\to\infty} \lVert \varianceTermIII - \varianceTermIV
-\rVert_1 = 0,
-\end{equation*}
-and
-\begin{equation*}
-\lim \lVert \E_R \varianceTermI - \sigma^2 \rVert_1 = 0.
-\end{equation*}
-Their proofs of these four convergence results use the fact that NED
-functions of mixing processes are also mixingale processes and do not
-use any other properties specific to NED processes, so their results
-hold here as well.  We do need to modify their proofs that
-\begin{equation*}
-  \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1 \to 0
-\end{equation*}
-and
-\begin{equation*}
-  \lVert \sh^2 - \varianceTermI \rVert_1 \to 0
-\end{equation*}
-for all positive $\delta$, though, since those proofs exploit NED
-properties. These results are presented as Lemmas~\ref{lem:a2}
-and~\ref{lem:a6} respectively.  \qed
-
-\subsection*{Proof of Theorem \ref{res:oostest}}
-Coverage of the confidence intervals is immediate from
-Theorem~\ref{res-oost}, so we will present a proof of~\eqref{eq:23}.
-By Lemma~\ref{res-convergence}, we know that $\E_R \oosA - \E_T \oosB
-\to^p 0$, so
-\begin{equation*}
-  \Pr[\E_R \oosA \leq 0] - \Pr[\E_T \oosB \leq 0] \to 0.
-\end{equation*}
-Now we can use Lemma~\ref{lem-basic-coupling} to define $D_t^*$ as in
-the proofs of Lemma~\ref{res-mixingale} and~\ref{res-convergence} so
-that $\E_R D_t^* = \E_{t-l} D_t^*$ a.s. and
-\[
-\lVert D_t - D_t^* \rVert_2 \leq \couplingBound{l}
-\]
-and define $\oosA^* = P^{-1} \sum_{t=R+1}^{T-\h} D_t^*$. Then
-\begin{equation*}
-  \lVert \sqrt{P} \oosA - \sqrt{P} \oosA^* \rVert_2
-  \leq P^{-1/2} \sum_{t=R+1}^{T-\h} \lVert \oosA - \oosA^* \rVert_2
-  = o(1),
-\end{equation*}
-and, consequently, we have convergence in probability of the following
-vectors:
-\begin{equation*}
-  (\sqrt{P} \oosA^*/\sigma,\ \E_R \oosA) -
-  (\sqrt{P} \oosA/\sh,\ \E_T \oosB) \to^p 0,
-\end{equation*}
-where we are implicitly using consistency of $\sh^2$ for $\sigma^2$.
-More importantly, this implies convergence in distribution of these
-vectors, so
-\begin{equation*}
-  \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha
-  \text{ and } \E_R \oosA \leq 0]
-  - \Pr[\sqrt{P} \oosA / \sh > z_\alpha \text{ and }
-  \E_T \oosB \leq 0] \to 0.
-\end{equation*}
-
-For large enough $T$, both $\Pr[\E_R \oosA \leq 0]$ and $\Pr[\E_T
-\oosB \leq 0]$ are positive (the second by assumption, the first by
-convergence to the second) so (for these $T$)
-\begin{align}\label{eq:31}
-  \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha
-  \mid \E_R \oosA \leq 0] &=
-  \frac{\Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha \text{ and }
-    \E_R \oosA \leq 0]}{\Pr[\E_R \oosA \leq 0]}
-\intertext{and}\label{eq:32}
-  \Pr[\sqrt{P} \oosA / \sh > z_\alpha
-  \mid \E_T \oosB \leq 0] &=
-  \frac{\Pr[\sqrt{P} \oosA / \sh > z_\alpha \text{ and }
-    \E_T \oosB \leq 0]}{\Pr[\E_T \oosB \leq 0]}
-\end{align}
-almost surely. Since the terms on the RHS of Equations~\eqref{eq:31}
-and~\eqref{eq:32} converge to the same limit in probability, we have
-\begin{equation*}
-  \Pr[\sqrt{P} \oosA / \sh > z_\alpha  \mid \E_T \oosB \leq 0]
-  - \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha \mid \E_R \oosA \leq 0]
-  \to^p 0
-\end{equation*}
-and it suffices to show that
-\begin{equation*}
-  \plim \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha \mid \E_R \oosA \leq 0]
-  \leq \alpha.
-\end{equation*}
-
-To establish this inequality, we have
-\begin{align*}
-  \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha \mid \E_R \oosA \leq 0]
-  &\leq \Pr[\sqrt{P} (\oosA^* - \E_R \oosA) / \sigma > z_\alpha
-  \mid \E_R \oosA \leq 0] \\
-  &\leq \E\big(
-  \Pr[\sqrt{P} (\oosA^* - \E_R \oosA) / \sigma > z_\alpha \mid \Fs_R]
-  \mid \E_R \oosA \leq 0\big).
-\end{align*}
-By construction,
-\begin{equation*}
-  \Pr[\sqrt{P} (\oosA^* - \E_R \oosA) / \sigma > z_\alpha \mid \Fs_R]
-  \to \alpha
-\end{equation*}
-since generated pseudo OOS observations in each $D_t^*$ are
-independent of $\Fs_R$, completing the proof.
-\qed
-
-\subsection*{Proof of Theorem~\ref{res:insample1}}
-
-Let $(\e_{t+h}, x_{t}) \sim i.i.d.\ N(0,I)$ and let $\theta_1 = 0$.
-For any $d \geq 0$, the event $\E_T \oosB = -d$ implies that
-\begin{equation*}
-  \E_T (y_{T+\h+1} - x_{1T+1}'\bh{1T})^2
-  = \E_T (y_{T+\h+1} - x_{2T+1}'\bh{2T})^2 - d \quad a.s.
-\end{equation*}
-which can be expressed as
-\begin{equation}\label{eq:34}
-  d + \theta_2'M_2' M_2 \theta_2 + \bh{1T}'\bh{1T} - \bh{2T}'M_1'M_1\bh{2T}
-  = (\bh{2T} - \theta_2)' M_2'M_2 (\bh{2T} - \theta_2) \quad a.s.
-\end{equation}
-$M_2 \bh{2T}$ is normally distributed conditional on $\bh{1T}$ and
-$M_1 \bh{2T}$, and is distributed on the surface of the sphere defined
-by~\eqref{eq:34} conditional on $\bh{1T}$, $M_1 \bh{2T}$, and the
-event $\E_T \oosB = -d$.
-
-Since $M_2 \bh{2T}$ is normal, this conditional distribution is
-invariant to reflection across the axes defined by the eigenvectors of
-its covariance matrix. So when $\theta_2$ lies outside the cylinder
-that contains the acceptance region of $\Lambda$, i.e. when
-$\theta_2'M_2' V_T M_2 \theta_2 > c$, we have\footnote{%
-  To keep the notation in these equations manageable, define the
-  information set
-  $\Gs = \sigma(\E_T \oosB \leq 0,~ \theta_2'M_2' V_T M_2 \theta_2 >
-  c)$.} %
-\begin{align*}
-  \Pr[ \bh{2T}' M_2' V_T M_2 \bh{2T} \leq c \mid \Gs]
-  &= \E\Big( \Pr[ \bh{2T}'M_2' V_T M_2 \bh{2T} \leq c \mid \Gs,~\bh{1T},~M_1 \bh{2T}] \mid \Gs \Big) \\
-  & < 1/2
-\end{align*}
-since the inner conditional probability is less than 1/2.
-
-Now let $\delta > 0$ be an arbitrary but small constant, and choose
-$\theta_2$ far enough from the origin to ensure that
-\begin{equation*}
-  \Pr[\theta_2'M_2' V_T M_2 \theta_2 \leq c] \leq \delta
-\end{equation*}
-for large enough $T$. Then
-\begin{align*}
-  \E(\Lambda \mid \E_T \oosB \leq 0) &
-  \geq \Pr[\bh{2T}' M_2' V_T M_2 \bh{2T} > c \mid \E_T \oosB \leq 0] \\
-  &= \Pr[\bh{2T}' M_2' V_T M_2 \bh{2T} > c \text{~~and~~}
-  \theta_2'M_2' V_T M_2 \theta_2 > c \mid \E_T \oosB  \leq 0] \\
-  & \quad + \Pr[\bh{2T}' V_T M_2 \bh{2T} > c \text{~~and~~ }
-  \theta_2'M_2' V_T M_2 \theta_2 \leq c \mid \E_T \oosB \leq 0].
-\end{align*}
-The second term is nonnegative by design. By conditioning on
-$\theta_2'M_2' V_T M_2 \theta_2 > c$ our earlier argument shows that
-the first term is greater than or equal to $(1 - \delta) / 2$. Since
-$\delta$ is arbitrarily small, this completes the proof.
-\qed
-
-\subsection*{Proof of Theorem~\ref{res:insample2}}
-As in the proof of Theorem~\ref{res:insample1}, let $(\e_{t+h}, x_{t})
-\sim i.i.d.\ N(0,I)$ and let $\theta_1 = 0$. The event $\E_T \oosB
-\geq 0$ implies that
-\begin{equation*}
-  \E_T (y_{T+\h+1} - x_{1T+1}'\bh{1T})^2
-  \geq \E_T (y_{T+\h+1} - x_{2T+1}'\bh{2T})^2 \quad a.s.
-\end{equation*}
-which can be expressed as
-\begin{equation}\label{eq:2}
-  \theta_2'M_2 M_2'\theta_2 + \bh{1T}'\bh{1T} - \bh{2T}'M_1'M_1\bh{2T}
-  \geq (\bh{2T} - \theta_2)' M_2'M_2 (\bh{2T} - \theta_2) \quad a.s.
-\end{equation}
-$M_2 \bh{2T}$ is normally distributed conditional on $\bh{1T}$ and
-$M_1 \bh{2T}$, and is a.s. contained in the sphere defined
-by~\eqref{eq:2} conditional on $\bh{1T}$, $M_1 \bh{2T}$, and the
-event $\E_T \oosB \geq 0$.
-
-Let $\delta$ be a small arbitrary constant, define $\theta^*$ as
-\begin{gather*}
-  \theta^* = \argmax_\theta \theta' M_2' M_2 \theta \\
-  s.t.\quad \theta_2'M_2'M_2\theta_2 +  \bh{1T}'\bh{1T} - \bh{2T}'M_1'M_1\bh{2T} = (\theta - \theta_2)' M_2'M_2 (\theta - \theta_2)
-\end{gather*}
-($\theta^*$ is stochastic and depends on $\bh{1T}$ and $M_1 \bh{2T}$)
-and choose $c$ so that
-\begin{equation*}
-  \Pr[ \theta^{* \prime} M_2 M_2 \theta^* > c] < \delta.
-\end{equation*}
-
-Then, we have for large enough $T$
-\begin{align*}
-  \E(\Lambda \mid \E_T \oosB \geq 0) &\leq
-  \Pr[\bh{2T}'M_2'M_2\bh{2T} > c \mid \E_T \oosB \geq 0) \\
-  &\leq \delta
-\end{align*}
-Since $\delta$ is arbitrarily close to zero, this completes the proof.
-
-\qed
-
-\clearpage
-\markboth{}{}
-\tryinput{floats/mc-ftest.tex}
-
-\begin{table}[tb]
-  \begin{tabularx}{\linewidth}{XX}
-    \toprule
-    Category & Variable \\
-    \midrule
-    Stock market variables
-    & Dividend to price ratio (log) \\
-    & Earnings to price ratio (log) \\
-    & Stock market variance \\
-    & Book to market ratio \\
-    & Net equity expansion \\
-    & Percent equity issuing \\\\
-    Interest rate variables
-    & Treasury Bill rate (3 month) \\
-    & Long term yield \\
-    & Long term rate \\
-    & Default return spread \\
-    & Default yield spread \\
-    & Inflation rate \\
-    \bottomrule
-  \end{tabularx}
-  \caption{Variables used to predict the equity premium
-    (Section~\ref{sec:empirics}).
-    Please see Goyal and Welch's original paper \citep{GoW:08}
-    for a detailed description of each variable.}
-  \label{tab:equity}
-\end{table}
-
-\tryinput{floats/empirics-insample.tex}
-\tryinput{floats/empirics-insample-tuned.tex}
-% These macros create tables. They are defined in
-% floats/empirics-insample.tex and possibly overwritten in the next
-% file.
-\insamplecoefs
-\insampletests
-
-\begin{figure}\centering
-  {\large Coverage of DMW OOS interval for $\E_R\oosA$ in simulations}
-  \tryinput{floats/mc-interval-testerror1.tex}
-  \caption{Simulated coverage of $\E_R \oosA$ at 90\% confidence using
-    a one-sided interval based on the DMW \oost\ test, plotted as a
-    function of the fraction of observations used in the test sample,
-    $P/T$. The solid horizontal line denotes the intervals' nominal
-    coverage.}
- \label{fig:interval-R}
-\end{figure}
-\clearpage
-
-\begin{figure}\centering
-  {\large Coverage of DMW OOS interval for $\E_T\oosB$ in simulations}
-  \tryinput{floats/mc-interval-generror1.tex}
-  \caption{Simulated coverage of $\E_T \oosB$ at 90\% confidence using
-    a one-sided interval based on the DMW \oost\ test, plotted as a
-    function of the fraction of observations used in the test sample,
-    $P/T$.  The solid horizontal line denotes the intervals' nominal
-    coverage.}
-  \label{fig:interval-T}
-\end{figure}
-\clearpage
-
-\begin{figure}\centering
-  {\large Size of DMW \oost\ test in simulations}
-  \tryinput{floats/mc-dmwsize.tex}
-  \caption{Simulated rejection probabilities for the DMW \oost\ test
-    under the null hypothesis that the benchmark model will forecast
-    better, $\E_T \oosB \leq 0$. The nominal size is 10\% and is
-    marked with a solid horizontal line. Values greater than 10\%
-    indicate that the test rejects the benchmark model too often. See
-    Section~\ref{sec:simulation-design} for a discussion of the
-    simulation design.}
-  \label{fig:ttest-size}
-\end{figure}
-\clearpage
-
-\begin{figure}\centering
-  {\large Size of Clark-West OOS test in simulations}
-  \tryinput{floats/mc-clarkwestsize.tex}
-  \caption{Simulated rejection probabilities for Clark and West's
-    (2006, 2007) OOS test statistic under the null hypothesis that the
-    benchmark will forecast better, $\E_T \oosB \leq 0$. The nominal
-    size is 10\% and is marked with a solid horizontal line. Values
-    greater than 10\% indicate that the test rejects the benchmark
-    model too often. See Section~\ref{sec:simulation-design} for a
-    discussion of the simulation design.}
-   \label{fig:clarkwest}
-\end{figure}
-\clearpage
-
-\begin{figure}\centering
-  {\large Size of McCracken \oost\ test in simulations}
-  \tryinput{floats/mc-mccrackensize.tex}
-  \caption{Simulated rejection probabilities for McCracken's (2007)
-    \oost\ test under the null hypothesis that the benchmark model is
-    more accurate, $\E_T \oosB \leq 0$. Nominal size is 10\% and is
-    marked with a solid horizontal line. Values greater than 10\%
-    indicate that the test rejects the benchmark model too often. See
-    Section~\ref{sec:simulation-design} for a discussion of the
-    simulation design.}
-  \label{fig:mccracken}
-\end{figure}
-\clearpage
-
-\begin{figure}\centering
-  {\large Power of DMW \oost\ test in simulations}
-  \tryinput{floats/mc-dmwpower.tex}
-  \caption{Simulated rejection probabilities for the DMW \oost\ test
-    under the alternative that the benchmark model is less accurate,
-    $\E_T \oosB > 0$. Nominal size is 10\% and is marked with a solid
-    horizontal line. Values greater than 10\% indicate that the test
-    rejects the benchmark model too often. See
-    Section~\ref{sec:simulation-design} for a discussion of the
-    simulation design.}
-  \label{fig:ttest-power}
-\end{figure}
-\clearpage
-
-\begin{figure}
-\centering
-\large{Difference in OOS MSE of Prevailing Mean and\\ Kitchen
-    Sink Models of Equity Premium (OLS)}
-\tryinput{floats/empirics-oos-mse-1.tex}
-\tryinput{floats/empirics-oos-mse-1b.tex}
-\caption{OOS difference in the MSE
-  of the prevailing mean benchmark and the kitchen sink model as a
-  function of the test sample size, $R$.  Both models forecast the
-  equity premium using annual data from 1928--2008.  The solid line
-  gives the OOS average, and the shaded region indicates the
-  one-sided 95\% confidence interval implied by the
-  DMW test.  The bottom panel is a detailed view of the top
-  panel for $R \geq 50$.}
-\label{fig:empirics1}
-\end{figure}
-\clearpage
-
-\begin{figure}
-\centering
-\large{Difference in OOS MSE of Prevailing Mean and\\ Kitchen
-    Sink Models of Equity Premium (CT)}
-\tryinput{floats/empirics-oos-mse-2.tex}
-\tryinput{floats/empirics-oos-mse-2b.tex}
-\caption{OOS difference in the MSE
-  of the prevailing mean benchmark and the kitchen sink model as a
-  function of the test sample size, $R$.  Both models forecast the
-  equity premium using annual data from 1928--2008.  The solid line
-  gives the OOS average, and the shaded region indicates the
-  one-sided 95\% confidence interval implied by the
-  DMW test.  The bottom panel is a detailed view of the top
-  panel for $R \geq 50$.}
-\label{fig:empirics2}
-\end{figure}
-\clearpage
-
-\begin{figure}
-\centering
-\large{OOS MSE of Individual Forecasts of Equity Premium}
-\tryinput{floats/empirics-oos-ind-ks.tex}
-\tryinput{floats/empirics-oos-ind-pm.tex}
-\caption{OOS MSE of the Prevailing Mean (PM) and
-    Kitchen Sink (KS) models for equity premium prediction as
-    a function of the size of the training sample, $R$.  Please note
-    that the vertical scales are different in the two plots.}
-\label{fig:empirics3}
-\end{figure}
-
-\clearpage
-
-\bibliographystyle{abbrvnat}
-\bibliography{latex-tools-0.2.1/references}
-
-\clearpage
-\section{Supplemental appendix (not for publication)}
-\input{appendix_contents}
-
-\end{document}
+are listed in the Appendix, as is an example DGP that illustrates
+the main theoretical results of the paper.
 
@@
 %%% End:
-
-%  LocalWords:  ClM Mcc ClW MeR StW InK CCS CoS GiW GiR BRC HTF BoH '
-%  LocalWords:  Tib BaN AIC BoB AkA AkP Efr iR eq FPE th Dou iS iT dx
-%  LocalWords:  JoD ixz Mcl RHS MSE homoskedastic Joh Widom TrW Sil
-%  LocalWords:  BFP dy LLNs VeR rlecuyer RSQLite Sar tikzDevice TikZ
-%  LocalWords:  PGF LaTeX jt test's CaT Coc BRW LeN RaW RaZ LeR ZeH
-%  LocalWords:  lmtest Zei dbframe Hmsic Har xtable Dah booktabs FeE
-%  LocalWords:  Bonferroni BWB Gia MeP indices Schwarz HaH Jong i1 1R
-%  LocalWords:  overcorrect 'X 's 2P i' 2i 2m 4C De eigenvectors 'M
-%  LocalWords:  2'M 1'M DiM GoW Cla Whi RoW HHK Rde

### 2017-04-21 2-setup.tex
[#40/move] Move extended example from Section 3.3 to appendix

--- 2016-03-09 paper.tex
@@
-\documentclass[12pt,draft]{article}
-\input{setup}
-
-\title{Out-of-Sample Comparisons of Overfit Models}
-\author{Gray Calhoun\thanks{email: gcalhoun@iastate.edu. I
-    would like to thank Julian Betts, Helle Bunzel,
-    St\'ephane Bonhomme, Marjorie Flavin,
-    Nir Jaimovich, Lutz Kilian, Ivana Komunjer, Michael McCracken,
-    Seth Pruitt, Ross Starr, Jim Stock, Yixiao Sun, Allan Timmermann,
-    Hal White, several anonymous referees, participants at the 2010
-    Midwest Economics Association Annual Meetings, the 2010
-    International Symposium on Forecasting, the 2010 Joint Statistical
-    Meetings, the 2011 NBER-NSF Time-Series
-    Conference, and in many seminars at UCSD, and especially
-    Graham Elliott for their valuable suggestions, feedback and advice
-    in writing this paper.  I would also like to thank Amit Goyal for
-    providing computer code and data for his 2008 RFS paper
-    with Ivo Welch \citep{GoW:08}.} \\ Iowa State University}
-
-\date{\VERSION}
-
-\begin{document}
-\maketitle
-
-\begin{abstract}\noindent
-  This paper uses dimension asymptotics to study the behavior of
-  out-of-sample (OOS) test statistics when they are used to compare
-  ``overfit'' linear regression models. Under these asymptotics, the
-  number of predictors used by the larger model increases with the
-  number of observations so that their ratio remains uniformly
-  positive. This analysis gives a theoretical motivation for using
-  out-of-sample (OOS) comparisons: the Diebold-Mariano-West OOS $t$-test
-  (Diebold and Mariano, 1995, \textit{JBES}, and West, 1996,
-  \textit{Econometrica}) allows a forecaster to conduct inference
-  about the models' generalization error, an important measure of
-  forecast accuracy that conditions on the models' parameter estimates.
-  We show analytically and through Monte Carlo that standard full-sample
-  test statistics can not test hypotheses about this measure of performance.
-  Our paper also suggests that comparisons of overfit models require small
-  OOS test samples. If $P$ denotes the number of observations used for the
-  OOS comparison and $T$ the total number of observations, $P^2/T$ must
-  converge to zero for the OOS $t$-test to be centered on the model's
-  generalization error.
-
-\noindent JEL Classification: C12, C22, C52, C53
-
-\noindent Keywords: Generalization Error, Forecasting, Model
-Selection, $t$-test, Dimension Asymptotics
-\end{abstract}
-\newpage
-
-\section{Introduction}
-\label{sec:introduction}
-
-Consider two sequences of length $P$ of prediction errors, the result
-of forecasting the same variable with two different estimated models.
-Both models are estimated with $R$ observations, collectively called
-the {\em estimation window}, and are used to forecast an additional
-$P$ observations, called the {\em test sample}.  There are $T$
-observations in all, and $R+P=T$.  This paper introduces a new limit
-theory for statistics constructed from these prediction errors
-designed to approximate the behavior of the statistics when one of the
-models is overfit.  In doing so, we provide a theoretical
-justification for forecasters to use out-of-sample (OOS) instead of in-sample
-comparisons: the DMW OOS test\footnote{%
-  In this paper, we will refer to the basic OOS $t$-test studied by
-  \citet{DiM:95} and \citet{Wes:96} as the DMW test.} %
-allows a forecaster to conduct
-inference about the expected future accuracy of his or her models when
-one or both is overfit.  We show analytically and through Monte Carlo simulations
-that standard full-sample test statistics can not test hypotheses
-about this performance.
-
-Our paper also shows that popular test and training sample sizes may
-give misleading results if researchers are concerned about overfit.
-We show that $P^2/T$ must converge to zero for the DMW test to give
-valid inference about the expected forecast accuracy, otherwise the
-test measures the accuracy of the estimates constructed using only the
-training sample.  In empirical research, $P$ is typically much larger
-than this.  Our simulations indicate that using large values of $P$
-with the DMW test gives undersized tests with low power, so this
-practice may favor simple benchmark models too much.  Existing
-corrections, proposed by \citet{ClM:01,ClM:05}, \citet{Mcc:07} and
-\citet{ClW:06,ClW:07}, seem to overcorrect for this problem, though, and reject
-too often when the benchmark model is more accurate.
-
-Although OOS comparisons have been popular in Macroeconomics and
-Finance since \citepos{MeR:83} seminal study of exchange rate models,
-it has been unclear from a theoretical perspective whether or not the
-statistics are useful.  Empirical researchers often cite ``overfit''
-or ``instability'' as reasons for using OOS comparisons, as in
-\citet{StW:03}, but neither term is precisely defined or formalized.
-Compounding this problem, the asymptotic distributions of these
-statistics are derived under conditions that rule out either
-instability or overfit and allow a researcher to use a conventional
-in-sample comparison---a variation of the $F$-test, for example.  As
-\citet{InK:04} argue, the statistics themselves are designed to test
-hypotheses that can be tested by these in-sample statistics.  For
-example, \citet{DiM:95} and \citet{Wes:96} derive the limiting
-distributions of many popular OOS test statistics under conditions
-that would justify these full-sample tests.  Much
-of the subsequent research by \citet{Mcc:00, Mcc:07}, \citet{CCS:01},
-\citet{ClM:01,ClM:05}, \citet{CoS:02,CoS:04}, \citet{ClW:06,ClW:07},
-\citet{Ana:07}, and others relaxes several of Diebold and Mariano's
-and West's assumptions, but maintains the stationarity and dependence
-conditions that permit in-sample comparisons \citep[see][for a
-review of this literature]{Wes:06}.\footnote{%
-  Like us, \citet{Ana:07} allows the number of regressors to increase
-  with $T$.  But in that paper, the number of regressors increases
-  slowly enough that the OLS coefficients are consistent and
-  asymptotically normal.} %
-\citet{GiW:06} and
-\citet{GiR:09, GiR:10} are exceptions.  Instead of focusing on
-hypotheses that can be tested by in-sample comparisons, \citet{GiW:06}
-derive an OOS test for the null hypothesis that the difference
-between two models' OOS forecasting performance is unpredictable, a
-martingale difference sequence (MDS); \citet{GiR:09} test whether the OOS
-forecasting performance of a model suffers from a breakdown relative
-to its in-sample performance; and \citet{GiR:10} test whether the
-forecasting performance is stable. However, those papers focus on a
-particular OOS estimation strategy and do not address why OOS
-comparisons might be useful as a general strategy.
-
-Since in-sample and OOS statistics require similar assumptions and
-test similar hypotheses, one might expect that they would give similar
-results.  They do not.  In-sample analyses tend to support more
-complicated theoretical models and OOS analyses support simple
-benchmarks, as seen in \citet{MeR:83}, \citet{StW:03}, and
-\citet{GoW:08}.  Since these different approaches strongly influence
-the outcome of research, it is important to know when each is
-appropriate.  The explanations in favor of OOS comparisons claim
-that they should be more robust to unmodeled instability
-\citep{ClM:05,GiW:06,GiR:09,GiR:10} or to overfit
-\citep{Mcc:98,Cla:04}.  Both explanations presume that the in-sample
-comparison is invalid and the OOS comparisons are more reliable.  Of
-course, as \citet{InK:04,InK:06} point out, both in-sample and OOS
-methods could be valid, but the OOS methods could have lower power.
-
-In this paper, we study the ``overfit'' possibility and leave
-``instability'' to future research. This paper uses dimension
-asymptotics to study the behavior of OOS comparisons when at least
-one of the models is overfit---the number of its regressors
-increases with the number of observations so that their ratio remains
-positive.  Although overfit is sometimes used to describe the
-situation where a forecaster chooses from many different models,
-i.e. \emph{data-mining} or \emph{data-snooping}, we view these as
-separate issues.  Procedures that account for the presence of many
-models have been, and are continuing to be, developed \citep[see, for
-example,][]{Whi:00,Han:05,RoW:05,HHK:10,ClM:12b}, but it is unclear
-whether those procedures should themselves use in-sample or OOS
-comparisons.  Understanding the difference between in-sample and OOS
-comparisons in the context of a simple comparison between two models
-is necessary before resolving any new issues that arise with multiple
-comparisons. Moreover, the empirical research that motivates
-this paper uses \emph{pseudo} OOS comparisons and not
-true OOS comparisons.  Even if a true OOS comparison
-could account for some forms of data-snooping better than
-\citepos{Whi:00} BRC or its extensions, in-sample and pseudo
-OOS comparisons would both be affected by the data-snooping, a
-point also made by \citet{InK:04}.
-
-We focus on linear regression models estimated with a fixed window
-for simplicity, but our basic conclusions should be true for other
-models and estimation strategies as well.  Under this
-asymptotic theory, where the number of regressors $K$ increases with $T$
-so that the limit of $K/T$ is positive and less than one,
-the OLS coefficient estimator is no longer
-consistent or asymptotically normal \citep{Hub:73} and has positive
-variance in the limit.  We show that, even so, the usual OOS average
-is asymptotically normal and can consistently estimate the difference
-between the models' generalization error, the expected loss in the
-future conditional on the data available in period
-$T$.\footnote{%
-  See, for example, \citet{HTF:08} for a discussion of generalization
-  error.} %
-Under these asymptotics, the generalization
-error does not converge to the expected performance of the pseudotrue
-models, so existing in-sample and OOS comparisons measure different
-quantities and should be expected to give different results for
-reasons beyond simple size and power comparisons.  Under our limit theory,
-the model that is closer to the true DGP in population can forecast
-worse.  In such a situation, a standard in-sample comparison would
-correctly reject the null hypothesis that the benchmark is true, and
-an OOS comparison would correctly fail to reject the null that the
-benchmark is more accurate.\footnote{%
-  In a pair of papers similar to ours, \citet{ClM:12,ClM:12b} study
-  in-sample and OOS tests that the larger model has nonzero
-  coefficients that are too close to zero to expect the model to
-  forecast more accurately.  Like this paper, they argue that the
-  larger model can be true but less accurate.  However, they focus on
-  an aspect of the DGP that makes this phenomenon likely, while we
-  focus on the coefficient estimates that produce less accurate
-  forecasts.  Moreover, the implications of our asymptotic theories
-  are different and their papers do not provide reasons to do OOS
-  comparisons.} %
-Also note that, in this situation, a model that performs well
-in-sample can perform badly out-of-sample even if there are no
-structural breaks or other forms of instability.  Researchers
-have argued that a breakdown of in-sample forecasting ability
-indicates a structural break (see \citealp{BoH:99}, and
-\citealp{StW:03}, among others), but we show that this breakdown
-can be caused by overfit as well.
-
-It is important to realize that we are not \emph{advocating} linear
-regression for highly overparametrized models. If $K$ is very large
-relative to $T$, researchers will often want to use some form of
-shrinkage forecast, for example the LASSO \citep{Tib:96} or a factor
-model \citep{StW:02,BaN:02}. Our main focus is practical settings
-where $K$ is \emph{moderately} large and it is not clear whether
-overfit will dominate the results. In these settings it is
-crucial to understand the behavior of different evaluation criteria
-when $K$ is large, in case overfit does turn out to be a concern, and to have reliable
-methods for estimating these overfit models' performance. This is the goal of
-this paper.
-
-Our theoretical results partially justify OOS comparisons when
-researchers want to
-choose a model for forecasting.  Although there has been little
-emphasis on hypothesis testing in this setting, testing is usually
-appropriate: there is usually a familiar benchmark model in place, and
-the cost of incorrectly abandoning the benchmark for a less accurate
-alternative model is higher than the cost of incorrectly failing to
-switch to a more accurate alternative.  We show that the DMW test
-lets the forecaster control the probability of the first error, just
-as with conventional hypothesis testing.
-
-But we also identify new practical limitations for applying the DMW
-test to overfit models.
-Since the models' coefficients are imprecisely estimated in the limit,
-the test sample must be small enough that the model estimated over the
-training sample is similar to the one that will be estimated over the
-full sample.  In particular, $P/T \to 0$ is required for consistent
-estimation of the difference in the two models' performance,
-and $P^2/T \to 0$ is required for valid confidence
-intervals and inference.  For larger $P$, the OOS comparisons remain
-asymptotically normal, but are centered on the forecasting performance
-associated with the period $R$ estimates.  In practice, researchers
-typically use large values of $P$, so these studies may be too
-pessimistic about their models' future accuracy if they use the DMW
-test.  Section~\ref{sec:oostheory} lays out the asymptotic behavior of
-the DMW test under this limit theory.
-
-Popular in-sample tests and model selection criteria, like the Wald
-test and the AIC, do not help forecasters in this setting. We show
-that these statistics do not select the more accurate model when
-choosing between overfit models. For many DGPs the Wald test
-will choose the larger model over a small benchmark
-with probability much greater than its nominal size, regardless of
-which model is more accurate, and the AIC behaves similarly. The BIC,
-however, chooses the benchmark model with probability approaching one
-even when the \emph{alternative} model is more accurate.\footnote{%
-  Our result holds for a broad class of full-sample statistics, but
-  there may be other potential statistics that mimic the OOS test and
-  remain valid. Exploring such statistics is left for future
-  research.} %
-This result holds even though modifications of the $F$-test are valid
-under this asymptotic theory, as shown by \citet{BoB:95},
-\citet{AkA:00}, \citet{AkP:04}, \citet{Cal:11c}, and \citet{Ana:12},
-among others.\footnote{%
-  Also see \citet{Efr:86,Efr:04} for a discussion of naive in-sample
-  loss comparisons.} %
-Moreover, under this asymptotic theory, many recent OOS test
-statistics, such as those derived by \cite{ClM:01,ClM:05},
-\citet{Mcc:07}, and \citet{ClW:06,ClW:07} should have the same
-problems as in-sample tests.\footnote{%
-  Our theoretical results apply directly to \citepos{Mcc:07} OOS
-  $t$-test, since it simply proposes more liberal critical values for
-  the same test statistic that we study.  Since \citet{ClW:06,ClW:07}
-  use a finite length estimation window, our asymptotics are
-  incompatible with theirs and prevent us from studying their test
-  directly, as well as \citepos{GiW:06} and other tests based on
-  \citepos{GiW:06} asymptotics.  But \clws\ test can be viewed as a
-  stochastic adjustment to the critical values of the usual \oost\
-  test, so our conclusions should apply informally as well.
-  Specifically, we show that the DMW test rejects with probability
-  equal to nominal size when the estimated benchmark model is expected
-  to be more accurate, so more liberal critical values result in
-  overrejection.} %
-These tests are also designed to reject the benchmark when the
-alternative model is true, and so they may reject too often when the
-benchmark is misspecified but more accurate.  Obviously, since the
-distribution of these statistics converges to the normal when $P/T \to
-0$ (with the number of regressors fixed), these statistics behave like
-the DMW test when $P$ is small, but should overreject the benchmark
-when $P$ is large. Section~\ref{sec:insample} presents our theoretical
-results for full-sample statistics and Section~\ref{sec:mc} presents
-Monte Carlo evidence to support these claims.
-
-Finally, this paper introduces a new method of proof for OOS
-statistics.  We use a coupling argument (Berbee's Lemma, 1979) to show
-that sequences of OOS loss behave like mixingales when the
-underlying series are absolutely regular, even if the forecasts depend
-on non-convergent estimators.  Moreover, we also show that transformations of these
-processes behave like mixingales after they are appropriately recentered, so
-many arguments used to prove asymptotic
-results for Near Epoch Dependent (NED) functions of mixing processes
-can be used for these OOS processes with only slight modification.
-
-The rest of the paper proceeds as follows.
-Section~\ref{sec:assumptions} introduces our notation and assumptions.
-Section~\ref{sec:theory} gives the main theoretical results for the
-DMW OOS test, shows that standard in-sample tests reject the
-benchmark model too often when it is misspecified but more accurate than the
-alternative, and shows that standard model selection methods can run
-into similar problems. Section~\ref{sec:theory} also presents an
-example DGP that illustrates these results. Section~\ref{sec:mc}
-presents a Monte Carlo study supporting our theoretical results.
-Section~\ref{sec:empirics} applies the OOS statistic to
-\citepos{GoW:08} dataset for equity premium prediction, and
-Section~\ref{sec:conclusion} concludes.  Proofs and supporting results
-are listed in the Appendix.
-
 \section{Setup and assumptions}
@@
 estimated coefficients to future values of the DGP.
-Section~\ref{sec:example} contains an extended example that shows how
-these assumptions are satisfied in a simple setting.
-
-\section{Theoretical results}
-\label{sec:theory}
-
-This section lays out our theoretical results. The first subsection
-presents results for the DMW \oost\ test; we show that it is
-asymptotically normal when one or both forecasting models is overfit.
-(i.e., under our increasing-$K$ asymptotic approximation.) We also
-present a new limitation on these statistics---OOS comparisons heavily
-penalize overfit models unless the size of the test sample is a very
-small proportion of the total sample size, which will not be practical
-in much applied research. The second subsection presents results for
-full-sample statistics and shows that widely used test statistics and
-model selection criteria are misleading when choosing a model for
-forecasting. In contrast to OOS comparisons, these full-sample
-criteria choose overfit models too often, even when they are less
-accurate than simple benchmark models. These results are somewhat
-abstract, so the third subsection works through an example DGP in
-detail.
-
-\subsection{Asymptotic normality of the DMW test}
-\label{sec:oostheory}
-
-This section has two main conceptual results. The first,
-Lemma~\ref{res-mixingale}, shows that the OOS average, $\oosA$, is
-asymptotically normal as the size of the test sample grows, even when
-the models are overfit. But $\oosA$ is centered at $\E_R \oosA$, the
-difference in the generalization error of the models estimated over
-the \emph{training sample}, which is not the quantity of interest to
-forecasters. Forecasters will generally want to estimate or test
-hypotheses about the difference in the generalization error of the
-models estimated with the full sample, $\E_T \oosB$. Our second
-result, Lemma~\ref{res-convergence}, shows that these quantities are
-approximately equal only when the test sample is very small relative
-to the total sample size. In particular, we show that $\oosA$ is a
-consistent estimator of $\E_T \oosB$ when $P/T \to 0$ and is
-asymptotically normal with mean $\E_T \oosB$ when $P^2/T \to 0$. After
-establishing these Lemmas, we then show that the \oost\ test is
-asymptotically standard normal and can be used to test hypotheses
-about $\E_T \oosB$, which requires the two Lemmas as well as a
-consistent estimator of the variance of the OOS average.
-
-In the first result, we show that
-$\sqrt{P} (\oosA - \E_R \oosA)$ is asymptotically normal as $P \to
-\infty$. This application of the CLT is complicated by a hidden source
-of dependence---the training sample estimators $\bh{iR}$. Under
-conventional asymptotic theory, we would replace each $\bh{iR}$ with
-its pseudotrue value $\theta_i$ and apply the CLT to
-$L(y_{t+\h} - x_{it}'\theta_i)$, with some complications potentially
-arising from the replacement (as in \citealp{Wes:96},
-\citealp{ClM:01}, or \citealp{Mcc:07}, for example). But we can not
-make that replacement here, because our asymptotic approximation
-prevents $x_{it}'\bh{iR}$ from converging to $x_{it}'\theta_i$.
-
-Instead, we show that $D_t - \E_R D_t$ is an $L_2$-mixingale that
-satisfies the CLT. Mixingales satisfy a weak-dependence condition
-similar to MDSes,\footnote{%
-  An array $Z_{n,t}$ and an increasing sequence of \sfields
-  $\Gs_{n,t}$ is an \emph{$L_2$-mixingale of size $-1/2$} if there is
-  an array of constants $\{c_{n,t}\}$ and a sequence of constants
-  $\zeta_l = O(l^{-1/2 - \delta})$ for some $\delta > 0$ such that
-  \begin{equation*}
-    \lVert \E(Z_{n,t} \mid \Gs_{n,t-l}) \rVert_2
-    \leq c_{n,t} \zeta_l
-    \qquad\text{and}\qquad
-    \lVert Z_{n,t} - \E(Z_{n,t} \mid \Gs_{n,t+l}) \rVert_2
-    \leq c_{n,t} \zeta_{l+1}.
-  \end{equation*}
-  Mixingales were introduced and developed by
-  \citet{Mcl:74,Mcl:75,Mcl:75b,Mcl:77}.} %
-but they have some limitations. Transformations of mixingales are
-typically not themselves mixingales, which means that CLTs for
-mixingale processes require additional assumptions to hold beyond the
-mixingale property.\footnote{%
-  See \citet{Jon:97} for an illustration. We will borrow heavily from
-  his results in our proofs.} %
-This is in contrast to Near Epoch Dependent (NED) processes, which
-retain the NED property after transformations. \citep[See chapter 17
-of][for further discussion of these properties.]{Dav:94} But the OOS
-loss has more structure than most mixingales and behaves like an NED
-process in important respects. (The key result here is
-Lemma~\ref{lem:a2} in the Appendix.) Lemma~\ref{res-mixingale} presents the
-CLT that we use later, and Section~\ref{sec:example} works through an
-i.i.d. example in detail. For i.i.d. observations, the OOS loss is an
-MDS and is easier to work with.
-
-\begin{lem}\label{res-mixingale}
-  If Assumptions~\ref{asmp-1}--\ref{asmp-3} hold then $\{D_t - \E_R
-  D_t, \mathcal F_t\}$ is an $L_2$-mixingale of size $-1/2$.
-  Moreover
-  \begin{equation}
-    \sqrt{P}(\oosA - \E_R \oosA)/\sigma \to^d N(0,1)
-  \end{equation}
-  as $P \to \infty$ if $\sigma^2$ is uniformly almost surely positive,
-  where $\sigma^2 = \var_R(\sqrt{P} \oosA)$ (which is equal to $P
-  \E_R(\bar{D}_R - \E_R \bar{D}_R)^2$).
-\end{lem}
-
-It may be helpful to compare Lemma~\ref{res-mixingale} to the method
-of proof in \citet{GiW:06}. \citet{GiW:06} show that the OOS average
-is asymptotically normal when the forecasts are estimated with a fixed
-length rolling window. In that case, each $\bh{it}$ depends on only
-the most recent $R$ observations and, since $R$ is fixed in their
-theory, the forecast errors $y_{t+\h} - x_{it}'\bh{it}$ are themselves
-mixing processes. Transformations of their forecast errors are
-still obviously mixing processes and obey the CLT.
-
-In our paper, $R$ is not fixed and the forecast errors are not a
-convenient weakly-dependent process, since the estimation error in
-$\bh{it}$ introduces strong dependence. Consequently,
-transformations of the forecast errors are not weakly dependent
-either. But this additional dependence has a special form and can be
-removed by subtracting the conditional mean; specifically $g(y_{t+\h} -
-x_{it}'\bh{it})$ is not weakly dependent but $g(y_{t+\h} -
-x_{it}'\bh{it}) - \E_R g(y_{t+\h} - x_{it}'\bh{it})$ is.
-Assumptions~\ref{asmp-1}--\ref{asmp-3} allow us to show directly
-that $D_t - \E_R D_t$ and (crucially) $D^2_t - \E_R D_t^2$ are both
-weakly dependent mixingales, ensuring Lemma~\ref{res-mixingale}.
-
-The next Lemma connects $E_R \oosA$ to $\E_T \oosB$, the difference in
-the models' generalization error. Under conventional asymptotics,
-these quantities are generally close. But they are not for overfit
-models and the models will tend to forecast better when estimated over the
-full sample than over the training sample. Consequently, OOS
-comparisons will penalize overfit models too much unless the test
-sample is small relative to the total data set.
-
-\begin{lem} \label{res-convergence}
-  Under Assumptions \ref{asmp-1}--\ref{asmp-4}a,
-  \begin{equation}\label{eq:7}
-    \E_T \oosB - \E_R \oosA = O_p(\sqrt{P/T}) + o_p(P^{-1/2})
-    + o_p(Q^{-1/2}).
-  \end{equation}
-\end{lem}
-We can view $\E_T \oosB - \E_R \oosA$ as noise introduced by
-approximating the performance of the full-sample estimates with that
-of the partial-sample estimates. The key term on the RHS
-of~\eqref{eq:7} in practice is $O_p(\sqrt{P/T})$---unless $P/T$ is
-small, this noise dominates the OOS average, making it an inconsistent
-estimator of $\E_T \oosB$. The $o_p(P^{-1/2})$ term is completely
-unrestrictive in our applications because we will multiply the OOS
-average by at most $\sqrt{P}$ (for the CLT). And the $o_p(Q^{-1/2})$
-term has some implications for interpreting these results: we can only
-measure the average performance of the forecasting models for an
-extended period in the future, long enough that the future
-observations are essentially independent of the current
-information. For $Q=1$, for example, the dependence between
-$y_{T+\h+1}$ and the current information set $\Fs_T$ may be very
-strong.
-
-Finally, we can use Lemmas~\ref{res-mixingale}
-and~\ref{res-convergence} to show that the DMW test is asymptotically
-normal and centered at $\E_T \oosB$, as long as
-Assumption~\ref{asmp-4}b holds.
-
-\begin{thm}\label{res-oost}
-  Suppose that Assumptions \ref{asmp-1}--\ref{asmp-5} hold (including
-  \ref{asmp-4}b), that $\gamma \to \infty$ and $\gamma/P \to 0$ as $T
-  \to \infty$, and that $\sigma^2$ is uniformly a.s. positive. Define
-  $\sh^2$ to be the usual OOS HAC estimator of the asymptotic variance
-  of $\oosA$,
-  \begin{equation}
-    \sh^2 \equiv P^{-1} \oosSum{s,t}{1} (D_t - \oosA)(D_s - \oosA)
-    \vWeight.
-  \end{equation}
-  Then
-  \begin{equation}
-    \sqrt{P}(\oosA - \E_T\oosB)/\sh \to^d N(0,1).
-  \end{equation}
-\end{thm}
-
-The requirement that $\sigma^2$ be uniformly a.s. positive is not
-restrictive under our asymptotic theory. Since the models'
-coefficients are estimated with uncertainty in the limit, the two
-models give different forecasts even if they both nest the DGP.  This
-is intuitively similar to \citepos{GiW:06} rolling-window result, but
-comes from different asymptotic theory; Giacomini and White keep the
-variance of the OOS average positive by letting $P \to \infty$ with
-$R$ fixed; in this paper, $R \to \infty$ but the variance remains
-positive since $K \to \infty$ (quickly) as well.
-
-If $K_1$ and $K_2$ were finite, West's (1996) and McCracken's (2007)
-asymptotic theories would apply and the \oost\ test would remain normal as long
-as $P/T \to 0$, even if $\sigma^2 \to 0$. Under that asymptotic
-approximation, the variance will converge to zero whenever the true
-DGP is nested in both of the forecasting models. The same principles
-may also apply if $K_1$ and $K_2$ grow slowly, with $K_2/T \to
-0$. It is likely that a second order expansion along the lines of
-\citet{Mcc:07} would lead to asymptotic normality for that
-intermediate case, but we leave that issue to future research.
-
-Finally, Theorem~\ref{res:oostest} establishes that the DMW test can be
-use to construct confidence intervals for $\E_T \oosB$ and test
-hypotheses about $\E_T \oosB$. In particular, forecasters will often
-want to test the null hypothesis that $\E_T \oosB \leq 0$, meaning
-that the benchmark model is expected to be more accurate than the
-alternative model in the future.
-
-\begin{thm}\label{res:oostest}
-  Suppose that the conditions of Theorem
-  \ref{res-oost} hold. Then each of the usual Gaussian
-  confidence intervals,
-  \begin{gather}
-    [\oosA - z_{\alpha/2} \, \sh /
-    \sqrt{P}, \oosA + z_{\alpha/2} \sh / \sqrt{P}],\label{interval-twosided} \\
-    [\oosA - z_{\alpha} \, \sh / \sqrt{P}, +\infty), \label{interval-greater}
-    \intertext{and}
-    (-\infty, \oosA + z_{\alpha} \, \sh / \sqrt{P}],
-  \end{gather}
-  contains $\E_T\oosB$ with probability $\alpha$ in the limit, with
-  $z_{\alpha}$ the $1-\alpha$ quantile of the standard normal
-  distribution. If, in addition, $\lim \Pr[\E_T \oosB \leq 0]$ is
-  positive then
-  \begin{equation}\label{eq:23}
-    \lim \Pr[P^{1/2}\oosA/\sh > z_{\alpha} \mid \E_T
-    \oosB \leq 0] \leq \alpha.
-  \end{equation}
-\end{thm}
-\noindent
-The results for confidence intervals in Theorem~\ref{res:oostest}
-follow immediately from Theorem~\ref{res-oost},
-but~\eqref{eq:23} requires additional proof.
-
-\subsection{Failure of in-sample statistics for forecast evaluation}
-\label{sec:insample}
-
-In this subsection we look at the behavior of some full-sample
-statistics under the same asymptotic theory as before.  We show that
-these statistics, which include common tests such as the Wald test as
-well as model selection criteria such as the AIC, do not measure the
-models' generalization error and consequently do not indicate which
-model will be more accurate in the future. Some of these statistics
-will tend to choose the larger model regardless of which model will be
-more accurate in the future, whereas others tend to choose the smaller
-model.  This is a different issue than whether or not full-sample
-tests are valid for testing hypotheses about the pseudotrue
-coefficients of the models; as \citet{Cal:11c} and \citet{Ana:12}
-demonstrate, variations of the Wald test can be valid for those
-hypotheses under increasing-$K$ asymptotics.\footnote{%
-  \citet{Ana:12} shows that the Wald test is invalid in general and
-  gives an adjustment that corrects the critical values; he also shows
-  that the $F$-test is asymptotically valid under certain conditions
-  on the distribution of the regressors.  \citet{Cal:11c} shows that
-  the $F$-test is asymptotically invalid without Anatolyev's
-  constraint, even under homoskedasticity, and provides a correction
-  that gives valid tests.  Both papers only consider independent
-  observations.} %
-To simplify the presentation and the intuition we only derive results
-for nested models and for MSE loss, but the conclusions hold much more
-generally.\footnote{%
-  In this section, we define
-  $M_1 = [I_{K_1} \ 0_{K_1 \times (K_2 - K_1)}]$ and
-  $M_2 = [0_{(K_2 - K_1) \times K_2} \ I_{K_2 - K_1}]$ as the
-  selection matrices that return the first $K_1$ and the last
-  $K_2 - K_1$ elements of $\theta_2$, and assume that the regressors
-  are ordered so that the first $K_1$ elements of $x_{2,t}$ correspond
-  to $x_{1,t}$.} %
-
-The full-sample statistics we study in this paper share a common
-property. They choose the alternative model when the distance between
-a subset of their coefficient estimates and the origin exceeds a
-threshold, and choose the benchmark otherwise. For the Wald test, for
-example, this threshold is chosen so that the test has correct size
-when those coefficients are zero in population. For small models that
-can be consistently estimated, these coefficient estimates are close
-to their true values and so this criterion can be a reasonable proxy
-for the relative accuracy of the larger model.
-
-But for overfit models, the estimates will typically be far from both
-their pseudotrue values and also from zero. In that case, the Wald test and
-the AIC will both tend to choose the larger model even when it is less
-accurate than the smaller benchmark model. This phenomenon is driven
-by the dimensionality of the alternative model, since there are more
-potential values of the coefficient estimator that are far from zero
-when it has many elements. The threshold for the Wald test and the AIC
-is set by construction to be a bounded distance from the origin, and
-every other statistic that shares this property has the same behavior
-and can reject the benchmark model with high probability, even when
-it is more accurate. This behavior is
-formalized in Theorem~\ref{res:insample1}.
-
-\begin{thm}\label{res:insample1}
-  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-4} hold and let
-  $\Lambda$ be a model selection statistic that takes the values zero
-  or one; $\Lambda = 0$ indicates that the benchmark model is chosen
-  and $\Lambda = 1$ indicates the alternative.  Moreover, assume that
-  $L(e) = e^2$ and that there exist a deterministic scalar $c$
-  and a sequence of possibly random matrices $V_T$ such that
-  \begin{equation}\label{eq:25}
-    \limsup_{T \to \infty}
-    \Pr[\Lambda \geq \1\{\bh{2T}'M_2' V_T M_2\bh{2T} > c \}]
-    \to 0
-  \end{equation}
-  where the eigenvalues of $V_T$ are uniformly bounded in probability,
-  $\plim \rank(V_T)/T > 0$, and neither $V_T$ nor $c$ depend on
-  $\theta$ or the value of $\bh{2T}$.
-
-  Then there exist DGPs satisfying these assumptions such that
-  \begin{equation}\label{eq:11}
-    \liminf_{T \to \infty} \E( \Lambda \mid \E_T \oosB \leq 0 ) \geq 1/2.
-  \end{equation}
-\end{thm}
-
-As we state above,~\eqref{eq:11} means that, with high probability,
-the benchmark model is rejected even when it is more accurate. In
-general, $\delta$ can be made arbitrarily small by increasing the
-region enclosed by $\1\{\bh{2T}'M_2' V_T M_2\bh{2T}\}$ and DGPs can be
-chosen to put the limiting quantity in~\eqref{eq:11}
-arbitrarily close to 1 while still satisfying
-the assumptions of the Theorem.  The DGPs and
-statistics used in Theorem~\ref{res:insample1} are simple and
-common. They include correctly specified linear models with normal and
-homoskedastic errors; and the statistics that meet the restrictions on
-$\Lambda$ include the $F$-test and AIC.
-
-For example, the $F$-statistic for the null hypothesis that the
-benchmark model is correctly specified is known to have the form
-\begin{equation*}
-  F = \frac{\bh{2T}' M_2' ( M_2 (X_{2T}'X_{2T})^{-1} M_2' )^{-1} M_2
-    \bh{2T}}{s^2 (K_2 - K_1)}
-\end{equation*}
-where $s^2$ is the usual estimator of the variance of the regression
-error. Then let $c$ be any number greater than 1 and define
-\begin{equation*}
-  V_T = M_2' \big( M_2 \big(\tfrac{1}{s^2 (K_2 - K_1)} X_{2T}'X_{2T}\big)^{-1}
-  M_2' \big)^{-1} M_2'.
-\end{equation*}
-If Assumption~\ref{asmp-2} holds and $s^2$ is consistent then $V_T$
-has uniformly bounded eigenvalues and has rank $K_2 - K_1$, so it
-satisfies~\eqref{eq:25}.
-Robust variations of the Wald test can obviously satisfy~\eqref{eq:25}
-for similar reasons, and the AIC for nested linear models is
-equivalent to using the $F$-test with the critical value %
-$(e^{2 (K_2 - K_1) / T} - 1) \cdot (T - K_2) / (K_2 - K_1)$, %
-which converges to a finite limit, so the AIC satisfies~\eqref{eq:25}
-as well.
-
-For statistics that don't satisfy~\eqref{eq:25}, the behavior can be
-quite different. The BIC, for example, can also be written in terms of
-the $F$-statistic and is equivalent to using the critical value $(T \,
-e^{2 (K_2 - K_1) / T} - 1) \cdot (T - K_2) / (K_2 - K_1)$. This
-critical value diverges as $T \to \infty$, ensuring that~\eqref{eq:25}
-fails for any $c$. For this statistic, we have the opposite problem as
-before: when the alternative model is \emph{more} accurate, the
-coefficient estimates of the larger model are contained in a bounded
-region of the parameter space. Since the acceptance region of the BIC
-grows, it eventually contains \emph{any} bounded region of the
-parameter space. For large enough $T$, the BIC will always choose the
-\emph{smaller model}, even when the larger model is more accurate.
-
-This behavior is formalized in Theorem~\ref{res:insample2}.
-\begin{thm}\label{res:insample2}
-  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-4} hold, let $L(e) =
-  e^2$, and let $\Lambda$ be a model selection statistic as in
-  Theorem~\ref{res:insample1}. Also assume that, for any finite scalar
-  $c$,
-  \begin{equation}\label{eq:27}
-    \Pr[\Lambda \leq \1\{\bh{2T}'M_2'J M_2\bh{2T} > c \}] \to 1
-    \quad \text{as } T \to \infty.
-  \end{equation}
-
-  Then there exist DGPs satisfying these assumptions such that
-  \begin{equation}\label{eq:15}
-    \E( \Lambda \mid \E_T \oosB \geq 0 ) \to^p 0.
-  \end{equation}
-\end{thm}
-
-The condition~\eqref{eq:27} requires that the acceptance region of
-$\Lambda$ eventually contains any finite cylinder centered at the
-origin. Again,~\eqref{eq:15} implies that statistics like the BIC
-will always choose the smaller model for some DGPs, even when the
-larger model will give more accurate forecasts. Both models may be
-overfit, in that both $K_1/T$ and $K_2/T$ may both be positive in the
-limit; the key is that $(K_2 - K_1)/T$ is also positive in the limit.
-
-It is important to remember that previous research, such as
-\citet{Cal:11c} and \citet{Ana:12}, does not predict these
-results. When $\Lambda$ represents a test statistic, the test may have
-correct size for the null hypothesis that the additional coefficients
-on the larger model are zero. The results in this subsection are being
-driven by the full-sample statistics' behavior when the smaller model
-is misspecified but more accurate.
-
-Any statistic that uses the distance of the models' estimated
-coefficients from a set point (the origin being the most common) is
-poorly suited for choosing between overfit forecasting models. These
-models only forecast well when their coefficient estimates are close
-to their pseudotrue values, which can be far from the origin or any
-other prespecified
-point. Depending on the statistic, it can be biased towards choosing
-the larger model or the smaller model. Formal in-sample \emph{tests}
-will likely be biased towards the larger model, as we show for the
-$F$-test and Wald test in Theorem~\ref{res:insample1}.
-
-\subsection{An extended simple example}
-\label{sec:example}
-
-This subsection illustrates the previous theoretical results with a
-concrete example. Let $L(e) = e^2$ and $h = 1$. Suppose that the benchmark is
-nested in the alternative and $(x_{2t}, \e_{2,t+1}) \sim i.i.d.\
-N(0,I)$, and let $y_{t+1} = x_{2t}'\theta_2 + \e_{2,t+1}$
-be the DGP. Also assume that $K_2/T \to c_2$ and $K_1 / T \to c_1 <
-c_2$.
-
-The first part of this subsection shows how the assumptions in
-Section~\ref{sec:asmp} are satisfied and the second part
-demonstrates asymptotic normality of the DMW \oost\ test. The third
-part explicitly shows that $\E_R \oosA$ converges to $\E_T \oosB$ only
-when the test sample is small. And the last part demonstrates that the
-$F$-test does not indicate which model will be more
-accurate in the future, even in this simple example.
-
-\subsubsection*{Fulfillment of Assumptions 1--5}
-
-We will go through the assumptions one by one. The first is
-a condition on the dependence and moments of the process. Since the
-DGP is i.i.d. Normal, these conditions are satisfied trivially.
-
-Assumption~\ref{asmp-2} deals with the design matrix. In this example,
-we directly assume that $K_2$ and $K_1$ grow at the correct rates so
-the the assumption is satisfied. The variance of $y_{t+1}$ given
-$\Fs_t$ is simply the unconditional variance of $\e_{2,t+1}$, which is
-1; and the eigenvalues of $\E x_{2t} x_{2t}$ all equal 1 as well; and
-so they are all uniformly positive and finite as required.
-
-Assumption~\ref{asmp-2} also requires the eigenvalues of $S^{-1}
-X_{iS}'X_{iS}$ to be positive and finite, and for the largest
-eigenvalue of $S^{-1} X_{iS}'X_{iS}$ to be bounded in $L_3$.  These
-results follow from developments in random matrix theory.
-\citet{Gem:80} establishes that the largest eigenvalue of
-$X_{iS}'X_{iS}$ is of order $S + K_i$ and \citet{Joh:01} shows that it
-converges in distribution to the Tracy-Widom law of order 1
-\citep{TrW:96}, which has finite 3rd moments. \citet{Sil:85} and
-\citet{BFP:98} prove similar results for the smallest eigenvalue.
-Assumption~\ref{asmp-2} also requires the largest eigenvalue of
-$(X_{iS}'X_{iS})^{-1}$ be bounded in $L_3$; this should follow from a
-similar argument, but we are unaware of any papers that explicitly
-derive moments for this eigenvalue.
-
-For the conditional expectation of %
-$\sum_{s,t=U}^{V-1} \e_{i,t+1} \e_{i,s+1} x_{i,s} x_{i,t}'$,
-independence implies that
-\begin{equation*}
-  \E\Big(
-  \sum_{s,t=U}^{V-1} \e_{i,s+1} \e_{i,t+1} x_{is}x_{it}'
-  \mBig
-  x_{i1},\dots,x_{i,U-1};
-  \sum_{s=U}^{V-1} x_{is} x_{is}';
-  x_{i,V},\dots,x_{i,T-1}
-  \Big)
-  = \sum_{s=U}^{V-1} x_{is} x_{is}'.
-\end{equation*}
-The largest eigenvalue of this last matrix is of order $K_i + V - U$,
-as discussed, and it has at most $V - U$ nonzero eigenvalues,
-ensuring that both~\eqref{eq:28} and~\eqref{eq:8} hold.
-
-Assumption~\ref{asmp-3} restricts the loss function and the realized
-OOS loss. In this example, we have
-\begin{equation*}
-  D_t^* =^d D_t = (e_{2,t+1} + x_{2t}'\theta_2 - x_{1t}'\bh{1t})^2
-  - (e_{2,t+1} + x_{2t}'(\theta_2 - \bh{2t}))^2
-\end{equation*}
-which has bounded $\rho$th moments by construction. The loss function
-is differentiable and $L'(e) = 2 e$, so \eqref{eq:29} holds as well.
-
-Finally, Assumption~\ref{asmp-4} deals with the choice of test and
-training sample and holds automatically. And Assumption~\ref{asmp-5}
-requires the kernel of the HAC variance estimator to be continuous at
-zero; it is straightforward to construct an estimator that satisfies
-this condition. However, in this section we will use the estimator
-\begin{equation*}
-  \sh^2 = \frac{1}{P} \sum_{t=R+1}^{T-1} (D_t - \oosA)^2
-\end{equation*}
-which does not satisfy Assumption~\ref{asmp-5} but nevertheless is
-consistent for the conditional variance of $\oosA$ because the
-underlying observations are independent.
-
-\subsubsection*{Asymptotic normality of the OOS average, Lemma 1}
-
-This subsection walks through Lemma 1's CLT. Since the observations in
-this example are i.i.d., we do not need to use mixingale theory to
-derive the results, but the OOS process is still affected by the
-estimation error in $\bh{1t}$ and $\bh{2t}$ and has a high degree of
-dependence. This dependence makes the OOS process an MDS, and MDS
-asymptotic theory replaces mixingale theory in this example.
-
-By construction, we have
-\begin{equation*}
-  D_t =
-  \begin{cases}
-    2 \e_{t+1} (x_{2t}'\bh{2R} - x_{1t}'\bh{1R})
-    + (x_{2t}'\theta_2 - x_{1t}'\bh{1R})^2
-    - (x_{2t}'\theta_2 - x_{2t}'\bh{2R})^2
-    & \text{if } t < T \\
-    2 \e_{t+1} (x_{2t}'\bh{2T} - x_{1t}'\bh{1T})
-    + (x_{2t}'\theta_2 - x_{1t}'\bh{1T})^2
-    - (x_{2t}'\theta_2 - x_{2t}'\bh{2T})^2
-    & \text{if } t > T
-  \end{cases}
-\end{equation*}
-and so we can explicitly derive the components of
-Lemma~\ref{res-mixingale}. First,
-\begin{multline*}
-  D_t - \E_R D_t
-  = 2 \e_{t+1} (x_{2t}'\bh{2R} - x_{1t}'\bh{1R})
-  + \Big\{(x_{2t}'\theta_2 - x_{1t}'\bh{1R})^2
-          - \E_R (x_{2t}'\theta_2 - x_{1t}'\bh{1R})^2 \Big\} \\
-  - \Big\{(x_{2t}'\theta_2 - x_{2t}'\bh{2R})^2
-          - \E_R (x_{2t}'\theta_2 - x_{2t}'\bh{2R})^2 \Big\}
-\end{multline*}
-for $t < T$. Since the underlying observations are i.i.d., $\E_{t-1}
-D_t = \E_R D_t$ a.s.\ and consequently $\{D_t - \E_R D_t, \Fs_{t};
-t=R+1,\dots,T-1\}$ is an MDS.
-
-Although transformations of $D_t - \E_R D_t$ will obviously not be
-MDSes in general, it should be clear that transformations of $D_t$
-will be MDSes after subtracting their conditional mean; i.e.
-\begin{equation*}
-  \{g(D_t) - \E_R g(D_t); \Fs_t; t = R+1,\dots,T-1\}
-\end{equation*}
-is an MDS as long as
-$g(D_t)$ has finite mean, but $g(D_t - \E_R D_t)$ is not. This MDS
-result holds because $x_t$ and $y_{t+1}$ are independent of $\bh{1R}$
-and $\bh{2R}$, so
-\begin{equation*}\begin{split}
-  \E_R g(D_t)
-  &= \int g\Big((x_1'\bh{1R})^2 - (x_2'\bh{2R})^2
-       + 2 y (x'\bh{2R} - x'\bh{1R})\Big) \, f(y, x) \, dx \, dy \\
-  &= \E_{t-1} g(D_t)
-\end{split}\end{equation*}
-a.s., where $f$ is the density of $(y_{t+1}, x_{2t})$ and $x_1$
-denotes the first $K_1$ elements of $x$. This result parallels our
-results for mixingales in the general case.
-
-As a result, $\oosA$ and $(1/P) \sum_{t=R+1}^{T-1} D_t^2$ both obey
-LLNs: $\oosA \to^p \E_R \oosA$ and
-\begin{equation*}
-  (1/P) \sum_{t=R+1}^{T-1} D_t^2 \to^p \E_R D_T^2.
-\end{equation*}
-Moreover, these convergence results imply that $\sh^2 - \var_R
-\sqrt{P} \oosA \to^p 0$. And so
-\begin{equation*}
-  \sqrt{P} \oosA/\sh \to N(0,1)
-\end{equation*}
-by the MDS CLT.
-
-\subsubsection*{Convergence of $\E_R \oosA$ to $\E_T \oosB$, Lemma 2}
-
-This subsection works through Lemma~\ref{res-convergence}. In this
-example, the difference between $\E_R \oosA$ and $\E_T \oosB$ equals
-\begin{equation*}
-  \begin{split}
-    \E_R \oosA - \E_T \oosB &= \Big\{(\bh{1R} - \theta_1)'(\bh{1R} -
-    \theta_1) -
-    (\bh{2R} - \theta_2)'(\bh{2R} - \theta_2)\Big\} \\
-    & \quad - \Big\{(\bh{1T} - \theta_1)'(\bh{1T} - \theta_1) -
-    (\bh{2T} - \theta_2)'(\bh{2T} - \theta_2)\Big\} \\
-    &\begin{split}
-      =\ep{T}'\Big\{
-      & \tilde{X}_{1R}(X_{1R}'X_{1R})^{-2} \tilde{X}_{1R}'
-      - X_{1T}(X_{1T}'X_{1T})^{-2} X_{1T}' \\
-      & - \tilde{X}_{2R}(X_{2R}'X_{2R})^{-2} \tilde{X}_{2R}'
-      + X_{2T}(X_{2T}'X_{2T})^{-2} X_{2T}'
-      \Big\}\ep{T}.
-    \end{split}
-  \end{split}
-\end{equation*}
-with $\tilde{X}_{iR}$ the $T \times K_i$ matrix $[X_{iR}'\ 0]'$. This
-last term is a quadratic form and the regressors and errors are
-assumed to be normal, so we can find the rate that the difference
-converges to zero in probability by calculating its first two moments.
-
-The mean difference is
-\begin{equation*}
-  \begin{split}
-  \E(\E_R \oosA - \E_T \oosB)
-      &=O\Big(\max_i \E \tr \big\{
-        \tilde{X}_{iR}(X_{iR}'X_{iR})^{-2} \tilde{X}_{iR}
-        - X_{iT}(X_{iT}'X_{iT})^{-2} X_{iT} \big\} \Big) \\
-      &=O\Big(\max_i \tr \big\{\E (X_{1R}'X_{1R})^{-1}
-         - \E (X_{1T}'X_{1T})^{-1} \big\}\Big) \\
-      &=O( K_1 P / (R-K_1)(T-K_1)) \\
-      &=O(P/T)
-    \end{split}
-\end{equation*}
-The first equality follows from the expectation of a quadratic form,
-the second from routine manipulations of the trace operator, and the
-third from the moments of the inverse Wishart distribution.
-
-Similarly, the variance of the difference is
-\begin{align*}
-  \var(\E_R & \oosA - \E_T \oosB) \\ &=
-  O\Big(\max_i \E\big[\tr((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1})\big]^2
-  + 2 \tr \E\big((X_{iR}'X_{iR})^{-2} - (X_{iT}'X_{iT})^{-2}\big) \\
-  &\qquad - \big[\tr \E((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}) \big]^2 \Big)\\
-  &= O(P/T)^2.
-\end{align*}
-So, in this example, $P^{1/2}(\E_R \oosA - \E_T \oosB) \to^p 0$
-if $P^3/T^2 \to 0$, which is slightly weaker than the general
-requirement that $P^2/T \to 0$.  If $\lim P^3/T^2 > 0$ the OOS average
-still obeys the MDS CLT, but it is not centered correctly at $\E_T
-\oosB$.
-
-\subsubsection*{Behavior of the F-test}
-
-This part illustrates the behavior of full-sample statistics in our
-simple example. To simplify the presentation even more, assume that
-the full-sample design matrix is orthogonal in-sample, not just in
-population, so $X_{2T}'X_{2T} = T \cdot I_{K_2 \times K_2}$, and again
-let $M_1$ and $M_2$ be the selection matrices for the first $K_1$ and
-the last $K_2-K_1$ elements of $\theta_2$. In this example,
-\begin{equation*}
-  M_2 \bh{2T} \sim
-  N(M_2 \theta_2, (1/T) \, I_{K_2-K_1})
-\end{equation*}
-and, conditional on $\E_T \oosB = 0$, the density of $M_2 \bh{2T}$
-concentrates uniformly on the surface of the sphere centered at $M_2
-\theta_2$ and passing through the origin:
-\begin{equation*}
-  (M_2 \bh{2T} - M_2 \theta_2)'(M_2 \bh{2T} - M_2 \theta_2) =
-  \theta_2'M_2' M_2 \theta_2.
-\end{equation*}
-To see intuitively that it must pass through the origin, note that the
-two models will give identical forecasts when $\bh{2T} = 0$ since the
-regressors are orthogonal. (Identical forecasts obviously have the
-same MSE.)
-
-This region is a cylinder in the original space, $\Re^{K_2}$.  We can
-also represent the null $\E_T \oosB \leq 0$ by conditioning on $\E_T
-\oosB = -d$ for a fixed positive constant $c$. In that case, the
-density of $M_2 \bh{2T}$ concentrates on the sphere
-\begin{equation*}
-  (M_2 \bh{2T} - M_2 \theta_2)'(M_2 \bh{2T} - M_2 \theta_2) =
-  \theta_2'M_2' M_2 \theta_2 + d
-\end{equation*}
-which has the same center but larger radius.
-
-For the $F$-test we have, as before,
-\begin{equation*}
-  F = \tfrac{T}{s^2 (K_2 - K_1)} \bh{2T}' M_2' M_2 \bh{2T}.
-\end{equation*}
-We know that $\sqrt{T}(F - 1)$ is asymptotically normal since its
-numerator is Chi-squared with $K_2-K_1$ degrees of freedom and obeys a
-CLT.  The test accepts if
-\begin{equation}\label{eq:26}
-  \tfrac{T}{s^2 (K_2 - K_1)} \bh{2T}' M_2' M_2 \bh{2T}
-  \leq 1 + \delta / \sqrt{T},
-\end{equation}
-where $\delta$ is chosen to determine the size of the test. In other
-words, the test accepts if $M_2 \bh{2T}$ falls in the sphere centered
-at the origin with radius $s ((K_2 - K_1) / T)^{1/2} +
-O_p(1/\sqrt{T})$.
-
-\input{floats/circles}
-\begin{figure}
-  \centering
-  \begin{tabular}{cc}
-  \subfloat[]{\circlefigA{1}{2.5}{1.4}{4.5}\label{fig:circleA}} &
-  \subfloat[]{\circlefigB{1}{2.5}{1.4}{4.5}\label{fig:circleB}}
-  \end{tabular}
-  \caption{Graphs indicating the rejection region and region of equal
-    generalization error for the models discussed in Section
-    \ref{sec:insample}.  The smaller model has no estimated parameters
-    and the larger has two coefficients.  The shaded regions in
-    Figures (a) and (b) show the rejection region and the acceptance
-    region respectively of the full-sample test given $\E_T \oosB \leq
-    0$. Here $e_1 = (1,0)$ and $e_2 = (0,1)$ are the first and second
-    selection vectors, so the horizontal axes represent changes in the
-    first unique element of $\bh{2T}$ and the vertical axes represent
-    changes in the second unique element.}
-\label{fig:rreject}
-\end{figure}
-
-This is perhaps best illustrated with a picture.
-Figure~\ref{fig:rreject} plots these quantities when $K_2 - K_1 =
-2$. The circle centered at the origin plots the threshold for the
-$F$-test; when $M_2 \bh{iT}$ falls outside this circle, the $F$-test
-rejects. The circle centered at $M_2 \theta_2$ plots the set of points
-for which $\E_T \oosB = 0$. The shaded region in
-Figure~\ref{fig:rreject}~(a) plots the rejection region given $\E_T
-\oosB \leq 0$ and the shaded region in Figure~\ref{fig:rreject}~(b)
-plots the acceptance region given $\E_T \oosB \leq 0$.
-
-In the picture, the true coefficients $\theta_2$ satisfy
-\begin{equation*}
-\theta_2'M_2'M_2\theta_2 > \var(\e_t)^{1/2} ((K_2 - K_1) / T)^{1/2}
-\end{equation*}
-so the center of the conditional distribution of $\bh{2T}$ given $\E_T
-\oosB \leq 0$ is outside the acceptance region of the $F$-test. When
-this is the case, the conditional probability that $\bh{2T}$ falls in
-the rejection region is less than 1/2, since $M_2 \bh{2T}$ is
-uniformly distributed on the cylinder
-\begin{equation*}
-  (M_2 \bh{2T} - M_2 \theta_2)'(M_2 \bh{2T} - M_2 \theta_2) =
-  \theta_2'M_2' M_2 \theta_2 + d
-\end{equation*}
-for some positive $d$.
-
-The AIC behaves essentially the same way. For the BIC, the radius of
-the cylinder centered at the origin increases with $T$ and eventually
-encompasses the cylinder centered at $M_2 \theta_2$, so it never
-selects the alternative once $T$ is large enough.
-\section{Monte Carlo}
-\label{sec:mc}
-
-This section presents two simulations that investigate the accuracy of
-our theory in small samples.
-We do several Monte Carlo exercises. The first looks at whether our
-theoretical results for the OOS average are accurate: whether or not
-the OOS average is approximately normal, and whether it is centered on
-$\E_R \oosA$, $\E_T \oosB$, or somewhere else entirely. The second
-issue is whether or not the \oost\ test is \emph{useful} for
-conducting inference about $\E_T \oosB$. Our theoretical results
-suggest that it may not be, because we require $P^2/T \to 0$ for
-inference about $\E_T \oosB$ to be valid. A highly related issue is
-whether other statistics are useful for conducting inference about
-$\E_T \oosB$---again, our theoretical results suggest that they are
-not.
-
-We use the same DGP for all of these simulations, and it is described
-in the next subsection. Results are presented in the subsection after
-that. Simulations were conducted in R \citep{Rde:10} using the
-\emph{MASS} \citep{VeR:02}, \emph{Matrix} \citep{BM:13}, and
-\emph{rlecuyer} \citep{SR:12} and graphs are produced using
-\emph{Lattice} \citep{Sar:10}. In this paper, we present results for
-the fixed window, but recursive window results are available in a
-separate Appendix and are similar.
-
-\subsection{Setup}
-\label{sec:simulation-design}
-
-The Monte Carlo experiment is intentionally very simple so that we can
-isolate the influence of the models' complexity.  In particular, we do
-not include some features that are common in forecasting
-environments---serial dependence, heteroskedasticity, and complicated
-DGPs. The DGP we use is given by the equation
-\begin{equation}\label{eq:6}
-  y_t = x_t'\theta + \e_t,\quad \e_t \sim N(0,1),
-  \quad t=1,\dots,T.
-\end{equation}
-The first element of $x_t$ is 1 and the remaining $K_2-1$ elements are
-independent Standard Normal.  The benchmark model is
-\begin{equation}
-  \label{eq:1}
-  y_{1t} = \sum_{j=1}^{K_1} x_{jt}\theta_j + \e_t
-\end{equation}
-and the alternative model is the DGP \eqref{eq:6}.  We let
-$(K_1,K_2)$ equal either $(2,3)$ or $(T/20,T/10)$ to study our theory
-in its intended application as well as for more parsimonious models.
-We let $T$ equal 100, 250, or 500.  We also vary $\theta$, and do
-so giving the benchmark and the alternative model comparable weight in
-predicting $y_t$.  Specifically, we set
-\begin{equation*}
-  \theta_j =
-\begin{cases} \frac{c}{\sqrt{K_1}} & j = 1,\dots,K_1 \\
-\frac{c}{\sqrt{K_2 - K_1}} & j = K_1 + 1,\dots,K_2 \end{cases}
-\end{equation*}
-with $c$ equal to zero or one.  When $c$ is one, we're more likely to
-draw values of $X$ and $Y$ that make the estimated larger model more
-accurate than the benchmark, and when $c$ is zero we're unlikely to
-draw such values of $X$ and $Y$.  For all of the studies, $L(e) =
-e^2$.
-
-To study the accuracy of our theoretical approximations, we first
-estimate the coverage probabilities of OOS confidence intervals for
-$\E_R \oosA$ and $\E_T \oosB$. For each draw of $X$ and $Y$, we
-construct the one-sided OOS interval defined in
-Theorem~\ref{res:oostest}:
-\begin{equation*}
-  [ \oosA - 1.28 \hat{\sigma}, \infty) \quad\text{with}\quad
-  \sh^2 = \frac1P \sum_{t=R+1}^T (D_t - \oosA)^{2}
-\end{equation*}
-for $P = 10,\dots,2T/3$; we then calculate the percentage of
-simulations where these intervals contain $\E_R \oosA$ and the
-percentage that contain $\E_T \oosB$.  Since the data are i.i.d., both
-of these quantities are easy to calculate (see
-Section~\ref{sec:example}). For these calculations, we draw 2000
-samples for each combination of the design parameters.
-
-Our second set of results studies whether these different OOS and
-in-sample statistics are valid for testing the null hypothesis
-\begin{equation*}
-  H_0:\quad E_T \oosB \leq 0,
-\end{equation*}
-namely that the benchmark model is expected to be more accurate in the
-future than the alternative. Informally, we are interested in whether
-the conditional probability
-\begin{equation*}
-  \Pr[\text{test rejects} \mid E_T \oosB \leq 0] \leq \alpha
-\end{equation*}
-where $\alpha$ is the nominal size of the test. If this inequality
-does not hold, the test statistic is rejecting the benchmark model too
-often.
-
-We look at four different statistics---the full-sample $F$-test, the
-DMW $t$-test, the OOS $t$-test using McCracken's (2007) critical
-values,\footnote{%
-  These critical values are not published for $K_2-K_1>10$, so we do
-  not report them for $K_2 = T/10$.} %
-and Clark and West's (2006, 2007) Gaussian out-of-sample
-statistic.\footnote{%
-  Clark and West (2006, 2007) derive their statistic using the rolling
-  window estimation scheme. Here we use the same statistic, but with a
-  fixed window scheme. A supplemental appendix presents results for
-  their statistic, using the recursive window.} %
-For the $F$-test, we simply test whether the coefficients on the
-larger model are nonzero.  For the out-of-sample tests, we conduct a
-one-sided test of out-of-sample performance for every value of $P$ as
-before. For each of these simulations, we discard draws from the DGP
-that violate the null hypothesis $E_T \oosB \leq 0$ and then use the
-remaining samples to calculate the conditional probability that each
-test rejects. The simulations end when 2000 draws have been retained
-for each choice of the design parameters.
-
-\subsection{Results}
-
-We discuss results for the confidence intervals first.
-Figures~\ref{fig:interval-R} and~\ref{fig:interval-T} show the
-coverage probability of these intervals as a function of $P$ for each
-combination of $T$, $K_1$ and $K_2$, and $c$.  The nominal coverage is
-90\% and is represented with a gray horizontal line. Each panel
-displays the coverage for a different choice of design parameters.
-
-Figure~\ref{fig:interval-R} gives the results for $\E_R \oosA$.  The
-actual coverage is very close to the nominal coverage except when $P$
-is very small.  The poor behavior for small $P$ is unsurprising, as it
-simply means that the CLT is a poor approximation when the test sample
-is small. The interval for $T = 100$, $K = T/10$, and $c = 0$ is the
-worst, with actual coverage near 85\% for most values of $P/T$. But
-the others are much closer to nominal coverage, even for the
-parsimonious models ($K_1=1$ and $K_2= 3$) where one might expect
-the theoretical results to break down.
-
-Figure~\ref{fig:interval-T} gives the results for $\E_T \oosB$.  In
-columns 2 and 4---the overfit models---the coverage is near nominal
-coverage for moderately small values of $P$.  As $P$ increases to
-$2T/3$, the coverage increases above nominal size; near 100\% for some
-DGPs.  With the parsimonious model, the coverage is near nominal
-coverage for all $P$ for the one-sided interval with $c=1$, but only
-for moderately small $P$ when $c=0$.
-
-The behavior for $K_2 = T/10$ is exactly what our theory predicts.
-When $P^2/T$ is small, the coverage is close to nominal levels.  The
-behavior as $P$ increases, combined with the results for $\E_R \oosA$,
-indicate that typically $\E_T \oosB \geq E_R \oosA$.  Since
-\begin{equation*}
-  E_{T} \oosB = E_{R} \oosA + (E_{T} \oosB - E_{R} \oosA),
-\end{equation*}
-and the interval is approximately centered at $\E_R \oosA$, the
-difference $\E_{T} \oosB - E_{R} \oosA$ adds a substantial positive
-quantity when $P^2/T$ is not near zero, increasing the coverage of the
-one-sided interval.
-
-We present the size simulations next, in
-Figures~\ref{fig:ftest}--\ref{fig:ttest-power}.  For the OOS tests
-we plot each OOS test's conditional rejection probability,
-\begin{equation*}
-  \Pr[\text{test rejects} \mid E_T \oosB \leq 0],
-\end{equation*}
-for each combination of $T$, $K_1$, $K_2$, and $c$ as a function of
-$P$.  The $F$-test does not depend on $P$, so we calculate and
-tabulate it's conditional rejection probability as a single value for
-each combination of design parameters.
-
-Table~\ref{fig:ftest} summarizes the simulation results for the
-$F$-test. For $c = 0$, the estimated conditional rejection probability
-is almost exactly equal to the test's nominal size (10\%), which is
-unsurprising.  For $c = 0$, the $F$-test is exact; moreover, the
-larger model will almost always be less accurate than the smaller one,
-so conditioning on $\E_T \oosB \leq 0$ is almost unrestrictive.  When
-$c$ increases, though, the $F$-test overrejects badly---rejecting at
-roughly 50\% when $c = 1$ for the parsimonious model and from 70\% to
-100\% for the overfit model. This agrees with our
-Section~\ref{sec:insample} results and matches results seen in
-empirical practice: the $F$-test rejects the benchmark with very high
-probability, even though it is, by construction, more accurate than
-the alternative model.
-
-Figure~\ref{fig:ttest-size} presents the size estimates for the DMW
-\oost\ test.  Again, different panels display results for different
-combinations of the design parameters.  Each graph plots the rejection
-probability against $P/T$.  For $K/T=10$, the rejection probability
-falls as $P/T$ increases, from near nominal size when $P/T$ is small
-to zero when $P/T$ is near $2/3$.  Moreover, the rejection probability
-falls faster when $T$ is large, as our theory predicts.  When $K=3$,
-the rejection probability stays closer to nominal size, but falls with
-$P/T$ for $c=0$, under-rejecting by about 5pp when $P/T = 2/3$, and
-rises with $P/T$ for $c=1$, overrejecting by about 10pp when
-$P/T=2/3$.  For small $P$, the rejection probability is near 10\% for
-all simulations (the farthest is $K=T/10$, $c=0$, where the rejection
-probability is about 5\%; the other simulations are much closer).
-
-We observe the following patterns.  The
-DMW test has close to nominal size when $P$ is small for every
-combination of design parameters.  In most cases, the rejection
-probability decreases as $P/T$ increases---the exception is for $K_2 =
-3$ and $c=1$.  For the large-$K$ simulations, the rejection
-probability drops to zero for most of the simulations as $P/T$
-increases.  The rejection probability increases with $c$, but the
-rejection probability still is near nominal probability for small $P$
-with $c=1$.
-
-Clark and West's (2006, 2007) statistic, presented in
-Figure~\ref{fig:clarkwest}, behaves quite differently.  For $c=0$ the
-test is correctly sized for both the overfit and parsimonious studies,
-as we saw for the $F$-test.  When $c=1$, the rejection probability
-increases rapidly with $P/T$.  For $K_2=3$, the rejection probability
-is near 10\% when $P$ is small but about 40\% when $P/T = 2/3$.  For
-$K=T/10$, the rejection probability is even higher and increases with
-$T$ as well, from a maximum over 50\% when $T=100$ to a maximum of
-nearly 100\% when $T=1000$.
-
-Results using \citepos{Mcc:07} critical values are presented in
-Figure~\ref{fig:mccracken} and are similar to those using Clark and
-West's test.  For $c=0$ the rejection probability is nearly the test's
-nominal size.  For $c=1$, the rejection probability increases with
-$P/T$, from close to the nominal size when $P/T$ is small to over 25\%
-when $P/T = 2/3$.  Note that all of the simulations use the
-parsimonious model.  McCracken's statistic overrejects here by
-slightly less than Clark and West's, but still by a substantial
-amount. Note that we are unable to plot results for McCracken's
-statistic when $K/T = 10$, which is where the breakdown in Clark and
-West's test is most pronounced.
-
-Since the DMW test tends to have low rejection probability, the test's
-power is a concern.  Figure~\ref{fig:ttest-power} power results for
-the DMW test, simulating from \eqref{eq:1} with $c = 1$ or 2 subject
-to the constraint that $\E_T \oosB > 0$.\footnote{%
-  Draws of $X$ and $Y$ with $\E_T \oosB > 0$ are very rare when $c=0$,
-  so we do not present results for that value of $c$.} %
-Since the other test statistics greatly overreject, we do not present
-their power.  For $c=1$, the power is never greater than nominal size
-and decreases to zero as $P/T$ increases for the overfit model.  For
-$c=2$ the power is better, increasing with $P/T$ at first stretch and
-then decreasing as $P/T$ grows beyond approximately 1/4 for the
-overfit model.  Larger values of $T$ give a higher peak and greater
-power overall, but the power still falls to nearly zero if $P/T$ is
-too large (approximately 2/3 in our simulations).  The power with the
-parsimonious model is typically quite low but greater than nominal
-size for $c = 2$.
-
-Both sets of simulations support our theoretical results.  The first
-simulation confirms that the DMW OOS $t$-test is centered at $\E_R
-\oosA$ for all choices of $P$ and $R$ and is centered on $\E_T \oosB$
-only when $P$ is small.  The second simulation confirms that the DMW
-test has correct size for the null hypothesis that $\E_T \oosB \leq 0$
-when $P$ is small and that tests designed to test whether the
-benchmark is true, like the $F$-test and Clark and West's (2006, 2007)
-and McCracken's (2007) OOS tests can reject by much more than their
-nominal size when testing the null $\E_T \oosB \leq 0$.  Moreover,
-these simulations demonstrate that the restriction that $P$ be small
-is binding in practice, as the DMW test under-rejects and has very low
-power when $P$ is too large.
-
-\section{Empirical analysis of equity premium predictability}
-\label{sec:empirics}
-
-This section presents a study of equity premium predictability based
-on \citet{GoW:08}. Goyal and Welch conduct an out of sample analysis
-of 18 different variables thought, based on previous research, to
-predict the equity premium (calculated as the difference between the
-return on the S\&P 500 index and the T-bill rate).\footnote{%
-  \citet{GoW:08} builds on previous research by \citet{BoH:99} and
-  \cite{GoW:03}.} %
-Their analysis has two notable features: Goyal and Welch compare different
-predictors across the same time periods and frequency as much as
-possible, making the accuracy of these predictors directly comparable;
-many of the papers that originally proposed these predictors used
-different time periods, methods, or observational frequencies so their
-results were not directly comparable. And Goyal and Welch compare
-these predictors out-of-sample; many of the original studies found
-in-sample evidence of equity premium predictability but did not look
-at out-of-sample evidence.
-
-Goyal and Welch consider many different models; most of them are very
-simple---regression onto a constant and a single stochastic
-predictor---but some are more complicated. They find that essentially
-none of the models outperform a simple benchmark, the prevailing mean
-of the equity premium, and conclude that these variables do not
-predict the equity premium. A large literature has subsequently sought
-to explain or rebut these results, including several responses to
-Goyal and Welch's original working paper published in the same special
-issue of \textit{The Review of Financial Studies} as
-\citet{GoW:08}.\footnote{%
-  Those papers are \citet{CaT:08}, \citet{Coc:08}, \citet{BRW:08}, and
-  \citet{LeN:08}.} %
-
-\citet{GoW:08}, as well as \citet{BoH:99}, \citet{LeN:08}, and many
-other authors, propose that instability could explain the OOS failure
-of these models. However, we have shown in this paper that overfit can
-also explain this pattern, significant in-sample results that do not
-hold up out of sample. In this section, we explore the extent to which
-overfit is a potential concern in this data set and estimate the
-expected forecasting performance of the largest model they consider, a
-model with 13 regressors, using 81 observations (annual data from 1928
-to 2009). The predictors are listed in Table~\ref{tab:equity}; please
-see Goyal and Welch's original paper for detailed information about
-these variables.\footnote{%
-  Table~\ref{tab:equity} only lists the variables used in
-  \citepos{GoW:08} ``kitchen sink'' model.  Some of the variables that
-  they use are excluded from this model either because the series are
-  too short or because the variables are linear combinations of other
-  variables.} %
-
-\citet{GoW:08} focus primarily on univariate regression models of the
-form
-\[
-r_{t+1} = \beta_0 + \beta_1 x_{it} + \e_{t+1}
-\]
-using OLS with a recursive window, where $r_{t+1}$ is the equity
-premium and $x_{it}$ is one of the predictors listed in
-Table~\ref{tab:equity}.
-This focus is consistent with much of the rest of the literature. But
-it is not clear that this approach---using a large number of
-restricted models---is any more reliable than using a single, large
-model. Very few papers in the equity-premium predictability literature
-explicitly account for the multiplicity of model comparisons\footnote{%
-  \citet{RaW:06}, \citet{RaZ:12}, and \citet{Cal:15} are
-  exceptions.} %
-and most widely-used statistics for multiple comparisons are
-derived under the assumption that there is a finite number of
-hypotheses or models (as is the case in \citealp{STW:99c},
-\citealp{Whi:00}, \citealp{Han:05}, and \citealp{LeR:05}), so there is
-little theoretical evidence that they are any more reliable than a
-regression model that encompasses all of the smaller models. Moreover,
-since \citet{GoW:08} (along with most of the rest of the literature)
-want to interpret these univariate regressions as meaningful
-statements about the true relationships between the equity premium and
-the regressors, omitted variable bias is a serious potential issue.
-
-For example, Table~\ref{tab:gwinsample} presents two full-sample
-coefficient estimates for each of the 12 predictors we
-consider.\footnote{%
-  For all of our full sample results, we studentize the
-  regressors to make it easier to compare coefficient estimates and we
-  express the equity premium in basis points.} %
-The first column is the estimator of the coefficient on the
-variable in the full regression,
-\begin{equation*}
-  r_{t+1} = \beta_0 + \sum_{i=1}^{12} \beta_{i} x_{it} + \e_{t+1},
-\end{equation*}
-and the third column is the $p$-value associated with a two-sided
-$t$-test that the coefficient is zero in population. The second column
-is the estimator of the coefficient from the univariate regression
-\begin{equation*}
-  r_{t+1} = \alpha_i + \gamma_{i} x_{it} + \e_{t+1},
-\end{equation*}
-and the fourth column is the $p$-value associated with its
-$t$-test.\footnote{%
-  All of the standard errors were calculated using a Newey-West kernel
-  with two lags.} %
-Some of the coefficient estimates agree, but some do not. The
-coefficient estimate for the \emph{default yield spread}, for example,
-is substantially and significantly negative in the full model ($-7.79$
-with $p$-value $0.042$), but is near zero in the univariate regression
-($0.79$ with $p$-value $0.720$). This pair of results implies that the
-the default yield spread contains information about the equity premium
-but is also correlated with other poor predictors, and that this
-additional correlation adds noise to the univariate regression
-and masks the true relationship. Similarly, \emph{net equity expansion}
-is significant at 10\% in the univariate regression but not in the
-full model ($p$-values of $0.060$ and $0.626$ respectively), which is
-likely attributable to omitted variable bias. So there is merit to
-studying a large model that includes all of the variables.
-
-Results for the full sample estimates of these models are in
-Table~\ref{tab:gwinsample}.\footnote{%
-  Calculations in this section are done in R \citep{Rde:10} using the
-  \emph{lmtest} \citep{ZeH:02} and \emph{sandwich} \citep{Zei:04}
-  packages.}\footnote{%
-  We compare the test statistic to critical values from the
-  $F$-distribution, which have been shown to be more reliable than
-  Chi-squared critical values when there are many regressors
-  \citep{Ana:12,Cal:11c}.} %
-The last rows of the table list measures of the full-model fit.  The
-$p$-value for the test of full model fit is very small (less than
-0.01), indicating that some of the coefficients are nonzero in
-population and at least one of these predictors is correlated with the
-equity premium.\footnote{%
-  We have done additional analysis to try to identify which predictors
-  were correlated with the equity premium, but none of the individual
-  regressors were significant after correcting for multiplicity. The
-  Bonferroni correction, for example, suggests that an individual
-  $p$-value would need to be less than $0.10/12 \approx 0.0083$ for
-  its corresponding coefficient to be significant at the 10\% level,
-  but the smallest $p$-value is $0.035$. One can improve on the
-  Bonferroni correction, of course, but a comprehensive analysis is
-  beyond the scope of this paper.} %
-As we argue throughout the paper, this result does not imply that the
-model will forecast well.
-
-To determine whether the full model can forecast well, we use the DMW
-\oost\ test to compare it to a sample mean benchmark,
-\begin{equation*}
-r_{t+1} = \mu + \e_{1,t+1}.
-\end{equation*}
-Both models are estimated by OLS using the fixed-window scheme. We
-also present results for a restricted model proposed by
-\citet{CaT:08} that imposes that $\hat r_{t+1}$ be non-negative for
-each forecast.
-To study the effect of the training sample size on the DMW statistic, we
-calculate the one-sided confidence interval for $\E_T \oosB$ given
-by \eqref{interval-greater} corresponding to the null and alternative
-hypotheses
-\[ H_0: \quad E_T \oosB \leq 0 \qquad
-H_A: \quad E_T \oosB > 0
-\]
-using the fixed-window scheme for each value of $R$ between 20 and
-$T-10$. The standard deviation is estimated using a Newey-West
-estimator with $\lfloor P^{1/4}\rfloor$ lags.  For small values of
-$R$, the OOS average is expected to underestimate the performance of
-the larger model relative to the smaller, but this may not hold in
-this particular dataset. For the OOS results, we express the equity
-premium in percentage points.
-
-Figure~\ref{fig:empirics1} plots the OLS results and
-Figure~\ref{fig:empirics2} imposes \citepos{CaT:08} restriction. The
-solid line in each figure shows the OOS average, $\oosA$, and the
-shaded region indicates the 95\% one-sided confidence interval implied
-by the DMW test.  Negative numbers indicate that the full model has
-higher out-of-sample loss.  We can see that the same patterns hold for
-both models: the performance difference decreases as $R$ grows, but
-the full model is never more accurate.  We also see that the
-performance difference decreases suddenly over the period $R=29$ to
-$R=34$ (corresponding to the years 1956--1961).
-Figure~\ref{fig:empirics3} plots the accuracy of the individual
-forecasts (only for the linear models) and shows that this change is
-the result of a sudden improvement in the full model.  This change may
-indicate instability in the underlying relationship, as proposed by
-\citet{GoW:08}.
-
-In summary, we fail to reject the null that the benchmark prevailing
-mean model is more accurate than the full model including all of
-\citepos{GoW:08} predictors.  This result is consistent with Goyal and
-Welch's original analysis.  Unlike Goyal and Welch, we attribute this
-result, at least in part, to parameter uncertainty---the full sample
-results indicate that there is a true predictive relationship between
-some of these variables and the equity premium and the larger model
-could predict better than the benchmark with enough data.\footnote{%
-  \citet{BWB:10} make a similar point about exchange rate models, but
-  see also \citet{Chi:10} and \citet{Gia:10}.} %
-These also indicate that combination or shrinkage estimators of the
-full model have the potential to significantly improve on the
-benchmark.\footnote{%
-  See \citet{RaZ:12} for a recent review of this literature.} %
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-This paper gives a theoretical motivation for using OOS comparisons:
-the DMW OOS test allows a forecaster to conduct inference about
-the expected future accuracy of his or her models when one or both is
-overfit.  We show analytically and through Monte Carlo that standard
-full-sample test statistics can not test hypotheses about this
-performance.
-
-Our paper also shows that popular test and training sample sizes may
-give misleading results if researchers are concerned about overfit.
-We show that $P^2/T$ must converge to zero for the DMW test to give
-valid inference about the expected forecast accuracy, otherwise the
-test measures the accuracy of the estimates constructed using only the
-training sample.  In empirical research, $P$ is typically much larger
-than this.  Our simulations indicate that using large values of $P$
-with the DMW test gives undersized tests with low power, so this
-practice may favor simple benchmark models too much.  Existing
-corrections, proposed by \citet{ClM:01,ClM:05}, \citet{Mcc:07} and
-\citet{ClW:06,ClW:07}, seem to correct too much, though, and reject
-too often when the benchmark model is more accurate.
-
-More work remains.  The requirement that $P^2/T$ converge to zero is
-limiting, as it implies that in typical macroeconomic datasets, only a
-handful of observations should be used for testing.  This requirement
-can be relaxed only slightly; $P = O(T^{1/2})$ is required for the
-OOS test to have nontrivial power in general, but there are loss
-functions and DGPs for which some relaxation is possible.  This
-constraint could be mitigated by extending our results to
-cross-validation or other resampling strategies, or by constructing
-full-sample statistics that allow inference about $\E_T \bar{D}_T$.
-It would also be useful to extend our results to other forecasting
-models and to explore how stationarity could be relaxed, but such
-extensions are less important than improving the available statistics.
-
-\appendix
-\section*{Appendix: mathematical details}
-\setcounter{section}{1}
-% Change lemma style to prepend 'A'
-\setcounter{lem}{0}
-\renewcommand{\thelem}{A\arabic{lem}}
-
-\subsection*{Supporting results}
-The results in this paper rely heavily on a coupling argument for
-absolutely regular sequences, Berbee's Lemma \citep{Ber:79}.  Many of
-the results of this paper (Lemma \ref{res-mixingale} and
-Theorem~\ref{res-oost}) use modifications of existing results
-for NED functions of mixing processes by \citet{Jon:97} and
-\citet{JoD:00}; this coupling argument is used to explicitly derive
-inequalities that arise naturally for NED processes.  Lemma
-\ref{lem-basic-coupling} establishes these inequalities, which are
-based on a proposition of \citet{MeP:02}.
-
-We present \citeauthor{MeP:02}'s
-(\citeyear{MeP:02}) statement of Berbee's Lemma for
-the reader's reference.  In the following Lemma, $\beta(X,Y)$ is the
-coefficient of absolute regularity:
-\begin{equation}
-\beta(X,Y) = \sup_{A \in \sigma(Y)} \E \lvert \Pr(A \mid \sigma(X))
-  - \Pr(A) \rvert.
-\end{equation}
-
-\begin{lem}\label{lem-berbee}\quad
-
-\begin{quotation}\noindent
-  Let $X$ and $Y$ be random variables defined on a probability space
-  $(\Omega, \mathcal{T}, \Pr)$ with values in a Polish space
-  $S$.  Let $\sigma(X)$ be a $\sigma$-algebra generated by $X$ and let
-  $U$ be a random variable uniformly distributed on $[0,1]$
-  independent of $(X,Y)$.  Then there exists a random variable $Y^{*}$
-  measurable with respect to $\sigma(X) \vee \sigma(Y) \vee
-  \sigma(U)$, independent of $X$ and distributed as $Y$, and such that
-  $\Pr(Y \neq Y^{*}) = \beta(X,Y)$.
-
-  \noindent\citep{MeP:02}
-\end{quotation}
-\end{lem}
-
-The advantage of this result over coupling arguments that use other
-forms of weak dependence is that the difference between the original
-variable, $Y$, and the new variable, $Y^{*}$, does not depend on their
-dimension.  Similar results for strong mixing sequences depend on the
-dimension of $Y$, which makes them unsuitable for this paper.
-
-\begin{lem}\label{lem-extend-mp}
-  Suppose that $X$ and $X^*$ are $L_p$-bounded random variables, with
-  $p > 2$, that satisfy ${\Pr[X \neq X^*] = c}$.  Then
-  \begin{equation}
-    \lVert X - X^* \rVert_2 \leq 2^{1/p} (\lVert X \rVert_p + \lVert
-    X^* \rVert_p) c^{(p-2)/2p}
-  \end{equation}
-\end{lem}
-
-The proof is virtually identical to the proof of Proposition 2.3 in
-\citet{MeP:02} and is omitted.
-
-\begin{lem}\label{lem-basic-coupling}
-  Suppose Assumptions \ref{asmp-1}--\ref{asmp-3} hold.  Then, for any
-  T, $s$, $t$, and $u$ with $s < t \leq u$, there exist random
-  variables $D_t^*,\dots,D_u^*$ such that
-  \begin{equation}\label{eq:coupling1}
-    P[(D_{t}^*,\dots,D_u^*) \neq (D_{t},\dots,D_u)] \leq \beta_{t-s}
-  \end{equation}
-  and
-  \begin{equation}\label{eq:coupling2}
-    \E(\phi(D_{t}^*,\dots, D_u^*) \mid \mathcal{F}_s ) =
-    \int
-    \phi(D_{t},\dots,D_u) f(\mathbf{x}, \mathbf{y})\ d\mathbf{x}\ d\mathbf{y}
-  \end{equation}
-  almost surely for all measurable functions $\phi$ such that the
-  expectations are finite, where
-  \[ \mathbf{x} = (x_{t}', \dots, x_{u}')', \qquad
-  \mathbf{y} = (y_{t+\h},\dots,y_{u+\h})',\] and $f$ is the
-  joint density of $(\mathbf{x}, \mathbf{y})$.  Moreover,
- \begin{equation}\label{eq:coupling3}
-   \| D_v^* - D_v \|_2 \leq 2^{1+1/\rho} B_L
-   \beta_{t-s}^{\rhoExp}, \qquad v = t,\dots,u.
- \end{equation}
-\end{lem}
-
-\begin{proof}
-  The proof follows as a consequence of Lemmas \ref{lem-berbee} and
-  \ref{lem-extend-mp}.  Let $l = u-t$.  For any fixed values of $l$
-  and $T$, the sequence of vectors
-  \[ V_{t} = (y_{t+\h}, x_{t}', \dots, y_{t+l+\h}, x_{t+l}') \] is
-  absolutely regular of size $\rho/(\rho-2)$.  Berbee's Lemma implies
-  that there is a random vector $V^*$ that is independent of
-  $\mathcal{F}_s$, equal to $V_{t}$ in distribution, and satisfies
-  \[\Pr[V^* \neq V_{t}] = \beta_{t-s}.\]
-
-  Now define
-  \begin{equation*}
-    D_v^* =
-    \begin{cases}
-      L(y_{v+\h}^* - x_{1v}^{*\prime} \hat{\theta}_{1R}) - L(y_{v+\h}^* -
-      x_{2v}^{*\prime} \hat{\theta}_{2R}) & v \leq T \\
-      L(y_{v+\h}^* - x_{1v}^{*\prime} \hat{\theta}_{1T}) - L(y_{v+\h}^* -
-      x_{2v}^{*\prime} \hat{\theta}_{2T}) & v > T
-    \end{cases}
-  \end{equation*}
-  with $y_{v+\h}^*$ and $x_{iv}^*$ denoting the elements of $V^*$
-  corresponding to $y_{v+\h}$ and $x_{iv}$ in $V_{t}$.  Equations
-  (\ref{eq:coupling1}) and (\ref{eq:coupling2}) are satisfied by
-  construction, and (\ref{eq:coupling3}) follows from Lemma
-  \ref{lem-extend-mp}.
-\end{proof}
-
-\begin{lem}\label{lem:a2}
-  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-3} hold.  Let $b_T$ be a
-  sequence of integers such that $b_T \to \infty$ and $b_T = o(P)$ and define
-  \begin{equation}
-    Z_i = \ZDef.
-  \end{equation}
-  Then
-  \begin{equation}
-    \label{eq:10}
-    \sum_{i=1}^{\lfloor P/b_T \rfloor} (\E_R Z_i^2 - \E_{R+(i-1) b_T}
-    Z_i^2) \to^p 0 \quad\text{ as } P \to \infty.
-  \end{equation}
-
-  If the assumptions of Theorem~\ref{res-oost} also hold, $b_T$ is
-  restricted further so that $b_T \equiv \lfloor \gamma/\delta
-  \rfloor$ for some positive scalar $\delta$, and we define
-  \begin{equation}\label{eq:13}
-    \kernelB{x} \equiv \kernelBDefn{x},
-  \end{equation}
-  then
-  \begin{equation}
-    \label{eq:12}
-    \vtSum (Z_{1t} Z_{2t} - \E_R Z_{1t} Z_{2t}) \to^p 0.
-  \end{equation}
-  where
-  \begin{gather}
-    Z_{1t} = \varianceTermIIIa,%
-    \intertext{and}%
-    Z_{2t} = \varianceTermIVb.
-  \end{gather}
-\end{lem}
-\begin{proof}
-\newcommand{\UFiltration}[1]{\ensuremath{\mathcal{F}_{(#1)b_{T}+R-P}}}%
-The first result,~\eqref{eq:10}, follows a similar argument to Lemma~5
-of \citet{Jon:97} and~\eqref{eq:12} to Lemma~A.4 of \citet{JoD:00}.
-Since these arguments are similar and our modification is the same for
-both, we'll just present the more complicated version,~\eqref{eq:12}.
-
-Note that $\{Z_{1t}^2 P\gamma_T/b_T\}$ and $\{Z_{2t}^2 P\gamma_T/b_T\}$
-are uniformly integrable.  As in~\citet[Lemma A.4]{JoD:00}, we can
-assume that there is a constant $C$ such that $Z_{1t}$ and $Z_{2t}$
-are bounded in absolute value by $C\sqrt{b_T/P\gamma_T}$; uniform
-integrability ensures that the difference between the unbounded random
-variables and these truncated versions is negligible for large enough
-values of $C$.
-
-Let $r = \lfloor 3P/2b_T \rfloor$ and rewrite the summation as
-\begin{align*}
-  \vtSum \vtIIIsummand &= \vtSumr \vtSuma \vtIIIsummand \\
-  &\quad+ \vtSumr \vtSumb \vtIIIsummand \\
-  &\quad+ \sum_{t=r b_T - P + R + 1}^{2P+R} \vtIIIsummand \\
-  &\equiv \vtSumr (U_i - \E_R U_i) + \vtSumr (U_i' - \E_R U_i') + o_{L_1}(1).
-\end{align*}
-The proof then holds if we can show that both $U_i$ and $U_i'$ obey
-LLNs.  We'll do so by proving that $\{U_i -\E_R U_i,
-\UFiltration{2i-1}\}$ and $\{U_i' - \E_R U_i', \UFiltration{2i}\}$ are
-$L_2$-mixingales of size $-1/2$ and using the bound $\E(\vtSumr (U_i -
-\E_R U_i))^2 = O(\vtSumr c_i^2)$ where the $c_i$ are the mixingale
-magnitude indices \citep{Mcl:75}.
-
-For non-negative $m$, we have
-\begin{equation*}
-U_i - \E_R U_i \in \UFiltration{2i+2m-1},
-\end{equation*}
-establishing half of the mixingale result trivially.  Now fix $i$ and $m >
-0$ and use Lemma \ref{lem-basic-coupling} to define $D_{ts}^*$
-for each $t =(2i-2)b_T-P+R+1,\dots,(2i-1)b_T-P+R$ and $s =
-\max(t-b_T,R+1),\dots,\min(t+b_T,T-\h)$ such that
-\begin{equation*}
- \E_R D_{ts}^* = \E_{(2i-2m-1)b_T+R-P} D_{ts}^* \quad a.s.
-\end{equation*}
-and
-\begin{equation*}
-  \lVert D_{ts}^* - D_s \rVert_2 \leq \couplingBound{s - (2i-2m-1)b_T+P}.
-\end{equation*}
-Also define
-\begin{equation*}
-  Z_{1t}^* = (P\gamma_T)^{-1/2} \sum_{l=\vttLower}^{\vttUpper}
-  (D_{t,t+l}^* - \E_R D_{t,t+l}^*)\ W(l/\gamma_T), \\
-\end{equation*}
-and
-\begin{equation*}
-Z_{2t}^* = (P\gamma_T)^{-1/2} \sum_{j=\vttLower}^{\vttUpper}
-    (D_{t,t+l}^* - \E_R D_{t,t+l}^*)\ \kernelB{j/\gamma_T}.
-\end{equation*}
-
-Now, we have the inequalities
-\begin{align*}
-  \lVert \E( U_i - \E_R U_i & \mid \UFiltration{2i-2m-1}) \rVert_2
-  \\ &\leq
-  \vtSuma \lVert \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) - \E_R
-  Z_{1t}Z_{2t} \rVert_2 \\
-  &= \vtSuma \lVert \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
-  &\quad - \E(Z_{1t}^* Z_{2t}^* \mid \UFiltration{2i-2m-1}) \\
-  &\quad + \E(Z_{1t}^* Z_{2t}^* \mid \UFiltration{2i-2m-1})
-  - \E_R Z_{1t}Z_{2t} \rVert_2 \\
-%  \leq \vtSuma (\wall \lVert \wall \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
-%  - \E(Z_{1t}^*Z_{2t}^* \mid \UFiltration{2i-2m-1}) \rVert_2\return
-%  \\ + \lVert \E_R Z_{1t}Z_{2t} - \E_R Z_{1t}^*Z_{2t}^*
-%  \rVert_2)\return \\
-  &\leq 2 \vtSuma \lVert Z_{1t} Z_{2t} - Z_{1t}^* Z_{2t}^*
-  \rVert_2 \\
-  &\leq 2 \vtSuma (\lVert Z_{1t} - Z_{1t}^* \rVert_2 \lVert
-  Z_{2t} \rVert_{\infty}
-  + \lVert Z_{2t} - Z_{2t}^* \rVert_2 \lVert Z_{1t}^* \rVert_{\infty}) \\
-  &\leq \frac{2 C b_T^{1/2}}{(P\gamma_T)^{1/2}} \vtSuma (\lVert Z_{1t} - Z_{1t}^* \rVert_2
-  + \lVert Z_{2t} - Z_{2t}^* \rVert_2).
-\end{align*}
-
-And we can finish the proof with the following inequalities:
-\begin{align*}
-  \frac{2 C b_T^{1/2}}{(P \gamma_T)^{1/2}} &\vtSuma \lVert Z_{1t} - Z_{1t}^* \rVert_2 \\& \leq
-  \frac{4C b_T^{1/2}}{P\gamma_T} \vtSuma \sum_{l=\vttLower}^{\vttUpper} \lVert
-  D_{t+l} - D_{t,t+l}^* \rVert_2 W(l/\gamma_T) \\&
-  \leq O\Bigg(\frac{b_T^{1/2}}{P\gamma_T}\Bigg) \vtSuma
-  \sum_{l=\vttLower}^{\vttUpper} \couplingBeta{t+l-(2i-2m-1)b_T+P}\\&
-  = O\Bigg(\frac{b_T^{1/2}}{P\gamma_T}\Bigg) O(b_T^{3/2-u}\, m^{-1/2-u})
-\end{align*}
-for some positive $u$.  The same argument holds for $Z_{2t}$.
-As a result,
-\[
-E\Big(\vtSumr (U_i - \E_R U_i)\Big)^2 = o\Big(\vtSumr b_T^2/P\gamma_T\Big) =
- o(b_T/\gamma_T) \to 0,
-\]
-as required.
-\end{proof}
-
-\begin{lem}\label{lem:a6}
-  Suppose the conditions of Theorem~\ref{res-oost} hold.
-  Then
-  \begin{equation}
-    \sh^2 - P^{-1} \sum_{s,t=R+1}^{T-h} (D_s - \E_R
-    D_s) (D_t - \E_R D_t) W((t-s)/\gamma) \to^{L_1} 0.
-  \end{equation}
-\end{lem}
-
-\begin{proof}
-   It follows from simple algebra that
-\begin{multline*}
-  \Big| \sh^2 -  P^{-1} \sum_{s,t=R+1}^{T-h} (D_s - \E_R
-    D_s) (D_t - \E_R D_t) W((t-s)/\gamma) \Big| \leq\\
-  \varianceDiffA \\ + P^{-1} \oosSum{s,t}{1} \lvert (D_s -
-  \oosA)(\E_R D_t - \oosA) \rvert \vWeight + o_p(1).
-\end{multline*}
-We'll prove that these two sums are $o_p(1)$; uniform integrability
-then implies convergence in $L_1$.  The arguments for each are almost
-identical, so we'll only present the first.
-
-Applying the Cauchy-Schwarz inequality twice and simplifying gives the
-upper bound
-\begin{multline*}
-\varianceDiffA \\ \leq O(1) \Big[\varianceDiffAii\Big]^{1/2} \Big[\varianceDiffAi\Big]^{1/2}.
-\end{multline*}
-Now,
-$P^{-1} \oosSum{s}{1}(D_s - \E_R D_s)^2 = O_p(1)$, and it suffices to prove
-that \[\varianceDiffAi = o_p(1).\]  Observe that
-\begin{align*}
-  \varianceDiffAi & = O_p\Big(P^{-1} \oosSum{s}{1}(\E_{R}D_s -
-  \E_R\oosA)^2\Big) + O_p(\oosA - \E_R\oosA)^{2} \\
-  &= O_p\Big(P^{-1} \oosSum{s}{1} (\E_RD_s)^2 - (\E_R\oosA)^2\Big) +
-  o_p(1),
-\end{align*}
-with the second term $o_p(1)$ by Lemma \ref{res-mixingale} and
-\citepos{Dav:93} mixingale LLN.
-
-Now define $D_s^*$, $s = R+1,\dots,T-\h$, as in Lemma
-\ref{lem-basic-coupling} so that $\E_{s-1} D_s^* = \E_R D_s^*$ almost
-surely.  Note that we also have the equality $\E_R D_s^* = \E_R
-D_{R+1}^*$ almost surely for all $s\geq R+1$, and so
-\[
-P^{-1} \oosSum{s}{1} (\E_R D_s^*)^2 = \Big(P^{-1} \oosSum{s}{1} \E_R
-D_s^*\Big)^2 \quad \text{a.s.}
-\]
-Consequently,
-\begin{align*}
-P^{-1} \oosSum{s}{1}& (\E_R D_s)^2 - (\E_R\oosA)^2 \\
-&= P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R D_s^*)^2]
- + \Big(P^{-1} \oosSum{s}{1} \E_R D_s^*\Big)^2 - (\E_R\oosA)^2 \quad \text{a.s}.\\
-&= O_p\Big(P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R D_s^*)^2]\Big)
- + O_p\Big(P^{-1} \oosSum{s}{1} \E_R (D_s - D_s^*)\Big).
-\end{align*}
-Finally,
-\begin{align*}
-\Big\lVert P^{-1} \oosSum{s}{1} [(\E_RD_s)^2 - (\E_R D_s^*)^2] \Big\rVert_1
-&\leq P^{-1} \oosSum{s}{1} \lVert \E_R (D_s - D_s^*) \rVert_2 \lVert
-\E_R (D_s + D_s^*) \rVert_2
-\\ &\leq (4 B_L/P) \oosSum{s}{1} \lVert \E_R (D_s - D_s^*) \rVert_2,
-\end{align*}
-and this last term vanishes as in the proof of Lemma~\ref{lem:a2},
-completing the proof.
-\end{proof}
-
-\subsection*{Proof of Lemma \ref{res-mixingale}}
-We will start by proving that $\{D_t - \E_R D_t, \Fs_t\}$ is an
-$L_2$-mixingale of size $-1/2$; $D_t$ is $\Fs_t$-measurable and so it
-suffices to prove that
-\begin{equation}\label{eq:24}
-  \| \E_{t-l} D_t  - \E_R D_t \|_2 \leq 2^{2 + 1/\rho} B_L \, \couplingBeta{l}
-\end{equation}
-for $l = 1,\dots,t-R$, since $\couplingBeta{l} = O(l^{-1/2 - \delta})$
-for some $\delta > 0$ by assumption. Fix $R$, $t$ and $l$ and use
-Lemma \ref{lem-basic-coupling} to define $D_t^*$ so that
-\[
-\E_R D_t^* = \E_{t-l} D_t^* \quad a.s.
-\]
-and
-\[
-\lVert D_t - D_t^* \rVert_2 \leq \couplingBound{l}.
-\]
-Then
-\begin{align*}
-\lVert \E_{t-l} D_t - \E_R D_t \rVert_2 & \leq
-\lVert \E_{t-l} D_t - \E_{t-l} D_t^* \rVert_2  + \lVert \E_{t-l} D_t^* - \E_R D_t \rVert_2 \\
-&\leq 2 \lVert D_t - D_t^* \rVert_2 \\
-&\leq 2^{2 + 1/\rho}\ B_L\ \couplingBeta{l}.\tag*{\qed}
-\end{align*}
-
-\noindent Asymptotic normality follows from~\eqref{eq:24} using a
-modification of \citepos{Jon:97} CLTs for mixingale and NED arrays.
-Define
-\begin{equation*}
-  Z_i = \ZDef
-\end{equation*}
-where $b_T$ is a sequence that satisfies $b_T\leq P$,
-$b_T\to\infty$, and $b_T/P\to 0$.  The same arguments used in
-\citepos{Jon:97} Theorem 1 show that
-\begin{equation*}
-   \SumOuterBlock{i} Z_i = P^{-1/2} \oosSum{s}{1} (D_t - \E_R D_t) + o_p(1).
-\end{equation*}
-and
-\begin{equation*}
-  \SumOuterBlock{i} Z_i = \SumOuterBlock{i} (Z_i - E_{R + (i-1)b_T}
-  Z_i) + o_p(1).
-\end{equation*}
-Note that $\{Z_i - E_{R + (i-1)b_T} Z_i,\mathcal{F}_{R + i b_T}\}_i$ is an
-MDS by construction, so \citepos{HaH:80} Theorem 3.2 and Corollary
-3.1 ensure that $\sigma^{-1} \SumOuterBlock{i} Z_i \to^d N(0,1) $ as
-long as
-\begin{equation*}
-  \sigma^2 - \SumOuterBlock{i} \E_R Z_i^2 \to^p 0,
-\end{equation*}
-and
-\begin{equation*}
-  \SumOuterBlock{i} \E_R Z_i^2 - \SumOuterBlock{i} \ZSqCE \to^p 0.\footnote{%
-    Note that $\sigma^2 \in \mathcal{F}_t$ for
-    all $t \geq R$, so Hall and Heyde's condition (3.21) is
-    unnecessary---see the remarks after their result.} %
-\end{equation*}
-The first equation holds as in \citet{Jon:97} (see the proof
-of his Theorem 2); the second is ensured by
-Lemma~\ref{lem:a2}. \qed
-
-\subsection*{Proof of Lemma \ref{res-convergence}}
-\newcommand{\resConvgRHS}[1]{\ensuremath{\E(L(y^* - x_1^{*\prime}\bh{1#1}) - L(y^{*} -
-x_2^{*\prime}\bh{2#1}) \mid \bh{#1})}}
-\newcommand{\resConvgEstDiff}[1]{\ensuremath{\E(L(y^{*} -
-    x_{#1}^{*\prime}\bh{#1R}) \mid \bh{R}) -
-\E(L(y^{*} - x_{#1}^{*\prime}\bh{#1T}) \mid \bh{T})}}
-\newcommand{\resConvgEstDiffRV}[1]{\ensuremath{L(y^{*} -
-    x_{#1}^{*\prime}\bh{#1R}) - L(y^{*} - x_{#1}^{*\prime}\bh{#1T})}}
-
-Equation~\eqref{eq:7} holds if we show
-\begin{gather}
-\E_R \oosA = \resConvgRHS{R} + o_p(P^{-1/2}),\label{eq:18}\\
-\E_T \oosB = \resConvgRHS{T} + o_p(Q^{-1/2}),\label{eq:19}
-\intertext{and}
-\resConvgEstDiff{i} = O_p(\sqrt{P/T}),\label{eq:20}
-\end{gather}
-where $\hat\theta_R = (\hat\theta_{1R}, \hat\theta_{2R})$,
-$\hat\theta_T = (\hat\theta_{1T}, \hat\theta_{2T})$, and $y^{*}$,
-$x_1^{*}$ and $x_2^{*}$ are random variables drawn from the joint
-distribution of $(y_{t+\h},x_{1t},x_{2t})$ independently of
-$\mathcal{F}_T$.
-
-\begin{proof}[Proof of~\eqref{eq:18} and~\eqref{eq:19}]
-For~\eqref{eq:18}, define $D_t^*$ for each $t=R+1,R+2,\dots,T-h$ so
-that
-\begin{equation*}
-  \| D_t^* - D_t \|_2 \leq 2^{(1+\rho)/\rho} B_L \beta_{t-R}^{(\rho-2)/2\rho}
-\end{equation*}
-and
-\begin{equation*}
-  \E_R D_t^* = \E(L(y^* - x_1^{*\prime}\hat\theta_{1R}) -
-  L(y^* - x_2^{*\prime}\hat\theta_{2R}) \mid \hat\theta_R) \qquad a.s.
-\end{equation*}
-Lemma~\ref{lem-basic-coupling} ensures that these $D_t^*$ exist.
-Now,
-\begin{align*}
-  \Big\lVert \E_R \oosA - \E\Big(P^{-1} \sum_{t=R+1}^{T-h} D_t^* \mid
-  \hat\theta_R\Big) \Big\rVert_2
-  &= \Big\lVert \E_R\Big( \oosA - P^{-1} \sum_{t=R+1}^{T-h} D_t^*
-  \Big) \Big\rVert_2 \\
-  &\leq P^{-1} \sum_{t=R+1}^{T-h} \lVert D_t - D_t^* \rVert_2\\
-  &= O(P^{-1}) \sum_{t=R+1}^{T-h} \beta_{t-R}^{(\rho-2)/2\rho}
-\end{align*}
-and this last term is $o(P^{-1/2})$ by assumption.
-Essentially the same argument proves~\eqref{eq:19} as well.
-\end{proof}
-
-\begin{proof}[Proof of~\eqref{eq:20}]
-Assumption~\ref{asmp-3} and the definition of the OLS estimator
-ensure that
-\begin{align*}
-  \|L(y^{*} -  x_i^{*\prime} \bh{iR}) - L(y^{*} - x_i^{*\prime} \bh{iT}) \|_1
-  &\leq B_{L} \| x_i^{*\prime} (\bh{iR} - \bh{iT}) \|_2 \\
-  &\leq B_{L} \, \| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
-  (X_{iR}'X_{iR})^{-1}] X_{iR}' \eb_{iR} \|_2 \\
-  &\quad+ B_L \, \| x_i^{*\prime}
-  (X_{iT}'X_{iT})^{-1}[X_{iT}'\eb_{iT} - X_{iR}
-  \eb_{iR} ] \|_2 .
-\end{align*}
-
-To simplify notation, define $V = (X_{iT}'X_{iT})^{-1} -
-(X_{iR}'X_{iR})^{-1}$ and $W = X_{iR}'\eb_{iR} \eb_{iR}'X_{iR}$. The
-first term in the upper bound satisfies
-\begin{align*}
-  \| x_i^{*\prime} V X_{iR}' \eb_{iR} \|_2^2
-  &\leq \eigen_{K_i}(\E x_i^* x_i^{*\prime}) \cdot \E \tr\big( V^2 W \big) \\
-  &= O(1) \cdot \E \tr\{ V^2 \E(W \mid
-  X_{iR}'X_{iR}, x_{i,R-\h+1} x_{i,R-\h+1}',\dots, x_{i,T-\h} x_{i,T-\h}')\}
-\end{align*}
-by assumption. Observe that
-\begin{multline*}
-  \E \tr\{ V^2 \E(W \mid X_{iR}'X_{iR}, x_{i,R-\h+1} x_{i,R-\h+1}',\dots, x_{i,T-\h} x_{i,T-\h}')\}
-  \\ \leq
-  \Big\rVert \sum_{i=1}^{K_i} \eigen_i^2 \big(V\big) \Big\rVert_{3/2}
-  \big\rVert \eigen_{K_i}(\E(W \mid
-  X_{iR}'X_{iR}, x_{i,R-\h+1} x_{i,R-\h+1}',\dots, x_{i,T-\h} x_{i,T-\h}')) \big\rVert_3.
-\end{multline*}
-The second term in this product is $O(R)$ by
-Assumption~\ref{asmp-2}. To bound the first term, note that
-$(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}$ has rank $P$ and
-each of its nonzero eigenvalues is bounded in absolute value by the
-eigenvalues of $(X_{iR}'X_{iR})^{-1}$. The eigenvalues of
-$(X_{iR}'X_{iR})^{-1}$ are $O_{L_3}(1/R)$ by Assumption~\ref{asmp-2}, so
-\begin{equation*}
-  \Big\|\sum_{j=1}^{K_i}
-  \eigen_j^2(V)\Big\|_{3/2}
-  \leq \Big\|\sum_{j=K_i - P+1}^{K_i} \eigen_j^2(V) \Big\|_{3/2}
-  = O(P/R^2).
-\end{equation*}
-Consequently,
-\begin{equation*}
-  \E \tr\bigg\{[(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}]^2
-  X_{iR}'\eb_{iR} \eb_{iR}X_{iR} \bigg\} = O(P/R)
-\end{equation*}
-and so
-\begin{equation*}
-  \| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
-  (X_{iR}'X_{iR})^{-1}] X_{iR}' \eb_{iR} \|_2 = O(\sqrt{P/R}).
-\end{equation*}
-
-A similar argument proves that
-\begin{equation*}
-  \big\| x_i^{*\prime} (X_{iR}'X_{iR})^{-1}
-  [X_{iT}'\eb_{iT} - X_{iR} \eb_{iR} ] \big\|_2 =  O(\sqrt{P/R}),
-\end{equation*}
-completing the proof.
-\end{proof}
-
-\subsection*{Proof of Theorem \ref{res-oost}}
-We can rewrite the centered \oost\ statistic as
-\[
-\sqrt{P}(\oosA - \E_T \oosB)/\sh
-= \frac{\sigma}{\sh}\, \Big( \sqrt{P}(\oosA - \E_R \oosA)/\sigma
-+ \sqrt{P}(\E_R \oosA - \E_T \oosB)/\sigma \Big)
-\]
-so Lemma \ref{res-mixingale} and \ref{res-convergence} ensure that
-this term is asymptotically standard normal as long as $\sigma/\sh
-\to^p 1$. Since $\sigma$ is almost surely positive, this convergence
-is equivalent to $\sigma^2 - \sh^2 \to^p 0$.
-
-The proof that $\sigma^2 - \sh^2 \to^p 0$ follows \citepos{JoD:00}
-Theorem 2.1 closely.  We start by defining similar quantities to
-theirs, borrowing their notation when possible to make the
-similarities apparent. Let $b_T \equiv \lfloor \gamma/\delta \rfloor$,
-define $\kernelB{x}$ as in Equation \eqref{eq:13}, and define the following
-terms as in \citet{JoD:00}:
-\begin{align*}
-  \varianceTermI &\equiv
-  \varianceTermIDefn,\\ \varianceTermII &\equiv \vtSum
-  \varianceTermIIa\\& \quad \times \varianceTermIIb,\\
-  \varianceTermIII &\equiv \vtSum \varianceTermIIIa\\
-  &\quad \times \varianceTermIIb,\\
-  \varianceTermIV &\equiv \vtSum \varianceTermIIIa \\
-  &\quad\times \varianceTermIVb.
-\end{align*}
-These definitions give the inequalities
-\begin{align*}
-  \lVert \sh^2 - \sigma^2 \rVert_1 &
-  \leq \lVert \sh^2 - \varianceTermI \rVert_1
-  + \lVert \varianceTermI - \varianceTermII \rVert_1
-  + \lVert \varianceTermII - \varianceTermIII \rVert_1
-  + \lVert \varianceTermIII - \varianceTermIV \rVert_1\\ & \quad
-  + \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1
-  + \lVert \E_R\varianceTermIII - \E_R\varianceTermIV \rVert_1
-  + \lVert \E_R\varianceTermII - \E_R\varianceTermIII \rVert_1\\ & \quad
-  + \lVert \E_R\varianceTermI - \E_R\varianceTermII \rVert_1
-  + \lVert \E_R \varianceTermI - \sigma^2 \rVert_1
-  \\ &
-  \leq  \lVert \sh^2 - \varianceTermI \rVert_1
-  + 2(\lVert \varianceTermI - \varianceTermII \rVert_1
-      + \lVert \varianceTermII - \varianceTermIII \rVert_1
-      + \lVert \varianceTermIII - \varianceTermIV \rVert_1) \\
-  & \quad + \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1
-  + \lVert \E_R \varianceTermI - \sigma^2 \rVert_1.
-\end{align*}
-De Jong and Davidson (2000) prove that
-\begin{equation*}
-\lim_{\delta\to0} \limsup_{T\to\infty} \lVert \varianceTermI -
-\varianceTermII\rVert_1 = 0,
-\end{equation*}
-\begin{equation*}
-\lim_{\delta\to0} \limsup_{T\to\infty} \lVert \varianceTermII - \varianceTermIII
-\rVert_1 = 0,
-\end{equation*}
-\begin{equation*}
-\lim_{\delta\to0} \limsup_{T\to\infty} \lVert \varianceTermIII - \varianceTermIV
-\rVert_1 = 0,
-\end{equation*}
-and
-\begin{equation*}
-\lim \lVert \E_R \varianceTermI - \sigma^2 \rVert_1 = 0.
-\end{equation*}
-Their proofs of these four convergence results use the fact that NED
-functions of mixing processes are also mixingale processes and do not
-use any other properties specific to NED processes, so their results
-hold here as well.  We do need to modify their proofs that
-\begin{equation*}
-  \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1 \to 0
-\end{equation*}
-and
-\begin{equation*}
-  \lVert \sh^2 - \varianceTermI \rVert_1 \to 0
-\end{equation*}
-for all positive $\delta$, though, since those proofs exploit NED
-properties. These results are presented as Lemmas~\ref{lem:a2}
-and~\ref{lem:a6} respectively.  \qed
-
-\subsection*{Proof of Theorem \ref{res:oostest}}
-Coverage of the confidence intervals is immediate from
-Theorem~\ref{res-oost}, so we will present a proof of~\eqref{eq:23}.
-By Lemma~\ref{res-convergence}, we know that $\E_R \oosA - \E_T \oosB
-\to^p 0$, so
-\begin{equation*}
-  \Pr[\E_R \oosA \leq 0] - \Pr[\E_T \oosB \leq 0] \to 0.
-\end{equation*}
-Now we can use Lemma~\ref{lem-basic-coupling} to define $D_t^*$ as in
-the proofs of Lemma~\ref{res-mixingale} and~\ref{res-convergence} so
-that $\E_R D_t^* = \E_{t-l} D_t^*$ a.s. and
-\[
-\lVert D_t - D_t^* \rVert_2 \leq \couplingBound{l}
-\]
-and define $\oosA^* = P^{-1} \sum_{t=R+1}^{T-\h} D_t^*$. Then
-\begin{equation*}
-  \lVert \sqrt{P} \oosA - \sqrt{P} \oosA^* \rVert_2
-  \leq P^{-1/2} \sum_{t=R+1}^{T-\h} \lVert \oosA - \oosA^* \rVert_2
-  = o(1),
-\end{equation*}
-and, consequently, we have convergence in probability of the following
-vectors:
-\begin{equation*}
-  (\sqrt{P} \oosA^*/\sigma,\ \E_R \oosA) -
-  (\sqrt{P} \oosA/\sh,\ \E_T \oosB) \to^p 0,
-\end{equation*}
-where we are implicitly using consistency of $\sh^2$ for $\sigma^2$.
-More importantly, this implies convergence in distribution of these
-vectors, so
-\begin{equation*}
-  \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha
-  \text{ and } \E_R \oosA \leq 0]
-  - \Pr[\sqrt{P} \oosA / \sh > z_\alpha \text{ and }
-  \E_T \oosB \leq 0] \to 0.
-\end{equation*}
-
-For large enough $T$, both $\Pr[\E_R \oosA \leq 0]$ and $\Pr[\E_T
-\oosB \leq 0]$ are positive (the second by assumption, the first by
-convergence to the second) so (for these $T$)
-\begin{align}\label{eq:31}
-  \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha
-  \mid \E_R \oosA \leq 0] &=
-  \frac{\Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha \text{ and }
-    \E_R \oosA \leq 0]}{\Pr[\E_R \oosA \leq 0]}
-\intertext{and}\label{eq:32}
-  \Pr[\sqrt{P} \oosA / \sh > z_\alpha
-  \mid \E_T \oosB \leq 0] &=
-  \frac{\Pr[\sqrt{P} \oosA / \sh > z_\alpha \text{ and }
-    \E_T \oosB \leq 0]}{\Pr[\E_T \oosB \leq 0]}
-\end{align}
-almost surely. Since the terms on the RHS of Equations~\eqref{eq:31}
-and~\eqref{eq:32} converge to the same limit in probability, we have
-\begin{equation*}
-  \Pr[\sqrt{P} \oosA / \sh > z_\alpha  \mid \E_T \oosB \leq 0]
-  - \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha \mid \E_R \oosA \leq 0]
-  \to^p 0
-\end{equation*}
-and it suffices to show that
-\begin{equation*}
-  \plim \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha \mid \E_R \oosA \leq 0]
-  \leq \alpha.
-\end{equation*}
-
-To establish this inequality, we have
-\begin{align*}
-  \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha \mid \E_R \oosA \leq 0]
-  &\leq \Pr[\sqrt{P} (\oosA^* - \E_R \oosA) / \sigma > z_\alpha
-  \mid \E_R \oosA \leq 0] \\
-  &\leq \E\big(
-  \Pr[\sqrt{P} (\oosA^* - \E_R \oosA) / \sigma > z_\alpha \mid \Fs_R]
-  \mid \E_R \oosA \leq 0\big).
-\end{align*}
-By construction,
-\begin{equation*}
-  \Pr[\sqrt{P} (\oosA^* - \E_R \oosA) / \sigma > z_\alpha \mid \Fs_R]
-  \to \alpha
-\end{equation*}
-since generated pseudo OOS observations in each $D_t^*$ are
-independent of $\Fs_R$, completing the proof.
-\qed
-
-\subsection*{Proof of Theorem~\ref{res:insample1}}
-
-Let $(\e_{t+h}, x_{t}) \sim i.i.d.\ N(0,I)$ and let $\theta_1 = 0$.
-For any $d \geq 0$, the event $\E_T \oosB = -d$ implies that
-\begin{equation*}
-  \E_T (y_{T+\h+1} - x_{1T+1}'\bh{1T})^2
-  = \E_T (y_{T+\h+1} - x_{2T+1}'\bh{2T})^2 - d \quad a.s.
-\end{equation*}
-which can be expressed as
-\begin{equation}\label{eq:34}
-  d + \theta_2'M_2' M_2 \theta_2 + \bh{1T}'\bh{1T} - \bh{2T}'M_1'M_1\bh{2T}
-  = (\bh{2T} - \theta_2)' M_2'M_2 (\bh{2T} - \theta_2) \quad a.s.
-\end{equation}
-$M_2 \bh{2T}$ is normally distributed conditional on $\bh{1T}$ and
-$M_1 \bh{2T}$, and is distributed on the surface of the sphere defined
-by~\eqref{eq:34} conditional on $\bh{1T}$, $M_1 \bh{2T}$, and the
-event $\E_T \oosB = -d$.
-
-Since $M_2 \bh{2T}$ is normal, this conditional distribution is
-invariant to reflection across the axes defined by the eigenvectors of
-its covariance matrix. So when $\theta_2$ lies outside the cylinder
-that contains the acceptance region of $\Lambda$, i.e. when
-$\theta_2'M_2' V_T M_2 \theta_2 > c$, we have\footnote{%
-  To keep the notation in these equations manageable, define the
-  information set
-  $\Gs = \sigma(\E_T \oosB \leq 0,~ \theta_2'M_2' V_T M_2 \theta_2 >
-  c)$.} %
-\begin{align*}
-  \Pr[ \bh{2T}' M_2' V_T M_2 \bh{2T} \leq c \mid \Gs]
-  &= \E\Big( \Pr[ \bh{2T}'M_2' V_T M_2 \bh{2T} \leq c \mid \Gs,~\bh{1T},~M_1 \bh{2T}] \mid \Gs \Big) \\
-  & < 1/2
-\end{align*}
-since the inner conditional probability is less than 1/2.
-
-Now let $\delta > 0$ be an arbitrary but small constant, and choose
-$\theta_2$ far enough from the origin to ensure that
-\begin{equation*}
-  \Pr[\theta_2'M_2' V_T M_2 \theta_2 \leq c] \leq \delta
-\end{equation*}
-for large enough $T$. Then
-\begin{align*}
-  \E(\Lambda \mid \E_T \oosB \leq 0) &
-  \geq \Pr[\bh{2T}' M_2' V_T M_2 \bh{2T} > c \mid \E_T \oosB \leq 0] \\
-  &= \Pr[\bh{2T}' M_2' V_T M_2 \bh{2T} > c \text{~~and~~}
-  \theta_2'M_2' V_T M_2 \theta_2 > c \mid \E_T \oosB  \leq 0] \\
-  & \quad + \Pr[\bh{2T}' V_T M_2 \bh{2T} > c \text{~~and~~ }
-  \theta_2'M_2' V_T M_2 \theta_2 \leq c \mid \E_T \oosB \leq 0].
-\end{align*}
-The second term is nonnegative by design. By conditioning on
-$\theta_2'M_2' V_T M_2 \theta_2 > c$ our earlier argument shows that
-the first term is greater than or equal to $(1 - \delta) / 2$. Since
-$\delta$ is arbitrarily small, this completes the proof.
-\qed
-
-\subsection*{Proof of Theorem~\ref{res:insample2}}
-As in the proof of Theorem~\ref{res:insample1}, let $(\e_{t+h}, x_{t})
-\sim i.i.d.\ N(0,I)$ and let $\theta_1 = 0$. The event $\E_T \oosB
-\geq 0$ implies that
-\begin{equation*}
-  \E_T (y_{T+\h+1} - x_{1T+1}'\bh{1T})^2
-  \geq \E_T (y_{T+\h+1} - x_{2T+1}'\bh{2T})^2 \quad a.s.
-\end{equation*}
-which can be expressed as
-\begin{equation}\label{eq:2}
-  \theta_2'M_2 M_2'\theta_2 + \bh{1T}'\bh{1T} - \bh{2T}'M_1'M_1\bh{2T}
-  \geq (\bh{2T} - \theta_2)' M_2'M_2 (\bh{2T} - \theta_2) \quad a.s.
-\end{equation}
-$M_2 \bh{2T}$ is normally distributed conditional on $\bh{1T}$ and
-$M_1 \bh{2T}$, and is a.s. contained in the sphere defined
-by~\eqref{eq:2} conditional on $\bh{1T}$, $M_1 \bh{2T}$, and the
-event $\E_T \oosB \geq 0$.
-
-Let $\delta$ be a small arbitrary constant, define $\theta^*$ as
-\begin{gather*}
-  \theta^* = \argmax_\theta \theta' M_2' M_2 \theta \\
-  s.t.\quad \theta_2'M_2'M_2\theta_2 +  \bh{1T}'\bh{1T} - \bh{2T}'M_1'M_1\bh{2T} = (\theta - \theta_2)' M_2'M_2 (\theta - \theta_2)
-\end{gather*}
-($\theta^*$ is stochastic and depends on $\bh{1T}$ and $M_1 \bh{2T}$)
-and choose $c$ so that
-\begin{equation*}
-  \Pr[ \theta^{* \prime} M_2 M_2 \theta^* > c] < \delta.
-\end{equation*}
-
-Then, we have for large enough $T$
-\begin{align*}
-  \E(\Lambda \mid \E_T \oosB \geq 0) &\leq
-  \Pr[\bh{2T}'M_2'M_2\bh{2T} > c \mid \E_T \oosB \geq 0) \\
-  &\leq \delta
-\end{align*}
-Since $\delta$ is arbitrarily close to zero, this completes the proof.
-
-\qed
-
-\clearpage
-\markboth{}{}
-\tryinput{floats/mc-ftest.tex}
-
-\begin{table}[tb]
-  \begin{tabularx}{\linewidth}{XX}
-    \toprule
-    Category & Variable \\
-    \midrule
-    Stock market variables
-    & Dividend to price ratio (log) \\
-    & Earnings to price ratio (log) \\
-    & Stock market variance \\
-    & Book to market ratio \\
-    & Net equity expansion \\
-    & Percent equity issuing \\\\
-    Interest rate variables
-    & Treasury Bill rate (3 month) \\
-    & Long term yield \\
-    & Long term rate \\
-    & Default return spread \\
-    & Default yield spread \\
-    & Inflation rate \\
-    \bottomrule
-  \end{tabularx}
-  \caption{Variables used to predict the equity premium
-    (Section~\ref{sec:empirics}).
-    Please see Goyal and Welch's original paper \citep{GoW:08}
-    for a detailed description of each variable.}
-  \label{tab:equity}
-\end{table}
-
-\tryinput{floats/empirics-insample.tex}
-\tryinput{floats/empirics-insample-tuned.tex}
-% These macros create tables. They are defined in
-% floats/empirics-insample.tex and possibly overwritten in the next
-% file.
-\insamplecoefs
-\insampletests
-
-\begin{figure}\centering
-  {\large Coverage of DMW OOS interval for $\E_R\oosA$ in simulations}
-  \tryinput{floats/mc-interval-testerror1.tex}
-  \caption{Simulated coverage of $\E_R \oosA$ at 90\% confidence using
-    a one-sided interval based on the DMW \oost\ test, plotted as a
-    function of the fraction of observations used in the test sample,
-    $P/T$. The solid horizontal line denotes the intervals' nominal
-    coverage.}
- \label{fig:interval-R}
-\end{figure}
-\clearpage
-
-\begin{figure}\centering
-  {\large Coverage of DMW OOS interval for $\E_T\oosB$ in simulations}
-  \tryinput{floats/mc-interval-generror1.tex}
-  \caption{Simulated coverage of $\E_T \oosB$ at 90\% confidence using
-    a one-sided interval based on the DMW \oost\ test, plotted as a
-    function of the fraction of observations used in the test sample,
-    $P/T$.  The solid horizontal line denotes the intervals' nominal
-    coverage.}
-  \label{fig:interval-T}
-\end{figure}
-\clearpage
-
-\begin{figure}\centering
-  {\large Size of DMW \oost\ test in simulations}
-  \tryinput{floats/mc-dmwsize.tex}
-  \caption{Simulated rejection probabilities for the DMW \oost\ test
-    under the null hypothesis that the benchmark model will forecast
-    better, $\E_T \oosB \leq 0$. The nominal size is 10\% and is
-    marked with a solid horizontal line. Values greater than 10\%
-    indicate that the test rejects the benchmark model too often. See
-    Section~\ref{sec:simulation-design} for a discussion of the
-    simulation design.}
-  \label{fig:ttest-size}
-\end{figure}
-\clearpage
-
-\begin{figure}\centering
-  {\large Size of Clark-West OOS test in simulations}
-  \tryinput{floats/mc-clarkwestsize.tex}
-  \caption{Simulated rejection probabilities for Clark and West's
-    (2006, 2007) OOS test statistic under the null hypothesis that the
-    benchmark will forecast better, $\E_T \oosB \leq 0$. The nominal
-    size is 10\% and is marked with a solid horizontal line. Values
-    greater than 10\% indicate that the test rejects the benchmark
-    model too often. See Section~\ref{sec:simulation-design} for a
-    discussion of the simulation design.}
-   \label{fig:clarkwest}
-\end{figure}
-\clearpage
-
-\begin{figure}\centering
-  {\large Size of McCracken \oost\ test in simulations}
-  \tryinput{floats/mc-mccrackensize.tex}
-  \caption{Simulated rejection probabilities for McCracken's (2007)
-    \oost\ test under the null hypothesis that the benchmark model is
-    more accurate, $\E_T \oosB \leq 0$. Nominal size is 10\% and is
-    marked with a solid horizontal line. Values greater than 10\%
-    indicate that the test rejects the benchmark model too often. See
-    Section~\ref{sec:simulation-design} for a discussion of the
-    simulation design.}
-  \label{fig:mccracken}
-\end{figure}
-\clearpage
-
-\begin{figure}\centering
-  {\large Power of DMW \oost\ test in simulations}
-  \tryinput{floats/mc-dmwpower.tex}
-  \caption{Simulated rejection probabilities for the DMW \oost\ test
-    under the alternative that the benchmark model is less accurate,
-    $\E_T \oosB > 0$. Nominal size is 10\% and is marked with a solid
-    horizontal line. Values greater than 10\% indicate that the test
-    rejects the benchmark model too often. See
-    Section~\ref{sec:simulation-design} for a discussion of the
-    simulation design.}
-  \label{fig:ttest-power}
-\end{figure}
-\clearpage
-
-\begin{figure}
-\centering
-\large{Difference in OOS MSE of Prevailing Mean and\\ Kitchen
-    Sink Models of Equity Premium (OLS)}
-\tryinput{floats/empirics-oos-mse-1.tex}
-\tryinput{floats/empirics-oos-mse-1b.tex}
-\caption{OOS difference in the MSE
-  of the prevailing mean benchmark and the kitchen sink model as a
-  function of the test sample size, $R$.  Both models forecast the
-  equity premium using annual data from 1928--2008.  The solid line
-  gives the OOS average, and the shaded region indicates the
-  one-sided 95\% confidence interval implied by the
-  DMW test.  The bottom panel is a detailed view of the top
-  panel for $R \geq 50$.}
-\label{fig:empirics1}
-\end{figure}
-\clearpage
-
-\begin{figure}
-\centering
-\large{Difference in OOS MSE of Prevailing Mean and\\ Kitchen
-    Sink Models of Equity Premium (CT)}
-\tryinput{floats/empirics-oos-mse-2.tex}
-\tryinput{floats/empirics-oos-mse-2b.tex}
-\caption{OOS difference in the MSE
-  of the prevailing mean benchmark and the kitchen sink model as a
-  function of the test sample size, $R$.  Both models forecast the
-  equity premium using annual data from 1928--2008.  The solid line
-  gives the OOS average, and the shaded region indicates the
-  one-sided 95\% confidence interval implied by the
-  DMW test.  The bottom panel is a detailed view of the top
-  panel for $R \geq 50$.}
-\label{fig:empirics2}
-\end{figure}
-\clearpage
-
-\begin{figure}
-\centering
-\large{OOS MSE of Individual Forecasts of Equity Premium}
-\tryinput{floats/empirics-oos-ind-ks.tex}
-\tryinput{floats/empirics-oos-ind-pm.tex}
-\caption{OOS MSE of the Prevailing Mean (PM) and
-    Kitchen Sink (KS) models for equity premium prediction as
-    a function of the size of the training sample, $R$.  Please note
-    that the vertical scales are different in the two plots.}
-\label{fig:empirics3}
-\end{figure}
-
-\clearpage
-
-\bibliographystyle{abbrvnat}
-\bibliography{latex-tools-0.2.1/references}
-
-\clearpage
-\section{Supplemental appendix (not for publication)}
-\input{appendix_contents}
-
-\end{document}
 

### 2017-04-21 3-theory.tex
[#40/move] Move extended example from Section 3.3 to appendix

--- 2016-03-09 paper.tex
@@
-\documentclass[12pt,draft]{article}
-\input{setup}
-
-\title{Out-of-Sample Comparisons of Overfit Models}
-\author{Gray Calhoun\thanks{email: gcalhoun@iastate.edu. I
-    would like to thank Julian Betts, Helle Bunzel,
-    St\'ephane Bonhomme, Marjorie Flavin,
-    Nir Jaimovich, Lutz Kilian, Ivana Komunjer, Michael McCracken,
-    Seth Pruitt, Ross Starr, Jim Stock, Yixiao Sun, Allan Timmermann,
-    Hal White, several anonymous referees, participants at the 2010
-    Midwest Economics Association Annual Meetings, the 2010
-    International Symposium on Forecasting, the 2010 Joint Statistical
-    Meetings, the 2011 NBER-NSF Time-Series
-    Conference, and in many seminars at UCSD, and especially
-    Graham Elliott for their valuable suggestions, feedback and advice
-    in writing this paper.  I would also like to thank Amit Goyal for
-    providing computer code and data for his 2008 RFS paper
-    with Ivo Welch \citep{GoW:08}.} \\ Iowa State University}
-
-\date{\VERSION}
-
-\begin{document}
-\maketitle
-
-\begin{abstract}\noindent
-  This paper uses dimension asymptotics to study the behavior of
-  out-of-sample (OOS) test statistics when they are used to compare
-  ``overfit'' linear regression models. Under these asymptotics, the
-  number of predictors used by the larger model increases with the
-  number of observations so that their ratio remains uniformly
-  positive. This analysis gives a theoretical motivation for using
-  out-of-sample (OOS) comparisons: the Diebold-Mariano-West OOS $t$-test
-  (Diebold and Mariano, 1995, \textit{JBES}, and West, 1996,
-  \textit{Econometrica}) allows a forecaster to conduct inference
-  about the models' generalization error, an important measure of
-  forecast accuracy that conditions on the models' parameter estimates.
-  We show analytically and through Monte Carlo that standard full-sample
-  test statistics can not test hypotheses about this measure of performance.
-  Our paper also suggests that comparisons of overfit models require small
-  OOS test samples. If $P$ denotes the number of observations used for the
-  OOS comparison and $T$ the total number of observations, $P^2/T$ must
-  converge to zero for the OOS $t$-test to be centered on the model's
-  generalization error.
-
-\noindent JEL Classification: C12, C22, C52, C53
-
-\noindent Keywords: Generalization Error, Forecasting, Model
-Selection, $t$-test, Dimension Asymptotics
-\end{abstract}
-\newpage
-
-\section{Introduction}
-\label{sec:introduction}
-
-Consider two sequences of length $P$ of prediction errors, the result
-of forecasting the same variable with two different estimated models.
-Both models are estimated with $R$ observations, collectively called
-the {\em estimation window}, and are used to forecast an additional
-$P$ observations, called the {\em test sample}.  There are $T$
-observations in all, and $R+P=T$.  This paper introduces a new limit
-theory for statistics constructed from these prediction errors
-designed to approximate the behavior of the statistics when one of the
-models is overfit.  In doing so, we provide a theoretical
-justification for forecasters to use out-of-sample (OOS) instead of in-sample
-comparisons: the DMW OOS test\footnote{%
-  In this paper, we will refer to the basic OOS $t$-test studied by
-  \citet{DiM:95} and \citet{Wes:96} as the DMW test.} %
-allows a forecaster to conduct
-inference about the expected future accuracy of his or her models when
-one or both is overfit.  We show analytically and through Monte Carlo simulations
-that standard full-sample test statistics can not test hypotheses
-about this performance.
-
-Our paper also shows that popular test and training sample sizes may
-give misleading results if researchers are concerned about overfit.
-We show that $P^2/T$ must converge to zero for the DMW test to give
-valid inference about the expected forecast accuracy, otherwise the
-test measures the accuracy of the estimates constructed using only the
-training sample.  In empirical research, $P$ is typically much larger
-than this.  Our simulations indicate that using large values of $P$
-with the DMW test gives undersized tests with low power, so this
-practice may favor simple benchmark models too much.  Existing
-corrections, proposed by \citet{ClM:01,ClM:05}, \citet{Mcc:07} and
-\citet{ClW:06,ClW:07}, seem to overcorrect for this problem, though, and reject
-too often when the benchmark model is more accurate.
-
-Although OOS comparisons have been popular in Macroeconomics and
-Finance since \citepos{MeR:83} seminal study of exchange rate models,
-it has been unclear from a theoretical perspective whether or not the
-statistics are useful.  Empirical researchers often cite ``overfit''
-or ``instability'' as reasons for using OOS comparisons, as in
-\citet{StW:03}, but neither term is precisely defined or formalized.
-Compounding this problem, the asymptotic distributions of these
-statistics are derived under conditions that rule out either
-instability or overfit and allow a researcher to use a conventional
-in-sample comparison---a variation of the $F$-test, for example.  As
-\citet{InK:04} argue, the statistics themselves are designed to test
-hypotheses that can be tested by these in-sample statistics.  For
-example, \citet{DiM:95} and \citet{Wes:96} derive the limiting
-distributions of many popular OOS test statistics under conditions
-that would justify these full-sample tests.  Much
-of the subsequent research by \citet{Mcc:00, Mcc:07}, \citet{CCS:01},
-\citet{ClM:01,ClM:05}, \citet{CoS:02,CoS:04}, \citet{ClW:06,ClW:07},
-\citet{Ana:07}, and others relaxes several of Diebold and Mariano's
-and West's assumptions, but maintains the stationarity and dependence
-conditions that permit in-sample comparisons \citep[see][for a
-review of this literature]{Wes:06}.\footnote{%
-  Like us, \citet{Ana:07} allows the number of regressors to increase
-  with $T$.  But in that paper, the number of regressors increases
-  slowly enough that the OLS coefficients are consistent and
-  asymptotically normal.} %
-\citet{GiW:06} and
-\citet{GiR:09, GiR:10} are exceptions.  Instead of focusing on
-hypotheses that can be tested by in-sample comparisons, \citet{GiW:06}
-derive an OOS test for the null hypothesis that the difference
-between two models' OOS forecasting performance is unpredictable, a
-martingale difference sequence (MDS); \citet{GiR:09} test whether the OOS
-forecasting performance of a model suffers from a breakdown relative
-to its in-sample performance; and \citet{GiR:10} test whether the
-forecasting performance is stable. However, those papers focus on a
-particular OOS estimation strategy and do not address why OOS
-comparisons might be useful as a general strategy.
-
-Since in-sample and OOS statistics require similar assumptions and
-test similar hypotheses, one might expect that they would give similar
-results.  They do not.  In-sample analyses tend to support more
-complicated theoretical models and OOS analyses support simple
-benchmarks, as seen in \citet{MeR:83}, \citet{StW:03}, and
-\citet{GoW:08}.  Since these different approaches strongly influence
-the outcome of research, it is important to know when each is
-appropriate.  The explanations in favor of OOS comparisons claim
-that they should be more robust to unmodeled instability
-\citep{ClM:05,GiW:06,GiR:09,GiR:10} or to overfit
-\citep{Mcc:98,Cla:04}.  Both explanations presume that the in-sample
-comparison is invalid and the OOS comparisons are more reliable.  Of
-course, as \citet{InK:04,InK:06} point out, both in-sample and OOS
-methods could be valid, but the OOS methods could have lower power.
-
-In this paper, we study the ``overfit'' possibility and leave
-``instability'' to future research. This paper uses dimension
-asymptotics to study the behavior of OOS comparisons when at least
-one of the models is overfit---the number of its regressors
-increases with the number of observations so that their ratio remains
-positive.  Although overfit is sometimes used to describe the
-situation where a forecaster chooses from many different models,
-i.e. \emph{data-mining} or \emph{data-snooping}, we view these as
-separate issues.  Procedures that account for the presence of many
-models have been, and are continuing to be, developed \citep[see, for
-example,][]{Whi:00,Han:05,RoW:05,HHK:10,ClM:12b}, but it is unclear
-whether those procedures should themselves use in-sample or OOS
-comparisons.  Understanding the difference between in-sample and OOS
-comparisons in the context of a simple comparison between two models
-is necessary before resolving any new issues that arise with multiple
-comparisons. Moreover, the empirical research that motivates
-this paper uses \emph{pseudo} OOS comparisons and not
-true OOS comparisons.  Even if a true OOS comparison
-could account for some forms of data-snooping better than
-\citepos{Whi:00} BRC or its extensions, in-sample and pseudo
-OOS comparisons would both be affected by the data-snooping, a
-point also made by \citet{InK:04}.
-
-We focus on linear regression models estimated with a fixed window
-for simplicity, but our basic conclusions should be true for other
-models and estimation strategies as well.  Under this
-asymptotic theory, where the number of regressors $K$ increases with $T$
-so that the limit of $K/T$ is positive and less than one,
-the OLS coefficient estimator is no longer
-consistent or asymptotically normal \citep{Hub:73} and has positive
-variance in the limit.  We show that, even so, the usual OOS average
-is asymptotically normal and can consistently estimate the difference
-between the models' generalization error, the expected loss in the
-future conditional on the data available in period
-$T$.\footnote{%
-  See, for example, \citet{HTF:08} for a discussion of generalization
-  error.} %
-Under these asymptotics, the generalization
-error does not converge to the expected performance of the pseudotrue
-models, so existing in-sample and OOS comparisons measure different
-quantities and should be expected to give different results for
-reasons beyond simple size and power comparisons.  Under our limit theory,
-the model that is closer to the true DGP in population can forecast
-worse.  In such a situation, a standard in-sample comparison would
-correctly reject the null hypothesis that the benchmark is true, and
-an OOS comparison would correctly fail to reject the null that the
-benchmark is more accurate.\footnote{%
-  In a pair of papers similar to ours, \citet{ClM:12,ClM:12b} study
-  in-sample and OOS tests that the larger model has nonzero
-  coefficients that are too close to zero to expect the model to
-  forecast more accurately.  Like this paper, they argue that the
-  larger model can be true but less accurate.  However, they focus on
-  an aspect of the DGP that makes this phenomenon likely, while we
-  focus on the coefficient estimates that produce less accurate
-  forecasts.  Moreover, the implications of our asymptotic theories
-  are different and their papers do not provide reasons to do OOS
-  comparisons.} %
-Also note that, in this situation, a model that performs well
-in-sample can perform badly out-of-sample even if there are no
-structural breaks or other forms of instability.  Researchers
-have argued that a breakdown of in-sample forecasting ability
-indicates a structural break (see \citealp{BoH:99}, and
-\citealp{StW:03}, among others), but we show that this breakdown
-can be caused by overfit as well.
-
-It is important to realize that we are not \emph{advocating} linear
-regression for highly overparametrized models. If $K$ is very large
-relative to $T$, researchers will often want to use some form of
-shrinkage forecast, for example the LASSO \citep{Tib:96} or a factor
-model \citep{StW:02,BaN:02}. Our main focus is practical settings
-where $K$ is \emph{moderately} large and it is not clear whether
-overfit will dominate the results. In these settings it is
-crucial to understand the behavior of different evaluation criteria
-when $K$ is large, in case overfit does turn out to be a concern, and to have reliable
-methods for estimating these overfit models' performance. This is the goal of
-this paper.
-
-Our theoretical results partially justify OOS comparisons when
-researchers want to
-choose a model for forecasting.  Although there has been little
-emphasis on hypothesis testing in this setting, testing is usually
-appropriate: there is usually a familiar benchmark model in place, and
-the cost of incorrectly abandoning the benchmark for a less accurate
-alternative model is higher than the cost of incorrectly failing to
-switch to a more accurate alternative.  We show that the DMW test
-lets the forecaster control the probability of the first error, just
-as with conventional hypothesis testing.
-
-But we also identify new practical limitations for applying the DMW
-test to overfit models.
-Since the models' coefficients are imprecisely estimated in the limit,
-the test sample must be small enough that the model estimated over the
-training sample is similar to the one that will be estimated over the
-full sample.  In particular, $P/T \to 0$ is required for consistent
-estimation of the difference in the two models' performance,
-and $P^2/T \to 0$ is required for valid confidence
-intervals and inference.  For larger $P$, the OOS comparisons remain
-asymptotically normal, but are centered on the forecasting performance
-associated with the period $R$ estimates.  In practice, researchers
-typically use large values of $P$, so these studies may be too
-pessimistic about their models' future accuracy if they use the DMW
-test.  Section~\ref{sec:oostheory} lays out the asymptotic behavior of
-the DMW test under this limit theory.
-
-Popular in-sample tests and model selection criteria, like the Wald
-test and the AIC, do not help forecasters in this setting. We show
-that these statistics do not select the more accurate model when
-choosing between overfit models. For many DGPs the Wald test
-will choose the larger model over a small benchmark
-with probability much greater than its nominal size, regardless of
-which model is more accurate, and the AIC behaves similarly. The BIC,
-however, chooses the benchmark model with probability approaching one
-even when the \emph{alternative} model is more accurate.\footnote{%
-  Our result holds for a broad class of full-sample statistics, but
-  there may be other potential statistics that mimic the OOS test and
-  remain valid. Exploring such statistics is left for future
-  research.} %
-This result holds even though modifications of the $F$-test are valid
-under this asymptotic theory, as shown by \citet{BoB:95},
-\citet{AkA:00}, \citet{AkP:04}, \citet{Cal:11c}, and \citet{Ana:12},
-among others.\footnote{%
-  Also see \citet{Efr:86,Efr:04} for a discussion of naive in-sample
-  loss comparisons.} %
-Moreover, under this asymptotic theory, many recent OOS test
-statistics, such as those derived by \cite{ClM:01,ClM:05},
-\citet{Mcc:07}, and \citet{ClW:06,ClW:07} should have the same
-problems as in-sample tests.\footnote{%
-  Our theoretical results apply directly to \citepos{Mcc:07} OOS
-  $t$-test, since it simply proposes more liberal critical values for
-  the same test statistic that we study.  Since \citet{ClW:06,ClW:07}
-  use a finite length estimation window, our asymptotics are
-  incompatible with theirs and prevent us from studying their test
-  directly, as well as \citepos{GiW:06} and other tests based on
-  \citepos{GiW:06} asymptotics.  But \clws\ test can be viewed as a
-  stochastic adjustment to the critical values of the usual \oost\
-  test, so our conclusions should apply informally as well.
-  Specifically, we show that the DMW test rejects with probability
-  equal to nominal size when the estimated benchmark model is expected
-  to be more accurate, so more liberal critical values result in
-  overrejection.} %
-These tests are also designed to reject the benchmark when the
-alternative model is true, and so they may reject too often when the
-benchmark is misspecified but more accurate.  Obviously, since the
-distribution of these statistics converges to the normal when $P/T \to
-0$ (with the number of regressors fixed), these statistics behave like
-the DMW test when $P$ is small, but should overreject the benchmark
-when $P$ is large. Section~\ref{sec:insample} presents our theoretical
-results for full-sample statistics and Section~\ref{sec:mc} presents
-Monte Carlo evidence to support these claims.
-
-Finally, this paper introduces a new method of proof for OOS
-statistics.  We use a coupling argument (Berbee's Lemma, 1979) to show
-that sequences of OOS loss behave like mixingales when the
-underlying series are absolutely regular, even if the forecasts depend
-on non-convergent estimators.  Moreover, we also show that transformations of these
-processes behave like mixingales after they are appropriately recentered, so
-many arguments used to prove asymptotic
-results for Near Epoch Dependent (NED) functions of mixing processes
-can be used for these OOS processes with only slight modification.
-
-The rest of the paper proceeds as follows.
-Section~\ref{sec:assumptions} introduces our notation and assumptions.
-Section~\ref{sec:theory} gives the main theoretical results for the
-DMW OOS test, shows that standard in-sample tests reject the
-benchmark model too often when it is misspecified but more accurate than the
-alternative, and shows that standard model selection methods can run
-into similar problems. Section~\ref{sec:theory} also presents an
-example DGP that illustrates these results. Section~\ref{sec:mc}
-presents a Monte Carlo study supporting our theoretical results.
-Section~\ref{sec:empirics} applies the OOS statistic to
-\citepos{GoW:08} dataset for equity premium prediction, and
-Section~\ref{sec:conclusion} concludes.  Proofs and supporting results
-are listed in the Appendix.
-
-\section{Setup and assumptions}
-\label{sec:assumptions}
-
-The first part of this section will describe the environment in detail
-and set up our models and notation. The second part lists the
-assumptions underlying our theoretical results.
-
-\subsection{Notation and forecasting environment}
-
-We assume the following forecasting environment. There are two
-competing linear models that give forecasts for the target,
-$y_{t+\h}$:
-\begin{equation*}
-y_{t+\h} = x_{1t}'\theta_1 + \e_{1,t+h}, \quad\text{and}\quad
-y_{t+\h} = x_{2t}'\theta_2 + \e_{2,t+h};
-\end{equation*}
-$t = 1,\dots,T-h$, $\h$ is the forecast horizon and the
-variables $y_t$, $x_{1t}$, and $x_{2t}$ are all known in period $t$.
-The coefficients $\theta_1$ and $\theta_2$ minimize the population
-Mean Square Error, so
-\begin{equation*}
-  \theta_i = \argmin_\theta \sum_{t=1}^{T-\h} \E (y_{t+\h} - x_{it}'\theta)^2,
-\end{equation*}
-making $\e_{i,t+\h}$ uncorrelated with $x_{i,t}$; $\e_{i,t+\h}$ can exhibit
-serial correlation so both of the linear models may be misspecified.
-Let $\mathcal{F}_t = \sigma(y_1, x_1, \dots, y_t, x_t)$ be the information
-set available in period $t$,
-with $x_t$ the vector of all stochastic elements of $x_{1t}$ and $x_{2t}$ after
-removing duplicates, and let $\E_t$ and $\var_t$ denote the
-conditional mean and variance given $\mathcal{F}_t$.  The first model
-uses $K_1$ regressors, and the second uses $K_2$.  Without loss of
-generality, assume that $K_1 \leq K_2$. At least one of the models is
-overfit, which we represent asymptotically by letting $K_2$ grow with
-$T$ quickly enough that $\lim K_2/T$ is positive; $K_1$ may grow with
-$T$ as well. Since the models change with $T$, a
-stochastic array underlies all of our asymptotic theory, but we
-suppress that notation to simplify the presentation.
-
-In the settings we are interested in, a forecaster observes the data
-$(y_t,x_t)$ for periods 1 through $T$ and divides these observations
-into an estimation sample of the first $R$ observations and a test
-sample of the remaining $P$ observations. The forecaster then compares
-the models' performance over the test sample, which entails
-constructing two sequences of forecasts with a fixed-window
-estimation strategy,
-\begin{equation*}
-\hat y_{i,t+\h} = x_{it}'\hat{\theta}_{it}, \qquad \text{for } i=1,2;
-\ t = R+1,\dots,T-h,
-\end{equation*}
-where
-\begin{equation*}
-  \bh{it} = \Big(\sum_{s=1}^{R-\h} x_{is}x_{is}'\Big)^{-1} \sum_{s=1}^{R-\h}
-  x_{is} y_{s+\h}, \qquad
-  \text{for } i=1,2;\ t = R+1,\dots, T - \h.\footnote{%
-    It may not be clear why we are using the index $t$ in $\bh{it}$,
-    since $\bh{it} = \bh{iR}$ almost surely for all $t \leq T-h$.
-    But $\bh{it}$ will be defined for $t > T-\h$
-    soon and will not equal $\bh{iR}$ for those values of $t$.} %
-\end{equation*}
-
-The models are then compared by their forecast performance over the test
-sample. There are many statistics that have been considered in the
-literature, but we focus on perhaps the most natural, the DMW \oost\
-test \citep{DiM:95,Wes:96}.\footnote{%
-  The core insights of our paper apply to other OOS statistics as
-  well.} %
-This statistic is based on
-the difference in the models' loss over the test sample, $\oosA$,
-defined as
-\begin{equation*}
-  \oosA \equiv P^{-1} \oosSum{t}{1} D_t
-\end{equation*}
-where
-\begin{equation*}
-  D_t = L(y_{t+\h} - x_{1t}'\bh{1t}) - L(y_{t+\h} - x_{2t}'\bh{2t}),
-\end{equation*}
-and $L$ is a known loss function. The \oost\ test is defined as
-$\sqrt{P} \oosA / \sh$, where $\sh^2$ is an estimator of the
-asymptotic variance of $\oosA$. (Possibly a Heteroskedasticity- and
-Autocorrelation-Consistent, or HAC, estimator.)
-
-Most theoretical research on these statistics, such as \citet{DiM:95}, \citet{Wes:96},
-and \cite{Mcc:07}, has focused on using the \oost\ statistic to test
-hypotheses about the pseudotrue values $\theta_1$ and $\theta_2$.  In
-particular, that research focuses on testing the null hypothesis that
-\begin{equation*}
-  \E L(y_{t+\h} - x_{1t}'\theta_{1}) = \E L(y_{t+\h} - x_{2t}'\theta_{2}).
-\end{equation*}
-But the population quantities in this equation do not determine which
-model is more accurate in practice. The models'
-accuracy will also depend on the specific estimates of $\theta_1$ and
-$\theta_2$ used to produce the forecasts.
-
-When the forecaster will use one of the models to make a number of
-predictions (call it $Q$) in the future, the quantity of interest
-becomes
-\begin{equation*}
-  \E_T \oosB = Q^{-1} \sum_{t=T+1}^{T+Q} \E_T D_t,
-\end{equation*}
-where $D_t$ is defined as before,
-\begin{equation*}
-  D_t = L(y_{t+\h} - x_{1t}'\bh{1t}) - L(y_{t+\h} - x_{2t}'\bh{2t}),
-\end{equation*}
-but now uses the full-sample estimates of the models' parameters,
-\begin{equation*}
-  \bh{it} = \Big(\sum_{s=1}^{T-\h} x_{is}x_{is}'\Big)^{-1} \sum_{s=1}^{T-\h}
-  x_{is} y_{s+\h}, \qquad \text{for } i=1,2;\ t = T+1,\dots, T + Q.
-\end{equation*}
-If $\E_T \oosB$ is positive, the second model is expected to forecast
-better than the first over the next $Q$ periods, and if $\E_T \oosB$
-is negative then the first model is better. We use a conditional
-expectation because the coefficient estimates in $\oosB$ are
-stochastic but known in period $T$, and their values will determine
-the performance of the two models.
-
-Under conventional fixed-$K$ asymptotic theory, $\E_T \oosB$ would
-converge in probability to the difference in the expected loss
-associated with the pseudotrue models,\footnote{%
-  This statement is subject to the usual assumptions: some form of
-  stationarity, bounded moments, and weak dependence.} %
-\begin{equation}\label{eq:22}
-  \E L(y_{t+\h} - x_{1t}'\theta_{1}) - \E L(y_{t+\h} - x_{2t}'\theta_{2}).
-\end{equation}
-But if $K_2$ increases with $T$ these quantities can have different
-limits. For a simple example, assume squared-error loss, let $x_{1,t}
-= 1$ for all $t$, and let $(y_{t+\h},x_{2,t})$ be i.i.d. $N(0,
-\Sigma)$.  Then the difference between $\E_T \oosB$ and
-the in quantity~\eqref{eq:22} is
-\begin{align*}
-  \E_T \oosB - \big(\E L(y_{t+\h} - x_{1t}'\theta_{1}&) - \E L(y_{t+\h} - x_{2t}'\theta_{2})\big) \\
-  &= \big(\E_T (y_{T+\h+1} - \bh{1,T})^2 -
-     \E_T (y_{T+\h+1} - x_{T+1}'\bh{2,T})^2\big) \\
-     &\quad - \big(\E y_{T+\h+1}^2 - \E (y_{T+\h+1} - x_{T+1}'\theta_2)^2 \big)\\
-  &= (\bh{2,t} - \theta_2)' \var(x_{2,t})\, (\bh{2,t} - \theta_2) + o_p(1).
-\end{align*}
-This last term has expectation equal to $\var(y_T) \frac{K_2}{T - K_2 - 1}$ and
-would converge to zero in probability if $K_2$ were fixed, but does not when $\lim
-K_2 / T > 0$. In Section~\ref{sec:oostheory} we show that the \oost\
-statistic can estimate $\E_T \oosB$ under our increasing $K$
-asymptotics and does not estimate the expected loss associated with
-the pseudotrue coefficients.
-
-The conditional expectation $\E_T \oosB$ has been studied heavily in
-cross-sectional settings with independent observations. In such a
-setting, $\E_T \oosB$ is equal to the difference in the models'
-\emph{generalization error}, which has been used widely as a measure
-of model accuracy in the machine
-learning literature \citep[see][for further discussion]{HTF:08}.
-Moreover, with i.i.d. observations, the expectation of $\E_T \oosB$
-equals \citepos{Aka:69} Final Prediction Error (FPE). Both
-generalization error and FPE are defined by a model's
-performance on a new, independent, data set, but, for lack of a better
-term, we will call $\E_T \oosB$ the ``difference in generalization error''
-for the rest of the paper with hopefully no risk of confusion.
-
-Finally, define the following notation.  The $l_v$-norm for vectors in
-$\Re^p$ (with $p$ arbitrary) is denoted $\lvert \cdot \rvert_v$, and
-the $L_v$-norm for $L_v$-integrable random variables is $\lVert \cdot
-\rVert_v$.  The functions $\eigen_i(\cdot)$ take a square-matrix
-argument and return its $i$th eigenvalue (with $\eigen_{i}(A) \leq
-\eigen_{i+1}(A)$ for any matrix $A$).  All limits are taken as $T \to
-\infty$ unless stated otherwise.
-
-\subsection{Assumptions}
-\label{sec:asmp}
-
-The next conditions are assumed to hold throughout the paper.  The first
-assumption controls the dependence of the underlying random array.
-The second lays out the details of our asymptotic approximation.
-The third assumption controls the
-smoothness of the loss function and bounds the moments of the
-difference in the models' performance; the fourth assumption describes
-the behavior of the estimation and test windows.  And the last
-assumption describes the kernel used to estimate the OOS average's
-asymptotic variance.
-
-\begin{asmp}\label{asmp-1}
-  The random array $\{y_t,x_t\}$ is strictly stationary and absolutely regular
-  with coefficients $\beta_j$ of size $-\rho/(\rho-2)$; $\rho$ is
-  greater than two and discussed further in Assumption \ref{asmp-3}.
-\end{asmp}
-
-This assumption is a standard condition on the dependence of the
-underlying stochastic array. The only novelty is that we use
-absolute regularity instead of strong or uniform mixing as our
-weak dependence condition; absolute regularity admits a particular
-coupling argument, \emph{Berbee's Lemma} \citep[reproduced in this
-paper as Lemma A.1 for reference]{Ber:79} that is
-unavailable for strong mixing sequences. Absolute regularity
-implies uniform mixing but is more restrictive than strong mixing,
-so this assumption is not unduly strong.
-For a detailed discussion of these weak dependence conditions,
-please see \citet{Dav:94} or \citet{Dou:94}.
-
-Our strict stationarity assumption is also somewhat stronger than is
-typically used; \citet{Wes:96} and \citet{Mcc:07}, for example,
-present results assuming covariance stationarity of the loss
-associated with the pseudotrue models. We need to make a stronger
-assumption because we will need to prove asymptotic results when the
-$\bh{it}$ remain random---so we would need covariance stationarity to
-hold for almost all estimates of $\theta_i$ and not just for the
-pseudotrue value. The only way to guarantee that condition is to
-assume strict stationarity for the underlying stochastic processes.
-
-The next assumption describes our asymptotic experiment.
-\begin{asmp}\label{asmp-2}
-  The number of regressors for each model, $K_1$ and $K_2$, are less
-  than $R$ and $(K_2-K_0)/T$ is uniformly positive;
-  $K_0$ is the number of regressors shared by the two models ($(K_1 - K_0)/T$
-  may be uniformly positive as well, but is not required to be).
-
-  The variance of $y_{t+\h}$ given $\mathcal{F}_t$ is uniformly
-  positive and finite and all of the eigenvalues of the covariance
-  matrix of $x_t$ are uniformly positive and finite as well.
-  Moreover,
-  \begin{equation}
-    \eigen_{\max}(X_{iS}'X_{iS}) = O_{L_3}(S),
-  \end{equation}
-  \begin{equation}
-    \eigen_{\max}((X_{iS}'X_{iS})^{-1}) = O_{L_3}(1/S),
-  \end{equation}
-  \begin{multline}\label{eq:28}
-    \eigen_{\max}\Bigg(\E\Big(
-    \sum_{s,t=U}^{V-\h} \e_{i,s+\h} \e_{i,t+\h} x_{is}x_{it}'
-    \mBig
-    x_{i1},\dots,x_{i,U-1};
-    \sum_{s=U}^{V-\h} x_{is} x_{is}';
-    x_{i,V-\h+1},\dots,x_{i,T-\h}
-    \Big)\Bigg) \\
-    = O_{L_3}(\max(V-U, K_i)),
-  \end{multline}
-  and
-  \begin{multline}\label{eq:8}
-    \tr \E\Big(
-    \sum_{s,t=U}^{V-\h} \e_{i,s+\h} \e_{i,t+\h} x_{is}x_{it}'
-    \mBig
-    x_{i1},\dots,x_{i,U-1};
-    \sum_{s=U}^{V-\h} x_{is} x_{is}';
-    x_{i,V-\h+1},\dots,x_{i,T-\h}
-    \Big)\Bigg) \\
-    = O_{L_3}((V-U) \times K_i)
-  \end{multline}
-  for large enough $T$, where $S = R,\dots,T$, $1 \leq U \leq V - \h
-  \leq T - \h$, $i = 1,2$,
-  \[ X_{iS} \equiv [x_{i1} \quad \dots \quad x_{i,S-\h}]' \qquad
-  \text{and} \qquad \ep{iS} = (\e_{i,1+\h}, \dots, \e_{i,S})'.\]
-
-  Additionally, the Euclidean norms of the pseudotrue coefficients,
-  $\theta_1$ and $\theta_2$, satisfy $|\theta_1|_2 = O(1)$ and
-  $|\theta_2|_2 = O(1)$.
-\end{asmp}
-
-The assumption on $K_1$ and $K_2$ is crucial to the paper; we assume
-that the model complexity grows with $T$ fast enough to break
-consistency. This assumption is how we derive an asymptotic
-concept of ``overfit.''
-
-The assumption that $y_{t+\h}$ and $x_t$ have positive and finite
-variance is straightforward. The conditions on the eigenvalues are
-technical and control the behavior of the OLS estimator as the number
-of regressors gets large---the third and fourth assumptions are
-nonstandard but can be easily verified under, for example,
-independence. Section~\ref{sec:example} contains such an example. The
-restrictions on the pseudotrue coefficients ensure that the regression
-model doesn't dominate the variance of $y_{t+\h}$ in the limit.
-
-The next assumption establishes moment conditions for the OOS loss
-process and smoothness conditions for the loss function itself. The
-moment conditions are standard and apply to $D_t$, and the smoothness
-conditions are relatively weak.
-
-\begin{asmp}\label{asmp-3}
-  The loss function $L$ is continuous, has finite left and right
-  derivatives, and $L(0) = 0$.  There is a constant $B_L$ and a
-  function $L'$ that bounds the left and right derivative of $L$ at
-  every point such that $\|D_t\|_\rho \leq B_L$; $\|D_t^*\|_\rho \leq
-  B_L$ for all $t$, where
-  \begin{equation}
-    D_t^* = L(y^* - x_1^{*\prime}\hat\theta_{1t})
-    - L(y^* - x_2^{*\prime}\hat\theta_{2t})
-  \end{equation}
-  and $(y^*, x_1^*, x_2^*)$ equals $(y_t, x_{1t}, x_{2t})$ in
-  distribution but is independent of $\mathcal{F}_T$ ($\rho$ is defined
-  in Assumption~\ref{asmp-1}); and
-  \begin{equation}\label{eq:29}
-    \| L'(y^* - x_{i}^{*\prime} (\alpha \bh{iR} + (1-\alpha) \bh{iT})) \|_2
-    \leq B_L
-  \end{equation}
-  for any $\alpha \in [0,1]$.
-\end{asmp}
-
-The differentiability condition in Assumption~\ref{asmp-3} is weak and
-allows the loss function itself to be non-differentiable; for example,
-absolute error and many asymmetric loss functions satisfy this
-assumption. The assumption makes use of both $(y_{t+\h}, x_{1t},
-x_{2t})$ and $(y^*, x_1^*, x_2^*)$ because the period $t$ observations
-can be dependent on $\bh{iT}$ in complicated ways. When the underlying
-observations are independent these assumptions can simplify
-considerably.
-
-The next assumption controls the growth of the test and
-training samples.
-\begin{asmp} \label{asmp-4} (a) $P, R, Q \to\infty$ as $T \to
-  \infty$. (b) $P^2/T \to 0$ and $P/Q \to 0$ as $T \to \infty$.
-\end{asmp}
-
-The requirements that $P$ and $R$ grow with $T$ are common. Parts of
-the assumption are new, in particular the requirement that $P^2/T \to
-0$.  See Lemma~\ref{res-convergence} for a discussion of its
-implications.  In practical terms, this assumption requires that the
-test sample be large and that the training sample be much larger, by
-enough that including or excluding the test sample does not affect the
-estimates of $\theta_1$ or $\theta_2$ very much.
-
-A final assumption restricts the class of variance estimators we will
-consider.  We use the same class of estimators studied by
-\citet{JoD:00} (their class $\mathcal{K}$); see
-their paper for further discussion.
-
-\begin{asmp}
-  \label{asmp-5} $W$ is a kernel from
-$\Re$ to $[-1,1]$ such that $W(0) = 1$, $W(x) = W(-x)$ for all $x$,
-\begin{equation}
-  \int_{-\infty}^{\infty} \lvert W(x) \rvert dx < \infty, \quad
-  \int_{-\infty}^{\infty} \lvert \psi(x) \rvert dx < \infty
-\end{equation}
-with
-\begin{equation}
-  \psi(x) = \frac1{\sqrt{2\pi}} \int_{-\infty}^{\infty} W(z) e^{ixz}dz,
-\end{equation}
-and $W(\cdot)$ is continuous at zero and all but a finite number of
-points.
-\end{asmp}
-
-These assumptions are broadly similar to those existing in the
-literature, with some differences in our assumptions relating the
-estimated coefficients to future values of the DGP.
-Section~\ref{sec:example} contains an extended example that shows how
-these assumptions are satisfied in a simple setting.
-
 \section{Theoretical results}
@@
 
-\subsection{An extended simple example}
-\label{sec:example}
-
-This subsection illustrates the previous theoretical results with a
-concrete example. Let $L(e) = e^2$ and $h = 1$. Suppose that the benchmark is
-nested in the alternative and $(x_{2t}, \e_{2,t+1}) \sim i.i.d.\
-N(0,I)$, and let $y_{t+1} = x_{2t}'\theta_2 + \e_{2,t+1}$
-be the DGP. Also assume that $K_2/T \to c_2$ and $K_1 / T \to c_1 <
-c_2$.
-
-The first part of this subsection shows how the assumptions in
-Section~\ref{sec:asmp} are satisfied and the second part
-demonstrates asymptotic normality of the DMW \oost\ test. The third
-part explicitly shows that $\E_R \oosA$ converges to $\E_T \oosB$ only
-when the test sample is small. And the last part demonstrates that the
-$F$-test does not indicate which model will be more
-accurate in the future, even in this simple example.
-
-\subsubsection*{Fulfillment of Assumptions 1--5}
-
-We will go through the assumptions one by one. The first is
-a condition on the dependence and moments of the process. Since the
-DGP is i.i.d. Normal, these conditions are satisfied trivially.
-
-Assumption~\ref{asmp-2} deals with the design matrix. In this example,
-we directly assume that $K_2$ and $K_1$ grow at the correct rates so
-the the assumption is satisfied. The variance of $y_{t+1}$ given
-$\Fs_t$ is simply the unconditional variance of $\e_{2,t+1}$, which is
-1; and the eigenvalues of $\E x_{2t} x_{2t}$ all equal 1 as well; and
-so they are all uniformly positive and finite as required.
-
-Assumption~\ref{asmp-2} also requires the eigenvalues of $S^{-1}
-X_{iS}'X_{iS}$ to be positive and finite, and for the largest
-eigenvalue of $S^{-1} X_{iS}'X_{iS}$ to be bounded in $L_3$.  These
-results follow from developments in random matrix theory.
-\citet{Gem:80} establishes that the largest eigenvalue of
-$X_{iS}'X_{iS}$ is of order $S + K_i$ and \citet{Joh:01} shows that it
-converges in distribution to the Tracy-Widom law of order 1
-\citep{TrW:96}, which has finite 3rd moments. \citet{Sil:85} and
-\citet{BFP:98} prove similar results for the smallest eigenvalue.
-Assumption~\ref{asmp-2} also requires the largest eigenvalue of
-$(X_{iS}'X_{iS})^{-1}$ be bounded in $L_3$; this should follow from a
-similar argument, but we are unaware of any papers that explicitly
-derive moments for this eigenvalue.
-
-For the conditional expectation of %
-$\sum_{s,t=U}^{V-1} \e_{i,t+1} \e_{i,s+1} x_{i,s} x_{i,t}'$,
-independence implies that
-\begin{equation*}
-  \E\Big(
-  \sum_{s,t=U}^{V-1} \e_{i,s+1} \e_{i,t+1} x_{is}x_{it}'
-  \mBig
-  x_{i1},\dots,x_{i,U-1};
-  \sum_{s=U}^{V-1} x_{is} x_{is}';
-  x_{i,V},\dots,x_{i,T-1}
-  \Big)
-  = \sum_{s=U}^{V-1} x_{is} x_{is}'.
-\end{equation*}
-The largest eigenvalue of this last matrix is of order $K_i + V - U$,
-as discussed, and it has at most $V - U$ nonzero eigenvalues,
-ensuring that both~\eqref{eq:28} and~\eqref{eq:8} hold.
-
-Assumption~\ref{asmp-3} restricts the loss function and the realized
-OOS loss. In this example, we have
-\begin{equation*}
-  D_t^* =^d D_t = (e_{2,t+1} + x_{2t}'\theta_2 - x_{1t}'\bh{1t})^2
-  - (e_{2,t+1} + x_{2t}'(\theta_2 - \bh{2t}))^2
-\end{equation*}
-which has bounded $\rho$th moments by construction. The loss function
-is differentiable and $L'(e) = 2 e$, so \eqref{eq:29} holds as well.
-
-Finally, Assumption~\ref{asmp-4} deals with the choice of test and
-training sample and holds automatically. And Assumption~\ref{asmp-5}
-requires the kernel of the HAC variance estimator to be continuous at
-zero; it is straightforward to construct an estimator that satisfies
-this condition. However, in this section we will use the estimator
-\begin{equation*}
-  \sh^2 = \frac{1}{P} \sum_{t=R+1}^{T-1} (D_t - \oosA)^2
-\end{equation*}
-which does not satisfy Assumption~\ref{asmp-5} but nevertheless is
-consistent for the conditional variance of $\oosA$ because the
-underlying observations are independent.
-
-\subsubsection*{Asymptotic normality of the OOS average, Lemma 1}
-
-This subsection walks through Lemma 1's CLT. Since the observations in
-this example are i.i.d., we do not need to use mixingale theory to
-derive the results, but the OOS process is still affected by the
-estimation error in $\bh{1t}$ and $\bh{2t}$ and has a high degree of
-dependence. This dependence makes the OOS process an MDS, and MDS
-asymptotic theory replaces mixingale theory in this example.
-
-By construction, we have
-\begin{equation*}
-  D_t =
-  \begin{cases}
-    2 \e_{t+1} (x_{2t}'\bh{2R} - x_{1t}'\bh{1R})
-    + (x_{2t}'\theta_2 - x_{1t}'\bh{1R})^2
-    - (x_{2t}'\theta_2 - x_{2t}'\bh{2R})^2
-    & \text{if } t < T \\
-    2 \e_{t+1} (x_{2t}'\bh{2T} - x_{1t}'\bh{1T})
-    + (x_{2t}'\theta_2 - x_{1t}'\bh{1T})^2
-    - (x_{2t}'\theta_2 - x_{2t}'\bh{2T})^2
-    & \text{if } t > T
-  \end{cases}
-\end{equation*}
-and so we can explicitly derive the components of
-Lemma~\ref{res-mixingale}. First,
-\begin{multline*}
-  D_t - \E_R D_t
-  = 2 \e_{t+1} (x_{2t}'\bh{2R} - x_{1t}'\bh{1R})
-  + \Big\{(x_{2t}'\theta_2 - x_{1t}'\bh{1R})^2
-          - \E_R (x_{2t}'\theta_2 - x_{1t}'\bh{1R})^2 \Big\} \\
-  - \Big\{(x_{2t}'\theta_2 - x_{2t}'\bh{2R})^2
-          - \E_R (x_{2t}'\theta_2 - x_{2t}'\bh{2R})^2 \Big\}
-\end{multline*}
-for $t < T$. Since the underlying observations are i.i.d., $\E_{t-1}
-D_t = \E_R D_t$ a.s.\ and consequently $\{D_t - \E_R D_t, \Fs_{t};
-t=R+1,\dots,T-1\}$ is an MDS.
-
-Although transformations of $D_t - \E_R D_t$ will obviously not be
-MDSes in general, it should be clear that transformations of $D_t$
-will be MDSes after subtracting their conditional mean; i.e.
-\begin{equation*}
-  \{g(D_t) - \E_R g(D_t); \Fs_t; t = R+1,\dots,T-1\}
-\end{equation*}
-is an MDS as long as
-$g(D_t)$ has finite mean, but $g(D_t - \E_R D_t)$ is not. This MDS
-result holds because $x_t$ and $y_{t+1}$ are independent of $\bh{1R}$
-and $\bh{2R}$, so
-\begin{equation*}\begin{split}
-  \E_R g(D_t)
-  &= \int g\Big((x_1'\bh{1R})^2 - (x_2'\bh{2R})^2
-       + 2 y (x'\bh{2R} - x'\bh{1R})\Big) \, f(y, x) \, dx \, dy \\
-  &= \E_{t-1} g(D_t)
-\end{split}\end{equation*}
-a.s., where $f$ is the density of $(y_{t+1}, x_{2t})$ and $x_1$
-denotes the first $K_1$ elements of $x$. This result parallels our
-results for mixingales in the general case.
-
-As a result, $\oosA$ and $(1/P) \sum_{t=R+1}^{T-1} D_t^2$ both obey
-LLNs: $\oosA \to^p \E_R \oosA$ and
-\begin{equation*}
-  (1/P) \sum_{t=R+1}^{T-1} D_t^2 \to^p \E_R D_T^2.
-\end{equation*}
-Moreover, these convergence results imply that $\sh^2 - \var_R
-\sqrt{P} \oosA \to^p 0$. And so
-\begin{equation*}
-  \sqrt{P} \oosA/\sh \to N(0,1)
-\end{equation*}
-by the MDS CLT.
-
-\subsubsection*{Convergence of $\E_R \oosA$ to $\E_T \oosB$, Lemma 2}
-
-This subsection works through Lemma~\ref{res-convergence}. In this
-example, the difference between $\E_R \oosA$ and $\E_T \oosB$ equals
-\begin{equation*}
-  \begin{split}
-    \E_R \oosA - \E_T \oosB &= \Big\{(\bh{1R} - \theta_1)'(\bh{1R} -
-    \theta_1) -
-    (\bh{2R} - \theta_2)'(\bh{2R} - \theta_2)\Big\} \\
-    & \quad - \Big\{(\bh{1T} - \theta_1)'(\bh{1T} - \theta_1) -
-    (\bh{2T} - \theta_2)'(\bh{2T} - \theta_2)\Big\} \\
-    &\begin{split}
-      =\ep{T}'\Big\{
-      & \tilde{X}_{1R}(X_{1R}'X_{1R})^{-2} \tilde{X}_{1R}'
-      - X_{1T}(X_{1T}'X_{1T})^{-2} X_{1T}' \\
-      & - \tilde{X}_{2R}(X_{2R}'X_{2R})^{-2} \tilde{X}_{2R}'
-      + X_{2T}(X_{2T}'X_{2T})^{-2} X_{2T}'
-      \Big\}\ep{T}.
-    \end{split}
-  \end{split}
-\end{equation*}
-with $\tilde{X}_{iR}$ the $T \times K_i$ matrix $[X_{iR}'\ 0]'$. This
-last term is a quadratic form and the regressors and errors are
-assumed to be normal, so we can find the rate that the difference
-converges to zero in probability by calculating its first two moments.
-
-The mean difference is
-\begin{equation*}
-  \begin{split}
-  \E(\E_R \oosA - \E_T \oosB)
-      &=O\Big(\max_i \E \tr \big\{
-        \tilde{X}_{iR}(X_{iR}'X_{iR})^{-2} \tilde{X}_{iR}
-        - X_{iT}(X_{iT}'X_{iT})^{-2} X_{iT} \big\} \Big) \\
-      &=O\Big(\max_i \tr \big\{\E (X_{1R}'X_{1R})^{-1}
-         - \E (X_{1T}'X_{1T})^{-1} \big\}\Big) \\
-      &=O( K_1 P / (R-K_1)(T-K_1)) \\
-      &=O(P/T)
-    \end{split}
-\end{equation*}
-The first equality follows from the expectation of a quadratic form,
-the second from routine manipulations of the trace operator, and the
-third from the moments of the inverse Wishart distribution.
-
-Similarly, the variance of the difference is
-\begin{align*}
-  \var(\E_R & \oosA - \E_T \oosB) \\ &=
-  O\Big(\max_i \E\big[\tr((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1})\big]^2
-  + 2 \tr \E\big((X_{iR}'X_{iR})^{-2} - (X_{iT}'X_{iT})^{-2}\big) \\
-  &\qquad - \big[\tr \E((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}) \big]^2 \Big)\\
-  &= O(P/T)^2.
-\end{align*}
-So, in this example, $P^{1/2}(\E_R \oosA - \E_T \oosB) \to^p 0$
-if $P^3/T^2 \to 0$, which is slightly weaker than the general
-requirement that $P^2/T \to 0$.  If $\lim P^3/T^2 > 0$ the OOS average
-still obeys the MDS CLT, but it is not centered correctly at $\E_T
-\oosB$.
-
-\subsubsection*{Behavior of the F-test}
-
-This part illustrates the behavior of full-sample statistics in our
-simple example. To simplify the presentation even more, assume that
-the full-sample design matrix is orthogonal in-sample, not just in
-population, so $X_{2T}'X_{2T} = T \cdot I_{K_2 \times K_2}$, and again
-let $M_1$ and $M_2$ be the selection matrices for the first $K_1$ and
-the last $K_2-K_1$ elements of $\theta_2$. In this example,
-\begin{equation*}
-  M_2 \bh{2T} \sim
-  N(M_2 \theta_2, (1/T) \, I_{K_2-K_1})
-\end{equation*}
-and, conditional on $\E_T \oosB = 0$, the density of $M_2 \bh{2T}$
-concentrates uniformly on the surface of the sphere centered at $M_2
-\theta_2$ and passing through the origin:
-\begin{equation*}
-  (M_2 \bh{2T} - M_2 \theta_2)'(M_2 \bh{2T} - M_2 \theta_2) =
-  \theta_2'M_2' M_2 \theta_2.
-\end{equation*}
-To see intuitively that it must pass through the origin, note that the
-two models will give identical forecasts when $\bh{2T} = 0$ since the
-regressors are orthogonal. (Identical forecasts obviously have the
-same MSE.)
-
-This region is a cylinder in the original space, $\Re^{K_2}$.  We can
-also represent the null $\E_T \oosB \leq 0$ by conditioning on $\E_T
-\oosB = -d$ for a fixed positive constant $c$. In that case, the
-density of $M_2 \bh{2T}$ concentrates on the sphere
-\begin{equation*}
-  (M_2 \bh{2T} - M_2 \theta_2)'(M_2 \bh{2T} - M_2 \theta_2) =
-  \theta_2'M_2' M_2 \theta_2 + d
-\end{equation*}
-which has the same center but larger radius.
-
-For the $F$-test we have, as before,
-\begin{equation*}
-  F = \tfrac{T}{s^2 (K_2 - K_1)} \bh{2T}' M_2' M_2 \bh{2T}.
-\end{equation*}
-We know that $\sqrt{T}(F - 1)$ is asymptotically normal since its
-numerator is Chi-squared with $K_2-K_1$ degrees of freedom and obeys a
-CLT.  The test accepts if
-\begin{equation}\label{eq:26}
-  \tfrac{T}{s^2 (K_2 - K_1)} \bh{2T}' M_2' M_2 \bh{2T}
-  \leq 1 + \delta / \sqrt{T},
-\end{equation}
-where $\delta$ is chosen to determine the size of the test. In other
-words, the test accepts if $M_2 \bh{2T}$ falls in the sphere centered
-at the origin with radius $s ((K_2 - K_1) / T)^{1/2} +
-O_p(1/\sqrt{T})$.
-
-\input{floats/circles}
-\begin{figure}
-  \centering
-  \begin{tabular}{cc}
-  \subfloat[]{\circlefigA{1}{2.5}{1.4}{4.5}\label{fig:circleA}} &
-  \subfloat[]{\circlefigB{1}{2.5}{1.4}{4.5}\label{fig:circleB}}
-  \end{tabular}
-  \caption{Graphs indicating the rejection region and region of equal
-    generalization error for the models discussed in Section
-    \ref{sec:insample}.  The smaller model has no estimated parameters
-    and the larger has two coefficients.  The shaded regions in
-    Figures (a) and (b) show the rejection region and the acceptance
-    region respectively of the full-sample test given $\E_T \oosB \leq
-    0$. Here $e_1 = (1,0)$ and $e_2 = (0,1)$ are the first and second
-    selection vectors, so the horizontal axes represent changes in the
-    first unique element of $\bh{2T}$ and the vertical axes represent
-    changes in the second unique element.}
-\label{fig:rreject}
-\end{figure}
-
-This is perhaps best illustrated with a picture.
-Figure~\ref{fig:rreject} plots these quantities when $K_2 - K_1 =
-2$. The circle centered at the origin plots the threshold for the
-$F$-test; when $M_2 \bh{iT}$ falls outside this circle, the $F$-test
-rejects. The circle centered at $M_2 \theta_2$ plots the set of points
-for which $\E_T \oosB = 0$. The shaded region in
-Figure~\ref{fig:rreject}~(a) plots the rejection region given $\E_T
-\oosB \leq 0$ and the shaded region in Figure~\ref{fig:rreject}~(b)
-plots the acceptance region given $\E_T \oosB \leq 0$.
-
-In the picture, the true coefficients $\theta_2$ satisfy
-\begin{equation*}
-\theta_2'M_2'M_2\theta_2 > \var(\e_t)^{1/2} ((K_2 - K_1) / T)^{1/2}
-\end{equation*}
-so the center of the conditional distribution of $\bh{2T}$ given $\E_T
-\oosB \leq 0$ is outside the acceptance region of the $F$-test. When
-this is the case, the conditional probability that $\bh{2T}$ falls in
-the rejection region is less than 1/2, since $M_2 \bh{2T}$ is
-uniformly distributed on the cylinder
-\begin{equation*}
-  (M_2 \bh{2T} - M_2 \theta_2)'(M_2 \bh{2T} - M_2 \theta_2) =
-  \theta_2'M_2' M_2 \theta_2 + d
-\end{equation*}
-for some positive $d$.
-
-The AIC behaves essentially the same way. For the BIC, the radius of
-the cylinder centered at the origin increases with $T$ and eventually
-encompasses the cylinder centered at $M_2 \theta_2$, so it never
-selects the alternative once $T$ is large enough.
-\section{Monte Carlo}
-\label{sec:mc}
-
-This section presents two simulations that investigate the accuracy of
-our theory in small samples.
-We do several Monte Carlo exercises. The first looks at whether our
-theoretical results for the OOS average are accurate: whether or not
-the OOS average is approximately normal, and whether it is centered on
-$\E_R \oosA$, $\E_T \oosB$, or somewhere else entirely. The second
-issue is whether or not the \oost\ test is \emph{useful} for
-conducting inference about $\E_T \oosB$. Our theoretical results
-suggest that it may not be, because we require $P^2/T \to 0$ for
-inference about $\E_T \oosB$ to be valid. A highly related issue is
-whether other statistics are useful for conducting inference about
-$\E_T \oosB$---again, our theoretical results suggest that they are
-not.
-
-We use the same DGP for all of these simulations, and it is described
-in the next subsection. Results are presented in the subsection after
-that. Simulations were conducted in R \citep{Rde:10} using the
-\emph{MASS} \citep{VeR:02}, \emph{Matrix} \citep{BM:13}, and
-\emph{rlecuyer} \citep{SR:12} and graphs are produced using
-\emph{Lattice} \citep{Sar:10}. In this paper, we present results for
-the fixed window, but recursive window results are available in a
-separate Appendix and are similar.
-
-\subsection{Setup}
-\label{sec:simulation-design}
-
-The Monte Carlo experiment is intentionally very simple so that we can
-isolate the influence of the models' complexity.  In particular, we do
-not include some features that are common in forecasting
-environments---serial dependence, heteroskedasticity, and complicated
-DGPs. The DGP we use is given by the equation
-\begin{equation}\label{eq:6}
-  y_t = x_t'\theta + \e_t,\quad \e_t \sim N(0,1),
-  \quad t=1,\dots,T.
-\end{equation}
-The first element of $x_t$ is 1 and the remaining $K_2-1$ elements are
-independent Standard Normal.  The benchmark model is
-\begin{equation}
-  \label{eq:1}
-  y_{1t} = \sum_{j=1}^{K_1} x_{jt}\theta_j + \e_t
-\end{equation}
-and the alternative model is the DGP \eqref{eq:6}.  We let
-$(K_1,K_2)$ equal either $(2,3)$ or $(T/20,T/10)$ to study our theory
-in its intended application as well as for more parsimonious models.
-We let $T$ equal 100, 250, or 500.  We also vary $\theta$, and do
-so giving the benchmark and the alternative model comparable weight in
-predicting $y_t$.  Specifically, we set
-\begin{equation*}
-  \theta_j =
-\begin{cases} \frac{c}{\sqrt{K_1}} & j = 1,\dots,K_1 \\
-\frac{c}{\sqrt{K_2 - K_1}} & j = K_1 + 1,\dots,K_2 \end{cases}
-\end{equation*}
-with $c$ equal to zero or one.  When $c$ is one, we're more likely to
-draw values of $X$ and $Y$ that make the estimated larger model more
-accurate than the benchmark, and when $c$ is zero we're unlikely to
-draw such values of $X$ and $Y$.  For all of the studies, $L(e) =
-e^2$.
-
-To study the accuracy of our theoretical approximations, we first
-estimate the coverage probabilities of OOS confidence intervals for
-$\E_R \oosA$ and $\E_T \oosB$. For each draw of $X$ and $Y$, we
-construct the one-sided OOS interval defined in
-Theorem~\ref{res:oostest}:
-\begin{equation*}
-  [ \oosA - 1.28 \hat{\sigma}, \infty) \quad\text{with}\quad
-  \sh^2 = \frac1P \sum_{t=R+1}^T (D_t - \oosA)^{2}
-\end{equation*}
-for $P = 10,\dots,2T/3$; we then calculate the percentage of
-simulations where these intervals contain $\E_R \oosA$ and the
-percentage that contain $\E_T \oosB$.  Since the data are i.i.d., both
-of these quantities are easy to calculate (see
-Section~\ref{sec:example}). For these calculations, we draw 2000
-samples for each combination of the design parameters.
-
-Our second set of results studies whether these different OOS and
-in-sample statistics are valid for testing the null hypothesis
-\begin{equation*}
-  H_0:\quad E_T \oosB \leq 0,
-\end{equation*}
-namely that the benchmark model is expected to be more accurate in the
-future than the alternative. Informally, we are interested in whether
-the conditional probability
-\begin{equation*}
-  \Pr[\text{test rejects} \mid E_T \oosB \leq 0] \leq \alpha
-\end{equation*}
-where $\alpha$ is the nominal size of the test. If this inequality
-does not hold, the test statistic is rejecting the benchmark model too
-often.
-
-We look at four different statistics---the full-sample $F$-test, the
-DMW $t$-test, the OOS $t$-test using McCracken's (2007) critical
-values,\footnote{%
-  These critical values are not published for $K_2-K_1>10$, so we do
-  not report them for $K_2 = T/10$.} %
-and Clark and West's (2006, 2007) Gaussian out-of-sample
-statistic.\footnote{%
-  Clark and West (2006, 2007) derive their statistic using the rolling
-  window estimation scheme. Here we use the same statistic, but with a
-  fixed window scheme. A supplemental appendix presents results for
-  their statistic, using the recursive window.} %
-For the $F$-test, we simply test whether the coefficients on the
-larger model are nonzero.  For the out-of-sample tests, we conduct a
-one-sided test of out-of-sample performance for every value of $P$ as
-before. For each of these simulations, we discard draws from the DGP
-that violate the null hypothesis $E_T \oosB \leq 0$ and then use the
-remaining samples to calculate the conditional probability that each
-test rejects. The simulations end when 2000 draws have been retained
-for each choice of the design parameters.
-
-\subsection{Results}
-
-We discuss results for the confidence intervals first.
-Figures~\ref{fig:interval-R} and~\ref{fig:interval-T} show the
-coverage probability of these intervals as a function of $P$ for each
-combination of $T$, $K_1$ and $K_2$, and $c$.  The nominal coverage is
-90\% and is represented with a gray horizontal line. Each panel
-displays the coverage for a different choice of design parameters.
-
-Figure~\ref{fig:interval-R} gives the results for $\E_R \oosA$.  The
-actual coverage is very close to the nominal coverage except when $P$
-is very small.  The poor behavior for small $P$ is unsurprising, as it
-simply means that the CLT is a poor approximation when the test sample
-is small. The interval for $T = 100$, $K = T/10$, and $c = 0$ is the
-worst, with actual coverage near 85\% for most values of $P/T$. But
-the others are much closer to nominal coverage, even for the
-parsimonious models ($K_1=1$ and $K_2= 3$) where one might expect
-the theoretical results to break down.
-
-Figure~\ref{fig:interval-T} gives the results for $\E_T \oosB$.  In
-columns 2 and 4---the overfit models---the coverage is near nominal
-coverage for moderately small values of $P$.  As $P$ increases to
-$2T/3$, the coverage increases above nominal size; near 100\% for some
-DGPs.  With the parsimonious model, the coverage is near nominal
-coverage for all $P$ for the one-sided interval with $c=1$, but only
-for moderately small $P$ when $c=0$.
-
-The behavior for $K_2 = T/10$ is exactly what our theory predicts.
-When $P^2/T$ is small, the coverage is close to nominal levels.  The
-behavior as $P$ increases, combined with the results for $\E_R \oosA$,
-indicate that typically $\E_T \oosB \geq E_R \oosA$.  Since
-\begin{equation*}
-  E_{T} \oosB = E_{R} \oosA + (E_{T} \oosB - E_{R} \oosA),
-\end{equation*}
-and the interval is approximately centered at $\E_R \oosA$, the
-difference $\E_{T} \oosB - E_{R} \oosA$ adds a substantial positive
-quantity when $P^2/T$ is not near zero, increasing the coverage of the
-one-sided interval.
-
-We present the size simulations next, in
-Figures~\ref{fig:ftest}--\ref{fig:ttest-power}.  For the OOS tests
-we plot each OOS test's conditional rejection probability,
-\begin{equation*}
-  \Pr[\text{test rejects} \mid E_T \oosB \leq 0],
-\end{equation*}
-for each combination of $T$, $K_1$, $K_2$, and $c$ as a function of
-$P$.  The $F$-test does not depend on $P$, so we calculate and
-tabulate it's conditional rejection probability as a single value for
-each combination of design parameters.
-
-Table~\ref{fig:ftest} summarizes the simulation results for the
-$F$-test. For $c = 0$, the estimated conditional rejection probability
-is almost exactly equal to the test's nominal size (10\%), which is
-unsurprising.  For $c = 0$, the $F$-test is exact; moreover, the
-larger model will almost always be less accurate than the smaller one,
-so conditioning on $\E_T \oosB \leq 0$ is almost unrestrictive.  When
-$c$ increases, though, the $F$-test overrejects badly---rejecting at
-roughly 50\% when $c = 1$ for the parsimonious model and from 70\% to
-100\% for the overfit model. This agrees with our
-Section~\ref{sec:insample} results and matches results seen in
-empirical practice: the $F$-test rejects the benchmark with very high
-probability, even though it is, by construction, more accurate than
-the alternative model.
-
-Figure~\ref{fig:ttest-size} presents the size estimates for the DMW
-\oost\ test.  Again, different panels display results for different
-combinations of the design parameters.  Each graph plots the rejection
-probability against $P/T$.  For $K/T=10$, the rejection probability
-falls as $P/T$ increases, from near nominal size when $P/T$ is small
-to zero when $P/T$ is near $2/3$.  Moreover, the rejection probability
-falls faster when $T$ is large, as our theory predicts.  When $K=3$,
-the rejection probability stays closer to nominal size, but falls with
-$P/T$ for $c=0$, under-rejecting by about 5pp when $P/T = 2/3$, and
-rises with $P/T$ for $c=1$, overrejecting by about 10pp when
-$P/T=2/3$.  For small $P$, the rejection probability is near 10\% for
-all simulations (the farthest is $K=T/10$, $c=0$, where the rejection
-probability is about 5\%; the other simulations are much closer).
-
-We observe the following patterns.  The
-DMW test has close to nominal size when $P$ is small for every
-combination of design parameters.  In most cases, the rejection
-probability decreases as $P/T$ increases---the exception is for $K_2 =
-3$ and $c=1$.  For the large-$K$ simulations, the rejection
-probability drops to zero for most of the simulations as $P/T$
-increases.  The rejection probability increases with $c$, but the
-rejection probability still is near nominal probability for small $P$
-with $c=1$.
-
-Clark and West's (2006, 2007) statistic, presented in
-Figure~\ref{fig:clarkwest}, behaves quite differently.  For $c=0$ the
-test is correctly sized for both the overfit and parsimonious studies,
-as we saw for the $F$-test.  When $c=1$, the rejection probability
-increases rapidly with $P/T$.  For $K_2=3$, the rejection probability
-is near 10\% when $P$ is small but about 40\% when $P/T = 2/3$.  For
-$K=T/10$, the rejection probability is even higher and increases with
-$T$ as well, from a maximum over 50\% when $T=100$ to a maximum of
-nearly 100\% when $T=1000$.
-
-Results using \citepos{Mcc:07} critical values are presented in
-Figure~\ref{fig:mccracken} and are similar to those using Clark and
-West's test.  For $c=0$ the rejection probability is nearly the test's
-nominal size.  For $c=1$, the rejection probability increases with
-$P/T$, from close to the nominal size when $P/T$ is small to over 25\%
-when $P/T = 2/3$.  Note that all of the simulations use the
-parsimonious model.  McCracken's statistic overrejects here by
-slightly less than Clark and West's, but still by a substantial
-amount. Note that we are unable to plot results for McCracken's
-statistic when $K/T = 10$, which is where the breakdown in Clark and
-West's test is most pronounced.
-
-Since the DMW test tends to have low rejection probability, the test's
-power is a concern.  Figure~\ref{fig:ttest-power} power results for
-the DMW test, simulating from \eqref{eq:1} with $c = 1$ or 2 subject
-to the constraint that $\E_T \oosB > 0$.\footnote{%
-  Draws of $X$ and $Y$ with $\E_T \oosB > 0$ are very rare when $c=0$,
-  so we do not present results for that value of $c$.} %
-Since the other test statistics greatly overreject, we do not present
-their power.  For $c=1$, the power is never greater than nominal size
-and decreases to zero as $P/T$ increases for the overfit model.  For
-$c=2$ the power is better, increasing with $P/T$ at first stretch and
-then decreasing as $P/T$ grows beyond approximately 1/4 for the
-overfit model.  Larger values of $T$ give a higher peak and greater
-power overall, but the power still falls to nearly zero if $P/T$ is
-too large (approximately 2/3 in our simulations).  The power with the
-parsimonious model is typically quite low but greater than nominal
-size for $c = 2$.
-
-Both sets of simulations support our theoretical results.  The first
-simulation confirms that the DMW OOS $t$-test is centered at $\E_R
-\oosA$ for all choices of $P$ and $R$ and is centered on $\E_T \oosB$
-only when $P$ is small.  The second simulation confirms that the DMW
-test has correct size for the null hypothesis that $\E_T \oosB \leq 0$
-when $P$ is small and that tests designed to test whether the
-benchmark is true, like the $F$-test and Clark and West's (2006, 2007)
-and McCracken's (2007) OOS tests can reject by much more than their
-nominal size when testing the null $\E_T \oosB \leq 0$.  Moreover,
-these simulations demonstrate that the restriction that $P$ be small
-is binding in practice, as the DMW test under-rejects and has very low
-power when $P$ is too large.
-
-\section{Empirical analysis of equity premium predictability}
-\label{sec:empirics}
-
-This section presents a study of equity premium predictability based
-on \citet{GoW:08}. Goyal and Welch conduct an out of sample analysis
-of 18 different variables thought, based on previous research, to
-predict the equity premium (calculated as the difference between the
-return on the S\&P 500 index and the T-bill rate).\footnote{%
-  \citet{GoW:08} builds on previous research by \citet{BoH:99} and
-  \cite{GoW:03}.} %
-Their analysis has two notable features: Goyal and Welch compare different
-predictors across the same time periods and frequency as much as
-possible, making the accuracy of these predictors directly comparable;
-many of the papers that originally proposed these predictors used
-different time periods, methods, or observational frequencies so their
-results were not directly comparable. And Goyal and Welch compare
-these predictors out-of-sample; many of the original studies found
-in-sample evidence of equity premium predictability but did not look
-at out-of-sample evidence.
-
-Goyal and Welch consider many different models; most of them are very
-simple---regression onto a constant and a single stochastic
-predictor---but some are more complicated. They find that essentially
-none of the models outperform a simple benchmark, the prevailing mean
-of the equity premium, and conclude that these variables do not
-predict the equity premium. A large literature has subsequently sought
-to explain or rebut these results, including several responses to
-Goyal and Welch's original working paper published in the same special
-issue of \textit{The Review of Financial Studies} as
-\citet{GoW:08}.\footnote{%
-  Those papers are \citet{CaT:08}, \citet{Coc:08}, \citet{BRW:08}, and
-  \citet{LeN:08}.} %
-
-\citet{GoW:08}, as well as \citet{BoH:99}, \citet{LeN:08}, and many
-other authors, propose that instability could explain the OOS failure
-of these models. However, we have shown in this paper that overfit can
-also explain this pattern, significant in-sample results that do not
-hold up out of sample. In this section, we explore the extent to which
-overfit is a potential concern in this data set and estimate the
-expected forecasting performance of the largest model they consider, a
-model with 13 regressors, using 81 observations (annual data from 1928
-to 2009). The predictors are listed in Table~\ref{tab:equity}; please
-see Goyal and Welch's original paper for detailed information about
-these variables.\footnote{%
-  Table~\ref{tab:equity} only lists the variables used in
-  \citepos{GoW:08} ``kitchen sink'' model.  Some of the variables that
-  they use are excluded from this model either because the series are
-  too short or because the variables are linear combinations of other
-  variables.} %
-
-\citet{GoW:08} focus primarily on univariate regression models of the
-form
-\[
-r_{t+1} = \beta_0 + \beta_1 x_{it} + \e_{t+1}
-\]
-using OLS with a recursive window, where $r_{t+1}$ is the equity
-premium and $x_{it}$ is one of the predictors listed in
-Table~\ref{tab:equity}.
-This focus is consistent with much of the rest of the literature. But
-it is not clear that this approach---using a large number of
-restricted models---is any more reliable than using a single, large
-model. Very few papers in the equity-premium predictability literature
-explicitly account for the multiplicity of model comparisons\footnote{%
-  \citet{RaW:06}, \citet{RaZ:12}, and \citet{Cal:15} are
-  exceptions.} %
-and most widely-used statistics for multiple comparisons are
-derived under the assumption that there is a finite number of
-hypotheses or models (as is the case in \citealp{STW:99c},
-\citealp{Whi:00}, \citealp{Han:05}, and \citealp{LeR:05}), so there is
-little theoretical evidence that they are any more reliable than a
-regression model that encompasses all of the smaller models. Moreover,
-since \citet{GoW:08} (along with most of the rest of the literature)
-want to interpret these univariate regressions as meaningful
-statements about the true relationships between the equity premium and
-the regressors, omitted variable bias is a serious potential issue.
-
-For example, Table~\ref{tab:gwinsample} presents two full-sample
-coefficient estimates for each of the 12 predictors we
-consider.\footnote{%
-  For all of our full sample results, we studentize the
-  regressors to make it easier to compare coefficient estimates and we
-  express the equity premium in basis points.} %
-The first column is the estimator of the coefficient on the
-variable in the full regression,
-\begin{equation*}
-  r_{t+1} = \beta_0 + \sum_{i=1}^{12} \beta_{i} x_{it} + \e_{t+1},
-\end{equation*}
-and the third column is the $p$-value associated with a two-sided
-$t$-test that the coefficient is zero in population. The second column
-is the estimator of the coefficient from the univariate regression
-\begin{equation*}
-  r_{t+1} = \alpha_i + \gamma_{i} x_{it} + \e_{t+1},
-\end{equation*}
-and the fourth column is the $p$-value associated with its
-$t$-test.\footnote{%
-  All of the standard errors were calculated using a Newey-West kernel
-  with two lags.} %
-Some of the coefficient estimates agree, but some do not. The
-coefficient estimate for the \emph{default yield spread}, for example,
-is substantially and significantly negative in the full model ($-7.79$
-with $p$-value $0.042$), but is near zero in the univariate regression
-($0.79$ with $p$-value $0.720$). This pair of results implies that the
-the default yield spread contains information about the equity premium
-but is also correlated with other poor predictors, and that this
-additional correlation adds noise to the univariate regression
-and masks the true relationship. Similarly, \emph{net equity expansion}
-is significant at 10\% in the univariate regression but not in the
-full model ($p$-values of $0.060$ and $0.626$ respectively), which is
-likely attributable to omitted variable bias. So there is merit to
-studying a large model that includes all of the variables.
-
-Results for the full sample estimates of these models are in
-Table~\ref{tab:gwinsample}.\footnote{%
-  Calculations in this section are done in R \citep{Rde:10} using the
-  \emph{lmtest} \citep{ZeH:02} and \emph{sandwich} \citep{Zei:04}
-  packages.}\footnote{%
-  We compare the test statistic to critical values from the
-  $F$-distribution, which have been shown to be more reliable than
-  Chi-squared critical values when there are many regressors
-  \citep{Ana:12,Cal:11c}.} %
-The last rows of the table list measures of the full-model fit.  The
-$p$-value for the test of full model fit is very small (less than
-0.01), indicating that some of the coefficients are nonzero in
-population and at least one of these predictors is correlated with the
-equity premium.\footnote{%
-  We have done additional analysis to try to identify which predictors
-  were correlated with the equity premium, but none of the individual
-  regressors were significant after correcting for multiplicity. The
-  Bonferroni correction, for example, suggests that an individual
-  $p$-value would need to be less than $0.10/12 \approx 0.0083$ for
-  its corresponding coefficient to be significant at the 10\% level,
-  but the smallest $p$-value is $0.035$. One can improve on the
-  Bonferroni correction, of course, but a comprehensive analysis is
-  beyond the scope of this paper.} %
-As we argue throughout the paper, this result does not imply that the
-model will forecast well.
-
-To determine whether the full model can forecast well, we use the DMW
-\oost\ test to compare it to a sample mean benchmark,
-\begin{equation*}
-r_{t+1} = \mu + \e_{1,t+1}.
-\end{equation*}
-Both models are estimated by OLS using the fixed-window scheme. We
-also present results for a restricted model proposed by
-\citet{CaT:08} that imposes that $\hat r_{t+1}$ be non-negative for
-each forecast.
-To study the effect of the training sample size on the DMW statistic, we
-calculate the one-sided confidence interval for $\E_T \oosB$ given
-by \eqref{interval-greater} corresponding to the null and alternative
-hypotheses
-\[ H_0: \quad E_T \oosB \leq 0 \qquad
-H_A: \quad E_T \oosB > 0
-\]
-using the fixed-window scheme for each value of $R$ between 20 and
-$T-10$. The standard deviation is estimated using a Newey-West
-estimator with $\lfloor P^{1/4}\rfloor$ lags.  For small values of
-$R$, the OOS average is expected to underestimate the performance of
-the larger model relative to the smaller, but this may not hold in
-this particular dataset. For the OOS results, we express the equity
-premium in percentage points.
-
-Figure~\ref{fig:empirics1} plots the OLS results and
-Figure~\ref{fig:empirics2} imposes \citepos{CaT:08} restriction. The
-solid line in each figure shows the OOS average, $\oosA$, and the
-shaded region indicates the 95\% one-sided confidence interval implied
-by the DMW test.  Negative numbers indicate that the full model has
-higher out-of-sample loss.  We can see that the same patterns hold for
-both models: the performance difference decreases as $R$ grows, but
-the full model is never more accurate.  We also see that the
-performance difference decreases suddenly over the period $R=29$ to
-$R=34$ (corresponding to the years 1956--1961).
-Figure~\ref{fig:empirics3} plots the accuracy of the individual
-forecasts (only for the linear models) and shows that this change is
-the result of a sudden improvement in the full model.  This change may
-indicate instability in the underlying relationship, as proposed by
-\citet{GoW:08}.
-
-In summary, we fail to reject the null that the benchmark prevailing
-mean model is more accurate than the full model including all of
-\citepos{GoW:08} predictors.  This result is consistent with Goyal and
-Welch's original analysis.  Unlike Goyal and Welch, we attribute this
-result, at least in part, to parameter uncertainty---the full sample
-results indicate that there is a true predictive relationship between
-some of these variables and the equity premium and the larger model
-could predict better than the benchmark with enough data.\footnote{%
-  \citet{BWB:10} make a similar point about exchange rate models, but
-  see also \citet{Chi:10} and \citet{Gia:10}.} %
-These also indicate that combination or shrinkage estimators of the
-full model have the potential to significantly improve on the
-benchmark.\footnote{%
-  See \citet{RaZ:12} for a recent review of this literature.} %
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-This paper gives a theoretical motivation for using OOS comparisons:
-the DMW OOS test allows a forecaster to conduct inference about
-the expected future accuracy of his or her models when one or both is
-overfit.  We show analytically and through Monte Carlo that standard
-full-sample test statistics can not test hypotheses about this
-performance.
-
-Our paper also shows that popular test and training sample sizes may
-give misleading results if researchers are concerned about overfit.
-We show that $P^2/T$ must converge to zero for the DMW test to give
-valid inference about the expected forecast accuracy, otherwise the
-test measures the accuracy of the estimates constructed using only the
-training sample.  In empirical research, $P$ is typically much larger
-than this.  Our simulations indicate that using large values of $P$
-with the DMW test gives undersized tests with low power, so this
-practice may favor simple benchmark models too much.  Existing
-corrections, proposed by \citet{ClM:01,ClM:05}, \citet{Mcc:07} and
-\citet{ClW:06,ClW:07}, seem to correct too much, though, and reject
-too often when the benchmark model is more accurate.
-
-More work remains.  The requirement that $P^2/T$ converge to zero is
-limiting, as it implies that in typical macroeconomic datasets, only a
-handful of observations should be used for testing.  This requirement
-can be relaxed only slightly; $P = O(T^{1/2})$ is required for the
-OOS test to have nontrivial power in general, but there are loss
-functions and DGPs for which some relaxation is possible.  This
-constraint could be mitigated by extending our results to
-cross-validation or other resampling strategies, or by constructing
-full-sample statistics that allow inference about $\E_T \bar{D}_T$.
-It would also be useful to extend our results to other forecasting
-models and to explore how stationarity could be relaxed, but such
-extensions are less important than improving the available statistics.
-
-\appendix
-\section*{Appendix: mathematical details}
-\setcounter{section}{1}
-% Change lemma style to prepend 'A'
-\setcounter{lem}{0}
-\renewcommand{\thelem}{A\arabic{lem}}
-
-\subsection*{Supporting results}
-The results in this paper rely heavily on a coupling argument for
-absolutely regular sequences, Berbee's Lemma \citep{Ber:79}.  Many of
-the results of this paper (Lemma \ref{res-mixingale} and
-Theorem~\ref{res-oost}) use modifications of existing results
-for NED functions of mixing processes by \citet{Jon:97} and
-\citet{JoD:00}; this coupling argument is used to explicitly derive
-inequalities that arise naturally for NED processes.  Lemma
-\ref{lem-basic-coupling} establishes these inequalities, which are
-based on a proposition of \citet{MeP:02}.
-
-We present \citeauthor{MeP:02}'s
-(\citeyear{MeP:02}) statement of Berbee's Lemma for
-the reader's reference.  In the following Lemma, $\beta(X,Y)$ is the
-coefficient of absolute regularity:
-\begin{equation}
-\beta(X,Y) = \sup_{A \in \sigma(Y)} \E \lvert \Pr(A \mid \sigma(X))
-  - \Pr(A) \rvert.
-\end{equation}
-
-\begin{lem}\label{lem-berbee}\quad
-
-\begin{quotation}\noindent
-  Let $X$ and $Y$ be random variables defined on a probability space
-  $(\Omega, \mathcal{T}, \Pr)$ with values in a Polish space
-  $S$.  Let $\sigma(X)$ be a $\sigma$-algebra generated by $X$ and let
-  $U$ be a random variable uniformly distributed on $[0,1]$
-  independent of $(X,Y)$.  Then there exists a random variable $Y^{*}$
-  measurable with respect to $\sigma(X) \vee \sigma(Y) \vee
-  \sigma(U)$, independent of $X$ and distributed as $Y$, and such that
-  $\Pr(Y \neq Y^{*}) = \beta(X,Y)$.
-
-  \noindent\citep{MeP:02}
-\end{quotation}
-\end{lem}
-
-The advantage of this result over coupling arguments that use other
-forms of weak dependence is that the difference between the original
-variable, $Y$, and the new variable, $Y^{*}$, does not depend on their
-dimension.  Similar results for strong mixing sequences depend on the
-dimension of $Y$, which makes them unsuitable for this paper.
-
-\begin{lem}\label{lem-extend-mp}
-  Suppose that $X$ and $X^*$ are $L_p$-bounded random variables, with
-  $p > 2$, that satisfy ${\Pr[X \neq X^*] = c}$.  Then
-  \begin{equation}
-    \lVert X - X^* \rVert_2 \leq 2^{1/p} (\lVert X \rVert_p + \lVert
-    X^* \rVert_p) c^{(p-2)/2p}
-  \end{equation}
-\end{lem}
-
-The proof is virtually identical to the proof of Proposition 2.3 in
-\citet{MeP:02} and is omitted.
-
-\begin{lem}\label{lem-basic-coupling}
-  Suppose Assumptions \ref{asmp-1}--\ref{asmp-3} hold.  Then, for any
-  T, $s$, $t$, and $u$ with $s < t \leq u$, there exist random
-  variables $D_t^*,\dots,D_u^*$ such that
-  \begin{equation}\label{eq:coupling1}
-    P[(D_{t}^*,\dots,D_u^*) \neq (D_{t},\dots,D_u)] \leq \beta_{t-s}
-  \end{equation}
-  and
-  \begin{equation}\label{eq:coupling2}
-    \E(\phi(D_{t}^*,\dots, D_u^*) \mid \mathcal{F}_s ) =
-    \int
-    \phi(D_{t},\dots,D_u) f(\mathbf{x}, \mathbf{y})\ d\mathbf{x}\ d\mathbf{y}
-  \end{equation}
-  almost surely for all measurable functions $\phi$ such that the
-  expectations are finite, where
-  \[ \mathbf{x} = (x_{t}', \dots, x_{u}')', \qquad
-  \mathbf{y} = (y_{t+\h},\dots,y_{u+\h})',\] and $f$ is the
-  joint density of $(\mathbf{x}, \mathbf{y})$.  Moreover,
- \begin{equation}\label{eq:coupling3}
-   \| D_v^* - D_v \|_2 \leq 2^{1+1/\rho} B_L
-   \beta_{t-s}^{\rhoExp}, \qquad v = t,\dots,u.
- \end{equation}
-\end{lem}
-
-\begin{proof}
-  The proof follows as a consequence of Lemmas \ref{lem-berbee} and
-  \ref{lem-extend-mp}.  Let $l = u-t$.  For any fixed values of $l$
-  and $T$, the sequence of vectors
-  \[ V_{t} = (y_{t+\h}, x_{t}', \dots, y_{t+l+\h}, x_{t+l}') \] is
-  absolutely regular of size $\rho/(\rho-2)$.  Berbee's Lemma implies
-  that there is a random vector $V^*$ that is independent of
-  $\mathcal{F}_s$, equal to $V_{t}$ in distribution, and satisfies
-  \[\Pr[V^* \neq V_{t}] = \beta_{t-s}.\]
-
-  Now define
-  \begin{equation*}
-    D_v^* =
-    \begin{cases}
-      L(y_{v+\h}^* - x_{1v}^{*\prime} \hat{\theta}_{1R}) - L(y_{v+\h}^* -
-      x_{2v}^{*\prime} \hat{\theta}_{2R}) & v \leq T \\
-      L(y_{v+\h}^* - x_{1v}^{*\prime} \hat{\theta}_{1T}) - L(y_{v+\h}^* -
-      x_{2v}^{*\prime} \hat{\theta}_{2T}) & v > T
-    \end{cases}
-  \end{equation*}
-  with $y_{v+\h}^*$ and $x_{iv}^*$ denoting the elements of $V^*$
-  corresponding to $y_{v+\h}$ and $x_{iv}$ in $V_{t}$.  Equations
-  (\ref{eq:coupling1}) and (\ref{eq:coupling2}) are satisfied by
-  construction, and (\ref{eq:coupling3}) follows from Lemma
-  \ref{lem-extend-mp}.
-\end{proof}
-
-\begin{lem}\label{lem:a2}
-  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-3} hold.  Let $b_T$ be a
-  sequence of integers such that $b_T \to \infty$ and $b_T = o(P)$ and define
-  \begin{equation}
-    Z_i = \ZDef.
-  \end{equation}
-  Then
-  \begin{equation}
-    \label{eq:10}
-    \sum_{i=1}^{\lfloor P/b_T \rfloor} (\E_R Z_i^2 - \E_{R+(i-1) b_T}
-    Z_i^2) \to^p 0 \quad\text{ as } P \to \infty.
-  \end{equation}
-
-  If the assumptions of Theorem~\ref{res-oost} also hold, $b_T$ is
-  restricted further so that $b_T \equiv \lfloor \gamma/\delta
-  \rfloor$ for some positive scalar $\delta$, and we define
-  \begin{equation}\label{eq:13}
-    \kernelB{x} \equiv \kernelBDefn{x},
-  \end{equation}
-  then
-  \begin{equation}
-    \label{eq:12}
-    \vtSum (Z_{1t} Z_{2t} - \E_R Z_{1t} Z_{2t}) \to^p 0.
-  \end{equation}
-  where
-  \begin{gather}
-    Z_{1t} = \varianceTermIIIa,%
-    \intertext{and}%
-    Z_{2t} = \varianceTermIVb.
-  \end{gather}
-\end{lem}
-\begin{proof}
-\newcommand{\UFiltration}[1]{\ensuremath{\mathcal{F}_{(#1)b_{T}+R-P}}}%
-The first result,~\eqref{eq:10}, follows a similar argument to Lemma~5
-of \citet{Jon:97} and~\eqref{eq:12} to Lemma~A.4 of \citet{JoD:00}.
-Since these arguments are similar and our modification is the same for
-both, we'll just present the more complicated version,~\eqref{eq:12}.
-
-Note that $\{Z_{1t}^2 P\gamma_T/b_T\}$ and $\{Z_{2t}^2 P\gamma_T/b_T\}$
-are uniformly integrable.  As in~\citet[Lemma A.4]{JoD:00}, we can
-assume that there is a constant $C$ such that $Z_{1t}$ and $Z_{2t}$
-are bounded in absolute value by $C\sqrt{b_T/P\gamma_T}$; uniform
-integrability ensures that the difference between the unbounded random
-variables and these truncated versions is negligible for large enough
-values of $C$.
-
-Let $r = \lfloor 3P/2b_T \rfloor$ and rewrite the summation as
-\begin{align*}
-  \vtSum \vtIIIsummand &= \vtSumr \vtSuma \vtIIIsummand \\
-  &\quad+ \vtSumr \vtSumb \vtIIIsummand \\
-  &\quad+ \sum_{t=r b_T - P + R + 1}^{2P+R} \vtIIIsummand \\
-  &\equiv \vtSumr (U_i - \E_R U_i) + \vtSumr (U_i' - \E_R U_i') + o_{L_1}(1).
-\end{align*}
-The proof then holds if we can show that both $U_i$ and $U_i'$ obey
-LLNs.  We'll do so by proving that $\{U_i -\E_R U_i,
-\UFiltration{2i-1}\}$ and $\{U_i' - \E_R U_i', \UFiltration{2i}\}$ are
-$L_2$-mixingales of size $-1/2$ and using the bound $\E(\vtSumr (U_i -
-\E_R U_i))^2 = O(\vtSumr c_i^2)$ where the $c_i$ are the mixingale
-magnitude indices \citep{Mcl:75}.
-
-For non-negative $m$, we have
-\begin{equation*}
-U_i - \E_R U_i \in \UFiltration{2i+2m-1},
-\end{equation*}
-establishing half of the mixingale result trivially.  Now fix $i$ and $m >
-0$ and use Lemma \ref{lem-basic-coupling} to define $D_{ts}^*$
-for each $t =(2i-2)b_T-P+R+1,\dots,(2i-1)b_T-P+R$ and $s =
-\max(t-b_T,R+1),\dots,\min(t+b_T,T-\h)$ such that
-\begin{equation*}
- \E_R D_{ts}^* = \E_{(2i-2m-1)b_T+R-P} D_{ts}^* \quad a.s.
-\end{equation*}
-and
-\begin{equation*}
-  \lVert D_{ts}^* - D_s \rVert_2 \leq \couplingBound{s - (2i-2m-1)b_T+P}.
-\end{equation*}
-Also define
-\begin{equation*}
-  Z_{1t}^* = (P\gamma_T)^{-1/2} \sum_{l=\vttLower}^{\vttUpper}
-  (D_{t,t+l}^* - \E_R D_{t,t+l}^*)\ W(l/\gamma_T), \\
-\end{equation*}
-and
-\begin{equation*}
-Z_{2t}^* = (P\gamma_T)^{-1/2} \sum_{j=\vttLower}^{\vttUpper}
-    (D_{t,t+l}^* - \E_R D_{t,t+l}^*)\ \kernelB{j/\gamma_T}.
-\end{equation*}
-
-Now, we have the inequalities
-\begin{align*}
-  \lVert \E( U_i - \E_R U_i & \mid \UFiltration{2i-2m-1}) \rVert_2
-  \\ &\leq
-  \vtSuma \lVert \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) - \E_R
-  Z_{1t}Z_{2t} \rVert_2 \\
-  &= \vtSuma \lVert \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
-  &\quad - \E(Z_{1t}^* Z_{2t}^* \mid \UFiltration{2i-2m-1}) \\
-  &\quad + \E(Z_{1t}^* Z_{2t}^* \mid \UFiltration{2i-2m-1})
-  - \E_R Z_{1t}Z_{2t} \rVert_2 \\
-%  \leq \vtSuma (\wall \lVert \wall \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
-%  - \E(Z_{1t}^*Z_{2t}^* \mid \UFiltration{2i-2m-1}) \rVert_2\return
-%  \\ + \lVert \E_R Z_{1t}Z_{2t} - \E_R Z_{1t}^*Z_{2t}^*
-%  \rVert_2)\return \\
-  &\leq 2 \vtSuma \lVert Z_{1t} Z_{2t} - Z_{1t}^* Z_{2t}^*
-  \rVert_2 \\
-  &\leq 2 \vtSuma (\lVert Z_{1t} - Z_{1t}^* \rVert_2 \lVert
-  Z_{2t} \rVert_{\infty}
-  + \lVert Z_{2t} - Z_{2t}^* \rVert_2 \lVert Z_{1t}^* \rVert_{\infty}) \\
-  &\leq \frac{2 C b_T^{1/2}}{(P\gamma_T)^{1/2}} \vtSuma (\lVert Z_{1t} - Z_{1t}^* \rVert_2
-  + \lVert Z_{2t} - Z_{2t}^* \rVert_2).
-\end{align*}
-
-And we can finish the proof with the following inequalities:
-\begin{align*}
-  \frac{2 C b_T^{1/2}}{(P \gamma_T)^{1/2}} &\vtSuma \lVert Z_{1t} - Z_{1t}^* \rVert_2 \\& \leq
-  \frac{4C b_T^{1/2}}{P\gamma_T} \vtSuma \sum_{l=\vttLower}^{\vttUpper} \lVert
-  D_{t+l} - D_{t,t+l}^* \rVert_2 W(l/\gamma_T) \\&
-  \leq O\Bigg(\frac{b_T^{1/2}}{P\gamma_T}\Bigg) \vtSuma
-  \sum_{l=\vttLower}^{\vttUpper} \couplingBeta{t+l-(2i-2m-1)b_T+P}\\&
-  = O\Bigg(\frac{b_T^{1/2}}{P\gamma_T}\Bigg) O(b_T^{3/2-u}\, m^{-1/2-u})
-\end{align*}
-for some positive $u$.  The same argument holds for $Z_{2t}$.
-As a result,
-\[
-E\Big(\vtSumr (U_i - \E_R U_i)\Big)^2 = o\Big(\vtSumr b_T^2/P\gamma_T\Big) =
- o(b_T/\gamma_T) \to 0,
-\]
-as required.
-\end{proof}
-
-\begin{lem}\label{lem:a6}
-  Suppose the conditions of Theorem~\ref{res-oost} hold.
-  Then
-  \begin{equation}
-    \sh^2 - P^{-1} \sum_{s,t=R+1}^{T-h} (D_s - \E_R
-    D_s) (D_t - \E_R D_t) W((t-s)/\gamma) \to^{L_1} 0.
-  \end{equation}
-\end{lem}
-
-\begin{proof}
-   It follows from simple algebra that
-\begin{multline*}
-  \Big| \sh^2 -  P^{-1} \sum_{s,t=R+1}^{T-h} (D_s - \E_R
-    D_s) (D_t - \E_R D_t) W((t-s)/\gamma) \Big| \leq\\
-  \varianceDiffA \\ + P^{-1} \oosSum{s,t}{1} \lvert (D_s -
-  \oosA)(\E_R D_t - \oosA) \rvert \vWeight + o_p(1).
-\end{multline*}
-We'll prove that these two sums are $o_p(1)$; uniform integrability
-then implies convergence in $L_1$.  The arguments for each are almost
-identical, so we'll only present the first.
-
-Applying the Cauchy-Schwarz inequality twice and simplifying gives the
-upper bound
-\begin{multline*}
-\varianceDiffA \\ \leq O(1) \Big[\varianceDiffAii\Big]^{1/2} \Big[\varianceDiffAi\Big]^{1/2}.
-\end{multline*}
-Now,
-$P^{-1} \oosSum{s}{1}(D_s - \E_R D_s)^2 = O_p(1)$, and it suffices to prove
-that \[\varianceDiffAi = o_p(1).\]  Observe that
-\begin{align*}
-  \varianceDiffAi & = O_p\Big(P^{-1} \oosSum{s}{1}(\E_{R}D_s -
-  \E_R\oosA)^2\Big) + O_p(\oosA - \E_R\oosA)^{2} \\
-  &= O_p\Big(P^{-1} \oosSum{s}{1} (\E_RD_s)^2 - (\E_R\oosA)^2\Big) +
-  o_p(1),
-\end{align*}
-with the second term $o_p(1)$ by Lemma \ref{res-mixingale} and
-\citepos{Dav:93} mixingale LLN.
-
-Now define $D_s^*$, $s = R+1,\dots,T-\h$, as in Lemma
-\ref{lem-basic-coupling} so that $\E_{s-1} D_s^* = \E_R D_s^*$ almost
-surely.  Note that we also have the equality $\E_R D_s^* = \E_R
-D_{R+1}^*$ almost surely for all $s\geq R+1$, and so
-\[
-P^{-1} \oosSum{s}{1} (\E_R D_s^*)^2 = \Big(P^{-1} \oosSum{s}{1} \E_R
-D_s^*\Big)^2 \quad \text{a.s.}
-\]
-Consequently,
-\begin{align*}
-P^{-1} \oosSum{s}{1}& (\E_R D_s)^2 - (\E_R\oosA)^2 \\
-&= P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R D_s^*)^2]
- + \Big(P^{-1} \oosSum{s}{1} \E_R D_s^*\Big)^2 - (\E_R\oosA)^2 \quad \text{a.s}.\\
-&= O_p\Big(P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R D_s^*)^2]\Big)
- + O_p\Big(P^{-1} \oosSum{s}{1} \E_R (D_s - D_s^*)\Big).
-\end{align*}
-Finally,
-\begin{align*}
-\Big\lVert P^{-1} \oosSum{s}{1} [(\E_RD_s)^2 - (\E_R D_s^*)^2] \Big\rVert_1
-&\leq P^{-1} \oosSum{s}{1} \lVert \E_R (D_s - D_s^*) \rVert_2 \lVert
-\E_R (D_s + D_s^*) \rVert_2
-\\ &\leq (4 B_L/P) \oosSum{s}{1} \lVert \E_R (D_s - D_s^*) \rVert_2,
-\end{align*}
-and this last term vanishes as in the proof of Lemma~\ref{lem:a2},
-completing the proof.
-\end{proof}
-
-\subsection*{Proof of Lemma \ref{res-mixingale}}
-We will start by proving that $\{D_t - \E_R D_t, \Fs_t\}$ is an
-$L_2$-mixingale of size $-1/2$; $D_t$ is $\Fs_t$-measurable and so it
-suffices to prove that
-\begin{equation}\label{eq:24}
-  \| \E_{t-l} D_t  - \E_R D_t \|_2 \leq 2^{2 + 1/\rho} B_L \, \couplingBeta{l}
-\end{equation}
-for $l = 1,\dots,t-R$, since $\couplingBeta{l} = O(l^{-1/2 - \delta})$
-for some $\delta > 0$ by assumption. Fix $R$, $t$ and $l$ and use
-Lemma \ref{lem-basic-coupling} to define $D_t^*$ so that
-\[
-\E_R D_t^* = \E_{t-l} D_t^* \quad a.s.
-\]
-and
-\[
-\lVert D_t - D_t^* \rVert_2 \leq \couplingBound{l}.
-\]
-Then
-\begin{align*}
-\lVert \E_{t-l} D_t - \E_R D_t \rVert_2 & \leq
-\lVert \E_{t-l} D_t - \E_{t-l} D_t^* \rVert_2  + \lVert \E_{t-l} D_t^* - \E_R D_t \rVert_2 \\
-&\leq 2 \lVert D_t - D_t^* \rVert_2 \\
-&\leq 2^{2 + 1/\rho}\ B_L\ \couplingBeta{l}.\tag*{\qed}
-\end{align*}
-
-\noindent Asymptotic normality follows from~\eqref{eq:24} using a
-modification of \citepos{Jon:97} CLTs for mixingale and NED arrays.
-Define
-\begin{equation*}
-  Z_i = \ZDef
-\end{equation*}
-where $b_T$ is a sequence that satisfies $b_T\leq P$,
-$b_T\to\infty$, and $b_T/P\to 0$.  The same arguments used in
-\citepos{Jon:97} Theorem 1 show that
-\begin{equation*}
-   \SumOuterBlock{i} Z_i = P^{-1/2} \oosSum{s}{1} (D_t - \E_R D_t) + o_p(1).
-\end{equation*}
-and
-\begin{equation*}
-  \SumOuterBlock{i} Z_i = \SumOuterBlock{i} (Z_i - E_{R + (i-1)b_T}
-  Z_i) + o_p(1).
-\end{equation*}
-Note that $\{Z_i - E_{R + (i-1)b_T} Z_i,\mathcal{F}_{R + i b_T}\}_i$ is an
-MDS by construction, so \citepos{HaH:80} Theorem 3.2 and Corollary
-3.1 ensure that $\sigma^{-1} \SumOuterBlock{i} Z_i \to^d N(0,1) $ as
-long as
-\begin{equation*}
-  \sigma^2 - \SumOuterBlock{i} \E_R Z_i^2 \to^p 0,
-\end{equation*}
-and
-\begin{equation*}
-  \SumOuterBlock{i} \E_R Z_i^2 - \SumOuterBlock{i} \ZSqCE \to^p 0.\footnote{%
-    Note that $\sigma^2 \in \mathcal{F}_t$ for
-    all $t \geq R$, so Hall and Heyde's condition (3.21) is
-    unnecessary---see the remarks after their result.} %
-\end{equation*}
-The first equation holds as in \citet{Jon:97} (see the proof
-of his Theorem 2); the second is ensured by
-Lemma~\ref{lem:a2}. \qed
-
-\subsection*{Proof of Lemma \ref{res-convergence}}
-\newcommand{\resConvgRHS}[1]{\ensuremath{\E(L(y^* - x_1^{*\prime}\bh{1#1}) - L(y^{*} -
-x_2^{*\prime}\bh{2#1}) \mid \bh{#1})}}
-\newcommand{\resConvgEstDiff}[1]{\ensuremath{\E(L(y^{*} -
-    x_{#1}^{*\prime}\bh{#1R}) \mid \bh{R}) -
-\E(L(y^{*} - x_{#1}^{*\prime}\bh{#1T}) \mid \bh{T})}}
-\newcommand{\resConvgEstDiffRV}[1]{\ensuremath{L(y^{*} -
-    x_{#1}^{*\prime}\bh{#1R}) - L(y^{*} - x_{#1}^{*\prime}\bh{#1T})}}
-
-Equation~\eqref{eq:7} holds if we show
-\begin{gather}
-\E_R \oosA = \resConvgRHS{R} + o_p(P^{-1/2}),\label{eq:18}\\
-\E_T \oosB = \resConvgRHS{T} + o_p(Q^{-1/2}),\label{eq:19}
-\intertext{and}
-\resConvgEstDiff{i} = O_p(\sqrt{P/T}),\label{eq:20}
-\end{gather}
-where $\hat\theta_R = (\hat\theta_{1R}, \hat\theta_{2R})$,
-$\hat\theta_T = (\hat\theta_{1T}, \hat\theta_{2T})$, and $y^{*}$,
-$x_1^{*}$ and $x_2^{*}$ are random variables drawn from the joint
-distribution of $(y_{t+\h},x_{1t},x_{2t})$ independently of
-$\mathcal{F}_T$.
-
-\begin{proof}[Proof of~\eqref{eq:18} and~\eqref{eq:19}]
-For~\eqref{eq:18}, define $D_t^*$ for each $t=R+1,R+2,\dots,T-h$ so
-that
-\begin{equation*}
-  \| D_t^* - D_t \|_2 \leq 2^{(1+\rho)/\rho} B_L \beta_{t-R}^{(\rho-2)/2\rho}
-\end{equation*}
-and
-\begin{equation*}
-  \E_R D_t^* = \E(L(y^* - x_1^{*\prime}\hat\theta_{1R}) -
-  L(y^* - x_2^{*\prime}\hat\theta_{2R}) \mid \hat\theta_R) \qquad a.s.
-\end{equation*}
-Lemma~\ref{lem-basic-coupling} ensures that these $D_t^*$ exist.
-Now,
-\begin{align*}
-  \Big\lVert \E_R \oosA - \E\Big(P^{-1} \sum_{t=R+1}^{T-h} D_t^* \mid
-  \hat\theta_R\Big) \Big\rVert_2
-  &= \Big\lVert \E_R\Big( \oosA - P^{-1} \sum_{t=R+1}^{T-h} D_t^*
-  \Big) \Big\rVert_2 \\
-  &\leq P^{-1} \sum_{t=R+1}^{T-h} \lVert D_t - D_t^* \rVert_2\\
-  &= O(P^{-1}) \sum_{t=R+1}^{T-h} \beta_{t-R}^{(\rho-2)/2\rho}
-\end{align*}
-and this last term is $o(P^{-1/2})$ by assumption.
-Essentially the same argument proves~\eqref{eq:19} as well.
-\end{proof}
-
-\begin{proof}[Proof of~\eqref{eq:20}]
-Assumption~\ref{asmp-3} and the definition of the OLS estimator
-ensure that
-\begin{align*}
-  \|L(y^{*} -  x_i^{*\prime} \bh{iR}) - L(y^{*} - x_i^{*\prime} \bh{iT}) \|_1
-  &\leq B_{L} \| x_i^{*\prime} (\bh{iR} - \bh{iT}) \|_2 \\
-  &\leq B_{L} \, \| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
-  (X_{iR}'X_{iR})^{-1}] X_{iR}' \eb_{iR} \|_2 \\
-  &\quad+ B_L \, \| x_i^{*\prime}
-  (X_{iT}'X_{iT})^{-1}[X_{iT}'\eb_{iT} - X_{iR}
-  \eb_{iR} ] \|_2 .
-\end{align*}
-
-To simplify notation, define $V = (X_{iT}'X_{iT})^{-1} -
-(X_{iR}'X_{iR})^{-1}$ and $W = X_{iR}'\eb_{iR} \eb_{iR}'X_{iR}$. The
-first term in the upper bound satisfies
-\begin{align*}
-  \| x_i^{*\prime} V X_{iR}' \eb_{iR} \|_2^2
-  &\leq \eigen_{K_i}(\E x_i^* x_i^{*\prime}) \cdot \E \tr\big( V^2 W \big) \\
-  &= O(1) \cdot \E \tr\{ V^2 \E(W \mid
-  X_{iR}'X_{iR}, x_{i,R-\h+1} x_{i,R-\h+1}',\dots, x_{i,T-\h} x_{i,T-\h}')\}
-\end{align*}
-by assumption. Observe that
-\begin{multline*}
-  \E \tr\{ V^2 \E(W \mid X_{iR}'X_{iR}, x_{i,R-\h+1} x_{i,R-\h+1}',\dots, x_{i,T-\h} x_{i,T-\h}')\}
-  \\ \leq
-  \Big\rVert \sum_{i=1}^{K_i} \eigen_i^2 \big(V\big) \Big\rVert_{3/2}
-  \big\rVert \eigen_{K_i}(\E(W \mid
-  X_{iR}'X_{iR}, x_{i,R-\h+1} x_{i,R-\h+1}',\dots, x_{i,T-\h} x_{i,T-\h}')) \big\rVert_3.
-\end{multline*}
-The second term in this product is $O(R)$ by
-Assumption~\ref{asmp-2}. To bound the first term, note that
-$(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}$ has rank $P$ and
-each of its nonzero eigenvalues is bounded in absolute value by the
-eigenvalues of $(X_{iR}'X_{iR})^{-1}$. The eigenvalues of
-$(X_{iR}'X_{iR})^{-1}$ are $O_{L_3}(1/R)$ by Assumption~\ref{asmp-2}, so
-\begin{equation*}
-  \Big\|\sum_{j=1}^{K_i}
-  \eigen_j^2(V)\Big\|_{3/2}
-  \leq \Big\|\sum_{j=K_i - P+1}^{K_i} \eigen_j^2(V) \Big\|_{3/2}
-  = O(P/R^2).
-\end{equation*}
-Consequently,
-\begin{equation*}
-  \E \tr\bigg\{[(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}]^2
-  X_{iR}'\eb_{iR} \eb_{iR}X_{iR} \bigg\} = O(P/R)
-\end{equation*}
-and so
-\begin{equation*}
-  \| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
-  (X_{iR}'X_{iR})^{-1}] X_{iR}' \eb_{iR} \|_2 = O(\sqrt{P/R}).
-\end{equation*}
-
-A similar argument proves that
-\begin{equation*}
-  \big\| x_i^{*\prime} (X_{iR}'X_{iR})^{-1}
-  [X_{iT}'\eb_{iT} - X_{iR} \eb_{iR} ] \big\|_2 =  O(\sqrt{P/R}),
-\end{equation*}
-completing the proof.
-\end{proof}
-
-\subsection*{Proof of Theorem \ref{res-oost}}
-We can rewrite the centered \oost\ statistic as
-\[
-\sqrt{P}(\oosA - \E_T \oosB)/\sh
-= \frac{\sigma}{\sh}\, \Big( \sqrt{P}(\oosA - \E_R \oosA)/\sigma
-+ \sqrt{P}(\E_R \oosA - \E_T \oosB)/\sigma \Big)
-\]
-so Lemma \ref{res-mixingale} and \ref{res-convergence} ensure that
-this term is asymptotically standard normal as long as $\sigma/\sh
-\to^p 1$. Since $\sigma$ is almost surely positive, this convergence
-is equivalent to $\sigma^2 - \sh^2 \to^p 0$.
-
-The proof that $\sigma^2 - \sh^2 \to^p 0$ follows \citepos{JoD:00}
-Theorem 2.1 closely.  We start by defining similar quantities to
-theirs, borrowing their notation when possible to make the
-similarities apparent. Let $b_T \equiv \lfloor \gamma/\delta \rfloor$,
-define $\kernelB{x}$ as in Equation \eqref{eq:13}, and define the following
-terms as in \citet{JoD:00}:
-\begin{align*}
-  \varianceTermI &\equiv
-  \varianceTermIDefn,\\ \varianceTermII &\equiv \vtSum
-  \varianceTermIIa\\& \quad \times \varianceTermIIb,\\
-  \varianceTermIII &\equiv \vtSum \varianceTermIIIa\\
-  &\quad \times \varianceTermIIb,\\
-  \varianceTermIV &\equiv \vtSum \varianceTermIIIa \\
-  &\quad\times \varianceTermIVb.
-\end{align*}
-These definitions give the inequalities
-\begin{align*}
-  \lVert \sh^2 - \sigma^2 \rVert_1 &
-  \leq \lVert \sh^2 - \varianceTermI \rVert_1
-  + \lVert \varianceTermI - \varianceTermII \rVert_1
-  + \lVert \varianceTermII - \varianceTermIII \rVert_1
-  + \lVert \varianceTermIII - \varianceTermIV \rVert_1\\ & \quad
-  + \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1
-  + \lVert \E_R\varianceTermIII - \E_R\varianceTermIV \rVert_1
-  + \lVert \E_R\varianceTermII - \E_R\varianceTermIII \rVert_1\\ & \quad
-  + \lVert \E_R\varianceTermI - \E_R\varianceTermII \rVert_1
-  + \lVert \E_R \varianceTermI - \sigma^2 \rVert_1
-  \\ &
-  \leq  \lVert \sh^2 - \varianceTermI \rVert_1
-  + 2(\lVert \varianceTermI - \varianceTermII \rVert_1
-      + \lVert \varianceTermII - \varianceTermIII \rVert_1
-      + \lVert \varianceTermIII - \varianceTermIV \rVert_1) \\
-  & \quad + \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1
-  + \lVert \E_R \varianceTermI - \sigma^2 \rVert_1.
-\end{align*}
-De Jong and Davidson (2000) prove that
-\begin{equation*}
-\lim_{\delta\to0} \limsup_{T\to\infty} \lVert \varianceTermI -
-\varianceTermII\rVert_1 = 0,
-\end{equation*}
-\begin{equation*}
-\lim_{\delta\to0} \limsup_{T\to\infty} \lVert \varianceTermII - \varianceTermIII
-\rVert_1 = 0,
-\end{equation*}
-\begin{equation*}
-\lim_{\delta\to0} \limsup_{T\to\infty} \lVert \varianceTermIII - \varianceTermIV
-\rVert_1 = 0,
-\end{equation*}
-and
-\begin{equation*}
-\lim \lVert \E_R \varianceTermI - \sigma^2 \rVert_1 = 0.
-\end{equation*}
-Their proofs of these four convergence results use the fact that NED
-functions of mixing processes are also mixingale processes and do not
-use any other properties specific to NED processes, so their results
-hold here as well.  We do need to modify their proofs that
-\begin{equation*}
-  \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1 \to 0
-\end{equation*}
-and
-\begin{equation*}
-  \lVert \sh^2 - \varianceTermI \rVert_1 \to 0
-\end{equation*}
-for all positive $\delta$, though, since those proofs exploit NED
-properties. These results are presented as Lemmas~\ref{lem:a2}
-and~\ref{lem:a6} respectively.  \qed
-
-\subsection*{Proof of Theorem \ref{res:oostest}}
-Coverage of the confidence intervals is immediate from
-Theorem~\ref{res-oost}, so we will present a proof of~\eqref{eq:23}.
-By Lemma~\ref{res-convergence}, we know that $\E_R \oosA - \E_T \oosB
-\to^p 0$, so
-\begin{equation*}
-  \Pr[\E_R \oosA \leq 0] - \Pr[\E_T \oosB \leq 0] \to 0.
-\end{equation*}
-Now we can use Lemma~\ref{lem-basic-coupling} to define $D_t^*$ as in
-the proofs of Lemma~\ref{res-mixingale} and~\ref{res-convergence} so
-that $\E_R D_t^* = \E_{t-l} D_t^*$ a.s. and
-\[
-\lVert D_t - D_t^* \rVert_2 \leq \couplingBound{l}
-\]
-and define $\oosA^* = P^{-1} \sum_{t=R+1}^{T-\h} D_t^*$. Then
-\begin{equation*}
-  \lVert \sqrt{P} \oosA - \sqrt{P} \oosA^* \rVert_2
-  \leq P^{-1/2} \sum_{t=R+1}^{T-\h} \lVert \oosA - \oosA^* \rVert_2
-  = o(1),
-\end{equation*}
-and, consequently, we have convergence in probability of the following
-vectors:
-\begin{equation*}
-  (\sqrt{P} \oosA^*/\sigma,\ \E_R \oosA) -
-  (\sqrt{P} \oosA/\sh,\ \E_T \oosB) \to^p 0,
-\end{equation*}
-where we are implicitly using consistency of $\sh^2$ for $\sigma^2$.
-More importantly, this implies convergence in distribution of these
-vectors, so
-\begin{equation*}
-  \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha
-  \text{ and } \E_R \oosA \leq 0]
-  - \Pr[\sqrt{P} \oosA / \sh > z_\alpha \text{ and }
-  \E_T \oosB \leq 0] \to 0.
-\end{equation*}
-
-For large enough $T$, both $\Pr[\E_R \oosA \leq 0]$ and $\Pr[\E_T
-\oosB \leq 0]$ are positive (the second by assumption, the first by
-convergence to the second) so (for these $T$)
-\begin{align}\label{eq:31}
-  \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha
-  \mid \E_R \oosA \leq 0] &=
-  \frac{\Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha \text{ and }
-    \E_R \oosA \leq 0]}{\Pr[\E_R \oosA \leq 0]}
-\intertext{and}\label{eq:32}
-  \Pr[\sqrt{P} \oosA / \sh > z_\alpha
-  \mid \E_T \oosB \leq 0] &=
-  \frac{\Pr[\sqrt{P} \oosA / \sh > z_\alpha \text{ and }
-    \E_T \oosB \leq 0]}{\Pr[\E_T \oosB \leq 0]}
-\end{align}
-almost surely. Since the terms on the RHS of Equations~\eqref{eq:31}
-and~\eqref{eq:32} converge to the same limit in probability, we have
-\begin{equation*}
-  \Pr[\sqrt{P} \oosA / \sh > z_\alpha  \mid \E_T \oosB \leq 0]
-  - \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha \mid \E_R \oosA \leq 0]
-  \to^p 0
-\end{equation*}
-and it suffices to show that
-\begin{equation*}
-  \plim \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha \mid \E_R \oosA \leq 0]
-  \leq \alpha.
-\end{equation*}
-
-To establish this inequality, we have
-\begin{align*}
-  \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha \mid \E_R \oosA \leq 0]
-  &\leq \Pr[\sqrt{P} (\oosA^* - \E_R \oosA) / \sigma > z_\alpha
-  \mid \E_R \oosA \leq 0] \\
-  &\leq \E\big(
-  \Pr[\sqrt{P} (\oosA^* - \E_R \oosA) / \sigma > z_\alpha \mid \Fs_R]
-  \mid \E_R \oosA \leq 0\big).
-\end{align*}
-By construction,
-\begin{equation*}
-  \Pr[\sqrt{P} (\oosA^* - \E_R \oosA) / \sigma > z_\alpha \mid \Fs_R]
-  \to \alpha
-\end{equation*}
-since generated pseudo OOS observations in each $D_t^*$ are
-independent of $\Fs_R$, completing the proof.
-\qed
-
-\subsection*{Proof of Theorem~\ref{res:insample1}}
-
-Let $(\e_{t+h}, x_{t}) \sim i.i.d.\ N(0,I)$ and let $\theta_1 = 0$.
-For any $d \geq 0$, the event $\E_T \oosB = -d$ implies that
-\begin{equation*}
-  \E_T (y_{T+\h+1} - x_{1T+1}'\bh{1T})^2
-  = \E_T (y_{T+\h+1} - x_{2T+1}'\bh{2T})^2 - d \quad a.s.
-\end{equation*}
-which can be expressed as
-\begin{equation}\label{eq:34}
-  d + \theta_2'M_2' M_2 \theta_2 + \bh{1T}'\bh{1T} - \bh{2T}'M_1'M_1\bh{2T}
-  = (\bh{2T} - \theta_2)' M_2'M_2 (\bh{2T} - \theta_2) \quad a.s.
-\end{equation}
-$M_2 \bh{2T}$ is normally distributed conditional on $\bh{1T}$ and
-$M_1 \bh{2T}$, and is distributed on the surface of the sphere defined
-by~\eqref{eq:34} conditional on $\bh{1T}$, $M_1 \bh{2T}$, and the
-event $\E_T \oosB = -d$.
-
-Since $M_2 \bh{2T}$ is normal, this conditional distribution is
-invariant to reflection across the axes defined by the eigenvectors of
-its covariance matrix. So when $\theta_2$ lies outside the cylinder
-that contains the acceptance region of $\Lambda$, i.e. when
-$\theta_2'M_2' V_T M_2 \theta_2 > c$, we have\footnote{%
-  To keep the notation in these equations manageable, define the
-  information set
-  $\Gs = \sigma(\E_T \oosB \leq 0,~ \theta_2'M_2' V_T M_2 \theta_2 >
-  c)$.} %
-\begin{align*}
-  \Pr[ \bh{2T}' M_2' V_T M_2 \bh{2T} \leq c \mid \Gs]
-  &= \E\Big( \Pr[ \bh{2T}'M_2' V_T M_2 \bh{2T} \leq c \mid \Gs,~\bh{1T},~M_1 \bh{2T}] \mid \Gs \Big) \\
-  & < 1/2
-\end{align*}
-since the inner conditional probability is less than 1/2.
-
-Now let $\delta > 0$ be an arbitrary but small constant, and choose
-$\theta_2$ far enough from the origin to ensure that
-\begin{equation*}
-  \Pr[\theta_2'M_2' V_T M_2 \theta_2 \leq c] \leq \delta
-\end{equation*}
-for large enough $T$. Then
-\begin{align*}
-  \E(\Lambda \mid \E_T \oosB \leq 0) &
-  \geq \Pr[\bh{2T}' M_2' V_T M_2 \bh{2T} > c \mid \E_T \oosB \leq 0] \\
-  &= \Pr[\bh{2T}' M_2' V_T M_2 \bh{2T} > c \text{~~and~~}
-  \theta_2'M_2' V_T M_2 \theta_2 > c \mid \E_T \oosB  \leq 0] \\
-  & \quad + \Pr[\bh{2T}' V_T M_2 \bh{2T} > c \text{~~and~~ }
-  \theta_2'M_2' V_T M_2 \theta_2 \leq c \mid \E_T \oosB \leq 0].
-\end{align*}
-The second term is nonnegative by design. By conditioning on
-$\theta_2'M_2' V_T M_2 \theta_2 > c$ our earlier argument shows that
-the first term is greater than or equal to $(1 - \delta) / 2$. Since
-$\delta$ is arbitrarily small, this completes the proof.
-\qed
-
-\subsection*{Proof of Theorem~\ref{res:insample2}}
-As in the proof of Theorem~\ref{res:insample1}, let $(\e_{t+h}, x_{t})
-\sim i.i.d.\ N(0,I)$ and let $\theta_1 = 0$. The event $\E_T \oosB
-\geq 0$ implies that
-\begin{equation*}
-  \E_T (y_{T+\h+1} - x_{1T+1}'\bh{1T})^2
-  \geq \E_T (y_{T+\h+1} - x_{2T+1}'\bh{2T})^2 \quad a.s.
-\end{equation*}
-which can be expressed as
-\begin{equation}\label{eq:2}
-  \theta_2'M_2 M_2'\theta_2 + \bh{1T}'\bh{1T} - \bh{2T}'M_1'M_1\bh{2T}
-  \geq (\bh{2T} - \theta_2)' M_2'M_2 (\bh{2T} - \theta_2) \quad a.s.
-\end{equation}
-$M_2 \bh{2T}$ is normally distributed conditional on $\bh{1T}$ and
-$M_1 \bh{2T}$, and is a.s. contained in the sphere defined
-by~\eqref{eq:2} conditional on $\bh{1T}$, $M_1 \bh{2T}$, and the
-event $\E_T \oosB \geq 0$.
-
-Let $\delta$ be a small arbitrary constant, define $\theta^*$ as
-\begin{gather*}
-  \theta^* = \argmax_\theta \theta' M_2' M_2 \theta \\
-  s.t.\quad \theta_2'M_2'M_2\theta_2 +  \bh{1T}'\bh{1T} - \bh{2T}'M_1'M_1\bh{2T} = (\theta - \theta_2)' M_2'M_2 (\theta - \theta_2)
-\end{gather*}
-($\theta^*$ is stochastic and depends on $\bh{1T}$ and $M_1 \bh{2T}$)
-and choose $c$ so that
-\begin{equation*}
-  \Pr[ \theta^{* \prime} M_2 M_2 \theta^* > c] < \delta.
-\end{equation*}
-
-Then, we have for large enough $T$
-\begin{align*}
-  \E(\Lambda \mid \E_T \oosB \geq 0) &\leq
-  \Pr[\bh{2T}'M_2'M_2\bh{2T} > c \mid \E_T \oosB \geq 0) \\
-  &\leq \delta
-\end{align*}
-Since $\delta$ is arbitrarily close to zero, this completes the proof.
-
-\qed
-
-\clearpage
-\markboth{}{}
-\tryinput{floats/mc-ftest.tex}
-
-\begin{table}[tb]
-  \begin{tabularx}{\linewidth}{XX}
-    \toprule
-    Category & Variable \\
-    \midrule
-    Stock market variables
-    & Dividend to price ratio (log) \\
-    & Earnings to price ratio (log) \\
-    & Stock market variance \\
-    & Book to market ratio \\
-    & Net equity expansion \\
-    & Percent equity issuing \\\\
-    Interest rate variables
-    & Treasury Bill rate (3 month) \\
-    & Long term yield \\
-    & Long term rate \\
-    & Default return spread \\
-    & Default yield spread \\
-    & Inflation rate \\
-    \bottomrule
-  \end{tabularx}
-  \caption{Variables used to predict the equity premium
-    (Section~\ref{sec:empirics}).
-    Please see Goyal and Welch's original paper \citep{GoW:08}
-    for a detailed description of each variable.}
-  \label{tab:equity}
-\end{table}
-
-\tryinput{floats/empirics-insample.tex}
-\tryinput{floats/empirics-insample-tuned.tex}
-% These macros create tables. They are defined in
-% floats/empirics-insample.tex and possibly overwritten in the next
-% file.
-\insamplecoefs
-\insampletests
-
-\begin{figure}\centering
-  {\large Coverage of DMW OOS interval for $\E_R\oosA$ in simulations}
-  \tryinput{floats/mc-interval-testerror1.tex}
-  \caption{Simulated coverage of $\E_R \oosA$ at 90\% confidence using
-    a one-sided interval based on the DMW \oost\ test, plotted as a
-    function of the fraction of observations used in the test sample,
-    $P/T$. The solid horizontal line denotes the intervals' nominal
-    coverage.}
- \label{fig:interval-R}
-\end{figure}
-\clearpage
-
-\begin{figure}\centering
-  {\large Coverage of DMW OOS interval for $\E_T\oosB$ in simulations}
-  \tryinput{floats/mc-interval-generror1.tex}
-  \caption{Simulated coverage of $\E_T \oosB$ at 90\% confidence using
-    a one-sided interval based on the DMW \oost\ test, plotted as a
-    function of the fraction of observations used in the test sample,
-    $P/T$.  The solid horizontal line denotes the intervals' nominal
-    coverage.}
-  \label{fig:interval-T}
-\end{figure}
-\clearpage
-
-\begin{figure}\centering
-  {\large Size of DMW \oost\ test in simulations}
-  \tryinput{floats/mc-dmwsize.tex}
-  \caption{Simulated rejection probabilities for the DMW \oost\ test
-    under the null hypothesis that the benchmark model will forecast
-    better, $\E_T \oosB \leq 0$. The nominal size is 10\% and is
-    marked with a solid horizontal line. Values greater than 10\%
-    indicate that the test rejects the benchmark model too often. See
-    Section~\ref{sec:simulation-design} for a discussion of the
-    simulation design.}
-  \label{fig:ttest-size}
-\end{figure}
-\clearpage
-
-\begin{figure}\centering
-  {\large Size of Clark-West OOS test in simulations}
-  \tryinput{floats/mc-clarkwestsize.tex}
-  \caption{Simulated rejection probabilities for Clark and West's
-    (2006, 2007) OOS test statistic under the null hypothesis that the
-    benchmark will forecast better, $\E_T \oosB \leq 0$. The nominal
-    size is 10\% and is marked with a solid horizontal line. Values
-    greater than 10\% indicate that the test rejects the benchmark
-    model too often. See Section~\ref{sec:simulation-design} for a
-    discussion of the simulation design.}
-   \label{fig:clarkwest}
-\end{figure}
-\clearpage
-
-\begin{figure}\centering
-  {\large Size of McCracken \oost\ test in simulations}
-  \tryinput{floats/mc-mccrackensize.tex}
-  \caption{Simulated rejection probabilities for McCracken's (2007)
-    \oost\ test under the null hypothesis that the benchmark model is
-    more accurate, $\E_T \oosB \leq 0$. Nominal size is 10\% and is
-    marked with a solid horizontal line. Values greater than 10\%
-    indicate that the test rejects the benchmark model too often. See
-    Section~\ref{sec:simulation-design} for a discussion of the
-    simulation design.}
-  \label{fig:mccracken}
-\end{figure}
-\clearpage
-
-\begin{figure}\centering
-  {\large Power of DMW \oost\ test in simulations}
-  \tryinput{floats/mc-dmwpower.tex}
-  \caption{Simulated rejection probabilities for the DMW \oost\ test
-    under the alternative that the benchmark model is less accurate,
-    $\E_T \oosB > 0$. Nominal size is 10\% and is marked with a solid
-    horizontal line. Values greater than 10\% indicate that the test
-    rejects the benchmark model too often. See
-    Section~\ref{sec:simulation-design} for a discussion of the
-    simulation design.}
-  \label{fig:ttest-power}
-\end{figure}
-\clearpage
-
-\begin{figure}
-\centering
-\large{Difference in OOS MSE of Prevailing Mean and\\ Kitchen
-    Sink Models of Equity Premium (OLS)}
-\tryinput{floats/empirics-oos-mse-1.tex}
-\tryinput{floats/empirics-oos-mse-1b.tex}
-\caption{OOS difference in the MSE
-  of the prevailing mean benchmark and the kitchen sink model as a
-  function of the test sample size, $R$.  Both models forecast the
-  equity premium using annual data from 1928--2008.  The solid line
-  gives the OOS average, and the shaded region indicates the
-  one-sided 95\% confidence interval implied by the
-  DMW test.  The bottom panel is a detailed view of the top
-  panel for $R \geq 50$.}
-\label{fig:empirics1}
-\end{figure}
-\clearpage
-
-\begin{figure}
-\centering
-\large{Difference in OOS MSE of Prevailing Mean and\\ Kitchen
-    Sink Models of Equity Premium (CT)}
-\tryinput{floats/empirics-oos-mse-2.tex}
-\tryinput{floats/empirics-oos-mse-2b.tex}
-\caption{OOS difference in the MSE
-  of the prevailing mean benchmark and the kitchen sink model as a
-  function of the test sample size, $R$.  Both models forecast the
-  equity premium using annual data from 1928--2008.  The solid line
-  gives the OOS average, and the shaded region indicates the
-  one-sided 95\% confidence interval implied by the
-  DMW test.  The bottom panel is a detailed view of the top
-  panel for $R \geq 50$.}
-\label{fig:empirics2}
-\end{figure}
-\clearpage
-
-\begin{figure}
-\centering
-\large{OOS MSE of Individual Forecasts of Equity Premium}
-\tryinput{floats/empirics-oos-ind-ks.tex}
-\tryinput{floats/empirics-oos-ind-pm.tex}
-\caption{OOS MSE of the Prevailing Mean (PM) and
-    Kitchen Sink (KS) models for equity premium prediction as
-    a function of the size of the training sample, $R$.  Please note
-    that the vertical scales are different in the two plots.}
-\label{fig:empirics3}
-\end{figure}
-
-\clearpage
-
-\bibliographystyle{abbrvnat}
-\bibliography{latex-tools-0.2.1/references}
-
-\clearpage
-\section{Supplemental appendix (not for publication)}
-\input{appendix_contents}
-
-\end{document}
-
 %%% Local Variables:

### 2017-04-21 D1-example.tex
[#40/move] Move extended example from Section 3.3 to appendix

--- 2016-12-22 paper.tex
@@
-\documentclass[12pt,draft]{article}
-\input{setup}
+\section*{Supplemental Appendix (not for publication)}
+\markright{Supplemental Appendix}
 
-\title{Out-of-Sample Comparisons of Overfit Models}
-\author{Gray Calhoun\thanks{email: gcalhoun@iastate.edu. I
-    would like to thank Julian Betts, Helle Bunzel,
-    St\'ephane Bonhomme, Marjorie Flavin,
-    Nir Jaimovich, Lutz Kilian, Ivana Komunjer, Michael McCracken,
-    Seth Pruitt, Ross Starr, Jim Stock, Yixiao Sun, Allan Timmermann,
-    Hal White, several anonymous referees, participants at the 2010
-    Midwest Economics Association Annual Meetings, the 2010
-    International Symposium on Forecasting, the 2010 Joint Statistical
-    Meetings, the 2011 NBER-NSF Time-Series
-    Conference, and in many seminars at UCSD, and especially
-    Graham Elliott for their valuable suggestions, feedback and advice
-    in writing this paper.  I would also like to thank Amit Goyal for
-    providing computer code and data for his 2008 RFS paper
-    with Ivo Welch \citep{GoW:08}.} \\ Iowa State University}
+\noindent%
+This appendix contains additional results to accompany
+\citet{Cal:15b}. The first section presents a simple example with
+i.i.d. observations that illustrates the main paper's theoretical
+results. Many of these results can be proven directly under
+independence and these proofs continue to demonstrate the key elements
+of the main proofs. The second section presents additional Monte Carlo
+simulations.
 
-\date{\VERSION}
-
-\begin{document}
-\maketitle
-
-\begin{abstract}\noindent
-  This paper uses dimension asymptotics to study the behavior of
-  out-of-sample (OOS) test statistics when they are used to compare
-  ``overfit'' linear regression models. Under these asymptotics, the
-  number of predictors used by the larger model increases with the
-  number of observations so that their ratio remains uniformly
-  positive. This analysis gives a theoretical motivation for using
-  out-of-sample (OOS) comparisons: the Diebold-Mariano-West OOS $t$-test
-  (Diebold and Mariano, 1995, \textit{JBES}, and West, 1996,
-  \textit{Econometrica}) allows a forecaster to conduct inference
-  about the models' generalization error, an important measure of
-  forecast accuracy that conditions on the models' parameter estimates.
-  We show analytically and through Monte Carlo that standard full-sample
-  test statistics can not test hypotheses about this measure of performance.
-  Our paper also suggests that comparisons of overfit models require small
-  OOS test samples. If $P$ denotes the number of observations used for the
-  OOS comparison and $T$ the total number of observations, $P^2/T$ must
-  converge to zero for the OOS $t$-test to be centered on the model's
-  generalization error.
-
-\noindent JEL Classification: C12, C22, C52, C53
-
-\noindent Keywords: Generalization Error, Forecasting, Model
-Selection, $t$-test, Dimension Asymptotics
-\end{abstract}
-\newpage
-
-\section{Introduction}
-\label{sec:introduction}
-
-Consider two sequences of length $P$ of prediction errors, the result
-of forecasting the same variable with two different estimated models.
-Both models are estimated with $R$ observations, collectively called
-the {\em estimation window}, and are used to forecast an additional
-$P$ observations, called the {\em test sample}.  There are $T$
-observations in all, and $R+P=T$.  This paper introduces a new limit
-theory for statistics constructed from these prediction errors
-designed to approximate the behavior of the statistics when one of the
-models is overfit.  In doing so, we provide a theoretical
-justification for forecasters to use out-of-sample (OOS) instead of in-sample
-comparisons: the DMW OOS test%
-\footnote{In this paper, we will refer to the basic OOS $t$-test
-  studied by \citet{DiM:95} and \citet{Wes:96} as the DMW test.} %
-allows a forecaster to conduct
-inference about the expected future accuracy of his or her models when
-one or both is overfit.  We show analytically and through Monte Carlo simulations
-that standard full-sample test statistics can not test hypotheses
-about this performance.
-
-Our paper also shows that popular test and training sample sizes may
-give misleading results if researchers are concerned about overfit.
-We show that $P^2/T$ must converge to zero for the DMW test to give
-valid inference about the expected forecast accuracy, otherwise the
-test measures the accuracy of the estimates constructed using only the
-training sample.  In empirical research, $P$ is typically much larger
-than this.  Our simulations indicate that using large values of $P$
-with the DMW test gives undersized tests with low power, so this
-practice may favor simple benchmark models too much.  Existing
-corrections, proposed by \citet{ClM:01,ClM:05}, \citet{Mcc:07} and
-\citet{ClW:06,ClW:07}, seem to overcorrect for this problem, though, and reject
-too often when the benchmark model is more accurate.
-
-Although OOS comparisons have been popular in Macroeconomics and
-Finance since \citepos{MeR:83} seminal study of exchange rate models,
-it has been unclear from a theoretical perspective whether or not the
-statistics are useful.  Empirical researchers often cite ``overfit''
-or ``instability'' as reasons for using OOS comparisons, as in
-\citet{StW:03}, but neither term is precisely defined or formalized.
-Compounding this problem, the asymptotic distributions of these
-statistics are derived under conditions that rule out either
-instability or overfit and allow a researcher to use a conventional
-in-sample comparison---a variation of the $F$-test, for example.  As
-\citet{InK:04} argue, the statistics themselves are designed to test
-hypotheses that can be tested by these in-sample statistics.  For
-example, \citet{DiM:95} and \citet{Wes:96} derive the limiting
-distributions of many popular OOS test statistics under conditions
-that would justify these full-sample tests.  Much
-of the subsequent research by \citet{Mcc:00, Mcc:07}, \citet{CCS:01},
-\citet{ClM:01,ClM:05}, \citet{CoS:02,CoS:04}, \citet{ClW:06,ClW:07},
-\citet{Ana:07}, and others relaxes several of Diebold and Mariano's
-and West's assumptions, but maintains the stationarity and dependence
-conditions that permit in-sample comparisons \citep[see][for a
-review of this literature]{Wes:06}.%
-\footnote{Like us, \citet{Ana:07} allows the number of regressors to
-  increase with $T$.  But in that paper, the number of regressors
-  increases slowly enough that the OLS coefficients are consistent and
-  asymptotically normal.} %
-\citet{GiW:06} and
-\citet{GiR:09, GiR:10} are exceptions.  Instead of focusing on
-hypotheses that can be tested by in-sample comparisons, \citet{GiW:06}
-derive an OOS test for the null hypothesis that the difference
-between two models' OOS forecasting performance is unpredictable, a
-martingale difference sequence (MDS); \citet{GiR:09} test whether the OOS
-forecasting performance of a model suffers from a breakdown relative
-to its in-sample performance; and \citet{GiR:10} test whether the
-forecasting performance is stable. However, those papers focus on a
-particular OOS estimation strategy and do not address why OOS
-comparisons might be useful as a general strategy.
-
-Since in-sample and OOS statistics require similar assumptions and
-test similar hypotheses, one might expect that they would give similar
-results.  They do not.  In-sample analyses tend to support more
-complicated theoretical models and OOS analyses support simple
-benchmarks, as seen in \citet{MeR:83}, \citet{StW:03}, and
-\citet{GoW:08}.  Since these different approaches strongly influence
-the outcome of research, it is important to know when each is
-appropriate.  The explanations in favor of OOS comparisons claim
-that they should be more robust to unmodeled instability
-\citep{ClM:05,GiW:06,GiR:09,GiR:10} or to overfit
-\citep{Mcc:98,Cla:04}.  Both explanations presume that the in-sample
-comparison is invalid and the OOS comparisons are more reliable.  Of
-course, as \citet{InK:04,InK:06} point out, both in-sample and OOS
-methods could be valid, but the OOS methods could have lower power.
-
-In this paper, we study the ``overfit'' possibility and leave
-``instability'' to future research. This paper uses dimension
-asymptotics to study the behavior of OOS comparisons when at least
-one of the models is overfit---the number of its regressors
-increases with the number of observations so that their ratio remains
-positive.  Although overfit is sometimes used to describe the
-situation where a forecaster chooses from many different models,
-i.e. \emph{data-mining} or \emph{data-snooping}, we view these as
-separate issues.  Procedures that account for the presence of many
-models have been, and are continuing to be, developed \citep[see, for
-example,][]{Whi:00,Han:05,RoW:05,HHK:10,ClM:12b}, but it is unclear
-whether those procedures should themselves use in-sample or OOS
-comparisons.  Understanding the difference between in-sample and OOS
-comparisons in the context of a simple comparison between two models
-is necessary before resolving any new issues that arise with multiple
-comparisons. Moreover, the empirical research that motivates
-this paper uses \emph{pseudo} OOS comparisons and not
-true OOS comparisons.  Even if a true OOS comparison
-could account for some forms of data-snooping better than
-\citepos{Whi:00} BRC or its extensions, in-sample and pseudo
-OOS comparisons would both be affected by the data-snooping, a
-point also made by \citet{InK:04}.
-
-We focus on linear regression models estimated with a fixed window
-for simplicity, but our basic conclusions should be true for other
-models and estimation strategies as well.  Under this
-asymptotic theory, where the number of regressors $K$ increases with $T$
-so that the limit of $K/T$ is positive and less than one,
-the OLS coefficient estimator is no longer
-consistent or asymptotically normal \citep{Hub:73} and has positive
-variance in the limit.  We show that, even so, the usual OOS average
-is asymptotically normal and can consistently estimate the difference
-between the models' generalization error, the expected loss in the
-future conditional on the data available in period
-$T$.%
-\footnote{See, for example, \citet{HTF:08} for a discussion of
-  generalization error.} %
-Under these asymptotics, the generalization
-error does not converge to the expected performance of the pseudotrue
-models, so existing in-sample and OOS comparisons measure different
-quantities and should be expected to give different results for
-reasons beyond simple size and power comparisons.  Under our limit theory,
-the model that is closer to the true DGP in population can forecast
-worse.  In such a situation, a standard in-sample comparison would
-correctly reject the null hypothesis that the benchmark is true, and
-an OOS comparison would correctly fail to reject the null that the
-benchmark is more accurate.%
-\footnote{In a pair of papers similar to
-  ours, \citet{ClM:12,ClM:12b} study in-sample and OOS tests that
-  the larger model has nonzero coefficients that are too close to zero
-  to expect the model to forecast more accurately.  Like this paper,
-  they argue that the larger model can be true but less accurate.
-  However, they focus on an aspect of the DGP that makes this
-  phenomenon likely, while we focus on the coefficient estimates that
-  produce less accurate forecasts.  Moreover, the implications of our
-  asymptotic theories are different and their papers do not provide
-  reasons to do OOS comparisons.} %
-Also note that, in this situation, a model that performs well
-in-sample can perform badly out-of-sample even if there are no
-structural breaks or other forms of instability.  Researchers
-have argued that a breakdown of in-sample forecasting ability
-indicates a structural break (see \citealp{BoH:99}, and
-\citealp{StW:03}, among others), but we show that this breakdown
-can be caused by overfit as well.
-
-It is important to realize that we are not \emph{advocating} linear
-regression for highly overparametrized models. If $K$ is very large
-relative to $T$, researchers will often want to use some form of
-shrinkage forecast, for example the LASSO \citep{Tib:96} or a factor
-model \citep{StW:02,BaN:02}. Our main focus is practical settings
-where $K$ is \emph{moderately} large and it is not clear whether
-overfit will dominate the results. In these settings it is
-crucial to understand the behavior of different evaluation criteria
-when $K$ is large, in case overfit does turn out to be a concern, and to have reliable
-methods for estimating these overfit models' performance. This is the goal of
-this paper.
-
-Our theoretical results partially justify OOS comparisons when
-researchers want to
-choose a model for forecasting.  Although there has been little
-emphasis on hypothesis testing in this setting, testing is usually
-appropriate: there is usually a familiar benchmark model in place, and
-the cost of incorrectly abandoning the benchmark for a less accurate
-alternative model is higher than the cost of incorrectly failing to
-switch to a more accurate alternative.  We show that the DMW test
-lets the forecaster control the probability of the first error, just
-as with conventional hypothesis testing.
-
-But we also identify new practical limitations for applying the DMW
-test to overfit models.
-Since the models' coefficients are imprecisely estimated in the limit,
-the test sample must be small enough that the model estimated over the
-training sample is similar to the one that will be estimated over the
-full sample.  In particular, $P/T \to 0$ is required for consistent
-estimation of the difference in the two models' performance,
-and $P^2/T \to 0$ is required for valid confidence
-intervals and inference.  For larger $P$, the OOS comparisons remain
-asymptotically normal, but are centered on the forecasting performance
-associated with the period $R$ estimates.  In practice, researchers
-typically use large values of $P$, so these studies may be too
-pessimistic about their models' future accuracy if they use the DMW
-test.  Section~\ref{sec:oostheory} lays out the asymptotic behavior of
-the DMW test under this limit theory.
-
-Popular in-sample tests and model selection criteria, like the Wald
-test and the AIC, do not help forecasters in this setting. We show
-that these statistics do not select the more accurate model when
-choosing between overfit models. For many DGPs the Wald test
-will choose the larger model over a small benchmark
-with probability much greater than its nominal size, regardless of
-which model is more accurate, and the AIC behaves similarly. The BIC,
-however, chooses the benchmark model with probability approaching one
-even when the \emph{alternative} model is more accurate.%
-\footnote{Our result holds for a broad class of full-sample
-  statistics, but there may be other potential statistics that mimic
-  the OOS test and remain valid. Exploring such statistics is left for
-  future research.} %
-This result holds even though modifications of the $F$-test are valid
-under this asymptotic theory, as shown by \citet{BoB:95},
-\citet{AkA:00}, \citet{AkP:04}, \citet{Cal:11c}, and \citet{Ana:12},
-among others.%
-\footnote{Also see \citet{Efr:86,Efr:04} for a discussion of naive
-  in-sample loss comparisons.} %
-Moreover, under this asymptotic theory, many recent OOS test
-statistics, such as those derived by \cite{ClM:01,ClM:05},
-\citet{Mcc:07}, and \citet{ClW:06,ClW:07} should have the same
-problems as in-sample tests.%
-\footnote{Our theoretical results apply directly to \citepos{Mcc:07}
-  OOS $t$-test, since it simply proposes more liberal critical values
-  for the same test statistic that we study.  Since
-  \citet{ClW:06,ClW:07} use a finite length estimation window, our
-  asymptotics are incompatible with theirs and prevent us from
-  studying their test directly, as well as \citepos{GiW:06} and other
-  tests based on \citepos{GiW:06} asymptotics.  But \clws\ test can be
-  viewed as a stochastic adjustment to the critical values of the
-  usual \oost\ test, so our conclusions should apply informally as
-  well.  Specifically, we show that the DMW test rejects with
-  probability equal to nominal size when the estimated benchmark model
-  is expected to be more accurate, so more liberal critical values
-  result in overrejection.} %
-These tests are also designed to reject the benchmark when the
-alternative model is true, and so they may reject too often when the
-benchmark is misspecified but more accurate.  Obviously, since the
-distribution of these statistics converges to the normal when $P/T \to
-0$ (with the number of regressors fixed), these statistics behave like
-the DMW test when $P$ is small, but should overreject the benchmark
-when $P$ is large. Section~\ref{sec:insample} presents our theoretical
-results for full-sample statistics and Section~\ref{sec:mc} presents
-Monte Carlo evidence to support these claims.
-
-Finally, this paper introduces a new method of proof for OOS
-statistics.  We use a coupling argument (Berbee's Lemma, 1979) to show
-that sequences of OOS loss behave like mixingales when the
-underlying series are absolutely regular, even if the forecasts depend
-on non-convergent estimators.  Moreover, we also show that transformations of these
-processes behave like mixingales after they are appropriately recentered, so
-many arguments used to prove asymptotic
-results for Near Epoch Dependent (NED) functions of mixing processes
-can be used for these OOS processes with only slight modification.
-
-The rest of the paper proceeds as follows.
-Section~\ref{sec:assumptions} introduces our notation and assumptions.
-Section~\ref{sec:theory} gives the main theoretical results for the
-DMW OOS test, shows that standard in-sample tests reject the
-benchmark model too often when it is misspecified but more accurate than the
-alternative, and shows that standard model selection methods can run
-into similar problems. Section~\ref{sec:theory} also presents an
-example DGP that illustrates these results. Section~\ref{sec:mc}
-presents a Monte Carlo study supporting our theoretical results.
-Section~\ref{sec:empirics} applies the OOS statistic to
-\citepos{GoW:08} dataset for equity premium prediction, and
-Section~\ref{sec:conclusion} concludes.  Proofs and supporting results
-are listed in the Appendix.
-
-\section{Setup and assumptions}
-\label{sec:assumptions}
-
-The first part of this section will describe the environment in detail
-and set up our models and notation. The second part lists the
-assumptions underlying our theoretical results.
-
-\subsection{Notation and forecasting environment}
-
-We assume the following forecasting environment. There are two
-competing linear models that give forecasts for the target,
-$y_{t+\h}$:
-\begin{equation*}
-y_{t+\h} = x_{1t}'\theta_1 + \e_{1,t+h}, \quad\text{and}\quad
-y_{t+\h} = x_{2t}'\theta_2 + \e_{2,t+h};
-\end{equation*}
-$t = 1,\dots,T-h$, $\h$ is the forecast horizon and the
-variables $y_t$, $x_{1t}$, and $x_{2t}$ are all known in period $t$.
-The coefficients $\theta_1$ and $\theta_2$ minimize the population
-Mean Square Error, so
-\begin{equation*}
-  \theta_i = \argmin_\theta \sum_{t=1}^{T-\h} \E (y_{t+\h} - x_{it}'\theta)^2,
-\end{equation*}
-making $\e_{i,t+\h}$ uncorrelated with $x_{i,t}$; $\e_{i,t+\h}$ can exhibit
-serial correlation so both of the linear models may be misspecified.
-Let $\mathcal{F}_t = \sigma(y_1, x_1, \dots, y_t, x_t)$ be the information
-set available in period $t$,
-with $x_t$ the vector of all stochastic elements of $x_{1t}$ and $x_{2t}$ after
-removing duplicates, and let $\E_t$ and $\var_t$ denote the
-conditional mean and variance given $\mathcal{F}_t$.  The first model
-uses $K_1$ regressors, and the second uses $K_2$.  Without loss of
-generality, assume that $K_1 \leq K_2$. At least one of the models is
-overfit, which we represent asymptotically by letting $K_2$ grow with
-$T$ quickly enough that $\lim K_2/T$ is positive; $K_1$ may grow with
-$T$ as well. Since the models change with $T$, a
-stochastic array underlies all of our asymptotic theory, but we
-suppress that notation to simplify the presentation.
-
-In the settings we are interested in, a forecaster observes the data
-$(y_t,x_t)$ for periods 1 through $T$ and divides these observations
-into an estimation sample of the first $R$ observations and a test
-sample of the remaining $P$ observations. The forecaster then compares
-the models' performance over the test sample, which entails
-constructing two sequences of forecasts with a fixed-window
-estimation strategy,
-\begin{equation*}
-\hat y_{i,t+\h} = x_{it}'\hat{\theta}_{it}, \qquad \text{for } i=1,2;
-\ t = R+1,\dots,T-h,
-\end{equation*}
-where
-\begin{equation*}
-  \bh{it} = \Big(\sum_{s=1}^{R-\h} x_{is}x_{is}'\Big)^{-1} \sum_{s=1}^{R-\h}
-  x_{is} y_{s+\h}, \qquad \text{for } i=1,2;\ t = R+1,\dots, T - \h.%
-\footnote{It may not be clear why we are using the index $t$ in $\bh{it}$,
-    since $\bh{it} = \bh{iR}$ almost surely for all $t \leq T-h$.
-    But $\bh{it}$ will be defined for $t > T-\h$
-    soon and will not equal $\bh{iR}$ for those values of $t$.} %
-\end{equation*}
-
-The models are then compared by their forecast performance over the test
-sample. There are many statistics that have been considered in the
-literature, but we focus on perhaps the most natural, the DMW \oost\
-test \citep{DiM:95,Wes:96}.%
-\footnote{The core insights of our paper apply to other OOS statistics
-  as well.} %
-This statistic is based on
-the difference in the models' loss over the test sample, $\oosA$,
-defined as
-\begin{equation*}
-  \oosA \equiv P^{-1} \oosSum{t}{1} D_t
-\end{equation*}
-where
-\begin{equation*}
-  D_t = L(y_{t+\h} - x_{1t}'\bh{1t}) - L(y_{t+\h} - x_{2t}'\bh{2t}),
-\end{equation*}
-and $L$ is a known loss function. The \oost\ test is defined as
-$\sqrt{P} \oosA / \sh$, where $\sh^2$ is an estimator of the
-asymptotic variance of $\oosA$. (Possibly a Heteroskedasticity- and
-Autocorrelation-Consistent, or HAC, estimator.)
-
-Most theoretical research on these statistics, such as \citet{DiM:95}, \citet{Wes:96},
-and \cite{Mcc:07}, has focused on using the \oost\ statistic to test
-hypotheses about the pseudotrue values $\theta_1$ and $\theta_2$.  In
-particular, that research focuses on testing the null hypothesis that
-\begin{equation*}
-  \E L(y_{t+\h} - x_{1t}'\theta_{1}) = \E L(y_{t+\h} - x_{2t}'\theta_{2}).
-\end{equation*}
-But the population quantities in this equation do not determine which
-model is more accurate in practice. The models'
-accuracy will also depend on the specific estimates of $\theta_1$ and
-$\theta_2$ used to produce the forecasts.
-
-When the forecaster will use one of the models to make a number of
-predictions (call it $Q$) in the future, the quantity of interest
-becomes
-\begin{equation*}
-  \E_T \oosB = Q^{-1} \sum_{t=T+1}^{T+Q} \E_T D_t,
-\end{equation*}
-where $D_t$ is defined as before,
-\begin{equation*}
-  D_t = L(y_{t+\h} - x_{1t}'\bh{1t}) - L(y_{t+\h} - x_{2t}'\bh{2t}),
-\end{equation*}
-but now uses the full-sample estimates of the models' parameters,
-\begin{equation*}
-  \bh{it} = \Big(\sum_{s=1}^{T-\h} x_{is}x_{is}'\Big)^{-1} \sum_{s=1}^{T-\h}
-  x_{is} y_{s+\h}, \qquad \text{for } i=1,2;\ t = T+1,\dots, T + Q.
-\end{equation*}
-If $\E_T \oosB$ is positive, the second model is expected to forecast
-better than the first over the next $Q$ periods, and if $\E_T \oosB$
-is negative then the first model is better. We use a conditional
-expectation because the coefficient estimates in $\oosB$ are
-stochastic but known in period $T$, and their values will determine
-the performance of the two models.
-
-Under conventional fixed-$K$ asymptotic theory, $\E_T \oosB$ would
-converge in probability to the difference in the expected loss
-associated with the pseudotrue models,%
-\footnote{This statement is subject to the usual assumptions: some
-  form of stationarity, bounded moments, and weak dependence.} %
-\begin{equation}\label{eq:22}
-  \E L(y_{t+\h} - x_{1t}'\theta_{1}) - \E L(y_{t+\h} - x_{2t}'\theta_{2}).
-\end{equation}
-But if $K_2$ increases with $T$ these quantities can have different
-limits. For a simple example, assume squared-error loss, let $x_{1,t}
-= 1$ for all $t$, and let $(y_{t+\h},x_{2,t})$ be i.i.d. $N(0,
-\Sigma)$.  Then the difference between $\E_T \oosB$ and
-the in quantity~\eqref{eq:22} is
-\begin{align*}
-  \E_T \oosB - \big(\E L(y_{t+\h} - x_{1t}'\theta_{1}&) - \E L(y_{t+\h} - x_{2t}'\theta_{2})\big) \\
-  &= \big(\E_T (y_{T+\h+1} - \bh{1,T})^2 -
-     \E_T (y_{T+\h+1} - x_{T+1}'\bh{2,T})^2\big) \\
-     &\quad - \big(\E y_{T+\h+1}^2 - \E (y_{T+\h+1} - x_{T+1}'\theta_2)^2 \big)\\
-  &= (\bh{2,t} - \theta_2)' \var(x_{2,t})\, (\bh{2,t} - \theta_2) + o_p(1).
-\end{align*}
-This last term has expectation equal to $\var(y_T) \frac{K_2}{T - K_2 - 1}$ and
-would converge to zero in probability if $K_2$ were fixed, but does not when $\lim
-K_2 / T > 0$. In Section~\ref{sec:oostheory} we show that the \oost\
-statistic can estimate $\E_T \oosB$ under our increasing $K$
-asymptotics and does not estimate the expected loss associated with
-the pseudotrue coefficients.
-
-The conditional expectation $\E_T \oosB$ has been studied heavily in
-cross-sectional settings with independent observations. In such a
-setting, $\E_T \oosB$ is equal to the difference in the models'
-\emph{generalization error}, which has been used widely as a measure
-of model accuracy in the machine
-learning literature \citep[see][for further discussion]{HTF:08}.
-Moreover, with i.i.d. observations, the expectation of $\E_T \oosB$
-equals \citepos{Aka:69} Final Prediction Error (FPE). Both
-generalization error and FPE are defined by a model's
-performance on a new, independent, data set, but, for lack of a better
-term, we will call $\E_T \oosB$ the ``difference in generalization error''
-for the rest of the paper with hopefully no risk of confusion.
-
-Finally, define the following notation.  The $l_v$-norm for vectors in
-$\Re^p$ (with $p$ arbitrary) is denoted $\lvert \cdot \rvert_v$, and
-the $L_v$-norm for $L_v$-integrable random variables is $\lVert \cdot
-\rVert_v$.  The functions $\eigen_i(\cdot)$ take a square-matrix
-argument and return its $i$th eigenvalue (with $\eigen_{i}(A) \leq
-\eigen_{i+1}(A)$ for any matrix $A$).  All limits are taken as $T \to
-\infty$ unless stated otherwise.
-
-\subsection{Assumptions}
-\label{sec:asmp}
-
-The next conditions are assumed to hold throughout the paper.  The first
-assumption controls the dependence of the underlying random array.
-The second lays out the details of our asymptotic approximation.
-The third assumption controls the
-smoothness of the loss function and bounds the moments of the
-difference in the models' performance; the fourth assumption describes
-the behavior of the estimation and test windows.  And the last
-assumption describes the kernel used to estimate the OOS average's
-asymptotic variance.
-
-\begin{asmp}\label{asmp-1}
-  The random array $\{y_t,x_t\}$ is strictly stationary and absolutely regular
-  with coefficients $\beta_j$ of size $-\rho/(\rho-2)$; $\rho$ is
-  greater than two and discussed further in Assumption \ref{asmp-3}.
-\end{asmp}
-
-This assumption is a standard condition on the dependence of the
-underlying stochastic array. The only novelty is that we use
-absolute regularity instead of strong or uniform mixing as our
-weak dependence condition; absolute regularity admits a particular
-coupling argument, \emph{Berbee's Lemma} \citep[reproduced in this
-paper as Lemma A.1 for reference]{Ber:79} that is
-unavailable for strong mixing sequences. Absolute regularity
-implies uniform mixing but is more restrictive than strong mixing,
-so this assumption is not unduly strong.
-For a detailed discussion of these weak dependence conditions,
-please see \citet{Dav:94} or \citet{Dou:94}.
-
-Our strict stationarity assumption is also somewhat stronger than is
-typically used; \citet{Wes:96} and \citet{Mcc:07}, for example,
-present results assuming covariance stationarity of the loss
-associated with the pseudotrue models. We need to make a stronger
-assumption because we will need to prove asymptotic results when the
-$\bh{it}$ remain random---so we would need covariance stationarity to
-hold for almost all estimates of $\theta_i$ and not just for the
-pseudotrue value. The only way to guarantee that condition is to
-assume strict stationarity for the underlying stochastic processes.
-
-The next assumption describes our asymptotic experiment.
-\begin{asmp}\label{asmp-2}
-  The number of regressors for each model, $K_1$ and $K_2$, are less
-  than $R$ and $(K_2-K_0)/T$ is uniformly positive;
-  $K_0$ is the number of regressors shared by the two models ($(K_1 - K_0)/T$
-  may be uniformly positive as well, but is not required to be).
-
-  The variance of $y_{t+\h}$ given $\mathcal{F}_t$ is uniformly
-  positive and finite and all of the eigenvalues of the covariance
-  matrix of $x_t$ are uniformly positive and finite as well.
-  Moreover,
-  \begin{equation}
-    \eigen_{\max}(X_{iS}'X_{iS}) = O_{L_3}(S),
-  \end{equation}
-  \begin{equation}
-    \eigen_{\max}((X_{iS}'X_{iS})^{-1}) = O_{L_3}(1/S),
-  \end{equation}
-  \begin{multline}\label{eq:28}
-    \eigen_{\max}\Bigg(\E\Big(
-    \sum_{s,t=U}^{V-\h} \e_{i,s+\h} \e_{i,t+\h} x_{is}x_{it}'
-    \mBig
-    x_{i1},\dots,x_{i,U-1};
-    \sum_{s=U}^{V-\h} x_{is} x_{is}';
-    x_{i,V-\h+1},\dots,x_{i,T-\h}
-    \Big)\Bigg) \\
-    = O_{L_3}(\max(V-U, K_i)),
-  \end{multline}
-  and
-  \begin{multline}\label{eq:8}
-    \tr \E\Big(
-    \sum_{s,t=U}^{V-\h} \e_{i,s+\h} \e_{i,t+\h} x_{is}x_{it}'
-    \mBig
-    x_{i1},\dots,x_{i,U-1};
-    \sum_{s=U}^{V-\h} x_{is} x_{is}';
-    x_{i,V-\h+1},\dots,x_{i,T-\h}
-    \Big)\Bigg) \\
-    = O_{L_3}((V-U) \times K_i)
-  \end{multline}
-  for large enough $T$, where $S = R,\dots,T$, $1 \leq U \leq V - \h
-  \leq T - \h$, $i = 1,2$,
-  \[ X_{iS} \equiv [x_{i1} \quad \dots \quad x_{i,S-\h}]' \qquad
-  \text{and} \qquad \ep{iS} = (\e_{i,1+\h}, \dots, \e_{i,S})'.\]
-
-  Additionally, the Euclidean norms of the pseudotrue coefficients,
-  $\theta_1$ and $\theta_2$, satisfy $|\theta_1|_2 = O(1)$ and
-  $|\theta_2|_2 = O(1)$.
-\end{asmp}
-
-The assumption on $K_1$ and $K_2$ is crucial to the paper; we assume
-that the model complexity grows with $T$ fast enough to break
-consistency. This assumption is how we derive an asymptotic
-concept of ``overfit.''
-
-The assumption that $y_{t+\h}$ and $x_t$ have positive and finite
-variance is straightforward. The conditions on the eigenvalues are
-technical and control the behavior of the OLS estimator as the number
-of regressors gets large---the third and fourth assumptions are
-nonstandard but can be easily verified under, for example,
-independence. Section~\ref{sec:example} contains such an example. The
-restrictions on the pseudotrue coefficients ensure that the regression
-model doesn't dominate the variance of $y_{t+\h}$ in the limit.
-
-The next assumption establishes moment conditions for the OOS loss
-process and smoothness conditions for the loss function itself. The
-moment conditions are standard and apply to $D_t$, and the smoothness
-conditions are relatively weak.
-
-\begin{asmp}\label{asmp-3}
-  The loss function $L$ is continuous, has finite left and right
-  derivatives, and $L(0) = 0$.  There is a constant $B_L$ and a
-  function $L'$ that bounds the left and right derivative of $L$ at
-  every point such that $\|D_t\|_\rho \leq B_L$; $\|D_t^*\|_\rho \leq
-  B_L$ for all $t$, where
-  \begin{equation}
-    D_t^* = L(y^* - x_1^{*\prime}\hat\theta_{1t})
-    - L(y^* - x_2^{*\prime}\hat\theta_{2t})
-  \end{equation}
-  and $(y^*, x_1^*, x_2^*)$ equals $(y_t, x_{1t}, x_{2t})$ in
-  distribution but is independent of $\mathcal{F}_T$ ($\rho$ is defined
-  in Assumption~\ref{asmp-1}); and
-  \begin{equation}\label{eq:29}
-    \| L'(y^* - x_{i}^{*\prime} (\alpha \bh{iR} + (1-\alpha) \bh{iT})) \|_2
-    \leq B_L
-  \end{equation}
-  for any $\alpha \in [0,1]$.
-\end{asmp}
-
-The differentiability condition in Assumption~\ref{asmp-3} is weak and
-allows the loss function itself to be non-differentiable; for example,
-absolute error and many asymmetric loss functions satisfy this
-assumption. The assumption makes use of both $(y_{t+\h}, x_{1t},
-x_{2t})$ and $(y^*, x_1^*, x_2^*)$ because the period $t$ observations
-can be dependent on $\bh{iT}$ in complicated ways. When the underlying
-observations are independent these assumptions can simplify
-considerably.
-
-The next assumption controls the growth of the test and
-training samples.
-\begin{asmp} \label{asmp-4} (a) $P, R, Q \to\infty$ as $T \to
-  \infty$. (b) $P^2/T \to 0$ and $P/Q \to 0$ as $T \to \infty$.
-\end{asmp}
-
-The requirements that $P$ and $R$ grow with $T$ are common. Parts of
-the assumption are new, in particular the requirement that $P^2/T \to
-0$.  See Lemma~\ref{res-convergence} for a discussion of its
-implications.  In practical terms, this assumption requires that the
-test sample be large and that the training sample be much larger, by
-enough that including or excluding the test sample does not affect the
-estimates of $\theta_1$ or $\theta_2$ very much.
-
-A final assumption restricts the class of variance estimators we will
-consider.  We use the same class of estimators studied by
-\citet{JoD:00} (their class $\mathcal{K}$); see
-their paper for further discussion.
-
-\begin{asmp}
-  \label{asmp-5} $W$ is a kernel from
-$\Re$ to $[-1,1]$ such that $W(0) = 1$, $W(x) = W(-x)$ for all $x$,
-\begin{equation}
-  \int_{-\infty}^{\infty} \lvert W(x) \rvert dx < \infty, \quad
-  \int_{-\infty}^{\infty} \lvert \psi(x) \rvert dx < \infty
-\end{equation}
-with
-\begin{equation}
-  \psi(x) = \frac1{\sqrt{2\pi}} \int_{-\infty}^{\infty} W(z) e^{ixz}dz,
-\end{equation}
-and $W(\cdot)$ is continuous at zero and all but a finite number of
-points.
-\end{asmp}
-
-These assumptions are broadly similar to those existing in the
-literature, with some differences in our assumptions relating the
-estimated coefficients to future values of the DGP.
-Section~\ref{sec:example} contains an extended example that shows how
-these assumptions are satisfied in a simple setting.
-
-\section{Theoretical results}
-\label{sec:theory}
-
-This section lays out our theoretical results. The first subsection
-presents results for the DMW \oost\ test; we show that it is
-asymptotically normal when one or both forecasting models is overfit.
-(i.e., under our increasing-$K$ asymptotic approximation.) We also
-present a new limitation on these statistics---OOS comparisons heavily
-penalize overfit models unless the size of the test sample is a very
-small proportion of the total sample size, which will not be practical
-in much applied research. The second subsection presents results for
-full-sample statistics and shows that widely used test statistics and
-model selection criteria are misleading when choosing a model for
-forecasting. In contrast to OOS comparisons, these full-sample
-criteria choose overfit models too often, even when they are less
-accurate than simple benchmark models. These results are somewhat
-abstract, so the third subsection works through an example DGP in
-detail.
-
-\subsection{Asymptotic normality of the DMW test}
-\label{sec:oostheory}
-
-This section has two main conceptual results. The first,
-Lemma~\ref{res-mixingale}, shows that the OOS average, $\oosA$, is
-asymptotically normal as the size of the test sample grows, even when
-the models are overfit. But $\oosA$ is centered at $\E_R \oosA$, the
-difference in the generalization error of the models estimated over
-the \emph{training sample}, which is not the quantity of interest to
-forecasters. Forecasters will generally want to estimate or test
-hypotheses about the difference in the generalization error of the
-models estimated with the full sample, $\E_T \oosB$. Our second
-result, Lemma~\ref{res-convergence}, shows that these quantities are
-approximately equal only when the test sample is very small relative
-to the total sample size. In particular, we show that $\oosA$ is a
-consistent estimator of $\E_T \oosB$ when $P/T \to 0$ and is
-asymptotically normal with mean $\E_T \oosB$ when $P^2/T \to 0$. After
-establishing these Lemmas, we then show that the \oost\ test is
-asymptotically standard normal and can be used to test hypotheses
-about $\E_T \oosB$, which requires the two Lemmas as well as a
-consistent estimator of the variance of the OOS average.
-
-In the first result, we show that
-$\sqrt{P} (\oosA - \E_R \oosA)$ is asymptotically normal as $P \to
-\infty$. This application of the CLT is complicated by a hidden source
-of dependence---the training sample estimators $\bh{iR}$. Under
-conventional asymptotic theory, we would replace each $\bh{iR}$ with
-its pseudotrue value $\theta_i$ and apply the CLT to
-$L(y_{t+\h} - x_{it}'\theta_i)$, with some complications potentially
-arising from the replacement (as in \citealp{Wes:96},
-\citealp{ClM:01}, or \citealp{Mcc:07}, for example). But we can not
-make that replacement here, because our asymptotic approximation
-prevents $x_{it}'\bh{iR}$ from converging to $x_{it}'\theta_i$.
-
-Instead, we show that $D_t - \E_R D_t$ is an $L_2$-mixingale that
-satisfies the CLT. Mixingales satisfy a weak-dependence condition
-similar to MDSes,%
-\footnote{An array $Z_{n,t}$ and an increasing sequence of \sfields
-  $\Gs_{n,t}$ is an \emph{$L_2$-mixingale of size $-1/2$} if there is
-  an array of constants $\{c_{n,t}\}$ and a sequence of constants
-  $\zeta_l = O(l^{-1/2 - \delta})$ for some $\delta > 0$ such that
-  \begin{equation*}
-    \lVert \E(Z_{n,t} \mid \Gs_{n,t-l}) \rVert_2
-    \leq c_{n,t} \zeta_l
-    \qquad\text{and}\qquad
-    \lVert Z_{n,t} - \E(Z_{n,t} \mid \Gs_{n,t+l}) \rVert_2
-    \leq c_{n,t} \zeta_{l+1}.
-  \end{equation*}
-  Mixingales were introduced and developed by
-  \citet{Mcl:74,Mcl:75,Mcl:75b,Mcl:77}.} %
-but they have some limitations. Transformations of mixingales are
-typically not themselves mixingales, which means that CLTs for
-mixingale processes require additional assumptions to hold beyond the
-mixingale property.%
-\footnote{See \citet{Jon:97} for an illustration. We will borrow
-  heavily from his results in our proofs.} %
-This is in contrast to Near Epoch Dependent (NED) processes, which
-retain the NED property after transformations. \citep[See chapter 17
-of][for further discussion of these properties.]{Dav:94} But the OOS
-loss has more structure than most mixingales and behaves like an NED
-process in important respects. (The key result here is
-Lemma~\ref{lem:a2} in the Appendix.) Lemma~\ref{res-mixingale} presents the
-CLT that we use later, and Section~\ref{sec:example} works through an
-i.i.d. example in detail. For i.i.d. observations, the OOS loss is an
-MDS and is easier to work with.
-
-\begin{lem}\label{res-mixingale}
-  If Assumptions~\ref{asmp-1}--\ref{asmp-3} hold then $\{D_t - \E_R
-  D_t, \mathcal F_t\}$ is an $L_2$-mixingale of size $-1/2$.
-  Moreover
-  \begin{equation}
-    \sqrt{P}(\oosA - \E_R \oosA)/\sigma \to^d N(0,1)
-  \end{equation}
-  as $P \to \infty$ if $\sigma^2$ is uniformly almost surely positive,
-  where $\sigma^2 = \var_R(\sqrt{P} \oosA)$ (which is equal to $P
-  \E_R(\bar{D}_R - \E_R \bar{D}_R)^2$).
-\end{lem}
-
-It may be helpful to compare Lemma~\ref{res-mixingale} to the method
-of proof in \citet{GiW:06}. \citet{GiW:06} show that the OOS average
-is asymptotically normal when the forecasts are estimated with a fixed
-length rolling window. In that case, each $\bh{it}$ depends on only
-the most recent $R$ observations and, since $R$ is fixed in their
-theory, the forecast errors $y_{t+\h} - x_{it}'\bh{it}$ are themselves
-mixing processes. Transformations of their forecast errors are
-still obviously mixing processes and obey the CLT.
-
-In our paper, $R$ is not fixed and the forecast errors are not a
-convenient weakly-dependent process, since the estimation error in
-$\bh{it}$ introduces strong dependence. Consequently,
-transformations of the forecast errors are not weakly dependent
-either. But this additional dependence has a special form and can be
-removed by subtracting the conditional mean; specifically $g(y_{t+\h} -
-x_{it}'\bh{it})$ is not weakly dependent but $g(y_{t+\h} -
-x_{it}'\bh{it}) - \E_R g(y_{t+\h} - x_{it}'\bh{it})$ is.
-Assumptions~\ref{asmp-1}--\ref{asmp-3} allow us to show directly
-that $D_t - \E_R D_t$ and (crucially) $D^2_t - \E_R D_t^2$ are both
-weakly dependent mixingales, ensuring Lemma~\ref{res-mixingale}.
-
-The next Lemma connects $E_R \oosA$ to $\E_T \oosB$, the difference in
-the models' generalization error. Under conventional asymptotics,
-these quantities are generally close. But they are not for overfit
-models and the models will tend to forecast better when estimated over the
-full sample than over the training sample. Consequently, OOS
-comparisons will penalize overfit models too much unless the test
-sample is small relative to the total data set.
-
-\begin{lem} \label{res-convergence}
-  Under Assumptions \ref{asmp-1}--\ref{asmp-4}a,
-  \begin{equation}\label{eq:7}
-    \E_T \oosB - \E_R \oosA = O_p(\sqrt{P/T}) + o_p(P^{-1/2})
-    + o_p(Q^{-1/2}).
-  \end{equation}
-\end{lem}
-We can view $\E_T \oosB - \E_R \oosA$ as noise introduced by
-approximating the performance of the full-sample estimates with that
-of the partial-sample estimates. The key term on the RHS
-of~\eqref{eq:7} in practice is $O_p(\sqrt{P/T})$---unless $P/T$ is
-small, this noise dominates the OOS average, making it an inconsistent
-estimator of $\E_T \oosB$. The $o_p(P^{-1/2})$ term is completely
-unrestrictive in our applications because we will multiply the OOS
-average by at most $\sqrt{P}$ (for the CLT). And the $o_p(Q^{-1/2})$
-term has some implications for interpreting these results: we can only
-measure the average performance of the forecasting models for an
-extended period in the future, long enough that the future
-observations are essentially independent of the current
-information. For $Q=1$, for example, the dependence between
-$y_{T+\h+1}$ and the current information set $\Fs_T$ may be very
-strong.
-
-Finally, we can use Lemmas~\ref{res-mixingale}
-and~\ref{res-convergence} to show that the DMW test is asymptotically
-normal and centered at $\E_T \oosB$, as long as
-Assumption~\ref{asmp-4}b holds.
-
-\begin{thm}\label{res-oost}
-  Suppose that Assumptions \ref{asmp-1}--\ref{asmp-5} hold (including
-  \ref{asmp-4}b), that $\gamma \to \infty$ and $\gamma/P \to 0$ as $T
-  \to \infty$, and that $\sigma^2$ is uniformly a.s. positive. Define
-  $\sh^2$ to be the usual OOS HAC estimator of the asymptotic variance
-  of $\oosA$,
-  \begin{equation}
-    \sh^2 \equiv P^{-1} \oosSum{s,t}{1} (D_t - \oosA)(D_s - \oosA)
-    \vWeight.
-  \end{equation}
-  Then
-  \begin{equation}
-    \sqrt{P}(\oosA - \E_T\oosB)/\sh \to^d N(0,1).
-  \end{equation}
-\end{thm}
-
-The requirement that $\sigma^2$ be uniformly a.s. positive is not
-restrictive under our asymptotic theory. Since the models'
-coefficients are estimated with uncertainty in the limit, the two
-models give different forecasts even if they both nest the DGP.  This
-is intuitively similar to \citepos{GiW:06} rolling-window result, but
-comes from different asymptotic theory; Giacomini and White keep the
-variance of the OOS average positive by letting $P \to \infty$ with
-$R$ fixed; in this paper, $R \to \infty$ but the variance remains
-positive since $K \to \infty$ (quickly) as well.
-
-If $K_1$ and $K_2$ were finite, West's (1996) and McCracken's (2007)
-asymptotic theories would apply and the \oost\ test would remain normal as long
-as $P/T \to 0$, even if $\sigma^2 \to 0$. Under that asymptotic
-approximation, the variance will converge to zero whenever the true
-DGP is nested in both of the forecasting models. The same principles
-may also apply if $K_1$ and $K_2$ grow slowly, with $K_2/T \to
-0$. It is likely that a second order expansion along the lines of
-\citet{Mcc:07} would lead to asymptotic normality for that
-intermediate case, but we leave that issue to future research.
-
-Finally, Theorem~\ref{res:oostest} establishes that the DMW test can be
-use to construct confidence intervals for $\E_T \oosB$ and test
-hypotheses about $\E_T \oosB$. In particular, forecasters will often
-want to test the null hypothesis that $\E_T \oosB \leq 0$, meaning
-that the benchmark model is expected to be more accurate than the
-alternative model in the future.
-
-\begin{thm}\label{res:oostest}
-  Suppose that the conditions of Theorem
-  \ref{res-oost} hold. Then each of the usual Gaussian
-  confidence intervals,
-  \begin{gather}
-    [\oosA - z_{\alpha/2} \, \sh /
-    \sqrt{P}, \oosA + z_{\alpha/2} \sh / \sqrt{P}],\label{interval-twosided} \\
-    [\oosA - z_{\alpha} \, \sh / \sqrt{P}, +\infty), \label{interval-greater}
-    \intertext{and}
-    (-\infty, \oosA + z_{\alpha} \, \sh / \sqrt{P}],
-  \end{gather}
-  contains $\E_T\oosB$ with probability $\alpha$ in the limit, with
-  $z_{\alpha}$ the $1-\alpha$ quantile of the standard normal
-  distribution. If, in addition, $\lim \Pr[\E_T \oosB \leq 0]$ is
-  positive then
-  \begin{equation}\label{eq:23}
-    \lim \Pr[P^{1/2}\oosA/\sh > z_{\alpha} \mid \E_T
-    \oosB \leq 0] \leq \alpha.
-  \end{equation}
-\end{thm}
-\noindent
-The results for confidence intervals in Theorem~\ref{res:oostest}
-follow immediately from Theorem~\ref{res-oost},
-but~\eqref{eq:23} requires additional proof.
-
-\subsection{Failure of in-sample statistics for forecast evaluation}
-\label{sec:insample}
-
-In this subsection we look at the behavior of some full-sample
-statistics under the same asymptotic theory as before.  We show that
-these statistics, which include common tests such as the Wald test as
-well as model selection criteria such as the AIC, do not measure the
-models' generalization error and consequently do not indicate which
-model will be more accurate in the future. Some of these statistics
-will tend to choose the larger model regardless of which model will be
-more accurate in the future, whereas others tend to choose the smaller
-model.  This is a different issue than whether or not full-sample
-tests are valid for testing hypotheses about the pseudotrue
-coefficients of the models; as \citet{Cal:11c} and \citet{Ana:12}
-demonstrate, variations of the Wald test can be valid for those
-hypotheses under increasing-$K$ asymptotics.%
-\footnote{\citet{Ana:12} shows that the Wald test is invalid in
-  general and gives an adjustment that corrects the critical values;
-  he also shows that the $F$-test is asymptotically valid under
-  certain conditions on the distribution of the regressors.
-  \citet{Cal:11c} shows that the $F$-test is asymptotically invalid
-  without Anatolyev's constraint, even under homoskedasticity, and
-  provides a correction that gives valid tests.  Both papers only
-  consider independent observations.} %
-To simplify the presentation and the intuition we only derive results
-for nested models and for MSE loss, but the conclusions hold much more
-generally.%
-\footnote{In this section, we define $M_1 = [I_{K_1} \ 0_{K_1 \times (K_2 - K_1)}]$
-  and $M_2 = [0_{(K_2 - K_1) \times K_2} \ I_{K_2 - K_1}]$ as the
-  selection matrices that return the first $K_1$ and the last $K_2 -
-  K_1$ elements of $\theta_2$, and assume that the regressors are
-  ordered so that the first $K_1$ elements of $x_{2,t}$ correspond to
-  $x_{1,t}$.} %
-
-The full-sample statistics we study in this paper share a common
-property. They choose the alternative model when the distance between
-a subset of their coefficient estimates and the origin exceeds a
-threshold, and choose the benchmark otherwise. For the Wald test, for
-example, this threshold is chosen so that the test has correct size
-when those coefficients are zero in population. For small models that
-can be consistently estimated, these coefficient estimates are close
-to their true values and so this criterion can be a reasonable proxy
-for the relative accuracy of the larger model.
-
-But for overfit models, the estimates will typically be far from both
-their pseudotrue values and also from zero. In that case, the Wald test and
-the AIC will both tend to choose the larger model even when it is less
-accurate than the smaller benchmark model. This phenomenon is driven
-by the dimensionality of the alternative model, since there are more
-potential values of the coefficient estimator that are far from zero
-when it has many elements. The threshold for the Wald test and the AIC
-is set by construction to be a bounded distance from the origin, and
-every other statistic that shares this property has the same behavior
-and can reject the benchmark model with high probability, even when
-it is more accurate. This behavior is
-formalized in Theorem~\ref{res:insample1}.
-
-\begin{thm}\label{res:insample1}
-  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-4} hold and let
-  $\Lambda$ be a model selection statistic that takes the values zero
-  or one; $\Lambda = 0$ indicates that the benchmark model is chosen
-  and $\Lambda = 1$ indicates the alternative.  Moreover, assume that
-  $L(e) = e^2$ and that there exist a deterministic scalar $c$
-  and a sequence of possibly random matrices $V_T$ such that
-  \begin{equation}\label{eq:25}
-    \limsup_{T \to \infty}
-    \Pr[\Lambda \geq \1\{\bh{2T}'M_2' V_T M_2\bh{2T} > c \}]
-    \to 0
-  \end{equation}
-  where the eigenvalues of $V_T$ are uniformly bounded in probability,
-  $\plim \rank(V_T)/T > 0$, and neither $V_T$ nor $c$ depend on
-  $\theta$ or the value of $\bh{2T}$.
-
-  Then there exist DGPs satisfying these assumptions such that
-  \begin{equation}\label{eq:11}
-    \liminf_{T \to \infty} \E( \Lambda \mid \E_T \oosB \leq 0 ) \geq 1/2.
-  \end{equation}
-\end{thm}
-
-As we state above,~\eqref{eq:11} means that, with high probability,
-the benchmark model is rejected even when it is more accurate. In
-general, $\delta$ can be made arbitrarily small by increasing the
-region enclosed by $\1\{\bh{2T}'M_2' V_T M_2\bh{2T}\}$ and DGPs can be
-chosen to put the limiting quantity in~\eqref{eq:11}
-arbitrarily close to 1 while still satisfying
-the assumptions of the Theorem.  The DGPs and
-statistics used in Theorem~\ref{res:insample1} are simple and
-common. They include correctly specified linear models with normal and
-homoskedastic errors; and the statistics that meet the restrictions on
-$\Lambda$ include the $F$-test and AIC.
-
-For example, the $F$-statistic for the null hypothesis that the
-benchmark model is correctly specified is known to have the form
-\begin{equation*}
-  F = \frac{\bh{2T}' M_2' ( M_2 (X_{2T}'X_{2T})^{-1} M_2' )^{-1} M_2
-    \bh{2T}}{s^2 (K_2 - K_1)}
-\end{equation*}
-where $s^2$ is the usual estimator of the variance of the regression
-error. Then let $c$ be any number greater than 1 and define
-\begin{equation*}
-  V_T = M_2' \big( M_2 \big(\tfrac{1}{s^2 (K_2 - K_1)} X_{2T}'X_{2T}\big)^{-1}
-  M_2' \big)^{-1} M_2'.
-\end{equation*}
-If Assumption~\ref{asmp-2} holds and $s^2$ is consistent then $V_T$
-has uniformly bounded eigenvalues and has rank $K_2 - K_1$, so it
-satisfies~\eqref{eq:25}.
-Robust variations of the Wald test can obviously satisfy~\eqref{eq:25}
-for similar reasons, and the AIC for nested linear models is
-equivalent to using the $F$-test with the critical value %
-$(e^{2 (K_2 - K_1) / T} - 1) \cdot (T - K_2) / (K_2 - K_1)$, %
-which converges to a finite limit, so the AIC satisfies~\eqref{eq:25}
-as well.
-
-For statistics that don't satisfy~\eqref{eq:25}, the behavior can be
-quite different. The BIC, for example, can also be written in terms of
-the $F$-statistic and is equivalent to using the critical value $(T \,
-e^{2 (K_2 - K_1) / T} - 1) \cdot (T - K_2) / (K_2 - K_1)$. This
-critical value diverges as $T \to \infty$, ensuring that~\eqref{eq:25}
-fails for any $c$. For this statistic, we have the opposite problem as
-before: when the alternative model is \emph{more} accurate, the
-coefficient estimates of the larger model are contained in a bounded
-region of the parameter space. Since the acceptance region of the BIC
-grows, it eventually contains \emph{any} bounded region of the
-parameter space. For large enough $T$, the BIC will always choose the
-\emph{smaller model}, even when the larger model is more accurate.
-
-This behavior is formalized in Theorem~\ref{res:insample2}.
-\begin{thm}\label{res:insample2}
-  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-4} hold, let $L(e) =
-  e^2$, and let $\Lambda$ be a model selection statistic as in
-  Theorem~\ref{res:insample1}. Also assume that, for any finite scalar
-  $c$,
-  \begin{equation}\label{eq:27}
-    \Pr[\Lambda \leq \1\{\bh{2T}'M_2'J M_2\bh{2T} > c \}] \to 1
-    \quad \text{as } T \to \infty.
-  \end{equation}
-
-  Then there exist DGPs satisfying these assumptions such that
-  \begin{equation}\label{eq:15}
-    \E( \Lambda \mid \E_T \oosB \geq 0 ) \to^p 0.
-  \end{equation}
-\end{thm}
-
-The condition~\eqref{eq:27} requires that the acceptance region of
-$\Lambda$ eventually contains any finite cylinder centered at the
-origin. Again,~\eqref{eq:15} implies that statistics like the BIC
-will always choose the smaller model for some DGPs, even when the
-larger model will give more accurate forecasts. Both models may be
-overfit, in that both $K_1/T$ and $K_2/T$ may both be positive in the
-limit; the key is that $(K_2 - K_1)/T$ is also positive in the limit.
-
-It is important to remember that previous research, such as
-\citet{Cal:11c} and \citet{Ana:12}, does not predict these
-results. When $\Lambda$ represents a test statistic, the test may have
-correct size for the null hypothesis that the additional coefficients
-on the larger model are zero. The results in this subsection are being
-driven by the full-sample statistics' behavior when the smaller model
-is misspecified but more accurate.
-
-Any statistic that uses the distance of the models' estimated
-coefficients from a set point (the origin being the most common) is
-poorly suited for choosing between overfit forecasting models. These
-models only forecast well when their coefficient estimates are close
-to their pseudotrue values, which can be far from the origin or any
-other prespecified
-point. Depending on the statistic, it can be biased towards choosing
-the larger model or the smaller model. Formal in-sample \emph{tests}
-will likely be biased towards the larger model, as we show for the
-$F$-test and Wald test in Theorem~\ref{res:insample1}.
-
-\subsection{An extended simple example}
+\section{An extended simple example}
 \label{sec:example}
 
-This subsection illustrates the previous theoretical results with a
+This section illustrates the previous theoretical results with a
 concrete example. Let $L(e) = e^2$ and $h = 1$. Suppose that the benchmark is
@@
 
-The first part of this subsection shows how the assumptions in
+The first part of this section shows how the assumptions in
 Section~\ref{sec:asmp} are satisfied and the second part
@@
 
-\subsubsection*{Fulfillment of Assumptions 1--5}
+\subsection{Fulfillment of Assumptions 1--5}
 
@@
 
-\subsubsection*{Asymptotic normality of the OOS average, Lemma 1}
+\subsection{Asymptotic normality of the OOS average, Lemma 1}
 
-This subsection walks through Lemma 1's CLT. Since the observations in
+This section walks through Lemma 1's CLT. Since the observations in
 this example are i.i.d., we do not need to use mixingale theory to
@@
 
-\subsubsection*{Convergence of $\E_R \oosA$ to $\E_T \oosB$, Lemma 2}
+\subsection{Convergence of $\E_R \oosA$ to $\E_T \oosB$, Lemma 2}
 
-This subsection works through Lemma~\ref{res-convergence}. In this
+This section works through Lemma~\ref{res-convergence}. In this
 example, the difference between $\E_R \oosA$ and $\E_T \oosB$ equals
@@
 
-\subsubsection*{Behavior of the F-test}
+\subsection{Behavior of the F-test}
 
@@
 selects the alternative once $T$ is large enough.
-\section{Monte Carlo}
-\label{sec:mc}
-
-This section presents two simulations that investigate the accuracy of
-our theory in small samples.
-We do several Monte Carlo exercises. The first looks at whether our
-theoretical results for the OOS average are accurate: whether or not
-the OOS average is approximately normal, and whether it is centered on
-$\E_R \oosA$, $\E_T \oosB$, or somewhere else entirely. The second
-issue is whether or not the \oost\ test is \emph{useful} for
-conducting inference about $\E_T \oosB$. Our theoretical results
-suggest that it may not be, because we require $P^2/T \to 0$ for
-inference about $\E_T \oosB$ to be valid. A highly related issue is
-whether other statistics are useful for conducting inference about
-$\E_T \oosB$---again, our theoretical results suggest that they are
-not.
-
-We use the same DGP for all of these simulations, and it is described
-in the next subsection. Results are presented in the subsection after
-that. Simulations were conducted in R \citep{Rde:10} using the
-\emph{MASS} \citep{VeR:02}, \emph{Matrix} \citep{BM:13}, and
-\emph{rlecuyer} \citep{SR:12} and graphs are produced using
-\emph{Lattice} \citep{Sar:10}. In this paper, we present results for
-the fixed window, but recursive window results are available in a
-separate Appendix and are similar.
-
-\subsection{Setup}
-\label{sec:simulation-design}
-
-The Monte Carlo experiment is intentionally very simple so that we can
-isolate the influence of the models' complexity.  In particular, we do
-not include some features that are common in forecasting
-environments---serial dependence, heteroskedasticity, and complicated
-DGPs. The DGP we use is given by the equation
-\begin{equation}\label{eq:6}
-  y_t = x_t'\theta + \e_t,\quad \e_t \sim N(0,1),
-  \quad t=1,\dots,T.
-\end{equation}
-The first element of $x_t$ is 1 and the remaining $K_2-1$ elements are
-independent Standard Normal.  The benchmark model is
-\begin{equation}
-  \label{eq:1}
-  y_{1t} = \sum_{j=1}^{K_1} x_{jt}\theta_j + \e_t
-\end{equation}
-and the alternative model is the DGP \eqref{eq:6}.  We let
-$(K_1,K_2)$ equal either $(2,3)$ or $(T/20,T/10)$ to study our theory
-in its intended application as well as for more parsimonious models.
-We let $T$ equal 100, 250, or 500.  We also vary $\theta$, and do
-so giving the benchmark and the alternative model comparable weight in
-predicting $y_t$.  Specifically, we set
-\begin{equation*}
-  \theta_j =
-\begin{cases} \frac{c}{\sqrt{K_1}} & j = 1,\dots,K_1 \\
-\frac{c}{\sqrt{K_2 - K_1}} & j = K_1 + 1,\dots,K_2 \end{cases}
-\end{equation*}
-with $c$ equal to zero or one.  When $c$ is one, we're more likely to
-draw values of $X$ and $Y$ that make the estimated larger model more
-accurate than the benchmark, and when $c$ is zero we're unlikely to
-draw such values of $X$ and $Y$.  For all of the studies, $L(e) =
-e^2$.
-
-To study the accuracy of our theoretical approximations, we first
-estimate the coverage probabilities of OOS confidence intervals for
-$\E_R \oosA$ and $\E_T \oosB$. For each draw of $X$ and $Y$, we
-construct the one-sided OOS interval defined in
-Theorem~\ref{res:oostest}:
-\begin{equation*}
-  [ \oosA - 1.28 \hat{\sigma}, \infty) \quad\text{with}\quad
-  \sh^2 = \frac1P \sum_{t=R+1}^T (D_t - \oosA)^{2}
-\end{equation*}
-for $P = 10,\dots,2T/3$; we then calculate the percentage of
-simulations where these intervals contain $\E_R \oosA$ and the
-percentage that contain $\E_T \oosB$.  Since the data are i.i.d., both
-of these quantities are easy to calculate (see
-Section~\ref{sec:example}). For these calculations, we draw 2000
-samples for each combination of the design parameters.
-
-Our second set of results studies whether these different OOS and
-in-sample statistics are valid for testing the null hypothesis
-\begin{equation*}
-  H_0:\quad E_T \oosB \leq 0,
-\end{equation*}
-namely that the benchmark model is expected to be more accurate in the
-future than the alternative. Informally, we are interested in whether
-the conditional probability
-\begin{equation*}
-  \Pr[\text{test rejects} \mid E_T \oosB \leq 0] \leq \alpha
-\end{equation*}
-where $\alpha$ is the nominal size of the test. If this inequality
-does not hold, the test statistic is rejecting the benchmark model too
-often.
-
-We look at four different statistics---the full-sample $F$-test, the
-DMW $t$-test, the OOS $t$-test using McCracken's (2007) critical
-values,%
-\footnote{These critical values are not published for $K_2-K_1>10$, so
-  we do not report them for $K_2 = T/10$.} %
-and Clark and West's (2006, 2007) Gaussian out-of-sample statistic.%
-\footnote{Clark and West (2006, 2007) derive their statistic using the
-  rolling window estimation scheme. Here we use the same statistic,
-  but with a fixed window scheme. A supplemental appendix presents
-  results for their statistic, using the recursive window.} %
-For the $F$-test, we simply test whether the coefficients on the
-larger model are nonzero.  For the out-of-sample tests, we conduct a
-one-sided test of out-of-sample performance for every value of $P$ as
-before. For each of these simulations, we discard draws from the DGP
-that violate the null hypothesis $E_T \oosB \leq 0$ and then use the
-remaining samples to calculate the conditional probability that each
-test rejects. The simulations end when 2000 draws have been retained
-for each choice of the design parameters.
-
-\subsection{Results}
-
-We discuss results for the confidence intervals first.
-Figures~\ref{fig:interval-R} and~\ref{fig:interval-T} show the
-coverage probability of these intervals as a function of $P$ for each
-combination of $T$, $K_1$ and $K_2$, and $c$.  The nominal coverage is
-90\% and is represented with a gray horizontal line. Each panel
-displays the coverage for a different choice of design parameters.
-
-Figure~\ref{fig:interval-R} gives the results for $\E_R \oosA$.  The
-actual coverage is very close to the nominal coverage except when $P$
-is very small.  The poor behavior for small $P$ is unsurprising, as it
-simply means that the CLT is a poor approximation when the test sample
-is small. The interval for $T = 100$, $K = T/10$, and $c = 0$ is the
-worst, with actual coverage near 85\% for most values of $P/T$. But
-the others are much closer to nominal coverage, even for the
-parsimonious models ($K_1=1$ and $K_2= 3$) where one might expect
-the theoretical results to break down.
-
-Figure~\ref{fig:interval-T} gives the results for $\E_T \oosB$.  In
-columns 2 and 4---the overfit models---the coverage is near nominal
-coverage for moderately small values of $P$.  As $P$ increases to
-$2T/3$, the coverage increases above nominal size; near 100\% for some
-DGPs.  With the parsimonious model, the coverage is near nominal
-coverage for all $P$ for the one-sided interval with $c=1$, but only
-for moderately small $P$ when $c=0$.
-
-The behavior for $K_2 = T/10$ is exactly what our theory predicts.
-When $P^2/T$ is small, the coverage is close to nominal levels.  The
-behavior as $P$ increases, combined with the results for $\E_R \oosA$,
-indicate that typically $\E_T \oosB \geq E_R \oosA$.  Since
-\begin{equation*}
-  E_{T} \oosB = E_{R} \oosA + (E_{T} \oosB - E_{R} \oosA),
-\end{equation*}
-and the interval is approximately centered at $\E_R \oosA$, the
-difference $\E_{T} \oosB - E_{R} \oosA$ adds a substantial positive
-quantity when $P^2/T$ is not near zero, increasing the coverage of the
-one-sided interval.
-
-We present the size simulations next, in
-Figures~\ref{fig:ftest}--\ref{fig:ttest-power}.  For the OOS tests
-we plot each OOS test's conditional rejection probability,
-\begin{equation*}
-  \Pr[\text{test rejects} \mid E_T \oosB \leq 0],
-\end{equation*}
-for each combination of $T$, $K_1$, $K_2$, and $c$ as a function of
-$P$.  The $F$-test does not depend on $P$, so we calculate and
-tabulate it's conditional rejection probability as a single value for
-each combination of design parameters.
-
-Table~\ref{fig:ftest} summarizes the simulation results for the
-$F$-test. For $c = 0$, the estimated conditional rejection probability
-is almost exactly equal to the test's nominal size (10\%), which is
-unsurprising.  For $c = 0$, the $F$-test is exact; moreover, the
-larger model will almost always be less accurate than the smaller one,
-so conditioning on $\E_T \oosB \leq 0$ is almost unrestrictive.  When
-$c$ increases, though, the $F$-test overrejects badly---rejecting at
-roughly 50\% when $c = 1$ for the parsimonious model and from 70\% to
-100\% for the overfit model. This agrees with our
-Section~\ref{sec:insample} results and matches results seen in
-empirical practice: the $F$-test rejects the benchmark with very high
-probability, even though it is, by construction, more accurate than
-the alternative model.
-
-Figure~\ref{fig:ttest-size} presents the size estimates for the DMW
-\oost\ test.  Again, different panels display results for different
-combinations of the design parameters.  Each graph plots the rejection
-probability against $P/T$.  For $K/T=10$, the rejection probability
-falls as $P/T$ increases, from near nominal size when $P/T$ is small
-to zero when $P/T$ is near $2/3$.  Moreover, the rejection probability
-falls faster when $T$ is large, as our theory predicts.  When $K=3$,
-the rejection probability stays closer to nominal size, but falls with
-$P/T$ for $c=0$, under-rejecting by about 5pp when $P/T = 2/3$, and
-rises with $P/T$ for $c=1$, overrejecting by about 10pp when
-$P/T=2/3$.  For small $P$, the rejection probability is near 10\% for
-all simulations (the farthest is $K=T/10$, $c=0$, where the rejection
-probability is about 5\%; the other simulations are much closer).
-
-We observe the following patterns.  The
-DMW test has close to nominal size when $P$ is small for every
-combination of design parameters.  In most cases, the rejection
-probability decreases as $P/T$ increases---the exception is for $K_2 =
-3$ and $c=1$.  For the large-$K$ simulations, the rejection
-probability drops to zero for most of the simulations as $P/T$
-increases.  The rejection probability increases with $c$, but the
-rejection probability still is near nominal probability for small $P$
-with $c=1$.
-
-Clark and West's (2006, 2007) statistic, presented in
-Figure~\ref{fig:clarkwest}, behaves quite differently.  For $c=0$ the
-test is correctly sized for both the overfit and parsimonious studies,
-as we saw for the $F$-test.  When $c=1$, the rejection probability
-increases rapidly with $P/T$.  For $K_2=3$, the rejection probability
-is near 10\% when $P$ is small but about 40\% when $P/T = 2/3$.  For
-$K=T/10$, the rejection probability is even higher and increases with
-$T$ as well, from a maximum over 50\% when $T=100$ to a maximum of
-nearly 100\% when $T=1000$.
-
-Results using \citepos{Mcc:07} critical values are presented in
-Figure~\ref{fig:mccracken} and are similar to those using Clark and
-West's test.  For $c=0$ the rejection probability is nearly the test's
-nominal size.  For $c=1$, the rejection probability increases with
-$P/T$, from close to the nominal size when $P/T$ is small to over 25\%
-when $P/T = 2/3$.  Note that all of the simulations use the
-parsimonious model.  McCracken's statistic overrejects here by
-slightly less than Clark and West's, but still by a substantial
-amount. Note that we are unable to plot results for McCracken's
-statistic when $K/T = 10$, which is where the breakdown in Clark and
-West's test is most pronounced.
-
-Since the DMW test tends to have low rejection probability, the test's
-power is a concern.  Figure~\ref{fig:ttest-power} power results for
-the DMW test, simulating from \eqref{eq:1} with $c = 1$ or 2 subject
-to the constraint that $\E_T \oosB > 0$.%
-\footnote{Draws of $X$ and $Y$ with $\E_T \oosB > 0$ are very rare
-  when $c=0$, so we do not present results for that value of $c$.} %
-Since the other test statistics greatly overreject, we do not present
-their power.  For $c=1$, the power is never greater than nominal size
-and decreases to zero as $P/T$ increases for the overfit model.  For
-$c=2$ the power is better, increasing with $P/T$ at first stretch and
-then decreasing as $P/T$ grows beyond approximately 1/4 for the
-overfit model.  Larger values of $T$ give a higher peak and greater
-power overall, but the power still falls to nearly zero if $P/T$ is
-too large (approximately 2/3 in our simulations).  The power with the
-parsimonious model is typically quite low but greater than nominal
-size for $c = 2$.
-
-Both sets of simulations support our theoretical results.  The first
-simulation confirms that the DMW OOS $t$-test is centered at $\E_R
-\oosA$ for all choices of $P$ and $R$ and is centered on $\E_T \oosB$
-only when $P$ is small.  The second simulation confirms that the DMW
-test has correct size for the null hypothesis that $\E_T \oosB \leq 0$
-when $P$ is small and that tests designed to test whether the
-benchmark is true, like the $F$-test and Clark and West's (2006, 2007)
-and McCracken's (2007) OOS tests can reject by much more than their
-nominal size when testing the null $\E_T \oosB \leq 0$.  Moreover,
-these simulations demonstrate that the restriction that $P$ be small
-is binding in practice, as the DMW test under-rejects and has very low
-power when $P$ is too large.
-
-\section{Empirical analysis of equity premium predictability}
-\label{sec:empirics}
-
-This section presents a study of equity premium predictability based
-on \citet{GoW:08}. Goyal and Welch conduct an out of sample analysis
-of 18 different variables thought, based on previous research, to
-predict the equity premium (calculated as the difference between the
-return on the S\&P 500 index and the T-bill rate).%
-\footnote{\citet{GoW:08} builds on previous research by \citet{BoH:99}
-  and \cite{GoW:03}.} %
-Their analysis has two notable features: Goyal and Welch compare different
-predictors across the same time periods and frequency as much as
-possible, making the accuracy of these predictors directly comparable;
-many of the papers that originally proposed these predictors used
-different time periods, methods, or observational frequencies so their
-results were not directly comparable. And Goyal and Welch compare
-these predictors out-of-sample; many of the original studies found
-in-sample evidence of equity premium predictability but did not look
-at out-of-sample evidence.
-
-Goyal and Welch consider many different models; most of them are very
-simple---regression onto a constant and a single stochastic
-predictor---but some are more complicated. They find that essentially
-none of the models outperform a simple benchmark, the prevailing mean
-of the equity premium, and conclude that these variables do not
-predict the equity premium. A large literature has subsequently sought
-to explain or rebut these results, including several responses to
-Goyal and Welch's original working paper published in the same special
-issue of \textit{The Review of Financial Studies} as \citet{GoW:08}.%
-\footnote{Those papers are \citet{CaT:08}, \citet{Coc:08},
-  \citet{BRW:08}, and \citet{LeN:08}.} %
-
-\citet{GoW:08}, as well as \citet{BoH:99}, \citet{LeN:08}, and many
-other authors, propose that instability could explain the OOS failure
-of these models. However, we have shown in this paper that overfit can
-also explain this pattern, significant in-sample results that do not
-hold up out of sample. In this section, we explore the extent to which
-overfit is a potential concern in this data set and estimate the
-expected forecasting performance of the largest model they consider, a
-model with 13 regressors, using 81 observations (annual data from 1928
-to 2009). The predictors are listed in Table~\ref{tab:equity}; please
-see Goyal and Welch's original paper for detailed information about
-these variables.%
-\footnote{Table~\ref{tab:equity} only lists the variables used in
-  \citepos{GoW:08} ``kitchen sink'' model.  Some of the variables that
-  they use are excluded from this model either
-  because the series are too short or because the variables are linear
-  combinations of other variables.} %
-
-\citet{GoW:08} focus primarily on univariate regression models of the
-form
-\[
-r_{t+1} = \beta_0 + \beta_1 x_{it} + \e_{t+1}
-\]
-using OLS with a recursive window, where $r_{t+1}$ is the equity
-premium and $x_{it}$ is one of the predictors listed in
-Table~\ref{tab:equity}.
-This focus is consistent with much of the rest of the literature. But
-it is not clear that this approach---using a large number of
-restricted models---is any more reliable than using a single, large
-model. Very few papers in the equity-premium predictability literature
-explicitly account for the multiplicity of model comparisons%
-\footnote{\citet{RaW:06}, \citet{RaZ:12}, and \citet{Cal:15} are
-  exceptions.} %
-and most widely-used statistics for multiple comparisons are
-derived under the assumption that there is a finite number of
-hypotheses or models (as is the case in \citealp{STW:99c},
-\citealp{Whi:00}, \citealp{Han:05}, and \citealp{LeR:05}), so there is
-little theoretical evidence that they are any more reliable than a
-regression model that encompasses all of the smaller models. Moreover,
-since \citet{GoW:08} (along with most of the rest of the literature)
-want to interpret these univariate regressions as meaningful
-statements about the true relationships between the equity premium and
-the regressors, omitted variable bias is a serious potential issue.
-
-For example, Table~\ref{tab:gwinsample} presents two full-sample
-coefficient estimates for each of the 12 predictors we consider.%
-\footnote{For all of our full sample results, we studentize the
-  regressors to make it easier to compare coefficient estimates and we
-  express the equity premium in basis points.} %
-The first column is the estimator of the coefficient on the
-variable in the full regression,
-\begin{equation*}
-  r_{t+1} = \beta_0 + \sum_{i=1}^{12} \beta_{i} x_{it} + \e_{t+1},
-\end{equation*}
-and the third column is the $p$-value associated with a two-sided
-$t$-test that the coefficient is zero in population. The second column
-is the estimator of the coefficient from the univariate regression
-\begin{equation*}
-  r_{t+1} = \alpha_i + \gamma_{i} x_{it} + \e_{t+1},
-\end{equation*}
-and the fourth column is the $p$-value associated with its $t$-test.%
-\footnote{All of the standard errors were calculated using a
-  Newey-West kernel with two lags.} %
-Some of the coefficient estimates agree, but some do not. The
-coefficient estimate for the \emph{default yield spread}, for example,
-is substantially and significantly negative in the full model ($-7.79$
-with $p$-value $0.042$), but is near zero in the univariate regression
-($0.79$ with $p$-value $0.720$). This pair of results implies that the
-the default yield spread contains information about the equity premium
-but is also correlated with other poor predictors, and that this
-additional correlation adds noise to the univariate regression
-and masks the true relationship. Similarly, \emph{net equity expansion}
-is significant at 10\% in the univariate regression but not in the
-full model ($p$-values of $0.060$ and $0.626$ respectively), which is
-likely attributable to omitted variable bias. So there is merit to
-studying a large model that includes all of the variables.
-
-Results for the full sample estimates of these models are in
-Table~\ref{tab:gwinsample}.%
-\footnote{Calculations in this section are done in R \citep{Rde:10}
-  using the \emph{lmtest} \citep{ZeH:02} and \emph{sandwich}
-  \citep{Zei:04} packages.}%
-\footnote{We compare the test statistic to critical values from the
-  $F$-distribution, which have been shown to be more reliable than
-  Chi-squared critical values when there are many regressors
-  \citep{Ana:12,Cal:11c}.} %
-The last rows of the table list measures of the full-model fit.  The
-$p$-value for the test of full model fit is very small (less than
-0.01), indicating that some of the coefficients are nonzero in
-population and at least one of these predictors is correlated with the
-equity premium.%
-\footnote{We have done additional analysis to try to identify which
-  predictors were correlated with the equity premium, but none of the
-  individual regressors were significant after correcting for
-  multiplicity. The Bonferroni correction, for example, suggests that
-  an individual $p$-value would need to be less than $0.10/12 \approx
-  0.0083$ for its corresponding coefficient to be significant at the
-  10\% level, but the smallest $p$-value is $0.035$. One can improve
-  on the Bonferroni correction, of course, but a comprehensive
-  analysis is beyond the scope of this paper.} %
-As we argue throughout the paper, this result does not imply that the
-model will forecast well.
-
-To determine whether the full model can forecast well, we use the DMW
-\oost\ test to compare it to a sample mean benchmark,
-\begin{equation*}
-r_{t+1} = \mu + \e_{1,t+1}.
-\end{equation*}
-Both models are estimated by OLS using the fixed-window scheme. We
-also present results for a restricted model proposed by
-\citet{CaT:08} that imposes that $\hat r_{t+1}$ be non-negative for
-each forecast.
-To study the effect of the training sample size on the DMW statistic, we
-calculate the one-sided confidence interval for $\E_T \oosB$ given
-by \eqref{interval-greater} corresponding to the null and alternative
-hypotheses
-\[ H_0: \quad E_T \oosB \leq 0 \qquad
-H_A: \quad E_T \oosB > 0
-\]
-using the fixed-window scheme for each value of $R$ between 20 and
-$T-10$. The standard deviation is estimated using a Newey-West
-estimator with $\lfloor P^{1/4}\rfloor$ lags.  For small values of
-$R$, the OOS average is expected to underestimate the performance of
-the larger model relative to the smaller, but this may not hold in
-this particular dataset. For the OOS results, we express the equity
-premium in percentage points.
-
-Figure~\ref{fig:empirics1} plots the OLS results and
-Figure~\ref{fig:empirics2} imposes \citepos{CaT:08} restriction. The
-solid line in each figure shows the OOS average, $\oosA$, and the
-shaded region indicates the 95\% one-sided confidence interval implied
-by the DMW test.  Negative numbers indicate that the full model has
-higher out-of-sample loss.  We can see that the same patterns hold for
-both models: the performance difference decreases as $R$ grows, but
-the full model is never more accurate.  We also see that the
-performance difference decreases suddenly over the period $R=29$ to
-$R=34$ (corresponding to the years 1956--1961).
-Figure~\ref{fig:empirics3} plots the accuracy of the individual
-forecasts (only for the linear models) and shows that this change is
-the result of a sudden improvement in the full model.  This change may
-indicate instability in the underlying relationship, as proposed by
-\citet{GoW:08}.
-
-In summary, we fail to reject the null that the benchmark prevailing
-mean model is more accurate than the full model including all of
-\citepos{GoW:08} predictors.  This result is consistent with Goyal and
-Welch's original analysis.  Unlike Goyal and Welch, we attribute this
-result, at least in part, to parameter uncertainty---the full sample
-results indicate that there is a true predictive relationship between
-some of these variables and the equity premium and the larger model
-could predict better than the benchmark with enough data.%
-\footnote{\citet{BWB:10} make a similar point about exchange rate
-  models, but see also \citet{Chi:10} and \citet{Gia:10}.} %
-These also indicate that combination or shrinkage estimators of the
-full model have the potential to significantly improve on the benchmark.%
-\footnote{See \citet{RaZ:12} for a recent review of this
-  literature.} %
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-This paper gives a theoretical motivation for using OOS comparisons:
-the DMW OOS test allows a forecaster to conduct inference about
-the expected future accuracy of his or her models when one or both is
-overfit.  We show analytically and through Monte Carlo that standard
-full-sample test statistics can not test hypotheses about this
-performance.
-
-Our paper also shows that popular test and training sample sizes may
-give misleading results if researchers are concerned about overfit.
-We show that $P^2/T$ must converge to zero for the DMW test to give
-valid inference about the expected forecast accuracy, otherwise the
-test measures the accuracy of the estimates constructed using only the
-training sample.  In empirical research, $P$ is typically much larger
-than this.  Our simulations indicate that using large values of $P$
-with the DMW test gives undersized tests with low power, so this
-practice may favor simple benchmark models too much.  Existing
-corrections, proposed by \citet{ClM:01,ClM:05}, \citet{Mcc:07} and
-\citet{ClW:06,ClW:07}, seem to correct too much, though, and reject
-too often when the benchmark model is more accurate.
-
-More work remains.  The requirement that $P^2/T$ converge to zero is
-limiting, as it implies that in typical macroeconomic datasets, only a
-handful of observations should be used for testing.  This requirement
-can be relaxed only slightly; $P = O(T^{1/2})$ is required for the
-OOS test to have nontrivial power in general, but there are loss
-functions and DGPs for which some relaxation is possible.  This
-constraint could be mitigated by extending our results to
-cross-validation or other resampling strategies, or by constructing
-full-sample statistics that allow inference about $\E_T \bar{D}_T$.
-It would also be useful to extend our results to other forecasting
-models and to explore how stationarity could be relaxed, but such
-extensions are less important than improving the available statistics.
-
-\appendix
-\section*{Appendix: mathematical details}
-\setcounter{section}{1}
-% Change lemma style to prepend 'A'
-\setcounter{lem}{0}
-\renewcommand{\thelem}{A\arabic{lem}}
-
-\subsection*{Supporting results}
-The results in this paper rely heavily on a coupling argument for
-absolutely regular sequences, Berbee's Lemma \citep{Ber:79}.  Many of
-the results of this paper (Lemma \ref{res-mixingale} and
-Theorem~\ref{res-oost}) use modifications of existing results
-for NED functions of mixing processes by \citet{Jon:97} and
-\citet{JoD:00}; this coupling argument is used to explicitly derive
-inequalities that arise naturally for NED processes.  Lemma
-\ref{lem-basic-coupling} establishes these inequalities, which are
-based on a proposition of \citet{MeP:02}.
-
-We present \citeauthor{MeP:02}'s
-(\citeyear{MeP:02}) statement of Berbee's Lemma for
-the reader's reference.  In the following Lemma, $\beta(X,Y)$ is the
-coefficient of absolute regularity:
-\begin{equation}
-\beta(X,Y) = \sup_{A \in \sigma(Y)} \E \lvert \Pr(A \mid \sigma(X))
-  - \Pr(A) \rvert.
-\end{equation}
-
-\begin{lem}\label{lem-berbee}\quad
-
-\begin{quotation}\noindent
-  Let $X$ and $Y$ be random variables defined on a probability space
-  $(\Omega, \mathcal{T}, \Pr)$ with values in a Polish space
-  $S$.  Let $\sigma(X)$ be a $\sigma$-algebra generated by $X$ and let
-  $U$ be a random variable uniformly distributed on $[0,1]$
-  independent of $(X,Y)$.  Then there exists a random variable $Y^{*}$
-  measurable with respect to $\sigma(X) \vee \sigma(Y) \vee
-  \sigma(U)$, independent of $X$ and distributed as $Y$, and such that
-  $\Pr(Y \neq Y^{*}) = \beta(X,Y)$.
-
-  \noindent\citep{MeP:02}
-\end{quotation}
-\end{lem}
-
-The advantage of this result over coupling arguments that use other
-forms of weak dependence is that the difference between the original
-variable, $Y$, and the new variable, $Y^{*}$, does not depend on their
-dimension.  Similar results for strong mixing sequences depend on the
-dimension of $Y$, which makes them unsuitable for this paper.
-
-\begin{lem}\label{lem-extend-mp}
-  Suppose that $X$ and $X^*$ are $L_p$-bounded random variables, with
-  $p > 2$, that satisfy ${\Pr[X \neq X^*] = c}$.  Then
-  \begin{equation}
-    \lVert X - X^* \rVert_2 \leq 2^{1/p} (\lVert X \rVert_p + \lVert
-    X^* \rVert_p) c^{(p-2)/2p}
-  \end{equation}
-\end{lem}
-
-The proof is virtually identical to the proof of Proposition 2.3 in
-\citet{MeP:02} and is omitted.
-
-\begin{lem}\label{lem-basic-coupling}
-  Suppose Assumptions \ref{asmp-1}--\ref{asmp-3} hold.  Then, for any
-  T, $s$, $t$, and $u$ with $s < t \leq u$, there exist random
-  variables $D_t^*,\dots,D_u^*$ such that
-  \begin{equation}\label{eq:coupling1}
-    P[(D_{t}^*,\dots,D_u^*) \neq (D_{t},\dots,D_u)] \leq \beta_{t-s}
-  \end{equation}
-  and
-  \begin{equation}\label{eq:coupling2}
-    \E(\phi(D_{t}^*,\dots, D_u^*) \mid \mathcal{F}_s ) =
-    \int
-    \phi(D_{t},\dots,D_u) f(\mathbf{x}, \mathbf{y})\ d\mathbf{x}\ d\mathbf{y}
-  \end{equation}
-  almost surely for all measurable functions $\phi$ such that the
-  expectations are finite, where
-  \[ \mathbf{x} = (x_{t}', \dots, x_{u}')', \qquad
-  \mathbf{y} = (y_{t+\h},\dots,y_{u+\h})',\] and $f$ is the
-  joint density of $(\mathbf{x}, \mathbf{y})$.  Moreover,
- \begin{equation}\label{eq:coupling3}
-   \| D_v^* - D_v \|_2 \leq 2^{1+1/\rho} B_L
-   \beta_{t-s}^{\rhoExp}, \qquad v = t,\dots,u.
- \end{equation}
-\end{lem}
-
-\begin{proof}
-  The proof follows as a consequence of Lemmas \ref{lem-berbee} and
-  \ref{lem-extend-mp}.  Let $l = u-t$.  For any fixed values of $l$
-  and $T$, the sequence of vectors
-  \[ V_{t} = (y_{t+\h}, x_{t}', \dots, y_{t+l+\h}, x_{t+l}') \] is
-  absolutely regular of size $\rho/(\rho-2)$.  Berbee's Lemma implies
-  that there is a random vector $V^*$ that is independent of
-  $\mathcal{F}_s$, equal to $V_{t}$ in distribution, and satisfies
-  \[\Pr[V^* \neq V_{t}] = \beta_{t-s}.\]
-
-  Now define
-  \begin{equation*}
-    D_v^* =
-    \begin{cases}
-      L(y_{v+\h}^* - x_{1v}^{*\prime} \hat{\theta}_{1R}) - L(y_{v+\h}^* -
-      x_{2v}^{*\prime} \hat{\theta}_{2R}) & v \leq T \\
-      L(y_{v+\h}^* - x_{1v}^{*\prime} \hat{\theta}_{1T}) - L(y_{v+\h}^* -
-      x_{2v}^{*\prime} \hat{\theta}_{2T}) & v > T
-    \end{cases}
-  \end{equation*}
-  with $y_{v+\h}^*$ and $x_{iv}^*$ denoting the elements of $V^*$
-  corresponding to $y_{v+\h}$ and $x_{iv}$ in $V_{t}$.  Equations
-  (\ref{eq:coupling1}) and (\ref{eq:coupling2}) are satisfied by
-  construction, and (\ref{eq:coupling3}) follows from Lemma
-  \ref{lem-extend-mp}.
-\end{proof}
-
-\begin{lem}\label{lem:a2}
-  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-3} hold.  Let $b_T$ be a
-  sequence of integers such that $b_T \to \infty$ and $b_T = o(P)$ and define
-  \begin{equation}
-    Z_i = \ZDef.
-  \end{equation}
-  Then
-  \begin{equation}
-    \label{eq:10}
-    \sum_{i=1}^{\lfloor P/b_T \rfloor} (\E_R Z_i^2 - \E_{R+(i-1) b_T}
-    Z_i^2) \to^p 0 \quad\text{ as } P \to \infty.
-  \end{equation}
-
-  If the assumptions of Theorem~\ref{res-oost} also hold, $b_T$ is
-  restricted further so that $b_T \equiv \lfloor \gamma/\delta
-  \rfloor$ for some positive scalar $\delta$, and we define
-  \begin{equation}\label{eq:13}
-    \kernelB{x} \equiv \kernelBDefn{x},
-  \end{equation}
-  then
-  \begin{equation}
-    \label{eq:12}
-    \vtSum (Z_{1t} Z_{2t} - \E_R Z_{1t} Z_{2t}) \to^p 0.
-  \end{equation}
-  where
-  \begin{gather}
-    Z_{1t} = \varianceTermIIIa,%
-    \intertext{and}%
-    Z_{2t} = \varianceTermIVb.
-  \end{gather}
-\end{lem}
-\begin{proof}
-\newcommand{\UFiltration}[1]{\ensuremath{\mathcal{F}_{(#1)b_{T}+R-P}}}%
-The first result,~\eqref{eq:10}, follows a similar argument to Lemma~5
-of \citet{Jon:97} and~\eqref{eq:12} to Lemma~A.4 of \citet{JoD:00}.
-Since these arguments are similar and our modification is the same for
-both, we'll just present the more complicated version,~\eqref{eq:12}.
-
-Note that $\{Z_{1t}^2 P\gamma_T/b_T\}$ and $\{Z_{2t}^2 P\gamma_T/b_T\}$
-are uniformly integrable.  As in~\citet[Lemma A.4]{JoD:00}, we can
-assume that there is a constant $C$ such that $Z_{1t}$ and $Z_{2t}$
-are bounded in absolute value by $C\sqrt{b_T/P\gamma_T}$; uniform
-integrability ensures that the difference between the unbounded random
-variables and these truncated versions is negligible for large enough
-values of $C$.
-
-Let $r = \lfloor 3P/2b_T \rfloor$ and rewrite the summation as
-\begin{align*}
-  \vtSum \vtIIIsummand &= \vtSumr \vtSuma \vtIIIsummand \\
-  &\quad+ \vtSumr \vtSumb \vtIIIsummand \\
-  &\quad+ \sum_{t=r b_T - P + R + 1}^{2P+R} \vtIIIsummand \\
-  &\equiv \vtSumr (U_i - \E_R U_i) + \vtSumr (U_i' - \E_R U_i') + o_{L_1}(1).
-\end{align*}
-The proof then holds if we can show that both $U_i$ and $U_i'$ obey
-LLNs.  We'll do so by proving that $\{U_i -\E_R U_i,
-\UFiltration{2i-1}\}$ and $\{U_i' - \E_R U_i', \UFiltration{2i}\}$ are
-$L_2$-mixingales of size $-1/2$ and using the bound $\E(\vtSumr (U_i -
-\E_R U_i))^2 = O(\vtSumr c_i^2)$ where the $c_i$ are the mixingale
-magnitude indices \citep{Mcl:75}.
-
-For non-negative $m$, we have
-\begin{equation*}
-U_i - \E_R U_i \in \UFiltration{2i+2m-1},
-\end{equation*}
-establishing half of the mixingale result trivially.  Now fix $i$ and $m >
-0$ and use Lemma \ref{lem-basic-coupling} to define $D_{ts}^*$
-for each $t =(2i-2)b_T-P+R+1,\dots,(2i-1)b_T-P+R$ and $s =
-\max(t-b_T,R+1),\dots,\min(t+b_T,T-\h)$ such that
-\begin{equation*}
- \E_R D_{ts}^* = \E_{(2i-2m-1)b_T+R-P} D_{ts}^* \quad a.s.
-\end{equation*}
-and
-\begin{equation*}
-  \lVert D_{ts}^* - D_s \rVert_2 \leq \couplingBound{s - (2i-2m-1)b_T+P}.
-\end{equation*}
-Also define
-\begin{equation*}
-  Z_{1t}^* = (P\gamma_T)^{-1/2} \sum_{l=\vttLower}^{\vttUpper}
-  (D_{t,t+l}^* - \E_R D_{t,t+l}^*)\ W(l/\gamma_T), \\
-\end{equation*}
-and
-\begin{equation*}
-Z_{2t}^* = (P\gamma_T)^{-1/2} \sum_{j=\vttLower}^{\vttUpper}
-    (D_{t,t+l}^* - \E_R D_{t,t+l}^*)\ \kernelB{j/\gamma_T}.
-\end{equation*}
-
-Now, we have the inequalities
-\begin{align*}
-  \lVert \E( U_i - \E_R U_i & \mid \UFiltration{2i-2m-1}) \rVert_2
-  \\ &\leq
-  \vtSuma \lVert \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) - \E_R
-  Z_{1t}Z_{2t} \rVert_2 \\
-  &= \vtSuma \lVert \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
-  &\quad - \E(Z_{1t}^* Z_{2t}^* \mid \UFiltration{2i-2m-1}) \\
-  &\quad + \E(Z_{1t}^* Z_{2t}^* \mid \UFiltration{2i-2m-1})
-  - \E_R Z_{1t}Z_{2t} \rVert_2 \\
-%  \leq \vtSuma (\wall \lVert \wall \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
-%  - \E(Z_{1t}^*Z_{2t}^* \mid \UFiltration{2i-2m-1}) \rVert_2\return
-%  \\ + \lVert \E_R Z_{1t}Z_{2t} - \E_R Z_{1t}^*Z_{2t}^*
-%  \rVert_2)\return \\
-  &\leq 2 \vtSuma \lVert Z_{1t} Z_{2t} - Z_{1t}^* Z_{2t}^*
-  \rVert_2 \\
-  &\leq 2 \vtSuma (\lVert Z_{1t} - Z_{1t}^* \rVert_2 \lVert
-  Z_{2t} \rVert_{\infty}
-  + \lVert Z_{2t} - Z_{2t}^* \rVert_2 \lVert Z_{1t}^* \rVert_{\infty}) \\
-  &\leq \frac{2 C b_T^{1/2}}{(P\gamma_T)^{1/2}} \vtSuma (\lVert Z_{1t} - Z_{1t}^* \rVert_2
-  + \lVert Z_{2t} - Z_{2t}^* \rVert_2).
-\end{align*}
-
-And we can finish the proof with the following inequalities:
-\begin{align*}
-  \frac{2 C b_T^{1/2}}{(P \gamma_T)^{1/2}} &\vtSuma \lVert Z_{1t} - Z_{1t}^* \rVert_2 \\& \leq
-  \frac{4C b_T^{1/2}}{P\gamma_T} \vtSuma \sum_{l=\vttLower}^{\vttUpper} \lVert
-  D_{t+l} - D_{t,t+l}^* \rVert_2 W(l/\gamma_T) \\&
-  \leq O\Bigg(\frac{b_T^{1/2}}{P\gamma_T}\Bigg) \vtSuma
-  \sum_{l=\vttLower}^{\vttUpper} \couplingBeta{t+l-(2i-2m-1)b_T+P}\\&
-  = O\Bigg(\frac{b_T^{1/2}}{P\gamma_T}\Bigg) O(b_T^{3/2-u}\, m^{-1/2-u})
-\end{align*}
-for some positive $u$.  The same argument holds for $Z_{2t}$.
-As a result,
-\[
-E\Big(\vtSumr (U_i - \E_R U_i)\Big)^2 = o\Big(\vtSumr b_T^2/P\gamma_T\Big) =
- o(b_T/\gamma_T) \to 0,
-\]
-as required.
-\end{proof}
-
-\begin{lem}\label{lem:a6}
-  Suppose the conditions of Theorem~\ref{res-oost} hold.
-  Then
-  \begin{equation}
-    \sh^2 - P^{-1} \sum_{s,t=R+1}^{T-h} (D_s - \E_R
-    D_s) (D_t - \E_R D_t) W((t-s)/\gamma) \to^{L_1} 0.
-  \end{equation}
-\end{lem}
-
-\begin{proof}
-   It follows from simple algebra that
-\begin{multline*}
-  \Big| \sh^2 -  P^{-1} \sum_{s,t=R+1}^{T-h} (D_s - \E_R
-    D_s) (D_t - \E_R D_t) W((t-s)/\gamma) \Big| \leq\\
-  \varianceDiffA \\ + P^{-1} \oosSum{s,t}{1} \lvert (D_s -
-  \oosA)(\E_R D_t - \oosA) \rvert \vWeight + o_p(1).
-\end{multline*}
-We'll prove that these two sums are $o_p(1)$; uniform integrability
-then implies convergence in $L_1$.  The arguments for each are almost
-identical, so we'll only present the first.
-
-Applying the Cauchy-Schwarz inequality twice and simplifying gives the
-upper bound
-\begin{multline*}
-\varianceDiffA \\ \leq O(1) \Big[\varianceDiffAii\Big]^{1/2} \Big[\varianceDiffAi\Big]^{1/2}.
-\end{multline*}
-Now,
-$P^{-1} \oosSum{s}{1}(D_s - \E_R D_s)^2 = O_p(1)$, and it suffices to prove
-that \[\varianceDiffAi = o_p(1).\]  Observe that
-\begin{align*}
-  \varianceDiffAi & = O_p\Big(P^{-1} \oosSum{s}{1}(\E_{R}D_s -
-  \E_R\oosA)^2\Big) + O_p(\oosA - \E_R\oosA)^{2} \\
-  &= O_p\Big(P^{-1} \oosSum{s}{1} (\E_RD_s)^2 - (\E_R\oosA)^2\Big) +
-  o_p(1),
-\end{align*}
-with the second term $o_p(1)$ by Lemma \ref{res-mixingale} and
-\citepos{Dav:93} mixingale LLN.
-
-Now define $D_s^*$, $s = R+1,\dots,T-\h$, as in Lemma
-\ref{lem-basic-coupling} so that $\E_{s-1} D_s^* = \E_R D_s^*$ almost
-surely.  Note that we also have the equality $\E_R D_s^* = \E_R
-D_{R+1}^*$ almost surely for all $s\geq R+1$, and so
-\[
-P^{-1} \oosSum{s}{1} (\E_R D_s^*)^2 = \Big(P^{-1} \oosSum{s}{1} \E_R
-D_s^*\Big)^2 \quad \text{a.s.}
-\]
-Consequently,
-\begin{align*}
-P^{-1} \oosSum{s}{1}& (\E_R D_s)^2 - (\E_R\oosA)^2 \\
-&= P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R D_s^*)^2]
- + \Big(P^{-1} \oosSum{s}{1} \E_R D_s^*\Big)^2 - (\E_R\oosA)^2 \quad \text{a.s}.\\
-&= O_p\Big(P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R D_s^*)^2]\Big)
- + O_p\Big(P^{-1} \oosSum{s}{1} \E_R (D_s - D_s^*)\Big).
-\end{align*}
-Finally,
-\begin{align*}
-\Big\lVert P^{-1} \oosSum{s}{1} [(\E_RD_s)^2 - (\E_R D_s^*)^2] \Big\rVert_1
-&\leq P^{-1} \oosSum{s}{1} \lVert \E_R (D_s - D_s^*) \rVert_2 \lVert
-\E_R (D_s + D_s^*) \rVert_2
-\\ &\leq (4 B_L/P) \oosSum{s}{1} \lVert \E_R (D_s - D_s^*) \rVert_2,
-\end{align*}
-and this last term vanishes as in the proof of Lemma~\ref{lem:a2},
-completing the proof.
-\end{proof}
-
-\subsection*{Proof of Lemma \ref{res-mixingale}}
-We will start by proving that $\{D_t - \E_R D_t, \Fs_t\}$ is an
-$L_2$-mixingale of size $-1/2$; $D_t$ is $\Fs_t$-measurable and so it
-suffices to prove that
-\begin{equation}\label{eq:24}
-  \| \E_{t-l} D_t  - \E_R D_t \|_2 \leq 2^{2 + 1/\rho} B_L \, \couplingBeta{l}
-\end{equation}
-for $l = 1,\dots,t-R$, since $\couplingBeta{l} = O(l^{-1/2 - \delta})$
-for some $\delta > 0$ by assumption. Fix $R$, $t$ and $l$ and use
-Lemma \ref{lem-basic-coupling} to define $D_t^*$ so that
-\[
-\E_R D_t^* = \E_{t-l} D_t^* \quad a.s.
-\]
-and
-\[
-\lVert D_t - D_t^* \rVert_2 \leq \couplingBound{l}.
-\]
-Then
-\begin{align*}
-\lVert \E_{t-l} D_t - \E_R D_t \rVert_2 & \leq
-\lVert \E_{t-l} D_t - \E_{t-l} D_t^* \rVert_2  + \lVert \E_{t-l} D_t^* - \E_R D_t \rVert_2 \\
-&\leq 2 \lVert D_t - D_t^* \rVert_2 \\
-&\leq 2^{2 + 1/\rho}\ B_L\ \couplingBeta{l}.\tag*{\qed}
-\end{align*}
-
-\noindent Asymptotic normality follows from~\eqref{eq:24} using a
-modification of \citepos{Jon:97} CLTs for mixingale and NED arrays.
-Define
-\begin{equation*}
-  Z_i = \ZDef
-\end{equation*}
-where $b_T$ is a sequence that satisfies $b_T\leq P$,
-$b_T\to\infty$, and $b_T/P\to 0$.  The same arguments used in
-\citepos{Jon:97} Theorem 1 show that
-\begin{equation*}
-   \SumOuterBlock{i} Z_i = P^{-1/2} \oosSum{s}{1} (D_t - \E_R D_t) + o_p(1).
-\end{equation*}
-and
-\begin{equation*}
-  \SumOuterBlock{i} Z_i = \SumOuterBlock{i} (Z_i - E_{R + (i-1)b_T}
-  Z_i) + o_p(1).
-\end{equation*}
-Note that $\{Z_i - E_{R + (i-1)b_T} Z_i,\mathcal{F}_{R + i b_T}\}_i$ is an
-MDS by construction, so \citepos{HaH:80} Theorem 3.2 and Corollary
-3.1 ensure that $\sigma^{-1} \SumOuterBlock{i} Z_i \to^d N(0,1) $ as
-long as
-\begin{equation*}
-  \sigma^2 - \SumOuterBlock{i} \E_R Z_i^2 \to^p 0,
-\end{equation*}
-and
-\begin{equation*}
-  \SumOuterBlock{i} \E_R Z_i^2 - \SumOuterBlock{i} \ZSqCE \to^p 0.%
-\footnote{Note that $\sigma^2 \in \mathcal{F}_t$ for
-    all $t \geq R$, so Hall and Heyde's condition (3.21) is
-    unnecessary---see the remarks after their result.} %
-\end{equation*}
-The first equation holds as in \citet{Jon:97} (see the proof
-of his Theorem 2); the second is ensured by
-Lemma~\ref{lem:a2}. \qed
-
-\subsection*{Proof of Lemma \ref{res-convergence}}
-\newcommand{\resConvgRHS}[1]{\ensuremath{\E(L(y^* - x_1^{*\prime}\bh{1#1}) - L(y^{*} -
-x_2^{*\prime}\bh{2#1}) \mid \bh{#1})}}
-\newcommand{\resConvgEstDiff}[1]{\ensuremath{\E(L(y^{*} -
-    x_{#1}^{*\prime}\bh{#1R}) \mid \bh{R}) -
-\E(L(y^{*} - x_{#1}^{*\prime}\bh{#1T}) \mid \bh{T})}}
-\newcommand{\resConvgEstDiffRV}[1]{\ensuremath{L(y^{*} -
-    x_{#1}^{*\prime}\bh{#1R}) - L(y^{*} - x_{#1}^{*\prime}\bh{#1T})}}
-
-Equation~\eqref{eq:7} holds if we show
-\begin{gather}
-\E_R \oosA = \resConvgRHS{R} + o_p(P^{-1/2}),\label{eq:18}\\
-\E_T \oosB = \resConvgRHS{T} + o_p(Q^{-1/2}),\label{eq:19}
-\intertext{and}
-\resConvgEstDiff{i} = O_p(\sqrt{P/T}),\label{eq:20}
-\end{gather}
-where $\hat\theta_R = (\hat\theta_{1R}, \hat\theta_{2R})$,
-$\hat\theta_T = (\hat\theta_{1T}, \hat\theta_{2T})$, and $y^{*}$,
-$x_1^{*}$ and $x_2^{*}$ are random variables drawn from the joint
-distribution of $(y_{t+\h},x_{1t},x_{2t})$ independently of
-$\mathcal{F}_T$.
-
-\begin{proof}[Proof of~\eqref{eq:18} and~\eqref{eq:19}]
-For~\eqref{eq:18}, define $D_t^*$ for each $t=R+1,R+2,\dots,T-h$ so
-that
-\begin{equation*}
-  \| D_t^* - D_t \|_2 \leq 2^{(1+\rho)/\rho} B_L \beta_{t-R}^{(\rho-2)/2\rho}
-\end{equation*}
-and
-\begin{equation*}
-  \E_R D_t^* = \E(L(y^* - x_1^{*\prime}\hat\theta_{1R}) -
-  L(y^* - x_2^{*\prime}\hat\theta_{2R}) \mid \hat\theta_R) \qquad a.s.
-\end{equation*}
-Lemma~\ref{lem-basic-coupling} ensures that these $D_t^*$ exist.
-Now,
-\begin{align*}
-  \Big\lVert \E_R \oosA - \E\Big(P^{-1} \sum_{t=R+1}^{T-h} D_t^* \mid
-  \hat\theta_R\Big) \Big\rVert_2
-  &= \Big\lVert \E_R\Big( \oosA - P^{-1} \sum_{t=R+1}^{T-h} D_t^*
-  \Big) \Big\rVert_2 \\
-  &\leq P^{-1} \sum_{t=R+1}^{T-h} \lVert D_t - D_t^* \rVert_2\\
-  &= O(P^{-1}) \sum_{t=R+1}^{T-h} \beta_{t-R}^{(\rho-2)/2\rho}
-\end{align*}
-and this last term is $o(P^{-1/2})$ by assumption.
-Essentially the same argument proves~\eqref{eq:19} as well.
-\end{proof}
-
-\begin{proof}[Proof of~\eqref{eq:20}]
-Assumption~\ref{asmp-3} and the definition of the OLS estimator
-ensure that
-\begin{align*}
-  \|L(y^{*} -  x_i^{*\prime} \bh{iR}) - L(y^{*} - x_i^{*\prime} \bh{iT}) \|_1
-  &\leq B_{L} \| x_i^{*\prime} (\bh{iR} - \bh{iT}) \|_2 \\
-  &\leq B_{L} \, \| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
-  (X_{iR}'X_{iR})^{-1}] X_{iR}' \eb_{iR} \|_2 \\
-  &\quad+ B_L \, \| x_i^{*\prime}
-  (X_{iT}'X_{iT})^{-1}[X_{iT}'\eb_{iT} - X_{iR}
-  \eb_{iR} ] \|_2 .
-\end{align*}
-
-To simplify notation, define $V = (X_{iT}'X_{iT})^{-1} -
-(X_{iR}'X_{iR})^{-1}$ and $W = X_{iR}'\eb_{iR} \eb_{iR}'X_{iR}$. The
-first term in the upper bound satisfies
-\begin{align*}
-  \| x_i^{*\prime} V X_{iR}' \eb_{iR} \|_2^2
-  &\leq \eigen_{K_i}(\E x_i^* x_i^{*\prime}) \cdot \E \tr\big( V^2 W \big) \\
-  &= O(1) \cdot \E \tr\{ V^2 \E(W \mid
-  X_{iR}'X_{iR}, x_{i,R-\h+1} x_{i,R-\h+1}',\dots, x_{i,T-\h} x_{i,T-\h}')\}
-\end{align*}
-by assumption. Observe that
-\begin{multline*}
-  \E \tr\{ V^2 \E(W \mid X_{iR}'X_{iR}, x_{i,R-\h+1} x_{i,R-\h+1}',\dots, x_{i,T-\h} x_{i,T-\h}')\}
-  \\ \leq
-  \Big\rVert \sum_{i=1}^{K_i} \eigen_i^2 \big(V\big) \Big\rVert_{3/2}
-  \big\rVert \eigen_{K_i}(\E(W \mid
-  X_{iR}'X_{iR}, x_{i,R-\h+1} x_{i,R-\h+1}',\dots, x_{i,T-\h} x_{i,T-\h}')) \big\rVert_3.
-\end{multline*}
-The second term in this product is $O(R)$ by
-Assumption~\ref{asmp-2}. To bound the first term, note that
-$(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}$ has rank $P$ and
-each of its nonzero eigenvalues is bounded in absolute value by the
-eigenvalues of $(X_{iR}'X_{iR})^{-1}$. The eigenvalues of
-$(X_{iR}'X_{iR})^{-1}$ are $O_{L_3}(1/R)$ by Assumption~\ref{asmp-2}, so
-\begin{equation*}
-  \Big\|\sum_{j=1}^{K_i}
-  \eigen_j^2(V)\Big\|_{3/2}
-  \leq \Big\|\sum_{j=K_i - P+1}^{K_i} \eigen_j^2(V) \Big\|_{3/2}
-  = O(P/R^2).
-\end{equation*}
-Consequently,
-\begin{equation*}
-  \E \tr\bigg\{[(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}]^2
-  X_{iR}'\eb_{iR} \eb_{iR}X_{iR} \bigg\} = O(P/R)
-\end{equation*}
-and so
-\begin{equation*}
-  \| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
-  (X_{iR}'X_{iR})^{-1}] X_{iR}' \eb_{iR} \|_2 = O(\sqrt{P/R}).
-\end{equation*}
-
-A similar argument proves that
-\begin{equation*}
-  \big\| x_i^{*\prime} (X_{iR}'X_{iR})^{-1}
-  [X_{iT}'\eb_{iT} - X_{iR} \eb_{iR} ] \big\|_2 =  O(\sqrt{P/R}),
-\end{equation*}
-completing the proof.
-\end{proof}
-
-\subsection*{Proof of Theorem \ref{res-oost}}
-We can rewrite the centered \oost\ statistic as
-\[
-\sqrt{P}(\oosA - \E_T \oosB)/\sh
-= \frac{\sigma}{\sh}\, \Big( \sqrt{P}(\oosA - \E_R \oosA)/\sigma
-+ \sqrt{P}(\E_R \oosA - \E_T \oosB)/\sigma \Big)
-\]
-so Lemma \ref{res-mixingale} and \ref{res-convergence} ensure that
-this term is asymptotically standard normal as long as $\sigma/\sh
-\to^p 1$. Since $\sigma$ is almost surely positive, this convergence
-is equivalent to $\sigma^2 - \sh^2 \to^p 0$.
-
-The proof that $\sigma^2 - \sh^2 \to^p 0$ follows \citepos{JoD:00}
-Theorem 2.1 closely.  We start by defining similar quantities to
-theirs, borrowing their notation when possible to make the
-similarities apparent. Let $b_T \equiv \lfloor \gamma/\delta \rfloor$,
-define $\kernelB{x}$ as in Equation \eqref{eq:13}, and define the following
-terms as in \citet{JoD:00}:
-\begin{align*}
-  \varianceTermI &\equiv
-  \varianceTermIDefn,\\ \varianceTermII &\equiv \vtSum
-  \varianceTermIIa\\& \quad \times \varianceTermIIb,\\
-  \varianceTermIII &\equiv \vtSum \varianceTermIIIa\\
-  &\quad \times \varianceTermIIb,\\
-  \varianceTermIV &\equiv \vtSum \varianceTermIIIa \\
-  &\quad\times \varianceTermIVb.
-\end{align*}
-These definitions give the inequalities
-\begin{align*}
-  \lVert \sh^2 - \sigma^2 \rVert_1 &
-  \leq \lVert \sh^2 - \varianceTermI \rVert_1
-  + \lVert \varianceTermI - \varianceTermII \rVert_1
-  + \lVert \varianceTermII - \varianceTermIII \rVert_1
-  + \lVert \varianceTermIII - \varianceTermIV \rVert_1\\ & \quad
-  + \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1
-  + \lVert \E_R\varianceTermIII - \E_R\varianceTermIV \rVert_1
-  + \lVert \E_R\varianceTermII - \E_R\varianceTermIII \rVert_1\\ & \quad
-  + \lVert \E_R\varianceTermI - \E_R\varianceTermII \rVert_1
-  + \lVert \E_R \varianceTermI - \sigma^2 \rVert_1
-  \\ &
-  \leq  \lVert \sh^2 - \varianceTermI \rVert_1
-  + 2(\lVert \varianceTermI - \varianceTermII \rVert_1
-      + \lVert \varianceTermII - \varianceTermIII \rVert_1
-      + \lVert \varianceTermIII - \varianceTermIV \rVert_1) \\
-  & \quad + \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1
-  + \lVert \E_R \varianceTermI - \sigma^2 \rVert_1.
-\end{align*}
-De Jong and Davidson (2000) prove that
-\begin{equation*}
-\lim_{\delta\to0} \limsup_{T\to\infty} \lVert \varianceTermI -
-\varianceTermII\rVert_1 = 0,
-\end{equation*}
-\begin{equation*}
-\lim_{\delta\to0} \limsup_{T\to\infty} \lVert \varianceTermII - \varianceTermIII
-\rVert_1 = 0,
-\end{equation*}
-\begin{equation*}
-\lim_{\delta\to0} \limsup_{T\to\infty} \lVert \varianceTermIII - \varianceTermIV
-\rVert_1 = 0,
-\end{equation*}
-and
-\begin{equation*}
-\lim \lVert \E_R \varianceTermI - \sigma^2 \rVert_1 = 0.
-\end{equation*}
-Their proofs of these four convergence results use the fact that NED
-functions of mixing processes are also mixingale processes and do not
-use any other properties specific to NED processes, so their results
-hold here as well.  We do need to modify their proofs that
-\begin{equation*}
-  \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1 \to 0
-\end{equation*}
-and
-\begin{equation*}
-  \lVert \sh^2 - \varianceTermI \rVert_1 \to 0
-\end{equation*}
-for all positive $\delta$, though, since those proofs exploit NED
-properties. These results are presented as Lemmas~\ref{lem:a2}
-and~\ref{lem:a6} respectively.  \qed
-
-\subsection*{Proof of Theorem \ref{res:oostest}}
-Coverage of the confidence intervals is immediate from
-Theorem~\ref{res-oost}, so we will present a proof of~\eqref{eq:23}.
-By Lemma~\ref{res-convergence}, we know that $\E_R \oosA - \E_T \oosB
-\to^p 0$, so
-\begin{equation*}
-  \Pr[\E_R \oosA \leq 0] - \Pr[\E_T \oosB \leq 0] \to 0.
-\end{equation*}
-Now we can use Lemma~\ref{lem-basic-coupling} to define $D_t^*$ as in
-the proofs of Lemma~\ref{res-mixingale} and~\ref{res-convergence} so
-that $\E_R D_t^* = \E_{t-l} D_t^*$ a.s. and
-\[
-\lVert D_t - D_t^* \rVert_2 \leq \couplingBound{l}
-\]
-and define $\oosA^* = P^{-1} \sum_{t=R+1}^{T-\h} D_t^*$. Then
-\begin{equation*}
-  \lVert \sqrt{P} \oosA - \sqrt{P} \oosA^* \rVert_2
-  \leq P^{-1/2} \sum_{t=R+1}^{T-\h} \lVert \oosA - \oosA^* \rVert_2
-  = o(1),
-\end{equation*}
-and, consequently, we have convergence in probability of the following
-vectors:
-\begin{equation*}
-  (\sqrt{P} \oosA^*/\sigma,\ \E_R \oosA) -
-  (\sqrt{P} \oosA/\sh,\ \E_T \oosB) \to^p 0,
-\end{equation*}
-where we are implicitly using consistency of $\sh^2$ for $\sigma^2$.
-More importantly, this implies convergence in distribution of these
-vectors, so
-\begin{equation*}
-  \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha
-  \text{ and } \E_R \oosA \leq 0]
-  - \Pr[\sqrt{P} \oosA / \sh > z_\alpha \text{ and }
-  \E_T \oosB \leq 0] \to 0.
-\end{equation*}
-
-For large enough $T$, both $\Pr[\E_R \oosA \leq 0]$ and $\Pr[\E_T
-\oosB \leq 0]$ are positive (the second by assumption, the first by
-convergence to the second) so (for these $T$)
-\begin{align}\label{eq:31}
-  \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha
-  \mid \E_R \oosA \leq 0] &=
-  \frac{\Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha \text{ and }
-    \E_R \oosA \leq 0]}{\Pr[\E_R \oosA \leq 0]}
-\intertext{and}\label{eq:32}
-  \Pr[\sqrt{P} \oosA / \sh > z_\alpha
-  \mid \E_T \oosB \leq 0] &=
-  \frac{\Pr[\sqrt{P} \oosA / \sh > z_\alpha \text{ and }
-    \E_T \oosB \leq 0]}{\Pr[\E_T \oosB \leq 0]}
-\end{align}
-almost surely. Since the terms on the RHS of Equations~\eqref{eq:31}
-and~\eqref{eq:32} converge to the same limit in probability, we have
-\begin{equation*}
-  \Pr[\sqrt{P} \oosA / \sh > z_\alpha  \mid \E_T \oosB \leq 0]
-  - \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha \mid \E_R \oosA \leq 0]
-  \to^p 0
-\end{equation*}
-and it suffices to show that
-\begin{equation*}
-  \plim \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha \mid \E_R \oosA \leq 0]
-  \leq \alpha.
-\end{equation*}
-
-To establish this inequality, we have
-\begin{align*}
-  \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha \mid \E_R \oosA \leq 0]
-  &\leq \Pr[\sqrt{P} (\oosA^* - \E_R \oosA) / \sigma > z_\alpha
-  \mid \E_R \oosA \leq 0] \\
-  &\leq \E\big(
-  \Pr[\sqrt{P} (\oosA^* - \E_R \oosA) / \sigma > z_\alpha \mid \Fs_R]
-  \mid \E_R \oosA \leq 0\big).
-\end{align*}
-By construction,
-\begin{equation*}
-  \Pr[\sqrt{P} (\oosA^* - \E_R \oosA) / \sigma > z_\alpha \mid \Fs_R]
-  \to \alpha
-\end{equation*}
-since generated pseudo OOS observations in each $D_t^*$ are
-independent of $\Fs_R$, completing the proof.
-\qed
-
-\subsection*{Proof of Theorem~\ref{res:insample1}}
-
-Let $(\e_{t+h}, x_{t}) \sim i.i.d.\ N(0,I)$ and let $\theta_1 = 0$.
-For any $d \geq 0$, the event $\E_T \oosB = -d$ implies that
-\begin{equation*}
-  \E_T (y_{T+\h+1} - x_{1T+1}'\bh{1T})^2
-  = \E_T (y_{T+\h+1} - x_{2T+1}'\bh{2T})^2 - d \quad a.s.
-\end{equation*}
-which can be expressed as
-\begin{equation}\label{eq:34}
-  d + \theta_2'M_2' M_2 \theta_2 + \bh{1T}'\bh{1T} - \bh{2T}'M_1'M_1\bh{2T}
-  = (\bh{2T} - \theta_2)' M_2'M_2 (\bh{2T} - \theta_2) \quad a.s.
-\end{equation}
-$M_2 \bh{2T}$ is normally distributed conditional on $\bh{1T}$ and
-$M_1 \bh{2T}$, and is distributed on the surface of the sphere defined
-by~\eqref{eq:34} conditional on $\bh{1T}$, $M_1 \bh{2T}$, and the
-event $\E_T \oosB = -d$.
-
-Since $M_2 \bh{2T}$ is normal, this conditional distribution is
-invariant to reflection across the axes defined by the eigenvectors of
-its covariance matrix. So when $\theta_2$ lies outside the cylinder
-that contains the acceptance region of $\Lambda$, i.e. when
-$\theta_2'M_2' V_T M_2 \theta_2 > c$, we have%
-\footnote{To keep the notation in these equations manageable, define
-  the information set $\Gs = \sigma(\E_T \oosB \leq 0,~ \theta_2'M_2'
-  V_T M_2 \theta_2 > c)$.} %
-\begin{align*}
-  \Pr[ \bh{2T}' M_2' V_T M_2 \bh{2T} \leq c \mid \Gs]
-  &= \E\Big( \Pr[ \bh{2T}'M_2' V_T M_2 \bh{2T} \leq c \mid \Gs,~\bh{1T},~M_1 \bh{2T}] \mid \Gs \Big) \\
-  & < 1/2
-\end{align*}
-since the inner conditional probability is less than 1/2.
-
-Now let $\delta > 0$ be an arbitrary but small constant, and choose
-$\theta_2$ far enough from the origin to ensure that
-\begin{equation*}
-  \Pr[\theta_2'M_2' V_T M_2 \theta_2 \leq c] \leq \delta
-\end{equation*}
-for large enough $T$. Then
-\begin{align*}
-  \E(\Lambda \mid \E_T \oosB \leq 0) &
-  \geq \Pr[\bh{2T}' M_2' V_T M_2 \bh{2T} > c \mid \E_T \oosB \leq 0] \\
-  &= \Pr[\bh{2T}' M_2' V_T M_2 \bh{2T} > c \text{~~and~~}
-  \theta_2'M_2' V_T M_2 \theta_2 > c \mid \E_T \oosB  \leq 0] \\
-  & \quad + \Pr[\bh{2T}' V_T M_2 \bh{2T} > c \text{~~and~~ }
-  \theta_2'M_2' V_T M_2 \theta_2 \leq c \mid \E_T \oosB \leq 0].
-\end{align*}
-The second term is nonnegative by design. By conditioning on
-$\theta_2'M_2' V_T M_2 \theta_2 > c$ our earlier argument shows that
-the first term is greater than or equal to $(1 - \delta) / 2$. Since
-$\delta$ is arbitrarily small, this completes the proof.
-\qed
-
-\subsection*{Proof of Theorem~\ref{res:insample2}}
-As in the proof of Theorem~\ref{res:insample1}, let $(\e_{t+h}, x_{t})
-\sim i.i.d.\ N(0,I)$ and let $\theta_1 = 0$. The event $\E_T \oosB
-\geq 0$ implies that
-\begin{equation*}
-  \E_T (y_{T+\h+1} - x_{1T+1}'\bh{1T})^2
-  \geq \E_T (y_{T+\h+1} - x_{2T+1}'\bh{2T})^2 \quad a.s.
-\end{equation*}
-which can be expressed as
-\begin{equation}\label{eq:2}
-  \theta_2'M_2 M_2'\theta_2 + \bh{1T}'\bh{1T} - \bh{2T}'M_1'M_1\bh{2T}
-  \geq (\bh{2T} - \theta_2)' M_2'M_2 (\bh{2T} - \theta_2) \quad a.s.
-\end{equation}
-$M_2 \bh{2T}$ is normally distributed conditional on $\bh{1T}$ and
-$M_1 \bh{2T}$, and is a.s. contained in the sphere defined
-by~\eqref{eq:2} conditional on $\bh{1T}$, $M_1 \bh{2T}$, and the
-event $\E_T \oosB \geq 0$.
-
-Let $\delta$ be a small arbitrary constant, define $\theta^*$ as
-\begin{gather*}
-  \theta^* = \argmax_\theta \theta' M_2' M_2 \theta \\
-  s.t.\quad \theta_2'M_2'M_2\theta_2 +  \bh{1T}'\bh{1T} - \bh{2T}'M_1'M_1\bh{2T} = (\theta - \theta_2)' M_2'M_2 (\theta - \theta_2)
-\end{gather*}
-($\theta^*$ is stochastic and depends on $\bh{1T}$ and $M_1 \bh{2T}$)
-and choose $c$ so that
-\begin{equation*}
-  \Pr[ \theta^{* \prime} M_2 M_2 \theta^* > c] < \delta.
-\end{equation*}
-
-Then, we have for large enough $T$
-\begin{align*}
-  \E(\Lambda \mid \E_T \oosB \geq 0) &\leq
-  \Pr[\bh{2T}'M_2'M_2\bh{2T} > c \mid \E_T \oosB \geq 0) \\
-  &\leq \delta
-\end{align*}
-Since $\delta$ is arbitrarily close to zero, this completes the proof.
-
-\qed
-
-\clearpage
-\markboth{}{}
-\tryinput{floats/mc-ftest.tex}
-
-\begin{table}[tb]
-  \begin{tabularx}{\linewidth}{XX}
-    \toprule
-    Category & Variable \\
-    \midrule
-    Stock market variables
-    & Dividend to price ratio (log) \\
-    & Earnings to price ratio (log) \\
-    & Stock market variance \\
-    & Book to market ratio \\
-    & Net equity expansion \\
-    & Percent equity issuing \\\\
-    Interest rate variables
-    & Treasury Bill rate (3 month) \\
-    & Long term yield \\
-    & Long term rate \\
-    & Default return spread \\
-    & Default yield spread \\
-    & Inflation rate \\
-    \bottomrule
-  \end{tabularx}
-  \caption{Variables used to predict the equity premium
-    (Section~\ref{sec:empirics}).
-    Please see Goyal and Welch's original paper \citep{GoW:08}
-    for a detailed description of each variable.}
-  \label{tab:equity}
-\end{table}
-
-\tryinput{floats/empirics-insample.tex}
-\tryinput{floats/empirics-insample-tuned.tex}
-% These macros create tables. They are defined in
-% floats/empirics-insample.tex and possibly overwritten in the next
-% file.
-\insamplecoefs
-\insampletests
-
-\begin{figure}\centering
-  {\large Coverage of DMW OOS interval for $\E_R\oosA$ in simulations}
-  \tryinput{floats/mc-interval-testerror1.tex}
-  \caption{Simulated coverage of $\E_R \oosA$ at 90\% confidence using
-    a one-sided interval based on the DMW \oost\ test, plotted as a
-    function of the fraction of observations used in the test sample,
-    $P/T$. The solid horizontal line denotes the intervals' nominal
-    coverage.}
- \label{fig:interval-R}
-\end{figure}
-\clearpage
-
-\begin{figure}\centering
-  {\large Coverage of DMW OOS interval for $\E_T\oosB$ in simulations}
-  \tryinput{floats/mc-interval-generror1.tex}
-  \caption{Simulated coverage of $\E_T \oosB$ at 90\% confidence using
-    a one-sided interval based on the DMW \oost\ test, plotted as a
-    function of the fraction of observations used in the test sample,
-    $P/T$.  The solid horizontal line denotes the intervals' nominal
-    coverage.}
-  \label{fig:interval-T}
-\end{figure}
-\clearpage
-
-\begin{figure}\centering
-  {\large Size of DMW \oost\ test in simulations}
-  \tryinput{floats/mc-dmwsize.tex}
-  \caption{Simulated rejection probabilities for the DMW \oost\ test
-    under the null hypothesis that the benchmark model will forecast
-    better, $\E_T \oosB \leq 0$. The nominal size is 10\% and is
-    marked with a solid horizontal line. Values greater than 10\%
-    indicate that the test rejects the benchmark model too often. See
-    Section~\ref{sec:simulation-design} for a discussion of the
-    simulation design.}
-  \label{fig:ttest-size}
-\end{figure}
-\clearpage
-
-\begin{figure}\centering
-  {\large Size of Clark-West OOS test in simulations}
-  \tryinput{floats/mc-clarkwestsize.tex}
-  \caption{Simulated rejection probabilities for Clark and West's
-    (2006, 2007) OOS test statistic under the null hypothesis that the
-    benchmark will forecast better, $\E_T \oosB \leq 0$. The nominal
-    size is 10\% and is marked with a solid horizontal line. Values
-    greater than 10\% indicate that the test rejects the benchmark
-    model too often. See Section~\ref{sec:simulation-design} for a
-    discussion of the simulation design.}
-   \label{fig:clarkwest}
-\end{figure}
-\clearpage
-
-\begin{figure}\centering
-  {\large Size of McCracken \oost\ test in simulations}
-  \tryinput{floats/mc-mccrackensize.tex}
-  \caption{Simulated rejection probabilities for McCracken's (2007)
-    \oost\ test under the null hypothesis that the benchmark model is
-    more accurate, $\E_T \oosB \leq 0$. Nominal size is 10\% and is
-    marked with a solid horizontal line. Values greater than 10\%
-    indicate that the test rejects the benchmark model too often. See
-    Section~\ref{sec:simulation-design} for a discussion of the
-    simulation design.}
-  \label{fig:mccracken}
-\end{figure}
-\clearpage
-
-\begin{figure}\centering
-  {\large Power of DMW \oost\ test in simulations}
-  \tryinput{floats/mc-dmwpower.tex}
-  \caption{Simulated rejection probabilities for the DMW \oost\ test
-    under the alternative that the benchmark model is less accurate,
-    $\E_T \oosB > 0$. Nominal size is 10\% and is marked with a solid
-    horizontal line. Values greater than 10\% indicate that the test
-    rejects the benchmark model too often. See
-    Section~\ref{sec:simulation-design} for a discussion of the
-    simulation design.}
-  \label{fig:ttest-power}
-\end{figure}
-\clearpage
-
-\begin{figure}
-\centering
-\large{Difference in OOS MSE of Prevailing Mean and\\ Kitchen
-    Sink Models of Equity Premium (OLS)}
-\tryinput{floats/empirics-oos-mse-1.tex}
-\tryinput{floats/empirics-oos-mse-1b.tex}
-\caption{OOS difference in the MSE
-  of the prevailing mean benchmark and the kitchen sink model as a
-  function of the test sample size, $R$.  Both models forecast the
-  equity premium using annual data from 1928--2008.  The solid line
-  gives the OOS average, and the shaded region indicates the
-  one-sided 95\% confidence interval implied by the
-  DMW test.  The bottom panel is a detailed view of the top
-  panel for $R \geq 50$.}
-\label{fig:empirics1}
-\end{figure}
-\clearpage
-
-\begin{figure}
-\centering
-\large{Difference in OOS MSE of Prevailing Mean and\\ Kitchen
-    Sink Models of Equity Premium (CT)}
-\tryinput{floats/empirics-oos-mse-2.tex}
-\tryinput{floats/empirics-oos-mse-2b.tex}
-\caption{OOS difference in the MSE
-  of the prevailing mean benchmark and the kitchen sink model as a
-  function of the test sample size, $R$.  Both models forecast the
-  equity premium using annual data from 1928--2008.  The solid line
-  gives the OOS average, and the shaded region indicates the
-  one-sided 95\% confidence interval implied by the
-  DMW test.  The bottom panel is a detailed view of the top
-  panel for $R \geq 50$.}
-\label{fig:empirics2}
-\end{figure}
-\clearpage
-
-\begin{figure}
-\centering
-\large{OOS MSE of Individual Forecasts of Equity Premium}
-\tryinput{floats/empirics-oos-ind-ks.tex}
-\tryinput{floats/empirics-oos-ind-pm.tex}
-\caption{OOS MSE of the Prevailing Mean (PM) and
-    Kitchen Sink (KS) models for equity premium prediction as
-    a function of the size of the training sample, $R$.  Please note
-    that the vertical scales are different in the two plots.}
-\label{fig:empirics3}
-\end{figure}
-
-\clearpage
-
-\bibliographystyle{abbrvnat}
-\bibliography{latex-tools-0.2.1/references}
-
-\end{document}
 
@@
 %%% TeX-master: "paper"
-%%% TeX-command-extra-options: "-shell-escape"
 %%% End:
-
-%  LocalWords:  ClM Mcc ClW MeR StW InK CCS CoS GiW GiR BRC HTF BoH '
-%  LocalWords:  Tib BaN AIC BoB AkA AkP Efr iR eq FPE th Dou iS iT dx
-%  LocalWords:  JoD ixz Mcl RHS MSE homoskedastic Joh Widom TrW Sil
-%  LocalWords:  BFP dy LLNs VeR rlecuyer RSQLite Sar tikzDevice TikZ
-%  LocalWords:  PGF LaTeX jt test's CaT Coc BRW LeN RaW RaZ LeR ZeH
-%  LocalWords:  lmtest Zei dbframe Hmsic Har xtable Dah booktabs FeE
-%  LocalWords:  Bonferroni BWB Gia MeP indices Schwarz HaH Jong i1 1R
-%  LocalWords:  overcorrect 'X 's 2P i' 2i 2m 4C De eigenvectors 'M
-%  LocalWords:  2'M 1'M DiM GoW Cla Whi RoW HHK Rde

### 2017-04-21 paper.tex
Change footnote source code
[#40/move] Move extended example from Section 3.3 to appendix

@@
 \end{abstract}
-\newpage
 
-\section{Introduction}
-\label{sec:introduction}
-
-Consider two sequences of length $P$ of prediction errors, the result
-of forecasting the same variable with two different estimated models.
-Both models are estimated with $R$ observations, collectively called
-the {\em estimation window}, and are used to forecast an additional
-$P$ observations, called the {\em test sample}.  There are $T$
-observations in all, and $R+P=T$.  This paper introduces a new limit
-theory for statistics constructed from these prediction errors
-designed to approximate the behavior of the statistics when one of the
-models is overfit.  In doing so, we provide a theoretical
-justification for forecasters to use out-of-sample (OOS) instead of in-sample
-comparisons: the DMW OOS test%
-\footnote{In this paper, we will refer to the basic OOS $t$-test
-  studied by \citet{DiM:95} and \citet{Wes:96} as the DMW test.} %
-allows a forecaster to conduct
-inference about the expected future accuracy of his or her models when
-one or both is overfit.  We show analytically and through Monte Carlo simulations
-that standard full-sample test statistics can not test hypotheses
-about this performance.
-
-Our paper also shows that popular test and training sample sizes may
-give misleading results if researchers are concerned about overfit.
-We show that $P^2/T$ must converge to zero for the DMW test to give
-valid inference about the expected forecast accuracy, otherwise the
-test measures the accuracy of the estimates constructed using only the
-training sample.  In empirical research, $P$ is typically much larger
-than this.  Our simulations indicate that using large values of $P$
-with the DMW test gives undersized tests with low power, so this
-practice may favor simple benchmark models too much.  Existing
-corrections, proposed by \citet{ClM:01,ClM:05}, \citet{Mcc:07} and
-\citet{ClW:06,ClW:07}, seem to overcorrect for this problem, though, and reject
-too often when the benchmark model is more accurate.
-
-Although OOS comparisons have been popular in Macroeconomics and
-Finance since \citepos{MeR:83} seminal study of exchange rate models,
-it has been unclear from a theoretical perspective whether or not the
-statistics are useful.  Empirical researchers often cite ``overfit''
-or ``instability'' as reasons for using OOS comparisons, as in
-\citet{StW:03}, but neither term is precisely defined or formalized.
-Compounding this problem, the asymptotic distributions of these
-statistics are derived under conditions that rule out either
-instability or overfit and allow a researcher to use a conventional
-in-sample comparison---a variation of the $F$-test, for example.  As
-\citet{InK:04} argue, the statistics themselves are designed to test
-hypotheses that can be tested by these in-sample statistics.  For
-example, \citet{DiM:95} and \citet{Wes:96} derive the limiting
-distributions of many popular OOS test statistics under conditions
-that would justify these full-sample tests.  Much
-of the subsequent research by \citet{Mcc:00, Mcc:07}, \citet{CCS:01},
-\citet{ClM:01,ClM:05}, \citet{CoS:02,CoS:04}, \citet{ClW:06,ClW:07},
-\citet{Ana:07}, and others relaxes several of Diebold and Mariano's
-and West's assumptions, but maintains the stationarity and dependence
-conditions that permit in-sample comparisons \citep[see][for a
-review of this literature]{Wes:06}.%
-\footnote{Like us, \citet{Ana:07} allows the number of regressors to
-  increase with $T$.  But in that paper, the number of regressors
-  increases slowly enough that the OLS coefficients are consistent and
-  asymptotically normal.} %
-\citet{GiW:06} and
-\citet{GiR:09, GiR:10} are exceptions.  Instead of focusing on
-hypotheses that can be tested by in-sample comparisons, \citet{GiW:06}
-derive an OOS test for the null hypothesis that the difference
-between two models' OOS forecasting performance is unpredictable, a
-martingale difference sequence (MDS); \citet{GiR:09} test whether the OOS
-forecasting performance of a model suffers from a breakdown relative
-to its in-sample performance; and \citet{GiR:10} test whether the
-forecasting performance is stable. However, those papers focus on a
-particular OOS estimation strategy and do not address why OOS
-comparisons might be useful as a general strategy.
-
-Since in-sample and OOS statistics require similar assumptions and
-test similar hypotheses, one might expect that they would give similar
-results.  They do not.  In-sample analyses tend to support more
-complicated theoretical models and OOS analyses support simple
-benchmarks, as seen in \citet{MeR:83}, \citet{StW:03}, and
-\citet{GoW:08}.  Since these different approaches strongly influence
-the outcome of research, it is important to know when each is
-appropriate.  The explanations in favor of OOS comparisons claim
-that they should be more robust to unmodeled instability
-\citep{ClM:05,GiW:06,GiR:09,GiR:10} or to overfit
-\citep{Mcc:98,Cla:04}.  Both explanations presume that the in-sample
-comparison is invalid and the OOS comparisons are more reliable.  Of
-course, as \citet{InK:04,InK:06} point out, both in-sample and OOS
-methods could be valid, but the OOS methods could have lower power.
-
-In this paper, we study the ``overfit'' possibility and leave
-``instability'' to future research. This paper uses dimension
-asymptotics to study the behavior of OOS comparisons when at least
-one of the models is overfit---the number of its regressors
-increases with the number of observations so that their ratio remains
-positive.  Although overfit is sometimes used to describe the
-situation where a forecaster chooses from many different models,
-i.e. \emph{data-mining} or \emph{data-snooping}, we view these as
-separate issues.  Procedures that account for the presence of many
-models have been, and are continuing to be, developed \citep[see, for
-example,][]{Whi:00,Han:05,RoW:05,HHK:10,ClM:12b}, but it is unclear
-whether those procedures should themselves use in-sample or OOS
-comparisons.  Understanding the difference between in-sample and OOS
-comparisons in the context of a simple comparison between two models
-is necessary before resolving any new issues that arise with multiple
-comparisons. Moreover, the empirical research that motivates
-this paper uses \emph{pseudo} OOS comparisons and not
-true OOS comparisons.  Even if a true OOS comparison
-could account for some forms of data-snooping better than
-\citepos{Whi:00} BRC or its extensions, in-sample and pseudo
-OOS comparisons would both be affected by the data-snooping, a
-point also made by \citet{InK:04}.
-
-We focus on linear regression models estimated with a fixed window
-for simplicity, but our basic conclusions should be true for other
-models and estimation strategies as well.  Under this
-asymptotic theory, where the number of regressors $K$ increases with $T$
-so that the limit of $K/T$ is positive and less than one,
-the OLS coefficient estimator is no longer
-consistent or asymptotically normal \citep{Hub:73} and has positive
-variance in the limit.  We show that, even so, the usual OOS average
-is asymptotically normal and can consistently estimate the difference
-between the models' generalization error, the expected loss in the
-future conditional on the data available in period
-$T$.%
-\footnote{See, for example, \citet{HTF:08} for a discussion of
-  generalization error.} %
-Under these asymptotics, the generalization
-error does not converge to the expected performance of the pseudotrue
-models, so existing in-sample and OOS comparisons measure different
-quantities and should be expected to give different results for
-reasons beyond simple size and power comparisons.  Under our limit theory,
-the model that is closer to the true DGP in population can forecast
-worse.  In such a situation, a standard in-sample comparison would
-correctly reject the null hypothesis that the benchmark is true, and
-an OOS comparison would correctly fail to reject the null that the
-benchmark is more accurate.%
-\footnote{In a pair of papers similar to
-  ours, \citet{ClM:12,ClM:12b} study in-sample and OOS tests that
-  the larger model has nonzero coefficients that are too close to zero
-  to expect the model to forecast more accurately.  Like this paper,
-  they argue that the larger model can be true but less accurate.
-  However, they focus on an aspect of the DGP that makes this
-  phenomenon likely, while we focus on the coefficient estimates that
-  produce less accurate forecasts.  Moreover, the implications of our
-  asymptotic theories are different and their papers do not provide
-  reasons to do OOS comparisons.} %
-Also note that, in this situation, a model that performs well
-in-sample can perform badly out-of-sample even if there are no
-structural breaks or other forms of instability.  Researchers
-have argued that a breakdown of in-sample forecasting ability
-indicates a structural break (see \citealp{BoH:99}, and
-\citealp{StW:03}, among others), but we show that this breakdown
-can be caused by overfit as well.
-
-It is important to realize that we are not \emph{advocating} linear
-regression for highly overparametrized models. If $K$ is very large
-relative to $T$, researchers will often want to use some form of
-shrinkage forecast, for example the LASSO \citep{Tib:96} or a factor
-model \citep{StW:02,BaN:02}. Our main focus is practical settings
-where $K$ is \emph{moderately} large and it is not clear whether
-overfit will dominate the results. In these settings it is
-crucial to understand the behavior of different evaluation criteria
-when $K$ is large, in case overfit does turn out to be a concern, and to have reliable
-methods for estimating these overfit models' performance. This is the goal of
-this paper.
-
-Our theoretical results partially justify OOS comparisons when
-researchers want to
-choose a model for forecasting.  Although there has been little
-emphasis on hypothesis testing in this setting, testing is usually
-appropriate: there is usually a familiar benchmark model in place, and
-the cost of incorrectly abandoning the benchmark for a less accurate
-alternative model is higher than the cost of incorrectly failing to
-switch to a more accurate alternative.  We show that the DMW test
-lets the forecaster control the probability of the first error, just
-as with conventional hypothesis testing.
-
-But we also identify new practical limitations for applying the DMW
-test to overfit models.
-Since the models' coefficients are imprecisely estimated in the limit,
-the test sample must be small enough that the model estimated over the
-training sample is similar to the one that will be estimated over the
-full sample.  In particular, $P/T \to 0$ is required for consistent
-estimation of the difference in the two models' performance,
-and $P^2/T \to 0$ is required for valid confidence
-intervals and inference.  For larger $P$, the OOS comparisons remain
-asymptotically normal, but are centered on the forecasting performance
-associated with the period $R$ estimates.  In practice, researchers
-typically use large values of $P$, so these studies may be too
-pessimistic about their models' future accuracy if they use the DMW
-test.  Section~\ref{sec:oostheory} lays out the asymptotic behavior of
-the DMW test under this limit theory.
-
-Popular in-sample tests and model selection criteria, like the Wald
-test and the AIC, do not help forecasters in this setting. We show
-that these statistics do not select the more accurate model when
-choosing between overfit models. For many DGPs the Wald test
-will choose the larger model over a small benchmark
-with probability much greater than its nominal size, regardless of
-which model is more accurate, and the AIC behaves similarly. The BIC,
-however, chooses the benchmark model with probability approaching one
-even when the \emph{alternative} model is more accurate.%
-\footnote{Our result holds for a broad class of full-sample
-  statistics, but there may be other potential statistics that mimic
-  the OOS test and remain valid. Exploring such statistics is left for
-  future research.} %
-This result holds even though modifications of the $F$-test are valid
-under this asymptotic theory, as shown by \citet{BoB:95},
-\citet{AkA:00}, \citet{AkP:04}, \citet{Cal:11c}, and \citet{Ana:12},
-among others.%
-\footnote{Also see \citet{Efr:86,Efr:04} for a discussion of naive
-  in-sample loss comparisons.} %
-Moreover, under this asymptotic theory, many recent OOS test
-statistics, such as those derived by \cite{ClM:01,ClM:05},
-\citet{Mcc:07}, and \citet{ClW:06,ClW:07} should have the same
-problems as in-sample tests.%
-\footnote{Our theoretical results apply directly to \citepos{Mcc:07}
-  OOS $t$-test, since it simply proposes more liberal critical values
-  for the same test statistic that we study.  Since
-  \citet{ClW:06,ClW:07} use a finite length estimation window, our
-  asymptotics are incompatible with theirs and prevent us from
-  studying their test directly, as well as \citepos{GiW:06} and other
-  tests based on \citepos{GiW:06} asymptotics.  But \clws\ test can be
-  viewed as a stochastic adjustment to the critical values of the
-  usual \oost\ test, so our conclusions should apply informally as
-  well.  Specifically, we show that the DMW test rejects with
-  probability equal to nominal size when the estimated benchmark model
-  is expected to be more accurate, so more liberal critical values
-  result in overrejection.} %
-These tests are also designed to reject the benchmark when the
-alternative model is true, and so they may reject too often when the
-benchmark is misspecified but more accurate.  Obviously, since the
-distribution of these statistics converges to the normal when $P/T \to
-0$ (with the number of regressors fixed), these statistics behave like
-the DMW test when $P$ is small, but should overreject the benchmark
-when $P$ is large. Section~\ref{sec:insample} presents our theoretical
-results for full-sample statistics and Section~\ref{sec:mc} presents
-Monte Carlo evidence to support these claims.
-
-Finally, this paper introduces a new method of proof for OOS
-statistics.  We use a coupling argument (Berbee's Lemma, 1979) to show
-that sequences of OOS loss behave like mixingales when the
-underlying series are absolutely regular, even if the forecasts depend
-on non-convergent estimators.  Moreover, we also show that transformations of these
-processes behave like mixingales after they are appropriately recentered, so
-many arguments used to prove asymptotic
-results for Near Epoch Dependent (NED) functions of mixing processes
-can be used for these OOS processes with only slight modification.
-
-The rest of the paper proceeds as follows.
-Section~\ref{sec:assumptions} introduces our notation and assumptions.
-Section~\ref{sec:theory} gives the main theoretical results for the
-DMW OOS test, shows that standard in-sample tests reject the
-benchmark model too often when it is misspecified but more accurate than the
-alternative, and shows that standard model selection methods can run
-into similar problems. Section~\ref{sec:theory} also presents an
-example DGP that illustrates these results. Section~\ref{sec:mc}
-presents a Monte Carlo study supporting our theoretical results.
-Section~\ref{sec:empirics} applies the OOS statistic to
-\citepos{GoW:08} dataset for equity premium prediction, and
-Section~\ref{sec:conclusion} concludes.  Proofs and supporting results
-are listed in the Appendix.
-
-\section{Setup and assumptions}
-\label{sec:assumptions}
-
-The first part of this section will describe the environment in detail
-and set up our models and notation. The second part lists the
-assumptions underlying our theoretical results.
-
-\subsection{Notation and forecasting environment}
-
-We assume the following forecasting environment. There are two
-competing linear models that give forecasts for the target,
-$y_{t+\h}$:
-\begin{equation*}
-y_{t+\h} = x_{1t}'\theta_1 + \e_{1,t+h}, \quad\text{and}\quad
-y_{t+\h} = x_{2t}'\theta_2 + \e_{2,t+h};
-\end{equation*}
-$t = 1,\dots,T-h$, $\h$ is the forecast horizon and the
-variables $y_t$, $x_{1t}$, and $x_{2t}$ are all known in period $t$.
-The coefficients $\theta_1$ and $\theta_2$ minimize the population
-Mean Square Error, so
-\begin{equation*}
-  \theta_i = \argmin_\theta \sum_{t=1}^{T-\h} \E (y_{t+\h} - x_{it}'\theta)^2,
-\end{equation*}
-making $\e_{i,t+\h}$ uncorrelated with $x_{i,t}$; $\e_{i,t+\h}$ can exhibit
-serial correlation so both of the linear models may be misspecified.
-Let $\mathcal{F}_t = \sigma(y_1, x_1, \dots, y_t, x_t)$ be the information
-set available in period $t$,
-with $x_t$ the vector of all stochastic elements of $x_{1t}$ and $x_{2t}$ after
-removing duplicates, and let $\E_t$ and $\var_t$ denote the
-conditional mean and variance given $\mathcal{F}_t$.  The first model
-uses $K_1$ regressors, and the second uses $K_2$.  Without loss of
-generality, assume that $K_1 \leq K_2$. At least one of the models is
-overfit, which we represent asymptotically by letting $K_2$ grow with
-$T$ quickly enough that $\lim K_2/T$ is positive; $K_1$ may grow with
-$T$ as well. Since the models change with $T$, a
-stochastic array underlies all of our asymptotic theory, but we
-suppress that notation to simplify the presentation.
-
-In the settings we are interested in, a forecaster observes the data
-$(y_t,x_t)$ for periods 1 through $T$ and divides these observations
-into an estimation sample of the first $R$ observations and a test
-sample of the remaining $P$ observations. The forecaster then compares
-the models' performance over the test sample, which entails
-constructing two sequences of forecasts with a fixed-window
-estimation strategy,
-\begin{equation*}
-\hat y_{i,t+\h} = x_{it}'\hat{\theta}_{it}, \qquad \text{for } i=1,2;
-\ t = R+1,\dots,T-h,
-\end{equation*}
-where
-\begin{equation*}
-  \bh{it} = \Big(\sum_{s=1}^{R-\h} x_{is}x_{is}'\Big)^{-1} \sum_{s=1}^{R-\h}
-  x_{is} y_{s+\h}, \qquad \text{for } i=1,2;\ t = R+1,\dots, T - \h.%
-\footnote{It may not be clear why we are using the index $t$ in $\bh{it}$,
-    since $\bh{it} = \bh{iR}$ almost surely for all $t \leq T-h$.
-    But $\bh{it}$ will be defined for $t > T-\h$
-    soon and will not equal $\bh{iR}$ for those values of $t$.} %
-\end{equation*}
-
-The models are then compared by their forecast performance over the test
-sample. There are many statistics that have been considered in the
-literature, but we focus on perhaps the most natural, the DMW \oost\
-test \citep{DiM:95,Wes:96}.%
-\footnote{The core insights of our paper apply to other OOS statistics
-  as well.} %
-This statistic is based on
-the difference in the models' loss over the test sample, $\oosA$,
-defined as
-\begin{equation*}
-  \oosA \equiv P^{-1} \oosSum{t}{1} D_t
-\end{equation*}
-where
-\begin{equation*}
-  D_t = L(y_{t+\h} - x_{1t}'\bh{1t}) - L(y_{t+\h} - x_{2t}'\bh{2t}),
-\end{equation*}
-and $L$ is a known loss function. The \oost\ test is defined as
-$\sqrt{P} \oosA / \sh$, where $\sh^2$ is an estimator of the
-asymptotic variance of $\oosA$. (Possibly a Heteroskedasticity- and
-Autocorrelation-Consistent, or HAC, estimator.)
-
-Most theoretical research on these statistics, such as \citet{DiM:95}, \citet{Wes:96},
-and \cite{Mcc:07}, has focused on using the \oost\ statistic to test
-hypotheses about the pseudotrue values $\theta_1$ and $\theta_2$.  In
-particular, that research focuses on testing the null hypothesis that
-\begin{equation*}
-  \E L(y_{t+\h} - x_{1t}'\theta_{1}) = \E L(y_{t+\h} - x_{2t}'\theta_{2}).
-\end{equation*}
-But the population quantities in this equation do not determine which
-model is more accurate in practice. The models'
-accuracy will also depend on the specific estimates of $\theta_1$ and
-$\theta_2$ used to produce the forecasts.
-
-When the forecaster will use one of the models to make a number of
-predictions (call it $Q$) in the future, the quantity of interest
-becomes
-\begin{equation*}
-  \E_T \oosB = Q^{-1} \sum_{t=T+1}^{T+Q} \E_T D_t,
-\end{equation*}
-where $D_t$ is defined as before,
-\begin{equation*}
-  D_t = L(y_{t+\h} - x_{1t}'\bh{1t}) - L(y_{t+\h} - x_{2t}'\bh{2t}),
-\end{equation*}
-but now uses the full-sample estimates of the models' parameters,
-\begin{equation*}
-  \bh{it} = \Big(\sum_{s=1}^{T-\h} x_{is}x_{is}'\Big)^{-1} \sum_{s=1}^{T-\h}
-  x_{is} y_{s+\h}, \qquad \text{for } i=1,2;\ t = T+1,\dots, T + Q.
-\end{equation*}
-If $\E_T \oosB$ is positive, the second model is expected to forecast
-better than the first over the next $Q$ periods, and if $\E_T \oosB$
-is negative then the first model is better. We use a conditional
-expectation because the coefficient estimates in $\oosB$ are
-stochastic but known in period $T$, and their values will determine
-the performance of the two models.
-
-Under conventional fixed-$K$ asymptotic theory, $\E_T \oosB$ would
-converge in probability to the difference in the expected loss
-associated with the pseudotrue models,%
-\footnote{This statement is subject to the usual assumptions: some
-  form of stationarity, bounded moments, and weak dependence.} %
-\begin{equation}\label{eq:22}
-  \E L(y_{t+\h} - x_{1t}'\theta_{1}) - \E L(y_{t+\h} - x_{2t}'\theta_{2}).
-\end{equation}
-But if $K_2$ increases with $T$ these quantities can have different
-limits. For a simple example, assume squared-error loss, let $x_{1,t}
-= 1$ for all $t$, and let $(y_{t+\h},x_{2,t})$ be i.i.d. $N(0,
-\Sigma)$.  Then the difference between $\E_T \oosB$ and
-the in quantity~\eqref{eq:22} is
-\begin{align*}
-  \E_T \oosB - \big(\E L(y_{t+\h} - x_{1t}'\theta_{1}&) - \E L(y_{t+\h} - x_{2t}'\theta_{2})\big) \\
-  &= \big(\E_T (y_{T+\h+1} - \bh{1,T})^2 -
-     \E_T (y_{T+\h+1} - x_{T+1}'\bh{2,T})^2\big) \\
-     &\quad - \big(\E y_{T+\h+1}^2 - \E (y_{T+\h+1} - x_{T+1}'\theta_2)^2 \big)\\
-  &= (\bh{2,t} - \theta_2)' \var(x_{2,t})\, (\bh{2,t} - \theta_2) + o_p(1).
-\end{align*}
-This last term has expectation equal to $\var(y_T) \frac{K_2}{T - K_2 - 1}$ and
-would converge to zero in probability if $K_2$ were fixed, but does not when $\lim
-K_2 / T > 0$. In Section~\ref{sec:oostheory} we show that the \oost\
-statistic can estimate $\E_T \oosB$ under our increasing $K$
-asymptotics and does not estimate the expected loss associated with
-the pseudotrue coefficients.
-
-The conditional expectation $\E_T \oosB$ has been studied heavily in
-cross-sectional settings with independent observations. In such a
-setting, $\E_T \oosB$ is equal to the difference in the models'
-\emph{generalization error}, which has been used widely as a measure
-of model accuracy in the machine
-learning literature \citep[see][for further discussion]{HTF:08}.
-Moreover, with i.i.d. observations, the expectation of $\E_T \oosB$
-equals \citepos{Aka:69} Final Prediction Error (FPE). Both
-generalization error and FPE are defined by a model's
-performance on a new, independent, data set, but, for lack of a better
-term, we will call $\E_T \oosB$ the ``difference in generalization error''
-for the rest of the paper with hopefully no risk of confusion.
-
-Finally, define the following notation.  The $l_v$-norm for vectors in
-$\Re^p$ (with $p$ arbitrary) is denoted $\lvert \cdot \rvert_v$, and
-the $L_v$-norm for $L_v$-integrable random variables is $\lVert \cdot
-\rVert_v$.  The functions $\eigen_i(\cdot)$ take a square-matrix
-argument and return its $i$th eigenvalue (with $\eigen_{i}(A) \leq
-\eigen_{i+1}(A)$ for any matrix $A$).  All limits are taken as $T \to
-\infty$ unless stated otherwise.
-
-\subsection{Assumptions}
-\label{sec:asmp}
-
-The next conditions are assumed to hold throughout the paper.  The first
-assumption controls the dependence of the underlying random array.
-The second lays out the details of our asymptotic approximation.
-The third assumption controls the
-smoothness of the loss function and bounds the moments of the
-difference in the models' performance; the fourth assumption describes
-the behavior of the estimation and test windows.  And the last
-assumption describes the kernel used to estimate the OOS average's
-asymptotic variance.
-
-\begin{asmp}\label{asmp-1}
-  The random array $\{y_t,x_t\}$ is strictly stationary and absolutely regular
-  with coefficients $\beta_j$ of size $-\rho/(\rho-2)$; $\rho$ is
-  greater than two and discussed further in Assumption \ref{asmp-3}.
-\end{asmp}
-
-This assumption is a standard condition on the dependence of the
-underlying stochastic array. The only novelty is that we use
-absolute regularity instead of strong or uniform mixing as our
-weak dependence condition; absolute regularity admits a particular
-coupling argument, \emph{Berbee's Lemma} \citep[reproduced in this
-paper as Lemma A.1 for reference]{Ber:79} that is
-unavailable for strong mixing sequences. Absolute regularity
-implies uniform mixing but is more restrictive than strong mixing,
-so this assumption is not unduly strong.
-For a detailed discussion of these weak dependence conditions,
-please see \citet{Dav:94} or \citet{Dou:94}.
-
-Our strict stationarity assumption is also somewhat stronger than is
-typically used; \citet{Wes:96} and \citet{Mcc:07}, for example,
-present results assuming covariance stationarity of the loss
-associated with the pseudotrue models. We need to make a stronger
-assumption because we will need to prove asymptotic results when the
-$\bh{it}$ remain random---so we would need covariance stationarity to
-hold for almost all estimates of $\theta_i$ and not just for the
-pseudotrue value. The only way to guarantee that condition is to
-assume strict stationarity for the underlying stochastic processes.
-
-The next assumption describes our asymptotic experiment.
-\begin{asmp}\label{asmp-2}
-  The number of regressors for each model, $K_1$ and $K_2$, are less
-  than $R$ and $(K_2-K_0)/T$ is uniformly positive;
-  $K_0$ is the number of regressors shared by the two models ($(K_1 - K_0)/T$
-  may be uniformly positive as well, but is not required to be).
-
-  The variance of $y_{t+\h}$ given $\mathcal{F}_t$ is uniformly
-  positive and finite and all of the eigenvalues of the covariance
-  matrix of $x_t$ are uniformly positive and finite as well.
-  Moreover,
-  \begin{equation}
-    \eigen_{\max}(X_{iS}'X_{iS}) = O_{L_3}(S),
-  \end{equation}
-  \begin{equation}
-    \eigen_{\max}((X_{iS}'X_{iS})^{-1}) = O_{L_3}(1/S),
-  \end{equation}
-  \begin{multline}\label{eq:28}
-    \eigen_{\max}\Bigg(\E\Big(
-    \sum_{s,t=U}^{V-\h} \e_{i,s+\h} \e_{i,t+\h} x_{is}x_{it}'
-    \mBig
-    x_{i1},\dots,x_{i,U-1};
-    \sum_{s=U}^{V-\h} x_{is} x_{is}';
-    x_{i,V-\h+1},\dots,x_{i,T-\h}
-    \Big)\Bigg) \\
-    = O_{L_3}(\max(V-U, K_i)),
-  \end{multline}
-  and
-  \begin{multline}\label{eq:8}
-    \tr \E\Big(
-    \sum_{s,t=U}^{V-\h} \e_{i,s+\h} \e_{i,t+\h} x_{is}x_{it}'
-    \mBig
-    x_{i1},\dots,x_{i,U-1};
-    \sum_{s=U}^{V-\h} x_{is} x_{is}';
-    x_{i,V-\h+1},\dots,x_{i,T-\h}
-    \Big)\Bigg) \\
-    = O_{L_3}((V-U) \times K_i)
-  \end{multline}
-  for large enough $T$, where $S = R,\dots,T$, $1 \leq U \leq V - \h
-  \leq T - \h$, $i = 1,2$,
-  \[ X_{iS} \equiv [x_{i1} \quad \dots \quad x_{i,S-\h}]' \qquad
-  \text{and} \qquad \ep{iS} = (\e_{i,1+\h}, \dots, \e_{i,S})'.\]
-
-  Additionally, the Euclidean norms of the pseudotrue coefficients,
-  $\theta_1$ and $\theta_2$, satisfy $|\theta_1|_2 = O(1)$ and
-  $|\theta_2|_2 = O(1)$.
-\end{asmp}
-
-The assumption on $K_1$ and $K_2$ is crucial to the paper; we assume
-that the model complexity grows with $T$ fast enough to break
-consistency. This assumption is how we derive an asymptotic
-concept of ``overfit.''
-
-The assumption that $y_{t+\h}$ and $x_t$ have positive and finite
-variance is straightforward. The conditions on the eigenvalues are
-technical and control the behavior of the OLS estimator as the number
-of regressors gets large---the third and fourth assumptions are
-nonstandard but can be easily verified under, for example,
-independence. Section~\ref{sec:example} contains such an example. The
-restrictions on the pseudotrue coefficients ensure that the regression
-model doesn't dominate the variance of $y_{t+\h}$ in the limit.
-
-The next assumption establishes moment conditions for the OOS loss
-process and smoothness conditions for the loss function itself. The
-moment conditions are standard and apply to $D_t$, and the smoothness
-conditions are relatively weak.
-
-\begin{asmp}\label{asmp-3}
-  The loss function $L$ is continuous, has finite left and right
-  derivatives, and $L(0) = 0$.  There is a constant $B_L$ and a
-  function $L'$ that bounds the left and right derivative of $L$ at
-  every point such that $\|D_t\|_\rho \leq B_L$; $\|D_t^*\|_\rho \leq
-  B_L$ for all $t$, where
-  \begin{equation}
-    D_t^* = L(y^* - x_1^{*\prime}\hat\theta_{1t})
-    - L(y^* - x_2^{*\prime}\hat\theta_{2t})
-  \end{equation}
-  and $(y^*, x_1^*, x_2^*)$ equals $(y_t, x_{1t}, x_{2t})$ in
-  distribution but is independent of $\mathcal{F}_T$ ($\rho$ is defined
-  in Assumption~\ref{asmp-1}); and
-  \begin{equation}\label{eq:29}
-    \| L'(y^* - x_{i}^{*\prime} (\alpha \bh{iR} + (1-\alpha) \bh{iT})) \|_2
-    \leq B_L
-  \end{equation}
-  for any $\alpha \in [0,1]$.
-\end{asmp}
-
-The differentiability condition in Assumption~\ref{asmp-3} is weak and
-allows the loss function itself to be non-differentiable; for example,
-absolute error and many asymmetric loss functions satisfy this
-assumption. The assumption makes use of both $(y_{t+\h}, x_{1t},
-x_{2t})$ and $(y^*, x_1^*, x_2^*)$ because the period $t$ observations
-can be dependent on $\bh{iT}$ in complicated ways. When the underlying
-observations are independent these assumptions can simplify
-considerably.
-
-The next assumption controls the growth of the test and
-training samples.
-\begin{asmp} \label{asmp-4} (a) $P, R, Q \to\infty$ as $T \to
-  \infty$. (b) $P^2/T \to 0$ and $P/Q \to 0$ as $T \to \infty$.
-\end{asmp}
-
-The requirements that $P$ and $R$ grow with $T$ are common. Parts of
-the assumption are new, in particular the requirement that $P^2/T \to
-0$.  See Lemma~\ref{res-convergence} for a discussion of its
-implications.  In practical terms, this assumption requires that the
-test sample be large and that the training sample be much larger, by
-enough that including or excluding the test sample does not affect the
-estimates of $\theta_1$ or $\theta_2$ very much.
-
-A final assumption restricts the class of variance estimators we will
-consider.  We use the same class of estimators studied by
-\citet{JoD:00} (their class $\mathcal{K}$); see
-their paper for further discussion.
-
-\begin{asmp}
-  \label{asmp-5} $W$ is a kernel from
-$\Re$ to $[-1,1]$ such that $W(0) = 1$, $W(x) = W(-x)$ for all $x$,
-\begin{equation}
-  \int_{-\infty}^{\infty} \lvert W(x) \rvert dx < \infty, \quad
-  \int_{-\infty}^{\infty} \lvert \psi(x) \rvert dx < \infty
-\end{equation}
-with
-\begin{equation}
-  \psi(x) = \frac1{\sqrt{2\pi}} \int_{-\infty}^{\infty} W(z) e^{ixz}dz,
-\end{equation}
-and $W(\cdot)$ is continuous at zero and all but a finite number of
-points.
-\end{asmp}
-
-These assumptions are broadly similar to those existing in the
-literature, with some differences in our assumptions relating the
-estimated coefficients to future values of the DGP.
-Section~\ref{sec:example} contains an extended example that shows how
-these assumptions are satisfied in a simple setting.
-
-\section{Theoretical results}
-\label{sec:theory}
-
-This section lays out our theoretical results. The first subsection
-presents results for the DMW \oost\ test; we show that it is
-asymptotically normal when one or both forecasting models is overfit.
-(i.e., under our increasing-$K$ asymptotic approximation.) We also
-present a new limitation on these statistics---OOS comparisons heavily
-penalize overfit models unless the size of the test sample is a very
-small proportion of the total sample size, which will not be practical
-in much applied research. The second subsection presents results for
-full-sample statistics and shows that widely used test statistics and
-model selection criteria are misleading when choosing a model for
-forecasting. In contrast to OOS comparisons, these full-sample
-criteria choose overfit models too often, even when they are less
-accurate than simple benchmark models. These results are somewhat
-abstract, so the third subsection works through an example DGP in
-detail.
-
-\subsection{Asymptotic normality of the DMW test}
-\label{sec:oostheory}
-
-This section has two main conceptual results. The first,
-Lemma~\ref{res-mixingale}, shows that the OOS average, $\oosA$, is
-asymptotically normal as the size of the test sample grows, even when
-the models are overfit. But $\oosA$ is centered at $\E_R \oosA$, the
-difference in the generalization error of the models estimated over
-the \emph{training sample}, which is not the quantity of interest to
-forecasters. Forecasters will generally want to estimate or test
-hypotheses about the difference in the generalization error of the
-models estimated with the full sample, $\E_T \oosB$. Our second
-result, Lemma~\ref{res-convergence}, shows that these quantities are
-approximately equal only when the test sample is very small relative
-to the total sample size. In particular, we show that $\oosA$ is a
-consistent estimator of $\E_T \oosB$ when $P/T \to 0$ and is
-asymptotically normal with mean $\E_T \oosB$ when $P^2/T \to 0$. After
-establishing these Lemmas, we then show that the \oost\ test is
-asymptotically standard normal and can be used to test hypotheses
-about $\E_T \oosB$, which requires the two Lemmas as well as a
-consistent estimator of the variance of the OOS average.
-
-In the first result, we show that
-$\sqrt{P} (\oosA - \E_R \oosA)$ is asymptotically normal as $P \to
-\infty$. This application of the CLT is complicated by a hidden source
-of dependence---the training sample estimators $\bh{iR}$. Under
-conventional asymptotic theory, we would replace each $\bh{iR}$ with
-its pseudotrue value $\theta_i$ and apply the CLT to
-$L(y_{t+\h} - x_{it}'\theta_i)$, with some complications potentially
-arising from the replacement (as in \citealp{Wes:96},
-\citealp{ClM:01}, or \citealp{Mcc:07}, for example). But we can not
-make that replacement here, because our asymptotic approximation
-prevents $x_{it}'\bh{iR}$ from converging to $x_{it}'\theta_i$.
-
-Instead, we show that $D_t - \E_R D_t$ is an $L_2$-mixingale that
-satisfies the CLT. Mixingales satisfy a weak-dependence condition
-similar to MDSes,%
-\footnote{An array $Z_{n,t}$ and an increasing sequence of \sfields
-  $\Gs_{n,t}$ is an \emph{$L_2$-mixingale of size $-1/2$} if there is
-  an array of constants $\{c_{n,t}\}$ and a sequence of constants
-  $\zeta_l = O(l^{-1/2 - \delta})$ for some $\delta > 0$ such that
-  \begin{equation*}
-    \lVert \E(Z_{n,t} \mid \Gs_{n,t-l}) \rVert_2
-    \leq c_{n,t} \zeta_l
-    \qquad\text{and}\qquad
-    \lVert Z_{n,t} - \E(Z_{n,t} \mid \Gs_{n,t+l}) \rVert_2
-    \leq c_{n,t} \zeta_{l+1}.
-  \end{equation*}
-  Mixingales were introduced and developed by
-  \citet{Mcl:74,Mcl:75,Mcl:75b,Mcl:77}.} %
-but they have some limitations. Transformations of mixingales are
-typically not themselves mixingales, which means that CLTs for
-mixingale processes require additional assumptions to hold beyond the
-mixingale property.%
-\footnote{See \citet{Jon:97} for an illustration. We will borrow
-  heavily from his results in our proofs.} %
-This is in contrast to Near Epoch Dependent (NED) processes, which
-retain the NED property after transformations. \citep[See chapter 17
-of][for further discussion of these properties.]{Dav:94} But the OOS
-loss has more structure than most mixingales and behaves like an NED
-process in important respects. (The key result here is
-Lemma~\ref{lem:a2} in the Appendix.) Lemma~\ref{res-mixingale} presents the
-CLT that we use later, and Section~\ref{sec:example} works through an
-i.i.d. example in detail. For i.i.d. observations, the OOS loss is an
-MDS and is easier to work with.
-
-\begin{lem}\label{res-mixingale}
-  If Assumptions~\ref{asmp-1}--\ref{asmp-3} hold then $\{D_t - \E_R
-  D_t, \mathcal F_t\}$ is an $L_2$-mixingale of size $-1/2$.
-  Moreover
-  \begin{equation}
-    \sqrt{P}(\oosA - \E_R \oosA)/\sigma \to^d N(0,1)
-  \end{equation}
-  as $P \to \infty$ if $\sigma^2$ is uniformly almost surely positive,
-  where $\sigma^2 = \var_R(\sqrt{P} \oosA)$ (which is equal to $P
-  \E_R(\bar{D}_R - \E_R \bar{D}_R)^2$).
-\end{lem}
-
-It may be helpful to compare Lemma~\ref{res-mixingale} to the method
-of proof in \citet{GiW:06}. \citet{GiW:06} show that the OOS average
-is asymptotically normal when the forecasts are estimated with a fixed
-length rolling window. In that case, each $\bh{it}$ depends on only
-the most recent $R$ observations and, since $R$ is fixed in their
-theory, the forecast errors $y_{t+\h} - x_{it}'\bh{it}$ are themselves
-mixing processes. Transformations of their forecast errors are
-still obviously mixing processes and obey the CLT.
-
-In our paper, $R$ is not fixed and the forecast errors are not a
-convenient weakly-dependent process, since the estimation error in
-$\bh{it}$ introduces strong dependence. Consequently,
-transformations of the forecast errors are not weakly dependent
-either. But this additional dependence has a special form and can be
-removed by subtracting the conditional mean; specifically $g(y_{t+\h} -
-x_{it}'\bh{it})$ is not weakly dependent but $g(y_{t+\h} -
-x_{it}'\bh{it}) - \E_R g(y_{t+\h} - x_{it}'\bh{it})$ is.
-Assumptions~\ref{asmp-1}--\ref{asmp-3} allow us to show directly
-that $D_t - \E_R D_t$ and (crucially) $D^2_t - \E_R D_t^2$ are both
-weakly dependent mixingales, ensuring Lemma~\ref{res-mixingale}.
-
-The next Lemma connects $E_R \oosA$ to $\E_T \oosB$, the difference in
-the models' generalization error. Under conventional asymptotics,
-these quantities are generally close. But they are not for overfit
-models and the models will tend to forecast better when estimated over the
-full sample than over the training sample. Consequently, OOS
-comparisons will penalize overfit models too much unless the test
-sample is small relative to the total data set.
-
-\begin{lem} \label{res-convergence}
-  Under Assumptions \ref{asmp-1}--\ref{asmp-4}a,
-  \begin{equation}\label{eq:7}
-    \E_T \oosB - \E_R \oosA = O_p(\sqrt{P/T}) + o_p(P^{-1/2})
-    + o_p(Q^{-1/2}).
-  \end{equation}
-\end{lem}
-We can view $\E_T \oosB - \E_R \oosA$ as noise introduced by
-approximating the performance of the full-sample estimates with that
-of the partial-sample estimates. The key term on the RHS
-of~\eqref{eq:7} in practice is $O_p(\sqrt{P/T})$---unless $P/T$ is
-small, this noise dominates the OOS average, making it an inconsistent
-estimator of $\E_T \oosB$. The $o_p(P^{-1/2})$ term is completely
-unrestrictive in our applications because we will multiply the OOS
-average by at most $\sqrt{P}$ (for the CLT). And the $o_p(Q^{-1/2})$
-term has some implications for interpreting these results: we can only
-measure the average performance of the forecasting models for an
-extended period in the future, long enough that the future
-observations are essentially independent of the current
-information. For $Q=1$, for example, the dependence between
-$y_{T+\h+1}$ and the current information set $\Fs_T$ may be very
-strong.
-
-Finally, we can use Lemmas~\ref{res-mixingale}
-and~\ref{res-convergence} to show that the DMW test is asymptotically
-normal and centered at $\E_T \oosB$, as long as
-Assumption~\ref{asmp-4}b holds.
-
-\begin{thm}\label{res-oost}
-  Suppose that Assumptions \ref{asmp-1}--\ref{asmp-5} hold (including
-  \ref{asmp-4}b), that $\gamma \to \infty$ and $\gamma/P \to 0$ as $T
-  \to \infty$, and that $\sigma^2$ is uniformly a.s. positive. Define
-  $\sh^2$ to be the usual OOS HAC estimator of the asymptotic variance
-  of $\oosA$,
-  \begin{equation}
-    \sh^2 \equiv P^{-1} \oosSum{s,t}{1} (D_t - \oosA)(D_s - \oosA)
-    \vWeight.
-  \end{equation}
-  Then
-  \begin{equation}
-    \sqrt{P}(\oosA - \E_T\oosB)/\sh \to^d N(0,1).
-  \end{equation}
-\end{thm}
-
-The requirement that $\sigma^2$ be uniformly a.s. positive is not
-restrictive under our asymptotic theory. Since the models'
-coefficients are estimated with uncertainty in the limit, the two
-models give different forecasts even if they both nest the DGP.  This
-is intuitively similar to \citepos{GiW:06} rolling-window result, but
-comes from different asymptotic theory; Giacomini and White keep the
-variance of the OOS average positive by letting $P \to \infty$ with
-$R$ fixed; in this paper, $R \to \infty$ but the variance remains
-positive since $K \to \infty$ (quickly) as well.
-
-If $K_1$ and $K_2$ were finite, West's (1996) and McCracken's (2007)
-asymptotic theories would apply and the \oost\ test would remain normal as long
-as $P/T \to 0$, even if $\sigma^2 \to 0$. Under that asymptotic
-approximation, the variance will converge to zero whenever the true
-DGP is nested in both of the forecasting models. The same principles
-may also apply if $K_1$ and $K_2$ grow slowly, with $K_2/T \to
-0$. It is likely that a second order expansion along the lines of
-\citet{Mcc:07} would lead to asymptotic normality for that
-intermediate case, but we leave that issue to future research.
-
-Finally, Theorem~\ref{res:oostest} establishes that the DMW test can be
-use to construct confidence intervals for $\E_T \oosB$ and test
-hypotheses about $\E_T \oosB$. In particular, forecasters will often
-want to test the null hypothesis that $\E_T \oosB \leq 0$, meaning
-that the benchmark model is expected to be more accurate than the
-alternative model in the future.
-
-\begin{thm}\label{res:oostest}
-  Suppose that the conditions of Theorem
-  \ref{res-oost} hold. Then each of the usual Gaussian
-  confidence intervals,
-  \begin{gather}
-    [\oosA - z_{\alpha/2} \, \sh /
-    \sqrt{P}, \oosA + z_{\alpha/2} \sh / \sqrt{P}],\label{interval-twosided} \\
-    [\oosA - z_{\alpha} \, \sh / \sqrt{P}, +\infty), \label{interval-greater}
-    \intertext{and}
-    (-\infty, \oosA + z_{\alpha} \, \sh / \sqrt{P}],
-  \end{gather}
-  contains $\E_T\oosB$ with probability $\alpha$ in the limit, with
-  $z_{\alpha}$ the $1-\alpha$ quantile of the standard normal
-  distribution. If, in addition, $\lim \Pr[\E_T \oosB \leq 0]$ is
-  positive then
-  \begin{equation}\label{eq:23}
-    \lim \Pr[P^{1/2}\oosA/\sh > z_{\alpha} \mid \E_T
-    \oosB \leq 0] \leq \alpha.
-  \end{equation}
-\end{thm}
-\noindent
-The results for confidence intervals in Theorem~\ref{res:oostest}
-follow immediately from Theorem~\ref{res-oost},
-but~\eqref{eq:23} requires additional proof.
-
-\subsection{Failure of in-sample statistics for forecast evaluation}
-\label{sec:insample}
-
-In this subsection we look at the behavior of some full-sample
-statistics under the same asymptotic theory as before.  We show that
-these statistics, which include common tests such as the Wald test as
-well as model selection criteria such as the AIC, do not measure the
-models' generalization error and consequently do not indicate which
-model will be more accurate in the future. Some of these statistics
-will tend to choose the larger model regardless of which model will be
-more accurate in the future, whereas others tend to choose the smaller
-model.  This is a different issue than whether or not full-sample
-tests are valid for testing hypotheses about the pseudotrue
-coefficients of the models; as \citet{Cal:11c} and \citet{Ana:12}
-demonstrate, variations of the Wald test can be valid for those
-hypotheses under increasing-$K$ asymptotics.%
-\footnote{\citet{Ana:12} shows that the Wald test is invalid in
-  general and gives an adjustment that corrects the critical values;
-  he also shows that the $F$-test is asymptotically valid under
-  certain conditions on the distribution of the regressors.
-  \citet{Cal:11c} shows that the $F$-test is asymptotically invalid
-  without Anatolyev's constraint, even under homoskedasticity, and
-  provides a correction that gives valid tests.  Both papers only
-  consider independent observations.} %
-To simplify the presentation and the intuition we only derive results
-for nested models and for MSE loss, but the conclusions hold much more
-generally.%
-\footnote{In this section, we define $M_1 = [I_{K_1} \ 0_{K_1 \times (K_2 - K_1)}]$
-  and $M_2 = [0_{(K_2 - K_1) \times K_2} \ I_{K_2 - K_1}]$ as the
-  selection matrices that return the first $K_1$ and the last $K_2 -
-  K_1$ elements of $\theta_2$, and assume that the regressors are
-  ordered so that the first $K_1$ elements of $x_{2,t}$ correspond to
-  $x_{1,t}$.} %
-
-The full-sample statistics we study in this paper share a common
-property. They choose the alternative model when the distance between
-a subset of their coefficient estimates and the origin exceeds a
-threshold, and choose the benchmark otherwise. For the Wald test, for
-example, this threshold is chosen so that the test has correct size
-when those coefficients are zero in population. For small models that
-can be consistently estimated, these coefficient estimates are close
-to their true values and so this criterion can be a reasonable proxy
-for the relative accuracy of the larger model.
-
-But for overfit models, the estimates will typically be far from both
-their pseudotrue values and also from zero. In that case, the Wald test and
-the AIC will both tend to choose the larger model even when it is less
-accurate than the smaller benchmark model. This phenomenon is driven
-by the dimensionality of the alternative model, since there are more
-potential values of the coefficient estimator that are far from zero
-when it has many elements. The threshold for the Wald test and the AIC
-is set by construction to be a bounded distance from the origin, and
-every other statistic that shares this property has the same behavior
-and can reject the benchmark model with high probability, even when
-it is more accurate. This behavior is
-formalized in Theorem~\ref{res:insample1}.
-
-\begin{thm}\label{res:insample1}
-  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-4} hold and let
-  $\Lambda$ be a model selection statistic that takes the values zero
-  or one; $\Lambda = 0$ indicates that the benchmark model is chosen
-  and $\Lambda = 1$ indicates the alternative.  Moreover, assume that
-  $L(e) = e^2$ and that there exist a deterministic scalar $c$
-  and a sequence of possibly random matrices $V_T$ such that
-  \begin{equation}\label{eq:25}
-    \limsup_{T \to \infty}
-    \Pr[\Lambda \geq \1\{\bh{2T}'M_2' V_T M_2\bh{2T} > c \}]
-    \to 0
-  \end{equation}
-  where the eigenvalues of $V_T$ are uniformly bounded in probability,
-  $\plim \rank(V_T)/T > 0$, and neither $V_T$ nor $c$ depend on
-  $\theta$ or the value of $\bh{2T}$.
-
-  Then there exist DGPs satisfying these assumptions such that
-  \begin{equation}\label{eq:11}
-    \liminf_{T \to \infty} \E( \Lambda \mid \E_T \oosB \leq 0 ) \geq 1/2.
-  \end{equation}
-\end{thm}
-
-As we state above,~\eqref{eq:11} means that, with high probability,
-the benchmark model is rejected even when it is more accurate. In
-general, $\delta$ can be made arbitrarily small by increasing the
-region enclosed by $\1\{\bh{2T}'M_2' V_T M_2\bh{2T}\}$ and DGPs can be
-chosen to put the limiting quantity in~\eqref{eq:11}
-arbitrarily close to 1 while still satisfying
-the assumptions of the Theorem.  The DGPs and
-statistics used in Theorem~\ref{res:insample1} are simple and
-common. They include correctly specified linear models with normal and
-homoskedastic errors; and the statistics that meet the restrictions on
-$\Lambda$ include the $F$-test and AIC.
-
-For example, the $F$-statistic for the null hypothesis that the
-benchmark model is correctly specified is known to have the form
-\begin{equation*}
-  F = \frac{\bh{2T}' M_2' ( M_2 (X_{2T}'X_{2T})^{-1} M_2' )^{-1} M_2
-    \bh{2T}}{s^2 (K_2 - K_1)}
-\end{equation*}
-where $s^2$ is the usual estimator of the variance of the regression
-error. Then let $c$ be any number greater than 1 and define
-\begin{equation*}
-  V_T = M_2' \big( M_2 \big(\tfrac{1}{s^2 (K_2 - K_1)} X_{2T}'X_{2T}\big)^{-1}
-  M_2' \big)^{-1} M_2'.
-\end{equation*}
-If Assumption~\ref{asmp-2} holds and $s^2$ is consistent then $V_T$
-has uniformly bounded eigenvalues and has rank $K_2 - K_1$, so it
-satisfies~\eqref{eq:25}.
-Robust variations of the Wald test can obviously satisfy~\eqref{eq:25}
-for similar reasons, and the AIC for nested linear models is
-equivalent to using the $F$-test with the critical value %
-$(e^{2 (K_2 - K_1) / T} - 1) \cdot (T - K_2) / (K_2 - K_1)$, %
-which converges to a finite limit, so the AIC satisfies~\eqref{eq:25}
-as well.
-
-For statistics that don't satisfy~\eqref{eq:25}, the behavior can be
-quite different. The BIC, for example, can also be written in terms of
-the $F$-statistic and is equivalent to using the critical value $(T \,
-e^{2 (K_2 - K_1) / T} - 1) \cdot (T - K_2) / (K_2 - K_1)$. This
-critical value diverges as $T \to \infty$, ensuring that~\eqref{eq:25}
-fails for any $c$. For this statistic, we have the opposite problem as
-before: when the alternative model is \emph{more} accurate, the
-coefficient estimates of the larger model are contained in a bounded
-region of the parameter space. Since the acceptance region of the BIC
-grows, it eventually contains \emph{any} bounded region of the
-parameter space. For large enough $T$, the BIC will always choose the
-\emph{smaller model}, even when the larger model is more accurate.
-
-This behavior is formalized in Theorem~\ref{res:insample2}.
-\begin{thm}\label{res:insample2}
-  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-4} hold, let $L(e) =
-  e^2$, and let $\Lambda$ be a model selection statistic as in
-  Theorem~\ref{res:insample1}. Also assume that, for any finite scalar
-  $c$,
-  \begin{equation}\label{eq:27}
-    \Pr[\Lambda \leq \1\{\bh{2T}'M_2'J M_2\bh{2T} > c \}] \to 1
-    \quad \text{as } T \to \infty.
-  \end{equation}
-
-  Then there exist DGPs satisfying these assumptions such that
-  \begin{equation}\label{eq:15}
-    \E( \Lambda \mid \E_T \oosB \geq 0 ) \to^p 0.
-  \end{equation}
-\end{thm}
-
-The condition~\eqref{eq:27} requires that the acceptance region of
-$\Lambda$ eventually contains any finite cylinder centered at the
-origin. Again,~\eqref{eq:15} implies that statistics like the BIC
-will always choose the smaller model for some DGPs, even when the
-larger model will give more accurate forecasts. Both models may be
-overfit, in that both $K_1/T$ and $K_2/T$ may both be positive in the
-limit; the key is that $(K_2 - K_1)/T$ is also positive in the limit.
-
-It is important to remember that previous research, such as
-\citet{Cal:11c} and \citet{Ana:12}, does not predict these
-results. When $\Lambda$ represents a test statistic, the test may have
-correct size for the null hypothesis that the additional coefficients
-on the larger model are zero. The results in this subsection are being
-driven by the full-sample statistics' behavior when the smaller model
-is misspecified but more accurate.
-
-Any statistic that uses the distance of the models' estimated
-coefficients from a set point (the origin being the most common) is
-poorly suited for choosing between overfit forecasting models. These
-models only forecast well when their coefficient estimates are close
-to their pseudotrue values, which can be far from the origin or any
-other prespecified
-point. Depending on the statistic, it can be biased towards choosing
-the larger model or the smaller model. Formal in-sample \emph{tests}
-will likely be biased towards the larger model, as we show for the
-$F$-test and Wald test in Theorem~\ref{res:insample1}.
-
-\subsection{An extended simple example}
-\label{sec:example}
-
-This subsection illustrates the previous theoretical results with a
-concrete example. Let $L(e) = e^2$ and $h = 1$. Suppose that the benchmark is
-nested in the alternative and $(x_{2t}, \e_{2,t+1}) \sim i.i.d.\
-N(0,I)$, and let $y_{t+1} = x_{2t}'\theta_2 + \e_{2,t+1}$
-be the DGP. Also assume that $K_2/T \to c_2$ and $K_1 / T \to c_1 <
-c_2$.
-
-The first part of this subsection shows how the assumptions in
-Section~\ref{sec:asmp} are satisfied and the second part
-demonstrates asymptotic normality of the DMW \oost\ test. The third
-part explicitly shows that $\E_R \oosA$ converges to $\E_T \oosB$ only
-when the test sample is small. And the last part demonstrates that the
-$F$-test does not indicate which model will be more
-accurate in the future, even in this simple example.
-
-\subsubsection*{Fulfillment of Assumptions 1--5}
-
-We will go through the assumptions one by one. The first is
-a condition on the dependence and moments of the process. Since the
-DGP is i.i.d. Normal, these conditions are satisfied trivially.
-
-Assumption~\ref{asmp-2} deals with the design matrix. In this example,
-we directly assume that $K_2$ and $K_1$ grow at the correct rates so
-the the assumption is satisfied. The variance of $y_{t+1}$ given
-$\Fs_t$ is simply the unconditional variance of $\e_{2,t+1}$, which is
-1; and the eigenvalues of $\E x_{2t} x_{2t}$ all equal 1 as well; and
-so they are all uniformly positive and finite as required.
-
-Assumption~\ref{asmp-2} also requires the eigenvalues of $S^{-1}
-X_{iS}'X_{iS}$ to be positive and finite, and for the largest
-eigenvalue of $S^{-1} X_{iS}'X_{iS}$ to be bounded in $L_3$.  These
-results follow from developments in random matrix theory.
-\citet{Gem:80} establishes that the largest eigenvalue of
-$X_{iS}'X_{iS}$ is of order $S + K_i$ and \citet{Joh:01} shows that it
-converges in distribution to the Tracy-Widom law of order 1
-\citep{TrW:96}, which has finite 3rd moments. \citet{Sil:85} and
-\citet{BFP:98} prove similar results for the smallest eigenvalue.
-Assumption~\ref{asmp-2} also requires the largest eigenvalue of
-$(X_{iS}'X_{iS})^{-1}$ be bounded in $L_3$; this should follow from a
-similar argument, but we are unaware of any papers that explicitly
-derive moments for this eigenvalue.
-
-For the conditional expectation of %
-$\sum_{s,t=U}^{V-1} \e_{i,t+1} \e_{i,s+1} x_{i,s} x_{i,t}'$,
-independence implies that
-\begin{equation*}
-  \E\Big(
-  \sum_{s,t=U}^{V-1} \e_{i,s+1} \e_{i,t+1} x_{is}x_{it}'
-  \mBig
-  x_{i1},\dots,x_{i,U-1};
-  \sum_{s=U}^{V-1} x_{is} x_{is}';
-  x_{i,V},\dots,x_{i,T-1}
-  \Big)
-  = \sum_{s=U}^{V-1} x_{is} x_{is}'.
-\end{equation*}
-The largest eigenvalue of this last matrix is of order $K_i + V - U$,
-as discussed, and it has at most $V - U$ nonzero eigenvalues,
-ensuring that both~\eqref{eq:28} and~\eqref{eq:8} hold.
-
-Assumption~\ref{asmp-3} restricts the loss function and the realized
-OOS loss. In this example, we have
-\begin{equation*}
-  D_t^* =^d D_t = (e_{2,t+1} + x_{2t}'\theta_2 - x_{1t}'\bh{1t})^2
-  - (e_{2,t+1} + x_{2t}'(\theta_2 - \bh{2t}))^2
-\end{equation*}
-which has bounded $\rho$th moments by construction. The loss function
-is differentiable and $L'(e) = 2 e$, so \eqref{eq:29} holds as well.
-
-Finally, Assumption~\ref{asmp-4} deals with the choice of test and
-training sample and holds automatically. And Assumption~\ref{asmp-5}
-requires the kernel of the HAC variance estimator to be continuous at
-zero; it is straightforward to construct an estimator that satisfies
-this condition. However, in this section we will use the estimator
-\begin{equation*}
-  \sh^2 = \frac{1}{P} \sum_{t=R+1}^{T-1} (D_t - \oosA)^2
-\end{equation*}
-which does not satisfy Assumption~\ref{asmp-5} but nevertheless is
-consistent for the conditional variance of $\oosA$ because the
-underlying observations are independent.
-
-\subsubsection*{Asymptotic normality of the OOS average, Lemma 1}
-
-This subsection walks through Lemma 1's CLT. Since the observations in
-this example are i.i.d., we do not need to use mixingale theory to
-derive the results, but the OOS process is still affected by the
-estimation error in $\bh{1t}$ and $\bh{2t}$ and has a high degree of
-dependence. This dependence makes the OOS process an MDS, and MDS
-asymptotic theory replaces mixingale theory in this example.
-
-By construction, we have
-\begin{equation*}
-  D_t =
-  \begin{cases}
-    2 \e_{t+1} (x_{2t}'\bh{2R} - x_{1t}'\bh{1R})
-    + (x_{2t}'\theta_2 - x_{1t}'\bh{1R})^2
-    - (x_{2t}'\theta_2 - x_{2t}'\bh{2R})^2
-    & \text{if } t < T \\
-    2 \e_{t+1} (x_{2t}'\bh{2T} - x_{1t}'\bh{1T})
-    + (x_{2t}'\theta_2 - x_{1t}'\bh{1T})^2
-    - (x_{2t}'\theta_2 - x_{2t}'\bh{2T})^2
-    & \text{if } t > T
-  \end{cases}
-\end{equation*}
-and so we can explicitly derive the components of
-Lemma~\ref{res-mixingale}. First,
-\begin{multline*}
-  D_t - \E_R D_t
-  = 2 \e_{t+1} (x_{2t}'\bh{2R} - x_{1t}'\bh{1R})
-  + \Big\{(x_{2t}'\theta_2 - x_{1t}'\bh{1R})^2
-          - \E_R (x_{2t}'\theta_2 - x_{1t}'\bh{1R})^2 \Big\} \\
-  - \Big\{(x_{2t}'\theta_2 - x_{2t}'\bh{2R})^2
-          - \E_R (x_{2t}'\theta_2 - x_{2t}'\bh{2R})^2 \Big\}
-\end{multline*}
-for $t < T$. Since the underlying observations are i.i.d., $\E_{t-1}
-D_t = \E_R D_t$ a.s.\ and consequently $\{D_t - \E_R D_t, \Fs_{t};
-t=R+1,\dots,T-1\}$ is an MDS.
-
-Although transformations of $D_t - \E_R D_t$ will obviously not be
-MDSes in general, it should be clear that transformations of $D_t$
-will be MDSes after subtracting their conditional mean; i.e.
-\begin{equation*}
-  \{g(D_t) - \E_R g(D_t); \Fs_t; t = R+1,\dots,T-1\}
-\end{equation*}
-is an MDS as long as
-$g(D_t)$ has finite mean, but $g(D_t - \E_R D_t)$ is not. This MDS
-result holds because $x_t$ and $y_{t+1}$ are independent of $\bh{1R}$
-and $\bh{2R}$, so
-\begin{equation*}\begin{split}
-  \E_R g(D_t)
-  &= \int g\Big((x_1'\bh{1R})^2 - (x_2'\bh{2R})^2
-       + 2 y (x'\bh{2R} - x'\bh{1R})\Big) \, f(y, x) \, dx \, dy \\
-  &= \E_{t-1} g(D_t)
-\end{split}\end{equation*}
-a.s., where $f$ is the density of $(y_{t+1}, x_{2t})$ and $x_1$
-denotes the first $K_1$ elements of $x$. This result parallels our
-results for mixingales in the general case.
-
-As a result, $\oosA$ and $(1/P) \sum_{t=R+1}^{T-1} D_t^2$ both obey
-LLNs: $\oosA \to^p \E_R \oosA$ and
-\begin{equation*}
-  (1/P) \sum_{t=R+1}^{T-1} D_t^2 \to^p \E_R D_T^2.
-\end{equation*}
-Moreover, these convergence results imply that $\sh^2 - \var_R
-\sqrt{P} \oosA \to^p 0$. And so
-\begin{equation*}
-  \sqrt{P} \oosA/\sh \to N(0,1)
-\end{equation*}
-by the MDS CLT.
-
-\subsubsection*{Convergence of $\E_R \oosA$ to $\E_T \oosB$, Lemma 2}
-
-This subsection works through Lemma~\ref{res-convergence}. In this
-example, the difference between $\E_R \oosA$ and $\E_T \oosB$ equals
-\begin{equation*}
-  \begin{split}
-    \E_R \oosA - \E_T \oosB &= \Big\{(\bh{1R} - \theta_1)'(\bh{1R} -
-    \theta_1) -
-    (\bh{2R} - \theta_2)'(\bh{2R} - \theta_2)\Big\} \\
-    & \quad - \Big\{(\bh{1T} - \theta_1)'(\bh{1T} - \theta_1) -
-    (\bh{2T} - \theta_2)'(\bh{2T} - \theta_2)\Big\} \\
-    &\begin{split}
-      =\ep{T}'\Big\{
-      & \tilde{X}_{1R}(X_{1R}'X_{1R})^{-2} \tilde{X}_{1R}'
-      - X_{1T}(X_{1T}'X_{1T})^{-2} X_{1T}' \\
-      & - \tilde{X}_{2R}(X_{2R}'X_{2R})^{-2} \tilde{X}_{2R}'
-      + X_{2T}(X_{2T}'X_{2T})^{-2} X_{2T}'
-      \Big\}\ep{T}.
-    \end{split}
-  \end{split}
-\end{equation*}
-with $\tilde{X}_{iR}$ the $T \times K_i$ matrix $[X_{iR}'\ 0]'$. This
-last term is a quadratic form and the regressors and errors are
-assumed to be normal, so we can find the rate that the difference
-converges to zero in probability by calculating its first two moments.
-
-The mean difference is
-\begin{equation*}
-  \begin{split}
-  \E(\E_R \oosA - \E_T \oosB)
-      &=O\Big(\max_i \E \tr \big\{
-        \tilde{X}_{iR}(X_{iR}'X_{iR})^{-2} \tilde{X}_{iR}
-        - X_{iT}(X_{iT}'X_{iT})^{-2} X_{iT} \big\} \Big) \\
-      &=O\Big(\max_i \tr \big\{\E (X_{1R}'X_{1R})^{-1}
-         - \E (X_{1T}'X_{1T})^{-1} \big\}\Big) \\
-      &=O( K_1 P / (R-K_1)(T-K_1)) \\
-      &=O(P/T)
-    \end{split}
-\end{equation*}
-The first equality follows from the expectation of a quadratic form,
-the second from routine manipulations of the trace operator, and the
-third from the moments of the inverse Wishart distribution.
-
-Similarly, the variance of the difference is
-\begin{align*}
-  \var(\E_R & \oosA - \E_T \oosB) \\ &=
-  O\Big(\max_i \E\big[\tr((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1})\big]^2
-  + 2 \tr \E\big((X_{iR}'X_{iR})^{-2} - (X_{iT}'X_{iT})^{-2}\big) \\
-  &\qquad - \big[\tr \E((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}) \big]^2 \Big)\\
-  &= O(P/T)^2.
-\end{align*}
-So, in this example, $P^{1/2}(\E_R \oosA - \E_T \oosB) \to^p 0$
-if $P^3/T^2 \to 0$, which is slightly weaker than the general
-requirement that $P^2/T \to 0$.  If $\lim P^3/T^2 > 0$ the OOS average
-still obeys the MDS CLT, but it is not centered correctly at $\E_T
-\oosB$.
-
-\subsubsection*{Behavior of the F-test}
-
-This part illustrates the behavior of full-sample statistics in our
-simple example. To simplify the presentation even more, assume that
-the full-sample design matrix is orthogonal in-sample, not just in
-population, so $X_{2T}'X_{2T} = T \cdot I_{K_2 \times K_2}$, and again
-let $M_1$ and $M_2$ be the selection matrices for the first $K_1$ and
-the last $K_2-K_1$ elements of $\theta_2$. In this example,
-\begin{equation*}
-  M_2 \bh{2T} \sim
-  N(M_2 \theta_2, (1/T) \, I_{K_2-K_1})
-\end{equation*}
-and, conditional on $\E_T \oosB = 0$, the density of $M_2 \bh{2T}$
-concentrates uniformly on the surface of the sphere centered at $M_2
-\theta_2$ and passing through the origin:
-\begin{equation*}
-  (M_2 \bh{2T} - M_2 \theta_2)'(M_2 \bh{2T} - M_2 \theta_2) =
-  \theta_2'M_2' M_2 \theta_2.
-\end{equation*}
-To see intuitively that it must pass through the origin, note that the
-two models will give identical forecasts when $\bh{2T} = 0$ since the
-regressors are orthogonal. (Identical forecasts obviously have the
-same MSE.)
-
-This region is a cylinder in the original space, $\Re^{K_2}$.  We can
-also represent the null $\E_T \oosB \leq 0$ by conditioning on $\E_T
-\oosB = -d$ for a fixed positive constant $c$. In that case, the
-density of $M_2 \bh{2T}$ concentrates on the sphere
-\begin{equation*}
-  (M_2 \bh{2T} - M_2 \theta_2)'(M_2 \bh{2T} - M_2 \theta_2) =
-  \theta_2'M_2' M_2 \theta_2 + d
-\end{equation*}
-which has the same center but larger radius.
-
-For the $F$-test we have, as before,
-\begin{equation*}
-  F = \tfrac{T}{s^2 (K_2 - K_1)} \bh{2T}' M_2' M_2 \bh{2T}.
-\end{equation*}
-We know that $\sqrt{T}(F - 1)$ is asymptotically normal since its
-numerator is Chi-squared with $K_2-K_1$ degrees of freedom and obeys a
-CLT.  The test accepts if
-\begin{equation}\label{eq:26}
-  \tfrac{T}{s^2 (K_2 - K_1)} \bh{2T}' M_2' M_2 \bh{2T}
-  \leq 1 + \delta / \sqrt{T},
-\end{equation}
-where $\delta$ is chosen to determine the size of the test. In other
-words, the test accepts if $M_2 \bh{2T}$ falls in the sphere centered
-at the origin with radius $s ((K_2 - K_1) / T)^{1/2} +
-O_p(1/\sqrt{T})$.
-
-\input{floats/circles}
-\begin{figure}
-  \centering
-  \begin{tabular}{cc}
-  \subfloat[]{\circlefigA{1}{2.5}{1.4}{4.5}\label{fig:circleA}} &
-  \subfloat[]{\circlefigB{1}{2.5}{1.4}{4.5}\label{fig:circleB}}
-  \end{tabular}
-  \caption{Graphs indicating the rejection region and region of equal
-    generalization error for the models discussed in Section
-    \ref{sec:insample}.  The smaller model has no estimated parameters
-    and the larger has two coefficients.  The shaded regions in
-    Figures (a) and (b) show the rejection region and the acceptance
-    region respectively of the full-sample test given $\E_T \oosB \leq
-    0$. Here $e_1 = (1,0)$ and $e_2 = (0,1)$ are the first and second
-    selection vectors, so the horizontal axes represent changes in the
-    first unique element of $\bh{2T}$ and the vertical axes represent
-    changes in the second unique element.}
-\label{fig:rreject}
-\end{figure}
-
-This is perhaps best illustrated with a picture.
-Figure~\ref{fig:rreject} plots these quantities when $K_2 - K_1 =
-2$. The circle centered at the origin plots the threshold for the
-$F$-test; when $M_2 \bh{iT}$ falls outside this circle, the $F$-test
-rejects. The circle centered at $M_2 \theta_2$ plots the set of points
-for which $\E_T \oosB = 0$. The shaded region in
-Figure~\ref{fig:rreject}~(a) plots the rejection region given $\E_T
-\oosB \leq 0$ and the shaded region in Figure~\ref{fig:rreject}~(b)
-plots the acceptance region given $\E_T \oosB \leq 0$.
-
-In the picture, the true coefficients $\theta_2$ satisfy
-\begin{equation*}
-\theta_2'M_2'M_2\theta_2 > \var(\e_t)^{1/2} ((K_2 - K_1) / T)^{1/2}
-\end{equation*}
-so the center of the conditional distribution of $\bh{2T}$ given $\E_T
-\oosB \leq 0$ is outside the acceptance region of the $F$-test. When
-this is the case, the conditional probability that $\bh{2T}$ falls in
-the rejection region is less than 1/2, since $M_2 \bh{2T}$ is
-uniformly distributed on the cylinder
-\begin{equation*}
-  (M_2 \bh{2T} - M_2 \theta_2)'(M_2 \bh{2T} - M_2 \theta_2) =
-  \theta_2'M_2' M_2 \theta_2 + d
-\end{equation*}
-for some positive $d$.
-
-The AIC behaves essentially the same way. For the BIC, the radius of
-the cylinder centered at the origin increases with $T$ and eventually
-encompasses the cylinder centered at $M_2 \theta_2$, so it never
-selects the alternative once $T$ is large enough.
-\section{Monte Carlo}
-\label{sec:mc}
-
-This section presents two simulations that investigate the accuracy of
-our theory in small samples.
-We do several Monte Carlo exercises. The first looks at whether our
-theoretical results for the OOS average are accurate: whether or not
-the OOS average is approximately normal, and whether it is centered on
-$\E_R \oosA$, $\E_T \oosB$, or somewhere else entirely. The second
-issue is whether or not the \oost\ test is \emph{useful} for
-conducting inference about $\E_T \oosB$. Our theoretical results
-suggest that it may not be, because we require $P^2/T \to 0$ for
-inference about $\E_T \oosB$ to be valid. A highly related issue is
-whether other statistics are useful for conducting inference about
-$\E_T \oosB$---again, our theoretical results suggest that they are
-not.
-
-We use the same DGP for all of these simulations, and it is described
-in the next subsection. Results are presented in the subsection after
-that. Simulations were conducted in R \citep{Rde:10} using the
-\emph{MASS} \citep{VeR:02}, \emph{Matrix} \citep{BM:13}, and
-\emph{rlecuyer} \citep{SR:12} and graphs are produced using
-\emph{Lattice} \citep{Sar:10}. In this paper, we present results for
-the fixed window, but recursive window results are available in a
-separate Appendix and are similar.
-
-\subsection{Setup}
-\label{sec:simulation-design}
-
-The Monte Carlo experiment is intentionally very simple so that we can
-isolate the influence of the models' complexity.  In particular, we do
-not include some features that are common in forecasting
-environments---serial dependence, heteroskedasticity, and complicated
-DGPs. The DGP we use is given by the equation
-\begin{equation}\label{eq:6}
-  y_t = x_t'\theta + \e_t,\quad \e_t \sim N(0,1),
-  \quad t=1,\dots,T.
-\end{equation}
-The first element of $x_t$ is 1 and the remaining $K_2-1$ elements are
-independent Standard Normal.  The benchmark model is
-\begin{equation}
-  \label{eq:1}
-  y_{1t} = \sum_{j=1}^{K_1} x_{jt}\theta_j + \e_t
-\end{equation}
-and the alternative model is the DGP \eqref{eq:6}.  We let
-$(K_1,K_2)$ equal either $(2,3)$ or $(T/20,T/10)$ to study our theory
-in its intended application as well as for more parsimonious models.
-We let $T$ equal 100, 250, or 500.  We also vary $\theta$, and do
-so giving the benchmark and the alternative model comparable weight in
-predicting $y_t$.  Specifically, we set
-\begin{equation*}
-  \theta_j =
-\begin{cases} \frac{c}{\sqrt{K_1}} & j = 1,\dots,K_1 \\
-\frac{c}{\sqrt{K_2 - K_1}} & j = K_1 + 1,\dots,K_2 \end{cases}
-\end{equation*}
-with $c$ equal to zero or one.  When $c$ is one, we're more likely to
-draw values of $X$ and $Y$ that make the estimated larger model more
-accurate than the benchmark, and when $c$ is zero we're unlikely to
-draw such values of $X$ and $Y$.  For all of the studies, $L(e) =
-e^2$.
-
-To study the accuracy of our theoretical approximations, we first
-estimate the coverage probabilities of OOS confidence intervals for
-$\E_R \oosA$ and $\E_T \oosB$. For each draw of $X$ and $Y$, we
-construct the one-sided OOS interval defined in
-Theorem~\ref{res:oostest}:
-\begin{equation*}
-  [ \oosA - 1.28 \hat{\sigma}, \infty) \quad\text{with}\quad
-  \sh^2 = \frac1P \sum_{t=R+1}^T (D_t - \oosA)^{2}
-\end{equation*}
-for $P = 10,\dots,2T/3$; we then calculate the percentage of
-simulations where these intervals contain $\E_R \oosA$ and the
-percentage that contain $\E_T \oosB$.  Since the data are i.i.d., both
-of these quantities are easy to calculate (see
-Section~\ref{sec:example}). For these calculations, we draw 2000
-samples for each combination of the design parameters.
-
-Our second set of results studies whether these different OOS and
-in-sample statistics are valid for testing the null hypothesis
-\begin{equation*}
-  H_0:\quad E_T \oosB \leq 0,
-\end{equation*}
-namely that the benchmark model is expected to be more accurate in the
-future than the alternative. Informally, we are interested in whether
-the conditional probability
-\begin{equation*}
-  \Pr[\text{test rejects} \mid E_T \oosB \leq 0] \leq \alpha
-\end{equation*}
-where $\alpha$ is the nominal size of the test. If this inequality
-does not hold, the test statistic is rejecting the benchmark model too
-often.
-
-We look at four different statistics---the full-sample $F$-test, the
-DMW $t$-test, the OOS $t$-test using McCracken's (2007) critical
-values,%
-\footnote{These critical values are not published for $K_2-K_1>10$, so
-  we do not report them for $K_2 = T/10$.} %
-and Clark and West's (2006, 2007) Gaussian out-of-sample statistic.%
-\footnote{Clark and West (2006, 2007) derive their statistic using the
-  rolling window estimation scheme. Here we use the same statistic,
-  but with a fixed window scheme. A supplemental appendix presents
-  results for their statistic, using the recursive window.} %
-For the $F$-test, we simply test whether the coefficients on the
-larger model are nonzero.  For the out-of-sample tests, we conduct a
-one-sided test of out-of-sample performance for every value of $P$ as
-before. For each of these simulations, we discard draws from the DGP
-that violate the null hypothesis $E_T \oosB \leq 0$ and then use the
-remaining samples to calculate the conditional probability that each
-test rejects. The simulations end when 2000 draws have been retained
-for each choice of the design parameters.
-
-\subsection{Results}
-
-We discuss results for the confidence intervals first.
-Figures~\ref{fig:interval-R} and~\ref{fig:interval-T} show the
-coverage probability of these intervals as a function of $P$ for each
-combination of $T$, $K_1$ and $K_2$, and $c$.  The nominal coverage is
-90\% and is represented with a gray horizontal line. Each panel
-displays the coverage for a different choice of design parameters.
-
-Figure~\ref{fig:interval-R} gives the results for $\E_R \oosA$.  The
-actual coverage is very close to the nominal coverage except when $P$
-is very small.  The poor behavior for small $P$ is unsurprising, as it
-simply means that the CLT is a poor approximation when the test sample
-is small. The interval for $T = 100$, $K = T/10$, and $c = 0$ is the
-worst, with actual coverage near 85\% for most values of $P/T$. But
-the others are much closer to nominal coverage, even for the
-parsimonious models ($K_1=1$ and $K_2= 3$) where one might expect
-the theoretical results to break down.
-
-Figure~\ref{fig:interval-T} gives the results for $\E_T \oosB$.  In
-columns 2 and 4---the overfit models---the coverage is near nominal
-coverage for moderately small values of $P$.  As $P$ increases to
-$2T/3$, the coverage increases above nominal size; near 100\% for some
-DGPs.  With the parsimonious model, the coverage is near nominal
-coverage for all $P$ for the one-sided interval with $c=1$, but only
-for moderately small $P$ when $c=0$.
-
-The behavior for $K_2 = T/10$ is exactly what our theory predicts.
-When $P^2/T$ is small, the coverage is close to nominal levels.  The
-behavior as $P$ increases, combined with the results for $\E_R \oosA$,
-indicate that typically $\E_T \oosB \geq E_R \oosA$.  Since
-\begin{equation*}
-  E_{T} \oosB = E_{R} \oosA + (E_{T} \oosB - E_{R} \oosA),
-\end{equation*}
-and the interval is approximately centered at $\E_R \oosA$, the
-difference $\E_{T} \oosB - E_{R} \oosA$ adds a substantial positive
-quantity when $P^2/T$ is not near zero, increasing the coverage of the
-one-sided interval.
-
-We present the size simulations next, in
-Figures~\ref{fig:ftest}--\ref{fig:ttest-power}.  For the OOS tests
-we plot each OOS test's conditional rejection probability,
-\begin{equation*}
-  \Pr[\text{test rejects} \mid E_T \oosB \leq 0],
-\end{equation*}
-for each combination of $T$, $K_1$, $K_2$, and $c$ as a function of
-$P$.  The $F$-test does not depend on $P$, so we calculate and
-tabulate it's conditional rejection probability as a single value for
-each combination of design parameters.
-
-Table~\ref{fig:ftest} summarizes the simulation results for the
-$F$-test. For $c = 0$, the estimated conditional rejection probability
-is almost exactly equal to the test's nominal size (10\%), which is
-unsurprising.  For $c = 0$, the $F$-test is exact; moreover, the
-larger model will almost always be less accurate than the smaller one,
-so conditioning on $\E_T \oosB \leq 0$ is almost unrestrictive.  When
-$c$ increases, though, the $F$-test overrejects badly---rejecting at
-roughly 50\% when $c = 1$ for the parsimonious model and from 70\% to
-100\% for the overfit model. This agrees with our
-Section~\ref{sec:insample} results and matches results seen in
-empirical practice: the $F$-test rejects the benchmark with very high
-probability, even though it is, by construction, more accurate than
-the alternative model.
-
-Figure~\ref{fig:ttest-size} presents the size estimates for the DMW
-\oost\ test.  Again, different panels display results for different
-combinations of the design parameters.  Each graph plots the rejection
-probability against $P/T$.  For $K/T=10$, the rejection probability
-falls as $P/T$ increases, from near nominal size when $P/T$ is small
-to zero when $P/T$ is near $2/3$.  Moreover, the rejection probability
-falls faster when $T$ is large, as our theory predicts.  When $K=3$,
-the rejection probability stays closer to nominal size, but falls with
-$P/T$ for $c=0$, under-rejecting by about 5pp when $P/T = 2/3$, and
-rises with $P/T$ for $c=1$, overrejecting by about 10pp when
-$P/T=2/3$.  For small $P$, the rejection probability is near 10\% for
-all simulations (the farthest is $K=T/10$, $c=0$, where the rejection
-probability is about 5\%; the other simulations are much closer).
-
-We observe the following patterns.  The
-DMW test has close to nominal size when $P$ is small for every
-combination of design parameters.  In most cases, the rejection
-probability decreases as $P/T$ increases---the exception is for $K_2 =
-3$ and $c=1$.  For the large-$K$ simulations, the rejection
-probability drops to zero for most of the simulations as $P/T$
-increases.  The rejection probability increases with $c$, but the
-rejection probability still is near nominal probability for small $P$
-with $c=1$.
-
-Clark and West's (2006, 2007) statistic, presented in
-Figure~\ref{fig:clarkwest}, behaves quite differently.  For $c=0$ the
-test is correctly sized for both the overfit and parsimonious studies,
-as we saw for the $F$-test.  When $c=1$, the rejection probability
-increases rapidly with $P/T$.  For $K_2=3$, the rejection probability
-is near 10\% when $P$ is small but about 40\% when $P/T = 2/3$.  For
-$K=T/10$, the rejection probability is even higher and increases with
-$T$ as well, from a maximum over 50\% when $T=100$ to a maximum of
-nearly 100\% when $T=1000$.
-
-Results using \citepos{Mcc:07} critical values are presented in
-Figure~\ref{fig:mccracken} and are similar to those using Clark and
-West's test.  For $c=0$ the rejection probability is nearly the test's
-nominal size.  For $c=1$, the rejection probability increases with
-$P/T$, from close to the nominal size when $P/T$ is small to over 25\%
-when $P/T = 2/3$.  Note that all of the simulations use the
-parsimonious model.  McCracken's statistic overrejects here by
-slightly less than Clark and West's, but still by a substantial
-amount. Note that we are unable to plot results for McCracken's
-statistic when $K/T = 10$, which is where the breakdown in Clark and
-West's test is most pronounced.
-
-Since the DMW test tends to have low rejection probability, the test's
-power is a concern.  Figure~\ref{fig:ttest-power} power results for
-the DMW test, simulating from \eqref{eq:1} with $c = 1$ or 2 subject
-to the constraint that $\E_T \oosB > 0$.%
-\footnote{Draws of $X$ and $Y$ with $\E_T \oosB > 0$ are very rare
-  when $c=0$, so we do not present results for that value of $c$.} %
-Since the other test statistics greatly overreject, we do not present
-their power.  For $c=1$, the power is never greater than nominal size
-and decreases to zero as $P/T$ increases for the overfit model.  For
-$c=2$ the power is better, increasing with $P/T$ at first stretch and
-then decreasing as $P/T$ grows beyond approximately 1/4 for the
-overfit model.  Larger values of $T$ give a higher peak and greater
-power overall, but the power still falls to nearly zero if $P/T$ is
-too large (approximately 2/3 in our simulations).  The power with the
-parsimonious model is typically quite low but greater than nominal
-size for $c = 2$.
-
-Both sets of simulations support our theoretical results.  The first
-simulation confirms that the DMW OOS $t$-test is centered at $\E_R
-\oosA$ for all choices of $P$ and $R$ and is centered on $\E_T \oosB$
-only when $P$ is small.  The second simulation confirms that the DMW
-test has correct size for the null hypothesis that $\E_T \oosB \leq 0$
-when $P$ is small and that tests designed to test whether the
-benchmark is true, like the $F$-test and Clark and West's (2006, 2007)
-and McCracken's (2007) OOS tests can reject by much more than their
-nominal size when testing the null $\E_T \oosB \leq 0$.  Moreover,
-these simulations demonstrate that the restriction that $P$ be small
-is binding in practice, as the DMW test under-rejects and has very low
-power when $P$ is too large.
-
-\section{Empirical analysis of equity premium predictability}
-\label{sec:empirics}
-
-This section presents a study of equity premium predictability based
-on \citet{GoW:08}. Goyal and Welch conduct an out of sample analysis
-of 18 different variables thought, based on previous research, to
-predict the equity premium (calculated as the difference between the
-return on the S\&P 500 index and the T-bill rate).%
-\footnote{\citet{GoW:08} builds on previous research by \citet{BoH:99}
-  and \cite{GoW:03}.} %
-Their analysis has two notable features: Goyal and Welch compare different
-predictors across the same time periods and frequency as much as
-possible, making the accuracy of these predictors directly comparable;
-many of the papers that originally proposed these predictors used
-different time periods, methods, or observational frequencies so their
-results were not directly comparable. And Goyal and Welch compare
-these predictors out-of-sample; many of the original studies found
-in-sample evidence of equity premium predictability but did not look
-at out-of-sample evidence.
-
-Goyal and Welch consider many different models; most of them are very
-simple---regression onto a constant and a single stochastic
-predictor---but some are more complicated. They find that essentially
-none of the models outperform a simple benchmark, the prevailing mean
-of the equity premium, and conclude that these variables do not
-predict the equity premium. A large literature has subsequently sought
-to explain or rebut these results, including several responses to
-Goyal and Welch's original working paper published in the same special
-issue of \textit{The Review of Financial Studies} as \citet{GoW:08}.%
-\footnote{Those papers are \citet{CaT:08}, \citet{Coc:08},
-  \citet{BRW:08}, and \citet{LeN:08}.} %
-
-\citet{GoW:08}, as well as \citet{BoH:99}, \citet{LeN:08}, and many
-other authors, propose that instability could explain the OOS failure
-of these models. However, we have shown in this paper that overfit can
-also explain this pattern, significant in-sample results that do not
-hold up out of sample. In this section, we explore the extent to which
-overfit is a potential concern in this data set and estimate the
-expected forecasting performance of the largest model they consider, a
-model with 13 regressors, using 81 observations (annual data from 1928
-to 2009). The predictors are listed in Table~\ref{tab:equity}; please
-see Goyal and Welch's original paper for detailed information about
-these variables.%
-\footnote{Table~\ref{tab:equity} only lists the variables used in
-  \citepos{GoW:08} ``kitchen sink'' model.  Some of the variables that
-  they use are excluded from this model either
-  because the series are too short or because the variables are linear
-  combinations of other variables.} %
-
-\citet{GoW:08} focus primarily on univariate regression models of the
-form
-\[
-r_{t+1} = \beta_0 + \beta_1 x_{it} + \e_{t+1}
-\]
-using OLS with a recursive window, where $r_{t+1}$ is the equity
-premium and $x_{it}$ is one of the predictors listed in
-Table~\ref{tab:equity}.
-This focus is consistent with much of the rest of the literature. But
-it is not clear that this approach---using a large number of
-restricted models---is any more reliable than using a single, large
-model. Very few papers in the equity-premium predictability literature
-explicitly account for the multiplicity of model comparisons%
-\footnote{\citet{RaW:06}, \citet{RaZ:12}, and \citet{Cal:15} are
-  exceptions.} %
-and most widely-used statistics for multiple comparisons are
-derived under the assumption that there is a finite number of
-hypotheses or models (as is the case in \citealp{STW:99c},
-\citealp{Whi:00}, \citealp{Han:05}, and \citealp{LeR:05}), so there is
-little theoretical evidence that they are any more reliable than a
-regression model that encompasses all of the smaller models. Moreover,
-since \citet{GoW:08} (along with most of the rest of the literature)
-want to interpret these univariate regressions as meaningful
-statements about the true relationships between the equity premium and
-the regressors, omitted variable bias is a serious potential issue.
-
-For example, Table~\ref{tab:gwinsample} presents two full-sample
-coefficient estimates for each of the 12 predictors we consider.%
-\footnote{For all of our full sample results, we studentize the
-  regressors to make it easier to compare coefficient estimates and we
-  express the equity premium in basis points.} %
-The first column is the estimator of the coefficient on the
-variable in the full regression,
-\begin{equation*}
-  r_{t+1} = \beta_0 + \sum_{i=1}^{12} \beta_{i} x_{it} + \e_{t+1},
-\end{equation*}
-and the third column is the $p$-value associated with a two-sided
-$t$-test that the coefficient is zero in population. The second column
-is the estimator of the coefficient from the univariate regression
-\begin{equation*}
-  r_{t+1} = \alpha_i + \gamma_{i} x_{it} + \e_{t+1},
-\end{equation*}
-and the fourth column is the $p$-value associated with its $t$-test.%
-\footnote{All of the standard errors were calculated using a
-  Newey-West kernel with two lags.} %
-Some of the coefficient estimates agree, but some do not. The
-coefficient estimate for the \emph{default yield spread}, for example,
-is substantially and significantly negative in the full model ($-7.79$
-with $p$-value $0.042$), but is near zero in the univariate regression
-($0.79$ with $p$-value $0.720$). This pair of results implies that the
-the default yield spread contains information about the equity premium
-but is also correlated with other poor predictors, and that this
-additional correlation adds noise to the univariate regression
-and masks the true relationship. Similarly, \emph{net equity expansion}
-is significant at 10\% in the univariate regression but not in the
-full model ($p$-values of $0.060$ and $0.626$ respectively), which is
-likely attributable to omitted variable bias. So there is merit to
-studying a large model that includes all of the variables.
-
-Results for the full sample estimates of these models are in
-Table~\ref{tab:gwinsample}.%
-\footnote{Calculations in this section are done in R \citep{Rde:10}
-  using the \emph{lmtest} \citep{ZeH:02} and \emph{sandwich}
-  \citep{Zei:04} packages.}%
-\footnote{We compare the test statistic to critical values from the
-  $F$-distribution, which have been shown to be more reliable than
-  Chi-squared critical values when there are many regressors
-  \citep{Ana:12,Cal:11c}.} %
-The last rows of the table list measures of the full-model fit.  The
-$p$-value for the test of full model fit is very small (less than
-0.01), indicating that some of the coefficients are nonzero in
-population and at least one of these predictors is correlated with the
-equity premium.%
-\footnote{We have done additional analysis to try to identify which
-  predictors were correlated with the equity premium, but none of the
-  individual regressors were significant after correcting for
-  multiplicity. The Bonferroni correction, for example, suggests that
-  an individual $p$-value would need to be less than $0.10/12 \approx
-  0.0083$ for its corresponding coefficient to be significant at the
-  10\% level, but the smallest $p$-value is $0.035$. One can improve
-  on the Bonferroni correction, of course, but a comprehensive
-  analysis is beyond the scope of this paper.} %
-As we argue throughout the paper, this result does not imply that the
-model will forecast well.
-
-To determine whether the full model can forecast well, we use the DMW
-\oost\ test to compare it to a sample mean benchmark,
-\begin{equation*}
-r_{t+1} = \mu + \e_{1,t+1}.
-\end{equation*}
-Both models are estimated by OLS using the fixed-window scheme. We
-also present results for a restricted model proposed by
-\citet{CaT:08} that imposes that $\hat r_{t+1}$ be non-negative for
-each forecast.
-To study the effect of the training sample size on the DMW statistic, we
-calculate the one-sided confidence interval for $\E_T \oosB$ given
-by \eqref{interval-greater} corresponding to the null and alternative
-hypotheses
-\[ H_0: \quad E_T \oosB \leq 0 \qquad
-H_A: \quad E_T \oosB > 0
-\]
-using the fixed-window scheme for each value of $R$ between 20 and
-$T-10$. The standard deviation is estimated using a Newey-West
-estimator with $\lfloor P^{1/4}\rfloor$ lags.  For small values of
-$R$, the OOS average is expected to underestimate the performance of
-the larger model relative to the smaller, but this may not hold in
-this particular dataset. For the OOS results, we express the equity
-premium in percentage points.
-
-Figure~\ref{fig:empirics1} plots the OLS results and
-Figure~\ref{fig:empirics2} imposes \citepos{CaT:08} restriction. The
-solid line in each figure shows the OOS average, $\oosA$, and the
-shaded region indicates the 95\% one-sided confidence interval implied
-by the DMW test.  Negative numbers indicate that the full model has
-higher out-of-sample loss.  We can see that the same patterns hold for
-both models: the performance difference decreases as $R$ grows, but
-the full model is never more accurate.  We also see that the
-performance difference decreases suddenly over the period $R=29$ to
-$R=34$ (corresponding to the years 1956--1961).
-Figure~\ref{fig:empirics3} plots the accuracy of the individual
-forecasts (only for the linear models) and shows that this change is
-the result of a sudden improvement in the full model.  This change may
-indicate instability in the underlying relationship, as proposed by
-\citet{GoW:08}.
-
-In summary, we fail to reject the null that the benchmark prevailing
-mean model is more accurate than the full model including all of
-\citepos{GoW:08} predictors.  This result is consistent with Goyal and
-Welch's original analysis.  Unlike Goyal and Welch, we attribute this
-result, at least in part, to parameter uncertainty---the full sample
-results indicate that there is a true predictive relationship between
-some of these variables and the equity premium and the larger model
-could predict better than the benchmark with enough data.%
-\footnote{\citet{BWB:10} make a similar point about exchange rate
-  models, but see also \citet{Chi:10} and \citet{Gia:10}.} %
-These also indicate that combination or shrinkage estimators of the
-full model have the potential to significantly improve on the benchmark.%
-\footnote{See \citet{RaZ:12} for a recent review of this
-  literature.} %
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-This paper gives a theoretical motivation for using OOS comparisons:
-the DMW OOS test allows a forecaster to conduct inference about
-the expected future accuracy of his or her models when one or both is
-overfit.  We show analytically and through Monte Carlo that standard
-full-sample test statistics can not test hypotheses about this
-performance.
-
-Our paper also shows that popular test and training sample sizes may
-give misleading results if researchers are concerned about overfit.
-We show that $P^2/T$ must converge to zero for the DMW test to give
-valid inference about the expected forecast accuracy, otherwise the
-test measures the accuracy of the estimates constructed using only the
-training sample.  In empirical research, $P$ is typically much larger
-than this.  Our simulations indicate that using large values of $P$
-with the DMW test gives undersized tests with low power, so this
-practice may favor simple benchmark models too much.  Existing
-corrections, proposed by \citet{ClM:01,ClM:05}, \citet{Mcc:07} and
-\citet{ClW:06,ClW:07}, seem to correct too much, though, and reject
-too often when the benchmark model is more accurate.
-
-More work remains.  The requirement that $P^2/T$ converge to zero is
-limiting, as it implies that in typical macroeconomic datasets, only a
-handful of observations should be used for testing.  This requirement
-can be relaxed only slightly; $P = O(T^{1/2})$ is required for the
-OOS test to have nontrivial power in general, but there are loss
-functions and DGPs for which some relaxation is possible.  This
-constraint could be mitigated by extending our results to
-cross-validation or other resampling strategies, or by constructing
-full-sample statistics that allow inference about $\E_T \bar{D}_T$.
-It would also be useful to extend our results to other forecasting
-models and to explore how stationarity could be relaxed, but such
-extensions are less important than improving the available statistics.
+\include{1-intro}
+\include{2-setup}
+\include{3-theory}
+\include{4-montecarlo}
+\include{5-goyalwelch}
+\include{6-conclusion}
 
 \appendix
-\section*{Appendix: mathematical details}
-\setcounter{section}{1}
-% Change lemma style to prepend 'A'
-\setcounter{lem}{0}
-\renewcommand{\thelem}{A\arabic{lem}}
 
-\subsection*{Supporting results}
-The results in this paper rely heavily on a coupling argument for
-absolutely regular sequences, Berbee's Lemma \citep{Ber:79}.  Many of
-the results of this paper (Lemma \ref{res-mixingale} and
-Theorem~\ref{res-oost}) use modifications of existing results
-for NED functions of mixing processes by \citet{Jon:97} and
-\citet{JoD:00}; this coupling argument is used to explicitly derive
-inequalities that arise naturally for NED processes.  Lemma
-\ref{lem-basic-coupling} establishes these inequalities, which are
-based on a proposition of \citet{MeP:02}.
+\include{A1-support}
+\include{A2-lemma}
+\include{A3-lemma}
+\include{A4-theorem}
+\include{A5-theorem}
+\include{A6-theorem}
+\include{A7-theorem}
 
-We present \citeauthor{MeP:02}'s
-(\citeyear{MeP:02}) statement of Berbee's Lemma for
-the reader's reference.  In the following Lemma, $\beta(X,Y)$ is the
-coefficient of absolute regularity:
-\begin{equation}
-\beta(X,Y) = \sup_{A \in \sigma(Y)} \E \lvert \Pr(A \mid \sigma(X))
-  - \Pr(A) \rvert.
-\end{equation}
-
-\begin{lem}\label{lem-berbee}\quad
-
-\begin{quotation}\noindent
-  Let $X$ and $Y$ be random variables defined on a probability space
-  $(\Omega, \mathcal{T}, \Pr)$ with values in a Polish space
-  $S$.  Let $\sigma(X)$ be a $\sigma$-algebra generated by $X$ and let
-  $U$ be a random variable uniformly distributed on $[0,1]$
-  independent of $(X,Y)$.  Then there exists a random variable $Y^{*}$
-  measurable with respect to $\sigma(X) \vee \sigma(Y) \vee
-  \sigma(U)$, independent of $X$ and distributed as $Y$, and such that
-  $\Pr(Y \neq Y^{*}) = \beta(X,Y)$.
-
-  \noindent\citep{MeP:02}
-\end{quotation}
-\end{lem}
-
-The advantage of this result over coupling arguments that use other
-forms of weak dependence is that the difference between the original
-variable, $Y$, and the new variable, $Y^{*}$, does not depend on their
-dimension.  Similar results for strong mixing sequences depend on the
-dimension of $Y$, which makes them unsuitable for this paper.
-
-\begin{lem}\label{lem-extend-mp}
-  Suppose that $X$ and $X^*$ are $L_p$-bounded random variables, with
-  $p > 2$, that satisfy ${\Pr[X \neq X^*] = c}$.  Then
-  \begin{equation}
-    \lVert X - X^* \rVert_2 \leq 2^{1/p} (\lVert X \rVert_p + \lVert
-    X^* \rVert_p) c^{(p-2)/2p}
-  \end{equation}
-\end{lem}
-
-The proof is virtually identical to the proof of Proposition 2.3 in
-\citet{MeP:02} and is omitted.
-
-\begin{lem}\label{lem-basic-coupling}
-  Suppose Assumptions \ref{asmp-1}--\ref{asmp-3} hold.  Then, for any
-  T, $s$, $t$, and $u$ with $s < t \leq u$, there exist random
-  variables $D_t^*,\dots,D_u^*$ such that
-  \begin{equation}\label{eq:coupling1}
-    P[(D_{t}^*,\dots,D_u^*) \neq (D_{t},\dots,D_u)] \leq \beta_{t-s}
-  \end{equation}
-  and
-  \begin{equation}\label{eq:coupling2}
-    \E(\phi(D_{t}^*,\dots, D_u^*) \mid \mathcal{F}_s ) =
-    \int
-    \phi(D_{t},\dots,D_u) f(\mathbf{x}, \mathbf{y})\ d\mathbf{x}\ d\mathbf{y}
-  \end{equation}
-  almost surely for all measurable functions $\phi$ such that the
-  expectations are finite, where
-  \[ \mathbf{x} = (x_{t}', \dots, x_{u}')', \qquad
-  \mathbf{y} = (y_{t+\h},\dots,y_{u+\h})',\] and $f$ is the
-  joint density of $(\mathbf{x}, \mathbf{y})$.  Moreover,
- \begin{equation}\label{eq:coupling3}
-   \| D_v^* - D_v \|_2 \leq 2^{1+1/\rho} B_L
-   \beta_{t-s}^{\rhoExp}, \qquad v = t,\dots,u.
- \end{equation}
-\end{lem}
-
-\begin{proof}
-  The proof follows as a consequence of Lemmas \ref{lem-berbee} and
-  \ref{lem-extend-mp}.  Let $l = u-t$.  For any fixed values of $l$
-  and $T$, the sequence of vectors
-  \[ V_{t} = (y_{t+\h}, x_{t}', \dots, y_{t+l+\h}, x_{t+l}') \] is
-  absolutely regular of size $\rho/(\rho-2)$.  Berbee's Lemma implies
-  that there is a random vector $V^*$ that is independent of
-  $\mathcal{F}_s$, equal to $V_{t}$ in distribution, and satisfies
-  \[\Pr[V^* \neq V_{t}] = \beta_{t-s}.\]
-
-  Now define
-  \begin{equation*}
-    D_v^* =
-    \begin{cases}
-      L(y_{v+\h}^* - x_{1v}^{*\prime} \hat{\theta}_{1R}) - L(y_{v+\h}^* -
-      x_{2v}^{*\prime} \hat{\theta}_{2R}) & v \leq T \\
-      L(y_{v+\h}^* - x_{1v}^{*\prime} \hat{\theta}_{1T}) - L(y_{v+\h}^* -
-      x_{2v}^{*\prime} \hat{\theta}_{2T}) & v > T
-    \end{cases}
-  \end{equation*}
-  with $y_{v+\h}^*$ and $x_{iv}^*$ denoting the elements of $V^*$
-  corresponding to $y_{v+\h}$ and $x_{iv}$ in $V_{t}$.  Equations
-  (\ref{eq:coupling1}) and (\ref{eq:coupling2}) are satisfied by
-  construction, and (\ref{eq:coupling3}) follows from Lemma
-  \ref{lem-extend-mp}.
-\end{proof}
-
-\begin{lem}\label{lem:a2}
-  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-3} hold.  Let $b_T$ be a
-  sequence of integers such that $b_T \to \infty$ and $b_T = o(P)$ and define
-  \begin{equation}
-    Z_i = \ZDef.
-  \end{equation}
-  Then
-  \begin{equation}
-    \label{eq:10}
-    \sum_{i=1}^{\lfloor P/b_T \rfloor} (\E_R Z_i^2 - \E_{R+(i-1) b_T}
-    Z_i^2) \to^p 0 \quad\text{ as } P \to \infty.
-  \end{equation}
-
-  If the assumptions of Theorem~\ref{res-oost} also hold, $b_T$ is
-  restricted further so that $b_T \equiv \lfloor \gamma/\delta
-  \rfloor$ for some positive scalar $\delta$, and we define
-  \begin{equation}\label{eq:13}
-    \kernelB{x} \equiv \kernelBDefn{x},
-  \end{equation}
-  then
-  \begin{equation}
-    \label{eq:12}
-    \vtSum (Z_{1t} Z_{2t} - \E_R Z_{1t} Z_{2t}) \to^p 0.
-  \end{equation}
-  where
-  \begin{gather}
-    Z_{1t} = \varianceTermIIIa,%
-    \intertext{and}%
-    Z_{2t} = \varianceTermIVb.
-  \end{gather}
-\end{lem}
-\begin{proof}
-\newcommand{\UFiltration}[1]{\ensuremath{\mathcal{F}_{(#1)b_{T}+R-P}}}%
-The first result,~\eqref{eq:10}, follows a similar argument to Lemma~5
-of \citet{Jon:97} and~\eqref{eq:12} to Lemma~A.4 of \citet{JoD:00}.
-Since these arguments are similar and our modification is the same for
-both, we'll just present the more complicated version,~\eqref{eq:12}.
-
-Note that $\{Z_{1t}^2 P\gamma_T/b_T\}$ and $\{Z_{2t}^2 P\gamma_T/b_T\}$
-are uniformly integrable.  As in~\citet[Lemma A.4]{JoD:00}, we can
-assume that there is a constant $C$ such that $Z_{1t}$ and $Z_{2t}$
-are bounded in absolute value by $C\sqrt{b_T/P\gamma_T}$; uniform
-integrability ensures that the difference between the unbounded random
-variables and these truncated versions is negligible for large enough
-values of $C$.
-
-Let $r = \lfloor 3P/2b_T \rfloor$ and rewrite the summation as
-\begin{align*}
-  \vtSum \vtIIIsummand &= \vtSumr \vtSuma \vtIIIsummand \\
-  &\quad+ \vtSumr \vtSumb \vtIIIsummand \\
-  &\quad+ \sum_{t=r b_T - P + R + 1}^{2P+R} \vtIIIsummand \\
-  &\equiv \vtSumr (U_i - \E_R U_i) + \vtSumr (U_i' - \E_R U_i') + o_{L_1}(1).
-\end{align*}
-The proof then holds if we can show that both $U_i$ and $U_i'$ obey
-LLNs.  We'll do so by proving that $\{U_i -\E_R U_i,
-\UFiltration{2i-1}\}$ and $\{U_i' - \E_R U_i', \UFiltration{2i}\}$ are
-$L_2$-mixingales of size $-1/2$ and using the bound $\E(\vtSumr (U_i -
-\E_R U_i))^2 = O(\vtSumr c_i^2)$ where the $c_i$ are the mixingale
-magnitude indices \citep{Mcl:75}.
-
-For non-negative $m$, we have
-\begin{equation*}
-U_i - \E_R U_i \in \UFiltration{2i+2m-1},
-\end{equation*}
-establishing half of the mixingale result trivially.  Now fix $i$ and $m >
-0$ and use Lemma \ref{lem-basic-coupling} to define $D_{ts}^*$
-for each $t =(2i-2)b_T-P+R+1,\dots,(2i-1)b_T-P+R$ and $s =
-\max(t-b_T,R+1),\dots,\min(t+b_T,T-\h)$ such that
-\begin{equation*}
- \E_R D_{ts}^* = \E_{(2i-2m-1)b_T+R-P} D_{ts}^* \quad a.s.
-\end{equation*}
-and
-\begin{equation*}
-  \lVert D_{ts}^* - D_s \rVert_2 \leq \couplingBound{s - (2i-2m-1)b_T+P}.
-\end{equation*}
-Also define
-\begin{equation*}
-  Z_{1t}^* = (P\gamma_T)^{-1/2} \sum_{l=\vttLower}^{\vttUpper}
-  (D_{t,t+l}^* - \E_R D_{t,t+l}^*)\ W(l/\gamma_T), \\
-\end{equation*}
-and
-\begin{equation*}
-Z_{2t}^* = (P\gamma_T)^{-1/2} \sum_{j=\vttLower}^{\vttUpper}
-    (D_{t,t+l}^* - \E_R D_{t,t+l}^*)\ \kernelB{j/\gamma_T}.
-\end{equation*}
-
-Now, we have the inequalities
-\begin{align*}
-  \lVert \E( U_i - \E_R U_i & \mid \UFiltration{2i-2m-1}) \rVert_2
-  \\ &\leq
-  \vtSuma \lVert \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) - \E_R
-  Z_{1t}Z_{2t} \rVert_2 \\
-  &= \vtSuma \lVert \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
-  &\quad - \E(Z_{1t}^* Z_{2t}^* \mid \UFiltration{2i-2m-1}) \\
-  &\quad + \E(Z_{1t}^* Z_{2t}^* \mid \UFiltration{2i-2m-1})
-  - \E_R Z_{1t}Z_{2t} \rVert_2 \\
-%  \leq \vtSuma (\wall \lVert \wall \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
-%  - \E(Z_{1t}^*Z_{2t}^* \mid \UFiltration{2i-2m-1}) \rVert_2\return
-%  \\ + \lVert \E_R Z_{1t}Z_{2t} - \E_R Z_{1t}^*Z_{2t}^*
-%  \rVert_2)\return \\
-  &\leq 2 \vtSuma \lVert Z_{1t} Z_{2t} - Z_{1t}^* Z_{2t}^*
-  \rVert_2 \\
-  &\leq 2 \vtSuma (\lVert Z_{1t} - Z_{1t}^* \rVert_2 \lVert
-  Z_{2t} \rVert_{\infty}
-  + \lVert Z_{2t} - Z_{2t}^* \rVert_2 \lVert Z_{1t}^* \rVert_{\infty}) \\
-  &\leq \frac{2 C b_T^{1/2}}{(P\gamma_T)^{1/2}} \vtSuma (\lVert Z_{1t} - Z_{1t}^* \rVert_2
-  + \lVert Z_{2t} - Z_{2t}^* \rVert_2).
-\end{align*}
-
-And we can finish the proof with the following inequalities:
-\begin{align*}
-  \frac{2 C b_T^{1/2}}{(P \gamma_T)^{1/2}} &\vtSuma \lVert Z_{1t} - Z_{1t}^* \rVert_2 \\& \leq
-  \frac{4C b_T^{1/2}}{P\gamma_T} \vtSuma \sum_{l=\vttLower}^{\vttUpper} \lVert
-  D_{t+l} - D_{t,t+l}^* \rVert_2 W(l/\gamma_T) \\&
-  \leq O\Bigg(\frac{b_T^{1/2}}{P\gamma_T}\Bigg) \vtSuma
-  \sum_{l=\vttLower}^{\vttUpper} \couplingBeta{t+l-(2i-2m-1)b_T+P}\\&
-  = O\Bigg(\frac{b_T^{1/2}}{P\gamma_T}\Bigg) O(b_T^{3/2-u}\, m^{-1/2-u})
-\end{align*}
-for some positive $u$.  The same argument holds for $Z_{2t}$.
-As a result,
-\[
-E\Big(\vtSumr (U_i - \E_R U_i)\Big)^2 = o\Big(\vtSumr b_T^2/P\gamma_T\Big) =
- o(b_T/\gamma_T) \to 0,
-\]
-as required.
-\end{proof}
-
-\begin{lem}\label{lem:a6}
-  Suppose the conditions of Theorem~\ref{res-oost} hold.
-  Then
-  \begin{equation}
-    \sh^2 - P^{-1} \sum_{s,t=R+1}^{T-h} (D_s - \E_R
-    D_s) (D_t - \E_R D_t) W((t-s)/\gamma) \to^{L_1} 0.
-  \end{equation}
-\end{lem}
-
-\begin{proof}
-   It follows from simple algebra that
-\begin{multline*}
-  \Big| \sh^2 -  P^{-1} \sum_{s,t=R+1}^{T-h} (D_s - \E_R
-    D_s) (D_t - \E_R D_t) W((t-s)/\gamma) \Big| \leq\\
-  \varianceDiffA \\ + P^{-1} \oosSum{s,t}{1} \lvert (D_s -
-  \oosA)(\E_R D_t - \oosA) \rvert \vWeight + o_p(1).
-\end{multline*}
-We'll prove that these two sums are $o_p(1)$; uniform integrability
-then implies convergence in $L_1$.  The arguments for each are almost
-identical, so we'll only present the first.
-
-Applying the Cauchy-Schwarz inequality twice and simplifying gives the
-upper bound
-\begin{multline*}
-\varianceDiffA \\ \leq O(1) \Big[\varianceDiffAii\Big]^{1/2} \Big[\varianceDiffAi\Big]^{1/2}.
-\end{multline*}
-Now,
-$P^{-1} \oosSum{s}{1}(D_s - \E_R D_s)^2 = O_p(1)$, and it suffices to prove
-that \[\varianceDiffAi = o_p(1).\]  Observe that
-\begin{align*}
-  \varianceDiffAi & = O_p\Big(P^{-1} \oosSum{s}{1}(\E_{R}D_s -
-  \E_R\oosA)^2\Big) + O_p(\oosA - \E_R\oosA)^{2} \\
-  &= O_p\Big(P^{-1} \oosSum{s}{1} (\E_RD_s)^2 - (\E_R\oosA)^2\Big) +
-  o_p(1),
-\end{align*}
-with the second term $o_p(1)$ by Lemma \ref{res-mixingale} and
-\citepos{Dav:93} mixingale LLN.
-
-Now define $D_s^*$, $s = R+1,\dots,T-\h$, as in Lemma
-\ref{lem-basic-coupling} so that $\E_{s-1} D_s^* = \E_R D_s^*$ almost
-surely.  Note that we also have the equality $\E_R D_s^* = \E_R
-D_{R+1}^*$ almost surely for all $s\geq R+1$, and so
-\[
-P^{-1} \oosSum{s}{1} (\E_R D_s^*)^2 = \Big(P^{-1} \oosSum{s}{1} \E_R
-D_s^*\Big)^2 \quad \text{a.s.}
-\]
-Consequently,
-\begin{align*}
-P^{-1} \oosSum{s}{1}& (\E_R D_s)^2 - (\E_R\oosA)^2 \\
-&= P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R D_s^*)^2]
- + \Big(P^{-1} \oosSum{s}{1} \E_R D_s^*\Big)^2 - (\E_R\oosA)^2 \quad \text{a.s}.\\
-&= O_p\Big(P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R D_s^*)^2]\Big)
- + O_p\Big(P^{-1} \oosSum{s}{1} \E_R (D_s - D_s^*)\Big).
-\end{align*}
-Finally,
-\begin{align*}
-\Big\lVert P^{-1} \oosSum{s}{1} [(\E_RD_s)^2 - (\E_R D_s^*)^2] \Big\rVert_1
-&\leq P^{-1} \oosSum{s}{1} \lVert \E_R (D_s - D_s^*) \rVert_2 \lVert
-\E_R (D_s + D_s^*) \rVert_2
-\\ &\leq (4 B_L/P) \oosSum{s}{1} \lVert \E_R (D_s - D_s^*) \rVert_2,
-\end{align*}
-and this last term vanishes as in the proof of Lemma~\ref{lem:a2},
-completing the proof.
-\end{proof}
-
-\subsection*{Proof of Lemma \ref{res-mixingale}}
-We will start by proving that $\{D_t - \E_R D_t, \Fs_t\}$ is an
-$L_2$-mixingale of size $-1/2$; $D_t$ is $\Fs_t$-measurable and so it
-suffices to prove that
-\begin{equation}\label{eq:24}
-  \| \E_{t-l} D_t  - \E_R D_t \|_2 \leq 2^{2 + 1/\rho} B_L \, \couplingBeta{l}
-\end{equation}
-for $l = 1,\dots,t-R$, since $\couplingBeta{l} = O(l^{-1/2 - \delta})$
-for some $\delta > 0$ by assumption. Fix $R$, $t$ and $l$ and use
-Lemma \ref{lem-basic-coupling} to define $D_t^*$ so that
-\[
-\E_R D_t^* = \E_{t-l} D_t^* \quad a.s.
-\]
-and
-\[
-\lVert D_t - D_t^* \rVert_2 \leq \couplingBound{l}.
-\]
-Then
-\begin{align*}
-\lVert \E_{t-l} D_t - \E_R D_t \rVert_2 & \leq
-\lVert \E_{t-l} D_t - \E_{t-l} D_t^* \rVert_2  + \lVert \E_{t-l} D_t^* - \E_R D_t \rVert_2 \\
-&\leq 2 \lVert D_t - D_t^* \rVert_2 \\
-&\leq 2^{2 + 1/\rho}\ B_L\ \couplingBeta{l}.\tag*{\qed}
-\end{align*}
-
-\noindent Asymptotic normality follows from~\eqref{eq:24} using a
-modification of \citepos{Jon:97} CLTs for mixingale and NED arrays.
-Define
-\begin{equation*}
-  Z_i = \ZDef
-\end{equation*}
-where $b_T$ is a sequence that satisfies $b_T\leq P$,
-$b_T\to\infty$, and $b_T/P\to 0$.  The same arguments used in
-\citepos{Jon:97} Theorem 1 show that
-\begin{equation*}
-   \SumOuterBlock{i} Z_i = P^{-1/2} \oosSum{s}{1} (D_t - \E_R D_t) + o_p(1).
-\end{equation*}
-and
-\begin{equation*}
-  \SumOuterBlock{i} Z_i = \SumOuterBlock{i} (Z_i - E_{R + (i-1)b_T}
-  Z_i) + o_p(1).
-\end{equation*}
-Note that $\{Z_i - E_{R + (i-1)b_T} Z_i,\mathcal{F}_{R + i b_T}\}_i$ is an
-MDS by construction, so \citepos{HaH:80} Theorem 3.2 and Corollary
-3.1 ensure that $\sigma^{-1} \SumOuterBlock{i} Z_i \to^d N(0,1) $ as
-long as
-\begin{equation*}
-  \sigma^2 - \SumOuterBlock{i} \E_R Z_i^2 \to^p 0,
-\end{equation*}
-and
-\begin{equation*}
-  \SumOuterBlock{i} \E_R Z_i^2 - \SumOuterBlock{i} \ZSqCE \to^p 0.%
-\footnote{Note that $\sigma^2 \in \mathcal{F}_t$ for
-    all $t \geq R$, so Hall and Heyde's condition (3.21) is
-    unnecessary---see the remarks after their result.} %
-\end{equation*}
-The first equation holds as in \citet{Jon:97} (see the proof
-of his Theorem 2); the second is ensured by
-Lemma~\ref{lem:a2}. \qed
-
-\subsection*{Proof of Lemma \ref{res-convergence}}
-\newcommand{\resConvgRHS}[1]{\ensuremath{\E(L(y^* - x_1^{*\prime}\bh{1#1}) - L(y^{*} -
-x_2^{*\prime}\bh{2#1}) \mid \bh{#1})}}
-\newcommand{\resConvgEstDiff}[1]{\ensuremath{\E(L(y^{*} -
-    x_{#1}^{*\prime}\bh{#1R}) \mid \bh{R}) -
-\E(L(y^{*} - x_{#1}^{*\prime}\bh{#1T}) \mid \bh{T})}}
-\newcommand{\resConvgEstDiffRV}[1]{\ensuremath{L(y^{*} -
-    x_{#1}^{*\prime}\bh{#1R}) - L(y^{*} - x_{#1}^{*\prime}\bh{#1T})}}
-
-Equation~\eqref{eq:7} holds if we show
-\begin{gather}
-\E_R \oosA = \resConvgRHS{R} + o_p(P^{-1/2}),\label{eq:18}\\
-\E_T \oosB = \resConvgRHS{T} + o_p(Q^{-1/2}),\label{eq:19}
-\intertext{and}
-\resConvgEstDiff{i} = O_p(\sqrt{P/T}),\label{eq:20}
-\end{gather}
-where $\hat\theta_R = (\hat\theta_{1R}, \hat\theta_{2R})$,
-$\hat\theta_T = (\hat\theta_{1T}, \hat\theta_{2T})$, and $y^{*}$,
-$x_1^{*}$ and $x_2^{*}$ are random variables drawn from the joint
-distribution of $(y_{t+\h},x_{1t},x_{2t})$ independently of
-$\mathcal{F}_T$.
-
-\begin{proof}[Proof of~\eqref{eq:18} and~\eqref{eq:19}]
-For~\eqref{eq:18}, define $D_t^*$ for each $t=R+1,R+2,\dots,T-h$ so
-that
-\begin{equation*}
-  \| D_t^* - D_t \|_2 \leq 2^{(1+\rho)/\rho} B_L \beta_{t-R}^{(\rho-2)/2\rho}
-\end{equation*}
-and
-\begin{equation*}
-  \E_R D_t^* = \E(L(y^* - x_1^{*\prime}\hat\theta_{1R}) -
-  L(y^* - x_2^{*\prime}\hat\theta_{2R}) \mid \hat\theta_R) \qquad a.s.
-\end{equation*}
-Lemma~\ref{lem-basic-coupling} ensures that these $D_t^*$ exist.
-Now,
-\begin{align*}
-  \Big\lVert \E_R \oosA - \E\Big(P^{-1} \sum_{t=R+1}^{T-h} D_t^* \mid
-  \hat\theta_R\Big) \Big\rVert_2
-  &= \Big\lVert \E_R\Big( \oosA - P^{-1} \sum_{t=R+1}^{T-h} D_t^*
-  \Big) \Big\rVert_2 \\
-  &\leq P^{-1} \sum_{t=R+1}^{T-h} \lVert D_t - D_t^* \rVert_2\\
-  &= O(P^{-1}) \sum_{t=R+1}^{T-h} \beta_{t-R}^{(\rho-2)/2\rho}
-\end{align*}
-and this last term is $o(P^{-1/2})$ by assumption.
-Essentially the same argument proves~\eqref{eq:19} as well.
-\end{proof}
-
-\begin{proof}[Proof of~\eqref{eq:20}]
-Assumption~\ref{asmp-3} and the definition of the OLS estimator
-ensure that
-\begin{align*}
-  \|L(y^{*} -  x_i^{*\prime} \bh{iR}) - L(y^{*} - x_i^{*\prime} \bh{iT}) \|_1
-  &\leq B_{L} \| x_i^{*\prime} (\bh{iR} - \bh{iT}) \|_2 \\
-  &\leq B_{L} \, \| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
-  (X_{iR}'X_{iR})^{-1}] X_{iR}' \eb_{iR} \|_2 \\
-  &\quad+ B_L \, \| x_i^{*\prime}
-  (X_{iT}'X_{iT})^{-1}[X_{iT}'\eb_{iT} - X_{iR}
-  \eb_{iR} ] \|_2 .
-\end{align*}
-
-To simplify notation, define $V = (X_{iT}'X_{iT})^{-1} -
-(X_{iR}'X_{iR})^{-1}$ and $W = X_{iR}'\eb_{iR} \eb_{iR}'X_{iR}$. The
-first term in the upper bound satisfies
-\begin{align*}
-  \| x_i^{*\prime} V X_{iR}' \eb_{iR} \|_2^2
-  &\leq \eigen_{K_i}(\E x_i^* x_i^{*\prime}) \cdot \E \tr\big( V^2 W \big) \\
-  &= O(1) \cdot \E \tr\{ V^2 \E(W \mid
-  X_{iR}'X_{iR}, x_{i,R-\h+1} x_{i,R-\h+1}',\dots, x_{i,T-\h} x_{i,T-\h}')\}
-\end{align*}
-by assumption. Observe that
-\begin{multline*}
-  \E \tr\{ V^2 \E(W \mid X_{iR}'X_{iR}, x_{i,R-\h+1} x_{i,R-\h+1}',\dots, x_{i,T-\h} x_{i,T-\h}')\}
-  \\ \leq
-  \Big\rVert \sum_{i=1}^{K_i} \eigen_i^2 \big(V\big) \Big\rVert_{3/2}
-  \big\rVert \eigen_{K_i}(\E(W \mid
-  X_{iR}'X_{iR}, x_{i,R-\h+1} x_{i,R-\h+1}',\dots, x_{i,T-\h} x_{i,T-\h}')) \big\rVert_3.
-\end{multline*}
-The second term in this product is $O(R)$ by
-Assumption~\ref{asmp-2}. To bound the first term, note that
-$(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}$ has rank $P$ and
-each of its nonzero eigenvalues is bounded in absolute value by the
-eigenvalues of $(X_{iR}'X_{iR})^{-1}$. The eigenvalues of
-$(X_{iR}'X_{iR})^{-1}$ are $O_{L_3}(1/R)$ by Assumption~\ref{asmp-2}, so
-\begin{equation*}
-  \Big\|\sum_{j=1}^{K_i}
-  \eigen_j^2(V)\Big\|_{3/2}
-  \leq \Big\|\sum_{j=K_i - P+1}^{K_i} \eigen_j^2(V) \Big\|_{3/2}
-  = O(P/R^2).
-\end{equation*}
-Consequently,
-\begin{equation*}
-  \E \tr\bigg\{[(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}]^2
-  X_{iR}'\eb_{iR} \eb_{iR}X_{iR} \bigg\} = O(P/R)
-\end{equation*}
-and so
-\begin{equation*}
-  \| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
-  (X_{iR}'X_{iR})^{-1}] X_{iR}' \eb_{iR} \|_2 = O(\sqrt{P/R}).
-\end{equation*}
-
-A similar argument proves that
-\begin{equation*}
-  \big\| x_i^{*\prime} (X_{iR}'X_{iR})^{-1}
-  [X_{iT}'\eb_{iT} - X_{iR} \eb_{iR} ] \big\|_2 =  O(\sqrt{P/R}),
-\end{equation*}
-completing the proof.
-\end{proof}
-
-\subsection*{Proof of Theorem \ref{res-oost}}
-We can rewrite the centered \oost\ statistic as
-\[
-\sqrt{P}(\oosA - \E_T \oosB)/\sh
-= \frac{\sigma}{\sh}\, \Big( \sqrt{P}(\oosA - \E_R \oosA)/\sigma
-+ \sqrt{P}(\E_R \oosA - \E_T \oosB)/\sigma \Big)
-\]
-so Lemma \ref{res-mixingale} and \ref{res-convergence} ensure that
-this term is asymptotically standard normal as long as $\sigma/\sh
-\to^p 1$. Since $\sigma$ is almost surely positive, this convergence
-is equivalent to $\sigma^2 - \sh^2 \to^p 0$.
-
-The proof that $\sigma^2 - \sh^2 \to^p 0$ follows \citepos{JoD:00}
-Theorem 2.1 closely.  We start by defining similar quantities to
-theirs, borrowing their notation when possible to make the
-similarities apparent. Let $b_T \equiv \lfloor \gamma/\delta \rfloor$,
-define $\kernelB{x}$ as in Equation \eqref{eq:13}, and define the following
-terms as in \citet{JoD:00}:
-\begin{align*}
-  \varianceTermI &\equiv
-  \varianceTermIDefn,\\ \varianceTermII &\equiv \vtSum
-  \varianceTermIIa\\& \quad \times \varianceTermIIb,\\
-  \varianceTermIII &\equiv \vtSum \varianceTermIIIa\\
-  &\quad \times \varianceTermIIb,\\
-  \varianceTermIV &\equiv \vtSum \varianceTermIIIa \\
-  &\quad\times \varianceTermIVb.
-\end{align*}
-These definitions give the inequalities
-\begin{align*}
-  \lVert \sh^2 - \sigma^2 \rVert_1 &
-  \leq \lVert \sh^2 - \varianceTermI \rVert_1
-  + \lVert \varianceTermI - \varianceTermII \rVert_1
-  + \lVert \varianceTermII - \varianceTermIII \rVert_1
-  + \lVert \varianceTermIII - \varianceTermIV \rVert_1\\ & \quad
-  + \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1
-  + \lVert \E_R\varianceTermIII - \E_R\varianceTermIV \rVert_1
-  + \lVert \E_R\varianceTermII - \E_R\varianceTermIII \rVert_1\\ & \quad
-  + \lVert \E_R\varianceTermI - \E_R\varianceTermII \rVert_1
-  + \lVert \E_R \varianceTermI - \sigma^2 \rVert_1
-  \\ &
-  \leq  \lVert \sh^2 - \varianceTermI \rVert_1
-  + 2(\lVert \varianceTermI - \varianceTermII \rVert_1
-      + \lVert \varianceTermII - \varianceTermIII \rVert_1
-      + \lVert \varianceTermIII - \varianceTermIV \rVert_1) \\
-  & \quad + \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1
-  + \lVert \E_R \varianceTermI - \sigma^2 \rVert_1.
-\end{align*}
-De Jong and Davidson (2000) prove that
-\begin{equation*}
-\lim_{\delta\to0} \limsup_{T\to\infty} \lVert \varianceTermI -
-\varianceTermII\rVert_1 = 0,
-\end{equation*}
-\begin{equation*}
-\lim_{\delta\to0} \limsup_{T\to\infty} \lVert \varianceTermII - \varianceTermIII
-\rVert_1 = 0,
-\end{equation*}
-\begin{equation*}
-\lim_{\delta\to0} \limsup_{T\to\infty} \lVert \varianceTermIII - \varianceTermIV
-\rVert_1 = 0,
-\end{equation*}
-and
-\begin{equation*}
-\lim \lVert \E_R \varianceTermI - \sigma^2 \rVert_1 = 0.
-\end{equation*}
-Their proofs of these four convergence results use the fact that NED
-functions of mixing processes are also mixingale processes and do not
-use any other properties specific to NED processes, so their results
-hold here as well.  We do need to modify their proofs that
-\begin{equation*}
-  \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1 \to 0
-\end{equation*}
-and
-\begin{equation*}
-  \lVert \sh^2 - \varianceTermI \rVert_1 \to 0
-\end{equation*}
-for all positive $\delta$, though, since those proofs exploit NED
-properties. These results are presented as Lemmas~\ref{lem:a2}
-and~\ref{lem:a6} respectively.  \qed
-
-\subsection*{Proof of Theorem \ref{res:oostest}}
-Coverage of the confidence intervals is immediate from
-Theorem~\ref{res-oost}, so we will present a proof of~\eqref{eq:23}.
-By Lemma~\ref{res-convergence}, we know that $\E_R \oosA - \E_T \oosB
-\to^p 0$, so
-\begin{equation*}
-  \Pr[\E_R \oosA \leq 0] - \Pr[\E_T \oosB \leq 0] \to 0.
-\end{equation*}
-Now we can use Lemma~\ref{lem-basic-coupling} to define $D_t^*$ as in
-the proofs of Lemma~\ref{res-mixingale} and~\ref{res-convergence} so
-that $\E_R D_t^* = \E_{t-l} D_t^*$ a.s. and
-\[
-\lVert D_t - D_t^* \rVert_2 \leq \couplingBound{l}
-\]
-and define $\oosA^* = P^{-1} \sum_{t=R+1}^{T-\h} D_t^*$. Then
-\begin{equation*}
-  \lVert \sqrt{P} \oosA - \sqrt{P} \oosA^* \rVert_2
-  \leq P^{-1/2} \sum_{t=R+1}^{T-\h} \lVert \oosA - \oosA^* \rVert_2
-  = o(1),
-\end{equation*}
-and, consequently, we have convergence in probability of the following
-vectors:
-\begin{equation*}
-  (\sqrt{P} \oosA^*/\sigma,\ \E_R \oosA) -
-  (\sqrt{P} \oosA/\sh,\ \E_T \oosB) \to^p 0,
-\end{equation*}
-where we are implicitly using consistency of $\sh^2$ for $\sigma^2$.
-More importantly, this implies convergence in distribution of these
-vectors, so
-\begin{equation*}
-  \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha
-  \text{ and } \E_R \oosA \leq 0]
-  - \Pr[\sqrt{P} \oosA / \sh > z_\alpha \text{ and }
-  \E_T \oosB \leq 0] \to 0.
-\end{equation*}
-
-For large enough $T$, both $\Pr[\E_R \oosA \leq 0]$ and $\Pr[\E_T
-\oosB \leq 0]$ are positive (the second by assumption, the first by
-convergence to the second) so (for these $T$)
-\begin{align}\label{eq:31}
-  \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha
-  \mid \E_R \oosA \leq 0] &=
-  \frac{\Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha \text{ and }
-    \E_R \oosA \leq 0]}{\Pr[\E_R \oosA \leq 0]}
-\intertext{and}\label{eq:32}
-  \Pr[\sqrt{P} \oosA / \sh > z_\alpha
-  \mid \E_T \oosB \leq 0] &=
-  \frac{\Pr[\sqrt{P} \oosA / \sh > z_\alpha \text{ and }
-    \E_T \oosB \leq 0]}{\Pr[\E_T \oosB \leq 0]}
-\end{align}
-almost surely. Since the terms on the RHS of Equations~\eqref{eq:31}
-and~\eqref{eq:32} converge to the same limit in probability, we have
-\begin{equation*}
-  \Pr[\sqrt{P} \oosA / \sh > z_\alpha  \mid \E_T \oosB \leq 0]
-  - \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha \mid \E_R \oosA \leq 0]
-  \to^p 0
-\end{equation*}
-and it suffices to show that
-\begin{equation*}
-  \plim \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha \mid \E_R \oosA \leq 0]
-  \leq \alpha.
-\end{equation*}
-
-To establish this inequality, we have
-\begin{align*}
-  \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha \mid \E_R \oosA \leq 0]
-  &\leq \Pr[\sqrt{P} (\oosA^* - \E_R \oosA) / \sigma > z_\alpha
-  \mid \E_R \oosA \leq 0] \\
-  &\leq \E\big(
-  \Pr[\sqrt{P} (\oosA^* - \E_R \oosA) / \sigma > z_\alpha \mid \Fs_R]
-  \mid \E_R \oosA \leq 0\big).
-\end{align*}
-By construction,
-\begin{equation*}
-  \Pr[\sqrt{P} (\oosA^* - \E_R \oosA) / \sigma > z_\alpha \mid \Fs_R]
-  \to \alpha
-\end{equation*}
-since generated pseudo OOS observations in each $D_t^*$ are
-independent of $\Fs_R$, completing the proof.
-\qed
-
-\subsection*{Proof of Theorem~\ref{res:insample1}}
-
-Let $(\e_{t+h}, x_{t}) \sim i.i.d.\ N(0,I)$ and let $\theta_1 = 0$.
-For any $d \geq 0$, the event $\E_T \oosB = -d$ implies that
-\begin{equation*}
-  \E_T (y_{T+\h+1} - x_{1T+1}'\bh{1T})^2
-  = \E_T (y_{T+\h+1} - x_{2T+1}'\bh{2T})^2 - d \quad a.s.
-\end{equation*}
-which can be expressed as
-\begin{equation}\label{eq:34}
-  d + \theta_2'M_2' M_2 \theta_2 + \bh{1T}'\bh{1T} - \bh{2T}'M_1'M_1\bh{2T}
-  = (\bh{2T} - \theta_2)' M_2'M_2 (\bh{2T} - \theta_2) \quad a.s.
-\end{equation}
-$M_2 \bh{2T}$ is normally distributed conditional on $\bh{1T}$ and
-$M_1 \bh{2T}$, and is distributed on the surface of the sphere defined
-by~\eqref{eq:34} conditional on $\bh{1T}$, $M_1 \bh{2T}$, and the
-event $\E_T \oosB = -d$.
-
-Since $M_2 \bh{2T}$ is normal, this conditional distribution is
-invariant to reflection across the axes defined by the eigenvectors of
-its covariance matrix. So when $\theta_2$ lies outside the cylinder
-that contains the acceptance region of $\Lambda$, i.e. when
-$\theta_2'M_2' V_T M_2 \theta_2 > c$, we have%
-\footnote{To keep the notation in these equations manageable, define
-  the information set $\Gs = \sigma(\E_T \oosB \leq 0,~ \theta_2'M_2'
-  V_T M_2 \theta_2 > c)$.} %
-\begin{align*}
-  \Pr[ \bh{2T}' M_2' V_T M_2 \bh{2T} \leq c \mid \Gs]
-  &= \E\Big( \Pr[ \bh{2T}'M_2' V_T M_2 \bh{2T} \leq c \mid \Gs,~\bh{1T},~M_1 \bh{2T}] \mid \Gs \Big) \\
-  & < 1/2
-\end{align*}
-since the inner conditional probability is less than 1/2.
-
-Now let $\delta > 0$ be an arbitrary but small constant, and choose
-$\theta_2$ far enough from the origin to ensure that
-\begin{equation*}
-  \Pr[\theta_2'M_2' V_T M_2 \theta_2 \leq c] \leq \delta
-\end{equation*}
-for large enough $T$. Then
-\begin{align*}
-  \E(\Lambda \mid \E_T \oosB \leq 0) &
-  \geq \Pr[\bh{2T}' M_2' V_T M_2 \bh{2T} > c \mid \E_T \oosB \leq 0] \\
-  &= \Pr[\bh{2T}' M_2' V_T M_2 \bh{2T} > c \text{~~and~~}
-  \theta_2'M_2' V_T M_2 \theta_2 > c \mid \E_T \oosB  \leq 0] \\
-  & \quad + \Pr[\bh{2T}' V_T M_2 \bh{2T} > c \text{~~and~~ }
-  \theta_2'M_2' V_T M_2 \theta_2 \leq c \mid \E_T \oosB \leq 0].
-\end{align*}
-The second term is nonnegative by design. By conditioning on
-$\theta_2'M_2' V_T M_2 \theta_2 > c$ our earlier argument shows that
-the first term is greater than or equal to $(1 - \delta) / 2$. Since
-$\delta$ is arbitrarily small, this completes the proof.
-\qed
-
-\subsection*{Proof of Theorem~\ref{res:insample2}}
-As in the proof of Theorem~\ref{res:insample1}, let $(\e_{t+h}, x_{t})
-\sim i.i.d.\ N(0,I)$ and let $\theta_1 = 0$. The event $\E_T \oosB
-\geq 0$ implies that
-\begin{equation*}
-  \E_T (y_{T+\h+1} - x_{1T+1}'\bh{1T})^2
-  \geq \E_T (y_{T+\h+1} - x_{2T+1}'\bh{2T})^2 \quad a.s.
-\end{equation*}
-which can be expressed as
-\begin{equation}\label{eq:2}
-  \theta_2'M_2 M_2'\theta_2 + \bh{1T}'\bh{1T} - \bh{2T}'M_1'M_1\bh{2T}
-  \geq (\bh{2T} - \theta_2)' M_2'M_2 (\bh{2T} - \theta_2) \quad a.s.
-\end{equation}
-$M_2 \bh{2T}$ is normally distributed conditional on $\bh{1T}$ and
-$M_1 \bh{2T}$, and is a.s. contained in the sphere defined
-by~\eqref{eq:2} conditional on $\bh{1T}$, $M_1 \bh{2T}$, and the
-event $\E_T \oosB \geq 0$.
-
-Let $\delta$ be a small arbitrary constant, define $\theta^*$ as
-\begin{gather*}
-  \theta^* = \argmax_\theta \theta' M_2' M_2 \theta \\
-  s.t.\quad \theta_2'M_2'M_2\theta_2 +  \bh{1T}'\bh{1T} - \bh{2T}'M_1'M_1\bh{2T} = (\theta - \theta_2)' M_2'M_2 (\theta - \theta_2)
-\end{gather*}
-($\theta^*$ is stochastic and depends on $\bh{1T}$ and $M_1 \bh{2T}$)
-and choose $c$ so that
-\begin{equation*}
-  \Pr[ \theta^{* \prime} M_2 M_2 \theta^* > c] < \delta.
-\end{equation*}
-
-Then, we have for large enough $T$
-\begin{align*}
-  \E(\Lambda \mid \E_T \oosB \geq 0) &\leq
-  \Pr[\bh{2T}'M_2'M_2\bh{2T} > c \mid \E_T \oosB \geq 0) \\
-  &\leq \delta
-\end{align*}
-Since $\delta$ is arbitrarily close to zero, this completes the proof.
-
-\qed
-
-\clearpage
-\markboth{}{}
-\tryinput{floats/mc-ftest.tex}
-
-\begin{table}[tb]
-  \begin{tabularx}{\linewidth}{XX}
-    \toprule
-    Category & Variable \\
-    \midrule
-    Stock market variables
-    & Dividend to price ratio (log) \\
-    & Earnings to price ratio (log) \\
-    & Stock market variance \\
-    & Book to market ratio \\
-    & Net equity expansion \\
-    & Percent equity issuing \\\\
-    Interest rate variables
-    & Treasury Bill rate (3 month) \\
-    & Long term yield \\
-    & Long term rate \\
-    & Default return spread \\
-    & Default yield spread \\
-    & Inflation rate \\
-    \bottomrule
-  \end{tabularx}
-  \caption{Variables used to predict the equity premium
-    (Section~\ref{sec:empirics}).
-    Please see Goyal and Welch's original paper \citep{GoW:08}
-    for a detailed description of each variable.}
-  \label{tab:equity}
-\end{table}
-
-\tryinput{floats/empirics-insample.tex}
-\tryinput{floats/empirics-insample-tuned.tex}
-% These macros create tables. They are defined in
-% floats/empirics-insample.tex and possibly overwritten in the next
-% file.
-\insamplecoefs
-\insampletests
-
-\begin{figure}\centering
-  {\large Coverage of DMW OOS interval for $\E_R\oosA$ in simulations}
-  \tryinput{floats/mc-interval-testerror1.tex}
-  \caption{Simulated coverage of $\E_R \oosA$ at 90\% confidence using
-    a one-sided interval based on the DMW \oost\ test, plotted as a
-    function of the fraction of observations used in the test sample,
-    $P/T$. The solid horizontal line denotes the intervals' nominal
-    coverage.}
- \label{fig:interval-R}
-\end{figure}
-\clearpage
-
-\begin{figure}\centering
-  {\large Coverage of DMW OOS interval for $\E_T\oosB$ in simulations}
-  \tryinput{floats/mc-interval-generror1.tex}
-  \caption{Simulated coverage of $\E_T \oosB$ at 90\% confidence using
-    a one-sided interval based on the DMW \oost\ test, plotted as a
-    function of the fraction of observations used in the test sample,
-    $P/T$.  The solid horizontal line denotes the intervals' nominal
-    coverage.}
-  \label{fig:interval-T}
-\end{figure}
-\clearpage
-
-\begin{figure}\centering
-  {\large Size of DMW \oost\ test in simulations}
-  \tryinput{floats/mc-dmwsize.tex}
-  \caption{Simulated rejection probabilities for the DMW \oost\ test
-    under the null hypothesis that the benchmark model will forecast
-    better, $\E_T \oosB \leq 0$. The nominal size is 10\% and is
-    marked with a solid horizontal line. Values greater than 10\%
-    indicate that the test rejects the benchmark model too often. See
-    Section~\ref{sec:simulation-design} for a discussion of the
-    simulation design.}
-  \label{fig:ttest-size}
-\end{figure}
-\clearpage
-
-\begin{figure}\centering
-  {\large Size of Clark-West OOS test in simulations}
-  \tryinput{floats/mc-clarkwestsize.tex}
-  \caption{Simulated rejection probabilities for Clark and West's
-    (2006, 2007) OOS test statistic under the null hypothesis that the
-    benchmark will forecast better, $\E_T \oosB \leq 0$. The nominal
-    size is 10\% and is marked with a solid horizontal line. Values
-    greater than 10\% indicate that the test rejects the benchmark
-    model too often. See Section~\ref{sec:simulation-design} for a
-    discussion of the simulation design.}
-   \label{fig:clarkwest}
-\end{figure}
-\clearpage
-
-\begin{figure}\centering
-  {\large Size of McCracken \oost\ test in simulations}
-  \tryinput{floats/mc-mccrackensize.tex}
-  \caption{Simulated rejection probabilities for McCracken's (2007)
-    \oost\ test under the null hypothesis that the benchmark model is
-    more accurate, $\E_T \oosB \leq 0$. Nominal size is 10\% and is
-    marked with a solid horizontal line. Values greater than 10\%
-    indicate that the test rejects the benchmark model too often. See
-    Section~\ref{sec:simulation-design} for a discussion of the
-    simulation design.}
-  \label{fig:mccracken}
-\end{figure}
-\clearpage
-
-\begin{figure}\centering
-  {\large Power of DMW \oost\ test in simulations}
-  \tryinput{floats/mc-dmwpower.tex}
-  \caption{Simulated rejection probabilities for the DMW \oost\ test
-    under the alternative that the benchmark model is less accurate,
-    $\E_T \oosB > 0$. Nominal size is 10\% and is marked with a solid
-    horizontal line. Values greater than 10\% indicate that the test
-    rejects the benchmark model too often. See
-    Section~\ref{sec:simulation-design} for a discussion of the
-    simulation design.}
-  \label{fig:ttest-power}
-\end{figure}
-\clearpage
-
-\begin{figure}
-\centering
-\large{Difference in OOS MSE of Prevailing Mean and\\ Kitchen
-    Sink Models of Equity Premium (OLS)}
-\tryinput{floats/empirics-oos-mse-1.tex}
-\tryinput{floats/empirics-oos-mse-1b.tex}
-\caption{OOS difference in the MSE
-  of the prevailing mean benchmark and the kitchen sink model as a
-  function of the test sample size, $R$.  Both models forecast the
-  equity premium using annual data from 1928--2008.  The solid line
-  gives the OOS average, and the shaded region indicates the
-  one-sided 95\% confidence interval implied by the
-  DMW test.  The bottom panel is a detailed view of the top
-  panel for $R \geq 50$.}
-\label{fig:empirics1}
-\end{figure}
-\clearpage
-
-\begin{figure}
-\centering
-\large{Difference in OOS MSE of Prevailing Mean and\\ Kitchen
-    Sink Models of Equity Premium (CT)}
-\tryinput{floats/empirics-oos-mse-2.tex}
-\tryinput{floats/empirics-oos-mse-2b.tex}
-\caption{OOS difference in the MSE
-  of the prevailing mean benchmark and the kitchen sink model as a
-  function of the test sample size, $R$.  Both models forecast the
-  equity premium using annual data from 1928--2008.  The solid line
-  gives the OOS average, and the shaded region indicates the
-  one-sided 95\% confidence interval implied by the
-  DMW test.  The bottom panel is a detailed view of the top
-  panel for $R \geq 50$.}
-\label{fig:empirics2}
-\end{figure}
-\clearpage
-
-\begin{figure}
-\centering
-\large{OOS MSE of Individual Forecasts of Equity Premium}
-\tryinput{floats/empirics-oos-ind-ks.tex}
-\tryinput{floats/empirics-oos-ind-pm.tex}
-\caption{OOS MSE of the Prevailing Mean (PM) and
-    Kitchen Sink (KS) models for equity premium prediction as
-    a function of the size of the training sample, $R$.  Please note
-    that the vertical scales are different in the two plots.}
-\label{fig:empirics3}
-\end{figure}
-
-\clearpage
+\include{B-tables}
+\include{C-figures}
 
@@
 \bibliography{latex-tools-0.2.1/references}
+
+\include{D1-example}
+\include{D2-simulations}
 

### 2017-05-03 3-theory.tex
Split main paper.tex into several smaller files
This commit moves the content of the paper into several smaller
files that are \included; this allows us to use \includeonly
to minimize compilation time.

@@
 
+\subsection{An extended simple example}
+\label{sec:example}
+
+This subsection illustrates the previous theoretical results with a
+concrete example. Let $L(e) = e^2$ and $h = 1$. Suppose that the benchmark is
+nested in the alternative and $(x_{2t}, \e_{2,t+1}) \sim i.i.d.\
+N(0,I)$, and let $y_{t+1} = x_{2t}'\theta_2 + \e_{2,t+1}$
+be the DGP. Also assume that $K_2/T \to c_2$ and $K_1 / T \to c_1 <
+c_2$.
+
+The first part of this subsection shows how the assumptions in
+Section~\ref{sec:asmp} are satisfied and the second part
+demonstrates asymptotic normality of the DMW \oost\ test. The third
+part explicitly shows that $\E_R \oosA$ converges to $\E_T \oosB$ only
+when the test sample is small. And the last part demonstrates that the
+$F$-test does not indicate which model will be more
+accurate in the future, even in this simple example.
+
+\subsubsection*{Fulfillment of Assumptions 1--5}
+
+We will go through the assumptions one by one. The first is
+a condition on the dependence and moments of the process. Since the
+DGP is i.i.d. Normal, these conditions are satisfied trivially.
+
+Assumption~\ref{asmp-2} deals with the design matrix. In this example,
+we directly assume that $K_2$ and $K_1$ grow at the correct rates so
+the the assumption is satisfied. The variance of $y_{t+1}$ given
+$\Fs_t$ is simply the unconditional variance of $\e_{2,t+1}$, which is
+1; and the eigenvalues of $\E x_{2t} x_{2t}$ all equal 1 as well; and
+so they are all uniformly positive and finite as required.
+
+Assumption~\ref{asmp-2} also requires the eigenvalues of $S^{-1}
+X_{iS}'X_{iS}$ to be positive and finite, and for the largest
+eigenvalue of $S^{-1} X_{iS}'X_{iS}$ to be bounded in $L_3$.  These
+results follow from developments in random matrix theory.
+\citet{Gem:80} establishes that the largest eigenvalue of
+$X_{iS}'X_{iS}$ is of order $S + K_i$ and \citet{Joh:01} shows that it
+converges in distribution to the Tracy-Widom law of order 1
+\citep{TrW:96}, which has finite 3rd moments. \citet{Sil:85} and
+\citet{BFP:98} prove similar results for the smallest eigenvalue.
+Assumption~\ref{asmp-2} also requires the largest eigenvalue of
+$(X_{iS}'X_{iS})^{-1}$ be bounded in $L_3$; this should follow from a
+similar argument, but we are unaware of any papers that explicitly
+derive moments for this eigenvalue.
+
+For the conditional expectation of %
+$\sum_{s,t=U}^{V-1} \e_{i,t+1} \e_{i,s+1} x_{i,s} x_{i,t}'$,
+independence implies that
+\begin{equation*}
+  \E\Big(
+  \sum_{s,t=U}^{V-1} \e_{i,s+1} \e_{i,t+1} x_{is}x_{it}'
+  \mBig
+  x_{i1},\dots,x_{i,U-1};
+  \sum_{s=U}^{V-1} x_{is} x_{is}';
+  x_{i,V},\dots,x_{i,T-1}
+  \Big)
+  = \sum_{s=U}^{V-1} x_{is} x_{is}'.
+\end{equation*}
+The largest eigenvalue of this last matrix is of order $K_i + V - U$,
+as discussed, and it has at most $V - U$ nonzero eigenvalues,
+ensuring that both~\eqref{eq:28} and~\eqref{eq:8} hold.
+
+Assumption~\ref{asmp-3} restricts the loss function and the realized
+OOS loss. In this example, we have
+\begin{equation*}
+  D_t^* =^d D_t = (e_{2,t+1} + x_{2t}'\theta_2 - x_{1t}'\bh{1t})^2
+  - (e_{2,t+1} + x_{2t}'(\theta_2 - \bh{2t}))^2
+\end{equation*}
+which has bounded $\rho$th moments by construction. The loss function
+is differentiable and $L'(e) = 2 e$, so \eqref{eq:29} holds as well.
+
+Finally, Assumption~\ref{asmp-4} deals with the choice of test and
+training sample and holds automatically. And Assumption~\ref{asmp-5}
+requires the kernel of the HAC variance estimator to be continuous at
+zero; it is straightforward to construct an estimator that satisfies
+this condition. However, in this section we will use the estimator
+\begin{equation*}
+  \sh^2 = \frac{1}{P} \sum_{t=R+1}^{T-1} (D_t - \oosA)^2
+\end{equation*}
+which does not satisfy Assumption~\ref{asmp-5} but nevertheless is
+consistent for the conditional variance of $\oosA$ because the
+underlying observations are independent.
+
+\subsubsection*{Asymptotic normality of the OOS average, Lemma 1}
+
+This subsection walks through Lemma 1's CLT. Since the observations in
+this example are i.i.d., we do not need to use mixingale theory to
+derive the results, but the OOS process is still affected by the
+estimation error in $\bh{1t}$ and $\bh{2t}$ and has a high degree of
+dependence. This dependence makes the OOS process an MDS, and MDS
+asymptotic theory replaces mixingale theory in this example.
+
+By construction, we have
+\begin{equation*}
+  D_t =
+  \begin{cases}
+    2 \e_{t+1} (x_{2t}'\bh{2R} - x_{1t}'\bh{1R})
+    + (x_{2t}'\theta_2 - x_{1t}'\bh{1R})^2
+    - (x_{2t}'\theta_2 - x_{2t}'\bh{2R})^2
+    & \text{if } t < T \\
+    2 \e_{t+1} (x_{2t}'\bh{2T} - x_{1t}'\bh{1T})
+    + (x_{2t}'\theta_2 - x_{1t}'\bh{1T})^2
+    - (x_{2t}'\theta_2 - x_{2t}'\bh{2T})^2
+    & \text{if } t > T
+  \end{cases}
+\end{equation*}
+and so we can explicitly derive the components of
+Lemma~\ref{res-mixingale}. First,
+\begin{multline*}
+  D_t - \E_R D_t
+  = 2 \e_{t+1} (x_{2t}'\bh{2R} - x_{1t}'\bh{1R})
+  + \Big\{(x_{2t}'\theta_2 - x_{1t}'\bh{1R})^2
+          - \E_R (x_{2t}'\theta_2 - x_{1t}'\bh{1R})^2 \Big\} \\
+  - \Big\{(x_{2t}'\theta_2 - x_{2t}'\bh{2R})^2
+          - \E_R (x_{2t}'\theta_2 - x_{2t}'\bh{2R})^2 \Big\}
+\end{multline*}
+for $t < T$. Since the underlying observations are i.i.d., $\E_{t-1}
+D_t = \E_R D_t$ a.s.\ and consequently $\{D_t - \E_R D_t, \Fs_{t};
+t=R+1,\dots,T-1\}$ is an MDS.
+
+Although transformations of $D_t - \E_R D_t$ will obviously not be
+MDSes in general, it should be clear that transformations of $D_t$
+will be MDSes after subtracting their conditional mean; i.e.
+\begin{equation*}
+  \{g(D_t) - \E_R g(D_t); \Fs_t; t = R+1,\dots,T-1\}
+\end{equation*}
+is an MDS as long as
+$g(D_t)$ has finite mean, but $g(D_t - \E_R D_t)$ is not. This MDS
+result holds because $x_t$ and $y_{t+1}$ are independent of $\bh{1R}$
+and $\bh{2R}$, so
+\begin{equation*}\begin{split}
+  \E_R g(D_t)
+  &= \int g\Big((x_1'\bh{1R})^2 - (x_2'\bh{2R})^2
+       + 2 y (x'\bh{2R} - x'\bh{1R})\Big) \, f(y, x) \, dx \, dy \\
+  &= \E_{t-1} g(D_t)
+\end{split}\end{equation*}
+a.s., where $f$ is the density of $(y_{t+1}, x_{2t})$ and $x_1$
+denotes the first $K_1$ elements of $x$. This result parallels our
+results for mixingales in the general case.
+
+As a result, $\oosA$ and $(1/P) \sum_{t=R+1}^{T-1} D_t^2$ both obey
+LLNs: $\oosA \to^p \E_R \oosA$ and
+\begin{equation*}
+  (1/P) \sum_{t=R+1}^{T-1} D_t^2 \to^p \E_R D_T^2.
+\end{equation*}
+Moreover, these convergence results imply that $\sh^2 - \var_R
+\sqrt{P} \oosA \to^p 0$. And so
+\begin{equation*}
+  \sqrt{P} \oosA/\sh \to N(0,1)
+\end{equation*}
+by the MDS CLT.
+
+\subsubsection*{Convergence of $\E_R \oosA$ to $\E_T \oosB$, Lemma 2}
+
+This subsection works through Lemma~\ref{res-convergence}. In this
+example, the difference between $\E_R \oosA$ and $\E_T \oosB$ equals
+\begin{equation*}
+  \begin{split}
+    \E_R \oosA - \E_T \oosB &= \Big\{(\bh{1R} - \theta_1)'(\bh{1R} -
+    \theta_1) -
+    (\bh{2R} - \theta_2)'(\bh{2R} - \theta_2)\Big\} \\
+    & \quad - \Big\{(\bh{1T} - \theta_1)'(\bh{1T} - \theta_1) -
+    (\bh{2T} - \theta_2)'(\bh{2T} - \theta_2)\Big\} \\
+    &\begin{split}
+      =\ep{T}'\Big\{
+      & \tilde{X}_{1R}(X_{1R}'X_{1R})^{-2} \tilde{X}_{1R}'
+      - X_{1T}(X_{1T}'X_{1T})^{-2} X_{1T}' \\
+      & - \tilde{X}_{2R}(X_{2R}'X_{2R})^{-2} \tilde{X}_{2R}'
+      + X_{2T}(X_{2T}'X_{2T})^{-2} X_{2T}'
+      \Big\}\ep{T}.
+    \end{split}
+  \end{split}
+\end{equation*}
+with $\tilde{X}_{iR}$ the $T \times K_i$ matrix $[X_{iR}'\ 0]'$. This
+last term is a quadratic form and the regressors and errors are
+assumed to be normal, so we can find the rate that the difference
+converges to zero in probability by calculating its first two moments.
+
+The mean difference is
+\begin{equation*}
+  \begin{split}
+  \E(\E_R \oosA - \E_T \oosB)
+      &=O\Big(\max_i \E \tr \big\{
+        \tilde{X}_{iR}(X_{iR}'X_{iR})^{-2} \tilde{X}_{iR}
+        - X_{iT}(X_{iT}'X_{iT})^{-2} X_{iT} \big\} \Big) \\
+      &=O\Big(\max_i \tr \big\{\E (X_{1R}'X_{1R})^{-1}
+         - \E (X_{1T}'X_{1T})^{-1} \big\}\Big) \\
+      &=O( K_1 P / (R-K_1)(T-K_1)) \\
+      &=O(P/T)
+    \end{split}
+\end{equation*}
+The first equality follows from the expectation of a quadratic form,
+the second from routine manipulations of the trace operator, and the
+third from the moments of the inverse Wishart distribution.
+
+Similarly, the variance of the difference is
+\begin{align*}
+  \var(\E_R & \oosA - \E_T \oosB) \\ &=
+  O\Big(\max_i \E\big[\tr((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1})\big]^2
+  + 2 \tr \E\big((X_{iR}'X_{iR})^{-2} - (X_{iT}'X_{iT})^{-2}\big) \\
+  &\qquad - \big[\tr \E((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}) \big]^2 \Big)\\
+  &= O(P/T)^2.
+\end{align*}
+So, in this example, $P^{1/2}(\E_R \oosA - \E_T \oosB) \to^p 0$
+if $P^3/T^2 \to 0$, which is slightly weaker than the general
+requirement that $P^2/T \to 0$.  If $\lim P^3/T^2 > 0$ the OOS average
+still obeys the MDS CLT, but it is not centered correctly at $\E_T
+\oosB$.
+
+\subsubsection*{Behavior of the F-test}
+
+This part illustrates the behavior of full-sample statistics in our
+simple example. To simplify the presentation even more, assume that
+the full-sample design matrix is orthogonal in-sample, not just in
+population, so $X_{2T}'X_{2T} = T \cdot I_{K_2 \times K_2}$, and again
+let $M_1$ and $M_2$ be the selection matrices for the first $K_1$ and
+the last $K_2-K_1$ elements of $\theta_2$. In this example,
+\begin{equation*}
+  M_2 \bh{2T} \sim
+  N(M_2 \theta_2, (1/T) \, I_{K_2-K_1})
+\end{equation*}
+and, conditional on $\E_T \oosB = 0$, the density of $M_2 \bh{2T}$
+concentrates uniformly on the surface of the sphere centered at $M_2
+\theta_2$ and passing through the origin:
+\begin{equation*}
+  (M_2 \bh{2T} - M_2 \theta_2)'(M_2 \bh{2T} - M_2 \theta_2) =
+  \theta_2'M_2' M_2 \theta_2.
+\end{equation*}
+To see intuitively that it must pass through the origin, note that the
+two models will give identical forecasts when $\bh{2T} = 0$ since the
+regressors are orthogonal. (Identical forecasts obviously have the
+same MSE.)
+
+This region is a cylinder in the original space, $\Re^{K_2}$.  We can
+also represent the null $\E_T \oosB \leq 0$ by conditioning on $\E_T
+\oosB = -d$ for a fixed positive constant $c$. In that case, the
+density of $M_2 \bh{2T}$ concentrates on the sphere
+\begin{equation*}
+  (M_2 \bh{2T} - M_2 \theta_2)'(M_2 \bh{2T} - M_2 \theta_2) =
+  \theta_2'M_2' M_2 \theta_2 + d
+\end{equation*}
+which has the same center but larger radius.
+
+For the $F$-test we have, as before,
+\begin{equation*}
+  F = \tfrac{T}{s^2 (K_2 - K_1)} \bh{2T}' M_2' M_2 \bh{2T}.
+\end{equation*}
+We know that $\sqrt{T}(F - 1)$ is asymptotically normal since its
+numerator is Chi-squared with $K_2-K_1$ degrees of freedom and obeys a
+CLT.  The test accepts if
+\begin{equation}\label{eq:26}
+  \tfrac{T}{s^2 (K_2 - K_1)} \bh{2T}' M_2' M_2 \bh{2T}
+  \leq 1 + \delta / \sqrt{T},
+\end{equation}
+where $\delta$ is chosen to determine the size of the test. In other
+words, the test accepts if $M_2 \bh{2T}$ falls in the sphere centered
+at the origin with radius $s ((K_2 - K_1) / T)^{1/2} +
+O_p(1/\sqrt{T})$.
+
+\input{floats/circles}
+\begin{figure}
+  \centering
+  \begin{tabular}{cc}
+  \subfloat[]{\circlefigA{1}{2.5}{1.4}{4.5}\label{fig:circleA}} &
+  \subfloat[]{\circlefigB{1}{2.5}{1.4}{4.5}\label{fig:circleB}}
+  \end{tabular}
+  \caption{Graphs indicating the rejection region and region of equal
+    generalization error for the models discussed in Section
+    \ref{sec:insample}.  The smaller model has no estimated parameters
+    and the larger has two coefficients.  The shaded regions in
+    Figures (a) and (b) show the rejection region and the acceptance
+    region respectively of the full-sample test given $\E_T \oosB \leq
+    0$. Here $e_1 = (1,0)$ and $e_2 = (0,1)$ are the first and second
+    selection vectors, so the horizontal axes represent changes in the
+    first unique element of $\bh{2T}$ and the vertical axes represent
+    changes in the second unique element.}
+\label{fig:rreject}
+\end{figure}
+
+This is perhaps best illustrated with a picture.
+Figure~\ref{fig:rreject} plots these quantities when $K_2 - K_1 =
+2$. The circle centered at the origin plots the threshold for the
+$F$-test; when $M_2 \bh{iT}$ falls outside this circle, the $F$-test
+rejects. The circle centered at $M_2 \theta_2$ plots the set of points
+for which $\E_T \oosB = 0$. The shaded region in
+Figure~\ref{fig:rreject}~(a) plots the rejection region given $\E_T
+\oosB \leq 0$ and the shaded region in Figure~\ref{fig:rreject}~(b)
+plots the acceptance region given $\E_T \oosB \leq 0$.
+
+In the picture, the true coefficients $\theta_2$ satisfy
+\begin{equation*}
+\theta_2'M_2'M_2\theta_2 > \var(\e_t)^{1/2} ((K_2 - K_1) / T)^{1/2}
+\end{equation*}
+so the center of the conditional distribution of $\bh{2T}$ given $\E_T
+\oosB \leq 0$ is outside the acceptance region of the $F$-test. When
+this is the case, the conditional probability that $\bh{2T}$ falls in
+the rejection region is less than 1/2, since $M_2 \bh{2T}$ is
+uniformly distributed on the cylinder
+\begin{equation*}
+  (M_2 \bh{2T} - M_2 \theta_2)'(M_2 \bh{2T} - M_2 \theta_2) =
+  \theta_2'M_2' M_2 \theta_2 + d
+\end{equation*}
+for some positive $d$.
+
+The AIC behaves essentially the same way. For the BIC, the radius of
+the cylinder centered at the origin increases with $T$ and eventually
+encompasses the cylinder centered at $M_2 \theta_2$, so it never
+selects the alternative once $T$ is large enough.
+
 %%% Local Variables:

### 2017-05-03 4-montecarlo.tex
Split main paper.tex into several smaller files
This commit moves the content of the paper into several smaller
files that are \included; this allows us to use \includeonly
to minimize compilation time.

\section{Monte Carlo}
\label{sec:mc}

This section presents two simulations that investigate the accuracy of
our theory in small samples.
We do several Monte Carlo exercises. The first looks at whether our
theoretical results for the OOS average are accurate: whether or not
the OOS average is approximately normal, and whether it is centered on
$\E_R \oosA$, $\E_T \oosB$, or somewhere else entirely. The second
issue is whether or not the \oost\ test is \emph{useful} for
conducting inference about $\E_T \oosB$. Our theoretical results
suggest that it may not be, because we require $P^2/T \to 0$ for
inference about $\E_T \oosB$ to be valid. A highly related issue is
whether other statistics are useful for conducting inference about
$\E_T \oosB$---again, our theoretical results suggest that they are
not.

We use the same DGP for all of these simulations, and it is described
in the next subsection. Results are presented in the subsection after
that. Simulations were conducted in R \citep{Rde:10} using the
\emph{MASS} \citep{VeR:02}, \emph{Matrix} \citep{BM:13}, and
\emph{rlecuyer} \citep{SR:12} and graphs are produced using
\emph{Lattice} \citep{Sar:10}. In this paper, we present results for
the fixed window, but recursive window results are available in a
separate Appendix and are similar.

\subsection{Setup}
\label{sec:simulation-design}

The Monte Carlo experiment is intentionally very simple so that we can
isolate the influence of the models' complexity.  In particular, we do
not include some features that are common in forecasting
environments---serial dependence, heteroskedasticity, and complicated
DGPs. The DGP we use is given by the equation
\begin{equation}\label{eq:6}
  y_t = x_t'\theta + \e_t,\quad \e_t \sim N(0,1),
  \quad t=1,\dots,T.
\end{equation}
The first element of $x_t$ is 1 and the remaining $K_2-1$ elements are
independent Standard Normal.  The benchmark model is
\begin{equation}
  \label{eq:1}
  y_{1t} = \sum_{j=1}^{K_1} x_{jt}\theta_j + \e_t
\end{equation}
and the alternative model is the DGP \eqref{eq:6}.  We let
$(K_1,K_2)$ equal either $(2,3)$ or $(T/20,T/10)$ to study our theory
in its intended application as well as for more parsimonious models.
We let $T$ equal 100, 250, or 500.  We also vary $\theta$, and do
so giving the benchmark and the alternative model comparable weight in
predicting $y_t$.  Specifically, we set
\begin{equation*}
  \theta_j =
\begin{cases} \frac{c}{\sqrt{K_1}} & j = 1,\dots,K_1 \\
\frac{c}{\sqrt{K_2 - K_1}} & j = K_1 + 1,\dots,K_2 \end{cases}
\end{equation*}
with $c$ equal to zero or one.  When $c$ is one, we're more likely to
draw values of $X$ and $Y$ that make the estimated larger model more
accurate than the benchmark, and when $c$ is zero we're unlikely to
draw such values of $X$ and $Y$.  For all of the studies, $L(e) =
e^2$.

To study the accuracy of our theoretical approximations, we first
estimate the coverage probabilities of OOS confidence intervals for
$\E_R \oosA$ and $\E_T \oosB$. For each draw of $X$ and $Y$, we
construct the one-sided OOS interval defined in
Theorem~\ref{res:oostest}:
\begin{equation*}
  [ \oosA - 1.28 \hat{\sigma}, \infty) \quad\text{with}\quad
  \sh^2 = \frac1P \sum_{t=R+1}^T (D_t - \oosA)^{2}
\end{equation*}
for $P = 10,\dots,2T/3$; we then calculate the percentage of
simulations where these intervals contain $\E_R \oosA$ and the
percentage that contain $\E_T \oosB$.  Since the data are i.i.d., both
of these quantities are easy to calculate (see
Section~\ref{sec:example}). For these calculations, we draw 2000
samples for each combination of the design parameters.

Our second set of results studies whether these different OOS and
in-sample statistics are valid for testing the null hypothesis
\begin{equation*}
  H_0:\quad E_T \oosB \leq 0,
\end{equation*}
namely that the benchmark model is expected to be more accurate in the
future than the alternative. Informally, we are interested in whether
the conditional probability
\begin{equation*}
  \Pr[\text{test rejects} \mid E_T \oosB \leq 0] \leq \alpha
\end{equation*}
where $\alpha$ is the nominal size of the test. If this inequality
does not hold, the test statistic is rejecting the benchmark model too
often.

We look at four different statistics---the full-sample $F$-test, the
DMW $t$-test, the OOS $t$-test using McCracken's (2007) critical
values,\footnote{%
  These critical values are not published for $K_2-K_1>10$, so we do
  not report them for $K_2 = T/10$.} %
and Clark and West's (2006, 2007) Gaussian out-of-sample
statistic.\footnote{%
  Clark and West (2006, 2007) derive their statistic using the rolling
  window estimation scheme. Here we use the same statistic, but with a
  fixed window scheme. A supplemental appendix presents results for
  their statistic, using the recursive window.} %
For the $F$-test, we simply test whether the coefficients on the
larger model are nonzero.  For the out-of-sample tests, we conduct a
one-sided test of out-of-sample performance for every value of $P$ as
before. For each of these simulations, we discard draws from the DGP
that violate the null hypothesis $E_T \oosB \leq 0$ and then use the
remaining samples to calculate the conditional probability that each
test rejects. The simulations end when 2000 draws have been retained
for each choice of the design parameters.

\subsection{Results}

We discuss results for the confidence intervals first.
Figures~\ref{fig:interval-R} and~\ref{fig:interval-T} show the
coverage probability of these intervals as a function of $P$ for each
combination of $T$, $K_1$ and $K_2$, and $c$.  The nominal coverage is
90\% and is represented with a gray horizontal line. Each panel
displays the coverage for a different choice of design parameters.

Figure~\ref{fig:interval-R} gives the results for $\E_R \oosA$.  The
actual coverage is very close to the nominal coverage except when $P$
is very small.  The poor behavior for small $P$ is unsurprising, as it
simply means that the CLT is a poor approximation when the test sample
is small. The interval for $T = 100$, $K = T/10$, and $c = 0$ is the
worst, with actual coverage near 85\% for most values of $P/T$. But
the others are much closer to nominal coverage, even for the
parsimonious models ($K_1=1$ and $K_2= 3$) where one might expect
the theoretical results to break down.

Figure~\ref{fig:interval-T} gives the results for $\E_T \oosB$.  In
columns 2 and 4---the overfit models---the coverage is near nominal
coverage for moderately small values of $P$.  As $P$ increases to
$2T/3$, the coverage increases above nominal size; near 100\% for some
DGPs.  With the parsimonious model, the coverage is near nominal
coverage for all $P$ for the one-sided interval with $c=1$, but only
for moderately small $P$ when $c=0$.

The behavior for $K_2 = T/10$ is exactly what our theory predicts.
When $P^2/T$ is small, the coverage is close to nominal levels.  The
behavior as $P$ increases, combined with the results for $\E_R \oosA$,
indicate that typically $\E_T \oosB \geq E_R \oosA$.  Since
\begin{equation*}
  E_{T} \oosB = E_{R} \oosA + (E_{T} \oosB - E_{R} \oosA),
\end{equation*}
and the interval is approximately centered at $\E_R \oosA$, the
difference $\E_{T} \oosB - E_{R} \oosA$ adds a substantial positive
quantity when $P^2/T$ is not near zero, increasing the coverage of the
one-sided interval.

We present the size simulations next, in
Figures~\ref{fig:ftest}--\ref{fig:ttest-power}.  For the OOS tests
we plot each OOS test's conditional rejection probability,
\begin{equation*}
  \Pr[\text{test rejects} \mid E_T \oosB \leq 0],
\end{equation*}
for each combination of $T$, $K_1$, $K_2$, and $c$ as a function of
$P$.  The $F$-test does not depend on $P$, so we calculate and
tabulate it's conditional rejection probability as a single value for
each combination of design parameters.

Table~\ref{fig:ftest} summarizes the simulation results for the
$F$-test. For $c = 0$, the estimated conditional rejection probability
is almost exactly equal to the test's nominal size (10\%), which is
unsurprising.  For $c = 0$, the $F$-test is exact; moreover, the
larger model will almost always be less accurate than the smaller one,
so conditioning on $\E_T \oosB \leq 0$ is almost unrestrictive.  When
$c$ increases, though, the $F$-test overrejects badly---rejecting at
roughly 50\% when $c = 1$ for the parsimonious model and from 70\% to
100\% for the overfit model. This agrees with our
Section~\ref{sec:insample} results and matches results seen in
empirical practice: the $F$-test rejects the benchmark with very high
probability, even though it is, by construction, more accurate than
the alternative model.

Figure~\ref{fig:ttest-size} presents the size estimates for the DMW
\oost\ test.  Again, different panels display results for different
combinations of the design parameters.  Each graph plots the rejection
probability against $P/T$.  For $K/T=10$, the rejection probability
falls as $P/T$ increases, from near nominal size when $P/T$ is small
to zero when $P/T$ is near $2/3$.  Moreover, the rejection probability
falls faster when $T$ is large, as our theory predicts.  When $K=3$,
the rejection probability stays closer to nominal size, but falls with
$P/T$ for $c=0$, under-rejecting by about 5pp when $P/T = 2/3$, and
rises with $P/T$ for $c=1$, overrejecting by about 10pp when
$P/T=2/3$.  For small $P$, the rejection probability is near 10\% for
all simulations (the farthest is $K=T/10$, $c=0$, where the rejection
probability is about 5\%; the other simulations are much closer).

We observe the following patterns.  The
DMW test has close to nominal size when $P$ is small for every
combination of design parameters.  In most cases, the rejection
probability decreases as $P/T$ increases---the exception is for $K_2 =
3$ and $c=1$.  For the large-$K$ simulations, the rejection
probability drops to zero for most of the simulations as $P/T$
increases.  The rejection probability increases with $c$, but the
rejection probability still is near nominal probability for small $P$
with $c=1$.

Clark and West's (2006, 2007) statistic, presented in
Figure~\ref{fig:clarkwest}, behaves quite differently.  For $c=0$ the
test is correctly sized for both the overfit and parsimonious studies,
as we saw for the $F$-test.  When $c=1$, the rejection probability
increases rapidly with $P/T$.  For $K_2=3$, the rejection probability
is near 10\% when $P$ is small but about 40\% when $P/T = 2/3$.  For
$K=T/10$, the rejection probability is even higher and increases with
$T$ as well, from a maximum over 50\% when $T=100$ to a maximum of
nearly 100\% when $T=1000$.

Results using \citepos{Mcc:07} critical values are presented in
Figure~\ref{fig:mccracken} and are similar to those using Clark and
West's test.  For $c=0$ the rejection probability is nearly the test's
nominal size.  For $c=1$, the rejection probability increases with
$P/T$, from close to the nominal size when $P/T$ is small to over 25\%
when $P/T = 2/3$.  Note that all of the simulations use the
parsimonious model.  McCracken's statistic overrejects here by
slightly less than Clark and West's, but still by a substantial
amount. Note that we are unable to plot results for McCracken's
statistic when $K/T = 10$, which is where the breakdown in Clark and
West's test is most pronounced.

Since the DMW test tends to have low rejection probability, the test's
power is a concern.  Figure~\ref{fig:ttest-power} power results for
the DMW test, simulating from \eqref{eq:1} with $c = 1$ or 2 subject
to the constraint that $\E_T \oosB > 0$.\footnote{%
  Draws of $X$ and $Y$ with $\E_T \oosB > 0$ are very rare when $c=0$,
  so we do not present results for that value of $c$.} %
Since the other test statistics greatly overreject, we do not present
their power.  For $c=1$, the power is never greater than nominal size
and decreases to zero as $P/T$ increases for the overfit model.  For
$c=2$ the power is better, increasing with $P/T$ at first stretch and
then decreasing as $P/T$ grows beyond approximately 1/4 for the
overfit model.  Larger values of $T$ give a higher peak and greater
power overall, but the power still falls to nearly zero if $P/T$ is
too large (approximately 2/3 in our simulations).  The power with the
parsimonious model is typically quite low but greater than nominal
size for $c = 2$.

Both sets of simulations support our theoretical results.  The first
simulation confirms that the DMW OOS $t$-test is centered at $\E_R
\oosA$ for all choices of $P$ and $R$ and is centered on $\E_T \oosB$
only when $P$ is small.  The second simulation confirms that the DMW
test has correct size for the null hypothesis that $\E_T \oosB \leq 0$
when $P$ is small and that tests designed to test whether the
benchmark is true, like the $F$-test and Clark and West's (2006, 2007)
and McCracken's (2007) OOS tests can reject by much more than their
nominal size when testing the null $\E_T \oosB \leq 0$.  Moreover,
these simulations demonstrate that the restriction that $P$ be small
is binding in practice, as the DMW test under-rejects and has very low
power when $P$ is too large.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "paper"
%%% TeX-command-extra-options: "-shell-escape"
%%% End:

### 2017-05-03 5-goyalwelch.tex
Split main paper.tex into several smaller files
This commit moves the content of the paper into several smaller
files that are \included; this allows us to use \includeonly
to minimize compilation time.

\section{Empirical analysis of equity premium predictability}
\label{sec:empirics}

This section presents a study of equity premium predictability based
on \citet{GoW:08}. Goyal and Welch conduct an out of sample analysis
of 18 different variables thought, based on previous research, to
predict the equity premium (calculated as the difference between the
return on the S\&P 500 index and the T-bill rate).\footnote{%
  \citet{GoW:08} builds on previous research by \citet{BoH:99} and
  \cite{GoW:03}.} %
Their analysis has two notable features: Goyal and Welch compare different
predictors across the same time periods and frequency as much as
possible, making the accuracy of these predictors directly comparable;
many of the papers that originally proposed these predictors used
different time periods, methods, or observational frequencies so their
results were not directly comparable. And Goyal and Welch compare
these predictors out-of-sample; many of the original studies found
in-sample evidence of equity premium predictability but did not look
at out-of-sample evidence.

Goyal and Welch consider many different models; most of them are very
simple---regression onto a constant and a single stochastic
predictor---but some are more complicated. They find that essentially
none of the models outperform a simple benchmark, the prevailing mean
of the equity premium, and conclude that these variables do not
predict the equity premium. A large literature has subsequently sought
to explain or rebut these results, including several responses to
Goyal and Welch's original working paper published in the same special
issue of \textit{The Review of Financial Studies} as
\citet{GoW:08}.\footnote{%
  Those papers are \citet{CaT:08}, \citet{Coc:08}, \citet{BRW:08}, and
  \citet{LeN:08}.} %

\citet{GoW:08}, as well as \citet{BoH:99}, \citet{LeN:08}, and many
other authors, propose that instability could explain the OOS failure
of these models. However, we have shown in this paper that overfit can
also explain this pattern, significant in-sample results that do not
hold up out of sample. In this section, we explore the extent to which
overfit is a potential concern in this data set and estimate the
expected forecasting performance of the largest model they consider, a
model with 13 regressors, using 81 observations (annual data from 1928
to 2009). The predictors are listed in Table~\ref{tab:equity}; please
see Goyal and Welch's original paper for detailed information about
these variables.\footnote{%
  Table~\ref{tab:equity} only lists the variables used in
  \citepos{GoW:08} ``kitchen sink'' model.  Some of the variables that
  they use are excluded from this model either because the series are
  too short or because the variables are linear combinations of other
  variables.} %

\citet{GoW:08} focus primarily on univariate regression models of the
form
\[
r_{t+1} = \beta_0 + \beta_1 x_{it} + \e_{t+1}
\]
using OLS with a recursive window, where $r_{t+1}$ is the equity
premium and $x_{it}$ is one of the predictors listed in
Table~\ref{tab:equity}.
This focus is consistent with much of the rest of the literature. But
it is not clear that this approach---using a large number of
restricted models---is any more reliable than using a single, large
model. Very few papers in the equity-premium predictability literature
explicitly account for the multiplicity of model comparisons\footnote{%
  \citet{RaW:06}, \citet{RaZ:12}, and \citet{Cal:15} are
  exceptions.} %
and most widely-used statistics for multiple comparisons are
derived under the assumption that there is a finite number of
hypotheses or models (as is the case in \citealp{STW:99c},
\citealp{Whi:00}, \citealp{Han:05}, and \citealp{LeR:05}), so there is
little theoretical evidence that they are any more reliable than a
regression model that encompasses all of the smaller models. Moreover,
since \citet{GoW:08} (along with most of the rest of the literature)
want to interpret these univariate regressions as meaningful
statements about the true relationships between the equity premium and
the regressors, omitted variable bias is a serious potential issue.

For example, Table~\ref{tab:gwinsample} presents two full-sample
coefficient estimates for each of the 12 predictors we
consider.\footnote{%
  For all of our full sample results, we studentize the
  regressors to make it easier to compare coefficient estimates and we
  express the equity premium in basis points.} %
The first column is the estimator of the coefficient on the
variable in the full regression,
\begin{equation*}
  r_{t+1} = \beta_0 + \sum_{i=1}^{12} \beta_{i} x_{it} + \e_{t+1},
\end{equation*}
and the third column is the $p$-value associated with a two-sided
$t$-test that the coefficient is zero in population. The second column
is the estimator of the coefficient from the univariate regression
\begin{equation*}
  r_{t+1} = \alpha_i + \gamma_{i} x_{it} + \e_{t+1},
\end{equation*}
and the fourth column is the $p$-value associated with its
$t$-test.\footnote{%
  All of the standard errors were calculated using a Newey-West kernel
  with two lags.} %
Some of the coefficient estimates agree, but some do not. The
coefficient estimate for the \emph{default yield spread}, for example,
is substantially and significantly negative in the full model ($-7.79$
with $p$-value $0.042$), but is near zero in the univariate regression
($0.79$ with $p$-value $0.720$). This pair of results implies that the
the default yield spread contains information about the equity premium
but is also correlated with other poor predictors, and that this
additional correlation adds noise to the univariate regression
and masks the true relationship. Similarly, \emph{net equity expansion}
is significant at 10\% in the univariate regression but not in the
full model ($p$-values of $0.060$ and $0.626$ respectively), which is
likely attributable to omitted variable bias. So there is merit to
studying a large model that includes all of the variables.

Results for the full sample estimates of these models are in
Table~\ref{tab:gwinsample}.\footnote{%
  Calculations in this section are done in R \citep{Rde:10} using the
  \emph{lmtest} \citep{ZeH:02} and \emph{sandwich} \citep{Zei:04}
  packages.}\footnote{%
  We compare the test statistic to critical values from the
  $F$-distribution, which have been shown to be more reliable than
  Chi-squared critical values when there are many regressors
  \citep{Ana:12,Cal:11c}.} %
The last rows of the table list measures of the full-model fit.  The
$p$-value for the test of full model fit is very small (less than
0.01), indicating that some of the coefficients are nonzero in
population and at least one of these predictors is correlated with the
equity premium.\footnote{%
  We have done additional analysis to try to identify which predictors
  were correlated with the equity premium, but none of the individual
  regressors were significant after correcting for multiplicity. The
  Bonferroni correction, for example, suggests that an individual
  $p$-value would need to be less than $0.10/12 \approx 0.0083$ for
  its corresponding coefficient to be significant at the 10\% level,
  but the smallest $p$-value is $0.035$. One can improve on the
  Bonferroni correction, of course, but a comprehensive analysis is
  beyond the scope of this paper.} %
As we argue throughout the paper, this result does not imply that the
model will forecast well.

To determine whether the full model can forecast well, we use the DMW
\oost\ test to compare it to a sample mean benchmark,
\begin{equation*}
r_{t+1} = \mu + \e_{1,t+1}.
\end{equation*}
Both models are estimated by OLS using the fixed-window scheme. We
also present results for a restricted model proposed by
\citet{CaT:08} that imposes that $\hat r_{t+1}$ be non-negative for
each forecast.
To study the effect of the training sample size on the DMW statistic, we
calculate the one-sided confidence interval for $\E_T \oosB$ given
by \eqref{interval-greater} corresponding to the null and alternative
hypotheses
\[ H_0: \quad E_T \oosB \leq 0 \qquad
H_A: \quad E_T \oosB > 0
\]
using the fixed-window scheme for each value of $R$ between 20 and
$T-10$. The standard deviation is estimated using a Newey-West
estimator with $\lfloor P^{1/4}\rfloor$ lags.  For small values of
$R$, the OOS average is expected to underestimate the performance of
the larger model relative to the smaller, but this may not hold in
this particular dataset. For the OOS results, we express the equity
premium in percentage points.

Figure~\ref{fig:empirics1} plots the OLS results and
Figure~\ref{fig:empirics2} imposes \citepos{CaT:08} restriction. The
solid line in each figure shows the OOS average, $\oosA$, and the
shaded region indicates the 95\% one-sided confidence interval implied
by the DMW test.  Negative numbers indicate that the full model has
higher out-of-sample loss.  We can see that the same patterns hold for
both models: the performance difference decreases as $R$ grows, but
the full model is never more accurate.  We also see that the
performance difference decreases suddenly over the period $R=29$ to
$R=34$ (corresponding to the years 1956--1961).
Figure~\ref{fig:empirics3} plots the accuracy of the individual
forecasts (only for the linear models) and shows that this change is
the result of a sudden improvement in the full model.  This change may
indicate instability in the underlying relationship, as proposed by
\citet{GoW:08}.

In summary, we fail to reject the null that the benchmark prevailing
mean model is more accurate than the full model including all of
\citepos{GoW:08} predictors.  This result is consistent with Goyal and
Welch's original analysis.  Unlike Goyal and Welch, we attribute this
result, at least in part, to parameter uncertainty---the full sample
results indicate that there is a true predictive relationship between
some of these variables and the equity premium and the larger model
could predict better than the benchmark with enough data.\footnote{%
  \citet{BWB:10} make a similar point about exchange rate models, but
  see also \citet{Chi:10} and \citet{Gia:10}.} %
These also indicate that combination or shrinkage estimators of the
full model have the potential to significantly improve on the
benchmark.\footnote{%
  See \citet{RaZ:12} for a recent review of this literature.} %

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "paper"
%%% TeX-command-extra-options: "-shell-escape"
%%% End:

### 2017-05-03 6-conclusion.tex
Split main paper.tex into several smaller files
This commit moves the content of the paper into several smaller
files that are \included; this allows us to use \includeonly
to minimize compilation time.

\section{Conclusion}
\label{sec:conclusion}

This paper gives a theoretical motivation for using OOS comparisons:
the DMW OOS test allows a forecaster to conduct inference about
the expected future accuracy of his or her models when one or both is
overfit.  We show analytically and through Monte Carlo that standard
full-sample test statistics can not test hypotheses about this
performance.

Our paper also shows that popular test and training sample sizes may
give misleading results if researchers are concerned about overfit.
We show that $P^2/T$ must converge to zero for the DMW test to give
valid inference about the expected forecast accuracy, otherwise the
test measures the accuracy of the estimates constructed using only the
training sample.  In empirical research, $P$ is typically much larger
than this.  Our simulations indicate that using large values of $P$
with the DMW test gives undersized tests with low power, so this
practice may favor simple benchmark models too much.  Existing
corrections, proposed by \citet{ClM:01,ClM:05}, \citet{Mcc:07} and
\citet{ClW:06,ClW:07}, seem to correct too much, though, and reject
too often when the benchmark model is more accurate.

More work remains.  The requirement that $P^2/T$ converge to zero is
limiting, as it implies that in typical macroeconomic datasets, only a
handful of observations should be used for testing.  This requirement
can be relaxed only slightly; $P = O(T^{1/2})$ is required for the
OOS test to have nontrivial power in general, but there are loss
functions and DGPs for which some relaxation is possible.  This
constraint could be mitigated by extending our results to
cross-validation or other resampling strategies, or by constructing
full-sample statistics that allow inference about $\E_T \bar{D}_T$.
It would also be useful to extend our results to other forecasting
models and to explore how stationarity could be relaxed, but such
extensions are less important than improving the available statistics.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "paper"
%%% TeX-command-extra-options: "-shell-escape"
%%% End:

### 2017-05-03 A1-support.tex
Split main paper.tex into several smaller files
This commit moves the content of the paper into several smaller
files that are \included; this allows us to use \includeonly
to minimize compilation time.

\section*{Appendix: mathematical details}
\markright{Appendix: mathematical details}
\setcounter{section}{1}
% Change lemma style to prepend 'A'
\setcounter{lem}{0}
\renewcommand{\thelem}{A\arabic{lem}}

\subsection{Supporting results}
The results in this paper rely heavily on a coupling argument for
absolutely regular sequences, Berbee's Lemma \citep{Ber:79}.  Many of
the results of this paper (Lemma \ref{res-mixingale} and
Theorem~\ref{res-oost}) use modifications of existing results
for NED functions of mixing processes by \citet{Jon:97} and
\citet{JoD:00}; this coupling argument is used to explicitly derive
inequalities that arise naturally for NED processes.  Lemma
\ref{lem-basic-coupling} establishes these inequalities, which are
based on a proposition of \citet{MeP:02}.

We present \citeauthor{MeP:02}'s
(\citeyear{MeP:02}) statement of Berbee's Lemma for
the reader's reference.  In the following Lemma, $\beta(X,Y)$ is the
coefficient of absolute regularity:
\begin{equation}
\beta(X,Y) = \sup_{A \in \sigma(Y)} \E \lvert \Pr(A \mid \sigma(X))
  - \Pr(A) \rvert.
\end{equation}

\begin{lem}\label{lem-berbee}\quad

\begin{quotation}\noindent
  Let $X$ and $Y$ be random variables defined on a probability space
  $(\Omega, \mathcal{T}, \Pr)$ with values in a Polish space
  $S$.  Let $\sigma(X)$ be a $\sigma$-algebra generated by $X$ and let
  $U$ be a random variable uniformly distributed on $[0,1]$
  independent of $(X,Y)$.  Then there exists a random variable $Y^{*}$
  measurable with respect to $\sigma(X) \vee \sigma(Y) \vee
  \sigma(U)$, independent of $X$ and distributed as $Y$, and such that
  $\Pr(Y \neq Y^{*}) = \beta(X,Y)$.

  \noindent\citep{MeP:02}
\end{quotation}
\end{lem}

The advantage of this result over coupling arguments that use other
forms of weak dependence is that the difference between the original
variable, $Y$, and the new variable, $Y^{*}$, does not depend on their
dimension.  Similar results for strong mixing sequences depend on the
dimension of $Y$, which makes them unsuitable for this paper.

\begin{lem}\label{lem-extend-mp}
  Suppose that $X$ and $X^*$ are $L_p$-bounded random variables, with
  $p > 2$, that satisfy ${\Pr[X \neq X^*] = c}$.  Then
  \begin{equation}
    \lVert X - X^* \rVert_2 \leq 2^{1/p} (\lVert X \rVert_p + \lVert
    X^* \rVert_p) c^{(p-2)/2p}
  \end{equation}
\end{lem}

The proof is virtually identical to the proof of Proposition 2.3 in
\citet{MeP:02} and is omitted.

\begin{lem}\label{lem-basic-coupling}
  Suppose Assumptions \ref{asmp-1}--\ref{asmp-3} hold.  Then, for any
  T, $s$, $t$, and $u$ with $s < t \leq u$, there exist random
  variables $D_t^*,\dots,D_u^*$ such that
  \begin{equation}\label{eq:coupling1}
    P[(D_{t}^*,\dots,D_u^*) \neq (D_{t},\dots,D_u)] \leq \beta_{t-s}
  \end{equation}
  and
  \begin{equation}\label{eq:coupling2}
    \E(\phi(D_{t}^*,\dots, D_u^*) \mid \mathcal{F}_s ) =
    \int
    \phi(D_{t},\dots,D_u) f(\mathbf{x}, \mathbf{y})\ d\mathbf{x}\ d\mathbf{y}
  \end{equation}
  almost surely for all measurable functions $\phi$ such that the
  expectations are finite, where
  \[ \mathbf{x} = (x_{t}', \dots, x_{u}')', \qquad
  \mathbf{y} = (y_{t+\h},\dots,y_{u+\h})',\] and $f$ is the
  joint density of $(\mathbf{x}, \mathbf{y})$.  Moreover,
 \begin{equation}\label{eq:coupling3}
   \| D_v^* - D_v \|_2 \leq 2^{1+1/\rho} B_L
   \beta_{t-s}^{\rhoExp}, \qquad v = t,\dots,u.
 \end{equation}
\end{lem}

\begin{proof}
  The proof follows as a consequence of Lemmas \ref{lem-berbee} and
  \ref{lem-extend-mp}.  Let $l = u-t$.  For any fixed values of $l$
  and $T$, the sequence of vectors
  \[ V_{t} = (y_{t+\h}, x_{t}', \dots, y_{t+l+\h}, x_{t+l}') \] is
  absolutely regular of size $\rho/(\rho-2)$.  Berbee's Lemma implies
  that there is a random vector $V^*$ that is independent of
  $\mathcal{F}_s$, equal to $V_{t}$ in distribution, and satisfies
  \[\Pr[V^* \neq V_{t}] = \beta_{t-s}.\]

  Now define
  \begin{equation*}
    D_v^* =
    \begin{cases}
      L(y_{v+\h}^* - x_{1v}^{*\prime} \hat{\theta}_{1R}) - L(y_{v+\h}^* -
      x_{2v}^{*\prime} \hat{\theta}_{2R}) & v \leq T \\
      L(y_{v+\h}^* - x_{1v}^{*\prime} \hat{\theta}_{1T}) - L(y_{v+\h}^* -
      x_{2v}^{*\prime} \hat{\theta}_{2T}) & v > T
    \end{cases}
  \end{equation*}
  with $y_{v+\h}^*$ and $x_{iv}^*$ denoting the elements of $V^*$
  corresponding to $y_{v+\h}$ and $x_{iv}$ in $V_{t}$.  Equations
  (\ref{eq:coupling1}) and (\ref{eq:coupling2}) are satisfied by
  construction, and (\ref{eq:coupling3}) follows from Lemma
  \ref{lem-extend-mp}.
\end{proof}

\begin{lem}\label{lem:a2}
  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-3} hold.  Let $b_T$ be a
  sequence of integers such that $b_T \to \infty$ and $b_T = o(P)$ and define
  \begin{equation}
    Z_i = \ZDef.
  \end{equation}
  Then
  \begin{equation}
    \label{eq:10}
    \sum_{i=1}^{\lfloor P/b_T \rfloor} (\E_R Z_i^2 - \E_{R+(i-1) b_T}
    Z_i^2) \to^p 0 \quad\text{ as } P \to \infty.
  \end{equation}

  If the assumptions of Theorem~\ref{res-oost} also hold, $b_T$ is
  restricted further so that $b_T \equiv \lfloor \gamma/\delta
  \rfloor$ for some positive scalar $\delta$, and we define
  \begin{equation}\label{eq:13}
    \kernelB{x} \equiv \kernelBDefn{x},
  \end{equation}
  then
  \begin{equation}
    \label{eq:12}
    \vtSum (Z_{1t} Z_{2t} - \E_R Z_{1t} Z_{2t}) \to^p 0.
  \end{equation}
  where
  \begin{gather}
    Z_{1t} = \varianceTermIIIa,%
    \intertext{and}%
    Z_{2t} = \varianceTermIVb.
  \end{gather}
\end{lem}
\begin{proof}
\newcommand{\UFiltration}[1]{\ensuremath{\mathcal{F}_{(#1)b_{T}+R-P}}}%
The first result,~\eqref{eq:10}, follows a similar argument to Lemma~5
of \citet{Jon:97} and~\eqref{eq:12} to Lemma~A.4 of \citet{JoD:00}.
Since these arguments are similar and our modification is the same for
both, we'll just present the more complicated version,~\eqref{eq:12}.

Note that $\{Z_{1t}^2 P\gamma_T/b_T\}$ and $\{Z_{2t}^2 P\gamma_T/b_T\}$
are uniformly integrable.  As in~\citet[Lemma A.4]{JoD:00}, we can
assume that there is a constant $C$ such that $Z_{1t}$ and $Z_{2t}$
are bounded in absolute value by $C\sqrt{b_T/P\gamma_T}$; uniform
integrability ensures that the difference between the unbounded random
variables and these truncated versions is negligible for large enough
values of $C$.

Let $r = \lfloor 3P/2b_T \rfloor$ and rewrite the summation as
\begin{align*}
  \vtSum \vtIIIsummand &= \vtSumr \vtSuma \vtIIIsummand \\
  &\quad+ \vtSumr \vtSumb \vtIIIsummand \\
  &\quad+ \sum_{t=r b_T - P + R + 1}^{2P+R} \vtIIIsummand \\
  &\equiv \vtSumr (U_i - \E_R U_i) + \vtSumr (U_i' - \E_R U_i') + o_{L_1}(1).
\end{align*}
The proof then holds if we can show that both $U_i$ and $U_i'$ obey
LLNs.  We'll do so by proving that $\{U_i -\E_R U_i,
\UFiltration{2i-1}\}$ and $\{U_i' - \E_R U_i', \UFiltration{2i}\}$ are
$L_2$-mixingales of size $-1/2$ and using the bound $\E(\vtSumr (U_i -
\E_R U_i))^2 = O(\vtSumr c_i^2)$ where the $c_i$ are the mixingale
magnitude indices \citep{Mcl:75}.

For non-negative $m$, we have
\begin{equation*}
U_i - \E_R U_i \in \UFiltration{2i+2m-1},
\end{equation*}
establishing half of the mixingale result trivially.  Now fix $i$ and $m >
0$ and use Lemma \ref{lem-basic-coupling} to define $D_{ts}^*$
for each $t =(2i-2)b_T-P+R+1,\dots,(2i-1)b_T-P+R$ and $s =
\max(t-b_T,R+1),\dots,\min(t+b_T,T-\h)$ such that
\begin{equation*}
 \E_R D_{ts}^* = \E_{(2i-2m-1)b_T+R-P} D_{ts}^* \quad a.s.
\end{equation*}
and
\begin{equation*}
  \lVert D_{ts}^* - D_s \rVert_2 \leq \couplingBound{s - (2i-2m-1)b_T+P}.
\end{equation*}
Also define
\begin{equation*}
  Z_{1t}^* = (P\gamma_T)^{-1/2} \sum_{l=\vttLower}^{\vttUpper}
  (D_{t,t+l}^* - \E_R D_{t,t+l}^*)\ W(l/\gamma_T), \\
\end{equation*}
and
\begin{equation*}
Z_{2t}^* = (P\gamma_T)^{-1/2} \sum_{j=\vttLower}^{\vttUpper}
    (D_{t,t+l}^* - \E_R D_{t,t+l}^*)\ \kernelB{j/\gamma_T}.
\end{equation*}

Now, we have the inequalities
\begin{align*}
  \lVert \E( U_i - \E_R U_i & \mid \UFiltration{2i-2m-1}) \rVert_2
  \\ &\leq
  \vtSuma \lVert \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) - \E_R
  Z_{1t}Z_{2t} \rVert_2 \\
  &= \vtSuma \lVert \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
  &\quad - \E(Z_{1t}^* Z_{2t}^* \mid \UFiltration{2i-2m-1}) \\
  &\quad + \E(Z_{1t}^* Z_{2t}^* \mid \UFiltration{2i-2m-1})
  - \E_R Z_{1t}Z_{2t} \rVert_2 \\
%  \leq \vtSuma (\wall \lVert \wall \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
%  - \E(Z_{1t}^*Z_{2t}^* \mid \UFiltration{2i-2m-1}) \rVert_2\return
%  \\ + \lVert \E_R Z_{1t}Z_{2t} - \E_R Z_{1t}^*Z_{2t}^*
%  \rVert_2)\return \\
  &\leq 2 \vtSuma \lVert Z_{1t} Z_{2t} - Z_{1t}^* Z_{2t}^*
  \rVert_2 \\
  &\leq 2 \vtSuma (\lVert Z_{1t} - Z_{1t}^* \rVert_2 \lVert
  Z_{2t} \rVert_{\infty}
  + \lVert Z_{2t} - Z_{2t}^* \rVert_2 \lVert Z_{1t}^* \rVert_{\infty}) \\
  &\leq \frac{2 C b_T^{1/2}}{(P\gamma_T)^{1/2}} \vtSuma (\lVert Z_{1t} - Z_{1t}^* \rVert_2
  + \lVert Z_{2t} - Z_{2t}^* \rVert_2).
\end{align*}

And we can finish the proof with the following inequalities:
\begin{align*}
  \frac{2 C b_T^{1/2}}{(P \gamma_T)^{1/2}} &\vtSuma \lVert Z_{1t} - Z_{1t}^* \rVert_2 \\& \leq
  \frac{4C b_T^{1/2}}{P\gamma_T} \vtSuma \sum_{l=\vttLower}^{\vttUpper} \lVert
  D_{t+l} - D_{t,t+l}^* \rVert_2 W(l/\gamma_T) \\&
  \leq O\Bigg(\frac{b_T^{1/2}}{P\gamma_T}\Bigg) \vtSuma
  \sum_{l=\vttLower}^{\vttUpper} \couplingBeta{t+l-(2i-2m-1)b_T+P}\\&
  = O\Bigg(\frac{b_T^{1/2}}{P\gamma_T}\Bigg) O(b_T^{3/2-u}\, m^{-1/2-u})
\end{align*}
for some positive $u$.  The same argument holds for $Z_{2t}$.
As a result,
\[
E\Big(\vtSumr (U_i - \E_R U_i)\Big)^2 = o\Big(\vtSumr b_T^2/P\gamma_T\Big) =
 o(b_T/\gamma_T) \to 0,
\]
as required.
\end{proof}

\begin{lem}\label{lem:a6}
  Suppose the conditions of Theorem~\ref{res-oost} hold.
  Then
  \begin{equation}
    \sh^2 - P^{-1} \sum_{s,t=R+1}^{T-h} (D_s - \E_R
    D_s) (D_t - \E_R D_t) W((t-s)/\gamma) \to^{L_1} 0.
  \end{equation}
\end{lem}

\begin{proof}
   It follows from simple algebra that
\begin{multline*}
  \Big| \sh^2 -  P^{-1} \sum_{s,t=R+1}^{T-h} (D_s - \E_R
    D_s) (D_t - \E_R D_t) W((t-s)/\gamma) \Big| \leq\\
  \varianceDiffA \\ + P^{-1} \oosSum{s,t}{1} \lvert (D_s -
  \oosA)(\E_R D_t - \oosA) \rvert \vWeight + o_p(1).
\end{multline*}
We'll prove that these two sums are $o_p(1)$; uniform integrability
then implies convergence in $L_1$.  The arguments for each are almost
identical, so we'll only present the first.

Applying the Cauchy-Schwarz inequality twice and simplifying gives the
upper bound
\begin{multline*}
\varianceDiffA \\ \leq O(1) \Big[\varianceDiffAii\Big]^{1/2} \Big[\varianceDiffAi\Big]^{1/2}.
\end{multline*}
Now,
$P^{-1} \oosSum{s}{1}(D_s - \E_R D_s)^2 = O_p(1)$, and it suffices to prove
that \[\varianceDiffAi = o_p(1).\]  Observe that
\begin{align*}
  \varianceDiffAi & = O_p\Big(P^{-1} \oosSum{s}{1}(\E_{R}D_s -
  \E_R\oosA)^2\Big) + O_p(\oosA - \E_R\oosA)^{2} \\
  &= O_p\Big(P^{-1} \oosSum{s}{1} (\E_RD_s)^2 - (\E_R\oosA)^2\Big) +
  o_p(1),
\end{align*}
with the second term $o_p(1)$ by Lemma \ref{res-mixingale} and
\citepos{Dav:93} mixingale LLN.

Now define $D_s^*$, $s = R+1,\dots,T-\h$, as in Lemma
\ref{lem-basic-coupling} so that $\E_{s-1} D_s^* = \E_R D_s^*$ almost
surely.  Note that we also have the equality $\E_R D_s^* = \E_R
D_{R+1}^*$ almost surely for all $s\geq R+1$, and so
\[
P^{-1} \oosSum{s}{1} (\E_R D_s^*)^2 = \Big(P^{-1} \oosSum{s}{1} \E_R
D_s^*\Big)^2 \quad \text{a.s.}
\]
Consequently,
\begin{align*}
P^{-1} \oosSum{s}{1}& (\E_R D_s)^2 - (\E_R\oosA)^2 \\
&= P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R D_s^*)^2]
 + \Big(P^{-1} \oosSum{s}{1} \E_R D_s^*\Big)^2 - (\E_R\oosA)^2 \quad \text{a.s}.\\
&= O_p\Big(P^{-1} \oosSum{s}{1} [(\E_R D_s)^2 - (\E_R D_s^*)^2]\Big)
 + O_p\Big(P^{-1} \oosSum{s}{1} \E_R (D_s - D_s^*)\Big).
\end{align*}
Finally,
\begin{align*}
\Big\lVert P^{-1} \oosSum{s}{1} [(\E_RD_s)^2 - (\E_R D_s^*)^2] \Big\rVert_1
&\leq P^{-1} \oosSum{s}{1} \lVert \E_R (D_s - D_s^*) \rVert_2 \lVert
\E_R (D_s + D_s^*) \rVert_2
\\ &\leq (4 B_L/P) \oosSum{s}{1} \lVert \E_R (D_s - D_s^*) \rVert_2,
\end{align*}
and this last term vanishes as in the proof of Lemma~\ref{lem:a2},
completing the proof.
\end{proof}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "paper"
%%% TeX-command-extra-options: "-shell-escape"
%%% End:

### 2017-05-03 A2-lemma.tex
Split main paper.tex into several smaller files
This commit moves the content of the paper into several smaller
files that are \included; this allows us to use \includeonly
to minimize compilation time.

\subsection{Proof of Lemma \ref{res-mixingale}}
We will start by proving that $\{D_t - \E_R D_t, \Fs_t\}$ is an
$L_2$-mixingale of size $-1/2$; $D_t$ is $\Fs_t$-measurable and so it
suffices to prove that
\begin{equation}\label{eq:24}
  \| \E_{t-l} D_t  - \E_R D_t \|_2 \leq 2^{2 + 1/\rho} B_L \, \couplingBeta{l}
\end{equation}
for $l = 1,\dots,t-R$, since $\couplingBeta{l} = O(l^{-1/2 - \delta})$
for some $\delta > 0$ by assumption. Fix $R$, $t$ and $l$ and use
Lemma \ref{lem-basic-coupling} to define $D_t^*$ so that
\[
\E_R D_t^* = \E_{t-l} D_t^* \quad a.s.
\]
and
\[
\lVert D_t - D_t^* \rVert_2 \leq \couplingBound{l}.
\]
Then
\begin{align*}
\lVert \E_{t-l} D_t - \E_R D_t \rVert_2 & \leq
\lVert \E_{t-l} D_t - \E_{t-l} D_t^* \rVert_2  + \lVert \E_{t-l} D_t^* - \E_R D_t \rVert_2 \\
&\leq 2 \lVert D_t - D_t^* \rVert_2 \\
&\leq 2^{2 + 1/\rho}\ B_L\ \couplingBeta{l}.\tag*{\qed}
\end{align*}

\noindent Asymptotic normality follows from~\eqref{eq:24} using a
modification of \citepos{Jon:97} CLTs for mixingale and NED arrays.
Define
\begin{equation*}
  Z_i = \ZDef
\end{equation*}
where $b_T$ is a sequence that satisfies $b_T\leq P$,
$b_T\to\infty$, and $b_T/P\to 0$.  The same arguments used in
\citepos{Jon:97} Theorem 1 show that
\begin{equation*}
   \SumOuterBlock{i} Z_i = P^{-1/2} \oosSum{s}{1} (D_t - \E_R D_t) + o_p(1).
\end{equation*}
and
\begin{equation*}
  \SumOuterBlock{i} Z_i = \SumOuterBlock{i} (Z_i - E_{R + (i-1)b_T}
  Z_i) + o_p(1).
\end{equation*}
Note that $\{Z_i - E_{R + (i-1)b_T} Z_i,\mathcal{F}_{R + i b_T}\}_i$ is an
MDS by construction, so \citepos{HaH:80} Theorem 3.2 and Corollary
3.1 ensure that $\sigma^{-1} \SumOuterBlock{i} Z_i \to^d N(0,1) $ as
long as
\begin{equation*}
  \sigma^2 - \SumOuterBlock{i} \E_R Z_i^2 \to^p 0,
\end{equation*}
and
\begin{equation*}
  \SumOuterBlock{i} \E_R Z_i^2 - \SumOuterBlock{i} \ZSqCE \to^p 0.\footnote{%
    Note that $\sigma^2 \in \mathcal{F}_t$ for
    all $t \geq R$, so Hall and Heyde's condition (3.21) is
    unnecessary---see the remarks after their result.} %
\end{equation*}
The first equation holds as in \citet{Jon:97} (see the proof
of his Theorem 2); the second is ensured by
Lemma~\ref{lem:a2}. \qed

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "paper"
%%% TeX-command-extra-options: "-shell-escape"
%%% End:

### 2017-05-03 A4-theorem.tex
Split main paper.tex into several smaller files
This commit moves the content of the paper into several smaller
files that are \included; this allows us to use \includeonly
to minimize compilation time.

\subsection{Proof of Theorem \ref{res-oost}}
We can rewrite the centered \oost\ statistic as
\[
\sqrt{P}(\oosA - \E_T \oosB)/\sh
= \frac{\sigma}{\sh}\, \Big( \sqrt{P}(\oosA - \E_R \oosA)/\sigma
+ \sqrt{P}(\E_R \oosA - \E_T \oosB)/\sigma \Big)
\]
so Lemma \ref{res-mixingale} and \ref{res-convergence} ensure that
this term is asymptotically standard normal as long as $\sigma/\sh
\to^p 1$. Since $\sigma$ is almost surely positive, this convergence
is equivalent to $\sigma^2 - \sh^2 \to^p 0$.

The proof that $\sigma^2 - \sh^2 \to^p 0$ follows \citepos{JoD:00}
Theorem 2.1 closely.  We start by defining similar quantities to
theirs, borrowing their notation when possible to make the
similarities apparent. Let $b_T \equiv \lfloor \gamma/\delta \rfloor$,
define $\kernelB{x}$ as in Equation \eqref{eq:13}, and define the following
terms as in \citet{JoD:00}:
\begin{align*}
  \varianceTermI &\equiv
  \varianceTermIDefn,\\ \varianceTermII &\equiv \vtSum
  \varianceTermIIa\\& \quad \times \varianceTermIIb,\\
  \varianceTermIII &\equiv \vtSum \varianceTermIIIa\\
  &\quad \times \varianceTermIIb,\\
  \varianceTermIV &\equiv \vtSum \varianceTermIIIa \\
  &\quad\times \varianceTermIVb.
\end{align*}
These definitions give the inequalities
\begin{align*}
  \lVert \sh^2 - \sigma^2 \rVert_1 &
  \leq \lVert \sh^2 - \varianceTermI \rVert_1
  + \lVert \varianceTermI - \varianceTermII \rVert_1
  + \lVert \varianceTermII - \varianceTermIII \rVert_1
  + \lVert \varianceTermIII - \varianceTermIV \rVert_1\\ & \quad
  + \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1
  + \lVert \E_R\varianceTermIII - \E_R\varianceTermIV \rVert_1
  + \lVert \E_R\varianceTermII - \E_R\varianceTermIII \rVert_1\\ & \quad
  + \lVert \E_R\varianceTermI - \E_R\varianceTermII \rVert_1
  + \lVert \E_R \varianceTermI - \sigma^2 \rVert_1
  \\ &
  \leq  \lVert \sh^2 - \varianceTermI \rVert_1
  + 2(\lVert \varianceTermI - \varianceTermII \rVert_1
      + \lVert \varianceTermII - \varianceTermIII \rVert_1
      + \lVert \varianceTermIII - \varianceTermIV \rVert_1) \\
  & \quad + \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1
  + \lVert \E_R \varianceTermI - \sigma^2 \rVert_1.
\end{align*}
De Jong and Davidson (2000) prove that
\begin{equation*}
\lim_{\delta\to0} \limsup_{T\to\infty} \lVert \varianceTermI -
\varianceTermII\rVert_1 = 0,
\end{equation*}
\begin{equation*}
\lim_{\delta\to0} \limsup_{T\to\infty} \lVert \varianceTermII - \varianceTermIII
\rVert_1 = 0,
\end{equation*}
\begin{equation*}
\lim_{\delta\to0} \limsup_{T\to\infty} \lVert \varianceTermIII - \varianceTermIV
\rVert_1 = 0,
\end{equation*}
and
\begin{equation*}
\lim \lVert \E_R \varianceTermI - \sigma^2 \rVert_1 = 0.
\end{equation*}
Their proofs of these four convergence results use the fact that NED
functions of mixing processes are also mixingale processes and do not
use any other properties specific to NED processes, so their results
hold here as well.  We do need to modify their proofs that
\begin{equation*}
  \lVert \varianceTermIV - \E_R \varianceTermIV \rVert_1 \to 0
\end{equation*}
and
\begin{equation*}
  \lVert \sh^2 - \varianceTermI \rVert_1 \to 0
\end{equation*}
for all positive $\delta$, though, since those proofs exploit NED
properties. These results are presented as Lemmas~\ref{lem:a2}
and~\ref{lem:a6} respectively.  \qed

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "paper"
%%% TeX-command-extra-options: "-shell-escape"
%%% End:

### 2017-05-03 A5-theorem.tex
Split main paper.tex into several smaller files
This commit moves the content of the paper into several smaller
files that are \included; this allows us to use \includeonly
to minimize compilation time.

\subsection{Proof of Theorem \ref{res:oostest}}
Coverage of the confidence intervals is immediate from
Theorem~\ref{res-oost}, so we will present a proof of~\eqref{eq:23}.
By Lemma~\ref{res-convergence}, we know that $\E_R \oosA - \E_T \oosB
\to^p 0$, so
\begin{equation*}
  \Pr[\E_R \oosA \leq 0] - \Pr[\E_T \oosB \leq 0] \to 0.
\end{equation*}
Now we can use Lemma~\ref{lem-basic-coupling} to define $D_t^*$ as in
the proofs of Lemma~\ref{res-mixingale} and~\ref{res-convergence} so
that $\E_R D_t^* = \E_{t-l} D_t^*$ a.s. and
\[
\lVert D_t - D_t^* \rVert_2 \leq \couplingBound{l}
\]
and define $\oosA^* = P^{-1} \sum_{t=R+1}^{T-\h} D_t^*$. Then
\begin{equation*}
  \lVert \sqrt{P} \oosA - \sqrt{P} \oosA^* \rVert_2
  \leq P^{-1/2} \sum_{t=R+1}^{T-\h} \lVert \oosA - \oosA^* \rVert_2
  = o(1),
\end{equation*}
and, consequently, we have convergence in probability of the following
vectors:
\begin{equation*}
  (\sqrt{P} \oosA^*/\sigma,\ \E_R \oosA) -
  (\sqrt{P} \oosA/\sh,\ \E_T \oosB) \to^p 0,
\end{equation*}
where we are implicitly using consistency of $\sh^2$ for $\sigma^2$.
More importantly, this implies convergence in distribution of these
vectors, so
\begin{equation*}
  \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha
  \text{ and } \E_R \oosA \leq 0]
  - \Pr[\sqrt{P} \oosA / \sh > z_\alpha \text{ and }
  \E_T \oosB \leq 0] \to 0.
\end{equation*}

For large enough $T$, both $\Pr[\E_R \oosA \leq 0]$ and $\Pr[\E_T
\oosB \leq 0]$ are positive (the second by assumption, the first by
convergence to the second) so (for these $T$)
\begin{align}\label{eq:31}
  \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha
  \mid \E_R \oosA \leq 0] &=
  \frac{\Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha \text{ and }
    \E_R \oosA \leq 0]}{\Pr[\E_R \oosA \leq 0]}
\intertext{and}\label{eq:32}
  \Pr[\sqrt{P} \oosA / \sh > z_\alpha
  \mid \E_T \oosB \leq 0] &=
  \frac{\Pr[\sqrt{P} \oosA / \sh > z_\alpha \text{ and }
    \E_T \oosB \leq 0]}{\Pr[\E_T \oosB \leq 0]}
\end{align}
almost surely. Since the terms on the RHS of Equations~\eqref{eq:31}
and~\eqref{eq:32} converge to the same limit in probability, we have
\begin{equation*}
  \Pr[\sqrt{P} \oosA / \sh > z_\alpha  \mid \E_T \oosB \leq 0]
  - \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha \mid \E_R \oosA \leq 0]
  \to^p 0
\end{equation*}
and it suffices to show that
\begin{equation*}
  \plim \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha \mid \E_R \oosA \leq 0]
  \leq \alpha.
\end{equation*}

To establish this inequality, we have
\begin{align*}
  \Pr[\sqrt{P} \oosA^* / \sigma > z_\alpha \mid \E_R \oosA \leq 0]
  &\leq \Pr[\sqrt{P} (\oosA^* - \E_R \oosA) / \sigma > z_\alpha
  \mid \E_R \oosA \leq 0] \\
  &\leq \E\big(
  \Pr[\sqrt{P} (\oosA^* - \E_R \oosA) / \sigma > z_\alpha \mid \Fs_R]
  \mid \E_R \oosA \leq 0\big).
\end{align*}
By construction,
\begin{equation*}
  \Pr[\sqrt{P} (\oosA^* - \E_R \oosA) / \sigma > z_\alpha \mid \Fs_R]
  \to \alpha
\end{equation*}
since generated pseudo OOS observations in each $D_t^*$ are
independent of $\Fs_R$, completing the proof.
\qed

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "paper"
%%% TeX-command-extra-options: "-shell-escape"
%%% End:

### 2017-05-03 A6-theorem.tex
Split main paper.tex into several smaller files
This commit moves the content of the paper into several smaller
files that are \included; this allows us to use \includeonly
to minimize compilation time.

\subsection{Proof of Theorem~\ref{res:insample1}}

Let $(\e_{t+h}, x_{t}) \sim i.i.d.\ N(0,I)$ and let $\theta_1 = 0$.
For any $d \geq 0$, the event $\E_T \oosB = -d$ implies that
\begin{equation*}
  \E_T (y_{T+\h+1} - x_{1T+1}'\bh{1T})^2
  = \E_T (y_{T+\h+1} - x_{2T+1}'\bh{2T})^2 - d \quad a.s.
\end{equation*}
which can be expressed as
\begin{equation}\label{eq:34}
  d + \theta_2'M_2' M_2 \theta_2 + \bh{1T}'\bh{1T} - \bh{2T}'M_1'M_1\bh{2T}
  = (\bh{2T} - \theta_2)' M_2'M_2 (\bh{2T} - \theta_2) \quad a.s.
\end{equation}
$M_2 \bh{2T}$ is normally distributed conditional on $\bh{1T}$ and
$M_1 \bh{2T}$, and is distributed on the surface of the sphere defined
by~\eqref{eq:34} conditional on $\bh{1T}$, $M_1 \bh{2T}$, and the
event $\E_T \oosB = -d$.

Since $M_2 \bh{2T}$ is normal, this conditional distribution is
invariant to reflection across the axes defined by the eigenvectors of
its covariance matrix. So when $\theta_2$ lies outside the cylinder
that contains the acceptance region of $\Lambda$, i.e. when
$\theta_2'M_2' V_T M_2 \theta_2 > c$, we have\footnote{%
  To keep the notation in these equations manageable, define the
  information set
  $\Gs = \sigma(\E_T \oosB \leq 0,~ \theta_2'M_2' V_T M_2 \theta_2 >
  c)$.} %
\begin{align*}
  \Pr[ \bh{2T}' M_2' V_T M_2 \bh{2T} \leq c \mid \Gs]
  &= \E\Big( \Pr[ \bh{2T}'M_2' V_T M_2 \bh{2T} \leq c \mid \Gs,~\bh{1T},~M_1 \bh{2T}] \mid \Gs \Big) \\
  & < 1/2
\end{align*}
since the inner conditional probability is less than 1/2.

Now let $\delta > 0$ be an arbitrary but small constant, and choose
$\theta_2$ far enough from the origin to ensure that
\begin{equation*}
  \Pr[\theta_2'M_2' V_T M_2 \theta_2 \leq c] \leq \delta
\end{equation*}
for large enough $T$. Then
\begin{align*}
  \E(\Lambda \mid \E_T \oosB \leq 0) &
  \geq \Pr[\bh{2T}' M_2' V_T M_2 \bh{2T} > c \mid \E_T \oosB \leq 0] \\
  &= \Pr[\bh{2T}' M_2' V_T M_2 \bh{2T} > c \text{~~and~~}
  \theta_2'M_2' V_T M_2 \theta_2 > c \mid \E_T \oosB  \leq 0] \\
  & \quad + \Pr[\bh{2T}' V_T M_2 \bh{2T} > c \text{~~and~~ }
  \theta_2'M_2' V_T M_2 \theta_2 \leq c \mid \E_T \oosB \leq 0].
\end{align*}
The second term is nonnegative by design. By conditioning on
$\theta_2'M_2' V_T M_2 \theta_2 > c$ our earlier argument shows that
the first term is greater than or equal to $(1 - \delta) / 2$. Since
$\delta$ is arbitrarily small, this completes the proof.
\qed

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "paper"
%%% TeX-command-extra-options: "-shell-escape"
%%% End:

### 2017-05-03 A7-theorem.tex
Split main paper.tex into several smaller files
This commit moves the content of the paper into several smaller
files that are \included; this allows us to use \includeonly
to minimize compilation time.

\subsection{Proof of Theorem~\ref{res:insample2}}
As in the proof of Theorem~\ref{res:insample1}, let $(\e_{t+h}, x_{t})
\sim i.i.d.\ N(0,I)$ and let $\theta_1 = 0$. The event $\E_T \oosB
\geq 0$ implies that
\begin{equation*}
  \E_T (y_{T+\h+1} - x_{1T+1}'\bh{1T})^2
  \geq \E_T (y_{T+\h+1} - x_{2T+1}'\bh{2T})^2 \quad a.s.
\end{equation*}
which can be expressed as
\begin{equation}\label{eq:2}
  \theta_2'M_2 M_2'\theta_2 + \bh{1T}'\bh{1T} - \bh{2T}'M_1'M_1\bh{2T}
  \geq (\bh{2T} - \theta_2)' M_2'M_2 (\bh{2T} - \theta_2) \quad a.s.
\end{equation}
$M_2 \bh{2T}$ is normally distributed conditional on $\bh{1T}$ and
$M_1 \bh{2T}$, and is a.s. contained in the sphere defined
by~\eqref{eq:2} conditional on $\bh{1T}$, $M_1 \bh{2T}$, and the
event $\E_T \oosB \geq 0$.

Let $\delta$ be a small arbitrary constant, define $\theta^*$ as
\begin{gather*}
  \theta^* = \argmax_\theta \theta' M_2' M_2 \theta \\
  s.t.\quad \theta_2'M_2'M_2\theta_2 +  \bh{1T}'\bh{1T} - \bh{2T}'M_1'M_1\bh{2T} = (\theta - \theta_2)' M_2'M_2 (\theta - \theta_2)
\end{gather*}
($\theta^*$ is stochastic and depends on $\bh{1T}$ and $M_1 \bh{2T}$)
and choose $c$ so that
\begin{equation*}
  \Pr[ \theta^{* \prime} M_2 M_2 \theta^* > c] < \delta.
\end{equation*}

Then, we have for large enough $T$
\begin{align*}
  \E(\Lambda \mid \E_T \oosB \geq 0) &\leq
  \Pr[\bh{2T}'M_2'M_2\bh{2T} > c \mid \E_T \oosB \geq 0) \\
  &\leq \delta
\end{align*}
Since $\delta$ is arbitrarily close to zero, this completes the proof.\qed

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "paper"
%%% TeX-command-extra-options: "-shell-escape"
%%% End:

### 2017-05-03 C-figures.tex
Split main paper.tex into several smaller files
This commit moves the content of the paper into several smaller
files that are \included; this allows us to use \includeonly
to minimize compilation time.

\markright{}

\begin{figure}\centering
  {\large Coverage of DMW OOS interval for $\E_R\oosA$ in simulations}
  \tryinput{floats/mc-interval-testerror1.tex}
  \caption{Simulated coverage of $\E_R \oosA$ at 90\% confidence using
    a one-sided interval based on the DMW \oost\ test, plotted as a
    function of the fraction of observations used in the test sample,
    $P/T$. The solid horizontal line denotes the intervals' nominal
    coverage.}
 \label{fig:interval-R}
\end{figure}
\clearpage

\begin{figure}\centering
  {\large Coverage of DMW OOS interval for $\E_T\oosB$ in simulations}
  \tryinput{floats/mc-interval-generror1.tex}
  \caption{Simulated coverage of $\E_T \oosB$ at 90\% confidence using
    a one-sided interval based on the DMW \oost\ test, plotted as a
    function of the fraction of observations used in the test sample,
    $P/T$.  The solid horizontal line denotes the intervals' nominal
    coverage.}
  \label{fig:interval-T}
\end{figure}
\clearpage

\begin{figure}\centering
  {\large Size of DMW \oost\ test in simulations}
  \tryinput{floats/mc-dmwsize.tex}
  \caption{Simulated rejection probabilities for the DMW \oost\ test
    under the null hypothesis that the benchmark model will forecast
    better, $\E_T \oosB \leq 0$. The nominal size is 10\% and is
    marked with a solid horizontal line. Values greater than 10\%
    indicate that the test rejects the benchmark model too often. See
    Section~\ref{sec:simulation-design} for a discussion of the
    simulation design.}
  \label{fig:ttest-size}
\end{figure}
\clearpage

\begin{figure}\centering
  {\large Size of Clark-West OOS test in simulations}
  \tryinput{floats/mc-clarkwestsize.tex}
  \caption{Simulated rejection probabilities for Clark and West's
    (2006, 2007) OOS test statistic under the null hypothesis that the
    benchmark will forecast better, $\E_T \oosB \leq 0$. The nominal
    size is 10\% and is marked with a solid horizontal line. Values
    greater than 10\% indicate that the test rejects the benchmark
    model too often. See Section~\ref{sec:simulation-design} for a
    discussion of the simulation design.}
   \label{fig:clarkwest}
\end{figure}
\clearpage

\begin{figure}\centering
  {\large Size of McCracken \oost\ test in simulations}
  \tryinput{floats/mc-mccrackensize.tex}
  \caption{Simulated rejection probabilities for McCracken's (2007)
    \oost\ test under the null hypothesis that the benchmark model is
    more accurate, $\E_T \oosB \leq 0$. Nominal size is 10\% and is
    marked with a solid horizontal line. Values greater than 10\%
    indicate that the test rejects the benchmark model too often. See
    Section~\ref{sec:simulation-design} for a discussion of the
    simulation design.}
  \label{fig:mccracken}
\end{figure}
\clearpage

\begin{figure}\centering
  {\large Power of DMW \oost\ test in simulations}
  \tryinput{floats/mc-dmwpower.tex}
  \caption{Simulated rejection probabilities for the DMW \oost\ test
    under the alternative that the benchmark model is less accurate,
    $\E_T \oosB > 0$. Nominal size is 10\% and is marked with a solid
    horizontal line. Values greater than 10\% indicate that the test
    rejects the benchmark model too often. See
    Section~\ref{sec:simulation-design} for a discussion of the
    simulation design.}
  \label{fig:ttest-power}
\end{figure}
\clearpage

\begin{figure}
\centering
\large{Difference in OOS MSE of Prevailing Mean and\\ Kitchen
    Sink Models of Equity Premium (OLS)}
\tryinput{floats/empirics-oos-mse-1.tex}
\tryinput{floats/empirics-oos-mse-1b.tex}
\caption{OOS difference in the MSE
  of the prevailing mean benchmark and the kitchen sink model as a
  function of the test sample size, $R$.  Both models forecast the
  equity premium using annual data from 1928--2008.  The solid line
  gives the OOS average, and the shaded region indicates the
  one-sided 95\% confidence interval implied by the
  DMW test.  The bottom panel is a detailed view of the top
  panel for $R \geq 50$.}
\label{fig:empirics1}
\end{figure}
\clearpage

\begin{figure}
\centering
\large{Difference in OOS MSE of Prevailing Mean and\\ Kitchen
    Sink Models of Equity Premium (CT)}
\tryinput{floats/empirics-oos-mse-2.tex}
\tryinput{floats/empirics-oos-mse-2b.tex}
\caption{OOS difference in the MSE
  of the prevailing mean benchmark and the kitchen sink model as a
  function of the test sample size, $R$.  Both models forecast the
  equity premium using annual data from 1928--2008.  The solid line
  gives the OOS average, and the shaded region indicates the
  one-sided 95\% confidence interval implied by the
  DMW test.  The bottom panel is a detailed view of the top
  panel for $R \geq 50$.}
\label{fig:empirics2}
\end{figure}
\clearpage

\begin{figure}
\centering
\large{OOS MSE of Individual Forecasts of Equity Premium}
\tryinput{floats/empirics-oos-ind-ks.tex}
\tryinput{floats/empirics-oos-ind-pm.tex}
\caption{OOS MSE of the Prevailing Mean (PM) and
    Kitchen Sink (KS) models for equity premium prediction as
    a function of the size of the training sample, $R$.  Please note
    that the vertical scales are different in the two plots.}
\label{fig:empirics3}
\end{figure}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "paper"
%%% TeX-command-extra-options: "-shell-escape"
%%% End:

### 2017-05-03 D1-example.tex
[#40/move] Revise the examples from the supplemental appendix
This commit changes some of the wording around the example
discussed in the supplemental appendix.

@@
 
-\section{An extended simple example}
+\section{Extended simple example}
 \label{sec:example}
 
-This section illustrates the previous theoretical results with a
-concrete example. Let $L(e) = e^2$ and $h = 1$. Suppose that the benchmark is
-nested in the alternative and $(x_{2t}, \e_{2,t+1}) \sim i.i.d.\
-N(0,I)$, and let $y_{t+1} = x_{2t}'\theta_2 + \e_{2,t+1}$
-be the DGP. Also assume that $K_2/T \to c_2$ and $K_1 / T \to c_1 <
-c_2$.
+Throughout this section, let the DGP and alternative model both be
+\[
+  y_{t+1} = x_{2t}'\theta_2 + \e_{2,t+1}
+\]
+with $(x_{2t}, \e_{2,t+1}) \sim i.i.d.\ N(0,I)$ and assume that this
+model nests the benchmark model. Also let $L(e) = e^2$
+and $h = 1$; assume that $K_1/T \to c_1$ and $K_2/T \to c_t$; and
+define
+\[
+  \sh^2 = (1/P) \oosSum{t}{1} (D_t - \oosA)^2.
+\]
 
-The first part of this section shows how the assumptions in
-Section~\ref{sec:asmp} are satisfied and the second part
-demonstrates asymptotic normality of the DMW \oost\ test. The third
-part explicitly shows that $\E_R \oosA$ converges to $\E_T \oosB$ only
-when the test sample is small. And the last part demonstrates that the
-$F$-test does not indicate which model will be more
-accurate in the future, even in this simple example.
+The first
+subsection shows that the DMW \oost\ test is asymptotically normal. The
+second directly shows that $\E_R \oosA$ converges to
+$\E_T \oosB$ only when the test sample is small. And the last
+subsection demonstrates that the $F$-test does not indicate which
+model will be more accurate in the future, even when its finite sample
+distribution is known.
 
-\subsection{Fulfillment of Assumptions 1--5}
+\subsection{Asymptotic normality of the OOS average (Lemma 1)}
 
-We will go through the assumptions one by one. The first is
-a condition on the dependence and moments of the process. Since the
-DGP is i.i.d. Normal, these conditions are satisfied trivially.
+This subsection proves directly that the DMW $t$-test is
+asymptotically normal and can be seen as a special case of
+Lemma~\ref{res-mixingale}. Since the underlying observations are
+independent, we can use asymptotic arguments for MDSes here instead of
+those for mixingales.  This substitution simplifies the proof
+considerably and highlights the role of the conditional expectation
+and conditional variance in this setting.  In particular, we will show
+that
+\begin{equation}
+  \sh^2 / \var_R(\sqrt{P} \oosA) \to^p 1
+\end{equation}
+and
+\begin{equation}
+  \sqrt{P} (\oosA - \E_R \oosA) / \sh \to^d N(0,1).
+\end{equation}
 
-Assumption~\ref{asmp-2} deals with the design matrix. In this example,
-we directly assume that $K_2$ and $K_1$ grow at the correct rates so
-the the assumption is satisfied. The variance of $y_{t+1}$ given
-$\Fs_t$ is simply the unconditional variance of $\e_{2,t+1}$, which is
-1; and the eigenvalues of $\E x_{2t} x_{2t}$ all equal 1 as well; and
-so they are all uniformly positive and finite as required.
-
-Assumption~\ref{asmp-2} also requires the eigenvalues of $S^{-1}
-X_{iS}'X_{iS}$ to be positive and finite, and for the largest
-eigenvalue of $S^{-1} X_{iS}'X_{iS}$ to be bounded in $L_3$.  These
-results follow from developments in random matrix theory.
-\citet{Gem:80} establishes that the largest eigenvalue of
-$X_{iS}'X_{iS}$ is of order $S + K_i$ and \citet{Joh:01} shows that it
-converges in distribution to the Tracy-Widom law of order 1
-\citep{TrW:96}, which has finite 3rd moments. \citet{Sil:85} and
-\citet{BFP:98} prove similar results for the smallest eigenvalue.
-Assumption~\ref{asmp-2} also requires the largest eigenvalue of
-$(X_{iS}'X_{iS})^{-1}$ be bounded in $L_3$; this should follow from a
-similar argument, but we are unaware of any papers that explicitly
-derive moments for this eigenvalue.
-
-For the conditional expectation of %
-$\sum_{s,t=U}^{V-1} \e_{i,t+1} \e_{i,s+1} x_{i,s} x_{i,t}'$,
-independence implies that
-\begin{equation*}
-  \E\Big(
-  \sum_{s,t=U}^{V-1} \e_{i,s+1} \e_{i,t+1} x_{is}x_{it}'
-  \mBig
-  x_{i1},\dots,x_{i,U-1};
-  \sum_{s=U}^{V-1} x_{is} x_{is}';
-  x_{i,V},\dots,x_{i,T-1}
-  \Big)
-  = \sum_{s=U}^{V-1} x_{is} x_{is}'.
-\end{equation*}
-The largest eigenvalue of this last matrix is of order $K_i + V - U$,
-as discussed, and it has at most $V - U$ nonzero eigenvalues,
-ensuring that both~\eqref{eq:28} and~\eqref{eq:8} hold.
-
-Assumption~\ref{asmp-3} restricts the loss function and the realized
-OOS loss. In this example, we have
-\begin{equation*}
-  D_t^* =^d D_t = (e_{2,t+1} + x_{2t}'\theta_2 - x_{1t}'\bh{1t})^2
-  - (e_{2,t+1} + x_{2t}'(\theta_2 - \bh{2t}))^2
-\end{equation*}
-which has bounded $\rho$th moments by construction. The loss function
-is differentiable and $L'(e) = 2 e$, so \eqref{eq:29} holds as well.
-
-Finally, Assumption~\ref{asmp-4} deals with the choice of test and
-training sample and holds automatically. And Assumption~\ref{asmp-5}
-requires the kernel of the HAC variance estimator to be continuous at
-zero; it is straightforward to construct an estimator that satisfies
-this condition. However, in this section we will use the estimator
-\begin{equation*}
-  \sh^2 = \frac{1}{P} \sum_{t=R+1}^{T-1} (D_t - \oosA)^2
-\end{equation*}
-which does not satisfy Assumption~\ref{asmp-5} but nevertheless is
-consistent for the conditional variance of $\oosA$ because the
-underlying observations are independent.
-
-\subsection{Asymptotic normality of the OOS average, Lemma 1}
-
-This section walks through Lemma 1's CLT. Since the observations in
-this example are i.i.d., we do not need to use mixingale theory to
-derive the results, but the OOS process is still affected by the
-estimation error in $\bh{1t}$ and $\bh{2t}$ and has a high degree of
-dependence. This dependence makes the OOS process an MDS, and MDS
-asymptotic theory replaces mixingale theory in this example.
-
-By construction, we have
-\begin{equation*}
+By construction,
+\begin{equation}\label{eq:3}
   D_t =
@@
     - (x_{2t}'\theta_2 - x_{2t}'\bh{2R})^2
-    & \text{if } t < T \\
+    & \text{if\ } t < T \\
     2 \e_{t+1} (x_{2t}'\bh{2T} - x_{1t}'\bh{1T})
@@
     - (x_{2t}'\theta_2 - x_{2t}'\bh{2T})^2
-    & \text{if } t > T
+    & \text{if\ } t \geq T.
   \end{cases}
+\end{equation}
+Since $(y_{t+1}, x_{2t})$ is independent of $\bh{R}$ and $\bh{t}$,
+\eqref{eq:3} ensures that
+\begin{equation*}
+  D_t - \E_{t-1} D_t = D_t - \E_R D_t
 \end{equation*}
-and so we can explicitly derive the components of
-Lemma~\ref{res-mixingale}. First,
-\begin{multline*}
-  D_t - \E_R D_t
-  = 2 \e_{t+1} (x_{2t}'\bh{2R} - x_{1t}'\bh{1R})
-  + \Big\{(x_{2t}'\theta_2 - x_{1t}'\bh{1R})^2
-          - \E_R (x_{2t}'\theta_2 - x_{1t}'\bh{1R})^2 \Big\} \\
-  - \Big\{(x_{2t}'\theta_2 - x_{2t}'\bh{2R})^2
-          - \E_R (x_{2t}'\theta_2 - x_{2t}'\bh{2R})^2 \Big\}
-\end{multline*}
-for $t < T$. Since the underlying observations are i.i.d., $\E_{t-1}
-D_t = \E_R D_t$ a.s.\ and consequently $\{D_t - \E_R D_t, \Fs_{t};
-t=R+1,\dots,T-1\}$ is an MDS.
+almost surely and, consequently, that
+$\{D_t - \E_R D_t, \Fs_{t}; t=R+1,\dots,T-1\}$ is an MDS.
 
-Although transformations of $D_t - \E_R D_t$ will obviously not be
-MDSes in general, it should be clear that transformations of $D_t$
-will be MDSes after subtracting their conditional mean; i.e.
+Moreover, independence also ensures that
+$\{g(D_t) - \E_R g(D_t); \Fs_t; t = R+1,\dots,T-1\}$
+is an MDS for any measurable $g$ as long as
+$g(D_t)$ has finite mean.
+As a result, $\oosA$ and $(1/P) \sum_{t=R+1}^{T-1} D_t^2$ both obey
+MDS LLNs: $\oosA \to^p \E_R \oosA$ and
 \begin{equation*}
-  \{g(D_t) - \E_R g(D_t); \Fs_t; t = R+1,\dots,T-1\}
+  (1/P) \sum_{t=R+1}^{T-1} (D_t^2 - \E_R D_t^2) \to^p 0,
 \end{equation*}
-is an MDS as long as
-$g(D_t)$ has finite mean, but $g(D_t - \E_R D_t)$ is not. This MDS
-result holds because $x_t$ and $y_{t+1}$ are independent of $\bh{1R}$
-and $\bh{2R}$, so
-\begin{equation*}\begin{split}
-  \E_R g(D_t)
-  &= \int g\Big((x_1'\bh{1R})^2 - (x_2'\bh{2R})^2
-       + 2 y (x'\bh{2R} - x'\bh{1R})\Big) \, f(y, x) \, dx \, dy \\
-  &= \E_{t-1} g(D_t)
-\end{split}\end{equation*}
-a.s., where $f$ is the density of $(y_{t+1}, x_{2t})$ and $x_1$
-denotes the first $K_1$ elements of $x$. This result parallels our
-results for mixingales in the general case.
+implying that $\sh^2/\var_R(\sqrt{P} \oosA) \to^p 0$.
+Asymptotic normality,
+\begin{equation*}
+  \sqrt{P} (\oosA - \E_R \oosA )/\sh \to N(0,1),
+\end{equation*}
+holds by the MDS CLT.
 
-As a result, $\oosA$ and $(1/P) \sum_{t=R+1}^{T-1} D_t^2$ both obey
-LLNs: $\oosA \to^p \E_R \oosA$ and
-\begin{equation*}
-  (1/P) \sum_{t=R+1}^{T-1} D_t^2 \to^p \E_R D_T^2.
-\end{equation*}
-Moreover, these convergence results imply that $\sh^2 - \var_R
-\sqrt{P} \oosA \to^p 0$. And so
-\begin{equation*}
-  \sqrt{P} \oosA/\sh \to N(0,1)
-\end{equation*}
-by the MDS CLT.
+\subsection{Convergence of $\E_R \oosA$ to the generalization error}
 
-\subsection{Convergence of $\E_R \oosA$ to $\E_T \oosB$, Lemma 2}
-
-This section works through Lemma~\ref{res-convergence}. In this
-example, the difference between $\E_R \oosA$ and $\E_T \oosB$ equals
-\begin{equation*}
-  \begin{split}
-    \E_R \oosA - \E_T \oosB &= \Big\{(\bh{1R} - \theta_1)'(\bh{1R} -
-    \theta_1) -
-    (\bh{2R} - \theta_2)'(\bh{2R} - \theta_2)\Big\} \\
+This subsection directly calculates the rate of convergence for
+$\E_R \oosA - \E_T \oosB$. From \eqref{eq:3}, this difference can
+be expressed as
+\begin{align}
+    \E_R \oosA - \E_T \oosB &= \Big\{(\bh{1R} - \theta_1)'(\bh{1R} - \theta_1) -
+    (\bh{2R} - \theta_2)'(\bh{2R} - \theta_2)\Big\} \notag \\
     & \quad - \Big\{(\bh{1T} - \theta_1)'(\bh{1T} - \theta_1) -
     (\bh{2T} - \theta_2)'(\bh{2T} - \theta_2)\Big\} \\
-    &\begin{split}
-      =\ep{T}'\Big\{
-      & \tilde{X}_{1R}(X_{1R}'X_{1R})^{-2} \tilde{X}_{1R}'
-      - X_{1T}(X_{1T}'X_{1T})^{-2} X_{1T}' \\
-      & - \tilde{X}_{2R}(X_{2R}'X_{2R})^{-2} \tilde{X}_{2R}'
+    &=\ep{T}'\Big\{
+      \tilde{X}_{1R}(X_{1R}'X_{1R})^{-2} \tilde{X}_{1R}'
+      - X_{1T}(X_{1T}'X_{1T})^{-2} X_{1T}' \notag \\
+      & \quad  - \tilde{X}_{2R}(X_{2R}'X_{2R})^{-2} \tilde{X}_{2R}'
       + X_{2T}(X_{2T}'X_{2T})^{-2} X_{2T}'
-      \Big\}\ep{T}.
-    \end{split}
-  \end{split}
-\end{equation*}
-with $\tilde{X}_{iR}$ the $T \times K_i$ matrix $[X_{iR}'\ 0]'$. This
-last term is a quadratic form and the regressors and errors are
-assumed to be normal, so we can find the rate that the difference
-converges to zero in probability by calculating its first two moments.
+      \Big\}\ep{T} \label{eq:4}
+\end{align}
+with $\tilde{X}_{iR}$ the $T \times K_2$ matrix $[X_{iR}'\ 0]'$.  We
+can directly calculate the rate that the first two moments of the RHS
+of~\eqref{eq:4} converge to zero since~\eqref{eq:4} is a quadratic
+form and all of the underlying random variables are normal.
 
-The mean difference is
+The order of the expected value of this difference is
 \begin{equation*}
@@
         - X_{iT}(X_{iT}'X_{iT})^{-2} X_{iT} \big\} \Big) \\
-      &=O\Big(\max_i \tr \big\{\E (X_{1R}'X_{1R})^{-1}
-         - \E (X_{1T}'X_{1T})^{-1} \big\}\Big) \\
+      &=O\Big(\max_i \tr \big\{\E (X_{iR}'X_{iR})^{-1}
+         - \E (X_{iT}'X_{iT})^{-1} \big\}\Big) \\
       &=O( K_1 P / (R-K_1)(T-K_1)) \\
-      &=O(P/T)
+      &=O(P/T).
     \end{split}
 \end{equation*}
-The first equality follows from the expectation of a quadratic form,
-the second from routine manipulations of the trace operator, and the
-third from the moments of the inverse Wishart distribution.
-
-Similarly, the variance of the difference is
+The first equality follows from well-known formulas for the
+expectation of a quadratic form, the second from routine manipulations
+of the trace operator, and the third from the moments of the inverse
+Wishart distribution.
+Similarly, the order of the variance of the difference is
 \begin{align*}
@@
 \end{align*}
-So, in this example, $P^{1/2}(\E_R \oosA - \E_T \oosB) \to^p 0$
-if $P^3/T^2 \to 0$, which is slightly weaker than the general
-requirement that $P^2/T \to 0$.  If $\lim P^3/T^2 > 0$ the OOS average
-still obeys the MDS CLT, but it is not centered correctly at $\E_T
-\oosB$.
+Consequently, $P^{1/2}(\E_R \oosA - \E_T \oosB) \to^p 0$ if
+$P^3/T^2 \to 0$ for this DGP, which is slightly weaker than the
+general requirement for Lemma~\ref{res-convergence} that
+$P^2/T \to 0$. When this condition is violated, i.e. if
+$\lim P^3/T^2 > 0$, the results from the previous subsection continue
+to hold and the OOS average still obeys the MDS CLT. However, it is
+centered on $\E_R \oosA$ and not $\E_T \oosB$.
 
@@
 
-This part illustrates the behavior of full-sample statistics in our
-simple example. To simplify the presentation even more, assume that
-the full-sample design matrix is orthogonal in-sample, not just in
-population, so $X_{2T}'X_{2T} = T \cdot I_{K_2 \times K_2}$, and again
-let $M_1$ and $M_2$ be the selection matrices for the first $K_1$ and
-the last $K_2-K_1$ elements of $\theta_2$. In this example,
+This subsection shows that, in this example, the F-test fails to test
+hypotheses about the generalization error.
+To further simplify the presentation, assume that the full-sample
+design matrix is orthogonal in-sample, not just in population, so
+$X_{2T}'X_{2T} = T \cdot I_{K_2 \times K_2}$, and let $M_1$ and
+$M_2$ be the selection matrices for the first $K_1$ and the last
+$K_2-K_1$ elements of $\theta_2$.
+
+Under these additional assumptions,
+$M_2 \bh{2T} \sim N(M_2 \theta_2, (1/T) \, I_{K_2-K_1})$. More
+importantly, given $\E_T \oosB = - c$ for any
+$c > -\theta_2'M_2'M_2\theta_2$, the estimator $M_2 \bh{2T}$ is
+distributed uniformly on the cylinder in $\Re^k$ defined by
 \begin{equation*}
-  M_2 \bh{2T} \sim
-  N(M_2 \theta_2, (1/T) \, I_{K_2-K_1})
+  \{\bh{2T} : (M_2 \bh{2T} - M_2 \theta_2)'(M_2 \bh{2T} - M_2 \theta_2) =
+  \theta_2'M_2' M_2 \theta_2 + c\},
 \end{equation*}
-and, conditional on $\E_T \oosB = 0$, the density of $M_2 \bh{2T}$
-concentrates uniformly on the surface of the sphere centered at $M_2
-\theta_2$ and passing through the origin:
+which is centered at $M_2\theta_2$. When $\E_T \oosB = 0$ this
+cylinder passes through the origin.  Values of $\bh{2T}$ that satisfy
+with the hypothesis $\E_T \oosB \leq 0$, i.e. that the smaller model
+is more accurate than the larger model, lie outside that cylinder and
+values of $\bh{2T}$ satisfying $\E_T \oosB > 0$ lie inside that
+cylinder.
+
+The F statistic for testing the null hypothesis $M_2'\theta = \eta$
+can be expressed as
 \begin{equation*}
-  (M_2 \bh{2T} - M_2 \theta_2)'(M_2 \bh{2T} - M_2 \theta_2) =
-  \theta_2'M_2' M_2 \theta_2.
+  F = \tfrac{T}{s^2 (K_2 - K_1)} (\bh{2T}' M_2' - \eta') (M_2 \bh{2T} - \eta)
 \end{equation*}
-To see intuitively that it must pass through the origin, note that the
-two models will give identical forecasts when $\bh{2T} = 0$ since the
-regressors are orthogonal. (Identical forecasts obviously have the
-same MSE.)
-
-This region is a cylinder in the original space, $\Re^{K_2}$.  We can
-also represent the null $\E_T \oosB \leq 0$ by conditioning on $\E_T
-\oosB = -d$ for a fixed positive constant $c$. In that case, the
-density of $M_2 \bh{2T}$ concentrates on the sphere
-\begin{equation*}
-  (M_2 \bh{2T} - M_2 \theta_2)'(M_2 \bh{2T} - M_2 \theta_2) =
-  \theta_2'M_2' M_2 \theta_2 + d
-\end{equation*}
-which has the same center but larger radius.
-
-For the $F$-test we have, as before,
-\begin{equation*}
-  F = \tfrac{T}{s^2 (K_2 - K_1)} \bh{2T}' M_2' M_2 \bh{2T}.
-\end{equation*}
-We know that $\sqrt{T}(F - 1)$ is asymptotically normal since its
-numerator is Chi-squared with $K_2-K_1$ degrees of freedom and obeys a
-CLT.  The test accepts if
+and $\sqrt{T}(F - 1)$ is asymptotically normal---its numerator is
+Chi-squared with $K_2-K_1$ degrees of freedom and obeys the CLT and
+its denominator obeys the LLN.
+Consequently, this test will fail to reject the null hypothesis that
+$M_2 \theta_2 = 0$ when it satisfies the inequality
 \begin{equation}\label{eq:26}
@@
 where $\delta$ is chosen to determine the size of the test. In other
-words, the test accepts if $M_2 \bh{2T}$ falls in the sphere centered
-at the origin with radius $s ((K_2 - K_1) / T)^{1/2} +
-O_p(1/\sqrt{T})$.
+words, the test fails to reject its implied null hypotheses whenever
+$M_2 \bh{2T}$ falls in the sphere centered at the origin with radius
+$s ((K_2 - K_1) / T)^{1/2} + O_p(1/\sqrt{T})$.
+
+Consequently, when $M_2\theta_2$ is in the rejection region of the
+F-test, the probability that the test will reject given
+$\E_T \oosB \leq 0$ is necessarily greater than 50\%, with the
+probability increasing as the length of $M_2\theta_2$ increases. So
+$\theta_2$ can be chosen to make the rejection probability given
+$\E_T \oosB \leq 0$ arbitrarily close to 1.
+
+Similarly, when $2 M_2\theta_2$ is in the F-test's acceptance region,
+then the acceptance region contains all of the parameter estimates
+satisfying $\E_T \oosB > 0$---i.e. all of the parameter estimates that
+would make the larger model forecast more accurately. So $\theta_2$
+can also be chosen to make the conditional rejection probability given
+$\E_T \oosB > 0$ have any value between $0$ and the nominal size of
+the test.
 
 \input{floats/circles}
-\begin{figure}
+\begin{figure}[t!]
   \centering
@@
 
-This is perhaps best illustrated with a picture.
-Figure~\ref{fig:rreject} plots these quantities when $K_2 - K_1 =
-2$. The circle centered at the origin plots the threshold for the
+These relationships are perhaps best illustrated with a picture.
+Figure~\ref{fig:rreject} (a) plots these quantities when $K_2 - K_1 =
+2$. The black circle centered at the origin plots the threshold for the
 $F$-test; when $M_2 \bh{iT}$ falls outside this circle, the $F$-test
-rejects. The circle centered at $M_2 \theta_2$ plots the set of points
-for which $\E_T \oosB = 0$. The shaded region in
+rejects. The black circle centered at $M_2 \theta_2$ plots the set of points
+for which $\E_T \oosB = 0$. The lighter shaded region in
 Figure~\ref{fig:rreject}~(a) plots the rejection region given $\E_T
-\oosB \leq 0$ and the shaded region in Figure~\ref{fig:rreject}~(b)
-plots the acceptance region given $\E_T \oosB \leq 0$.
+\oosB \leq 0$ and the darker shaded region in Figure~\ref{fig:rreject}~(b)
+plots the acceptance region given $\E_T \oosB \leq 0$. The dark
+gray lines in each figure represent contour lines for the sampling
+density of $M_2 \bh{2T}$ given rejection or acceptance.
 
@@
 \end{equation*}
-so the center of the conditional distribution of $\bh{2T}$ given $\E_T
-\oosB \leq 0$ is outside the acceptance region of the $F$-test. When
-this is the case, the conditional probability that $\bh{2T}$ falls in
-the rejection region is less than 1/2, since $M_2 \bh{2T}$ is
-uniformly distributed on the cylinder
-\begin{equation*}
-  (M_2 \bh{2T} - M_2 \theta_2)'(M_2 \bh{2T} - M_2 \theta_2) =
-  \theta_2'M_2' M_2 \theta_2 + d
-\end{equation*}
-for some positive $d$.
+so the center of the conditional distribution of $\bh{2T}$ given
+$\E_T \oosB \leq 0$ is outside the acceptance region of the
+$F$-test. As can be seen from the figure, the F-test has a rejection
+probability greater than 50\% when $\E_T \oosB \leq 0$ holds, since
+most of the density of $M_2 \bh{T2}$ is not close to the origin. By
+moving $M_2 \theta$ to other points outside the acceptance region of
+the F-test, we can make its rejection probability under this null
+arbitrarily close to one. Similarly, by moving $M_2 \theta_2$ to
+points inside the F-test's acceptance region, we can make its
+power to reject the hypothesis $\E_T \oosB \leq 0$ when it is
+false arbitrarily close to zero.
 
-The AIC behaves essentially the same way. For the BIC, the radius of
-the cylinder centered at the origin increases with $T$ and eventually
-encompasses the cylinder centered at $M_2 \theta_2$, so it never
-selects the alternative once $T$ is large enough.
+In summary, the F-test can not be used for inference on the models'
+forecasting performance. It does not control size for the null
+$\E_T \oosB \leq 0$ and it has arbitrarily low power to detect the
+alternative $\E_T \oosB > 0$ for some parameter values. Full-sample
+model selection statistics like the AIC and BIC, which add or discard
+covariates based on how far their coefficient estimates are from zero,
+behave similarly.
 

### 2017-05-05 D1-example.tex
[#40/move] Change graphics reflecting in-sample rejection

@@
     generalization error for the models discussed in Section
-    \ref{sec:insample}.  The smaller model has no estimated parameters
-    and the larger has two coefficients.  The shaded regions in
-    Figures (a) and (b) show the rejection region and the acceptance
-    region respectively of the full-sample test given $\E_T \oosB \leq
-    0$. Here $e_1 = (1,0)$ and $e_2 = (0,1)$ are the first and second
+    \ref{sec:insample}.
+    In Figure (a), the union of
+    the two shaded areas shows the parameter estimates consistent
+    with the null hypothesis $\E_T \oosB \leq 0$ and in Figure (b), the union of
+    the two shaded areas shows the parameter estimates consistent
+    with the alternative hypothesis $\E_T \oosB > 0$. The
+    dark gray circles are contour lines for the sampling density of
+    $M_2 \bh{2T}$, at increments of 0.01. In both figures, the lighter
+    region shows the rejection region of the F-test and the darker
+    region shows its acceptance region.
+    Here $e_1 = (1,0)$ and $e_2 = (0,1)$ are the first and second
     selection vectors, so the horizontal axes represent changes in the
